### 2023-11-02 Scripts/Manuscript/manuscript.Rmd
pasted the personal version of the worcs template into the project.

---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "Cas Goos"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Professor Cobbenhagenlaan 125, 5037 DB, Tilburg, The Netherlands"
    email         : "casgoos99@gmail.com"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Second Author"
    affiliation   : "1,2"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Tilburg University"
  - id            : "2"
    institution   : "Other UNI"

authornote: |
  1 Department of Methodology and Statistics, Tilburg School of Social and Behavioral Sciences, Tilburg University, Tilburg, NL. 
  complete departmental affiliations: Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib", "references.bib"]

floatsintext      : no
linenumbers       : no
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
knit              : worcs::cite_all
---

```{r setup, include = FALSE}
# loading R libraries
library("papaja")
library("worcs")

# loading source script
source(file = "../source_script.R")

# Code below loads the processed data. The raw data was prepared for analysis in 'prepare_data.R.
load_data(worcs_directory = "../../Data/AnalysisData")

# creates a reference list for all used R packages and the installed R version (does not include Rstudio)
r_refs("r-references.bib")
```

This manuscript uses the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCSWorkflowOpen2021] to ensure reproducibility and transparency. All code <!--and data--> are available at <https://github.com/CasGoos/WORCSPersonalTemplate.git>.

This is an example of a non-essential citation [\@ @vanlissaWORCSWorkflowOpen2021]. If you change the rendering function to `worcs::cite_essential`, it will be removed.

<!--The function below inserts a notification if the manuscript is knit using synthetic data. Make sure to insert it after load_data().-->

`r notify_synthetic()`

```{r analysis-preferences}
# Seed for random number generation
set.seed(31102023)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction

## Description

```{=html}
<!-- Please give a brief description of your study, including some background, the purpose of the of the study, or broad research questions. The description should be no longer than the length of an abstract. It can give some context for the proposed study, but great detail is not needed here for your preregistration.

Example: Though there is strong evidence to suggest that sugar affects taste preferences, the effect has never been demonstrated in brownies. Therefore, we will measure taste preference for four different levels of sugar concentration in a standard brownie recipe to determine if the effect exists in this pastry. -->
```
### Key Concepts

### Background Overview

### Contribution & Relevance

## Aims

```{=html}
<!-- List specific, concise, and testable hypotheses. Please state if the hypotheses are directional or non-directional. If directional, state the direction. A predicted effect is also appropriate here. If a specific interaction or moderation is important to your research, you can list that as a separate hypothesis.

Example: If taste affects preference, then mean preference indices will be higher with higher concentrations of sugar. -->
```
### Research Questions

### Hypotheses

# Methods

## Study Design

```{=html}
<!-- Describe your study design. Examples include two-group, factorial, randomized block, and repeated measures. Is it a between (unpaired), within-subject (paired), or mixed design? Describe any counterbalancing required. Typical study designs for observation studies include cohort, cross sectional, and case-control studies.

This question has a variety of possible answers. The key is for a researcher to be as detailed as is necessary given the specifics of their design. Be careful to determine if every parameter has been specified in the description of the study design. There may be some overlap between this question and the following questions. That is OK, as long as sufficient detail is given in one of the areas to provide all of the requested information. For example, if the study design describes a complete factorial, 2 X 3 design and the treatments and levels are specified previously, you do not have to repeat that information.

Example: We have a between subjects design with 1 factor (sugar by mass) with 4 levels. -->
```
### Study Type

**Experiment**. A researcher randomly assigns treatments to study subjects, this includes field or lab experiments. This is also known as an intervention experiment and includes randomized controlled trials.

**Observational Study**. Data is collected from study subjects that are not randomly assigned to a treatment. This includes surveys, natural experiments, and regression discontinuity designs.

**Meta-Analysis**. A systematic review of published studies.

**Other**. Please explain.

### Materials

What materials were used (with reference)

### Blinding

<!-- Blinding describes who is aware of the experimental manipulations within a study. Select all that apply. Is there any additional blinding in this study? -->

No blinding is involved in this study.

For studies that involve human subjects, they will not know the treatment group to which they have been assigned.

Personnel who interact directly with the study subjects (either human or non-human subjects) will not be aware of the assigned treatments.

Personnel who analyze the data collected from the study are not aware of the treatment applied to any given group.

### Randomization

```{=html}
<!-- If you are doing a randomized study, how will you randomize, and at what level? Typical randomization techniques include: simple, block, stratified, and adaptive covariate randomization. If randomization is required for the study, the method should be specified here, not simply the source of random numbers.

Example: We will use block randomization, where each participant will be randomly assigned to one of the four equally sized, predetermined blocks. The random number list used to create these four blocks will be created using the web applications available at https://random.org. -->
```
## Sampling Plan

<!-- In this section we’ll ask you to describe how you plan to collect samples, as well as the number of samples you plan to collect and your rationale for this decision. Please keep in mind that the data described in this section should be the actual data used for analysis, so if you are using a subset of a larger dataset, please describe the subset that will actually be used in your study. -->

### Data Description

<!-- Preregistration is designed to make clear the distinction between confirmatory tests, specified prior to seeing the data, and exploratory analyses conducted after observing the data. Therefore, creating a research plan in which existing data will be used presents unique challenges. Please select the description that best describes your situation. Please do not hesitate to contact us if you have questions about how to answer this question (prereg@cos.io). -->

**Registration prior to creation of data**. As of the date of submission of this research plan for preregistration, the data have not yet been collected, created, or realized.

**Registration prior to any human observation of the data**. As of the date of submission, the data exist but have not yet been quantified, constructed, observed, or reported by anyone - including individuals that are not associated with the proposed study. Examples include museum specimens that have not been measured and data that have been collected by non-human collectors and are inaccessible.

**Registration prior to accessing the data**. As of the date of submission, the data exist, but have not been accessed by you or your collaborators. Commonly, this includes data that has been collected by another researcher or institution.

**Registration prior to analysis of the data**. As of the date of submission, the data exist and you have accessed it, though no analysis has been conducted related to the research plan (including calculation of summary statistics). A common situation for this scenario when a large dataset exists that is used for many different studies over time, or when a data set is randomly split into a sample for exploratory analyses, and the other section of data is reserved for later confirmatory data analysis.

**Registration following analysis of the data**. As of the date of submission, you have accessed and analyzed some of the data relevant to the research plan. This includes preliminary analysis of variables, calculation of descriptive statistics, and observation of data distributions. Please see <https://cos.io/prereg> for more information.

```{=html}
<!-- If you indicate that you will be using some data that already exist in this study, please describe the steps you have taken to assure that you are unaware of any patterns or summary statistics in the data. This may include an explanation of how access to the data has been limited, who has observed the data, or how you have avoided observing any analysis of the specific data you will use in your study.

An appropriate instance of using existing data would be collecting a sample size much larger than is required for the study, using a small portion of it to conduct exploratory analysis, and then registering one particular analysis that showed promising results. After registration, conduct the specified analysis on that part of the dataset that had not been investigated by the researcher up to that point.

Example: An appropriate instance of using existing data would be collecting a sample size much larger than is required for the study, using a small portion of it to conduct exploratory analysis, and then registering one particular analysis that showed promising results. After registration, conduct the specified analysis on that part of the dataset that had not been investigated by the researcher up to that point. -->
```
### Data Collection Procedures

```{=html}
<!-- Please describe the process by which you will collect your data. If you are using human subjects, this should include the population from which you obtain subjects, recruitment efforts, payment for participation, how subjects will be selected for eligibility from the initial pool (e.g. inclusion and exclusion rules), and your study timeline. For studies that donÍt include human subjects, include information about how you will collect samples, duration of data gathering efforts, source or location of samples, or batch numbers you will use.

The answer to this question requires a specific set of instructions so that another person could repeat the data collection procedures and recreate the study population. Alternatively, if the study population would be unable to be reproduced because it relies on a specific set of circumstances unlikely to be recreated (e.g., a community of people from a specific time and location), the criteria and methods for creating the group and the rationale for this unique set of subjects should be clear.

Example: Participants will be recruited through advertisements at local pastry shops. Participants will be paid $10 for agreeing to participate (raised to $30 if our sample size is not reached within 15 days of beginning recruitment). Participants must be at least 18 years old and be able to eat the ingredients of the pastries. -->
```
### Sample size

```{=html}
<!-- Describe the sample size of your study. How many units will be analyzed in the study? This could be the number of people, birds, classrooms, plots, interactions, or countries included. If the units are not individuals, then describe the size requirements for each unit. If you are using a clustered or multilevel design, how many units are you collecting at each level of the analysis? For some studies, this will simply be the number of samples or the number of clusters. For others, this could be an expected range, minimum, or maximum number.

Example: Our target sample size is 280 participants. We will attempt to recruit up to 320, assuming that not all will complete the total task. -->
```
Include also the rationale for the sample size:

```{=html}
<!-- This could include a power analysis or an arbitrary constraint such as time, money, or personnel. This gives you an opportunity to specifically state how the sample size will be determined. A wide range of possible answers is acceptable; remember that transparency is more important than principled justifications. If you state any reason for a sample size upfront, it is better than stating no reason and leaving the reader to "fill in the blanks." Acceptable rationales include: a power analysis, an arbitrary number of subjects, or a number based on time or monetary constraints.

Example: We used the software program G*Power to conduct a power analysis. Our goal was to obtain .95 power to detect a medium effect size of .25 at the standard .05 alpha error probability. -->
```
And the stopping ruel, when applicable

```{=html}
<!-- If your data collection procedures do not give you full control over your exact sample size, specify how you will decide when to terminate your data collection.

You may specify a stopping rule based on p-values only in the specific case of sequential analyses with pre-specified checkpoints, alphas levels, and stopping rules. Unacceptable rationales include stopping based on p-values if checkpoints and stopping rules are not specified. If you have control over your sample size, then including a stopping rule is not necessary, though it must be clear in this question or a previous question how an exact sample size is attained.

Example: We will post participant sign-up slots by week on the preceding Friday night, with 20 spots posted per week. We will post 20 new slots each week if, on that Friday night, we are below 320 participants. -->
```
## Variables

<!-- In this section you can describe all variables (both manipulated and measured variables) that will later be used in your confirmatory analysis plan. In your analysis plan, you will have the opportunity to describe how each variable will be used. If you have variables which you are measuring for exploratory analyses, you are not required to list them, though you are permitted to do so. -->

### Manipulated Variables

```{=html}
<!-- Describe all variables you plan to manipulate and the levels or treatment arms of each variable. This is not applicable to any observational study. For any experimental manipulation, you should give a precise definition of each manipulated variable. This must include a precise description of the levels at which each variable will be set, or a specific definition for each categorical treatment. For example, “loud or quiet,” should instead give either a precise decibel level or a means of recreating each level. 'Presence/absence' or 'positive/negative' is an acceptable description if the variable is precisely described.

Example: We manipulated the percentage of sugar by mass added to brownies. The four levels of this categorical variable are: 15%, 20%, 25%, or 40% cane sugar by mass. -->
```
### Measured Variables

```{=html}
<!-- Describe each variable that you will measure. This will include outcome measures, as well as any predictors or covariates that you will measure. You do not need to include any variables that you plan on collecting if they are not going to be included in the confirmatory analyses of this study.

Observational studies and meta-analyses will include only measured variables. As with the previous questions, the answers here must be precise. For example, 'intelligence,' 'accuracy,' 'aggression,' and 'color' are too vague. Acceptable alternatives could be 'IQ as measured by Wechsler Adult Intelligence Scale' 'percent correct,' 'number of threat displays,' and 'percent reflectance at 400 nm.'

Example: The single outcome variable will be the perceived tastiness of the single brownie each participant will eat. We will measure this by asking participants ‘How much did you enjoy eating the brownie’ (on a scale of 1-7, 1 being 'not at all', 7 being 'a great deal') and 'How good did the brownie taste' (on a scale of 1-7, 1 being 'very bad', 7 being 'very good'). -->
```
### Indices

```{=html}
<!-- If any measurements are  going to be combined into an index (or even a mean), what measures will you use and how will they be combined? Include either a formula or a precise description of your method. If your are using a more complicated statistical method to combine measures (e.g. a factor analysis), you can note that here but describe the exact method in the analysis plan section.

If you are using multiple pieces of data to construct a single variable, how will this occur? Both the data that are included and the formula or weights for each measure must be specified. Standard summary statistics, such as "means" do not require a formula, though more complicated indices require either the exact formula or, if it is an established index in the field, the index must be unambiguously defined. For example, "biodiversity index" is too broad, whereas "Shannon’s biodiversity index" is appropriate.

Example: We will take the mean of the two questions above to create a single measure of 'brownie enjoyment.'  -->
```
## Data Processing

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

### Data Exclusion

```{=html}
<!-- How will you determine what data or samples, if any, to exclude from your analyses? How will outliers be handled? Will you use any awareness check? Any rule for excluding a particular set of data is acceptable. One may describe rules for excluding a participant or for identifying outlier data.

Example: No checks will be performed to determine eligibility for inclusion besides verification that each subject answered each of the three tastiness indices. Outliers will be included in the analysis. -->
```
### Missing Data

```{=html}
<!-- How will you deal with incomplete or missing data? Any relevant explanation is acceptable. As a final reminder, remember that the final analysis must follow the specified plan, and deviations must be either strongly justified or included as a separate, exploratory analysis.

Example: If a subject does not complete any of the three indices of tastiness, that subject will not be included in the analysis. -->
```
### Data transformations

```{=html}
<!-- If you plan on transforming, centering, recoding the data, or will require a coding scheme for categorical variables, please describe that process. If any categorical predictors are included in a regression, indicate how those variables will be coded (e.g. dummy coding, summation coding, etc.) and what the reference category will be.

Example: The "Effect of sugar on brownie tastiness" does not require any additional transformations. However, if it were using a regression analysis and each level of sweet had been categorically described (e.g. not sweet, somewhat sweet, sweet, and very sweet), 'sweet' could be dummy coded with 'not sweet' as the reference category. -->
```
# Results

```{=html}
<!-- You may describe one or more confirmatory analysis in this preregistration. Please remember that all analyses specified below must be reported in the final article, and any additional analyses must be noted as exploratory or hypothesis generating.

A confirmatory analysis plan must state up front which variables are predictors (independent) and which are the outcomes (dependent), otherwise it is an exploratory analysis. You are allowed to describe any exploratory work here, but a clear confirmatory analysis is required. -->
```
## General

We have used `r cite_r("r-references.bib")` since the pre-reg, and will use XXX for all our analyses.

## Confirmatory Analyses

For each hypothesis, include the model(s) used, the relevant variables, inference criteria, and model specification.

```{=html}
<!-- What statistical model will you use to test each hypothesis? Please include the type of model (e.g. ANOVA, multiple regression, SEM, etc) and the specification of the model (this includes each variable that will be included as predictors, outcomes, or covariates). Please specify any interactions, subgroup analyses, pairwise or complex contrasts, or follow-up tests from omnibus tests. If you plan on using any positive controls, negative controls, or manipulation checks you may mention that here. Remember that any test not included here must be noted as an exploratory test in your final article.

This is perhaps the most important and most complicated question within the preregistration. As with all of the other questions, the key is to provide a specific recipe for analyzing the collected data. Ask yourself: is enough detail provided to run the same analysis again with the information provided by the user? Be aware for instances where the statistical models appear specific, but actually leave openings for the precise test. See the following examples:

- If someone specifies a 2x3 ANOVA with both factors within subjects, there is still flexibility with the various types of ANOVAs that could be run. Either a repeated measures ANOVA (RMANOVA) or a multivariate ANOVA (MANOVA) could be used for that design, which are two different tests. 
- If you are going to perform a sequential analysis and check after 50, 100, and 150 samples, you must also specify the p-values you’ll test against at those three points.

Example:  We will use a one-way between subjects ANOVA to analyze our results. The manipulated, categorical independent variable is 'sugar' whereas the dependent variable is our taste index. -->
```
```{=html}
<!-- What criteria will you use to make inferences? Please describe the information youÍll use (e.g. p-values, bayes factors, specific model fit indices), as well as cut-off criterion, where appropriate. Will you be using one or two tailed tests for each of your analyses? If you are comparing multiple conditions or testing multiple hypotheses, will you account for this?

p-values, confidence intervals, and effect sizes are standard means for making an inference, and any level is acceptable, though some criteria must be specified in this or previous fields. Bayesian analyses should specify a Bayes factor or a credible interval. If you are selecting models, then how will you determine the relative quality of each? In regards to multiple comparisons, this is a question with few "wrong" answers. In other words, transparency is more important than any specific method of controlling the false discovery rate or false error rate. One may state an intention to report all tests conducted or one may conduct a specific correction procedure; either strategy is acceptable.

Example: We will use the standard p<.05 criteria for determining if the ANOVA and the post hoc test suggest that the results are significantly different from those expected if the null hypothesis were correct. The post-hoc Tukey-Kramer test adjusts for multiple comparisons. -->
```
### Hypothesis 1

### Hypothesis 2, etc.

## Exploratory Analyses

```{=html}
<!-- If you plan to explore your data set to look for unexpected differences or relationships, you may describe those tests here. An exploratory test is any test where a prediction is not made up front, or there are multiple possible tests that you are going to use. A statistically significant finding in an exploratory test is a great way to form a new confirmatory hypothesis, which could be registered at a later time.

Example: We expect that certain demographic traits may be related to taste preferences. Therefore, we will look for relationships between demographic variables (age, gender, income, and marital status) and the primary outcome measures of taste preferences. -->
```

# Other
This will contain only any remaining (other) notes that have not been mentioned in any point above. This section will change post-pre-registration to be the Discussion section.

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::

### 2023-11-02 Scripts/prepare_data.R

@@ -1,0 +1,25 @@
+# In this file, write the R-code necessary to load your original data file
+# (e.g., an SPSS, Excel, or SAS-file), and convert it to a data.frame. Then,
+# use the function open_data(your_data_frame) or closed_data(your_data_frame)
+# to store the data. When starting out, this project will be set up to generate
+# a fake dataset fro the pre-registration.
+
+# set-up -----------------------------------------------------------------------
+library(worcs) # reproducible workflow template package
+set.seed(30102023) # seed for random number generators
+
+
+# Data-generating --------------------------------------------------------------
+
+
+# Dataframe Creation -----------------------------------------------------------
+
+
+# Data Storing -----------------------------------------------------------------
+# replace iris with your own dataframe
+open_data(data = iris, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(iris))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", deparse(substitute(iris))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", deparse(substitute(iris))), ".yml")) 

### 2023-11-02 Scripts/source_script.R

@@ -1,0 +1,9 @@
+# source_script
+
+# sample function to be deleted
+get_number <- function(){
+  return(rnorm(1, 100, 15))
+}
+
+
+# source("Scripts/source_script.R")

### 2023-11-02 Scripts/Manuscript/manuscript.Rmd
added metadata, references, and the abstract to the project

@@
 ---
-title             : "The title"
-shorttitle        : "Title"
+title             : "The Impact of Measurement Practices and Measurement Error on Construct Validity and Replication Outcomes in Psychological Science"
+shorttitle        : "Measurement and Replicability"
 
 author: 
-  - name          : "Cas Goos"
+  - name          : "Goos, C."
     affiliation   : "1"
@@
       - "Conceptualization"
+      - "Data curation"
+      - "Formal Analysis"
+      - "Investigation"
+      - "Methodology"
+      - "Visualization"
       - "Writing - Original Draft Preparation"
       - "Writing - Review & Editing"
-  - name          : "Second Author"
-    affiliation   : "1,2"
+  - name          : "Nuijten, M.B."
+    affiliation   : "1"
     role:
+      - "Project Administration"
+      - "Writing - Review & Editing"
+      - "Supervision"
+
+  - name          : "Nuijten, M.B."
+    affiliation   : "1"
+    role:
+      - "Project Administration"
       - "Writing - Review & Editing"
@@
     institution   : "Tilburg University"
-  - id            : "2"
-    institution   : "Other UNI"
 
@@
   1 Department of Methodology and Statistics, Tilburg School of Social and Behavioral Sciences, Tilburg University, Tilburg, NL.
-  complete departmental affiliations: Each new line herein must be indented, like this line.
 
-  Enter author note here.
+  Enter author note here. Caspar?
 
 abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-  One or two sentences to put the results into a more **general context**.
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
+  Recently, the influence of measurement related issues on replicability has received more investigations. 
+  In particular, studies have indicated that low reliability, and poor measurement reporting can negatively influence the replicability of an effect. 
+  Building on this new line of research, this thesis assessed these influences in large scale replication projects. 
+  Protocols from the Many Labs replication projects [@klein2014data; @klein2018many; @ebersole2016many; @ebersole2020many], and the original articles that the replications were based on were used to assess the  reporting of the measures, while publicly available data from the Many Labs replications was used to assess the reliability of the measures.
+Reliability did not relate to replicability, and was generally consistent between labs for each measure in the Many Labs projects.
+  The quality of measurement reporting in replication protocols did however relate to replicability.
+  Additionally, tentative evidence was found for a relation between quality of measurement reporting in the protocol of a replication and the quality of measurement reporting in its related original study.
+  Recommendations are given for researchers and replicators in order to improve measurement practices in replication, and ward its negative impact on replicability. 
+  Additionally, directions are given for future research investigating the relationship between measurement issues and replicability.
 
-  <!-- https://tinyurl.com/ybremelq -->
-
-keywords          : "keywords"
+keywords          : "reliability, measurement, measurement reporting, replicability, construct validity"
 wordcount         : "X"
@@
 
-floatsintext      : no
+floatsintext      : yes
 linenumbers       : no
@@
 # Code below loads the processed data. The raw data was prepared for analysis in 'prepare_data.R.
-load_data(worcs_directory = "../../Data/AnalysisData")
+# load_data(worcs_directory = "../../Data/AnalysisData")
 
@@
 
-This manuscript uses the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCSWorkflowOpen2021] to ensure reproducibility and transparency.
+This manuscript uses the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency.
 All code <!--and data--> are available at <https://github.com/CasGoos/WORCSPersonalTemplate.git>.
 
-This is an example of a non-essential citation [\@ @vanlissaWORCSWorkflowOpen2021]. If you change the rendering function to `worcs::cite_essential`, it will be removed.
-
-<!--The function below inserts a notification if the manuscript is knit using synthetic data. Make sure to insert it after load_data().-->
-
-`r notify_synthetic()`
+This is an example of a non-essential citation [\@ @vanlissaWORCS2021]. If you change the rendering function to `worcs::cite_essential`, it will be removed.
 
@@
 ```
+# Other
 
-# Other
 This will contain only any remaining (other) notes that have not been mentioned in any point above. This section will change post-pre-registration to be the Discussion section.

### 2023-11-02 Scripts/Manuscript/manuscript.Rmd
changed the structure of the manuscript to fit the master thesis' structure.

@@
 title             : "The Impact of Measurement Practices and Measurement Error on Construct Validity and Replication Outcomes in Psychological Science"
-shorttitle        : "Measurement and Replicability"
+shorttitle        : "Measurement Quality and Replicability"
 
@@
 
-  - name          : "Nuijten, M.B."
-    affiliation   : "1"
-    role:
-      - "Project Administration"
-      - "Writing - Review & Editing"
-      - "Supervision"
-
 affiliation:
@@
   Building on this new line of research, this thesis assessed these influences in large scale replication projects. 
-  Protocols from the Many Labs replication projects [@klein2014data; @klein2018many; @ebersole2016many; @ebersole2020many], and the original articles that the replications were based on were used to assess the  reporting of the measures, while publicly available data from the Many Labs replications was used to assess the reliability of the measures.
+  Protocols from the Many Labs replication projects, and the original articles that the replications were based on were used to assess the  reporting of the measures, while publicly available data from the Many Labs replications was used to assess the reliability of the measures.
 Reliability did not relate to replicability, and was generally consistent between labs for each measure in the Many Labs projects.
@@
 
-## Description
+## Measurement Error
 
-```{=html}
-<!-- Please give a brief description of your study, including some background, the purpose of the of the study, or broad research questions.
-The description should be no longer than the length of an abstract.
-It can give some context for the proposed study, but great detail is not needed here for your preregistration.
+## Questionable Measurement Practices
 
-Example: Though there is strong evidence to suggest that sugar affects taste preferences, the effect has never been demonstrated in brownies.
-Therefore, we will measure taste preference for four different levels of sugar concentration in a standard brownie recipe to determine if the effect exists in this pastry.
--->
-```
-### Key Concepts
+# Method
 
-### Background Overview
+## Sample
 
-### Contribution & Relevance
+### Replication Datasets
 
-## Aims
+### Preregistered Replication Protocols
 
-```{=html}
-<!-- List specific, concise, and testable hypotheses.
-Please state if the hypotheses are directional or non-directional.
-If directional, state the direction.
-A predicted effect is also appropriate here.
-If a specific interaction or moderation is important to your research, you can list that as a separate hypothesis.
+### Original Study
 
-Example: If taste affects preference, then mean preference indices will be higher with higher concentrations of sugar. -->
-```
-### Research Questions
+## Data Collection
 
-### Hypotheses
+## Measures
 
-# Methods
+### Measurement Error Measures
 
-## Study Design
+### Replicability Measure
 
-```{=html}
-<!-- Describe your study design.
-Examples include two-group, factorial, randomized block, and repeated measures.
-Is it a between (unpaired), within-subject (paired), or mixed design?
-Describe any counterbalancing required.
-Typical study designs for observation studies include cohort, cross sectional, and case-control studies.
+### QMP measures
 
-This question has a variety of possible answers.
-The key is for a researcher to be as detailed as is necessary given the specifics of their design.
-Be careful to determine if every parameter has been specified in the description of the study design.
-There may be some overlap between this question and the following questions.
-That is OK, as long as sufficient detail is given in one of the areas to provide all of the requested information.
-For example, if the study design describes a complete factorial, 2 X 3 design and the treatments and levels are specified previously, you do not have to repeat that information.
+### Validity Measure
 
-Example: We have a between subjects design with 1 factor (sugar by mass) with 4 levels. -->
-```
-### Study Type
+## Analyses
 
-**Experiment**.
-A researcher randomly assigns treatments to study subjects, this includes field or lab experiments.
-This is also known as an intervention experiment and includes randomized controlled trials.
+### Analyses Measurement Error
 
-**Observational Study**. Data is collected from study subjects that are not randomly assigned to a treatment. This includes surveys, natural experiments, and regression discontinuity designs.
+### Analyses QMPs
 
-**Meta-Analysis**. A systematic review of published studies.
+### Exploratory Analyses
 
-**Other**. Please explain.
-
-### Materials
-
-What materials were used (with reference)
-
-### Blinding
-
-<!-- Blinding describes who is aware of the experimental manipulations within a study. Select all that apply. Is there any additional blinding in this study? -->
-
-No blinding is involved in this study.
-
-For studies that involve human subjects, they will not know the treatment group to which they have been assigned.
-
-Personnel who interact directly with the study subjects (either human or non-human subjects) will not be aware of the assigned treatments.
-
-Personnel who analyze the data collected from the study are not aware of the treatment applied to any given group.
-
-### Randomization
-
-```{=html}
-<!-- If you are doing a randomized study, how will you randomize, and at what level?
-Typical randomization techniques include: simple, block, stratified, and adaptive covariate randomization.
-If randomization is required for the study, the method should be specified here, not simply the source of random numbers.
-
-Example: We will use block randomization, where each participant will be randomly assigned to one of the four equally sized, predetermined blocks.
-The random number list used to create these four blocks will be created using the web applications available at https://random.org.
--->
-```
-## Sampling Plan
-
-<!-- In this section we’ll ask you to describe how you plan to collect samples, as well as the number of samples you plan to collect and your rationale for this decision.
-Please keep in mind that the data described in this section should be the actual data used for analysis, so if you are using a subset of a larger dataset, please describe the subset that will actually be used in your study.
--->
-
-### Data Description
-
-<!-- Preregistration is designed to make clear the distinction between confirmatory tests, specified prior to seeing the data, and exploratory analyses conducted after observing the data.
-Therefore, creating a research plan in which existing data will be used presents unique challenges.
-Please select the description that best describes your situation.
-Please do not hesitate to contact us if you have questions about how to answer this question (prereg@cos.io).
--->
-
-**Registration prior to creation of data**. As of the date of submission of this research plan for preregistration, the data have not yet been collected, created, or realized.
-
-**Registration prior to any human observation of the data**.
-As of the date of submission, the data exist but have not yet been quantified, constructed, observed, or reported by anyone - including individuals that are not associated with the proposed study.
-Examples include museum specimens that have not been measured and data that have been collected by non-human collectors and are inaccessible.
-
-**Registration prior to accessing the data**.
-As of the date of submission, the data exist, but have not been accessed by you or your collaborators.
-Commonly, this includes data that has been collected by another researcher or institution.
-
-**Registration prior to analysis of the data**.
-As of the date of submission, the data exist and you have accessed it, though no analysis has been conducted related to the research plan (including calculation of summary statistics).
-A common situation for this scenario when a large dataset exists that is used for many different studies over time, or when a data set is randomly split into a sample for exploratory analyses, and the other section of data is reserved for later confirmatory data analysis.
-
-**Registration following analysis of the data**.
-As of the date of submission, you have accessed and analyzed some of the data relevant to the research plan.
-This includes preliminary analysis of variables, calculation of descriptive statistics, and observation of data distributions.
-Please see <https://cos.io/prereg> for more information.
-
-```{=html}
-<!-- If you indicate that you will be using some data that already exist in this study, please describe the steps you have taken to assure that you are unaware of any patterns or summary statistics in the data.
-This may include an explanation of how access to the data has been limited, who has observed the data, or how you have avoided observing any analysis of the specific data you will use in your study.
-
-An appropriate instance of using existing data would be collecting a sample size much larger than is required for the study, using a small portion of it to conduct exploratory analysis, and then registering one particular analysis that showed promising results.
-After registration, conduct the specified analysis on that part of the dataset that had not been investigated by the researcher up to that point.
-
-Example: An appropriate instance of using existing data would be collecting a sample size much larger than is required for the study, using a small portion of it to conduct exploratory analysis, and then registering one particular analysis that showed promising results.
-After registration, conduct the specified analysis on that part of the dataset that had not been investigated by the researcher up to that point.
--->
-```
-### Data Collection Procedures
-
-```{=html}
-<!-- Please describe the process by which you will collect your data.
-If you are using human subjects, this should include the population from which you obtain subjects, recruitment efforts, payment for participation, how subjects will be selected for eligibility from the initial pool (e.g.
-inclusion and exclusion rules), and your study timeline.
-For studies that donÍt include human subjects, include information about how you will collect samples, duration of data gathering efforts, source or location of samples, or batch numbers you will use.
-
-The answer to this question requires a specific set of instructions so that another person could repeat the data collection procedures and recreate the study population.
-Alternatively, if the study population would be unable to be reproduced because it relies on a specific set of circumstances unlikely to be recreated (e.g., a community of people from a specific time and location), the criteria and methods for creating the group and the rationale for this unique set of subjects should be clear.
-
-Example: Participants will be recruited through advertisements at local pastry shops.
-Participants will be paid $10 for agreeing to participate (raised to $30 if our sample size is not reached within 15 days of beginning recruitment).
-Participants must be at least 18 years old and be able to eat the ingredients of the pastries.
--->
-```
-### Sample size
-
-```{=html}
-<!-- Describe the sample size of your study.
-How many units will be analyzed in the study?
-This could be the number of people, birds, classrooms, plots, interactions, or countries included.
-If the units are not individuals, then describe the size requirements for each unit.
-If you are using a clustered or multilevel design, how many units are you collecting at each level of the analysis?
-For some studies, this will simply be the number of samples or the number of clusters.
-For others, this could be an expected range, minimum, or maximum number.
-
-Example: Our target sample size is 280 participants. We will attempt to recruit up to 320, assuming that not all will complete the total task. -->
-```
-Include also the rationale for the sample size:
-
-```{=html}
-<!-- This could include a power analysis or an arbitrary constraint such as time, money, or personnel.
-This gives you an opportunity to specifically state how the sample size will be determined.
-A wide range of possible answers is acceptable; remember that transparency is more important than principled justifications.
-If you state any reason for a sample size upfront, it is better than stating no reason and leaving the reader to "fill in the blanks." Acceptable rationales include: a power analysis, an arbitrary number of subjects, or a number based on time or monetary constraints.
-
-Example: We used the software program G*Power to conduct a power analysis. Our goal was to obtain .95 power to detect a medium effect size of .25 at the standard .05 alpha error probability. -->
-```
-And the stopping ruel, when applicable
-
-```{=html}
-<!-- If your data collection procedures do not give you full control over your exact sample size, specify how you will decide when to terminate your data collection.
-
-You may specify a stopping rule based on p-values only in the specific case of sequential analyses with pre-specified checkpoints, alphas levels, and stopping rules.
-Unacceptable rationales include stopping based on p-values if checkpoints and stopping rules are not specified.
-If you have control over your sample size, then including a stopping rule is not necessary, though it must be clear in this question or a previous question how an exact sample size is attained.
-
-Example: We will post participant sign-up slots by week on the preceding Friday night, with 20 spots posted per week.
-We will post 20 new slots each week if, on that Friday night, we are below 320 participants.
--->
-```
-## Variables
-
-<!-- In this section you can describe all variables (both manipulated and measured variables) that will later be used in your confirmatory analysis plan.
-In your analysis plan, you will have the opportunity to describe how each variable will be used.
-If you have variables which you are measuring for exploratory analyses, you are not required to list them, though you are permitted to do so.
--->
-
-### Manipulated Variables
-
-```{=html}
-<!-- Describe all variables you plan to manipulate and the levels or treatment arms of each variable.
-This is not applicable to any observational study.
-For any experimental manipulation, you should give a precise definition of each manipulated variable.
-This must include a precise description of the levels at which each variable will be set, or a specific definition for each categorical treatment.
-For example, “loud or quiet,” should instead give either a precise decibel level or a means of recreating each level.
-'Presence/absence' or 'positive/negative' is an acceptable description if the variable is precisely described.
-
-Example: We manipulated the percentage of sugar by mass added to brownies. The four levels of this categorical variable are: 15%, 20%, 25%, or 40% cane sugar by mass. -->
-```
-### Measured Variables
-
-```{=html}
-<!-- Describe each variable that you will measure.
-This will include outcome measures, as well as any predictors or covariates that you will measure.
-You do not need to include any variables that you plan on collecting if they are not going to be included in the confirmatory analyses of this study.
-
-Observational studies and meta-analyses will include only measured variables.
-As with the previous questions, the answers here must be precise.
-For example, 'intelligence,' 'accuracy,' 'aggression,' and 'color' are too vague.
-Acceptable alternatives could be 'IQ as measured by Wechsler Adult Intelligence Scale' 'percent correct,' 'number of threat displays,' and 'percent reflectance at 400 nm.'
-
-Example: The single outcome variable will be the perceived tastiness of the single brownie each participant will eat.
-We will measure this by asking participants ‘How much did you enjoy eating the brownie’ (on a scale of 1-7, 1 being 'not at all', 7 being 'a great deal') and 'How good did the brownie taste' (on a scale of 1-7, 1 being 'very bad', 7 being 'very good').
--->
-```
-### Indices
-
-```{=html}
-<!-- If any measurements are  going to be combined into an index (or even a mean), what measures will you use and how will they be combined?
-Include either a formula or a precise description of your method.
-If your are using a more complicated statistical method to combine measures (e.g.
-a factor analysis), you can note that here but describe the exact method in the analysis plan section.
-
-If you are using multiple pieces of data to construct a single variable, how will this occur?
-Both the data that are included and the formula or weights for each measure must be specified.
-Standard summary statistics, such as "means" do not require a formula, though more complicated indices require either the exact formula or, if it is an established index in the field, the index must be unambiguously defined.
-For example, "biodiversity index" is too broad, whereas "Shannon’s biodiversity index" is appropriate.
-
-Example: We will take the mean of the two questions above to create a single measure of 'brownie enjoyment.'  -->
-```
-## Data Processing
-
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
-
-### Data Exclusion
-
-```{=html}
-<!-- How will you determine what data or samples, if any, to exclude from your analyses?
-How will outliers be handled?
-Will you use any awareness check?
-Any rule for excluding a particular set of data is acceptable.
-One may describe rules for excluding a participant or for identifying outlier data.
-
-Example: No checks will be performed to determine eligibility for inclusion besides verification that each subject answered each of the three tastiness indices.
-Outliers will be included in the analysis.
--->
-```
-### Missing Data
-
-```{=html}
-<!-- How will you deal with incomplete or missing data?
-Any relevant explanation is acceptable.
-As a final reminder, remember that the final analysis must follow the specified plan, and deviations must be either strongly justified or included as a separate, exploratory analysis.
-
-Example: If a subject does not complete any of the three indices of tastiness, that subject will not be included in the analysis. -->
-```
-### Data transformations
-
-```{=html}
-<!-- If you plan on transforming, centering, recoding the data, or will require a coding scheme for categorical variables, please describe that process.
-If any categorical predictors are included in a regression, indicate how those variables will be coded (e.g.
-dummy coding, summation coding, etc.) and what the reference category will be.
-
-Example: The "Effect of sugar on brownie tastiness" does not require any additional transformations.
-However, if it were using a regression analysis and each level of sweet had been categorically described (e.g.
-not sweet, somewhat sweet, sweet, and very sweet), 'sweet' could be dummy coded with 'not sweet' as the reference category.
--->
-```
 # Results
 
-```{=html}
-<!-- You may describe one or more confirmatory analysis in this preregistration.
-Please remember that all analyses specified below must be reported in the final article, and any additional analyses must be noted as exploratory or hypothesis generating.
+## Descriptives
 
-A confirmatory analysis plan must state up front which variables are predictors (independent) and which are the outcomes (dependent), otherwise it is an exploratory analysis.
-You are allowed to describe any exploratory work here, but a clear confirmatory analysis is required.
--->
-```
-## General
+## Reliability
 
-We have used `r cite_r("r-references.bib")` since the pre-reg, and will use XXX for all our analyses.
+## Questionable Measurement Practices
 
-## Confirmatory Analyses
+## Exploratory Results
 
-For each hypothesis, include the model(s) used, the relevant variables, inference criteria, and model specification.
+# Discussion
 
-```{=html}
-<!-- What statistical model will you use to test each hypothesis?
-Please include the type of model (e.g.
-ANOVA, multiple regression, SEM, etc) and the specification of the model (this includes each variable that will be included as predictors, outcomes, or covariates).
-Please specify any interactions, subgroup analyses, pairwise or complex contrasts, or follow-up tests from omnibus tests.
-If you plan on using any positive controls, negative controls, or manipulation checks you may mention that here.
-Remember that any test not included here must be noted as an exploratory test in your final article.
+## Quality of Measurement
 
-This is perhaps the most important and most complicated question within the preregistration.
-As with all of the other questions, the key is to provide a specific recipe for analyzing the collected data.
-Ask yourself: is enough detail provided to run the same analysis again with the information provided by the user?
-Be aware for instances where the statistical models appear specific, but actually leave openings for the precise test.
-See the following examples:
+## Impact on replicability
 
-- If someone specifies a 2x3 ANOVA with both factors within subjects, there is still flexibility with the various types of ANOVAs that could be run.
-Either a repeated measures ANOVA (RMANOVA) or a multivariate ANOVA (MANOVA) could be used for that design, which are two different tests.
-- If you are going to perform a sequential analysis and check after 50, 100, and 150 samples, you must also specify the p-values you’ll test against at those three points.
+## Limitations & Future Research
 
-Example:  We will use a one-way between subjects ANOVA to analyze our results. The manipulated, categorical independent variable is 'sugar' whereas the dependent variable is our taste index. -->
-```
-```{=html}
-<!-- What criteria will you use to make inferences?
-Please describe the information youÍll use (e.g.
-p-values, bayes factors, specific model fit indices), as well as cut-off criterion, where appropriate.
-Will you be using one or two tailed tests for each of your analyses?
-If you are comparing multiple conditions or testing multiple hypotheses, will you account for this?
+## Implications for Research and Replications in Psychological Science
 
-p-values, confidence intervals, and effect sizes are standard means for making an inference, and any level is acceptable, though some criteria must be specified in this or previous fields.
-Bayesian analyses should specify a Bayes factor or a credible interval.
-If you are selecting models, then how will you determine the relative quality of each?
-In regards to multiple comparisons, this is a question with few "wrong" answers.
-In other words, transparency is more important than any specific method of controlling the false discovery rate or false error rate.
-One may state an intention to report all tests conducted or one may conduct a specific correction procedure; either strategy is acceptable.
-
-Example: We will use the standard p<.05 criteria for determining if the ANOVA and the post hoc test suggest that the results are significantly different from those expected if the null hypothesis were correct.
-The post-hoc Tukey-Kramer test adjusts for multiple comparisons.
--->
-```
-### Hypothesis 1
-
-### Hypothesis 2, etc.
-
-## Exploratory Analyses
-
-```{=html}
-<!-- If you plan to explore your data set to look for unexpected differences or relationships, you may describe those tests here.
-An exploratory test is any test where a prediction is not made up front, or there are multiple possible tests that you are going to use.
-A statistically significant finding in an exploratory test is a great way to form a new confirmatory hypothesis, which could be registered at a later time.
-
-Example: We expect that certain demographic traits may be related to taste preferences.
-Therefore, we will look for relationships between demographic variables (age, gender, income, and marital status) and the primary outcome measures of taste preferences.
--->
-```
-# Other
-
-This will contain only any remaining (other) notes that have not been mentioned in any point above. This section will change post-pre-registration to be the Discussion section.
+# Conclusion
 

### 2023-11-02 Scripts/Manuscript/manuscript.Rmd
added the intial part of the intro as a test drive.

@@
 This manuscript uses the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency.
-All code <!--and data--> are available at <https://github.com/CasGoos/WORCSPersonalTemplate.git>.
+All code and XXX data are available at <https://github.com/CasGoos/WORCSPersonalTemplate.git>.
 
@@
 # Introduction
+
+For many years, methodologists and statisticians have raised concerns about the way that research practices [@cumming2014new; @wicherts2016degrees], reporting practices [@bakker2011mis; @nuijten2016prevalence], and publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science] may undermine the credibility of psychology's scientific claims.
+Replicability of a finding is seen as one crucial step in establishing its credibility [@nosek2022replicability].
+In order to investigate the replicability of psychological science, the large scale Reproducibility Project: Psychology (RPP) was set-up [@osc2015estimating].
+Replications of 100 published studies were performed using similar materials, procedures, and analyses, while using a new sample of participants for each study.
+They found however, that in many instances the results did no match those of the original studies.
+This lack of replicability of psychological findings illustrated that psychology was facing a so-called 'replication crisis' [@hughes2018psychology; @giner2019crisis].
+
+As a response, the demand to verify the credibility of psychological findings through replications rose.
+In order to attempt replications of various psychological findings, numerous large scale projects were set-up [@klein2014data; @camerer2016evaluating; @camerer2018evaluating; @ebersole2016many; @ebersole2020many; @klein2018many; @klein2022many}.
+Among these were the Many Labs projects, which operated similarly to the RPP, with the additional feature that each original article was replicated multiple times across different labs in various locations around the world.
+The results from these replication projects generally showed smaller effects than those reported in the original studies.
+Similarly, effects that had reached statistical significance in the original no longer did across the aggregate results of its replications.
+
+Several explanations for this discrepancy between original and replication findings have been suggested and investigated, with many being centred around the concept of Questionable Research Practices [QRPs, @john2012measuring].
+QRPs are practices, which either misrepresent or omit essential methodological information that is necessary for the evaluation of the research.
+Without this information, a reader will not know whether the result was in line with the author's expectation or simply the result of repeated trial and error until a suitable result was found [@simmons2011false].
+Consequently, much of the discourse and the subsequent proposed solutions have been centred around preventing these QRPs through increased transparency in scientific reporting.
+Preregistrations are one method for preventing QRPs.
+Preregistrations provide a clear description of the originally planned methodology of a study, which remains publicly available alongside the final report of the study.
+As a result, the author's original expectations and intentions can be accessed by the reader [@nosek2022replicability].
+
+However, many researchers have also raised concerns that other factors, such as low power [@stanley2018what], lack of strong theoretical foundations [@eronen2021theory], and validity [@finkel2017replicability], which have not been given as much attention, are just as if not more responsible for the lack of successful replications found in psychology.
+An idea which has gained more traction recently is that measurement related issues have a large problematic influence on replicability.
+In particular, studies have focused on the effects of issues such as measurement error and questionable measurement practices on replicability [@stanley2014expectations; @shaw2020measurement; @flake2017construct; @flake2020measurement].
+
+Measurement in psychological science is defined in large part by one overarching issue: psychological constructs, such as affective state and intelligence, cannot be measured directly.
+As a result, psychologists face two primary challenges in the use of measurement: First of all, the measure has to assess the construct it intends to measure, even though it can only do so indirectly.
+Secondly, because the measurement is indirect, it also comes with some degree of error surrounding its assessment of the construct.
+The first issue relates to the concept of validity, and specifically construct validity.
+Validity refers to the overall extent to which a measure measures what it is supposed to [@borsboom2004concept], while construct validity specifically refers to the substantial relation between the item scores on a psychological measure and the psychological construct it intends to measure.
+In order for indirect assessment of psychological constructs to be a viable approach, the measure needs to have construct validity [@cook2002experimental].
+However, both original and replication research are often not reported with sufficient details on construct validity [@shaw2020measurement; @flake2022construct].
+The second issue relates to the concept of measurement error and reliability.
+Measurement error indicates the amount of variation in item scores that is the result of the used measures inaccuracies, and not due to differences in the underlying psychological construct of interest.
+While what should be considered acceptable levels of measurement error is a subject of debate, and dependent upon context [@cho2015cronbach], it is generally agreed upon that too much measurement error is problematic.
+If measurement error is too large, the item scores relate to a construct no more than they do to random noise.
+As a result, the interpretability of these scores as indicators of a psychological construct is limited.
+
+@stanley2014expectations demonstrated, using a simulation study, the drastic effect measurement error can have on attempts to verify or falsify original findings.
+In practice, measurement error is commonly indicated using score-reliability.
+Score-reliability is an index of consistency of a measure, showing how much the items converge to the same point, with the point being the measured variable.
+Thus, [@stanley2014expectations] generated scalar item data with levels of score-reliability that mimicked what is standard in psychological research, to ensure that the resulting degree of measurement error was representative.
+Using this data, they found that the degree of measurement error can explain a large amount of the variation in observed effects found in replication research.
+It could therefore be that a failed replication was simply the result of measurement of the true effect varying from the original, rather than the true effect itself being different from what was originally reported.
+As a result, interpretations of replications might not be based on tests of the true effect, if the impact of measurement error is not attenuated for.
+
+Another key aspect in evaluating the use of measures is how they are reported.
+Questionable Measurement Practices (QMPs) have been coined as a conjugate term to QRPs.
+QMPs are practices that decrease the information necessary to evaluate the measurement of a study.
+They range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of measure and procedure of any sourced measures [@flake2020measurement].
+[@flake2022construct] coded the presence of a series of QMPs in the replication report in both the replication protocols of each replication in the RPP, as well as the original articles the replications were based on.
+They found that QMPs linked to issues for replicators in recreating the measurement to closely match the measurement in the original.
+As a result, there was a lack of measurement related information in both replication reports, and original articles.
+Without this information, it becomes difficult to establish that original and replication are measuring the same construct(s), which has detrimental consequences for direct replication attempts.
+
+This thesis aims to investigate the influence of measurement error and QMPs on replicability, using data and reports from the large scale Many Labs replication projects.
+One goal is to expand the research by [@stanley2014expectations] with a practical example.
+Whereas they obtained their findings using a simulation study, this thesis intended to investigate the scope of their findings in practice.
+QMPs in the context of replication research were already investigated by [@flake2022construct].
+However, the investigations remained mostly descriptive.
+This thesis aims to expand upon the findings of [@flake2022construct] through the use of a new set of replication data, and by investigating the relation between QMP and replicability.
 

### 2023-11-02 Scripts/Manuscript/manuscript.Rmd
finished adding the remainder of the introduction section into the manuscript file.

@@
 Score-reliability is an index of consistency of a measure, showing how much the items converge to the same point, with the point being the measured variable.
-Thus, [@stanley2014expectations] generated scalar item data with levels of score-reliability that mimicked what is standard in psychological research, to ensure that the resulting degree of measurement error was representative.
+Thus, @stanley2014expectations generated scalar item data with levels of score-reliability that mimicked what is standard in psychological research, to ensure that the resulting degree of measurement error was representative.
 Using this data, they found that the degree of measurement error can explain a large amount of the variation in observed effects found in replication research.
@@
 They range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of measure and procedure of any sourced measures [@flake2020measurement].
-[@flake2022construct] coded the presence of a series of QMPs in the replication report in both the replication protocols of each replication in the RPP, as well as the original articles the replications were based on.
+@flake2022construct coded the presence of a series of QMPs in the replication report in both the replication protocols of each replication in the RPP, as well as the original articles the replications were based on.
 They found that QMPs linked to issues for replicators in recreating the measurement to closely match the measurement in the original.
@@
 
+As a first step it is worth investigating what the state of measurement error is in original and psychological research, in order to assess the scope of @stanley2014expectations's findings in practice.
+Thus, this thesis will investigate the following:
+
+-   RQ1a. What is the degree of score reliability in replications of psychological research?
+
+-   RQ1b. What is the degree of score reliability in original psychological research?
+
+It is difficult to suggest an expected or informed cut-off value for what could be considered a sufficient score reliability coefficient for both original and replication studies.
+While suggested cut-off points for reliability do exist [@nunnaly1994assessment], they are not without their criticism [@cho2015cronbach; @crutzen2017scale].
+Instead a comparison of scores between original and their associated replication studies should be of more substantive interest.
+Since direct replications intend to investigate effects in nearly identical scenarios with nearly identical measures as the original study, it is expected that measurement errors are as present in replication research as in original psychological research.
+
+-   H1. No difference is present in the degree of score reliability between replication research and original psychological research.
+
+While reliability estimates are generally considered a measure specific feature, this is false.
+They are context dependent, and as a result the estimates of an effect can differ across contexts [@cho2015cronbach; @pauly2018resampling].
+With large enough differences across contexts, the effect estimates between different replication attempts could deviate from each other beyond direct comparison.
+For instance, suppose that we have a measure of multiple items assessing agreeableness in relation to both parents as well as peers.
+In a non-traditional society we might find high reliability for this measure, because participants that score high on one item, score high on another item since they are generally agreeable, while participants that score low one item, score low for all the other items.
+On the other hand, in a more traditional society we might find that reliability is low, because agreeableness towards parents is normative in that society, and as a result items relating to agreeableness towards parents may not be indicative of general agreeableness as a personality trait.
+In this example, a high score on the measure in the first context relates more strongly to a single agreeableness construct compared to the second context.
+The findings across these two populations would then no longer be directly comparable.
+Consequently, the value of any direct replication would become limited.
+To investigate this potential problem, the variation in score reliability is assessed for each measure when used in different contexts.
+
+- RQ2. To what degree do reliability estimates differ within a replication set of the same original study?
+
+Even though reliability estimates are context dependent, sufficient protocol structure can counteract the variance in reliability estimates.
+An example of the standardising impact a structured protocol can have on reducing variability within an effect can be found in investigations into the closely related issue of heterogeneity [@patacchini2007unobserved].
+Heterogeneity refers to the true variation in the true effect size due to minor but key differences in context, environment, and procedure.
+Heterogeneity is yet another proposed explanation for failed replications.
+This concern even prompted a Many Labs centred around the testing of heterogeneity in replications [@klein2018many].
+However analyses from Many Labs 2, and @olsson2020heterogeneity showed little empirical evidence for widespread heterogeneity in effects amongst replications.
+These findings demonstrate that it is possible to reduce variability as the result of context using structured protocols, as was done in the Many Labs projects this thesis analyzed.
+
+- H2. There is no significant variation in the reliability estimates of replications of the same original study.
+
+This thesis investigated whether there is something in the measures used for replicated findings that sets them apart from those used for non-replicated findings.
+In particular, this thesis extends research by @stanley2014expectations on the relationship between reliability and replicability, by using data from real life replication projects.
+
+- RQ3. What is the association between replication study score reliability and replication outcome?
+
+Greater score-reliability means greater consistency in estimation as variance around the estimate of the true effect is decreased.
+Consequently measures across different occasions, including between original and replication, should also become more consistent [@nunnaly1994assessment].
+When original and replication research share consistent result, and as long as the studied effect is true, then on average their statistical conclusions should converge.
+
+- H3. Score reliability in replication research is positively associated with successful replication of an original finding.
+
+Reliability is only one aspect by which a measure can be judged, with validity being another important way to determine the scientific rigour of a measure [@roberts2006reliability].
+Therefore as part of the exploratory analyses, validity was assessed for the same data source used to test the aforementioned hypotheses.
+Specifically, the unidimensionality of the measure was determined, meaning whether or not the items of a measure all related to a single variable.
+
+Validity of measures can be assessed not only through features found in the data.
+The measure must also be chosen and implemented in a way that enables proper measurement of the variables [@flake2020measurement].
+Any scientific report should therefore clearly motivate the measure and procedure that was used.
+Without clear reporting on these aspects, the validity of measurement will remain uncertain.
+Therefore, the other tests of this paper focused on the reporting aspects of measurement, assessed through QMPs.
+
 ## Questionable Measurement Practices
+@flake2022construct descriptively investigated QMPs within the reproducibility project psychology [@osc2015estimating].
+This thesis seeks to conceptually replicate some of their findings within the Many Labs replication projects.
+
+- RQ4a. To what degree are QMPs present in replications of psychological research?
+- RQ4b. To what degree are QMPs present in original psychological research?
+
+The investigations by @flake2022construct have shown not only that  QMPs are common in psychological research, they can be even more common in replications reports.
+However, the reporting of the Many Labs projects differ from the RPP data used in @flake2022construct.
+The structured and preregistered protocols used for the Many Labs projects were hypothesized to lead to consistent reporting of important measurement details, and as a result contain less QMPs.
+
+- H4. QMPs are expected to be more frequent in original psychological research than in replication research.
+
+QMPs put the validity of a study into question.
+If there is a lack of transparency and the used measures are invalid, replication results become difficult to interpret [@flake2020measurement].
+With a lack of transparency, closely mimicking the original's measurement becomes challenging.
+Furthermore, if a replication does not properly measure the variables of the original effect, the effect analysed within the replication may not be the same as the original.
+For these reasons, establishing a link between QMPs and non-replicability should confirm suspicions of their detrimental effects on replications [@flake2017construct; @flake2020measurement; @flake2022construct].
+
+- RQ5. What is the association between QMPs in replication studies and replication outcome?
+
+Fewer QMPs means that measurement decisions in a report are transparent with the number arbitrary methodological decisions being limited as well.
+Fewer arbitrary decisions means less ways that a replicator can deviate from the original's intended effect.
+One of the Many Labs projects even touched on this concept [@ebersole2020many].
+In this project, peer-review of replication protocols by original authors was used to ensure that approved methods were used.
+Additionally, it has been observed that authors who promote greater transparency in their work, have on average stronger evidence for their hypotheses [@wicherts2011willingness].
+Finally, the results shown in @protzko2020high illustrate that when original studies are transparent, preregistered, and have adequate sample size, subsequent replication attempts find nearly the same effect size as the original.
+All of these findings point towards a positive relation between successful replication and various types of good research practices.
+A similar relation is expected for good measurement practices.
+
+- H5. QMPs in replication research are negatively associated with replication of an original finding.
+
+@flake2022construct have already demonstrated the issues replicators face in transparently reporting the appropriate evidence for the measures they used.
+That study identified among other issues, a lack of available information in original articles.
+If essential information on a measure is not available in an original article, it may be difficult to know the specifics of that measure when used in a replication.
+In that case, the lack of proper reporting on measurement would impact the transparency and validity of future replications.
+Consequently, the article's findings become difficult to verify.
+To provide insight into this issue, an investigation of the relationship between original and replication QMPs was included.
+
+- RQ6. What is the association between QMPs in original research and QMPs in replications of psychological research?
+
+If the relationship exists, it is expected that questionable measurement practices in an original paper might cause a spill-over effect of QMPs into the replication.
+If the original paper does not specify how a measure was used, the replication may implement it differently.
+In that case, the replication can no longer be considered a direct replication.
+Additionally, investigations by @shaw2020measurement have shown that more validity evidence in an original article is associated with better psychometric properties in the replication sample.
+Based on these arguments, hypotheses are expected to be associated across original and replication studies.
+
+- H6. Total number of QMPs in original psychological research is positively related to total number of QMPs in replication research.
 

### 2023-11-03 Scripts/Manuscript/manuscript.Rmd
added the measurement section text, but not yet the formulas and table. Also solved an issue with the renv not being up to date.

@@
 As a response, the demand to verify the credibility of psychological findings through replications rose.
-In order to attempt replications of various psychological findings, numerous large scale projects were set-up [@klein2014data; @camerer2016evaluating; @camerer2018evaluating; @ebersole2016many; @ebersole2020many; @klein2018many; @klein2022many}.
+In order to attempt replications of various psychological findings, numerous large scale projects were set-up [@klein2014data; @camerer2016evaluating; @camerer2018evaluating; @ebersole2016many; @ebersole2020many; @klein2018many; @klein2022many].
 Among these were the Many Labs projects, which operated similarly to the RPP, with the additional feature that each original article was replicated multiple times across different labs in various locations around the world.
@@
 ## Questionable Measurement Practices
+
 @flake2022construct descriptively investigated QMPs within the reproducibility project psychology [@osc2015estimating].
@@
 
+Data collection, coding protocol, and planned analyses were all preregistered.
+The preregistration and supplementary materials can be found on this thesis' OSF page: <https://osf.io/9r8yt/>.
+Any deviations from the preregistration are explicitly mentioned in the text.
+
 ## Sample
+
+The data used for the analyses in this thesis consists of three main sources: replication datasets, preregistered replication protocols, and original study articles.
+The data came from the Many Labs series of studies.
+In particular, data from Many Labs 1, 2, 3, & 5 was used [@klein2014data; @klein2018many; @ebersole2016many; @ebersole2020many].
+Data from Many Labs 4 [@klein2022many] was not part of the sample, as there was no publicly available protocol which contains the information needed to code QMPs.
+Additionally, the replication of [@crosby2008we] in Many Labs 5 did not contain contain data suitable for this project.
+The replication made use of videos and eye-tracking as measures, which does not match this thesis' focus on scale and item measures.
+
+The total number of psychological findings for which replication was attempted across the four included Many Labs projects amounts to a total of 60: 13 in Many Labs 1; 28 in Many Labs 2; 10 in Many Labs 3; & finally 9 out of the 10 tested findings in Many Labs 5.
+Since each replication set is related to an original study, the number of effects in original studies matches the number of effects in replication research.
+
+However, the unit of measurement was not a single study or replication.
+Instead each measure of a unique variable within a Many Labs project was treated as the unit of measurement.
+The reason being that studies could have and did use multiple measures.
+Additionally, measures can assess multiple dimensions.
+These dimensions, meaning unique variables, were separated into different units whenever possible, otherwise the measure was discarded from analysis.
+However, not all measures of unique variables were used.
+Only data from measures of primary variables, meaning those variables included in the primary test of the replication, were used.
+This was done to ensure that the analyses could link directly to the replicability of a study.
+Acquiescence bias checks, manipulation checks, measures used for pilot testing, and measures added for exploratory analyses in replication studies were not included.
+The result was a total sample size of 77 measures: 14 in Many Labs 1; 35 in Many Labs 2; 15 in Many Labs 3; & 13 in Many Labs 5.
+Again, the sample was equivalent between replications and original studies.
 
@@
 
+The replication datasets refer to the data of each of the replication attempts for each of the original psychological effects undertaken as part of a Many Labs study.
+The specific data was extracted from the replication datasets for each relevant measure.
+The measure had to consist of multiple scalar items to be considered relevant for the related analyses.
+Single item measures were not usable for the analyses on score reliability [@wanous1996estimating] as they do not translate directly to the findings of @stanley2014expectations, which this thesis is following up on.
+
+For Many Labs 1, all the relevant replication data was available in a single csv file.
+For Many Labs 2 & 3 the situation was similar, only here the files were split across two csv files for each project.
+For Many Labs 5, the data was made available for each of the ten replication sets separately.
+Three out of the ten datasets were furthermore split across the various locations at which they were taken.
+If cleaned data was available this was chosen over raw data.
+Pilot data were omitted from the analyses entirely.
+This resulted in suitable measure data from eighteen replication sets spread across on average 40 lab locations for the analyses of hypotheses 2 & 3.
+
 ### Preregistered Replication Protocols
+
+The preregistered replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each replication set.
+These protocols were available through the OSF pages of each Many Labs project.
+These preregistered replication protocols, as well as the replication datasets mentioned earlier were scanned through to ensure that the planned analyses were feasible.
+However, no coding or analysis of either of them had taken place before the analyses were preregistered.
+This includes any systematic coding of the QMPs present in the report.
+Furthermore, no overview of these and the qualitative topics were available at the time of preregistration.
+
+Finally, the reports of the Many Labs projects, meaning the published articles [@klein2014data; @klein2018many; @ebersole2016many; @ebersole2020many], were used to determine whether not the replication was considered successful.
 
@@
 
+The original study articles are the published articles of the original effect on which the Many Labs replication sets were based.
+In the case of Many Labs 5 the original studies refer to the studies which first tested the effect to be replicated, not the earlier replication attempts of the same effects in the RPP [@osc2015estimating].
+
 ## Data Collection
 
-## Measures
+The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>.
+When available, codebooks and study materials were used to identify the specific data for each measure.
+
+The publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio [@Posit2023RStudio] with R version 4.2.2 [@R2021R].
+Using the replication protocols, codebooks, and analysis scripts from each replication set as a guide, the variables associated with each measure were extracted into their own data frame containing the data from all studies in one replication set.
+These pieces of information formed the replication datasets in the analysis.
+
+The OSF page for each Many Labs project was combed through, in order to identify the components of the research which contained information on the measurement practice and reported reliability.
+The focus was on finding the preregistered protocols which contained information on the entirety of the replication sets in each Many Labs project.
+This was successful for Many Labs 2, & 3.
+For Many Labs 1 the Proposal_V1.1 was selected as the proper candidate for the QMP analysis.
+Despite the difference in name, it is the equivalent in Many Labs 1 to the protocols of Many Labs 2 & 3.
+For Many Labs 5 the protocols were made accessible for each replication set separately.
+The relevant OSF page of each replication set was searched through for a file which contained protocol in its name.
+If available, a version of the protocol labelled as revised, post-review, peer-review, or endorsed was selected.
+In case there was doubt about which was most appropriate, the latest uploaded relevant protocol was selected.
+Only regular protocols were taken, meaning those not labelled as data collection, analysis protocol or anything similar[^1].
+
+[^1]: The steps taken to access the replication protocol data from Many Labs 5 were not preregistered, and only became clear upon further investigation of the accessible information.
+The specific names and locations of the files that were used as the datasets can be found under the supplementary materials of the OSF page of this thesis <https://osf.io/gft46/%7D>
+
+The original articles were identified through the citations in each replication protocol, using Web of Science, Google Scholar, and PsychInfo (in that order).
+An issue was encountered while trying to access @hyman1950current.
+However, after contacting the first author of @klein2014data a suitable version of the article was obtained for use in the analyses.
+
+The measures of primary variables were identified by combing through the entire methods section of each preregistered replication protocols.
+Then using the structured coding protocol (made using Qualtrics) available on the OSF page for this thesis (<https://osf.io/9r8yt/>), each measure of a unique variable was coded on measurement reporting and reported reliability.
+
+The structured coding protocol was used for both replication protocols and original studies.
+A series of questions relating to measurement practices and measurement error were used to extract the information.
+Descriptions of the extracted variables can be found in the Measures section below.
+The scope of the coding was limited to the abstract, method, procedure, materials, measure, and initial parts of the results sections.
+Additionally, a keyword search using the name of the measured variable was used to search for any potentially missed information.
+An exception to this procedure was a question asking about the presence of example items.
+For this question, information from supplementary materials was uniquely considered as relevant.
+Another exception was the question regarding the replication of the original effect.
+Tables from the final report of each Many Labs project were used to answer that question.
+
+<!-- \@ref(sec:measures) didn't work for section corss-reference in the paragraph above-->
+
+After the data was initially coded according to the preregistered coding protocol, it was determined, based on discussion with the supervisor, that some of the initial ratings were possibly to stringent.
+As a result, some of the items in the protocol were reformulated, so that the conclusions from the resulting analyses were based on a more favourable judgement of QMPs.
+These changes included: accepting linked online appendices as a data source for example items; assuming that if no differences between replication and original are measurement is mentioned, that there is no difference, even if it is not explicitly clear; and generally simplified criteria for what constituted sufficiently clear reporting.
+The revision of the coding protocol happened after all the data were coded using the initial protocol.
+As a result the coded data using the initial protocol, and the coded data using the revised protocol are both available available on this thesis' OSF page: <https://osf.io/9r8yt/>.
+Both raw and processed formats are present.
+
+## Measures {#sec:measures}
 
 ### Measurement Error Measures
+Two main sources of information were used to test hypothesis 1, the reported reliability coefficient from the replication protocols, and the reported reliability coefficient in the original articles.
+The reported reliability coefficient is the score reliability reported per measure in the replication protocol or original article.
+Both the type (Cronbach's alpha, retest, interrater, etc.) and the value itself were extracted.
+
+The test of hypothesis 2 was based on different score reliabilities.
+As stated earlier, only score reliabilities of scalar measures with multiple items were included in the test of hypothesis 2.
+Because data was available for each lab location within a replication set, it was possible to calculate score reliabilities of a measure for each lab location.
+With location specific score reliabilities, it was possible to assess the variation of score reliabilities of the same measure across different contexts.
+
+Two different types of score reliabilities were calculated: Cronbach's alpha and omega.
+Cronbach's alpha was used as it is one of the most popular indices of score reliability [@cho2015cronbach].
+Omega was added to the analysis as it has been argued to be a more informative measure of score reliability, while also providing validity evidence for the scale [@crutzen2017scale; @deng2017testing].
+Cronbach's alpha and omega were calculated using the alpha and omega functions respectively in the psych R package [@revelle2022psych].
+Default arguments were used for both functions except the nfactors in the omega function, which was set to 1.
 
 ### Replicability Measure
+Hypothesis 3 as well as 5 specify an association between either score reliability or QMPs respectively, and replication success.
+Replication success was based on the test of the main effect of a study.
+However, the unit of measurement for the data in this thesis was a measure of a unique variable, not an effect.
+Fortunately, since only primary measures were included in the data, each measured a variable of the main effect, and as a result the measure remains related to the test of the main effect.
+Replication was based on the significance of the meta-analytic effect of the replication set as reported in its respective Many Labs report.
+An effect was considered replicated if the meta-analytic p-value was lower than .05, and in the same direction as the original effect.
+In all cases, meta-analytic significance of an effect meant that support in the direction of the original effect was found.
+
+The tests for hypotheses 4, 5, & 6 were all based on the number of QMPs per category that were determined by the research using the coding protocol.
+An overview of the QMP categories of the coding variables, based on @flake2020measurement, can be seen in Table INSERT TABLE 1 REF HERE
+
+INSERT TABLE 1 HERE
+
+Selection and creation share a category as the justifications and requirements in selecting a measure are similar to those for creating a new measure.
+Modification variables were only assessed when it was clear that the measure was modified from an original source in some way.
+The questions were all answered as either true, false, or not applicable.
+Questions related to modification had 'no modification' as an additional answer option, in case the specific aspect of the measure was explicitly not modified.
+Beside these quantitative variables, a total of four qualitative variables were also included to measure details surrounding measurement practices.
+These variables assessed: the specific version of the measure (if reported); whether and what previous materials were used for the study; what, if any, psychometric evidence beyond reliability score (e.g.
+factor analysis, IRT model, convergent validity) was provided; and whether it was specified or not that the measure was or was not modified.
+
+Two of the qualitative items have an equivalent in the coding key of @flake2022construct.
+Eleven out of twenty of the quantitative coding variables have an equivalent in @flake2022construct.
+Variables related to the specific measurement scaling and purpose in the paper, were omitted from the analyses of this thesis as they were deemed neither relevant for the analyses of this study, nor necessary in matching this study to the key results of @flake2022construct.
+Questions about more general measurement features such as the number of items and how scores were aggregated were altered from @flake2022construct to better fit the aims of this thesis.
+
+The tests for hypotheses 4, 5, & 6 were all based on QMP ratios, both total QMP ratios and ratios per QMP type.
+This ratio was based on the number of coded trues divided by the number of applicable QMPs.
+When a question was coded as true, this equated to a count of one QMP for that type and in total, whereas false equated to a zero.
+If coded as not applicable or no modification (for the modification items), this item was considered not applicable.
+Non applicable responses were not only counted as a zero, but additionally the denominator for calculating the ratio of QMPs was lowered by one.
+These ratios were preferred over counts, since non applicable items could thus be accounted for.
 
 ### QMP measures
+The same data as for the test of hypothesis 2 was used to check for the unidimensionality of the factor structure, as part of the exploratory analyses.
+A check for unidimensionality as validity evidence only makes sense if the measure was intended to be unidimensional.
+Therefore, for each replication for which data was available, the protocol was checked to ensure that the scores on each measure were meant to assess a single construct.
 
 ### Validity Measure
+The same data as for the test of hypothesis 2 was used to check for the unidimensionality of the factor structure, as part of the exploratory analyses.
+A check for unidimensionality as validity evidence only makes sense if the measure was intended to be unidimensional.
+Therefore, for each replication for which data was available, the protocol was checked to ensure that the scores on each measure were meant to assess a single construct.
 
 ## Analyses
+### Analyses Measurement Error
+Every hypothesis test in this thesis used an alpha significance cutoff of .05.
+No correction for multiple testing was applied, to avoid inflating type II error rate.
+The generally small sample size and consequently low power of these analyses meant that a smaller alpha would increase the number of false negatives.
+On top of that, these analyses were considered as exploratory.
+In this exploratory context, the rate of discovery of any potential true effects was given more value relative to decreasing any false positives compared to typical confirmatory research.
+That as a consequence obtaining false positives was more likely has been accepted, as false negatives were deemed more harmful to this study's aims.
 
-### Analyses Measurement Error
+The measurement error analyses testing hypotheses 1, 2, & 3 deviated from the preregistration for two main reasons: there were too few reported reliability coefficients, and too few multiple item scalar measures to calculate the reliability coefficients from.
+Because of the small sample size, the test for hypothesis 1 was changed, and the low power as a result of the sample size was accepted for hypothesis 2 & 3.
+This should be kept in mind while interpreting the results from these hypothesis tests.
+
+Thus for testing hypothesis 1, instead of comparing the reported Cronbach's alpha coefficient between original and replication, the total number of reported reliability coefficients were compared instead.
+This total also included reliability coefficients other than Cronbach's alpha.
+This comparison was implemented via a chi-square test using the base R stats package [@R2021R].
+
+The number of usable datasets to calculate reliability coefficients from was similarly limited in number.
+However, the number of datasets were still sufficient to be able to estimate the models of the planned analysis for hypothesis 2, albeit with a more exploratory goal than intended.
+
+Using the lmer function from the lme4 package [@bates2015lme4], a multilevel null model with the Cronbach's alpha or omega coefficient of a replication as dependent was specified, where the random intercept was grouped by replication set.
+The formulas for this model, where $alpha_{ij}$ represents the calculated Cronbach's alpha coefficient of a single study at one lab location with $i = 1,..., n_{locations}$ and $j = 1,...,n_{replications}$ look as follows:
+
+INSERT H2 FORMULA HERE
+
+The purpose of this analysis was to investigate variability in calculated reliability coefficients within and between replication sets.
+However, to the author’s knowledge no formal test exists as of the writing of this thesis for testing the significance of within group variance after controlling for between group variance.
+Instead the intraclass correlation (ICC) coefficient was calculated an indicator of within vs.
+between variability.
+Formula XXX shows the formula used to calculate the ICC.
+
+INSERT ICC FORMULA HERE
+
+A high ICC indicates low within group variance relative to between group variance, which would be in line with hypothesis 2.
+
+In order to test hypothesis 3, the average calculated Cronbach's alpha level within a replication set is used as a predictor of replication success.
+Replication success was either set to 1 if it reached meta analytic significance at an alpha of .05 in the same direction as that found in the original study, or 0 otherwise.
+This test aligns with a logistic regression model.
+With $i = 1,..., n_{replications}$, $p_{replicated}$ being binomially distributed, and $alpha$ referring to the averaged calculated Cronbach's alpha coefficient, the following regression equation was used to model the relation:
+
+INSERT H3 FORMULA HERE
+
+Where:
+
+INSET f(.) FORMULA HERE
+
+In this data, replication attempts at different lab locations can be seen as nested within a replication set.
+In order to see if this nesting might impact the analyses of hypothesis 3, multilevel logistic regression models were included as sensitivity checks.
+The dependent variable remains replication success at the replication set level, while Cronbach's alpha is no longer averaged across locations.
+The models used were a multilevel logistic random intercept and random slope model.
 
 ### Analyses QMPs
+The reported analyses were primarily based on the revised set of QMP data.
+The results using the original QMP data are mentioned when the results led to different conclusions.
+The analysis code for both the original and revised QMP data are available in R script on the OSF page of this thesis: <https://osf.io/9r8yt/>.
+
+Hypothesis 4, 5, & 6 were all tested using a model with the same dependent variable: total QMP ratio.
+In order to model a ratio dependent variable, beta regression was used.
+Beta regression models operate similarly to standard generalized linear models with similar interpretations of the results.
+What differentiates them is that they are suitable to model dependent variables with values in the interval of $(0, 1)$, meaning ratios.
+Furthermore, they are well suited for modelling heteroskedastic and asymmetrically distributed dependent variables [@cribari2010beta].
+The beta regression model was implemented using the betareg function within the betareg package [@cribari2010beta].
+Defaults were used for all function parameters besides the model formula and data.
+All beta regression models used the beta link function, which is as follows:
+
+INSERT BETALINK FORMULA HERE
+
+All of these models assume that the QMPs are the same across each replication set.
+The reason being that only one protocol was analysed per replication set, and several of the questions regarding QMPs focus solely on the reporting of relevant measurement information.
+This assumption was deemed likely, since each replication within a set was based on the same protocol.
+Furthermore, the goal of these protocols is to ensure that the measurement practices are equal across the different replication studies of the same original effect.
+
+To test hypothesis 4, the total QMP ratios between replication and original research was compared. The model formula for this test looked as follows:
+
+INSERT H4 FORMULA HERE
+
+Where $replication_{i}$ is a dummy coded variable, which was coded as 1 in case the reported QMP ratio belonged to a replications, and 0 if it belonged to an original study.
+For hypothesis 5 a similar formula was used:
+
+INSERT H5 FORMULA HERE
+
+Where $replicated_{i}$ is a dummy coded variable, which was coded as 1 if the meta-analytic effect in the replication set matches the original effect in direction at a significance alpha level of .05, and 0 otherwise.
+Note here that unlike in the test for hypothesis 4, $QMP\_ratio_{i}$ refers only to the QMP ratios of the replications, meaning that original article QMPs were not included in this analysis.
+
+The relationship between original article QMPs and replication protocol QMPs was modelled to test hypothesis 6.
+The outcome variable remains the same as in the model for hypothesis 5.
+The independent variable is changed to the QMP ratio for original articles.
+The resulting model formula is as follows:
+
+INSERT H6 FORMULA HERE
+
+These models had independence of observations as another assumption, the observations here referring to a replication set.
+this is known to be false since the data is nested within four separate Many Labs projects.
+In order to test if this nested structure might influence the relations described in hypothesis 5 & 6, random intercept and random slope multilevel models were implemented as sensitivity analyses for the tests of both hypothesis 5 & 6.
+In these models each replication set was treated as being nested in its respective Many Labs project.
+Worth noting is that currently the betareg package does not allow for estimation of multilevel models.
+As an approximation, Gaussian random-intercept multilevel models were implemented using the lmer function from the lme4 package [@bates2015lme4].
+The outcome QMP ratio variable was transformed using the logit link function (the default link function in the betareg package) to better fit the Gaussian model.
 
 ### Exploratory Analyses
+Follow-up analyses were preregistered for hypothesis 6.
+Using a similar model to the main hypothesis test with all unique combination of the five different QMP types being tested across original and replication data.
+The goal of these analyses was to see if there are any type specific carry-over effects in QMPs between original and replication.
+As these analyses are exploratory in nature, due to the large number of tests, the focus was on visualisation rather than inference.
+
+Finally, in order to present additional validity evidence alongside the analyses of Cronbach's alpha and omega coefficients, the unidimensionality of each measure was investigated.
+To test this, each multiple item scalar measure had their factor structure investigated on the entire measure data of the replication set.
+A single factor confirmatory factor analysis was implemented using the *fa* function from the *psych* package [@revelle2022psych] in R.
+The maximum likelihood factoring method was used, with defaults being used for all other function arguments.
+From this analysis, the RMSEA of the one factor solution was extracted.
+Additionally, a parallel test was conducted using the *fa.parallel* function also from the psych package.
+If either the RMSEA score < .08, or the parallel analysis returned a one factor solution, unidimensionality was coded as true, otherwise it was coded as false.
 

### 2023-11-03 Scripts/Manuscript/manuscript.Rmd
added the formulas to the manuscript.

@@
 r_refs("r-references.bib")
+
+### DON'T FORGET THAT I SHOULD REMOVE HERE THE R PACKAGE REFERENCES FROM MY REFERENCES BIB AND SHOULD HAVE THE R=REFERENCES BIB TAKE CARE OF THAT INSTEAD.
 ```
@@
 
-<!-- \@ref(sec:measures) didn't work for section corss-reference in the paragraph above-->
+<!-- @ref(sec:measures) didn't work for section corss-reference in the paragraph above-->
 
@@
 ### Measurement Error Measures
+
 Two main sources of information were used to test hypothesis 1, the reported reliability coefficient from the replication protocols, and the reported reliability coefficient in the original articles.
@@
 ### Replicability Measure
+
 Hypothesis 3 as well as 5 specify an association between either score reliability or QMPs respectively, and replication success.
@@
 ### QMP measures
+
 The same data as for the test of hypothesis 2 was used to check for the unidimensionality of the factor structure, as part of the exploratory analyses.
@@
 ### Validity Measure
+
 The same data as for the test of hypothesis 2 was used to check for the unidimensionality of the factor structure, as part of the exploratory analyses.
@@
 ## Analyses
+
 ### Analyses Measurement Error
+
 Every hypothesis test in this thesis used an alpha significance cutoff of .05.
@@
 
-INSERT H2 FORMULA HERE
+```{=tex}
+\begin{align*}
+& Level 1: alpha_{ij} = \beta_{0j} + e_{ij} \qquad\qquad\quad e_{ij} \sim N(0, \sigma_{e}^{2}) \\
+& Level 2: \beta_{0j} = \gamma_{00} + u_{0j} \qquad\qquad\qquad u_{0j} \sim N(0, \sigma_{u0}^{2}) \\
+& Mixed: alpha_{ij} = \gamma_{00} + u_{0j} + e_{ij}
+\end{align*}
+```
 
 The purpose of this analysis was to investigate variability in calculated reliability coefficients within and between replication sets.
-However, to the author’s knowledge no formal test exists as of the writing of this thesis for testing the significance of within group variance after controlling for between group variance.
+However, to the author's knowledge no formal test exists as of the writing of this thesis for testing the significance of within group variance after controlling for between group variance.
 Instead the intraclass correlation (ICC) coefficient was calculated an indicator of within vs.
 between variability.
-Formula XXX shows the formula used to calculate the ICC.
+The formula used to calculate the ICC is presented below.
 
-INSERT ICC FORMULA HERE
+$$ICC = \frac{u_{0j}}{(e_{ij} + u_{0j})}$$
 
@@
 
-INSERT H3 FORMULA HERE
+$$f(replicated_{i}) = \beta_{0} + \beta_{1} alpha_{i}$$
 
@@
 
-INSET f(.) FORMULA HERE
+$$f(.) = log\frac{p_{replicated}}{1 - p_{replicated}}$$
 
@@
 ### Analyses QMPs
+
 The reported analyses were primarily based on the revised set of QMP data.
@@
 
-INSERT BETALINK FORMULA HERE
+$$g(.) = (0, 1) \mapsto \mathbb{R}$$
 
@@
 
-INSERT H4 FORMULA HERE
+$$g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replication_{i}$$
 
@@
 
-INSERT H5 FORMULA HERE
+$$g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replicated_{i}$$
 
@@
 
-INSERT H6 FORMULA HERE
+$$g(QMP\_ratio\_replication_{i}) = \beta_{0} + \beta_{1} QMP\_ratio\_original_{i}$$
 
@@
 ### Exploratory Analyses
+
 Follow-up analyses were preregistered for hypothesis 6.
@@
 Additionally, a parallel test was conducted using the *fa.parallel* function also from the psych package.
-If either the RMSEA score < .08, or the parallel analysis returned a one factor solution, unidimensionality was coded as true, otherwise it was coded as false.
+If either the RMSEA score \< .08, or the parallel analysis returned a one factor solution, unidimensionality was coded as true, otherwise it was coded as false.
 

### 2023-11-03 Scripts/Manuscript/manuscript.Rmd
added the results minus tables and figures to the manuscript.

@@
 ```
-
 The purpose of this analysis was to investigate variability in calculated reliability coefficients within and between replication sets.
@@
 
+The mean sample size within the replications was 4844 participants (IQR = 3816).
+In the original articles the mean sample size was 244 (IQR = 140).
+In total, support was found for hypothesized effects of 34 of the 77 measures.
+Proportions of replication success per Many Labs project can be found in Table XXX.
+
+INSERT REPLICATION RATIO TABLE HERE
+
+Existing materials were used for 73 of the 77 measures in replications and for 28 in original studies.
+The specific version of the measure was reported for thirteen measures in replications, and nine measures in original articles.
+For those measures that were not based on existing materials, one in the replications and twelve in original articles clearly stated that they were newly created for the study.
+Only one measure in the original articles was modified from its original source during the data collection period, all other measures were modified before that, if at all.
+
 ## Reliability
+
+Figure XXX depicts the type of measure (single-item, multiple item, or not a scale), if for the measure reliability was reported or not, and what type of reliability coefficient was reported.
+Reliabilities were only assessed for multiple item measures, which were approximately equal between replication and original (35 and 38, respectively).
+Looking at the multiple item measures, four in the replication protocols and twelve in the original articles reported a reliability coefficient.
+The most commonly reported reliability coefficient was Cronbach's alpha, which accounted for three out of four reported reliabilities in the replication protocols, and eleven out of twelve in the original articles.
+
+INSERT RELIABILITY REPORTING FLOW DIAGRAM FIGURE
+
+A chi-squared test compared whether the number of reliabilities reported among multiple item measures differed between replications and original.
+Reliabilities were found to be more commonly reported in original articles compared to replication protocols ($\chi^{2}(1) = 4.09, p = 0.043$).
+These results are contradictory to hypothesis 1.
+
+The average Cronbach's alpha coefficient across replication sets was $0.618$ with a standard deviation of $0.554$, for omega the mean was $0.773$ with a standard deviation of $0.161$.
+Figure XXX shows the distributions of the Cronbach's alpha coefficients for each replication set separated by successful and unsuccessful replication.
+
+INSERT PLOT 34
+
+The between-group (across different replication set) variance and within-group (lab locations within a replication set) variance in the Cronbach's alpha coefficient were assessed using a multilevel model as specified in Formulas XXX, XXX, & XXX.
+The between-group and within-group variance for Cronbach's alpha were approximately $0.198$ and $0.044$ respectively.
+The resulting ICC, obtained using formula XXX, was approximately $0.819$.
+This suggests that variance was larger between replication sets than within.
+The same analysis for omega coefficients even showed a relatively larger degree of between group variance (between-group variance $= 0.034$, within-group variance $= 0.004$, ICC = $0.900$).
+Both results are in line with hypothesis 2, although caution in interpreting this result is advised due to the small sample size and the lack of an available inferential test.
+
+The relationship between reliability and replication success was primarily tested via logistic regression, with replication success as the dependent variable.
+Further sensitivity analyses were performed using multilevel logistic models, with each measure as an overarching group wherein its reliability at each lab location is nested.
+The results of the logistic and multilevel logistic models are shown in Table XXX for both Cronbach's alpha and omega reliability coefficients.
+
+INSERT REPLICABILITY AND RELIAIBLITY TESTS TABLE HERE
+
+Cronbach's alpha and omega did not significantly relate to replication success in the main logistic regression model (Cronbach's alpha: $B = -1.621, SD = 1.527, p = .288$; omega: $B = 0.495, SD = 3.776, p = .896$), nor in any of the multilevel sensitivity analyses models (see Table XXX).
+This is contradictory to the expectation in hypothesis 3.
+However, the results from these analyses should be evaluated with caution, given the small sample number of measures used to estimate these models.
 
@@
 
+The counts of the QMP ratio obtained for each QMP type (see Table XXX) are shown across the top layer of Figure XXX for both replication protocols and original articles.
+The overall number of counts for the QMP ratios of the QMP modification type were lower compared to the others, because only 52 out of 77 measures in replications, and only ten measures used in original studies were modified.
+The bottom layer of Figure XXX shows the overlayed distributions of the total QMP ratios from the replication protocols and original studies, with dots indicating each datapoint, and the line indicating the mean for either distribution.
+
+INSERT HERE 256
+
+Beta-regression was used to test the difference in QMP ratio between original articles and replication protocols.
+Results showed that original articles contained a significantly larger proportion of QMPs than replication protocols for the measures of the same effects ($B = -0.779, SD = 0.140, p < .001$).
+This result is in line with hypothesis 4.
+
+A similar beta-regression tested the association between replication success and QMP ratio in replication protocols.
+Results showed that successful replication significantly related to a decrease in the ratio of QMPs in replication protocols $\left(B = -0.588, SD = 0.212, p < .001 \right)$.
+Sensitivity analyses were performed using a random-intercept multilevel regression function.
+This model also found a significant association between replication success and QMP ratio $\left(B = -0.963, t(70.319) = -1.491, p = .011 \right)$.
+Both of these results are in line with hypothesis 5.
+However, the relationship in the multilevel model is no longer significant for QMP ratios obtained with the initial coding protocol $\left(B = -0.517, t(63.122) = -2.635, p = .140 \right)$.
+
+The relation between QMP ratios in the replication protocols and corresponding original articles were investigated using a beta regression model.
+It showed that total QMP ratio in the original article can significantly predict total QMP ratio in the subsequent replication ($B = 1.477, SD = 0.579, p < .001$), which provides some evidence in favor of hypothesis 6.
+However, this relation was not significant for the QMP ratios obtained with the initial protocol ($B = -0.387, SD = 0.511, p = 0.449$).
+Sensitivity analyses using a random intercept logistic multilevel model also found similar discrepancy in results between revised and initial protocol (revised protocol: $B = 0.249, t(74.473) = 1.498, p < 0.001$; initial protocol $B = -0.057, t(74.620) = -0.332, p = 0.741$).
+
+INSERT FIGURE 26 HERE
+
 ## Exploratory Results
+
+Planned exploratory analyses were preformed to expand on the test for hypothesis 6.
+The relationships between original article QMP ratios and replication protocol QMP ratios were investigated for each QMP type separately.
+Table XXX shows the results from these tests with the revised protocol QMP coding, while Table XXX shows the results for the QMP ratios obtained via the initial protocol.
+There were few significant relations and even fewer that are consistent between both coding protocols.
+The relations that are consistent are those between original article definition QMPs with replication selection and total QMPs, original article selection QMPs with replication total QMPs, and finally original article quantification QMPs with replication selection QMPs.
+All of these relations were positive across both coding protocols, illustrating that a greater QMP ratio of the specified type in an original article is associated with an increase in QMP ratio for the specific QMP type, or total QMP ratio in the replication protocol.
+
+INSERT QMP REPLICATION ASSOCIATION TESTS TABLE
+
+INSERT QMP ORIGINAL REPLICATION ASSOCIATION TESTS TABLE
+
+Figure XXX visually illustrates the relations of QMP ratios from different QMP types between replication protocols and original articles further.
+
+The unidimensionality of the measures used in the Many Labs projects was assessed through factor analyses, and evaluated based on the criteria discussed in section XXX.
+Suitable data for factor analyses was available for nineteen measures.
+These measures were the same as those shown in Figure XXX, with the addition of one more measure from [@cacioppo1983effects].
+A composite score based on the measurement responses was used for sixteen of the nineteen measures to form a single variable in the analyses, and were thus regarded as intended to be unidimensional.
+The number of dimensions for the remaining three were unclear.
+Sufficient fit of the unidimensional model was found for six out of the nineteen evaluated measures.
+However, as shown in Table XXX the unidimensional model did not hold for any measure data based on the parallel analysis test alone.
+Only the RMSEA $< .08$ criteria suggested evidence for single factor structures.
+
+INSERT FACTOR ANALYSES RESULTS TABLE HERE
 

### 2023-11-03 Scripts/Manuscript/manuscript.Rmd

@@
 
+In the current study, measurement error and QMPs were assessed in both replications and original research.
+These measurement related concepts were then linked to replicability in order to investigate them as potential causes inhibiting successful replications.
+The results of the tests for the hypotheses showed mixed results.
+However, when including exploratory and descriptive analyses, a clearer picture of the state of measurement in replication and original research emerges.
+
+Before interpreting of the results, it should be reiterated that the sample size for several analyses was smaller than what is generally recommended for such analyses.
+This holds especially for the tests of hypotheses 2, & 3, since the number of measures for which reliability could be calculated for these analyses was only eighteen.
+This was less than anticipated, which brings us to the first topic of the discussion.
+
 ## Quality of Measurement
+
+This thesis assessed the quality of measurement and measurement reporting in original and replication research by investigating the quality of measurement in the Many Labs projects.
+Findings were in line with similar investigations in the literature by @shaw2020measurement & @flake2022construct.
+These two studies found that sufficient validity evidence and reliability reporting for measures was lacking, even more so for replications than for original studies.
+The lack of support found for hypothesis 1 shows that this also held for this thesis' sample.
+In fact, support was found for an effect in the direction opposite to what was hypothesized in the preregistration, as the original articles reported reliability coefficients more often than replication studies.
+
+However, even the original articles only reported reliability for approximately one third of the used multiple item measures.
+Reliability coefficients were reported in such small numbers that the original analysis plan for hypothesis 1 was altered, from evaluating the reliability coefficient value to the number of times reliability was reported in an article or protocol.
+As a result, the interpretation of rejecting the hypothesis based on this new test changed compared to the preregistered test.
+Still, the test provides evidence towards the same point, which is that reliability evidence for the used measure is lacking more in replication protocols than in original articles, although most multiple item measures in original articles were also reported without reliability evidence.
+This shows that lack of reliability evidence is a widespread issue, something that has been shown in earlier literature on this topic [@vacha1999practices; @green2011recent].
+
+Furthermore, across measures used in both original and replication studies, less than half of the measures were multiple item scales.
+Research commonly made use of single item measures (see Figure XXX for more details), an observation that was also made by @shaw2020measurement.
+The use of these single item measures comes with risks, since by virtue of being singular they assume that whatever they are measuring is unidimensional, while not being able to test this assumption [@shaw2020measurement].
+This is potentially quite worrying given that the exploratory analyses of the multiple item measures, for which unidimensionality could be tested, showed only little support for unidimensionality of the measures used in replications.
+While the measures that were tested for unidimensionality were mostly used as single indicators in the analyses for the replication protocol, one could argue this does not necessarily mean these measures all assessed constructs with a unidimensional structure.
+For example, IQ is often used as a singular indicator, even though it consists of several factors [@weiss2013wisc].
+However, it should be noted that at least with respect to Many Labs 2, all of the measures that were considered unidimensional for the analyses in this thesis were also considered unidimensional in the investigation by @shaw2020measurement} who also observed a lack of unidimensionality evidence in their investigation of Many Labs 2.
+To conclude, there is an indication that validity evidence for measures used in replication research is lacking overall.
+
+Several results did show more promising findings for the way measurement related issues are treated in replications.
+Firstly, the support found for hypothesis 2 showed some evidence that most of the variability in reliability coefficients is between measures, rather than within measures across different locations.
+If variation in the reliability of a measurement across locations is little, it could indicate that the measurement operated similarly across these locations, which would make the scores from the different lab locations directly comparable and aggregatable.
+However, again the small sample number of measures for which reliability could be assessed does mean that this estimate remains uncertain.
+Secondly, most replication protocols clearly stated that their measure was either newly created or based on existing materials.
+Still, in most instances neither original nor replication provided information on the exact version of their measure.
+This may largely be due to the fact that many of the used measures were single-item, for which specifying the exact versions may not be seen as crucial because they more or less describe themselves.
+Finally, QMPs were overall less common in replication protocols than they were in original articles, supporting hypothesis 4.
+This runs counter to the findings of @shaw2020measurement & @flake2022construct, who found that measures came with less validity evidence in replications than in original studies, as the result of QMPs.
+
+The structured replication protocols that were used in the Many Labs projects, I suspect improved the reporting practices and measurement consistency in replication protocols compared to original articles.
+Most replication protocols even contained a section under each replicated study, which listed any deviations from the original and as a result many potential QMPs were averted.
+[@protzko2020high] already demonstrated that transparent reporting of methodology before conducting research can improve the robustness of psychological science, and I believe the same holds true here.
 
@@
 
+Besides assessing the overall quality of measurement reporting, this thesis also investigated if the reliability of a measure, and QMPs can impact replicability.
+First of all, contrary to expectations (see Hypothesis 3), less reliable measures were not associated with a decrease in replicability.
+This result is surprising, since @stanley2014expectations demonstrated the potential impact that measurement error can have on the veracity of determining replication success based on a significance test without attenuating for measurement error.
+The significance test cut-off criteria that was used in this thesis to assess replication success similarly did not attenuate for measurement error, and thus results in line with the simulation studies of @stanley2014expectations were expected.
+
+While no evidence for hypothesis 3 was found, caution in interpreting the test results is needed.
+The number of measures for which reliability was calculated was quite low (eighteen for Cronbach's alpha, fifteen for omega), it could be that the test was simply underpowered to detect the effect.
+On the other hand, it might be that the detrimental influence of measurement error on interpretations of replication results is small in large scale replication projects.
+Across the multiple replications, measurement error's influence on the effect could have been cancelled out at the meta-analytic level.
+This would require the measurement error to be random and small, and as a result the average value of the effect and the error around would remain similar, thus not altering the result of the meta-analytic significance test.
+
+Results regarding the relationship between QMPs and replicability were more in line with expectations.
+In particular, support was found for hypothesis 5, showing that an increase in total QMP ratio was associated with a decrease in replicability.
+Existing literature has already warned about the potential detrimental effects of QMPs on replications [@shaw2020measurement; @flake2022construct].
+This result provides further evidence supporting these claims.
+However, the association was only significant when data was used from the revised coding protocol, data from the initial protocol, which was more stringent in its assessment of QMP, did not indicate a significant association with replicability.
+
+Similarly, the test for hypothesis 6 showed inconsistent results between the revised and initial coding protocols.
+Only for the revised protocol data was an increase in total QMPs in the original study associated with an increase in total QMPs in the protocol of the replication for that study.
+The result obtained with the data from the revised protocol are in line with expectations.
+If information on measurement is lacking or the measure is poorly motivated in a study, then any subsequent replication attempt will lack information needed match its measurement to the original.
+Even if it does match the original, when the measure itself is a poor indicator of the assessed variable or construct, both the original and replication data obtained from this measure may not substantially relate to the investigated psychological phenomenon the original study set out to investigate [@flake2022construct].
+However, the fact that the conclusions were different based on the protocol makes it difficult to determine the exact nature of the influence of original study QMPs on replication protocol QMPs.
+
+Further analyses based on the QMP ratios of each specific type indicated that across both the initial and revised coding protocols together, only selection, definition, and quantification QMPs in the original article related significantly to selection type QMPs, total QMPs, or both in the replication (see Tables XXX & XXX).
+
+It could be that original articles have to provide a clear definition as well as details on the scale, in order for a replication to be able to justify selecting the measure.
+A replication may also be in general more dependent on the original article for information on the definition of the constructs and the choice of measurement, compared to a description of the Operationalisation, quantification, and any modifications.
+These former are features of a measurement, which while preferably similar in a replication to the original, can and should be reported in the replication protocol even if the original article does not contain the details on these features itself.
+However, these are just speculations as the results showed no clear relations between different QMP types across original and replication (see Figure XXX), and testing of causal links was not possible with this data.
+
+For both hypothesis 5 & 6, the results were in line with expectations, but only for the revised coding protocol.
+Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol.
+The initial protocol was revised because the ratings based on that protocol were consider to stringent, and as a result, several items were reformulated so that criteria for what constituted sufficiently clear reporting were lowered.
+This meant that in the revised protocol, coded QMPs would need to clearly inhibit evaluation of the measurement, whereas for the initial protocol some aspects of the measurement reporting which were coded as questionable, may have been questionable only to a small degree.
+As a consequence, QMPs coded with the revised protocol represent measurement practices that represent on average more questionable practices than QMPs coded with the initial protocol.
+With this in mind, the difference between total QMP ratio of initial and revised protocol can be seen as a form of effect size difference.
+It could be that only replication QMPs that represented robust violations of good measurement practices significantly lower the probability of successful replication.
+In that case, a stronger relation between replicability and QMPs would be found with the revised protocol, since these QMPs represented more clearly questionable practices in measurement reporting than QMPs coded with the initial protocol, which would explain the disparate results that were found.
+
 ## Limitations & Future Research
+
+The design of this thesis came with certain limitations.
+First of all, there was no experimental manipulation included.
+As a result, the ability to investigate the exact causal links between QMPs and replicability was limited.
+This thesis was intended to be exploratory in nature, and thus did not focus on causal analyses.
+However, future research establishing causal links will prove to be very beneficial in improving the understanding of the relationships between measurement issues and replicability.
+
+Another limitation of this study is that the results differed based on whether data from the revised or the initial coding protocol was used.
+As a result, any relationship between QMPs and replicability remains uncertain.
+The revised coding protocol was adapted from the initial coding protocol before any analyses were performed, it is however still possible that a change in protocol may have biased results.
+Future research investigating this topic should use a coding protocol which is verified independently by several researchers on a sample of articles and protocols first, before being used to code the QMP data that will be analysed.
+As a first step, the coding protocol from this thesis and the coding key from @flake2022construct can be used as a basis.
+
+It is important to also consider whether or not replication protocols and research articles can be fairly compared in terms of QMPs.
+Articles are generally longer than a study's description within a replication protocol, and as a result it seems reasonable to expect research articles to generally contain more measurement details than replication protocols.
+Regardless, this thesis assumed that a replication protocol is comparable to an article in providing an overview of the measure and how it was used, as it is the only comparable source for such information that would otherwise be difficult to find anywhere else.
+This assumption seems practical if not tenable when the replication protocol is the only available sources of measurement details.
+However, in case more detailed information on a measurement is available in other sources, such as an online appendix, it could be important data to include when assessing QMPs.
+This research did not make use of any online appendices in assessing QMPs, future research may wish to include them and other sources as part of the data.
+
+As a last note on QMPs, it is worth highlighting the way the QMP ratios were calculated.
+The total QMP ratio was based on the counts for each of the items from all the different QMP types divided by the total number of applicable questions.
+However, for each QMP type the number of items was different.
+This means that QMP types with a larger number of items (such as operationalisation) had a greater impact on the total QMP ratio than QMP types with a smaller number of items (such as definition).
+If the impact for each QMP type on each other and replicability is considered equally important, the total QMP ratio may not be considered a valid indice.
+On the other hand, it could be that each item should be considered equally important rather than each QMP type.
+For this study, the protocol was made and the analyses were conducted under the assumption that each item had equal weight.
+However, this is an assumption this article cannot provide evidence for.
+
+The small sample of measures for which reliability coefficients and unidimensional factor structure could be assessed limited the degree to which substantial interpretations can be made from the reliability and validity analyses.
+While future research will also unlikely be able to increase the number of multiple item measures used by replications, future research can broaden their analyses to include a larger number of replications, or take into account a type of measure which this thesis mostly ignored in the analyses of reliability and validity: single-item measures.
+
+Reliability assessment for single item measures differs substantially from multiple item measures [@wanous1996estimating], and for this reason was not included as part of the analyses for this thesis.
+Furthermore, single items cannot be tested on unidimensionality, since a single item is already assumed to measure only a single dimension by definition.
+However, future research might consider methods specifically designed to assess reliability and validity of single item measures.
+This could prove to be a worthwhile contribution, given the proportionally large number of single item measures that were encountered in the data for this thesis (see Figure XXX).
+
+Finally, this paper investigated the consistency of measures, by assessing the variance in reliability across different labs wherein the measure was conducted, and comparing it to the variance in reliability between the different measures.
+Besides comparing the degree of reliability across labs, it is also possible to assess whether a measure assesses the same underlying construct across lab locations.
+This can be done through measurement invariance testing.
+Measurement invariance is a concept in latent factor modelling that illustrates the extent to which the relationship between items and factors is dependent on some other variable, usually a group [@mellenbergh1989item].
+@shaw2020measurement investigated measurement invariance for the responses to measures at each lab location within the replication sets of Many Labs 2.
+Investigations similar to this have also been suggested for future replication projects [@flake2022construct].
+For these reasons, future research should consider measurement invariance tests, if assessing measurement consistency in replications across different labs.
 
@@
 
+Taking all the findings together, the following assessments will be relevant to consider for future replication research.
+With respect to the quality of measurement reporting, the small number of reported reliabilities, small number of reported psychometric validity evidence, and lack of unidimensionality evidence for data aggregated to a single indicator corroborate findings by @shaw2020measurement & @flake2022construct.
+Evidence supporting the measures used in replication should be reported more frequently, so that they can be evaluated and the validity of replication research can be improved.
+
+There are additional validity issues in measurement as the result of QMPs.
+While it is debatable whether or not $17.9\%$ average QMP ratio in replications is too much, the association between original paper and replication protocol QMPs demonstrates how a lack of information for measurement in the original can spill over to the reporting in replications.
+This could lead to issues for replication attempts if the measure in an original article has poor reliability and validity.
+In that case, the tests in the original article are based on data from measures that do not accurately capture the construct they were intended to measure.
+The results of any direct replication attempt will face the same issues, and as a consequence the replication is unlikely to provide a relevant test of a psychological theory, as the original study itself was not a robust test of that psychological theory to begin with [@isager2020deciding, @isager2021deciding, @nuijten2022assessin].
+Thus, future replicators should first evaluate the quality of the measurement (reporting) in an article before deciding to replicate it.
+
+In case the quality appears low, replication attempts can still proceed with some adjustments.
+One option is to change the focus of the replication to be conceptual rather than direct.
+In that case the measure and the operationalisation can be freely altered from the original, which means that a more sufficient test of the theory can be developed.
+If deemed necessary, a direct replication can always be performed later based on the conceptual replication.
+In that case, the direct replication will be able to provide a sufficient test of a psychological theory, on the condition that the conceptual replication's test improvements led to it becoming a sufficient test.
+
+The results also suggest that the use of structured protocols in the reporting of measurement may be an effective way of reducing QMPs, and increasing the reporting of reliability and validity evidence.
+However, even in the Many Labs projects, which made use of structured protocols to report their measures, low reliability and validity evidence reporting was found.
+These protocols could therefore still increase the attention they give to reporting reliability and validity evidence.
+In particular, Figure XXX shows descriptive evidence that replication protocols are lacking in definition and selection evidence.
+Furthermore, since replications must base their measures on those of the original articles they are replicating, it is important that articles chosen for replications provide clear evidence on what is being measured, how it is scored, why it was chosen or why it was constructed the way it is, and how it is used in practice.
+It is these last two aspects that original articles appear to particularly be underreporting (See Figure XXX).
+When original articles do not report their measurement details, replication attempts cannot guarantee a direct replication of the original.
+By improving the quality of measurement reporting in original articles, the validity of both original research results and future replication attempts would increase.
+It would be particularly important to focus on remedying strong violations of good measurement reporting, as these were shown to have a significant detrimental impact on replicability.
+This suggests that even small but critical improvements in the reporting of measurement information could lead to a substantial increase in the replicability of psychological science.
+
 # Conclusion
+
+Overall, the observed quality of measurement and frequency of measurement reporting in psychological research and replications was low, which is in line with other research on the topic.
+Improvements in the reporting on measurement are needed for both original and replication research.
+The measure source, content, and how it was used should be described in detail, and evidence illustrating the reliability and validity of the measure should be provided.
+Not only would the clarity of research improve, higher quality of measurement reporting in replications was shown to be related to an increase in replicability of the findings related to that measure.
+Tentative evidence was also found for spill-over effects of the quality of measurement reporting from original study to replications.
+These results combined suggest that improvements in the reporting of measurements are necessary in both replications and original articles.
+Furthermore, future replicators should carefully consider the quality of measurement in a study before attempting a direct replication, even considering a conceptual replication instead if the measurement in the original was not of sufficient quality.
+However, the evidence for the relationship between measurement quality and replicability was not robustly identified, and future research will be needed to confirm the exact nature of this relationship.
 

### 2023-11-03 Scripts/Manuscript/manuscript.Rmd
added code to load in the retrieved ML data to soon be able to store the data.

@@
 
-This manuscript uses the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency.
-All code and XXX data are available at <https://github.com/CasGoos/WORCSPersonalTemplate.git>.
-
 This is an example of a non-essential citation [\@ @vanlissaWORCS2021]. If you change the rendering function to `worcs::cite_essential`, it will be removed.
@@
 # Seed for random number generation
-set.seed(31102023)
+set.seed(17042023)
 knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
@@
 Any deviations from the preregistration are explicitly mentioned in the text.
+This manuscript was generated using the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency.
+All code and XXX data are available at <https://github.com/CasGoos/measurement_and_replication.git>.
 

### 2023-11-03 Scripts/prepare_data.R

@@ -2,24 +2,92 @@
 # (e.g., an SPSS, Excel, or SAS-file), and convert it to a data.frame. Then,
 # use the function open_data(your_data_frame) or closed_data(your_data_frame)
 # to store the data. When starting out, this project will be set up to generate
-# a fake dataset fro the pre-registration.
+# a fake dataset for the pre-registration.
 
 # set-up -----------------------------------------------------------------------
 library(worcs) # reproducible workflow template package
-set.seed(30102023) # seed for random number generators
+library(foreign)
+library(readxl)
+set.seed(17042023) # seed for random number generators
 
 
-# Data-generating --------------------------------------------------------------
+
+# Data Loading -----------------------------------------------------------------
+### ML Retrieved Data
+## List of measures X.Y.Z to extract, where X is Many Labs number, Y is study
+## in the order as reported in the Many Labs protocol, & Z is the specific 
+## measure from study Y as in line with the order of the measurement coding.
+# Likely reliability: 1.10, 1.11, 1.12.3, 2.4.1, 2.4.2, 2.8, 2.10.1, 2.12.1, 
+# 2.12.2, 2.12.3, 2.15, 2.19.2, 2.23, 3.7.1, 3.7.2, 3.8.1, 3.8.2, 5.7, 5.9.1
+# Likely factor: 1.10, 1.11, 1.12.3, 2.4.1, 2.4.2, 2.8, 2.10.1, 2.12.1, 2.12.2,
+# 2,12,3, 2.15, 2.19.2, 2.23, 3.7.1, 3.7.2, 3.8.1, 3.8.2, 5.7, 5.9.1
+# Maybe reliability: 1.3, 1.12.1, 2.2, 2.3, 2.19.1, 2.20, 3.2.1, 3.5, 5.1.1, 
+# 5.1.2, 5.4, 5.5.1, 5.5.2
+# Maybe factor: 1.3, 1.12.1, 2.3, 2.19.1, 2.20, 3.2.1, 3.5, 5.1.1, 5.1.2, 5.4,
+# 5.5.1, 5.5.2
+
+## ML 1
+Data_ML1 <- read.spss("Data/LoadingInputData/MLRetrievedData/Full_Dataset_De-Identified.sav", 
+                      to.data.frame = TRUE, use.value.labels = FALSE)
 
 
[…]

### 2023-11-06 Scripts/prepare_data.R
made slight adjustements to project structure, and added the coded data to the prepare data file loading.

@@ -1,93 +1,0 @@
-# In this file, write the R-code necessary to load your original data file
-# (e.g., an SPSS, Excel, or SAS-file), and convert it to a data.frame. Then,
-# use the function open_data(your_data_frame) or closed_data(your_data_frame)
-# to store the data. When starting out, this project will be set up to generate
-# a fake dataset for the pre-registration.
-
-# set-up -----------------------------------------------------------------------
-library(worcs) # reproducible workflow template package
-library(foreign)
-library(readxl)
-set.seed(17042023) # seed for random number generators
-
-
-
-# Data Loading -----------------------------------------------------------------
-### ML Retrieved Data
-## List of measures X.Y.Z to extract, where X is Many Labs number, Y is study
-## in the order as reported in the Many Labs protocol, & Z is the specific 
-## measure from study Y as in line with the order of the measurement coding.
-# Likely reliability: 1.10, 1.11, 1.12.3, 2.4.1, 2.4.2, 2.8, 2.10.1, 2.12.1, 
-# 2.12.2, 2.12.3, 2.15, 2.19.2, 2.23, 3.7.1, 3.7.2, 3.8.1, 3.8.2, 5.7, 5.9.1
-# Likely factor: 1.10, 1.11, 1.12.3, 2.4.1, 2.4.2, 2.8, 2.10.1, 2.12.1, 2.12.2,
-# 2,12,3, 2.15, 2.19.2, 2.23, 3.7.1, 3.7.2, 3.8.1, 3.8.2, 5.7, 5.9.1
-# Maybe reliability: 1.3, 1.12.1, 2.2, 2.3, 2.19.1, 2.20, 3.2.1, 3.5, 5.1.1, 
-# 5.1.2, 5.4, 5.5.1, 5.5.2
-# Maybe factor: 1.3, 1.12.1, 2.3, 2.19.1, 2.20, 3.2.1, 3.5, 5.1.1, 5.1.2, 5.4,
-# 5.5.1, 5.5.2
-
-## ML 1
-Data_ML1 <- read.spss("Data/LoadingInputData/MLRetrievedData/Full_Dataset_De-Identified.sav", 
-                      to.data.frame = TRUE, use.value.labels = FALSE)
-
-
-## ML 2
-# 2.2
[…]

### 2023-11-06 Scripts/process_data.R

@@ -1,0 +1,103 @@
+# In this file, write the R-code necessary to load your original data file
+# (e.g., an SPSS, Excel, or SAS-file), and convert it to a data.frame. Then,
+# use the function open_data(your_data_frame) or closed_data(your_data_frame)
+# to store the data. When starting out, this project will be set up to generate
+# a fake dataset for the pre-registration.
+
+# set-up -----------------------------------------------------------------------
+library(worcs) # reproducible workflow template package
+library(foreign)
+library(readxl)
+set.seed(17042023) # seed for random number generators
+
+
+
+# Data Loading -----------------------------------------------------------------
+### ML Retrieved Data
+## List of measures X.Y.Z to extract, where X is Many Labs number, Y is study
+## in the order as reported in the Many Labs protocol, & Z is the specific 
+## measure from study Y as in line with the order of the measurement coding.
+# Likely reliability: 1.10, 1.11, 1.12.3, 2.4.1, 2.4.2, 2.8, 2.10.1, 2.12.1, 
+# 2.12.2, 2.12.3, 2.15, 2.19.2, 2.23, 3.7.1, 3.7.2, 3.8.1, 3.8.2, 5.7, 5.9.1
+# Likely factor: 1.10, 1.11, 1.12.3, 2.4.1, 2.4.2, 2.8, 2.10.1, 2.12.1, 2.12.2,
+# 2,12,3, 2.15, 2.19.2, 2.23, 3.7.1, 3.7.2, 3.8.1, 3.8.2, 5.7, 5.9.1
+# Maybe reliability: 1.3, 1.12.1, 2.2, 2.3, 2.19.1, 2.20, 3.2.1, 3.5, 5.1.1, 
+# 5.1.2, 5.4, 5.5.1, 5.5.2
+# Maybe factor: 1.3, 1.12.1, 2.3, 2.19.1, 2.20, 3.2.1, 3.5, 5.1.1, 5.1.2, 5.4,
+# 5.5.1, 5.5.2
+
+## ML 1
+Data_ML1 <- read.spss("Data/LoadingInputData/MLRetrievedData/Full_Dataset_De-Identified.sav", 
+                      to.data.frame = TRUE, use.value.labels = FALSE)
+
+
+## ML 2
+# 2.2
+Data_2.2 <- read.csv("Data/LocalInputData/MLRetrievedData/Kay_1_study_global_include_all_CLEAN_CASE.csv")
[…]

### 2023-11-06 Scripts/Manuscript/manuscript.Rmd
added the storing of the raw data as functions.

@@
 # Code below loads the processed data. The raw data was prepared for analysis in 'prepare_data.R.
-# load_data(worcs_directory = "../../Data/AnalysisData")
+# load_data()
 
@@
 
-<!-- @ref(sec:measures) didn't work for section corss-reference in the paragraph above-->
+<!-- @ref(sec:measures) didn't work for section cross-reference in the paragraph above-->
 
@@
 Both raw and processed formats are present.
+
+```{r}
+open_data(data = Data_ML1, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(Data_ML1))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", deparse(substitute(Data_ML1))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", deparse(substitute(Data_ML1))), ".yml")) 
+```
 

### 2023-11-06 Scripts/prepare_data.R

@@ -69,7 +69,7 @@ Data_5.1 <- read_excel("Data/LocalInputData/MLRetrievedData/ML5 Alb 5 Revised Pr
 Data_5.4 <- read.spss("Data/LocalInputData/MLRetrievedData/dataset_LoBue_raw.sav", 
                       to.data.frame = TRUE)
 # 5.5.1 & 5.5.2
-Data_5.5.1 <- read.csv("Data/LocalInputData/MLRetrievedData/Payne replication Data/Genova_ML5.csv")
+Data_5.5 <- read.csv("Data/LocalInputData/MLRetrievedData/Payne replication Data/Genova_ML5.csv")
 # 5.7 
 Data_5.7 <- read.csv("Data/LocalInputData/MLRetrievedData/ml5_computed_dataset.csv")
 # 5.9.1
@@ -88,16 +88,94 @@ Coded_Data_Vignette_raw <- read.csv("Data/LocalInputData/CodedData/Coded Data (V
 
 
 # Data Storing -----------------------------------------------------------------
-# replace iris with your own dataframe
-open_data(data = iris, filename = paste0(paste0(
-  "Data/InputData/", deparse(substitute(iris))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/InputData/codebook_", deparse(substitute(iris))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/InputData/value_labels_", deparse(substitute(iris))), ".yml")) 
+closed_data(data = Data_ML1, filename = paste0(paste0(
+  "Data/InputData/", deparse(substitute(Data_ML1))), ".csv"),
+  codebook = NULL, value_labels = NULL) 
+
+closed_data(data = Data_2.2, filename = paste0(paste0(
+  "Data/InputData/", deparse(substitute(Data_2.2))), ".csv"),
+  codebook = NULL, value_labels = NULL) 
+
+closed_data(data = Data_2.3, filename = paste0(paste0(
+  "Data/InputData/", deparse(substitute(Data_2.3))), ".csv"),
+  codebook = NULL, value_labels = NULL) 
+
+closed_data(data = Data_2.4.1, filename = paste0(paste0(
+  "Data/InputData/", deparse(substitute(Data_2.4.1))), ".csv"),
+  codebook = NULL, value_labels = NULL) 
+
+closed_data(data = Data_2.4.2, filename = paste0(paste0(
[…]

### 2023-11-06 Scripts/source_script.R
added the source script

@@ -1,9 +1,612 @@
 # source_script
 
-# sample function to be deleted
-get_number <- function(){
-  return(rnorm(1, 100, 15))
+# QMP Related Functions --------------------------------------------------------
+### Hypothesis 2 
+# data load and prep function
+data_prep_H2 <- function(Data_Original, Data_Replications){
+  # data prep for model (using the (y * (n - 1) + 0.5) / n to adjust for any 0 
+  # or 1 proportions in the data).
+  Data_H2 <- rbind(Coded_Data_Original_Shortened, Coded_Data_Replications)
+  Data_H2$QMP_ratio <- ((Data_H2$QMP_ratio * (77 - 1) + 0.5) / 77)
+  Data_H2$QMP_REV_ratio <- ((Data_H2$QMP_REV_ratio * (77 - 1) + 0.5) / 77)
+  
+  return(Data_H2)
+}
+
+# modelling and results returning function
+Model_H2 <- function(Data){
+  return_list <- list(first = 0, revised = 0)
+  # running the models one with none revised QMP ratio's and one with
+  Model_H2 <- betareg(QMP_ratio ~ rep_org, data = Data)
+  return_list[[1]] <- summary(Model_H2)$coefficients
+  
+  Model_H2_REV <- betareg(QMP_REV_ratio ~ rep_org, data = Data)
+  return_list[[2]] <- summary(Model_H2_REV)$coefficients
+  
+  return(return_list) 
 }
 
 
-# source("Scripts/source_script.R")
+### Hypothesis 5
+# data load and prep function
+data_prep_H5 <- function(Data_Replications){
+  # data prep for model (using the (y * (n - 1) + 0.5) / n to adjust for any 0 
+  # or 1 proportions in the data).
+  Data_H5 <- Coded_Data_Replications[-c(53:55),]
+  Data_H5$hypothesis_support <- droplevels(Data_H5$hypothesis_support)
+  levels(Data_H5$hypothesis_support) <- c(FALSE, TRUE)
+  Data_H5$hypothesis_support <- as.logical(Data_H5$hypothesis_support)
+  Data_H5$QMP_ratio <- ((Data_H5$QMP_ratio * (77 - 1) + 0.5) / 77)
+  Data_H5$QMP_REV_ratio <- ((Data_H5$QMP_REV_ratio * (77 - 1) + 0.5) / 77)
+  Data_H5$many_labs_version <- as.factor(Data_H5$many_labs_version)
+  
[…]

### 2023-11-06 Scripts/prepare_data.R
added the raw data to the project.

@@ -27,7 +27,7 @@ set.seed(17042023) # seed for random number generators
 # 5.5.1, 5.5.2
 
 ## ML 1
-Data_ML1 <- read.spss("Data/LoadingInputData/MLRetrievedData/Full_Dataset_De-Identified.sav", 
+Data_ML1 <- read.spss("Data/LocalInputData/MLRetrievedData/Full_Dataset_De-Identified.sav", 
                       to.data.frame = TRUE, use.value.labels = FALSE)
 
 
@@ -69,7 +69,7 @@ Data_5.1 <- read_excel("Data/LocalInputData/MLRetrievedData/ML5 Alb 5 Revised Pr
 Data_5.4 <- read.spss("Data/LocalInputData/MLRetrievedData/dataset_LoBue_raw.sav", 
                       to.data.frame = TRUE)
 # 5.5.1 & 5.5.2
-Data_5.5 <- read.csv("Data/LocalInputData/MLRetrievedData/Payne replication Data/Genova_ML5.csv")
+Data_5.5 <- read.csv("Data/LocalInputData/MLRetrievedData/Genova_ML5.csv")
 # 5.7 
 Data_5.7 <- read.csv("Data/LocalInputData/MLRetrievedData/ml5_computed_dataset.csv")
 # 5.9.1
@@ -90,79 +90,79 @@ Coded_Data_Vignette_raw <- read.csv("Data/LocalInputData/CodedData/Coded Data (V
 # Data Storing -----------------------------------------------------------------
 closed_data(data = Data_ML1, filename = paste0(paste0(
   "Data/InputData/", deparse(substitute(Data_ML1))), ".csv"),
-  codebook = NULL, value_labels = NULL) 
+  codebook = NULL, value_labels = NULL, synthetic = FALSE) 
 
 closed_data(data = Data_2.2, filename = paste0(paste0(
   "Data/InputData/", deparse(substitute(Data_2.2))), ".csv"),
-  codebook = NULL, value_labels = NULL) 
+  codebook = NULL, value_labels = NULL, synthetic = FALSE) 
 
 closed_data(data = Data_2.3, filename = paste0(paste0(
   "Data/InputData/", deparse(substitute(Data_2.3))), ".csv"),
-  codebook = NULL, value_labels = NULL) 
+  codebook = NULL, value_labels = NULL, synthetic = FALSE) 
 
 closed_data(data = Data_2.4.1, filename = paste0(paste0(
   "Data/InputData/", deparse(substitute(Data_2.4.1))), ".csv"),
[…]

### 2023-11-06 Data/IntermediateData/codebook_coded_data_original.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:01:41.370241"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = 'asis')
```

A codebook contains documentation and metadata describing the contents, structure, and layout of a data file.

## Dataset description
The data contains 80 cases and 91 variables.

## Codebook

```{r}
summaries <- read.csv("codebook_coded_data_original.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### Legend

* __Name__: Variable name
* __type__: Data type of the variable
* __missing__: Proportion of missing values for this variable
* __unique__: Number of unique values
* __mean__: Mean value
* __median__: Median value
* __mode__: Most common value (for categorical variables, this shows the frequency of the most common category)
* **mode_value**: For categorical variables, the value of the most common category
* __sd__: Standard deviation (measure of dispersion for numerical variables
* __v__: Agresti's V (measure of dispersion for categorical variables)
* __min__: Minimum value
* __max__: Maximum value
* __range__: Range between minimum and maximum value
* __skew__: Skewness of the variable
* __skew_2se__: Skewness of the variable divided by 2*SE of the skewness. If this is greater than abs(1), skewness is significant
* __kurt__: Kurtosis (peakedness) of the variable
* __kurt_2se__: Kurtosis of the variable divided by 2*SE of the kurtosis. If this is greater than abs(1), kurtosis is significant.

This codebook was generated using the [Workflow for Open Reproducible Code in Science (WORCS)](https://osf.io/zcvbs/)

### 2023-11-06 Data/IntermediateData/codebook_coded_data_original_shortened.Rmd
added the data cleaning functions

--- 2023-11-06 Data/IntermediateData/codebook_coded_data_original.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 15:01:41.370241"
+title: "Codebook created on 2023-11-06 at 2023-11-06 15:01:43.074438"
 output: github_document
@@
 ## Dataset description
-The data contains 80 cases and 91 variables.
+The data contains 77 cases and 91 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_coded_data_original.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_coded_data_original_shortened.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-06 Data/IntermediateData/codebook_coded_data_replications.Rmd
added the data cleaning functions

--- 2023-11-06 Data/IntermediateData/codebook_coded_data_original_shortened.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 15:01:43.074438"
+title: "Codebook created on 2023-11-06 at 2023-11-06 15:01:38.034183"
 output: github_document
@@
 ```{r}
-summaries <- read.csv("codebook_coded_data_original_shortened.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_coded_data_replications.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-06 Data/IntermediateData/codebook_data_1.10_clean.Rmd
added the data cleaning functions

--- 2023-11-06 Data/IntermediateData/codebook_coded_data_original.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 15:01:41.370241"
+title: "Codebook created on 2023-11-06 at 2023-11-06 14:59:48.763887"
 output: github_document
@@
 ## Dataset description
-The data contains 80 cases and 91 variables.
+The data contains 6344 cases and 9 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_coded_data_original.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_1.10_clean.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-06 Data/IntermediateData/codebook_data_1.11_clean.Rmd
added the data cleaning functions

--- 2023-11-06 Data/IntermediateData/codebook_data_1.10_clean.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 14:59:48.763887"
+title: "Codebook created on 2023-11-06 at 2023-11-06 14:59:53.640585"
 output: github_document
@@
 ## Dataset description
-The data contains 6344 cases and 9 variables.
+The data contains 6344 cases and 5 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_1.10_clean.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_1.11_clean.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-06 Data/IntermediateData/codebook_data_1.12.3.1_clean.Rmd
added the data cleaning functions

--- 2023-11-06 Data/IntermediateData/codebook_data_1.11_clean.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 14:59:53.640585"
+title: "Codebook created on 2023-11-06 at 2023-11-06 14:59:55.690988"
 output: github_document
@@
 ## Dataset description
-The data contains 6344 cases and 5 variables.
+The data contains 6344 cases and 7 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_1.11_clean.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_1.12.3.1_clean.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-06 Data/IntermediateData/codebook_data_1.12.3.2_clean.Rmd
added the data cleaning functions

--- 2023-11-06 Data/IntermediateData/codebook_data_1.12.3.1_clean.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 14:59:55.690988"
+title: "Codebook created on 2023-11-06 at 2023-11-06 14:59:59.490912"
 output: github_document
@@
 ```{r}
-summaries <- read.csv("codebook_data_1.12.3.1_clean.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_1.12.3.2_clean.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-06 Data/IntermediateData/codebook_data_1.3_clean.Rmd
added the data cleaning functions

--- 2023-11-06 Data/IntermediateData/codebook_data_1.10_clean.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 14:59:48.763887"
+title: "Codebook created on 2023-11-06 at 2023-11-06 14:59:47.592344"
 output: github_document
@@
 ```{r}
-summaries <- read.csv("codebook_data_1.10_clean.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_1.3_clean.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-06 Data/IntermediateData/codebook_data_2.10.1_clean.Rmd
added the data cleaning functions

--- 2023-11-06 Data/IntermediateData/codebook_data_1.3_clean.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 14:59:47.592344"
+title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:03.000904"
 output: github_document
@@
 ## Dataset description
-The data contains 6344 cases and 9 variables.
+The data contains 6234 cases and 7 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_1.3_clean.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_2.10.1_clean.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-06 Data/IntermediateData/codebook_data_2.12.1_clean.Rmd
added the data cleaning functions

--- 2023-11-06 Data/IntermediateData/codebook_data_1.3_clean.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 14:59:47.592344"
+title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:04.937275"
 output: github_document
@@
 ## Dataset description
-The data contains 6344 cases and 9 variables.
+The data contains 6905 cases and 6 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_1.3_clean.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_2.12.1_clean.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-06 Data/IntermediateData/codebook_data_2.12.2_clean.Rmd
added the data cleaning functions

--- 2023-11-06 Data/IntermediateData/codebook_data_1.3_clean.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 14:59:47.592344"
+title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:08.026037"
 output: github_document
@@
 ## Dataset description
-The data contains 6344 cases and 9 variables.
+The data contains 6905 cases and 11 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_1.3_clean.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_2.12.2_clean.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-06 Data/IntermediateData/codebook_data_2.12.3_clean.Rmd
added the data cleaning functions

--- 2023-11-06 Data/IntermediateData/codebook_data_2.12.2_clean.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:08.026037"
+title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:10.467392"
 output: github_document
@@
 ```{r}
-summaries <- read.csv("codebook_data_2.12.2_clean.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_2.12.3_clean.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-06 Data/IntermediateData/codebook_data_2.15_clean.Rmd
added the data cleaning functions

--- 2023-11-06 Data/IntermediateData/codebook_data_2.12.1_clean.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:04.937275"
+title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:11.960889"
 output: github_document
@@
 ## Dataset description
-The data contains 6905 cases and 6 variables.
+The data contains 7890 cases and 6 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_2.12.1_clean.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_2.15_clean.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-06 Data/IntermediateData/codebook_data_2.20_clean.Rmd
added the data cleaning functions

--- 2023-11-06 Data/IntermediateData/codebook_data_2.15_clean.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:11.960889"
+title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:15.161093"
 output: github_document
@@
 ## Dataset description
-The data contains 7890 cases and 6 variables.
+The data contains 7396 cases and 21 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_2.15_clean.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_2.20_clean.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-06 Data/IntermediateData/codebook_data_2.23_clean.Rmd
added the data cleaning functions

--- 2023-11-06 Data/IntermediateData/codebook_data_2.15_clean.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:11.960889"
+title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:17.859936"
 output: github_document
@@
 ## Dataset description
-The data contains 7890 cases and 6 variables.
+The data contains 7001 cases and 6 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_2.15_clean.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_2.23_clean.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-06 Data/IntermediateData/codebook_data_3.2.1.1_clean.Rmd
added the data cleaning functions

--- 2023-11-06 Data/IntermediateData/codebook_data_2.23_clean.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:17.859936"
+title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:19.053091"
 output: github_document
@@
 ## Dataset description
-The data contains 7001 cases and 6 variables.
+The data contains 1620 cases and 6 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_2.23_clean.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_3.2.1.1_clean.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-06 Data/IntermediateData/codebook_data_3.2.1.2_clean.Rmd
added the data cleaning functions

--- 2023-11-06 Data/IntermediateData/codebook_data_2.23_clean.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:17.859936"
+title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:21.765723"
 output: github_document
@@
 ## Dataset description
-The data contains 7001 cases and 6 variables.
+The data contains 1666 cases and 6 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_2.23_clean.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_3.2.1.2_clean.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-06 Data/IntermediateData/codebook_data_3.7.1_clean.Rmd
added the data cleaning functions

--- 2023-11-06 Data/IntermediateData/codebook_data_2.23_clean.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:17.859936"
+title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:24.954882"
 output: github_document
@@
 ## Dataset description
-The data contains 7001 cases and 6 variables.
+The data contains 2429 cases and 6 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_2.23_clean.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_3.7.1_clean.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-06 Data/IntermediateData/codebook_data_3.7.2_clean.Rmd
added the data cleaning functions

--- 2023-11-06 Data/IntermediateData/codebook_data_3.7.1_clean.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:24.954882"
+title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:26.441641"
 output: github_document
@@
 ## Dataset description
-The data contains 2429 cases and 6 variables.
+The data contains 3178 cases and 7 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_3.7.1_clean.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_3.7.2_clean.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-06 Data/IntermediateData/codebook_data_3.8.2_clean.Rmd
added the data cleaning functions

--- 2023-11-06 Data/IntermediateData/codebook_data_3.7.2_clean.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:26.441641"
+title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:29.432437"
 output: github_document
@@
 ## Dataset description
-The data contains 3178 cases and 7 variables.
+The data contains 3208 cases and 3 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_3.7.2_clean.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_3.8.2_clean.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-06 Data/IntermediateData/codebook_data_5.1.1_clean.Rmd
added the data cleaning functions

--- 2023-11-06 Data/IntermediateData/codebook_data_3.8.2_clean.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:29.432437"
+title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:31.816934"
 output: github_document
@@
 ## Dataset description
-The data contains 3208 cases and 3 variables.
+The data contains 471 cases and 22 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_3.8.2_clean.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_5.1.1_clean.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-06 Data/IntermediateData/codebook_data_5.4_clean.Rmd
added the data cleaning functions

--- 2023-11-06 Data/IntermediateData/codebook_data_5.1.1_clean.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:31.816934"
+title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:33.922557"
 output: github_document
@@
 ## Dataset description
-The data contains 471 cases and 22 variables.
+The data contains 556 cases and 25 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_5.1.1_clean.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_5.4_clean.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-06 Data/IntermediateData/codebook_data_5.7_clean.Rmd
added the data cleaning functions

--- 2023-11-06 Data/IntermediateData/codebook_data_5.4_clean.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:33.922557"
+title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:36.662196"
 output: github_document
@@
 ## Dataset description
-The data contains 556 cases and 25 variables.
+The data contains 5476 cases and 11 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_5.4_clean.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_5.7_clean.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-06 Data/IntermediateData/codebook_data_5.9.1_clean.Rmd
added the data cleaning functions

--- 2023-11-06 Data/IntermediateData/codebook_data_5.4_clean.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:33.922557"
+title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:38.16236"
 output: github_document
@@
 ## Dataset description
-The data contains 556 cases and 25 variables.
+The data contains 341 cases and 8 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_5.4_clean.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_5.9.1_clean.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-06 Scripts/Manuscript/manuscript.Rmd
added the source script
added the data cleaning functions

--- 2023-11-03 Scripts/Manuscript/manuscript.Rmd
@@
 # loading R libraries
-library("papaja")
-library("worcs")
+library(papaja)
+library(worcs)
+library(psych)
 
@@
 # Code below loads the processed data. The raw data was prepared for analysis in 'prepare_data.R.
-# load_data(worcs_directory = "../../Data/AnalysisData")
+load_data()
 
@@
 
+```{r Cleaning Replication Datasets Data}
+##### Data already available, code does not need to be run!
+### ML 1
+# 1.3
+data_1.3_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[22:29])
+colnames(data_1.3_clean)[1] <- "g"
+# 1.10
+data_1.10_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[108:115])
+colnames(data_1.10_clean)[1] <- "g"
+# 1.11
+data_1.11_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[73:76])
+colnames(data_1.11_clean)[1] <- "g"
+# 1.12.1
+# not found
+# 1.12.3
+data_1.12.3.1_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[54:59])
+colnames(data_1.12.3.1_clean)[1] <- "g"
+data_1.12.3.2_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[60:65])
+colnames(data_1.12.3.2_clean)[1] <- "g"
+
+### ML 2
+# 2.2
+data_2.2_clean <- cbind(as.factor(data_2.2[[5]]), data_2.2[6:11])
+colnames(data_2.2_clean)[1] <- "g"
+# 2.3
+# data does not appear suitable
+# 2.4.1
+data_2.4.1_clean <- cbind(as.factor(data_2.4.1[[5]]), data_2.4.1[6:11])
+colnames(data_2.4.1_clean)[1] <- "g"
+# 2.4.2
+data_2.4.2_clean <- cbind(as.factor(data_2.4.2[[5]]), data_2.4.2[6:14])
+colnames(data_2.4.2_clean)[1] <- "g"
+# 2.8.2
+data_2.8.2_clean <- cbind(as.factor(data_2.8.2[[6]]), data_2.8.2[9:13])
+colnames(data_2.8.2_clean)[1] <- "g"
+# 2.10.1
+data_2.10.1_clean <- cbind(as.factor(data_2.10.1[[5]]), data_2.10.1[6:11])
+colnames(data_2.10.1_clean)[1] <- "g"
+# 2.12.1
+data_2.12.1_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(6,7,8,9,10,31,32,33,34,35)]) 
+data_2.12.1_clean[3465:6905,2:6] <- data_2.12.1_clean[3465:6905,7:11]
+data_2.12.1_clean <- data_2.12.1_clean[1:6]
+colnames(data_2.12.1_clean)[1] <- "g"
+# 2.12.2
+data_2.12.2_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(11,14,15,18,19,22,24,27,28,29,36,39,40,43,44,47,49,52,53,54)]) 
+data_2.12.2_clean[3465:6905,2:11] <- data_2.12.2_clean[3465:6905,12:21]
+data_2.12.2_clean <- data_2.12.2_clean[1:11]
+colnames(data_2.12.2_clean)[1] <- "g"
+# 2.12.3
+data_2.12.3_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(12,13,16,17,20,21,23,25,26,30,37,38,41,42,45,46,48,50,51,55)]) 
+data_2.12.3_clean[3465:6905,2:11] <- data_2.12.3_clean[3465:6905,12:21]
+data_2.12.3_clean <- data_2.12.3_clean[1:11]
+colnames(data_2.12.3_clean)[1] <- "g"
+# 2.15
+data_2.15_clean <- cbind(as.factor(data_2.15[[5]]), data_2.15[8:12])
+colnames(data_2.15_clean)[1] <- "g"
+# 2.19.1
+# difficult to extract
+# 2.19.2
+# difficult to extract
+# 2.20
+data_2.20_clean <- cbind(as.factor(data_2.20[[5]]), data_2.20[6:45] - 1) 
+data_2.20_clean[3729:7396,2:21] <- data_2.20_clean[3729:7396,22:41]
+data_2.20_clean <- data_2.20_clean[1:21] 
+colnames(data_2.20_clean)[1] <- "g"
+# 2.23
+data_2.23_clean <- cbind(as.factor(data_2.23[[5]]), data_2.23[c(7,8,12,13,15)])
+colnames(data_2.23_clean)[1] <- "g"
+
+### ML 3
+# 3.2.1
+data_3.2.1 <- cbind(as.factor(data_ml3[[1]]), data_ml3[77:86] - 1)
+data_3.2.1.1_clean <- na.omit(data_3.2.1[1:6])
+colnames(data_3.2.1.1_clean)[1] <- "g"
+data_3.2.1.2_clean <- na.omit(data_3.2.1[c(1, 7:11)])
+colnames(data_3.2.1.2_clean)[1] <- "g"
+# 3.5
+# data appears unusable
+# 3.7.1
+data_3.7.1_clean <- na.omit(cbind(as.factor(data_ml3[[1]]), data_ml3[38:42]))
+colnames(data_3.7.1_clean)[1] <- "g"
+# 3.7.2
+data_3.7.2_clean <- na.omit(cbind(as.factor(data_ml3[[1]]), data_ml3[89:94]))
+colnames(data_3.7.2_clean)[1] <- "g"
+# 3.8.1
+# a single measure was reported
+# 3.8.2
+data_3.8.2_clean <- na.omit(cbind(as.factor(data_ml3[[1]]), data_ml3[29:30])) 
+colnames(data_3.8.2_clean)[1] <- "g"
+
+### ML 5
+# 5.1.1
+data_5.1.1_clean <- cbind(as.factor(data_5.1[[2]]), data_5.1[13:33])
+colnames(data_5.1.1_clean)[1] <- "g"
+# 5.1.2
+# difficult to separate .1 from .2
+# 5.4
+data_5.4_clean <- cbind(as.factor(data_5.4[[1]]), data_5.4[18:41])
+colnames(data_5.4_clean)[1] <- "g"
+# 5.5.1 & 5.5.2
+# from this dataset it appears that this data will be difficult to use.
+# 5.5.2
+# also difficult to use
+# 5.7 
+data_5.7_clean <- cbind(as.factor(data_5.7[[3]]), data_5.7[c(25, 34, 35, 36, 37, 38, 39, 40, 41, 42)])
+colnames(data_5.7_clean)[1] <- "g"
+# 5.9.1
+data_5.9.1_clean <- na.omit(cbind(as.factor(data_5.9.1[[4]]), data_5.9.1[c(79, 83, 87, 91, 95, 98, 101)]))
+colnames(data_5.9.1_clean)[1] <- "g"
+
+### to summarize
+# total number of likely usable: 15 (1.10, 1.11, 1.12.3.1, 1.12.3.2, 2.10.1, 
+# 2.12.1, 2.12.2, 2.12.3, 2.15, 2.23, 3.7.1, 3.7.2, 3.8.2, 5.7, 5.9.1)
+# total number of maybe usable: 6 (1.3, 2.20, 3.2.1.1, 3.2.1.2, 5.1.1, 5.4)
+# total alpha coefficient comparison usable: 3 
+#                                           1.11: 0.82
+#                                           3.7.2: 0.67
+#                                           5.9.1: 0.84
+
+### Saving to Intermediate Data Folder
+closed_data(data = data_1.3_clean, filename = "Data/IntermediateData/data_1.3_clean.csv",
+            codebook = "Data/IntermediateData/codebook_data_1.3_clean.Rmd", 
+            value_labels = "Data/IntermediateData/value_labels_data_1.3_clean.yml", 
+            synthetic = FALSE)
+
+closed_data(data = data_1.10_clean, filename = "Data/IntermediateData/data_1.10_clean.csv",
+            codebook = "Data/IntermediateData/codebook_data_1.10_clean.Rmd", 
+            value_labels = "Data/IntermediateData/value_labels_data_1.10_clean.yml", 
+            synthetic = FALSE)
+
+closed_data(data = data_1.11_clean, filename = "Data/IntermediateData/data_1.11_clean.csv",
+            codebook = "Data/IntermediateData/codebook_data_1.11_clean.Rmd", 
+            value_labels = "Data/IntermediateData/value_labels_data_1.11_clean.yml", 
+            synthetic = FALSE)
+
+closed_data(data = data_1.12.3.1_clean, filename = "Data/IntermediateData/data_1.12.3.1_clean.csv",
+            codebook = "Data/IntermediateData/codebook_data_1.12.3.1_clean.Rmd", 
+            value_labels = "Data/IntermediateData/value_labels_data_1.12.3.1_clean.yml", 
+            synthetic = FALSE)
+
+closed_data(data = data_1.12.3.2_clean, filename = "Data/IntermediateData/data_1.12.3.2_clean.csv",
+            codebook = "Data/IntermediateData/codebook_data_1.12.3.2_clean.Rmd", 
+            value_labels = "Data/IntermediateData/value_labels_data_1.12.3.2_clean.yml", 
+            synthetic = FALSE)
+
+closed_data(data = data_2.10.1_clean, filename = "Data/IntermediateData/data_2.10.1_clean.csv",
+            codebook = "Data/IntermediateData/codebook_data_2.10.1_clean.Rmd", 
+            value_labels = "Data/IntermediateData/value_labels_data_2.10.1_clean.yml", 
+            synthetic = FALSE)
+
+closed_data(data = data_2.12.1_clean, filename = "Data/IntermediateData/data_2.12.1_clean.csv",
+            codebook = "Data/IntermediateData/codebook_data_2.12.1_clean.Rmd", 
+            value_labels = "Data/IntermediateData/value_labels_data_2.12.1_clean.yml", 
+            synthetic = FALSE)
+
+closed_data(data = data_2.12.2_clean, filename = "Data/IntermediateData/data_2.12.2_clean.csv",
+            codebook = "Data/IntermediateData/codebook_data_2.12.2_clean.Rmd", 
+            value_labels = "Data/IntermediateData/value_labels_data_2.12.2_clean.yml", 
+            synthetic = FALSE)
+
+closed_data(data = data_2.12.3_clean, filename = "Data/IntermediateData/data_2.12.3_clean.csv",
+            codebook = "Data/IntermediateData/codebook_data_2.12.3_clean.Rmd", 
+            value_labels = "Data/IntermediateData/value_labels_data_2.12.3_clean.yml", 
+            synthetic = FALSE)
+
+closed_data(data = data_2.15_clean, filename = "Data/IntermediateData/data_2.15_clean.csv",
+            codebook = "Data/IntermediateData/codebook_data_2.15_clean.Rmd", 
+            value_labels = "Data/IntermediateData/value_labels_data_2.15_clean.yml", 
+            synthetic = FALSE)
+
+closed_data(data = data_2.20_clean, filename = "Data/IntermediateData/data_2.20_clean.csv",
+            codebook = "Data/IntermediateData/codebook_data_2.20_clean.Rmd", 
+            value_labels = "Data/IntermediateData/value_labels_data_2.20_clean.yml", 
+            synthetic = FALSE)
+
+closed_data(data = data_2.23_clean, filename = "Data/IntermediateData/data_2.23_clean.csv",
+            codebook = "Data/IntermediateData/codebook_data_2.23_clean.Rmd", 
+            value_labels = "Data/IntermediateData/value_labels_data_2.23_clean.yml", 
+            synthetic = FALSE)
+
+closed_data(data = data_3.2.1.1_clean, filename = "Data/IntermediateData/data_3.2.1.1_clean.csv",
+            codebook = "Data/IntermediateData/codebook_data_3.2.1.1_clean.Rmd", 
+            value_labels = "Data/IntermediateData/value_labels_data_3.2.1.1_clean.yml", 
+            synthetic = FALSE)
+
+closed_data(data = data_3.2.1.2_clean, filename = "Data/IntermediateData/data_3.2.1.2_clean.csv",
+            codebook = "Data/IntermediateData/codebook_data_3.2.1.2_clean.Rmd", 
+            value_labels = "Data/IntermediateData/value_labels_data_3.2.1.2_clean.yml", 
+            synthetic = FALSE)
+
+closed_data(data = data_3.7.1_clean, filename = "Data/IntermediateData/data_3.7.1_clean.csv",
+            codebook = "Data/IntermediateData/codebook_data_3.7.1_clean.Rmd", 
+            value_labels = "Data/IntermediateData/value_labels_data_3.7.1_clean.yml", 
+            synthetic = FALSE)
+
+closed_data(data = data_3.7.2_clean, filename = "Data/IntermediateData/data_3.7.2_clean.csv",
+            codebook = "Data/IntermediateData/codebook_data_3.7.2_clean.Rmd", 
+            value_labels = "Data/IntermediateData/value_labels_data_3.7.2_clean.yml", 
+            synthetic = FALSE)
+
+closed_data(data = data_3.8.2_clean, filename = "Data/IntermediateData/data_3.8.2_clean.csv",
+            codebook = "Data/IntermediateData/codebook_data_3.8.2_clean.Rmd", 
+            value_labels = "Data/IntermediateData/value_labels_data_3.8.2_clean.yml", 
+            synthetic = FALSE)
+
+closed_data(data = data_5.1.1_clean, filename = "Data/IntermediateData/data_5.1.1_clean.csv",
+            codebook = "Data/IntermediateData/codebook_data_5.1.1_clean.Rmd", 
+            value_labels = "Data/IntermediateData/value_labels_data_5.1.1_clean.yml", 
+            synthetic = FALSE)
+
+closed_data(data = data_5.4_clean, filename = "Data/IntermediateData/data_5.4_clean.csv",
+            codebook = "Data/IntermediateData/codebook_data_5.4_clean.Rmd", 
+            value_labels = "Data/IntermediateData/value_labels_data_5.4_clean.yml", 
+            synthetic = FALSE)
+
+closed_data(data = data_5.7_clean, filename = "Data/IntermediateData/data_5.7_clean.csv",
+            codebook = "Data/IntermediateData/codebook_data_5.7_clean.Rmd", 
+            value_labels = "Data/IntermediateData/value_labels_data_5.7_clean.yml", 
+            synthetic = FALSE)
+
+closed_data(data = data_5.9.1_clean, filename = "Data/IntermediateData/data_5.9.1_clean.csv",
+            codebook = "Data/IntermediateData/codebook_data_5.9.1_clean.Rmd", 
+            value_labels = "Data/IntermediateData/value_labels_data_5.9.1_clean.yml", 
+            synthetic = FALSE)
+
+```
+
 ### Preregistered Replication Protocols
@@
 In the case of Many Labs 5 the original studies refer to the studies which first tested the effect to be replicated, not the earlier replication attempts of the same effects in the RPP [@osc2015estimating].
+
+```{r Cleaning Coded Data}
+##### Data already available, code does not need to be run!
+# Selecting the relevant rows and columns for the data
+coded_data_initial_sel <- coded_data_initial_raw[3:160, 18:57]
+coded_data_revised_sel <- coded_data_revised_raw[3:160, 18:38]
+coded_data_vignette_raw <- coded_data_vignette_raw[3:160, 2]
+
+# Combining the datasets
+coded_data_full <- cbind(coded_data_initial_sel, 
+                         cbind(coded_data_revised_sel, coded_data_vignette_raw))
+
+# filtering out unnecessary double columns
+coded_data_full <- cbind(coded_data_full[, 1:40], coded_data_full[, 45:62])
+
+### creating the cleaned dataset using the functions in the source code 
+coded_data_clean <- calculating(recoding(restructuring(fixing(
+  renaming(coded_data_full)))))
+
+### Saving to Intermediate Data Folder
+# Splitting data into replication and original
+coded_data_replications <- coded_data_clean[1:77,]
+coded_data_original <- coded_data_clean[78:157,]
+
+# difference in dataset row number is due to the fact that the moral foundations
+# questionnaire in original 2.4 is reported using all 5 of its factors, whereas
+# in replication 2.4 only the two overarching groups of binding and 
+# individualizing foundations are described.
+# For that reason a shortened original dataset will be used for any direct
+# comparisons between original and replication coding.
+coded_data_original_shortened <- coded_data_original[c(1:17, 19, 22:80),] 
+coded_data_original_shortened[c(18,19),5] <- 
+  c("individualizing moral foundations", "binding moral foundations")
+coded_data_original_shortened[18,13] <- NA
+coded_data_original_shortened[19,13] <- NA
+
+# exporting cleaned data
+open_data(data = coded_data_replications, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(coded_data_replications))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(coded_data_replications))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(coded_data_replications))), ".yml"))
+
+open_data(data = coded_data_original, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(coded_data_original))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(coded_data_original))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(coded_data_original))), ".yml"))
+
+open_data(data = coded_data_original_shortened, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(coded_data_original_shortened))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(coded_data_original_shortened))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(coded_data_original_shortened))), ".yml"))
+
+```
 
@@
 Both raw and processed formats are present.
+
+```{r}
+
+```
 
@@
 Therefore, for each replication for which data was available, the protocol was checked to ensure that the scores on each measure were meant to assess a single construct.
+
+```{r Check for Reliability and Validity Testability}
+## Checking the measures to recalculate the reliability and factor analysis for.
+## The question: "Are they psychometrics scales or not?", is key here.
+View(coded_data_replications)
+
+# Likely reliability: 1.10, 1.11, 1.12.3, 2.4.1, 2.4.2, 2.8.2, 2.10.1, 2.12.1, 
+# 2.12.2, 2.12.3, 2.15, 2.19.2, 2.23, 3.7.1, 3.7.2, 3.8.1, 3.8.2, 5.7, 5.9.1
+# Likely factor: 1.10, 1.11, 1.12.3, 2.4.1, 2.4.2, 2.8.2, 2.10.1, 2.12.1, 2.12.2,
+# 2,12,3, 2.15, 2.19.2, 2.23, 3.7.1, 3.7.2, 3.8.1, 3.8.2, 5.7, 5.9.1
+# Maybe reliability: 1.3, 1.12.1, 2.2, 2.3, 2.19.1, 2.20, 3.2.1, 3.5, 5.1.1, 
+# 5.1.2, 5.4, 5.5.1, 5.5.2
+# Maybe factor: 1.3, 1.12.1, 2.3, 2.19.1, 2.20, 3.2.1, 3.5, 5.1.1, 5.1.2, 5.4,
+# 5.5.1, 5.5.2
+
+# 1.9 is difficult, might be a scale as dv rather than voting behaviour.
+```
 

### 2023-11-06 Scripts/prepare_data.R

@@ -88,93 +88,74 @@ Coded_Data_Vignette_raw <- read.csv("Data/LocalInputData/CodedData/Coded Data (V
 
 
 # Data Storing -----------------------------------------------------------------
-closed_data(data = Data_ML1, filename = paste0(paste0(
-  "Data/InputData/", deparse(substitute(Data_ML1))), ".csv"),
+closed_data(data = Data_ML1, filename = "Data/InputData/Data_ML1.csv",
   codebook = NULL, value_labels = NULL, synthetic = FALSE) 
 
-closed_data(data = Data_2.2, filename = paste0(paste0(
-  "Data/InputData/", deparse(substitute(Data_2.2))), ".csv"),
+closed_data(data = Data_2.2, filename = "Data/InputData/Data_2.2.csv",
   codebook = NULL, value_labels = NULL, synthetic = FALSE) 
 
-closed_data(data = Data_2.3, filename = paste0(paste0(
-  "Data/InputData/", deparse(substitute(Data_2.3))), ".csv"),
+closed_data(data = Data_2.3, filename = "Data/InputData/Data_2.3.csv",
   codebook = NULL, value_labels = NULL, synthetic = FALSE) 
 
-closed_data(data = Data_2.4.1, filename = paste0(paste0(
-  "Data/InputData/", deparse(substitute(Data_2.4.1))), ".csv"),
+closed_data(data = Data_2.4.1, filename = "Data/InputData/Data_2.4.1.csv",
   codebook = NULL, value_labels = NULL, synthetic = FALSE) 
 
-closed_data(data = Data_2.4.2, filename = paste0(paste0(
-  "Data/InputData/", deparse(substitute(Data_2.4.2))), ".csv"),
+closed_data(data = Data_2.4.2, filename = "Data/InputData/Data_2.4.2.csv",
   codebook = NULL, value_labels = NULL, synthetic = FALSE) 
 
-closed_data(data = Data_2.8.2, filename = paste0(paste0(
-  "Data/InputData/", deparse(substitute(Data_2.8.2))), ".csv"),
+closed_data(data = Data_2.8.2, filename = "Data/InputData/Data_2.8.2.csv",
   codebook = NULL, value_labels = NULL, synthetic = FALSE) 
 
-closed_data(data = Data_2.10.1, filename = paste0(paste0(
-  "Data/InputData/", deparse(substitute(Data_2.10.1))), ".csv"),
[…]

### 2023-11-06 Scripts/source_script.R

@@ -1,5 +1,223 @@
 # source_script
 
+# Data Cleaning Functions ------------------------------------------------------
+### renaming the columns and rows to accommodate the joining of the three 
+### datasets.
+renaming <- function(Data){
+  # renaming columns
+  colnames(Data) <- 
+    c("many_labs_version", "rep_org", "title", "measure_name", "variable_name",
+      "multi", "appearance", "N", "N_items", "hypothesis_support", 
+      "reliability_type", "reliability_type_text", "reliability_coeff",
+      "def1", "op_version", "op_1", "op_2", "op_3", "op_4", "op_5", 
+      "sel_existing", "sel_existing_text", "sel_1", "sel_2", "sel_3", "sel_4",
+      "sel_psychometric_evidence", "sel_psychometric_evidence_text", "quant_1",
+      "quant_2", "quant_3", "quant_4", "mod_check", "mod_1", "mod_2", "mod_3",
+      "mod_4", "mod_5", "mod_6", "mod_time", "op_1_REV", "op_2_REV",
+      "op_5_REV", "sel_1_REV", "sel_3_REV", "sel_psychometric_evidence_REV", 
+      "sel_psychometric_evidence_text_REV", "quant_1_REV", "quant_2_REV", 
+      "quant_3_REV", "mod_check_REV", "mod_1_REV", "mod_2_REV", "mod_3_REV", 
+      "mod_4_REV", "mod_5_REV", "mod_6_REV", "inseperable_material")
+  
+  # renaming rows
+  rownames(Data) <- 1:nrow(Data)
+  
+  return(Data)
+}
+
+
+### Fixing some coding misses.
+fixing <- function(Data){
+  Data$variable_name[79] <- "quote attribution effect"
+  Data$N[3] <- "5284"
+  Data$N[158] <- "1202"
+  Data$reliability_type[50] <- "Not Reported"
+  Data$reliability_type[127] <- "Not Reported"
+  Data$op_1[145] <- "False"
+  Data$op_3[121] <- "True"
+  Data$op_5[157] <- "True"
+  Data$sel_1[59] <- "True"
+  Data$quant_2[113] <- "True"
+  Data$mod_time[1] <- "Before"
+  
+  return(Data)
+}
+
+
+
+### Moving around of entries
+restructuring <- function(Data){
+  # removing missing entry 77
+  Data <- data.frame(Data)[-77,]
+  
[…]

### 2023-11-07 Data/AnalysisData/codebook_Plot_26_data.Rmd
added the final data preparation step, and the models for H1 and H3.

--- 2023-11-06 Data/IntermediateData/codebook_data_5.9.1_clean.Rmd
@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:38.16236"
+title: "Codebook created on 2023-11-07 at 2023-11-07 10:59:14.419679"
 output: github_document
@@
 ## Dataset description
-The data contains 341 cases and 8 variables.
+The data contains 1925 cases and 4 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_5.9.1_clean.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_Plot_26_data.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-07 Data/AnalysisData/codebook_data_H1.Rmd
added the final data preparation step, and the models for H1 and H3.

--- 2023-11-07 Data/AnalysisData/codebook_Plot_26_data.Rmd
@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 10:59:14.419679"
+title: "Codebook created on 2023-11-07 at 2023-11-07 10:58:46.380662"
 output: github_document
@@
 ## Dataset description
-The data contains 1925 cases and 4 variables.
+The data contains 154 cases and 91 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_Plot_26_data.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_H1.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-07 Data/AnalysisData/codebook_data_H2.Rmd
added the final data preparation step, and the models for H1 and H3.

--- 2023-11-07 Data/AnalysisData/codebook_data_H1.Rmd
@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 10:58:46.380662"
+title: "Codebook created on 2023-11-07 at 2023-11-07 10:52:58.610667"
 output: github_document
@@
 ## Dataset description
-The data contains 154 cases and 91 variables.
+The data contains 154 cases and 90 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_H1.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_H2.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-07 Data/AnalysisData/codebook_data_H3.Rmd
added the final data preparation step, and the models for H1 and H3.

--- 2023-11-07 Data/AnalysisData/codebook_data_H2.Rmd
@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 10:52:58.610667"
+title: "Codebook created on 2023-11-07 at 2023-11-07 11:00:04.653618"
 output: github_document
@@
 ## Dataset description
-The data contains 154 cases and 90 variables.
+The data contains 713 cases and 3 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_H2.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_H3.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-07 Data/AnalysisData/codebook_data_H4_avg.Rmd
added the final data preparation step, and the models for H1 and H3.

--- 2023-11-07 Data/AnalysisData/codebook_data_H3.Rmd
@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 11:00:04.653618"
+title: "Codebook created on 2023-11-07 at 2023-11-07 11:03:47.475669"
 output: github_document
@@
 ## Dataset description
-The data contains 713 cases and 3 variables.
+The data contains 18 cases and 3 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_H3.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_H4_avg.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-07 Data/AnalysisData/codebook_data_H4_multiple.Rmd
added the final data preparation step, and the models for H1 and H3.

--- 2023-11-07 Data/AnalysisData/codebook_data_H3.Rmd
@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 11:00:04.653618"
+title: "Codebook created on 2023-11-07 at 2023-11-07 11:03:41.005817"
 output: github_document
@@
 ## Dataset description
-The data contains 713 cases and 3 variables.
+The data contains 713 cases and 4 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_H3.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_H4_multiple.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-07 Data/AnalysisData/codebook_data_H5.Rmd
added the final data preparation step, and the models for H1 and H3.

--- 2023-11-07 Data/AnalysisData/codebook_data_H3.Rmd
@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 11:00:04.653618"
+title: "Codebook created on 2023-11-07 at 2023-11-07 10:56:39.032172"
 output: github_document
@@
 ## Dataset description
-The data contains 713 cases and 3 variables.
+The data contains 74 cases and 89 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_H3.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_H5.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-07 Data/AnalysisData/codebook_data_H6.Rmd
added the final data preparation step, and the models for H1 and H3.

--- 2023-11-07 Data/AnalysisData/codebook_data_H5.Rmd
@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 10:56:39.032172"
+title: "Codebook created on 2023-11-07 at 2023-11-07 10:47:39.749165"
 output: github_document
@@
 ## Dataset description
-The data contains 74 cases and 89 variables.
+The data contains 77 cases and 67 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_H5.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_H6.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-07 Data/AnalysisData/codebook_plot_256_data.Rmd
added the final data preparation step, and the models for H1 and H3.

--- 2023-11-07 Data/AnalysisData/codebook_data_H6.Rmd
@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 10:47:39.749165"
+title: "Codebook created on 2023-11-07 at 2023-11-07 10:58:51.91642"
 output: github_document
@@
 ## Dataset description
-The data contains 77 cases and 67 variables.
+The data contains 924 cases and 3 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_H6.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_plot_256_data.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-07 Data/AnalysisData/codebook_plot_34_data_alpha.Rmd
added the final data preparation step, and the models for H1 and H3.

--- 2023-11-07 Data/AnalysisData/codebook_data_H6.Rmd
@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 10:47:39.749165"
+title: "Codebook created on 2023-11-07 at 2023-11-07 11:03:49.637916"
 output: github_document
@@
 ## Dataset description
-The data contains 77 cases and 67 variables.
+The data contains 658 cases and 5 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_H6.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_plot_34_data_alpha.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-07 Data/AnalysisData/codebook_plot_34_data_omega.Rmd
added the final data preparation step, and the models for H1 and H3.

--- 2023-11-07 Data/AnalysisData/codebook_data_H6.Rmd
@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 10:47:39.749165"
+title: "Codebook created on 2023-11-07 at 2023-11-07 11:04:46.430554"
 output: github_document
@@
 ## Dataset description
-The data contains 77 cases and 67 variables.
+The data contains 558 cases and 5 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_H6.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_plot_34_data_omega.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-07 Scripts/Manuscript/manuscript.Rmd
added the final data preparation step, and the models for H1 and H3.

@@
 library(worcs)
+library(tidyr)
 library(psych)
+library(betareg)
+library(lmerTest)
+library(forcats)
+library(GPArotation)
 
@@
 
+# clearing up memory space by removing raw files from the environment
+rm(coded_data_initial_raw, coded_data_revised_raw, coded_data_vignette_raw, 
+   data_2.10.1, data_2.12, data_2.15, data_2.19.1, data_2.2, data_2.20, 
+   data_2.23, data_2.3, data_2.4.1, data_2.4.2, data_2.8.2, data_3.5, data_5.1,
+   data_5.4, data_5.5, data_5.7, data_5.9.1, data_ml1, data_ml3)
+
 ```
@@
 
-```{r}
-
-```
-
 ## Measures {#sec:measures}
@@
 
-# 1.9 is difficult, might be a scale as dv rather than voting behaviour.
+# 1.9 is difficult, might be a scale as dv rather than voting behavior.
 ```
@@
 ## Analyses
+
+```{r Final Preparation of Data}
+### this code prepares the various pieces of data to be ready to use for the analyses.
+## confirmatory analyses
+# for hypothesis 2
+data_H2 <- data_prep_H2(coded_data_original_shortened, coded_data_replications)
+# for hypothesis 5
+data_H5 <- data_prep_H5(coded_data_replications)
+# for hypothesis 6
+data_H6 <- data_prep_H6(coded_data_original_shortened, coded_data_replications)
+
+# for hypothesis 1
+data_H1 <- data_prep_H1(coded_data_original_shortened, coded_data_replications)
+# for hypothesis 3
+data_H3 <- data_prep_H3(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, 
+  data_1.12.3.2_clean, data_2.10.1_clean, data_2.12.1_clean, data_2.12.2_clean, 
+  data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, 
+  data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.2_clean, data_3.8.2_clean, 
+  data_5.1.1_clean, data_5.7_clean, data_5.9.1_clean)
+# for hypothesis 4
+data_H4_multiple <- Data_prep_H4_multiple(data_H5, data_H3)
+data_H4_avg <- Data_prep_H4_avg(data_H5, data_H4_multiple)
+
+## graphs
+# plot accompanying the results for Hypotheses 2, 5, & 6.
+plot_256_data <- data_prep_plot_256(data_H6)
+# plot accompanying the results for Hypotheses 2, & 6
+Plot_26_data <- data_prep_plot_26(data_H6[c(3, 6, 9, 12, 15, 36, 39, 42, 45, 48)])
+# plot accompanying the results for Hypotheses 3, & 4
+plot_34_data_alpha <- data_prep_plot_34_alpha(data_H4_multiple)
+plot_34_data_omega <- data_prep_plot_34_omega(data_H4_multiple)
+
+### Exporting the final datasets for the analyses
+# the open data
+open_data(data = data_H2, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_H2))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(data_H2))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(data_H2))), ".yml"))
+
+open_data(data = data_H6, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_H6))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(data_H6))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(data_H6))), ".yml"))
+
+open_data(data = data_H5, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_H5))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(data_H5))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(data_H5))), ".yml"))
+
+open_data(data = data_H1, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_H1))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(data_H1))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(data_H1))), ".yml"))
+
+open_data(data = plot_256_data, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(plot_256_data))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(plot_256_data))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(plot_256_data))), ".yml"))
+
+open_data(data = Plot_26_data, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(Plot_26_data))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(Plot_26_data))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(Plot_26_data))), ".yml"))
+
+open_data(data = data_H3, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_H3))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(data_H3))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(data_H3))), ".yml"))
+
+open_data(data = data_H4_multiple, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_H4_multiple))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(data_H4_multiple))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(data_H4_multiple))), ".yml"))
+
+open_data(data = data_H4_avg, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_H4_avg))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(data_H4_avg))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(data_H4_avg))), ".yml"))
+
+open_data(data = plot_34_data_alpha, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(plot_34_data_alpha))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(plot_34_data_alpha))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(plot_34_data_alpha))), ".yml"))
+
+open_data(data = plot_34_data_omega, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(plot_34_data_omega))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(plot_34_data_omega))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(plot_34_data_omega))), ".yml"))
+
+# clearing up memory space by removing intermediate files from the environment
+rm(coded_data_original, coded_data_original_shortened, coded_data_replications)
+
+```
 
@@
 This comparison was implemented via a chi-square test using the base R stats package [@R2021R].
+
+```{r Hypothesis 1 Model}
+# first some descriptives of reliability reporting
+# Measurement type per original and replication:
+H1_descriptive_table_1 <- table(data_H1$rep_org, data_H1$N_items)
+
+# amount of reliability reported per original and replication 
+# (given that measure is a multiple item measure):
+H1_descriptive_table_2 <- table(data_H1$rep_org[data_H1$N_items == "multiple item measure"], data_H1$reliability_type[data_H1$N_items == "multiple item measure"])
+
+# New H1 test
+# A chi square test for difference in N reliability reported for multiple 
+# item measures.
+H1_test_result <- chisq.test(data_H1$rep_org[data_H1$N_items == "multiple item measure"], data_H1$reliability_reported[data_H1$N_items == "multiple item measure"])
+
+```
 
@@
 ```
+
+```{r Hypothesis 3 Model}
+# intercept only model to check the within and between group variance.
+H3_test_result_alpha <- summary(lmer(formula = alpha ~ 1 + (1|g), data = data_H3))
+
+# and same analyses for omega
+# intercept only model to check the within and between group variance.
+H3_test_result_omega <- summary(lmer(formula = omega.tot ~ 1 + (1|g), data = data_H3[complete.cases(data_H3),]))
+
+```
+
 The purpose of this analysis was to investigate variability in calculated reliability coefficients within and between replication sets.
@@
 
-A high ICC indicates low within group variance relative to between group variance, which would be in line with hypothesis 2.
+A high ICC indicates low within group variance relative to between group variance, which would be in line with hypothesis 3.
+
+```{r ICC calculations}
+# alpha
+# within group variance: 0.04384
+# between group variance: 0.19824
+ICC_alpha <- 0.19824 / (0.04384 + 0.19824)
+
+# omega
+# within group variance: 0.003779
+# between group variance: 0.034025
+ICC_omega <- 0.034025 / (0.003779 + 0.034025)
+
+```
 

### 2023-11-07 Scripts/source_script.R

@@ -224,10 +224,13 @@ calculating <- function(Data){
 data_prep_H2 <- function(Data_Original, Data_Replications){
   # data prep for model (using the (y * (n - 1) + 0.5) / n to adjust for any 0 
   # or 1 proportions in the data).
-  Data_H2 <- rbind(Coded_Data_Original_Shortened, Coded_Data_Replications)
+  Data_H2 <- rbind(Data_Original, Data_Replications)
   Data_H2$QMP_ratio <- ((Data_H2$QMP_ratio * (77 - 1) + 0.5) / 77)
   Data_H2$QMP_REV_ratio <- ((Data_H2$QMP_REV_ratio * (77 - 1) + 0.5) / 77)
   
+  # removing the empty sel_psychometric_evidence_text column to prevent codebook
+  # generation issues.
+  Data_H2 <- subset(Data_H2, select = -c(sel_psychometric_evidence_text))
   return(Data_H2)
 }
 
@@ -250,13 +253,18 @@ Model_H2 <- function(Data){
 data_prep_H5 <- function(Data_Replications){
   # data prep for model (using the (y * (n - 1) + 0.5) / n to adjust for any 0 
   # or 1 proportions in the data).
-  Data_H5 <- Coded_Data_Replications[-c(53:55),]
+  Data_H5 <- Data_Replications[-c(53:55),]
   Data_H5$hypothesis_support <- droplevels(Data_H5$hypothesis_support)
   levels(Data_H5$hypothesis_support) <- c(FALSE, TRUE)
   Data_H5$hypothesis_support <- as.logical(Data_H5$hypothesis_support)
   Data_H5$QMP_ratio <- ((Data_H5$QMP_ratio * (77 - 1) + 0.5) / 77)
   Data_H5$QMP_REV_ratio <- ((Data_H5$QMP_REV_ratio * (77 - 1) + 0.5) / 77)
   Data_H5$many_labs_version <- as.factor(Data_H5$many_labs_version)
+  
+  # removing the empty sel_psychometric_evidence_text & reliability_type_text 
+  # column to prevent codebook generation issues.
+  Data_H5 <- subset(Data_H5, select = -c(sel_psychometric_evidence_text, 
+                                         reliability_type_text))
   
   return(Data_H5)
 }
@@ -532,6 +540,10 @@ data_prep_H1 <- function(Data_Original, Data_Replications){
     ifelse(Data_H1$reliability_type[Data_H1$N_items == "multiple item measure"] 
[…]

### 2023-11-07 Scripts/Manuscript/manuscript.Rmd
added the hypothesis 4 (3) models.

@@
 
-```{r Hypothesis 3 Model}
+```{r Hypothesis 2 Model}
 # intercept only model to check the within and between group variance.
@@
 
-A high ICC indicates low within group variance relative to between group variance, which would be in line with hypothesis 3.
+A high ICC indicates low within group variance relative to between group variance, which would be in line with hypothesis 2.
 
@@
 
+```{r Hypothesis 3 Main Test}
+## The main model to test hypothesis 3, through a logistic regression model.
+H4_test_result_main_alpha <- summary(glm(formula = replication ~ 1 + alpha_avg, 
+                                     family = binomial(), data = data_H4_avg))
+
+# and for omega
+H4_test_result_main_omega <- summary(glm(formula = replication ~ 1 + 
+                                     omega.tot_avg, family = binomial(), 
+                                     data = data_H4_avg))
+
+# alpha says negative, omega says positive, neither are significant though.
+
+```
+
 In this data, replication attempts at different lab locations can be seen as nested within a replication set.
@@
 The models used were a multilevel logistic random intercept and random slope model.
+
+```{r Hypothesis 3 Multilevel Model Sensitivity Analyses}
+## sensitivity analyses.
+# running a random intercept multilevel logistic model
+H4_test_result_int_sensitivity_alpha <- summary(glmer(formula = replication ~ 1 
+                                                + alpha + (1|g), family = 
+                                                binomial(), data = 
+                                                data_H4_multiple))
+
+# and for omega
+H4_test_result_int_sensitivity_omega <- summary(glmer(formula = replication ~ 1 
+                                                + omega.tot + (1|g), family = 
+                                                  binomial(), data = 
+                                                  data_H4_multiple))
+
+# same as for non-multilevel model
+
+# running a random slope multilevel logistic model
+H4_test_result_slp_sensitivity_alpha <- summary(glmer(formula = replication ~ 1 
+                                                + alpha + (1 + alpha|g), 
+                                                family = binomial(), data =
+                                                data_H4_multiple))
+
+# and for omega
+H4_test_result_slp_sensitivity_omega <- summary(glmer(formula = replication ~ 1 
+                                                + omega.tot + (1 + omega.tot|g), 
+                                                family = binomial(), data =
+                                                data_H4_multiple))
+
+# alpha did not converge, and omega shows no significant effect.
+```
 

### 2023-11-07 Data/AnalysisData/codebook_Plot_46_data.Rmd
changed the naming for the hypothesis related functions to match the hypothesis numbering in the manuscript.

--- 2023-11-07 Data/AnalysisData/codebook_Plot_26_data.Rmd
@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 10:59:14.419679"
+title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:47.216976"
 output: github_document
@@
 ```{r}
-summaries <- read.csv("codebook_Plot_26_data.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_Plot_46_data.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-07 Data/AnalysisData/codebook_data_H2.Rmd
changed the naming for the hypothesis related functions to match the hypothesis numbering in the manuscript.

@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 10:52:58.610667"
+title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:49.767935"
 output: github_document

### 2023-11-07 Data/AnalysisData/codebook_data_H3_avg.Rmd
changed the naming for the hypothesis related functions to match the hypothesis numbering in the manuscript.

--- 2023-11-07 Data/AnalysisData/codebook_data_H4_avg.Rmd
@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 11:03:47.475669"
+title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:55.749084"
 output: github_document
@@
 ```{r}
-summaries <- read.csv("codebook_data_H4_avg.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_H3_avg.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-07 Data/AnalysisData/codebook_data_H3_multiple.Rmd
changed the naming for the hypothesis related functions to match the hypothesis numbering in the manuscript.

--- 2023-11-07 Data/AnalysisData/codebook_data_H4_multiple.Rmd
@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 11:03:41.005817"
+title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:53.662957"
 output: github_document
@@
 ```{r}
-summaries <- read.csv("codebook_data_H4_multiple.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_H3_multiple.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-07 Data/AnalysisData/codebook_data_H4.Rmd
changed the naming for the hypothesis related functions to match the hypothesis numbering in the manuscript.

--- 2023-11-07 Data/AnalysisData/codebook_data_H4_avg.Rmd
@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 11:03:47.475669"
+title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:23.774949"
 output: github_document
@@
 ## Dataset description
-The data contains 18 cases and 3 variables.
+The data contains 154 cases and 90 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_H4_avg.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_H4.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-07 Data/AnalysisData/codebook_plot_23_data_alpha.Rmd
changed the naming for the hypothesis related functions to match the hypothesis numbering in the manuscript.

--- 2023-11-07 Data/AnalysisData/codebook_plot_34_data_alpha.Rmd
@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 11:03:49.637916"
+title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:58.540839"
 output: github_document
@@
 ```{r}
-summaries <- read.csv("codebook_plot_34_data_alpha.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_plot_23_data_alpha.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-07 Data/AnalysisData/codebook_plot_23_data_omega.Rmd
changed the naming for the hypothesis related functions to match the hypothesis numbering in the manuscript.

--- 2023-11-07 Data/AnalysisData/codebook_plot_34_data_omega.Rmd
@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 11:04:46.430554"
+title: "Codebook created on 2023-11-07 at 2023-11-07 11:59:02.156609"
 output: github_document
@@
 ```{r}
-summaries <- read.csv("codebook_plot_34_data_omega.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_plot_23_data_omega.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-07 Data/AnalysisData/codebook_plot_456_data.Rmd
changed the naming for the hypothesis related functions to match the hypothesis numbering in the manuscript.

--- 2023-11-07 Data/AnalysisData/codebook_plot_256_data.Rmd
@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 10:58:51.91642"
+title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:44.141596"
 output: github_document
@@
 ```{r}
-summaries <- read.csv("codebook_plot_256_data.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_plot_456_data.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-07 Scripts/Manuscript/manuscript.Rmd
changed the naming for the hypothesis related functions to match the hypothesis numbering in the manuscript.

--- 2023-11-06 Scripts/Manuscript/manuscript.Rmd
@@
 ## Analyses
+
+```{r Final Preparation of Data}
+### this code prepares the various pieces of data to be ready to use for the analyses.
+## confirmatory analyses
+# for hypothesis 4
+data_H4 <- data_prep_H4(coded_data_original_shortened, coded_data_replications)
+# for hypothesis 5
+data_H5 <- data_prep_H5(coded_data_replications)
+# for hypothesis 6
+data_H6 <- data_prep_H6(coded_data_original_shortened, coded_data_replications)
+
+# for hypothesis 1
+data_H1 <- data_prep_H1(coded_data_original_shortened, coded_data_replications)
+# for hypothesis 2
+data_H2 <- data_prep_H2(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, 
+  data_1.12.3.2_clean, data_2.10.1_clean, data_2.12.1_clean, data_2.12.2_clean, 
+  data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, 
+  data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.2_clean, data_3.8.2_clean, 
+  data_5.1.1_clean, data_5.7_clean, data_5.9.1_clean)
+# for hypothesis 3
+data_H3_multiple <- Data_prep_H3_multiple(data_H5, data_H2)
+data_H3_avg <- Data_prep_H3_avg(data_H5, data_H3_multiple)
+
+## graphs
+# plot accompanying the results for Hypotheses 4, 5, & 6.
+plot_456_data <- data_prep_plot_456(data_H6)
+# plot accompanying the results for Hypotheses 4, & 6
+Plot_46_data <- data_prep_plot_46(data_H6[c(3, 6, 9, 12, 15, 36, 39, 42, 45, 48)])
+# plot accompanying the results for Hypotheses 2, & 3
+plot_23_data_alpha <- data_prep_plot_23_alpha(data_H3_multiple)
+plot_23_data_omega <- data_prep_plot_23_omega(data_H3_multiple)
+
+### Exporting the final datasets for the analyses
+# the open data
+open_data(data = data_H4, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_H4))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(data_H4))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(data_H4))), ".yml"))
+
+open_data(data = data_H6, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_H6))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(data_H6))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(data_H6))), ".yml"))
+
+open_data(data = data_H5, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_H5))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(data_H5))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(data_H5))), ".yml"))
+
+open_data(data = data_H1, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_H1))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(data_H1))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(data_H1))), ".yml"))
+
+open_data(data = plot_456_data, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(plot_456_data))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(plot_456_data))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(plot_456_data))), ".yml"))
+
+open_data(data = Plot_46_data, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(Plot_46_data))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(Plot_46_data))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(Plot_46_data))), ".yml"))
+
+open_data(data = data_H2, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_H2))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(data_H2))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(data_H2))), ".yml"))
+
+open_data(data = data_H3_multiple, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_H3_multiple))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(data_H3_multiple))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(data_H3_multiple))), ".yml"))
+
+open_data(data = data_H3_avg, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_H3_avg))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(data_H3_avg))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(data_H3_avg))), ".yml"))
+
+open_data(data = plot_23_data_alpha, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(plot_23_data_alpha))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(plot_23_data_alpha))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(plot_23_data_alpha))), ".yml"))
+
+open_data(data = plot_23_data_omega, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(plot_23_data_omega))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(plot_23_data_omega))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(plot_23_data_omega))), ".yml"))
+
+# clearing up memory space by removing intermediate files from the environment
+rm(coded_data_original, coded_data_original_shortened, coded_data_replications)
+
+```
 
@@
 ```
+
+```{r Hypothesis 2 Model}
+# intercept only model to check the within and between group variance.
+H2_test_result_alpha <- summary(lmer(formula = alpha ~ 1 + (1|g), data = data_H2))
+
+# and same analyses for omega
+# intercept only model to check the within and between group variance.
+H2_test_result_omega <- summary(lmer(formula = omega.tot ~ 1 + (1|g), data = data_H2[complete.cases(data_H2),]))
+
+```
+
 The purpose of this analysis was to investigate variability in calculated reliability coefficients within and between replication sets.
@@
 
+```{r ICC calculations}
+# alpha
+# within group variance: 0.04384
+# between group variance: 0.19824
+ICC_alpha <- 0.19824 / (0.04384 + 0.19824)
+
+# omega
+# within group variance: 0.003779
+# between group variance: 0.034025
+ICC_omega <- 0.034025 / (0.003779 + 0.034025)
+
+```
+
 In order to test hypothesis 3, the average calculated Cronbach's alpha level within a replication set is used as a predictor of replication success.
@@
 
+```{r Hypothesis 3 Main Test}
+## The main model to test hypothesis 3, through a logistic regression model.
+H3_test_result_main_alpha <- summary(glm(formula = replication ~ 1 + alpha_avg, 
+                                     family = binomial(), data = data_H3_avg))
+
+# and for omega
+H3_test_result_main_omega <- summary(glm(formula = replication ~ 1 + 
+                                     omega.tot_avg, family = binomial(), 
+                                     data = data_H3_avg))
+
+# alpha says negative, omega says positive, neither are significant though.
+
+```
+
 In this data, replication attempts at different lab locations can be seen as nested within a replication set.
@@
 The models used were a multilevel logistic random intercept and random slope model.
+
+```{r Hypothesis 3 Multilevel Model Sensitivity Analyses}
+## sensitivity analyses.
+# running a random intercept multilevel logistic model
+H3_test_result_int_sensitivity_alpha <- summary(glmer(formula = replication ~ 1 
+                                                + alpha + (1|g), family = 
+                                                binomial(), data = 
+                                                data_H3_multiple))
+
+# and for omega
+H3_test_result_int_sensitivity_omega <- summary(glmer(formula = replication ~ 1 
+                                                + omega.tot + (1|g), family = 
+                                                  binomial(), data = 
+                                                  data_H3_multiple))
+
+# same as for non-multilevel model
+
+# running a random slope multilevel logistic model
+H3_test_result_slp_sensitivity_alpha <- summary(glmer(formula = replication ~ 1 
+                                                + alpha + (1 + alpha|g), 
+                                                family = binomial(), data =
+                                                data_H3_multiple))
+
+# and for omega
+H3_test_result_slp_sensitivity_omega <- summary(glmer(formula = replication ~ 1 
+                                                + omega.tot + (1 + omega.tot|g), 
+                                                family = binomial(), data =
+                                                data_H3_multiple))
+
+# alpha did not converge, and omega shows no significant effect.
+```
 

### 2023-11-07 Scripts/source_script.R

@@ -219,30 +219,30 @@ calculating <- function(Data){
 }
 
 # QMP Related Functions --------------------------------------------------------
-### Hypothesis 2 
+### Hypothesis 4 
 # data load and prep function
-data_prep_H2 <- function(Data_Original, Data_Replications){
+data_prep_H4 <- function(Data_Original, Data_Replications){
   # data prep for model (using the (y * (n - 1) + 0.5) / n to adjust for any 0 
   # or 1 proportions in the data).
-  Data_H2 <- rbind(Data_Original, Data_Replications)
-  Data_H2$QMP_ratio <- ((Data_H2$QMP_ratio * (77 - 1) + 0.5) / 77)
-  Data_H2$QMP_REV_ratio <- ((Data_H2$QMP_REV_ratio * (77 - 1) + 0.5) / 77)
+  Data_H4 <- rbind(Data_Original, Data_Replications)
+  Data_H4$QMP_ratio <- ((Data_H4$QMP_ratio * (77 - 1) + 0.5) / 77)
+  Data_H4$QMP_REV_ratio <- ((Data_H4$QMP_REV_ratio * (77 - 1) + 0.5) / 77)
   
   # removing the empty sel_psychometric_evidence_text column to prevent codebook
   # generation issues.
-  Data_H2 <- subset(Data_H2, select = -c(sel_psychometric_evidence_text))
-  return(Data_H2)
+  Data_H4 <- subset(Data_H4, select = -c(sel_psychometric_evidence_text))
+  return(Data_H4)
 }
 
 # modelling and results returning function
-Model_H2 <- function(Data){
+Model_H4 <- function(Data){
   return_list <- list(first = 0, revised = 0)
   # running the models one with none revised QMP ratio's and one with
-  Model_H2 <- betareg(QMP_ratio ~ rep_org, data = Data)
-  return_list[[1]] <- summary(Model_H2)$coefficients
+  Model_H4 <- betareg(QMP_ratio ~ rep_org, data = Data)
+  return_list[[1]] <- summary(Model_H4)$coefficients
   
-  Model_H2_REV <- betareg(QMP_REV_ratio ~ rep_org, data = Data)
-  return_list[[2]] <- summary(Model_H2_REV)$coefficients
+  Model_H4_REV <- betareg(QMP_REV_ratio ~ rep_org, data = Data)
+  return_list[[2]] <- summary(Model_H4_REV)$coefficients
   
[…]

### 2023-11-07 Scripts/Manuscript/manuscript.Rmd
H4, 5, & 6 and exploratory analyses

@@
 
+```{r Hypothesis 4 Model}
+## Hypothesis 4 beta regression model
+# running the model with none revised QMP ratio's
+H4_test_results <- betareg(QMP_ratio ~ rep_org, data = data_h4)
+
+# running the models with revised QMP ratio's
+H4_test_results_REV  <- betareg(QMP_REV_ratio ~ rep_org, data = data_h4)
+
+```
+
 Where $replication_{i}$ is a dummy coded variable, which was coded as 1 in case the reported QMP ratio belonged to a replications, and 0 if it belonged to an original study.
@@
 Note here that unlike in the test for hypothesis 4, $QMP\_ratio_{i}$ refers only to the QMP ratios of the replications, meaning that original article QMPs were not included in this analysis.
+
+```{r Hypothesis 5 Model}
+## Hypothesis 4 beta regression model
+H5_test_results <- betareg(QMP_ratio ~ hypothesis_support, data = data_h5)
+
+H5_test_results_REV <- betareg(QMP_REV_ratio ~ hypothesis_support, data = data_h5)
+
+```
 
@@
 $$g(QMP\_ratio\_replication_{i}) = \beta_{0} + \beta_{1} QMP\_ratio\_original_{i}$$
+```{r Hypothesis 6 Model}
+H6_test_results <- betareg(Rep_QMP_ratio ~ QMP_ratio, data = data_h6)
+
+H6_test_results_REV <- betareg(Rep_QMP_REV_ratio ~ QMP_REV_ratio, data = data_h6)
+
+```
 
@@
 
+```{r Hypotheses 5 & 6 Sensitivity Analyses}
+## Hypothesis 5 sensitivity test using a random intercept Guassian model.
+# create dummy H5 dataframe for use in sensitivity test
+data_h5_sens <- data_h5
+
+# convert outcome variable to be usable with Gaussian distribution via
+# logit transform.
+data_h5_sens$QMP <- log(data_h5_sens$QMP_ratio /(1 - data_h5_sens$QMP_ratio))
+data_h5_sens$QMP_REV <- log(data_h5_sens$QMP_REV_ratio /(1 - data_h5_sens$QMP_REV_ratio))
+
+check_h5 <- lmer(formula = QMP ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens)
+H5_sensitivity_test_results <- summary(check_h5)$coefficients
+
+check_h5_REV <- lmer(formula = QMP_REV ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens)
+H5_sensitivity_test_results_REV <- summary(check_h5_REV)$coefficients
+
+## Hypothesis 6 sensitivity test using a random intercept Guassian model.
+# create dummy H6 dataframe for use in sensitivity test
+data_h6_sens <- data_h6
+
+# convert outcome variable to be usable with Gaussian distribution via
+# logit transform.
+data_h6_sens$QMP <- log(data_h6_sens$QMP_ratio /(1 - data_h6_sens$QMP_ratio))
+data_h6_sens$Rep_QMP <- log(data_h6_sens$Rep_QMP_ratio /(1 - data_h6_sens$Rep_QMP_ratio))
+data_h6_sens$QMP_REV <- log(data_h6_sens$QMP_REV_ratio /(1 - data_h6_sens$QMP_REV_ratio))
+data_h6_sens$Rep_QMP_REV <- log(data_h6_sens$Rep_QMP_REV_ratio /(1 - data_h6_sens$Rep_QMP_REV_ratio))
+
+# running the models one with none revised QMP ratio's and one with
+check_h6 <- lmer(formula = Rep_QMP ~ 1 + QMP + (1|many_labs_version), data = data_h6_sens)
+H6_sensitivity_test_results <- summary(check_h6)$coefficients
+
+check_h6_REV <- lmer(formula = Rep_QMP_REV ~ 1 + QMP_REV + (1|many_labs_version), data = data_h6_sens)
+H6_sensitivity_test_results_REV <- summary(check_h6_REV)$coefficients
+
+# n of mod ratio's pressent check
+H6_n_check_results <- betareg(Rep_op_ratio ~ mod_ratio, data = data_h6)$n
+H6_n_check_results_REV <- betareg(Rep_op_REV_ratio ~ mod_REV_ratio, data = data_h6)$n
+
+```
+
+```{r Hypothesis 6 Associations}
+## Associations between the QMP categories
+# associations are generated using a helper function available in the source_ 
+# script. These associations correspond to the coefficients between replication
+# and original article QMPs of the various QMP types, as estimated through a 
+# beta regression.
+# Associations between the QMP categories (original QMP coding)
+Results_H6_between <- Associations_H6(data_h6)
+
+# keep in mind mod_ratio (not Rep) is based on a very small sample size, less
+# of a concern for the revised.
+
+# Associations between the QMP categories (revised QMP coding)
+Results_H6_between_REV <- Associations_H6_REV(data_h6)
+
+```
+
 ### Exploratory Analyses
@@
 If either the RMSEA score \< .08, or the parallel analysis returned a one factor solution, unidimensionality was coded as true, otherwise it was coded as false.
+
+```{r Unidimensionality Exploratory Analysis}
+extracted_data_list <- list(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean,
+                            data_1.12.3.2_clean, data_2.10.1_clean,
+                            data_2.12.1_clean, data_2.12.2_clean, 
+                            data_2.12.3_clean, data_2.15_clean, data_2.20_clean,
+                            data_2.23_clean, data_3.2.1.1_clean, 
+                            data_3.2.1.2_clean, data_3.7.1_clean, 
+                            data_3.7.2_clean, data_3.8.2_clean,
+                            data_5.1.1_clean, data_5.7_clean, data_5.9.1_clean)
+
+# creating an empty dataframe to store the results in
+cfa_results <- data.frame(RMSEA = 0,
+                          N_factors = 0,
+                          Single_factor = FALSE)
+
+# running the cfas for all of the extracted datasets
+for (i in 1:length(extracted_data_list)){
+  # obtaining single factor model cfa RMSEA value for evaluation
+  RMSEA_value <- fa(extracted_data_list[[i]][-1])$RMSEA[1]
+
+  # conducting parallel test to check if one factor solution is best.
+  parallel_N_factors <- fa.parallel(extracted_data_list[[i]][-1], 
+                                    fa = "fa")$nfact
+
+  # adding a single factor check indicator value
+  single_factor <- ifelse(RMSEA_value < 0.08 | parallel_N_factors == 1, TRUE, 
+                          FALSE)
+
+  # adding the cfa results of one factor analysis to the results dataframe.
+  cfa_results <- rbind(cfa_results, c(RMSEA_value, parallel_N_factors, 
+                                      single_factor))
+}
+# removing the initial empty row
+cfa_results <- cfa_results[-1,]
+
+```
 

### 2023-11-07 Scripts/source_script.R

@@ -696,6 +696,164 @@ cfa_ML_measures <- function(Extracted_Data_List){
 
 
 
+# Analyses Test Functions ------------------------------------------------------
+# creates and returns the associations between QMP categories
+Associations_H6 <- function(Data){
+  return_list <- list(def_def = 0, def_op = 0, def_sel = 0, def_quant = 0, 
+                      def_mod = 0, op_def = 0, op_op = 0, op_sel = 0, 
+                      op_quant = 0, op_mod = 0, sel_def = 0, sel_op = 0, 
+                      sel_sel = 0, sel_quant = 0, sel_mod = 0, quant_def = 0,
+                      quant_op = 0, quant_sel = 0, quant_quant = 0, 
+                      quant_mod = 0, mod_def = 0, mod_op = 0, mod_sel = 0, 
+                      mod_quant = 0, mod_mod = 0, tot_def = 0, tot_op = 0, 
+                      tot_sel = 0, tot_quant = 0, tot_mod = 0)
+  # Associations between the QMP categories
+  # Mod_ratio is compared on a subset of the data, because it has several 
+  # missing cases, due to some files not having any modifications.
+  return_list[[1]] <- summary(betareg(Rep_def_ratio ~ def_ratio, 
+                                      data = Data))$coefficients[1]
+  return_list[[2]] <- summary(betareg(Rep_def_ratio ~ op_ratio, 
+                                      data = Data))$coefficients[1]
+  return_list[[3]] <- summary(betareg(Rep_def_ratio ~ sel_ratio, 
+                                      data = Data))$coefficients[1]
+  return_list[[4]] <- summary(betareg(Rep_def_ratio ~ quant_ratio, 
+                                      data = Data))$coefficients[1]
+  return_list[[5]] <- summary(betareg(Rep_def_ratio ~ mod_ratio, 
+                                      data = Data[!is.na(Data$mod_ratio),]))$coefficients[1]
+  return_list[[6]] <- summary(betareg(Rep_op_ratio ~ def_ratio, 
+                                      data = Data))$coefficients[1]
+  return_list[[7]] <- summary(betareg(Rep_op_ratio ~ op_ratio, 
+                                      data = Data))$coefficients[1]
+  return_list[[8]] <- summary(betareg(Rep_op_ratio ~ sel_ratio, 
+                                      data = Data))$coefficients[1]
[…]

### 2023-11-07 Scripts/Manuscript/manuscript.Rmd
failed attempt to include R results as numbers in text.

@@
 
-```{r Cleaning Replication Datasets Data}
+```{r Cleaning Replication Datasets Data, include = FALSE, eval = FALSE}
 ##### Data already available, code does not need to be run!
@@
 
-```{r Cleaning Coded Data}
+```{r Cleaning Coded Data, include = FALSE, eval = FALSE}
 ##### Data already available, code does not need to be run!
@@
 
-```{r Check for Reliability and Validity Testability}
+```{r Check for Reliability and Validity Testability, include = FALSE}
 ## Checking the measures to recalculate the reliability and factor analysis for.
@@
 
-```{r Final Preparation of Data}
-### this code prepares the various pieces of data to be ready to use for the analyses.
+```{r Final Preparation of Data, include = FALSE, eval = FALSE}
+##### Data already available, code does not need to be run!
+### this code prepares the various pieces of data to be ready to use for the 
+### analyses.
 ## confirmatory analyses
 # for hypothesis 4
-data_H4 <- data_prep_H4(coded_data_original_shortened, coded_data_replications)
+data_h4 <- data_prep_H4(coded_data_original_shortened, coded_data_replications)
 # for hypothesis 5
-data_H5 <- data_prep_H5(coded_data_replications)
+data_h5 <- data_prep_H5(coded_data_replications)
 # for hypothesis 6
-data_H6 <- data_prep_H6(coded_data_original_shortened, coded_data_replications)
+data_h6 <- data_prep_H6(coded_data_original_shortened, coded_data_replications)
 
 # for hypothesis 1
-data_H1 <- data_prep_H1(coded_data_original_shortened, coded_data_replications)
+data_h1 <- data_prep_H1(coded_data_original_shortened, coded_data_replications)
 # for hypothesis 2
-data_H2 <- data_prep_H2(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, 
+data_h2 <- data_prep_H2(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, 
   data_1.12.3.2_clean, data_2.10.1_clean, data_2.12.1_clean, data_2.12.2_clean, 
@@
 # for hypothesis 3
-data_H3_multiple <- Data_prep_H3_multiple(data_H5, data_H2)
-data_H3_avg <- Data_prep_H3_avg(data_H5, data_H3_multiple)
+data_h3_multiple <- Data_prep_H3_multiple(data_h5, data_h2)
+data_h3_avg <- Data_prep_H3_avg(data_h5, data_h3_multiple)
 
@@
 # plot accompanying the results for Hypotheses 4, 5, & 6.
-plot_456_data <- data_prep_plot_456(data_H6)
+plot_456_data <- data_prep_plot_456(data_h6)
 # plot accompanying the results for Hypotheses 4, & 6
-Plot_46_data <- data_prep_plot_46(data_H6[c(3, 6, 9, 12, 15, 36, 39, 42, 45, 48)])
+Plot_46_data <- data_prep_plot_46(data_h6[c(3, 6, 9, 12, 15, 36, 39, 42, 45, 48)])
 # plot accompanying the results for Hypotheses 2, & 3
-plot_23_data_alpha <- data_prep_plot_23_alpha(data_H3_multiple)
-plot_23_data_omega <- data_prep_plot_23_omega(data_H3_multiple)
+plot_23_data_alpha <- data_prep_plot_23_alpha(data_h3_multiple)
+plot_23_data_omega <- data_prep_plot_23_omega(data_h3_multiple)
 
@@
 # the open data
-open_data(data = data_H4, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_H4))), ".csv"),
+open_data(data = data_h4, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_h4))), ".csv"),
   codebook = paste0(paste0(
     "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_H4))), ".Rmd"),
+    deparse(substitute(data_h4))), ".Rmd"),
   value_labels = paste0(paste0(
     "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_H4))), ".yml"))
-
-open_data(data = data_H6, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_H6))), ".csv"),
+    deparse(substitute(data_h4))), ".yml"))
+
+open_data(data = data_h6, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_h6))), ".csv"),
   codebook = paste0(paste0(
     "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_H6))), ".Rmd"),
+    deparse(substitute(data_h6))), ".Rmd"),
   value_labels = paste0(paste0(
     "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_H6))), ".yml"))
-
-open_data(data = data_H5, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_H5))), ".csv"),
+    deparse(substitute(data_h6))), ".yml"))
+
+open_data(data = data_h5, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_h5))), ".csv"),
   codebook = paste0(paste0(
     "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_H5))), ".Rmd"),
+    deparse(substitute(data_h5))), ".Rmd"),
   value_labels = paste0(paste0(
     "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_H5))), ".yml"))
-
-open_data(data = data_H1, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_H1))), ".csv"),
+    deparse(substitute(data_h5))), ".yml"))
+
+open_data(data = data_h1, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_h1))), ".csv"),
   codebook = paste0(paste0(
     "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_H1))), ".Rmd"),
+    deparse(substitute(data_h1))), ".Rmd"),
   value_labels = paste0(paste0(
     "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_H1))), ".yml"))
+    deparse(substitute(data_h1))), ".yml"))
 
@@
 
-open_data(data = data_H2, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_H2))), ".csv"),
+open_data(data = data_h2, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_h2))), ".csv"),
   codebook = paste0(paste0(
     "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_H2))), ".Rmd"),
+    deparse(substitute(data_h2))), ".Rmd"),
   value_labels = paste0(paste0(
     "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_H2))), ".yml"))
-
-open_data(data = data_H3_multiple, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_H3_multiple))), ".csv"),
+    deparse(substitute(data_h2))), ".yml"))
+
+open_data(data = data_h3_multiple, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_h3_multiple))), ".csv"),
   codebook = paste0(paste0(
     "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_H3_multiple))), ".Rmd"),
+    deparse(substitute(data_h3_multiple))), ".Rmd"),
   value_labels = paste0(paste0(
     "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_H3_multiple))), ".yml"))
-
-open_data(data = data_H3_avg, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_H3_avg))), ".csv"),
+    deparse(substitute(data_h3_multiple))), ".yml"))
+
+open_data(data = data_h3_avg, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_h3_avg))), ".csv"),
   codebook = paste0(paste0(
     "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_H3_avg))), ".Rmd"),
+    deparse(substitute(data_h3_avg))), ".Rmd"),
   value_labels = paste0(paste0(
     "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_H3_avg))), ".yml"))
+    deparse(substitute(data_h3_avg))), ".yml"))
 
@@
 
-# clearing up memory space by removing intermediate files from the environment
-rm(coded_data_original, coded_data_original_shortened, coded_data_replications)
-
 ```
@@
 # Measurement type per original and replication:
-H1_descriptive_table_1 <- table(data_H1$rep_org, data_H1$N_items)
+H1_descriptive_table_1 <- table(data_h1$rep_org, data_h1$N_items)
 
@@
 # (given that measure is a multiple item measure):
-H1_descriptive_table_2 <- table(data_H1$rep_org[data_H1$N_items == "multiple item measure"], data_H1$reliability_type[data_H1$N_items == "multiple item measure"])
+H1_descriptive_table_2 <- table(data_h1$rep_org[data_h1$N_items == "multiple item measure"], data_h1$reliability_type[data_h1$N_items == "multiple item measure"])
 
@@
 # item measures.
-H1_test_result <- chisq.test(data_H1$rep_org[data_H1$N_items == "multiple item measure"], data_H1$reliability_reported[data_H1$N_items == "multiple item measure"])
+H1_test_result <- chisq.test(data_h1$rep_org[data_h1$N_items == "multiple item measure"], data_h1$reliability_reported[data_h1$N_items == "multiple item measure"])
 
@@
 ```
-
 ```{r Hypothesis 2 Model}
 # intercept only model to check the within and between group variance.
-H2_test_result_alpha <- summary(lmer(formula = alpha ~ 1 + (1|g), data = data_H2))
+H2_test_result_alpha <- summary(lmer(formula = alpha ~ 1 + (1|g), data = data_h2))
 
@@
 # intercept only model to check the within and between group variance.
-H2_test_result_omega <- summary(lmer(formula = omega.tot ~ 1 + (1|g), data = data_H2[complete.cases(data_H2),]))
+H2_test_result_omega <- summary(lmer(formula = omega.tot ~ 1 + (1|g), data = data_h2[complete.cases(data_h2),]))
 
@@
 H3_test_result_main_alpha <- summary(glm(formula = replication ~ 1 + alpha_avg, 
-                                     family = binomial(), data = data_H3_avg))
+                                     family = binomial(), data = data_h3_avg))
 
@@
                                      omega.tot_avg, family = binomial(), 
-                                     data = data_H3_avg))
+                                     data = data_h3_avg))
 
@@
                                                 binomial(), data = 
-                                                data_H3_multiple))
+                                                data_h3_multiple))
 
@@
                                                   binomial(), data = 
-                                                  data_H3_multiple))
+                                                  data_h3_multiple))
 
@@
                                                 family = binomial(), data =
-                                                data_H3_multiple))
+                                                data_h3_multiple))
 
@@
 $$g(QMP\_ratio\_replication_{i}) = \beta_{0} + \beta_{1} QMP\_ratio\_original_{i}$$
+
 ```{r Hypothesis 6 Model}
@@
 }
+
 # removing the initial empty row
@@
 ## Descriptives
-
-The mean sample size within the replications was 4844 participants (IQR = 3816).
-In the original articles the mean sample size was 244 (IQR = 140).
-In total, support was found for hypothesized effects of 34 of the 77 measures.
+The mean sample size within the replications was `r printnum(round(mean(coded_data_replications$N, na.rm = TRUE)))` participants (IQR = `r printnum(round(IQR(coded_data_replications$N, na.rm = TRUE)))`).
+In the original articles the mean sample size was `r printnum(round(mean(coded_data_original_shortened$N, na.rm = TRUE)))` (IQR = `r printnum(round(IQR(coded_data_original_shortened$N, na.rm = TRUE)))`).
+In total, support was found for hypothesized effects of `r printnum(table(coded_data_replications$hypothesis_support)["Yes"])` of the `r printnum(nrow(coded_data_replications)` measures.
 Proportions of replication success per Many Labs project can be found in Table XXX.
@@
 
-INSERT RELIABILITY REPORTING FLOW DIAGRAM FIGURE
+![Figure 1. Reliability reporting flow diagram](../../SupplementaryMaterials/reliability_reporting_flow_diagram.png)
 
@@
 In that case, the tests in the original article are based on data from measures that do not accurately capture the construct they were intended to measure.
-The results of any direct replication attempt will face the same issues, and as a consequence the replication is unlikely to provide a relevant test of a psychological theory, as the original study itself was not a robust test of that psychological theory to begin with [@isager2020deciding, @isager2021deciding, @nuijten2022assessin].
+The results of any direct replication attempt will face the same issues, and as a consequence the replication is unlikely to provide a relevant test of a psychological theory, as the original study itself was not a robust test of that psychological theory to begin with [@isager2020deciding, @isager2021deciding, @nuijten2022assessing].
 Thus, future replicators should first evaluate the quality of the measurement (reporting) in an article before deciding to replicate it.

### 2023-11-07 Scripts/prepare_data.R

@@ -148,15 +148,18 @@ closed_data(data = Data_5.9.1, filename = "Data/InputData/Data_5.9.1.csv",
 
 open_data(data = Coded_Data_Initial_raw, 
           filename = "Data/InputData/Coded_Data_Initial_raw.csv",
-  codebook = NULL, value_labels = NULL) 
+  codebook = NULL, value_labels = NULL, 
+  load_expression = read.csv(file = filename, stringsAsFactors = FALSE)) 
 
 open_data(data = Coded_Data_Revised_raw, 
           filename = "Data/InputData/Coded_Data_Revised_raw.csv",
-  codebook = NULL, value_labels = NULL) 
+  codebook = NULL, value_labels = NULL,
+  load_expression = read.csv(file = filename, stringsAsFactors = FALSE)) 
 
 open_data(data = Coded_Data_Vignette_raw, 
           filename = "Data/InputData/Coded_Data_Vignette_raw.csv",
-  codebook = NULL, value_labels = NULL) 
+  codebook = NULL, value_labels = NULL,
+  load_expression = read.csv(file = filename, stringsAsFactors = FALSE)) 
 
 
 

### 2023-11-08 Scripts/Manuscript/manuscript.Rmd
succesfully included R results in the manuscript.

@@
 library(tidyr)
-library(psych)
 library(betareg)
 library(lmerTest)
+library(psych)
 library(forcats)
@@
 ## Descriptives
-The mean sample size within the replications was `r printnum(round(mean(coded_data_replications$N, na.rm = TRUE)))` participants (IQR = `r printnum(round(IQR(coded_data_replications$N, na.rm = TRUE)))`).
-In the original articles the mean sample size was `r printnum(round(mean(coded_data_original_shortened$N, na.rm = TRUE)))` (IQR = `r printnum(round(IQR(coded_data_original_shortened$N, na.rm = TRUE)))`).
-In total, support was found for hypothesized effects of `r printnum(table(coded_data_replications$hypothesis_support)["Yes"])` of the `r printnum(nrow(coded_data_replications)` measures.
+
+```{r Code for Descriptives Retrieval}
+N_replications <- mean(coded_data_replications$N, na.rm = TRUE)
+IQR_replications <- IQR(coded_data_replications$N, na.rm = TRUE)
+N_original <- mean(coded_data_original_shortened$N, na.rm = TRUE)
+IQR_original <- IQR(coded_data_original_shortened$N, na.rm = TRUE)
+
+N_h_support <- table(coded_data_replications$hypothesis_support)["Yes"]
+N_measures <- nrow(coded_data_replications)
+```
+
+The mean sample size within the replications was `r apa_num(N_replications, digits = 0)` participants (IQR = `r apa_num(IQR_replications, digits = 0)`).
+In the original articles the mean sample size was `r apa_num(N_original, digits = 0)` (IQR = `r apa_num(IQR_original, digits = 0)`).
+In total, support was found for hypothesized effects of `r apa_num(N_h_support, digits = 0)` of the `r apa_num(N_measures, digits = 0)` measures.
 Proportions of replication success per Many Labs project can be found in Table XXX.

### 2023-11-08 Scripts/Manuscript/manuscript.Rmd
added replication ratio table with not right formatting and stopped some output from appearing in code.

@@
 
-```{r Hypothesis 1 Model}
+```{r Hypothesis 1 Model, include = FALSE}
 # first some descriptives of reliability reporting
@@
 ```
-```{r Hypothesis 2 Model}
+```{r Hypothesis 2 Model, include = FALSE}
 # intercept only model to check the within and between group variance.
@@
 
-```{r ICC calculations}
+```{r ICC calculations, include = FALSE}
 # alpha
@@
 
-```{r Hypothesis 3 Main Test}
+```{r Hypothesis 3 Main Test, include = FALSE}
 ## The main model to test hypothesis 3, through a logistic regression model.
@@
 
-```{r Hypothesis 3 Multilevel Model Sensitivity Analyses}
+```{r Hypothesis 3 Multilevel Model Sensitivity Analyses, include = FALSE}
 ## sensitivity analyses.
@@
 
-```{r Hypothesis 4 Model}
+```{r Hypothesis 4 Model, include = FALSE}
 ## Hypothesis 4 beta regression model
@@
 
-```{r Hypothesis 5 Model}
+```{r Hypothesis 5 Model, include = FALSE}
 ## Hypothesis 4 beta regression model
@@
 
-```{r Hypothesis 6 Model}
+```{r Hypothesis 6 Model, include = FALSE}
 H6_test_results <- betareg(Rep_QMP_ratio ~ QMP_ratio, data = data_h6)
@@
 
-```{r Hypotheses 5 & 6 Sensitivity Analyses}
+```{r Hypotheses 5 & 6 Sensitivity Analyses, include = FALSE}
 ## Hypothesis 5 sensitivity test using a random intercept Guassian model.
@@
 
-```{r Hypothesis 6 Associations}
+```{r Hypothesis 6 Associations, include = FALSE}
 ## Associations between the QMP categories
@@
 
-```{r Unidimensionality Exploratory Analysis}
+```{r Unidimensionality Exploratory Analysis, include = FALSE}
 extracted_data_list <- list(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean,
@@
 
-```{r Code for Descriptives Retrieval}
-N_replications <- mean(coded_data_replications$N, na.rm = TRUE)
-IQR_replications <- IQR(coded_data_replications$N, na.rm = TRUE)
-N_original <- mean(coded_data_original_shortened$N, na.rm = TRUE)
-IQR_original <- IQR(coded_data_original_shortened$N, na.rm = TRUE)
-
-N_h_support <- table(coded_data_replications$hypothesis_support)["Yes"]
-N_measures <- nrow(coded_data_replications)
-```
-
-The mean sample size within the replications was `r apa_num(N_replications, digits = 0)` participants (IQR = `r apa_num(IQR_replications, digits = 0)`).
-In the original articles the mean sample size was `r apa_num(N_original, digits = 0)` (IQR = `r apa_num(IQR_original, digits = 0)`).
-In total, support was found for hypothesized effects of `r apa_num(N_h_support, digits = 0)` of the `r apa_num(N_measures, digits = 0)` measures.
+The mean sample size within the replications was `r apa_num(mean(coded_data_replications$N, na.rm = TRUE), digits = 0)` participants (IQR = `r apa_num(IQR(coded_data_replications$N, na.rm = TRUE), digits = 0)`).
+In the original articles the mean sample size was `r apa_num(mean(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)` (IQR = `r apa_num(IQR(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)`).
+In total, support was found for hypothesized effects of `r apa_num(table(coded_data_replications$hypothesis_support)["Yes"], digits = 0)` of the `r apa_num(nrow(coded_data_replications), digits = 0)` measures.
 Proportions of replication success per Many Labs project can be found in Table XXX.
+
+```{r Replication Ratio Table}
+# construct the replication ratio table to be printed
+replication_ratio_table <- data.frame("Many Labs Version" = c("1", "2", "3", "5", "Total"),
+                                      "N Total" = c(table(coded_data_replications$many_labs_version), nrow(coded_data_replications)), 
+                                      "N Replicated" = c(table(coded_data_replications$many_labs_version, coded_data_replications$hypothesis_support)[, "Yes"], table(coded_data_replications$hypothesis_support)["Yes"]))
+
+# calculate the replication ratio from the N measures whose studies were replicated
+# and the N total measures, per Many Labs study.
+replication_ratio_table$"Replication Ratio" <- replication_ratio_table$N.Replicated / replication_ratio_table$N.Total
+
+# print the table in apa formatting
+apa_table(
+  replication_ratio_table, align = c("l", "r", "r", "r")
+  , caption = "Ratio of measures for which the effect was considered replicated, across many labs projects"
+  , note = "AWITHSUPERSCRIPT replication was assessed as unclear for three of the measures, since their effect was not fully replicated.
+These have been treated as not replicated within this table and further analyses throughout the thesis"
+  , escape = TRUE, placement= "h")
+
+### add a midrule before total
+
+```
 

### 2023-11-08 Scripts/Manuscript/manuscript.Rmd
made a succesful replication ratio table.

@@
 
+# Changing column names to be less computer speak-y looking
+colnames(replication_ratio_table) <- c("Many Labs Version", "N Total", "N Replicated",
+                                       "Replication Ratio")
+
+# converting columns to string to then add a superscript to one of the elements
+# in the table.
+replication_ratio_table$"N Replicated" <- as.character(replication_ratio_table$"N Replicated")
+
+# adding a superscript for a later footnote
+replication_ratio_table$"N Replicated"[3] <- "$3^a$"
+
 # print the table in apa formatting
@@
   , caption = "Ratio of measures for which the effect was considered replicated, across many labs projects"
-  , note = "AWITHSUPERSCRIPT replication was assessed as unclear for three of the measures, since their effect was not fully replicated.
+  , note = "$^a$replication was assessed as unclear for three of the measures, since their effect was not fully replicated.
 These have been treated as not replicated within this table and further analyses throughout the thesis"
-  , escape = TRUE, placement= "h")
-
-### add a midrule before total
+  , escape = FALSE, placement= "h", midrules = 4)
 

### 2023-11-08 Scripts/Manuscript/manuscript.Rmd
added the statistics for Hypothesis 1.

@@
 
-INSERT REPLICATION RATIO TABLE HERE
-
-Existing materials were used for 73 of the 77 measures in replications and for 28 in original studies.
-The specific version of the measure was reported for thirteen measures in replications, and nine measures in original articles.
-For those measures that were not based on existing materials, one in the replications and twelve in original articles clearly stated that they were newly created for the study.
-Only one measure in the original articles was modified from its original source during the data collection period, all other measures were modified before that, if at all.
+Existing materials were used for `r apa_num(table(coded_data_replications$sel_existing)["True, namely:"], digits = 0)` of the `r apa_num(nrow(coded_data_replications), digits = 0)` measures in replications and for `r apa_num(table(coded_data_original_shortened$sel_existing)["True, namely:"], digits = 0)` in original studies.
+The specific version of the measure was reported for `r apa_num(length(coded_data_replications$op_version[coded_data_replications$op_version != ""]), numerals = FALSE)` measures in replications, and `r apa_num(length(coded_data_original_shortened$op_version[coded_data_original_shortened$op_version != ""]), numerals = FALSE)` measures in original articles.
+For those measures that were not based on existing materials, `r apa_num(table(coded_data_replications$sel_existing)["False, materials were newly developped for this study"], numerals = FALSE)` in the replications and `r apa_num(table(coded_data_original_shortened$sel_existing)["False, materials were newly developped for this study"], numerals = FALSE)` in original articles clearly stated that they were newly created for the study.
+Only `r apa_num(table(coded_data_original_shortened$mod_time)["After/During"], numerals = FALSE)` measure in the original articles was modified from its original source during the data collection period, all other measures were modified before that, if at all.
 
@@
 Figure XXX depicts the type of measure (single-item, multiple item, or not a scale), if for the measure reliability was reported or not, and what type of reliability coefficient was reported.
-Reliabilities were only assessed for multiple item measures, which were approximately equal between replication and original (35 and 38, respectively).
-Looking at the multiple item measures, four in the replication protocols and twelve in the original articles reported a reliability coefficient.
-The most commonly reported reliability coefficient was Cronbach's alpha, which accounted for three out of four reported reliabilities in the replication protocols, and eleven out of twelve in the original articles.
+Reliabilities were only assessed for multiple item measures, which were approximately equal between replication and original (`r apa_num(table(coded_data_replications$N_items)["multiple item measure"])` and `r apa_num(table(coded_data_original_shortened$N_items)["multiple item measure"])`, respectively).
+Looking at the multiple item measures, `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` in the replication protocols and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles reported a reliability coefficient.
+The most commonly reported reliability coefficient was Cronbach's alpha, which accounted for `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles.
 
@@
 A chi-squared test compared whether the number of reliabilities reported among multiple item measures differed between replications and original.
-Reliabilities were found to be more commonly reported in original articles compared to replication protocols ($\chi^{2}(1) = 4.09, p = 0.043$).
+Reliabilities were found to be more commonly reported in original articles compared to replication protocols ($\chi^{2}$(`r apa_num(H1_test_result$parameter)`) = `r apa_num(H1_test_result$statistic)`, *p* = `r apa_p(H1_test_result$p.value)`).
 These results are contradictory to hypothesis 1.

### 2023-11-09 Data/AnalysisData/codebook_data_H1.Rmd
changed the naming for the hypothesis related functions to match the hypothesis numbering in the manuscript.
failed attempt to include R results as numbers in text.
added the replicability and reliability test table.

@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 10:58:46.380662"
+title: "Codebook created on 2023-11-09 at 2023-11-09 13:46:37.92829"
 output: github_document
@@
 ```{r}
-summaries <- read.csv("codebook_data_H1.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_h1.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-09 Data/AnalysisData/codebook_data_H2.Rmd
failed attempt to include R results as numbers in text.
added the replicability and reliability test table.

@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:49.767935"
+title: "Codebook created on 2023-11-09 at 2023-11-09 13:46:42.481222"
 output: github_document
@@
 ```{r}
-summaries <- read.csv("codebook_data_H2.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_h2.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-09 Data/AnalysisData/codebook_data_H3_avg.Rmd
failed attempt to include R results as numbers in text.
added the replicability and reliability test table.

@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:55.749084"
+title: "Codebook created on 2023-11-09 at 2023-11-09 13:46:45.103283"
 output: github_document
@@
 ```{r}
-summaries <- read.csv("codebook_data_H3_avg.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_h3_avg.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-09 Data/AnalysisData/codebook_data_H3_multiple.Rmd
failed attempt to include R results as numbers in text.
added the replicability and reliability test table.

@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:53.662957"
+title: "Codebook created on 2023-11-09 at 2023-11-09 13:46:43.923892"
 output: github_document
@@
 ```{r}
-summaries <- read.csv("codebook_data_H3_multiple.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_h3_multiple.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-09 Data/AnalysisData/codebook_data_H4.Rmd
failed attempt to include R results as numbers in text.
added the replicability and reliability test table.

@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:23.774949"
+title: "Codebook created on 2023-11-09 at 2023-11-09 13:46:31.706902"
 output: github_document
@@
 ```{r}
-summaries <- read.csv("codebook_data_H4.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_h4.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-09 Data/AnalysisData/codebook_data_H5.Rmd
changed the naming for the hypothesis related functions to match the hypothesis numbering in the manuscript.
failed attempt to include R results as numbers in text.
added the replicability and reliability test table.

@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 10:56:39.032172"
+title: "Codebook created on 2023-11-09 at 2023-11-09 13:46:36.127949"
 output: github_document
@@
 ```{r}
-summaries <- read.csv("codebook_data_H5.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_h5.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-09 Data/AnalysisData/codebook_data_H6.Rmd
changed the naming for the hypothesis related functions to match the hypothesis numbering in the manuscript.
failed attempt to include R results as numbers in text.
added the replicability and reliability test table.

@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 10:47:39.749165"
+title: "Codebook created on 2023-11-09 at 2023-11-09 13:46:34.332851"
 output: github_document
@@
 ```{r}
-summaries <- read.csv("codebook_data_H6.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_h6.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-09 Scripts/Manuscript/manuscript.Rmd
added the replicability and reliability test table.

@@
 library(GPArotation)
+library(ggplot2)
+library(grid)
+library(gridExtra)
 
@@
 # intercept only model to check the within and between group variance.
-H2_test_result_alpha <- summary(lmer(formula = alpha ~ 1 + (1|g), data = data_h2))
+H2_test_result_alpha <- lmer(formula = alpha ~ 1 + (1|g), data = data_h2)
 
@@
 # intercept only model to check the within and between group variance.
-H2_test_result_omega <- summary(lmer(formula = omega.tot ~ 1 + (1|g), data = data_h2[complete.cases(data_h2),]))
+H2_test_result_omega <- lmer(formula = omega ~ 1 + (1|g), data = data_h2[complete.cases(data_h2),])
 
@@
 # alpha
-# within group variance: 0.04384
-# between group variance: 0.19824
-ICC_alpha <- 0.19824 / (0.04384 + 0.19824)
+within_group_variance_alpha <- attr(VarCorr(H2_test_result_alpha), "sc")^2
+between_group_variance_alpha <- attr(VarCorr(H2_test_result_alpha)$g, "stddev")^2
+
+ICC_alpha <- between_group_variance_alpha / (within_group_variance_alpha + between_group_variance_alpha)
 
 # omega
-# within group variance: 0.003779
-# between group variance: 0.034025
-ICC_omega <- 0.034025 / (0.003779 + 0.034025)
+within_group_variance_omega <- attr(VarCorr(H2_test_result_omega), "sc")^2
+between_group_variance_omega <- attr(VarCorr(H2_test_result_omega)$g, "stddev")^2
+
+ICC_omega <- between_group_variance_omega / (within_group_variance_omega + between_group_variance_omega)
 
@@
 ## The main model to test hypothesis 3, through a logistic regression model.
-H3_test_result_main_alpha <- summary(glm(formula = replication ~ 1 + alpha_avg, 
+H3_test_result_main_alpha <- apa_print(glm(formula = replication ~ 1 + alpha, 
                                       family = binomial(), data = data_h3_avg))
@@
 # and for omega
-H3_test_result_main_omega <- summary(glm(formula = replication ~ 1 + 
-                                     omega.tot_avg, family = binomial(), 
+H3_test_result_main_omega <- apa_print(glm(formula = replication ~ 1 + 
+                                     omega, family = binomial(), 
                                      data = data_h3_avg))
@@
 # running a random intercept multilevel logistic model
-H3_test_result_int_sensitivity_alpha <- summary(glmer(formula = replication ~ 1 
+H3_test_result_int_sensitivity_alpha <- apa_print(glmer(formula = replication ~ 1 
                                                 + alpha + (1|g), family = 
@@
 # and for omega
-H3_test_result_int_sensitivity_omega <- summary(glmer(formula = replication ~ 1 
-                                                + omega.tot + (1|g), family = 
+H3_test_result_int_sensitivity_omega <- apa_print(glmer(formula = replication ~ 1 
+                                                + omega + (1|g), family = 
                                                   binomial(), data = 
@@
 # running a random slope multilevel logistic model
-H3_test_result_slp_sensitivity_alpha <- summary(glmer(formula = replication ~ 1 
+H3_test_result_slp_sensitivity_alpha <- apa_print(glmer(formula = replication ~ 1 
                                                 + alpha + (1 + alpha|g), 
@@
 # and for omega
-H3_test_result_slp_sensitivity_omega <- summary(glmer(formula = replication ~ 1 
-                                                + omega.tot + (1 + omega.tot|g), 
+H3_test_result_slp_sensitivity_omega <- apa_print(glmer(formula = replication ~ 1 
+                                                + omega + (1 + omega|g), 
                                                 family = binomial(), data =
@@
 
-The average Cronbach's alpha coefficient across replication sets was $0.618$ with a standard deviation of $0.554$, for omega the mean was $0.773$ with a standard deviation of $0.161$.
+The average Cronbach's alpha coefficient across replication sets was `r apa_num(mean(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(mean(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`, for omega the mean was `r apa_num(sd(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`.
 Figure XXX shows the distributions of the Cronbach's alpha coefficients for each replication set separated by successful and unsuccessful replication.
 
-INSERT PLOT 34
+```{r Plot 23 Alpha Code}
+# plot for alpha
+ggplot(plot_23_data_alpha, aes(x = alpha, y = g)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_hline(yintercept = 6.5, color = "red", size = 1) +
+  geom_point(alpha = 0.1) +
+  theme_minimal() +
+  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), 
+                                                     "lines")) +
+  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0),
+    ymin = 7, ymax = 7, xmin = 1.08, xmax = 1.08) +
+  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0),
+    ymin = 6, ymax = 6, xmin = 1.08, xmax = 1.08) +
+  coord_cartesian(xlim = c(0, 1), clip = "off") +
+  ylab("") +
+  xlab("Cronbach's alpha")
+
+```
+
+```{r Plot 23 Omega Code, include = FALSE, eval = FALSE}
+# plot for omega
+ggplot(plot_23_data_omega, aes(x = alpha, y = g)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_hline(yintercept = 6.5, color = "red", size = 1) +
+  geom_point(alpha = 0.1) +
+  theme_minimal() +
+  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), 
+                                                     "lines")) +
+  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0),
+    ymin = 6, ymax = 6, xmin = 1.08, xmax = 1.08) +
+  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0),
+    ymin = 5, ymax = 5, xmin = 1.08, xmax = 1.08) +
+  coord_cartesian(xlim = c(0, 1), clip = "off") +
+  ylab("") +
+  xlab("Omega")
+
+```
 
 The between-group (across different replication set) variance and within-group (lab locations within a replication set) variance in the Cronbach's alpha coefficient were assessed using a multilevel model as specified in Formulas XXX, XXX, & XXX.
-The between-group and within-group variance for Cronbach's alpha were approximately $0.198$ and $0.044$ respectively.
-The resulting ICC, obtained using formula XXX, was approximately $0.819$.
+The between-group and within-group variance for Cronbach's alpha were approximately `r apa_num(between_group_variance_alpha, digits = 3)` and `r apa_num(within_group_variance_alpha, digits = 3)` respectively.
+The resulting ICC, obtained using formula XXX, was approximately `r apa_num(ICC_alpha, digits = 3)`.
 This suggests that variance was larger between replication sets than within.
-The same analysis for omega coefficients even showed a relatively larger degree of between group variance (between-group variance $= 0.034$, within-group variance $= 0.004$, ICC = $0.900$).
+The same analysis for omega coefficients even showed a relatively larger degree of between group variance (between-group variance `r apa_num(within_group_variance_omega, digits = 3)`, within-group variance `r apa_num(between_group_variance_omega, digits = 3)`, ICC = `r apa_num(ICC_omega, digits = 3)`).
 Both results are in line with hypothesis 2, although caution in interpreting this result is advised due to the small sample size and the lack of an available inferential test.
@@
 
-INSERT REPLICABILITY AND RELIAIBLITY TESTS TABLE HERE
-
-Cronbach's alpha and omega did not significantly relate to replication success in the main logistic regression model (Cronbach's alpha: $B = -1.621, SD = 1.527, p = .288$; omega: $B = 0.495, SD = 3.776, p = .896$), nor in any of the multilevel sensitivity analyses models (see Table XXX).
+```{r Replicability and Reliability Test Table}
+# creating the dtaframe for the table
+H3_table_dataframe <- rbind(H3_test_result_main_alpha$table, H3_test_result_int_sensitivity_alpha$table, H3_test_result_main_omega$table, H3_test_result_int_sensitivity_omega$table, H3_test_result_slp_sensitivity_omega$table)
+
+# adding an asterix for significance to the significant p in the dataframe
+H3_table_dataframe[3,5] <- paste0(H3_table_dataframe[3,5], "^*")
+
+# adding rows to give indication of specific sections (apa_table being awkward)
+H3_table_for_printing <- rbind(c("Alpha", "", "", "", ""), c("Logistic Regression Model", "", "", "", ""), H3_table_dataframe[1:2,], c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(3:4),], c("Omega", "", "", "", ""), c("Logistic Regression Model", "", "", "", ""), H3_table_dataframe[(5:6),], c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(7:8),], c("Random-Slope Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(9:10),])
+
+# print the table in apa formatting
+apa_table(
+  H3_table_for_printing, align = c("l", "r", "r", "r", "r")
+  , caption = "Model Results from Tests of Hypothesis 3"
+  , note = "The Cronbach's alpha section shows the models where the calculated Cronbach's alpha coefficient was the independent variable.
+In the Omega section it was the calculated omega coefficient.
+The random slope model for Cronbach's alpha did not converge, thus it results are not shown here.
+$^* p < .05$"
+  , escape = FALSE, placement= "ht", midrules = c(1, 2, 5, 7, 8, 9, 12, 15))
+
+```
+
+Cronbach's alpha and omega did not significantly relate to replication success in the main logistic regression model (Cronbachs alpha: `r H3_test_result_main_alpha$full_result$alpha`; omega: `r H3_test_result_main_omega$full_result$omega`), nor in any of the multilevel sensitivity analyses models (see Table XXX).
 This is contradictory to the expectation in hypothesis 3.
@@
 ## Questionable Measurement Practices
+
+```{r}
+#apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)
+
+```
 

### 2023-11-09 Scripts/source_script.R

@@ -596,8 +596,11 @@ data_prep_H2 <- function(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean,
     
     Data_H2 <- rbind(Data_H2, reliability_frame)
   }
-  
+
   Data_H2 <- Data_H2[-1,]
+  
+  
+  colnames(Data_H2) <- c("alpha", "omega", "g")
   
   return(Data_H2)
 }
@@ -631,10 +634,10 @@ Data_prep_H3_multiple <- function(Data_H5, Data_H2){
 
 Data_prep_H3_avg <- function(Data_H5, Data_H3_multiple){
   # alpha averaged across sites
-  Data_H3_avg <- data.frame(alpha_avg = sapply(split(Data_H3_multiple$alpha, 
+  Data_H3_avg <- data.frame(alpha = sapply(split(Data_H3_multiple$alpha, 
                                                      Data_H3_multiple$g), mean),
-                            omega.tot_avg = sapply(split(
-                              Data_H3_multiple$omega.tot, Data_H3_multiple$g), 
+                            omega = sapply(split(
+                              Data_H3_multiple$omega, Data_H3_multiple$g), 
                               mean),
                             replication = c(Data_H5[c(10, 11, 12, 13, 26, 29, 
                                                       30, 31, 34, 39, 42, 51, 
@@ -877,9 +880,9 @@ data_prep_plot_23_alpha <- function(Data){
 
 # and for omega
 data_prep_plot_23_omega <- function(Data){
-  Data <- Data[!is.na(Data$omega.tot),]
-  Data$avg.omega.tot <- ave(Data$omega.tot, Data$g)
-  Plot_23_data <- Data[order(-Data$replication, -Data$avg.omega.tot),]
+  Data <- Data[!is.na(Data$omega),]
+  Data$avg.omega <- ave(Data$omega, Data$g)
+  Plot_23_data <- Data[order(-Data$replication, -Data$avg.omega),]
   Plot_23_data$g <- fct_inorder(as.factor(Plot_23_data$g), ordered = NA)
   levels(Plot_23_data$g) <- c("Husnu & Crisp (2010)", 
                               "Nosek et al. (2002), Math", "Nosek et al. (2002), Art", 

### 2023-11-10 Scripts/Manuscript/manuscript.Rmd
added figure 456, and the test result for H4 plus the function used for that to help convert betareg output to apa output.

@@
 library(ggplot2)
+library(ggridges)
+library(GGally)
+library(ggforce)
 library(grid)
@@
 ## Questionable Measurement Practices
+The counts of the QMP ratio obtained for each QMP type (see Table XXX) are shown across the top layer of Figure XXX for both replication protocols and original articles.
+The overall number of counts for the QMP ratios of the QMP modification type were lower compared to the others, because only `r apa_num(table(coded_data_replications$mod_check)["True"])` out of `r apa_num(length(coded_data_replications$mod_check))` measures in replications, and only `r apa_num(table(coded_data_original_shortened$mod_check)["True"], numerals = FALSE)` measures used in original studies were modified.
+The bottom layer of Figure XXX shows the overlayed distributions of the total QMP ratios from the replication protocols and original studies, with dots indicating each datapoint, and the line indicating the mean for either distribution.
+
+INSERT HERE 256
+
+```{r Plot 456 Code}
+# plot for alpha
+### ratio (REV) Original and Rep
+Plot_456_1 <- ggplot(plot_456_data[plot_456_data$QMP_type != "Total",], 
+       aes(x = QMP_ratio, fill = RepOrg)) + 
+  geom_bar(position = "dodge", stat = "bin", bins = 10) +
+  facet_grid(~QMP_type) +
+  theme_minimal() +
+  theme(plot.title = element_text(face = "bold")) +
+  scale_fill_manual(values=c("brown", "blue4")) +
+  theme(legend.position = "none") +
+  ylab("Count") +
+  xlab("QMP Ratio") +
+  ggtitle("QMP Ratio's Per QMP Type Grouped by Original and Replication") +
+  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1"))
+
+Mean_Rat_Rep <- mean(plot_456_data$QMP_ratio[
+  plot_456_data$QMP_type == "Total" & plot_456_data$RepOrg == "Replication"])
+Mean_Rat_Org <- mean(plot_456_data$QMP_ratio[
+  plot_456_data$QMP_type == "Total" & plot_456_data$RepOrg == "Original"])
+
+Plot_456_2 <- ggplot(plot_456_data[plot_456_data$QMP_type == "Total",], 
+       aes(x = QMP_ratio, fill = RepOrg, colour = RepOrg)) +
+  geom_density(alpha = 0.2) +
+  geom_point(y = 0, alpha = 0.2, size = 3) +
+  geom_segment(aes(x = Mean_Rat_Rep, xend = Mean_Rat_Rep, y = 0, yend = 2.66)
+               , color = "blue4") +
+  geom_segment(aes(x = Mean_Rat_Org, xend = Mean_Rat_Org, y = 0, yend = 2.183)
+               , color = "brown") +
+  coord_cartesian(xlim = c(0, 1)) +
+  theme_ridges() + 
+  theme(axis.text.y=element_blank(),
+        axis.ticks.y=element_blank()) +
+  scale_fill_manual(values=c("brown", "blue4")) +
+  scale_color_manual(values=c("brown2", "blue")) +
+  scale_x_continuous(breaks = c(0, Mean_Rat_Rep, 0.25, Mean_Rat_Org, 
+                                0.5, 0.75, 1), 
+                     labels = c("0", "0.18", "0.25", "0.31", "0.5", 
+                                "0.75", "1")) + 
+  ggtitle("Distribution of Total QMP Ratio's by Original and Replication") +
+  guides(color = "none") +
+  labs(fill = "Coded from") +
+  ylab("") +
+  xlab("")
+
+Plot_456_2
+
+# combine both plots into one figure
+grid.arrange(Plot_456_1, 
+             Plot_456_2, 
+             nrow = 2)
+
+```
+
+Beta-regression was used to test the difference in QMP ratio between original articles and replication protocols.
+Results showed that original articles contained a significantly larger proportion of QMPs than replication protocols for the measures of the same effects (`r betareg_output_to_apa_full(H4_test_results_REV)`).
+This result is in line with hypothesis 4.
 
@@
 ```
-
-The counts of the QMP ratio obtained for each QMP type (see Table XXX) are shown across the top layer of Figure XXX for both replication protocols and original articles.
-The overall number of counts for the QMP ratios of the QMP modification type were lower compared to the others, because only 52 out of 77 measures in replications, and only ten measures used in original studies were modified.
-The bottom layer of Figure XXX shows the overlayed distributions of the total QMP ratios from the replication protocols and original studies, with dots indicating each datapoint, and the line indicating the mean for either distribution.
-
-INSERT HERE 256
-
-Beta-regression was used to test the difference in QMP ratio between original articles and replication protocols.
-Results showed that original articles contained a significantly larger proportion of QMPs than replication protocols for the measures of the same effects ($B = -0.779, SD = 0.140, p < .001$).
-This result is in line with hypothesis 4.
 

### 2023-11-10 Scripts/source_script.R

@@ -528,6 +528,33 @@ Sensitivity_H6 <- function(Data){
   return(return_list) 
 }
 
+# function to convert betareg output to apa full style from papaja's apa_print
+betareg_output_to_apa_full<- function(betareg_output, coefficient_number = 2){
+  sum_object <- summary(H4_test_results_REV)$coefficients$mean[coefficient_number,]
+  
+  estimate <- sum_object[1]
+  std_error <- sum_object[2]
+  z_value <- sum_object[3]
+  p_value <- sum_object[4]
+  n <- H4_test_results_REV$n
+  
+  if(z_value < 0){
+    CI_HI <- estimate - z_value * (std_error / sqrt(n))
+    CI_LO <- estimate + z_value * (std_error / sqrt(n))
+  } else{
+    CI_LO <- estimate - z_value * (std_error / sqrt(n))
+    CI_HI <- estimate + z_value * (std_error / sqrt(n))
+  }
+  
+  estimate_string <- paste0("$b = ", apa_num(estimate), "$, ")
+  CI_string <- paste0("95\\% CI $[", apa_num(CI_LO), ", ", apa_num(CI_HI), "]$, ")
+  z_string <- paste0("$z = ", apa_num(z_value), "$, ")
+  p_string <- paste0("$p = ", apa_p(p_value), "$")
+  
+  
+  return(paste0(estimate_string, CI_string, z_string, p_string))
+}
+
 
 
 # Reliability Related Functions ------------------------------------------------

### 2023-11-10 Scripts/Manuscript/manuscript.Rmd
fixed a couple rendering issues

@@
 # adding an asterix for significance to the significant p in the dataframe
-H3_table_dataframe[3,5] <- paste0(H3_table_dataframe[3,5], "^*")
+H3_table_dataframe[3,5] <- paste0(H3_table_dataframe[3,5], "$^*$")
 
@@
   , caption = "Model Results from Tests of Hypothesis 3"
-  , note = "The Cronbach's alpha section shows the models where the calculated Cronbach's alpha coefficient was the independent variable.
-In the Omega section it was the calculated omega coefficient.
+  , note = "The Alpha and Omega sections show the models where the independent variable was the calculated Cronbach's alpha and omega coefficient respectively.
 The random slope model for Cronbach's alpha did not converge, thus it results are not shown here.
@@
 
-Plot_456_2
-
 # combine both plots into one figure

### 2023-11-10 Scripts/source_script.R

@@ -530,13 +530,13 @@ Sensitivity_H6 <- function(Data){
 
 # function to convert betareg output to apa full style from papaja's apa_print
 betareg_output_to_apa_full<- function(betareg_output, coefficient_number = 2){
-  sum_object <- summary(H4_test_results_REV)$coefficients$mean[coefficient_number,]
+  sum_object <- summary(betareg_output)$coefficients$mean[coefficient_number,]
   
   estimate <- sum_object[1]
   std_error <- sum_object[2]
   z_value <- sum_object[3]
   p_value <- sum_object[4]
-  n <- H4_test_results_REV$n
+  n <- betareg_output$n
   
   if(z_value < 0){
     CI_HI <- estimate - z_value * (std_error / sqrt(n))

### 2023-11-13 Data/AnalysisData/codebook_plot_46_data_REV.Rmd
added the results for H5 and H6, including plot 46, which also required the adition of the plot_46_data_rev file, which lead to a rerun of the final data creation code.

--- 2023-11-07 Data/AnalysisData/codebook_Plot_46_data.Rmd
@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:47.216976"
+title: "Codebook created on 2023-11-13 at 2023-11-13 11:23:32.03741"
 output: github_document
@@
 ```{r}
-summaries <- read.csv("codebook_Plot_46_data.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_plot_46_data_REV.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2023-11-13 Scripts/Manuscript/manuscript.Rmd
added the results for H5 and H6, including plot 46, which also required the adition of the plot_46_data_rev file, which lead to a rerun of the final data creation code.

@@
 # plot accompanying the results for Hypotheses 4, & 6
-Plot_46_data <- data_prep_plot_46(data_h6[c(3, 6, 9, 12, 15, 36, 39, 42, 45, 48)])
+plot_46_data <- data_prep_plot_46(data_h6[c(3, 6, 9, 12, 15, 36, 39, 42, 45, 48)])
+plot_46_data_rev <- data_prep_plot_46(data_h6[c(3, 21, 24, 27, 30, 36, 54, 57, 60, 63)])
 # plot accompanying the results for Hypotheses 2, & 3
@@
 
-open_data(data = Plot_46_data, filename = paste0(paste0(
+open_data(data = plot_46_data, filename = paste0(paste0(
   "Data/AnalysisData/", deparse(substitute(Plot_46_data))), ".csv"),
@@
     deparse(substitute(Plot_46_data))), ".yml"))
+
+open_data(data = plot_46_data_rev, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(plot_46_data_rev))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(plot_46_data_rev))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(plot_46_data_rev))), ".yml"))
 
@@
 
-check_h5 <- lmer(formula = QMP ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens)
-H5_sensitivity_test_results <- summary(check_h5)$coefficients
-
-check_h5_REV <- lmer(formula = QMP_REV ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens)
-H5_sensitivity_test_results_REV <- summary(check_h5_REV)$coefficients
+check_h5 <- apa_print(lmer(formula = QMP ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens))
+
+check_h5_REV <- apa_print(lmer(formula = QMP_REV ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens))
 
@@
 # running the models one with none revised QMP ratio's and one with
-check_h6 <- lmer(formula = Rep_QMP ~ 1 + QMP + (1|many_labs_version), data = data_h6_sens)
-H6_sensitivity_test_results <- summary(check_h6)$coefficients
-
-check_h6_REV <- lmer(formula = Rep_QMP_REV ~ 1 + QMP_REV + (1|many_labs_version), data = data_h6_sens)
-H6_sensitivity_test_results_REV <- summary(check_h6_REV)$coefficients
-
-# n of mod ratio's pressent check
+check_h6 <- apa_print(lmer(formula = Rep_QMP ~ 1 + QMP + (1|many_labs_version), data = data_h6_sens))
+
+check_h6_REV <- apa_print(lmer(formula = Rep_QMP_REV ~ 1 + QMP_REV + (1|many_labs_version), data = data_h6_sens))
+
+# n of mod ratio's that are present (check)
 H6_n_check_results <- betareg(Rep_op_ratio ~ mod_ratio, data = data_h6)$n
@@
 The bottom layer of Figure XXX shows the overlayed distributions of the total QMP ratios from the replication protocols and original studies, with dots indicating each datapoint, and the line indicating the mean for either distribution.
-
-INSERT HERE 256
 
@@
 
+A similar beta-regression tested the association between replication success and QMP ratio in replication protocols.
+Results showed that successful replication significantly related to a decrease in the ratio of QMPs in replication protocols (`r betareg_output_to_apa_full(H5_test_results_REV)`).
+Sensitivity analyses were performed using a random-intercept multilevel regression function.
+This model also found a significant association between replication success and QMP ratio (`r check_h5_REV$full_result$hypothesis_supportTRUE`).
+Both of these results are in line with hypothesis 5.
+However, the relationship in the multilevel model is no longer significant for QMP ratios obtained with the initial coding protocol (`r check_h5$full_result$hypothesis_supportTRUE`).
+
+The relation between QMP ratios in the replication protocols and corresponding original articles were investigated using a beta regression model.
+It showed that total QMP ratio in the original article can significantly predict total QMP ratio in the subsequent replication (`r betareg_output_to_apa_full(H6_test_results_REV)`), which provides some evidence in favor of hypothesis 6.
+However, this relation was not significant for the QMP ratios obtained with the initial protocol (`r betareg_output_to_apa_full(H6_test_results)`).
+Sensitivity analyses using a random intercept logistic multilevel model also found some discrepancy in results between revised and initial protocol, albeit with both being non-significant (revised protocol: `r check_h6_REV$full_result$QMP_REV`; initial protocol `r check_h6$full_result$QMP`).
+
+INSERT FIGURE 46 HERE
+
+```{r Plot 46 Initial Data Code, include = FALSE, eval = FALSE}
+# Initial
+ggplot(plot_46_data, aes(QMP_ratio, QMP_Rep_ratio)) + 
+  geom_point() +
+  geom_jitter(width = 0.05, height = 0.05) +
+  stat_smooth(method="lm") + 
+  theme_bw() +
+  theme(strip.text.y = element_text(size = 7), strip.background = element_rect(
+    color = "black", fill = "white", size = 1, linetype = "solid"
+  )) +
+  xlab("QMP Ratio (Original)") + ylab("QMP Ratio (Replication)") +
+  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1")) + 
+  facet_grid(vars(QMP_Rep_type), vars(QMP_type))
+
+```
+
+1
+```{r Plot 46 Revised Data Code}
+# Revised
+ggplot(plot_46_data_rev, aes(QMP_ratio, QMP_Rep_ratio)) + 
+  geom_point() +
+  geom_jitter(width = 0.05, height = 0.05) +
+  stat_smooth(method="lm") + 
+  theme_bw() +
+  theme(strip.text.y = element_text(size = 7), strip.background = element_rect(
+    color = "black", fill = "white", size = 1, linetype = "solid"
+  )) +
+  xlab("QMP Ratio (Original)") + ylab("QMP Ratio (Replication)") +
+  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1")) + 
+  facet_grid(vars(QMP_Rep_type), vars(QMP_type))
+
+```
+
+## Exploratory Results
+
 ```{r}
@@
 
-```
-
-A similar beta-regression tested the association between replication success and QMP ratio in replication protocols.
-Results showed that successful replication significantly related to a decrease in the ratio of QMPs in replication protocols $\left(B = -0.588, SD = 0.212, p < .001 \right)$.
-Sensitivity analyses were performed using a random-intercept multilevel regression function.
-This model also found a significant association between replication success and QMP ratio $\left(B = -0.963, t(70.319) = -1.491, p = .011 \right)$.
-Both of these results are in line with hypothesis 5.
-However, the relationship in the multilevel model is no longer significant for QMP ratios obtained with the initial coding protocol $\left(B = -0.517, t(63.122) = -2.635, p = .140 \right)$.
-
-The relation between QMP ratios in the replication protocols and corresponding original articles were investigated using a beta regression model.
-It showed that total QMP ratio in the original article can significantly predict total QMP ratio in the subsequent replication ($B = 1.477, SD = 0.579, p < .001$), which provides some evidence in favor of hypothesis 6.
-However, this relation was not significant for the QMP ratios obtained with the initial protocol ($B = -0.387, SD = 0.511, p = 0.449$).
-Sensitivity analyses using a random intercept logistic multilevel model also found similar discrepancy in results between revised and initial protocol (revised protocol: $B = 0.249, t(74.473) = 1.498, p < 0.001$; initial protocol $B = -0.057, t(74.620) = -0.332, p = 0.741$).
-
-INSERT FIGURE 26 HERE
-
-## Exploratory Results
+# $\left(B = -0.963, t(70.319) = -1.491, p = .011 \right)$
+
+```
 

### 2023-11-14 Scripts/Manuscript/manuscript.Rmd
added the exploratory analyses results tables.

@@
                           N_factors = 0,
-                          Single_factor = FALSE)
+                          Single_factor = "")
 
@@
 
+  if(is.null(RMSEA_value) != TRUE){
+    RMSEA_value <- apa_num(RMSEA_value, digits = 3)
+  }
+
   # conducting parallel test to check if one factor solution is best.
@@
   # adding a single factor check indicator value
-  single_factor <- ifelse(RMSEA_value < 0.08 | parallel_N_factors == 1, TRUE, 
-                          FALSE)
+  single_factor <- ifelse(RMSEA_value < 0.08 | parallel_N_factors == 1, "Yes", 
+                          "No")
 
@@
 
-INSERT FIGURE 46 HERE
-
-```{r Plot 46 Initial Data Code, include = FALSE, eval = FALSE}
+```{r Plot 46 Initial Data Code, include = FALSE, eval = FALSE, error = FALSE}
 # Initial
@@
 
-1
-```{r Plot 46 Revised Data Code}
+```{r Plot 46 Revised Data Code, error = FALSE}
 # Revised
@@
 
-```{r}
-#apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)
-
-# $\left(B = -0.963, t(70.319) = -1.491, p = .011 \right)$
-
-```
-
 Planned exploratory analyses were preformed to expand on the test for hypothesis 6.
@@
 
-INSERT QMP REPLICATION ASSOCIATION TESTS TABLE
-
-INSERT QMP ORIGINAL REPLICATION ASSOCIATION TESTS TABLE
+```{r H6 Exploratory Associations Revised Table}
+# creating the dataframe for the table
+H6_table_dataframe_l_REV <- rbind(Results_H6_between_REV$def_def, Results_H6_between_REV$def_op,
+  Results_H6_between_REV$def_sel, Results_H6_between_REV$def_quant, Results_H6_between_REV$def_mod, 
+  Results_H6_between_REV$op_def, Results_H6_between_REV$op_op, Results_H6_between_REV$op_sel, 
+  Results_H6_between_REV$op_quant, Results_H6_between_REV$op_mod, Results_H6_between_REV$sel_def, 
+  Results_H6_between_REV$sel_op, Results_H6_between_REV$sel_sel, Results_H6_between_REV$sel_quant, 
+  Results_H6_between_REV$sel_mod)
+
+H6_table_dataframe_r_REV <- rbind(Results_H6_between_REV$quant_def, Results_H6_between_REV$quant_op,
+  Results_H6_between_REV$quant_sel, Results_H6_between_REV$quant_quant, Results_H6_between_REV$quant_mod, 
+  Results_H6_between_REV$mod_def, Results_H6_between_REV$mod_op, Results_H6_between_REV$mod_sel, 
+  Results_H6_between_REV$mod_quant, Results_H6_between_REV$mod_mod, Results_H6_between_REV$tot_def, 
+  Results_H6_between_REV$tot_op, Results_H6_between_REV$tot_sel, Results_H6_between_REV$tot_quant, 
+  Results_H6_between_REV$tot_mod)
+
+H6_table_dataframe_REV <- cbind(H6_table_dataframe_l_REV, H6_table_dataframe_r_REV)
+
+# adding asterices for significance to the significant p in the dataframe
+H6_table_dataframe_REV[11,3] <- paste0(H6_table_dataframe_REV[11,3], "$^*$")
+H6_table_dataframe_REV[13,3] <- paste0(H6_table_dataframe_REV[13,3], "$^*$")
+H6_table_dataframe_REV[14,3] <- paste0(H6_table_dataframe_REV[14,3], "$^*$")
+H6_table_dataframe_REV[4,6] <- paste0(H6_table_dataframe_REV[4,6], "$^*$")
+H6_table_dataframe_REV[11,6] <- paste0(H6_table_dataframe_REV[11,6], "$^*$")
+H6_table_dataframe_REV[13,6] <- paste0(H6_table_dataframe_REV[13,6], "$^*$")
+H6_table_dataframe_REV[14,6] <- paste0(H6_table_dataframe_REV[14,6], "$^*$")
+
+# adding a column to help indicate the original QMP type
+H6_table_dataframe_REV_expanded <- cbind(c("Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification"), H6_table_dataframe_REV)
+
+# adding rows to give indication of specific sections (apa_table being awkward)
+H6_table_REV_for_printing <- rbind(c("QMP Type", "", "Definition", "", "", "Quantification", ""), H6_table_dataframe_REV_expanded[1:5,], c("QMP Type", "", "Operationalisation", "", "", "Modification", ""),  H6_table_dataframe_REV_expanded[(6:10),], c("QMP Type", "", "Selection", "", "", "Total", ""), H6_table_dataframe_REV_expanded[(11:15),])
+
+colnames(H6_table_REV_for_printing) <-  c("Original", "$b$", "SD", "$p$", "$b$", "SD", "$p$")
+
+# print the table in apa formatting
+apa_table(
+  H6_table_REV_for_printing, align = c("l", "r", "c", "r", "r", "c", "r")
+  , caption = "Beta Regression Test Results for the Association between Replication
+QMP Ratio and Original QMP Ratio as obtained using the Revised Protocol"
+  , note = "Rows indicate Original QMP type, and within table indicates Replication QMP type.
+Sample size for comparisons involving modification were lower since not all measures were modified.
+Therefore the standard errors are larger.
+$^* p < .05$"
+  , escape = FALSE, placement= "ht", midrules = c(1, 6, 7, 12, 13))
+
+### Possible change: omit sd and p-value, and instead show CI and n, in which case also the note should be changed.
+
+```
+
+```{r H6 Exploratory Associations Initial Table}
+# creating the dataframe for the table
+H6_table_dataframe_l <- rbind(Results_H6_between$def_def, Results_H6_between$def_op,
+  Results_H6_between$def_sel, Results_H6_between$def_quant, Results_H6_between$def_mod, 
+  Results_H6_between$op_def, Results_H6_between$op_op, Results_H6_between$op_sel, 
+  Results_H6_between$op_quant, Results_H6_between$op_mod, Results_H6_between$sel_def, 
+  Results_H6_between$sel_op, Results_H6_between$sel_sel, Results_H6_between$sel_quant, 
+  Results_H6_between$sel_mod)
+
+H6_table_dataframe_r <- rbind(Results_H6_between$quant_def, Results_H6_between$quant_op,
+  Results_H6_between$quant_sel, Results_H6_between$quant_quant, Results_H6_between$quant_mod, 
+  Results_H6_between$mod_def, Results_H6_between$mod_op, Results_H6_between$mod_sel, 
+  Results_H6_between$mod_quant, Results_H6_between$mod_mod, Results_H6_between$tot_def, 
+  Results_H6_between$tot_op, Results_H6_between$tot_sel, Results_H6_between$tot_quant, 
+  Results_H6_between$tot_mod)
+
+H6_table_dataframe <- cbind(H6_table_dataframe_l, H6_table_dataframe_r)
+
+# adding asterices for significance to the significant p in the dataframe
+H6_table_dataframe[8,3] <- paste0(H6_table_dataframe[8,3], "$^*$")
+H6_table_dataframe[11,3] <- paste0(H6_table_dataframe[11,3], "$^*$")
+H6_table_dataframe[14,3] <- paste0(H6_table_dataframe[14,3], "$^*$")
+H6_table_dataframe[8,6] <- paste0(H6_table_dataframe[8,6], "$^*$")
+H6_table_dataframe[9,6] <- paste0(H6_table_dataframe[9,6], "$^*$")
+H6_table_dataframe[11,6] <- paste0(H6_table_dataframe[11,6], "$^*$")
+H6_table_dataframe[13,6] <- paste0(H6_table_dataframe[13,6], "$^*$")
+
+# adding a column to help indicate the original QMP type
+H6_table_dataframe_expanded <- cbind(c("Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification"), H6_table_dataframe)
+
+# adding rows to give indication of specific sections (apa_table being awkward)
+H6_table_for_printing <- rbind(c("QMP Type", "", "Definition", "", "", "Quantification", ""), H6_table_dataframe_expanded[1:5,], c("QMP Type", "", "Operationalisation", "", "", "Modification", ""),  H6_table_dataframe_expanded[(6:10),], c("QMP Type", "", "Selection", "", "", "Total", ""), H6_table_dataframe_expanded[(11:15),])
+
+colnames(H6_table_for_printing) <-  c("Original", "$b$", "SD", "$p$", "$b$", "SD", "$p$")
+
+# print the table in apa formatting
+apa_table(
+  H6_table_for_printing, align = c("l", "r", "c", "r", "r", "c", "r")
+  , caption = "Beta Regression Test Results for the Association between Replication
+QMP Ratio and Original QMP Ratio as obtained using the Initial Protocol"
+  , note = "Rows indicate Original QMP type, and within table indicates Replication QMP type.
+Sample size for comparisons involving modification were lower since not all measures were modified.
+Therefore the standard errors are larger.
+$^* p < .05$"
+  , escape = FALSE, placement= "ht", midrules = c(1, 6, 7, 12, 13))
+
+```
 
@@
 
-INSERT FACTOR ANALYSES RESULTS TABLE HERE
+```{r Unidimesnionality Test Results Table}
+# add the names of the relevant papers and a shortcut for the measure used.
+cfa_results_expanded <- cbind(c("Caruso et al.
+(2012)", "Husnu & Crisp (2010)", "Nosek et al.
+(2002), Art", "Nosek et al.
+(2002), Math", "Van Lange et al.
+(1997)", "Anderson et al.
+(2012), SWL", "Anderson et al.
+(2012), PA", "Anderson et al.
+(2012), NA", "Giessner & Schubert (2007)", "Norenzayan et al.
+(2002)", "Zhong & Liljenquist (2006)", "Monin & Miller (2001), most", "Monin & Miller (2001), some", "Cacioppo et al.
+(1983), elm", "Cacioppo et al.
+(1983), nfc", "De Fruyt et al.
+(2000), consc", "Albarracín et al.
+(2008), exp.
+5", "Shnabel & Nadler (2008)", "Vohs & Schooler (2008)"), cfa_results)
+
+# adding sensible column names
+colnames(cfa_results_expanded) <- c("Original Article", "RMSEA", "N Factors", "Unidimensional")
+
+# Renaming the columns for the not converged cfa.
+cfa_results_for_print <- cfa_results_expanded
+cfa_results_for_print$RMSEA[16] <- "Did"
+cfa_results_for_print$`N Factors`[16] <- "Not"
+cfa_results_for_print$Unidimensional[16] <- "Converge"
+
+# print the table in apa formatting
+apa_table(
+  cfa_results_for_print, align = c("l", "r", "r", "r")
+  , caption = "RMSEA and Parallel Analysis Suggested Factors based on Factor Analysis
+for Measure Data", note = "N Factors refer to the number of factors suggested based on parallel analysis of the measure data.
+The word or abbreviation after the author names and year indicates the specific measure within that original article that was analysed.", escape = FALSE, row.names = FALSE, placement= "ht")
+
+```
 

### 2023-11-14 Scripts/source_script.R

@@ -546,15 +546,28 @@ betareg_output_to_apa_full<- function(betareg_output, coefficient_number = 2){
     CI_HI <- estimate + z_value * (std_error / sqrt(n))
   }
   
+  
   estimate_string <- paste0("$b = ", apa_num(estimate), "$, ")
   CI_string <- paste0("95\\% CI $[", apa_num(CI_LO), ", ", apa_num(CI_HI), "]$, ")
   z_string <- paste0("$z = ", apa_num(z_value), "$, ")
+
+  
   p_string <- paste0("$p = ", apa_p(p_value), "$")
   
   
   return(paste0(estimate_string, CI_string, z_string, p_string))
 }
 
+# function to convert betareg output to apa style for a simple table
+betareg_output_to_apa_simple_table <- function(betareg_output, coefficient_number = 2){
+  sum_object <- summary(betareg_output)$coefficients$mean[coefficient_number,]
+  
+  estimate <- apa_num(sum_object[1])
+  std_error <- apa_num(sum_object[2])
+  p_value <- apa_p(sum_object[4])
+  
+  return(c(estimate, std_error, p_value))
+}
 
 
 # Reliability Related Functions ------------------------------------------------
@@ -727,7 +740,7 @@ cfa_ML_measures <- function(Extracted_Data_List){
 
 
 # Analyses Test Functions ------------------------------------------------------
-# creates and returns the associations between QMP categories
+  # creates and returns the associations between QMP categories
 Associations_H6 <- function(Data){
   return_list <- list(def_def = 0, def_op = 0, def_sel = 0, def_quant = 0, 
                       def_mod = 0, op_def = 0, op_op = 0, op_sel = 0, 
@@ -740,66 +753,66 @@ Associations_H6 <- function(Data){
   # Associations between the QMP categories
   # Mod_ratio is compared on a subset of the data, because it has several 
   # missing cases, due to some files not having any modifications.
-  return_list[[1]] <- summary(betareg(Rep_def_ratio ~ def_ratio, 
-                                      data = Data))$coefficients[1]
-  return_list[[2]] <- summary(betareg(Rep_def_ratio ~ op_ratio, 
-                                      data = Data))$coefficients[1]
-  return_list[[3]] <- summary(betareg(Rep_def_ratio ~ sel_ratio, 
-                                      data = Data))$coefficients[1]
-  return_list[[4]] <- summary(betareg(Rep_def_ratio ~ quant_ratio, 
[…]

### 2023-11-15 Scripts/Manuscript/manuscript.Rmd
added the QMPCodingInfoTable.

@@
 The tests for hypotheses 4, 5, & 6 were all based on the number of QMPs per category that were determined by the research using the coding protocol.
-An overview of the QMP categories of the coding variables, based on @flake2020measurement, can be seen in Table INSERT TABLE 1 REF HERE
-
-INSERT TABLE 1 HERE
+An overview of the QMP categories of the coding variables, based on @flake2020measurement, can be seen in Table \@ref(tab:QMPCodingInfoTable)
+
+\renewcommand{\arraystretch}{0.5}
+```{r QMPCodingInfoTable}
+QMP_info_dataframe <-data.frame(Category = c("Definition", "", "", "Operationalisation", "", "", "", "Selection/Creation", "", "", "Quantification", "Modification", "", "", "", "", ""),
+           'N Questions' = c("1", "", "", "5", "", "", "", "4", "", "", "4", "6", "", "", "", "", ""),
+           'Example Question' = c("A psychological/sociological definition",
+            "is given to the name of the measured",
+            "variable within the paper.", 
+            "The administration format (pen-and-",
+            "paper/computer) and environment (in",
+            "public/in a lab) are described (Note:",
+            "both should be present for a true rating).", 
+            "The source of the scale is provided",
+            "(in case the scale was newly developed",
+            "this should be clearly stated).", 
+            "The number of items are described.", 
+            "Any format changes are mentioned",
+            "(paper-and-pencil <–> computer), if no",
+            "changes were made to the format, and",
+            "this was mentioned then code as No",
+            "modification. If it is not clear, then code",
+            "as False."))
+
+# transfer the data to an APA table for printing
+apa_table(
+  QMP_info_dataframe, align = c("l", "r", "l")
+  , caption = "Information of QMP coding variables per category."
+  , note = "N Questions refers only to the questions considered quantative as specified in the text below."
+  , escape = FALSE, placement= "ht", booktabs = TRUE)
+
+```
+\renewcommand{\arraystretch}{1}
 
@@
 These have been treated as not replicated within this table and further analyses throughout the thesis"
-  , escape = FALSE, placement= "h", midrules = 4)
+  , escape = FALSE, placement = "ht", midrules = 4)
 
@@
 ## Questionable Measurement Practices
+
 The counts of the QMP ratio obtained for each QMP type (see Table XXX) are shown across the top layer of Figure XXX for both replication protocols and original articles.

### 2023-11-15 Scripts/Manuscript/manuscript.Rmd
added all of the figure and table cross-references to the project, and changed the spacing in tables to be smaller.

@@
 
-  Enter author note here. Caspar?
+  Enter author note here. Caspar/Jelte/Marjan?
 
@@
 
-# creates a reference list for all used R packages and the installed R version (does not include Rstudio)
+# creates a reference list for all used R packages and the installed R version (does not automatically include Rstudio)
 r_refs("r-references.bib")
+
+# manually retrieving the Rstudio version
 
@@
 
-The publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio [@Posit2023RStudio] with R version 4.2.2 [@R2021R].
+The publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio XXXRSTUDIOREFERENCEHEREXXX.
+with R version 4.2.2 XXXRREFERENCEHEREXXX.
 Using the replication protocols, codebooks, and analysis scripts from each replication set as a guide, the variables associated with each measure were extracted into their own data frame containing the data from all studies in one replication set.
@@
 
-## Measures {#sec:measures}
+## Measures
 
@@
 
-\renewcommand{\arraystretch}{0.5}
+\renewcommand{\arraystretch}{0.7}
+
 ```{r QMPCodingInfoTable}
@@
 ```
-\renewcommand{\arraystretch}{1}
 
@@
 ```{=tex}
-\begin{align*}
-& Level 1: alpha_{ij} = \beta_{0j} + e_{ij} \qquad\qquad\quad e_{ij} \sim N(0, \sigma_{e}^{2}) \\
-& Level 2: \beta_{0j} = \gamma_{00} + u_{0j} \qquad\qquad\qquad u_{0j} \sim N(0, \sigma_{u0}^{2}) \\
-& Mixed: alpha_{ij} = \gamma_{00} + u_{0j} + e_{ij}
-\end{align*}
+\begin{align}
+& Level 1: alpha_{ij} = \beta_{0j} + e_{ij} \qquad\qquad\quad e_{ij} \sim N(0, \sigma_{e}^{2}) (\#eq:level1H2) \\
+& Level 2: \beta_{0j} = \gamma_{00} + u_{0j} \qquad\qquad\qquad u_{0j} \sim N(0, \sigma_{u0}^{2}) (\#eq:level2H2) \\
+& Mixed: alpha_{ij} = \gamma_{00} + u_{0j} + e_{ij} (\#eq:mixedH2)
+\end{align}
 ```
@@
 
-$$ICC = \frac{u_{0j}}{(e_{ij} + u_{0j})}$$
+```{=tex}
+\begin{equation}
+ICC = \frac{u_{0j}}{(e_{ij} + u_{0j})} (\#eq:ICC)
+\end{equation}
+```
 
@@
 
-$$f(replicated_{i}) = \beta_{0} + \beta_{1} alpha_{i}$$
+```{=tex}
+\begin{equation}
+f(replicated_{i}) = \beta_{0} + \beta_{1} alpha_{i} (\#eq:H3Main)
+\end{equation}
+```
 
@@
 
-$$f(.) = log\frac{p_{replicated}}{1 - p_{replicated}}$$
+```{=tex}
+\begin{equation}
+f(.) = log\frac{p_{replicated}}{1 - p_{replicated}} (\#eq:LogitLink)
+\end{equation}
+```
 
@@
 The results using the original QMP data are mentioned when the results led to different conclusions.
-The analysis code for both the original and revised QMP data are available in R script on the OSF page of this thesis: <https://osf.io/9r8yt/>.
+The analysis code for both the original and revised QMP data are available in the R script on both the OSF page (<https://osf.io/9r8yt/>) and github page (<https://github.com/CasGoos/measurement_and_replication.git>) of this article.
 
@@
 
-$$g(.) = (0, 1) \mapsto \mathbb{R}$$
+```{=tex}
+\begin{equation}
+g(.) = (0, 1) \mapsto \mathbb{R} (\#eq:BetaLink)
+\end{equation}
+```
 
@@
 
-$$g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replication_{i}$$
+```{=tex}
+\begin{equation}
+g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replication_{i} (\#eq:H4Main)
+\end{equation}
+```
 
@@
 
-$$g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replicated_{i}$$
+```{=tex}
+\begin{equation}
+g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replicated_{i} (\#eq:H5Main)
+\end{equation}
+```
 
@@
 
-$$g(QMP\_ratio\_replication_{i}) = \beta_{0} + \beta_{1} QMP\_ratio\_original_{i}$$
+```{=tex}
+\begin{equation}
+g(QMP\_ratio\_replication_{i}) = \beta_{0} + \beta_{1} QMP\_ratio\_original_{i} (\#eq:H6Main)
+\end{equation}
+```
 
@@
 In total, support was found for hypothesized effects of `r apa_num(table(coded_data_replications$hypothesis_support)["Yes"], digits = 0)` of the `r apa_num(nrow(coded_data_replications), digits = 0)` measures.
-Proportions of replication success per Many Labs project can be found in Table XXX.
-
-```{r Replication Ratio Table}
+Proportions of replication success per Many Labs project can be found in Table \@ref(tab:ReplicationRatioTable).
+
+```{r ReplicationRatioTable}
 # construct the replication ratio table to be printed
@@
 
-Figure XXX depicts the type of measure (single-item, multiple item, or not a scale), if for the measure reliability was reported or not, and what type of reliability coefficient was reported.
+Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts the type of measure (single-item, multiple item, or not a scale), if for the measure reliability was reported or not, and what type of reliability coefficient was reported.
 Reliabilities were only assessed for multiple item measures, which were approximately equal between replication and original (`r apa_num(table(coded_data_replications$N_items)["multiple item measure"])` and `r apa_num(table(coded_data_original_shortened$N_items)["multiple item measure"])`, respectively).
@@
 
-![Figure 1. Reliability reporting flow diagram](../../SupplementaryMaterials/reliability_reporting_flow_diagram.png)
+```{r ReliabilityReportingFlowDiagram, fig.cap = "Reliability reporting flow diagram."}
+knitr::include_graphics(path = "../../SupplementaryMaterials/reliability_reporting_flow_diagram.png")
+```
 
@@
 The average Cronbach's alpha coefficient across replication sets was `r apa_num(mean(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(mean(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`, for omega the mean was `r apa_num(sd(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`.
-Figure XXX shows the distributions of the Cronbach's alpha coefficients for each replication set separated by successful and unsuccessful replication.
-
-```{r Plot 23 Alpha Code}
+Figure \@ref(fig:Plot23AlphaCode) shows the distributions of the Cronbach's alpha coefficients for each replication set separated by successful and unsuccessful replication.
+
+```{r Plot23AlphaCode, fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the eighteen distinct measures for which suitable raw data was available to calculate Cronbach’s alpha coefficients from."}
 # plot for alpha
@@
 
-```{r Plot 23 Omega Code, include = FALSE, eval = FALSE}
+```{r Plot23OmegaCode, include = FALSE, eval = FALSE}
 # plot for omega
@@
   xlab("Omega")
-
-```
-
-The between-group (across different replication set) variance and within-group (lab locations within a replication set) variance in the Cronbach's alpha coefficient were assessed using a multilevel model as specified in Formulas XXX, XXX, & XXX.
-The between-group and within-group variance for Cronbach's alpha were approximately `r apa_num(between_group_variance_alpha, digits = 3)` and `r apa_num(within_group_variance_alpha, digits = 3)` respectively.
-The resulting ICC, obtained using formula XXX, was approximately `r apa_num(ICC_alpha, digits = 3)`.
+```
+
+The between-group (across different replication set) variance and within-group (lab locations within a replication set) variance in the Cronbach's alpha coefficient were assessed using a multilevel model as specified in Formulas \@ref(eq:level1H2), \@ref(eq:level2H2), & \@ref(eq:mixedH2) The between-group and within-group variance for Cronbach's alpha were approximately `r apa_num(between_group_variance_alpha, digits = 3)` and `r apa_num(within_group_variance_alpha, digits = 3)` respectively.
+The resulting ICC, obtained using formula \@ref(eq:ICC), was approximately `r apa_num(ICC_alpha, digits = 3)`.
 This suggests that variance was larger between replication sets than within.
@@
 Further sensitivity analyses were performed using multilevel logistic models, with each measure as an overarching group wherein its reliability at each lab location is nested.
-The results of the logistic and multilevel logistic models are shown in Table XXX for both Cronbach's alpha and omega reliability coefficients.
-
-```{r Replicability and Reliability Test Table}
+The results of the logistic and multilevel logistic models are shown in Table \@ref(tab:ReplicabilityReliabilityTestTable) for both Cronbach's alpha and omega reliability coefficients.
+
+```{r ReplicabilityReliabilityTestTable}
 # creating the dtaframe for the table
@@
 
-Cronbach's alpha and omega did not significantly relate to replication success in the main logistic regression model (Cronbachs alpha: `r H3_test_result_main_alpha$full_result$alpha`; omega: `r H3_test_result_main_omega$full_result$omega`), nor in any of the multilevel sensitivity analyses models (see Table XXX).
+Cronbach's alpha and omega did not significantly relate to replication success in the main logistic regression model (Cronbachs alpha: `r H3_test_result_main_alpha$full_result$alpha`; omega: `r H3_test_result_main_omega$full_result$omega`), nor in any of the multilevel sensitivity analyses models (see Table \@ref(tab:ReplicabilityReliabilityTestTable)).
 This is contradictory to the expectation in hypothesis 3.
@@
 
-The counts of the QMP ratio obtained for each QMP type (see Table XXX) are shown across the top layer of Figure XXX for both replication protocols and original articles.
+The counts of the QMP ratio obtained for each QMP type (see Table \@ref(tab:QMPCodingInfoTable)) are shown across the top layer of Figure \@ref(fig:Plot456Code) for both replication protocols and original articles.
 The overall number of counts for the QMP ratios of the QMP modification type were lower compared to the others, because only `r apa_num(table(coded_data_replications$mod_check)["True"])` out of `r apa_num(length(coded_data_replications$mod_check))` measures in replications, and only `r apa_num(table(coded_data_original_shortened$mod_check)["True"], numerals = FALSE)` measures used in original studies were modified.
-The bottom layer of Figure XXX shows the overlayed distributions of the total QMP ratios from the replication protocols and original studies, with dots indicating each datapoint, and the line indicating the mean for either distribution.
-
-```{r Plot 456 Code}
+The bottom layer of Figure \@ref(fig:Plot456Code) shows the overlayed distributions of the total QMP ratios from the replication protocols and original studies, with dots indicating each datapoint, and the line indicating the mean for either distribution.
+
+```{r Plot456Code, fig.cap = "QMP ratio counts for each QMP Type and QMP total ratio distribution grouped by where each was coded from.
+The top row shows binned counts of QMP ratio’s that were observed for each replication protocol and original article, across the different QMP types.
+The bottom graph shows the distributions of total QMP ratios for both replication protocols and original articles, with the line indicating the mean QMP ratio.
+The specific observed values are indicated along the bottom row with dots"}
 # plot for alpha
@@
 
-```{r Plot 46 Initial Data Code, include = FALSE, eval = FALSE, error = FALSE}
+```{r Plot46InitialDataCode, include = FALSE, eval = FALSE, error = FALSE}
 # Initial
@@
 
-```{r Plot 46 Revised Data Code, error = FALSE}
+```{r Plot46RevisedDataCode, error = FALSE, fig.cap = "Scatterplot of original and replication QMP ratio’s per type with linear regression line.
+The abbreviations on the axes relate to the QMP categories described in Table 1: Def.
+is definition, Op.
+is operationalization, Sel.
+is selection/creation, Quant.
+is quantification, and Mod.
+is modification.
+The X axis facets across the QMP ratios in the original articles, and the Y axis facets across the QMP ratios in the replication protocols.
+Each dot in the figure relates to describes the QMP ratio for the types in that graph across an original article and its replication protocol.
+Note: jitter was applied to these dots in order to show the number of observations at points where multiple dots were present"}
 # Revised
@@
 The relationships between original article QMP ratios and replication protocol QMP ratios were investigated for each QMP type separately.
-Table XXX shows the results from these tests with the revised protocol QMP coding, while Table XXX shows the results for the QMP ratios obtained via the initial protocol.
+Table \@ref(tab:H6ExploratoryAssociationsRevisedTable) shows the results from these tests with the revised protocol QMP coding, while Table \@ref(tab:H6ExploratoryAssociationsInitialTable) shows the results for the QMP ratios obtained via the initial protocol.
 There were few significant relations and even fewer that are consistent between both coding protocols.
@@
 
-```{r H6 Exploratory Associations Revised Table}
+```{r H6ExploratoryAssociationsRevisedTable}
 # creating the dataframe for the table
@@
 
-```{r H6 Exploratory Associations Initial Table}
+```{r H6ExploratoryAssociationsInitialTable}
 # creating the dataframe for the table
@@
 
-Figure XXX visually illustrates the relations of QMP ratios from different QMP types between replication protocols and original articles further.
-
-The unidimensionality of the measures used in the Many Labs projects was assessed through factor analyses, and evaluated based on the criteria discussed in section XXX.
+Figure \@ref(fig:Plot46RevisedDataCode) visually illustrates the relations of QMP ratios from different QMP types between replication protocols and original articles further.
+
+The unidimensionality of the measures used in the Many Labs projects was assessed through factor analyses, and evaluated based on the criteria discussed in the Exploratory Analyses section above.
 Suitable data for factor analyses was available for nineteen measures.
-These measures were the same as those shown in Figure XXX, with the addition of one more measure from [@cacioppo1983effects].
+These measures were the same as those shown in Figure \@ref(fig:Plot23AlphaCode), with the addition of one more measure from [@cacioppo1983effects].
 A composite score based on the measurement responses was used for sixteen of the nineteen measures to form a single variable in the analyses, and were thus regarded as intended to be unidimensional.
@@
 Sufficient fit of the unidimensional model was found for six out of the nineteen evaluated measures.
-However, as shown in Table XXX the unidimensional model did not hold for any measure data based on the parallel analysis test alone.
+However, as shown in Table \@ref(tab:UnidimesnionalityTestResultsTable) the unidimensional model did not hold for any measure data based on the parallel analysis test alone.
 Only the RMSEA $< .08$ criteria suggested evidence for single factor structures.
 
-```{r Unidimesnionality Test Results Table}
+```{r UnidimesnionalityTestResultsTable}
 # add the names of the relevant papers and a shortcut for the measure used.
@@
 Furthermore, across measures used in both original and replication studies, less than half of the measures were multiple item scales.
-Research commonly made use of single item measures (see Figure XXX for more details), an observation that was also made by @shaw2020measurement.
+Research commonly made use of single item measures (see Figure \@ref(fig:ReliabilityReportingFlowDiagram) for more details), an observation that was also made by @shaw2020measurement.
 The use of these single item measures comes with risks, since by virtue of being singular they assume that whatever they are measuring is unidimensional, while not being able to test this assumption [@shaw2020measurement].
@@
 
-Further analyses based on the QMP ratios of each specific type indicated that across both the initial and revised coding protocols together, only selection, definition, and quantification QMPs in the original article related significantly to selection type QMPs, total QMPs, or both in the replication (see Tables XXX & XXX).
+Further analyses based on the QMP ratios of each specific type indicated that across both the initial and revised coding protocols together, only selection, definition, and quantification QMPs in the original article related significantly to selection type QMPs, total QMPs, or both in the replication (see Tables \@ref(tab:H6ExploratoryAssociationsRevisedTable) & \@ref(tab:H6ExploratoryAssociationsInitialTable)).
 
@@
 These former are features of a measurement, which while preferably similar in a replication to the original, can and should be reported in the replication protocol even if the original article does not contain the details on these features itself.
-However, these are just speculations as the results showed no clear relations between different QMP types across original and replication (see Figure XXX), and testing of causal links was not possible with this data.
+However, these are just speculations as the results showed no clear relations between different QMP types across original and replication (see Figure \@ref(fig:Plot46RevisedDataCode)), and testing of causal links was not possible with this data.
 
@@
 However, future research might consider methods specifically designed to assess reliability and validity of single item measures.
-This could prove to be a worthwhile contribution, given the proportionally large number of single item measures that were encountered in the data for this thesis (see Figure XXX).
+This could prove to be a worthwhile contribution, given the proportionally large number of single item measures that were encountered in the data for this thesis (see Figure \@ref(fig:ReliabilityReportingFlowDiagram)).
 
@@
 These protocols could therefore still increase the attention they give to reporting reliability and validity evidence.
-In particular, Figure XXX shows descriptive evidence that replication protocols are lacking in definition and selection evidence.
+In particular, Figure \@ref(fig:Plot456Code) shows descriptive evidence that replication protocols are lacking in definition and selection evidence.
 Furthermore, since replications must base their measures on those of the original articles they are replicating, it is important that articles chosen for replications provide clear evidence on what is being measured, how it is scored, why it was chosen or why it was constructed the way it is, and how it is used in practice.
-It is these last two aspects that original articles appear to particularly be underreporting (See Figure XXX).
+It is these last two aspects that original articles appear to particularly be underreporting (See Figure \@ref(fig:Plot456Code)).
 When original articles do not report their measurement details, replication attempts cannot guarantee a direct replication of the original.

### 2023-11-15 Scripts/Manuscript/manuscript.Rmd
replaced the R package citations in the original bib file with those from the r-references.bib file, including the references in text.

@@
 # manually retrieving the Rstudio version
-
-### DON'T FORGET THAT I SHOULD REMOVE HERE THE R PACKAGE REFERENCES FROM MY REFERENCES BIB AND SHOULD HAVE THE R=REFERENCES BIB TAKE CARE OF THAT INSTEAD.
-```
-
-This is an example of a non-essential citation [\@ @vanlissaWORCS2021]. If you change the rendering function to `worcs::cite_essential`, it will be removed.
+RStudio.Version()
+```
 
@@
 Omega was added to the analysis as it has been argued to be a more informative measure of score reliability, while also providing validity evidence for the scale [@crutzen2017scale; @deng2017testing].
-Cronbach's alpha and omega were calculated using the alpha and omega functions respectively in the psych R package [@revelle2022psych].
+Cronbach's alpha and omega were calculated using the alpha and omega functions respectively in the psych R package [@R-psych].
 Default arguments were used for both functions except the nfactors in the omega function, which was set to 1.
@@
 This total also included reliability coefficients other than Cronbach's alpha.
-This comparison was implemented via a chi-square test using the base R stats package [@R2021R].
+This comparison was implemented via a chi-square test using the base R stats package [@R-base].
 
@@
 
-Using the lmer function from the lme4 package [@bates2015lme4], a multilevel null model with the Cronbach's alpha or omega coefficient of a replication as dependent was specified, where the random intercept was grouped by replication set.
+Using the lmer function from the lme4 package [@R-lme4], a multilevel null model with the Cronbach's alpha or omega coefficient of a replication as dependent was specified, where the random intercept was grouped by replication set.
 The formulas for this model, where $alpha_{ij}$ represents the calculated Cronbach's alpha coefficient of a single study at one lab location with $i = 1,..., n_{locations}$ and $j = 1,...,n_{replications}$ look as follows:
@@
 Furthermore, they are well suited for modelling heteroskedastic and asymmetrically distributed dependent variables [@cribari2010beta].
-The beta regression model was implemented using the betareg function within the betareg package [@cribari2010beta].
+The beta regression model was implemented using the betareg function within the betareg package [@R-betareg_a; @R-betareg_b].
 Defaults were used for all function parameters besides the model formula and data.
@@
 Worth noting is that currently the betareg package does not allow for estimation of multilevel models.
-As an approximation, Gaussian random-intercept multilevel models were implemented using the lmer function from the lme4 package [@bates2015lme4].
+As an approximation, Gaussian random-intercept multilevel models were implemented using the lmer function from the lme4 package [@R-lme4].
 The outcome QMP ratio variable was transformed using the logit link function (the default link function in the betareg package) to better fit the Gaussian model.
@@
 To test this, each multiple item scalar measure had their factor structure investigated on the entire measure data of the replication set.
-A single factor confirmatory factor analysis was implemented using the *fa* function from the *psych* package [@revelle2022psych] in R.
+A single factor confirmatory factor analysis was implemented using the *fa* function from the *psych* package [@R-psych] in R.
 The maximum likelihood factoring method was used, with defaults being used for all other function arguments.

### 2023-11-15 Scripts/Manuscript/manuscript.Rmd
added some missed R references.

@@
 # manually retrieving the Rstudio version
-RStudio.Version()
+rstudioapi::versionInfo()
 ```
@@
 
-The publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio XXXRSTUDIOREFERENCEHEREXXX.
-with R version 4.2.2 XXXRREFERENCEHEREXXX.
-Using the replication protocols, codebooks, and analysis scripts from each replication set as a guide, the variables associated with each measure were extracted into their own data frame containing the data from all studies in one replication set.
+The publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base] Using the replication protocols, codebooks, and analysis scripts from each replication set as a guide, the variables associated with each measure were extracted into their own data frame containing the data from all studies in one replication set.
 These pieces of information formed the replication datasets in the analysis.

### 2023-11-17 Scripts/Manuscript/manuscript.Rmd
included section references.

@@
 # Introduction 
-
 For many years, methodologists and statisticians have raised concerns about the way that research practices [@cumming2014new; @wicherts2016degrees], reporting practices [@bakker2011mis; @nuijten2016prevalence], and publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science] may undermine the credibility of psychology's scientific claims.
@@
 A series of questions relating to measurement practices and measurement error were used to extract the information.
-Descriptions of the extracted variables can be found in the Measures section below.
+Descriptions of the extracted variables can be found in the [Measures](#Measures) section below.
 The scope of the coding was limited to the abstract, method, procedure, materials, measure, and initial parts of the results sections.
@@
 
-<!-- @ref(sec:measures) didn't work for section cross-reference in the paragraph above-->
-
 After the data was initially coded according to the preregistered coding protocol, it was determined, based on discussion with the supervisor, that some of the initial ratings were possibly to stringent.
@@
 
-## Measures
+## Measures {#Measures}
 
@@
 
-### Exploratory Analyses
+### Exploratory Analyses {#ExploratoryAnalyses}
 
@@
 
-The unidimensionality of the measures used in the Many Labs projects was assessed through factor analyses, and evaluated based on the criteria discussed in the Exploratory Analyses section above.
+The unidimensionality of the measures used in the Many Labs projects was assessed through factor analyses, and evaluated based on the criteria discussed in the [Exploratory Analyses](#ExploratoryAnalyses) section above.
 Suitable data for factor analyses was available for nineteen measures.

### 2023-11-22 Scripts/Manuscript/manuscript.Rmd
removed warning messages in manuscript pdf, and improved the placement of floats.

@@
 ```
+
+<!-- altering latex defaults to get better figure and table placement -->
+\renewcommand{\arraystretch}{0.7} <!-- reducing the line spacing within tables -->
+\renewcommand{\topfraction}{.85} <!-- max fraction of page for floats at top -->
+\renewcommand{\bottomfraction}{.7} <!-- max fraction of page for floats at bottom -->
+\renewcommand{\textfraction}{.15} <!-- min fraction of page for text -->
+\renewcommand{\floatpagefraction}{.66} <!-- min fraction of page that should have floats -->
+\setcounter{topnumber}{3} <!-- max number of floats at top of page -->
+\setcounter{bottomnumber}{3} <!-- max number of floats at bottom of page -->
+\setcounter{totalnumber}{4} <!-- max number of floats on a page -->
+<!-- remember to use [htp] or [htpb] for placement -->
 
@@
 
-\renewcommand{\arraystretch}{0.7}
-
-```{r QMPCodingInfoTable}
+```{r QMPCodingInfoTable, warning = FALSE}
 QMP_info_dataframe <-data.frame(Category = c("Definition", "", "", "Operationalisation", "", "", "", "Selection/Creation", "", "", "Quantification", "Modification", "", "", "", "", ""),
@@
   , note = "N Questions refers only to the questions considered quantative as specified in the text below."
-  , escape = FALSE, placement= "ht", booktabs = TRUE)
+  , escape = FALSE, placement= "htp", booktabs = TRUE)
 
@@
 
-```{r Check for Reliability and Validity Testability, include = FALSE}
+```{r Check for Reliability and Validity Testability, include = FALSE, warning = FALSE}
 ## Checking the measures to recalculate the reliability and factor analysis for.
@@
 ```
+
 ```{r Hypothesis 2 Model, include = FALSE}
@@
 
-```{r ReplicationRatioTable}
+```{r ReplicationRatioTable, warning = FALSE}
 # construct the replication ratio table to be printed
@@
 These have been treated as not replicated within this table and further analyses throughout the thesis"
-  , escape = FALSE, placement = "ht", midrules = 4)
+  , escape = FALSE, placement = "htp", midrules = 4)
 
@@
 
-```{r Plot23AlphaCode, fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the eighteen distinct measures for which suitable raw data was available to calculate Cronbach’s alpha coefficients from."}
+```{r Plot23AlphaCode,warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the eighteen distinct measures for which suitable raw data was available to calculate Cronbach’s alpha coefficients from."}
 # plot for alpha
@@
 
-```{r ReplicabilityReliabilityTestTable}
+```{r ReplicabilityReliabilityTestTable, warning = FALSE}
 # creating the dtaframe for the table
@@
 $^* p < .05$"
-  , escape = FALSE, placement= "ht", midrules = c(1, 2, 5, 7, 8, 9, 12, 15))
+  , escape = FALSE, placement= "htp", midrules = c(1, 2, 5, 7, 8, 9, 12, 15))
 
@@
 
-```{r Plot456Code, fig.cap = "QMP ratio counts for each QMP Type and QMP total ratio distribution grouped by where each was coded from.
+```{r Plot456Code, warning = FALSE, fig.cap = "QMP ratio counts for each QMP Type and QMP total ratio distribution grouped by where each was coded from.
 The top row shows binned counts of QMP ratio’s that were observed for each replication protocol and original article, across the different QMP types.
@@
 
-```{r Plot46RevisedDataCode, error = FALSE, fig.cap = "Scatterplot of original and replication QMP ratio’s per type with linear regression line.
+```{r Plot46RevisedDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication QMP ratio’s per type with linear regression line.
 The abbreviations on the axes relate to the QMP categories described in Table 1: Def.
@@
 
-```{r H6ExploratoryAssociationsRevisedTable}
+```{r H6ExploratoryAssociationsRevisedTable, warning = FALSE}
 # creating the dataframe for the table
@@
 $^* p < .05$"
-  , escape = FALSE, placement= "ht", midrules = c(1, 6, 7, 12, 13))
+  , escape = FALSE, placement= "htp", midrules = c(1, 6, 7, 12, 13))
 
@@
 
-```{r H6ExploratoryAssociationsInitialTable}
+```{r H6ExploratoryAssociationsInitialTable, warning = FALSE}
 # creating the dataframe for the table
@@
 
-```{r UnidimesnionalityTestResultsTable}
+```{r UnidimesnionalityTestResultsTable, warning = FALSE}
 # add the names of the relevant papers and a shortcut for the measure used.
@@
 for Measure Data", note = "N Factors refer to the number of factors suggested based on parallel analysis of the measure data.
-The word or abbreviation after the author names and year indicates the specific measure within that original article that was analysed.", escape = FALSE, row.names = FALSE, placement= "ht")
+The word or abbreviation after the author names and year indicates the specific measure within that original article that was analysed.", escape = FALSE, row.names = FALSE, placement= "htp")
 

### 2023-11-30 Data/DataPackageProtocol.Rmd
changed project structure based on personal template change.

# Provide here a full description of each dataset in the project not captured by
#  the automated dataset-specific codebooks.

# InputData --------------------------------------------------------------------

# IntermediateData -------------------------------------------------------------

# OutputData -------------------------------------------------------------------

### 2023-12-19 Data/DataPackageProtocol.Rmd
updated the readme file, and changed the .gitignore file to allow data to be open.

@@
-# Provide here a full description of each dataset in the project not captured by
-#  the automated dataset-specific codebooks.
+<!-- Provide here a full description of each dataset in the project not captured by the automated dataset-specific codebooks. -->
 
-# InputData --------------------------------------------------------------------
+# InputData
 
-# IntermediateData -------------------------------------------------------------
+### Coded_Data_Initial_raw.csv
 
-# OutputData -------------------------------------------------------------------
+*Origin*: This dataset was created originally for this research project.
+It was obtained using the ???.pdf that can be found in the SupplementaryMaterials folder of this project on the Many Labs protocols mentioned in the texts and the related original articles for each of the many labs replications.
+
+*Explanation*: The information in this dataset was used for analyses relating to QMP ratios among original articles and replication studies.
+It additionally contains peripheral information about the articles and study in it that were used throughout the analyses and for descriptives.
+
+*Variables*:
+
+### Coded_Data_Revised_raw.csv
+
+*Origin*: This dataset was created originally for this research project.
+It was obtained using the ???.pdf that can be found in the SupplementaryMaterials folder of this project on the Many Labs protocols mentioned in the texts and the related original articles for each of the many labs replications (the same sample as was used to obtain the Coded_Data_Initial_raw.csv).
+
+*Explanation*: After discussion with the supervisor based on the experiences of the initial coding round it was determined that several of the demarcation for meeting several QMP criteria were likely too strict, and thus several of the more strictly coded questions were revised and coded again using a new coding protocol.
+The goal being to offer an as lenient as possible overview of the errors in reporting in the investigated literature.
+
+*Variables*:
+
+### Coded_Data_Vignette_raw.csv
+
+*Origin*: This dataset was created originally for this research project.
+It was obtained using the ???.pdf that can be found in the SupplementaryMaterials folder of this project on the Many Labs protocols mentioned in the texts and the related original articles for each of the many labs replications (the same sample as was used to obtain the Coded_Data_Initial_raw.csv).
+
+*Explanation*: This dataset was collected after the intial round of coding with the intention to control on certain analyses whether items described a vignette and not an ordinary questionnaire, which might have different standards with regards to measurement reporting and reliability.
+As of yet, it has remained unused in any analyses
+
+*Variables*:
+
+-   **RecordedDate**: Records the date the variable was coded, was not used further.
+
+-   **Vignette**: Boolean variable indicating whether or not a particular measure was inseparably tied to a vignette describing some form of quoted text, visual, imagined scenario, cognitive task, or game.
+
+### Data_ML1.csv
+
+*Origin*: This dataset was obtained from the Datasets.zip archive as "Full_Dataset_De-Identified.sav", from the following OSF page: <https://osf.io/pqf9r/>.
+
+*Attribution*: The datatset is related to the following article: Klein, R.
+A., Ratliff, K., Vianello, M., Adams Jr, R.
+B., Bahník, S., Bernstein, M.
+J., .
+.
+.
+Nosek, B.
+A.
+(2014).
+Investigating variation in replicability: A "many labs" replication project.
+Social Psychology, 45 (3), 142--152.
+<https://doi.org/10.1027/1864-9335/a000178>, the dataset itself has the following doi: 10.17605/OSF.IO/PQF9R.
+
+*Alterations*: the only alterations made to the dataset at this stage were: the name of the dataset was changed, and the format was changed from .sav to .csv.
+
+### Data_2.2.csv
+
+*Origin*: This dataset was obtained from the OSFdata.zip archive in file path "Structure & Goal Pursuit (Kay et al., 2014)/Kay.1/Global/Data/" as "Kay_1_study_global_include_all_CLEAN_CASE.csv", from the following OSF page: <https://osf.io/ag2pd>.
+
+*Attribution*: The datatset is related to the following article: Klein, R.
+A., Vianello, M., Hasselman, F., Adams, B.
+G., Adams Jr, R.
+B., Alper, S., .
+.
+.
+Bahnìk, Š.
+(2018).
+Many labs 2: Investigating variation in replicability across samples and settings.
+Advances in Methods and Practices in Psychological Science, 1 (4), 443--490.
+<https://doi.org/10.1177/2515245918810225>, the dataset itself has the following doi: 10.17605/OSF.IO/FANRE.
+
+*Alterations*: the only alteration made to the dataset at this stage was: the name of the dataset was changed.
+
+### Data_2.3.csv
+
+*Origin*: This dataset was obtained from the OSFdata.zip archive in file path "Incidental Disfluency (Alter et al., 2007)/Alter.1/Global/Data/" as "Alter_1_study_global_include_all_CLEAN_CASE.csv", from the following OSF page: <https://osf.io/ag2pd>.
+
+*Attribution*: The datatset is related to the following article: Klein, R.
+A., Vianello, M., Hasselman, F., Adams, B.
+G., Adams Jr, R.
+B., Alper, S., .
+.
+.
+Bahnìk, Š.
+(2018).
+Many labs 2: Investigating variation in replicability across samples and settings.
+Advances in Methods and Practices in Psychological Science, 1 (4), 443--490.
+<https://doi.org/10.1177/2515245918810225>, the dataset itself has the following doi: 10.17605/OSF.IO/FANRE.
+
+*Alterations*: the only alteration made to the dataset at this stage was: the name of the dataset was changed.
+
+### Data_2.4.1.csv
+
+*Origin*: This dataset was obtained from the OSFdata.zip archive in file path "Moral Foundations (Graham et al., 2009)/Graham.1/Global/Data/" as "Graham_1_study_global_include_all_CLEAN_CASE.csv", from the following OSF page: <https://osf.io/ag2pd>.
+
+*Attribution*: The datatset is related to the following article: Klein, R.
+A., Vianello, M., Hasselman, F., Adams, B.
+G., Adams Jr, R.
+B., Alper, S., .
+.
+.
+Bahnìk, Š.
+(2018).
+Many labs 2: Investigating variation in replicability across samples and settings.
+Advances in Methods and Practices in Psychological Science, 1 (4), 443--490.
+<https://doi.org/10.1177/2515245918810225>, the dataset itself has the following doi: 10.17605/OSF.IO/FANRE.
+
+*Alterations*: the only alteration made to the dataset at this stage was: the name of the dataset was changed.
+
+### Data_2.4.2.csv
+
+*Origin*: This dataset was obtained from the OSFdata.zip archive in file path "Moral Foundations (Graham et al., 2009)/Graham.2/Global/Data/" as "Graham_2_study_global_include_all_CLEAN_CASE.csv", from the following OSF page: <https://osf.io/ag2pd>.
+
+*Attribution*: The datatset is related to the following article: Klein, R.
+A., Vianello, M., Hasselman, F., Adams, B.
+G., Adams Jr, R.
+B., Alper, S., .
+.
+.
+Bahnìk, Š.
+(2018).
+Many labs 2: Investigating variation in replicability across samples and settings.
+Advances in Methods and Practices in Psychological Science, 1 (4), 443--490.
+<https://doi.org/10.1177/2515245918810225>, the dataset itself has the following doi: 10.17605/OSF.IO/FANRE.
+
+*Alterations*: the only alteration made to the dataset at this stage was: the name of the dataset was changed.
+
+### Data_2.8.2.csv
+
+*Origin*: This dataset was obtained from the OSFdata.zip archive in file path "Disgust & Homophobia (Inbar et al., 2009)/Inbar.1b/Global/Data/" as "Inbar_1b_study_global_include_all_CLEAN_CASE.csv", from the following OSF page: <https://osf.io/ag2pd>.
+
+*Attribution*: The datatset is related to the following article: Klein, R.
+A., Vianello, M., Hasselman, F., Adams, B.
+G., Adams Jr, R.
+B., Alper, S., .
+.
+.
+Bahnìk, Š.
+(2018).
+Many labs 2: Investigating variation in replicability across samples and settings.
+Advances in Methods and Practices in Psychological Science, 1 (4), 443--490.
+<https://doi.org/10.1177/2515245918810225>, the dataset itself has the following doi: 10.17605/OSF.IO/FANRE.
+
+*Alterations*: the only alteration made to the dataset at this stage was: the name of the dataset was changed.
+
+### Data_2.10.1.csv
+
+*Origin*: This dataset was obtained from the OSFdata.zip archive in file path "Social Value Orientation (Van Lange et al., 1997)/vanLange.1/Global/Data/" as "vanLange_1_study_global_include_all_CLEAN_CASE.csv", from the following OSF page: <https://osf.io/ag2pd>.
+
+*Attribution*: The datatset is related to the following article: Klein, R.
+A., Vianello, M., Hasselman, F., Adams, B.
+G., Adams Jr, R.
+B., Alper, S., .
+.
+.
+Bahnìk, Š.
+(2018).
+Many labs 2: Investigating variation in replicability across samples and settings.
+Advances in Methods and Practices in Psychological Science, 1 (4), 443--490.
+<https://doi.org/10.1177/2515245918810225>, the dataset itself has the following doi: 10.17605/OSF.IO/FANRE.
+
+*Alterations*: the only alteration made to the dataset at this stage was: the name of the dataset was changed.
+
+### Data_2.12.csv
+
+*Origin*: This dataset was obtained from the OSFdata.zip archive in file path "SMS & Well-Being (Anderson et al., 2012)/Anderson.1/Global/Data/" as "Anderson_1_study_global_include_all_CLEAN_CASE.csv", from the following OSF page: <https://osf.io/ag2pd>.
+
+*Attribution*: The datatset is related to the following article: Klein, R.
+A., Vianello, M., Hasselman, F., Adams, B.
+G., Adams Jr, R.
+B., Alper, S., .
+.
+.
+Bahnìk, Š.
+(2018).
+Many labs 2: Investigating variation in replicability across samples and settings.
+Advances in Methods and Practices in Psychological Science, 1 (4), 443--490.
+<https://doi.org/10.1177/2515245918810225>, the dataset itself has the following doi: 10.17605/OSF.IO/FANRE.
+
+*Alterations*: the only alteration made to the dataset at this stage was: the name of the dataset was changed.
+
+### Data_2.15.csv
+
+*Origin*: This dataset was obtained from the OSFdata.zip archive in file path "Position & Power (Giessner & Schubert, 2007)/Giessner.1/Global/Data/" as "Giessner_1_study_global_include_all_CLEAN_CASE.csv", from the following OSF page: <https://osf.io/ag2pd>.
+
+*Attribution*: The datatset is related to the following article: Klein, R.
+A., Vianello, M., Hasselman, F., Adams, B.
+G., Adams Jr, R.
+B., Alper, S., .
+.
+.
+Bahnìk, Š.
+(2018).
+Many labs 2: Investigating variation in replicability across samples and settings.
+Advances in Methods and Practices in Psychological Science, 1 (4), 443--490.
+<https://doi.org/10.1177/2515245918810225>, the dataset itself has the following doi: 10.17605/OSF.IO/FANRE.
+
+*Alterations*: the only alteration made to the dataset at this stage was: the name of the dataset was changed.
+
+### Data_2.19.1.csv
+
+*Origin*: This dataset was obtained from the OSFdata.zip archive in file path "Actions are Choices (Savani et al., 2010)/Savani.3a/Global/Data/" as "Savani_3a_study_global_include_all_CLEAN_CASE.csv", from the following OSF page: <https://osf.io/ag2pd>.
+
+*Attribution*: The datatset is related to the following article: Klein, R.
+A., Vianello, M., Hasselman, F., Adams, B.
+G., Adams Jr, R.
+B., Alper, S., .
+.
+.
+Bahnìk, Š.
+(2018).
+Many labs 2: Investigating variation in replicability across samples and settings.
+Advances in Methods and Practices in Psychological Science, 1 (4), 443--490.
+<https://doi.org/10.1177/2515245918810225>, the dataset itself has the following doi: 10.17605/OSF.IO/FANRE.
+
+*Alterations*: the only alteration made to the dataset at this stage was: the name of the dataset was changed.
+
+### Data_2.20.csv
+
+*Origin*: This dataset was obtained from the OSFdata.zip archive in file path "Intuitive Reasoning (Norenzayan et al., 2002)/Norenzayan.1/Global/Data" as "Norenzayan_1_study_global_include_all_CLEAN_CASE.csv", from the following OSF page: <https://osf.io/ag2pd>.
+
+*Attribution*: The datatset is related to the following article: Klein, R.
+A., Vianello, M., Hasselman, F., Adams, B.
+G., Adams Jr, R.
+B., Alper, S., .
+.
+.
+Bahnìk, Š.
+(2018).
+Many labs 2: Investigating variation in replicability across samples and settings.
+Advances in Methods and Practices in Psychological Science, 1 (4), 443--490.
+<https://doi.org/10.1177/2515245918810225>, the dataset itself has the following doi: 10.17605/OSF.IO/FANRE.
+
+*Alterations*: the only alteration made to the dataset at this stage was: the name of the dataset was changed.
+
+### Data_2.23.csv
+
+*Origin*: This dataset was obtained from the OSFdata.zip archive in file path "/Moral Cleansing (Zhong & Liljenquist, 2006)/Zhong.1/Global/Data/" as "Zhong_1_study_global_include_all_CLEAN_CASE.csv", from the following OSF page: <https://osf.io/ag2pd>.
+
+*Attribution*: The datatset is related to the following article: Klein, R.
+A., Vianello, M., Hasselman, F., Adams, B.
+G., Adams Jr, R.
+B., Alper, S., .
+.
+.
+Bahnìk, Š.
+(2018).
+Many labs 2: Investigating variation in replicability across samples and settings.
+Advances in Methods and Practices in Psychological Science, 1 (4), 443--490.
+<https://doi.org/10.1177/2515245918810225>, the dataset itself has the following doi: 10.17605/OSF.IO/FANRE.
+
+*Alterations*: the only alteration made to the dataset at this stage was: the name of the dataset was changed.
+
+### Data_ML3.csv
+
+*Origin*: This dataset was obtained from the ML3 Final Data.zip archive in the base folder as "ML3AllSitesandmTurk.csv", from the following OSF page: <https://osf.io/bxw8j>.
+
+*Attribution*: The datatset is related to the following article: Ebersole, C.
+R., Atherton, O.
+E., Belanger, A.
+L., Skulborstad, H.
+M., Allen, J.
+M., Banks, J.
+B., .
+.
+.
+Nosek, B.
+A.
+(2016).
+Many labs 3: Evaluating participant pool quality across the academic semester via replication.
+Journal of Experimental Social Psychology, 67, 68--82.
+<https://doi.org/10.1016/j.jesp.2015.10.012>.
+
+*Alterations*: the only alteration made to the dataset at this stage was: the name of the dataset was changed.
+
+### Data_3.5.csv
+
+*Origin*: This dataset was obtained from the ML3 Final Data.zip archive in the base folder as "ML3StroopData.csv", from the following OSF page: <https://osf.io/bxw8j>.
+
+*Attribution*: The datatset is related to the following article: Ebersole, C.
+R., Atherton, O.
+E., Belanger, A.
+L., Skulborstad, H.
+M., Allen, J.
+M., Banks, J.
+B., .
+.
+.
+Nosek, B.
+A.
+(2016).
+Many labs 3: Evaluating participant pool quality across the academic semester via replication.
+Journal of Experimental Social Psychology, 67, 68--82.
+<https://doi.org/10.1016/j.jesp.2015.10.012>.
+
+*Alterations*: the only alteration made to the dataset at this stage was: the name of the dataset was changed.
+
+### Data_5.1.csv
+
+*Origin*: This dataset was obtained as "ML5 Alb 5 Revised Protocol In Lab.xlsx", from the following OSF page: <https://osf.io/64njs>.
+
+*Attribution*: The datatset is related to the following article: Ebersole, C.
+R., Mathur, M.
+B., Baranski, E., Bart-Plange, D.-J., Buttrick, N.
+R., Chartier, C.
+R., .
+.
+.
+Nosek, B.
+A.
+(2020).
+Many labs 5: Testing pre-data-collection peer review as an intervention to increase replicability.
+Advances in Methods and Practices in Psychological Science, 3 (3), 309--331.
+<https://doi.org/10.1177/2515245920958687>.
+
+*Alterations*: the only alterations made to the dataset at this stage were: the name of the dataset was changed, and the format was changed from .xlsx to .csv.
+
+### Data_5.4.csv
+
+*Origin*: This dataset was obtained as "dataset_LoBue_raw.sav", from the following OSF page: <https://osf.io/w7ft9>.
+
+*Attribution*: The datatset is related to the following article: Ebersole, C.
+R., Mathur, M.
+B., Baranski, E., Bart-Plange, D.-J., Buttrick, N.
+R., Chartier, C.
+R., .
+.
+.
+Nosek, B.
+A.
+(2020).
+Many labs 5: Testing pre-data-collection peer review as an intervention to increase replicability.
+Advances in Methods and Practices in Psychological Science, 3 (3), 309--331.
+<https://doi.org/10.1177/2515245920958687>.
+
+*Alterations*: the only alterations made to the dataset at this stage were: the name of the dataset was changed, and the format was changed from .sav to .csv.
+
+### Data_5.5.csv
+
+*Origin*: This dataset was obtained as "Genova_ML5.csv", from the following OSF page: <https://osf.io/prj7y>.
+
+*Attribution*: The datatset is related to the following article: Ebersole, C.
+R., Mathur, M.
+B., Baranski, E., Bart-Plange, D.-J., Buttrick, N.
+R., Chartier, C.
+R., .
+.
+.
+Nosek, B.
+A.
+(2020).
+Many labs 5: Testing pre-data-collection peer review as an intervention to increase replicability.
+Advances in Methods and Practices in Psychological Science, 3 (3), 309--331.
+<https://doi.org/10.1177/2515245920958687>.
+
+*Alterations*: the only alteration made to the dataset at this stage was: the name of the dataset was changed.
+
+### Data_5.7.csv
+
+*Origin*: This dataset was obtained as "ml5_computed_dataset.csv", from the following OSF page: <https://osf.io/da8bh>.
+
+*Attribution*: The datatset is related to the following article: Ebersole, C.
+R., Mathur, M.
+B., Baranski, E., Bart-Plange, D.-J., Buttrick, N.
+R., Chartier, C.
+R., .
+.
+.
+Nosek, B.
+A.
+(2020).
+Many labs 5: Testing pre-data-collection peer review as an intervention to increase replicability.
+Advances in Methods and Practices in Psychological Science, 3 (3), 309--331.
+<https://doi.org/10.1177/2515245920958687>.
+
+*Alterations*: the only alteration made to the dataset at this stage was: the name of the dataset was changed.
+
+### Data_5.9.csv
+
+*Origin*: This dataset was obtained as "ML5_fulldataset_with_suspicion.csv", from the following OSF page: <https://osf.io/5w6e7>.
+
+*Attribution*: The datatset is related to the following article: Ebersole, C.
+R., Mathur, M.
+B., Baranski, E., Bart-Plange, D.-J., Buttrick, N.
+R., Chartier, C.
+R., .
+.
+.
+Nosek, B.
+A.
+(2020).
+Many labs 5: Testing pre-data-collection peer review as an intervention to increase replicability.
+Advances in Methods and Practices in Psychological Science, 3 (3), 309--331.
+<https://doi.org/10.1177/2515245920958687>.
+
+*Alterations*: the only alteration made to the dataset at this stage was: the name of the dataset was changed.
+
+<!-- Should look into the datasets that were considered not usable and see what I might find for them now. Particularly Data_2.4.1, Data_2.4.2, Data_5.5, and Data_2.19.2 -->
+
+# IntermediateData
+
+### coded_data_original.csv
+
+*Explanation*: contains all coded data on the original articles with renamed columns, fixed bad data, restructured to match the ordering of the protocols more ineligibly, recoded to be close to suitable for analysis, and with several composite variables added that were calculated from the raw data.
+
+<!-- add information here on all of the coded variables, and then paste it to the datasets below too. -->
+
+### coded_data_original_shortened.csv
+
+*Explanation*: similar to the coded_data_original.csv only with the coded data on 3 measures that did not appear in the replication protocols being removed to allow for easier comparisons between replications and original studies.
+
+### coded_data_replications.csv
+
+*Explanation*: contains all coded data on the replications as described in the many labs protocols with renamed columns, fixed bad data, restructured to match the ordering of the protocols more ineligibly, recoded to be close to suitable for analysis, and with several composite variables added that were calculated from the raw data.
+
+### Data_1.3_clean.csv
+
+*Explanation*: The first column of this dataset indicates the lab location where the data was collected as a factor.
+Besides that, this dataset contains all of the columns that could be identified as item scores on the scale relating to anchoring used in study 3 (as stated in the Many Labs 1 Proposal_V1.1) from Many Labs 1 that was checked for reliability and unidimensionality.
+
+### Data_1.10_clean.csv
+
+*Explanation*: The first column of this dataset indicates the lab location where the data was collected as a factor.
+Besides that, this dataset contains all of the columns that could be identified as item scores on the scale relating to system justification used in study 10 (as stated in the Many Labs 1 Proposal_V1.1) from Many Labs 1 that was checked for reliability and unidimensionality.
+
+### Data_1.11_clean.csv
+
+*Explanation*: The first column of this dataset indicates the lab location where the data was collected as a factor.
+Besides that, this dataset contains all of the columns that could be identified as item scores on the scale relating to intentions to engage used in study 11 (as stated in the Many Labs 1 Proposal_V1.1) from Many Labs 1 that was checked for reliability and unidimensionality.
+
+### Data_1.12.3.1_clean.csv
+
+*Explanation*: The first column of this dataset indicates the lab location where the data was collected as a factor.
+Besides that, this dataset contains all of the columns that could be identified as item scores on the scale relating to explicit attitudes towards art used in study 12 (as stated in the Many Labs 1 Proposal_V1.1) from Many Labs 1 that was checked for reliability and unidimensionality.
+
+### Data_1.12.3.2_clean.csv
+
+*Explanation*: The first column of this dataset indicates the lab location where the data was collected as a factor.
+Besides that, this dataset contains all of the columns that could be identified as item scores on the scale relating to explicit attitudes towards math used in study 12 (as stated in the Many Labs 1 Proposal_V1.1) from Many Labs 1 that was checked for reliability and unidimensionality.
+
+### Data_2.10.1_clean.csv
+
+*Explanation*: The first column of this dataset indicates the lab location where the data was collected as a factor.
+Besides that, this dataset contains all of the columns that could be identified as item scores on the scale relating to social value orientation used in study 10 (as stated in the Many Labs 2 protocol) from Many Labs 2 that was checked for reliability and unidimensionality.
+
+### Data_2.12.1_clean.csv
+
+*Explanation*: The first column of this dataset indicates the lab location where the data was collected as a factor.
+Besides that, this dataset contains all of the columns that could be identified as item scores on the scale relating to satisfaction with life used in study 12 (as stated in the Many Labs 2 protocol) from Many Labs 2 that was checked for reliability and unidimensionality.
+
+### Data_2.12.2_clean.csv
+
+*Explanation*: The first column of this dataset indicates the lab location where the data was collected as a factor.
+Besides that, this dataset contains all of the columns that could be identified as item scores on the scale relating to positive affect used in study 12 (as stated in the Many Labs 2 protocol) from Many Labs 2 that was checked for reliability and unidimensionality.
+
+### Data_2.12.3_clean.csv
+
+*Explanation*: The first column of this dataset indicates the lab location where the data was collected as a factor.
+Besides that, this dataset contains all of the columns that could be identified as item scores on the scale relating to negative affect used in study 12 (as stated in the Many Labs 2 protocol) from Many Labs 2 that was checked for reliability and unidimensionality.
+
+### Data_2.15_clean.csv
+
+*Explanation*: The first column of this dataset indicates the lab location where the data was collected as a factor.
+Besides that, this dataset contains all of the columns that could be identified as item scores on the scale relating to rated power used in study 15 (as stated in the Many Labs 2 protocol) from Many Labs 2 that was checked for reliability and unidimensionality.
+
+### Data_2.20_clean.csv
+
+*Explanation*: The first column of this dataset indicates the lab location where the data was collected as a factor.
+Besides that, this dataset contains all of the columns that could be identified as item scores on the scale relating to rule or similarity based judgement used in study 20 (as stated in the Many Labs 2 protocol) from Many Labs 2 that was checked for reliability and unidimensionality.
+
+### Data_2.23_clean.csv
+
+*Explanation*: The first column of this dataset indicates the lab location where the data was collected as a factor.
+Besides that, this dataset contains all of the columns that could be identified as item scores on the scale relating to cleaning product ratings used in study 23 (as stated in the Many Labs 2 protocol) from Many Labs 2 that was checked for reliability and unidimensionality.
+
+### Data_3.2.1.1_clean.csv
+
+*Explanation*: The first column of this dataset indicates the lab location where the data was collected as a factor.
+Besides that, this dataset contains all of the columns that could be identified as item scores on the scale relating to list of most expressions used in study 2 (as stated in the Many Labs 3 protocol) from Many Labs 3 that was checked for reliability and unidimensionality.
+
+### Data_3.2.1.2_clean.csv
+
+*Explanation*: The first column of this dataset indicates the lab location where the data was collected as a factor.
+Besides that, this dataset contains all of the columns that could be identified as item scores on the scale relating to list of some expressions used in study 2 (as stated in the Many Labs 3 protocol) from Many Labs 3 that was checked for reliability and unidimensionality.
+
+### Data_3.7.1_clean.csv
+
+*Explanation*: The first column of this dataset indicates the lab location where the data was collected as a factor.
+Besides that, this dataset contains all of the columns that could be identified as item scores on the scale relating to argument quality used in study 7 (as stated in the Many Labs 3 protocol) from Many Labs 3 that was checked for reliability and unidimensionality.
+
+### Data_3.7.2_clean.csv
+
+*Explanation*: The first column of this dataset indicates the lab location where the data was collected as a factor.
+Besides that, this dataset contains all of the columns that could be identified as item scores on the scale relating to need for cognition used in study 7 (as stated in the Many Labs 3 protocol) from Many Labs 3 that was checked for reliability and unidimensionality.
+
+### Data_3.8.2_clean.csv
+
+*Explanation*: The first column of this dataset indicates the lab location where the data was collected as a factor.
+Besides that, this dataset contains all of the columns that could be identified as item scores on the scale relating to conscientousness used in study 8 (as stated in the Many Labs 3 protocol) from Many Labs 3 that was checked for reliability and unidimensionality.
+
+### Data_5.1.1_clean.csv
+
+*Explanation*: The first column of this dataset indicates the lab location where the data was collected as a factor.
+Besides that, this dataset contains all of the columns that could be identified as item scores on the scale relating to verbal ability used in study 1 (as ordered in Table 1.
+in the Many Labs 5 manuscript) from Many Labs 5 that was checked for reliability and unidimensionality.
+
+### Data_5.1.2_clean.csv
+
+*Explanation*: The first column of this dataset indicates the lab location where the data was collected as a factor.
+Besides that, this dataset contains all of the columns that could be identified as item scores on the scale relating to quantitative ability used in study 1 (as ordered in Table 1.
+in the Many Labs 5 manuscript) from Many Labs 5 that was checked for reliability and unidimensionality.
+
+### Data_5.4_clean.csv
+
+*Explanation*: The first column of this dataset indicates the lab location where the data was collected as a factor.
+Besides that, this dataset contains all of the columns that could be identified as item scores on the scale relating to antogonist trait description used in study 4 (as ordered in Table 1.
+in the Many Labs 5 manuscript) from Many Labs 5 that was checked for reliability and unidimensionality.
+
+### Data_5.7_clean.csv
+
+*Explanation*: The first column of this dataset indicates the lab location where the data was collected as a factor.
+Besides that, this dataset contains all of the columns that could be identified as item scores on the scale relating to willingness to reconcile used in study 7 (as ordered in Table 1.
+in the Many Labs 5 manuscript) from Many Labs 5 that was checked for reliability and unidimensionality.
+
+### Data_5.9.1_clean.csv
+
+*Explanation*: The first column of this dataset indicates the lab location where the data was collected as a factor.
+Besides that, this dataset contains all of the columns that could be identified as item scores on the scale relating to free will used in study 9 (as ordered in Table 1.
+in the Many Labs 5 manuscript) from Many Labs 5 that was checked for reliability and unidimensionality.
+
+# OutputData
+
+### data_H1.csv
+
+*Explanation*: Contain all of the data from the coded_data_original_shortened.csv and coded_data_replications.csv except for an empty column that was meant to contain any types of reported psychometric evidence not included in the multiple choice response options, since it caused codebook generation issues.
+The two datasets of which this dataset was composed were bound so that each row contained both the coded data of the original article and the coded data on the same measure as described in the replication protocols.
+An additional variable was added which indicated for the multiple item measures only whether or not any form of reliability evidence was reported or not as a boolean variable.
+
+### data_H2.csv
+
+*Explanation*: This dataset list contains the calculated Cronbach's alpha and the omega reliability coefficient calculated for the responses to the questionnaire items from several of the Many Labs studies, namely those responses encoded in: Data_1.10_clean.csv, data_1.11_clean.csv, data_1.12.3.1_clean.csv, data_1.12.3.2_clean.csv, data_2.10.1_clean.csv, data_2.12.1_clean.csv, data_2.12.2_clean.csv, data_2.12.3_clean.csv, data_2.15_clean.csv, data_2.20_clean.csv, data_2.23_clean.csv, data_3.2.1.1_clean.csv, data_3.2.1.2_clean.csv, data_3.7.2_clean.csv, data_3.8.2_clean.csv, data_5.1.1_clean.csv, data_5.7_clean.csv, data_5.9.1_clean.csv.
+The Cronbach's alpha and omega are calculated separately for each lab location within each study/questionnaire in the Many Labs datasets.
+
+### data_H3_avg.csv
+
+*Explanation*: For each many labs replication, the mean Cronbach's alpha and omega reliability coefficients of each lab location are captured in the datasets.
+Additionally, a boolean indicator that indicated whether or not the original effect was replicated in the many labs replications when looking at the significance of the meta-analytic p-value was also included.
+
+### data_H3_multiple.csv
+
+*Explanation*: Combination of data_H2.csv and a boolean indicator that indicated whether or not the original effect was replicated in the many labs replications when looking at the significance of the meta-analytic p-value.
+
+### data_H4.csv
+
+*Explanation*: Contain all of the data from the coded_data_original_shortened.csv and coded_data_replications.csv except for an empty column that was meant to contain any types of reported psychometric evidence not included in the multiple choice response options, since it caused codebook generation issues.
+The two datasets of which this dataset was composed were bound so that each row contained both the coded data of the original article and the coded data on the same measure as described in the replication protocols.
+Additionally, it contains two variables of the total QMP ratio based on both the initial and revised coded QMPs for each measure with some correction applied to the 0 and 1 total QMP scores as they caused issues for the beta regression model.
+
+### data_H5.csv
+
+*Explanation*: Contain all of the data from the coded_data_replications.csv except for two empty columns that were meant to contain any types of reported psychometric evidence and reliability measures respectively not included in the multiple choice response options, since it caused codebook generation issues.
+3 rows were omitted from this analysis due to the fact that the support for the hypothesis was coded as being unclear.
+The support for hypothesis, variable, based on the significance of the meta-analytic p-value, was afterwards recoded from a factor to a boolean variable with True for support and False for no support.
+The many labs version variable was recoded from numeric into a factor.
+Additionally, it contains two variables of the total QMP ratio based on both the initial and revised coded QMPs for each measure with some correction applied to the 0 and 1 total QMP scores as they caused issues for the beta regression model.
+It furthermore contains
+
+### data_H6.csv
+
+*Explanation*: Contain all of the data from the coded_data_original_shortened.csv and coded_data_replications.csv.
+The two datasets of which this dataset was composed were bound so that each row contained both the coded data of the original article and the coded data on the same measure as described in the replication protocols.
+Additionally, the QMP ratio for each of the initial and revised QMP categories for both the original and revised codes had some correction applied to the 0 and 1 total QMP scores as they caused issues for the beta regression model.
+
+### plot_23_data_alpha.csv
+
+*Explanation*: Contain all of the data from the data_h3_multiple.csv that had a calculated alpha level larger than 0.
+Additionally, it contains a column of alpha scores averaged across many lab locations for each article.
+For each remaining replication, the names of the articles were adjusted to look better in the figure this dataset was used for.
+
+### plot_23_data_omega.csv
+
+*Explanation*: Contain all of the data from the data_h3_multiple.csv.
+Additionally, it contains a column of omega scores averaged across many lab locations for each article.
+The names of the articles were adjusted to look better in the figure this dataset was used for.
+
+### plot_456_data.csv
+
+*Explanation*: Contains three variables for each QMP type for all the replication studies and original articles.
+The QMP_ratio column indicates the QMP ratio for that QMP type for that study/article.
+The RepOrg column indicates whether the QMP ratio belongs to a replication or an original article.
+The QMP_type column indicates the QMP type the QMP ratio belongs to.
+The rows are ordered to have the original studies first and then the replications, then they are ordered based on QMP type from Definition to Operationalization to Selection to Quantification to Modification to Total.
+Finally, within each type the QMPs are ordering matches the order of the studies/articles as in the coded_data_replications.csv and coded_data_original_shortened.csv.
+
+### plot_46_data.csv
+
+*Explanation*: Contains four variables for each QMP type for both replication studies and original articles combined per row.
+The QMP_ratio column indicates the initial QMP ratio for the specific QMP type for that original article.
+The QMP_type column indicates the specific QMP type the QMP_ratio column belongs to.
+The QMP_Rep_ratio column indicates the initial QMP ratio for the specific QMP type for that replication study.
+The QMP_Rep_type column indicates the specific QMP type the QMP_Rep_ratio column belongs to.
+The rows are ordered so that within each QMP type it matches the order of the studies/articles as in the coded_data_replications.csv and coded_data_original_shortened.csv.
+
+### plot_46_data_REV.csv
+
+*Explanation*: Contains four variables for each QMP type for both replication studies and original articles combined per row.
+The QMP_ratio column indicates the revised QMP ratio for the specific QMP type for that original article.
+The QMP_type column indicates the specific QMP type the QMP_ratio column belongs to.
+The QMP_Rep_ratio column indicates the revised QMP ratio for the specific QMP type for that replication study.
+The QMP_Rep_type column indicates the specific QMP type the QMP_Rep_ratio column belongs to.
+The rows are ordered so that within each QMP type it matches the order of the studies/articles as in the coded_data_replications.csv and coded_data_original_shortened.csv.

### 2023-12-19 Scripts/Manuscript/manuscript.Rmd
updated the readme file, and changed the .gitignore file to allow data to be open.

@@
 As a response, the demand to verify the credibility of psychological findings through replications rose.
-In order to attempt replications of various psychological findings, numerous large scale projects were set-up [@klein2014data; @camerer2016evaluating; @camerer2018evaluating; @ebersole2016many; @ebersole2020many; @klein2018many; @klein2022many].
+In order to attempt replications of various psychological findings, numerous large scale projects were set-up [@klein2014investigating; @camerer2016evaluating; @camerer2018evaluating; @ebersole2016many; @ebersole2020many; @klein2018many; @klein2022many].
 Among these were the Many Labs projects, which operated similarly to the RPP, with the additional feature that each original article was replicated multiple times across different labs in various locations around the world.
@@
 The data came from the Many Labs series of studies.
-In particular, data from Many Labs 1, 2, 3, & 5 was used [@klein2014data; @klein2018many; @ebersole2016many; @ebersole2020many].
+In particular, data from Many Labs 1, 2, 3, & 5 was used [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many].
 Data from Many Labs 4 [@klein2022many] was not part of the sample, as there was no publicly available protocol which contains the information needed to code QMPs.
@@
 
-Finally, the reports of the Many Labs projects, meaning the published articles [@klein2014data; @klein2018many; @ebersole2016many; @ebersole2020many], were used to determine whether not the replication was considered successful.
+Finally, the reports of the Many Labs projects, meaning the published articles [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many], were used to determine whether not the replication was considered successful.
 
@@
 An issue was encountered while trying to access @hyman1950current.
-However, after contacting the first author of @klein2014data a suitable version of the article was obtained for use in the analyses.
+However, after contacting the first author of @klein2014investigating a suitable version of the article was obtained for use in the analyses.
 

### 2023-12-19 Scripts/prepare_data.R

@@ -17,6 +17,8 @@ set.seed(17042023) # seed for random number generators
 ## List of measures X.Y.Z to extract, where X is Many Labs number, Y is study
 ## in the order as reported in the Many Labs protocol, & Z is the specific 
 ## measure from study Y as in line with the order of the measurement coding.
+## Each is indicated to reflect what the usefulness of the data should be based 
+## their reporting in the original article and initial screening.
 # Likely reliability: 1.10, 1.11, 1.12.3, 2.4.1, 2.4.2, 2.8, 2.10.1, 2.12.1, 
 # 2.12.2, 2.12.3, 2.15, 2.19.2, 2.23, 3.7.1, 3.7.2, 3.8.1, 3.8.2, 5.7, 5.9.1
 # Likely factor: 1.10, 1.11, 1.12.3, 2.4.1, 2.4.2, 2.8, 2.10.1, 2.12.1, 2.12.2,
@@ -37,9 +39,9 @@ Data_2.2 <- read.csv("Data/LocalInputData/MLRetrievedData/Kay_1_study_global_inc
 # 2.3
 Data_2.3 <- read.csv("Data/LocalInputData/MLRetrievedData/Alter_1_study_global_include_all_CLEAN_CASE.csv")
 # 2.4.1
-Data_2.4.1 <- read.csv("Data/LocalInputData/MLRetrievedData/Graham_2_study_global_include_all_CLEAN_CASE.csv")
+Data_2.4.1 <- read.csv("Data/LocalInputData/MLRetrievedData/Graham_1_study_global_include_all_CLEAN_CASE.csv")
 # 2.4.2
-Data_2.4.2 <- read.csv("Data/LocalInputData/MLRetrievedData/Graham_1_study_global_include_all_CLEAN_CASE.csv")
+Data_2.4.2 <- read.csv("Data/LocalInputData/MLRetrievedData/Graham_2_study_global_include_all_CLEAN_CASE.csv")
 # 2.8.2
 Data_2.8.2 <- read.csv("Data/LocalInputData/MLRetrievedData/Inbar_1b_study_global_include_all_CLEAN_CASE.csv")
 # 2.10.1

### 2023-12-19 Scripts/source_script.R

@@ -977,7 +977,6 @@ data_prep_plot_456 <- function(Data){
   #  "Rep_quant_REV_count", "Rep_mod_REV_count", "Rep_MP_REV_count"), 
   #  factor_key = TRUE)
   
-  
   levels(Plot_456_ratio_data_REV$QMP_type) <- c("Definition", 
                                                 "Operationalization",
                                                 "Selection", "Quantification", 

### 2024-01-02 Data/DataPackageProtocol.Rmd
finished the data package protocol and set the raw data up to be made fully open.

@@
 *Origin*: This dataset was created originally for this research project.
-It was obtained using the ???.pdf that can be found in the SupplementaryMaterials folder of this project on the Many Labs protocols mentioned in the texts and the related original articles for each of the many labs replications.
+It was obtained using the Measurement_Error_Reporting_Coding_Protocol.pdf that can be found in the SupplementaryMaterials/CodingProtocols folder of this project on the Many Labs protocols mentioned in the texts and the related original articles for each of the many labs replications.
 
@@
 
+-   **StartDate, EndData, Status, IPAdress, Progress, Duration..in.seconds., Finished, RecordedDate, Responseid, RecipientLastName, RecipientFirstName, RecipientEmail, ExternalReference, LocationLatitude, LocationLongitude, DistributionChannel,** & **UserLanguage:** automated Qualtrics metadata, not used in study.
+
+-   **Many_labs_version:** Indicates using a number the Many Labs version the study/replication under investigation belongs to.
+
+-   **research_type:** Indicates using text whether a coded measurement comes from a Replication protocol, or an Original article.
+
+-   **research_title:** the title of the replicated study as it appears in the associated Many Labs protocol/original article.
+
+-   **measure_name:** the measure's name as stated within the Many Labs protocol/original article, or a short description based on what was said in the many labs protocol/original article.
+
+-   **variable_name:** the name of the variable the measure was intended to measure based on the description in the many labs protocol/original article.
+
+-   **Q58:** Boolean variable indicating whether or not the variable assessed by the measure was assessed as [part of a larger measure intending to measure multiple variables/dimensions of a construct.
+
+-   **variable_order:** a number indicating the order of appearance for the measure within the total number of measures for that study/article.
+
+-   **N:** the number of people that took the measure as indicated in the many labs report/original article.
+
+-   **N_items:** a three choice option variable indicating whether a measure was single item, multiple item, or not a scale expected to have regular psychometric properties.
+
+-   **hypothesis_support:** question indicating whether or not the Many Labs replications found support for the original hypothesis at a meta-analytic alpha level of .05 in the same direction as the original effect.
+
+-   Reliability Coefficient Variables
+
+    -   **reliability_type:** for multiple item measures only, a question asking if a reliability coefficient was reported, and if so which one with a couple of options and the option to select Other.
+
+    -   **reliability_type_5_TEXT:** for questions that answered Oher on the reliability_type question, a text description of the specific reliability index.
+
+    -   **reliability_coeff:** for all measures with a reliability coefficient, the value of that coefficient as reported in the Many Labs protocol or original article.
+
+-   QMP Variables
+
+    -   **Def1:** A boolean variable with an additional Not Applicable option, indicating whether or not a psychological/sociological definition was given within the protocol study description or original article to the measured variable from the measure.
+
+    -   **Op_version:** if described within the protocol or article, the name and citation for the specific version of the measure that was used.
+
+    -   **Op1:** A boolean variable with an additional Not Applicable option, indicating if the specific version of the measure is described.
+
+    -   **Op2:** A boolean variable with an additional Not Applicable option, indicating whether or not the administration format of the measure and the environment the measure was taken in was described.
+
+    -   **Op3:** A boolean variable with an additional Not Applicable option, indicating whether or not the steps taken in administering the measure were described or not.
+
+    -   **Op4:** A boolean variable with an additional Not Applicable option, indicating whether or not the authors justified the way they conducted the measurement and why the specific choice was necessary to properly measure what they were investigating.
+
+    -   **Op5:** A boolean variable with an additional Not Applicable option, indicating whether or not example items are presented in the text, or in an appendix.
+
+    -   **Sel_existing:** Variable indicating whether existing articles were used, the measure was newly created for the study, or if it was not clearly stated.
+
+    -   **Sel_existing_2_TEXT:** A textual description giving the (general) name or explanation of which previous measure was used, in case an already existing measure was used.
+
+    -   **Sel1:** A boolean variable with an additional Not Applicable option, indicating whether or not the source of the scale is provided, including if it is new that this is clearly stated.
+
+    -   **Sel2:** A boolean variable with an additional Not Applicable option, indicating whether or not reasoning is given for choosing a particular measure either existing or creating a new one.
+
+    -   **Sel3:** A boolean variable with an additional Not Applicable option, indicating whether or not psychometric evidence for the validity of a scale was presented.
+
+    -   **Sel4:** A boolean variable with an additional Not Applicable option, indicating whether or not there is psychometric evidence for the measure outside of the main analyses of the protocol or study, this can be either from an earlier study, or from a pilot study testing the measure.
+
+    -   **Sel_psych_evidence:** A variable meant to indicate whether an analysis of the measure's validity was applicable, and if so whether or not it was there, and if so too, what type of psychometric evidence was reported.
+
+    -   **Sel_psych_evidence_4_TEXT:** A textual description of the specific analyses of validity that was used in case the Other, namely: option was picked in the last question.
+
+    -   **Quant1:** A boolean variable with an additional Not Applicable option, indicating whether or not the number of items in the measure are described.
+
+    -   **Quant2:** A boolean variable with an additional Not Applicable option, indicating whether or not the number of response options for the items in the measure are described.
+
+    -   **Quant3:** A boolean variable with an additional Not Applicable option, indicating whether or not recoding of responses is indicated for multiple item measures.
+
+    -   **Quant4:** A boolean variable with an additional Not Applicable option, indicating whether or not the aggregation of the scores on the items on a multiple item measure into a single index was described.
+
+    -   **Mod_check:** A variable indicating whether or not measurement modifications were mentioned at all, and if so whether the measurement was modified or not.
+
+    -   **Mod1:** A boolean variable with an additional No Modification (in case there was clear that there was no modification to this aspect) and Not Applicable option, indicating whether or not any modification to the administration format was mentioned or not.
+
+    -   **Mod2:** A boolean variable with an additional No Modification (in case there was clear that there was no modification to this aspect) and Not Applicable option, indicating whether or not there is validity evidence to support the change in the administration format.
+
+    -   **Mod3:** A boolean variable with an additional No Modification (in case there was clear that there was no modification to this aspect) and Not Applicable option, indicating whether or not any modification to the language of the questionnaire was mentioned or not.
+
+    -   **Mod4:** A boolean variable with an additional No Modification (in case there was clear that there was no modification to this aspect) and Not Applicable option, indicating whether or not there is validity evidence for the translated measure.
+
+    -   **Mod5:** A boolean variable with an additional No Modification (in case there was clear that there was no modification to this aspect) and Not Applicable option, indicating whether or not any a change in the number of items or response options deviated from the orginal source.
+
+    -   **Mod6:** A boolean variable with an additional No Modification (in case there was clear that there was no modification to this aspect) and Not Applicable option, indicating whether or not there is validity evidence for the measure with a change in the number of items or response options.
+
+    -   **Mod_time:** A variable indicating whether or not the moment the modifications was reported, and if so whether this occurred before or after the data collection for the study.
+
 ### Coded_Data_Revised_raw.csv
@@
 *Origin*: This dataset was created originally for this research project.
-It was obtained using the ???.pdf that can be found in the SupplementaryMaterials folder of this project on the Many Labs protocols mentioned in the texts and the related original articles for each of the many labs replications (the same sample as was used to obtain the Coded_Data_Initial_raw.csv).
+It was obtained using the Measurement_Error_Reporting_Revised_Coding_Protocol.pdf that can be found in the SupplementaryMaterials/CodingProtocols folder of this project on the Many Labs protocols mentioned in the texts and the related original articles for each of the many labs replications (the same sample as was used to obtain the Coded_Data_Initial_raw.csv).
 
@@
 
+-   **StartDate, EndData, Status, IPAdress, Progress, Duration..in.seconds., Finished, RecordedDate, Responseid, RecipientLastName, RecipientFirstName, RecipientEmail, ExternalReference, LocationLatitude, LocationLongitude, DistributionChannel,** & **UserLanguage:** automated Qualtrics metadata, not used in study.
+
+-   **Many_labs_version:** Indicates using a number the Many Labs version the study/replication under investigation belongs to.
+
+-   **research_type:** Indicates using text whether a coded measurement comes from a Replication protocol, or an Original article.
+
+-   **research_title:** the title of the replicated study as it appears in the associated Many Labs protocol/original article.
+
+-   **variable_order:** a number indicating the order of appearance for the measure within the total number of measures for that study/article.
+
+-   QMP Variables
+
+    -   **Op1:** A boolean variable with an additional Not Applicable option, indicating if the specific version of the measure is described, or the item in a single item measure is itself described in sufficient detail.
+
+    -   **Op2:** A boolean variable with an additional Not Applicable option, indicating whether or not the administration format of the measure and the environment the measure was taken in was described generally in as far as it is relevant to the construct.
+
+    -   **Op5:** A boolean variable with an additional Not Applicable option, indicating whether or not example items are presented in the text, or in an (online) appendix.
+
+    -   **Sel1:** A boolean variable with an additional Not Applicable option, indicating whether or not the source of the scale is provided.
+In case the scale is new, the context should make this apparent such that no source needs to be provided for this scale.
+
+    -   **Sel3:** A boolean variable with an additional Not Applicable option, indicating whether or not psychometric evidence for the validity of a scale was presented.
+Or in case such evidence is not relevant for that particular measure, a statement that clarifies this.
+
+    -   **Sel_psych_evidence:** A variable meant to indicate whether an analysis of the measure's validity was applicable, and if so whether or not it was there, and if so too, what type of psychometric evidence was reported.
+
+    -   **Sel_psych_evidence_4_TEXT:** A textual description of the specific analyses of validity that was used in case the Other, namely: option was picked in the last question.
+
+    -   **Quant1:** A boolean variable with an additional Not Applicable option, indicating whether or not the number of items in the measure are described.
+
+    -   **Quant2:** A boolean variable with an additional Not Applicable option, indicating whether or not the number of response options for the items in the measure are described.
+
+    -   **Quant3:** A boolean variable with an additional Not Applicable option, indicating whether or not recoding of responses is indicated for multiple item measures.
+
+    -   **Mod_check:** A variable indicating whether or not there were known modifications to the measurement before use in the research, and if so whether the measurement was modified or not.
+
+    -   **Mod1:** A boolean variable with an additional No Modification (in case there was clear that there was no modification to this aspect) and Not Applicable option, indicating whether or not any modification to the administration format of the overarching study protocol was mentioned or not.
+
+    -   **Mod2:** A boolean variable with an additional No Modification (in case there was clear that there was no modification to this aspect, or the modification was of little impact) and Not Applicable option, indicating whether or not there is validity evidence to support the change in the administration format.
+
+    -   **Mod3:** A boolean variable with an additional No Modification (in case there was clear that there was no modification to this aspect) and Not Applicable option, indicating whether or not any modification to the language of the overarching study protocol was mentioned or not.
+
+    -   **Mod4:** A boolean variable with an additional No Modification (in case there was clear that there was no modification to this aspect, or the modification was of little impact) and Not Applicable option, indicating whether or not there is validity evidence for the translated measure.
+
+    -   **Mod5:** A boolean variable with an additional No Modification (in case there was clear that there was no modification to this aspect) and Not Applicable option, indicating whether or not any a change in the number of items or response options deviated from the original source, for those items relevant to the original source.
+
+    -   **Mod6:** A boolean variable with an additional No Modification (in case there was clear that there was no modification to this aspect, or the modification was of little impact) and Not Applicable option, indicating whether or not there is validity evidence for the measure with a change in the number of items or response options.
+
 ### Coded_Data_Vignette_raw.csv
@@
 *Origin*: This dataset was created originally for this research project.
-It was obtained using the ???.pdf that can be found in the SupplementaryMaterials folder of this project on the Many Labs protocols mentioned in the texts and the related original articles for each of the many labs replications (the same sample as was used to obtain the Coded_Data_Initial_raw.csv).
+It was obtained using the Vignette_Item_Coding_Protocol.pdf that can be found in the SupplementaryMaterials/CodingProtocols folder of this project on the Many Labs protocols mentioned in the texts and the related original articles for each of the many labs replications (the same sample as was used to obtain the Coded_Data_Initial_raw.csv).
 
-*Explanation*: This dataset was collected after the intial round of coding with the intention to control on certain analyses whether items described a vignette and not an ordinary questionnaire, which might have different standards with regards to measurement reporting and reliability.
+*Explanation*: This dataset was collected after the initial round of coding with the intention to control on certain analyses whether items described a vignette and not an ordinary questionnaire, which might have different standards with regards to measurement reporting and reliability.
 As of yet, it has remained unused in any analyses
@@
 
-*Explanation*: contains all coded data on the original articles with renamed columns, fixed bad data, restructured to match the ordering of the protocols more ineligibly, recoded to be close to suitable for analysis, and with several composite variables added that were calculated from the raw data.
+*Explanation*: contains all coded data on the original articles with renamed columns, fixed bad data, restructured to match the ordering of the protocols more eligibly, recoded to be close to suitable for analysis, and with several composite variables added that were calculated from the raw data.
 
-<!-- add information here on all of the coded variables, and then paste it to the datasets below too. -->
+*Newly Coded Variables*:
+
+-   **\_REV variables:** these relate to the coding obtained for that particular variable using the revised coding protocol instead of the initial coding protocol.
+
+-   **Inseparable material:** the Vignette variable from the Coded_Data_Vignette_raw.csv dataset.
+
+-   **\_count variables**: a sum of the total number of TRUE coded variables within the named QMP category or the total across all categories.
+
+-   **\_total variables**: the sum of all the variables within the named QMP category or the total across all categories that was not coded as Not Applicable or No Modification.
+
+-   **\_ratio variables**: the ratio (rounded to four decimals) between the count of TRUE scores and the total applicable variables within the named QMP category or the total across all categories.
 
@@
 *Explanation*: contains all coded data on the replications as described in the many labs protocols with renamed columns, fixed bad data, restructured to match the ordering of the protocols more ineligibly, recoded to be close to suitable for analysis, and with several composite variables added that were calculated from the raw data.
+
+*Newly Coded Variables*:
+
+-   **\_REV variables:** these relate to the coding obtained for that particular variable using the revised coding protocol instead of the initial coding protocol.
+
+-   **Inseparable material:** the Vignette variable from the Coded_Data_Vignette_raw.csv dataset.
+
+-   **\_count variables**: a sum of the total number of TRUE coded variables within the named QMP category or the total across all categories.
+
+-   **\_total variables**: the sum of all the variables within the named QMP category or the total across all categories that was not coded as Not Applicable or No Modification.
+
+-   **\_ratio variables**: the ratio (rounded to four decimals) between the count of TRUE scores and the total applicable variables within the named QMP category or the total across all categories.
 

### 2024-01-02 Scripts/Manuscript/manuscript.Rmd
finished the data package protocol and set the raw data up to be made fully open.

@@
 ### Saving to Intermediate Data Folder
-closed_data(data = data_1.3_clean, filename = "Data/IntermediateData/data_1.3_clean.csv",
-            codebook = "Data/IntermediateData/codebook_data_1.3_clean.Rmd", 
-            value_labels = "Data/IntermediateData/value_labels_data_1.3_clean.yml", 
-            synthetic = FALSE)
-
-closed_data(data = data_1.10_clean, filename = "Data/IntermediateData/data_1.10_clean.csv",
-            codebook = "Data/IntermediateData/codebook_data_1.10_clean.Rmd", 
-            value_labels = "Data/IntermediateData/value_labels_data_1.10_clean.yml", 
-            synthetic = FALSE)
-
-closed_data(data = data_1.11_clean, filename = "Data/IntermediateData/data_1.11_clean.csv",
-            codebook = "Data/IntermediateData/codebook_data_1.11_clean.Rmd", 
-            value_labels = "Data/IntermediateData/value_labels_data_1.11_clean.yml", 
-            synthetic = FALSE)
-
-closed_data(data = data_1.12.3.1_clean, filename = "Data/IntermediateData/data_1.12.3.1_clean.csv",
-            codebook = "Data/IntermediateData/codebook_data_1.12.3.1_clean.Rmd", 
-            value_labels = "Data/IntermediateData/value_labels_data_1.12.3.1_clean.yml", 
-            synthetic = FALSE)
-
-closed_data(data = data_1.12.3.2_clean, filename = "Data/IntermediateData/data_1.12.3.2_clean.csv",
-            codebook = "Data/IntermediateData/codebook_data_1.12.3.2_clean.Rmd", 
-            value_labels = "Data/IntermediateData/value_labels_data_1.12.3.2_clean.yml", 
-            synthetic = FALSE)
-
-closed_data(data = data_2.10.1_clean, filename = "Data/IntermediateData/data_2.10.1_clean.csv",
-            codebook = "Data/IntermediateData/codebook_data_2.10.1_clean.Rmd", 
-            value_labels = "Data/IntermediateData/value_labels_data_2.10.1_clean.yml", 
-            synthetic = FALSE)
-
-closed_data(data = data_2.12.1_clean, filename = "Data/IntermediateData/data_2.12.1_clean.csv",
-            codebook = "Data/IntermediateData/codebook_data_2.12.1_clean.Rmd", 
-            value_labels = "Data/IntermediateData/value_labels_data_2.12.1_clean.yml", 
-            synthetic = FALSE)
-
-closed_data(data = data_2.12.2_clean, filename = "Data/IntermediateData/data_2.12.2_clean.csv",
-            codebook = "Data/IntermediateData/codebook_data_2.12.2_clean.Rmd", 
-            value_labels = "Data/IntermediateData/value_labels_data_2.12.2_clean.yml", 
-            synthetic = FALSE)
-
-closed_data(data = data_2.12.3_clean, filename = "Data/IntermediateData/data_2.12.3_clean.csv",
-            codebook = "Data/IntermediateData/codebook_data_2.12.3_clean.Rmd", 
-            value_labels = "Data/IntermediateData/value_labels_data_2.12.3_clean.yml", 
-            synthetic = FALSE)
-
-closed_data(data = data_2.15_clean, filename = "Data/IntermediateData/data_2.15_clean.csv",
-            codebook = "Data/IntermediateData/codebook_data_2.15_clean.Rmd", 
-            value_labels = "Data/IntermediateData/value_labels_data_2.15_clean.yml", 
-            synthetic = FALSE)
-
-closed_data(data = data_2.20_clean, filename = "Data/IntermediateData/data_2.20_clean.csv",
-            codebook = "Data/IntermediateData/codebook_data_2.20_clean.Rmd", 
-            value_labels = "Data/IntermediateData/value_labels_data_2.20_clean.yml", 
-            synthetic = FALSE)
-
-closed_data(data = data_2.23_clean, filename = "Data/IntermediateData/data_2.23_clean.csv",
-            codebook = "Data/IntermediateData/codebook_data_2.23_clean.Rmd", 
-            value_labels = "Data/IntermediateData/value_labels_data_2.23_clean.yml", 
-            synthetic = FALSE)
-
-closed_data(data = data_3.2.1.1_clean, filename = "Data/IntermediateData/data_3.2.1.1_clean.csv",
-            codebook = "Data/IntermediateData/codebook_data_3.2.1.1_clean.Rmd", 
-            value_labels = "Data/IntermediateData/value_labels_data_3.2.1.1_clean.yml", 
-            synthetic = FALSE)
-
-closed_data(data = data_3.2.1.2_clean, filename = "Data/IntermediateData/data_3.2.1.2_clean.csv",
-            codebook = "Data/IntermediateData/codebook_data_3.2.1.2_clean.Rmd", 
-            value_labels = "Data/IntermediateData/value_labels_data_3.2.1.2_clean.yml", 
-            synthetic = FALSE)
-
-closed_data(data = data_3.7.1_clean, filename = "Data/IntermediateData/data_3.7.1_clean.csv",
-            codebook = "Data/IntermediateData/codebook_data_3.7.1_clean.Rmd", 
-            value_labels = "Data/IntermediateData/value_labels_data_3.7.1_clean.yml", 
-            synthetic = FALSE)
-
-closed_data(data = data_3.7.2_clean, filename = "Data/IntermediateData/data_3.7.2_clean.csv",
-            codebook = "Data/IntermediateData/codebook_data_3.7.2_clean.Rmd", 
-            value_labels = "Data/IntermediateData/value_labels_data_3.7.2_clean.yml", 
-            synthetic = FALSE)
-
-closed_data(data = data_3.8.2_clean, filename = "Data/IntermediateData/data_3.8.2_clean.csv",
-            codebook = "Data/IntermediateData/codebook_data_3.8.2_clean.Rmd", 
-            value_labels = "Data/IntermediateData/value_labels_data_3.8.2_clean.yml", 
-            synthetic = FALSE)
-
-closed_data(data = data_5.1.1_clean, filename = "Data/IntermediateData/data_5.1.1_clean.csv",
-            codebook = "Data/IntermediateData/codebook_data_5.1.1_clean.Rmd", 
-            value_labels = "Data/IntermediateData/value_labels_data_5.1.1_clean.yml", 
-            synthetic = FALSE)
-
-closed_data(data = data_5.4_clean, filename = "Data/IntermediateData/data_5.4_clean.csv",
-            codebook = "Data/IntermediateData/codebook_data_5.4_clean.Rmd", 
-            value_labels = "Data/IntermediateData/value_labels_data_5.4_clean.yml", 
-            synthetic = FALSE)
-
-closed_data(data = data_5.7_clean, filename = "Data/IntermediateData/data_5.7_clean.csv",
-            codebook = "Data/IntermediateData/codebook_data_5.7_clean.Rmd", 
-            value_labels = "Data/IntermediateData/value_labels_data_5.7_clean.yml", 
-            synthetic = FALSE)
-
-closed_data(data = data_5.9.1_clean, filename = "Data/IntermediateData/data_5.9.1_clean.csv",
-            codebook = "Data/IntermediateData/codebook_data_5.9.1_clean.Rmd", 
-            value_labels = "Data/IntermediateData/value_labels_data_5.9.1_clean.yml", 
-            synthetic = FALSE)
+open_data(data = data_1.3_clean, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(data_1.3_clean))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(data_1.3_clean))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(data_1.3_clean))), ".yml"))
+
+open_data(data = data_1.10_clean, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(data_1.10_clean))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(data_1.10_clean))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(data_1.10_clean))), ".yml"))
+
+open_data(data = data_1.11_clean, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(data_1.11_clean))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(data_1.11_clean))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(data_1.11_clean))), ".yml"))
+
+open_data(data = data_1.12.3.1_clean, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(data_1.12.3.1_clean))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(data_1.12.3.1_clean))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(data_1.12.3.1_clean))), ".yml"))
+
+open_data(data = data_1.12.3.2_clean, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(data_1.12.3.2_clean))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(data_1.12.3.2_clean))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(data_1.12.3.2_clean))), ".yml"))
+
+open_data(data = data_2.10.1_clean, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(data_2.10.1_clean))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(data_2.10.1_clean))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(data_2.10.1_clean))), ".yml"))
+
+open_data(data = data_2.12.1_clean, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(data_2.12.1_clean))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(data_2.12.1_clean))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(data_2.12.1_clean))), ".yml"))
+
+open_data(data = data_2.12.2_clean, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(data_2.12.2_clean))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(data_2.12.2_clean))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(data_2.12.2_clean))), ".yml"))
+
+open_data(data = data_2.12.3_clean, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(data_2.12.3_clean))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(data_2.12.3_clean))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(data_2.12.3_clean))), ".yml"))
+
+open_data(data = data_2.15_clean, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(data_2.15_clean))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(data_2.15_clean))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(data_2.15_clean))), ".yml"))
+
+open_data(data = data_2.20_clean, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(data_2.20_clean))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(data_2.20_clean))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(data_2.20_clean))), ".yml"))
+
+open_data(data = data_2.23_clean, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(data_2.23_clean))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(data_2.23_clean))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(data_2.23_clean))), ".yml"))
+
+open_data(data = data_3.2.1.1_clean, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(data_3.2.1.1_clean))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(data_3.2.1.1_clean))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(data_3.2.1.1_clean))), ".yml"))
+
+open_data(data = data_3.2.1.2_clean, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(data_3.2.1.2_clean))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(data_3.2.1.2_clean))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(data_3.2.1.2_clean))), ".yml"))
+
+open_data(data = data_3.7.1_clean, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(data_3.7.1_clean))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(data_3.7.1_clean))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(data_3.7.1_clean))), ".yml"))
+
+open_data(data = data_3.7.2_clean, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(data_3.7.2_clean))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(data_3.7.2_clean))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(data_3.7.2_clean))), ".yml"))
+
+open_data(data = data_3.8.2_clean, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(data_3.8.2_clean))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(data_3.8.2_clean))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(data_3.8.2_clean))), ".yml"))
+
+open_data(data = data_5.1.1_clean, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(data_5.1.1_clean))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(data_5.1.1_clean))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(data_5.1.1_clean))), ".yml"))
+
+open_data(data = data_5.4_clean, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(data_5.4_clean))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(data_5.4_clean))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(data_5.4_clean))), ".yml"))
+
+open_data(data = data_5.7_clean, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(data_5.7_clean))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(data_5.7_clean))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(data_5.7_clean))), ".yml"))
+
+open_data(data = data_5.9.1_clean, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(data_5.9.1_clean))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(data_5.9.1_clean))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(data_5.9.1_clean))), ".yml"))
 

### 2024-01-02 Scripts/prepare_data.R

@@ -90,62 +90,101 @@ Coded_Data_Vignette_raw <- read.csv("Data/LocalInputData/CodedData/Coded Data (V
 
 
 # Data Storing -----------------------------------------------------------------
-closed_data(data = Data_ML1, filename = "Data/InputData/Data_ML1.csv",
-  codebook = NULL, value_labels = NULL, synthetic = FALSE) 
+open_data(data = Data_ML1, 
+          filename = "Data/InputData/Data_ML1.csv",
+          codebook = NULL, value_labels = NULL, 
+          load_expression = read.csv(file = filename, stringsAsFactors = FALSE)) 
 
-closed_data(data = Data_2.2, filename = "Data/InputData/Data_2.2.csv",
-  codebook = NULL, value_labels = NULL, synthetic = FALSE) 
+open_data(data = Data_2.2, 
+          filename = "Data/InputData/Data_2.2.csv",
+          codebook = NULL, value_labels = NULL, 
+          load_expression = read.csv(file = filename, stringsAsFactors = FALSE)) 
 
-closed_data(data = Data_2.3, filename = "Data/InputData/Data_2.3.csv",
-  codebook = NULL, value_labels = NULL, synthetic = FALSE) 
+open_data(data = Data_2.3, 
+          filename = "Data/InputData/Data_2.3.csv",
+          codebook = NULL, value_labels = NULL, 
+          load_expression = read.csv(file = filename, stringsAsFactors = FALSE)) 
 
-closed_data(data = Data_2.4.1, filename = "Data/InputData/Data_2.4.1.csv",
-  codebook = NULL, value_labels = NULL, synthetic = FALSE) 
+open_data(data = Data_2.4.1, 
+          filename = "Data/InputData/Data_2.4.1.csv",
+          codebook = NULL, value_labels = NULL, 
+          load_expression = read.csv(file = filename, stringsAsFactors = FALSE)) 
 
-closed_data(data = Data_2.4.2, filename = "Data/InputData/Data_2.4.2.csv",
-  codebook = NULL, value_labels = NULL, synthetic = FALSE) 
+open_data(data = Data_2.4.2, 
+          filename = "Data/InputData/Data_2.4.2.csv",
+          codebook = NULL, value_labels = NULL, 
+          load_expression = read.csv(file = filename, stringsAsFactors = FALSE)) 
 
-closed_data(data = Data_2.8.2, filename = "Data/InputData/Data_2.8.2.csv",
[…]

### 2024-01-02 Data/AnalysisData/codebook_plot_46_data_REV.Rmd
Opened up the Many Labs retrieved data for the project.

--- 2023-11-07 Data/AnalysisData/codebook_Plot_46_data.Rmd
@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:47.216976"
+title: "Codebook created on 2024-01-02 at 2024-01-02 11:37:22.192211"
 output: github_document
@@
 ```{r}
-summaries <- read.csv("codebook_Plot_46_data.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_plot_46_data_rev.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2024-01-02 Scripts/prepare_data.R

@@ -181,7 +181,7 @@ open_data(data = Data_5.7,
           load_expression = read.csv(file = filename, stringsAsFactors = FALSE)) 
 
 open_data(data = Data_5.9.1, 
-          filename = "Data/InputData/Data_5.1.csv",
+          filename = "Data/InputData/Data_5.9.1.csv",
           codebook = NULL, value_labels = NULL, 
           load_expression = read.csv(file = filename, stringsAsFactors = FALSE)) 
 

### 2024-01-02 Scripts/Manuscript/manuscript.Rmd
changed the uses of the word thesis to either study or article, and added references to the github page were relevant.

@@
   In particular, studies have indicated that low reliability, and poor measurement reporting can negatively influence the replicability of an effect. 
-  Building on this new line of research, this thesis assessed these influences in large scale replication projects. 
+  Building on this new line of research, this study assessed these influences in large scale replication projects. 
   Protocols from the Many Labs replication projects, and the original articles that the replications were based on were used to assess the  reporting of the measures, while publicly available data from the Many Labs replications was used to assess the reliability of the measures.
@@
 <!-- altering latex defaults to get better figure and table placement -->
-\renewcommand{\arraystretch}{0.7} <!-- reducing the line spacing within tables -->
-\renewcommand{\topfraction}{.85} <!-- max fraction of page for floats at top -->
-\renewcommand{\bottomfraction}{.7} <!-- max fraction of page for floats at bottom -->
-\renewcommand{\textfraction}{.15} <!-- min fraction of page for text -->
-\renewcommand{\floatpagefraction}{.66} <!-- min fraction of page that should have floats -->
-\setcounter{topnumber}{3} <!-- max number of floats at top of page -->
-\setcounter{bottomnumber}{3} <!-- max number of floats at bottom of page -->
-\setcounter{totalnumber}{4} <!-- max number of floats on a page -->
-<!-- remember to use [htp] or [htpb] for placement -->
+
+\renewcommand{\arraystretch}{0.7}
+
+<!-- reducing the line spacing within tables -->
+
+\renewcommand{\topfraction}{.85}
+
+<!-- max fraction of page for floats at top -->
+
+\renewcommand{\bottomfraction}{.7}
+
+<!-- max fraction of page for floats at bottom -->
+
+\renewcommand{\textfraction}{.15}
+
+<!-- min fraction of page for text -->
+
+\renewcommand{\floatpagefraction}{.66}
+
+<!-- min fraction of page that should have floats -->
+
+\setcounter{topnumber}{3} <!-- max number of floats at top of page --> \setcounter{bottomnumber}{3} <!-- max number of floats at bottom of page --> \setcounter{totalnumber}{4} <!-- max number of floats on a page --> <!-- remember to use [htp] or [htpb] for placement -->
 
@@
 # Introduction
+
 For many years, methodologists and statisticians have raised concerns about the way that research practices [@cumming2014new; @wicherts2016degrees], reporting practices [@bakker2011mis; @nuijten2016prevalence], and publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science] may undermine the credibility of psychology's scientific claims.
@@
 
-This thesis aims to investigate the influence of measurement error and QMPs on replicability, using data and reports from the large scale Many Labs replication projects.
+This study aims to investigate the influence of measurement error and QMPs on replicability, using data and reports from the large scale Many Labs replication projects.
 One goal is to expand the research by [@stanley2014expectations] with a practical example.
-Whereas they obtained their findings using a simulation study, this thesis intended to investigate the scope of their findings in practice.
+Whereas they obtained their findings using a simulation study, this study investigated the scope of their findings in practice.
 QMPs in the context of replication research were already investigated by [@flake2022construct].
 However, the investigations remained mostly descriptive.
-This thesis aims to expand upon the findings of [@flake2022construct] through the use of a new set of replication data, and by investigating the relation between QMP and replicability.
+This study aims to expand upon the findings of [@flake2022construct] through the use of a new set of replication data, and by investigating the relation between QMP and replicability.
 
@@
 As a first step it is worth investigating what the state of measurement error is in original and psychological research, in order to assess the scope of @stanley2014expectations's findings in practice.
-Thus, this thesis will investigate the following:
+Thus, this study investigated the following:
 
@@
 However analyses from Many Labs 2, and @olsson2020heterogeneity showed little empirical evidence for widespread heterogeneity in effects amongst replications.
-These findings demonstrate that it is possible to reduce variability as the result of context using structured protocols, as was done in the Many Labs projects this thesis analyzed.
+These findings demonstrate that it is possible to reduce variability as the result of context using structured protocols, as was done in the Many Labs projects this study analyzed.
 
@@
 
-This thesis investigated whether there is something in the measures used for replicated findings that sets them apart from those used for non-replicated findings.
-In particular, this thesis extends research by @stanley2014expectations on the relationship between reliability and replicability, by using data from real life replication projects.
+This study investigated whether there is something in the measures used for replicated findings that sets them apart from those used for non-replicated findings.
+In particular, this study extends research by @stanley2014expectations on the relationship between reliability and replicability, by using data from real life replication projects.
 
@@
 @flake2022construct descriptively investigated QMPs within the reproducibility project psychology [@osc2015estimating].
-This thesis seeks to conceptually replicate some of their findings within the Many Labs replication projects.
+This study seeks to conceptually replicate some of their findings within the Many Labs replication projects.
 
@@
 Data collection, coding protocol, and planned analyses were all preregistered.
-The preregistration and supplementary materials can be found on this thesis' OSF page: <https://osf.io/9r8yt/>.
+The preregistration and supplementary materials can be found on this article's OSF page: <https://osf.io/9r8yt/>.
 Any deviations from the preregistration are explicitly mentioned in the text.
 This manuscript was generated using the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency.
-All code and XXX data are available at <https://github.com/CasGoos/measurement_and_replication.git>.
+All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication.git>.
 
@@
 
-The data used for the analyses in this thesis consists of three main sources: replication datasets, preregistered replication protocols, and original study articles.
+The data used for the analyses in this study consists of three main sources: replication datasets, preregistered replication protocols, and original study articles.
 The data came from the Many Labs series of studies.
@@
 Additionally, the replication of [@crosby2008we] in Many Labs 5 did not contain contain data suitable for this project.
-The replication made use of videos and eye-tracking as measures, which does not match this thesis' focus on scale and item measures.
+The replication made use of videos and eye-tracking as measures, which does not match this study's focus on scale and item measures.
 
@@
 The measure had to consist of multiple scalar items to be considered relevant for the related analyses.
-Single item measures were not usable for the analyses on score reliability [@wanous1996estimating] as they do not translate directly to the findings of @stanley2014expectations, which this thesis is following up on.
+Single item measures were not usable for the analyses on score reliability [@wanous1996estimating] as they do not translate directly to the findings of @stanley2014expectations, which this study is following up on.
 
@@
 
-```{r Cleaning Replication Datasets Data, include = FALSE, eval = FALSE}
+```{r CleaningReplicationDatasetsData, include = FALSE, eval = FALSE}
 ##### Data already available, code does not need to be run!
@@
 
-```{r Cleaning Coded Data, include = FALSE, eval = FALSE}
+```{r CleaningCodedData, include = FALSE, eval = FALSE}
 ##### Data already available, code does not need to be run!
@@
 [^1]: The steps taken to access the replication protocol data from Many Labs 5 were not preregistered, and only became clear upon further investigation of the accessible information.
-The specific names and locations of the files that were used as the datasets can be found under the supplementary materials of the OSF page of this thesis <https://osf.io/gft46/%7D>
+The specific names and locations of the files that were used as the datasets can be found under the supplementary materials of the OSF page of this article <https://osf.io/gft46/%7D>
 
@@
 The measures of primary variables were identified by combing through the entire methods section of each preregistered replication protocols.
-Then using the structured coding protocol (made using Qualtrics) available on the OSF page for this thesis (<https://osf.io/9r8yt/>), each measure of a unique variable was coded on measurement reporting and reported reliability.
+Then using the structured coding protocol (made using Qualtrics) that is available on the OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages of this study, each measure of a unique variable was coded on measurement reporting and reported reliability.
 
@@
 The revision of the coding protocol happened after all the data were coded using the initial protocol.
-As a result the coded data using the initial protocol, and the coded data using the revised protocol are both available available on this thesis' OSF page: <https://osf.io/9r8yt/>.
+As a result the coded data using the initial protocol, and the coded data using the revised protocol are both available available on this article's OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages.
 Both raw and processed formats are present.
@@
 Replication success was based on the test of the main effect of a study.
-However, the unit of measurement for the data in this thesis was a measure of a unique variable, not an effect.
+However, the unit of measurement for the data in this study was a measure of a unique variable, not an effect.
 Fortunately, since only primary measures were included in the data, each measured a variable of the main effect, and as a result the measure remains related to the test of the main effect.
@@
 Eleven out of twenty of the quantitative coding variables have an equivalent in @flake2022construct.
-Variables related to the specific measurement scaling and purpose in the paper, were omitted from the analyses of this thesis as they were deemed neither relevant for the analyses of this study, nor necessary in matching this study to the key results of @flake2022construct.
-Questions about more general measurement features such as the number of items and how scores were aggregated were altered from @flake2022construct to better fit the aims of this thesis.
+Variables related to the specific measurement scaling and purpose in the paper, were omitted from the analyses of this study as they were deemed neither relevant for the analyses of this study, nor necessary in matching this study to the key results of @flake2022construct.
+Questions about more general measurement features such as the number of items and how scores were aggregated were altered from @flake2022construct to better fit the aims of this study.
 
@@
 
-```{r Check for Reliability and Validity Testability, include = FALSE, warning = FALSE}
+```{r ReliabilityValidityTestabilityCheck, include = FALSE, warning = FALSE}
 ## Checking the measures to recalculate the reliability and factor analysis for.
@@
 
-```{r Final Preparation of Data, include = FALSE, eval = FALSE}
+```{r FinalPreparationData, include = FALSE, eval = FALSE}
 ##### Data already available, code does not need to be run!
@@
 
-Every hypothesis test in this thesis used an alpha significance cutoff of .05.
+Every hypothesis test in this study used an alpha significance cutoff of .05.
 No correction for multiple testing was applied, to avoid inflating type II error rate.
@@
 
-```{r Hypothesis 1 Model, include = FALSE}
+```{r Hypothesis1Model, include = FALSE}
 # first some descriptives of reliability reporting
@@
 ```
-
-```{r Hypothesis 2 Model, include = FALSE}
+```{r Hypothesis2Model, include = FALSE}
 # intercept only model to check the within and between group variance.
@@
 ```
-
 A high ICC indicates low within group variance relative to between group variance, which would be in line with hypothesis 2.
 
-```{r ICC calculations, include = FALSE}
+```{r ICCCalculations, include = FALSE}
 # alpha
@@
 ```
-
 Where:
@@
 ```
-
-```{r Hypothesis 3 Main Test, include = FALSE}
+```{r Hypothesis3MainTest, include = FALSE}
 ## The main model to test hypothesis 3, through a logistic regression model.
@@
 
-```{r Hypothesis 3 Multilevel Model Sensitivity Analyses, include = FALSE}
+```{r Hypothesis3MultilevelModelSensitivityAnalyses, include = FALSE}
 ## sensitivity analyses.
@@
 The results using the original QMP data are mentioned when the results led to different conclusions.
-The analysis code for both the original and revised QMP data are available in the R script on both the OSF page (<https://osf.io/9r8yt/>) and github page (<https://github.com/CasGoos/measurement_and_replication.git>) of this article.
+The analysis code for both the original and revised QMP data are available in the R script on both the OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages of this article.
 
@@
 ```
-
 All of these models assume that the QMPs are the same across each replication set.
@@
 ```
-
-```{r Hypothesis 4 Model, include = FALSE}
+```{r Hypothesis4Model, include = FALSE}
 ## Hypothesis 4 beta regression model
@@
 ```
-
 Where $replicated_{i}$ is a dummy coded variable, which was coded as 1 if the meta-analytic effect in the replication set matches the original effect in direction at a significance alpha level of .05, and 0 otherwise.
@@
 
-```{r Hypothesis 5 Model, include = FALSE}
-## Hypothesis 4 beta regression model
+```{r Hypothesis5Model, include = FALSE}
+## Hypothesis 5 beta regression model
 H5_test_results <- betareg(QMP_ratio ~ hypothesis_support, data = data_h5)
@@
 ```
-
-```{r Hypothesis 6 Model, include = FALSE}
+```{r Hypothesis6Model, include = FALSE}
+## Hypothesis 6 beta regression model
 H6_test_results <- betareg(Rep_QMP_ratio ~ QMP_ratio, data = data_h6)
@@
 
-```{r Hypotheses 5 & 6 Sensitivity Analyses, include = FALSE}
+```{r Hypotheses5&6SensitivityAnalyses, include = FALSE}
 ## Hypothesis 5 sensitivity test using a random intercept Guassian model.
@@
 
-```{r Hypothesis 6 Associations, include = FALSE}
+```{r Hypothesis6Associations, include = FALSE}
 ## Associations between the QMP categories
@@
 
-```{r Unidimensionality Exploratory Analysis, include = FALSE}
+```{r UnidimensionalityExploratoryAnalysis, include = FALSE}
 extracted_data_list <- list(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean,
@@
   , note = "$^a$replication was assessed as unclear for three of the measures, since their effect was not fully replicated.
-These have been treated as not replicated within this table and further analyses throughout the thesis"
+These have been treated as not replicated within this table and further analyses throughout the article"
   , escape = FALSE, placement = "htp", midrules = 4)
@@
 
-This thesis assessed the quality of measurement and measurement reporting in original and replication research by investigating the quality of measurement in the Many Labs projects.
+This study assessed the quality of measurement and measurement reporting in original and replication research by investigating the quality of measurement in the Many Labs projects.
 Findings were in line with similar investigations in the literature by @shaw2020measurement & @flake2022construct.
 These two studies found that sufficient validity evidence and reliability reporting for measures was lacking, even more so for replications than for original studies.
-The lack of support found for hypothesis 1 shows that this also held for this thesis' sample.
+The lack of support found for hypothesis 1 shows that this also held for this study's sample.
 In fact, support was found for an effect in the direction opposite to what was hypothesized in the preregistration, as the original articles reported reliability coefficients more often than replication studies.
@@
 For example, IQ is often used as a singular indicator, even though it consists of several factors [@weiss2013wisc].
-However, it should be noted that at least with respect to Many Labs 2, all of the measures that were considered unidimensional for the analyses in this thesis were also considered unidimensional in the investigation by @shaw2020measurement} who also observed a lack of unidimensionality evidence in their investigation of Many Labs 2.
+However, it should be noted that at least with respect to Many Labs 2, all of the measures that were considered unidimensional for the analyses in this study were also considered unidimensional in the investigation by @shaw2020measurement} who also observed a lack of unidimensionality evidence in their investigation of Many Labs 2.
 To conclude, there is an indication that validity evidence for measures used in replication research is lacking overall.
@@
 
-Besides assessing the overall quality of measurement reporting, this thesis also investigated if the reliability of a measure, and QMPs can impact replicability.
+Besides assessing the overall quality of measurement reporting, this study also investigated if the reliability of a measure, and QMPs can impact replicability.
 First of all, contrary to expectations (see Hypothesis 3), less reliable measures were not associated with a decrease in replicability.
 This result is surprising, since @stanley2014expectations demonstrated the potential impact that measurement error can have on the veracity of determining replication success based on a significance test without attenuating for measurement error.
-The significance test cut-off criteria that was used in this thesis to assess replication success similarly did not attenuate for measurement error, and thus results in line with the simulation studies of @stanley2014expectations were expected.
+The significance test cut-off criteria that was used in this study to assess replication success similarly did not attenuate for measurement error, and thus results in line with the simulation studies of @stanley2014expectations were expected.
 
@@
 
-The design of this thesis came with certain limitations.
+The design of this study came with certain limitations.
 First of all, there was no experimental manipulation included.
 As a result, the ability to investigate the exact causal links between QMPs and replicability was limited.
-This thesis was intended to be exploratory in nature, and thus did not focus on causal analyses.
+This study was intended to be exploratory in nature, and thus did not focus on causal analyses.
 However, future research establishing causal links will prove to be very beneficial in improving the understanding of the relationships between measurement issues and replicability.
@@
 Future research investigating this topic should use a coding protocol which is verified independently by several researchers on a sample of articles and protocols first, before being used to code the QMP data that will be analysed.
-As a first step, the coding protocol from this thesis and the coding key from @flake2022construct can be used as a basis.
+As a first step, the coding protocol from this study and the coding key from @flake2022construct can be used as a basis.
 
@@
 Articles are generally longer than a study's description within a replication protocol, and as a result it seems reasonable to expect research articles to generally contain more measurement details than replication protocols.
-Regardless, this thesis assumed that a replication protocol is comparable to an article in providing an overview of the measure and how it was used, as it is the only comparable source for such information that would otherwise be difficult to find anywhere else.
+Regardless, this study assumed that a replication protocol is comparable to an article in providing an overview of the measure and how it was used, as it is the only comparable source for such information that would otherwise be difficult to find anywhere else.
 This assumption seems practical if not tenable when the replication protocol is the only available sources of measurement details.
@@
 For this study, the protocol was made and the analyses were conducted under the assumption that each item had equal weight.
-However, this is an assumption this article cannot provide evidence for.
+However, this is an assumption this study cannot provide evidence for.
 
 The small sample of measures for which reliability coefficients and unidimensional factor structure could be assessed limited the degree to which substantial interpretations can be made from the reliability and validity analyses.
-While future research will also unlikely be able to increase the number of multiple item measures used by replications, future research can broaden their analyses to include a larger number of replications, or take into account a type of measure which this thesis mostly ignored in the analyses of reliability and validity: single-item measures.
-
-Reliability assessment for single item measures differs substantially from multiple item measures [@wanous1996estimating], and for this reason was not included as part of the analyses for this thesis.
+While future research will also unlikely be able to increase the number of multiple item measures used by replications, future research can broaden their analyses to include a larger number of replications, or take into account a type of measure which this study mostly ignored in the analyses of reliability and validity: single-item measures.
+
+Reliability assessment for single item measures differs substantially from multiple item measures [@wanous1996estimating], and for this reason was not included as part of the analyses for this study.
 Furthermore, single items cannot be tested on unidimensionality, since a single item is already assumed to measure only a single dimension by definition.
 However, future research might consider methods specifically designed to assess reliability and validity of single item measures.
-This could prove to be a worthwhile contribution, given the proportionally large number of single item measures that were encountered in the data for this thesis (see Figure \@ref(fig:ReliabilityReportingFlowDiagram)).
+This could prove to be a worthwhile contribution, given the proportionally large number of single item measures that were encountered in the data for this study (see Figure \@ref(fig:ReliabilityReportingFlowDiagram)).
 

### 2024-02-16 Data/AnalysisData/codebook_plot_23_data_reported_alpha.Rmd
starting to restructure the article based on feedback. Start on adding meta-analysis component to H2

--- 2023-11-07 Data/AnalysisData/codebook_Plot_46_data.Rmd
@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:47.216976"
+title: "Codebook created on 2024-02-14 at 2024-02-14 09:47:30.71879"
 output: github_document
@@
 ## Dataset description
-The data contains 1925 cases and 4 variables.
+The data contains 9 cases and 4 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_Plot_46_data.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_plot_23_data_reported_alpha.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2024-02-16 Data/DataPackageProtocol.Rmd
starting to restructure the article based on feedback. Start on adding meta-analysis component to H2

@@
 
+### plot_23_data_reported_alpha.csv
+
+*Explanation:* Contains reported alpha reliability coefficients extracted from original articles from which such data was available, and for which data was available from the replications from the Many Labs data to calculate reliabilities for.
+The goal of this data was to be superimposed on top of figure 2 (plot_23_alpha) to compare calculated reliability coefficients with reported reliability coefficients.
+
+*Variables*:
+
+-   **title:** The title of the article relating to the particular measure of that row, extracted from coded_data_original_shortened.csv
+
+-   **graph_title:** author, year, and optional word indicating the specific measure. Relates directly to the indication of the measures as shown in figure 2 (plot_23_alpha).
+
+-   **article_order:** numerical variable giving the index for placing the reliability coefficients in the right row in figure 2 (plot_23_alpha).
+
+-   **coefficient:** the value for the reported alpha coefficient for the specific measure as extracted from the original article the measure was reported in.
+
 ### plot_23_data_omega.csv

### 2024-02-16 Data/IntermediateData/codebook_data_5.1.1_clean.Rmd
added the final data preparation step, and the models for H1 and H3.
failed attempt to include R results as numbers in text.
Opened up the Many Labs retrieved data for the project.
starting to restructure the article based on feedback. Start on adding meta-analysis component to H2

@@
 ---
-title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:31.816934"
+title: "Codebook created on 2024-02-16 at 2024-02-16 14:19:38.624634"
 output: github_document
@@
 ## Dataset description
-The data contains 471 cases and 22 variables.
+The data contains 471 cases and 16 variables.
 

### 2024-02-16 Data/IntermediateData/codebook_data_5.1.2_clean.Rmd
starting to restructure the article based on feedback. Start on adding meta-analysis component to H2

--- 2023-11-13 Data/AnalysisData/codebook_plot_46_data_REV.Rmd
@@
 ---
-title: "Codebook created on 2023-11-13 at 2023-11-13 11:23:32.03741"
+title: "Codebook created on 2024-02-16 at 2024-02-16 14:19:42.46426"
 output: github_document
@@
 ## Dataset description
-The data contains 1925 cases and 4 variables.
+The data contains 471 cases and 7 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_plot_46_data_REV.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_5.1.2_clean.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2024-02-16 Scripts/Manuscript/manuscript_v.master_thesis.Rmd
starting to restructure the article based on feedback. Start on adding meta-analysis component to H2

--- 2024-01-02 Scripts/Manuscript/manuscript.Rmd
@@
 keywords          : "reliability, measurement, measurement reporting, replicability, construct validity"
-wordcount         : "X"
+wordcount         : "194"
 
@@
 # loading source script
-source(file = "../source_script.R")
+source(file = "C:/Users/u686785/OneDrive - Tilburg University/Documents/uvt/PHD/Master Thesis to Paper/Reproducible_R_Project/Scripts/source_script.R")
 
@@
 
-As a first step it is worth investigating what the state of measurement error is in original and psychological research, in order to assess the scope of @stanley2014expectations's findings in practice.
+As a first step it is worth investigating what the state of measurement error is in original and replication research in psychology, in order to assess the scope of @stanley2014expectations's findings in practice.
 Thus, this study investigated the following:
@@
 
+### QMP measures
+
 The tests for hypotheses 4, 5, & 6 were all based on the number of QMPs per category that were determined by the research using the coding protocol.
@@
 These ratios were preferred over counts, since non applicable items could thus be accounted for.
-
-### QMP measures
-
-The same data as for the test of hypothesis 2 was used to check for the unidimensionality of the factor structure, as part of the exploratory analyses.
-A check for unidimensionality as validity evidence only makes sense if the measure was intended to be unidimensional.
-Therefore, for each replication for which data was available, the protocol was checked to ensure that the scores on each measure were meant to assess a single construct.
 

### 2024-02-16 Scripts/source_script.R

@@ -589,14 +589,49 @@ data_prep_H1 <- function(Data_Original, Data_Replications){
 
 
 ### Hypothesis 2
-# obtaining the omega and alpha values for each measure (helper function)
-omega_and_alpha <- function(Data, m_length){
-  return(omega(Data[2:m_length], nfactors = 1)[3:4])
+# ASE (alpha standard error) formula for a single lab
+ASE_for_Lab <- function(lab_data){
+  V_matrix <- cov(lab_data)
+  p_num <- ncol(lab_data)
+  j_vec <- rep(1, times = p_num)
+  
+  ### missing data issue
+  
+  # not sure about this implementation:
+  Q_value <- ((2 * p_num^2) / ((p_num - 1)^2 * (crossprod(j_vec, V_matrix) %*% 
+    j_vec)^3)) * ((crossprod(j_vec, V_matrix) %*% j_vec) * (sum(diag(
+      V_matrix^2)) + sum(diag(V_matrix))^2) - 2*(sum(diag(V_matrix))) * (
+        crossprod(j_vec, V_matrix^2) %*% j_vec))
+  
+  ASE <- as.numeric(sqrt(Q_value / nrow(lab_data)))
+  
+  return(ASE)
 }
 
-# obtaining the alpha values for 2.12.3, 2.20, & 3.2.1.1 (helper function)
+# obtaining the omega and alpha values for each measure (helper function).
+omega_and_alpha <- function(Data, m_length){
+  # selecting only the complete cases for the ASE calculations
+  Data_complete <- Data[complete.cases(Data),]
+  
+  omega_and_alpha_vec <- c(t(omega(Data[2:m_length], nfactors = 1)[3:4]), 
+                           ASE_for_Lab(Data_complete[2:m_length]))
+  
+  names(omega_and_alpha_vec) <- c("alpha", "omega.tot", "ASE")
+  
+  return(omega_and_alpha_vec)
+}
+
+# obtaining the alpha values for 2.12.3, 2.20, & 3.2.1.1 (helper function).
 just_alpha <- function(Data, m_length){
-  return(c(alpha = psych::alpha(Data[2:m_length])$total[[2]], omega.tot = NA))
+  # selecting only the complete cases for the ASE calculations
+  Data_complete <- Data[complete.cases(Data),]
+  
+  alpha_vec <- c(t(psych::alpha(Data[2:m_length])$total[[2]]), NA, 
+                 ASE_for_Lab(Data_complete[2:m_length]))
+ 
[…]

### 2024-02-28 Data/AnalysisData/codebook_data_H2.Rmd
added the results for H5 and H6, including plot 46, which also required the adition of the plot_46_data_rev file, which lead to a rerun of the final data creation code.
Opened up the Many Labs retrieved data for the project.
starting to restructure the article based on feedback. Start on adding meta-analysis component to H2
changed plot456 and plot46, and first stages of restructuring results.

@@
 ---
-title: "Codebook created on 2023-11-09 at 2023-11-09 13:46:42.481222"
+title: "Codebook created on 2024-02-26 at 2024-02-26 14:50:07.480565"
 output: github_document
@@
 ## Dataset description
-The data contains 713 cases and 3 variables.
+The data contains 670 cases and 9 variables.
 

### 2024-02-28 Data/AnalysisData/codebook_data_H3_avg.Rmd
added the results for H5 and H6, including plot 46, which also required the adition of the plot_46_data_rev file, which lead to a rerun of the final data creation code.
Opened up the Many Labs retrieved data for the project.
starting to restructure the article based on feedback. Start on adding meta-analysis component to H2
changed plot456 and plot46, and first stages of restructuring results.

@@
 ---
-title: "Codebook created on 2023-11-09 at 2023-11-09 13:46:45.103283"
+title: "Codebook created on 2024-02-26 at 2024-02-26 14:50:10.406518"
 output: github_document
@@
 ## Dataset description
-The data contains 18 cases and 3 variables.
+The data contains 19 cases and 9 variables.
 

### 2024-02-28 Data/AnalysisData/codebook_data_H3_multiple.Rmd
added the results for H5 and H6, including plot 46, which also required the adition of the plot_46_data_rev file, which lead to a rerun of the final data creation code.
Opened up the Many Labs retrieved data for the project.
starting to restructure the article based on feedback. Start on adding meta-analysis component to H2
changed plot456 and plot46, and first stages of restructuring results.

@@
 ---
-title: "Codebook created on 2023-11-09 at 2023-11-09 13:46:43.923892"
+title: "Codebook created on 2024-02-26 at 2024-02-26 14:50:09.116352"
 output: github_document
@@
 ## Dataset description
-The data contains 713 cases and 4 variables.
+The data contains 670 cases and 10 variables.
 

### 2024-02-28 Data/AnalysisData/codebook_plot_23_data_alpha.Rmd
failed attempt to include R results as numbers in text.
added the replicability and reliability test table.
added the results for H5 and H6, including plot 46, which also required the adition of the plot_46_data_rev file, which lead to a rerun of the final data creation code.
Opened up the Many Labs retrieved data for the project.
changed plot456 and plot46, and first stages of restructuring results.

@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:58.540839"
+title: "Codebook created on 2024-02-26 at 2024-02-26 14:50:12.063393"
 output: github_document
@@
 ## Dataset description
-The data contains 658 cases and 5 variables.
+The data contains 669 cases and 11 variables.
 

### 2024-02-28 Data/AnalysisData/codebook_plot_23_data_omega.Rmd
failed attempt to include R results as numbers in text.
added the replicability and reliability test table.
added the results for H5 and H6, including plot 46, which also required the adition of the plot_46_data_rev file, which lead to a rerun of the final data creation code.
Opened up the Many Labs retrieved data for the project.
starting to restructure the article based on feedback. Start on adding meta-analysis component to H2
changed plot456 and plot46, and first stages of restructuring results.

@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 11:59:02.156609"
+title: "Codebook created on 2024-02-26 at 2024-02-26 14:50:13.488761"
 output: github_document
@@
 ## Dataset description
-The data contains 558 cases and 5 variables.
+The data contains 515 cases and 11 variables.
 

### 2024-02-28 Data/AnalysisData/codebook_plot_23_data_reported_alpha.Rmd
changed plot456 and plot46, and first stages of restructuring results.

@@
 ---
-title: "Codebook created on 2024-02-14 at 2024-02-14 09:47:30.71879"
+title: "Codebook created on 2024-02-26 at 2024-02-26 16:01:29.661356"
 output: github_document
@@
 ## Dataset description
-The data contains 9 cases and 4 variables.
+The data contains 9 cases and 7 variables.
 

### 2024-02-28 Data/AnalysisData/codebook_plot_456_data.Rmd
failed attempt to include R results as numbers in text.
added the replicability and reliability test table.
added the results for H5 and H6, including plot 46, which also required the adition of the plot_46_data_rev file, which lead to a rerun of the final data creation code.
Opened up the Many Labs retrieved data for the project.
starting to restructure the article based on feedback. Start on adding meta-analysis component to H2
changed plot456 and plot46, and first stages of restructuring results.

@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:44.141596"
+title: "Codebook created on 2024-02-27 at 2024-02-27 16:22:04.046895"
 output: github_document
@@
 ## Dataset description
-The data contains 924 cases and 3 variables.
+The data contains 924 cases and 4 variables.
 

### 2024-02-28 Scripts/Manuscript/manuscript.Rmd
added endpoint_check, failed to add replicate check.
changed plot456 and plot46, and first stages of restructuring results.

@@
 knit              : worcs::cite_all
+bibliography: references.bib
 ---
@@
 library(gridExtra)
+library(metafor)
 
 # loading source script
-source(file = "../source_script.R")
+source(file = "C:/Users/u686785/OneDrive - Tilburg University/Documents/uvt/PHD/Master Thesis to Paper/Reproducible_R_Project/Scripts/source_script.R")
 
@@
 Consequently, much of the discourse and the subsequent proposed solutions have been centred around preventing these QRPs through increased transparency in scientific reporting.
-Preregistrations are one method for preventing QRPs.
-Preregistrations provide a clear description of the originally planned methodology of a study, which remains publicly available alongside the final report of the study.
-As a result, the author's original expectations and intentions can be accessed by the reader [@nosek2022replicability].
 
@@
 In order for indirect assessment of psychological constructs to be a viable approach, the measure needs to have construct validity [@cook2002experimental].
-However, both original and replication research are often not reported with sufficient details on construct validity [@shaw2020measurement; @flake2022construct].
 The second issue relates to the concept of measurement error and reliability.
 Measurement error indicates the amount of variation in item scores that is the result of the used measures inaccuracies, and not due to differences in the underlying psychological construct of interest.
-While what should be considered acceptable levels of measurement error is a subject of debate, and dependent upon context [@cho2015cronbach], it is generally agreed upon that too much measurement error is problematic.
-If measurement error is too large, the item scores relate to a construct no more than they do to random noise.
-As a result, the interpretability of these scores as indicators of a psychological construct is limited.
-
-@stanley2014expectations demonstrated, using a simulation study, the drastic effect measurement error can have on attempts to verify or falsify original findings.
-In practice, measurement error is commonly indicated using score-reliability.
-Score-reliability is an index of consistency of a measure, showing how much the items converge to the same point, with the point being the measured variable.
-Thus, @stanley2014expectations generated scalar item data with levels of score-reliability that mimicked what is standard in psychological research, to ensure that the resulting degree of measurement error was representative.
-Using this data, they found that the degree of measurement error can explain a large amount of the variation in observed effects found in replication research.
-It could therefore be that a failed replication was simply the result of measurement of the true effect varying from the original, rather than the true effect itself being different from what was originally reported.
-As a result, interpretations of replications might not be based on tests of the true effect, if the impact of measurement error is not attenuated for.
+
+@stanley2014expectations demonstrated, using a simulation study, the impact measurement error has on attempts to verify or falsify findings.
+Scalar item data was generated based on levels of sampling error and score-reliability, as the inverse of measurement error, that mimicked what is standard in psychological research, to ensure that the resulting degree of error was representative.
+The results indicated that measurement error caused observed effects found in replication research to vary heavily.
+???relation measurement error and replicability (As a result, interpretations of replications might not be based on tests of the true effect, if the impact of measurement error is not attenuated for.)???
 
@@
 They range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of measure and procedure of any sourced measures [@flake2020measurement].
-@flake2022construct coded the presence of a series of QMPs in the replication report in both the replication protocols of each replication in the RPP, as well as the original articles the replications were based on.
-They found that QMPs linked to issues for replicators in recreating the measurement to closely match the measurement in the original.
-As a result, there was a lack of measurement related information in both replication reports, and original articles.
-Without this information, it becomes difficult to establish that original and replication are measuring the same construct(s), which has detrimental consequences for direct replication attempts.
+When this information is missing, it becomes difficult to establish that original and replication are measuring the same construct(s), which has detrimental consequences for direct replication attempts.
 
@@
 
-As a first step it is worth investigating what the state of measurement error is in original and psychological research, in order to assess the scope of @stanley2014expectations's findings in practice.
+???connection/throughline of the measurement error hypotheses and other (including measurement error) hypotheses –\> is there a way to rewrite this part of the article to fit better as support/precedence to the QMP stuff????
+–\> risky use of measurement!?!
+
+As a first step it is worth investigating what the state of measurement error is in original and replication research in psychology, in order to assess the scope of @stanley2014expectations's findings in practice.
 Thus, this study investigated the following:
@@
 
-It is difficult to suggest an expected or informed cut-off value for what could be considered a sufficient score reliability coefficient for both original and replication studies.
-While suggested cut-off points for reliability do exist [@nunnaly1994assessment], they are not without their criticism [@cho2015cronbach; @crutzen2017scale].
-Instead a comparison of scores between original and their associated replication studies should be of more substantive interest.
 Since direct replications intend to investigate effects in nearly identical scenarios with nearly identical measures as the original study, it is expected that measurement errors are as present in replication research as in original psychological research.
@@
 With large enough differences across contexts, the effect estimates between different replication attempts could deviate from each other beyond direct comparison.
-For instance, suppose that we have a measure of multiple items assessing agreeableness in relation to both parents as well as peers.
-In a non-traditional society we might find high reliability for this measure, because participants that score high on one item, score high on another item since they are generally agreeable, while participants that score low one item, score low for all the other items.
-On the other hand, in a more traditional society we might find that reliability is low, because agreeableness towards parents is normative in that society, and as a result items relating to agreeableness towards parents may not be indicative of general agreeableness as a personality trait.
-In this example, a high score on the measure in the first context relates more strongly to a single agreeableness construct compared to the second context.
-The findings across these two populations would then no longer be directly comparable.
-Consequently, the value of any direct replication would become limited.
+???RELIABILITY VARIANCE IN META ANALYSIS???.
 To investigate this potential problem, the variation in score reliability is assessed for each measure when used in different contexts.
@@
 This concern even prompted a Many Labs centred around the testing of heterogeneity in replications [@klein2018many].
-However analyses from Many Labs 2, and @olsson2020heterogeneity showed little empirical evidence for widespread heterogeneity in effects amongst replications.
+However analyses from Many Labs 2, and @olsson2020heterogeneity showed little empirical evidence for widespread heterogeneity in effects among replications.
 These findings demonstrate that it is possible to reduce variability as the result of context using structured protocols, as was done in the Many Labs projects this study analyzed.
@@
 -   H3. Score reliability in replication research is positively associated with successful replication of an original finding.
-
-Reliability is only one aspect by which a measure can be judged, with validity being another important way to determine the scientific rigour of a measure [@roberts2006reliability].
-Therefore as part of the exploratory analyses, validity was assessed for the same data source used to test the aforementioned hypotheses.
-Specifically, the unidimensionality of the measure was determined, meaning whether or not the items of a measure all related to a single variable.
 
@@
 
-@flake2022construct descriptively investigated QMPs within the reproducibility project psychology [@osc2015estimating].
-This study seeks to conceptually replicate some of their findings within the Many Labs replication projects.
+This study seeks to conceptually replicate some of the findings of @flake2022construct about QMP reporting in the RPP within the Many Labs replication projects.
 
@@
 
-The investigations by @flake2022construct have shown not only that QMPs are common in psychological research, they can be even more common in replications reports.
+@flake2022construct coded the presence of a series of QMPs in the replication report in both the replication protocols of each replication in the RPP, as well as the original articles the replications were based on.
+They found that not only are QMPs common in psychological research, they can be even more common in replications reports.
 However, the reporting of the Many Labs projects differ from the RPP data used in @flake2022construct.
@@
 
-QMPs put the validity of a study into question.
-If there is a lack of transparency and the used measures are invalid, replication results become difficult to interpret [@flake2020measurement].
-With a lack of transparency, closely mimicking the original's measurement becomes challenging.
-Furthermore, if a replication does not properly measure the variables of the original effect, the effect analysed within the replication may not be the same as the original.
+QMPs may obscure relevant information needed to evaluate the use of measurement in a study.
+If the replication used the measure differently from the original, the replication may no longer be a direct replication.
+???link not direct replication to lack of replication through larger variance argument???
 For these reasons, establishing a link between QMPs and non-replicability should confirm suspicions of their detrimental effects on replications [@flake2017construct; @flake2020measurement; @flake2022construct].
@@
 
-@flake2022construct have already demonstrated the issues replicators face in transparently reporting the appropriate evidence for the measures they used.
-That study identified among other issues, a lack of available information in original articles.
-If essential information on a measure is not available in an original article, it may be difficult to know the specifics of that measure when used in a replication.
-In that case, the lack of proper reporting on measurement would impact the transparency and validity of future replications.
-Consequently, the article's findings become difficult to verify.
-To provide insight into this issue, an investigation of the relationship between original and replication QMPs was included.
+This study additionally aims to see if the relation between QMPs and replicability can be traced back to original article QMPs.
+When essential information on a measure is not available in an original article, it may be difficult to know the specifics of that measure to report for a replication.
+Therefore this study also investigates the relation between original QMPs and replication QMPs.
 
@@
 If the relationship exists, it is expected that questionable measurement practices in an original paper might cause a spill-over effect of QMPs into the replication.
-If the original paper does not specify how a measure was used, the replication may implement it differently.
-In that case, the replication can no longer be considered a direct replication.
+@flake2022construct found that QMPs linked to issues for replicators in recreating the measurement to closely match the measurement in the original.
+As a result, there was a lack of measurement related information in both replication reports, and original articles.
 Additionally, investigations by @shaw2020measurement have shown that more validity evidence in an original article is associated with better psychometric properties in the replication sample.
-Based on these arguments, hypotheses are expected to be associated across original and replication studies.
+Based on these arguments, QMPs are expected to be associated across original and replication studies.
 
@@
 Data from Many Labs 4 [@klein2022many] was not part of the sample, as there was no publicly available protocol which contains the information needed to code QMPs.
-Additionally, the replication of [@crosby2008we] in Many Labs 5 did not contain contain data suitable for this project.
-The replication made use of videos and eye-tracking as measures, which does not match this study's focus on scale and item measures.
-
-The total number of psychological findings for which replication was attempted across the four included Many Labs projects amounts to a total of 60: 13 in Many Labs 1; 28 in Many Labs 2; 10 in Many Labs 3; & finally 9 out of the 10 tested findings in Many Labs 5.
-Since each replication set is related to an original study, the number of effects in original studies matches the number of effects in replication research.
-
-However, the unit of measurement was not a single study or replication.
-Instead each measure of a unique variable within a Many Labs project was treated as the unit of measurement.
-The reason being that studies could have and did use multiple measures.
-Additionally, measures can assess multiple dimensions.
-These dimensions, meaning unique variables, were separated into different units whenever possible, otherwise the measure was discarded from analysis.
-However, not all measures of unique variables were used.
-Only data from measures of primary variables, meaning those variables included in the primary test of the replication, were used.
+Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking as measures, which did not match this study's focus on scale and item measures.
+
+The total number of psychological findings for which replication was attempted across the four included Many Labs projects amounts to a total of 60.
+Each finding was tested across several labs, and was related to a finding from an original study, the combination of all these studies and their associated information formed a replication set.
+For each research finding, any primary measures assessing a unique variable were taken to form the final unit of measurement.
+Here primary measures refers to measures assessing variables included in the primary test of the replication, were used.
 This was done to ensure that the analyses could link directly to the replicability of a study.
-Acquiescence bias checks, manipulation checks, measures used for pilot testing, and measures added for exploratory analyses in replication studies were not included.
-The result was a total sample size of 77 measures: 14 in Many Labs 1; 35 in Many Labs 2; 15 in Many Labs 3; & 13 in Many Labs 5.
-Again, the sample was equivalent between replications and original studies.
+Acquiescence bias checks, manipulation checks, measures used for pilot testing, and measures added for exploratory analyses in replication studies were not included..
+The result was a total sample size of 77 measures.
+The Table BELOW show descriptive information about the data for each Many Labs Project.
+
+DESCRIPTIVE TABLE
+
+(Row 1: Many Labs projects - 13 in Many Labs 1; 28 in Many Labs 2; 10 in Many Labs 3; & finally 9 out of the 10 tested findings in Many Labs 5)
+
+(Row 2: Primary measures - 14 in Many Labs 1; 35 in Many Labs 2; 15 in Many Labs 3; & 13 in Many Labs 5)
+
+(Row 3: ???)
+
+Footnote about sample size differences between original and original shortened.
+
+## Data Collection
+
+The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>.
+Both the replication protocols and replication datasets were scanned through to ensure that the planned analyses were feasible.
+However, no coding or analysis of either of them had taken place before the analyses were preregistered.
+When available, codebooks and study materials were used to identify the specific data for each measure.
 
@@
 The replication datasets refer to the data of each of the replication attempts for each of the original psychological effects undertaken as part of a Many Labs study.
-The specific data was extracted from the replication datasets for each relevant measure.
-The measure had to consist of multiple scalar items to be considered relevant for the related analyses.
-Single item measures were not usable for the analyses on score reliability [@wanous1996estimating] as they do not translate directly to the findings of @stanley2014expectations, which this study is following up on.
-
-For Many Labs 1, all the relevant replication data was available in a single csv file.
-For Many Labs 2 & 3 the situation was similar, only here the files were split across two csv files for each project.
-For Many Labs 5, the data was made available for each of the ten replication sets separately.
-Three out of the ten datasets were furthermore split across the various locations at which they were taken.
-If cleaned data was available this was chosen over raw data.
+These publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base] Using the replication protocols, codebooks, and analysis scripts from each replication set as a guide, the variables associated with each relevant measure were extracted into their own data frame containing the data from all studies in one replication set.
+These pieces of information were used as the datasets in the analysis.
+
+The measure had to consist of multiple scalar items to be considered relevant, as single item measures were not usable for the planned analyses on score reliability [@wanous1996estimating], which followed up on @stanley2014expectations simulation study.
+If cleaned data was available this was chosen over raw data, to ensure that variables were coded as intended.
 Pilot data were omitted from the analyses entirely.
-This resulted in suitable measure data from eighteen replication sets spread across on average 40 lab locations for the analyses of hypotheses 2 & 3.
+These criterion resulted in suitable measure data from eighteen replication sets spread across on average 40 lab locations for the analyses of hypotheses 2 & 3.
+
+DESCRIPTIVE TABLE???
 
@@
 # 2.20
-data_2.20_clean <- cbind(as.factor(data_2.20[[5]]), data_2.20[6:45] - 1) 
+data_2.20_clean <- cbind(as.factor(data_2.20[[5]]), data_2.20[6:45]) 
 data_2.20_clean[3729:7396,2:21] <- data_2.20_clean[3729:7396,22:41]
 data_2.20_clean <- data_2.20_clean[1:21] 
+# coding so all 1's means somebody used rule-based grouping strategy
+data_2.20_clean[,c(2, 4, 6, 8, 10, 12, 14, 16, 18, 20)] <- ifelse(data_2.20_clean[,c(2, 4, 6, 8, 10, 12, 14, 16, 18, 20)] == 1, 1, 0)
+data_2.20_clean[,c(3, 5, 7, 9, 11, 13, 15, 17, 19, 21)] <- ifelse(data_2.20_clean[,c(3, 5, 7, 9, 11, 13, 15, 17, 19, 21)] == 2, 1, 0)
 colnames(data_2.20_clean)[1] <- "g"
@@
 # 5.1.1
-data_5.1.1_clean <- cbind(as.factor(data_5.1[[2]]), data_5.1[13:33])
+data_5.1.1_clean <- cbind(as.factor(data_5.1[[2]]), data_5.1[13:27])
 colnames(data_5.1.1_clean)[1] <- "g"
 # 5.1.2
-# difficult to separate .1 from .2
+data_5.1.2_clean <- cbind(as.factor(data_5.1[[2]]), data_5.1[28:33])
+colnames(data_5.1.2_clean)[1] <- "g"
 # 5.4
@@
 
+open_data(data = data_5.1.2_clean, filename = paste0(paste0(
+  "Data/IntermediateData/", deparse(substitute(data_5.1.2_clean))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/IntermediateData/codebook_", 
+    deparse(substitute(data_5.1.2_clean))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/IntermediateData/value_labels_", 
+    deparse(substitute(data_5.1.2_clean))), ".yml"))
+
 open_data(data = data_5.4_clean, filename = paste0(paste0(
@@
 These protocols were available through the OSF pages of each Many Labs project.
-These preregistered replication protocols, as well as the replication datasets mentioned earlier were scanned through to ensure that the planned analyses were feasible.
-However, no coding or analysis of either of them had taken place before the analyses were preregistered.
-This includes any systematic coding of the QMPs present in the report.
-Furthermore, no overview of these and the qualitative topics were available at the time of preregistration.
+
+The OSF page for each Many Labs project was combed through, in order to identify the components of the research which contained information on the measurement practice and reported reliability.
+The focus was on finding the preregistered protocols which contained information on the entirety of the replication sets in each Many Labs project.
+For Many Labs 2, & 3 a common protocol could be identified, for Many Labs 1 the Proposal_V1.1 provided the equivalent information, while for Many Labs 5 protocols were available for each replication set separately.
+
+MAKE ALL FOOTNOTE?: (in reference to ML 5 mostly) The relevant OSF page of each replication set was searched through for a file which contained protocol in its name.
+If available, a version of the protocol labelled as revised, post-review, peer-review, or endorsed was selected.
+In case there was doubt about which was most appropriate, the latest uploaded relevant protocol was selected.
+Only regular protocols were taken, meaning those not labelled as data collection, analysis protocol or anything similar[^1].
+
+[^1]: The steps taken to access the replication protocol data from Many Labs 5 were not preregistered, and only became clear upon further investigation of the accessible information.
+The specific names and locations of the files that were used as the datasets can be found under the supplementary materials of the OSF page of this article <https://osf.io/gft46/%7D>
 
@@
 The original study articles are the published articles of the original effect on which the Many Labs replication sets were based.
-In the case of Many Labs 5 the original studies refer to the studies which first tested the effect to be replicated, not the earlier replication attempts of the same effects in the RPP [@osc2015estimating].
+In the case of Many Labs 5 [@ebersole2020] the original studies refer to the studies which first tested the effect to be replicated, not the earlier replication attempts of the same effects in the RPP [@osc2015estimating].
+
+FOOTNOTE:The original articles were identified through the citations in each replication protocol, using Web of Science, Google Scholar, and PsychInfo (in that order).
+An issue was encountered while trying to access @hyman1950current.
+However, after contacting the first author of @klein2014investigating a suitable version of the article was obtained for use in the analyses.
 
@@
 
-## Data Collection
-
-The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>.
-When available, codebooks and study materials were used to identify the specific data for each measure.
-
-The publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base] Using the replication protocols, codebooks, and analysis scripts from each replication set as a guide, the variables associated with each measure were extracted into their own data frame containing the data from all studies in one replication set.
-These pieces of information formed the replication datasets in the analysis.
-
-The OSF page for each Many Labs project was combed through, in order to identify the components of the research which contained information on the measurement practice and reported reliability.
-The focus was on finding the preregistered protocols which contained information on the entirety of the replication sets in each Many Labs project.
-This was successful for Many Labs 2, & 3.
-For Many Labs 1 the Proposal_V1.1 was selected as the proper candidate for the QMP analysis.
-Despite the difference in name, it is the equivalent in Many Labs 1 to the protocols of Many Labs 2 & 3.
-For Many Labs 5 the protocols were made accessible for each replication set separately.
-The relevant OSF page of each replication set was searched through for a file which contained protocol in its name.
-If available, a version of the protocol labelled as revised, post-review, peer-review, or endorsed was selected.
-In case there was doubt about which was most appropriate, the latest uploaded relevant protocol was selected.
-Only regular protocols were taken, meaning those not labelled as data collection, analysis protocol or anything similar[^1].
-
-[^1]: The steps taken to access the replication protocol data from Many Labs 5 were not preregistered, and only became clear upon further investigation of the accessible information.
-The specific names and locations of the files that were used as the datasets can be found under the supplementary materials of the OSF page of this article <https://osf.io/gft46/%7D>
-
-The original articles were identified through the citations in each replication protocol, using Web of Science, Google Scholar, and PsychInfo (in that order).
-An issue was encountered while trying to access @hyman1950current.
-However, after contacting the first author of @klein2014investigating a suitable version of the article was obtained for use in the analyses.
-
 The measures of primary variables were identified by combing through the entire methods section of each preregistered replication protocols.
-Then using the structured coding protocol (made using Qualtrics) that is available on the OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages of this study, each measure of a unique variable was coded on measurement reporting and reported reliability.
-
-The structured coding protocol was used for both replication protocols and original studies.
-A series of questions relating to measurement practices and measurement error were used to extract the information.
+Then using questions and the accompanying search strategies as documented in the structured coding protocol of this study (available on the relevant OSF: <https://osf.io/9r8yt/>, and github pages: <https://github.com/CasGoos/measurement_and_replication.git>), information on the reported measurement evidence and reporting quality was assessed for both replication protocols and original studies.
 Descriptions of the extracted variables can be found in the [Measures](#Measures) section below.
-The scope of the coding was limited to the abstract, method, procedure, materials, measure, and initial parts of the results sections.
+Exact descriptions of the search strategy can be found in Appendix ???.
+
+MOVE TO APPENDIX/COMBINE WITH EXTERNAL SEARCH STRATEGY FILE: The scope of the coding was limited to the abstract, method, procedure, materials, measure, and initial parts of the results sections.
 Additionally, a keyword search using the name of the measured variable was used to search for any potentially missed information.
@@
 After the data was initially coded according to the preregistered coding protocol, it was determined, based on discussion with the supervisor, that some of the initial ratings were possibly to stringent.
-As a result, some of the items in the protocol were reformulated, so that the conclusions from the resulting analyses were based on a more favourable judgement of QMPs.
-These changes included: accepting linked online appendices as a data source for example items; assuming that if no differences between replication and original are measurement is mentioned, that there is no difference, even if it is not explicitly clear; and generally simplified criteria for what constituted sufficiently clear reporting.
+As a result, some of the items in the protocol were reformulated, so that the conclusions from the resulting analyses were based on a more lenient judgement of QMPs.
 The revision of the coding protocol happened after all the data were coded using the initial protocol.
 As a result the coded data using the initial protocol, and the coded data using the revised protocol are both available available on this article's OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages.
-Both raw and processed formats are present.
+
+MOVE TO APPENDIX/COMBINE WITH EXTERNAL SEARCH STRATEGY FILE: These changes included: accepting linked online appendices as a data source for example items; assuming that if no differences between replication and original are measurement is mentioned, that there is no difference, even if it is not explicitly clear; and generally simplified criteria for what constituted sufficiently clear reporting.
 
@@
 
-Two main sources of information were used to test hypothesis 1, the reported reliability coefficient from the replication protocols, and the reported reliability coefficient in the original articles.
+In order to answer questions regarding reported reliability, the reported reliability coefficient were extracted from both the replication protocols and the original articles.
 The reported reliability coefficient is the score reliability reported per measure in the replication protocol or original article.
@@
 
-The test of hypothesis 2 was based on different score reliabilities.
-As stated earlier, only score reliabilities of scalar measures with multiple items were included in the test of hypothesis 2.
-Because data was available for each lab location within a replication set, it was possible to calculate score reliabilities of a measure for each lab location.
-With location specific score reliabilities, it was possible to assess the variation of score reliabilities of the same measure across different contexts.
-
-Two different types of score reliabilities were calculated: Cronbach's alpha and omega.
-Cronbach's alpha was used as it is one of the most popular indices of score reliability [@cho2015cronbach].
-Omega was added to the analysis as it has been argued to be a more informative measure of score reliability, while also providing validity evidence for the scale [@crutzen2017scale; @deng2017testing].
+Because data from the Many Labs replications was available for each lab location within a replication set, it was possible to not only calculate score reliabilities for the scalar measures used, but also calculate it for each lab location separately.
+This made it possible to assess the variation of score reliabilities of the same measure across different contexts.
+
+Cronbach's alpha was calculated as the main score reliability index used in the analyses as it is one of the most popular [@cho2015cronbach].
+Hpowever, in the supplementary materials ???, Omega was added to the analysis as it has been argued to be a more informative measure of score reliability, while also providing validity evidence for the scale [@crutzen2017scale; @deng2017testing].
 Cronbach's alpha and omega were calculated using the alpha and omega functions respectively in the psych R package [@R-psych].
@@
 
-### Replicability Measure
-
-Hypothesis 3 as well as 5 specify an association between either score reliability or QMPs respectively, and replication success.
-Replication success was based on the test of the main effect of a study.
-However, the unit of measurement for the data in this study was a measure of a unique variable, not an effect.
-Fortunately, since only primary measures were included in the data, each measured a variable of the main effect, and as a result the measure remains related to the test of the main effect.
-Replication was based on the significance of the meta-analytic effect of the replication set as reported in its respective Many Labs report.
-An effect was considered replicated if the meta-analytic p-value was lower than .05, and in the same direction as the original effect.
-In all cases, meta-analytic significance of an effect meant that support in the direction of the original effect was found.
-
-The tests for hypotheses 4, 5, & 6 were all based on the number of QMPs per category that were determined by the research using the coding protocol.
-An overview of the QMP categories of the coding variables, based on @flake2020measurement, can be seen in Table \@ref(tab:QMPCodingInfoTable)
+```{r ReliabilityValidityTestabilityCheck, include = FALSE, warning = FALSE}
+## Checking the measures to recalculate the reliability and factor analysis for.
+## The question: "Are they psychometrics scales or not?", is key here.
+View(coded_data_replications)
+
+# Likely reliability: 1.10, 1.11, 1.12.3, 2.4.1, 2.4.2, 2.8.2, 2.10.1, 2.12.1, 
+# 2.12.2, 2.12.3, 2.15, 2.19.2, 2.23, 3.7.1, 3.7.2, 3.8.1, 3.8.2, 5.7, 5.9.1
+# Likely factor: 1.10, 1.11, 1.12.3, 2.4.1, 2.4.2, 2.8.2, 2.10.1, 2.12.1, 2.12.2,
+# 2,12,3, 2.15, 2.19.2, 2.23, 3.7.1, 3.7.2, 3.8.1, 3.8.2, 5.7, 5.9.1
+# Maybe reliability: 1.3, 1.12.1, 2.2, 2.3, 2.19.1, 2.20, 3.2.1, 3.5, 5.1.1, 
+# 5.1.2, 5.4, 5.5.1, 5.5.2
+# Maybe factor: 1.3, 1.12.1, 2.3, 2.19.1, 2.20, 3.2.1, 3.5, 5.1.1, 5.1.2, 5.4,
+# 5.5.1, 5.5.2
+
+# 1.9 is difficult, might be a scale as dv rather than voting behavior.
+```
+
+### QMP measures
+
+The tests for hypotheses 4, 5, & 6 were all based on the number of QMPs coded across both original articles and replication protocols.
+QMPs were all coded to be either true, false, or not applicable.
+Questions related to modification had 'no modification' as an additional answer option, in case the specific aspect of the measure was explicitly not modified.
+Each coded QMP belonged to one of five QMP type categories that were derived from the classification in @flake2020measurement.
+An overview of the QMP categories of the coding variables can be seen in Table \@ref(tab:QMPCodingInfoTable)
 
@@
 Selection and creation share a category as the justifications and requirements in selecting a measure are similar to those for creating a new measure.
-Modification variables were only assessed when it was clear that the measure was modified from an original source in some way.
-The questions were all answered as either true, false, or not applicable.
-Questions related to modification had 'no modification' as an additional answer option, in case the specific aspect of the measure was explicitly not modified.
-Beside these quantitative variables, a total of four qualitative variables were also included to measure details surrounding measurement practices.
-These variables assessed: the specific version of the measure (if reported); whether and what previous materials were used for the study; what, if any, psychometric evidence beyond reliability score (e.g.
+Modification variables were only assessed when it was clear that the measure was modified from an original source in some way, and were otherwise omitted from the QMP calculations for that measure.
+
+For the analyses of these variables both the total QMP ratios and ratios per QMP type category were used.
+This ratio was based on the number of coded trues divided by the total number of applicable QMPs.
+QMPs were considered applicable if not coded as not applicable or no modification.
+These ratios were preferred over counts, since non applicable items could thus be accounted for.
+Formula \@ref(eq:QMPRatioType) shows the formula that was used to calculate the QMP ratio for a particular QMP type j, where True is 1 if that item was coded as True and 0 otherwise, and False is 1 if that item was coded as False and 0 otherwise, $j \subset \{ definition, operationalisation, selection/creation, quanitification, modification \}$, and $i = 1,..., n_{j-items}$.
+
+FORMULA of QMP ratio:
+
+```{=tex}
+\begin{equation}
+QMP_ratio_{j} = \frac{\sum_{n=1}^i True_{ij}}{\sum_{n=1}^i True_{ij} + False_{ij}} (\#eq:QMPRatioType)
+\end{equation}
+```
+For the total QMP ratio:
+
+```{=tex}
+\begin{equation}
+QMP_ratio = \frac{\sum_{n=1}^j \sum_{n=1}^i True_{ij}}{\sum_{n=1}^j \sum_{n=1}^i True_{ij} + False_{ij}} (\#eq:QMPRatioTotal)
+\end{equation}
+```
+Eleven out of twenty of the QMP variables used to calculate the QMP ratio have an equivalent in the coding key of @flake2022construct.
+The remaining nine were either altered from the coding key to better fit the QMP counting operationalization, all newly created or modified items were based on the definitions of the QMP categories and their criteria as specified in @flake2020measurement.
+Beside these quantitative variables, a total of four qualitative variables were also included to provide more detailed information on some aspects of the measure and its reporting.
+Details on the items used, their origin and justifications can be seen in Appendix ???.
+
+APPENDIX: on item revision and origin
+
+Two of the qualitative items have an equivalent in the coding key of Variables related to the specific measurement scaling and purpose in the paper, were omitted from the analyses of this study as they were deemed neither relevant for the analyses of this study, nor necessary in matching this study to the key results of @flake2022construct.
+Questions about more general measurement features such as the number of items and how scores were aggregated were altered from @flake2022construct to better fit the use of QMP ratios and associations between them and other coded aspects.
+
+These (qualitative) variables assessed with two having an equivalent in @flake2022construct: the specific version of the measure (if reported); whether and what previous materials were used for the study; what, if any, psychometric evidence beyond reliability score (e.g.
 factor analysis, IRT model, convergent validity) was provided; and whether it was specified or not that the measure was or was not modified.
 
-Two of the qualitative items have an equivalent in the coding key of @flake2022construct.
-Eleven out of twenty of the quantitative coding variables have an equivalent in @flake2022construct.
-Variables related to the specific measurement scaling and purpose in the paper, were omitted from the analyses of this study as they were deemed neither relevant for the analyses of this study, nor necessary in matching this study to the key results of @flake2022construct.
-Questions about more general measurement features such as the number of items and how scores were aggregated were altered from @flake2022construct to better fit the aims of this study.
-
-The tests for hypotheses 4, 5, & 6 were all based on QMP ratios, both total QMP ratios and ratios per QMP type.
-This ratio was based on the number of coded trues divided by the number of applicable QMPs.
-When a question was coded as true, this equated to a count of one QMP for that type and in total, whereas false equated to a zero.
-If coded as not applicable or no modification (for the modification items), this item was considered not applicable.
-Non applicable responses were not only counted as a zero, but additionally the denominator for calculating the ratio of QMPs was lowered by one.
-These ratios were preferred over counts, since non applicable items could thus be accounted for.
-
-### QMP measures
-
-The same data as for the test of hypothesis 2 was used to check for the unidimensionality of the factor structure, as part of the exploratory analyses.
-A check for unidimensionality as validity evidence only makes sense if the measure was intended to be unidimensional.
-Therefore, for each replication for which data was available, the protocol was checked to ensure that the scores on each measure were meant to assess a single construct.
-
-### Validity Measure
-
-The same data as for the test of hypothesis 2 was used to check for the unidimensionality of the factor structure, as part of the exploratory analyses.
-A check for unidimensionality as validity evidence only makes sense if the measure was intended to be unidimensional.
-Therefore, for each replication for which data was available, the protocol was checked to ensure that the scores on each measure were meant to assess a single construct.
-
-```{r ReliabilityValidityTestabilityCheck, include = FALSE, warning = FALSE}
-## Checking the measures to recalculate the reliability and factor analysis for.
-## The question: "Are they psychometrics scales or not?", is key here.
-View(coded_data_replications)
-
-# Likely reliability: 1.10, 1.11, 1.12.3, 2.4.1, 2.4.2, 2.8.2, 2.10.1, 2.12.1, 
-# 2.12.2, 2.12.3, 2.15, 2.19.2, 2.23, 3.7.1, 3.7.2, 3.8.1, 3.8.2, 5.7, 5.9.1
-# Likely factor: 1.10, 1.11, 1.12.3, 2.4.1, 2.4.2, 2.8.2, 2.10.1, 2.12.1, 2.12.2,
-# 2,12,3, 2.15, 2.19.2, 2.23, 3.7.1, 3.7.2, 3.8.1, 3.8.2, 5.7, 5.9.1
-# Maybe reliability: 1.3, 1.12.1, 2.2, 2.3, 2.19.1, 2.20, 3.2.1, 3.5, 5.1.1, 
-# 5.1.2, 5.4, 5.5.1, 5.5.2
-# Maybe factor: 1.3, 1.12.1, 2.3, 2.19.1, 2.20, 3.2.1, 3.5, 5.1.1, 5.1.2, 5.4,
-# 5.5.1, 5.5.2
-
-# 1.9 is difficult, might be a scale as dv rather than voting behavior.
-```
+### Replicability Measure
+
+Hypothesis 3 as well as 5 specify an association between either score reliability or QMPs respectively, and replication success.
+Replication success was based on the test of the main effect of a study.
+Since only primary measures were used to form the dataset, each measure related to the test of a main effect.
+Replication success was determined based on the significance of the meta-analytic effect of the replication set as reported in its respective Many Labs report.
+An effect was considered replicated if the meta-analytic p-value was lower than .05, and in the same direction as the original effect.
+In all cases, meta-analytic significance of an effect meant that support in the direction of the original effect was found.
 
 ## Analyses
+
+Every hypothesis test in this study used an alpha significance cutoff of .05.
+No correction for multiple testing was applied, to ensure that the rate of false negatives remained low, the increase in false positive rate was accepted as they deemed less harmful to the exploratory aims of this study.
+This exploratory focus combined with the generally small sample size and consequently low power of the analyses in this article means that descriptives will be used to facilitate the interpretation of the results.
 
@@
 # for hypothesis 2
-data_h2 <- data_prep_H2(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, 
-  data_1.12.3.2_clean, data_2.10.1_clean, data_2.12.1_clean, data_2.12.2_clean, 
-  data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, 
-  data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.2_clean, data_3.8.2_clean, 
-  data_5.1.1_clean, data_5.7_clean, data_5.9.1_clean)
+data_h2 <- data_prep_H2(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, data_1.12.3.2_clean, data_2.12.1_clean, data_2.12.2_clean, data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.1_clean, data_3.7.2_clean, data_3.8.2_clean, data_5.1.1_clean, data_5.1.2_clean, data_5.7_clean, data_5.9.1_clean)
 # for hypothesis 3
@@
 plot_23_data_omega <- data_prep_plot_23_omega(data_h3_multiple)
+plot_23_data_reported_alpha <- data_prep_plot_23_alpha_reported(coded_data_original_shortened, data_h3_avg, data_h3_multiple)
 
@@
 
+open_data(data = plot_23_data_reported_alpha, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(plot_23_data_reported_alpha))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(plot_23_data_reported_alpha))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(plot_23_data_reported_alpha))), ".yml")) 
 ```
@@
 
-Every hypothesis test in this study used an alpha significance cutoff of .05.
-No correction for multiple testing was applied, to avoid inflating type II error rate.
-The generally small sample size and consequently low power of these analyses meant that a smaller alpha would increase the number of false negatives.
-On top of that, these analyses were considered as exploratory.
-In this exploratory context, the rate of discovery of any potential true effects was given more value relative to decreasing any false positives compared to typical confirmatory research.
-That as a consequence obtaining false positives was more likely has been accepted, as false negatives were deemed more harmful to this study's aims.
-
-The measurement error analyses testing hypotheses 1, 2, & 3 deviated from the preregistration for two main reasons: there were too few reported reliability coefficients, and too few multiple item scalar measures to calculate the reliability coefficients from.
-Because of the small sample size, the test for hypothesis 1 was changed, and the low power as a result of the sample size was accepted for hypothesis 2 & 3.
-This should be kept in mind while interpreting the results from these hypothesis tests.
-
-Thus for testing hypothesis 1, instead of comparing the reported Cronbach's alpha coefficient between original and replication, the total number of reported reliability coefficients were compared instead.
-This total also included reliability coefficients other than Cronbach's alpha.
-This comparison was implemented via a chi-square test using the base R stats package [@R-base].
+The original test for hypothesis 1, a t-test of the reported Cronbach's alpha coefficient values between original and replication, could not be conducted, since not enough score reliabilities were reported to conduct the test and expect sensible results.
+Instead, the total number of reported reliability coefficients were compared between the replication protocols and the original articles.
+This comparison was tested via a chi-square test using the base R stats package [@R-base].
 
@@
 
-The number of usable datasets to calculate reliability coefficients from was similarly limited in number.
-However, the number of datasets were still sufficient to be able to estimate the models of the planned analysis for hypothesis 2, albeit with a more exploratory goal than intended.
-
-Using the lmer function from the lme4 package [@R-lme4], a multilevel null model with the Cronbach's alpha or omega coefficient of a replication as dependent was specified, where the random intercept was grouped by replication set.
-The formulas for this model, where $alpha_{ij}$ represents the calculated Cronbach's alpha coefficient of a single study at one lab location with $i = 1,..., n_{locations}$ and $j = 1,...,n_{replications}$ look as follows:
+While reported reliabilities were rare, some reliabilities could still be calculated from the replication datasets.
+On top of that, reliabilities could be calculated for each individual lab per replication set so that the variance of them could be assessed.
+In order to separate between and within variance in reliability, a multilevel random intercept model was specified with replication set as the grouping variable and the Cronbach's alpha or omega value of a replication as dependent using the lmer function from the lme4 package [@R-lme4] t.
+The formulas for this model, where $alpha_{ij}$ represents the calculated Cronbach's alpha coefficient of a single study at one lab location with $i = 1,..., n_{locations}$ and $j = 1,...,n_{replicationsets}$ look as follows:
 
@@
 
-The purpose of this analysis was to investigate variability in calculated reliability coefficients within and between replication sets.
-However, to the author's knowledge no formal test exists as of the writing of this thesis for testing the significance of within group variance after controlling for between group variance.
-Instead the intraclass correlation (ICC) coefficient was calculated an indicator of within vs.
+The main author was not aware of the existence of any formal test as of the writing of the pre-regsitration for testing for within group variance after controlling for between group variance.
+Thus, the intraclass correlation (ICC) coefficient was pre-registered as the indicator of within vs.
 between variability.
@@
 
-In order to test hypothesis 3, the average calculated Cronbach's alpha level within a replication set is used as a predictor of replication success.
-Replication success was either set to 1 if it reached meta analytic significance at an alpha of .05 in the same direction as that found in the original study, or 0 otherwise.
-This test aligns with a logistic regression model.
-With $i = 1,..., n_{replications}$, $p_{replicated}$ being binomially distributed, and $alpha$ referring to the averaged calculated Cronbach's alpha coefficient, the following regression equation was used to model the relation:
+???Other analyses were considered after [meta-analyses in particular]???
+
+One of the key tests was that of hypothesis 3 relating to the association between reliability and replicability that had been indicated by @stanley2014expectations.
+The logistic regression shown in equation \@ref(eq:H3Main) was used to model this association, where $f(.)$ represents the logit link function, $i = 1,..., n_{replications}$, the outcome $replicated$ which was coded as 1 if the meta-analytic effect in the replication set matches the original effect in direction at a significance alpha level of .05, and 0 otherwise, and the predictor $alpha$ referred to the averaged calculated Cronbach's alpha coefficient:
 
@@
 ```
-Where:
-
-```{=tex}
-\begin{equation}
-f(.) = log\frac{p_{replicated}}{1 - p_{replicated}} (\#eq:LogitLink)
-\end{equation}
-```
 ```{r Hypothesis3MainTest, include = FALSE}
@@
 In this data, replication attempts at different lab locations can be seen as nested within a replication set.
-In order to see if this nesting might impact the analyses of hypothesis 3, multilevel logistic regression models were included as sensitivity checks.
-The dependent variable remains replication success at the replication set level, while Cronbach's alpha is no longer averaged across locations.
-The models used were a multilevel logistic random intercept and random slope model.
+In order to see if this nesting might impact the analyses of hypothesis 3, multilevel logistic regression random intercept and random slope model were included as sensitivity checks.
+The dependent variable remains replication success at the replication set level ???(as recommended, but heterogeneity correction)???, while Cronbach's alpha was no longer averaged across locations.
 
@@
 All of these models assume that the QMPs are the same across each replication set.
-The reason being that only one protocol was analysed per replication set, and several of the questions regarding QMPs focus solely on the reporting of relevant measurement information.
-This assumption was deemed likely, since each replication within a set was based on the same protocol.
-Furthermore, the goal of these protocols is to ensure that the measurement practices are equal across the different replication studies of the same original effect.
+This was necessary as only one protocol was available for coding per replication set.
+The assumption was deemed likely to hold, since each replication within a set was based on the same protocol containing all the measurement details that were reported and upon which measurement was based.
 
@@
 Where $replication_{i}$ is a dummy coded variable, which was coded as 1 in case the reported QMP ratio belonged to a replications, and 0 if it belonged to an original study.
-For hypothesis 5 a similar formula was used:
+For hypothesis 5 a similar formula was used [[[change to logistic regression, with footnote that pre-reg was inverted]]]:
 
@@
 ```
-Where $replicated_{i}$ is a dummy coded variable, which was coded as 1 if the meta-analytic effect in the replication set matches the original effect in direction at a significance alpha level of .05, and 0 otherwise.
+Where $replicated$ is a dummy coded variable, which is the same as for equation \@ref(eq:H3Main).
 Note here that unlike in the test for hypothesis 4, $QMP\_ratio_{i}$ refers only to the QMP ratios of the replications, meaning that original article QMPs were not included in this analysis.
@@
 
-These models had independence of observations as another assumption, the observations here referring to a replication set.
+These models had independence of observations as an assumption, the observations here referring to a replication set.
 this is known to be false since the data is nested within four separate Many Labs projects.
-In order to test if this nested structure might influence the relations described in hypothesis 5 & 6, random intercept and random slope multilevel models were implemented as sensitivity analyses for the tests of both hypothesis 5 & 6.
-In these models each replication set was treated as being nested in its respective Many Labs project.
-Worth noting is that currently the betareg package does not allow for estimation of multilevel models.
+In order to test if this nested structure might influence the relations described in hypothesis 5 & 6, random intercept and random slope multilevel models with each Many Labs project as a group were implemented as sensitivity analyses.
+As of writing this article the betareg package does not allow for estimation of multilevel models.
 As an approximation, Gaussian random-intercept multilevel models were implemented using the lmer function from the lme4 package [@R-lme4].
@@
 
-```{r Hypotheses5&6SensitivityAnalyses, include = FALSE}
+```{r Hypotheses5And6SensitivityAnalyses, include = FALSE}
 ## Hypothesis 5 sensitivity test using a random intercept Guassian model.
@@
 The goal of these analyses was to see if there are any type specific carry-over effects in QMPs between original and replication.
-As these analyses are exploratory in nature, due to the large number of tests, the focus was on visualisation rather than inference.
+Due to the large number of tests, the focus was exploratory using visualisation rather than inference.
+
+APPENDIX:
 
@@
 ```{r UnidimensionalityExploratoryAnalysis, include = FALSE}
-extracted_data_list <- list(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean,
-                            data_1.12.3.2_clean, data_2.10.1_clean,
-                            data_2.12.1_clean, data_2.12.2_clean, 
-                            data_2.12.3_clean, data_2.15_clean, data_2.20_clean,
-                            data_2.23_clean, data_3.2.1.1_clean, 
-                            data_3.2.1.2_clean, data_3.7.1_clean, 
-                            data_3.7.2_clean, data_3.8.2_clean,
-                            data_5.1.1_clean, data_5.7_clean, data_5.9.1_clean)
+extracted_data_list <- list(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, data_1.12.3.2_clean,data_2.12.1_clean, data_2.12.2_clean, data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.1_clean, data_3.7.2_clean, data_3.8.2_clean, data_5.1.2_clean, data_5.1.1_clean, data_5.7_clean, data_5.9.1_clean)
 
@@
 
-## Descriptives
-
-The mean sample size within the replications was `r apa_num(mean(coded_data_replications$N, na.rm = TRUE), digits = 0)` participants (IQR = `r apa_num(IQR(coded_data_replications$N, na.rm = TRUE), digits = 0)`).
-In the original articles the mean sample size was `r apa_num(mean(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)` (IQR = `r apa_num(IQR(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)`).
-In total, support was found for hypothesized effects of `r apa_num(table(coded_data_replications$hypothesis_support)["Yes"], digits = 0)` of the `r apa_num(nrow(coded_data_replications), digits = 0)` measures.
-Proportions of replication success per Many Labs project can be found in Table \@ref(tab:ReplicationRatioTable).
+## Data Visualization
+
+Table \@ref(tab:ReplicationRatioTable) displays the proportion of replication success per Many Labs project. ???Cronbach's alpha of the QMP items???
 
@@
 
-Existing materials were used for `r apa_num(table(coded_data_replications$sel_existing)["True, namely:"], digits = 0)` of the `r apa_num(nrow(coded_data_replications), digits = 0)` measures in replications and for `r apa_num(table(coded_data_original_shortened$sel_existing)["True, namely:"], digits = 0)` in original studies.
-The specific version of the measure was reported for `r apa_num(length(coded_data_replications$op_version[coded_data_replications$op_version != ""]), numerals = FALSE)` measures in replications, and `r apa_num(length(coded_data_original_shortened$op_version[coded_data_original_shortened$op_version != ""]), numerals = FALSE)` measures in original articles.
-For those measures that were not based on existing materials, `r apa_num(table(coded_data_replications$sel_existing)["False, materials were newly developped for this study"], numerals = FALSE)` in the replications and `r apa_num(table(coded_data_original_shortened$sel_existing)["False, materials were newly developped for this study"], numerals = FALSE)` in original articles clearly stated that they were newly created for the study.
-Only `r apa_num(table(coded_data_original_shortened$mod_time)["After/During"], numerals = FALSE)` measure in the original articles was modified from its original source during the data collection period, all other measures were modified before that, if at all.
-
-## Reliability
-
-Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts the type of measure (single-item, multiple item, or not a scale), if for the measure reliability was reported or not, and what type of reliability coefficient was reported.
-Reliabilities were only assessed for multiple item measures, which were approximately equal between replication and original (`r apa_num(table(coded_data_replications$N_items)["multiple item measure"])` and `r apa_num(table(coded_data_original_shortened$N_items)["multiple item measure"])`, respectively).
-Looking at the multiple item measures, `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` in the replication protocols and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles reported a reliability coefficient.
-The most commonly reported reliability coefficient was Cronbach's alpha, which accounted for `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles.
-
-```{r ReliabilityReportingFlowDiagram, fig.cap = "Reliability reporting flow diagram."}
-knitr::include_graphics(path = "../../SupplementaryMaterials/reliability_reporting_flow_diagram.png")
-```
-
-A chi-squared test compared whether the number of reliabilities reported among multiple item measures differed between replications and original.
-Reliabilities were found to be more commonly reported in original articles compared to replication protocols ($\chi^{2}$(`r apa_num(H1_test_result$parameter)`) = `r apa_num(H1_test_result$statistic)`, *p* = `r apa_p(H1_test_result$p.value)`).
-These results are contradictory to hypothesis 1.
-
-The average Cronbach's alpha coefficient across replication sets was `r apa_num(mean(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(mean(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`, for omega the mean was `r apa_num(sd(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`.
-Figure \@ref(fig:Plot23AlphaCode) shows the distributions of the Cronbach's alpha coefficients for each replication set separated by successful and unsuccessful replication.
-
-```{r Plot23AlphaCode,warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the eighteen distinct measures for which suitable raw data was available to calculate Cronbach’s alpha coefficients from."}
-# plot for alpha
-ggplot(plot_23_data_alpha, aes(x = alpha, y = g)) +
-  geom_boxplot(outlier.shape = NA) +
-  geom_hline(yintercept = 6.5, color = "red", size = 1) +
-  geom_point(alpha = 0.1) +
-  theme_minimal() +
-  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), 
-                                                     "lines")) +
-  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0),
-    ymin = 7, ymax = 7, xmin = 1.08, xmax = 1.08) +
-  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0),
-    ymin = 6, ymax = 6, xmin = 1.08, xmax = 1.08) +
-  coord_cartesian(xlim = c(0, 1), clip = "off") +
-  ylab("") +
-  xlab("Cronbach's alpha")
-
-```
-
-```{r Plot23OmegaCode, include = FALSE, eval = FALSE}
-# plot for omega
-ggplot(plot_23_data_omega, aes(x = alpha, y = g)) +
-  geom_boxplot(outlier.shape = NA) +
-  geom_hline(yintercept = 6.5, color = "red", size = 1) +
-  geom_point(alpha = 0.1) +
-  theme_minimal() +
-  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), 
-                                                     "lines")) +
-  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0),
-    ymin = 6, ymax = 6, xmin = 1.08, xmax = 1.08) +
-  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0),
-    ymin = 5, ymax = 5, xmin = 1.08, xmax = 1.08) +
-  coord_cartesian(xlim = c(0, 1), clip = "off") +
-  ylab("") +
-  xlab("Omega")
-```
-
-The between-group (across different replication set) variance and within-group (lab locations within a replication set) variance in the Cronbach's alpha coefficient were assessed using a multilevel model as specified in Formulas \@ref(eq:level1H2), \@ref(eq:level2H2), & \@ref(eq:mixedH2) The between-group and within-group variance for Cronbach's alpha were approximately `r apa_num(between_group_variance_alpha, digits = 3)` and `r apa_num(within_group_variance_alpha, digits = 3)` respectively.
-The resulting ICC, obtained using formula \@ref(eq:ICC), was approximately `r apa_num(ICC_alpha, digits = 3)`.
-This suggests that variance was larger between replication sets than within.
-The same analysis for omega coefficients even showed a relatively larger degree of between group variance (between-group variance `r apa_num(within_group_variance_omega, digits = 3)`, within-group variance `r apa_num(between_group_variance_omega, digits = 3)`, ICC = `r apa_num(ICC_omega, digits = 3)`).
-Both results are in line with hypothesis 2, although caution in interpreting this result is advised due to the small sample size and the lack of an available inferential test.
-
-The relationship between reliability and replication success was primarily tested via logistic regression, with replication success as the dependent variable.
-Further sensitivity analyses were performed using multilevel logistic models, with each measure as an overarching group wherein its reliability at each lab location is nested.
-The results of the logistic and multilevel logistic models are shown in Table \@ref(tab:ReplicabilityReliabilityTestTable) for both Cronbach's alpha and omega reliability coefficients.
-
-```{r ReplicabilityReliabilityTestTable, warning = FALSE}
-# creating the dtaframe for the table
-H3_table_dataframe <- rbind(H3_test_result_main_alpha$table, H3_test_result_int_sensitivity_alpha$table, H3_test_result_main_omega$table, H3_test_result_int_sensitivity_omega$table, H3_test_result_slp_sensitivity_omega$table)
-
-# adding an asterix for significance to the significant p in the dataframe
-H3_table_dataframe[3,5] <- paste0(H3_table_dataframe[3,5], "$^*$")
-
-# adding rows to give indication of specific sections (apa_table being awkward)
-H3_table_for_printing <- rbind(c("Alpha", "", "", "", ""), c("Logistic Regression Model", "", "", "", ""), H3_table_dataframe[1:2,], c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(3:4),], c("Omega", "", "", "", ""), c("Logistic Regression Model", "", "", "", ""), H3_table_dataframe[(5:6),], c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(7:8),], c("Random-Slope Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(9:10),])
-
-# print the table in apa formatting
-apa_table(
-  H3_table_for_printing, align = c("l", "r", "r", "r", "r")
-  , caption = "Model Results from Tests of Hypothesis 3"
-  , note = "The Alpha and Omega sections show the models where the independent variable was the calculated Cronbach's alpha and omega coefficient respectively.
-The random slope model for Cronbach's alpha did not converge, thus it results are not shown here.
-$^* p < .05$"
-  , escape = FALSE, placement= "htp", midrules = c(1, 2, 5, 7, 8, 9, 12, 15))
-
-```
-
-Cronbach's alpha and omega did not significantly relate to replication success in the main logistic regression model (Cronbachs alpha: `r H3_test_result_main_alpha$full_result$alpha`; omega: `r H3_test_result_main_omega$full_result$omega`), nor in any of the multilevel sensitivity analyses models (see Table \@ref(tab:ReplicabilityReliabilityTestTable)).
-This is contradictory to the expectation in hypothesis 3.
-However, the results from these analyses should be evaluated with caution, given the small sample number of measures used to estimate these models.
-
-## Questionable Measurement Practices
-
-The counts of the QMP ratio obtained for each QMP type (see Table \@ref(tab:QMPCodingInfoTable)) are shown across the top layer of Figure \@ref(fig:Plot456Code) for both replication protocols and original articles.
-The overall number of counts for the QMP ratios of the QMP modification type were lower compared to the others, because only `r apa_num(table(coded_data_replications$mod_check)["True"])` out of `r apa_num(length(coded_data_replications$mod_check))` measures in replications, and only `r apa_num(table(coded_data_original_shortened$mod_check)["True"], numerals = FALSE)` measures used in original studies were modified.
-The bottom layer of Figure \@ref(fig:Plot456Code) shows the overlayed distributions of the total QMP ratios from the replication protocols and original studies, with dots indicating each datapoint, and the line indicating the mean for either distribution.
-
-```{r Plot456Code, warning = FALSE, fig.cap = "QMP ratio counts for each QMP Type and QMP total ratio distribution grouped by where each was coded from.
-The top row shows binned counts of QMP ratio’s that were observed for each replication protocol and original article, across the different QMP types.
+In order to visualise the results on QMPs, the proportions of the QMP ratio obtained for each QMP type (see Table \@ref(tab:QMPCodingInfoTable)) are shown across the top layer of Figure \@ref(fig:Plot456Code) for both replication protocols and original articles.
+While in the bottom layer of Figure \@ref(fig:Plot456Code) the overlayed distributions of the total QMP ratios from the replication protocols and original studies are displaued, with dots indicating each datapoint, and the line indicating the mean for either distribution.
+A large number of QMP ratios are missing for the QMP modification type , because only `r apa_num(table(coded_data_replications$mod_check)["True"])` out of `r apa_num(length(coded_data_replications$mod_check))` measures in replications, and only `r apa_num(table(coded_data_original_shortened$mod_check)["True"], numerals = FALSE)` measures used in original studies were modified.
+.
+
+```{r Plot456Code, warning = FALSE, fig.cap = "QMP ratio counts for each QMP Type and QMP total ratio distribution grouped by whether the QMP ratio was obtained from an original article or a replication protocol.
+The top row shows for each QMP type the proportions of each QMP ratio obtained, darker colours represent proportionally more QMPS, grey means modification did not occur for that measure.
 The bottom graph shows the distributions of total QMP ratios for both replication protocols and original articles, with the line indicating the mean QMP ratio.
 The specific observed values are indicated along the bottom row with dots"}
+# re-ordering the QMP-types, because it didn't save
+plot_456_data$QMP_type <- factor(plot_456_data$QMP_type, levels = c("Definition", "Selection", "Operationalization", "Quantification", "Modification", "Total"))
+
 # plot for alpha
@@
 Plot_456_1 <- ggplot(plot_456_data[plot_456_data$QMP_type != "Total",], 
-       aes(x = QMP_ratio, fill = RepOrg)) + 
-  geom_bar(position = "dodge", stat = "bin", bins = 10) +
-  facet_grid(~QMP_type) +
+                      aes(x = RepOrg, fill = as.factor(QMP_ratio_1))) + 
+  geom_bar(position = "fill") +
   theme_minimal() +
-  theme(plot.title = element_text(face = "bold")) +
-  scale_fill_manual(values=c("brown", "blue4")) +
+  scale_fill_manual(values = c("#ff766c", "#ef6f65", "#ce5f57", "#be5851", "#aa4f48", "#994741", "#803b36", "#672f2b", "#562824", "#411e1b", "#341816", "#030101","#4366ff", "#4265fc", "#3551cb", "#324dc1", "#324cbe", "#2d44aa", "#2c44a9", "#283d99", "#223380", "#162255", "#10193e", "#010206", "#000102")) +
   theme(legend.position = "none") +
-  ylab("Count") +
-  xlab("QMP Ratio") +
-  ggtitle("QMP Ratio's Per QMP Type Grouped by Original and Replication") +
-  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1"))
+  facet_grid(~ QMP_type) + 
+  ylab("Percentage of Overal Coding") +
+  xlab("QMP Type") +
+  ggtitle("QMP Ratio's Per QMP Type Grouped by Original and Replication")
 
@@
 
+Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts the flow of measures for which reliability was reported.
+The first split shows the number of measures which consisted of multiple items in a scale, which were approximately equal between replication and original (`r apa_num(table(coded_data_replications$N_items)["multiple item measure"])` and `r apa_num(table(coded_data_original_shortened$N_items)["multiple item measure"])`, respectively).
+Reliability was expected to be reported only for these measures.
+Taking these multiple item measures, the graph illustrates that `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` measures in the replication protocols and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles reported a reliability coefficient.
+Looking closer at these reported reliability coefficients, it can be seen in the graph that the most commonly reported coefficient was the Cronbach's alpha, which accounted for `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles.
+
+```{r ReliabilityReportingFlowDiagram, fig.cap = "Reliability reporting flow diagram.
+Figure shows the number of measures as reported in both the replication protocols and original article, which meet the criterion in the box within the diagram and those criteria before it."}
+knitr::include_graphics(path = "../../SupplementaryMaterials/reliability_reporting_flow_diagram.png")
+```
+
+If we look at the reliabilities obtained from the Many Labs responses on each measure for which scalar data could be accessed, the distributions of the Cronbach's alpha coefficients for each replication set for  are displayed in Figure \@ref(fig:Plot23AlphaCode), separated by successful and unsuccessful replication.
+The average calculated Cronbach's alpha coefficient across replication sets was `r apa_num(mean(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(mean(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`
+
+```{r Plot23AlphaCode,warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the eighteen distinct measures for which suitable raw data was available to calculate Cronbach’s alpha coefficients from.
+The green lines indicate the meta-analytic prediction interval lower and upper bound.
+The blue triangles indicate the reported alpha coefficient for that measure from the original article, when available.
+The Tau column besides the figure shows the tau heterogeneity estimate based on a meta-analysis of the calculated reliabilities for each measure, meta-analysis for which the Q-test for Heterogeneity was signicant at alpha < .05 are in black, not significant results are left grey.
+The Diff column shows the difference between reported reliability and the average reliability calculated from the Many Labs data for the applicable measures, the differences in bold are for reported reliabilities that fell outside the 95% quantile of calculated reliability scores."}
+
+# data re-ordering (was not saved in export)
+plot_23_data_alpha_reordered <- data_prep_plot_23_alpha(plot_23_data_alpha)
+
+### use ggarange for aranging things at the side of this graph
+
+# plot for alpha
+ggplot(plot_23_data_alpha_reordered, aes(x = alpha, y = g)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_hline(yintercept = 6.5, color = "red", size = 1) +
+  geom_point(alpha = 0.1) +
+
+  # adding in the tau values
+  geom_text(label = format(plot_23_data_alpha_reordered$tau, digits = 1), x = 1.15, size = 2.8, alpha = ifelse(plot_23_data_alpha_reordered$QEp < .05, 1, 0)) +
+  geom_text(label = format(plot_23_data_alpha_reordered$tau, digits = 1), x = 1.15, size = 2.8, alpha = ifelse(plot_23_data_alpha_reordered$QEp >= .05, 1, 0), colour = "grey") +
+
+  # adding in the alpha annotations
+   annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[1], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[1], "bold", "plain"))), ymin = 1, ymax = 1, xmin = 1.24, xmax = 1.24) +
+  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[2], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[2], "bold", "plain"))), ymin = 2, ymax = 2, xmin = 1.24, xmax = 1.24) +
+  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[3], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[3], "bold", "plain"))), ymin = 3, ymax = 3, xmin = 1.24, xmax = 1.24) +
+  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[4], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[4], "bold", "plain"))), ymin = 5, ymax = 5, xmin = 1.24, xmax = 1.24) +
+  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[5], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[5], "bold", "plain"))), ymin = 8, ymax = 8, xmin = 1.25, xmax = 1.25) +
+  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[6], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[6], "bold", "plain"))), ymin = 9, ymax = 9, xmin = 1.24, xmax = 1.24) +
+  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[7], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[7], "bold", "plain"))), ymin = 10, ymax = 10, xmin = 1.24, xmax = 1.24) +
+  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[8], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[8], "bold", "plain"))), ymin = 11, ymax = 11, xmin = 1.24, xmax = 1.24) +
+  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[9], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[9], "bold", "plain"))), ymin = 12, ymax = 12, xmin = 1.25, xmax = 1.25) +
+
+  theme_minimal() +
+  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), "lines")) +
+
+  # adding the necessary indicative texts
+  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 7.25, ymax = 7.25, xmin = 0.01, xmax = 0.01) +
+  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 6, ymax = 6, xmin = 0.01, xmax = 0.01) +
+  annotation_custom(grob = textGrob(label = "Tau", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.08, xmax = 1.08) +
+  annotation_custom(grob = textGrob(label = "Diff", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.24, xmax = 1.24) +
+
+  coord_cartesian(xlim = c(0, 1), clip = "off") +
+
+  # adding the blue triangles for reported reliability and green prediction intervals
+  geom_point(data = plot_23_data_reported_alpha, mapping = aes(x = coefficient_reported, y = article_order), color = "blue", shape = 17, size = 3) +
+  geom_point(mapping = aes(x = pi.lb), color = "green", shape = 124, size = 2.5) + 
+  geom_point(mapping = aes(x = pi.ub), color = "green", shape = 124, size = 2.5) +
+
+  ylab("") +
+  xlab("Cronbach's alpha") 
+```
+
+[BIG Original vs. Replication DESCRIPTIVES TABLE SOMEWHERE]
+
+Existing materials were used for `r apa_num(table(coded_data_replications$sel_existing)["True, namely:"], digits = 0)` of the `r apa_num(nrow(coded_data_replications), digits = 0)` measures in replications (FOOTNOTE: the relevant question asking participants to rate how much they agreed with a certain quote remained the same, however the quote itself and the people it was attributed too were both completely new compared to the original) and for `r apa_num(table(coded_data_original_shortened$sel_existing)["True, namely:"], digits = 0)` in original studies.
+The specific version of the measure was reported for `r apa_num(length(coded_data_replications$op_version[coded_data_replications$op_version != ""]), numerals = FALSE)` measures in replications, and `r apa_num(length(coded_data_original_shortened$op_version[coded_data_original_shortened$op_version != ""]), numerals = FALSE)` measures in original articles.
+For those measures that were not based on existing materials, `r apa_num(table(coded_data_replications$sel_existing)["False, materials were newly developped for this study"], numerals = FALSE)` in the replications and `r apa_num(table(coded_data_original_shortened$sel_existing)["False, materials were newly developped for this study"], numerals = FALSE)` in original articles clearly stated that they were newly created for the study.
+Only `r apa_num(table(coded_data_original_shortened$mod_time)["After/During"], numerals = FALSE)` measure in the original articles was modified from its original source during the data collection period, all other measures were modified before that, if at all.
+The mean sample size within the replications was `r apa_num(mean(coded_data_replications$N, na.rm = TRUE), digits = 0)` participants (IQR = `r apa_num(IQR(coded_data_replications$N, na.rm = TRUE), digits = 0)`).
+In the original articles the mean sample size was `r apa_num(mean(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)` (IQR = `r apa_num(IQR(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)`).
+
+## Reliability
+
+Based on a chi square comparison, reliabilities were found to be more commonly reported in original articles compared to replication protocols ($\chi^{2}$(`r apa_num(H1_test_result$parameter)`) = `r apa_num(H1_test_result$statistic)`, *p* = `r apa_p(H1_test_result$p.value)`).
+These results are contradictory to hypothesis 1.
+
+The between-group (across different replication set) variance and within-group (lab locations within a replication set) variance in the Cronbach's alpha coefficient were assessed using a multilevel model as specified in Formulas \@ref(eq:level1H2), \@ref(eq:level2H2), & \@ref(eq:mixedH2) The between-group and within-group variance for Cronbach's alpha were approximately `r apa_num(between_group_variance_alpha, digits = 3)` and `r apa_num(within_group_variance_alpha, digits = 3)` respectively.
+The resulting ICC, obtained using formula \@ref(eq:ICC), was approximately `r apa_num(ICC_alpha, digits = 3)`.
+This suggests that variance was larger between replication sets than within.
+These results are in line with hypothesis 2.
+However, the measures with lower average reliabilities did show a large amount of variation in the reliability coefficient as can be seen figure \@ref(fig:Plot23AlphaCode)
+
+The relationship between reliability and replication success was primarily tested via logistic regression, with replication success as the dependent variable.
+The results of the logistic and multilevel sensitivity analysis models are shown in Table \@ref(tab:ReplicabilityReliabilityTestTable) for Cronbach's alpha.
+
+[???sensitivity analyses??? to appendix]
+
+```{r ReplicabilityReliabilityTestTable, warning = FALSE}
+# creating the dtaframe for the table
+H3_table_dataframe <- rbind(H3_test_result_main_alpha$table, H3_test_result_int_sensitivity_alpha$table, H3_test_result_main_omega$table, H3_test_result_int_sensitivity_omega$table, H3_test_result_slp_sensitivity_omega$table)
+
+# adding an asterix for significance to the significant p in the dataframe
+H3_table_dataframe[3,5] <- paste0(H3_table_dataframe[3,5], "$^*$")
+
+# adding rows to give indication of specific sections (apa_table being awkward)
+H3_table_for_printing <- rbind(c("Alpha", "", "", "", ""), c("Logistic Regression Model", "", "", "", ""), H3_table_dataframe[1:2,], c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(3:4),], c("Omega", "", "", "", ""), c("Logistic Regression Model", "", "", "", ""), H3_table_dataframe[(5:6),], c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(7:8),], c("Random-Slope Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(9:10),])
+
+# print the table in apa formatting
+apa_table(
+  H3_table_for_printing, align = c("l", "r", "r", "r", "r")
+  , caption = "Model Results from Tests of Hypothesis 3"
+  , note = "The Alpha and Omega sections show the models where the independent variable was the calculated Cronbach's alpha and omega coefficient respectively.
+The random slope model for Cronbach's alpha did not converge, thus it results are not shown here.
+$^* p < .05$"
+  , escape = FALSE, placement= "htp", midrules = c(1, 2, 5, 7, 8, 9, 12, 15))
+
+```
+
+Cronbach's alpha did not significantly relate to replication success in the main logistic regression model (Cronbach's alpha: `r H3_test_result_main_alpha$full_result$alpha`), nor in any of the multilevel sensitivity analyses models (see Table \@ref(tab:ReplicabilityReliabilityTestTable)).
+This is contradictory to the expectation in hypothesis 3.
+Similar results were found for the analyses when using Omega as the reliability coefficient of choice (see supplementary materials ???).
+However, caution should be taken in evaluating the results from these analyses should, given the small sample number of measures used to estimate the models for these tests.
+
+[other relevant info such as: ???]
+
+## Questionable Measurement Practices
+
 Beta-regression was used to test the difference in QMP ratio between original articles and replication protocols.
@@
 Results showed that successful replication significantly related to a decrease in the ratio of QMPs in replication protocols (`r betareg_output_to_apa_full(H5_test_results_REV)`).
-Sensitivity analyses were performed using a random-intercept multilevel regression function.
-This model also found a significant association between replication success and QMP ratio (`r check_h5_REV$full_result$hypothesis_supportTRUE`).
-Both of these results are in line with hypothesis 5.
-However, the relationship in the multilevel model is no longer significant for QMP ratios obtained with the initial coding protocol (`r check_h5$full_result$hypothesis_supportTRUE`).
+
+```{r Plot46RevisedDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication total QMP ratio’s with linear regression line.
+Each dot in the figure describes the QMP ratio in that graph across both the original article and its replication protocol.
+Note: jitter was applied to these dots in order to show the number of observations at points where multiple dots were present"}
+ggplot(plot_46_data_rev[plot_46_data_rev$QMP_type == "QMP.Ratio" & plot_46_data_rev$QMP_Rep_type == "Rep.QMP.Ratio",], aes(QMP_ratio, QMP_Rep_ratio)) + 
+  geom_point() +
+  geom_jitter(width = 0.01, height = 0.01) +
+  stat_smooth(method="lm") + 
+  theme_minimal() +
+  theme(strip.text.y = element_text(size = 7), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
+  ylab("QMP Replication Ratio") +
+  xlab("QMP Ratio")
+
+```
 
@@
 It showed that total QMP ratio in the original article can significantly predict total QMP ratio in the subsequent replication (`r betareg_output_to_apa_full(H6_test_results_REV)`), which provides some evidence in favor of hypothesis 6.
+Figure \@ref(fig:Plot46RevisedDataCode) displays this relationship visually.
 However, this relation was not significant for the QMP ratios obtained with the initial protocol (`r betareg_output_to_apa_full(H6_test_results)`).
-Sensitivity analyses using a random intercept logistic multilevel model also found some discrepancy in results between revised and initial protocol, albeit with both being non-significant (revised protocol: `r check_h6_REV$full_result$QMP_REV`; initial protocol `r check_h6$full_result$QMP`).
-
-```{r Plot46InitialDataCode, include = FALSE, eval = FALSE, error = FALSE}
+
+## Appendixable Results
+
+[APPENDIX sensitivity analyses & co: for omega the mean (values calculated in the population across replication sets) was `r apa_num(sd(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`.???...
+The same analysis for omega coefficients even showed a relatively larger degree of between group variance (between-group variance `r apa_num(within_group_variance_omega, digits = 3)`, within-group variance `r apa_num(between_group_variance_omega, digits = 3)`, ICC = `r apa_num(ICC_omega, digits = 3)`).]
+
+```{r Plot23OmegaCode}
+# data re-ordering (was not saved in export)
+plot_23_data_omega_reordered <- data_prep_plot_23_omega(plot_23_data_omega)
+
+# plot for omega
+ggplot(plot_23_data_omega_reordered, aes(x = alpha, y = g)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_hline(yintercept = 5.5, color = "red", size = 1) +
+  geom_point(alpha = 0.1) +
+  theme_minimal() +
+  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), 
+                                                     "lines")) +
+  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0),
+    ymin = 6, ymax = 6, xmin = 1.08, xmax = 1.08) +
+  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0),
+    ymin = 5, ymax = 5, xmin = 1.08, xmax = 1.08) +
+  coord_cartesian(xlim = c(0, 1), clip = "off") +
+  ylab("") +
+  xlab("Omega")
+```
+
+[[[APPENDIX sensitivity analyses: H5, Sensitivity analyses using a random-intercept multilevel regression also found a similar significant association (`r check_h5_REV$full_result$hypothesis_supportTRUE`).
+Both of these results are in line with hypothesis 5.
+However, the relationship in the multilevel model was no longer significant for QMP ratios obtained with the initial coding protocol (`r check_h5$full_result$hypothesis_supportTRUE`).
+For the sensitivity analyses using a random intercept logistic multilevel mode both revised and initial protocol resulted in non-significant results (revised protocol: `r check_h6_REV$full_result$QMP_REV`; initial protocol `r check_h6$full_result$QMP`).]]]
+
+[[[APPENDIX???
+sensitivity analyses and so on: Planned exploratory analyses were preformed to expand on the test for hypothesis 6.
+The relationships between original article QMP ratios and replication protocol QMP ratios were investigated for each QMP type separately.
+Figure \@ref(fig:Plot46RevisedDataCode) visually illustrates the relations of the revised QMP ratios from different QMP types between replication protocols and original articles.
+As shown in the figure, no relation was strong and highly stable, and even fewer were consistent between initial and revised coding protocols.
+]]] IF SO, check rest of article to remove this part by in large.
+
+[[[OMIT: The relations that are consistent are those between original article definition QMPs with replication selection and total QMPs, original article selection QMPs with replication total QMPs, and finally original article quantification QMPs with replication selection QMPs.
+All of these relations were positive across both coding protocols, illustrating that a greater QMP ratio of the specified type in an original article is associated with an increase in QMP ratio for the specific QMP type, or total QMP ratio in the replication protocol.]]]
+
+```{r Plot46FullInitialDataCode, include = FALSE, eval = FALSE, error = FALSE}
 # Initial
@@
 
-```{r Plot46RevisedDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication QMP ratio’s per type with linear regression line.
+```{r Plot46FullRevisedDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication QMP ratio’s per type with linear regression line.
 The abbreviations on the axes relate to the QMP categories described in Table 1: Def.
@@
 
-## Exploratory Results
-
-Planned exploratory analyses were preformed to expand on the test for hypothesis 6.
-The relationships between original article QMP ratios and replication protocol QMP ratios were investigated for each QMP type separately.
-Table \@ref(tab:H6ExploratoryAssociationsRevisedTable) shows the results from these tests with the revised protocol QMP coding, while Table \@ref(tab:H6ExploratoryAssociationsInitialTable) shows the results for the QMP ratios obtained via the initial protocol.
-There were few significant relations and even fewer that are consistent between both coding protocols.
-The relations that are consistent are those between original article definition QMPs with replication selection and total QMPs, original article selection QMPs with replication total QMPs, and finally original article quantification QMPs with replication selection QMPs.
-All of these relations were positive across both coding protocols, illustrating that a greater QMP ratio of the specified type in an original article is associated with an increase in QMP ratio for the specific QMP type, or total QMP ratio in the replication protocol.
+[[[TO APPENDIX sensitivity analyses: Table \@ref(tab:H6ExploratoryAssociationsRevisedTable) shows the results from these tests with the revised protocol QMP coding, while Table \@ref(tab:H6ExploratoryAssociationsInitialTable) shows the results for the QMP ratios obtained via the initial protocol.
+INCLUDING TABLES]]]
 
@@
 
-Figure \@ref(fig:Plot46RevisedDataCode) visually illustrates the relations of QMP ratios from different QMP types between replication protocols and original articles further.
-
-The unidimensionality of the measures used in the Many Labs projects was assessed through factor analyses, and evaluated based on the criteria discussed in the [Exploratory Analyses](#ExploratoryAnalyses) section above.
+[[[To Appendix ???: The unidimensionality of the measures used in the Many Labs projects was assessed through factor analyses, and evaluated based on the criteria discussed in the [Exploratory Analyses](#ExploratoryAnalyses) section above.
 Suitable data for factor analyses was available for nineteen measures.
@@
 Only the RMSEA $< .08$ criteria suggested evidence for single factor structures.
+INCLUDES THE TABLE BELOW]]]
 
@@
 (2002), Art", "Nosek et al.
-(2002), Math", "Van Lange et al.
-(1997)", "Anderson et al.
+(2002), Math", "Anderson et al.
 (2012), SWL", "Anderson et al.
@@
 (2008), exp.
-5", "Shnabel & Nadler (2008)", "Vohs & Schooler (2008)"), cfa_results)
+5, verb", "Albarracín et al.
+(2008), exp.
+5, math", "Shnabel & Nadler (2008)", "Vohs & Schooler (2008)"), cfa_results)
 
@@
 cfa_results_for_print <- cfa_results_expanded
-cfa_results_for_print$RMSEA[16] <- "Did"
-cfa_results_for_print$`N Factors`[16] <- "Not"
-cfa_results_for_print$Unidimensional[16] <- "Converge"
+cfa_results_for_print$RMSEA[15] <- "Did"
+cfa_results_for_print$`N Factors`[15] <- "Not"
+cfa_results_for_print$Unidimensional[15] <- "Converge"
 
@@
 These measurement related concepts were then linked to replicability in order to investigate them as potential causes inhibiting successful replications.
-The results of the tests for the hypotheses showed mixed results.
+The results of the tests for the hypotheses were often underpowered, especially the tests of hypotheses 2 & 3 for which only eighteen measures were available to calculate reliability from.
+Additionally, most tests showed mixed results.
 However, when including exploratory and descriptive analyses, a clearer picture of the state of measurement in replication and original research emerges.
 
-Before interpreting of the results, it should be reiterated that the sample size for several analyses was smaller than what is generally recommended for such analyses.
-This holds especially for the tests of hypotheses 2, & 3, since the number of measures for which reliability could be calculated for these analyses was only eighteen.
-This was less than anticipated, which brings us to the first topic of the discussion.
-
-## Quality of Measurement
+## Risky Measurement Usage
 
@@
 Findings were in line with similar investigations in the literature by @shaw2020measurement & @flake2022construct.
-These two studies found that sufficient validity evidence and reliability reporting for measures was lacking, even more so for replications than for original studies.
-The lack of support found for hypothesis 1 shows that this also held for this study's sample.
-In fact, support was found for an effect in the direction opposite to what was hypothesized in the preregistration, as the original articles reported reliability coefficients more often than replication studies.
-
-However, even the original articles only reported reliability for approximately one third of the used multiple item measures.
-Reliability coefficients were reported in such small numbers that the original analysis plan for hypothesis 1 was altered, from evaluating the reliability coefficient value to the number of times reliability was reported in an article or protocol.
-As a result, the interpretation of rejecting the hypothesis based on this new test changed compared to the preregistered test.
-Still, the test provides evidence towards the same point, which is that reliability evidence for the used measure is lacking more in replication protocols than in original articles, although most multiple item measures in original articles were also reported without reliability evidence.
-This shows that lack of reliability evidence is a widespread issue, something that has been shown in earlier literature on this topic [@vacha1999practices; @green2011recent].
-
-Furthermore, across measures used in both original and replication studies, less than half of the measures were multiple item scales.
+These two studies found that sufficient validity evidence and reliability reporting for measures was lacking in replications and original studies.
+The fact that not enough reliability coefficients were reported to even conduct the planned analysis for hypothesis 1, and [[[VALIDITY EVIDENCE REPORTING DECRIPTIVE NEEDED (all but X of the 77 measures (replication/original) reported any validity evidence)]]] shows that reliability and validity evidence was similarly underreported in our sample, a problem that has also been addressed in earlier literature on this topic [@vacha1999practices; @green2011recent].
+
+The adjusted test for hypothesis 1, while not able to test differences in actual coefficient values, did show contradictory to hypothesis 1 and similarly to @flake2022construct, that original articles reported reliability coefficients more often than replication studies.
+Still, even for original articles a little over two-thirds of the multiple item measures were also reported without reliability evidence.
+???Interestingly enough, when looking at the measures for which alpha could be calculated, alpha coefficients were reported only for those measures that were among the higher calculated mean alpha among the sample of measures for which alpha could be calculated as can be seen in figure \@ref(fig:Plot23AlphaCode)???
+
+This only covers part of the spectrum of the measures found in the sample, across both original and replication studies, less than half of the coded measures were multiple item scales.
 Research commonly made use of single item measures (see Figure \@ref(fig:ReliabilityReportingFlowDiagram) for more details), an observation that was also made by @shaw2020measurement.
-The use of these single item measures comes with risks, since by virtue of being singular they assume that whatever they are measuring is unidimensional, while not being able to test this assumption [@shaw2020measurement].
-This is potentially quite worrying given that the exploratory analyses of the multiple item measures, for which unidimensionality could be tested, showed only little support for unidimensionality of the measures used in replications.
+The use of these single item measures comes with risks, since by virtue of being singular they assume that whatever they are measuring is unidimensional, while not being able to test this assumption [@shaw2020measurement], ???and reliability risks???.
+This is particularly concerning given that the analyses of the calculated reliabilities of the multiple item measures showed that some measures ???EXPLORATORY ANALYSIS IDEA: relation of the calculated reliabilities and N items of the measure???, and exploratory analyses of the multiple item measure replication datas, for which unidimensionality could be tested, showed only little support for unidimensionality (see Appendix ???, as was also observed by @shaw2020measurement.
+
+[[[APPENDIX with SENSITIVITY ANALYSES/UNIDIMIMENSIONALITY ANALYSIS: This is potentially quite worrying given that the exploratory analyses of the multiple item measures, for which unidimensionality could be tested, showed only little support for unidimensionality of the measures used in replications.
 While the measures that were tested for unidimensionality were mostly used as single indicators in the analyses for the replication protocol, one could argue this does not necessarily mean these measures all assessed constructs with a unidimensional structure.
@@
 However, it should be noted that at least with respect to Many Labs 2, all of the measures that were considered unidimensional for the analyses in this study were also considered unidimensional in the investigation by @shaw2020measurement} who also observed a lack of unidimensionality evidence in their investigation of Many Labs 2.
-To conclude, there is an indication that validity evidence for measures used in replication research is lacking overall.
+To conclude, there is an indication that validity evidence for measures used in replication research is lacking overall.]]]
 
 Several results did show more promising findings for the way measurement related issues are treated in replications.
-Firstly, the support found for hypothesis 2 showed some evidence that most of the variability in reliability coefficients is between measures, rather than within measures across different locations.
-If variation in the reliability of a measurement across locations is little, it could indicate that the measurement operated similarly across these locations, which would make the scores from the different lab locations directly comparable and aggregatable.
-However, again the small sample number of measures for which reliability could be assessed does mean that this estimate remains uncertain.
+Firstly, the support found for hypothesis 2 provided some evidence showing that most of the variability in reliability coefficients is between measures, rather than within measures across different locations.
+This would be a prerequisite showing that the measurement operated similarly across these locations, which would make the scores from the different lab locations directly comparable and aggregatable.
+However, the small sample number of measures for which reliability could be assessed does mean that this estimate remains uncertain.
 Secondly, most replication protocols clearly stated that their measure was either newly created or based on existing materials.
@@
 
-## Impact on replicability
-
-Besides assessing the overall quality of measurement reporting, this study also investigated if the reliability of a measure, and QMPs can impact replicability.
-First of all, contrary to expectations (see Hypothesis 3), less reliable measures were not associated with a decrease in replicability.
+## Impact of reliability on replicability
+
+Contrary to expectations (see Hypothesis 3), less reliable measures were not associated with a decrease in replicability.
 This result is surprising, since @stanley2014expectations demonstrated the potential impact that measurement error can have on the veracity of determining replication success based on a significance test without attenuating for measurement error.
@@
 While no evidence for hypothesis 3 was found, caution in interpreting the test results is needed.
-The number of measures for which reliability was calculated was quite low (eighteen for Cronbach's alpha, fifteen for omega), it could be that the test was simply underpowered to detect the effect.
+The number of measures for which reliability was calculated was quite low (eighteen for Cronbach's alpha, fifteen for omega) , it could be that the test was simply underpowered to detect the effect.
 On the other hand, it might be that the detrimental influence of measurement error on interpretations of replication results is small in large scale replication projects.
 Across the multiple replications, measurement error's influence on the effect could have been cancelled out at the meta-analytic level.
-This would require the measurement error to be random and small, and as a result the average value of the effect and the error around would remain similar, thus not altering the result of the meta-analytic significance test.
+This would require the measurement error to be random and small, and as a result the average value of the effect and the error around would remain similar, thus not altering the result of the meta-analytic significance test ???logic/cited work???.
+
+[[[??? reliability meta-analysis???
+
+## Impact of QMPs on replicability
 
@@
 This result provides further evidence supporting these claims.
-However, the association was only significant when data was used from the revised coding protocol, data from the initial protocol, which was more stringent in its assessment of QMP, did not indicate a significant association with replicability.
-
-Similarly, the test for hypothesis 6 showed inconsistent results between the revised and initial coding protocols.
-Only for the revised protocol data was an increase in total QMPs in the original study associated with an increase in total QMPs in the protocol of the replication for that study.
-The result obtained with the data from the revised protocol are in line with expectations.
-If information on measurement is lacking or the measure is poorly motivated in a study, then any subsequent replication attempt will lack information needed match its measurement to the original.
-Even if it does match the original, when the measure itself is a poor indicator of the assessed variable or construct, both the original and replication data obtained from this measure may not substantially relate to the investigated psychological phenomenon the original study set out to investigate [@flake2022construct].
-However, the fact that the conclusions were different based on the protocol makes it difficult to determine the exact nature of the influence of original study QMPs on replication protocol QMPs.
-
-Further analyses based on the QMP ratios of each specific type indicated that across both the initial and revised coding protocols together, only selection, definition, and quantification QMPs in the original article related significantly to selection type QMPs, total QMPs, or both in the replication (see Tables \@ref(tab:H6ExploratoryAssociationsRevisedTable) & \@ref(tab:H6ExploratoryAssociationsInitialTable)).
-
-It could be that original articles have to provide a clear definition as well as details on the scale, in order for a replication to be able to justify selecting the measure.
-A replication may also be in general more dependent on the original article for information on the definition of the constructs and the choice of measurement, compared to a description of the Operationalisation, quantification, and any modifications.
-These former are features of a measurement, which while preferably similar in a replication to the original, can and should be reported in the replication protocol even if the original article does not contain the details on these features itself.
-However, these are just speculations as the results showed no clear relations between different QMP types across original and replication (see Figure \@ref(fig:Plot46RevisedDataCode)), and testing of causal links was not possible with this data.
-
-For both hypothesis 5 & 6, the results were in line with expectations, but only for the revised coding protocol.
+
+The effect of QMPs on replicability can additionally be traced back to the effect of original article QMPs on replication QMPs.
+The test for hypothesis 6 showed that, in line with expectations, there was a positive association between the total QMPs of an original study and the total QMPs in the protocol of the replication for that study.
+The idea here is that when information on or support for the use of a measurement is lacking, any subsequent replication attempt is expected to also lack information on the measure.
+As a result, both the underreporting of measurement details and use of unverified measurements may persist.
+[make the domino effect more clear/better written here]
+
+Furthermore, ensuring that the original measurement is mimicked becomes difficult to verify when the measurement was not documented well originally.
+As a result, the relation between the original and replication studies weakens, lowering the chances that similar results will be found, and possibly even invalidating the replication's relation to the original study as a replication [@flake2022construct].
+
+However, it is worth noting that hese relations were only found for QMPs coded with the revised coding protocol.
 Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol.
-The initial protocol was revised because the ratings based on that protocol were consider to stringent, and as a result, several items were reformulated so that criteria for what constituted sufficiently clear reporting were lowered.
+The initial protocol was revised because the ratings based on that protocol were considered to stringent, and as a result, several items were reformulated so that criteria for what constituted sufficiently clear reporting were lowered.
 This meant that in the revised protocol, coded QMPs would need to clearly inhibit evaluation of the measurement, whereas for the initial protocol some aspects of the measurement reporting which were coded as questionable, may have been questionable only to a small degree.
@@
 
+[[[APPENDIX: SENSITIVITY and exploratory ANALYSES: Further analyses based on the QMP ratios of each specific type indicated that across both the initial and revised coding protocols together, only selection, definition, and quantification QMPs in the original article related significantly to selection type QMPs, total QMPs, or both in the replication (see Tables \@ref(tab:H6ExploratoryAssociationsRevisedTable) & \@ref(tab:H6ExploratoryAssociationsInitialTable)).
+It could be that original articles have to provide a clear definition as well as details on the scale, in order for a replication to be able to justify selecting the measure.
+A replication may also be in general more dependent on the original article for information on the definition of the constructs and the choice of measurement, compared to a description of the Operationalisation, quantification, and any modifications.
+These former are features of a measurement, which while preferably similar in a replication to the original, can and should be reported in the replication protocol even if the original article does not contain the details on these features itself.
+However, these are just speculations as the results showed no clear relations between different QMP types across original and replication (see Figure \@ref(fig:Plot46RevisedDataCode)), and testing of causal links was not possible with this data.]]]
+
 ## Limitations & Future Research
@@
 The design of this study came with certain limitations.
-First of all, there was no experimental manipulation included.
+First of all, there was no (quasi-)experimental manipulation included of the quality or reporting practices of the measures.
 As a result, the ability to investigate the exact causal links between QMPs and replicability was limited.
-This study was intended to be exploratory in nature, and thus did not focus on causal analyses.
-However, future research establishing causal links will prove to be very beneficial in improving the understanding of the relationships between measurement issues and replicability.
-
-Another limitation of this study is that the results differed based on whether data from the revised or the initial coding protocol was used.
-As a result, any relationship between QMPs and replicability remains uncertain.
-The revised coding protocol was adapted from the initial coding protocol before any analyses were performed, it is however still possible that a change in protocol may have biased results.
-Future research investigating this topic should use a coding protocol which is verified independently by several researchers on a sample of articles and protocols first, before being used to code the QMP data that will be analysed.
-As a first step, the coding protocol from this study and the coding key from @flake2022construct can be used as a basis.
+Secondly, alternative ways to analyse the data could have been used, or certain parts of the data could have been examined more closely.
+Several methodologies for doing so have already been suggested throughout the article such as ???insert methodology here???, and others are presented in the appendix ???sensitcity and exploratory analysis appendix???.
+Future research can use this study as a basis to find relevant data sources and methodologies to use in order to compliment and extend the findings of this study, or test causal links between measurement usage and replicability.
 
@@
 This research did not make use of any online appendices in assessing QMPs, future research may wish to include them and other sources as part of the data.
+\<-- try to collpase with previous paragraph???
+
+Another limitation of this study is that the results differed based on whether data from the revised or the initial coding protocol was used.
+The revised coding protocol was adapted from the initial coding protocol before any analyses were performed, it is however still possible that a change in protocol may have biased results.
+Future research investigating this topic should use a coding protocol which is verified independently by several researchers on a sample of articles and protocols first, before being used to code the QMP data that will be analysed.
+As a first step, the coding protocol from this study and the coding key from @flake2022construct can be used as a basis.
+\<- importance ???
 
@@
 However, this is an assumption this study cannot provide evidence for.
+[Focus more on the fact that there is a mixture in the QMP ratio’s: which influences the relations perhaps like ...]
 
@@
 For these reasons, future research should consider measurement invariance tests, if assessing measurement consistency in replications across different labs.
+\<-- also include other suggestions like for paragraph 1 of this section???
 
@@
 There are additional validity issues in measurement as the result of QMPs.
-While it is debatable whether or not $17.9\%$ average QMP ratio in replications is too much, the association between original paper and replication protocol QMPs demonstrates how a lack of information for measurement in the original can spill over to the reporting in replications.
+While it is debatable whether or not $17.9\%$ [add code for this percentage] average QMP ratio in replications is too much, the association between original paper and replication protocol QMPs demonstrates how a lack of information for measurement in the original can spill over to the reporting in replications.
 This could lead to issues for replication attempts if the measure in an original article has poor reliability and validity.
@@
 Thus, future replicators should first evaluate the quality of the measurement (reporting) in an article before deciding to replicate it.
+\<-- work this narrative into the discussion section for QMP -\> replicability???
+
+The results also suggest that the use of structured protocols in the reporting of measurement may be an effective way of reducing QMPs, and increasing the reporting of reliability and validity evidence.
+However, even in the Many Labs projects, which made use of structured protocols to report their measures, low reliability and validity evidence reporting was found.
+These protocols could therefore still increase the attention they give to reporting reliability and validity evidence.
+When original articles do not report their measurement details, replication attempts cannot guarantee a direct replication of the original.
+By improving the quality of measurement reporting in original articles, the validity of both original research results and future replication attempts would increase.
+It would be particularly important to focus on remedying strong violations of good measurement reporting, as these were shown to have a significant detrimental impact on replicability.
+This suggests that even small but critical improvements in the reporting of measurement information could lead to a substantial increase in the replicability of psychological science.
+\<-- work into paragraph above and shorten heavily...
+paragraph 2 is about the importance of structured protocols.
+Paragraph 3 about the need to consider the options when replicating a study.
 
@@
 In that case, the direct replication will be able to provide a sufficient test of a psychological theory, on the condition that the conceptual replication's test improvements led to it becoming a sufficient test.
-
-The results also suggest that the use of structured protocols in the reporting of measurement may be an effective way of reducing QMPs, and increasing the reporting of reliability and validity evidence.
-However, even in the Many Labs projects, which made use of structured protocols to report their measures, low reliability and validity evidence reporting was found.
-These protocols could therefore still increase the attention they give to reporting reliability and validity evidence.
-In particular, Figure \@ref(fig:Plot456Code) shows descriptive evidence that replication protocols are lacking in definition and selection evidence.
-Furthermore, since replications must base their measures on those of the original articles they are replicating, it is important that articles chosen for replications provide clear evidence on what is being measured, how it is scored, why it was chosen or why it was constructed the way it is, and how it is used in practice.
-It is these last two aspects that original articles appear to particularly be underreporting (See Figure \@ref(fig:Plot456Code)).
-When original articles do not report their measurement details, replication attempts cannot guarantee a direct replication of the original.
-By improving the quality of measurement reporting in original articles, the validity of both original research results and future replication attempts would increase.
-It would be particularly important to focus on remedying strong violations of good measurement reporting, as these were shown to have a significant detrimental impact on replicability.
-This suggests that even small but critical improvements in the reporting of measurement information could lead to a substantial increase in the replicability of psychological science.
+\<-- less direct vs.
+conceptual???
 

### 2024-02-28 Scripts/source_script.R

@@ -591,11 +591,13 @@ data_prep_H1 <- function(Data_Original, Data_Replications){
 ### Hypothesis 2
 # ASE (alpha standard error) formula for a single lab
 ASE_for_Lab <- function(lab_data){
+  # NOTE: only works with non-missing data:
+  # selecting only the complete cases for the ASE calculations
+  lab_data <- lab_data[complete.cases(lab_data),]
+  
   V_matrix <- cov(lab_data)
   p_num <- ncol(lab_data)
   j_vec <- rep(1, times = p_num)
-  
-  ### missing data issue
   
   # not sure about this implementation:
   Q_value <- ((2 * p_num^2) / ((p_num - 1)^2 * (crossprod(j_vec, V_matrix) %*% 
@@ -610,11 +612,8 @@ ASE_for_Lab <- function(lab_data){
 
 # obtaining the omega and alpha values for each measure (helper function).
 omega_and_alpha <- function(Data, m_length){
-  # selecting only the complete cases for the ASE calculations
-  Data_complete <- Data[complete.cases(Data),]
-  
   omega_and_alpha_vec <- c(t(omega(Data[2:m_length], nfactors = 1)[3:4]), 
-                           ASE_for_Lab(Data_complete[2:m_length]))
+                           ASE_for_Lab(Data[2:m_length]))
   
   names(omega_and_alpha_vec) <- c("alpha", "omega.tot", "ASE")
   
@@ -623,11 +622,8 @@ omega_and_alpha <- function(Data, m_length){
 
 # obtaining the alpha values for 2.12.3, 2.20, & 3.2.1.1 (helper function).
 just_alpha <- function(Data, m_length){
-  # selecting only the complete cases for the ASE calculations
-  Data_complete <- Data[complete.cases(Data),]
-  
   alpha_vec <- c(t(psych::alpha(Data[2:m_length])$total[[2]]), NA, 
-                 ASE_for_Lab(Data_complete[2:m_length]))
+                 ASE_for_Lab(Data[2:m_length]))
  
   names(alpha_vec) <- c("alpha", "omega.tot", "ASE")
   
@@ -637,26 +633,29 @@ just_alpha <- function(Data, m_length){
 
 # data load and prep function (including calculations)
 data_prep_H2 <- function(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, 
-                         data_1.12.3.2_clean, data_2.10.1_clean, data_2.12.1_clean, data_2.12.2_clean, 
[…]

### 2024-03-06 Data/AnalysisData/codebook_Plot_46_data.Rmd
failed attempt to include R results as numbers in text.
added the replicability and reliability test table.
added the results for H5 and H6, including plot 46, which also required the adition of the plot_46_data_rev file, which lead to a rerun of the final data creation code.
Opened up the Many Labs retrieved data for the project.
starting to restructure the article based on feedback. Start on adding meta-analysis component to H2
changed plot456 and plot46, and first stages of restructuring results.
added (suggested) changes to methods section, and made the first appendix containing additional

@@
 ---
-title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:47.216976"
+title: "Codebook created on 2024-03-04 at 2024-03-04 10:16:26.447391"
 output: github_document
@@
 ## Dataset description
-The data contains 1925 cases and 4 variables.
+The data contains 2772 cases and 4 variables.
 

### 2024-03-06 Data/AnalysisData/codebook_plot_46_data_REV.Rmd
starting to restructure the article based on feedback. Start on adding meta-analysis component to H2
changed plot456 and plot46, and first stages of restructuring results.
added (suggested) changes to methods section, and made the first appendix containing additional models and results.

@@
 ---
-title: "Codebook created on 2024-01-02 at 2024-01-02 11:37:22.192211"
+title: "Codebook created on 2024-03-04 at 2024-03-04 10:16:28.052337"
 output: github_document

### 2024-03-06 Scripts/Appendix_scripts/Appendix_pre-reg_analyses.Rmd
added (suggested) changes to methods section, and made the first appendix containing additional models and results.

--- 2024-01-02 Scripts/Manuscript/manuscript.Rmd
@@
----
-title             : "The Impact of Measurement Practices and Measurement Error on Construct Validity and Replication Outcomes in Psychological Science"
-shorttitle        : "Measurement Quality and Replicability"
+# Appendix A
 
-author: 
-  - name          : "Goos, C."
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Professor Cobbenhagenlaan 125, 5037 DB, Tilburg, The Netherlands"
-    email         : "casgoos99@gmail.com"
-    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
-      - "Conceptualization"
-      - "Data curation"
-      - "Formal Analysis"
-      - "Investigation"
-      - "Methodology"
-      - "Visualization"
-      - "Writing - Original Draft Preparation"
-      - "Writing - Review & Editing"
-  - name          : "Nuijten, M.B."
-    affiliation   : "1"
-    role:
-      - "Project Administration"
-      - "Writing - Review & Editing"
-      - "Supervision"
+```{r setup, include=FALSE}
+# loading R libraries, perhaps unnecessary
+library(papaja)
 
-affiliation:
-  - id            : "1"
-    institution   : "Tilburg University"
+# loading source script, perhaps unnecessary
+source(file = "C:/Users/u686785/OneDrive - Tilburg University/Documents/uvt/PHD/Master Thesis to Paper/Reproducible_R_Project/Scripts/source_script.R")
 
-authornote: |
-  1 Department of Methodology and Statistics, Tilburg School of Social and Behavioral Sciences, Tilburg University, Tilburg, NL.
-
-  Enter author note here. Caspar/Jelte/Marjan?
-
-abstract: |
-  Recently, the influence of measurement related issues on replicability has received more investigations. 
-  In particular, studies have indicated that low reliability, and poor measurement reporting can negatively influence the replicability of an effect. 
-  Building on this new line of research, this study assessed these influences in large scale replication projects. 
-  Protocols from the Many Labs replication projects, and the original articles that the replications were based on were used to assess the  reporting of the measures, while publicly available data from the Many Labs replications was used to assess the reliability of the measures.
-Reliability did not relate to replicability, and was generally consistent between labs for each measure in the Many Labs projects.
-  The quality of measurement reporting in replication protocols did however relate to replicability.
-  Additionally, tentative evidence was found for a relation between quality of measurement reporting in the protocol of a replication and the quality of measurement reporting in its related original study.
-  Recommendations are given for researchers and replicators in order to improve measurement practices in replication, and ward its negative impact on replicability. 
-  Additionally, directions are given for future research investigating the relationship between measurement issues and replicability.
-
-keywords          : "reliability, measurement, measurement reporting, replicability, construct validity"
-wordcount         : "X"
-
-bibliography      : ["r-references.bib", "references.bib"]
-
-floatsintext      : yes
-linenumbers       : no
-draft             : no
-mask              : no
-
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-
-classoption       : "man"
-output            : papaja::apa6_pdf
-knit              : worcs::cite_all
----
-
-```{r setup, include = FALSE}
-# loading R libraries
-library(papaja)
-library(worcs)
-library(tidyr)
-library(betareg)
-library(lmerTest)
-library(psych)
-library(forcats)
-library(GPArotation)
-library(ggplot2)
-library(ggridges)
-library(GGally)
-library(ggforce)
-library(grid)
-library(gridExtra)
-
-# loading source script
-source(file = "../source_script.R")
-
-# Code below loads the processed data. The raw data was prepared for analysis in 'prepare_data.R.
-load_data()
-
-# creates a reference list for all used R packages and the installed R version (does not automatically include Rstudio)
-r_refs("r-references.bib")
-
-# manually retrieving the Rstudio version
-rstudioapi::versionInfo()
 ```
-
-<!-- altering latex defaults to get better figure and table placement -->
-
-\renewcommand{\arraystretch}{0.7}
-
-<!-- reducing the line spacing within tables -->
-
-\renewcommand{\topfraction}{.85}
-
-<!-- max fraction of page for floats at top -->
-
-\renewcommand{\bottomfraction}{.7}
-
-<!-- max fraction of page for floats at bottom -->
-
-\renewcommand{\textfraction}{.15}
-
-<!-- min fraction of page for text -->
-
-\renewcommand{\floatpagefraction}{.66}
-
-<!-- min fraction of page that should have floats -->
-
-\setcounter{topnumber}{3} <!-- max number of floats at top of page --> \setcounter{bottomnumber}{3} <!-- max number of floats at bottom of page --> \setcounter{totalnumber}{4} <!-- max number of floats on a page --> <!-- remember to use [htp] or [htpb] for placement -->
 
@@
 
-# Introduction
+This appendix contains all of the pre-registered analyses that were either changed or omitted from the article.
 
-For many years, methodologists and statisticians have raised concerns about the way that research practices [@cumming2014new; @wicherts2016degrees], reporting practices [@bakker2011mis; @nuijten2016prevalence], and publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science] may undermine the credibility of psychology's scientific claims.
-Replicability of a finding is seen as one crucial step in establishing its credibility [@nosek2022replicability].
-In order to investigate the replicability of psychological science, the large scale Reproducibility Project: Psychology (RPP) was set-up [@osc2015estimating].
-Replications of 100 published studies were performed using similar materials, procedures, and analyses, while using a new sample of participants for each study.
-They found however, that in many instances the results did no match those of the original studies.
-This lack of replicability of psychological findings illustrated that psychology was facing a so-called 'replication crisis' [@hughes2018psychology; @giner2019crisis].
+## Test for H5 as Beta-Regression
 
-As a response, the demand to verify the credibility of psychological findings through replications rose.
-In order to attempt replications of various psychological findings, numerous large scale projects were set-up [@klein2014investigating; @camerer2016evaluating; @camerer2018evaluating; @ebersole2016many; @ebersole2020many; @klein2018many; @klein2022many].
-Among these were the Many Labs projects, which operated similarly to the RPP, with the additional feature that each original article was replicated multiple times across different labs in various locations around the world.
-The results from these replication projects generally showed smaller effects than those reported in the original studies.
-Similarly, effects that had reached statistical significance in the original no longer did across the aggregate results of its replications.
+### Explanation Change
 
-Several explanations for this discrepancy between original and replication findings have been suggested and investigated, with many being centred around the concept of Questionable Research Practices [QRPs, @john2012measuring].
-QRPs are practices, which either misrepresent or omit essential methodological information that is necessary for the evaluation of the research.
-Without this information, a reader will not know whether the result was in line with the author's expectation or simply the result of repeated trial and error until a suitable result was found [@simmons2011false].
-Consequently, much of the discourse and the subsequent proposed solutions have been centred around preventing these QRPs through increased transparency in scientific reporting.
-Preregistrations are one method for preventing QRPs.
-Preregistrations provide a clear description of the originally planned methodology of a study, which remains publicly available alongside the final report of the study.
-As a result, the author's original expectations and intentions can be accessed by the reader [@nosek2022replicability].
+This analysis was the originally planned analysis to test Hypothesis 5.
+However, for the sake of interpretation this test was changed to have the Independent Variable (IV) and Dependent Variable (DV) swapped in the article, and as a result it became a logistic regression.
 
-However, many researchers have also raised concerns that other factors, such as low power [@stanley2018what], lack of strong theoretical foundations [@eronen2021theory], and validity [@finkel2017replicability], which have not been given as much attention, are just as if not more responsible for the lack of successful replications found in psychology.
-An idea which has gained more traction recently is that measurement related issues have a large problematic influence on replicability.
-In particular, studies have focused on the effects of issues such as measurement error and questionable measurement practices on replicability [@stanley2014expectations; @shaw2020measurement; @flake2017construct; @flake2020measurement].
+### Model
 
-Measurement in psychological science is defined in large part by one overarching issue: psychological constructs, such as affective state and intelligence, cannot be measured directly.
-As a result, psychologists face two primary challenges in the use of measurement: First of all, the measure has to assess the construct it intends to measure, even though it can only do so indirectly.
-Secondly, because the measurement is indirect, it also comes with some degree of error surrounding its assessment of the construct.
-The first issue relates to the concept of validity, and specifically construct validity.
-Validity refers to the overall extent to which a measure measures what it is supposed to [@borsboom2004concept], while construct validity specifically refers to the substantial relation between the item scores on a psychological measure and the psychological construct it intends to measure.
-In order for indirect assessment of psychological constructs to be a viable approach, the measure needs to have construct validity [@cook2002experimental].
-However, both original and replication research are often not reported with sufficient details on construct validity [@shaw2020measurement; @flake2022construct].
-The second issue relates to the concept of measurement error and reliability.
-Measurement error indicates the amount of variation in item scores that is the result of the used measures inaccuracies, and not due to differences in the underlying psychological construct of interest.
-While what should be considered acceptable levels of measurement error is a subject of debate, and dependent upon context [@cho2015cronbach], it is generally agreed upon that too much measurement error is problematic.
-If measurement error is too large, the item scores relate to a construct no more than they do to random noise.
-As a result, the interpretability of these scores as indicators of a psychological construct is limited.
-
-@stanley2014expectations demonstrated, using a simulation study, the drastic effect measurement error can have on attempts to verify or falsify original findings.
-In practice, measurement error is commonly indicated using score-reliability.
-Score-reliability is an index of consistency of a measure, showing how much the items converge to the same point, with the point being the measured variable.
-Thus, @stanley2014expectations generated scalar item data with levels of score-reliability that mimicked what is standard in psychological research, to ensure that the resulting degree of measurement error was representative.
-Using this data, they found that the degree of measurement error can explain a large amount of the variation in observed effects found in replication research.
-It could therefore be that a failed replication was simply the result of measurement of the true effect varying from the original, rather than the true effect itself being different from what was originally reported.
-As a result, interpretations of replications might not be based on tests of the true effect, if the impact of measurement error is not attenuated for.
-
-Another key aspect in evaluating the use of measures is how they are reported.
-Questionable Measurement Practices (QMPs) have been coined as a conjugate term to QRPs.
-QMPs are practices that decrease the information necessary to evaluate the measurement of a study.
-They range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of measure and procedure of any sourced measures [@flake2020measurement].
-@flake2022construct coded the presence of a series of QMPs in the replication report in both the replication protocols of each replication in the RPP, as well as the original articles the replications were based on.
-They found that QMPs linked to issues for replicators in recreating the measurement to closely match the measurement in the original.
-As a result, there was a lack of measurement related information in both replication reports, and original articles.
-Without this information, it becomes difficult to establish that original and replication are measuring the same construct(s), which has detrimental consequences for direct replication attempts.
-
-This study aims to investigate the influence of measurement error and QMPs on replicability, using data and reports from the large scale Many Labs replication projects.
-One goal is to expand the research by [@stanley2014expectations] with a practical example.
-Whereas they obtained their findings using a simulation study, this study investigated the scope of their findings in practice.
-QMPs in the context of replication research were already investigated by [@flake2022construct].
-However, the investigations remained mostly descriptive.
-This study aims to expand upon the findings of [@flake2022construct] through the use of a new set of replication data, and by investigating the relation between QMP and replicability.
-
-## Measurement Error
-
-As a first step it is worth investigating what the state of measurement error is in original and psychological research, in order to assess the scope of @stanley2014expectations's findings in practice.
-Thus, this study investigated the following:
-
--   RQ1a. What is the degree of score reliability in replications of psychological research?
-
--   RQ1b. What is the degree of score reliability in original psychological research?
-
-It is difficult to suggest an expected or informed cut-off value for what could be considered a sufficient score reliability coefficient for both original and replication studies.
-While suggested cut-off points for reliability do exist [@nunnaly1994assessment], they are not without their criticism [@cho2015cronbach; @crutzen2017scale].
-Instead a comparison of scores between original and their associated replication studies should be of more substantive interest.
-Since direct replications intend to investigate effects in nearly identical scenarios with nearly identical measures as the original study, it is expected that measurement errors are as present in replication research as in original psychological research.
-
--   H1. No difference is present in the degree of score reliability between replication research and original psychological research.
-
-While reliability estimates are generally considered a measure specific feature, this is false.
-They are context dependent, and as a result the estimates of an effect can differ across contexts [@cho2015cronbach; @pauly2018resampling].
-With large enough differences across contexts, the effect estimates between different replication attempts could deviate from each other beyond direct comparison.
-For instance, suppose that we have a measure of multiple items assessing agreeableness in relation to both parents as well as peers.
-In a non-traditional society we might find high reliability for this measure, because participants that score high on one item, score high on another item since they are generally agreeable, while participants that score low one item, score low for all the other items.
-On the other hand, in a more traditional society we might find that reliability is low, because agreeableness towards parents is normative in that society, and as a result items relating to agreeableness towards parents may not be indicative of general agreeableness as a personality trait.
-In this example, a high score on the measure in the first context relates more strongly to a single agreeableness construct compared to the second context.
-The findings across these two populations would then no longer be directly comparable.
-Consequently, the value of any direct replication would become limited.
-To investigate this potential problem, the variation in score reliability is assessed for each measure when used in different contexts.
-
--   RQ2. To what degree do reliability estimates differ within a replication set of the same original study?
-
-Even though reliability estimates are context dependent, sufficient protocol structure can counteract the variance in reliability estimates.
-An example of the standardising impact a structured protocol can have on reducing variability within an effect can be found in investigations into the closely related issue of heterogeneity [@patacchini2007unobserved].
-Heterogeneity refers to the true variation in the true effect size due to minor but key differences in context, environment, and procedure.
-Heterogeneity is yet another proposed explanation for failed replications.
-This concern even prompted a Many Labs centred around the testing of heterogeneity in replications [@klein2018many].
-However analyses from Many Labs 2, and @olsson2020heterogeneity showed little empirical evidence for widespread heterogeneity in effects amongst replications.
-These findings demonstrate that it is possible to reduce variability as the result of context using structured protocols, as was done in the Many Labs projects this study analyzed.
-
--   H2. There is no significant variation in the reliability estimates of replications of the same original study.
-
-This study investigated whether there is something in the measures used for replicated findings that sets them apart from those used for non-replicated findings.
-In particular, this study extends research by @stanley2014expectations on the relationship between reliability and replicability, by using data from real life replication projects.
-
--   RQ3. What is the association between replication study score reliability and replication outcome?
-
-Greater score-reliability means greater consistency in estimation as variance around the estimate of the true effect is decreased.
-Consequently measures across different occasions, including between original and replication, should also become more consistent [@nunnaly1994assessment].
-When original and replication research share consistent result, and as long as the studied effect is true, then on average their statistical conclusions should converge.
-
--   H3. Score reliability in replication research is positively associated with successful replication of an original finding.
-
-Reliability is only one aspect by which a measure can be judged, with validity being another important way to determine the scientific rigour of a measure [@roberts2006reliability].
-Therefore as part of the exploratory analyses, validity was assessed for the same data source used to test the aforementioned hypotheses.
-Specifically, the unidimensionality of the measure was determined, meaning whether or not the items of a measure all related to a single variable.
-
-Validity of measures can be assessed not only through features found in the data.
-The measure must also be chosen and implemented in a way that enables proper measurement of the variables [@flake2020measurement].
-Any scientific report should therefore clearly motivate the measure and procedure that was used.
-Without clear reporting on these aspects, the validity of measurement will remain uncertain.
-Therefore, the other tests of this paper focused on the reporting aspects of measurement, assessed through QMPs.
-
-## Questionable Measurement Practices
-
-@flake2022construct descriptively investigated QMPs within the reproducibility project psychology [@osc2015estimating].
-This study seeks to conceptually replicate some of their findings within the Many Labs replication projects.
-
--   RQ4a. To what degree are QMPs present in replications of psychological research?
--   RQ4b. To what degree are QMPs present in original psychological research?
-
-The investigations by @flake2022construct have shown not only that QMPs are common in psychological research, they can be even more common in replications reports.
-However, the reporting of the Many Labs projects differ from the RPP data used in @flake2022construct.
-The structured and preregistered protocols used for the Many Labs projects were hypothesized to lead to consistent reporting of important measurement details, and as a result contain less QMPs.
-
--   H4. QMPs are expected to be more frequent in original psychological research than in replication research.
-
-QMPs put the validity of a study into question.
-If there is a lack of transparency and the used measures are invalid, replication results become difficult to interpret [@flake2020measurement].
-With a lack of transparency, closely mimicking the original's measurement becomes challenging.
-Furthermore, if a replication does not properly measure the variables of the original effect, the effect analysed within the replication may not be the same as the original.
-For these reasons, establishing a link between QMPs and non-replicability should confirm suspicions of their detrimental effects on replications [@flake2017construct; @flake2020measurement; @flake2022construct].
-
--   RQ5. What is the association between QMPs in replication studies and replication outcome?
-
-Fewer QMPs means that measurement decisions in a report are transparent with the number arbitrary methodological decisions being limited as well.
-Fewer arbitrary decisions means less ways that a replicator can deviate from the original's intended effect.
-One of the Many Labs projects even touched on this concept [@ebersole2020many].
-In this project, peer-review of replication protocols by original authors was used to ensure that approved methods were used.
-Additionally, it has been observed that authors who promote greater transparency in their work, have on average stronger evidence for their hypotheses [@wicherts2011willingness].
-Finally, the results shown in @protzko2020high illustrate that when original studies are transparent, preregistered, and have adequate sample size, subsequent replication attempts find nearly the same effect size as the original.
-All of these findings point towards a positive relation between successful replication and various types of good research practices.
-A similar relation is expected for good measurement practices.
-
--   H5. QMPs in replication research are negatively associated with replication of an original finding.
-
-@flake2022construct have already demonstrated the issues replicators face in transparently reporting the appropriate evidence for the measures they used.
-That study identified among other issues, a lack of available information in original articles.
-If essential information on a measure is not available in an original article, it may be difficult to know the specifics of that measure when used in a replication.
-In that case, the lack of proper reporting on measurement would impact the transparency and validity of future replications.
-Consequently, the article's findings become difficult to verify.
-To provide insight into this issue, an investigation of the relationship between original and replication QMPs was included.
-
--   RQ6. What is the association between QMPs in original research and QMPs in replications of psychological research?
-
-If the relationship exists, it is expected that questionable measurement practices in an original paper might cause a spill-over effect of QMPs into the replication.
-If the original paper does not specify how a measure was used, the replication may implement it differently.
-In that case, the replication can no longer be considered a direct replication.
-Additionally, investigations by @shaw2020measurement have shown that more validity evidence in an original article is associated with better psychometric properties in the replication sample.
-Based on these arguments, hypotheses are expected to be associated across original and replication studies.
-
--   H6. Total number of QMPs in original psychological research is positively related to total number of QMPs in replication research.
-
-# Method
-
-Data collection, coding protocol, and planned analyses were all preregistered.
-The preregistration and supplementary materials can be found on this article's OSF page: <https://osf.io/9r8yt/>.
-Any deviations from the preregistration are explicitly mentioned in the text.
-This manuscript was generated using the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency.
-All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication.git>.
-
-## Sample
-
-The data used for the analyses in this study consists of three main sources: replication datasets, preregistered replication protocols, and original study articles.
-The data came from the Many Labs series of studies.
-In particular, data from Many Labs 1, 2, 3, & 5 was used [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many].
-Data from Many Labs 4 [@klein2022many] was not part of the sample, as there was no publicly available protocol which contains the information needed to code QMPs.
-Additionally, the replication of [@crosby2008we] in Many Labs 5 did not contain contain data suitable for this project.
-The replication made use of videos and eye-tracking as measures, which does not match this study's focus on scale and item measures.
-
-The total number of psychological findings for which replication was attempted across the four included Many Labs projects amounts to a total of 60: 13 in Many Labs 1; 28 in Many Labs 2; 10 in Many Labs 3; & finally 9 out of the 10 tested findings in Many Labs 5.
-Since each replication set is related to an original study, the number of effects in original studies matches the number of effects in replication research.
-
-However, the unit of measurement was not a single study or replication.
-Instead each measure of a unique variable within a Many Labs project was treated as the unit of measurement.
-The reason being that studies could have and did use multiple measures.
-Additionally, measures can assess multiple dimensions.
-These dimensions, meaning unique variables, were separated into different units whenever possible, otherwise the measure was discarded from analysis.
-However, not all measures of unique variables were used.
-Only data from measures of primary variables, meaning those variables included in the primary test of the replication, were used.
-This was done to ensure that the analyses could link directly to the replicability of a study.
-Acquiescence bias checks, manipulation checks, measures used for pilot testing, and measures added for exploratory analyses in replication studies were not included.
-The result was a total sample size of 77 measures: 14 in Many Labs 1; 35 in Many Labs 2; 15 in Many Labs 3; & 13 in Many Labs 5.
-Again, the sample was equivalent between replications and original studies.
-
-### Replication Datasets
-
-The replication datasets refer to the data of each of the replication attempts for each of the original psychological effects undertaken as part of a Many Labs study.
-The specific data was extracted from the replication datasets for each relevant measure.
-The measure had to consist of multiple scalar items to be considered relevant for the related analyses.
-Single item measures were not usable for the analyses on score reliability [@wanous1996estimating] as they do not translate directly to the findings of @stanley2014expectations, which this study is following up on.
-
-For Many Labs 1, all the relevant replication data was available in a single csv file.
-For Many Labs 2 & 3 the situation was similar, only here the files were split across two csv files for each project.
-For Many Labs 5, the data was made available for each of the ten replication sets separately.
-Three out of the ten datasets were furthermore split across the various locations at which they were taken.
-If cleaned data was available this was chosen over raw data.
-Pilot data were omitted from the analyses entirely.
-This resulted in suitable measure data from eighteen replication sets spread across on average 40 lab locations for the analyses of hypotheses 2 & 3.
-
-```{r CleaningReplicationDatasetsData, include = FALSE, eval = FALSE}
-##### Data already available, code does not need to be run!
-### ML 1
-# 1.3
-data_1.3_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[22:29])
-colnames(data_1.3_clean)[1] <- "g"
-# 1.10
-data_1.10_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[108:115])
-colnames(data_1.10_clean)[1] <- "g"
-# 1.11
-data_1.11_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[73:76])
-colnames(data_1.11_clean)[1] <- "g"
-# 1.12.1
-# not found
-# 1.12.3
-data_1.12.3.1_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[54:59])
-colnames(data_1.12.3.1_clean)[1] <- "g"
-data_1.12.3.2_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[60:65])
-colnames(data_1.12.3.2_clean)[1] <- "g"
-
-### ML 2
-# 2.2
-data_2.2_clean <- cbind(as.factor(data_2.2[[5]]), data_2.2[6:11])
-colnames(data_2.2_clean)[1] <- "g"
-# 2.3
-# data does not appear suitable
-# 2.4.1
-data_2.4.1_clean <- cbind(as.factor(data_2.4.1[[5]]), data_2.4.1[6:11])
-colnames(data_2.4.1_clean)[1] <- "g"
-# 2.4.2
-data_2.4.2_clean <- cbind(as.factor(data_2.4.2[[5]]), data_2.4.2[6:14])
-colnames(data_2.4.2_clean)[1] <- "g"
-# 2.8.2
-data_2.8.2_clean <- cbind(as.factor(data_2.8.2[[6]]), data_2.8.2[9:13])
-colnames(data_2.8.2_clean)[1] <- "g"
-# 2.10.1
-data_2.10.1_clean <- cbind(as.factor(data_2.10.1[[5]]), data_2.10.1[6:11])
-colnames(data_2.10.1_clean)[1] <- "g"
-# 2.12.1
-data_2.12.1_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(6,7,8,9,10,31,32,33,34,35)]) 
-data_2.12.1_clean[3465:6905,2:6] <- data_2.12.1_clean[3465:6905,7:11]
-data_2.12.1_clean <- data_2.12.1_clean[1:6]
-colnames(data_2.12.1_clean)[1] <- "g"
-# 2.12.2
-data_2.12.2_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(11,14,15,18,19,22,24,27,28,29,36,39,40,43,44,47,49,52,53,54)]) 
-data_2.12.2_clean[3465:6905,2:11] <- data_2.12.2_clean[3465:6905,12:21]
-data_2.12.2_clean <- data_2.12.2_clean[1:11]
-colnames(data_2.12.2_clean)[1] <- "g"
-# 2.12.3
-data_2.12.3_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(12,13,16,17,20,21,23,25,26,30,37,38,41,42,45,46,48,50,51,55)]) 
-data_2.12.3_clean[3465:6905,2:11] <- data_2.12.3_clean[3465:6905,12:21]
-data_2.12.3_clean <- data_2.12.3_clean[1:11]
-colnames(data_2.12.3_clean)[1] <- "g"
-# 2.15
-data_2.15_clean <- cbind(as.factor(data_2.15[[5]]), data_2.15[8:12])
-colnames(data_2.15_clean)[1] <- "g"
-# 2.19.1
-# difficult to extract
-# 2.19.2
-# difficult to extract
-# 2.20
-data_2.20_clean <- cbind(as.factor(data_2.20[[5]]), data_2.20[6:45] - 1) 
-data_2.20_clean[3729:7396,2:21] <- data_2.20_clean[3729:7396,22:41]
-data_2.20_clean <- data_2.20_clean[1:21] 
-colnames(data_2.20_clean)[1] <- "g"
-# 2.23
-data_2.23_clean <- cbind(as.factor(data_2.23[[5]]), data_2.23[c(7,8,12,13,15)])
-colnames(data_2.23_clean)[1] <- "g"
-
-### ML 3
-# 3.2.1
-data_3.2.1 <- cbind(as.factor(data_ml3[[1]]), data_ml3[77:86] - 1)
-data_3.2.1.1_clean <- na.omit(data_3.2.1[1:6])
-colnames(data_3.2.1.1_clean)[1] <- "g"
-data_3.2.1.2_clean <- na.omit(data_3.2.1[c(1, 7:11)])
-colnames(data_3.2.1.2_clean)[1] <- "g"
-# 3.5
-# data appears unusable
-# 3.7.1
-data_3.7.1_clean <- na.omit(cbind(as.factor(data_ml3[[1]]), data_ml3[38:42]))
-colnames(data_3.7.1_clean)[1] <- "g"
-# 3.7.2
-data_3.7.2_clean <- na.omit(cbind(as.factor(data_ml3[[1]]), data_ml3[89:94]))
-colnames(data_3.7.2_clean)[1] <- "g"
-# 3.8.1
-# a single measure was reported
-# 3.8.2
-data_3.8.2_clean <- na.omit(cbind(as.factor(data_ml3[[1]]), data_ml3[29:30])) 
-colnames(data_3.8.2_clean)[1] <- "g"
-
-### ML 5
-# 5.1.1
-data_5.1.1_clean <- cbind(as.factor(data_5.1[[2]]), data_5.1[13:33])
-colnames(data_5.1.1_clean)[1] <- "g"
-# 5.1.2
-# difficult to separate .1 from .2
-# 5.4
-data_5.4_clean <- cbind(as.factor(data_5.4[[1]]), data_5.4[18:41])
-colnames(data_5.4_clean)[1] <- "g"
-# 5.5.1 & 5.5.2
-# from this dataset it appears that this data will be difficult to use.
-# 5.5.2
-# also difficult to use
-# 5.7 
-data_5.7_clean <- cbind(as.factor(data_5.7[[3]]), data_5.7[c(25, 34, 35, 36, 37, 38, 39, 40, 41, 42)])
-colnames(data_5.7_clean)[1] <- "g"
-# 5.9.1
-data_5.9.1_clean <- na.omit(cbind(as.factor(data_5.9.1[[4]]), data_5.9.1[c(79, 83, 87, 91, 95, 98, 101)]))
-colnames(data_5.9.1_clean)[1] <- "g"
-
-### to summarize
-# total number of likely usable: 15 (1.10, 1.11, 1.12.3.1, 1.12.3.2, 2.10.1, 
-# 2.12.1, 2.12.2, 2.12.3, 2.15, 2.23, 3.7.1, 3.7.2, 3.8.2, 5.7, 5.9.1)
-# total number of maybe usable: 6 (1.3, 2.20, 3.2.1.1, 3.2.1.2, 5.1.1, 5.4)
-# total alpha coefficient comparison usable: 3 
-#                                           1.11: 0.82
-#                                           3.7.2: 0.67
-#                                           5.9.1: 0.84
-
-### Saving to Intermediate Data Folder
-open_data(data = data_1.3_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_1.3_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_1.3_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_1.3_clean))), ".yml"))
-
-open_data(data = data_1.10_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_1.10_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_1.10_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_1.10_clean))), ".yml"))
-
-open_data(data = data_1.11_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_1.11_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_1.11_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_1.11_clean))), ".yml"))
-
-open_data(data = data_1.12.3.1_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_1.12.3.1_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_1.12.3.1_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_1.12.3.1_clean))), ".yml"))
-
-open_data(data = data_1.12.3.2_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_1.12.3.2_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_1.12.3.2_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_1.12.3.2_clean))), ".yml"))
-
-open_data(data = data_2.10.1_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_2.10.1_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_2.10.1_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_2.10.1_clean))), ".yml"))
-
-open_data(data = data_2.12.1_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_2.12.1_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_2.12.1_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_2.12.1_clean))), ".yml"))
-
-open_data(data = data_2.12.2_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_2.12.2_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_2.12.2_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_2.12.2_clean))), ".yml"))
-
-open_data(data = data_2.12.3_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_2.12.3_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_2.12.3_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_2.12.3_clean))), ".yml"))
-
-open_data(data = data_2.15_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_2.15_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_2.15_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_2.15_clean))), ".yml"))
-
-open_data(data = data_2.20_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_2.20_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_2.20_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_2.20_clean))), ".yml"))
-
-open_data(data = data_2.23_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_2.23_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_2.23_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_2.23_clean))), ".yml"))
-
-open_data(data = data_3.2.1.1_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_3.2.1.1_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_3.2.1.1_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_3.2.1.1_clean))), ".yml"))
-
-open_data(data = data_3.2.1.2_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_3.2.1.2_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_3.2.1.2_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_3.2.1.2_clean))), ".yml"))
-
-open_data(data = data_3.7.1_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_3.7.1_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_3.7.1_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_3.7.1_clean))), ".yml"))
-
-open_data(data = data_3.7.2_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_3.7.2_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_3.7.2_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_3.7.2_clean))), ".yml"))
-
-open_data(data = data_3.8.2_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_3.8.2_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_3.8.2_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_3.8.2_clean))), ".yml"))
-
-open_data(data = data_5.1.1_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_5.1.1_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_5.1.1_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_5.1.1_clean))), ".yml"))
-
-open_data(data = data_5.4_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_5.4_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_5.4_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_5.4_clean))), ".yml"))
-
-open_data(data = data_5.7_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_5.7_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_5.7_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_5.7_clean))), ".yml"))
-
-open_data(data = data_5.9.1_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_5.9.1_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_5.9.1_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_5.9.1_clean))), ".yml"))
-
-```
-
-### Preregistered Replication Protocols
-
-The preregistered replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each replication set.
-These protocols were available through the OSF pages of each Many Labs project.
-These preregistered replication protocols, as well as the replication datasets mentioned earlier were scanned through to ensure that the planned analyses were feasible.
-However, no coding or analysis of either of them had taken place before the analyses were preregistered.
-This includes any systematic coding of the QMPs present in the report.
-Furthermore, no overview of these and the qualitative topics were available at the time of preregistration.
-
-Finally, the reports of the Many Labs projects, meaning the published articles [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many], were used to determine whether not the replication was considered successful.
-
-### Original Study
-
-The original study articles are the published articles of the original effect on which the Many Labs replication sets were based.
-In the case of Many Labs 5 the original studies refer to the studies which first tested the effect to be replicated, not the earlier replication attempts of the same effects in the RPP [@osc2015estimating].
-
-```{r CleaningCodedData, include = FALSE, eval = FALSE}
-##### Data already available, code does not need to be run!
-# Selecting the relevant rows and columns for the data
-coded_data_initial_sel <- coded_data_initial_raw[3:160, 18:57]
-coded_data_revised_sel <- coded_data_revised_raw[3:160, 18:38]
-coded_data_vignette_raw <- coded_data_vignette_raw[3:160, 2]
-
-# Combining the datasets
-coded_data_full <- cbind(coded_data_initial_sel, 
-                         cbind(coded_data_revised_sel, coded_data_vignette_raw))
-
-# filtering out unnecessary double columns
-coded_data_full <- cbind(coded_data_full[, 1:40], coded_data_full[, 45:62])
-
-### creating the cleaned dataset using the functions in the source code 
-coded_data_clean <- calculating(recoding(restructuring(fixing(
-  renaming(coded_data_full)))))
-
-### Saving to Intermediate Data Folder
-# Splitting data into replication and original
-coded_data_replications <- coded_data_clean[1:77,]
-coded_data_original <- coded_data_clean[78:157,]
-
-# difference in dataset row number is due to the fact that the moral foundations
-# questionnaire in original 2.4 is reported using all 5 of its factors, whereas
-# in replication 2.4 only the two overarching groups of binding and 
-# individualizing foundations are described.
-# For that reason a shortened original dataset will be used for any direct
-# comparisons between original and replication coding.
-coded_data_original_shortened <- coded_data_original[c(1:17, 19, 22:80),] 
-coded_data_original_shortened[c(18,19),5] <- 
-  c("individualizing moral foundations", "binding moral foundations")
-coded_data_original_shortened[18,13] <- NA
-coded_data_original_shortened[19,13] <- NA
-
-# exporting cleaned data
-open_data(data = coded_data_replications, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(coded_data_replications))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(coded_data_replications))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(coded_data_replications))), ".yml"))
-
-open_data(data = coded_data_original, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(coded_data_original))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(coded_data_original))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(coded_data_original))), ".yml"))
-
-open_data(data = coded_data_original_shortened, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(coded_data_original_shortened))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(coded_data_original_shortened))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(coded_data_original_shortened))), ".yml"))
-
-# clearing up memory space by removing raw files from the environment
-rm(coded_data_initial_raw, coded_data_revised_raw, coded_data_vignette_raw, 
-   data_2.10.1, data_2.12, data_2.15, data_2.19.1, data_2.2, data_2.20, 
-   data_2.23, data_2.3, data_2.4.1, data_2.4.2, data_2.8.2, data_3.5, data_5.1,
-   data_5.4, data_5.5, data_5.7, data_5.9.1, data_ml1, data_ml3)
-
-```
-
-## Data Collection
-
-The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>.
-When available, codebooks and study materials were used to identify the specific data for each measure.
-
-The publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base] Using the replication protocols, codebooks, and analysis scripts from each replication set as a guide, the variables associated with each measure were extracted into their own data frame containing the data from all studies in one replication set.
-These pieces of information formed the replication datasets in the analysis.
-
-The OSF page for each Many Labs project was combed through, in order to identify the components of the research which contained information on the measurement practice and reported reliability.
-The focus was on finding the preregistered protocols which contained information on the entirety of the replication sets in each Many Labs project.
-This was successful for Many Labs 2, & 3.
-For Many Labs 1 the Proposal_V1.1 was selected as the proper candidate for the QMP analysis.
-Despite the difference in name, it is the equivalent in Many Labs 1 to the protocols of Many Labs 2 & 3.
-For Many Labs 5 the protocols were made accessible for each replication set separately.
-The relevant OSF page of each replication set was searched through for a file which contained protocol in its name.
-If available, a version of the protocol labelled as revised, post-review, peer-review, or endorsed was selected.
-In case there was doubt about which was most appropriate, the latest uploaded relevant protocol was selected.
-Only regular protocols were taken, meaning those not labelled as data collection, analysis protocol or anything similar[^1].
-
-[^1]: The steps taken to access the replication protocol data from Many Labs 5 were not preregistered, and only became clear upon further investigation of the accessible information.
-The specific names and locations of the files that were used as the datasets can be found under the supplementary materials of the OSF page of this article <https://osf.io/gft46/%7D>
-
-The original articles were identified through the citations in each replication protocol, using Web of Science, Google Scholar, and PsychInfo (in that order).
-An issue was encountered while trying to access @hyman1950current.
-However, after contacting the first author of @klein2014investigating a suitable version of the article was obtained for use in the analyses.
-
-The measures of primary variables were identified by combing through the entire methods section of each preregistered replication protocols.
-Then using the structured coding protocol (made using Qualtrics) that is available on the OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages of this study, each measure of a unique variable was coded on measurement reporting and reported reliability.
-
-The structured coding protocol was used for both replication protocols and original studies.
-A series of questions relating to measurement practices and measurement error were used to extract the information.
-Descriptions of the extracted variables can be found in the [Measures](#Measures) section below.
-The scope of the coding was limited to the abstract, method, procedure, materials, measure, and initial parts of the results sections.
-Additionally, a keyword search using the name of the measured variable was used to search for any potentially missed information.
-An exception to this procedure was a question asking about the presence of example items.
-For this question, information from supplementary materials was uniquely considered as relevant.
-Another exception was the question regarding the replication of the original effect.
-Tables from the final report of each Many Labs project were used to answer that question.
-
-After the data was initially coded according to the preregistered coding protocol, it was determined, based on discussion with the supervisor, that some of the initial ratings were possibly to stringent.
-As a result, some of the items in the protocol were reformulated, so that the conclusions from the resulting analyses were based on a more favourable judgement of QMPs.
-These changes included: accepting linked online appendices as a data source for example items; assuming that if no differences between replication and original are measurement is mentioned, that there is no difference, even if it is not explicitly clear; and generally simplified criteria for what constituted sufficiently clear reporting.
-The revision of the coding protocol happened after all the data were coded using the initial protocol.
-As a result the coded data using the initial protocol, and the coded data using the revised protocol are both available available on this article's OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages.
-Both raw and processed formats are present.
-
-## Measures {#Measures}
-
-### Measurement Error Measures
-
-Two main sources of information were used to test hypothesis 1, the reported reliability coefficient from the replication protocols, and the reported reliability coefficient in the original articles.
-The reported reliability coefficient is the score reliability reported per measure in the replication protocol or original article.
-Both the type (Cronbach's alpha, retest, interrater, etc.) and the value itself were extracted.
-
-The test of hypothesis 2 was based on different score reliabilities.
-As stated earlier, only score reliabilities of scalar measures with multiple items were included in the test of hypothesis 2.
-Because data was available for each lab location within a replication set, it was possible to calculate score reliabilities of a measure for each lab location.
-With location specific score reliabilities, it was possible to assess the variation of score reliabilities of the same measure across different contexts.
-
-Two different types of score reliabilities were calculated: Cronbach's alpha and omega.
-Cronbach's alpha was used as it is one of the most popular indices of score reliability [@cho2015cronbach].
-Omega was added to the analysis as it has been argued to be a more informative measure of score reliability, while also providing validity evidence for the scale [@crutzen2017scale; @deng2017testing].
-Cronbach's alpha and omega were calculated using the alpha and omega functions respectively in the psych R package [@R-psych].
-Default arguments were used for both functions except the nfactors in the omega function, which was set to 1.
-
-### Replicability Measure
-
-Hypothesis 3 as well as 5 specify an association between either score reliability or QMPs respectively, and replication success.
-Replication success was based on the test of the main effect of a study.
-However, the unit of measurement for the data in this study was a measure of a unique variable, not an effect.
-Fortunately, since only primary measures were included in the data, each measured a variable of the main effect, and as a result the measure remains related to the test of the main effect.
-Replication was based on the significance of the meta-analytic effect of the replication set as reported in its respective Many Labs report.
-An effect was considered replicated if the meta-analytic p-value was lower than .05, and in the same direction as the original effect.
-In all cases, meta-analytic significance of an effect meant that support in the direction of the original effect was found.
-
-The tests for hypotheses 4, 5, & 6 were all based on the number of QMPs per category that were determined by the research using the coding protocol.
-An overview of the QMP categories of the coding variables, based on @flake2020measurement, can be seen in Table \@ref(tab:QMPCodingInfoTable)
-
-```{r QMPCodingInfoTable, warning = FALSE}
-QMP_info_dataframe <-data.frame(Category = c("Definition", "", "", "Operationalisation", "", "", "", "Selection/Creation", "", "", "Quantification", "Modification", "", "", "", "", ""),
-           'N Questions' = c("1", "", "", "5", "", "", "", "4", "", "", "4", "6", "", "", "", "", ""),
-           'Example Question' = c("A psychological/sociological definition",
-            "is given to the name of the measured",
-            "variable within the paper.", 
-            "The administration format (pen-and-",
-            "paper/computer) and environment (in",
-            "public/in a lab) are described (Note:",
-            "both should be present for a true rating).", 
-            "The source of the scale is provided",
-            "(in case the scale was newly developed",
-            "this should be clearly stated).", 
-            "The number of items are described.", 
-            "Any format changes are mentioned",
-            "(paper-and-pencil <–> computer), if no",
-            "changes were made to the format, and",
-            "this was mentioned then code as No",
-            "modification. If it is not clear, then code",
-            "as False."))
-
-# transfer the data to an APA table for printing
-apa_table(
-  QMP_info_dataframe, align = c("l", "r", "l")
-  , caption = "Information of QMP coding variables per category."
-  , note = "N Questions refers only to the questions considered quantative as specified in the text below."
-  , escape = FALSE, placement= "htp", booktabs = TRUE)
-
-```
-
-Selection and creation share a category as the justifications and requirements in selecting a measure are similar to those for creating a new measure.
-Modification variables were only assessed when it was clear that the measure was modified from an original source in some way.
-The questions were all answered as either true, false, or not applicable.
-Questions related to modification had 'no modification' as an additional answer option, in case the specific aspect of the measure was explicitly not modified.
-Beside these quantitative variables, a total of four qualitative variables were also included to measure details surrounding measurement practices.
-These variables assessed: the specific version of the measure (if reported); whether and what previous materials were used for the study; what, if any, psychometric evidence beyond reliability score (e.g.
-factor analysis, IRT model, convergent validity) was provided; and whether it was specified or not that the measure was or was not modified.
-
-Two of the qualitative items have an equivalent in the coding key of @flake2022construct.
-Eleven out of twenty of the quantitative coding variables have an equivalent in @flake2022construct.
-Variables related to the specific measurement scaling and purpose in the paper, were omitted from the analyses of this study as they were deemed neither relevant for the analyses of this study, nor necessary in matching this study to the key results of @flake2022construct.
-Questions about more general measurement features such as the number of items and how scores were aggregated were altered from @flake2022construct to better fit the aims of this study.
-
-The tests for hypotheses 4, 5, & 6 were all based on QMP ratios, both total QMP ratios and ratios per QMP type.
-This ratio was based on the number of coded trues divided by the number of applicable QMPs.
-When a question was coded as true, this equated to a count of one QMP for that type and in total, whereas false equated to a zero.
-If coded as not applicable or no modification (for the modification items), this item was considered not applicable.
-Non applicable responses were not only counted as a zero, but additionally the denominator for calculating the ratio of QMPs was lowered by one.
-These ratios were preferred over counts, since non applicable items could thus be accounted for.
-
-### QMP measures
-
-The same data as for the test of hypothesis 2 was used to check for the unidimensionality of the factor structure, as part of the exploratory analyses.
-A check for unidimensionality as validity evidence only makes sense if the measure was intended to be unidimensional.
-Therefore, for each replication for which data was available, the protocol was checked to ensure that the scores on each measure were meant to assess a single construct.
-
-### Validity Measure
-
-The same data as for the test of hypothesis 2 was used to check for the unidimensionality of the factor structure, as part of the exploratory analyses.
-A check for unidimensionality as validity evidence only makes sense if the measure was intended to be unidimensional.
-Therefore, for each replication for which data was available, the protocol was checked to ensure that the scores on each measure were meant to assess a single construct.
-
-```{r ReliabilityValidityTestabilityCheck, include = FALSE, warning = FALSE}
-## Checking the measures to recalculate the reliability and factor analysis for.
-## The question: "Are they psychometrics scales or not?", is key here.
-View(coded_data_replications)
-
-# Likely reliability: 1.10, 1.11, 1.12.3, 2.4.1, 2.4.2, 2.8.2, 2.10.1, 2.12.1, 
-# 2.12.2, 2.12.3, 2.15, 2.19.2, 2.23, 3.7.1, 3.7.2, 3.8.1, 3.8.2, 5.7, 5.9.1
-# Likely factor: 1.10, 1.11, 1.12.3, 2.4.1, 2.4.2, 2.8.2, 2.10.1, 2.12.1, 2.12.2,
-# 2,12,3, 2.15, 2.19.2, 2.23, 3.7.1, 3.7.2, 3.8.1, 3.8.2, 5.7, 5.9.1
-# Maybe reliability: 1.3, 1.12.1, 2.2, 2.3, 2.19.1, 2.20, 3.2.1, 3.5, 5.1.1, 
-# 5.1.2, 5.4, 5.5.1, 5.5.2
-# Maybe factor: 1.3, 1.12.1, 2.3, 2.19.1, 2.20, 3.2.1, 3.5, 5.1.1, 5.1.2, 5.4,
-# 5.5.1, 5.5.2
-
-# 1.9 is difficult, might be a scale as dv rather than voting behavior.
-```
-
-## Analyses
-
-```{r FinalPreparationData, include = FALSE, eval = FALSE}
-##### Data already available, code does not need to be run!
-### this code prepares the various pieces of data to be ready to use for the 
-### analyses.
-## confirmatory analyses
-# for hypothesis 4
-data_h4 <- data_prep_H4(coded_data_original_shortened, coded_data_replications)
-# for hypothesis 5
-data_h5 <- data_prep_H5(coded_data_replications)
-# for hypothesis 6
-data_h6 <- data_prep_H6(coded_data_original_shortened, coded_data_replications)
-
-# for hypothesis 1
-data_h1 <- data_prep_H1(coded_data_original_shortened, coded_data_replications)
-# for hypothesis 2
-data_h2 <- data_prep_H2(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, 
-  data_1.12.3.2_clean, data_2.10.1_clean, data_2.12.1_clean, data_2.12.2_clean, 
-  data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, 
-  data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.2_clean, data_3.8.2_clean, 
-  data_5.1.1_clean, data_5.7_clean, data_5.9.1_clean)
-# for hypothesis 3
-data_h3_multiple <- Data_prep_H3_multiple(data_h5, data_h2)
-data_h3_avg <- Data_prep_H3_avg(data_h5, data_h3_multiple)
-
-## graphs
-# plot accompanying the results for Hypotheses 4, 5, & 6.
-plot_456_data <- data_prep_plot_456(data_h6)
-# plot accompanying the results for Hypotheses 4, & 6
-plot_46_data <- data_prep_plot_46(data_h6[c(3, 6, 9, 12, 15, 36, 39, 42, 45, 48)])
-plot_46_data_rev <- data_prep_plot_46(data_h6[c(3, 21, 24, 27, 30, 36, 54, 57, 60, 63)])
-# plot accompanying the results for Hypotheses 2, & 3
-plot_23_data_alpha <- data_prep_plot_23_alpha(data_h3_multiple)
-plot_23_data_omega <- data_prep_plot_23_omega(data_h3_multiple)
-
-### Exporting the final datasets for the analyses
-# the open data
-open_data(data = data_h4, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_h4))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_h4))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_h4))), ".yml"))
-
-open_data(data = data_h6, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_h6))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_h6))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_h6))), ".yml"))
-
-open_data(data = data_h5, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_h5))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_h5))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_h5))), ".yml"))
-
-open_data(data = data_h1, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_h1))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_h1))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_h1))), ".yml"))
-
-open_data(data = plot_456_data, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(plot_456_data))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(plot_456_data))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(plot_456_data))), ".yml"))
-
-open_data(data = plot_46_data, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(Plot_46_data))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(Plot_46_data))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(Plot_46_data))), ".yml"))
-
-open_data(data = plot_46_data_rev, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(plot_46_data_rev))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(plot_46_data_rev))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(plot_46_data_rev))), ".yml"))
-
-open_data(data = data_h2, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_h2))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_h2))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_h2))), ".yml"))
-
-open_data(data = data_h3_multiple, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_h3_multiple))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_h3_multiple))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_h3_multiple))), ".yml"))
-
-open_data(data = data_h3_avg, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_h3_avg))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_h3_avg))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_h3_avg))), ".yml"))
-
-open_data(data = plot_23_data_alpha, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(plot_23_data_alpha))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(plot_23_data_alpha))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(plot_23_data_alpha))), ".yml"))
-
-open_data(data = plot_23_data_omega, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(plot_23_data_omega))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(plot_23_data_omega))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(plot_23_data_omega))), ".yml"))
-
-```
-
-### Analyses Measurement Error
-
-Every hypothesis test in this study used an alpha significance cutoff of .05.
-No correction for multiple testing was applied, to avoid inflating type II error rate.
-The generally small sample size and consequently low power of these analyses meant that a smaller alpha would increase the number of false negatives.
-On top of that, these analyses were considered as exploratory.
-In this exploratory context, the rate of discovery of any potential true effects was given more value relative to decreasing any false positives compared to typical confirmatory research.
-That as a consequence obtaining false positives was more likely has been accepted, as false negatives were deemed more harmful to this study's aims.
-
-The measurement error analyses testing hypotheses 1, 2, & 3 deviated from the preregistration for two main reasons: there were too few reported reliability coefficients, and too few multiple item scalar measures to calculate the reliability coefficients from.
-Because of the small sample size, the test for hypothesis 1 was changed, and the low power as a result of the sample size was accepted for hypothesis 2 & 3.
-This should be kept in mind while interpreting the results from these hypothesis tests.
-
-Thus for testing hypothesis 1, instead of comparing the reported Cronbach's alpha coefficient between original and replication, the total number of reported reliability coefficients were compared instead.
-This total also included reliability coefficients other than Cronbach's alpha.
-This comparison was implemented via a chi-square test using the base R stats package [@R-base].
-
-```{r Hypothesis1Model, include = FALSE}
-# first some descriptives of reliability reporting
-# Measurement type per original and replication:
-H1_descriptive_table_1 <- table(data_h1$rep_org, data_h1$N_items)
-
-# amount of reliability reported per original and replication 
-# (given that measure is a multiple item measure):
-H1_descriptive_table_2 <- table(data_h1$rep_org[data_h1$N_items == "multiple item measure"], data_h1$reliability_type[data_h1$N_items == "multiple item measure"])
-
-# New H1 test
-# A chi square test for difference in N reliability reported for multiple 
-# item measures.
-H1_test_result <- chisq.test(data_h1$rep_org[data_h1$N_items == "multiple item measure"], data_h1$reliability_reported[data_h1$N_items == "multiple item measure"])
-
-```
-
-The number of usable datasets to calculate reliability coefficients from was similarly limited in number.
-However, the number of datasets were still sufficient to be able to estimate the models of the planned analysis for hypothesis 2, albeit with a more exploratory goal than intended.
-
-Using the lmer function from the lme4 package [@R-lme4], a multilevel null model with the Cronbach's alpha or omega coefficient of a replication as dependent was specified, where the random intercept was grouped by replication set.
-The formulas for this model, where $alpha_{ij}$ represents the calculated Cronbach's alpha coefficient of a single study at one lab location with $i = 1,..., n_{locations}$ and $j = 1,...,n_{replications}$ look as follows:
-
-```{=tex}
-\begin{align}
-& Level 1: alpha_{ij} = \beta_{0j} + e_{ij} \qquad\qquad\quad e_{ij} \sim N(0, \sigma_{e}^{2}) (\#eq:level1H2) \\
-& Level 2: \beta_{0j} = \gamma_{00} + u_{0j} \qquad\qquad\qquad u_{0j} \sim N(0, \sigma_{u0}^{2}) (\#eq:level2H2) \\
-& Mixed: alpha_{ij} = \gamma_{00} + u_{0j} + e_{ij} (\#eq:mixedH2)
-\end{align}
-```
-```{r Hypothesis2Model, include = FALSE}
-# intercept only model to check the within and between group variance.
-H2_test_result_alpha <- lmer(formula = alpha ~ 1 + (1|g), data = data_h2)
-
-# and same analyses for omega
-# intercept only model to check the within and between group variance.
-H2_test_result_omega <- lmer(formula = omega ~ 1 + (1|g), data = data_h2[complete.cases(data_h2),])
-
-```
-
-The purpose of this analysis was to investigate variability in calculated reliability coefficients within and between replication sets.
-However, to the author's knowledge no formal test exists as of the writing of this thesis for testing the significance of within group variance after controlling for between group variance.
-Instead the intraclass correlation (ICC) coefficient was calculated an indicator of within vs.
-between variability.
-The formula used to calculate the ICC is presented below.
+The originally planned analysis made use of beta-regression similarly to the test for H4 and H6.
+The variables are the same as those used in the test published in the article, just swapped from IV to DV, and from DV to IV.
 
@@
 \begin{equation}
-ICC = \frac{u_{0j}}{(e_{ij} + u_{0j})} (\#eq:ICC)
+g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replicated_{i} (\#eq:H5AppendixA)
 \end{equation}
 ```
-A high ICC indicates low within group variance relative to between group variance, which would be in line with hypothesis 2.
+Where $g(.)$ refers to the same link function as described in formula \@ref(eq:BetaLink) in the article.
 
-```{r ICCCalculations, include = FALSE}
-# alpha
-within_group_variance_alpha <- attr(VarCorr(H2_test_result_alpha), "sc")^2
-between_group_variance_alpha <- attr(VarCorr(H2_test_result_alpha)$g, "stddev")^2
+```{r H5 beta-regression pre-registration model}
+## Hypothesis 5 beta regression model ADD FIRST PART TO INITIAL PROTOCOL RESULTS
+H5_prereg_test_results <- betareg(QMP_ratio ~ hypothesis_support, data = data_h5)
+H5_prereg_test_results_with_OR <- OR_to_apa_full_supplier(betareg_output_to_apa_full(H5_prereg_test_results), negative_b = TRUE)
 
-ICC_alpha <- between_group_variance_alpha / (within_group_variance_alpha + between_group_variance_alpha)
-
-# omega
-within_group_variance_omega <- attr(VarCorr(H2_test_result_omega), "sc")^2
-between_group_variance_omega <- attr(VarCorr(H2_test_result_omega)$g, "stddev")^2
-
-ICC_omega <- between_group_variance_omega / (within_group_variance_omega + between_group_variance_omega)
-
+H5_prereg_test_results_REV <- betareg(QMP_REV_ratio ~ hypothesis_support, data = data_h5)
+H5_prereg_test_results_REV_with_OR <- OR_to_apa_full_supplier(betareg_output_to_apa_full(H5_prereg_test_results_REV))
 ```
 
-In order to test hypothesis 3, the average calculated Cronbach's alpha level within a replication set is used as a predictor of replication success.
-Replication success was either set to 1 if it reached meta analytic significance at an alpha of .05 in the same direction as that found in the original study, or 0 otherwise.
-This test aligns with a logistic regression model.
-With $i = 1,..., n_{replications}$, $p_{replicated}$ being binomially distributed, and $alpha$ referring to the averaged calculated Cronbach's alpha coefficient, the following regression equation was used to model the relation:
+## Results
 
-```{=tex}
-\begin{equation}
-f(replicated_{i}) = \beta_{0} + \beta_{1} alpha_{i} (\#eq:H3Main)
-\end{equation}
-```
-Where:
+With this model specification the relationship between the two variables remains negative and significant (`r H5_prereg_test_results_REV_with_OR`).
 
-```{=tex}
-\begin{equation}
-f(.) = log\frac{p_{replicated}}{1 - p_{replicated}} (\#eq:LogitLink)
-\end{equation}
-```
-```{r Hypothesis3MainTest, include = FALSE}
-## The main model to test hypothesis 3, through a logistic regression model.
-H3_test_result_main_alpha <- apa_print(glm(formula = replication ~ 1 + alpha, 
-                                      family = binomial(), data = data_h3_avg))
+## Unidimensionality Exploratory Analyses
 
-# and for omega
-H3_test_result_main_omega <- apa_print(glm(formula = replication ~ 1 + 
-                                     omega, family = binomial(), 
-                                     data = data_h3_avg))
+### Pre-registration Analysis Justification & Reason for Omission from Article
 
-# alpha says negative, omega says positive, neither are significant though.
+In order to present additional validity evidence alongside the analyses of Cronbach's alpha and omega coefficients, the unidimensionality of each measure was investigated.
+To test this, each multiple item scalar measure had their factor structure investigated on the entire measure data of the replication set.
 
-```
+This analysis was omitted from the main article due to the fact that determining when a measure should be unidimensional would require an in-depth review and expert evaluation for the literature surrounding the measure, which is outside of the scope of this article and the authors' expertise (it additionally may not always be available).
 
-In this data, replication attempts at different lab locations can be seen as nested within a replication set.
-In order to see if this nesting might impact the analyses of hypothesis 3, multilevel logistic regression models were included as sensitivity checks.
-The dependent variable remains replication success at the replication set level, while Cronbach's alpha is no longer averaged across locations.
-The models used were a multilevel logistic random intercept and random slope model.
+For the sake of this analysis the simple heuristic was chosen that if the measure was used as a single composite variable in the analyses, then it should be uni-dimensional.
+This is similar to what was done by ..., but for the sake of this article it was deemed to strong an assumption to make that this heuristic would always hold.
+For instance, IQ score is often used as a single indicator score, however the construct of IQ is not considered unidimensional, and is instead understood to have many sub-dimensions (e.g.
+verbal comprehension, perceptual reasoning, etc.).
+As a result, the use of a single score in the analyses cannot be taken as evidence that the construct is considered unidimensional by the authors, or broader literature on the topic.
 
-```{r Hypothesis3MultilevelModelSensitivityAnalyses, include = FALSE}
-## sensitivity analyses.
-# running a random intercept multilevel logistic model
-H3_test_result_int_sensitivity_alpha <- apa_print(glmer(formula = replication ~ 1 
-                                                + alpha + (1|g), family = 
-                                                binomial(), data = 
-                                                data_h3_multiple))
+Nevertheless, we present here the result of the analyses made under the assumption that the one score, one dimension heuristic holds, for those researchers that believe this heuristic to not undermine the relevance of these results in provding some valid information on the validity of the measures used in the Many Labs projects.
 
-# and for omega
-H3_test_result_int_sensitivity_omega <- apa_print(glmer(formula = replication ~ 1 
-                                                + omega + (1|g), family = 
-                                                  binomial(), data = 
-                                                  data_h3_multiple))
+## models
 
-# same as for non-multilevel model
-
-# running a random slope multilevel logistic model
-H3_test_result_slp_sensitivity_alpha <- apa_print(glmer(formula = replication ~ 1 
-                                                + alpha + (1 + alpha|g), 
-                                                family = binomial(), data =
-                                                data_h3_multiple))
-
-# and for omega
-H3_test_result_slp_sensitivity_omega <- apa_print(glmer(formula = replication ~ 1 
-                                                + omega + (1 + omega|g), 
-                                                family = binomial(), data =
-                                                data_h3_multiple))
-
-# alpha did not converge, and omega shows no significant effect.
-```
-
-### Analyses QMPs
-
-The reported analyses were primarily based on the revised set of QMP data.
-The results using the original QMP data are mentioned when the results led to different conclusions.
-The analysis code for both the original and revised QMP data are available in the R script on both the OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages of this article.
-
-Hypothesis 4, 5, & 6 were all tested using a model with the same dependent variable: total QMP ratio.
-In order to model a ratio dependent variable, beta regression was used.
-Beta regression models operate similarly to standard generalized linear models with similar interpretations of the results.
-What differentiates them is that they are suitable to model dependent variables with values in the interval of $(0, 1)$, meaning ratios.
-Furthermore, they are well suited for modelling heteroskedastic and asymmetrically distributed dependent variables [@cribari2010beta].
-The beta regression model was implemented using the betareg function within the betareg package [@R-betareg_a; @R-betareg_b].
-Defaults were used for all function parameters besides the model formula and data.
-All beta regression models used the beta link function, which is as follows:
-
-```{=tex}
-\begin{equation}
-g(.) = (0, 1) \mapsto \mathbb{R} (\#eq:BetaLink)
-\end{equation}
-```
-All of these models assume that the QMPs are the same across each replication set.
-The reason being that only one protocol was analysed per replication set, and several of the questions regarding QMPs focus solely on the reporting of relevant measurement information.
-This assumption was deemed likely, since each replication within a set was based on the same protocol.
-Furthermore, the goal of these protocols is to ensure that the measurement practices are equal across the different replication studies of the same original effect.
-
-To test hypothesis 4, the total QMP ratios between replication and original research was compared. The model formula for this test looked as follows:
-
-```{=tex}
-\begin{equation}
-g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replication_{i} (\#eq:H4Main)
-\end{equation}
-```
-```{r Hypothesis4Model, include = FALSE}
-## Hypothesis 4 beta regression model
-# running the model with none revised QMP ratio's
-H4_test_results <- betareg(QMP_ratio ~ rep_org, data = data_h4)
-
-# running the models with revised QMP ratio's
-H4_test_results_REV  <- betareg(QMP_REV_ratio ~ rep_org, data = data_h4)
-
-```
-
-Where $replication_{i}$ is a dummy coded variable, which was coded as 1 in case the reported QMP ratio belonged to a replications, and 0 if it belonged to an original study.
-For hypothesis 5 a similar formula was used:
-
-```{=tex}
-\begin{equation}
-g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replicated_{i} (\#eq:H5Main)
-\end{equation}
-```
-Where $replicated_{i}$ is a dummy coded variable, which was coded as 1 if the meta-analytic effect in the replication set matches the original effect in direction at a significance alpha level of .05, and 0 otherwise.
-Note here that unlike in the test for hypothesis 4, $QMP\_ratio_{i}$ refers only to the QMP ratios of the replications, meaning that original article QMPs were not included in this analysis.
-
-```{r Hypothesis5Model, include = FALSE}
-## Hypothesis 5 beta regression model
-H5_test_results <- betareg(QMP_ratio ~ hypothesis_support, data = data_h5)
-
-H5_test_results_REV <- betareg(QMP_REV_ratio ~ hypothesis_support, data = data_h5)
-
-```
-
-The relationship between original article QMPs and replication protocol QMPs was modelled to test hypothesis 6.
-The outcome variable remains the same as in the model for hypothesis 5.
-The independent variable is changed to the QMP ratio for original articles.
-The resulting model formula is as follows:
-
-```{=tex}
-\begin{equation}
-g(QMP\_ratio\_replication_{i}) = \beta_{0} + \beta_{1} QMP\_ratio\_original_{i} (\#eq:H6Main)
-\end{equation}
-```
-```{r Hypothesis6Model, include = FALSE}
-## Hypothesis 6 beta regression model
-H6_test_results <- betareg(Rep_QMP_ratio ~ QMP_ratio, data = data_h6)
-
-H6_test_results_REV <- betareg(Rep_QMP_REV_ratio ~ QMP_REV_ratio, data = data_h6)
-
-```
-
-These models had independence of observations as another assumption, the observations here referring to a replication set.
-this is known to be false since the data is nested within four separate Many Labs projects.
-In order to test if this nested structure might influence the relations described in hypothesis 5 & 6, random intercept and random slope multilevel models were implemented as sensitivity analyses for the tests of both hypothesis 5 & 6.
-In these models each replication set was treated as being nested in its respective Many Labs project.
-Worth noting is that currently the betareg package does not allow for estimation of multilevel models.
-As an approximation, Gaussian random-intercept multilevel models were implemented using the lmer function from the lme4 package [@R-lme4].
-The outcome QMP ratio variable was transformed using the logit link function (the default link function in the betareg package) to better fit the Gaussian model.
-
-```{r Hypotheses5&6SensitivityAnalyses, include = FALSE}
-## Hypothesis 5 sensitivity test using a random intercept Guassian model.
-# create dummy H5 dataframe for use in sensitivity test
-data_h5_sens <- data_h5
-
-# convert outcome variable to be usable with Gaussian distribution via
-# logit transform.
-data_h5_sens$QMP <- log(data_h5_sens$QMP_ratio /(1 - data_h5_sens$QMP_ratio))
-data_h5_sens$QMP_REV <- log(data_h5_sens$QMP_REV_ratio /(1 - data_h5_sens$QMP_REV_ratio))
-
-check_h5 <- apa_print(lmer(formula = QMP ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens))
-
-check_h5_REV <- apa_print(lmer(formula = QMP_REV ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens))
-
-## Hypothesis 6 sensitivity test using a random intercept Guassian model.
-# create dummy H6 dataframe for use in sensitivity test
-data_h6_sens <- data_h6
-
-# convert outcome variable to be usable with Gaussian distribution via
-# logit transform.
-data_h6_sens$QMP <- log(data_h6_sens$QMP_ratio /(1 - data_h6_sens$QMP_ratio))
-data_h6_sens$Rep_QMP <- log(data_h6_sens$Rep_QMP_ratio /(1 - data_h6_sens$Rep_QMP_ratio))
-data_h6_sens$QMP_REV <- log(data_h6_sens$QMP_REV_ratio /(1 - data_h6_sens$QMP_REV_ratio))
-data_h6_sens$Rep_QMP_REV <- log(data_h6_sens$Rep_QMP_REV_ratio /(1 - data_h6_sens$Rep_QMP_REV_ratio))
-
-# running the models one with none revised QMP ratio's and one with
-check_h6 <- apa_print(lmer(formula = Rep_QMP ~ 1 + QMP + (1|many_labs_version), data = data_h6_sens))
-
-check_h6_REV <- apa_print(lmer(formula = Rep_QMP_REV ~ 1 + QMP_REV + (1|many_labs_version), data = data_h6_sens))
-
-# n of mod ratio's that are present (check)
-H6_n_check_results <- betareg(Rep_op_ratio ~ mod_ratio, data = data_h6)$n
-H6_n_check_results_REV <- betareg(Rep_op_REV_ratio ~ mod_REV_ratio, data = data_h6)$n
-
-```
-
-```{r Hypothesis6Associations, include = FALSE}
-## Associations between the QMP categories
-# associations are generated using a helper function available in the source_ 
-# script. These associations correspond to the coefficients between replication
-# and original article QMPs of the various QMP types, as estimated through a 
-# beta regression.
-# Associations between the QMP categories (original QMP coding)
-Results_H6_between <- Associations_H6(data_h6)
-
-# keep in mind mod_ratio (not Rep) is based on a very small sample size, less
-# of a concern for the revised.
-
-# Associations between the QMP categories (revised QMP coding)
-Results_H6_between_REV <- Associations_H6_REV(data_h6)
-
-```
-
-### Exploratory Analyses {#ExploratoryAnalyses}
-
-Follow-up analyses were preregistered for hypothesis 6.
-Using a similar model to the main hypothesis test with all unique combination of the five different QMP types being tested across original and replication data.
-The goal of these analyses was to see if there are any type specific carry-over effects in QMPs between original and replication.
-As these analyses are exploratory in nature, due to the large number of tests, the focus was on visualisation rather than inference.
-
-Finally, in order to present additional validity evidence alongside the analyses of Cronbach's alpha and omega coefficients, the unidimensionality of each measure was investigated.
-To test this, each multiple item scalar measure had their factor structure investigated on the entire measure data of the replication set.
 A single factor confirmatory factor analysis was implemented using the *fa* function from the *psych* package [@R-psych] in R.
@@
 ```{r UnidimensionalityExploratoryAnalysis, include = FALSE}
-extracted_data_list <- list(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean,
-                            data_1.12.3.2_clean, data_2.10.1_clean,
-                            data_2.12.1_clean, data_2.12.2_clean, 
-                            data_2.12.3_clean, data_2.15_clean, data_2.20_clean,
-                            data_2.23_clean, data_3.2.1.1_clean, 
-                            data_3.2.1.2_clean, data_3.7.1_clean, 
-                            data_3.7.2_clean, data_3.8.2_clean,
-                            data_5.1.1_clean, data_5.7_clean, data_5.9.1_clean)
+extracted_data_list <- list(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, data_1.12.3.2_clean,data_2.12.1_clean, data_2.12.2_clean, data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.1_clean, data_3.7.2_clean, data_3.8.2_clean, data_5.1.1_clean, data_5.1.2_clean, data_5.7_clean, data_5.9.1_clean)
 
@@
 
-# Results
+## Results
 
-## Descriptives
+Suitable data for factor analyses was available for `r nrow(cfa_results_expanded)` measures.
+These measures were the same as those shown in Figure \@ref(fig:Plot23AlphaCode).
+The results are shown in Table \@ref(tab:UnidimesnionalityTestResultsTable).
+A composite score based on the measurement responses was used for sixteen of the `r nrow(cfa_results_expanded)` measures to form a single variable in the analyses, and were thus regarded as intended to be unidimensional.
+The number of dimensions for the remaining three were unclear.
+Sufficient fit of the unidimensional model was found for six out of the `r nrow(cfa_results_expanded)` evaluated measures.
+However, as shown in Table \@ref(tab:UnidimesnionalityTestResultsTable) the unidimensional model held based on the parallel analysis test alone, for only `r sum(cfa_results_expanded$`N Factors`== 1, na.rm = TRUE)` of the `r nrow(cfa_results_expanded)` measures.
+For those `r sum(cfa_results_expanded$`N Factors`== 1, na.rm = TRUE)` measures and an additional `r sum(cfa_results_expanded$RMSEA < .08, na.rm = TRUE) - sum(cfa_results_expanded$`N Factors`== 1, na.rm = TRUE)` the RMSEA $< .08$ criteria suggested evidence for single factor structures.
 
-The mean sample size within the replications was `r apa_num(mean(coded_data_replications$N, na.rm = TRUE), digits = 0)` participants (IQR = `r apa_num(IQR(coded_data_replications$N, na.rm = TRUE), digits = 0)`).
-In the original articles the mean sample size was `r apa_num(mean(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)` (IQR = `r apa_num(IQR(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)`).
-In total, support was found for hypothesized effects of `r apa_num(table(coded_data_replications$hypothesis_support)["Yes"], digits = 0)` of the `r apa_num(nrow(coded_data_replications), digits = 0)` measures.
-Proportions of replication success per Many Labs project can be found in Table \@ref(tab:ReplicationRatioTable).
+```{r UnidimesnionalityTestResultsTable, warning = FALSE}
+# add the names of the relevant papers and a shortcut for the measure used.
+cfa_results_expanded <- cbind(c("Caruso et al.
+(2012)", "Husnu & Crisp (2010)", "Nosek et al.
+(2002), Art", "Nosek et al.
+(2002), Math", "Anderson et al.
+(2012), SWL", "Anderson et al.
+(2012), PA", "Anderson et al.
+(2012), NA", "Giessner & Schubert (2007)", "Norenzayan et al.
+(2002)", "Zhong & Liljenquist (2006)", "Monin & Miller (2001), most", "Monin & Miller (2001), some", "Cacioppo et al.
+(1983), elm", "Cacioppo et al.
+(1983), nfc", "De Fruyt et al.
+(2000), consc", "Albarracín et al.
+(2008), exp.
+5, math", "Albarracín et al.
+(2008), exp.
+5, verb",  "Shnabel & Nadler (2008)", "Vohs & Schooler (2008)"), cfa_results)
 
-```{r ReplicationRatioTable, warning = FALSE}
-# construct the replication ratio table to be printed
-replication_ratio_table <- data.frame("Many Labs Version" = c("1", "2", "3", "5", "Total"),
-                                      "N Total" = c(table(coded_data_replications$many_labs_version), nrow(coded_data_replications)), 
-                                      "N Replicated" = c(table(coded_data_replications$many_labs_version, coded_data_replications$hypothesis_support)[, "Yes"], table(coded_data_replications$hypothesis_support)["Yes"]))
+# adding sensible column names
+colnames(cfa_results_expanded) <- c("Original Article", "RMSEA", "N Factors", "Unidimensional")
 
-# calculate the replication ratio from the N measures whose studies were replicated
-# and the N total measures, per Many Labs study.
-replication_ratio_table$"Replication Ratio" <- replication_ratio_table$N.Replicated / replication_ratio_table$N.Total
-
-# Changing column names to be less computer speak-y looking
-colnames(replication_ratio_table) <- c("Many Labs Version", "N Total", "N Replicated",
-                                       "Replication Ratio")
-
-# converting columns to string to then add a superscript to one of the elements
-# in the table.
-replication_ratio_table$"N Replicated" <- as.character(replication_ratio_table$"N Replicated")
-
-# adding a superscript for a later footnote
-replication_ratio_table$"N Replicated"[3] <- "$3^a$"
+# Renaming the columns for the not converged cfa.
+cfa_results_for_print <- cfa_results_expanded
+cfa_results_for_print$RMSEA[15] <- "Did"
+cfa_results_for_print$`N Factors`[15] <- "Not"
+cfa_results_for_print$Unidimensional[15] <- "Converge"
 
@@
 apa_table(
-  replication_ratio_table, align = c("l", "r", "r", "r")
-  , caption = "Ratio of measures for which the effect was considered replicated, across many labs projects"
-  , note = "$^a$replication was assessed as unclear for three of the measures, since their effect was not fully replicated.
-These have been treated as not replicated within this table and further analyses throughout the article"
-  , escape = FALSE, placement = "htp", midrules = 4)
+  cfa_results_for_print, align = c("l", "r", "r", "r")
+  , caption = "RMSEA and Parallel Analysis Suggested Factors based on Factor Analysis
+for Measure Data", note = "N Factors refer to the number of factors suggested based on parallel analysis of the measure data.
+The word or abbreviation after the author names and year indicates the specific measure within that original article that was analysed.", escape = FALSE, row.names = FALSE, placement= "htp")
 
@@
 
-Existing materials were used for `r apa_num(table(coded_data_replications$sel_existing)["True, namely:"], digits = 0)` of the `r apa_num(nrow(coded_data_replications), digits = 0)` measures in replications and for `r apa_num(table(coded_data_original_shortened$sel_existing)["True, namely:"], digits = 0)` in original studies.
-The specific version of the measure was reported for `r apa_num(length(coded_data_replications$op_version[coded_data_replications$op_version != ""]), numerals = FALSE)` measures in replications, and `r apa_num(length(coded_data_original_shortened$op_version[coded_data_original_shortened$op_version != ""]), numerals = FALSE)` measures in original articles.
-For those measures that were not based on existing materials, `r apa_num(table(coded_data_replications$sel_existing)["False, materials were newly developped for this study"], numerals = FALSE)` in the replications and `r apa_num(table(coded_data_original_shortened$sel_existing)["False, materials were newly developped for this study"], numerals = FALSE)` in original articles clearly stated that they were newly created for the study.
-Only `r apa_num(table(coded_data_original_shortened$mod_time)["After/During"], numerals = FALSE)` measure in the original articles was modified from its original source during the data collection period, all other measures were modified before that, if at all.
+## H6 QMP-Category Specific Exploratory Analyses
 
-## Reliability
+### Pre-registration Analysis Justification & Reason for Omission from Article
+Follow-up analyses were preregistered for hypothesis 6.
+Using a similar model to the main hypothesis test with all unique combination of the five different QMP types being tested across original and replication data.
+The goal of these analyses was to see if there are any type specific carry-over effects in QMPs between original and replication.
+Due to the large number of tests, the focus was exploratory using visualisation rather than inference.
 
-Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts the type of measure (single-item, multiple item, or not a scale), if for the measure reliability was reported or not, and what type of reliability coefficient was reported.
-Reliabilities were only assessed for multiple item measures, which were approximately equal between replication and original (`r apa_num(table(coded_data_replications$N_items)["multiple item measure"])` and `r apa_num(table(coded_data_original_shortened$N_items)["multiple item measure"])`, respectively).
-Looking at the multiple item measures, `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` in the replication protocols and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles reported a reliability coefficient.
-The most commonly reported reliability coefficient was Cronbach's alpha, which accounted for `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles.
+It is partly this large number of tests, as well as the resulting lack of clear interpretability in the results that caused this analysis to be omitted from the main article.
+However, for completeness and transparency sake it is reported here.
 
-```{r ReliabilityReportingFlowDiagram, fig.cap = "Reliability reporting flow diagram."}
-knitr::include_graphics(path = "../../SupplementaryMaterials/reliability_reporting_flow_diagram.png")
-```
+### Model
+The model was the same as that used for the main test of hypothesis 6 (see formula \@ref(eq:H6Main)), only now QMP_ratio's for each of the five categories were used one at a time for each unique combination of original article and replication protocol QMP.
 
-A chi-squared test compared whether the number of reliabilities reported among multiple item measures differed between replications and original.
-Reliabilities were found to be more commonly reported in original articles compared to replication protocols ($\chi^{2}$(`r apa_num(H1_test_result$parameter)`) = `r apa_num(H1_test_result$statistic)`, *p* = `r apa_p(H1_test_result$p.value)`).
-These results are contradictory to hypothesis 1.
+```{r Hypothesis6Associations, include = FALSE}
+## Associations between the QMP categories
+# associations are generated using a helper function available in the source_ 
+# script. These associations correspond to the coefficients between replication
+# and original article QMPs of the various QMP types, as estimated through a 
+# beta regression.
+# Associations between the QMP categories (original QMP coding) MOVE THIS ANALYSIS TO INITIAL CODING APPENDIX
+Results_H6_between <- Associations_H6(data_h6)
 
-The average Cronbach's alpha coefficient across replication sets was `r apa_num(mean(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(mean(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`, for omega the mean was `r apa_num(sd(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`.
-Figure \@ref(fig:Plot23AlphaCode) shows the distributions of the Cronbach's alpha coefficients for each replication set separated by successful and unsuccessful replication.
+# keep in mind mod_ratio (not Rep) is based on a very small sample size, less
+# of a concern for the revised.
 
-```{r Plot23AlphaCode,warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the eighteen distinct measures for which suitable raw data was available to calculate Cronbach’s alpha coefficients from."}
-# plot for alpha
-ggplot(plot_23_data_alpha, aes(x = alpha, y = g)) +
-  geom_boxplot(outlier.shape = NA) +
-  geom_hline(yintercept = 6.5, color = "red", size = 1) +
-  geom_point(alpha = 0.1) +
-  theme_minimal() +
-  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), 
-                                                     "lines")) +
-  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0),
-    ymin = 7, ymax = 7, xmin = 1.08, xmax = 1.08) +
-  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0),
-    ymin = 6, ymax = 6, xmin = 1.08, xmax = 1.08) +
-  coord_cartesian(xlim = c(0, 1), clip = "off") +
-  ylab("") +
-  xlab("Cronbach's alpha")
+# Associations between the QMP categories (revised QMP coding)
+Results_H6_between_REV <- Associations_H6_REV(data_h6)
 
@@
 
-```{r Plot23OmegaCode, include = FALSE, eval = FALSE}
-# plot for omega
-ggplot(plot_23_data_omega, aes(x = alpha, y = g)) +
-  geom_boxplot(outlier.shape = NA) +
-  geom_hline(yintercept = 6.5, color = "red", size = 1) +
-  geom_point(alpha = 0.1) +
-  theme_minimal() +
-  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), 
-                                                     "lines")) +
-  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0),
-    ymin = 6, ymax = 6, xmin = 1.08, xmax = 1.08) +
-  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0),
-    ymin = 5, ymax = 5, xmin = 1.08, xmax = 1.08) +
-  coord_cartesian(xlim = c(0, 1), clip = "off") +
-  ylab("") +
-  xlab("Omega")
-```
+### Results
+Planned exploratory analyses were preformed to expand on the test for hypothesis 6.
+The relationships between original article QMP ratios and replication protocol QMP ratios were investigated for each QMP type separately.
+Figure \@ref(fig:Plot46RevisedDataCode) visually illustrates the relations of the revised QMP ratios from different QMP types between replication protocols and original articles.
+As shown in the figure, no relation was strong and highly stable, and even fewer were consistent between initial and revised coding protocols.
 
-The between-group (across different replication set) variance and within-group (lab locations within a replication set) variance in the Cronbach's alpha coefficient were assessed using a multilevel model as specified in Formulas \@ref(eq:level1H2), \@ref(eq:level2H2), & \@ref(eq:mixedH2) The between-group and within-group variance for Cronbach's alpha were approximately `r apa_num(between_group_variance_alpha, digits = 3)` and `r apa_num(within_group_variance_alpha, digits = 3)` respectively.
-The resulting ICC, obtained using formula \@ref(eq:ICC), was approximately `r apa_num(ICC_alpha, digits = 3)`.
-This suggests that variance was larger between replication sets than within.
-The same analysis for omega coefficients even showed a relatively larger degree of between group variance (between-group variance `r apa_num(within_group_variance_omega, digits = 3)`, within-group variance `r apa_num(between_group_variance_omega, digits = 3)`, ICC = `r apa_num(ICC_omega, digits = 3)`).
-Both results are in line with hypothesis 2, although caution in interpreting this result is advised due to the small sample size and the lack of an available inferential test.
-
-The relationship between reliability and replication success was primarily tested via logistic regression, with replication success as the dependent variable.
-Further sensitivity analyses were performed using multilevel logistic models, with each measure as an overarching group wherein its reliability at each lab location is nested.
-The results of the logistic and multilevel logistic models are shown in Table \@ref(tab:ReplicabilityReliabilityTestTable) for both Cronbach's alpha and omega reliability coefficients.
-
-```{r ReplicabilityReliabilityTestTable, warning = FALSE}
-# creating the dtaframe for the table
-H3_table_dataframe <- rbind(H3_test_result_main_alpha$table, H3_test_result_int_sensitivity_alpha$table, H3_test_result_main_omega$table, H3_test_result_int_sensitivity_omega$table, H3_test_result_slp_sensitivity_omega$table)
-
-# adding an asterix for significance to the significant p in the dataframe
-H3_table_dataframe[3,5] <- paste0(H3_table_dataframe[3,5], "$^*$")
-
-# adding rows to give indication of specific sections (apa_table being awkward)
-H3_table_for_printing <- rbind(c("Alpha", "", "", "", ""), c("Logistic Regression Model", "", "", "", ""), H3_table_dataframe[1:2,], c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(3:4),], c("Omega", "", "", "", ""), c("Logistic Regression Model", "", "", "", ""), H3_table_dataframe[(5:6),], c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(7:8),], c("Random-Slope Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(9:10),])
-
-# print the table in apa formatting
-apa_table(
-  H3_table_for_printing, align = c("l", "r", "r", "r", "r")
-  , caption = "Model Results from Tests of Hypothesis 3"
-  , note = "The Alpha and Omega sections show the models where the independent variable was the calculated Cronbach's alpha and omega coefficient respectively.
-The random slope model for Cronbach's alpha did not converge, thus it results are not shown here.
-$^* p < .05$"
-  , escape = FALSE, placement= "htp", midrules = c(1, 2, 5, 7, 8, 9, 12, 15))
-
-```
-
-Cronbach's alpha and omega did not significantly relate to replication success in the main logistic regression model (Cronbachs alpha: `r H3_test_result_main_alpha$full_result$alpha`; omega: `r H3_test_result_main_omega$full_result$omega`), nor in any of the multilevel sensitivity analyses models (see Table \@ref(tab:ReplicabilityReliabilityTestTable)).
-This is contradictory to the expectation in hypothesis 3.
-However, the results from these analyses should be evaluated with caution, given the small sample number of measures used to estimate these models.
-
-## Questionable Measurement Practices
-
-The counts of the QMP ratio obtained for each QMP type (see Table \@ref(tab:QMPCodingInfoTable)) are shown across the top layer of Figure \@ref(fig:Plot456Code) for both replication protocols and original articles.
-The overall number of counts for the QMP ratios of the QMP modification type were lower compared to the others, because only `r apa_num(table(coded_data_replications$mod_check)["True"])` out of `r apa_num(length(coded_data_replications$mod_check))` measures in replications, and only `r apa_num(table(coded_data_original_shortened$mod_check)["True"], numerals = FALSE)` measures used in original studies were modified.
-The bottom layer of Figure \@ref(fig:Plot456Code) shows the overlayed distributions of the total QMP ratios from the replication protocols and original studies, with dots indicating each datapoint, and the line indicating the mean for either distribution.
-
-```{r Plot456Code, warning = FALSE, fig.cap = "QMP ratio counts for each QMP Type and QMP total ratio distribution grouped by where each was coded from.
-The top row shows binned counts of QMP ratio’s that were observed for each replication protocol and original article, across the different QMP types.
-The bottom graph shows the distributions of total QMP ratios for both replication protocols and original articles, with the line indicating the mean QMP ratio.
-The specific observed values are indicated along the bottom row with dots"}
-# plot for alpha
-### ratio (REV) Original and Rep
-Plot_456_1 <- ggplot(plot_456_data[plot_456_data$QMP_type != "Total",], 
-       aes(x = QMP_ratio, fill = RepOrg)) + 
-  geom_bar(position = "dodge", stat = "bin", bins = 10) +
-  facet_grid(~QMP_type) +
-  theme_minimal() +
-  theme(plot.title = element_text(face = "bold")) +
-  scale_fill_manual(values=c("brown", "blue4")) +
-  theme(legend.position = "none") +
-  ylab("Count") +
-  xlab("QMP Ratio") +
-  ggtitle("QMP Ratio's Per QMP Type Grouped by Original and Replication") +
-  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1"))
-
-Mean_Rat_Rep <- mean(plot_456_data$QMP_ratio[
-  plot_456_data$QMP_type == "Total" & plot_456_data$RepOrg == "Replication"])
-Mean_Rat_Org <- mean(plot_456_data$QMP_ratio[
-  plot_456_data$QMP_type == "Total" & plot_456_data$RepOrg == "Original"])
-
-Plot_456_2 <- ggplot(plot_456_data[plot_456_data$QMP_type == "Total",], 
-       aes(x = QMP_ratio, fill = RepOrg, colour = RepOrg)) +
-  geom_density(alpha = 0.2) +
-  geom_point(y = 0, alpha = 0.2, size = 3) +
-  geom_segment(aes(x = Mean_Rat_Rep, xend = Mean_Rat_Rep, y = 0, yend = 2.66)
-               , color = "blue4") +
-  geom_segment(aes(x = Mean_Rat_Org, xend = Mean_Rat_Org, y = 0, yend = 2.183)
-               , color = "brown") +
-  coord_cartesian(xlim = c(0, 1)) +
-  theme_ridges() + 
-  theme(axis.text.y=element_blank(),
-        axis.ticks.y=element_blank()) +
-  scale_fill_manual(values=c("brown", "blue4")) +
-  scale_color_manual(values=c("brown2", "blue")) +
-  scale_x_continuous(breaks = c(0, Mean_Rat_Rep, 0.25, Mean_Rat_Org, 
-                                0.5, 0.75, 1), 
-                     labels = c("0", "0.18", "0.25", "0.31", "0.5", 
-                                "0.75", "1")) + 
-  ggtitle("Distribution of Total QMP Ratio's by Original and Replication") +
-  guides(color = "none") +
-  labs(fill = "Coded from") +
-  ylab("") +
-  xlab("")
-
-# combine both plots into one figure
-grid.arrange(Plot_456_1, 
-             Plot_456_2, 
-             nrow = 2)
-
-```
-
-Beta-regression was used to test the difference in QMP ratio between original articles and replication protocols.
-Results showed that original articles contained a significantly larger proportion of QMPs than replication protocols for the measures of the same effects (`r betareg_output_to_apa_full(H4_test_results_REV)`).
-This result is in line with hypothesis 4.
-
-A similar beta-regression tested the association between replication success and QMP ratio in replication protocols.
-Results showed that successful replication significantly related to a decrease in the ratio of QMPs in replication protocols (`r betareg_output_to_apa_full(H5_test_results_REV)`).
-Sensitivity analyses were performed using a random-intercept multilevel regression function.
-This model also found a significant association between replication success and QMP ratio (`r check_h5_REV$full_result$hypothesis_supportTRUE`).
-Both of these results are in line with hypothesis 5.
-However, the relationship in the multilevel model is no longer significant for QMP ratios obtained with the initial coding protocol (`r check_h5$full_result$hypothesis_supportTRUE`).
-
-The relation between QMP ratios in the replication protocols and corresponding original articles were investigated using a beta regression model.
-It showed that total QMP ratio in the original article can significantly predict total QMP ratio in the subsequent replication (`r betareg_output_to_apa_full(H6_test_results_REV)`), which provides some evidence in favor of hypothesis 6.
-However, this relation was not significant for the QMP ratios obtained with the initial protocol (`r betareg_output_to_apa_full(H6_test_results)`).
-Sensitivity analyses using a random intercept logistic multilevel model also found some discrepancy in results between revised and initial protocol, albeit with both being non-significant (revised protocol: `r check_h6_REV$full_result$QMP_REV`; initial protocol `r check_h6$full_result$QMP`).
-
-```{r Plot46InitialDataCode, include = FALSE, eval = FALSE, error = FALSE}
-# Initial
-ggplot(plot_46_data, aes(QMP_ratio, QMP_Rep_ratio)) + 
-  geom_point() +
-  geom_jitter(width = 0.05, height = 0.05) +
-  stat_smooth(method="lm") + 
-  theme_bw() +
-  theme(strip.text.y = element_text(size = 7), strip.background = element_rect(
-    color = "black", fill = "white", size = 1, linetype = "solid"
-  )) +
-  xlab("QMP Ratio (Original)") + ylab("QMP Ratio (Replication)") +
-  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1")) + 
-  facet_grid(vars(QMP_Rep_type), vars(QMP_type))
-
-```
-
-```{r Plot46RevisedDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication QMP ratio’s per type with linear regression line.
+```{r Plot46FullRevisedDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication QMP ratio’s per type with linear regression line.
 The abbreviations on the axes relate to the QMP categories described in Table 1: Def.
@@
 ```
-
-## Exploratory Results
-
-Planned exploratory analyses were preformed to expand on the test for hypothesis 6.
-The relationships between original article QMP ratios and replication protocol QMP ratios were investigated for each QMP type separately.
-Table \@ref(tab:H6ExploratoryAssociationsRevisedTable) shows the results from these tests with the revised protocol QMP coding, while Table \@ref(tab:H6ExploratoryAssociationsInitialTable) shows the results for the QMP ratios obtained via the initial protocol.
-There were few significant relations and even fewer that are consistent between both coding protocols.
+Table \@ref(tab:H6ExploratoryAssociationsRevisedTable) shows the beta-regression tests for each of the QMP category comparisons.
 The relations that are consistent are those between original article definition QMPs with replication selection and total QMPs, original article selection QMPs with replication total QMPs, and finally original article quantification QMPs with replication selection QMPs.
-All of these relations were positive across both coding protocols, illustrating that a greater QMP ratio of the specified type in an original article is associated with an increase in QMP ratio for the specific QMP type, or total QMP ratio in the replication protocol.
+All of these relations were positive across both coding protocols (see Appendix ???), illustrating that a greater QMP ratio of the specified type in an original article is associated with an increase in QMP ratio for the specific QMP type, or total QMP ratio in the replication protocol.
 
@@
 
-### Possible change: omit sd and p-value, and instead show CI and n, in which case also the note should be changed.
-
 ```
 
-```{r H6ExploratoryAssociationsInitialTable, warning = FALSE}
-# creating the dataframe for the table
-H6_table_dataframe_l <- rbind(Results_H6_between$def_def, Results_H6_between$def_op,
-  Results_H6_between$def_sel, Results_H6_between$def_quant, Results_H6_between$def_mod, 
-  Results_H6_between$op_def, Results_H6_between$op_op, Results_H6_between$op_sel, 
-  Results_H6_between$op_quant, Results_H6_between$op_mod, Results_H6_between$sel_def, 
-  Results_H6_between$sel_op, Results_H6_between$sel_sel, Results_H6_between$sel_quant, 
-  Results_H6_between$sel_mod)
-
-H6_table_dataframe_r <- rbind(Results_H6_between$quant_def, Results_H6_between$quant_op,
-  Results_H6_between$quant_sel, Results_H6_between$quant_quant, Results_H6_between$quant_mod, 
-  Results_H6_between$mod_def, Results_H6_between$mod_op, Results_H6_between$mod_sel, 
-  Results_H6_between$mod_quant, Results_H6_between$mod_mod, Results_H6_between$tot_def, 
-  Results_H6_between$tot_op, Results_H6_between$tot_sel, Results_H6_between$tot_quant, 
-  Results_H6_between$tot_mod)
-
-H6_table_dataframe <- cbind(H6_table_dataframe_l, H6_table_dataframe_r)
-
-# adding asterices for significance to the significant p in the dataframe
-H6_table_dataframe[8,3] <- paste0(H6_table_dataframe[8,3], "$^*$")
-H6_table_dataframe[11,3] <- paste0(H6_table_dataframe[11,3], "$^*$")
-H6_table_dataframe[14,3] <- paste0(H6_table_dataframe[14,3], "$^*$")
-H6_table_dataframe[8,6] <- paste0(H6_table_dataframe[8,6], "$^*$")
-H6_table_dataframe[9,6] <- paste0(H6_table_dataframe[9,6], "$^*$")
-H6_table_dataframe[11,6] <- paste0(H6_table_dataframe[11,6], "$^*$")
-H6_table_dataframe[13,6] <- paste0(H6_table_dataframe[13,6], "$^*$")
-
-# adding a column to help indicate the original QMP type
-H6_table_dataframe_expanded <- cbind(c("Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification"), H6_table_dataframe)
-
-# adding rows to give indication of specific sections (apa_table being awkward)
-H6_table_for_printing <- rbind(c("QMP Type", "", "Definition", "", "", "Quantification", ""), H6_table_dataframe_expanded[1:5,], c("QMP Type", "", "Operationalisation", "", "", "Modification", ""),  H6_table_dataframe_expanded[(6:10),], c("QMP Type", "", "Selection", "", "", "Total", ""), H6_table_dataframe_expanded[(11:15),])
-
-colnames(H6_table_for_printing) <-  c("Original", "$b$", "SD", "$p$", "$b$", "SD", "$p$")
-
-# print the table in apa formatting
-apa_table(
-  H6_table_for_printing, align = c("l", "r", "c", "r", "r", "c", "r")
-  , caption = "Beta Regression Test Results for the Association between Replication
-QMP Ratio and Original QMP Ratio as obtained using the Initial Protocol"
-  , note = "Rows indicate Original QMP type, and within table indicates Replication QMP type.
-Sample size for comparisons involving modification were lower since not all measures were modified.
-Therefore the standard errors are larger.
-$^* p < .05$"
-  , escape = FALSE, placement= "htp", midrules = c(1, 6, 7, 12, 13))
-
-```
-
-Figure \@ref(fig:Plot46RevisedDataCode) visually illustrates the relations of QMP ratios from different QMP types between replication protocols and original articles further.
-
-The unidimensionality of the measures used in the Many Labs projects was assessed through factor analyses, and evaluated based on the criteria discussed in the [Exploratory Analyses](#ExploratoryAnalyses) section above.
-Suitable data for factor analyses was available for nineteen measures.
-These measures were the same as those shown in Figure \@ref(fig:Plot23AlphaCode), with the addition of one more measure from [@cacioppo1983effects].
-A composite score based on the measurement responses was used for sixteen of the nineteen measures to form a single variable in the analyses, and were thus regarded as intended to be unidimensional.
-The number of dimensions for the remaining three were unclear.
-Sufficient fit of the unidimensional model was found for six out of the nineteen evaluated measures.
-However, as shown in Table \@ref(tab:UnidimesnionalityTestResultsTable) the unidimensional model did not hold for any measure data based on the parallel analysis test alone.
-Only the RMSEA $< .08$ criteria suggested evidence for single factor structures.
-
-```{r UnidimesnionalityTestResultsTable, warning = FALSE}
-# add the names of the relevant papers and a shortcut for the measure used.
-cfa_results_expanded <- cbind(c("Caruso et al.
-(2012)", "Husnu & Crisp (2010)", "Nosek et al.
-(2002), Art", "Nosek et al.
-(2002), Math", "Van Lange et al.
-(1997)", "Anderson et al.
-(2012), SWL", "Anderson et al.
-(2012), PA", "Anderson et al.
-(2012), NA", "Giessner & Schubert (2007)", "Norenzayan et al.
-(2002)", "Zhong & Liljenquist (2006)", "Monin & Miller (2001), most", "Monin & Miller (2001), some", "Cacioppo et al.
-(1983), elm", "Cacioppo et al.
-(1983), nfc", "De Fruyt et al.
-(2000), consc", "Albarracín et al.
-(2008), exp.
-5", "Shnabel & Nadler (2008)", "Vohs & Schooler (2008)"), cfa_results)
-
-# adding sensible column names
-colnames(cfa_results_expanded) <- c("Original Article", "RMSEA", "N Factors", "Unidimensional")
-
-# Renaming the columns for the not converged cfa.
-cfa_results_for_print <- cfa_results_expanded
-cfa_results_for_print$RMSEA[16] <- "Did"
-cfa_results_for_print$`N Factors`[16] <- "Not"
-cfa_results_for_print$Unidimensional[16] <- "Converge"
-
-# print the table in apa formatting
-apa_table(
-  cfa_results_for_print, align = c("l", "r", "r", "r")
-  , caption = "RMSEA and Parallel Analysis Suggested Factors based on Factor Analysis
-for Measure Data", note = "N Factors refer to the number of factors suggested based on parallel analysis of the measure data.
-The word or abbreviation after the author names and year indicates the specific measure within that original article that was analysed.", escape = FALSE, row.names = FALSE, placement= "htp")
-
-```
-
-# Discussion
-
-In the current study, measurement error and QMPs were assessed in both replications and original research.
-These measurement related concepts were then linked to replicability in order to investigate them as potential causes inhibiting successful replications.
-The results of the tests for the hypotheses showed mixed results.
-However, when including exploratory and descriptive analyses, a clearer picture of the state of measurement in replication and original research emerges.
-
-Before interpreting of the results, it should be reiterated that the sample size for several analyses was smaller than what is generally recommended for such analyses.
-This holds especially for the tests of hypotheses 2, & 3, since the number of measures for which reliability could be calculated for these analyses was only eighteen.
-This was less than anticipated, which brings us to the first topic of the discussion.
-
-## Quality of Measurement
-
-This study assessed the quality of measurement and measurement reporting in original and replication research by investigating the quality of measurement in the Many Labs projects.
-Findings were in line with similar investigations in the literature by @shaw2020measurement & @flake2022construct.
-These two studies found that sufficient validity evidence and reliability reporting for measures was lacking, even more so for replications than for original studies.
-The lack of support found for hypothesis 1 shows that this also held for this study's sample.
-In fact, support was found for an effect in the direction opposite to what was hypothesized in the preregistration, as the original articles reported reliability coefficients more often than replication studies.
-
-However, even the original articles only reported reliability for approximately one third of the used multiple item measures.
-Reliability coefficients were reported in such small numbers that the original analysis plan for hypothesis 1 was altered, from evaluating the reliability coefficient value to the number of times reliability was reported in an article or protocol.
-As a result, the interpretation of rejecting the hypothesis based on this new test changed compared to the preregistered test.
-Still, the test provides evidence towards the same point, which is that reliability evidence for the used measure is lacking more in replication protocols than in original articles, although most multiple item measures in original articles were also reported without reliability evidence.
-This shows that lack of reliability evidence is a widespread issue, something that has been shown in earlier literature on this topic [@vacha1999practices; @green2011recent].
-
-Furthermore, across measures used in both original and replication studies, less than half of the measures were multiple item scales.
-Research commonly made use of single item measures (see Figure \@ref(fig:ReliabilityReportingFlowDiagram) for more details), an observation that was also made by @shaw2020measurement.
-The use of these single item measures comes with risks, since by virtue of being singular they assume that whatever they are measuring is unidimensional, while not being able to test this assumption [@shaw2020measurement].
-This is potentially quite worrying given that the exploratory analyses of the multiple item measures, for which unidimensionality could be tested, showed only little support for unidimensionality of the measures used in replications.
-While the measures that were tested for unidimensionality were mostly used as single indicators in the analyses for the replication protocol, one could argue this does not necessarily mean these measures all assessed constructs with a unidimensional structure.
-For example, IQ is often used as a singular indicator, even though it consists of several factors [@weiss2013wisc].
-However, it should be noted that at least with respect to Many Labs 2, all of the measures that were considered unidimensional for the analyses in this study were also considered unidimensional in the investigation by @shaw2020measurement} who also observed a lack of unidimensionality evidence in their investigation of Many Labs 2.
-To conclude, there is an indication that validity evidence for measures used in replication research is lacking overall.
-
-Several results did show more promising findings for the way measurement related issues are treated in replications.
-Firstly, the support found for hypothesis 2 showed some evidence that most of the variability in reliability coefficients is between measures, rather than within measures across different locations.
-If variation in the reliability of a measurement across locations is little, it could indicate that the measurement operated similarly across these locations, which would make the scores from the different lab locations directly comparable and aggregatable.
-However, again the small sample number of measures for which reliability could be assessed does mean that this estimate remains uncertain.
-Secondly, most replication protocols clearly stated that their measure was either newly created or based on existing materials.
-Still, in most instances neither original nor replication provided information on the exact version of their measure.
-This may largely be due to the fact that many of the used measures were single-item, for which specifying the exact versions may not be seen as crucial because they more or less describe themselves.
-Finally, QMPs were overall less common in replication protocols than they were in original articles, supporting hypothesis 4.
-This runs counter to the findings of @shaw2020measurement & @flake2022construct, who found that measures came with less validity evidence in replications than in original studies, as the result of QMPs.
-
-The structured replication protocols that were used in the Many Labs projects, I suspect improved the reporting practices and measurement consistency in replication protocols compared to original articles.
-Most replication protocols even contained a section under each replicated study, which listed any deviations from the original and as a result many potential QMPs were averted.
-[@protzko2020high] already demonstrated that transparent reporting of methodology before conducting research can improve the robustness of psychological science, and I believe the same holds true here.
-
-## Impact on replicability
-
-Besides assessing the overall quality of measurement reporting, this study also investigated if the reliability of a measure, and QMPs can impact replicability.
-First of all, contrary to expectations (see Hypothesis 3), less reliable measures were not associated with a decrease in replicability.
-This result is surprising, since @stanley2014expectations demonstrated the potential impact that measurement error can have on the veracity of determining replication success based on a significance test without attenuating for measurement error.
-The significance test cut-off criteria that was used in this study to assess replication success similarly did not attenuate for measurement error, and thus results in line with the simulation studies of @stanley2014expectations were expected.
-
-While no evidence for hypothesis 3 was found, caution in interpreting the test results is needed.
-The number of measures for which reliability was calculated was quite low (eighteen for Cronbach's alpha, fifteen for omega), it could be that the test was simply underpowered to detect the effect.
-On the other hand, it might be that the detrimental influence of measurement error on interpretations of replication results is small in large scale replication projects.
-Across the multiple replications, measurement error's influence on the effect could have been cancelled out at the meta-analytic level.
-This would require the measurement error to be random and small, and as a result the average value of the effect and the error around would remain similar, thus not altering the result of the meta-analytic significance test.
-
-Results regarding the relationship between QMPs and replicability were more in line with expectations.
-In particular, support was found for hypothesis 5, showing that an increase in total QMP ratio was associated with a decrease in replicability.
-Existing literature has already warned about the potential detrimental effects of QMPs on replications [@shaw2020measurement; @flake2022construct].
-This result provides further evidence supporting these claims.
-However, the association was only significant when data was used from the revised coding protocol, data from the initial protocol, which was more stringent in its assessment of QMP, did not indicate a significant association with replicability.
-
-Similarly, the test for hypothesis 6 showed inconsistent results between the revised and initial coding protocols.
-Only for the revised protocol data was an increase in total QMPs in the original study associated with an increase in total QMPs in the protocol of the replication for that study.
-The result obtained with the data from the revised protocol are in line with expectations.
-If information on measurement is lacking or the measure is poorly motivated in a study, then any subsequent replication attempt will lack information needed match its measurement to the original.
-Even if it does match the original, when the measure itself is a poor indicator of the assessed variable or construct, both the original and replication data obtained from this measure may not substantially relate to the investigated psychological phenomenon the original study set out to investigate [@flake2022construct].
-However, the fact that the conclusions were different based on the protocol makes it difficult to determine the exact nature of the influence of original study QMPs on replication protocol QMPs.
-
-Further analyses based on the QMP ratios of each specific type indicated that across both the initial and revised coding protocols together, only selection, definition, and quantification QMPs in the original article related significantly to selection type QMPs, total QMPs, or both in the replication (see Tables \@ref(tab:H6ExploratoryAssociationsRevisedTable) & \@ref(tab:H6ExploratoryAssociationsInitialTable)).
-
-It could be that original articles have to provide a clear definition as well as details on the scale, in order for a replication to be able to justify selecting the measure.
+A possibler explanation for these results could be that original articles have to provide a clear definition as well as details on the scale, in order for a replication to be able to justify selecting the measure.
 A replication may also be in general more dependent on the original article for information on the definition of the constructs and the choice of measurement, compared to a description of the Operationalisation, quantification, and any modifications.
 These former are features of a measurement, which while preferably similar in a replication to the original, can and should be reported in the replication protocol even if the original article does not contain the details on these features itself.
-However, these are just speculations as the results showed no clear relations between different QMP types across original and replication (see Figure \@ref(fig:Plot46RevisedDataCode)), and testing of causal links was not possible with this data.
-
-For both hypothesis 5 & 6, the results were in line with expectations, but only for the revised coding protocol.
-Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol.
-The initial protocol was revised because the ratings based on that protocol were consider to stringent, and as a result, several items were reformulated so that criteria for what constituted sufficiently clear reporting were lowered.
-This meant that in the revised protocol, coded QMPs would need to clearly inhibit evaluation of the measurement, whereas for the initial protocol some aspects of the measurement reporting which were coded as questionable, may have been questionable only to a small degree.
-As a consequence, QMPs coded with the revised protocol represent measurement practices that represent on average more questionable practices than QMPs coded with the initial protocol.
-With this in mind, the difference between total QMP ratio of initial and revised protocol can be seen as a form of effect size difference.
-It could be that only replication QMPs that represented robust violations of good measurement practices significantly lower the probability of successful replication.
-In that case, a stronger relation between replicability and QMPs would be found with the revised protocol, since these QMPs represented more clearly questionable practices in measurement reporting than QMPs coded with the initial protocol, which would explain the disparate results that were found.
-
-## Limitations & Future Research
-
-The design of this study came with certain limitations.
-First of all, there was no experimental manipulation included.
-As a result, the ability to investigate the exact causal links between QMPs and replicability was limited.
-This study was intended to be exploratory in nature, and thus did not focus on causal analyses.
-However, future research establishing causal links will prove to be very beneficial in improving the understanding of the relationships between measurement issues and replicability.
-
-Another limitation of this study is that the results differed based on whether data from the revised or the initial coding protocol was used.
-As a result, any relationship between QMPs and replicability remains uncertain.
-The revised coding protocol was adapted from the initial coding protocol before any analyses were performed, it is however still possible that a change in protocol may have biased results.
-Future research investigating this topic should use a coding protocol which is verified independently by several researchers on a sample of articles and protocols first, before being used to code the QMP data that will be analysed.
-As a first step, the coding protocol from this study and the coding key from @flake2022construct can be used as a basis.
-
-It is important to also consider whether or not replication protocols and research articles can be fairly compared in terms of QMPs.
-Articles are generally longer than a study's description within a replication protocol, and as a result it seems reasonable to expect research articles to generally contain more measurement details than replication protocols.
-Regardless, this study assumed that a replication protocol is comparable to an article in providing an overview of the measure and how it was used, as it is the only comparable source for such information that would otherwise be difficult to find anywhere else.
-This assumption seems practical if not tenable when the replication protocol is the only available sources of measurement details.
-However, in case more detailed information on a measurement is available in other sources, such as an online appendix, it could be important data to include when assessing QMPs.
-This research did not make use of any online appendices in assessing QMPs, future research may wish to include them and other sources as part of the data.
-
-As a last note on QMPs, it is worth highlighting the way the QMP ratios were calculated.
-The total QMP ratio was based on the counts for each of the items from all the different QMP types divided by the total number of applicable questions.
-However, for each QMP type the number of items was different.
-This means that QMP types with a larger number of items (such as operationalisation) had a greater impact on the total QMP ratio than QMP types with a smaller number of items (such as definition).
-If the impact for each QMP type on each other and replicability is considered equally important, the total QMP ratio may not be considered a valid indice.
-On the other hand, it could be that each item should be considered equally important rather than each QMP type.
-For this study, the protocol was made and the analyses were conducted under the assumption that each item had equal weight.
-However, this is an assumption this study cannot provide evidence for.
-
-The small sample of measures for which reliability coefficients and unidimensional factor structure could be assessed limited the degree to which substantial interpretations can be made from the reliability and validity analyses.
-While future research will also unlikely be able to increase the number of multiple item measures used by replications, future research can broaden their analyses to include a larger number of replications, or take into account a type of measure which this study mostly ignored in the analyses of reliability and validity: single-item measures.
-
-Reliability assessment for single item measures differs substantially from multiple item measures [@wanous1996estimating], and for this reason was not included as part of the analyses for this study.
-Furthermore, single items cannot be tested on unidimensionality, since a single item is already assumed to measure only a single dimension by definition.
-However, future research might consider methods specifically designed to assess reliability and validity of single item measures.
-This could prove to be a worthwhile contribution, given the proportionally large number of single item measures that were encountered in the data for this study (see Figure \@ref(fig:ReliabilityReportingFlowDiagram)).
-
-Finally, this paper investigated the consistency of measures, by assessing the variance in reliability across different labs wherein the measure was conducted, and comparing it to the variance in reliability between the different measures.
-Besides comparing the degree of reliability across labs, it is also possible to assess whether a measure assesses the same underlying construct across lab locations.
-This can be done through measurement invariance testing.
-Measurement invariance is a concept in latent factor modelling that illustrates the extent to which the relationship between items and factors is dependent on some other variable, usually a group [@mellenbergh1989item].
-@shaw2020measurement investigated measurement invariance for the responses to measures at each lab location within the replication sets of Many Labs 2.
-Investigations similar to this have also been suggested for future replication projects [@flake2022construct].
-For these reasons, future research should consider measurement invariance tests, if assessing measurement consistency in replications across different labs.
-
-## Implications for Research and Replications in Psychological Science
-
-Taking all the findings together, the following assessments will be relevant to consider for future replication research.
-With respect to the quality of measurement reporting, the small number of reported reliabilities, small number of reported psychometric validity evidence, and lack of unidimensionality evidence for data aggregated to a single indicator corroborate findings by @shaw2020measurement & @flake2022construct.
-Evidence supporting the measures used in replication should be reported more frequently, so that they can be evaluated and the validity of replication research can be improved.
-
-There are additional validity issues in measurement as the result of QMPs.
-While it is debatable whether or not $17.9\%$ average QMP ratio in replications is too much, the association between original paper and replication protocol QMPs demonstrates how a lack of information for measurement in the original can spill over to the reporting in replications.
-This could lead to issues for replication attempts if the measure in an original article has poor reliability and validity.
-In that case, the tests in the original article are based on data from measures that do not accurately capture the construct they were intended to measure.
-The results of any direct replication attempt will face the same issues, and as a consequence the replication is unlikely to provide a relevant test of a psychological theory, as the original study itself was not a robust test of that psychological theory to begin with [@isager2020deciding, @isager2021deciding, @nuijten2022assessing].
-Thus, future replicators should first evaluate the quality of the measurement (reporting) in an article before deciding to replicate it.
-
-In case the quality appears low, replication attempts can still proceed with some adjustments.
-One option is to change the focus of the replication to be conceptual rather than direct.
-In that case the measure and the operationalisation can be freely altered from the original, which means that a more sufficient test of the theory can be developed.
-If deemed necessary, a direct replication can always be performed later based on the conceptual replication.
-In that case, the direct replication will be able to provide a sufficient test of a psychological theory, on the condition that the conceptual replication's test improvements led to it becoming a sufficient test.
-
-The results also suggest that the use of structured protocols in the reporting of measurement may be an effective way of reducing QMPs, and increasing the reporting of reliability and validity evidence.
-However, even in the Many Labs projects, which made use of structured protocols to report their measures, low reliability and validity evidence reporting was found.
-These protocols could therefore still increase the attention they give to reporting reliability and validity evidence.
-In particular, Figure \@ref(fig:Plot456Code) shows descriptive evidence that replication protocols are lacking in definition and selection evidence.
-Furthermore, since replications must base their measures on those of the original articles they are replicating, it is important that articles chosen for replications provide clear evidence on what is being measured, how it is scored, why it was chosen or why it was constructed the way it is, and how it is used in practice.
-It is these last two aspects that original articles appear to particularly be underreporting (See Figure \@ref(fig:Plot456Code)).
-When original articles do not report their measurement details, replication attempts cannot guarantee a direct replication of the original.
-By improving the quality of measurement reporting in original articles, the validity of both original research results and future replication attempts would increase.
-It would be particularly important to focus on remedying strong violations of good measurement reporting, as these were shown to have a significant detrimental impact on replicability.
-This suggests that even small but critical improvements in the reporting of measurement information could lead to a substantial increase in the replicability of psychological science.
-
-# Conclusion
-
-Overall, the observed quality of measurement and frequency of measurement reporting in psychological research and replications was low, which is in line with other research on the topic.
-Improvements in the reporting on measurement are needed for both original and replication research.
-The measure source, content, and how it was used should be described in detail, and evidence illustrating the reliability and validity of the measure should be provided.
-Not only would the clarity of research improve, higher quality of measurement reporting in replications was shown to be related to an increase in replicability of the findings related to that measure.
-Tentative evidence was also found for spill-over effects of the quality of measurement reporting from original study to replications.
-These results combined suggest that improvements in the reporting of measurements are necessary in both replications and original articles.
-Furthermore, future replicators should carefully consider the quality of measurement in a study before attempting a direct replication, even considering a conceptual replication instead if the measurement in the original was not of sufficient quality.
-However, the evidence for the relationship between measurement quality and replicability was not robustly identified, and future research will be needed to confirm the exact nature of this relationship.
-
-\newpage
-
-# References
-
-::: {#refs custom-style="Bibliography"}
-:::
+However, these are just speculations as the results showed no clear relations between different QMP types across original and replication (see Figure \@ref(fig:Plot46RevisedDataCode)), the number of tests were many while multiple testing was not corrected for, and finally testing of causal links was not possible with this data.

### 2024-03-06 Scripts/Manuscript/manuscript.Rmd
added (suggested) changes to methods section, and made the first appendix containing additional models and results.

@@
 Any deviations from the preregistration are explicitly mentioned in the text.
-This manuscript was generated using the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency.
+This manuscript was created in Rstudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency.
 All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication.git>.
@@
 Data from Many Labs 4 [@klein2022many] was not part of the sample, as there was no publicly available protocol which contains the information needed to code QMPs.
-Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking as measures, which did not match this study's focus on scale and item measures.
+Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study's focus on scale and item measures.
 
@@
 Each finding was tested across several labs, and was related to a finding from an original study, the combination of all these studies and their associated information formed a replication set.
-For each research finding, any primary measures assessing a unique variable were taken to form the final unit of measurement.
-Here primary measures refers to measures assessing variables included in the primary test of the replication, were used.
+For each research finding, any primary measures assessing a unique variable were taken to form the key unit of analysis.
+Here primary measures refers to measures assessing variables included in the primary test of the replication.
 This was done to ensure that the analyses could link directly to the replicability of a study.
@@
 The replication datasets refer to the data of each of the replication attempts for each of the original psychological effects undertaken as part of a Many Labs study.
-These publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base] Using the replication protocols, codebooks, and analysis scripts from each replication set as a guide, the variables associated with each relevant measure were extracted into their own data frame containing the data from all studies in one replication set.
-These pieces of information were used as the datasets in the analysis.
+These publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio [@R-Rstudio].
+Using the replication protocols, codebooks, and analysis scripts from each replication set as a guide, the variables associated with each relevant measure were extracted into their own data frame containing the data from all studies in one replication set.
+These pieces of information were used as the datasets for their respective analyses.
 
@@
 
-FOOTNOTE:The original articles were identified through the citations in each replication protocol, using Web of Science, Google Scholar, and PsychInfo (in that order).
+FOOTNOTE: The original articles were identified through the citations in each replication protocol, using Web of Science, Google Scholar, and PsychInfo (in that order).
 An issue was encountered while trying to access @hyman1950current.
@@
 
-The measures of primary variables were identified by combing through the entire methods section of each preregistered replication protocols.
-Then using questions and the accompanying search strategies as documented in the structured coding protocol of this study (available on the relevant OSF: <https://osf.io/9r8yt/>, and github pages: <https://github.com/CasGoos/measurement_and_replication.git>), information on the reported measurement evidence and reporting quality was assessed for both replication protocols and original studies.
-Descriptions of the extracted variables can be found in the [Measures](#Measures) section below.
-Exact descriptions of the search strategy can be found in Appendix ???.
-
 MOVE TO APPENDIX/COMBINE WITH EXTERNAL SEARCH STRATEGY FILE: The scope of the coding was limited to the abstract, method, procedure, materials, measure, and initial parts of the results sections.
@@
 
-After the data was initially coded according to the preregistered coding protocol, it was determined, based on discussion with the supervisor, that some of the initial ratings were possibly to stringent.
-As a result, some of the items in the protocol were reformulated, so that the conclusions from the resulting analyses were based on a more lenient judgement of QMPs.
-The revision of the coding protocol happened after all the data were coded using the initial protocol.
-As a result the coded data using the initial protocol, and the coded data using the revised protocol are both available available on this article's OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages.
-
-MOVE TO APPENDIX/COMBINE WITH EXTERNAL SEARCH STRATEGY FILE: These changes included: accepting linked online appendices as a data source for example items; assuming that if no differences between replication and original are measurement is mentioned, that there is no difference, even if it is not explicitly clear; and generally simplified criteria for what constituted sufficiently clear reporting.
+MOVE TO APPENDIX/COMBINE WITH EXTERNAL SEARCH STRATEGY FILE: These changes (to the QMP coding protocol) included: accepting linked online appendices as a data source for example items; assuming that if no differences between replication and original are measurement is mentioned, that there is no difference, even if it is not explicitly clear; and generally simplified criteria for what constituted sufficiently clear reporting.
 
 ## Measures {#Measures}
+
+Relevant primary measures were identified by combing through the entirety of the methods section for each preregistered replication protocol.
+Then using questions and the accompanying search strategies as documented in the structured coding protocol of this study (available on the relevant OSF: <https://osf.io/9r8yt/>, and github pages: <https://github.com/CasGoos/measurement_and_replication.git>), information on the reported measurement evidence and reporting quality was assessed for both replication protocols and original studies.
+Descriptions of the extracted variables can be found in the sections below.
+The coding protocol and explanations on how the articles and replication protocols were searched through to answer the questions in the coding protocol can be found in the supplementary materials ???.
 
@@
 Cronbach's alpha was calculated as the main score reliability index used in the analyses as it is one of the most popular [@cho2015cronbach].
-Hpowever, in the supplementary materials ???, Omega was added to the analysis as it has been argued to be a more informative measure of score reliability, while also providing validity evidence for the scale [@crutzen2017scale; @deng2017testing].
+Analyses based on the Omega can be found in Appendix ???.
+Omega was included since it has been argued to be a more informative measure of score reliability, while also providing validity evidence for the scale [@crutzen2017scale; @deng2017testing].
 Cronbach's alpha and omega were calculated using the alpha and omega functions respectively in the psych R package [@R-psych].
@@
 Each coded QMP belonged to one of five QMP type categories that were derived from the classification in @flake2020measurement.
-An overview of the QMP categories of the coding variables can be seen in Table \@ref(tab:QMPCodingInfoTable)
+An overview of the QMP categories of the coding variables can be seen in Table \@ref(tab:QMPCodingInfoTable).
 
@@
 Beside these quantitative variables, a total of four qualitative variables were also included to provide more detailed information on some aspects of the measure and its reporting.
-Details on the items used, their origin and justifications can be seen in Appendix ???.
-
-APPENDIX: on item revision and origin
+Details on the items used, their origin and justifications can be seen in Supplementary Materials ???.
+
+FOOTNOTE: additional analyses, tables and figures based on QMPs obtained with the initial protocol can be found in Appendix ???.
+
+???Supplementary Materials: on item revision and origin
 
@@
 These (qualitative) variables assessed with two having an equivalent in @flake2022construct: the specific version of the measure (if reported); whether and what previous materials were used for the study; what, if any, psychometric evidence beyond reliability score (e.g.
-factor analysis, IRT model, convergent validity) was provided; and whether it was specified or not that the measure was or was not modified.
+factor analysis, IRT model, convergent validity) was provided; and whether it was specified or not that the measure was or was not modified.???
+
+After the data was initially coded according to the preregistered coding protocol, it was determined, based on discussion with the supervisor, that some of the initial ratings were possibly to stringent.
+As a result, some of the items in the protocol were reformulated, so that the conclusions from the resulting analyses were based on a more lenient judgement of QMPs.
+The revision of the coding protocol happened after all the data were coded using the initial protocol.
+As a result the coded data using the initial protocol, and the coded data using the revised protocol are both available available on this article's OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages.
 
@@
 # plot accompanying the results for Hypotheses 4, & 6
-plot_46_data <- data_prep_plot_46(data_h6[c(3, 6, 9, 12, 15, 36, 39, 42, 45, 48)])
-plot_46_data_rev <- data_prep_plot_46(data_h6[c(3, 21, 24, 27, 30, 36, 54, 57, 60, 63)])
+plot_46_data <- data_prep_plot_46(data_h6[c(3, 6, 9, 12, 15, 18, 36, 39, 42, 45, 48, 51)])
+plot_46_data_rev <- data_prep_plot_46(data_h6[c(3, 21, 24, 27, 30, 33, 36, 54, 57, 60, 63, 66)])
 # plot accompanying the results for Hypotheses 2, & 3
@@
 
-```
+# adding OR to the result
+H3_main_full_results_alpha_with_OR <- OR_to_apa_full_supplier(H3_test_result_main_alpha$full_result$alpha, negative_b = FALSE)
+
+# well this OR is quite a ridiculous number now..., but then again a step from 0 alpha to 1, is quite a jump too...
+
+```
+
+???Put in appendix???:
 
@@
 
-Hypothesis 4, 5, & 6 were all tested using a model with the same dependent variable: total QMP ratio.
+Hypothesis 4 & 6 were both tested using a model with the same dependent variable: total QMP ratio.
 In order to model a ratio dependent variable, beta regression was used.
@@
 ```
-All of these models assume that the QMPs are the same across each replication set.
+
+These models assume that the QMPs are the same across each replication set.
 This was necessary as only one protocol was available for coding per replication set.
@@
 Where $replication_{i}$ is a dummy coded variable, which was coded as 1 in case the reported QMP ratio belonged to a replications, and 0 if it belonged to an original study.
-For hypothesis 5 a similar formula was used [[[change to logistic regression, with footnote that pre-reg was inverted]]]:
+For hypothesis 5 the QMP ratio was used as the predictor for replication success, while replication success was used as the outcome[^2].
+
+[^2]: This analysis differs from what was pre-registered.
+Initially this analysis was also a beta-regression where QMP ratio was the outcome variable, while replication success was the predictor.
+The pre-registered analysis outcomes are available in Appendix ???A???.
 
@@
 \begin{equation}
-g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replicated_{i} (\#eq:H5Main)
+logit(replicated_{i}) = \beta_{0} + \beta_{1} QMP\_ratio_{i} (\#eq:H5Main)
 \end{equation}
 ```
-Where $replicated$ is a dummy coded variable, which is the same as for equation \@ref(eq:H3Main).
+
+Where $replicated$ is a dummy coded variable, which is the same as for equation \@ref(eq:H3Main), and $logit(.)$ refers to the logit link function commonly used for logistic regression models.
 Note here that unlike in the test for hypothesis 4, $QMP\_ratio_{i}$ refers only to the QMP ratios of the replications, meaning that original article QMPs were not included in this analysis.
@@
 ```{r Hypothesis5Model, include = FALSE}
-## Hypothesis 5 beta regression model
-H5_test_results <- betareg(QMP_ratio ~ hypothesis_support, data = data_h5)
-
-H5_test_results_REV <- betareg(QMP_REV_ratio ~ hypothesis_support, data = data_h5)
+## Hypothesis 5 logistic regression model
+H5_test_results <- apa_print(glm(hypothesis_support ~ QMP_ratio, data = data_h5, family = binomial))
+
+H5_test_results_REV <- apa_print(glm(hypothesis_support ~ QMP_REV_ratio, data = data_h5, family = binomial))
+
+H5_test_results_with_OR <- OR_to_apa_full_supplier(H5_test_results$full_result$QMP_ratio, negative_b = TRUE)
+
+H5_test_results_REV_with_OR <- OR_to_apa_full_supplier(H5_test_results_REV$full_result$QMP_REV_ratio, negative_b = TRUE)
 
@@
 The relationship between original article QMPs and replication protocol QMPs was modelled to test hypothesis 6.
-The outcome variable remains the same as in the model for hypothesis 5.
-The independent variable is changed to the QMP ratio for original articles.
+The outcome variable is the same as the predictor in the model for hypothesis 5.
+The independent variable in this model is instead the QMP ratio for the original articles.
 The resulting model formula is as follows:
@@
 
-These models had independence of observations as an assumption, the observations here referring to a replication set.
+APPENDIX:"These models had independence of observations as an assumption, the observations here referring to a replication set.
 this is known to be false since the data is nested within four separate Many Labs projects.
@@
 The outcome QMP ratio variable was transformed using the logit link function (the default link function in the betareg package) to better fit the Gaussian model.
+???FOOTNOTE: exploratory analyses were preregistered for this but left out.???
 
@@
 H6_n_check_results_REV <- betareg(Rep_op_REV_ratio ~ mod_REV_ratio, data = data_h6)$n
-
-```
-
-```{r Hypothesis6Associations, include = FALSE}
-## Associations between the QMP categories
-# associations are generated using a helper function available in the source_ 
-# script. These associations correspond to the coefficients between replication
-# and original article QMPs of the various QMP types, as estimated through a 
-# beta regression.
-# Associations between the QMP categories (original QMP coding)
-Results_H6_between <- Associations_H6(data_h6)
-
-# keep in mind mod_ratio (not Rep) is based on a very small sample size, less
-# of a concern for the revised.
-
-# Associations between the QMP categories (revised QMP coding)
-Results_H6_between_REV <- Associations_H6_REV(data_h6)
-
-```
-
-### Exploratory Analyses {#ExploratoryAnalyses}
-
-Follow-up analyses were preregistered for hypothesis 6.
-Using a similar model to the main hypothesis test with all unique combination of the five different QMP types being tested across original and replication data.
-The goal of these analyses was to see if there are any type specific carry-over effects in QMPs between original and replication.
-Due to the large number of tests, the focus was exploratory using visualisation rather than inference.
-
-APPENDIX:
-
-Finally, in order to present additional validity evidence alongside the analyses of Cronbach's alpha and omega coefficients, the unidimensionality of each measure was investigated.
-To test this, each multiple item scalar measure had their factor structure investigated on the entire measure data of the replication set.
-A single factor confirmatory factor analysis was implemented using the *fa* function from the *psych* package [@R-psych] in R.
-The maximum likelihood factoring method was used, with defaults being used for all other function arguments.
-From this analysis, the RMSEA of the one factor solution was extracted.
-Additionally, a parallel test was conducted using the *fa.parallel* function also from the psych package.
-If either the RMSEA score \< .08, or the parallel analysis returned a one factor solution, unidimensionality was coded as true, otherwise it was coded as false.
-
-```{r UnidimensionalityExploratoryAnalysis, include = FALSE}
-extracted_data_list <- list(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, data_1.12.3.2_clean,data_2.12.1_clean, data_2.12.2_clean, data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.1_clean, data_3.7.2_clean, data_3.8.2_clean, data_5.1.2_clean, data_5.1.1_clean, data_5.7_clean, data_5.9.1_clean)
-
-# creating an empty dataframe to store the results in
-cfa_results <- data.frame(RMSEA = 0,
-                          N_factors = 0,
-                          Single_factor = "")
-
-# running the cfas for all of the extracted datasets
-for (i in 1:length(extracted_data_list)){
-  # obtaining single factor model cfa RMSEA value for evaluation
-  RMSEA_value <- fa(extracted_data_list[[i]][-1])$RMSEA[1]
-
-  if(is.null(RMSEA_value) != TRUE){
-    RMSEA_value <- apa_num(RMSEA_value, digits = 3)
-  }
-
-  # conducting parallel test to check if one factor solution is best.
-  parallel_N_factors <- fa.parallel(extracted_data_list[[i]][-1], 
-                                    fa = "fa")$nfact
-
-  # adding a single factor check indicator value
-  single_factor <- ifelse(RMSEA_value < 0.08 | parallel_N_factors == 1, "Yes", 
-                          "No")
-
-  # adding the cfa results of one factor analysis to the results dataframe.
-  cfa_results <- rbind(cfa_results, c(RMSEA_value, parallel_N_factors, 
-                                      single_factor))
-}
-
-# removing the initial empty row
-cfa_results <- cfa_results[-1,]
 
@@
 
-Based on a chi square comparison, reliabilities were found to be more commonly reported in original articles compared to replication protocols ($\chi^{2}$(`r apa_num(H1_test_result$parameter)`) = `r apa_num(H1_test_result$statistic)`, *p* = `r apa_p(H1_test_result$p.value)`).
+Figure ...
+already demonstrates that multiple item measures are most commonly not accompanied by a reported reliability coefficient in neither original articles nor replication protocols.
+Additionally, when comparing between the two using a chi square comparison, it was observed that in replication protocols reliability coefficients are reported significantly less often than in original articles ($\chi^{2}$(`r apa_num(H1_test_result$parameter)`) = `r apa_num(H1_test_result$statistic)`, *p* = `r apa_p(H1_test_result$p.value)`).
 These results are contradictory to hypothesis 1.
 
-The between-group (across different replication set) variance and within-group (lab locations within a replication set) variance in the Cronbach's alpha coefficient were assessed using a multilevel model as specified in Formulas \@ref(eq:level1H2), \@ref(eq:level2H2), & \@ref(eq:mixedH2) The between-group and within-group variance for Cronbach's alpha were approximately `r apa_num(between_group_variance_alpha, digits = 3)` and `r apa_num(within_group_variance_alpha, digits = 3)` respectively.
-The resulting ICC, obtained using formula \@ref(eq:ICC), was approximately `r apa_num(ICC_alpha, digits = 3)`.
-This suggests that variance was larger between replication sets than within.
-These results are in line with hypothesis 2.
-However, the measures with lower average reliabilities did show a large amount of variation in the reliability coefficient as can be seen figure \@ref(fig:Plot23AlphaCode)
-
-The relationship between reliability and replication success was primarily tested via logistic regression, with replication success as the dependent variable.
-The results of the logistic and multilevel sensitivity analysis models are shown in Table \@ref(tab:ReplicabilityReliabilityTestTable) for Cronbach's alpha.
-
-[???sensitivity analyses??? to appendix]
-
-```{r ReplicabilityReliabilityTestTable, warning = FALSE}
-# creating the dtaframe for the table
-H3_table_dataframe <- rbind(H3_test_result_main_alpha$table, H3_test_result_int_sensitivity_alpha$table, H3_test_result_main_omega$table, H3_test_result_int_sensitivity_omega$table, H3_test_result_slp_sensitivity_omega$table)
-
-# adding an asterix for significance to the significant p in the dataframe
-H3_table_dataframe[3,5] <- paste0(H3_table_dataframe[3,5], "$^*$")
-
-# adding rows to give indication of specific sections (apa_table being awkward)
-H3_table_for_printing <- rbind(c("Alpha", "", "", "", ""), c("Logistic Regression Model", "", "", "", ""), H3_table_dataframe[1:2,], c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(3:4),], c("Omega", "", "", "", ""), c("Logistic Regression Model", "", "", "", ""), H3_table_dataframe[(5:6),], c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(7:8),], c("Random-Slope Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(9:10),])
-
-# print the table in apa formatting
-apa_table(
-  H3_table_for_printing, align = c("l", "r", "r", "r", "r")
-  , caption = "Model Results from Tests of Hypothesis 3"
-  , note = "The Alpha and Omega sections show the models where the independent variable was the calculated Cronbach's alpha and omega coefficient respectively.
-The random slope model for Cronbach's alpha did not converge, thus it results are not shown here.
-$^* p < .05$"
-  , escape = FALSE, placement= "htp", midrules = c(1, 2, 5, 7, 8, 9, 12, 15))
-
-```
-
-Cronbach's alpha did not significantly relate to replication success in the main logistic regression model (Cronbach's alpha: `r H3_test_result_main_alpha$full_result$alpha`), nor in any of the multilevel sensitivity analyses models (see Table \@ref(tab:ReplicabilityReliabilityTestTable)).
+The ICC of the between-group (across different replication set) variance and within-group (lab locations within a replication set) variance in the Cronbach's alpha coefficient was approximately `r apa_num(ICC_alpha, digits = 3)`.
+Because this number is larger than .5, it suggests that variance was larger between replication sets than within.
+A more sophisticated, albeit not pre-registered, test based on the Tau heterogeneity estimate and Q-test for heterogeneity obtained from a meta-analysis of the calculated reliability coefficients was additionally performed to test hypothesis 2.
+Figure \@ref(fig:Plot23AlphaCode) shows that there is quite some variance in Tau (the indicator of true differences in reliability scores between labs) with some having a Tau estimate of approximately 0, and others reaching beyond .1, which suggests that ???the true variance in reliability for that measure is as large as .1 point of Cronbach's alpha???.
+Based on the Q-test for heterogeneity, ???5???
+out of the total of ???18???
+estimates of heterogeneity were judged to be significant.
+However, the Q-test and tau are both highly sensitive to the number of studies in the meta-analyses (CITATION HERE), which may explain some of the results.
+
+Therefore, while evidence for heterogeneity would not be in line with hypothesis 2, the evidence remains inconsistent when looking across all studies, and sensitive to the sample size of the meta-analyses.
+
+In figure ...
+the calculated reliabilities were separated by a red line based on whether the replications the measures mere used in were successful when judged at a meta-analytic significance level of .05.
+A logistic regression was performed to detect if there was indeed a relation between calculated reliabilities and replication success.
+
+Cronbach's alpha did not significantly relate to replication success in the main logistic regression model (Cronbach's alpha: `r H3_main_full_results_alpha_with_OR`), nor in any of the multilevel sensitivity analyses models (see Appendix ???).
 This is contradictory to the expectation in hypothesis 3.
-Similar results were found for the analyses when using Omega as the reliability coefficient of choice (see supplementary materials ???).
-However, caution should be taken in evaluating the results from these analyses should, given the small sample number of measures used to estimate the models for these tests.
-
-[other relevant info such as: ???]
+Similar results were found for the analyses when using Omega as the reliability coefficient of choice (see Appendix ???).
+However, caution should be taken in evaluating these results, given the small sample number of measures used to estimate the models and the resulting large uncertainty around the estimate.
 
@@
 
+The bottom pannel of Figure \@ref(fig:Plot456Code) already shows that original articles contained a significantly larger proportion of QMPs than replication protocols for the measures of the same effects.
 Beta-regression was used to test the difference in QMP ratio between original articles and replication protocols.
-Results showed that original articles contained a significantly larger proportion of QMPs than replication protocols for the measures of the same effects (`r betareg_output_to_apa_full(H4_test_results_REV)`).
+The results of this test indicated that this difference was significant (`r betareg_output_to_apa_full(H4_test_results_REV)`).
 This result is in line with hypothesis 4.
@@
 A similar beta-regression tested the association between replication success and QMP ratio in replication protocols.
-Results showed that successful replication significantly related to a decrease in the ratio of QMPs in replication protocols (`r betareg_output_to_apa_full(H5_test_results_REV)`).
+Results showed that successful replication significantly related to a decrease in the ratio of QMPs in replication protocols (`r H5_test_results_REV_with_OR`).
+However, this result did not hold for the QMP ratios obtained with the initial coding protocol (`r H5_test_results_with_OR`).
+
+???Footnote: analysis was changed from the pre-registered beta-regression to logistic regression for interpretation sake, significance did not change between the two.
+The original beta-regression results can be found in Appendix ???
 
@@
   theme(strip.text.y = element_text(size = 7), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
-  ylab("QMP Replication Ratio") +
-  xlab("QMP Ratio")
-
+  ylab("QMP Ratio (Replication Protocol)") +
+  xlab("QMP Ratio (Original Article)") 
 ```
@@
 The relation between QMP ratios in the replication protocols and corresponding original articles were investigated using a beta regression model.
-It showed that total QMP ratio in the original article can significantly predict total QMP ratio in the subsequent replication (`r betareg_output_to_apa_full(H6_test_results_REV)`), which provides some evidence in favor of hypothesis 6.
+It showed that total QMP ratio in the original article can significantly relates to the total QMP ratio in the subsequent replication (`r betareg_output_to_apa_full(H6_test_results_REV)`), which provides some evidence in favor of hypothesis 6.
 Figure \@ref(fig:Plot46RevisedDataCode) displays this relationship visually.
-However, this relation was not significant for the QMP ratios obtained with the initial protocol (`r betareg_output_to_apa_full(H6_test_results)`).
+However, similarly to the previous test, the relation was not significant for the QMP ratios obtained with the initial protocol (`r betareg_output_to_apa_full(H6_test_results)`).
 
@@
 
-[[[APPENDIX???
-sensitivity analyses and so on: Planned exploratory analyses were preformed to expand on the test for hypothesis 6.
-The relationships between original article QMP ratios and replication protocol QMP ratios were investigated for each QMP type separately.
-Figure \@ref(fig:Plot46RevisedDataCode) visually illustrates the relations of the revised QMP ratios from different QMP types between replication protocols and original articles.
-As shown in the figure, no relation was strong and highly stable, and even fewer were consistent between initial and revised coding protocols.
-]]] IF SO, check rest of article to remove this part by in large.
-
-[[[OMIT: The relations that are consistent are those between original article definition QMPs with replication selection and total QMPs, original article selection QMPs with replication total QMPs, and finally original article quantification QMPs with replication selection QMPs.
-All of these relations were positive across both coding protocols, illustrating that a greater QMP ratio of the specified type in an original article is associated with an increase in QMP ratio for the specific QMP type, or total QMP ratio in the replication protocol.]]]
-
 ```{r Plot46FullInitialDataCode, include = FALSE, eval = FALSE, error = FALSE}
@@
 
-```{r Plot46FullRevisedDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication QMP ratio’s per type with linear regression line.
-The abbreviations on the axes relate to the QMP categories described in Table 1: Def.
-is definition, Op.
-is operationalization, Sel.
-is selection/creation, Quant.
-is quantification, and Mod.
-is modification.
-The X axis facets across the QMP ratios in the original articles, and the Y axis facets across the QMP ratios in the replication protocols.
-Each dot in the figure relates to describes the QMP ratio for the types in that graph across an original article and its replication protocol.
-Note: jitter was applied to these dots in order to show the number of observations at points where multiple dots were present"}
-# Revised
-ggplot(plot_46_data_rev, aes(QMP_ratio, QMP_Rep_ratio)) + 
-  geom_point() +
-  geom_jitter(width = 0.05, height = 0.05) +
-  stat_smooth(method="lm") + 
-  theme_bw() +
-  theme(strip.text.y = element_text(size = 7), strip.background = element_rect(
-    color = "black", fill = "white", size = 1, linetype = "solid"
-  )) +
-  xlab("QMP Ratio (Original)") + ylab("QMP Ratio (Replication)") +
-  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1")) + 
-  facet_grid(vars(QMP_Rep_type), vars(QMP_type))
-
-```
-
-[[[TO APPENDIX sensitivity analyses: Table \@ref(tab:H6ExploratoryAssociationsRevisedTable) shows the results from these tests with the revised protocol QMP coding, while Table \@ref(tab:H6ExploratoryAssociationsInitialTable) shows the results for the QMP ratios obtained via the initial protocol.
-INCLUDING TABLES]]]
-
-```{r H6ExploratoryAssociationsRevisedTable, warning = FALSE}
-# creating the dataframe for the table
-H6_table_dataframe_l_REV <- rbind(Results_H6_between_REV$def_def, Results_H6_between_REV$def_op,
-  Results_H6_between_REV$def_sel, Results_H6_between_REV$def_quant, Results_H6_between_REV$def_mod, 
-  Results_H6_between_REV$op_def, Results_H6_between_REV$op_op, Results_H6_between_REV$op_sel, 
-  Results_H6_between_REV$op_quant, Results_H6_between_REV$op_mod, Results_H6_between_REV$sel_def, 
-  Results_H6_between_REV$sel_op, Results_H6_between_REV$sel_sel, Results_H6_between_REV$sel_quant, 
-  Results_H6_between_REV$sel_mod)
-
-H6_table_dataframe_r_REV <- rbind(Results_H6_between_REV$quant_def, Results_H6_between_REV$quant_op,
-  Results_H6_between_REV$quant_sel, Results_H6_between_REV$quant_quant, Results_H6_between_REV$quant_mod, 
-  Results_H6_between_REV$mod_def, Results_H6_between_REV$mod_op, Results_H6_between_REV$mod_sel, 
-  Results_H6_between_REV$mod_quant, Results_H6_between_REV$mod_mod, Results_H6_between_REV$tot_def, 
-  Results_H6_between_REV$tot_op, Results_H6_between_REV$tot_sel, Results_H6_between_REV$tot_quant, 
-  Results_H6_between_REV$tot_mod)
-
-H6_table_dataframe_REV <- cbind(H6_table_dataframe_l_REV, H6_table_dataframe_r_REV)
-
-# adding asterices for significance to the significant p in the dataframe
-H6_table_dataframe_REV[11,3] <- paste0(H6_table_dataframe_REV[11,3], "$^*$")
-H6_table_dataframe_REV[13,3] <- paste0(H6_table_dataframe_REV[13,3], "$^*$")
-H6_table_dataframe_REV[14,3] <- paste0(H6_table_dataframe_REV[14,3], "$^*$")
-H6_table_dataframe_REV[4,6] <- paste0(H6_table_dataframe_REV[4,6], "$^*$")
-H6_table_dataframe_REV[11,6] <- paste0(H6_table_dataframe_REV[11,6], "$^*$")
-H6_table_dataframe_REV[13,6] <- paste0(H6_table_dataframe_REV[13,6], "$^*$")
-H6_table_dataframe_REV[14,6] <- paste0(H6_table_dataframe_REV[14,6], "$^*$")
-
-# adding a column to help indicate the original QMP type
-H6_table_dataframe_REV_expanded <- cbind(c("Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification"), H6_table_dataframe_REV)
+```{r ReplicabilityReliabilityTestTable, warning=FALSE}
+# creating the dtaframe for the table
+H3_table_dataframe <- rbind(H3_test_result_main_alpha$table, H3_test_result_int_sensitivity_alpha$table, H3_test_result_main_omega$table, H3_test_result_int_sensitivity_omega$table, H3_test_result_slp_sensitivity_omega$table)
+
+# adding an asterix for significance to the significant p in the dataframe
+H3_table_dataframe[3,5] <- paste0(H3_table_dataframe[3,5], "$^*$")
 
 # adding rows to give indication of specific sections (apa_table being awkward)
-H6_table_REV_for_printing <- rbind(c("QMP Type", "", "Definition", "", "", "Quantification", ""), H6_table_dataframe_REV_expanded[1:5,], c("QMP Type", "", "Operationalisation", "", "", "Modification", ""),  H6_table_dataframe_REV_expanded[(6:10),], c("QMP Type", "", "Selection", "", "", "Total", ""), H6_table_dataframe_REV_expanded[(11:15),])
-
-colnames(H6_table_REV_for_printing) <-  c("Original", "$b$", "SD", "$p$", "$b$", "SD", "$p$")
+H3_table_for_printing <- rbind(c("Alpha", "", "", "", ""), c("Logistic Regression Model", "", "", "", ""), H3_table_dataframe[1:2,], c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(3:4),], c("Omega", "", "", "", ""), c("Logistic Regression Model", "", "", "", ""), H3_table_dataframe[(5:6),], c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(7:8),], c("Random-Slope Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(9:10),])
 
@@
 apa_table(
-  H6_table_REV_for_printing, align = c("l", "r", "c", "r", "r", "c", "r")
-  , caption = "Beta Regression Test Results for the Association between Replication
-QMP Ratio and Original QMP Ratio as obtained using the Revised Protocol"
-  , note = "Rows indicate Original QMP type, and within table indicates Replication QMP type.
-Sample size for comparisons involving modification were lower since not all measures were modified.
-Therefore the standard errors are larger.
+  H3_table_for_printing, align = c("l", "r", "r", "r", "r")
+  , caption = "Model Results from Tests of Hypothesis 3"
+  , note = "The Alpha and Omega sections show the models where the independent variable was the calculated Cronbach's alpha and omega coefficient respectively.
+The random slope model for Cronbach's alpha did not converge, thus it results are not shown here.
 $^* p < .05$"
-  , escape = FALSE, placement= "htp", midrules = c(1, 6, 7, 12, 13))
-
-### Possible change: omit sd and p-value, and instead show CI and n, in which case also the note should be changed.
-
-```
+  , escape = FALSE, placement= "htp", midrules = c(1, 2, 5, 7, 8, 9, 12, 15))
+
+```
+
+[[[TO APPENDIX initial analyses: Table \@ref(tab:H6ExploratoryAssociationsInitialTable) shows the results for the QMP ratios obtained via the initial protocol. INCLUDING TABLES]]]
 
@@
 
-[[[To Appendix ???: The unidimensionality of the measures used in the Many Labs projects was assessed through factor analyses, and evaluated based on the criteria discussed in the [Exploratory Analyses](#ExploratoryAnalyses) section above.
-Suitable data for factor analyses was available for nineteen measures.
-These measures were the same as those shown in Figure \@ref(fig:Plot23AlphaCode), with the addition of one more measure from [@cacioppo1983effects].
-A composite score based on the measurement responses was used for sixteen of the nineteen measures to form a single variable in the analyses, and were thus regarded as intended to be unidimensional.
-The number of dimensions for the remaining three were unclear.
-Sufficient fit of the unidimensional model was found for six out of the nineteen evaluated measures.
-However, as shown in Table \@ref(tab:UnidimesnionalityTestResultsTable) the unidimensional model did not hold for any measure data based on the parallel analysis test alone.
-Only the RMSEA $< .08$ criteria suggested evidence for single factor structures.
-INCLUDES THE TABLE BELOW]]]
-
-```{r UnidimesnionalityTestResultsTable, warning = FALSE}
-# add the names of the relevant papers and a shortcut for the measure used.
-cfa_results_expanded <- cbind(c("Caruso et al.
-(2012)", "Husnu & Crisp (2010)", "Nosek et al.
-(2002), Art", "Nosek et al.
-(2002), Math", "Anderson et al.
-(2012), SWL", "Anderson et al.
-(2012), PA", "Anderson et al.
-(2012), NA", "Giessner & Schubert (2007)", "Norenzayan et al.
-(2002)", "Zhong & Liljenquist (2006)", "Monin & Miller (2001), most", "Monin & Miller (2001), some", "Cacioppo et al.
-(1983), elm", "Cacioppo et al.
-(1983), nfc", "De Fruyt et al.
-(2000), consc", "Albarracín et al.
-(2008), exp.
-5, verb", "Albarracín et al.
-(2008), exp.
-5, math", "Shnabel & Nadler (2008)", "Vohs & Schooler (2008)"), cfa_results)
-
-# adding sensible column names
-colnames(cfa_results_expanded) <- c("Original Article", "RMSEA", "N Factors", "Unidimensional")
-
-# Renaming the columns for the not converged cfa.
-cfa_results_for_print <- cfa_results_expanded
-cfa_results_for_print$RMSEA[15] <- "Did"
-cfa_results_for_print$`N Factors`[15] <- "Not"
-cfa_results_for_print$Unidimensional[15] <- "Converge"
-
-# print the table in apa formatting
-apa_table(
-  cfa_results_for_print, align = c("l", "r", "r", "r")
-  , caption = "RMSEA and Parallel Analysis Suggested Factors based on Factor Analysis
-for Measure Data", note = "N Factors refer to the number of factors suggested based on parallel analysis of the measure data.
-The word or abbreviation after the author names and year indicates the specific measure within that original article that was analysed.", escape = FALSE, row.names = FALSE, placement= "htp")
-
-```
-
 # Discussion
@@
 The use of these single item measures comes with risks, since by virtue of being singular they assume that whatever they are measuring is unidimensional, while not being able to test this assumption [@shaw2020measurement], ???and reliability risks???.
-This is particularly concerning given that the analyses of the calculated reliabilities of the multiple item measures showed that some measures ???EXPLORATORY ANALYSIS IDEA: relation of the calculated reliabilities and N items of the measure???, and exploratory analyses of the multiple item measure replication datas, for which unidimensionality could be tested, showed only little support for unidimensionality (see Appendix ???, as was also observed by @shaw2020measurement.
-
-[[[APPENDIX with SENSITIVITY ANALYSES/UNIDIMIMENSIONALITY ANALYSIS: This is potentially quite worrying given that the exploratory analyses of the multiple item measures, for which unidimensionality could be tested, showed only little support for unidimensionality of the measures used in replications.
+This is particularly concerning given that the analyses of the calculated reliabilities of the multiple item measures showed that some measures ???EXPLORATORY ANALYSIS IDEA: relation of the calculated reliabilities and N items of the measure???, and exploratory analyses of the multiple item measure replication datas, for which unidimensionality could be tested, showed only little support for unidimensionality (see Appendix ???, as was also observed by @shaw2020measurement).
+
+???APPENDIX with SENSITIVITY ANALYSES/UNIDIMIMENSIONALITY ANALYSIS???: This is potentially quite worrying given that the exploratory analyses of the multiple item measures, for which unidimensionality could be tested, showed only little support for unidimensionality of the measures used in replications.
 While the measures that were tested for unidimensionality were mostly used as single indicators in the analyses for the replication protocol, one could argue this does not necessarily mean these measures all assessed constructs with a unidimensional structure.
@@
 
-[[[APPENDIX: SENSITIVITY and exploratory ANALYSES: Further analyses based on the QMP ratios of each specific type indicated that across both the initial and revised coding protocols together, only selection, definition, and quantification QMPs in the original article related significantly to selection type QMPs, total QMPs, or both in the replication (see Tables \@ref(tab:H6ExploratoryAssociationsRevisedTable) & \@ref(tab:H6ExploratoryAssociationsInitialTable)).
-It could be that original articles have to provide a clear definition as well as details on the scale, in order for a replication to be able to justify selecting the measure.
-A replication may also be in general more dependent on the original article for information on the definition of the constructs and the choice of measurement, compared to a description of the Operationalisation, quantification, and any modifications.
-These former are features of a measurement, which while preferably similar in a replication to the original, can and should be reported in the replication protocol even if the original article does not contain the details on these features itself.
-However, these are just speculations as the results showed no clear relations between different QMP types across original and replication (see Figure \@ref(fig:Plot46RevisedDataCode)), and testing of causal links was not possible with this data.]]]
-
 ## Limitations & Future Research
@@
 Secondly, alternative ways to analyse the data could have been used, or certain parts of the data could have been examined more closely.
-Several methodologies for doing so have already been suggested throughout the article such as ???insert methodology here???, and others are presented in the appendix ???sensitcity and exploratory analysis appendix???.
+Several methodologies for doing so have already been suggested throughout the article such as ???insert methodology here???, and others are presented in the appendix ???sensitvity and exploratory analysis appendix???.
 Future research can use this study as a basis to find relevant data sources and methodologies to use in order to compliment and extend the findings of this study, or test causal links between measurement usage and replicability.

### 2024-03-06 Scripts/source_script.R

@@ -772,6 +772,20 @@ Data_prep_H3_avg <- function(Data_H5, Data_H3_multiple){
 }
 
 
+
+OR_to_apa_full_supplier <- function(apa_print_result, negative_b = FALSE){
+  OR <- round(exp(as.numeric(substr(apa_print_result, start = 6, 
+                                    stop = 9 + negative_b))), 3) 
+  
+  result_string_with_OR <- paste0(substr(apa_print_result, start = 0, 
+                                  stop = 12 + negative_b), "$OR = ", OR, "$, ", 
+                                  substr(apa_print_result, 
+                                         start = 13 + negative_b, stop = 99))
+  
+  return(result_string_with_OR)
+}
+
+
 # Validity Related Functions ---------------------------------------------------
 # Data loading for the extracted measure data
 Data_unidimensionality_test <- function(Data_1.10, Data_1.11, Data_1.12.3.1, 
@@ -1131,4 +1145,7 @@ data_prep_plot_46 <- function(Data){
   
   return(Plot_46_data)
 }
+
+
+
 

### 2024-03-13 Scripts/Appendix_scripts/Appendix_multilevel_analyses.rmd
finished appendices, and adjusted introductionb, methods. and results sections.

# Appendix B

```{r setup, include=FALSE}
# loading R libraries, perhaps unnecessary
library(papaja)

# loading source script, perhaps unnecessary
source(file = "C:/Users/u686785/OneDrive - Tilburg University/Documents/uvt/PHD/Master Thesis to Paper/Reproducible_R_Project/Scripts/source_script.R")

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(17042023)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

This appendix contains the multilevel model versions of the models used to test Hypothesis 3, 5, & 6. These models were excluded from the published article for the sake of brevity, and because the sample size was no large enough to support multilevel modelling in most cases.

## Hypothesis 3, nested within replication set
### Explanation of Relevance
In this data, replication attempts at different lab locations can be seen as nested within a replication set. In order to see if this nesting might impact the analyses of hypothesis 3, multilevel models are included here as sensitivity checks.

## Model
The specific models used were a multilevel logistic regression random intercept and random slope model. The dependent variable remains replication success at the replication set level, while Cronbach's alpha was no longer averaged across locations.

```{r Hypothesis3MultilevelModelSensitivityAnalyses}
## sensitivity analyses.
# running a random intercept multilevel logistic model
H3_test_result_int_sensitivity_alpha <- apa_print(glmer(formula = replication ~ 1 
                                                + alpha + (1|g), family = 
                                                binomial(), data = 
                                                data_h3_multiple))

# same as for non-multilevel model

# running a random slope multilevel logistic model
H3_test_result_slp_sensitivity_alpha <- apa_print(glmer(formula = replication ~ 1 
                                                + alpha + (1 + alpha|g), 
                                                family = binomial(), data =
                                                data_h3_multiple))

# did not converge
```

### Results
The results of these analyses can be seen in the table below

```{r ReplicabilityReliabilityTestTable, warning=FALSE}
# creating the dtaframe for the table <- separate the OMEGA from here???
H3_table_dataframe <- rbind(H3_test_result_int_sensitivity_alpha$table, H3_test_result_main_omega$table, H3_test_result_int_sensitivity_omega$table, H3_test_result_slp_sensitivity_omega$table)

# adding rows to give indication of specific sections (apa_table being awkward)
H3_table_for_printing <- rbind(c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(1:2),], c("Omega", "", "", "", ""), c("Logistic Regression Model", "", "", "", ""), H3_table_dataframe[(3:4),], c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(5:6),], c("Random-Slope Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(7:8),])

# print the table in apa formatting
apa_table(
  H3_table_for_printing, align = c("l", "r", "r", "r", "r")
  , caption = "Model Results from Tests of Hypothesis 3"
  , note = "The Alpha and Omega sections show the models where the independent variable was the calculated Cronbach's alpha and omega coefficient respectively. The random slope model for Cronbach's alpha did not converge, thus it results are not shown here. $^* p < .05$"
  , escape = FALSE, placement= "htp", midrules = c(3, 5, 6, 7, 10, 13))

```

In none of these models is the relation between reliability and replication success significant (random intercept: `r H3_test_result_int_sensitivity_alpha$full_result$alpha`; random slope: `r H3_test_result_slp_sensitivity_alpha$full_result$alpha`). This corroborates the findings in the article, only now using a random intercept and random slope multilevel model. However, also similarly to the results in the article and perhaps even more so for these multilevel models, the small sample size for these tests means that caution should be taken in interpreting these results.

## Hypotheses 5 & 6, nested within Many Labs
### Explanation of Relevance
The models used in the article to test hypotheses 5 & 6 had independence of observations as an assumption, the observations here referring to a replication set. this is known to be false since the data is nested within four separate Many Labs projects.

### Models
In order to test if this nested structure might influence the relations described in hypothesis 5 & 6, random intercept and random slope multilevel models with each Many Labs project as a group were implemented as sensitivity analyses. As of writing this article the betareg package does not allow for estimation of multilevel models. As an approximation, Gaussian random-intercept multilevel models were implemented using the lmer function from the lme4 package [@R-lme4]. The outcome QMP ratio variable was transformed using the logit link function (the default link function in the betareg package) to better fit the Gaussian model.

```{r Hypotheses5And6SensitivityAnalyses}
## Hypothesis 5 sensitivity test using a random intercept Guassian model.
# create dummy H5 dataframe for use in sensitivity test
data_h5_sens <- data_h5

# convert outcome variable to be usable with Gaussian distribution via
# logit transform.
data_h5_sens$QMP_REV <- log(data_h5_sens$QMP_REV_ratio /(1 - data_h5_sens$QMP_REV_ratio))

check_h5_REV <- apa_print(lmer(formula = QMP_REV ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens))

## Hypothesis 6 sensitivity test using a random intercept Guassian model.
# create dummy H6 dataframe for use in sensitivity test
data_h6_sens <- data_h6

# convert outcome variable to be usable with Gaussian distribution via
# logit transform. 
data_h6_sens$QMP_REV <- log(data_h6_sens$QMP_REV_ratio /(1 - data_h6_sens$QMP_REV_ratio))
data_h6_sens$Rep_QMP_REV <- log(data_h6_sens$Rep_QMP_REV_ratio /(1 - data_h6_sens$Rep_QMP_REV_ratio))

# running the models one with none revised QMP ratio's and one with
check_h6_REV <- apa_print(lmer(formula = Rep_QMP_REV ~ 1 + QMP_REV + (1|many_labs_version), data = data_h6_sens))

# n of mod ratio's that are present (check)
H6_n_check_results_REV <- betareg(Rep_op_REV_ratio ~ mod_REV_ratio, data = data_h6)$n

```

### Results
For hypothesis 5, the sensitivity analyses using a random-intercept multilevel regression found a similar significant association as that found by the main test (`r check_h5_REV$full_result$hypothesis_supportTRUE`). This result is in line with hypothesis 5. This result provides some additional evidence for the stability of hypotehsis 5.

For hypothesis 6, the sensitivity analyses using a random intercept logistic multilevel model resulted in non-significant results, which is contrary to the results found with the main test and is not in line with hypothesis 6 (revised protocol: `r check_h6_REV$full_result$QMP_REV`). This result puts some dents in the confidence that can be attached to the results found through the main test reported in the article.

### 2024-03-13 Scripts/Appendix_scripts/Appendix_pre-reg_analyses.Rmd
finished appendices, and adjusted introductionb, methods. and results sections.

@@
 
-```{r UnidimensionalityExploratoryAnalysis, include = FALSE}
+```{r UnidimensionalityExploratoryAnalysis}
 extracted_data_list <- list(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, data_1.12.3.2_clean,data_2.12.1_clean, data_2.12.2_clean, data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.1_clean, data_3.7.2_clean, data_3.8.2_clean, data_5.1.1_clean, data_5.1.2_clean, data_5.7_clean, data_5.9.1_clean)
@@
 
-```{r Hypothesis6Associations, include = FALSE}
+```{r Hypothesis6Associations}
 ## Associations between the QMP categories
@@
 The relations that are consistent are those between original article definition QMPs with replication selection and total QMPs, original article selection QMPs with replication total QMPs, and finally original article quantification QMPs with replication selection QMPs.
-All of these relations were positive across both coding protocols (see Appendix ???), illustrating that a greater QMP ratio of the specified type in an original article is associated with an increase in QMP ratio for the specific QMP type, or total QMP ratio in the replication protocol.
+All of these relations were positive across both coding protocols (see Appendix D), illustrating that a greater QMP ratio of the specified type in an original article is associated with an increase in QMP ratio for the specific QMP type, or total QMP ratio in the replication protocol.
 
@@
 
-A possibler explanation for these results could be that original articles have to provide a clear definition as well as details on the scale, in order for a replication to be able to justify selecting the measure.
+A possible explanation for these results could be that original articles have to provide a clear definition as well as details on the scale, in order for a replication to be able to justify selecting the measure.
 A replication may also be in general more dependent on the original article for information on the definition of the constructs and the choice of measurement, compared to a description of the Operationalisation, quantification, and any modifications.

### 2024-03-13 Scripts/Manuscript/manuscript.Rmd
finished appendices, and adjusted introductionb, methods. and results sections.

@@
 However, many researchers have also raised concerns that other factors, such as low power [@stanley2018what], lack of strong theoretical foundations [@eronen2021theory], and validity [@finkel2017replicability], which have not been given as much attention, are just as if not more responsible for the lack of successful replications found in psychology.
-An idea which has gained more traction recently is that measurement related issues have a large problematic influence on replicability.
+Another factor which has gained more traction recently are measurement related issues' impact on replicability.
 In particular, studies have focused on the effects of issues such as measurement error and questionable measurement practices on replicability [@stanley2014expectations; @shaw2020measurement; @flake2017construct; @flake2020measurement].
 
-Measurement in psychological science is defined in large part by one overarching issue: psychological constructs, such as affective state and intelligence, cannot be measured directly.
+Measurement in psychological science is defined in large part by one overarching issue: the psychological constructs of interest, such as affective state and intelligence, cannot be measured directly.
 As a result, psychologists face two primary challenges in the use of measurement: First of all, the measure has to assess the construct it intends to measure, even though it can only do so indirectly.
@@
 The results indicated that measurement error caused observed effects found in replication research to vary heavily.
-???relation measurement error and replicability (As a result, interpretations of replications might not be based on tests of the true effect, if the impact of measurement error is not attenuated for.)???
-
-Another key aspect in evaluating the use of measures is how they are reported.
-Questionable Measurement Practices (QMPs) have been coined as a conjugate term to QRPs.
-QMPs are practices that decrease the information necessary to evaluate the measurement of a study.
+
+Even when ignoring reliability, a measurement's content and implementation still need to validly capture what it intends to measure.
+Questionable Measurement Practices (QMPs) are practices that decrease the information that is necessary to evaluate a measurement's validity, and have been coined as a conjugate term to QRPs.
 They range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of measure and procedure of any sourced measures [@flake2020measurement].
@@
 
-This study aims to investigate the influence of measurement error and QMPs on replicability, using data and reports from the large scale Many Labs replication projects.
+This study aims to investigate the influence of both measurement error and QMPs on replicability, using data and reports from the large scale Many Labs replication projects.
 One goal is to expand the research by [@stanley2014expectations] with a practical example.
@@
 However, the investigations remained mostly descriptive.
-This study aims to expand upon the findings of [@flake2022construct] through the use of a new set of replication data, and by investigating the relation between QMP and replicability.
+This study additionally aims to expand upon the findings of [@flake2022construct] through the use of a new set of replication data, and by exploratively investigating the relation between QMP and replicability.
 
@@
 
-As a first step it is worth investigating what the state of measurement error is in original and replication research in psychology, in order to assess the scope of @stanley2014expectations's findings in practice.
-Thus, this study investigated the following:
+As a first step the state of measurement error in original and replication research in psychology is investigated, to assess the scope of @stanley2014expectations's findings in practice:
 
@@
 
-Since direct replications intend to investigate effects in nearly identical scenarios with nearly identical measures as the original study, it is expected that measurement errors are as present in replication research as in original psychological research.
+Since direct replications intend to investigate effects in nearly identical scenarios with nearly identical measures as the original study, it is expected that measurement errors are as present in the replication research looked at in this study as in the accompanying original psychological research.
 
@@
 With large enough differences across contexts, the effect estimates between different replication attempts could deviate from each other beyond direct comparison.
-???RELIABILITY VARIANCE IN META ANALYSIS???.
-To investigate this potential problem, the variation in score reliability is assessed for each measure when used in different contexts.
+To investigate this potential problem, the variation in score reliability is assessed for each measure when used across a set of replications of the same effect in contexts.
 
@@
 Even though reliability estimates are context dependent, sufficient protocol structure can counteract the variance in reliability estimates.
-An example of the standardising impact a structured protocol can have on reducing variability within an effect can be found in investigations into the closely related issue of heterogeneity [@patacchini2007unobserved].
+An example of the standardizing impact a structured protocol can have on reducing variability within an effect can be found in investigations into the closely related issue of heterogeneity [@patacchini2007unobserved].
 Heterogeneity refers to the true variation in the true effect size due to minor but key differences in context, environment, and procedure.
 Heterogeneity is yet another proposed explanation for failed replications.
-This concern even prompted a Many Labs centred around the testing of heterogeneity in replications [@klein2018many].
+This concern even prompted a Many Labs centered around the testing of heterogeneity in replications [@klein2018many].
 However analyses from Many Labs 2, and @olsson2020heterogeneity showed little empirical evidence for widespread heterogeneity in effects among replications.
@@
 This study investigated whether there is something in the measures used for replicated findings that sets them apart from those used for non-replicated findings.
-In particular, this study extends research by @stanley2014expectations on the relationship between reliability and replicability, by using data from real life replication projects.
+One of the elements this study looked at is the reliability of replicated studies compared to the non-replicated studies, thus extending the research by @stanley2014expectations on the relationship between reliability and replicability with data from real life replication projects.
 
@@
 
-Validity of measures can be assessed not only through features found in the data.
-The measure must also be chosen and implemented in a way that enables proper measurement of the variables [@flake2020measurement].
-Any scientific report should therefore clearly motivate the measure and procedure that was used.
+## Questionable Measurement Practices
+A measure not only needs to be reliable, it should also in its design and implementation adequately capture what it intends to measure [@flake2020measurement].
+Any scientific report should therefore clearly motivate the use of measure and procedure.
 Without clear reporting on these aspects, the validity of measurement will remain uncertain.
@@
 
-## Questionable Measurement Practices
-
-This study seeks to conceptually replicate some of the findings of @flake2022construct about QMP reporting in the RPP within the Many Labs replication projects.
+This study sought first of all to conceptually replicate some of the findings of @flake2022construct about QMP reporting in the RPP within the Many Labs replication projects.
 
@@
 If the replication used the measure differently from the original, the replication may no longer be a direct replication.
-???link not direct replication to lack of replication through larger variance argument???
-For these reasons, establishing a link between QMPs and non-replicability should confirm suspicions of their detrimental effects on replications [@flake2017construct; @flake2020measurement; @flake2022construct].
+As a result, there is additional deviation in the estimate of the effect from the original, due to differences in measurement.
+Establishing a link between QMPs and non-replicability should confirm suspicions of their detrimental effects on replications [@flake2017construct; @flake2020measurement; @flake2022construct].
 
@@
 
-The total number of psychological findings for which replication was attempted across the four included Many Labs projects amounts to a total of 60.
+The total number of identified psychological findings for which replication was attempted across the four included Many Labs projects amounts to a total of `r sum(table(coded_data_replications$many_labs_version, coded_data_replications$appearance)[,1])`.
 Each finding was tested across several labs, and was related to a finding from an original study, the combination of all these studies and their associated information formed a replication set.
@@
 This was done to ensure that the analyses could link directly to the replicability of a study.
-Acquiescence bias checks, manipulation checks, measures used for pilot testing, and measures added for exploratory analyses in replication studies were not included..
-The result was a total sample size of 77 measures.
-The Table BELOW show descriptive information about the data for each Many Labs Project.
-
-DESCRIPTIVE TABLE
-
-(Row 1: Many Labs projects - 13 in Many Labs 1; 28 in Many Labs 2; 10 in Many Labs 3; & finally 9 out of the 10 tested findings in Many Labs 5)
-
-(Row 2: Primary measures - 14 in Many Labs 1; 35 in Many Labs 2; 15 in Many Labs 3; & 13 in Many Labs 5)
-
-(Row 3: ???)
-
-Footnote about sample size differences between original and original shortened.
+Acquiescence bias checks, manipulation checks, measures used for pilot testing, and measures added for exploratory analyses in replication studies were not included.
+The result was a total sample size of `r nrow(coded_data_replications)` measures used in both original and replication research [^1].
+Table BELOW shows further descriptive information about the data for each Many Labs Project.
+
+[^1]: Initially the original articles were coded to have 3 more measures than the replication protocols.
+However, these measures were all related to the moral foundations questionnaire, and could be altered from representing five different moral foundations to the two overarching categories of individualizing and binding foundations found described in the replication protocol without much issue or loss of information.
+
+```{r ManyLabsDescriptivesTable, warning = FALSE}
+# construct the Many Labs descriptives table to be printed
+many_labs_descriptives_table <- data.frame("Many Labs Version" = c("1", "2", "3", "5", "Total"),
+                                      "N ML Projects" = c(table(coded_data_replications$many_labs_version, coded_data_replications$appearance)[,1], sum(table(coded_data_replications$many_labs_version, coded_data_replications$appearance)[,1])),
+                                      "N Primary Measures" = c(table(coded_data_replications$many_labs_version), nrow(coded_data_replications)), 
+                                      "Replication Total N" = c(apa_num(mean(coded_data_replications$N[coded_data_replications$many_labs_version == "1"], na.rm = TRUE), digits = 0),
+apa_num(mean(coded_data_replications$N[coded_data_replications$many_labs_version == "2"], na.rm = TRUE), digits = 0),
+apa_num(mean(coded_data_replications$N[coded_data_replications$many_labs_version == "3"], na.rm = TRUE), digits = 0),
+apa_num(mean(coded_data_replications$N[coded_data_replications$many_labs_version == "5"], na.rm = TRUE), digits = 0), apa_num(mean(coded_data_replications$N, na.rm = TRUE), digits = 0)), 
+"Replication Total IQR" = c(apa_num(IQR(coded_data_replications$N[coded_data_replications$many_labs_version == "1"], na.rm = TRUE), digits = 0),
+apa_num(IQR(coded_data_replications$N[coded_data_replications$many_labs_version == "2"], na.rm = TRUE), digits = 0),
+apa_num(IQR(coded_data_replications$N[coded_data_replications$many_labs_version == "3"], na.rm = TRUE), digits = 0),
+apa_num(IQR(coded_data_replications$N[coded_data_replications$many_labs_version == "5"], na.rm = TRUE), digits = 0), apa_num(IQR(coded_data_replications$N, na.rm = TRUE), digits = 0)),
+"Original Total N" = c(apa_num(mean(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "1"], na.rm = TRUE), digits = 0),
+apa_num(mean(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "2"], na.rm = TRUE), digits = 0),
+apa_num(mean(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "3"], na.rm = TRUE), digits = 0),
+apa_num(mean(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "5"], na.rm = TRUE), digits = 0), apa_num(mean(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)),
+"Original Total IQR" = c(apa_num(IQR(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "1"], na.rm = TRUE), digits = 0),
+apa_num(IQR(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "2"], na.rm = TRUE), digits = 0),
+apa_num(IQR(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "3"], na.rm = TRUE), digits = 0),
+apa_num(IQR(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "5"], na.rm = TRUE), digits = 0), apa_num(IQR(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)))
+
+# Changing column names to be less computer speak-y looking
+colnames(many_labs_descriptives_table) <- c("Many Labs Version", "N ML Projects", "N Primary Measures",
+                                            "Replication Total N", "Replication Total IQR", "Original Total N", 
+                                            "Original Total IQR")
+
+# print the table in apa formatting
+apa_table(
+  many_labs_descriptives_table, align = c("l", "r", "r", "r", "r", "r", "r")
+  , caption = "Descriptive information of number of included projects measures, and their sample size, across many labs projects for both original articles and replication protocols"
+  , escape = FALSE, placement = "htp", midrules = 4)
+
+```
 
@@
 However, no coding or analysis of either of them had taken place before the analyses were preregistered.
-When available, codebooks and study materials were used to identify the specific data for each measure.
+Further details on the search strategy can be found in the ???
+supplementary materials.
 
@@
 These publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio [@R-Rstudio].
-Using the replication protocols, codebooks, and analysis scripts from each replication set as a guide, the variables associated with each relevant measure were extracted into their own data frame containing the data from all studies in one replication set.
-These pieces of information were used as the datasets for their respective analyses.
-
-The measure had to consist of multiple scalar items to be considered relevant, as single item measures were not usable for the planned analyses on score reliability [@wanous1996estimating], which followed up on @stanley2014expectations simulation study.
-If cleaned data was available this was chosen over raw data, to ensure that variables were coded as intended.
+When available, codebooks, analysis scripts and study materials were used to identify the specific data for each measure.
+The variables associated with each relevant measure were extracted into their own dataframe containing the data from all studies in one replication set.
+These dataframes together formed the dataset used for the analyses.
+
+In order to be considered relevant for the analysis, the measure had to consist of multiple scalar items, as single item measures were not usable for the planned analyses on score reliability [@wanous1996estimating], following up on simulation study of @stanley2014expectations.
+If cleaned data was available this was chosen over raw data, to ensure that variables were coded as intended (e.g.
+no reverse-coded items).
 Pilot data were omitted from the analyses entirely.
-These criterion resulted in suitable measure data from eighteen replication sets spread across on average 40 lab locations for the analyses of hypotheses 2 & 3.
-
-DESCRIPTIVE TABLE???
+These criterion resulted in suitable measure data from `r apa_num(length(unique(data_h3_multiple$g)), numerals = FALSE)` replication sets spread across on average `r apa_num(mean(table(data_h3_multiple$g)), digits = 0)` lab locations for the analyses of hypotheses 2 & 3.
 
@@
 
-MAKE ALL FOOTNOTE?: (in reference to ML 5 mostly) The relevant OSF page of each replication set was searched through for a file which contained protocol in its name.
+The relevant OSF page of each replication set was searched through for a file which contained protocol in its name.
 If available, a version of the protocol labelled as revised, post-review, peer-review, or endorsed was selected.
 In case there was doubt about which was most appropriate, the latest uploaded relevant protocol was selected.
-Only regular protocols were taken, meaning those not labelled as data collection, analysis protocol or anything similar[^1].
-
-[^1]: The steps taken to access the replication protocol data from Many Labs 5 were not preregistered, and only became clear upon further investigation of the accessible information.
-The specific names and locations of the files that were used as the datasets can be found under the supplementary materials of the OSF page of this article <https://osf.io/gft46/%7D>
+Only regular protocols were taken, meaning those not labelled as data collection, analysis protocol or anything similar[^2].
+
+[^2]: The steps taken to access the replication protocol data from Many Labs 5 were not preregistered, and only became clear upon further investigation of the accessible information.
+The specific names and locations of the files that were used as the datasets can be found under the supplementary materials of the OSF page of this article <https://osf.io/gft46/%7D>.
 
@@
 
-FOOTNOTE: The original articles were identified through the citations in each replication protocol, using Web of Science, Google Scholar, and PsychInfo (in that order).
-An issue was encountered while trying to access @hyman1950current.
+The original articles were identified using the citations in each replication protocol.
+Then through searches via Web of Science, Google Scholar, and PsychInfo (in that order), the articles were retrieved[^3].
+
+[^3]: An issue was encountered while trying to access @hyman1950current.
 However, after contacting the first author of @klein2014investigating a suitable version of the article was obtained for use in the analyses.
@@
 
-MOVE TO APPENDIX/COMBINE WITH EXTERNAL SEARCH STRATEGY FILE: The scope of the coding was limited to the abstract, method, procedure, materials, measure, and initial parts of the results sections.
-Additionally, a keyword search using the name of the measured variable was used to search for any potentially missed information.
-An exception to this procedure was a question asking about the presence of example items.
-For this question, information from supplementary materials was uniquely considered as relevant.
-Another exception was the question regarding the replication of the original effect.
-Tables from the final report of each Many Labs project were used to answer that question.
-
-MOVE TO APPENDIX/COMBINE WITH EXTERNAL SEARCH STRATEGY FILE: These changes (to the QMP coding protocol) included: accepting linked online appendices as a data source for example items; assuming that if no differences between replication and original are measurement is mentioned, that there is no difference, even if it is not explicitly clear; and generally simplified criteria for what constituted sufficiently clear reporting.
-
 ## Measures {#Measures}
@@
 
-In order to answer questions regarding reported reliability, the reported reliability coefficient were extracted from both the replication protocols and the original articles.
+In order to answer questions regarding reported reliability, the reported reliability coefficient was extracted from both the replication protocols and the original articles.
 The reported reliability coefficient is the score reliability reported per measure in the replication protocol or original article.
@@
 
-Cronbach's alpha was calculated as the main score reliability index used in the analyses as it is one of the most popular [@cho2015cronbach].
-Analyses based on the Omega can be found in Appendix ???.
-Omega was included since it has been argued to be a more informative measure of score reliability, while also providing validity evidence for the scale [@crutzen2017scale; @deng2017testing].
-Cronbach's alpha and omega were calculated using the alpha and omega functions respectively in the psych R package [@R-psych].
-Default arguments were used for both functions except the nfactors in the omega function, which was set to 1.
+Cronbach's alpha was calculated as the main score reliability index used in the analyses, as remains the most commonly used indicator of the reliability of a measure.
+Cronbach's alpha was calculated using the alpha function from the psych R package [@R-psych].
+Default arguments were used for the function.
 
@@
 
-The tests for hypotheses 4, 5, & 6 were all based on the number of QMPs coded across both original articles and replication protocols.
-QMPs were all coded to be either true, false, or not applicable.
+The tests for hypotheses 4, 5, & 6 were all based on the QMPs coded across both original articles and replication protocols.
+QMPs were all coded to be either true, false, or not applicable if not relevant for that particular measure (e.g.
+reporting results from a factor analysis in case a single item measure was used).
 Questions related to modification had 'no modification' as an additional answer option, in case the specific aspect of the measure was explicitly not modified.
@@
 
+Eleven out of twenty of the QMP variables used to calculate the QMP ratio have an equivalent in the coding key of @flake2022construct.
+The remaining nine were either altered from the coding key to better fit the QMP counting operationalization, all newly created or modified items were based on the definitions of the QMP categories and their criteria as specified in @flake2020measurement.
+Beside these quantitative variables, a total of four qualitative variables were also included to provide more detailed information on some aspects of the measure and its reporting.
+Details on the items used, their origin, changes, and justifications can be found in supplementary materials ???.
+
 For the analyses of these variables both the total QMP ratios and ratios per QMP type category were used.
@@
 These ratios were preferred over counts, since non applicable items could thus be accounted for.
-Formula \@ref(eq:QMPRatioType) shows the formula that was used to calculate the QMP ratio for a particular QMP type j, where True is 1 if that item was coded as True and 0 otherwise, and False is 1 if that item was coded as False and 0 otherwise, $j \subset \{ definition, operationalisation, selection/creation, quanitification, modification \}$, and $i = 1,..., n_{j-items}$.
-
-FORMULA of QMP ratio:
+Formula \@ref(eq:QMPRatioType) shows the formula that was used to calculate the QMP ratio for a particular QMP type j, where $True_{ij}$ is 1 if $item_{ij}$ was coded as True and 0 otherwise, and $False_{ij}$ is 1 if $item_{ij}$ was coded as False and 0 otherwise, $j \subset \{ definition, operationalisation, selection/creation, quanitification, modification \}$, and $i = 1,..., n_{j-items}$.
 
@@
 ```
+
 For the total QMP ratio:
@@
 ```
-Eleven out of twenty of the QMP variables used to calculate the QMP ratio have an equivalent in the coding key of @flake2022construct.
-The remaining nine were either altered from the coding key to better fit the QMP counting operationalization, all newly created or modified items were based on the definitions of the QMP categories and their criteria as specified in @flake2020measurement.
-Beside these quantitative variables, a total of four qualitative variables were also included to provide more detailed information on some aspects of the measure and its reporting.
-Details on the items used, their origin and justifications can be seen in Supplementary Materials ???.
-
-FOOTNOTE: additional analyses, tables and figures based on QMPs obtained with the initial protocol can be found in Appendix ???.
-
-???Supplementary Materials: on item revision and origin
-
-Two of the qualitative items have an equivalent in the coding key of Variables related to the specific measurement scaling and purpose in the paper, were omitted from the analyses of this study as they were deemed neither relevant for the analyses of this study, nor necessary in matching this study to the key results of @flake2022construct.
-Questions about more general measurement features such as the number of items and how scores were aggregated were altered from @flake2022construct to better fit the use of QMP ratios and associations between them and other coded aspects.
-
-These (qualitative) variables assessed with two having an equivalent in @flake2022construct: the specific version of the measure (if reported); whether and what previous materials were used for the study; what, if any, psychometric evidence beyond reliability score (e.g.
-factor analysis, IRT model, convergent validity) was provided; and whether it was specified or not that the measure was or was not modified.???
 
@@
 The revision of the coding protocol happened after all the data were coded using the initial protocol.
-As a result the coded data using the initial protocol, and the coded data using the revised protocol are both available available on this article's OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages.
+As a result the coded data using the initial protocol, and the coded data using the revised protocol are both available on this article's OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages.
+The analyses, tables and figures presented in this article are all based on the revised coding protocol, the equivalent results based on QMPs obtained with the initial protocol can be found in Appendix D.
 
@@
 No correction for multiple testing was applied, to ensure that the rate of false negatives remained low, the increase in false positive rate was accepted as they deemed less harmful to the exploratory aims of this study.
-This exploratory focus combined with the generally small sample size and consequently low power of the analyses in this article means that descriptives will be used to facilitate the interpretation of the results.
 
@@
 
-The original test for hypothesis 1, a t-test of the reported Cronbach's alpha coefficient values between original and replication, could not be conducted, since not enough score reliabilities were reported to conduct the test and expect sensible results.
+The pre-registered test for hypothesis 1, a t-test of the reported Cronbach's alpha coefficient values between original and replication, could not be conducted, since not enough score reliabilities were reported to conduct the test and expect sensible results.
 Instead, the total number of reported reliability coefficients were compared between the replication protocols and the original articles.
@@
 
-While reported reliabilities were rare, some reliabilities could still be calculated from the replication datasets.
-On top of that, reliabilities could be calculated for each individual lab per replication set so that the variance of them could be assessed.
-In order to separate between and within variance in reliability, a multilevel random intercept model was specified with replication set as the grouping variable and the Cronbach's alpha or omega value of a replication as dependent using the lmer function from the lme4 package [@R-lme4] t.
+While reported reliabilities were rare, reliabilities could still be calculated from `r apa_num(length(unique(data_h3_multiple$g)), numerals = FALSE)` replication datasets.
+On top of that, reliabilities could be calculated for each individual lab per replication set so that the variance of the coefficients of a single measure could be assessed.
+In order to separate between and within variance in reliability, a multilevel random intercept model was specified with replication set as the grouping variable and the Cronbach's alpha value of a replication as dependent using the lmer function from the lme4 package [@R-lme4].
 The formulas for this model, where $alpha_{ij}$ represents the calculated Cronbach's alpha coefficient of a single study at one lab location with $i = 1,..., n_{locations}$ and $j = 1,...,n_{replicationsets}$ look as follows:
@@
 
-# and same analyses for omega
-# intercept only model to check the within and between group variance.
-H2_test_result_omega <- lmer(formula = omega ~ 1 + (1|g), data = data_h2[complete.cases(data_h2),])
-
 ```
@@
 ```{r ICCCalculations, include = FALSE}
-# alpha
+# Variances
 within_group_variance_alpha <- attr(VarCorr(H2_test_result_alpha), "sc")^2
@@
 
+# ICC
 ICC_alpha <- between_group_variance_alpha / (within_group_variance_alpha + between_group_variance_alpha)
 
-# omega
-within_group_variance_omega <- attr(VarCorr(H2_test_result_omega), "sc")^2
-between_group_variance_omega <- attr(VarCorr(H2_test_result_omega)$g, "stddev")^2
-
-ICC_omega <- between_group_variance_omega / (within_group_variance_omega + between_group_variance_omega)
-
-```
-
-???Other analyses were considered after [meta-analyses in particular]???
-
-One of the key tests was that of hypothesis 3 relating to the association between reliability and replicability that had been indicated by @stanley2014expectations.
+```
+
+After the pre-registration was registered, and data had been collected and analysed, it came to the author's attention that it is possible to conduct meta-analyses on reliability coefficients, commonly referred to as Reliability Generalization Meta-Analyses [@botella2012ManagingHeterogeneityVariance; @lopez-ibanez2024ReliabilityGeneralizationMetaanalysis].
+Using meta-analysis, it is possible to quantify within the model the degree of true variation in the metric of interest across samples [@cooper2019handbook].
+Subsequently, the true variation in the metric, or heterogeneity, can be tested to constitute a significant part of the total variation in the observed estimates of the metric or not.
+
+Because heterogeneity estimates line up well as a test for hypothesis 2, a random-effects meta-analysis was conducted on the calculated Cronbach's alpha for each measure for which replication datasets were available and usable.
+The rma function from metafor package [@R-metafor] was used to run the meta-analysis.
+No correction for bias or weighting of the effects has been implemented, to reduce model complexity, and because the data came from Many Labs replication projects and not typical literature.
+
+A meta-analysis requires an estimate of the standard error in order to be conducted.
+For Cronbach's alpha, formulas 2 & 3 from @duhachek2004AlphaStandardError was used to calculate alpha's standard error.
+Heterogeneity was estimated using the tau value, meaning the standard deviation of the distribution of true Cronbach's alpha coefficients for that measure, and tested using the Cochran's Q test for each measure.
+
+In order to test the association between reliability and replicability that had been indicated by @stanley2014expectations on non-simulated data, the calculated reliabilties were used as a predictor for the coded replication success of the effect the measure was used for.
 The logistic regression shown in equation \@ref(eq:H3Main) was used to model this association, where $f(.)$ represents the logit link function, $i = 1,..., n_{replications}$, the outcome $replicated$ which was coded as 1 if the meta-analytic effect in the replication set matches the original effect in direction at a significance alpha level of .05, and 0 otherwise, and the predictor $alpha$ referred to the averaged calculated Cronbach's alpha coefficient:
@@
 
-# and for omega
-H3_test_result_main_omega <- apa_print(glm(formula = replication ~ 1 + 
-                                     omega, family = binomial(), 
-                                     data = data_h3_avg))
-
-# alpha says negative, omega says positive, neither are significant though.
+# coefficient is positive but not significant.
 
@@
 
-```
-
-???Put in appendix???:
-
-In this data, replication attempts at different lab locations can be seen as nested within a replication set.
-In order to see if this nesting might impact the analyses of hypothesis 3, multilevel logistic regression random intercept and random slope model were included as sensitivity checks.
-The dependent variable remains replication success at the replication set level ???(as recommended, but heterogeneity correction)???, while Cronbach's alpha was no longer averaged across locations.
-
-```{r Hypothesis3MultilevelModelSensitivityAnalyses, include = FALSE}
-## sensitivity analyses.
-# running a random intercept multilevel logistic model
-H3_test_result_int_sensitivity_alpha <- apa_print(glmer(formula = replication ~ 1 
-                                                + alpha + (1|g), family = 
-                                                binomial(), data = 
-                                                data_h3_multiple))
-
-# and for omega
-H3_test_result_int_sensitivity_omega <- apa_print(glmer(formula = replication ~ 1 
-                                                + omega + (1|g), family = 
-                                                  binomial(), data = 
-                                                  data_h3_multiple))
-
-# same as for non-multilevel model
-
-# running a random slope multilevel logistic model
-H3_test_result_slp_sensitivity_alpha <- apa_print(glmer(formula = replication ~ 1 
-                                                + alpha + (1 + alpha|g), 
-                                                family = binomial(), data =
-                                                data_h3_multiple))
-
-# and for omega
-H3_test_result_slp_sensitivity_omega <- apa_print(glmer(formula = replication ~ 1 
-                                                + omega + (1 + omega|g), 
-                                                family = binomial(), data =
-                                                data_h3_multiple))
-
-# alpha did not converge, and omega shows no significant effect.
 ```
@@
 ## Hypothesis 4 beta regression model
-# running the model with none revised QMP ratio's
-H4_test_results <- betareg(QMP_ratio ~ rep_org, data = data_h4)
-
 # running the models with revised QMP ratio's
@@
 Where $replication_{i}$ is a dummy coded variable, which was coded as 1 in case the reported QMP ratio belonged to a replications, and 0 if it belonged to an original study.
-For hypothesis 5 the QMP ratio was used as the predictor for replication success, while replication success was used as the outcome[^2].
-
-[^2]: This analysis differs from what was pre-registered.
-Initially this analysis was also a beta-regression where QMP ratio was the outcome variable, while replication success was the predictor.
-The pre-registered analysis outcomes are available in Appendix ???A???.
+For hypothesis 5 the QMP ratio was used as the predictor for replication success, while replication success was used as the outcome[^4].
+
+[^4]: This analysis was changed from the pre-registered analysis.
+In the pre-registered analysis a beta-regression was used to model the same relation, only with replication success as the predictor variables and replication QMP ratio as the outcome.
+The outcome was swapped in the article for the sake of interpretability.
+The results based on the original analyses are presented in Appendix A.
 
@@
 ## Hypothesis 5 logistic regression model
-H5_test_results <- apa_print(glm(hypothesis_support ~ QMP_ratio, data = data_h5, family = binomial))
-
 H5_test_results_REV <- apa_print(glm(hypothesis_support ~ QMP_REV_ratio, data = data_h5, family = binomial))
 
-H5_test_results_with_OR <- OR_to_apa_full_supplier(H5_test_results$full_result$QMP_ratio, negative_b = TRUE)
-
 H5_test_results_REV_with_OR <- OR_to_apa_full_supplier(H5_test_results_REV$full_result$QMP_REV_ratio, negative_b = TRUE)
@@
 
-The relationship between original article QMPs and replication protocol QMPs was modelled to test hypothesis 6.
+The relationship between original article QMPs and replication protocol QMPs was modeled to test hypothesis 6.
 The outcome variable is the same as the predictor in the model for hypothesis 5.
@@
 ## Hypothesis 6 beta regression model
-H6_test_results <- betareg(Rep_QMP_ratio ~ QMP_ratio, data = data_h6)
-
 H6_test_results_REV <- betareg(Rep_QMP_REV_ratio ~ QMP_REV_ratio, data = data_h6)
@@
 
-APPENDIX:"These models had independence of observations as an assumption, the observations here referring to a replication set.
-this is known to be false since the data is nested within four separate Many Labs projects.
-In order to test if this nested structure might influence the relations described in hypothesis 5 & 6, random intercept and random slope multilevel models with each Many Labs project as a group were implemented as sensitivity analyses.
-As of writing this article the betareg package does not allow for estimation of multilevel models.
-As an approximation, Gaussian random-intercept multilevel models were implemented using the lmer function from the lme4 package [@R-lme4].
-The outcome QMP ratio variable was transformed using the logit link function (the default link function in the betareg package) to better fit the Gaussian model.
-???FOOTNOTE: exploratory analyses were preregistered for this but left out.???
-
-```{r Hypotheses5And6SensitivityAnalyses, include = FALSE}
-## Hypothesis 5 sensitivity test using a random intercept Guassian model.
-# create dummy H5 dataframe for use in sensitivity test
-data_h5_sens <- data_h5
-
-# convert outcome variable to be usable with Gaussian distribution via
-# logit transform.
-data_h5_sens$QMP <- log(data_h5_sens$QMP_ratio /(1 - data_h5_sens$QMP_ratio))
-data_h5_sens$QMP_REV <- log(data_h5_sens$QMP_REV_ratio /(1 - data_h5_sens$QMP_REV_ratio))
-
-check_h5 <- apa_print(lmer(formula = QMP ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens))
-
-check_h5_REV <- apa_print(lmer(formula = QMP_REV ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens))
-
-## Hypothesis 6 sensitivity test using a random intercept Guassian model.
-# create dummy H6 dataframe for use in sensitivity test
-data_h6_sens <- data_h6
-
-# convert outcome variable to be usable with Gaussian distribution via
-# logit transform.
-data_h6_sens$QMP <- log(data_h6_sens$QMP_ratio /(1 - data_h6_sens$QMP_ratio))
-data_h6_sens$Rep_QMP <- log(data_h6_sens$Rep_QMP_ratio /(1 - data_h6_sens$Rep_QMP_ratio))
-data_h6_sens$QMP_REV <- log(data_h6_sens$QMP_REV_ratio /(1 - data_h6_sens$QMP_REV_ratio))
-data_h6_sens$Rep_QMP_REV <- log(data_h6_sens$Rep_QMP_REV_ratio /(1 - data_h6_sens$Rep_QMP_REV_ratio))
-
-# running the models one with none revised QMP ratio's and one with
-check_h6 <- apa_print(lmer(formula = Rep_QMP ~ 1 + QMP + (1|many_labs_version), data = data_h6_sens))
-
-check_h6_REV <- apa_print(lmer(formula = Rep_QMP_REV ~ 1 + QMP_REV + (1|many_labs_version), data = data_h6_sens))
-
-# n of mod ratio's that are present (check)
-H6_n_check_results <- betareg(Rep_op_ratio ~ mod_ratio, data = data_h6)$n
-H6_n_check_results_REV <- betareg(Rep_op_REV_ratio ~ mod_REV_ratio, data = data_h6)$n
-
-```
+MOVE TO EXTERNAL SEARCH STRATEGY FILE: 
+The scope of the coding was limited to the abstract, method, procedure, materials, measure, and initial parts of the results sections.
+Additionally, a keyword search using the name of the measured variable was used to search for any potentially missed information.
+An exception to this procedure was a question asking about the presence of example items.
+For this question, information from supplementary materials was uniquely considered as relevant.
+Another exception was the question regarding the replication of the original effect.
+Tables from the final report of each Many Labs project were used to answer that question.
+
+These changes (to the QMP coding protocol) included: accepting linked online appendices as a data source for example items; assuming that if no differences between replication and original are measurement is mentioned, that there is no difference, even if it is not explicitly clear; and generally simplified criteria for what constituted sufficiently clear reporting.
+
+SUPPLEMENTARY MATERIALS ON ITEM REVISION AND ORIGIN:
+Two of the qualitative items have an equivalent in the coding key of Variables related to the specific measurement scaling and purpose in the paper, were omitted from the analyses of this study as they were deemed neither relevant for the analyses of this study, nor necessary in matching this study to the key results of @flake2022construct.
+Questions about more general measurement features such as the number of items and how scores were aggregated were altered from @flake2022construct to better fit the use of QMP ratios and associations between them and other coded aspects.
+
+These (qualitative) variables assessed with two having an equivalent in @flake2022construct: the specific version of the measure (if reported); whether and what previous materials were used for the study; what, if any, psychometric evidence beyond reliability score (e.g.
+factor analysis, IRT model, convergent validity) was provided; and whether it was specified or not that the measure was or was not modified.
 
@@
 ## Data Visualization
-
-Table \@ref(tab:ReplicationRatioTable) displays the proportion of replication success per Many Labs project. ???Cronbach's alpha of the QMP items???
-
-```{r ReplicationRatioTable, warning = FALSE}
-# construct the replication ratio table to be printed
-replication_ratio_table <- data.frame("Many Labs Version" = c("1", "2", "3", "5", "Total"),
-                                      "N Total" = c(table(coded_data_replications$many_labs_version), nrow(coded_data_replications)), 
-                                      "N Replicated" = c(table(coded_data_replications$many_labs_version, coded_data_replications$hypothesis_support)[, "Yes"], table(coded_data_replications$hypothesis_support)["Yes"]))
-
-# calculate the replication ratio from the N measures whose studies were replicated
-# and the N total measures, per Many Labs study.
-replication_ratio_table$"Replication Ratio" <- replication_ratio_table$N.Replicated / replication_ratio_table$N.Total
-
-# Changing column names to be less computer speak-y looking
-colnames(replication_ratio_table) <- c("Many Labs Version", "N Total", "N Replicated",
-                                       "Replication Ratio")
-
-# converting columns to string to then add a superscript to one of the elements
-# in the table.
-replication_ratio_table$"N Replicated" <- as.character(replication_ratio_table$"N Replicated")
-
-# adding a superscript for a later footnote
-replication_ratio_table$"N Replicated"[3] <- "$3^a$"
-
-# print the table in apa formatting
-apa_table(
-  replication_ratio_table, align = c("l", "r", "r", "r")
-  , caption = "Ratio of measures for which the effect was considered replicated, across many labs projects"
-  , note = "$^a$replication was assessed as unclear for three of the measures, since their effect was not fully replicated.
-These have been treated as not replicated within this table and further analyses throughout the article"
-  , escape = FALSE, placement = "htp", midrules = 4)
-
-```
-
-In order to visualise the results on QMPs, the proportions of the QMP ratio obtained for each QMP type (see Table \@ref(tab:QMPCodingInfoTable)) are shown across the top layer of Figure \@ref(fig:Plot456Code) for both replication protocols and original articles.
+This study's focus is mainly exploratory and descriptive.
+Additionally, the number of coded and extracted data is quite substantial.
+Therefore, the result section will start with a number of visuals and descriptives to provide some clarity on the data and its characteristics.
+
+Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts the flow of measures for which reliability was reported.
+The first split shows the number of measures which consisted of multiple items in a scale, which were approximately equal between replication and original (`r apa_num(table(coded_data_replications$N_items)["multiple item measure"])` and `r apa_num(table(coded_data_original_shortened$N_items)["multiple item measure"])`, respectively).
+Reliability was expected to be reported only for these measures.
+Taking these multiple item measures, the graph illustrates that `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` measures in the replication protocols and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles reported a reliability coefficient.
+Looking closer at these reported reliability coefficients, it can be seen in the graph that the most commonly reported coefficient was the Cronbach's alpha, which accounted for `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles.
+
+```{r ReliabilityReportingFlowDiagram, fig.cap = "Reliability reporting flow diagram.
+Figure shows the number of measures as reported in both the replication protocols and original article, which meet the criterion in the box within the diagram and those criteria before it."}
+knitr::include_graphics(path = "../../SupplementaryMaterials/reliability_reporting_flow_diagram.png")
+```
+
+If we look at the reliabilities obtained from the Many Labs responses on each measure for which scalar data could be accessed, the distributions of the Cronbach's alpha coefficients for each replication set for are displayed in Figure \@ref(fig:Plot23AlphaCode), separated by successful and unsuccessful replication.
+The average calculated Cronbach's alpha coefficient across replication sets was `r apa_num(mean(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$alpha, na.rm = TRUE), digits = 3)`
+
+```{r Plot23AlphaCode,warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the eighteen distinct measures for which suitable raw data was available to calculate Cronbach’s alpha coefficients from.
+The green lines indicate the meta-analytic prediction interval lower and upper bound.
+The blue triangles indicate the reported alpha coefficient for that measure from the original article, when available.
+The Tau column besides the figure shows the tau heterogeneity estimate based on a meta-analysis of the calculated reliabilities for each measure, meta-analysis for which the Q-test for Heterogeneity was signicant at alpha < .05 are in black, not significant results are left grey.
+The Diff column shows the difference between reported reliability and the average reliability calculated from the Many Labs data for the applicable measures, the differences in bold are for reported reliabilities that fell outside the 95% quantile of calculated reliability scores."}
+
+# data re-ordering (was not saved in export)
+plot_23_data_alpha_reordered <- data_prep_plot_23_alpha(plot_23_data_alpha)
+
+### use ggarange for aranging things at the side of this graph
+
+# plot for alpha
+ggplot(plot_23_data_alpha_reordered, aes(x = alpha, y = g)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_hline(yintercept = 6.5, color = "red", size = 1) +
+  geom_point(alpha = 0.1) +
+
+  # adding in the tau values
+  geom_text(label = format(plot_23_data_alpha_reordered$tau, digits = 1), x = 1.15, size = 2.8, alpha = ifelse(plot_23_data_alpha_reordered$QEp < .05, 1, 0)) +
+  geom_text(label = format(plot_23_data_alpha_reordered$tau, digits = 1), x = 1.15, size = 2.8, alpha = ifelse(plot_23_data_alpha_reordered$QEp >= .05, 1, 0), colour = "grey") +
+
+  # adding in the alpha annotations
+   annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[1], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[1], "bold", "plain"))), ymin = 1, ymax = 1, xmin = 1.24, xmax = 1.24) +
+  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[2], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[2], "bold", "plain"))), ymin = 2, ymax = 2, xmin = 1.24, xmax = 1.24) +
+  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[3], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[3], "bold", "plain"))), ymin = 3, ymax = 3, xmin = 1.24, xmax = 1.24) +
+  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[4], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[4], "bold", "plain"))), ymin = 5, ymax = 5, xmin = 1.24, xmax = 1.24) +
+  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[5], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[5], "bold", "plain"))), ymin = 8, ymax = 8, xmin = 1.25, xmax = 1.25) +
+  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[6], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[6], "bold", "plain"))), ymin = 9, ymax = 9, xmin = 1.24, xmax = 1.24) +
+  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[7], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[7], "bold", "plain"))), ymin = 10, ymax = 10, xmin = 1.24, xmax = 1.24) +
+  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[8], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[8], "bold", "plain"))), ymin = 11, ymax = 11, xmin = 1.24, xmax = 1.24) +
+  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[9], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[9], "bold", "plain"))), ymin = 12, ymax = 12, xmin = 1.25, xmax = 1.25) +
+
+  theme_minimal() +
+  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), "lines")) +
+
+  # adding the necessary indicative texts
+  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 7.25, ymax = 7.25, xmin = 0.01, xmax = 0.01) +
+  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 6, ymax = 6, xmin = 0.01, xmax = 0.01) +
+  annotation_custom(grob = textGrob(label = "Tau", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.08, xmax = 1.08) +
+  annotation_custom(grob = textGrob(label = "Diff", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.24, xmax = 1.24) +
+
+  coord_cartesian(xlim = c(0, 1), clip = "off") +
+
+  # adding the blue triangles for reported reliability and green prediction intervals
+  geom_point(data = plot_23_data_reported_alpha, mapping = aes(x = coefficient_reported, y = article_order), color = "blue", shape = 17, size = 3) +
+  geom_point(mapping = aes(x = pi.lb), color = "green", shape = 124, size = 2.5) + 
+  geom_point(mapping = aes(x = pi.ub), color = "green", shape = 124, size = 2.5) +
+
+  ylab("") +
+  xlab("Cronbach's alpha") 
+```
+
+In order to visualize the results on QMPs, the proportions of the QMP ratio obtained for each QMP type (see Table \@ref(tab:QMPCodingInfoTable)) are shown across the top layer of Figure \@ref(fig:Plot456Code) for both replication protocols and original articles.
 While in the bottom layer of Figure \@ref(fig:Plot456Code) the overlayed distributions of the total QMP ratios from the replication protocols and original studies are displaued, with dots indicating each datapoint, and the line indicating the mean for either distribution.
 A large number of QMP ratios are missing for the QMP modification type , because only `r apa_num(table(coded_data_replications$mod_check)["True"])` out of `r apa_num(length(coded_data_replications$mod_check))` measures in replications, and only `r apa_num(table(coded_data_original_shortened$mod_check)["True"], numerals = FALSE)` measures used in original studies were modified.
-.
+???Cronbach's alpha of the QMP items???
 
@@
 
-# plot for alpha
 ### ratio (REV) Original and Rep
 Plot_456_1 <- ggplot(plot_456_data[plot_456_data$QMP_type != "Total",], 
-                      aes(x = RepOrg, fill = as.factor(QMP_ratio_1))) + 
+                      aes(x = RepOrg, fill = as.factor(QMP_ratio_1_REV))) + 
   geom_bar(position = "fill") +
@@
   facet_grid(~ QMP_type) + 
-  ylab("Percentage of Overal Coding") +
+  ylab("Relative Prevalence of\nQMP Ratio in Sample") +
   xlab("QMP Type") +
@@
 
-Mean_Rat_Rep <- mean(plot_456_data$QMP_ratio[
+Mean_Rat_Rep <- mean(plot_456_data$QMP_ratio_REV[
   plot_456_data$QMP_type == "Total" & plot_456_data$RepOrg == "Replication"])
-Mean_Rat_Org <- mean(plot_456_data$QMP_ratio[
+Mean_Rat_Org <- mean(plot_456_data$QMP_ratio_REV[
   plot_456_data$QMP_type == "Total" & plot_456_data$RepOrg == "Original"])
@@
 Plot_456_2 <- ggplot(plot_456_data[plot_456_data$QMP_type == "Total",], 
-       aes(x = QMP_ratio, fill = RepOrg, colour = RepOrg)) +
+       aes(x = QMP_ratio_REV, fill = RepOrg, colour = RepOrg)) +
   geom_density(alpha = 0.2) +
@@
 
-Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts the flow of measures for which reliability was reported.
-The first split shows the number of measures which consisted of multiple items in a scale, which were approximately equal between replication and original (`r apa_num(table(coded_data_replications$N_items)["multiple item measure"])` and `r apa_num(table(coded_data_original_shortened$N_items)["multiple item measure"])`, respectively).
-Reliability was expected to be reported only for these measures.
-Taking these multiple item measures, the graph illustrates that `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` measures in the replication protocols and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles reported a reliability coefficient.
-Looking closer at these reported reliability coefficients, it can be seen in the graph that the most commonly reported coefficient was the Cronbach's alpha, which accounted for `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles.
-
-```{r ReliabilityReportingFlowDiagram, fig.cap = "Reliability reporting flow diagram.
-Figure shows the number of measures as reported in both the replication protocols and original article, which meet the criterion in the box within the diagram and those criteria before it."}
-knitr::include_graphics(path = "../../SupplementaryMaterials/reliability_reporting_flow_diagram.png")
-```
-
-If we look at the reliabilities obtained from the Many Labs responses on each measure for which scalar data could be accessed, the distributions of the Cronbach's alpha coefficients for each replication set for are displayed in Figure \@ref(fig:Plot23AlphaCode), separated by successful and unsuccessful replication.
-The average calculated Cronbach's alpha coefficient across replication sets was `r apa_num(mean(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(mean(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`
-
-```{r Plot23AlphaCode,warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the eighteen distinct measures for which suitable raw data was available to calculate Cronbach’s alpha coefficients from.
-The green lines indicate the meta-analytic prediction interval lower and upper bound.
-The blue triangles indicate the reported alpha coefficient for that measure from the original article, when available.
-The Tau column besides the figure shows the tau heterogeneity estimate based on a meta-analysis of the calculated reliabilities for each measure, meta-analysis for which the Q-test for Heterogeneity was signicant at alpha < .05 are in black, not significant results are left grey.
-The Diff column shows the difference between reported reliability and the average reliability calculated from the Many Labs data for the applicable measures, the differences in bold are for reported reliabilities that fell outside the 95% quantile of calculated reliability scores."}
-
-# data re-ordering (was not saved in export)
-plot_23_data_alpha_reordered <- data_prep_plot_23_alpha(plot_23_data_alpha)
-
-### use ggarange for aranging things at the side of this graph
-
-# plot for alpha
-ggplot(plot_23_data_alpha_reordered, aes(x = alpha, y = g)) +
-  geom_boxplot(outlier.shape = NA) +
-  geom_hline(yintercept = 6.5, color = "red", size = 1) +
-  geom_point(alpha = 0.1) +
-
-  # adding in the tau values
-  geom_text(label = format(plot_23_data_alpha_reordered$tau, digits = 1), x = 1.15, size = 2.8, alpha = ifelse(plot_23_data_alpha_reordered$QEp < .05, 1, 0)) +
-  geom_text(label = format(plot_23_data_alpha_reordered$tau, digits = 1), x = 1.15, size = 2.8, alpha = ifelse(plot_23_data_alpha_reordered$QEp >= .05, 1, 0), colour = "grey") +
-
-  # adding in the alpha annotations
-   annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[1], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[1], "bold", "plain"))), ymin = 1, ymax = 1, xmin = 1.24, xmax = 1.24) +
-  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[2], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[2], "bold", "plain"))), ymin = 2, ymax = 2, xmin = 1.24, xmax = 1.24) +
-  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[3], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[3], "bold", "plain"))), ymin = 3, ymax = 3, xmin = 1.24, xmax = 1.24) +
-  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[4], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[4], "bold", "plain"))), ymin = 5, ymax = 5, xmin = 1.24, xmax = 1.24) +
-  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[5], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[5], "bold", "plain"))), ymin = 8, ymax = 8, xmin = 1.25, xmax = 1.25) +
-  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[6], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[6], "bold", "plain"))), ymin = 9, ymax = 9, xmin = 1.24, xmax = 1.24) +
-  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[7], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[7], "bold", "plain"))), ymin = 10, ymax = 10, xmin = 1.24, xmax = 1.24) +
-  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[8], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[8], "bold", "plain"))), ymin = 11, ymax = 11, xmin = 1.24, xmax = 1.24) +
-  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[9], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[9], "bold", "plain"))), ymin = 12, ymax = 12, xmin = 1.25, xmax = 1.25) +
-
-  theme_minimal() +
-  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), "lines")) +
-
-  # adding the necessary indicative texts
-  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 7.25, ymax = 7.25, xmin = 0.01, xmax = 0.01) +
-  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 6, ymax = 6, xmin = 0.01, xmax = 0.01) +
-  annotation_custom(grob = textGrob(label = "Tau", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.08, xmax = 1.08) +
-  annotation_custom(grob = textGrob(label = "Diff", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.24, xmax = 1.24) +
-
-  coord_cartesian(xlim = c(0, 1), clip = "off") +
-
-  # adding the blue triangles for reported reliability and green prediction intervals
-  geom_point(data = plot_23_data_reported_alpha, mapping = aes(x = coefficient_reported, y = article_order), color = "blue", shape = 17, size = 3) +
-  geom_point(mapping = aes(x = pi.lb), color = "green", shape = 124, size = 2.5) + 
-  geom_point(mapping = aes(x = pi.ub), color = "green", shape = 124, size = 2.5) +
-
-  ylab("") +
-  xlab("Cronbach's alpha") 
-```
-
-[BIG Original vs. Replication DESCRIPTIVES TABLE SOMEWHERE]
-
-Existing materials were used for `r apa_num(table(coded_data_replications$sel_existing)["True, namely:"], digits = 0)` of the `r apa_num(nrow(coded_data_replications), digits = 0)` measures in replications (FOOTNOTE: the relevant question asking participants to rate how much they agreed with a certain quote remained the same, however the quote itself and the people it was attributed too were both completely new compared to the original) and for `r apa_num(table(coded_data_original_shortened$sel_existing)["True, namely:"], digits = 0)` in original studies.
-The specific version of the measure was reported for `r apa_num(length(coded_data_replications$op_version[coded_data_replications$op_version != ""]), numerals = FALSE)` measures in replications, and `r apa_num(length(coded_data_original_shortened$op_version[coded_data_original_shortened$op_version != ""]), numerals = FALSE)` measures in original articles.
-For those measures that were not based on existing materials, `r apa_num(table(coded_data_replications$sel_existing)["False, materials were newly developped for this study"], numerals = FALSE)` in the replications and `r apa_num(table(coded_data_original_shortened$sel_existing)["False, materials were newly developped for this study"], numerals = FALSE)` in original articles clearly stated that they were newly created for the study.
-Only `r apa_num(table(coded_data_original_shortened$mod_time)["After/During"], numerals = FALSE)` measure in the original articles was modified from its original source during the data collection period, all other measures were modified before that, if at all.
-The mean sample size within the replications was `r apa_num(mean(coded_data_replications$N, na.rm = TRUE), digits = 0)` participants (IQR = `r apa_num(IQR(coded_data_replications$N, na.rm = TRUE), digits = 0)`).
-In the original articles the mean sample size was `r apa_num(mean(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)` (IQR = `r apa_num(IQR(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)`).
+Table \@ref(tab:MeasurementReportingDescriptivesTable) shows additional descriptive information on measurement reporting based on counts of reported information that were not used to calculate QMP ratios.
+When it was not stated that existing materials were used, it was expected that the remaining articles would clearly specify that they newly created the materials, however this was not always the case for neither original articles (`r table(coded_data_original_shortened$sel_existing)[["False, materials were newly developped for this study"]]` out of `r nrow(coded_data_original_shortened) - table(coded_data_original_shortened$sel_existing)[["True, namely:"]]` relevant measures) nor replication protocols (`r table(coded_data_original_shortened$sel_existing)[["False, materials were newly developped for this study"]]` out of `rnrow(coded_data_replications) - table(coded_data_replications$sel_existing)[["True, namely:"]]` relevant measures).
+
+```{r MeasurementReportingDescriptivesTable}
+# construct the replication descriptives table to be printed
+reporting_descriptives_table <- data.frame("Original Article" = c(length(coded_data_original_shortened$op_version[coded_data_original_shortened$op_version != ""]), table(coded_data_original_shortened$sel_existing)[["True, namely:"]], table(coded_data_original_shortened$sel_existing)[["False, materials were newly developped for this study"]], sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), table(coded_data_original_shortened$mod_check_REV)[["True"]], sum(coded_data_original_shortened$mod_time == "After/During"), nrow(coded_data_original_shortened)),
+                                             "Replication Protocol" = c(length(coded_data_replications$op_version[coded_data_replications$op_version != ""]), table(coded_data_replications$sel_existing)[["True, namely:"]], table(coded_data_replications$sel_existing)[["False, materials were newly developped for this study"]], sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), table(coded_data_replications$mod_check_REV)[["True"]], sum(coded_data_replications$mod_time == "After/During"), nrow(coded_data_replications)))
+
+# Changing rownames to reflect the variables
+rownames(reporting_descriptives_table) <- c("Specified measure version", "Used existing materials", "Specified being newly created", "Reported psychometric evidence", "N modified", "Modified after/during data collection", "Total")
+
+# Changing column names to be less robot speak
+colnames(reporting_descriptives_table) <- c("Original Article", "Replication Protocol")
+
+# converting columns to string to then add a superscript to one of the elements
+# in the table.
+reporting_descriptives_table$"Replication Protocol" <- as.character(reporting_descriptives_table$"Replication Protocol")
+
+# adding a superscript for a later footnote
+reporting_descriptives_table$"Replication Protocol"[3] <- "$1^a$"
+
+# print the table in apa formatting
+apa_table(
+  reporting_descriptives_table, align = c("l", "r", "r")
+  , caption = "Descriptives of Measurement Reporting Variables not used for calculating QMP Ratios for both Original Articles and Replication Protocols"
+  , note = "$^a$ the relevant question asking participants to rate how much they agreed with a certain quote remained the same, however the quote itself and the people it was attributed too were both completely new compared to the original"
+  , escape = FALSE, placement = "htp", midrules = 6)
+
+```
+
+Finally, table \@ref(tab:ReplicationRatioTable) displays the proportion of replication success based on the criteria of a meta-significance cutoff smaller than .05 per Many Labs project.
+
+```{r ReplicationRatioTable, warning = FALSE}
+# construct the replication ratio table to be printed
+replication_ratio_table <- data.frame("Many Labs Version" = c("1", "2", "3", "5", "Total"),
+                                      "N Total" = c(table(coded_data_replications$many_labs_version), nrow(coded_data_replications)), 
+                                      "N Replicated" = c(table(coded_data_replications$many_labs_version, coded_data_replications$hypothesis_support)[, "Yes"], table(coded_data_replications$hypothesis_support)["Yes"]))
+
+# calculate the replication ratio from the N measures whose studies were replicated
+# and the N total measures, per Many Labs study.
+replication_ratio_table$"Replication Ratio" <- round(replication_ratio_table$N.Replicated / replication_ratio_table$N.Total, digits = 2)
+
+# Changing column names to be less computer speak-y looking
+colnames(replication_ratio_table) <- c("Many Labs Version", "N Total", "N Replicated",
+                                       "Replication Ratio")
+
+# converting columns to string to then add a superscript to one of the elements
+# in the table.
+replication_ratio_table$"N Replicated" <- as.character(replication_ratio_table$"N Replicated")
+
+# adding a superscript for a later footnote
+replication_ratio_table$"N Replicated"[3] <- "$3^a$"
+
+# print the table in apa formatting
+apa_table(
+  replication_ratio_table, align = c("l", "r", "r", "r")
+  , caption = "Ratio of measures for which the effect was considered replicated, across many labs projects"
+  , note = "$^a$replication was assessed as unclear for three of the measures, since their effect was not fully replicated.
+These have been treated as not replicated within this table and further analyses throughout the article"
+  , escape = FALSE, placement = "htp", midrules = 4)
+
+```
 
 ## Reliability
-
-Figure ...
-already demonstrates that multiple item measures are most commonly not accompanied by a reported reliability coefficient in neither original articles nor replication protocols.
-Additionally, when comparing between the two using a chi square comparison, it was observed that in replication protocols reliability coefficients are reported significantly less often than in original articles ($\chi^{2}$(`r apa_num(H1_test_result$parameter)`) = `r apa_num(H1_test_result$statistic)`, *p* = `r apa_p(H1_test_result$p.value)`).
-These results are contradictory to hypothesis 1.
+Figure \@ref(fig:ReliabilityReportingFlowDiagram) illustrates that multiple item measures are most commonly not accompanied by a reported reliability coefficient in neither original articles (`r sum(coded_data_original_shortened$reliability_type[coded_data_original_shortened$N_items == "multiple item measure"] != "Not Reported")` out of `r sum(coded_data_original_shortened$N_items == "multiple item measure")` multiple item measures) nor replication protocols (`r sum(coded_data_replications$reliability_type[coded_data_replications$N_items == "multiple item measure"] != "Not Reported")` out of `r sum(coded_data_replications$N_items == "multiple item measure")` multiple item measures).
+Additionally, when comparing between the two using a chi square comparison, it was observed that reliability coefficients are reported significantly less often in replication protocols than in original articles ($\chi^{2}$(`r apa_num(H1_test_result$parameter)`) = `r apa_num(H1_test_result$statistic)`, *p* = `r apa_p(H1_test_result$p.value)`).
+These results are contradictory to hypothesis 1, which predicted the opposite.
 
@@
 Because this number is larger than .5, it suggests that variance was larger between replication sets than within.
-A more sophisticated, albeit not pre-registered, test based on the Tau heterogeneity estimate and Q-test for heterogeneity obtained from a meta-analysis of the calculated reliability coefficients was additionally performed to test hypothesis 2.
-Figure \@ref(fig:Plot23AlphaCode) shows that there is quite some variance in Tau (the indicator of true differences in reliability scores between labs) with some having a Tau estimate of approximately 0, and others reaching beyond .1, which suggests that ???the true variance in reliability for that measure is as large as .1 point of Cronbach's alpha???.
-Based on the Q-test for heterogeneity, ???5???
-out of the total of ???18???
-estimates of heterogeneity were judged to be significant.
-However, the Q-test and tau are both highly sensitive to the number of studies in the meta-analyses (CITATION HERE), which may explain some of the results.
-
-Therefore, while evidence for heterogeneity would not be in line with hypothesis 2, the evidence remains inconsistent when looking across all studies, and sensitive to the sample size of the meta-analyses.
-
-In figure ...
-the calculated reliabilities were separated by a red line based on whether the replications the measures mere used in were successful when judged at a meta-analytic significance level of .05.
-A logistic regression was performed to detect if there was indeed a relation between calculated reliabilities and replication success.
-
-Cronbach's alpha did not significantly relate to replication success in the main logistic regression model (Cronbach's alpha: `r H3_main_full_results_alpha_with_OR`), nor in any of the multilevel sensitivity analyses models (see Appendix ???).
-This is contradictory to the expectation in hypothesis 3.
-Similar results were found for the analyses when using Omega as the reliability coefficient of choice (see Appendix ???).
-However, caution should be taken in evaluating these results, given the small sample number of measures used to estimate the models and the resulting large uncertainty around the estimate.
+
+A more sophisticated, albeit not pre-registered, exploratory analysis was also performed using a meta-analysis of the calculated reliability coefficients.
+The tau score (the indicator of true differences in reliability scores between labs) is displayed for each replication set's calculated Cronbach's alpha coefficients in Figure \@ref(fig:Plot23AlphaCode).
+The tau scores vary considerably between replication sets, some had a Tau estimate of approximately 0, while others were above .1.
+The latter result implies that for the measurements on that replication set, the standard deviation of the distribution of true reliability coefficients between the replications from various lab locations was more than .1 point of Cronbach's alpha [@cooper2019handbook].
+Based on the Q-test for heterogeneity, `r sum(data_h3_avg$QEp < .05)` out of the total of `r nrow(data_h3_avg)` estimates of heterogeneity were significant.
+
+However, since the Q-test is sensitive to the number of studies in the meta-analyses [@li2015DilemmaHeterogeneityTests], some of the discrepancy in the estimate of heterogeneity based on this test may in part be due to the fact that for some measures the sample size of labs that used them was too low.
+Therefore, while consistent evidence for heterogeneity would imply true variance in Cronbach's alpha within replication sets would run counter to hypothesis 2, the evidence id inconsistent when looking across all studies, and remains sensitive to the sample size in the meta-analyses.
+
+Figure \@ref(fig:Plot23AlphaCode) further shows whether the replication sets were successful when judged at a meta-analytic significance level of .05, or not.
+A logistic regression was performed to detect if the calculated reliabilities related to the replication success.
+
+The logistic model indicated that Cronbach's alpha did not significantly relate to replication success in the main logistic regression model (Cronbach's alpha: `r H3_main_full_results_alpha_with_OR`).
+Similar results were found based on the calculated omega coefficient (see Appendix C) and in all of the multilevel sensitivity analyses models (see Appendix D).
+These results are contradictory to the expectation in hypothesis 3.
+However, the reliability coefficient could be calculated for only a small sample number of measures.
+As a result, the estimates of the relation between reliability and replication success obtained using these models each come with large uncertainty and remains inconclusive.
 
@@
 Beta-regression was used to test the difference in QMP ratio between original articles and replication protocols.
-The results of this test indicated that this difference was significant (`r betareg_output_to_apa_full(H4_test_results_REV)`).
+The results of indicated that this difference was significant (`r betareg_output_to_apa_full(H4_test_results_REV)`).
 This result is in line with hypothesis 4.
 
-A similar beta-regression tested the association between replication success and QMP ratio in replication protocols.
-Results showed that successful replication significantly related to a decrease in the ratio of QMPs in replication protocols (`r H5_test_results_REV_with_OR`).
-However, this result did not hold for the QMP ratios obtained with the initial coding protocol (`r H5_test_results_with_OR`).
-
-???Footnote: analysis was changed from the pre-registered beta-regression to logistic regression for interpretation sake, significance did not change between the two.
-The original beta-regression results can be found in Appendix ???
+A logistic regression model was used to test the association between the QMP ratio in replication protocols and replication success.
+Results showed that a decrease in the ratio of QMPs in replication protocols significantly related to successful replication (`r H5_test_results_REV_with_OR`).
 
@@
 Figure \@ref(fig:Plot46RevisedDataCode) displays this relationship visually.
-However, similarly to the previous test, the relation was not significant for the QMP ratios obtained with the initial protocol (`r betareg_output_to_apa_full(H6_test_results)`).
-
-## Appendixable Results
-
-[APPENDIX sensitivity analyses & co: for omega the mean (values calculated in the population across replication sets) was `r apa_num(sd(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`.???...
-The same analysis for omega coefficients even showed a relatively larger degree of between group variance (between-group variance `r apa_num(within_group_variance_omega, digits = 3)`, within-group variance `r apa_num(between_group_variance_omega, digits = 3)`, ICC = `r apa_num(ICC_omega, digits = 3)`).]
-
-```{r Plot23OmegaCode}
-# data re-ordering (was not saved in export)
-plot_23_data_omega_reordered <- data_prep_plot_23_omega(plot_23_data_omega)
-
-# plot for omega
-ggplot(plot_23_data_omega_reordered, aes(x = alpha, y = g)) +
-  geom_boxplot(outlier.shape = NA) +
-  geom_hline(yintercept = 5.5, color = "red", size = 1) +
-  geom_point(alpha = 0.1) +
-  theme_minimal() +
-  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), 
-                                                     "lines")) +
-  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0),
-    ymin = 6, ymax = 6, xmin = 1.08, xmax = 1.08) +
-  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0),
-    ymin = 5, ymax = 5, xmin = 1.08, xmax = 1.08) +
-  coord_cartesian(xlim = c(0, 1), clip = "off") +
-  ylab("") +
-  xlab("Omega")
-```
-
-[[[APPENDIX sensitivity analyses: H5, Sensitivity analyses using a random-intercept multilevel regression also found a similar significant association (`r check_h5_REV$full_result$hypothesis_supportTRUE`).
-Both of these results are in line with hypothesis 5.
-However, the relationship in the multilevel model was no longer significant for QMP ratios obtained with the initial coding protocol (`r check_h5$full_result$hypothesis_supportTRUE`).
-For the sensitivity analyses using a random intercept logistic multilevel mode both revised and initial protocol resulted in non-significant results (revised protocol: `r check_h6_REV$full_result$QMP_REV`; initial protocol `r check_h6$full_result$QMP`).]]]
-
-```{r Plot46FullInitialDataCode, include = FALSE, eval = FALSE, error = FALSE}
-# Initial
-ggplot(plot_46_data, aes(QMP_ratio, QMP_Rep_ratio)) + 
-  geom_point() +
-  geom_jitter(width = 0.05, height = 0.05) +
-  stat_smooth(method="lm") + 
-  theme_bw() +
-  theme(strip.text.y = element_text(size = 7), strip.background = element_rect(
-    color = "black", fill = "white", size = 1, linetype = "solid"
-  )) +
-  xlab("QMP Ratio (Original)") + ylab("QMP Ratio (Replication)") +
-  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1")) + 
-  facet_grid(vars(QMP_Rep_type), vars(QMP_type))
-
-```
-
-```{r ReplicabilityReliabilityTestTable, warning=FALSE}
-# creating the dtaframe for the table
-H3_table_dataframe <- rbind(H3_test_result_main_alpha$table, H3_test_result_int_sensitivity_alpha$table, H3_test_result_main_omega$table, H3_test_result_int_sensitivity_omega$table, H3_test_result_slp_sensitivity_omega$table)
-
-# adding an asterix for significance to the significant p in the dataframe
-H3_table_dataframe[3,5] <- paste0(H3_table_dataframe[3,5], "$^*$")
-
-# adding rows to give indication of specific sections (apa_table being awkward)
-H3_table_for_printing <- rbind(c("Alpha", "", "", "", ""), c("Logistic Regression Model", "", "", "", ""), H3_table_dataframe[1:2,], c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(3:4),], c("Omega", "", "", "", ""), c("Logistic Regression Model", "", "", "", ""), H3_table_dataframe[(5:6),], c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(7:8),], c("Random-Slope Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(9:10),])
-
-# print the table in apa formatting
-apa_table(
-  H3_table_for_printing, align = c("l", "r", "r", "r", "r")
-  , caption = "Model Results from Tests of Hypothesis 3"
-  , note = "The Alpha and Omega sections show the models where the independent variable was the calculated Cronbach's alpha and omega coefficient respectively.
-The random slope model for Cronbach's alpha did not converge, thus it results are not shown here.
-$^* p < .05$"
-  , escape = FALSE, placement= "htp", midrules = c(1, 2, 5, 7, 8, 9, 12, 15))
-
-```
-
-[[[TO APPENDIX initial analyses: Table \@ref(tab:H6ExploratoryAssociationsInitialTable) shows the results for the QMP ratios obtained via the initial protocol. INCLUDING TABLES]]]
-
-```{r H6ExploratoryAssociationsInitialTable, warning = FALSE}
-# creating the dataframe for the table
-H6_table_dataframe_l <- rbind(Results_H6_between$def_def, Results_H6_between$def_op,
-  Results_H6_between$def_sel, Results_H6_between$def_quant, Results_H6_between$def_mod, 
-  Results_H6_between$op_def, Results_H6_between$op_op, Results_H6_between$op_sel, 
-  Results_H6_between$op_quant, Results_H6_between$op_mod, Results_H6_between$sel_def, 
-  Results_H6_between$sel_op, Results_H6_between$sel_sel, Results_H6_between$sel_quant, 
-  Results_H6_between$sel_mod)
-
-H6_table_dataframe_r <- rbind(Results_H6_between$quant_def, Results_H6_between$quant_op,
-  Results_H6_between$quant_sel, Results_H6_between$quant_quant, Results_H6_between$quant_mod, 
-  Results_H6_between$mod_def, Results_H6_between$mod_op, Results_H6_between$mod_sel, 
-  Results_H6_between$mod_quant, Results_H6_between$mod_mod, Results_H6_between$tot_def, 
-  Results_H6_between$tot_op, Results_H6_between$tot_sel, Results_H6_between$tot_quant, 
-  Results_H6_between$tot_mod)
-
-H6_table_dataframe <- cbind(H6_table_dataframe_l, H6_table_dataframe_r)
-
-# adding asterices for significance to the significant p in the dataframe
-H6_table_dataframe[8,3] <- paste0(H6_table_dataframe[8,3], "$^*$")
-H6_table_dataframe[11,3] <- paste0(H6_table_dataframe[11,3], "$^*$")
-H6_table_dataframe[14,3] <- paste0(H6_table_dataframe[14,3], "$^*$")
-H6_table_dataframe[8,6] <- paste0(H6_table_dataframe[8,6], "$^*$")
-H6_table_dataframe[9,6] <- paste0(H6_table_dataframe[9,6], "$^*$")
-H6_table_dataframe[11,6] <- paste0(H6_table_dataframe[11,6], "$^*$")
-H6_table_dataframe[13,6] <- paste0(H6_table_dataframe[13,6], "$^*$")
-
-# adding a column to help indicate the original QMP type
-H6_table_dataframe_expanded <- cbind(c("Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification"), H6_table_dataframe)
-
-# adding rows to give indication of specific sections (apa_table being awkward)
-H6_table_for_printing <- rbind(c("QMP Type", "", "Definition", "", "", "Quantification", ""), H6_table_dataframe_expanded[1:5,], c("QMP Type", "", "Operationalisation", "", "", "Modification", ""),  H6_table_dataframe_expanded[(6:10),], c("QMP Type", "", "Selection", "", "", "Total", ""), H6_table_dataframe_expanded[(11:15),])
-
-colnames(H6_table_for_printing) <-  c("Original", "$b$", "SD", "$p$", "$b$", "SD", "$p$")
-
-# print the table in apa formatting
-apa_table(
-  H6_table_for_printing, align = c("l", "r", "c", "r", "r", "c", "r")
-  , caption = "Beta Regression Test Results for the Association between Replication
-QMP Ratio and Original QMP Ratio as obtained using the Initial Protocol"
-  , note = "Rows indicate Original QMP type, and within table indicates Replication QMP type.
-Sample size for comparisons involving modification were lower since not all measures were modified.
-Therefore the standard errors are larger.
-$^* p < .05$"
-  , escape = FALSE, placement= "htp", midrules = c(1, 6, 7, 12, 13))
-
-```
 
@@
 These measurement related concepts were then linked to replicability in order to investigate them as potential causes inhibiting successful replications.
-The results of the tests for the hypotheses were often underpowered, especially the tests of hypotheses 2 & 3 for which only eighteen measures were available to calculate reliability from.
+The results of the tests for the hypotheses were often underpowered, especially the tests of hypotheses 2 & 3 for which only `r nrow(data_h3_avg)` measures were available to calculate reliability from.
 Additionally, most tests showed mixed results.
-However, when including exploratory and descriptive analyses, a clearer picture of the state of measurement in replication and original research emerges.
+However, when including exploratory and descriptive analyses, a clearer picture on measurement in replication and original research emerges.
 
@@
 
-This study assessed the quality of measurement and measurement reporting in original and replication research by investigating the quality of measurement in the Many Labs projects.
+???
+Results based on calculated reliability are somewhat unstable, but we can definitely say that a large number of single item measures are used, not many multiple item measures are accompanied by a reported alpha coefficient, and when looking at the heterogeneity and selective reporting of alpha we see this...???
+
+This study assessed the quality of measurement and measurement reporting in original and replication research by investigating the quality of measurement in the Many Labs projects, and the original articles they attempted to replicate.
 Findings were in line with similar investigations in the literature by @shaw2020measurement & @flake2022construct.
-These two studies found that sufficient validity evidence and reliability reporting for measures was lacking in replications and original studies.
-The fact that not enough reliability coefficients were reported to even conduct the planned analysis for hypothesis 1, and [[[VALIDITY EVIDENCE REPORTING DECRIPTIVE NEEDED (all but X of the 77 measures (replication/original) reported any validity evidence)]]] shows that reliability and validity evidence was similarly underreported in our sample, a problem that has also been addressed in earlier literature on this topic [@vacha1999practices; @green2011recent].
+These two studies found that validity evidence and reliability coefficient reporting for measures was lacking in replications and original studies.
+lllnot enough reliability coefficients were reported to conduct the planned analysis for hypothesis 1, and of the 77 measures only X measures in original articles and X in replication protocol reported any validity evidence.
+These findings show that reliability and validity evidence was similarly underreported in our sample, a problem that has also been addressed in earlier literature on this topic [@vacha1999practices; @green2011recent].
 
@@
 The use of these single item measures comes with risks, since by virtue of being singular they assume that whatever they are measuring is unidimensional, while not being able to test this assumption [@shaw2020measurement], ???and reliability risks???.
-This is particularly concerning given that the analyses of the calculated reliabilities of the multiple item measures showed that some measures ???EXPLORATORY ANALYSIS IDEA: relation of the calculated reliabilities and N items of the measure???, and exploratory analyses of the multiple item measure replication datas, for which unidimensionality could be tested, showed only little support for unidimensionality (see Appendix ???, as was also observed by @shaw2020measurement).
+This is particularly concerning given that the analyses of the calculated reliabilities of the multiple item measures showed that some measures ???EXPLORATORY ANALYSIS IDEA: relation of the calculated reliabilities and N items of the measure???, and exploratory analyses of the multiple item measure replication datas, for which unidimensionality could be tested, showed only little support for unidimensionality (see Appendix A as was also observed by @shaw2020measurement).
 
@@
 While no evidence for hypothesis 3 was found, caution in interpreting the test results is needed.
-The number of measures for which reliability was calculated was quite low (eighteen for Cronbach's alpha, fifteen for omega) , it could be that the test was simply underpowered to detect the effect.
+The number of measures for which reliability was calculated was quite low (`r apa_num(sum(!is.na(data_h3_avg$alpha)), numerals = FALSE)`), it could be that the test was simply underpowered to detect the effect.
 On the other hand, it might be that the detrimental influence of measurement error on interpretations of replication results is small in large scale replication projects.
@@
 However, it is worth noting that hese relations were only found for QMPs coded with the revised coding protocol.
-Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol.
+Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see Appendix D).
 The initial protocol was revised because the ratings based on that protocol were considered to stringent, and as a result, several items were reformulated so that criteria for what constituted sufficiently clear reporting were lowered.

### 2024-03-13 Scripts/source_script.R

@@ -1022,10 +1022,6 @@ data_prep_plot_23_alpha <- function(Data){
 }
 
 
-#c(caruso, husnu, nosek, nosek, anderson, anderson, anderson, giessner, 
-# norenzayan, zhong, monin, monin, cacciopo, cacciopo, defruyt, albaraccin, 
-#  albaraccin, shnabel, vos)
-
 
 # and for omega
 data_prep_plot_23_omega <- function(Data){
@@ -1087,17 +1083,33 @@ data_prep_plot_23_alpha_reported <- function(Data_reporting, Data_calculated,
 }
 
 
-
 ### 456 plots data prep
 data_prep_plot_456 <- function(Data){
+  Plot_456_ratio_data <- gather(Data[c("def_ratio", "op_ratio", 
+                                           "sel_ratio", "quant_ratio", "mod_ratio", "QMP_ratio")], 
+                                    QMP_type, QMP_ratio, c("def_ratio", "op_ratio", "sel_ratio", 
+                                                           "quant_ratio", "mod_ratio", "QMP_ratio"), factor_key = TRUE)
+  
+  Plot_456_ratio_rep_data <- gather(Data[c("Rep_def_ratio", 
+                                               "Rep_op_ratio", "Rep_sel_ratio", "Rep_quant_ratio", 
+                                               "Rep_mod_ratio", "Rep_QMP_ratio")], QMP_type, QMP_ratio, 
+                                        c("Rep_def_ratio", "Rep_op_ratio", "Rep_sel_ratio", 
+                                          "Rep_quant_ratio", "Rep_mod_ratio", "Rep_QMP_ratio"), 
+                                        factor_key = TRUE)
+  
+  Plot_456_ratio_data$QMP_ratio_1 <- Plot_456_ratio_data$QMP_ratio
+  Plot_456_ratio_rep_data$QMP_ratio_1 <- Plot_456_ratio_rep_data$QMP_ratio + 1
+  
+  
+  
   Plot_456_ratio_data_REV <- gather(Data[c("def_ratio", "op_REV_ratio", 
                                            "sel_REV_ratio", "quant_REV_ratio", "mod_REV_ratio", "QMP_REV_ratio")], 
-                                    QMP_type, QMP_ratio, c("def_ratio", "op_REV_ratio", "sel_REV_ratio", 
[…]

### 2024-03-18 Data/Data_package_description.Rmd
cleaned up manuscript, expanded readme file, and revised the data package desciptive information.

--- 2024-02-16 Data/DataPackageProtocol.Rmd
@@
 
-*Explanation*: This dataset list contains the calculated Cronbach's alpha and the omega reliability coefficient calculated for the responses to the questionnaire items from several of the Many Labs studies, namely those responses encoded in: Data_1.10_clean.csv, data_1.11_clean.csv, data_1.12.3.1_clean.csv, data_1.12.3.2_clean.csv, data_2.10.1_clean.csv, data_2.12.1_clean.csv, data_2.12.2_clean.csv, data_2.12.3_clean.csv, data_2.15_clean.csv, data_2.20_clean.csv, data_2.23_clean.csv, data_3.2.1.1_clean.csv, data_3.2.1.2_clean.csv, data_3.7.2_clean.csv, data_3.8.2_clean.csv, data_5.1.1_clean.csv, data_5.7_clean.csv, data_5.9.1_clean.csv.
-The Cronbach's alpha and omega are calculated separately for each lab location within each study/questionnaire in the Many Labs datasets.
+*Explanation*: This dataset list contains information on the calculated Cronbach's alpha and the omega reliability coefficient calculated for the responses to the questionnaire items from several of the Many Labs studies, namely those responses encoded in: Data_1.10_clean.csv, data_1.11_clean.csv, data_1.12.3.1_clean.csv, data_1.12.3.2_clean.csv, data_2.10.1_clean.csv, data_2.12.1_clean.csv, data_2.12.2_clean.csv, data_2.12.3_clean.csv, data_2.15_clean.csv, data_2.20_clean.csv, data_2.23_clean.csv, data_3.2.1.1_clean.csv, data_3.2.1.2_clean.csv, data_3.7.2_clean.csv, data_3.8.2_clean.csv, data_5.1.1_clean.csv, data_5.7_clean.csv, data_5.9.1_clean.csv.
+
+*Variables*:
+
+-   **alpha:** Cronbach's alpha calculated for a measure at a particular lab location within a single study/questionnaire as extracted from the Many Labs datasets.
+
+-   **omega:** McDonald's omega calculated for a measure at a particular lab location within a single study/questionnaire as extracted from the Many Labs datasets.
+
+-   **ASE:** Standard error of Cronbach's alpha at a particular lab location, based on formulas 2 & 3 from @duhachek2004AlphaStandardError.
+
+-   **tau:** the tau estimate fo heterogeneity as obtained from a meta-analysis of the Cronbach's alpha of the same measure across multiple lab locations.
+
+-   **Qep:** the p-value of the Q test for heterogeneity as obtained from a meta-analysis of the Cronbach's alpha of the same measure across multiple lab locations.
+
+-   **pi.lb & pi.ub:** the lower and upper bound of the meta-analytic prediction interval for the meta-analysis of the Cronbach's alpha of the same measure across multiple lab locations.
+
+-   **g:** index showing that the alpha values belonged to a particular single measure.
+
+-   **reporting_index:** same as above, only now the numbers correspond to the row in the coded_data_replication.csv dataset that the indexed measure belongs to.
 
@@
 
-*Explanation*: For each many labs replication, the mean Cronbach's alpha and omega reliability coefficients of each lab location are captured in the datasets.
+*Explanation*: For each measure, the mean of the variables from data_H2.csv, excluding the g indexing variable.
 Additionally, a boolean indicator that indicated whether or not the original effect was replicated in the many labs replications when looking at the significance of the meta-analytic p-value was also included.
@@
 Additionally, it contains a column of alpha scores averaged across many lab locations for each article.
-For each remaining replication, the names of the articles were adjusted to look better in the figure this dataset was used for.
+For each remaining replication, the g indexing variable was changed to reflect the names of the articles were adjusted to look better in the figure this dataset was used for.
 
@@
 
--   **coefficient:** the value for the reported alpha coefficient for the specific measure as extracted from the original article the measure was reported in.
+-   **coefficient_reported:** the value for the reported alpha coefficient for the specific measure as extracted from the original article the measure was reported in.
+
+-   **coefficient_calculated:** the mean value of the calculated alpha coefficients for the specific measure in the row.
+
+-   **coefficient_difference:** The difference between coefficient_reported and coefficient_calculated.
+
+-   **significance:** boolean value indicating whether or not the coeffcient_reported value of a measure is outside the 95% percentile of calculated alpha coefficient score of the same measure.
 
@@
 Additionally, it contains a column of omega scores averaged across many lab locations for each article.
-The names of the articles were adjusted to look better in the figure this dataset was used for.
+The g indexing variable was changed to reflect the names of the articles were adjusted to look better in the figure this dataset was used for.
 
@@
 
-*Explanation*: Contains three variables for each QMP type for all the replication studies and original articles.
-The QMP_ratio column indicates the QMP ratio for that QMP type for that study/article.
-The RepOrg column indicates whether the QMP ratio belongs to a replication or an original article.
-The QMP_type column indicates the QMP type the QMP ratio belongs to.
+*Explanation*: Contains four variables for each QMP type for all the replication studies and original articles that were coded on QMPs.
 The rows are ordered to have the original studies first and then the replications, then they are ordered based on QMP type from Definition to Operationalization to Selection to Quantification to Modification to Total.
-Finally, within each type the QMPs are ordering matches the order of the studies/articles as in the coded_data_replications.csv and coded_data_original_shortened.csv.
+Within each type the QMPs are ordering matches the order of the studies/articles as in the coded_data_replications.csv and coded_data_original_shortened.csv.
+
+*Variables:*
+
+-   **QMP_type:** factor that indicates the QMP type the QMP ratio belongs to (Definition, Operationalization, Selection, Quantification, or Modification).
+
+-   **QMP_ratio:** float number between 0 and 1 that indicates the QMP ratio for that QMP type for that study/article.
+
+-   **RepOrg:** factor that indicates whether the QMP ratio belongs to a replication or an original article.
+
+-   **QMP_ratio_1:** transformed version of the QMP_ratio column, where QMPs for all original articles have a 1 added to their ratio.
+This was done for the sake of making the figure possible in ggplot as it is right now.
 
@@
 
-*Explanation*: Contains four variables for each QMP type for both replication studies and original articles combined per row.
+*Explanation*: Contains four variables for each QMP type (including total) for both replication studies and original articles combined per row.
 The QMP_ratio column indicates the initial QMP ratio for the specific QMP type for that original article.
@@
 
-*Explanation*: Contains four variables for each QMP type for both replication studies and original articles combined per row.
+*Explanation*: Contains four variables for each QMP type (including total) for both replication studies and original articles combined per row.
 The QMP_ratio column indicates the revised QMP ratio for the specific QMP type for that original article.

### 2024-03-18 Scripts/AppendixScripts/Appendix_initial_QMP_analyses.rmd
cleaned up manuscript, expanded readme file, and revised the data package desciptive information.

# Appendix D

```{r setup, include=FALSE}
# loading R libraries, perhaps unnecessary
library(papaja)

# loading source script, perhaps unnecessary
source(file = "C:/Users/u686785/OneDrive - Tilburg University/Documents/uvt/PHD/Master Thesis to Paper/Reproducible_R_Project/Scripts/source_script.R")

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(17042023)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

This appendix contains all of the QMP analyses that in the article and appendices were based on the revised QMP, but then performed based on the QMPs obtained using the initial coding protocol.

### Explanation Why
The data was initially coded using to the preregistered coding protocol. After the coding was completed using the preregistered coding protocol, it was determined that some of the initial ratings were possibly to stringent. As a result, some of the items in the protocol were reformulated, so that the conclusions from the resulting analyses were based on a more lenient judgement of QMPs. The coded data using the initial protocol was still separately available, and because this protocol was the one that was pre-registered the results for those analyses are shown here.

### Models
To test hypothesis 4, the total QMP ratios between replication and original research was compared using a beta-regression where total QMP ratio was predicted by whether the QMP ratio came from an original article, or a replication protocol.

```{r Hypothesis4ModelInitial, include = FALSE}
## Hypothesis 4 beta regression model
# running the model with none revised QMP ratio's
H4_test_results <- betareg(QMP_ratio ~ rep_org, data = data_h4)

```

For hypothesis 5, a logistic regression model was used to test the association between the QMP ratio in replication protocols and replication success. In this appendix we run the model based on the QMP ratios obtained using the initial protocol.

```{r Hypothesis5ModelInitial, include = FALSE}
## Hypothesis 5 logistic regression model
H5_test_results <- apa_print(glm(hypothesis_support ~ QMP_ratio, data = data_h5, family = binomial))

H5_test_results_with_OR <- OR_to_apa_full_supplier(H5_test_results$full_result$QMP_ratio, negative_b = TRUE)

```

The relation between QMP ratios in the replication protocols and corresponding original articles were investigated using a beta regression model.

```{r Hypothesis6ModelInitial, include = FALSE}
## Hypothesis 6 beta regression model
H6_test_results <- betareg(Rep_QMP_ratio ~ QMP_ratio, data = data_h6)

```

Appendix B already contained the results of the multilevel sensitivity models for hypothesis 5 & 6 based on the QMP ratios obtained using the revised coding protocol. In this appendix we show the result for the same models based on the QMP ratios obtained using the initial protocol.

```{r Hypotheses5And6SensitivityAnalysesInitial}
## Hypothesis 5 sensitivity test using a random intercept Guassian model.
# create dummy H5 dataframe for use in sensitivity test
data_h5_sens <- data_h5

# convert outcome variable to be usable with Gaussian distribution via
# logit transform.
data_h5_sens$QMP <- log(data_h5_sens$QMP_ratio /(1 - data_h5_sens$QMP_ratio)) # TO INITIAL APPENDIX

check_h5 <- apa_print(lmer(formula = QMP ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens))

## Hypothesis 6 sensitivity test using a random intercept Guassian model.
# create dummy H6 dataframe for use in sensitivity test
data_h6_sens <- data_h6

# convert outcome variable to be usable with Gaussian distribution via
# logit transform. FIRST ELEMENTS TO INITIAL APPENDIX
data_h6_sens$QMP <- log(data_h6_sens$QMP_ratio /(1 - data_h6_sens$QMP_ratio))
data_h6_sens$Rep_QMP <- log(data_h6_sens$Rep_QMP_ratio /(1 - data_h6_sens$Rep_QMP_ratio))

# running the models one with none revised QMP ratio's and one with
check_h6 <- apa_print(lmer(formula = Rep_QMP ~ 1 + QMP + (1|many_labs_version), data = data_h6_sens))

# n of mod ratio's that are present (check)
H6_n_check_results <- betareg(Rep_op_ratio ~ mod_ratio, data = data_h6)$n

```

### Results + Comparison Interpretation
The figure below displays the distribution of observed QMP ratio's across original articles and replication protocols based on the initial coding protocol.

```{r Plot456CodeInitial, warning = FALSE, fig.cap = "QMP ratio counts for each QMP Type and QMP total ratio distribution grouped by whether the QMP ratio was obtained from an original article or a replication protocol. The top row shows for each QMP type the proportions of each QMP ratio obtained, darker colours represent proportionally more QMPS, grey means modification did not occur for that measure. The bottom graph shows the distributions of total QMP ratios for both replication protocols and original articles, with the line indicating the mean QMP ratio. The specific observed values are indicated along the bottom row with dots"}
# re-ordering the QMP-types, because it didn't save
plot_456_data$QMP_type <- factor(plot_456_data$QMP_type, levels = c("Definition", "Selection", "Operationalization", "Quantification", "Modification", "Total"))

### ratio Original and Rep
Plot_456_1 <- ggplot(plot_456_data[plot_456_data$QMP_type != "Total",], 
                      aes(x = RepOrg, fill = as.factor(QMP_ratio_1))) + 
  geom_bar(position = "fill") +
  theme_minimal() +
  scale_fill_manual(values = c("#ff766c", "#cb5e56", "#be5850", "#aa4f48", "#994741", "#803b36", "#672f2b", "#5b2a26", "#562824", "#411e1b", "#341816", "#120606", "#030101","#4366ff", "#4265fc", "#3652ce", "#324cbe", "#324cbe", "#2c44aa", "#2c44aa", "#293e9b", "#293e9b", "#213380", "#1c2a69", "#1c2a69", "#172256", "#172256", "#111a41", "#111a41", "#010103", "#010103")) +
  theme(legend.position = "none") +
  facet_grid(~ QMP_type) + 
  ylab("Relative Prevalence of\nQMP Ratio in Sample") +
  xlab("QMP Type") +
  ggtitle("QMP Ratio's Per QMP Type Grouped by Original and Replication")

Mean_Rat_Rep <- mean(plot_456_data$QMP_ratio[
  plot_456_data$QMP_type == "Total" & plot_456_data$RepOrg == "Replication"])
Mean_Rat_Org <- mean(plot_456_data$QMP_ratio[
  plot_456_data$QMP_type == "Total" & plot_456_data$RepOrg == "Original"])

Plot_456_2 <- ggplot(plot_456_data[plot_456_data$QMP_type == "Total",], 
       aes(x = QMP_ratio, fill = RepOrg, colour = RepOrg)) +
  geom_density(alpha = 0.2) +
  geom_point(y = 0, alpha = 0.2, size = 3) +
  geom_segment(aes(x = Mean_Rat_Rep, xend = Mean_Rat_Rep, y = 0, yend = 2.66)
               , color = "blue4") +
  geom_segment(aes(x = Mean_Rat_Org, xend = Mean_Rat_Org, y = 0, yend = 2.183)
               , color = "brown") +
  coord_cartesian(xlim = c(0, 1)) +
  theme_ridges() + 
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
  scale_fill_manual(values=c("brown", "blue4")) +
  scale_color_manual(values=c("brown2", "blue")) +
  scale_x_continuous(breaks = c(0, 0.25, Mean_Rat_Rep, Mean_Rat_Org, 
                                0.5, 0.75, 1), 
                     labels = c("0", "0.25", "0.28", "0.44", "0.5", 
                                "0.75", "1")) + 
  ggtitle("Distribution of Total QMP Ratio's by Original and Replication") +
  guides(color = "none") +
  labs(fill = "Coded from") +
  ylab("") +
  xlab("")

# combine both plots into one figure
grid.arrange(Plot_456_1, 
             Plot_456_2, 
             nrow = 2)

```

The bottom panel of Figure \@ref(fig:Plot456CodeInitial) already shows that original articles contained a significantly larger proportion of QMPs than replication protocols for the measures of the same effects. Beta-regression was used to test the difference in QMP ratio based on the initial protocol coding, between original articles and replication protocols. The results of this test indicated that this difference was significant (`r betareg_output_to_apa_full(H4_test_results)`). This result is similar to the result found using the revised coding protocol in line with hypothesis 4.

Contrary to the results based on the revised coding protocol, a decrease in QMP ratio based on the initial coding protocol did not significantly relate to replication success (`r H5_test_results_with_OR`). Thus not supporting hypothesis 5.

Similarly to the previous test, the relation was not significant for the QMP ratios obtained with the initial protocol (`r betareg_output_to_apa_full(H6_test_results)`). Thus not supporting hypothesis 6. Figure \@ref(fig:Plot46InitialDataCode) displays this relationship visually.

```{r Plot46InitialDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication total QMP ratio’s with linear regression line. Each dot in the figure describes the QMP ratio in that graph across both the original article and its replication protocol. Note: jitter was applied to these dots in order to show the number of observations at points where multiple dots were present"}
ggplot(plot_46_data[plot_46_data$QMP_type == "QMP.Ratio" & plot_46_data$QMP_Rep_type == "Rep.QMP.Ratio",], aes(QMP_ratio, QMP_Rep_ratio)) + 
  geom_point() +
  geom_jitter(width = 0.01, height = 0.01) +
  stat_smooth(method="lm") + 
  theme_minimal() +
  theme(strip.text.y = element_text(size = 7), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
  ylab("QMP Ratio (Replication Protocol)") +
  xlab("QMP Ratio (Original Article)") 
```

Table \@ref(tab:H6ExploratoryAssociationsInitialTable) shows the relations between original and replication QMP ratios for each QMP type based on the initial protocol. Figure \@ref(fig:Plot46FullInitialDataCode) shows the same relations displayed visually.

```{r H6ExploratoryAssociationsInitialTable, warning = FALSE}
# creating the dataframe for the table
H6_table_dataframe_l <- rbind(Results_H6_between$def_def, Results_H6_between$def_op,
  Results_H6_between$def_sel, Results_H6_between$def_quant, Results_H6_between$def_mod, 
  Results_H6_between$op_def, Results_H6_between$op_op, Results_H6_between$op_sel, 
  Results_H6_between$op_quant, Results_H6_between$op_mod, Results_H6_between$sel_def, 
  Results_H6_between$sel_op, Results_H6_between$sel_sel, Results_H6_between$sel_quant, 
  Results_H6_between$sel_mod)

H6_table_dataframe_r <- rbind(Results_H6_between$quant_def, Results_H6_between$quant_op,
  Results_H6_between$quant_sel, Results_H6_between$quant_quant, Results_H6_between$quant_mod, 
  Results_H6_between$mod_def, Results_H6_between$mod_op, Results_H6_between$mod_sel, 
  Results_H6_between$mod_quant, Results_H6_between$mod_mod, Results_H6_between$tot_def, 
  Results_H6_between$tot_op, Results_H6_between$tot_sel, Results_H6_between$tot_quant, 
  Results_H6_between$tot_mod)

H6_table_dataframe <- cbind(H6_table_dataframe_l, H6_table_dataframe_r)

# adding asterices for significance to the significant p in the dataframe
H6_table_dataframe[8,3] <- paste0(H6_table_dataframe[8,3], "$^*$")
H6_table_dataframe[11,3] <- paste0(H6_table_dataframe[11,3], "$^*$")
H6_table_dataframe[14,3] <- paste0(H6_table_dataframe[14,3], "$^*$")
H6_table_dataframe[8,6] <- paste0(H6_table_dataframe[8,6], "$^*$")
H6_table_dataframe[9,6] <- paste0(H6_table_dataframe[9,6], "$^*$")
H6_table_dataframe[11,6] <- paste0(H6_table_dataframe[11,6], "$^*$")
H6_table_dataframe[13,6] <- paste0(H6_table_dataframe[13,6], "$^*$")

# adding a column to help indicate the original QMP type
H6_table_dataframe_expanded <- cbind(c("Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification"), H6_table_dataframe)

# adding rows to give indication of specific sections (apa_table being awkward)
H6_table_for_printing <- rbind(c("QMP Type", "", "Definition", "", "", "Quantification", ""), H6_table_dataframe_expanded[1:5,], c("QMP Type", "", "Operationalisation", "", "", "Modification", ""),  H6_table_dataframe_expanded[(6:10),], c("QMP Type", "", "Selection", "", "", "Total", ""), H6_table_dataframe_expanded[(11:15),])

colnames(H6_table_for_printing) <-  c("Original", "$b$", "SD", "$p$", "$b$", "SD", "$p$")

# print the table in apa formatting
apa_table(
  H6_table_for_printing, align = c("l", "r", "c", "r", "r", "c", "r")
  , caption = "Beta Regression Test Results for the Association between Replication
QMP Ratio and Original QMP Ratio as obtained using the Initial Protocol"
  , note = "Rows indicate Original QMP type, and within table indicates Replication QMP type. Sample size for comparisons involving modification were lower since not all measures were modified. Therefore the standard errors are larger. $^* p < .05$"
  , escape = FALSE, placement= "htp", midrules = c(1, 6, 7, 12, 13))

```

```{r Plot46FullInitialDataCode}
# Initial
ggplot(plot_46_data, aes(QMP_ratio, QMP_Rep_ratio)) + 
  geom_point() +
  geom_jitter(width = 0.05, height = 0.05) +
  stat_smooth(method="lm") + 
  theme_bw() +
  theme(strip.text.y = element_text(size = 7), strip.background = element_rect(
    color = "black", fill = "white", size = 1, linetype = "solid"
  )) +
  xlab("QMP Ratio (Original)") + ylab("QMP Ratio (Replication)") +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1")) + 
  facet_grid(vars(QMP_Rep_type), vars(QMP_type))

```

Now looking at the multilevel sensitivity analyses (see appendix B), only now using the QMP ratios based on the initial coding protocol.

Contrary to the results of the multilevel sensitivity model testing hypothesis 5 using QMP ratios obtained with the revised coding protocol, the relationship in the multilevel model was no longer significant for QMP ratios obtained with the initial coding protocol (`r check_h5$full_result$hypothesis_supportTRUE`).

Similarly to the results of the multilevel sensitivity model testing hypothesis 5 using QMP ratios obtained with the revised coding protocol, he relationship in the multilevel model was not significant for QMP ratios obtained with the initial coding protocol (`r check_h6$full_result$QMP`).

### 2024-03-18 Scripts/AppendixScripts/Appendix_omega_analyses.rmd
cleaned up manuscript, expanded readme file, and revised the data package desciptive information.

# Appendix C

```{r setup, include=FALSE}
# loading R libraries, perhaps unnecessary
library(papaja)

# loading source script, perhaps unnecessary
source(file = "C:/Users/u686785/OneDrive - Tilburg University/Documents/uvt/PHD/Master Thesis to Paper/Reproducible_R_Project/Scripts/source_script.R")

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(17042023)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

This appendix contains all results based on calculated reliabilities only using the omega coefficient as the coefficient of choice instead of the alpha coefficient.

### explanation why
Omega was included since it has been argued to be a more informative measure of score reliability than alpha, while also providing validity evidence for the scale [@crutzen2017scale; @deng2017testing]. Omega was calculated using the omega function in the psych R package [@R-psych]. Default arguments were used in the function except the nfactors argument, which was set to 1.

### Models
In order to separate between and within variance in reliability, a multilevel random intercept model was specified with replication set as the grouping variable, which was the same model used for testing. The difference was that the omega value of a replication was used as dependent variable in this instance, using the lmer function from the lme4 package [@R-lme4].

```{r Hypothesis2ModelOmega, include = FALSE}
# intercept only model to check the within and between group variance.
H2_test_result_omega <- lmer(formula = omega ~ 1 + (1|g), data = data_h2[complete.cases(data_h2),])

```

The ICC was calculated similarly based on the omega as was done for Cronbach's alpha in the article.

```{r ICCCalculations, include = FALSE}
# Variances
within_group_variance_omega <- attr(VarCorr(H2_test_result_omega), "sc")^2
between_group_variance_omega <- attr(VarCorr(H2_test_result_omega)$g, "stddev")^2

# ICC
ICC_omega <- between_group_variance_omega / (within_group_variance_omega + between_group_variance_omega)

```

The analysis for H3 related the calculated average reliability coefficients for each replication set to whether or not the replication was successful when judged at meta-significance level of $alpha <.05$.

```{r Hypothesis3MainTestOmega, include = FALSE}
## The main model to test hypothesis 3, through a logistic regression model.
H3_test_result_main_omega <- apa_print(glm(formula = replication ~ 1 + 
                                     omega, family = binomial(), 
                                     data = data_h3_avg))

# coefficient is positive, but not significant

# adding OR to the result
H3_main_full_results_omega_with_OR <- OR_to_apa_full_supplier(H3_test_result_main_omega$full_result$omega, negative_b = FALSE)

# well this OR is still quite a ridiculous number now..., but then again a step from 0 omega to 1, is quite a jump too...
```

A multilevel random-intercept, and a random-slope equivalent model to the model above were also run for Omega, similarly to what was done for Cronbach's alpha in Appendix B.

```{r Hypothesis3MultilevelModelSensitivityAnalysesOmega}
## sensitivity analyses.
# running a random intercept multilevel logistic model
H3_test_result_int_sensitivity_omega <- apa_print(glmer(formula = replication ~ 1 
                                                + omega + (1|g), family = 
                                                  binomial(), data = 
                                                  data_h3_multiple))

# same as for non-multilevel model and alpha

# running a random slope multilevel logistic model
H3_test_result_slp_sensitivity_omega <- apa_print(glmer(formula = replication ~ 1 
                                                + omega + (1 + omega|g), 
                                                family = binomial(), data =
                                                data_h3_multiple))

# omega shows no significant effect just like main.
```

### Results + Comparison Interpretation
For omega the mean (values calculated in the population across replication sets) was `r apa_num(mean(data_h3_multiple$omega), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`.

When looking at the between and within group variance in omega coefficients, compared to alpha an even larger relative degree of the variance was between group rather than within group when compared (between-group variance `r apa_num(within_group_variance_omega, digits = 3)`, within-group variance `r apa_num(between_group_variance_omega, digits = 3)`, ICC = `r apa_num(ICC_omega, digits = 3)`). This result thus provides evidence in a similar direction to the Cronbach's Alpha results, meaning that most variance in reliability coefficients is observed between studies rather than within studies.

The calculated Omega coefficient did not significantly relate to replication success in the main logistic regression model. Similarly, non-significance was also observed in the multilevel random-intercept and random-slope models (random intercept: `r H3_test_result_int_sensitivity_omega$full_result$omega`; random slope: `r H3_test_result_slp_sensitivity_omega$full_result$omega`).

Thus no evidence for hypothesis 3 was found. However, caution in interpreting the test results is needed. The number of measures for which the omega coefficient could be and was calculated was quite low (`r apa_num(sum(!is.na(data_h3_avg$omega)), numerals = FALSE)`).

The figure below shows additional information on the distributions of the calculated omega scores and their relation to replication success. It mostly resembles Figure \@ref(fig:Plot23AlphaCode) from the article, with some studies being omitted as the omega coefficient function did not converge or run properly for those results.

```{r Plot23OmegaCode}
# data re-ordering (was not saved in export)
plot_23_data_omega_reordered <- data_prep_plot_23_omega(plot_23_data_omega)

# plot for omega
ggplot(plot_23_data_omega_reordered, aes(x = alpha, y = g)) +
  geom_boxplot(outlier.shape = NA) +
  geom_hline(yintercept = 5.5, color = "red", size = 1) +
  geom_point(alpha = 0.1) +
  theme_minimal() +
  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), 
                                                     "lines")) +
  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0),
    ymin = 6, ymax = 6, xmin = 1.08, xmax = 1.08) +
  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0),
    ymin = 5, ymax = 5, xmin = 1.08, xmax = 1.08) +
  coord_cartesian(xlim = c(0, 1), clip = "off") +
  ylab("") +
  xlab("Omega")
```

### 2024-03-18 Scripts/AppendixScripts/Appendix_pre-reg_analyses.Rmd
cleaned up manuscript, expanded readme file, and revised the data package desciptive information.

--- 2024-03-13 Scripts/Appendix_scripts/Appendix_pre-reg_analyses.Rmd
@@
 
+These results are potentially quite worrying given that many studies made use of single item measures, which assume unidimensionality by default without being able to assess it.
+These results show that for the measures that could be tested for unidimensionality, and that were mostly used as single indicators in the analyses for the replication protocol, unidimensionality commonly did not hold.
+However, one could argue that measures being used as singular indicators does not necessarily mean these measures all assessed constructs with a unidimensional structure.
+For example, IQ is often used as a singular indicator, even though it consists of several factors [@weiss2013wisc].
+However, it should be noted that at least with respect to Many Labs 2, all of the measures that were considered unidimensional for the analyses in this study were also considered unidimensional in the investigation by @shaw2020measurement} who also observed a lack of unidimensionality evidence in their investigation of Many Labs 2.
+To conclude, there is an indication that validity evidence for measures used in replication research is lacking, and that this may have further implications beyond the measures for which it could be assessed here.
+
 ## H6 QMP-Category Specific Exploratory Analyses

### 2024-03-18 Scripts/Manuscript/manuscript.Rmd
cleaned up manuscript, expanded readme file, and revised the data package desciptive information.

@@
 
+appendix:
+  - "Scripts/AppendixScripts/Appendix_pre-reg_analyses.Rmd"
+  - "Scripts/AppendixScripts/Appendix_multilevel_analyses.Rmd"
+  - "Scripts/AppendixScripts/Appendix_omega_analyses.Rmd"
+  - "Scripts/AppendixScripts/Appendix_initial_QMP_analyses.Rmd"
+
 classoption       : "man"
@@
 
-Measurement in psychological science is defined in large part by one overarching issue: the psychological constructs of interest, such as affective state and intelligence, cannot be measured directly.
+Measurement in psychological science is defined in large part by one overarching issue: the psychological constructs of interest, such as affective state and intelligence, cannot be measured directly [@flake2017construct].
 As a result, psychologists face two primary challenges in the use of measurement: First of all, the measure has to assess the construct it intends to measure, even though it can only do so indirectly.
@@
 ## Measurement Error
-
-???connection/throughline of the measurement error hypotheses and other (including measurement error) hypotheses –\> is there a way to rewrite this part of the article to fit better as support/precedence to the QMP stuff????
-–\> risky use of measurement!?!
-
 As a first step the state of measurement error in original and replication research in psychology is investigated, to assess the scope of @stanley2014expectations's findings in practice:
@@
 However, no coding or analysis of either of them had taken place before the analyses were preregistered.
-Further details on the search strategy can be found in the ???
-supplementary materials.
+Further details on the search strategy can be found in the data_search_details.pdf supplementary materials.
 
@@
 [^2]: The steps taken to access the replication protocol data from Many Labs 5 were not preregistered, and only became clear upon further investigation of the accessible information.
-The specific names and locations of the files that were used as the datasets can be found under the supplementary materials of the OSF page of this article <https://osf.io/gft46/%7D>.
+The specific names and locations of the files that were used as the datasets can be found in the data_search_details.pdf supplementary materials of the OSF page of this article <https://osf.io/gft46/%7D>.
 
@@
 Descriptions of the extracted variables can be found in the sections below.
-The coding protocol and explanations on how the articles and replication protocols were searched through to answer the questions in the coding protocol can be found in the supplementary materials ???.
+The coding protocol and explanations on how the articles and replication protocols were searched through to answer the questions in the coding protocol can be found in the coding protocols folder of the supplementary materials.
 
@@
 
-Cronbach's alpha was calculated as the main score reliability index used in the analyses, as remains the most commonly used indicator of the reliability of a measure.
+Cronbach's alpha was calculated as the main score reliability index used in the analyses, as remains the most commonly used indicator of the reliability of a measure [@flake2017construct].
 Cronbach's alpha was calculated using the alpha function from the psych R package [@R-psych].
@@
 
-Eleven out of twenty of the QMP variables used to calculate the QMP ratio have an equivalent in the coding key of @flake2022construct.
-The remaining nine were either altered from the coding key to better fit the QMP counting operationalization, all newly created or modified items were based on the definitions of the QMP categories and their criteria as specified in @flake2020measurement.
 Beside these quantitative variables, a total of four qualitative variables were also included to provide more detailed information on some aspects of the measure and its reporting.
-Details on the items used, their origin, changes, and justifications can be found in supplementary materials ???.
+Details on the items used, their origin, changes, and justifications can be found in the coding protocol information supplementary materials.
 
@@
 
-MOVE TO EXTERNAL SEARCH STRATEGY FILE: 
-The scope of the coding was limited to the abstract, method, procedure, materials, measure, and initial parts of the results sections.
-Additionally, a keyword search using the name of the measured variable was used to search for any potentially missed information.
-An exception to this procedure was a question asking about the presence of example items.
-For this question, information from supplementary materials was uniquely considered as relevant.
-Another exception was the question regarding the replication of the original effect.
-Tables from the final report of each Many Labs project were used to answer that question.
-
-These changes (to the QMP coding protocol) included: accepting linked online appendices as a data source for example items; assuming that if no differences between replication and original are measurement is mentioned, that there is no difference, even if it is not explicitly clear; and generally simplified criteria for what constituted sufficiently clear reporting.
-
-SUPPLEMENTARY MATERIALS ON ITEM REVISION AND ORIGIN:
-Two of the qualitative items have an equivalent in the coding key of Variables related to the specific measurement scaling and purpose in the paper, were omitted from the analyses of this study as they were deemed neither relevant for the analyses of this study, nor necessary in matching this study to the key results of @flake2022construct.
-Questions about more general measurement features such as the number of items and how scores were aggregated were altered from @flake2022construct to better fit the use of QMP ratios and associations between them and other coded aspects.
-
-These (qualitative) variables assessed with two having an equivalent in @flake2022construct: the specific version of the measure (if reported); whether and what previous materials were used for the study; what, if any, psychometric evidence beyond reliability score (e.g.
-factor analysis, IRT model, convergent validity) was provided; and whether it was specified or not that the measure was or was not modified.
-
 # Results
@@
 
-If we look at the reliabilities obtained from the Many Labs responses on each measure for which scalar data could be accessed, the distributions of the Cronbach's alpha coefficients for each replication set for are displayed in Figure \@ref(fig:Plot23AlphaCode), separated by successful and unsuccessful replication.
-The average calculated Cronbach's alpha coefficient across replication sets was `r apa_num(mean(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$alpha, na.rm = TRUE), digits = 3)`
-
-```{r Plot23AlphaCode,warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the eighteen distinct measures for which suitable raw data was available to calculate Cronbach’s alpha coefficients from.
+Despite the lack of reliability reporting,if scalar data could be accessed for a measure the reliability could be calculated for each lab it was used in.
+The distributions of the Cronbach's alpha coefficients for each replication set are displayed in figure \@ref(fig:Plot23AlphaCode), separated by successful and unsuccessful replication.
+The average calculated Cronbach's alpha coefficient across replication sets was `r apa_num(mean(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$alpha, na.rm = TRUE), digits = 3)`.
+
+When comparing the reported reliabilities with the calculated reliabilities displayed in figure \@ref(fig:Plot23AlphaCode), all but `r apa_num(sum(plot_23_data_reported_alpha$coefficient_difference > 0), numerals = FALSE)` of the reported reliabilities are in the lower half of the distribution of the calculated reliabilities within their own measure.
+However when looking across the measures, the mean of the distribution of the calculated coefficients of all but `r apa_num(sum(aggregate(plot_23_data_alpha_reordered$alpha, list(plot_23_data_alpha_reordered$g), FUN = mean)[plot_23_data_reported_alpha$article_order,2] <= mean(data_h3_multiple$alpha)), numerals = FALSE)` of the measures that have reported reliability coefficients is larger than the mean calculated Cronbach's alpha.
+
+```{r Plot23AlphaCode, warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the eighteen distinct measures for which suitable raw data was available to calculate Cronbach’s alpha coefficients from.
 The green lines indicate the meta-analytic prediction interval lower and upper bound.
@@
 A large number of QMP ratios are missing for the QMP modification type , because only `r apa_num(table(coded_data_replications$mod_check)["True"])` out of `r apa_num(length(coded_data_replications$mod_check))` measures in replications, and only `r apa_num(table(coded_data_original_shortened$mod_check)["True"], numerals = FALSE)` measures used in original studies were modified.
-???Cronbach's alpha of the QMP items???
 
@@
 # Changing rownames to reflect the variables
-rownames(reporting_descriptives_table) <- c("Specified measure version", "Used existing materials", "Specified being newly created", "Reported psychometric evidence", "N modified", "Modified after/during data collection", "Total")
+rownames(reporting_descriptives_table) <- c("Specified measure version", "Used existing materials", "Specified being newly created", "Reported validity evidence", "N modified", "Modified after/during data collection", "Total")
 
@@
 ## Risky Measurement Usage
-
-???
-Results based on calculated reliability are somewhat unstable, but we can definitely say that a large number of single item measures are used, not many multiple item measures are accompanied by a reported alpha coefficient, and when looking at the heterogeneity and selective reporting of alpha we see this...???
-
 This study assessed the quality of measurement and measurement reporting in original and replication research by investigating the quality of measurement in the Many Labs projects, and the original articles they attempted to replicate.
@@
 These two studies found that validity evidence and reliability coefficient reporting for measures was lacking in replications and original studies.
-lllnot enough reliability coefficients were reported to conduct the planned analysis for hypothesis 1, and of the 77 measures only X measures in original articles and X in replication protocol reported any validity evidence.
-These findings show that reliability and validity evidence was similarly underreported in our sample, a problem that has also been addressed in earlier literature on this topic [@vacha1999practices; @green2011recent].
+This is illustrated in our sample by the fact that reliability coefficients were reported in too small quantity to conduct the planned analysis for hypothesis 1, and because of the `r nrow(coded_data_replications)` measures only `r sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")` measures in original articles and `r sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")` in replication protocol reported any validity evidence.
+Thus, reliability and validity evidence was underreported in our sample similarly to the findings of @shaw2020measurement, @flake2017construct & @flake2022construct, a problem that has also been addressed in earlier literature on this topic [@vacha1999practices; @green2011recent].
 
 The adjusted test for hypothesis 1, while not able to test differences in actual coefficient values, did show contradictory to hypothesis 1 and similarly to @flake2022construct, that original articles reported reliability coefficients more often than replication studies.
-Still, even for original articles a little over two-thirds of the multiple item measures were also reported without reliability evidence.
-???Interestingly enough, when looking at the measures for which alpha could be calculated, alpha coefficients were reported only for those measures that were among the higher calculated mean alpha among the sample of measures for which alpha could be calculated as can be seen in figure \@ref(fig:Plot23AlphaCode)???
+Still, even for original articles `r round(100 * (table(coded_data_original_shortened$N_items)[["multiple item measure"]] - sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)])) / table(coded_data_original_shortened$N_items)[["multiple item measure"]], digits = 0)`% of the multiple item measures were also reported without reliability evidence.
 
@@
 Research commonly made use of single item measures (see Figure \@ref(fig:ReliabilityReportingFlowDiagram) for more details), an observation that was also made by @shaw2020measurement.
-The use of these single item measures comes with risks, since by virtue of being singular they assume that whatever they are measuring is unidimensional, while not being able to test this assumption [@shaw2020measurement], ???and reliability risks???.
-This is particularly concerning given that the analyses of the calculated reliabilities of the multiple item measures showed that some measures ???EXPLORATORY ANALYSIS IDEA: relation of the calculated reliabilities and N items of the measure???, and exploratory analyses of the multiple item measure replication datas, for which unidimensionality could be tested, showed only little support for unidimensionality (see Appendix A as was also observed by @shaw2020measurement).
-
-???APPENDIX with SENSITIVITY ANALYSES/UNIDIMIMENSIONALITY ANALYSIS???: This is potentially quite worrying given that the exploratory analyses of the multiple item measures, for which unidimensionality could be tested, showed only little support for unidimensionality of the measures used in replications.
-While the measures that were tested for unidimensionality were mostly used as single indicators in the analyses for the replication protocol, one could argue this does not necessarily mean these measures all assessed constructs with a unidimensional structure.
-For example, IQ is often used as a singular indicator, even though it consists of several factors [@weiss2013wisc].
-However, it should be noted that at least with respect to Many Labs 2, all of the measures that were considered unidimensional for the analyses in this study were also considered unidimensional in the investigation by @shaw2020measurement} who also observed a lack of unidimensionality evidence in their investigation of Many Labs 2.
-To conclude, there is an indication that validity evidence for measures used in replication research is lacking overall.]]]
-
-Several results did show more promising findings for the way measurement related issues are treated in replications.
-Firstly, the support found for hypothesis 2 provided some evidence showing that most of the variability in reliability coefficients is between measures, rather than within measures across different locations.
-This would be a prerequisite showing that the measurement operated similarly across these locations, which would make the scores from the different lab locations directly comparable and aggregatable.
-However, the small sample number of measures for which reliability could be assessed does mean that this estimate remains uncertain.
+The use of single item measures comes with many risks with regard to validity [@diamantopoulos2012GuidelinesChoosingMultiItem; @nunnallyOverviewPsychologicalMeasurement1978].
+Additionaly, by virtue of being singular they assume that whatever they are measuring is unidimensional, while not being able to test this assumption [@shaw2020measurement].
+This is particularly concerning given that the exploratory unidimensionality tests for the multiple item measures (appendix A) revealed that only `r sum(cfa_results$Single_factor == "Yes", na.rm = TRUE)` of the `r nrow(cfa_results)` relevant measures satisfied the conditions for unidemensionality.
+Thus showing little support for unidimensionality of measurement in general, although the result from this analysis is tentative on several assumptions (see Appendix A).
+
+Several results did show more promising findings for the way measurement related issues are treated in replications at least.
+Firstly, the pre-registered test for hypothesis 2 showed that most of the variability in reliability coefficients in the sample is between measures, rather than within measures across different locations.
+Additionally, the meta-analysis of Cronbach's alpha showed non-significant and small heterogeneity estimates for most of the measures analysed.
+This is a prerequisite showing that measurement generally operated similarly across locations, which would make the scores from the different lab locations directly comparable and aggregatable.
+However, the small sample number of measures for which reliability could be assessed does mean that the generalisability remains uncertain.
 Secondly, most replication protocols clearly stated that their measure was either newly created or based on existing materials.
@@
 The number of measures for which reliability was calculated was quite low (`r apa_num(sum(!is.na(data_h3_avg$alpha)), numerals = FALSE)`), it could be that the test was simply underpowered to detect the effect.
-On the other hand, it might be that the detrimental influence of measurement error on interpretations of replication results is small in large scale replication projects.
-Across the multiple replications, measurement error's influence on the effect could have been cancelled out at the meta-analytic level.
-This would require the measurement error to be random and small, and as a result the average value of the effect and the error around would remain similar, thus not altering the result of the meta-analytic significance test ???logic/cited work???.
-
-[[[??? reliability meta-analysis???
+On the other hand, it might be the result of measurement error's tendency to reduce heterogeneity in estimates of the same effect, making the observed effects more similar [@olsson-collentine2023UnreliableHeterogeneityHow].
+This may have resulted in effects that appeared to homogeneously show evidence in one direction, which may explain the differences in conclusions observed between this article and the simulation studies of @stanley2014expectations.
 
@@
 The test for hypothesis 6 showed that, in line with expectations, there was a positive association between the total QMPs of an original study and the total QMPs in the protocol of the replication for that study.
+
 The idea here is that when information on or support for the use of a measurement is lacking, any subsequent replication attempt is expected to also lack information on the measure.
-As a result, both the underreporting of measurement details and use of unverified measurements may persist.
-[make the domino effect more clear/better written here]
-
-Furthermore, ensuring that the original measurement is mimicked becomes difficult to verify when the measurement was not documented well originally.
-As a result, the relation between the original and replication studies weakens, lowering the chances that similar results will be found, and possibly even invalidating the replication's relation to the original study as a replication [@flake2022construct].
-
-However, it is worth noting that hese relations were only found for QMPs coded with the revised coding protocol.
+As a result, both the underreporting of measurement details and use of unverified measurements may persist in the replication.
+Consequently, ensuring that the original measurement is mimicked becomes difficult to verify when the measurement was not documented well originally.
+In turn, the relation between the original and replication studies may weaken [@flake2022construct], and as a result, constructs are measured substantially differently, thus the subsequent test in the replication is substantially different from the test in the original article.
+This would mean that the observed effects in the replication may differ from the original not only due to sampling error, but also due to true differences in the assessed effect as the result of the measurement used.
+
+However, it is worth noting that these relations were only found for QMPs coded with the revised coding protocol.
 Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see Appendix D).
@@
 As a result, the ability to investigate the exact causal links between QMPs and replicability was limited.
-Secondly, alternative ways to analyse the data could have been used, or certain parts of the data could have been examined more closely.
-Several methodologies for doing so have already been suggested throughout the article such as ???insert methodology here???, and others are presented in the appendix ???sensitvity and exploratory analysis appendix???.
-Future research can use this study as a basis to find relevant data sources and methodologies to use in order to compliment and extend the findings of this study, or test causal links between measurement usage and replicability.
+Secondly, alternative ways to analyse or expand the sample could have been used.
+The coding protocol was changed within the scope of this study, which illustrates that there was no validated methodology for analyzing the data, and there is no prior evidence validating the use of QMP ratios to represent questionable measurement practices.
+Future research can use this study as a basis to find relevant data sources, and develop methodologies that can be used to compliment and extend the findings of this study, or test causal links between measurement usage and replicability.
 
@@
 This research did not make use of any online appendices in assessing QMPs, future research may wish to include them and other sources as part of the data.
-\<-- try to collpase with previous paragraph???
-
-Another limitation of this study is that the results differed based on whether data from the revised or the initial coding protocol was used.
-The revised coding protocol was adapted from the initial coding protocol before any analyses were performed, it is however still possible that a change in protocol may have biased results.
-Future research investigating this topic should use a coding protocol which is verified independently by several researchers on a sample of articles and protocols first, before being used to code the QMP data that will be analysed.
-As a first step, the coding protocol from this study and the coding key from @flake2022construct can be used as a basis.
-\<- importance ???
-
-As a last note on QMPs, it is worth highlighting the way the QMP ratios were calculated.
-The total QMP ratio was based on the counts for each of the items from all the different QMP types divided by the total number of applicable questions.
-However, for each QMP type the number of items was different.
-This means that QMP types with a larger number of items (such as operationalisation) had a greater impact on the total QMP ratio than QMP types with a smaller number of items (such as definition).
-If the impact for each QMP type on each other and replicability is considered equally important, the total QMP ratio may not be considered a valid indice.
-On the other hand, it could be that each item should be considered equally important rather than each QMP type.
-For this study, the protocol was made and the analyses were conducted under the assumption that each item had equal weight.
-However, this is an assumption this study cannot provide evidence for.
-[Focus more on the fact that there is a mixture in the QMP ratio’s: which influences the relations perhaps like ...]
-
-The small sample of measures for which reliability coefficients and unidimensional factor structure could be assessed limited the degree to which substantial interpretations can be made from the reliability and validity analyses.
+
+As a final note on QMPs, it is worth highlighting a specific aspect about the way the QMP ratios were calculated.
+This relates to the fact that non-applicable items, while adjusted for by coding those items as 0 in both the numerator and denominator of the QMP ratio calculation, could exert a strong influence on the value of the QMP ratio.
+For example, for one measure all relevant information regarding the measure was reported, for another no information was provided on the measure at all and the items were all non-applicable.
+In both cases the QMP ratio would be 0, however we would not consider the latter case to be nearly as informative as the first.
+As a result the relation between QMP ratio and measurement reporting quality is obscured.
+There is no simple solution to this problem based on teh current data, however future research may wish to include qualitative analyses of the informativeness of measurement detail reporting to provide a more thorough and complete picture.
+
+The small sample of measures for which reliability coefficients could be assessed limited the degree to which substantial interpretations can be made from the reliability analyses.
 While future research will also unlikely be able to increase the number of multiple item measures used by replications, future research can broaden their analyses to include a larger number of replications, or take into account a type of measure which this study mostly ignored in the analyses of reliability and validity: single-item measures.
@@
 Reliability assessment for single item measures differs substantially from multiple item measures [@wanous1996estimating], and for this reason was not included as part of the analyses for this study.
-Furthermore, single items cannot be tested on unidimensionality, since a single item is already assumed to measure only a single dimension by definition.
-However, future research might consider methods specifically designed to assess reliability and validity of single item measures.
+However, future research might consider methods specifically designed to assess the reliability of single item measures.
 This could prove to be a worthwhile contribution, given the proportionally large number of single item measures that were encountered in the data for this study (see Figure \@ref(fig:ReliabilityReportingFlowDiagram)).
@@
 Investigations similar to this have also been suggested for future replication projects [@flake2022construct].
-For these reasons, future research should consider measurement invariance tests, if assessing measurement consistency in replications across different labs.
-\<-- also include other suggestions like for paragraph 1 of this section???
+For these reasons, future research should consider using measurement invariance tests, when assessing measurement consistency in replications across different labs.
 
@@
 Taking all the findings together, the following assessments will be relevant to consider for future replication research.
-With respect to the quality of measurement reporting, the small number of reported reliabilities, small number of reported psychometric validity evidence, and lack of unidimensionality evidence for data aggregated to a single indicator corroborate findings by @shaw2020measurement & @flake2022construct.
-Evidence supporting the measures used in replication should be reported more frequently, so that they can be evaluated and the validity of replication research can be improved.
-
-There are additional validity issues in measurement as the result of QMPs.
-While it is debatable whether or not $17.9\%$ [add code for this percentage] average QMP ratio in replications is too much, the association between original paper and replication protocol QMPs demonstrates how a lack of information for measurement in the original can spill over to the reporting in replications.
+With respect to the quality of measurement reporting, the small number of reported reliabilities, and lack of reported validity evidence corroborate findings by @shaw2020measurement & @flake2022construct.
+Evidence on the reliability and validity of the measures used in both replication and original research should be reported more frequently, so that measures can be evaluated and the validity of replication research can be improved.
+
+The results suggest that the use of structured measurement reporting protocols may be an effective way of reducing QMPs, and may explain why the replication protocols had on average lower QMPs than original articles in this study.
+However, the reliability and validity evidence reporting rate was lower in the Many Labs replication protocols that made use of structured reporting protocols compared to original articles.
+These protocols could therefore still increase the attention they give to reporting reliability and validity evidence.
+
+Furthermore, the association between original paper and replication protocol QMPs demonstrates how a lack of information for measurement in the original can spill over to the reporting in replications.
 This could lead to issues for replication attempts if the measure in an original article has poor reliability and validity.
@@
 The results of any direct replication attempt will face the same issues, and as a consequence the replication is unlikely to provide a relevant test of a psychological theory, as the original study itself was not a robust test of that psychological theory to begin with [@isager2020deciding, @isager2021deciding, @nuijten2022assessing].
-Thus, future replicators should first evaluate the quality of the measurement (reporting) in an article before deciding to replicate it.
-\<-- work this narrative into the discussion section for QMP -\> replicability???
-
-The results also suggest that the use of structured protocols in the reporting of measurement may be an effective way of reducing QMPs, and increasing the reporting of reliability and validity evidence.
-However, even in the Many Labs projects, which made use of structured protocols to report their measures, low reliability and validity evidence reporting was found.
-These protocols could therefore still increase the attention they give to reporting reliability and validity evidence.
-When original articles do not report their measurement details, replication attempts cannot guarantee a direct replication of the original.
-By improving the quality of measurement reporting in original articles, the validity of both original research results and future replication attempts would increase.
-It would be particularly important to focus on remedying strong violations of good measurement reporting, as these were shown to have a significant detrimental impact on replicability.
-This suggests that even small but critical improvements in the reporting of measurement information could lead to a substantial increase in the replicability of psychological science.
-\<-- work into paragraph above and shorten heavily...
-paragraph 2 is about the importance of structured protocols.
-Paragraph 3 about the need to consider the options when replicating a study.
+Thus, future replicators should first evaluate the quality of the measurement (reporting) in an article before deciding to replicate.
 
@@
 In that case, the direct replication will be able to provide a sufficient test of a psychological theory, on the condition that the conceptual replication's test improvements led to it becoming a sufficient test.
-\<-- less direct vs.
-conceptual???
 

### 2024-03-18 SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd
cleaned up manuscript, expanded readme file, and revised the data package desciptive information.

# Coding Protocol Information

This supplementary material file contains information regarding the origin of the items used and how they were modified to better fit this study's aims; a summary of the changes between the initial and revised coding protocol; & general notes on the procedure of coding measurement information in the replication protocols and original articles using the the coding protocol (further details can be found in the coding protocol pdf files present in this folder of the supplementary materials).

## Item origin & modifications
Eleven out of twenty of the QMP variables used to calculate the QMP ratio have an equivalent in the coding key of @flake2022construct. The remaining nine were altered from the coding key to better fit the QMP counting operationalization. Because QMPs were aggregated they would need to have equivalent weighting in the importance of the overall QMP judgement of the protocol or article being evaluated.

All of the newly created or modified items were based on the definitions of the QMP categories and their criteria as specified in @flake2020measurement. The information to report for each of the categories as presented in Table 1 in @flake2020measurement were used to determine what information there should be questions about in the protocol. However, feasibility of coding the information was also taken into account, and whether a lack of information could clearly be labelled as a QMP.

Two of the qualitative items have an equivalent in the coding key of Variables related to the specific measurement scaling and purpose in the paper, were omitted from the analyses of this study as they were deemed neither relevant for the analyses of this study, nor necessary in matching this study to the key results of @flake2022construct. Questions about more general measurement features such as the number of items and how scores were aggregated were altered from @flake2022construct to be used for obtaining QMP ratios.

These (qualitative) variables assessed with two having an equivalent in @flake2022construct: the specific version of the measure (if reported); whether and what previous materials were used for the study; what, if any, psychometric evidence beyond reliability score (e.g. factor analysis, IRT model, convergent validity) was provided; and whether it was specified or not that the measure was or was not modified.

## summary of changes between initial and revised protocol
Based on discussion with the supervising author, the initial coding protocol was revised and changed to be more lenient in the judgement of attributing QMPs.

These changes to the QMP coding protocol included: accepting linked online appendices as a data source for example items; assuming that if no differences between replication and original are measurement is mentioned, that there is no difference, even if it is not explicitly clear; and generally simplified criteria for what constituted sufficiently clear reporting.

## General description coding procedure
The scope of the coding was limited to the abstract, method, procedure, materials, measure, and initial parts of the results sections. Additionally, a keyword search using the name of the measured variable was used to search for any potentially missed information. An exception to this procedure was a question asking about the presence of example items. For this question, information from supplementary materials was uniquely considered as relevant. Another exception was the question regarding the replication of the original effect. Tables from the final report of each Many Labs project were used to answer that question.

Further details about the description of the coding procedure for each section and item is explained in the coding protocols themselves.

### 2024-03-18 SupplementaryMaterials/reproducible_data_retrieval_information.Rmd
cleaned up manuscript, expanded readme file, and revised the data package desciptive information.

# Reproducible data retrieval information

This supplementary material file contains detailed information on the specific path files and names of the used registered replication protocols and datasets.

## Registered Replication Protocols

Below are the relevant OSF pages, and exact path and file names of the relevant pre-registered replication protocols that were extracted, to be then coded on measurement reporting information in the Many Labs replications projects.

???look up and add osf pages + project path + file names, and format like:???

Many Labs 1 (<https://osf.io/wx7ck/>):
- Path: OSF Storage (United States)/
- Protocol File: ManyLabsProposal_V1.1.docx

Many Labs 2 (<https://osf.io/8cd4r/>):
- Path: OSF Storage (United States)/
- Protocol File: ML2_-_Protocol.pdf

Many Labs 3 (<https://osf.io/ct89g/>):
- Path: OSF Storage (United States)/
- Protocol File: ML3_Protocol_9152014.pdf

Many Labs 5 Study 1, Albarracín et al. (2008), Experiment 5 (<https://osf.io/a9hk2/>):
-	Path: ML5 Site Replications/Protocol and Analysis Plan/OSF Storage (United States)/
-	Protocol File: ML5Alb5Pre-RegProtocolAndAnalysisPlan.docx

Many Labs 5 Study 2, Albarracín et al. (2008), Experiment 7 (<https://osf.io/j5s8c/>):
-	Path: OSF Storage (United States)/Proposal and Manuscript/
-	Protocol File: Albarracinetal.Study7RevisedProtocol.docx

Many Labs 5 Study 3, Förster, Liberman, & Kuschel (2008) (<https://osf.io/rje4t/>):
-	Path: Materials/Revised Protocol/
-	Protocol File: Förster et al. Replication Endorsed Protocol Final.docx

Many Labs 5 Study 4, LoBue & DeLoache (2008) (<https://osf.io/9g7pw/>):
-	Path: OSF Storage (United States)/ 0. Protocols/
-	Protocol File: LoBueDeLoache2008_ML5RevisedProtocol.pdf

Many Labs 5 Study 5, Payne, Burkley, & Stokes (2008) (<https://osf.io/wxd4g/>):
-	Path: OSF Storage (United States)/
-	Protocol File: PayneBurkleyStokes2008RevisedProtocol.docx

Many Labs 5 Study 6, Risen & Gilovich (2008) (<https://osf.io/h5a9y/>):
-	Path: Dropbox: ML5_risen_Gilovich_git/protocols/Post-review protocol (for preregistration)/
-	Protocol File: Risen & Gilovich Revised Protocol.docx

Many Labs 5 Study 7, Shnabel & Nadler (2008) (<https://osf.io/vz5ru/>):
-	Path: OSF Storage (United States)/
-	Protocol File: ML5 ShnabelNadler Revised Protocol.docx

Many Labs 5 Study 8, van Dijk et al. (2008)) (<https://osf.io/f6n27/>):
-	Path: Replications/OSF Storage (United States)/Protocols/
-	Protocol File: vanDijketal.2008RevisedProtocol.pdf

Many Labs 5 Study 9, Vohs & Schooler (2008) (<https://osf.io/8rcbk/>):
-	Path: Research Protocols (and other things you might want to read)/OSF Storage (United States)/
-	Protocol File: ML5 Protocol.docx

## Registered Replication Datasets
Below are the relevant OSF pages, and exact path and file names of the relevant replication datasets that were extracted, to be then used for calculating the reliability and testing the unidimensionality of the measures used in the Many Labs replications projects.

Many Labs 1 (<https://osf.io/wx7ck/>):
-	Path: Data/Datasets.zip
-	Data File: Full_Dataset_De-Identified.sav

Many Labs 2 Study 2, Kay et al. (2014) (<https://osf.io/8cd4r/>):
-	Path: Data and Results (per site, etc.)/OSF Storage (United States)/Structure & Goal Pursuit (Kay et al., 2014)/Kay.1/Global/Data/
-	Data File: Kay_1_study_global_include_all_CLEAN_CASE.csv

Many Labs 2 Study 3, Alter et al. (2007) (<https://osf.io/8cd4r/>):
-	Path: Data and Results (per site, etc.)/OSF Storage (United States)/Incidental Disfluency (Alter et al., 2007)/Alter.1/Global/Data/
-	Data File: Alter_1_study_global_include_all_CLEAN_CASE.csv

Many Labs 2 Study 4 measure 1, Graham et al. (2009) (<https://osf.io/8cd4r/>):
-	Path: Data and Results (per site, etc.)/OSF Storage (United States)/Moral Foundations (Graham et al., 2009)/Graham.1/Global/Data/
-	Data File: Graham_1_study_global_include_all_CLEAN_CASE.csv

Many Labs 2 Study 4 measure 2, Graham et al. (2009) (<https://osf.io/8cd4r/>):
-	Path: Data and Results (per site, etc.)/OSF Storage (United States)/Moral Foundations (Graham et al., 2009)/Graham.2/Global/Data/
-	Data File: Graham_2_study_global_include_all_CLEAN_CASE.csv

Many Labs 2 Study 8 measure 2, Inbar et al. (2009) (<https://osf.io/8cd4r/>):
-	Path: Data and Results (per site, etc.)/OSF Storage (United States)/Disgust & Homophobia (Inbar et al., 2009)/Graham.1b/Global/Data/
-	Data File: Inbar_1b_study_global_include_all_CLEAN_CASE.csv

Many Labs 2 Study 10 measure 1, vanLange et al. (1997) (<https://osf.io/8cd4r/>):
-	Path: Data and Results (per site, etc.)/OSF Storage (United States)/Social Value Orientation (Van Lange et al., 1997)/vanLange.1/Global/Data/
-	Data File: vanLange_1_study_global_include_all_CLEAN_CASE.csv

Many Labs 2 Study 12, Anderson et al. (2012) (<https://osf.io/8cd4r/>):
-	Path: Data and Results (per site, etc.)/OSF Storage (United States)/SMS & Well-Being (Anderson et al., 2012)/Anderson.1/Global/Data/
-	Data File: Anderson_1_study_global_include_all_CLEAN_CASE.csv

Many Labs 2 Study 15, Giessner & Schubert (2007) (<https://osf.io/8cd4r/>):
-	Path: Data and Results (per site, etc.)/OSF Storage (United States)/Position & Power (Giessner & Schubert, 2007)/Giessner.1/Global/Data/
-	Data File: Giessner_1_study_global_include_all_CLEAN_CASE.csv

Many Labs 2 Study 19 measure 1, Savani et al. (2010) (<https://osf.io/8cd4r/>):
-	Path: Data and Results (per site, etc.)/OSF Storage (United States)/Actions are Choices (Savani et al., 2010)/Savani.3a/Global/Data/
-	Data File: Savani_3a_study_global_include_all_CLEAN_CASE.csv

Many Labs 2 Study 20, Norenzayan (2002) (<https://osf.io/8cd4r/>):
-	Path: Data and Results (per site, etc.)/OSF Storage (United States)/Intuitive Reasoning (Norenzayan et al., 2002)/Savani.1/Global/Data/
-	Data File: Norenzayan_1_study_global_include_all_CLEAN_CASE.csv

Many Labs 2 Study 23, Zhong & Liljenquist (2006) (<https://osf.io/8cd4r/>):
-	Path: Data and Results (per site, etc.)/OSF Storage (United States)/Moral Cleansing (Zhong & Liljenquist, 2006)/Zhong.1/Global/Data/
-	Data File: Zhong_1_study_global_include_all_CLEAN_CASE.csv

Many Labs 3 (<https://osf.io/ct89g/>):
-	Path: OSF Storage (United States)/ML3 Final Data.zip
-	Data File: ML3AllSitesandmTurk.csv

Many Labs 5 Study 1, Albarracín et al. (2008), Experiment 5 (<https://osf.io/a9hk2/>):
-	Path: Data/OSF Storage (United States)/
-	Data File: ML5 Alb 5 Revised Protocol In Lab.xlsx

Many Labs 5 Study 4, LoBue & DeLoache (2008) (<https://osf.io/9g7pw/>):
-	Path: ML5 Dataset & Analysis LoBue & DeLoache/OSF Storage (United States)/
-	Data File: dataset_LoBue_raw.sav

Many Labs 5 Study 5, Payne, Burkley, & Stokes (2008) (<https://osf.io/wxd4g/>):
-	Path: Data/OSF Storage (United States)/
-	Data File: Genova_ML5.csv

Many Labs 5 Study 7, Shnabel & Nadler (2008) (<https://osf.io/vz5ru/>):
-	Path: Data, Materials, Reports: ML5 Replication of Shnabel & Nadler (2008)/Data, Codebook, and syntax/OSF Storage (United States)/
-	Data File: ml5_computed_dataset.csv

Many Labs 5 Study 9 measure 1, Vohs & Schooler (2008) (<https://osf.io/8rcbk/>):
-	Path: Data/OSF Storage (United States)/FinalData/
-	Data File: ML5_fulldataset_with_suspicion.csv

### 2024-03-18 Scripts/source_script.R

@@ -714,13 +714,9 @@ data_prep_H2 <- function(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean,
 # use the rma function from the metafor package, for each replication set:
 # yi = calculated alpha
 # sei = ASE
-# method = "REML" <- probably
+# method = "REML" 
 # then, extract tau^2 from metafor output for each replication set & use the
 # predict function to obtain prediction intervals (to add in green?)
-
-# first row of each data is the lab location indicator
-
-
 
 
 ### Hypothesis 3

### 2024-03-19 Data/AnalysisData/codebook_cfa_results.Rmd
fixed compiling errors and plot 456 and table 1 look.

--- 2024-02-16 Data/IntermediateData/codebook_data_5.1.2_clean.Rmd
@@
 ---
-title: "Codebook created on 2024-02-16 at 2024-02-16 14:19:42.46426"
+title: "Codebook created on 2024-03-18 at 2024-03-18 14:12:52.006764"
 output: github_document
@@
 ## Dataset description
-The data contains 471 cases and 7 variables.
+The data contains 19 cases and 3 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_5.1.2_clean.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_cfa_results.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2024-03-19 Data/Data_package_description.Rmd
fixed compiling errors and plot 456 and table 1 look.

@@
 
-# OutputData
+# AnalysisData
+
+### cfa_results.csv
+
+*Explanation:* contains the results obtained from the exploratory unidimensionality check analyses based on factor analyses of the measures related to the data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, data_1.12.3.2_clean,data_2.12.1_clean, data_2.12.2_clean, data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.1_clean, data_3.7.2_clean, data_3.8.2_clean, data_5.1.1_clean, data_5.1.2_clean, data_5.7_clean, & data_5.9.1_clean datasets.
+This is part of the pre-registered exploratory analyses documented in appendix A.
+
+*Variables:*
+
+-   **RMSEA:** the rmsea value for a single factor confirmatory factor analysis model when in turn applied to each of the datasets under consideration.
+
+-   **N factors:** the number of factors selected for each of the datasets based on the parallel test for selecting factors.
+
+-   **Single_factor:** a boolean variable indicating whether or not the measure was unidimensional based on the criteria that either the rmsea for the single factor model was smaller than .08, or the parallel test returned a single factor solution.
 
@@
 
+-   **QMP_ratio:** float number between 0 and 1 that indicates the QMP ratio based on the initial coding protocol for that QMP type for that study/article.
+
+-   **QMP_ratio_1:** transformed version of the QMP_ratio column, where QMPs for all original articles have a 1 added to their ratio.
+This was done for the sake of making the figure possible in ggplot as it is right now.
+
 -   **QMP_type:** factor that indicates the QMP type the QMP ratio belongs to (Definition, Operationalization, Selection, Quantification, or Modification).
 
--   **QMP_ratio:** float number between 0 and 1 that indicates the QMP ratio for that QMP type for that study/article.
+-   **QMP_ratio_REV:** float number between 0 and 1 that indicates the QMP ratio based on the revised coding protocol for that QMP type for that study/article.
 
@@
 
--   **QMP_ratio_1:** transformed version of the QMP_ratio column, where QMPs for all original articles have a 1 added to their ratio.
+-   **QMP_ratio_1_REV:** transformed version of the QMP_ratio_REV column, where QMPs for all original articles have a 1 added to their ratio.
 This was done for the sake of making the figure possible in ggplot as it is right now.

### 2024-03-19 Scripts/Manuscript/AppendixScripts/Appendix_initial_QMP_analyses.rmd
fixed compiling errors and plot 456 and table 1 look.

--- 2024-03-18 Scripts/AppendixScripts/Appendix_initial_QMP_analyses.rmd
@@
-# Appendix D
+<!-- Appendix D -->
 
-```{r setup, include=FALSE}
-# loading R libraries, perhaps unnecessary
-library(papaja)
-
-# loading source script, perhaps unnecessary
-source(file = "C:/Users/u686785/OneDrive - Tilburg University/Documents/uvt/PHD/Master Thesis to Paper/Reproducible_R_Project/Scripts/source_script.R")
-
-```
-
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(17042023)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
-```
+# Initial Coding Protocol QMP Analyses
 
@@
 
+# shortening the replication and original labels for nicer plot 1
+levels(plot_456_data$RepOrg) <- c("Org.", "Rep.")
+
 ### ratio Original and Rep
@@
   scale_fill_manual(values = c("#ff766c", "#cb5e56", "#be5850", "#aa4f48", "#994741", "#803b36", "#672f2b", "#5b2a26", "#562824", "#411e1b", "#341816", "#120606", "#030101","#4366ff", "#4265fc", "#3652ce", "#324cbe", "#324cbe", "#2c44aa", "#2c44aa", "#293e9b", "#293e9b", "#213380", "#1c2a69", "#1c2a69", "#172256", "#172256", "#111a41", "#111a41", "#010103", "#010103")) +
-  theme(legend.position = "none") +
   facet_grid(~ QMP_type) + 
+  theme(legend.position = "none", strip.text = element_text(size = 7)) +
   ylab("Relative Prevalence of\nQMP Ratio in Sample") +
@@
   ggtitle("QMP Ratio's Per QMP Type Grouped by Original and Replication")
+
+# changing the replication and original labels back for plot 2
+levels(plot_456_data$RepOrg) <- c("Original", "Replication")
 
@@
 
-# combine both plots into one figure
+## the following two plots are constructed solely for the purpose of extracting
+# a legend from them.
+for_legend_plot_456_org <- ggplot(plot_456_data[plot_456_data$QMP_type != "Total",], 
+                                  aes(x = RepOrg, y = abs(QMP_ratio - 1), fill = abs(QMP_ratio - 1))) + 
+  geom_bar(stat = "identity") +
+  theme_minimal() +
+  scale_fill_gradient(name = "Original", low = "#030101", high = "#ff766c", limits = c(0, 1), 
+                      breaks = c(0.001, 0.5, 0.999), labels = c(1, 0.5, 0)) +
+  theme(legend.title=element_text(size = 9)) + 
+  facet_grid(~ QMP_type)
+
+for_legend_plot_456_rep <- ggplot(plot_456_data[plot_456_data$QMP_type != "Total",], 
+                                  aes(x = RepOrg, y = abs(QMP_ratio - 1), fill = abs(QMP_ratio - 1))) + 
+  geom_bar(stat = "identity") +
+  theme_minimal() +
+  scale_fill_gradient(name = "Replication", low = "#000102", high = "#4366ff", limits = c(0, 1), 
+                      breaks = c(0.001, 0.5, 0.999), labels = c(1, 0.5, 0)) +
+  theme(legend.title=element_text(size = 9)) + 
+  facet_grid(~ QMP_type)
+
+# extracting the legends from the plot
+legend_456_org <- get_legend(for_legend_plot_456_org) 
+legend_456_rep <- get_legend(for_legend_plot_456_rep)
+
+# combining both plots and the legends into one figure
 grid.arrange(Plot_456_1, 
              Plot_456_2, 
-             nrow = 2)
-
+             legend_456_org,
+             legend_456_rep,
+             layout_matrix = rbind(c(1, 3, 4),
+                                    c(2, 2, 2)),
+              widths = c(8, 1, 1))
 ```
@@
 
-```{r Plot46FullInitialDataCode}
+```{r Plot46FullInitialDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication total QMP ratio’s obtained using the intial coding protocol with linear regression line.
+Each dot in the figure describes the QMP ratio in that graph across both the original article and its replication protocol.
+Note: jitter was applied to these dots in order to show the number of observations at points where multiple dots were present"}
 # Initial

### 2024-03-19 Scripts/Manuscript/AppendixScripts/Appendix_multilevel_analyses.rmd
fixed compiling errors and plot 456 and table 1 look.

--- 2024-03-13 Scripts/Appendix_scripts/Appendix_multilevel_analyses.rmd
@@
-# Appendix B
+<!-- Appendix B -->
 
-```{r setup, include=FALSE}
-# loading R libraries, perhaps unnecessary
-library(papaja)
-
-# loading source script, perhaps unnecessary
-source(file = "C:/Users/u686785/OneDrive - Tilburg University/Documents/uvt/PHD/Master Thesis to Paper/Reproducible_R_Project/Scripts/source_script.R")
-
-```
-
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(17042023)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
-```
+# Multilevel Analyses
 
@@
 
-```{r Hypothesis3MultilevelModelSensitivityAnalyses}
+```{r Hypothesis3MultilevelModelSensitivityAnalyses, warning = FALSE}
 ## sensitivity analyses.
@@
 
-```{r ReplicabilityReliabilityTestTable, warning=FALSE}
-# creating the dtaframe for the table <- separate the OMEGA from here???
-H3_table_dataframe <- rbind(H3_test_result_int_sensitivity_alpha$table, H3_test_result_main_omega$table, H3_test_result_int_sensitivity_omega$table, H3_test_result_slp_sensitivity_omega$table)
-
+```{r ReplicabilityReliabilityTestTable, warning = FALSE}
 # adding rows to give indication of specific sections (apa_table being awkward)
-H3_table_for_printing <- rbind(c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(1:2),], c("Omega", "", "", "", ""), c("Logistic Regression Model", "", "", "", ""), H3_table_dataframe[(3:4),], c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(5:6),], c("Random-Slope Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(7:8),])
+H3_table_for_printing <- rbind(c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_test_result_int_sensitivity_alpha$table)
 
@@
   , caption = "Model Results from Tests of Hypothesis 3"
-  , note = "The Alpha and Omega sections show the models where the independent variable was the calculated Cronbach's alpha and omega coefficient respectively.
-The random slope model for Cronbach's alpha did not converge, thus it results are not shown here.
-$^* p < .05$"
-  , escape = FALSE, placement= "htp", midrules = c(3, 5, 6, 7, 10, 13))
+  , note = "The random slope model for Cronbach's alpha did not converge, thus it results are not shown here."
+  , escape = FALSE, placement= "htp", midrules = 1)
 
@@
 
-```{r Hypotheses5And6SensitivityAnalyses}
+```{r Hypotheses5And6SensitivityAnalyses, warning = FALSE}
 ## Hypothesis 5 sensitivity test using a random intercept Guassian model.

### 2024-03-19 Scripts/Manuscript/AppendixScripts/Appendix_omega_analyses.rmd
fixed compiling errors and plot 456 and table 1 look.

--- 2024-03-18 Scripts/AppendixScripts/Appendix_omega_analyses.rmd
@@
-# Appendix C
+<!-- Appendix C -->
 
-```{r setup, include=FALSE}
-# loading R libraries, perhaps unnecessary
-library(papaja)
-
-# loading source script, perhaps unnecessary
-source(file = "C:/Users/u686785/OneDrive - Tilburg University/Documents/uvt/PHD/Master Thesis to Paper/Reproducible_R_Project/Scripts/source_script.R")
-
-```
-
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(17042023)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
-```
+# Omega Coefficient Analyses
 
@@
 
-```{r ICCCalculations, include = FALSE}
+```{r ICCCalculationsOmega, include = FALSE}
 # Variances
@@
 
+```{r ReplicabilityReliabilityTestTableOmega, warning=FALSE}
+# creating the dataframe for the table <- separate the OMEGA from here???
+H3_table_dataframe_omega <- rbind(H3_test_result_main_omega$table, H3_test_result_int_sensitivity_omega$table, H3_test_result_slp_sensitivity_omega$table)
+
+# adding rows to give indication of specific sections (apa_table being awkward)
+H3_table_for_printing_omega <- rbind(c("Logistic Regression Model", "", "", "", ""), H3_table_dataframe_omega[(1:2),], c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe_omega[(3:4),], c("Random-Slope Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe_omega[(5:6),])
+
+# print the table in apa formatting
+apa_table(
+  H3_table_for_printing_omega, align = c("l", "r", "r", "r", "r")
+  , caption = "Model Results from Tests of Hypothesis 3 based on the Omega COefficient"
+  , escape = FALSE, placement= "htp", midrules = c(2, 4, 6))
+
+```
+
 Thus no evidence for hypothesis 3 was found.

### 2024-03-19 Scripts/Manuscript/AppendixScripts/Appendix_pre-reg_analyses.Rmd
fixed compiling errors and plot 456 and table 1 look.

--- 2024-03-18 Scripts/AppendixScripts/Appendix_pre-reg_analyses.Rmd
@@
-# Appendix A
+<!-- Appendix A -->
 
-```{r setup, include=FALSE}
-# loading R libraries, perhaps unnecessary
-library(papaja)
-
-# loading source script, perhaps unnecessary
-source(file = "C:/Users/u686785/OneDrive - Tilburg University/Documents/uvt/PHD/Master Thesis to Paper/Reproducible_R_Project/Scripts/source_script.R")
-
-```
-
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(17042023)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
-```
+# Pre-registration Analyses
 
@@
 
-```{r UnidimensionalityExploratoryAnalysis}
+```{r UnidimensionalityExploratoryAnalysis, include = FALSE}
 extracted_data_list <- list(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, data_1.12.3.2_clean,data_2.12.1_clean, data_2.12.2_clean, data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.1_clean, data_3.7.2_clean, data_3.8.2_clean, data_5.1.1_clean, data_5.1.2_clean, data_5.7_clean, data_5.9.1_clean)
@@
   parallel_N_factors <- fa.parallel(extracted_data_list[[i]][-1], 
-                                    fa = "fa")$nfact
+                                    fa = "fa", plot = FALSE)$nfact
 
@@
 
+```{r cfaResultsStoring, include = FALSE, eval = FALSE}
+# storing the cfa_results, so they can be referenced within the main manuscript.
+open_data(data = cfa_results, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(cfa_results))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(cfa_results))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(cfa_results))), ".yml")) 
+```
+
 ## Results
 
-Suitable data for factor analyses was available for `r nrow(cfa_results_expanded)` measures.
+Suitable data for factor analyses was available for `r apa_num(nrow(cfa_results), numerals = FALSE)` measures.
 These measures were the same as those shown in Figure \@ref(fig:Plot23AlphaCode).
 The results are shown in Table \@ref(tab:UnidimesnionalityTestResultsTable).
-A composite score based on the measurement responses was used for sixteen of the `r nrow(cfa_results_expanded)` measures to form a single variable in the analyses, and were thus regarded as intended to be unidimensional.
+A composite score based on the measurement responses was used for sixteen of the `r apa_num(nrow(cfa_results), numerals = FALSE)` measures to form a single variable in the analyses, and were thus regarded as intended to be unidimensional.
 The number of dimensions for the remaining three were unclear.
-Sufficient fit of the unidimensional model was found for six out of the `r nrow(cfa_results_expanded)` evaluated measures.
-However, as shown in Table \@ref(tab:UnidimesnionalityTestResultsTable) the unidimensional model held based on the parallel analysis test alone, for only `r sum(cfa_results_expanded$`N Factors`== 1, na.rm = TRUE)` of the `r nrow(cfa_results_expanded)` measures.
-For those `r sum(cfa_results_expanded$`N Factors`== 1, na.rm = TRUE)` measures and an additional `r sum(cfa_results_expanded$RMSEA < .08, na.rm = TRUE) - sum(cfa_results_expanded$`N Factors`== 1, na.rm = TRUE)` the RMSEA $< .08$ criteria suggested evidence for single factor structures.
+Sufficient fit of the unidimensional model was found for `r apa_num(sum(cfa_results$Single_factor == "Yes", na.rm = TRUE), numerals = FALSE)` out of the `r apa_num(nrow(cfa_results), numerals = FALSE)` evaluated measures.
+However, as shown in Table \@ref(tab:UnidimesnionalityTestResultsTable) the unidimensional model held based on the parallel analysis test alone, for only `r apa_num(sum(cfa_results$N_factors == 1, na.rm = TRUE), numerals = FALSE)` of the `r apa_num(nrow(cfa_results), numerals = FALSE)` measures.
+For those `r apa_num(sum(cfa_results$N_factors == 1, na.rm = TRUE), numerals = FALSE)` measures and an additional `r apa_num(sum(cfa_results$RMSEA < .08, na.rm = TRUE) - sum(cfa_results$N_factors == 1, na.rm = TRUE), numerals = FALSE)` the RMSEA $< .08$ criteria suggested evidence for single factor structures.
 
@@
 ### Pre-registration Analysis Justification & Reason for Omission from Article
+
 Follow-up analyses were preregistered for hypothesis 6.
@@
 ### Model
+
 The model was the same as that used for the main test of hypothesis 6 (see formula \@ref(eq:H6Main)), only now QMP_ratio's for each of the five categories were used one at a time for each unique combination of original article and replication protocol QMP.
 
-```{r Hypothesis6Associations}
+```{r Hypothesis6Associations, warning = FALSE}
 ## Associations between the QMP categories
@@
 ### Results
+
 Planned exploratory analyses were preformed to expand on the test for hypothesis 6.
@@
 ```
+
 Table \@ref(tab:H6ExploratoryAssociationsRevisedTable) shows the beta-regression tests for each of the QMP category comparisons.

### 2024-03-19 Scripts/Manuscript/manuscript.Rmd
fixed compiling errors and plot 456 and table 1 look.

@@
 
-appendix:
-  - "Scripts/AppendixScripts/Appendix_pre-reg_analyses.Rmd"
-  - "Scripts/AppendixScripts/Appendix_multilevel_analyses.Rmd"
-  - "Scripts/AppendixScripts/Appendix_omega_analyses.Rmd"
-  - "Scripts/AppendixScripts/Appendix_initial_QMP_analyses.Rmd"
-
 classoption       : "man"
@@
 knit              : worcs::cite_all
-bibliography: references.bib
 ---
@@
 # loading source script
-source(file = "C:/Users/u686785/OneDrive - Tilburg University/Documents/uvt/PHD/Master Thesis to Paper/Reproducible_R_Project/Scripts/source_script.R")
+source(file = "../source_script.R")
 
@@
 Greater score-reliability means greater consistency in estimation as variance around the estimate of the true effect is decreased.
-Consequently measures across different occasions, including between original and replication, should also become more consistent [@nunnaly1994assessment].
+Consequently measures across different occasions, including between original and replication, should also become more consistent [@nunnally1994assessment].
 When original and replication research share consistent result, and as long as the studied effect is true, then on average their statistical conclusions should converge.
@@
 The result was a total sample size of `r nrow(coded_data_replications)` measures used in both original and replication research [^1].
-Table BELOW shows further descriptive information about the data for each Many Labs Project.
+Table \@ref(tab:ManyLabsDescriptivesTable) shows further descriptive information about the data for each Many Labs Project.
 
@@
 
-# Changing column names to be less computer speak-y looking
-colnames(many_labs_descriptives_table) <- c("Many Labs Version", "N ML Projects", "N Primary Measures",
-                                            "Replication Total N", "Replication Total IQR", "Original Total N", 
-                                            "Original Total IQR")
+# Adding column names to the table for readability
+colnames(many_labs_descriptives_table) <- c("ML Version", "N Projects", "N measures$^a$", "Rep. N", "Rep. IQR", "Org. N", "Org. IQR")
+
+### failed table
+# colnames(many_labs_descriptives_table) <- c("Version", "Projects", "Measures", "Total N", "Total IQR", "Total N", "Total IQR")
+
+# c("", "N ML", "N Primary", "Replication", "Replication", "Original", "Original")
+
+# kableExtra::kbl(many_labs_descriptives_table, align = c("l", "r", "r", "r", "r", "r", "r"), escape = FALSE, placement = "htp", row.names = FALSE) %>%
+#   kableExtra::kable_classic( full_width = FALSE) %>%
+#   kableExtra::add_header_above(c("Many Labs" = 1, "N ML" = 1, "N Primary" = 1, "Replication" = 1, "Replication" = 1, "Original" = 1, "Original" = 1), line = FALSE) %>% 
+#   kableExtra::row_spec(4, extra_latex_after = "\\cmidrule(l{3pt}r{3pt}){2-5}")
+
+# midrule wouldn't add ):<
 
@@
 apa_table(
-  many_labs_descriptives_table, align = c("l", "r", "r", "r", "r", "r", "r")
-  , caption = "Descriptive information of number of included projects measures, and their sample size, across many labs projects for both original articles and replication protocols"
-  , escape = FALSE, placement = "htp", midrules = 4)
-
+  many_labs_descriptives_table, align = c("l", "r", "r", "r", "r", "r", "r"), escape = FALSE, placement = "htp", midrules = 4, caption = "General Descriptives of the Many Labs Projects"
+  , note = "$^a$ refers only to the number of identified primary measures, which this study is concerned with. Rep. = Replicaiton, Org. = Original., N = number of, IQR = Interquartile range.")
 ```
@@
 
+```{r  ReorderPlot23Data}
+# data re-ordering (factor order was not saved in export)
+plot_23_data_alpha_reordered <- data_prep_plot_23_alpha(plot_23_data_alpha)
+```
+
 When comparing the reported reliabilities with the calculated reliabilities displayed in figure \@ref(fig:Plot23AlphaCode), all but `r apa_num(sum(plot_23_data_reported_alpha$coefficient_difference > 0), numerals = FALSE)` of the reported reliabilities are in the lower half of the distribution of the calculated reliabilities within their own measure.
-However when looking across the measures, the mean of the distribution of the calculated coefficients of all but `r apa_num(sum(aggregate(plot_23_data_alpha_reordered$alpha, list(plot_23_data_alpha_reordered$g), FUN = mean)[plot_23_data_reported_alpha$article_order,2] <= mean(data_h3_multiple$alpha)), numerals = FALSE)` of the measures that have reported reliability coefficients is larger than the mean calculated Cronbach's alpha.
+However when looking across the measures, the mean of the distribution of the calculated coefficients of all but `r apa_num(sum(aggregate(plot_23_data_alpha_reordered$alpha, list(plot_23_data_alpha_reordered$g), FUN = mean)[plot_23_data_reported_alpha$article_order,2] <= mean(data_h3_multiple$alpha)), numerals = FALSE)` of the measures that had a reported reliability coefficient was larger than the mean calculated Cronbach's alpha.
 
@@
 The Diff column shows the difference between reported reliability and the average reliability calculated from the Many Labs data for the applicable measures, the differences in bold are for reported reliabilities that fell outside the 95% quantile of calculated reliability scores."}
-
-# data re-ordering (was not saved in export)
-plot_23_data_alpha_reordered <- data_prep_plot_23_alpha(plot_23_data_alpha)
 
@@
 In order to visualize the results on QMPs, the proportions of the QMP ratio obtained for each QMP type (see Table \@ref(tab:QMPCodingInfoTable)) are shown across the top layer of Figure \@ref(fig:Plot456Code) for both replication protocols and original articles.
-While in the bottom layer of Figure \@ref(fig:Plot456Code) the overlayed distributions of the total QMP ratios from the replication protocols and original studies are displaued, with dots indicating each datapoint, and the line indicating the mean for either distribution.
+While in the bottom layer of Figure \@ref(fig:Plot456Code) the overlayed distributions of the total QMP ratios from the replication protocols and original studies are displayed, with dots indicating each datapoint, and the line indicating the mean for either distribution.
 A large number of QMP ratios are missing for the QMP modification type , because only `r apa_num(table(coded_data_replications$mod_check)["True"])` out of `r apa_num(length(coded_data_replications$mod_check))` measures in replications, and only `r apa_num(table(coded_data_original_shortened$mod_check)["True"], numerals = FALSE)` measures used in original studies were modified.
@@
 The specific observed values are indicated along the bottom row with dots"}
+
 # re-ordering the QMP-types, because it didn't save
@@
 
+# shortening the replication and original labels for nicer plot 1
+levels(plot_456_data$RepOrg) <- c("Org.", "Rep.")
+
 ### ratio (REV) Original and Rep
+# QMP type specific QMP ratios
 Plot_456_1 <- ggplot(plot_456_data[plot_456_data$QMP_type != "Total",], 
@@
   theme_minimal() +
-  scale_fill_manual(values = c("#ff766c", "#ef6f65", "#ce5f57", "#be5851", "#aa4f48", "#994741", "#803b36", "#672f2b", "#562824", "#411e1b", "#341816", "#030101","#4366ff", "#4265fc", "#3551cb", "#324dc1", "#324cbe", "#2d44aa", "#2c44a9", "#283d99", "#223380", "#162255", "#10193e", "#010206", "#000102")) +
-  theme(legend.position = "none") +
+  scale_fill_manual(values = c("#ff766c", "#ef6f65", "#ce5f57", "#be5851", "#aa4f48", "#994741", "#803b36", "#672f2b", "#562824", "#411e1b", "#341816", "#030101","#4366ff", "#4265fc", "#3551cb", "#324dc1", "#324cbe", "#2d44aa", "#2c44a9", "#283d99", "#223380", "#162255", "#10193e", "#010206", "#000102")) + # gradient for the colors was found by changing the brightness of the colour in a hsl color editor (in GIMP) to be equal to the inverse of the QMP ratio value.
   facet_grid(~ QMP_type) + 
+  theme(legend.position = "none", strip.text = element_text(size = 7)) +
   ylab("Relative Prevalence of\nQMP Ratio in Sample") +
@@
 
+# changing the replication and original labels back for plot 2
+levels(plot_456_data$RepOrg) <- c("Original", "Replication")
+
+# calculating mean total QMP ratios
 Mean_Rat_Rep <- mean(plot_456_data$QMP_ratio_REV[
@@
 
+# total QMP ratios
 Plot_456_2 <- ggplot(plot_456_data[plot_456_data$QMP_type == "Total",], 
@@
 
-# combine both plots into one figure
+## the following two plots are constructed solely for the purpose of extracting
+# a legend from them.
+for_legend_plot_456_org <- ggplot(plot_456_data[plot_456_data$QMP_type != "Total",], 
+                                  aes(x = RepOrg, y = abs(QMP_ratio_REV - 1), fill = abs(QMP_ratio_REV - 1))) + 
+  geom_bar(stat = "identity") +
+  theme_minimal() +
+  scale_fill_gradient(name = "Original", low = "#030101", high = "#ff766c", limits = c(0, 1), 
+                      breaks = c(0.001, 0.5, 0.999), labels = c(1, 0.5, 0)) +
+  theme(legend.title=element_text(size = 9)) + 
+  facet_grid(~ QMP_type)
+
+for_legend_plot_456_rep <- ggplot(plot_456_data[plot_456_data$QMP_type != "Total",], 
+                                  aes(x = RepOrg, y = abs(QMP_ratio_REV - 1), fill = abs(QMP_ratio_REV - 1))) + 
+  geom_bar(stat = "identity") +
+  theme_minimal() +
+  scale_fill_gradient(name = "Replication", low = "#000102", high = "#4366ff", limits = c(0, 1), 
+                      breaks = c(0.001, 0.5, 0.999), labels = c(1, 0.5, 0)) +
+  theme(legend.title=element_text(size = 9)) + 
+  facet_grid(~ QMP_type)
+
+# extracting the legends from the plot
+legend_456_org <- get_legend(for_legend_plot_456_org) 
+legend_456_rep <- get_legend(for_legend_plot_456_rep)
+
+# combining both plots and the legends into one figure
 grid.arrange(Plot_456_1, 
              Plot_456_2, 
-             nrow = 2)
+             legend_456_org,
+             legend_456_rep,
+             layout_matrix = rbind(c(1, 3, 4),
+                                    c(2, 2, 2)),
+              widths = c(8, 1, 1))
 
@@
 This is illustrated in our sample by the fact that reliability coefficients were reported in too small quantity to conduct the planned analysis for hypothesis 1, and because of the `r nrow(coded_data_replications)` measures only `r sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")` measures in original articles and `r sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")` in replication protocol reported any validity evidence.
-Thus, reliability and validity evidence was underreported in our sample similarly to the findings of @shaw2020measurement, @flake2017construct & @flake2022construct, a problem that has also been addressed in earlier literature on this topic [@vacha1999practices; @green2011recent].
+Thus, reliability and validity evidence was underreported in our sample similarly to the findings of @shaw2020measurement, @flake2017construct, and @flake2022construct, a problem that has also been addressed in earlier literature on this topic [@vacha1999practices; @green2011recent].
 
@@
 :::
+
+\newpage
+
+# (APPENDIX) Appendix {-}
+
+```{r child = "AppendixScripts/Appendix_pre-reg_analyses.Rmd"}
+```
+
+```{r child = "AppendixScripts/Appendix_multilevel_analyses.Rmd"}
+```
+
+```{r child = "AppendixScripts/Appendix_omega_analyses.Rmd"}
+```
+
+```{r child = "AppendixScripts/Appendix_initial_QMP_analyses.Rmd"}
+```

### 2024-03-19 Scripts/source_script.R

@@ -1137,6 +1137,17 @@ data_prep_plot_456 <- function(Data){
 }
 
 
+
+### Function to extract legend from plot for plot 456
+get_legend <- function(a_plot){ 
+  tmp <- ggplot_gtable(ggplot_build(a_plot)) 
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box") 
+  legend <- tmp$grobs[[leg]] 
+  legend
+} 
+
+
+
 ### 46 plots data prep
 data_prep_plot_46 <- function(Data){
   colnames(Data) <- c("Def.Ratio", "Op.Ratio", "Sel.Ratio", 

### 2024-03-25 Scripts/Manuscript/AppendixScripts/Appendix_initial_QMP_analyses.rmd
adjusted appendices and Discussion section.

@@
 
-### Explanation Why
+### Explanation
 The data was initially coded using to the preregistered coding protocol.
@@
   theme(axis.text.y=element_blank(),
-        axis.ticks.y=element_blank()) +
+        axis.ticks.y=element_blank(),
+        axis.text.x = element_text(size = 7)) +
   scale_fill_manual(values=c("brown", "blue4")) +
@@
 
-Similarly to the results of the multilevel sensitivity model testing hypothesis 5 using QMP ratios obtained with the revised coding protocol, he relationship in the multilevel model was not significant for QMP ratios obtained with the initial coding protocol (`r check_h6$full_result$QMP`).
+Similarly to the results of the multilevel sensitivity model testing hypothesis 5 using QMP ratios obtained with the revised coding protocol, the relationship in the multilevel model was not significant for QMP ratios obtained with the initial coding protocol (`r check_h6$full_result$QMP`).

### 2024-03-25 Scripts/Manuscript/AppendixScripts/Appendix_multilevel_analyses.rmd
adjusted appendices and Discussion section.

@@
 This appendix contains the multilevel model versions of the models used to test Hypothesis 3, 5, & 6.
-These models were excluded from the published article for the sake of brevity, and because the sample size was no large enough to support multilevel modelling in most cases.
+These models were excluded from the published article for the sake of brevity, and because the sample size was not large enough to support multilevel modelling in most cases.
 
@@
 
-## Model
+### Model
 The specific models used were a multilevel logistic regression random intercept and random slope model.
@@
 ### Results
-The results of these analyses can be seen in the table below
+The results of these analyses can be seen in the table below.
+In none of these models is the relation between reliability and replication success significant (random intercept: `r H3_test_result_int_sensitivity_alpha$full_result$alpha`; random slope: `r H3_test_result_slp_sensitivity_alpha$full_result$alpha`).
+This corroborates the findings in the article, only now using a random intercept multilevel model.
+However, also similarly to the results in the article and perhaps even more so for the multilevel model, the small sample size for these tests means that caution should be taken in interpreting these results.
 
@@
   , caption = "Model Results from Tests of Hypothesis 3"
-  , note = "The random slope model for Cronbach's alpha did not converge, thus it results are not shown here."
+  , note = "The random slope model for Cronbach's alpha did not converge, thus its results are not shown here."
   , escape = FALSE, placement= "htp", midrules = 1)
@@
 ```
-
-In none of these models is the relation between reliability and replication success significant (random intercept: `r H3_test_result_int_sensitivity_alpha$full_result$alpha`; random slope: `r H3_test_result_slp_sensitivity_alpha$full_result$alpha`).
-This corroborates the findings in the article, only now using a random intercept and random slope multilevel model.
-However, also similarly to the results in the article and perhaps even more so for these multilevel models, the small sample size for these tests means that caution should be taken in interpreting these results.
 
@@
 For hypothesis 6, the sensitivity analyses using a random intercept logistic multilevel model resulted in non-significant results, which is contrary to the results found with the main test and is not in line with hypothesis 6 (revised protocol: `r check_h6_REV$full_result$QMP_REV`).
-This result puts some dents in the confidence that can be attached to the results found through the main test reported in the article.
+This result places some doubt in the results found through the main test reported in the article.

### 2024-03-25 Scripts/Manuscript/AppendixScripts/Appendix_omega_analyses.rmd
adjusted appendices and Discussion section.

@@
 
-This appendix contains all results based on calculated reliabilities only using the omega coefficient as the coefficient of choice instead of the alpha coefficient.
+This appendix contains all results based on calculated reliabilities using the omega coefficient as the coefficient of choice instead of the alpha coefficient.
 
@@
 ### Results + Comparison Interpretation
-For omega the mean (values calculated in the population across replication sets) was `r apa_num(mean(data_h3_multiple$omega), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`.
+For omega the mean (values calculated in the population across replication sets) was `r apa_num(mean(data_h3_multiple$omega, na.rm = TRUE), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`.
 
@@
 The figure below shows additional information on the distributions of the calculated omega scores and their relation to replication success.
-It mostly resembles Figure \@ref(fig:Plot23AlphaCode) from the article, with some studies being omitted as the omega coefficient function did not converge or run properly for those results.
+It mostly resembles Figure \@ref(fig:Plot23AlphaCode) from the article, with some studies being omitted as the omega coefficient function did not converge or run properly on those data.
+Furthermore, information with regard to heterogeneity was not present since the standard error of omega was not known, and comparisons between reported coefficients were omitted, since no article reported any omega coefficients.
 

### 2024-03-25 Scripts/Manuscript/AppendixScripts/Appendix_pre-reg_analyses.Rmd
adjusted appendices and Discussion section.

@@
 
-This appendix contains all of the pre-registered analyses that were either changed or omitted from the article.
-
-## Test for H5 as Beta-Regression
-
-### Explanation Change
-
-This analysis was the originally planned analysis to test Hypothesis 5.
-However, for the sake of interpretation this test was changed to have the Independent Variable (IV) and Dependent Variable (DV) swapped in the article, and as a result it became a logistic regression.
-
-### Model
-
-The originally planned analysis made use of beta-regression similarly to the test for H4 and H6.
-The variables are the same as those used in the test published in the article, just swapped from IV to DV, and from DV to IV.
-
-```{=tex}
-\begin{equation}
-g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replicated_{i} (\#eq:H5AppendixA)
-\end{equation}
-```
-Where $g(.)$ refers to the same link function as described in formula \@ref(eq:BetaLink) in the article.
-
-```{r H5 beta-regression pre-registration model}
-## Hypothesis 5 beta regression model ADD FIRST PART TO INITIAL PROTOCOL RESULTS
-H5_prereg_test_results <- betareg(QMP_ratio ~ hypothesis_support, data = data_h5)
-H5_prereg_test_results_with_OR <- OR_to_apa_full_supplier(betareg_output_to_apa_full(H5_prereg_test_results), negative_b = TRUE)
-
-H5_prereg_test_results_REV <- betareg(QMP_REV_ratio ~ hypothesis_support, data = data_h5)
-H5_prereg_test_results_REV_with_OR <- OR_to_apa_full_supplier(betareg_output_to_apa_full(H5_prereg_test_results_REV))
-```
-
-## Results
-
-With this model specification the relationship between the two variables remains negative and significant (`r H5_prereg_test_results_REV_with_OR`).
+This appendix contains the pre-registered analyses that were either changed or omitted from the article.
 
@@
 
-This analysis was omitted from the main article due to the fact that determining when a measure should be unidimensional would require an in-depth review and expert evaluation for the literature surrounding the measure, which is outside of the scope of this article and the authors' expertise (it additionally may not always be available).
+This analysis was omitted from the main article due to the fact that determining when a measure should be unidimensional would require an in-depth review and expert evaluation for the literature surrounding the measure, which is outside of the scope of this article and the authors' expertise.
+Additionally, this information may also simply not be available, further complicating the analyses.
 
 For the sake of this analysis the simple heuristic was chosen that if the measure was used as a single composite variable in the analyses, then it should be uni-dimensional.
-This is similar to what was done by ..., but for the sake of this article it was deemed to strong an assumption to make that this heuristic would always hold.
+This is somewhat similar to what was done by @shaw2020measurement, but for the sake of this article it was deemed to strong an assumption to make that this heuristic would always hold.
 For instance, IQ score is often used as a single indicator score, however the construct of IQ is not considered unidimensional, and is instead understood to have many sub-dimensions (e.g.
 verbal comprehension, perceptual reasoning, etc.).
-As a result, the use of a single score in the analyses cannot be taken as evidence that the construct is considered unidimensional by the authors, or broader literature on the topic.
+As a result, the use of a single score in the analyses cannot be taken as evidence that the construct is considered unidimensional by neither the authors, nor the broader literature on the topic.
 
-Nevertheless, we present here the result of the analyses made under the assumption that the one score, one dimension heuristic holds, for those researchers that believe this heuristic to not undermine the relevance of these results in provding some valid information on the validity of the measures used in the Many Labs projects.
+Nevertheless, we present here the result of the analyses made under the assumpti on that the one score, one dimension heuristic holds, for the readers that are comfortable with this heuristic.
 
-## models
+## Model
 
@@
 Sufficient fit of the unidimensional model was found for `r apa_num(sum(cfa_results$Single_factor == "Yes", na.rm = TRUE), numerals = FALSE)` out of the `r apa_num(nrow(cfa_results), numerals = FALSE)` evaluated measures.
-However, as shown in Table \@ref(tab:UnidimesnionalityTestResultsTable) the unidimensional model held based on the parallel analysis test alone, for only `r apa_num(sum(cfa_results$N_factors == 1, na.rm = TRUE), numerals = FALSE)` of the `r apa_num(nrow(cfa_results), numerals = FALSE)` measures.
+However, as shown in Table \@ref(tab:UnidimesnionalityTestResultsTable), based on the parallel analysis test alone the unidimensional model held for only `r apa_num(sum(cfa_results$N_factors == 1, na.rm = TRUE), numerals = FALSE)` of the `r apa_num(nrow(cfa_results), numerals = FALSE)` measures.
 For those `r apa_num(sum(cfa_results$N_factors == 1, na.rm = TRUE), numerals = FALSE)` measures and an additional `r apa_num(sum(cfa_results$RMSEA < .08, na.rm = TRUE) - sum(cfa_results$N_factors == 1, na.rm = TRUE), numerals = FALSE)` the RMSEA $< .08$ criteria suggested evidence for single factor structures.
@@
 For example, IQ is often used as a singular indicator, even though it consists of several factors [@weiss2013wisc].
-However, it should be noted that at least with respect to Many Labs 2, all of the measures that were considered unidimensional for the analyses in this study were also considered unidimensional in the investigation by @shaw2020measurement} who also observed a lack of unidimensionality evidence in their investigation of Many Labs 2.
+However, it should be noted that at least with respect to Many Labs 2, all of the measures that were considered unidimensional for the analyses in this study were also considered unidimensional in the investigation by @shaw2020measurement who also observed a lack of unidimensionality evidence in their investigation of Many Labs 2.
 To conclude, there is an indication that validity evidence for measures used in replication research is lacking, and that this may have further implications beyond the measures for which it could be assessed here.
@@
 The goal of these analyses was to see if there are any type specific carry-over effects in QMPs between original and replication.
-Due to the large number of tests, the focus was exploratory using visualisation rather than inference.
+Due to the large number of tests, the focus was exploratory using visualization rather than inference.
 
 It is partly this large number of tests, as well as the resulting lack of clear interpretability in the results that caused this analysis to be omitted from the main article.
-However, for completeness and transparency sake it is reported here.
+However, for completeness and transparency it is reported here.
 
@@
 
-The model was the same as that used for the main test of hypothesis 6 (see formula \@ref(eq:H6Main)), only now QMP_ratio's for each of the five categories were used one at a time for each unique combination of original article and replication protocol QMP.
+The model was the same as that used for the main test of hypothesis 6 (see formula \@ref(eq:H6Main)), only now QMP ratios for each of the five categories were used one at a time for each unique combination of original article and replication protocol QMP.
 
@@
 Figure \@ref(fig:Plot46RevisedDataCode) visually illustrates the relations of the revised QMP ratios from different QMP types between replication protocols and original articles.
-As shown in the figure, no relation was strong and highly stable, and even fewer were consistent between initial and revised coding protocols.
+As shown in the figure, no relation was strong nor highly stable, and few were consistent between initial and revised coding protocols.
 
@@
 A possible explanation for these results could be that original articles have to provide a clear definition as well as details on the scale, in order for a replication to be able to justify selecting the measure.
-A replication may also be in general more dependent on the original article for information on the definition of the constructs and the choice of measurement, compared to a description of the Operationalisation, quantification, and any modifications.
+A replication may also be in general more dependent on the original article for information on the definition of the constructs and the choice of measurement, compared to a description of the operationalisation, quantification, and any modifications.
 These former are features of a measurement, which while preferably similar in a replication to the original, can and should be reported in the replication protocol even if the original article does not contain the details on these features itself.

### 2024-03-25 Scripts/Manuscript/manuscript.Rmd
adjusted appendices and Discussion section.

@@
 
-  Enter author note here. Caspar/Jelte/Marjan?
+  Enter author note here. Jelte/Marjan?
 
@@
   In particular, studies have indicated that low reliability, and poor measurement reporting can negatively influence the replicability of an effect. 
-  Building on this new line of research, this study assessed these influences in large scale replication projects. 
-  Protocols from the Many Labs replication projects, and the original articles that the replications were based on were used to assess the  reporting of the measures, while publicly available data from the Many Labs replications was used to assess the reliability of the measures.
-Reliability did not relate to replicability, and was generally consistent between labs for each measure in the Many Labs projects.
-  The quality of measurement reporting in replication protocols did however relate to replicability.
-  Additionally, tentative evidence was found for a relation between quality of measurement reporting in the protocol of a replication and the quality of measurement reporting in its related original study.
-  Recommendations are given for researchers and replicators in order to improve measurement practices in replication, and ward its negative impact on replicability. 
-  Additionally, directions are given for future research investigating the relationship between measurement issues and replicability.
+  Building on this new line of research, this study assessed the influences of poor measurement reporting in replications from the Many Labs replication projects, and the original articles that the replications were based on, while publicly available data from the Many Labs replications was used to assess the reliability of the measures.
+  Here we show that while contrary to expectations reliability did not relate to replicability, the quality of measurement reporting in replications did relate. 
+  For original articles the quality was indirectly related to replicability through the quality of measurement reporting in replications.
+  These and other descriptive results indicate similarly to previous research that measurement details in both original research and replications are underreported.
+  However, some of the issues in measurement reporting that were identified as most critical in this study differ from what has been stated in previous research.
+  Measurement is a crucial part of almost all empirical research, it's details should tehrefore be transparently reported to enable critical evaluation and independent replication.
+  Consequently, recommendations are given to researchers and replicators on the measurement practices that are  most crucial to improve on.. 
+  Finally, directions are given for future research to further investigate the (causal) relationship between measurement practices and replicability.
 
 keywords          : "reliability, measurement, measurement reporting, replicability, construct validity"
-wordcount         : "194"
+wordcount         : "234"
 
@@
 
-\renewcommand{\topfraction}{.85}
+\renewcommand{\topfraction}{.8}
 
@@
 
-\renewcommand{\bottomfraction}{.7}
+\renewcommand{\bottomfraction}{.8}
 
@@
 
-\renewcommand{\floatpagefraction}{.66}
-
-<!-- min fraction of page that should have floats -->
+\renewcommand{\floatpagefraction}{.8}
+
+<!-- min fraction of page that should have floats .66 -->
 
@@
 They found however, that in many instances the results did no match those of the original studies.
-This lack of replicability of psychological findings illustrated that psychology was facing a so-called 'replication crisis' [@hughes2018psychology; @giner2019crisis].
+This lack of replicability of psychological findings led to the claim that psychology was facing a 'replication crisis' [@hughes2018psychology; @giner2019crisis].
 
@@
 Several explanations for this discrepancy between original and replication findings have been suggested and investigated, with many being centred around the concept of Questionable Research Practices [QRPs, @john2012measuring].
-QRPs are practices, which either misrepresent or omit essential methodological information that is necessary for the evaluation of the research.
+QRPs are practices, which either misrepresent or omit essential methodological information that is needed to evaluate the research.
 Without this information, a reader will not know whether the result was in line with the author's expectation or simply the result of repeated trial and error until a suitable result was found [@simmons2011false].
@@
 Another factor which has gained more traction recently are measurement related issues' impact on replicability.
-In particular, studies have focused on the effects of issues such as measurement error and questionable measurement practices on replicability [@stanley2014expectations; @shaw2020measurement; @flake2017construct; @flake2020measurement].
+In particular, studies shown that measurement error and questionable measurement practices may impact replicability [@stanley2014expectations; @shaw2020measurement; @flake2017construct; @flake2020measurement].
 
@@
 Even when ignoring reliability, a measurement's content and implementation still need to validly capture what it intends to measure.
-Questionable Measurement Practices (QMPs) are practices that decrease the information that is necessary to evaluate a measurement's validity, and have been coined as a conjugate term to QRPs.
+Questionable Measurement Practices (QMPs) are practices that decrease the availability of information needed to evaluate a measurement's validity, and have been coined as a conjugate term to QRPs.
 They range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of measure and procedure of any sourced measures [@flake2020measurement].
@@
 One goal is to expand the research by [@stanley2014expectations] with a practical example.
-Whereas they obtained their findings using a simulation study, this study investigated the scope of their findings in practice.
+Whereas they obtained their findings using a simulation study, this study investigated the scope of their findings on data from real replications.
 QMPs in the context of replication research were already investigated by [@flake2022construct].
 However, the investigations remained mostly descriptive.
-This study additionally aims to expand upon the findings of [@flake2022construct] through the use of a new set of replication data, and by exploratively investigating the relation between QMP and replicability.
+This study additionally aims to expand upon the findings of [@flake2022construct] through the use of a new set of replication data, and by exploratively investigating the relation between QMPs and replicability.
 
@@
 This concern even prompted a Many Labs centered around the testing of heterogeneity in replications [@klein2018many].
-However analyses from Many Labs 2, and @olsson2020heterogeneity showed little empirical evidence for widespread heterogeneity in effects among replications.
+However analyses from this Many Labs, and @olsson2020heterogeneity showed little empirical evidence for widespread heterogeneity in effects among replications.
 These findings demonstrate that it is possible to reduce variability as the result of context using structured protocols, as was done in the Many Labs projects this study analyzed.
@@
 Any scientific report should therefore clearly motivate the use of measure and procedure.
-Without clear reporting on these aspects, the validity of measurement will remain uncertain.
+When these aspects are not clearly reported on, the validity of measurement remains uncertain.
 Therefore, the other tests of this paper focused on the reporting aspects of measurement, assessed through QMPs.
@@
 Acquiescence bias checks, manipulation checks, measures used for pilot testing, and measures added for exploratory analyses in replication studies were not included.
-The result was a total sample size of `r nrow(coded_data_replications)` measures used in both original and replication research [^1].
+The result was a total sample size of `r nrow(coded_data_replications)` measures used in both original and replication research[^1].
 Table \@ref(tab:ManyLabsDescriptivesTable) shows further descriptive information about the data for each Many Labs Project.
@@
   many_labs_descriptives_table, align = c("l", "r", "r", "r", "r", "r", "r"), escape = FALSE, placement = "htp", midrules = 4, caption = "General Descriptives of the Many Labs Projects"
-  , note = "$^a$ refers only to the number of identified primary measures, which this study is concerned with. Rep. = Replicaiton, Org. = Original., N = number of, IQR = Interquartile range.")
+  , note = "$^a$ refers only to the number of identified primary measures, which this study is concerned with. Rep. = Replicaiton, Org. = Original., N = total number of, IQR = Interquartile range.")
 ```
@@
 ```{r QMPCodingInfoTable, warning = FALSE}
-QMP_info_dataframe <-data.frame(Category = c("Definition", "", "", "Operationalisation", "", "", "", "Selection/Creation", "", "", "Quantification", "Modification", "", "", "", "", ""),
+QMP_info_dataframe <- data.frame(Category = c("Definition", "", "", "Operationalisation", "", "", "", "Selection/Creation", "", "", "Quantification", "Modification", "", "", "", "", ""),
            'N Questions' = c("1", "", "", "5", "", "", "", "4", "", "", "4", "6", "", "", "", "", ""),
@@
 
+# making the column names look less robot speak-y.
+colnames(QMP_info_dataframe) <- c("CategorWy", "N Questions", "Example Question")
+
 # transfer the data to an APA table for printing
@@
   , caption = "Information of QMP coding variables per category."
-  , note = "N Questions refers only to the questions considered quantative as specified in the text below."
+  , note = "N Questions refers only to the questions considered used for calculating QMP ratios."
   , escape = FALSE, placement= "htp", booktabs = TRUE)
@@
 Beside these quantitative variables, a total of four qualitative variables were also included to provide more detailed information on some aspects of the measure and its reporting.
-Details on the items used, their origin, changes, and justifications can be found in the coding protocol information supplementary materials.
+Further details on all the items used, their origin, changes, and justifications can be found in the coding protocol information supplementary materials.
 
@@
 \begin{equation}
-QMP_ratio_{j} = \frac{\sum_{n=1}^i True_{ij}}{\sum_{n=1}^i True_{ij} + False_{ij}} (\#eq:QMPRatioType)
+QMP\_ratio_{j} = \frac{\sum_{n=1}^i True_{ij}}{\sum_{n=1}^i True_{ij} + False_{ij}} (\#eq:QMPRatioType)
 \end{equation}
@@
 \begin{equation}
-QMP_ratio = \frac{\sum_{n=1}^j \sum_{n=1}^i True_{ij}}{\sum_{n=1}^j \sum_{n=1}^i True_{ij} + False_{ij}} (\#eq:QMPRatioTotal)
+QMP\_ratio = \frac{\sum_{n=1}^j \sum_{n=1}^i True_{ij}}{\sum_{n=1}^j \sum_{n=1}^i True_{ij} + False_{ij}} (\#eq:QMPRatioTotal)
 \end{equation}
@@
 
-After the data was initially coded according to the preregistered coding protocol, it was determined, based on discussion with the supervisor, that some of the initial ratings were possibly to stringent.
+After the data was initially coded according to the preregistered coding protocol, it was determined, based on discussion with the supervisor, that some of the initial ratings were possibly too stringent.
 As a result, some of the items in the protocol were reformulated, so that the conclusions from the resulting analyses were based on a more lenient judgement of QMPs.
@@
 In all cases, meta-analytic significance of an effect meant that support in the direction of the original effect was found.
-
-## Analyses
-
-Every hypothesis test in this study used an alpha significance cutoff of .05.
-No correction for multiple testing was applied, to ensure that the rate of false negatives remained low, the increase in false positive rate was accepted as they deemed less harmful to the exploratory aims of this study.
 
@@
 
+## Analyses
+
+Every hypothesis test in this study used an alpha significance cutoff of .05.
+No correction for multiple testing was applied, to ensure that the rate of false negatives remained low, the increase in false positive rate was accepted as less harmful to the exploratory aims of this study.
+
 ### Analyses Measurement Error
@@
 
-After the pre-registration was registered, and data had been collected and analysed, it came to the author's attention that it is possible to conduct meta-analyses on reliability coefficients, commonly referred to as Reliability Generalization Meta-Analyses [@botella2012ManagingHeterogeneityVariance; @lopez-ibanez2024ReliabilityGeneralizationMetaanalysis].
+After data had been collected and analysed, it came to the author's attention a meta-analyses could be conducted on reliability coefficients, commonly referred to as Reliability Generalization Meta-Analyses [@botella2012ManagingHeterogeneityVariance; @lopez-ibanez2024ReliabilityGeneralizationMetaanalysis].
 Using meta-analysis, it is possible to quantify within the model the degree of true variation in the metric of interest across samples [@cooper2019handbook].
-Subsequently, the true variation in the metric, or heterogeneity, can be tested to constitute a significant part of the total variation in the observed estimates of the metric or not.
-
-Because heterogeneity estimates line up well as a test for hypothesis 2, a random-effects meta-analysis was conducted on the calculated Cronbach's alpha for each measure for which replication datasets were available and usable.
+
+In order to test whether or not the true variation in the metric, or heterogeneity, constituted a significant part of the total variation in the observed estimates of the metric or not, a random-effects meta-analysis was conducted on the calculated Cronbach's alpha for each measure for which replication datasets were available and usable.
 The rma function from metafor package [@R-metafor] was used to run the meta-analysis.
-No correction for bias or weighting of the effects has been implemented, to reduce model complexity, and because the data came from Many Labs replication projects and not typical literature.
+No correction for bias or weighting of the effects was implemented, to reduce model complexity, and because the data from the Many Labs replication projects do not reflect a typical literature.
 
 A meta-analysis requires an estimate of the standard error in order to be conducted.
-For Cronbach's alpha, formulas 2 & 3 from @duhachek2004AlphaStandardError was used to calculate alpha's standard error.
+For Cronbach's alpha, formulas 2 & 3 from @duhachek2004AlphaStandardError were used to calculate alpha's standard error.
 Heterogeneity was estimated using the tau value, meaning the standard deviation of the distribution of true Cronbach's alpha coefficients for that measure, and tested using the Cochran's Q test for each measure.
@@
 Where $replication_{i}$ is a dummy coded variable, which was coded as 1 in case the reported QMP ratio belonged to a replications, and 0 if it belonged to an original study.
-For hypothesis 5 the QMP ratio was used as the predictor for replication success, while replication success was used as the outcome[^4].
-
-[^4]: This analysis was changed from the pre-registered analysis.
-In the pre-registered analysis a beta-regression was used to model the same relation, only with replication success as the predictor variables and replication QMP ratio as the outcome.
-The outcome was swapped in the article for the sake of interpretability.
-The results based on the original analyses are presented in Appendix A.
+For hypothesis 5 the QMP ratio was used as the predictor for replication success, while replication success was used as the outcome.
 
@@
 The outcome variable is the same as the predictor in the model for hypothesis 5.
-The independent variable in this model is instead the QMP ratio for the original articles.
+The independent variable in this model is instead the QMP ratio for the original articles[^4].
 The resulting model formula is as follows:
+
+[^4]: This analysis was not pre-registered.
+Only the analyses for each combination of QMP types were pre-registered and can be found in appendix A, however all analyses of hypothesis 6 were originally planned to use contingency tables with no inferential test.
+This was changed quickly after the study was pre-registered to using beta-regression as is done here and in appendix A.
 
@@
 Additionally, the number of coded and extracted data is quite substantial.
-Therefore, the result section will start with a number of visuals and descriptives to provide some clarity on the data and its characteristics.
+Therefore, the result section will start with a number of descriptives and figures to provide an overview of the data.
 
@@
 
-Despite the lack of reliability reporting,if scalar data could be accessed for a measure the reliability could be calculated for each lab it was used in.
+If scalar data could be accessed for a measure, the reliability could also be calculated from the replication data for each lab.
 The distributions of the Cronbach's alpha coefficients for each replication set are displayed in figure \@ref(fig:Plot23AlphaCode), separated by successful and unsuccessful replication.
@@
 The blue triangles indicate the reported alpha coefficient for that measure from the original article, when available.
-The Tau column besides the figure shows the tau heterogeneity estimate based on a meta-analysis of the calculated reliabilities for each measure, meta-analysis for which the Q-test for Heterogeneity was signicant at alpha < .05 are in black, not significant results are left grey.
+The Tau column besides the figure shows the tau heterogeneity estimate based on a meta-analysis of the calculated reliabilities for each measure.
+Meta-analyses for which the Q-test for heterogeneity was signicant at alpha < .05 are in black, not significant results are left grey.
 The Diff column shows the difference between reported reliability and the average reliability calculated from the Many Labs data for the applicable measures, the differences in bold are for reported reliabilities that fell outside the 95% quantile of calculated reliability scores."}
@@
 While in the bottom layer of Figure \@ref(fig:Plot456Code) the overlayed distributions of the total QMP ratios from the replication protocols and original studies are displayed, with dots indicating each datapoint, and the line indicating the mean for either distribution.
-A large number of QMP ratios are missing for the QMP modification type , because only `r apa_num(table(coded_data_replications$mod_check)["True"])` out of `r apa_num(length(coded_data_replications$mod_check))` measures in replications, and only `r apa_num(table(coded_data_original_shortened$mod_check)["True"], numerals = FALSE)` measures used in original studies were modified.
+A large number of QMP ratios are missing for the QMP modification type , because only `r apa_num(table(coded_data_replications$mod_check_REV)["True"])` out of `r apa_num(nrow(coded_data_replications))` measures in replications, and only `r apa_num(table(coded_data_original_shortened$mod_check_REV)["True"], numerals = FALSE)` measures used in original studies were modified.
 
 ```{r Plot456Code, warning = FALSE, fig.cap = "QMP ratio counts for each QMP Type and QMP total ratio distribution grouped by whether the QMP ratio was obtained from an original article or a replication protocol.
-The top row shows for each QMP type the proportions of each QMP ratio obtained, darker colours represent proportionally more QMPS, grey means modification did not occur for that measure.
+The top row shows for each QMP type the proportions of each QMP ratio obtained, darker colours represent proportionally more QMPs, grey means modification did not occur for that measure.
 The bottom graph shows the distributions of total QMP ratios for both replication protocols and original articles, with the line indicating the mean QMP ratio.
@@
   theme(axis.text.y=element_blank(),
-        axis.ticks.y=element_blank()) +
+        axis.ticks.y=element_blank(),
+        axis.text.x = element_text(size = 8)) +
   scale_fill_manual(values=c("brown", "blue4")) +
@@
 Table \@ref(tab:MeasurementReportingDescriptivesTable) shows additional descriptive information on measurement reporting based on counts of reported information that were not used to calculate QMP ratios.
-When it was not stated that existing materials were used, it was expected that the remaining articles would clearly specify that they newly created the materials, however this was not always the case for neither original articles (`r table(coded_data_original_shortened$sel_existing)[["False, materials were newly developped for this study"]]` out of `r nrow(coded_data_original_shortened) - table(coded_data_original_shortened$sel_existing)[["True, namely:"]]` relevant measures) nor replication protocols (`r table(coded_data_original_shortened$sel_existing)[["False, materials were newly developped for this study"]]` out of `rnrow(coded_data_replications) - table(coded_data_replications$sel_existing)[["True, namely:"]]` relevant measures).
+When it was not stated that existing materials were used, it was expected that the remaining articles would clearly specify that they newly created the materials, however this was not always the case for neither original articles (`r table(coded_data_original_shortened$sel_existing)[["False, materials were newly developped for this study"]]` out of `r nrow(coded_data_original_shortened) - table(coded_data_original_shortened$sel_existing)[["True, namely:"]]` relevant measures) nor replication protocols (`r table(coded_data_replications$sel_existing)[["False, materials were newly developped for this study"]]` out of `r nrow(coded_data_replications) - table(coded_data_replications$sel_existing)[["True, namely:"]]` relevant measures).
 
@@
 The ICC of the between-group (across different replication set) variance and within-group (lab locations within a replication set) variance in the Cronbach's alpha coefficient was approximately `r apa_num(ICC_alpha, digits = 3)`.
-Because this number is larger than .5, it suggests that variance was larger between replication sets than within.
+Because this number is larger than .5, it suggests that the majority of the total variance in the calculated Cronbach's alpha was between replication sets rather than within.
 
@@
 However, since the Q-test is sensitive to the number of studies in the meta-analyses [@li2015DilemmaHeterogeneityTests], some of the discrepancy in the estimate of heterogeneity based on this test may in part be due to the fact that for some measures the sample size of labs that used them was too low.
-Therefore, while consistent evidence for heterogeneity would imply true variance in Cronbach's alpha within replication sets would run counter to hypothesis 2, the evidence id inconsistent when looking across all studies, and remains sensitive to the sample size in the meta-analyses.
+Therefore, while consistent evidence for heterogeneity would imply true variance in Cronbach's alpha within replication sets would run counter to hypothesis 2, the evidence is inconsistent when looking across all studies, and remains sensitive to the sample size in the meta-analyses.
 
@@
 The logistic model indicated that Cronbach's alpha did not significantly relate to replication success in the main logistic regression model (Cronbach's alpha: `r H3_main_full_results_alpha_with_OR`).
-Similar results were found based on the calculated omega coefficient (see Appendix C) and in all of the multilevel sensitivity analyses models (see Appendix D).
+Similar results were found based on the calculated omega coefficient (see Appendix C) and in all of the multilevel sensitivity analyses models (see Appendix B).
 These results are contradictory to the expectation in hypothesis 3.
@@
 These measurement related concepts were then linked to replicability in order to investigate them as potential causes inhibiting successful replications.
-The results of the tests for the hypotheses were often underpowered, especially the tests of hypotheses 2 & 3 for which only `r nrow(data_h3_avg)` measures were available to calculate reliability from.
-Additionally, most tests showed mixed results.
-However, when including exploratory and descriptive analyses, a clearer picture on measurement in replication and original research emerges.
+The tests for the hypotheses were often underpowered.
+Additionally, some tests showed mixed results.
+However, when including exploratory and descriptive analyses, a clearer picture on measurement usage and quality in original and replication research emerges.
 
@@
 This study assessed the quality of measurement and measurement reporting in original and replication research by investigating the quality of measurement in the Many Labs projects, and the original articles they attempted to replicate.
-Findings were in line with similar investigations in the literature by @shaw2020measurement & @flake2022construct.
-These two studies found that validity evidence and reliability coefficient reporting for measures was lacking in replications and original studies.
-This is illustrated in our sample by the fact that reliability coefficients were reported in too small quantity to conduct the planned analysis for hypothesis 1, and because of the `r nrow(coded_data_replications)` measures only `r sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")` measures in original articles and `r sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")` in replication protocol reported any validity evidence.
-Thus, reliability and validity evidence was underreported in our sample similarly to the findings of @shaw2020measurement, @flake2017construct, and @flake2022construct, a problem that has also been addressed in earlier literature on this topic [@vacha1999practices; @green2011recent].
-
+Findings were in line with similar investigations in the literature by @shaw2020measurement, @flake2017construct, and @flake2022construct.
+Those studies found that validity evidence and reliability coefficient reporting for measures was lacking in replications and original studies.
+This is a problem that has been addressed in literature on this topic for a long time [@vacha1999practices; @green2011recent], and illustrated yet again in our sample by the fact that reliability coefficients were reported in too small an amount to conduct the planned analysis for hypothesis 1.
 The adjusted test for hypothesis 1, while not able to test differences in actual coefficient values, did show contradictory to hypothesis 1 and similarly to @flake2022construct, that original articles reported reliability coefficients more often than replication studies.
-Still, even for original articles `r round(100 * (table(coded_data_original_shortened$N_items)[["multiple item measure"]] - sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)])) / table(coded_data_original_shortened$N_items)[["multiple item measure"]], digits = 0)`% of the multiple item measures were also reported without reliability evidence.
-
-This only covers part of the spectrum of the measures found in the sample, across both original and replication studies, less than half of the coded measures were multiple item scales.
+However, even for original articles `r round(100 * (table(coded_data_original_shortened$N_items)[["multiple item measure"]] - sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)])) / table(coded_data_original_shortened$N_items)[["multiple item measure"]], digits = 0)`% of the multiple item measures were reported without any reliability evidence.
+Interestingly, the reliability coefficients that were reported, were reported for measures that obtained large calculated reliabilities.
+
+Furthermore, of the `r nrow(coded_data_replications)` measures only `r sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")` in original articles and `r sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")` in replication protocols reported any validity evidence.
+Even the exact version of the measure was difficult to ascertain for neither original nor replication.
+
+This only covers part of the spectrum of the measures found across both original and replication studies, as less than half of the coded measures in the sample were multiple item scales.
 Research commonly made use of single item measures (see Figure \@ref(fig:ReliabilityReportingFlowDiagram) for more details), an observation that was also made by @shaw2020measurement.
 The use of single item measures comes with many risks with regard to validity [@diamantopoulos2012GuidelinesChoosingMultiItem; @nunnallyOverviewPsychologicalMeasurement1978].
-Additionaly, by virtue of being singular they assume that whatever they are measuring is unidimensional, while not being able to test this assumption [@shaw2020measurement].
-This is particularly concerning given that the exploratory unidimensionality tests for the multiple item measures (appendix A) revealed that only `r sum(cfa_results$Single_factor == "Yes", na.rm = TRUE)` of the `r nrow(cfa_results)` relevant measures satisfied the conditions for unidemensionality.
-Thus showing little support for unidimensionality of measurement in general, although the result from this analysis is tentative on several assumptions (see Appendix A).
-
-Several results did show more promising findings for the way measurement related issues are treated in replications at least.
-Firstly, the pre-registered test for hypothesis 2 showed that most of the variability in reliability coefficients in the sample is between measures, rather than within measures across different locations.
-Additionally, the meta-analysis of Cronbach's alpha showed non-significant and small heterogeneity estimates for most of the measures analysed.
-This is a prerequisite showing that measurement generally operated similarly across locations, which would make the scores from the different lab locations directly comparable and aggregatable.
-However, the small sample number of measures for which reliability could be assessed does mean that the generalisability remains uncertain.
-Secondly, most replication protocols clearly stated that their measure was either newly created or based on existing materials.
-Still, in most instances neither original nor replication provided information on the exact version of their measure.
-This may largely be due to the fact that many of the used measures were single-item, for which specifying the exact versions may not be seen as crucial because they more or less describe themselves.
-Finally, QMPs were overall less common in replication protocols than they were in original articles, supporting hypothesis 4.
-This runs counter to the findings of @shaw2020measurement & @flake2022construct, who found that measures came with less validity evidence in replications than in original studies, as the result of QMPs.
-
-The structured replication protocols that were used in the Many Labs projects, I suspect improved the reporting practices and measurement consistency in replication protocols compared to original articles.
-Most replication protocols even contained a section under each replicated study, which listed any deviations from the original and as a result many potential QMPs were averted.
-[@protzko2020high] already demonstrated that transparent reporting of methodology before conducting research can improve the robustness of psychological science, and I believe the same holds true here.
-
-## Impact of reliability on replicability
-
-Contrary to expectations (see Hypothesis 3), less reliable measures were not associated with a decrease in replicability.
-This result is surprising, since @stanley2014expectations demonstrated the potential impact that measurement error can have on the veracity of determining replication success based on a significance test without attenuating for measurement error.
-The significance test cut-off criteria that was used in this study to assess replication success similarly did not attenuate for measurement error, and thus results in line with the simulation studies of @stanley2014expectations were expected.
-
-While no evidence for hypothesis 3 was found, caution in interpreting the test results is needed.
-The number of measures for which reliability was calculated was quite low (`r apa_num(sum(!is.na(data_h3_avg$alpha)), numerals = FALSE)`), it could be that the test was simply underpowered to detect the effect.
-On the other hand, it might be the result of measurement error's tendency to reduce heterogeneity in estimates of the same effect, making the observed effects more similar [@olsson-collentine2023UnreliableHeterogeneityHow].
-This may have resulted in effects that appeared to homogeneously show evidence in one direction, which may explain the differences in conclusions observed between this article and the simulation studies of @stanley2014expectations.
-
-## Impact of QMPs on replicability
-
-Results regarding the relationship between QMPs and replicability were more in line with expectations.
+Additionally, by virtue of being singular they assume that whatever they are measuring is unidimensional, while not being able to test this assumption [@shaw2020measurement].
+
+Other results did show more promise.
+For instance, QMPs were found to be overall less common in replication protocols than they were in original articles, supporting hypothesis 4.
+This runs counter to the findings of @shaw2020measurement & @flake2022construct, who found that measures came with less validity evidence in replications compared to original studies, and shows that QMPs can be systematically reduced across a series of studies.
+The structured replication protocols that were used in the Many Labs projects, I suspect were the reason that the reporting practices were improved in replication protocols compared to original articles.
+Most replication protocols even contained a section under each replicated study, which listed deviations from the original, providing much relevant information.
+As a result many potential QMPs were averted.
+@protzko2020high already demonstrated that transparent reporting of methodology before conducting research can improve the robustness of psychological science, and I believe the same holds true here.
+
+## Impact on Replicability
+Indeed the robustness of the research investigated in this study, as judged by its replicability, did appear to be affected by the reporting of measurement details.
 In particular, support was found for hypothesis 5, showing that an increase in total QMP ratio was associated with a decrease in replicability.
@@
 This result provides further evidence supporting these claims.
-
 The effect of QMPs on replicability can additionally be traced back to the effect of original article QMPs on replication QMPs.
@@
 
-The idea here is that when information on or support for the use of a measurement is lacking, any subsequent replication attempt is expected to also lack information on the measure.
+When information on, or support for the use of a measurement is lacking, any subsequent replication attempt is expected to also lack information on the measure.
 As a result, both the underreporting of measurement details and use of unverified measurements may persist in the replication.
 Consequently, ensuring that the original measurement is mimicked becomes difficult to verify when the measurement was not documented well originally.
-In turn, the relation between the original and replication studies may weaken [@flake2022construct], and as a result, constructs are measured substantially differently, thus the subsequent test in the replication is substantially different from the test in the original article.
-This would mean that the observed effects in the replication may differ from the original not only due to sampling error, but also due to true differences in the assessed effect as the result of the measurement used.
+In turn, the relation between the original and replication studies may weaken [@flake2022construct].
+As a result, constructs are measured substantially differently, causing subsequent replication tests to substantially differ from the test in the original article.
+This implies that the observed effects in the replication may differ from the original not only due to sampling error, but also due to true differences in the assessed effect as the result of the measurement used.
 
@@
 
+What did not appear to affect the replicability of a study was the reliability of the measure used in the study.
+This result is surprising, given that @stanley2014expectations demonstrated the potential impact that measurement error can have on the veracity of determining replication success based on a significance test without attenuating for measurement error.
+The significance test cut-off criteria that was used in this study to assess replication success similarly did not attenuate for measurement error, and thus results in line with the simulation studies of @stanley2014expectations were expected.
+However contrary to both Hypothesis 3 and @stanley2014expectations, less reliable measures were not associated with a decrease in replicability.
+
+While no evidence for hypothesis 3 was found, caution in interpreting the test results is advised.
+The number of measures for which reliability was calculated was quite low (`r apa_num(sum(!is.na(data_h3_avg$alpha)), numerals = FALSE)`), it could be that the test was simply underpowered to detect the effect.
+On the other hand, it might be the result of measurement error's tendency to reduce heterogeneity in estimates of the same effect, making the observed effects more similar [@olsson-collentine2023UnreliableHeterogeneityHow].
+This may have resulted in effects that appeared to homogeneously show evidence in one direction.
+The relation becomes even more complicated for the measures that showed evidence of reliability heterogeneity, which while not many, does invalidate the use of reliability averages in the model for hypothesis 3.
+These factors may help to explain the differences in conclusions observed between this article and the simulation studies of @stanley2014expectations.
+
 ## Limitations & Future Research
-
 The design of this study came with certain limitations.
-First of all, there was no (quasi-)experimental manipulation included of the quality or reporting practices of the measures.
-As a result, the ability to investigate the exact causal links between QMPs and replicability was limited.
+First of all, there was no (quasi-)experimental manipulation included.
+As a result, the ability to investigate the causal links between QMPs and replicability was limited.
 Secondly, alternative ways to analyse or expand the sample could have been used.
@@
 It is important to also consider whether or not replication protocols and research articles can be fairly compared in terms of QMPs.
-Articles are generally longer than a study's description within a replication protocol, and as a result it seems reasonable to expect research articles to generally contain more measurement details than replication protocols.
-Regardless, this study assumed that a replication protocol is comparable to an article in providing an overview of the measure and how it was used, as it is the only comparable source for such information that would otherwise be difficult to find anywhere else.
-This assumption seems practical if not tenable when the replication protocol is the only available sources of measurement details.
+Articles are generally longer than a study's description within a replication protocol, and thus it seems reasonable to expect research articles to generally contain more measurement details than replication protocols.
+Regardless, this study assumed that a replication protocol is comparable to an article in providing an overview of the measure and how it was used, as it was the only comparable source for such information that would not easily be found anywhere else.
+This assumption is practical if not tenable when the replication protocol is the only available sources of measurement details.
 However, in case more detailed information on a measurement is available in other sources, such as an online appendix, it could be important data to include when assessing QMPs.
@@
 This relates to the fact that non-applicable items, while adjusted for by coding those items as 0 in both the numerator and denominator of the QMP ratio calculation, could exert a strong influence on the value of the QMP ratio.
-For example, for one measure all relevant information regarding the measure was reported, for another no information was provided on the measure at all and the items were all non-applicable.
-In both cases the QMP ratio would be 0, however we would not consider the latter case to be nearly as informative as the first.
-As a result the relation between QMP ratio and measurement reporting quality is obscured.
-There is no simple solution to this problem based on teh current data, however future research may wish to include qualitative analyses of the informativeness of measurement detail reporting to provide a more thorough and complete picture.
-
-The small sample of measures for which reliability coefficients could be assessed limited the degree to which substantial interpretations can be made from the reliability analyses.
-While future research will also unlikely be able to increase the number of multiple item measures used by replications, future research can broaden their analyses to include a larger number of replications, or take into account a type of measure which this study mostly ignored in the analyses of reliability and validity: single-item measures.
+For example, for one measure all relevant information regarding the measure was reported, for another no information was provided on the measure at all and furthermore the items were all non-applicable.
+In both cases the QMP ratio would be 0.
+However, we would not consider the latter case to indicate the same quality of measurement reporting as the first.
+As a result, the relation between QMP ratio and measurement reporting quality is obscured[^5].
+There is no simple solution to this problem based on the current data.
+Regardless, future research may wish to include qualitative analyses of the informativeness of measurement reporting to provide a more thorough and complete picture.
+
+[^5]: Because the relation is obscured and since the scale was constructed as a means to capture QMPs as broadly as feasible, the QMP items should be held equivalent to a psychometric scale.
+For these reasons, psychometric evidence for the scale is not given, as it would hard to decide how Not Applicable responses should be treated, and because the goal of the scale was not to capture one or multiple latent constructs.
+
+The small sample of measures for which reliability coefficients could be assessed limited the robustness of the reliability analyses.
+While future research will also unlikely be able to increase the number of multiple item measures used by replications, future research can broaden their analyses to include a larger number of replications, or take into account a type of measure which this study mostly ignored in this study's analyses of reliability and validity: single-item measures.
 
@@
 Investigations similar to this have also been suggested for future replication projects [@flake2022construct].
-For these reasons, future research should consider using measurement invariance tests, when assessing measurement consistency in replications across different labs.
+For these reasons, future research should consider using measurement invariance tests to assess the measurement consistency in replications.
 
@@
 Taking all the findings together, the following assessments will be relevant to consider for future replication research.
-With respect to the quality of measurement reporting, the small number of reported reliabilities, and lack of reported validity evidence corroborate findings by @shaw2020measurement & @flake2022construct.
-Evidence on the reliability and validity of the measures used in both replication and original research should be reported more frequently, so that measures can be evaluated and the validity of replication research can be improved.
-
 The results suggest that the use of structured measurement reporting protocols may be an effective way of reducing QMPs, and may explain why the replication protocols had on average lower QMPs than original articles in this study.
-However, the reliability and validity evidence reporting rate was lower in the Many Labs replication protocols that made use of structured reporting protocols compared to original articles.
-These protocols could therefore still increase the attention they give to reporting reliability and validity evidence.
+This suggests that reporting guidelines can be a successful tool in improving measurement reporting.
+However, not only was reliability and validity evidence rarely reported in both replication protocols in original articles, corroborating findings by @shaw2020measurement & @flake2022construct.
+Reliability and validity evidence was reported even less in the replication protocols, that made use of reporting guidelines, compared to original articles.
+It may therefore be necessary for reporting protocols to increase the attention they give to reporting reliability and validity evidence.
 
@@
 
-In case the quality appears low, replication attempts can still proceed with some adjustments.
+In case the quality appears low or the exact details of the measurement such as the version used was not clear, which was not uncommon in our sample, replication attempts can still proceed with some adjustments.
 One option is to change the focus of the replication to be conceptual rather than direct.
@@
 
-Overall, the observed quality of measurement and frequency of measurement reporting in psychological research and replications was low, which is in line with other research on the topic.
+Overall, the observed quality of measurement and frequency of measurement reporting in psychological research and replications was low, which is in line with earlier research.
 Improvements in the reporting on measurement are needed for both original and replication research.
@@
 These results combined suggest that improvements in the reporting of measurements are necessary in both replications and original articles.
-Furthermore, future replicators should carefully consider the quality of measurement in a study before attempting a direct replication, even considering a conceptual replication instead if the measurement in the original was not of sufficient quality.
+Furthermore, future replicators should carefully consider the quality of measurement in a study before attempting a direct replication.
+A conceptual replication may be the better choice if the measurement in the original was not of sufficient quality.
 However, the evidence for the relationship between measurement quality and replicability was not robustly identified, and future research will be needed to confirm the exact nature of this relationship.

### 2024-05-28 Data/AnalysisData/codebook_plot_data_structure_data.Rmd
revised the entire text to the main article form. Added a new figure, removed some tables and analyses, appendiced some analyses.

--- 2024-03-19 Data/AnalysisData/codebook_cfa_results.Rmd
@@
 ---
-title: "Codebook created on 2024-03-18 at 2024-03-18 14:12:52.006764"
+title: "Codebook created on 2024-05-22 at 2024-05-22 10:01:49.511004"
 output: github_document
@@
 ## Dataset description
-The data contains 19 cases and 3 variables.
+The data contains 112 cases and 91 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_cfa_results.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_plot_data_structure_data.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2024-05-28 Data/Data_package_description.Rmd
revised the entire text to the main article form. Added a new figure, removed some tables and analyses, appendiced some analyses.

@@
 It additionally contains peripheral information about the articles and study in it that were used throughout the analyses and for descriptives.
+Questions related to modification had 'no modification' as an additional answer option, in case that specific aspect of the measure was explicitly not modified, but might possibly have been applicable, because it was a relevant aspect albeit unmodified.
+But these operated equivalently to the Not applicable response with respect to the calculation of the QMP ratio.
+They are included here for future reference.
 
@@
 
+### plot_data_structure_data.csv
+
+*Explanation*: Contain all of the data from the data_h4.csv filtered based on having a unique title (that was not due to a typo or copying error) to extract the individual studies and replication rather than individual measures into a dataset.
+Furthermore, the total count of measures for each study or replication was added to this dataset.
+
 ### plot_23_data_alpha.csv

### 2024-05-28 Scripts/Manuscript/AppendixScripts/Appendix_pre-reg_analyses.Rmd
revised the entire text to the main article form. Added a new figure, removed some tables and analyses, appendiced some analyses.

@@
 This appendix contains the pre-registered analyses that were either changed or omitted from the article.
+
+## Intraclasscorelation assessment for within measure variation in reliability
+
+### Pre-registration Analysis Justification & Reason for Omission from Article
+Reliabilities could be calculated from the replication datasets.
+On top of that, reliabilities could be calculated for each individual lab per replication set so that the variance of them could be assessed.
+In order to separate between and within variance in reliability, a multilevel random intercept model was specified with replication set as the grouping variable and the Cronbach's alpha or omega value of a replication as dependent using the lmer function from the lme4 package [@R-lme4] t.
+
+```{r Hypothesis2Model, include = FALSE}
+# intercept only model to check the within and between group variance.
+H2_test_result_alpha <- lmer(formula = alpha ~ 1 + (1|g), data = data_h2)
+
+```
+
+The purpose of this analysis was to investigate variability in calculated reliability coefficients within and between replication sets.
+However, at the time of pre-registering we did not know of any formal test for the significance of within group variance after controlling for between group variance.
+Instead the intraclass correlation (ICC) coefficient was calculated an indicator of within vs.
+between variability.
+
+```{r ICCCalculations, include = FALSE}
+# Variances
+within_group_variance_alpha <- attr(VarCorr(H2_test_result_alpha), "sc")^2
+between_group_variance_alpha <- attr(VarCorr(H2_test_result_alpha)$g, "stddev")^2
+
+# ICC
+ICC_alpha <- between_group_variance_alpha / (within_group_variance_alpha + between_group_variance_alpha)
+
+```
+
+This analysis was omitted from the article because it did not link well enough to hypothesis 2.
+THe test results also do not give use a very informative representations of variance in reliability in the data for us to draw further inferences from.
+For instance, it assumes that we should observe large differences in reliabilities between measures for this to provide an accurate test of whether or not the variance within measures is large or not.
+
+### Results
+The between-group and within-group variance for Cronbach's alpha were approximately `r apa_num(between_group_variance_alpha, digits = 3)` and `r apa_num(within_group_variance_alpha, digits = 3)` respectively.
+The resulting ICC, was approximately `r apa_num(ICC_alpha, digits = 3)`.
+This suggests that variance was larger between replication sets than within.
+These results are generally in line with hypothesis 2.
+However, this statistic does not necessarily gives a test of hypothesis 2, as outlined above.
 
@@
 
-The model was the same as that used for the main test of hypothesis 6 (see formula \@ref(eq:H6Main)), only now QMP ratios for each of the five categories were used one at a time for each unique combination of original article and replication protocol QMP.
+The model was the same as that used for the main test of hypothesis 6, only now QMP ratios for each of the five categories were used one at a time for each unique combination of original article and replication protocol QMP.
 

### 2024-05-28 Scripts/Manuscript/manuscript.Rmd
revised the entire text to the main article form. Added a new figure, removed some tables and analyses, appendiced some analyses.

@@
 ---
-title             : "The Impact of Measurement Practices and Measurement Error on Construct Validity and Replication Outcomes in Psychological Science"
-shorttitle        : "Measurement Quality and Replicability"
+title             : "An Empirical Assessment of Reliable and Valid Measurement as a Prerequisite for Informative Replications"
+shorttitle        : "Measurement Quality and Informative Replications"
 
@@
       - "Methodology"
+      - "Project Administration"
+      - "Software"
       - "Visualization"
       - "Writing - Original Draft Preparation"
+      - "Writing - Review & Editing"
+  - name          : "Bakker, M."
+    affiliation   : "1"
+    role:
+      - "Supervision"
+      - "Writing - Review & Editing"
+  - name          : "Wicherts, J.M."
+    affiliation   : "1"
+    role:
+      - "Supervision"
       - "Writing - Review & Editing"
@@
     role:
+      - "Conceptualization"
       - "Project Administration"
+      - "Supervision"
+      - "Validation"
       - "Writing - Review & Editing"
-      - "Supervision"
 
@@
 
-  Enter author note here. Jelte/Marjan?
-
 abstract: |
-  Recently, the influence of measurement related issues on replicability has received more investigations. 
-  In particular, studies have indicated that low reliability, and poor measurement reporting can negatively influence the replicability of an effect. 
-  Building on this new line of research, this study assessed the influences of poor measurement reporting in replications from the Many Labs replication projects, and the original articles that the replications were based on, while publicly available data from the Many Labs replications was used to assess the reliability of the measures.
-  Here we show that while contrary to expectations reliability did not relate to replicability, the quality of measurement reporting in replications did relate. 
-  For original articles the quality was indirectly related to replicability through the quality of measurement reporting in replications.
-  These and other descriptive results indicate similarly to previous research that measurement details in both original research and replications are underreported.
-  However, some of the issues in measurement reporting that were identified as most critical in this study differ from what has been stated in previous research.
-  Measurement is a crucial part of almost all empirical research, it's details should tehrefore be transparently reported to enable critical evaluation and independent replication.
-  Consequently, recommendations are given to researchers and replicators on the measurement practices that are  most crucial to improve on.. 
-  Finally, directions are given for future research to further investigate the (causal) relationship between measurement practices and replicability.
-
-keywords          : "reliability, measurement, measurement reporting, replicability, construct validity"
-wordcount         : "234"
+  Psychological science has been facing threats to the credibility of its findings, particularly due to the lack of replicability of findings.
+  Recently, there has been increasing attention towards the impact that features of psychological measurement, specifically reliability and measurement reporting, has on replicability.
+  In this article, we assessed the reliability and measurement reporting within the Many Labs replications and the original studies they were based on. 
+  We then empirically investigated the associations of replicability with reliability and measurement reporting.
+  The results indicated that not all measures were sufficiently reliable across contexts. 
+  Additionally, reliability and validity evidence was rarely reported. 
+  Finally, incompleteness in measurement reporting was associated with lower replicability of the findings tested with that measure.
+  The results not only indicate potential issues in reliability and validity of measures, but also that incomplete measurement reporting may negatively affect replicability. 
+  These findings illustrate the importance of reliable measurement, and complete measurement reporting for establishing credible findings. 
+  The article ends with suggestions to improve measurement reporting. 
+  We further suggest that the reported measurement information should be evaluated when  researchers decide what studies to replicate.
+
+keywords          : "reliability, validity, measurement, measurement reporting, replicability, credibilitys"
+wordcount         : "182"
 
@@
 
-\setcounter{topnumber}{3} <!-- max number of floats at top of page --> \setcounter{bottomnumber}{3} <!-- max number of floats at bottom of page --> \setcounter{totalnumber}{4} <!-- max number of floats on a page --> <!-- remember to use [htp] or [htpb] for placement -->
+\setcounter{topnumber}{3} <!-- max number of floats at top of page -->
+
+\setcounter{bottomnumber}{3} <!-- max number of floats at bottom of page -->
+
+\setcounter{totalnumber}{4} <!-- max number of floats on a page -->
+
+<!-- remember to use [htp] or [htpb] for placement -->
 
@@
 
-For many years, methodologists and statisticians have raised concerns about the way that research practices [@cumming2014new; @wicherts2016degrees], reporting practices [@bakker2011mis; @nuijten2016prevalence], and publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science] may undermine the credibility of psychology's scientific claims.
-Replicability of a finding is seen as one crucial step in establishing its credibility [@nosek2022replicability].
-In order to investigate the replicability of psychological science, the large scale Reproducibility Project: Psychology (RPP) was set-up [@osc2015estimating].
-Replications of 100 published studies were performed using similar materials, procedures, and analyses, while using a new sample of participants for each study.
-They found however, that in many instances the results did no match those of the original studies.
-This lack of replicability of psychological findings led to the claim that psychology was facing a 'replication crisis' [@hughes2018psychology; @giner2019crisis].
-
-As a response, the demand to verify the credibility of psychological findings through replications rose.
-In order to attempt replications of various psychological findings, numerous large scale projects were set-up [@klein2014investigating; @camerer2016evaluating; @camerer2018evaluating; @ebersole2016many; @ebersole2020many; @klein2018many; @klein2022many].
-Among these were the Many Labs projects, which operated similarly to the RPP, with the additional feature that each original article was replicated multiple times across different labs in various locations around the world.
-The results from these replication projects generally showed smaller effects than those reported in the original studies.
-Similarly, effects that had reached statistical significance in the original no longer did across the aggregate results of its replications.
-
-Several explanations for this discrepancy between original and replication findings have been suggested and investigated, with many being centred around the concept of Questionable Research Practices [QRPs, @john2012measuring].
-QRPs are practices, which either misrepresent or omit essential methodological information that is needed to evaluate the research.
-Without this information, a reader will not know whether the result was in line with the author's expectation or simply the result of repeated trial and error until a suitable result was found [@simmons2011false].
-Consequently, much of the discourse and the subsequent proposed solutions have been centred around preventing these QRPs through increased transparency in scientific reporting.
-
-However, many researchers have also raised concerns that other factors, such as low power [@stanley2018what], lack of strong theoretical foundations [@eronen2021theory], and validity [@finkel2017replicability], which have not been given as much attention, are just as if not more responsible for the lack of successful replications found in psychology.
-Another factor which has gained more traction recently are measurement related issues' impact on replicability.
-In particular, studies shown that measurement error and questionable measurement practices may impact replicability [@stanley2014expectations; @shaw2020measurement; @flake2017construct; @flake2020measurement].
-
-Measurement in psychological science is defined in large part by one overarching issue: the psychological constructs of interest, such as affective state and intelligence, cannot be measured directly [@flake2017construct].
-As a result, psychologists face two primary challenges in the use of measurement: First of all, the measure has to assess the construct it intends to measure, even though it can only do so indirectly.
-Secondly, because the measurement is indirect, it also comes with some degree of error surrounding its assessment of the construct.
-The first issue relates to the concept of validity, and specifically construct validity.
-Validity refers to the overall extent to which a measure measures what it is supposed to [@borsboom2004concept], while construct validity specifically refers to the substantial relation between the item scores on a psychological measure and the psychological construct it intends to measure.
-In order for indirect assessment of psychological constructs to be a viable approach, the measure needs to have construct validity [@cook2002experimental].
-The second issue relates to the concept of measurement error and reliability.
-Measurement error indicates the amount of variation in item scores that is the result of the used measures inaccuracies, and not due to differences in the underlying psychological construct of interest.
-
-@stanley2014expectations demonstrated, using a simulation study, the impact measurement error has on attempts to verify or falsify findings.
-Scalar item data was generated based on levels of sampling error and score-reliability, as the inverse of measurement error, that mimicked what is standard in psychological research, to ensure that the resulting degree of error was representative.
-The results indicated that measurement error caused observed effects found in replication research to vary heavily.
-
-Even when ignoring reliability, a measurement's content and implementation still need to validly capture what it intends to measure.
-Questionable Measurement Practices (QMPs) are practices that decrease the availability of information needed to evaluate a measurement's validity, and have been coined as a conjugate term to QRPs.
-They range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of measure and procedure of any sourced measures [@flake2020measurement].
-When this information is missing, it becomes difficult to establish that original and replication are measuring the same construct(s), which has detrimental consequences for direct replication attempts.
-
-This study aims to investigate the influence of both measurement error and QMPs on replicability, using data and reports from the large scale Many Labs replication projects.
-One goal is to expand the research by [@stanley2014expectations] with a practical example.
-Whereas they obtained their findings using a simulation study, this study investigated the scope of their findings on data from real replications.
-QMPs in the context of replication research were already investigated by [@flake2022construct].
-However, the investigations remained mostly descriptive.
-This study additionally aims to expand upon the findings of [@flake2022construct] through the use of a new set of replication data, and by exploratively investigating the relation between QMPs and replicability.
-
-## Measurement Error
-As a first step the state of measurement error in original and replication research in psychology is investigated, to assess the scope of @stanley2014expectations's findings in practice:
+For solid scientific progress in psychology, we need to be able to rely on previous findings - findings should be credible.
+Unfortunately, psychology seems to face several threats to the credibility of its findings.
+In this article, we investigate how the credibility of psychological findings may be affected by problems in psychological measurement, and in turn, how those problems may affect successful replication.
+
+### Credibility & Replicability
+
+A prerequisite for a credible finding is that it is replicable [@vazire2022CredibilityReplicabilityImproving].
+This means that the observed effect should be comparable across the original study and subsequent replications as long as the differences between them are believed to be of little relevance to the effect [@nosek2022replicability].
+
+In practice, effects deviate substantially between original and replication research.
+In 2015, the Replication Project: Psychology (RPP) attempted replications of 100 research findings in psychology, they observed a substantial discrepancy between the replication findings as compared to the original findings [@osc2015estimating].
+Similarly, the Many Labs projects replicated the effects reported in original articles across different labs in various locations around the world [@klein2014investigating; @camerer2016evaluating; @camerer2018evaluating; @ebersole2016many; @ebersole2020many; @klein2018many; @klein2022many].
+There it was observed that effects were on average smaller in replication compared to original research.
+Furthermore, there was variation within the estimates of the effect between different lab locations.
+
+In response to this string of failed replications, there was widespread alarm regarding the credibility and robustness of findings in psychological science [@hughes2018psychology; @giner2019crisis].
+Simultaneously researchers sought to explain this discrepancy.
+The factors that have been proposed include, questionable research practices [@simmons2011false; @john2012measuring; @cumming2014new; @wicherts2016degrees], questionable reporting practices [@bakker2011mis; @nuijten2016prevalence], and biased publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science].
+A factor that has gained more traction recently is the impact of measurement-related challenges on replicability.
+
+### Credibility & Measurement
+
+Measurement in psychological science is characterized in large part by one overarching issue: psychological constructs, such as affective state or intelligence, can usually not be measured directly [@flake2017construct].
+As a result, psychologists face two primary challenges in the use of measurement: First of all, because the measurement is indirect, it also comes with some degree of random error surrounding its assessment.
+Secondly, the responses on the measure have to relate to the psychological construct(s) of interest, but as the construct is not directly observable, this is difficult to assess.
+
+The first issue relates to the concept of reliability, which gives an indication of how consistent the responses on a measurement are.
+Reliability is a critical first step to obtaining credible findings.
+Because if the scores on a measure are not consistent with themselves, it is unlikely that any effect associated with the measure can be consistently established.
+
+The second issue relates to the concept of validity, and specifically construct validity.
+Validity in measurement refers to the overall extent to which a measure measures what it is supposed to [@borsboom2004concept], while construct validity refers to the substantial relation between the scores on a measure and the related psychological construct.
+A researcher cannot assume to have found a credible psychological effect, if the measures do not relate to a psychological construct [@cook2002experimental].
+
+### Replicability & Measurement
+
+Whereas both reliable and valid measurement and replicability are important elements that independently contribute to the overall credibility of a finding, there may also be a relation between the two.
+Indeed, recent studies have illustrated that both the reliability of the measure [@stanley2014expectations] and the reporting of the measure [@shaw2020measurement; @flake2017construct; @flake2020measurement] can affect the credibility of psychological studies, and in turn explain the lack of replication success.
+This study aims to investigate the influence of both measurement reliability and measurement reporting on replicability, using data and reports from the large scale Many Labs replication projects.
+
+### Many Labs Sample Description
+
+In the Many Labs projects each effect was directly replicated across multiple lab locations over the world.
+As a result the data obtained from these measures allows us to say something about the variability in these measures across different contexts.
+Another important aspect of the Many Labs projects is that the measurement was preregistered and documented in structured protocols that were used to instruct all the participating labs.
+We believe that these represent some of the best practices in measurement usage in psychology.
+Therefore, any problems with the measurement and its reporting encountered in this sample would not bode well for measurement in the rest of psychology.
+
+## Existing Research
+
+### Reliability
+
+While reliability is generally considered a measure specific feature, this is false.
+The reliability of a measure is context dependent [@cho2015cronbach; @pauly2018resampling], and as a result so are the scores obtained with that measure.
+The contextual variations in the measurement scores could explain the discrepancy between effects in original and replication research, as well as within replications of the same original effect.
+Besides random variation due the sampling error, the variations can also reflect true variation in reliability, also known as reliability heterogeneity [@vacha-haase1998ReliabilityGeneralizationExploring].
+For instance, measures are known to generally show lower reliability in more homogeneous samples as compared to heterogeneous samples [@pike1998reliability].
+
+However, even when reliability is the same across studies, reliability can still cause estimates of the same effect to vary significantly.
+@stanley2014expectations simulated data of items on a scale based on levels of sampling error and reliability similar to what is standard in psychological research.
+The results indicated that measurement error due to imperfect reliability caused variation in the observed effect sizes in the simulated replications, on top of sampling error.
+The added variation was substantial enough to cause replications of a positive small effect to observe anywhere between a medium negative effect and a large positive effect [@stanley2014expectations].
+This implies that studies using unreliable measures have a lower probability to be successfully replicated, even if the underlying effect is true and the measurement is equally reliable between original and replication.
+
+### Measurement Reporting
+
+Despite the importance of having reliable and valid measures, research has shown that Questionable Measurement Practices (QMPs) in reporting are not uncommon.
+QMPs are practices that raise doubts about a measurement's validity [@flake2020measurement], and have been coined as a conjugate term to Questionable Research Practices [QRPs, @john2012measuring].
+QMPs range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of measure and procedure of any sourced measures [@flake2020measurement].
+
+@flake2020measurement identified the main questions that the article should answer in relation to the measurement used: the definition of the construct, how the measure was selected, how the measure was operationalized, how the measure was quantified, whether it was modified or not and why, and the reasons and details of creating a measure if applicable.
+The questions together form the basis of the information that a researcher should present in order to be transparent and promote a more cumulative psychological science.
+
+@flake2022construct documented QMPs among 100 replications and their respective original articles from the RPP [@osc2015estimating].
+They coded the number of measures, the number of items in the measure, and the information that was reported describing the measure and providing evidence justifying its use.
+Besides limited reporting of validity and reliability evidence for the coded measures, @flake2022construct found that several of the measures in the RPP did not report the number of items, the response format, or the scoring of the scale.
+Furthermore, only 8 of the 40 translated scales contained validity evidence for the translated version of the scale.
+Measures were similarly modified between original and replication in other ways without evidence showing that the modification did not invalidate the measurement.
+
+Further findings by @flake2022construct and others [@flake2017construct; @shaw2020measurement] illustrated how QMPs create challenges for replicating researchers.
+Replicating researchers will need detailed information on the measurement in the original study to reconstruct it.
+If the measure is not reconstructed exactly, original and replication may be measuring different construct(s).
+In that case, different effect size estimates in original compared to replication research may very well be due to the fact that the effects are between different constructs, and not because the effect was not robust to sampling error.
+
+### Research Contribution
+
+Our study aimed to investigate the influence of both measurement reliability and measurement reporting on replicability, using data and reports from the large scale Many Labs replication projects.
+Firstly, this study expands on the research by @stanley2014expectations using an empirical example.
+Our goal was to see whether reliability was related to replication success on real life replication data.
+In practical terms, we investigated whether or not replicated studies differed in their reliability scores from non-replicated studies.
+In their study @stanley2014expectations assumed reliability to be constant across studies, which we know to be an oversimplification.
+Therefore, to add further context to relation between reliability and replication, this study also investigated the variation in reliability as observed across separate measurement occasions.
+
+Furthermore, this research conceptually replicates the study by @flake2022construct on QMPs in replications and original research, now in the context of the Many Labs projects.
+We then expand on @flake2022construct by exploring associations between QMPs and the replicability of psychological findings.
+
+## Research Questions & Hypotheses:
+
+### Reliability
+
+Measurement reliability varies across contexts. It is crucial for evaluating replications that differences between replication and original are understood and accounted for.
 
 -   RQ1a. What is the degree of score reliability in replications of psychological research?
-
 -   RQ1b. What is the degree of score reliability in original psychological research?
 
-Since direct replications intend to investigate effects in nearly identical scenarios with nearly identical measures as the original study, it is expected that measurement errors are as present in the replication research looked at in this study as in the accompanying original psychological research.
+The Many Labs studies were intended as direct replications.
+In direct replications, any deviations from the original research are believed to be irrelevant for testing the same effect as the original study [@nosek2022replicability].
+In that case, the reliability of measurements in replications should also not deviate systematically from the original research.
 
@@
 
-While reliability estimates are generally considered a measure specific feature, this is false.
-They are context dependent, and as a result the estimates of an effect can differ across contexts [@cho2015cronbach; @pauly2018resampling].
-With large enough differences across contexts, the effect estimates between different replication attempts could deviate from each other beyond direct comparison.
-To investigate this potential problem, the variation in score reliability is assessed for each measure when used across a set of replications of the same effect in contexts.
+Reliability has the potential to vary not only between replication and original research, but also within replications of the same effect [@vacha-haase1998ReliabilityGeneralizationExploring].
 
@@
 
-Even though reliability estimates are context dependent, sufficient protocol structure can counteract the variance in reliability estimates.
-An example of the standardizing impact a structured protocol can have on reducing variability within an effect can be found in investigations into the closely related issue of heterogeneity [@patacchini2007unobserved].
-Heterogeneity refers to the true variation in the true effect size due to minor but key differences in context, environment, and procedure.
-Heterogeneity is yet another proposed explanation for failed replications.
-This concern even prompted a Many Labs centered around the testing of heterogeneity in replications [@klein2018many].
-However analyses from this Many Labs, and @olsson2020heterogeneity showed little empirical evidence for widespread heterogeneity in effects among replications.
-These findings demonstrate that it is possible to reduce variability as the result of context using structured protocols, as was done in the Many Labs projects this study analyzed.
+Heterogeneity could be a major contributor to this variation.
+However for effect sizes there is little empirical evidence of widespread heterogeneity among the Many Labs replications [@klein2018many; @olsson2020heterogeneity].
+The same is expected to hold true for the heterogeneity in reliability coefficients among the Many Labs replications.
 
@@
 
-This study investigated whether there is something in the measures used for replicated findings that sets them apart from those used for non-replicated findings.
-One of the elements this study looked at is the reliability of replicated studies compared to the non-replicated studies, thus extending the research by @stanley2014expectations on the relationship between reliability and replicability with data from real life replication projects.
+In order to see if reliability has an impact on replication attempts, we investigated whether or not successfully replicated studies differ in the reliability of their measures as compared to non-replicated studies.
 
@@
 
-Greater score-reliability means greater consistency in estimation as variance around the estimate of the true effect is decreased.
-Consequently measures across different occasions, including between original and replication, should also become more consistent [@nunnally1994assessment].
-When original and replication research share consistent result, and as long as the studied effect is true, then on average their statistical conclusions should converge.
+Greater reliability means the variance around the estimate of the true effect is decreased [@nunnally1994assessment].
+Assuming that the true effect is not null, then the statistical conclusions tested with reliable measures are be more likely to converge to significance.
 
@@
 
-## Questionable Measurement Practices
-A measure not only needs to be reliable, it should also in its design and implementation adequately capture what it intends to measure [@flake2020measurement].
-Any scientific report should therefore clearly motivate the use of measure and procedure.
-When these aspects are not clearly reported on, the validity of measurement remains uncertain.
-Therefore, the other tests of this paper focused on the reporting aspects of measurement, assessed through QMPs.
-
-This study sought first of all to conceptually replicate some of the findings of @flake2022construct about QMP reporting in the RPP within the Many Labs replication projects.
+### Measurement Reporting
+
+With respect to measurement reporting, this study first of all aims to conceptually replicate some of the findings of @flake2022construct.
 
@@
 
-@flake2022construct coded the presence of a series of QMPs in the replication report in both the replication protocols of each replication in the RPP, as well as the original articles the replications were based on.
-They found that not only are QMPs common in psychological research, they can be even more common in replications reports.
-However, the reporting of the Many Labs projects differ from the RPP data used in @flake2022construct.
-The structured and preregistered protocols used for the Many Labs projects were hypothesized to lead to consistent reporting of important measurement details, and as a result contain less QMPs.
+@flake2022construct found that QMPs were overall more common in the RPP replications as compared to the original research.
+We did not hypothesize this same effect to hold for the Many Labs sample, because of the use of structured protocols documenting the measurement.
 
@@
 
-QMPs may obscure relevant information needed to evaluate the use of measurement in a study.
-If the replication used the measure differently from the original, the replication may no longer be a direct replication.
-As a result, there is additional deviation in the estimate of the effect from the original, due to differences in measurement.
-Establishing a link between QMPs and non-replicability should confirm suspicions of their detrimental effects on replications [@flake2017construct; @flake2020measurement; @flake2022construct].
+Differences in measurement resulting from QMPs have been suspected to cause replication and original effects to deviate [@flake2022construct].
+Investigating the link between QMPs and non-replicability should put this suspicion to the test.
 
@@
 
-Fewer QMPs means that measurement decisions in a report are transparent with the number arbitrary methodological decisions being limited as well.
-Fewer arbitrary decisions means less ways that a replicator can deviate from the original's intended effect.
-One of the Many Labs projects even touched on this concept [@ebersole2020many].
-In this project, peer-review of replication protocols by original authors was used to ensure that approved methods were used.
-Additionally, it has been observed that authors who promote greater transparency in their work, have on average stronger evidence for their hypotheses [@wicherts2011willingness].
-Finally, the results shown in @protzko2020high illustrate that when original studies are transparent, preregistered, and have adequate sample size, subsequent replication attempts find nearly the same effect size as the original.
-All of these findings point towards a positive relation between successful replication and various types of good research practices.
-A similar relation is expected for good measurement practices.
-
--   H5. QMPs in replication research are negatively associated with replication of an original finding.
-
-This study additionally aims to see if the relation between QMPs and replicability can be traced back to original article QMPs.
-When essential information on a measure is not available in an original article, it may be difficult to know the specifics of that measure to report for a replication.
-Therefore this study also investigates the relation between original QMPs and replication QMPs.
+A reduction in QMPs corresponds to greater transparency in reporting of measurement.
+Research on other transparency related practices have shown that these are associated with more robust estimates of effects [@wicherts2011willingness; @protzko2020high].
+We expect a similar effect for QMPs.
+
+-   H5. QMPs in replication research are negatively associated with successful replication of an original finding.
+
+One of the reasons measurement in replication may deviate is because original articles did not report all the necessary information needed to mimic the original measurement.
+In this way a lack of information may carry over from the original article to the replication.
 
@@
 
-If the relationship exists, it is expected that questionable measurement practices in an original paper might cause a spill-over effect of QMPs into the replication.
-@flake2022construct found that QMPs linked to issues for replicators in recreating the measurement to closely match the measurement in the original.
-As a result, there was a lack of measurement related information in both replication reports, and original articles.
-Additionally, investigations by @shaw2020measurement have shown that more validity evidence in an original article is associated with better psychometric properties in the replication sample.
-Based on these arguments, QMPs are expected to be associated across original and replication studies.
+Previous research by @flake2022construct has shown that QMPs in original articles cause issues for recreating measurements for replication research.
+Additionally, @shaw2020measurement found similar spill-over effects for validity.
+Based on these findings, QMPs in original research were expected to be associated with QMPs in replication research.
 
@@
 
-# Method
+# Disclosures
+
+### Preregistration
 
@@
 Any deviations from the preregistration are explicitly mentioned in the text.
+
+### Data, materials, and online resources
+
 This manuscript was created in Rstudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency.
-All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication.git>.
+All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> & <https://osf.io/9r8yt/>.
+
+### Reporting
+
+We report how we determined all data exclusions, all manipulations, and all measures in the study. Our sample size was based on the number of usable studies in the Many Labs studies.
+
+### Ethical Approval
+
+This research was approved by the Tilburg University School of Social and Behavioral Sciences Ethical Review Board.
+
+# Method
 
 ## Sample
+
+### Data Source
 
@@
 Data from Many Labs 4 [@klein2022many] was not part of the sample, as there was no publicly available protocol which contains the information needed to code QMPs.
-Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study's focus on scale and item measures.
-
-The total number of identified psychological findings for which replication was attempted across the four included Many Labs projects amounts to a total of `r sum(table(coded_data_replications$many_labs_version, coded_data_replications$appearance)[,1])`.
-Each finding was tested across several labs, and was related to a finding from an original study, the combination of all these studies and their associated information formed a replication set.
-For each research finding, any primary measures assessing a unique variable were taken to form the key unit of analysis.
-Here primary measures refers to measures assessing variables included in the primary test of the replication.
-This was done to ensure that the analyses could link directly to the replicability of a study.
-Acquiescence bias checks, manipulation checks, measures used for pilot testing, and measures added for exploratory analyses in replication studies were not included.
+Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study's focus on item-based measures.
+
+### Unit of analysis
+
+Measures were identified using the preregistered replication protocols.
+Acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses were not included.
 The result was a total sample size of `r nrow(coded_data_replications)` measures used in both original and replication research[^1].
-Table \@ref(tab:ManyLabsDescriptivesTable) shows further descriptive information about the data for each Many Labs Project.
-
-[^1]: Initially the original articles were coded to have 3 more measures than the replication protocols.
-However, these measures were all related to the moral foundations questionnaire, and could be altered from representing five different moral foundations to the two overarching categories of individualizing and binding foundations found described in the replication protocol without much issue or loss of information.
-
-```{r ManyLabsDescriptivesTable, warning = FALSE}
-# construct the Many Labs descriptives table to be printed
-many_labs_descriptives_table <- data.frame("Many Labs Version" = c("1", "2", "3", "5", "Total"),
-                                      "N ML Projects" = c(table(coded_data_replications$many_labs_version, coded_data_replications$appearance)[,1], sum(table(coded_data_replications$many_labs_version, coded_data_replications$appearance)[,1])),
-                                      "N Primary Measures" = c(table(coded_data_replications$many_labs_version), nrow(coded_data_replications)), 
-                                      "Replication Total N" = c(apa_num(mean(coded_data_replications$N[coded_data_replications$many_labs_version == "1"], na.rm = TRUE), digits = 0),
-apa_num(mean(coded_data_replications$N[coded_data_replications$many_labs_version == "2"], na.rm = TRUE), digits = 0),
-apa_num(mean(coded_data_replications$N[coded_data_replications$many_labs_version == "3"], na.rm = TRUE), digits = 0),
-apa_num(mean(coded_data_replications$N[coded_data_replications$many_labs_version == "5"], na.rm = TRUE), digits = 0), apa_num(mean(coded_data_replications$N, na.rm = TRUE), digits = 0)), 
-"Replication Total IQR" = c(apa_num(IQR(coded_data_replications$N[coded_data_replications$many_labs_version == "1"], na.rm = TRUE), digits = 0),
-apa_num(IQR(coded_data_replications$N[coded_data_replications$many_labs_version == "2"], na.rm = TRUE), digits = 0),
-apa_num(IQR(coded_data_replications$N[coded_data_replications$many_labs_version == "3"], na.rm = TRUE), digits = 0),
-apa_num(IQR(coded_data_replications$N[coded_data_replications$many_labs_version == "5"], na.rm = TRUE), digits = 0), apa_num(IQR(coded_data_replications$N, na.rm = TRUE), digits = 0)),
-"Original Total N" = c(apa_num(mean(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "1"], na.rm = TRUE), digits = 0),
-apa_num(mean(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "2"], na.rm = TRUE), digits = 0),
-apa_num(mean(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "3"], na.rm = TRUE), digits = 0),
-apa_num(mean(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "5"], na.rm = TRUE), digits = 0), apa_num(mean(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)),
-"Original Total IQR" = c(apa_num(IQR(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "1"], na.rm = TRUE), digits = 0),
-apa_num(IQR(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "2"], na.rm = TRUE), digits = 0),
-apa_num(IQR(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "3"], na.rm = TRUE), digits = 0),
-apa_num(IQR(coded_data_original_shortened$N[coded_data_original_shortened$many_labs_version == "5"], na.rm = TRUE), digits = 0), apa_num(IQR(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)))
-
-# Adding column names to the table for readability
-colnames(many_labs_descriptives_table) <- c("ML Version", "N Projects", "N measures$^a$", "Rep. N", "Rep. IQR", "Org. N", "Org. IQR")
-
-### failed table
-# colnames(many_labs_descriptives_table) <- c("Version", "Projects", "Measures", "Total N", "Total IQR", "Total N", "Total IQR")
-
-# c("", "N ML", "N Primary", "Replication", "Replication", "Original", "Original")
-
-# kableExtra::kbl(many_labs_descriptives_table, align = c("l", "r", "r", "r", "r", "r", "r"), escape = FALSE, placement = "htp", row.names = FALSE) %>%
-#   kableExtra::kable_classic( full_width = FALSE) %>%
-#   kableExtra::add_header_above(c("Many Labs" = 1, "N ML" = 1, "N Primary" = 1, "Replication" = 1, "Replication" = 1, "Original" = 1, "Original" = 1), line = FALSE) %>% 
-#   kableExtra::row_spec(4, extra_latex_after = "\\cmidrule(l{3pt}r{3pt}){2-5}")
-
-# midrule wouldn't add ):<
-
-# print the table in apa formatting
-apa_table(
-  many_labs_descriptives_table, align = c("l", "r", "r", "r", "r", "r", "r"), escape = FALSE, placement = "htp", midrules = 4, caption = "General Descriptives of the Many Labs Projects"
-  , note = "$^a$ refers only to the number of identified primary measures, which this study is concerned with. Rep. = Replicaiton, Org. = Original., N = total number of, IQR = Interquartile range.")
-```
+
+[^1]: Initially the original articles contained 3 more measures than the replication protocols.
+This difference was due to the way that the moral foundations questionnaire was framed in the original articles compared to in the original article.
+In the original article it was framed as measuring five different moral foundations, while in the replication protocol the measure was described as measuring the two overarching categories that were used to test the main effect in the original and replication research.
+The measurement information reported was comparable across all five categories, and thus it was deemed that the measurement could be reduced to reflect two overarching categories to make comparison between original and replication easier.
 
@@
 However, no coding or analysis of either of them had taken place before the analyses were preregistered.
-Further details on the search strategy can be found in the data_search_details.pdf supplementary materials.
+Further details on the search strategy can be found in the [coding protocol information file](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) supplementary materials.
 
@@
 
-The replication datasets refer to the data of each of the replication attempts for each of the original psychological effects undertaken as part of a Many Labs study.
-These publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio [@R-Rstudio].
-When available, codebooks, analysis scripts and study materials were used to identify the specific data for each measure.
-The variables associated with each relevant measure were extracted into their own dataframe containing the data from all studies in one replication set.
-These dataframes together formed the dataset used for the analyses.
-
-In order to be considered relevant for the analysis, the measure had to consist of multiple scalar items, as single item measures were not usable for the planned analyses on score reliability [@wanous1996estimating], following up on simulation study of @stanley2014expectations.
+The replication datasets refer to the publicly available datasets containing the data obtained from all of the labs that took part in one of the Many Labs studies.
+These datasets were accessed through their OSF page.
+For the analyses, the scores on the items of an identified measure were identified and extracted.
+When scores could not be clearly identified, any available codebooks, analysis scripts or study materials were used to identify the relevant scores.
+
+In order to be considered suitable for the planned analyses on calculated reliabilities, the measure had to be a scale consisting of multiple items.
 If cleaned data was available this was chosen over raw data, to ensure that variables were coded as intended (e.g.
@@
 Pilot data were omitted from the analyses entirely.
-These criterion resulted in suitable measure data from `r apa_num(length(unique(data_h3_multiple$g)), numerals = FALSE)` replication sets spread across on average `r apa_num(mean(table(data_h3_multiple$g)), digits = 0)` lab locations for the analyses of hypotheses 2 & 3.
+These criteria resulted in suitable item score data from `r apa_num(length(unique(data_h3_multiple$g)), numerals = FALSE)` replication sets spread across on average `r apa_num(mean(table(data_h3_multiple$g)), digits = 0)` lab locations for the analyses of hypotheses 2 & 3.
 
@@
 
-The preregistered replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each replication set.
-These protocols were available through the OSF pages of each Many Labs project.
-
-The OSF page for each Many Labs project was combed through, in order to identify the components of the research which contained information on the measurement practice and reported reliability.
-The focus was on finding the preregistered protocols which contained information on the entirety of the replication sets in each Many Labs project.
-For Many Labs 2, & 3 a common protocol could be identified, for Many Labs 1 the Proposal_V1.1 provided the equivalent information, while for Many Labs 5 protocols were available for each replication set separately.
+The preregistered replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each set of replications replicating a single original study across multiple labs.
+
+The OSF page for each Many Labs project was combed through, in order to identify the documents that contained information on the measurement practice and reported reliability.
+For Many Labs 2, & 3 a single replication protocol for all studies could be identified.
+For Many Labs 1, the Proposal_V1.1 provided the equivalent information, while for Many Labs 5 protocols were available for each set of replications separately.
 
@@
 If available, a version of the protocol labelled as revised, post-review, peer-review, or endorsed was selected.
-In case there was doubt about which was most appropriate, the latest uploaded relevant protocol was selected.
-Only regular protocols were taken, meaning those not labelled as data collection, analysis protocol or anything similar[^2].
+Otherwise, the latest uploaded relevant protocol was selected.
+Protocols labelled as data collection, analysis protocol or anything similar were excluded[^2].
 
 [^2]: The steps taken to access the replication protocol data from Many Labs 5 were not preregistered, and only became clear upon further investigation of the accessible information.
-The specific names and locations of the files that were used as the datasets can be found in the data_search_details.pdf supplementary materials of the OSF page of this article <https://osf.io/gft46/%7D>.
-
-Finally, the reports of the Many Labs projects, meaning the published articles [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many], were used to determine whether not the replication was considered successful.
-
-### Original Study
+The specific names and locations of the files that were used as the datasets can be found in the data_search_details.pdf supplementary materials of this article <https://osf.io/gft46/%7D>.
+
+Finally, the published reports of the Many Labs projects [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many] were used to determine whether not the replication was considered successful.
+
+### Original Articles
 
 The original study articles are the published articles of the original effect on which the Many Labs replication sets were based.
-In the case of Many Labs 5 [@ebersole2020] the original studies refer to the studies which first tested the effect to be replicated, not the earlier replication attempts of the same effects in the RPP [@osc2015estimating].
-
-The original articles were identified using the citations in each replication protocol.
-Then through searches via Web of Science, Google Scholar, and PsychInfo (in that order), the articles were retrieved[^3].
-
-[^3]: An issue was encountered while trying to access @hyman1950current.
-However, after contacting the first author of @klein2014investigating a suitable version of the article was obtained for use in the analyses.
+They were identified using the citations for these articles in each replication protocol.
+In the end all articles could be retrieved through searches on Web of Science, Google Scholar, and PsychInfo (in that order)[^3].
+
+[^3]: An issue was encountered while trying to access @hyman1950current. However, after contacting the first author of @klein2014investigating a suitable version of the article was obtained.
 
@@
 
-Relevant primary measures were identified by combing through the entirety of the methods section for each preregistered replication protocol.
-Then using questions and the accompanying search strategies as documented in the structured coding protocol of this study (available on the relevant OSF: <https://osf.io/9r8yt/>, and github pages: <https://github.com/CasGoos/measurement_and_replication.git>), information on the reported measurement evidence and reporting quality was assessed for both replication protocols and original studies.
-Descriptions of the extracted variables can be found in the sections below.
-The coding protocol and explanations on how the articles and replication protocols were searched through to answer the questions in the coding protocol can be found in the coding protocols folder of the supplementary materials.
-
-### Measurement Error Measures
-
-In order to answer questions regarding reported reliability, the reported reliability coefficient was extracted from both the replication protocols and the original articles.
-The reported reliability coefficient is the score reliability reported per measure in the replication protocol or original article.
-Both the type (Cronbach's alpha, retest, interrater, etc.) and the value itself were extracted.
-
-Because data from the Many Labs replications was available for each lab location within a replication set, it was possible to not only calculate score reliabilities for the scalar measures used, but also calculate it for each lab location separately.
+A structured coding protocol (available on the relevant OSF: <https://osf.io/9r8yt/>, and github pages: <https://github.com/CasGoos/measurement_and_replication.git>) was used to extract information on the reported measurement evidence and reporting quality for both replication protocols and original studies.
+The coding protocol and explanation of its use can be found in the coding protocols folder of the supplementary materials.
+
+### Measures of Reliability
+
+Because data from the Many Labs replications was available for each lab location within a replication set, it was possible to calculate score reliabilities for the item scale measure used for each lab location separately.
 This made it possible to assess the variation of score reliabilities of the same measure across different contexts.
 
-Cronbach's alpha was calculated as the main score reliability index used in the analyses, as remains the most commonly used indicator of the reliability of a measure [@flake2017construct].
+Cronbach's alpha was calculated as the main score reliability index used in the analyses, as it remains the most commonly used indicator of the reliability of a measure [@flake2017construct].
+This is important for facilitating comparison between the calculated replication reliabilities and the reported original article reliabilities.
 Cronbach's alpha was calculated using the alpha function from the psych R package [@R-psych].
 Default arguments were used for the function.
+Omega was pre-registered as an additional reliability index score, because it is regarded by numerous psychometricians as a more informative alternative to Cronbach’s Alpha.
+The results based on Omega can be found in [Appendix C](AppendixScripts/Appendix_multilevel_analyses.Rmd).
 
@@
 
-### QMP measures
-
-The tests for hypotheses 4, 5, & 6 were all based on the QMPs coded across both original articles and replication protocols.
-QMPs were all coded to be either true, false, or not applicable if not relevant for that particular measure (e.g.
-reporting results from a factor analysis in case a single item measure was used).
-Questions related to modification had 'no modification' as an additional answer option, in case the specific aspect of the measure was explicitly not modified.
-Each coded QMP belonged to one of five QMP type categories that were derived from the classification in @flake2020measurement.
-An overview of the QMP categories of the coding variables can be seen in Table \@ref(tab:QMPCodingInfoTable).
+### Measures of Measurement Reporting
+
+In order to answer questions regarding reported reliability, the reported reliability coefficient of a measure was extracted from both the replication protocols and the original articles when present.
+Both the type (Cronbach's alpha, retest, interrater, etc.) and the value itself were extracted.
+Similarly, we coded the presence of any validity evidence, such as a factor analysis, alongside the measure.
+The aim here was to gauge the presence of factor analyses within the articles and protocols, for comparison with @shaw2020measurement.
+
+The tests for hypotheses 4, 5, & 6 were all based on the QMPs coded for both original articles and replication protocols.
+The QMPs we coded were in part based on @flake2022construct.
+Additional items were added to more fully reflect the broader questions regarding transparent measurement reporting laid out in @flake2020measurement.
+In total, we coded `r sum(colnames(coded_data_replications) == "def1" | colnames(coded_data_replications) == "op_1" | colnames(coded_data_replications) == "op_2" | colnames(coded_data_replications) == "op_3" | colnames(coded_data_replications) == "op_4" | colnames(coded_data_replications) == "op_5" | colnames(coded_data_replications) == "sel_1" | colnames(coded_data_replications) == "sel_2" | colnames(coded_data_replications) == "sel_3" | colnames(coded_data_replications) == "sel_4" | colnames(coded_data_replications) == "quant_1" | colnames(coded_data_replications) == "quant_2" | colnames(coded_data_replications) == "quant_3" | colnames(coded_data_replications) == "quant_4" | colnames(coded_data_replications) == "mod_1" | colnames(coded_data_replications) == "mod_2" | colnames(coded_data_replications) == "mod_3" | colnames(coded_data_replications) == "mod_4" | colnames(coded_data_replications) == "mod_5" | colnames(coded_data_replications) == "mod_6")` different QMPs, categorized into five QMP type categories based on @flake2020measurement.
+An overview of the QMP categories and items can be seen in Table \@ref(tab:QMPCodingInfoTable).
 
@@
 # making the column names look less robot speak-y.
-colnames(QMP_info_dataframe) <- c("CategorWy", "N Questions", "Example Question")
+colnames(QMP_info_dataframe) <- c("Category", "N Questions", "Example Question")
 
@@
   , caption = "Information of QMP coding variables per category."
-  , note = "N Questions refers only to the questions considered used for calculating QMP ratios."
+  , note = "N Questions refers only to the questions considered used for calculating QMP ratios.
+Selection and creation share a category as the justifications and requirements in selecting a measure are similar to those for creating a new measure."
   , escape = FALSE, placement= "htp", booktabs = TRUE)
@@
 
-Selection and creation share a category as the justifications and requirements in selecting a measure are similar to those for creating a new measure.
-Modification variables were only assessed when it was clear that the measure was modified from an original source in some way, and were otherwise omitted from the QMP calculations for that measure.
-
-Beside these quantitative variables, a total of four qualitative variables were also included to provide more detailed information on some aspects of the measure and its reporting.
-Further details on all the items used, their origin, changes, and justifications can be found in the coding protocol information supplementary materials.
-
-For the analyses of these variables both the total QMP ratios and ratios per QMP type category were used.
-This ratio was based on the number of coded trues divided by the total number of applicable QMPs.
-QMPs were considered applicable if not coded as not applicable or no modification.
-These ratios were preferred over counts, since non applicable items could thus be accounted for.
-Formula \@ref(eq:QMPRatioType) shows the formula that was used to calculate the QMP ratio for a particular QMP type j, where $True_{ij}$ is 1 if $item_{ij}$ was coded as True and 0 otherwise, and $False_{ij}$ is 1 if $item_{ij}$ was coded as False and 0 otherwise, $j \subset \{ definition, operationalisation, selection/creation, quanitification, modification \}$, and $i = 1,..., n_{j-items}$.
-
-```{=tex}
-\begin{equation}
-QMP\_ratio_{j} = \frac{\sum_{n=1}^i True_{ij}}{\sum_{n=1}^i True_{ij} + False_{ij}} (\#eq:QMPRatioType)
-\end{equation}
-```
-
-For the total QMP ratio:
-
-```{=tex}
-\begin{equation}
-QMP\_ratio = \frac{\sum_{n=1}^j \sum_{n=1}^i True_{ij}}{\sum_{n=1}^j \sum_{n=1}^i True_{ij} + False_{ij}} (\#eq:QMPRatioTotal)
-\end{equation}
-```
-
-After the data was initially coded according to the preregistered coding protocol, it was determined, based on discussion with the supervisor, that some of the initial ratings were possibly too stringent.
-As a result, some of the items in the protocol were reformulated, so that the conclusions from the resulting analyses were based on a more lenient judgement of QMPs.
-The revision of the coding protocol happened after all the data were coded using the initial protocol.
-As a result the coded data using the initial protocol, and the coded data using the revised protocol are both available on this article's OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages.
-The analyses, tables and figures presented in this article are all based on the revised coding protocol, the equivalent results based on QMPs obtained with the initial protocol can be found in Appendix D.
-
-### Replicability Measure
-
-Hypothesis 3 as well as 5 specify an association between either score reliability or QMPs respectively, and replication success.
-Replication success was based on the test of the main effect of a study.
-Since only primary measures were used to form the dataset, each measure related to the test of a main effect.
+QMPs were all coded to be either true, false, or not applicable if not relevant for that particular measure (e.g.
+reporting results from a factor analysis for single item measures).
+For the analyses a ratio was calculated based on the responses to the QMP questions.
+This ratio was based on the number of true responses divided by the number of responses coded to be applicable.
+The ratio was calculated for each QMP type and across all QMPs together.
+
+After the initial coding was completed, we made a small revision to the preregistered coding protocol.
+The protocol was changed because some items were considered too stringent in their criteria for what constituted a QMP.
+For example, in the initial protocol an example item had to be present within the article or protocol itself, or else this was counted as a QMP.
+In the revised protocol, references to online appendices with example items were also considered sufficient.
+The analyses, tables and figures presented in this article are all based on the revised coding protocol, the equivalent results based on QMPs obtained with the initial protocol can be found in [Appendix D](AppendixScripts/Appendix_initial_QMP_analyses.Rmd), the initial protocol data and analysis code is available on this article's OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages.
+
+### Measure of Replication Success
+
 Replication success was determined based on the significance of the meta-analytic effect of the replication set as reported in its respective Many Labs report.
-An effect was considered replicated if the meta-analytic p-value was lower than .05, and in the same direction as the original effect.
-In all cases, meta-analytic significance of an effect meant that support in the direction of the original effect was found.
+An effect was considered replicated if the meta-analytic effect was in the same direction as the original effect and had a p-value lower than .05.
 
@@
 ## graphs
+# plot for data visualization overview
+plot_data_structure_data <- data_prep_data_structure_plot(data_h4)
 # plot accompanying the results for Hypotheses 4, 5, & 6.
@@
 
+open_data(data = plot_data_structure_data, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(plot_data_structure_data))), ".csv"),
+  codebook = paste0(paste0(
+    "Data/AnalysisData/codebook_", 
+    deparse(substitute(plot_data_structure_data))), ".Rmd"),
+  value_labels = paste0(paste0(
+    "Data/AnalysisData/value_labels_", 
+    deparse(substitute(plot_data_structure_data))), ".yml"))
+
 open_data(data = plot_23_data_alpha, filename = paste0(paste0(
@@
 
-Every hypothesis test in this study used an alpha significance cutoff of .05.
-No correction for multiple testing was applied, to ensure that the rate of false negatives remained low, the increase in false positive rate was accepted as less harmful to the exploratory aims of this study.
-
-### Analyses Measurement Error
-
-The pre-registered test for hypothesis 1, a t-test of the reported Cronbach's alpha coefficient values between original and replication, could not be conducted, since not enough score reliabilities were reported to conduct the test and expect sensible results.
-Instead, the total number of reported reliability coefficients were compared between the replication protocols and the original articles.
-This comparison was tested via a chi-square test using the base R stats package [@R-base].
-
-```{r Hypothesis1Model, include = FALSE}
-# first some descriptives of reliability reporting
-# Measurement type per original and replication:
-H1_descriptive_table_1 <- table(data_h1$rep_org, data_h1$N_items)
-
-# amount of reliability reported per original and replication 
-# (given that measure is a multiple item measure):
-H1_descriptive_table_2 <- table(data_h1$rep_org[data_h1$N_items == "multiple item measure"], data_h1$reliability_type[data_h1$N_items == "multiple item measure"])
-
-# New H1 test
-# A chi square test for difference in N reliability reported for multiple 
-# item measures.
-H1_test_result <- chisq.test(data_h1$rep_org[data_h1$N_items == "multiple item measure"], data_h1$reliability_reported[data_h1$N_items == "multiple item measure"])
-
-```
-
-While reported reliabilities were rare, reliabilities could still be calculated from `r apa_num(length(unique(data_h3_multiple$g)), numerals = FALSE)` replication datasets.
-On top of that, reliabilities could be calculated for each individual lab per replication set so that the variance of the coefficients of a single measure could be assessed.
-In order to separate between and within variance in reliability, a multilevel random intercept model was specified with replication set as the grouping variable and the Cronbach's alpha value of a replication as dependent using the lmer function from the lme4 package [@R-lme4].
-The formulas for this model, where $alpha_{ij}$ represents the calculated Cronbach's alpha coefficient of a single study at one lab location with $i = 1,..., n_{locations}$ and $j = 1,...,n_{replicationsets}$ look as follows:
-
-```{=tex}
-\begin{align}
-& Level 1: alpha_{ij} = \beta_{0j} + e_{ij} \qquad\qquad\quad e_{ij} \sim N(0, \sigma_{e}^{2}) (\#eq:level1H2) \\
-& Level 2: \beta_{0j} = \gamma_{00} + u_{0j} \qquad\qquad\qquad u_{0j} \sim N(0, \sigma_{u0}^{2}) (\#eq:level2H2) \\
-& Mixed: alpha_{ij} = \gamma_{00} + u_{0j} + e_{ij} (\#eq:mixedH2)
-\end{align}
-```
-```{r Hypothesis2Model, include = FALSE}
-# intercept only model to check the within and between group variance.
-H2_test_result_alpha <- lmer(formula = alpha ~ 1 + (1|g), data = data_h2)
-
-```
-
-The main author was not aware of the existence of any formal test as of the writing of the pre-regsitration for testing for within group variance after controlling for between group variance.
-Thus, the intraclass correlation (ICC) coefficient was pre-registered as the indicator of within vs.
-between variability.
-The formula used to calculate the ICC is presented below.
-
-```{=tex}
-\begin{equation}
-ICC = \frac{u_{0j}}{(e_{ij} + u_{0j})} (\#eq:ICC)
-\end{equation}
-```
-A high ICC indicates low within group variance relative to between group variance, which would be in line with hypothesis 2.
-
-```{r ICCCalculations, include = FALSE}
-# Variances
-within_group_variance_alpha <- attr(VarCorr(H2_test_result_alpha), "sc")^2
-between_group_variance_alpha <- attr(VarCorr(H2_test_result_alpha)$g, "stddev")^2
-
-# ICC
-ICC_alpha <- between_group_variance_alpha / (within_group_variance_alpha + between_group_variance_alpha)
-
-```
-
-After data had been collected and analysed, it came to the author's attention a meta-analyses could be conducted on reliability coefficients, commonly referred to as Reliability Generalization Meta-Analyses [@botella2012ManagingHeterogeneityVariance; @lopez-ibanez2024ReliabilityGeneralizationMetaanalysis].
-Using meta-analysis, it is possible to quantify within the model the degree of true variation in the metric of interest across samples [@cooper2019handbook].
-
-In order to test whether or not the true variation in the metric, or heterogeneity, constituted a significant part of the total variation in the observed estimates of the metric or not, a random-effects meta-analysis was conducted on the calculated Cronbach's alpha for each measure for which replication datasets were available and usable.
-The rma function from metafor package [@R-metafor] was used to run the meta-analysis.
-No correction for bias or weighting of the effects was implemented, to reduce model complexity, and because the data from the Many Labs replication projects do not reflect a typical literature.
-
-A meta-analysis requires an estimate of the standard error in order to be conducted.
-For Cronbach's alpha, formulas 2 & 3 from @duhachek2004AlphaStandardError were used to calculate alpha's standard error.
-Heterogeneity was estimated using the tau value, meaning the standard deviation of the distribution of true Cronbach's alpha coefficients for that measure, and tested using the Cochran's Q test for each measure.
-
-In order to test the association between reliability and replicability that had been indicated by @stanley2014expectations on non-simulated data, the calculated reliabilties were used as a predictor for the coded replication success of the effect the measure was used for.
-The logistic regression shown in equation \@ref(eq:H3Main) was used to model this association, where $f(.)$ represents the logit link function, $i = 1,..., n_{replications}$, the outcome $replicated$ which was coded as 1 if the meta-analytic effect in the replication set matches the original effect in direction at a significance alpha level of .05, and 0 otherwise, and the predictor $alpha$ referred to the averaged calculated Cronbach's alpha coefficient:
-
-```{=tex}
-\begin{equation}
-f(replicated_{i}) = \beta_{0} + \beta_{1} alpha_{i} (\#eq:H3Main)
-\end{equation}
-```
-```{r Hypothesis3MainTest, include = FALSE}
-## The main model to test hypothesis 3, through a logistic regression model.
-H3_test_result_main_alpha <- apa_print(glm(formula = replication ~ 1 + alpha, 
-                                      family = binomial(), data = data_h3_avg))
-
-# coefficient is positive but not significant.
-
-# adding OR to the result
-H3_main_full_results_alpha_with_OR <- OR_to_apa_full_supplier(H3_test_result_main_alpha$full_result$alpha, negative_b = FALSE)
-
-# well this OR is quite a ridiculous number now..., but then again a step from 0 alpha to 1, is quite a jump too...
-
-```
-
-### Analyses QMPs
-
-The reported analyses were primarily based on the revised set of QMP data.
-The results using the original QMP data are mentioned when the results led to different conclusions.
-The analysis code for both the original and revised QMP data are available in the R script on both the OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages of this article.
-
-Hypothesis 4 & 6 were both tested using a model with the same dependent variable: total QMP ratio.
-In order to model a ratio dependent variable, beta regression was used.
-Beta regression models operate similarly to standard generalized linear models with similar interpretations of the results.
-What differentiates them is that they are suitable to model dependent variables with values in the interval of $(0, 1)$, meaning ratios.
-Furthermore, they are well suited for modelling heteroskedastic and asymmetrically distributed dependent variables [@cribari2010beta].
-The beta regression model was implemented using the betareg function within the betareg package [@R-betareg_a; @R-betareg_b].
-Defaults were used for all function parameters besides the model formula and data.
-All beta regression models used the beta link function, which is as follows:
-
-```{=tex}
-\begin{equation}
-g(.) = (0, 1) \mapsto \mathbb{R} (\#eq:BetaLink)
-\end{equation}
-```
-
-These models assume that the QMPs are the same across each replication set.
-This was necessary as only one protocol was available for coding per replication set.
-The assumption was deemed likely to hold, since each replication within a set was based on the same protocol containing all the measurement details that were reported and upon which measurement was based.
-
-To test hypothesis 4, the total QMP ratios between replication and original research was compared. The model formula for this test looked as follows:
-
-```{=tex}
-\begin{equation}
-g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replication_{i} (\#eq:H4Main)
-\end{equation}
-```
-```{r Hypothesis4Model, include = FALSE}
-## Hypothesis 4 beta regression model
-# running the models with revised QMP ratio's
-H4_test_results_REV <- betareg(QMP_REV_ratio ~ rep_org, data = data_h4)
-
-```
-
-Where $replication_{i}$ is a dummy coded variable, which was coded as 1 in case the reported QMP ratio belonged to a replications, and 0 if it belonged to an original study.
-For hypothesis 5 the QMP ratio was used as the predictor for replication success, while replication success was used as the outcome.
-
-```{=tex}
-\begin{equation}
-logit(replicated_{i}) = \beta_{0} + \beta_{1} QMP\_ratio_{i} (\#eq:H5Main)
-\end{equation}
-```
-
-Where $replicated$ is a dummy coded variable, which is the same as for equation \@ref(eq:H3Main), and $logit(.)$ refers to the logit link function commonly used for logistic regression models.
-Note here that unlike in the test for hypothesis 4, $QMP\_ratio_{i}$ refers only to the QMP ratios of the replications, meaning that original article QMPs were not included in this analysis.
-
-```{r Hypothesis5Model, include = FALSE}
-## Hypothesis 5 logistic regression model
-H5_test_results_REV <- apa_print(glm(hypothesis_support ~ QMP_REV_ratio, data = data_h5, family = binomial))
-
-H5_test_results_REV_with_OR <- OR_to_apa_full_supplier(H5_test_results_REV$full_result$QMP_REV_ratio, negative_b = TRUE)
-
-```
-
-The relationship between original article QMPs and replication protocol QMPs was modeled to test hypothesis 6.
-The outcome variable is the same as the predictor in the model for hypothesis 5.
-The independent variable in this model is instead the QMP ratio for the original articles[^4].
-The resulting model formula is as follows:
-
-[^4]: This analysis was not pre-registered.
-Only the analyses for each combination of QMP types were pre-registered and can be found in appendix A, however all analyses of hypothesis 6 were originally planned to use contingency tables with no inferential test.
-This was changed quickly after the study was pre-registered to using beta-regression as is done here and in appendix A.
-
-```{=tex}
-\begin{equation}
-g(QMP\_ratio\_replication_{i}) = \beta_{0} + \beta_{1} QMP\_ratio\_original_{i} (\#eq:H6Main)
-\end{equation}
-```
-```{r Hypothesis6Model, include = FALSE}
-## Hypothesis 6 beta regression model
-H6_test_results_REV <- betareg(Rep_QMP_REV_ratio ~ QMP_REV_ratio, data = data_h6)
-
-```
+Every hypothesis test in this study was a two-sided test with an alpha of .05.
+No correction for multiple testing was applied, to ensure that the rate of false negatives remained low.
+False negatives were considered more harmful than false positives, because with our hypothesis tests we exploratively investigated associations that have been alluded to in the literature, but not yet empirically tested.
 
@@
 
-## Data Visualization
-This study's focus is mainly exploratory and descriptive.
-Additionally, the number of coded and extracted data is quite substantial.
-Therefore, the result section will start with a number of descriptives and figures to provide an overview of the data.
-
-Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts the flow of measures for which reliability was reported.
-The first split shows the number of measures which consisted of multiple items in a scale, which were approximately equal between replication and original (`r apa_num(table(coded_data_replications$N_items)["multiple item measure"])` and `r apa_num(table(coded_data_original_shortened$N_items)["multiple item measure"])`, respectively).
-Reliability was expected to be reported only for these measures.
-Taking these multiple item measures, the graph illustrates that `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` measures in the replication protocols and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles reported a reliability coefficient.
-Looking closer at these reported reliability coefficients, it can be seen in the graph that the most commonly reported coefficient was the Cronbach's alpha, which accounted for `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles.
-
-```{r ReliabilityReportingFlowDiagram, fig.cap = "Reliability reporting flow diagram.
-Figure shows the number of measures as reported in both the replication protocols and original article, which meet the criterion in the box within the diagram and those criteria before it."}
-knitr::include_graphics(path = "../../SupplementaryMaterials/reliability_reporting_flow_diagram.png")
-```
-
-If scalar data could be accessed for a measure, the reliability could also be calculated from the replication data for each lab.
-The distributions of the Cronbach's alpha coefficients for each replication set are displayed in figure \@ref(fig:Plot23AlphaCode), separated by successful and unsuccessful replication.
+## Descriptives
+
+The number of replication sets, measures, and measures per study that were extracted, as well as the ratio of successful replications can be seen in Table \@ref(tab:ReplicationRatioTable), for each of the Many Labs separately and in total.
+
+```{r ReplicationRatioTable, warning = FALSE}
+# construct the replication ratio table to be printed
+replication_ratio_table <- data.frame("Many Labs Version" = c("1", "2", "3", "5", "Total"),
+                                      "N Total" = c(table(coded_data_replications$many_labs_version), nrow(coded_data_replications)), 
+                                      "N Replicated" = c(table(coded_data_replications$many_labs_version, coded_data_replications$hypothesis_support)[, "Yes"], table(coded_data_replications$hypothesis_support)["Yes"]))
+
+# calculate the replication ratio from the N measures whose studies were replicated
+# and the N total measures, per Many Labs study.
+replication_ratio_table$"Replication Ratio" <- round(replication_ratio_table$N.Replicated / replication_ratio_table$N.Total, digits = 2)
+
+# Changing column names to be less computer speak-y looking
+colnames(replication_ratio_table) <- c("Many Labs Version", "Nr. Measures$^a$", 
+                                       "Nr. Replicated", "Replication Ratio")
+
+# converting columns to string to then add a superscript to one of the elements
+# in the table.
+replication_ratio_table$"Nr. Replicated" <- as.character(replication_ratio_table$"Nr. Replicated")
+
+# adding a superscript for a later footnote
+replication_ratio_table$"Nr. Replicated"[3] <- "$3^b$"
+
+# print the table in apa formatting
+apa_table(
+  replication_ratio_table, align = c("l", "r", "r", "r")
+  , caption = "Ratio of measures for which the effect was considered replicated, across many labs projects"
+  , note = "Nr.
+measures refers to the total number of measures extracted, while Nr.
+replicated displays the number of measures for which the associated effect was replicated succesfully.
+$^a$ refers only to the number of identified primary measures, which this study is concerned with.
+$^b$replication was assessed as unclear for three other measures, since their effect was only partially replicated.
+These have been treated as not replicated within this table and further analyses throughout the article.
+"
+  , escape = FALSE, placement = "htp", midrules = 4)
+
+```
+
+The number of participants in the replication studies, and the associated articles are displayed in Figure \@ref(fig:DataStructurePlotCode).
+As might be expected, the Many Labs replications always had larger sample sizes than the original articles.
+Furthermore, the figure shows that the replications are nested in Many Labs projects, and for some replications multiple measures were used within one replication.
+
+```{r DataStructurePlotCode, warning = FALSE, fig.cap = "This figure displays the sample size for the included original articles and total sample size for multiple replications.
+The color of the point indicates whether it represents an original article or a replication.
+The point's shape relates to whether the hypothesis was supported or not, while the size indicates the number of measures for that article or replication.
+The figure is log10-scaled, each light grey vertical line represents a step of 500 in sample size.
+Two original articles are not represented in this figure due to them containing no reported sample size.", fig.height = 3.5, fig.width = 12}
+
+# plot of the multilevel data structure
+ggplot(plot_data_structure_data, aes(x = N, y = factor(many_labs_version, levels = c("5", "3", "2", "1")), 
+                                colour = rep_org, shape = hypothesis_support, size = measure_count)) +
+  geom_point(alpha = .33) +
+
+  scale_x_continuous(trans = "log10", breaks = c(10, 100, 1000, 10000), 
+                     labels = c(10, 100, 1000, 10000), limits = c(10, 10000),  
+                     minor_breaks = seq(500, 10000, 500)) +
+
+  theme_minimal() +
+  theme(plot.margin = unit(c(1, 6.5, 1, 1), "lines"), 
+        panel.grid.major.x = element_line(color = "grey",
+                                          size = 0.5,
+                                          linetype = 1)) +
+
+  guides(color = guide_legend(nrow = 1, byrow = TRUE)) +
+  guides(shape = guide_legend(nrow = 2, byrow = TRUE)) +
+  guides(size = guide_legend(nrow = 2, byrow = TRUE)) +
+
+  labs(x = "N", y = "Many Labs Version", color = "Obtained from:", 
+       size = "Nr. measures", shape = "Replicated")
+
+```
+
+## Measurement Reliability
+
+If data from a multiple item scale could be accessed, the Cronbach’s Alpha of that scale was calculated from that data for each lab that administered the scale.
+As a result, it was possible to include the multiple estimates of Cronbach’s Alpha into a meta-analysis of the reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analyses [@vacha-haase1998ReliabilityGeneralizationExploring; @botella2012ManagingHeterogeneityVariance; @lopez-ibanez2024ReliabilityGeneralizationMetaanalysis], for each of the measures.
+This enabled us to quantify the degree of true variation (or heterogeneity) in reliability coefficients across different studies.
+
+A meta-analysis requires an estimate of the standard error.
+For Cronbach's alpha, formulas 2 & 3 from @duhachek2004AlphaStandardError were used to calculate its standard error.
+Heterogeneity was estimated using the tau value, which indicates the standard deviation of the distribution of true Cronbach's alpha coefficients for a measure, and tested using the Cochran's Q test for each measure.
+
+The RG meta-analysis was performed using the *rma* function from the *metafor* R package [@R-metafor].
+Defaults settings were used.
+No correction for bias was implemented, because the Many Labs replications were not at risk of publication bias.
+
 The average calculated Cronbach's alpha coefficient across replication sets was `r apa_num(mean(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$alpha, na.rm = TRUE), digits = 3)`.
+Figure \@ref(fig:Plot23AlphaCode) displays the distributions of the calculated Cronbach’s Alpha scores from each lab for each measure, separated by successful and unsuccessful replication.
 
@@
 ```
-
-When comparing the reported reliabilities with the calculated reliabilities displayed in figure \@ref(fig:Plot23AlphaCode), all but `r apa_num(sum(plot_23_data_reported_alpha$coefficient_difference > 0), numerals = FALSE)` of the reported reliabilities are in the lower half of the distribution of the calculated reliabilities within their own measure.
-However when looking across the measures, the mean of the distribution of the calculated coefficients of all but `r apa_num(sum(aggregate(plot_23_data_alpha_reordered$alpha, list(plot_23_data_alpha_reordered$g), FUN = mean)[plot_23_data_reported_alpha$article_order,2] <= mean(data_h3_multiple$alpha)), numerals = FALSE)` of the measures that had a reported reliability coefficient was larger than the mean calculated Cronbach's alpha.
 
@@
 
-In order to visualize the results on QMPs, the proportions of the QMP ratio obtained for each QMP type (see Table \@ref(tab:QMPCodingInfoTable)) are shown across the top layer of Figure \@ref(fig:Plot456Code) for both replication protocols and original articles.
-While in the bottom layer of Figure \@ref(fig:Plot456Code) the overlayed distributions of the total QMP ratios from the replication protocols and original studies are displayed, with dots indicating each datapoint, and the line indicating the mean for either distribution.
-A large number of QMP ratios are missing for the QMP modification type , because only `r apa_num(table(coded_data_replications$mod_check_REV)["True"])` out of `r apa_num(nrow(coded_data_replications))` measures in replications, and only `r apa_num(table(coded_data_original_shortened$mod_check_REV)["True"], numerals = FALSE)` measures used in original studies were modified.
+The distribution of the measures varies highly.
+Most of the measures near the bottom show average reliability scores of at least .80, corresponding to an adequate reliability for general research purposes [@nunnally1994assessment], with minimal variation between labs.
+However, other measures show not only considerably lower average reliability scores, but also greater variation.
+
+Finally, the blue triangles indicate the reported Cronbach’s Alpha.
+Noteworthy here is that the reliabilities were generally only reported for those measures with a large average calculated reliability.
+
+### H1
+
+Initially, a Mann-Whitney U test was planned to test whether or not the value of the reported Cronbach’s Alpha was different for replications compared to original articles.
+However, there were not enough reported reliabilities to perform the test.
+However, if we take an exploratory look at Figure 2, we can see the difference between the reported reliability in the original article and the calculated average reliability in replications in the Diff column.
+The results show that the original article reliability is generally lower than the average calculated reliability of the same measure.
+These results are not in line with H1.
+However, more than half of the reported reliabilities fell within the 95 percentile range around the average.
+
+### H2
+
+We used the RG meta-analyses to test if there was heterogeneity in these estimates, which would give us an indication of the true variability in these reliability scores.
+This analysis was not preregistered, because we were not aware of this technique at the time of preregistering.
+
+Figure \@ref(fig:Plot23AlphaCode) displays the tau score for each measure’s Cronbach’s Alpha, which indicates the true differences in reliability scores between labs.
+For some measures the tau estimate was approximately 0.
+But this was certainly not the case for all measures.
+For instance, for the top measure the Tau estimate was .108.
+This means that for the true effect one standard deviation is equal to .108 points of Cronbach’s Alpha.
+This estimate is without variance cause by sampling error.
+Figure \@ref(fig:Plot23AlphaCode) shows that for `r sum(data_h3_avg$QEp < .05)` out of the `r nrow(data_h3_avg)` measures, the Q-test for heterogeneity indicated that the true variation in reliability estimates was significant.
+
+These results would indeed indicate that for several measures in our sample, the reliability of the measures is heterogeneous, thus showing evidence in favor of rejecting H2.
+However, these results need to be taken with a grain of salt.
+Some of the measures had a lower number of studies and the Q-test is sensitive to sample size [@li2015DilemmaHeterogeneityTests].
+Furthermore, the evidence remains inconsistent when looking across all measures.
+
+### H3
+
+Figure \@ref(fig:Plot23AlphaCode) additionally indicates whether or not the measures were part of a successful or failed replication.
+A logistic regression model was used to test whether there was a significant difference in the average calculated reliability coefficient value based on whether or not the associated replication was successful or not based on the meta-significance of the effect.
+
+```{r Hypothesis3MainTest, include = FALSE}
+## The main model to test hypothesis 3, through a logistic regression model.
+H3_test_result_main_alpha <- apa_print(glm(formula = replication ~ 1 + alpha, 
+                                      family = binomial(), data = data_h3_avg))
+
+# coefficient is positive but not significant.
+
+# adding OR to the result
+H3_main_full_results_alpha_with_OR <- OR_to_apa_full_supplier(H3_test_result_main_alpha$full_result$alpha, negative_b = FALSE)
+
+# well this OR is quite a ridiculous number now..., but then again a step from 0 alpha to 1, is quite a jump too...
+
+```
+
+Contradictory to hypothesis 3, the logistic model indicated that Cronbach's alpha did not significantly relate to replication success in the main logistic regression model (Cronbach's alpha: `r H3_main_full_results_alpha_with_OR`).
+However, it should be noted that the reliability coefficient could be calculated for only a small sample number of measures.
+As a result, the estimates of the relation between reliability and replication success obtained using these models each come with large uncertainty.
+
+## Measurement Reporting
+
+### Reliability & Validity Reporting
+
+Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts the flow of measures in relation to reliability reporting.
+First of all, it shows that almost half of the measures in both replication (n = `r apa_num(table(coded_data_replications$N_items)["1 item measure"])`) and original research (n = `r apa_num(table(coded_data_original_shortened$N_items)["1 item measure"])`) were single item measures.
+When looking at the multiple item measures, the graph illustrates that `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` measures in the replication protocols and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles reported a reliability coefficient.
+The most commonly reported reliability coefficient was Cronbach's alpha, which accounted for `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles.
+
+```{r ReliabilityReportingFlowDiagram, fig.cap = "Reliability reporting flow diagram.
+Figure shows the number of measures as reported in both the replication protocols and original article, which meet the criterion in the box within the diagram and those criteria before it."}
+knitr::include_graphics(path = "../../SupplementaryMaterials/reliability_reporting_flow_diagram.png")
+```
+
+```{r Hypothesis1Model, include = FALSE}
+# first some descriptives of reliability reporting
+# Measurement type per original and replication:
+H1_descriptive_table_1 <- table(data_h1$rep_org, data_h1$N_items)
+
+# amount of reliability reported per original and replication 
+# (given that measure is a multiple item measure):
+H1_descriptive_table_2 <- table(data_h1$rep_org[data_h1$N_items == "multiple item measure"], data_h1$reliability_type[data_h1$N_items == "multiple item measure"])
+
+# New H1 test
+# A chi square test for difference in N reliability reported for multiple 
+# item measures.
+H1_test_result <- chisq.test(data_h1$rep_org[data_h1$N_items == "multiple item measure"], data_h1$reliability_reported[data_h1$N_items == "multiple item measure"])
+
+```
+
+Reliability was more commonly reported in original as compared to replication research ($\chi^{2}$(`r apa_num(H1_test_result$parameter)`) = `r apa_num(H1_test_result$statistic)`, *p* = `r apa_p(H1_test_result$p.value)`).
+Validity evidence was similarly reported infrequently.
+The number of original articles that reported validity evidence from a factor analysis was `r sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")`, for replications this number was `r sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")`.
+
+### H4
+
+```{r numberNAsForQMPRatio}
+ratio_of_NAs <- sum(is.na(data_h4$def1) + is.na(data_h4$op_1_REV) + is.na(data_h4$op_2_REV) + is.na(data_h4$op_3) + is.na(data_h4$op_4) + is.na(data_h4$op_5_REV) + is.na(data_h4$sel_1_REV) + is.na(data_h4$sel_1) + is.na(data_h4$sel_2) + is.na(data_h4$sel_3_REV) + is.na(data_h4$sel_4) + is.na(data_h4$quant_1_REV) + is.na(data_h4$quant_2_REV) + is.na(data_h4$quant_3_REV) + is.na(data_h4$quant_4) + is.na(data_h4$mod_1_REV) + is.na(data_h4$mod_2_REV) + is.na(data_h4$mod_3_REV) + is.na(data_h4$mod_4_REV) + is.na(data_h4$mod_5_REV) + is.na(data_h4$mod_6_REV)) / (20 * 154)
+
+QMP_NA_percentage <- paste0(apa_num(ratio_of_NAs * 100), "%")
+
+```
+
+```{r MeanQMPCode, warning = FALSE, include = FALSE}
+# calculating mean total QMP ratios
+Mean_Rat_Rep <- mean(plot_456_data$QMP_ratio_REV[
+  plot_456_data$QMP_type == "Total" & plot_456_data$RepOrg == "Replication"])
+Mean_Rat_Org <- mean(plot_456_data$QMP_ratio_REV[
+  plot_456_data$QMP_type == "Total" & plot_456_data$RepOrg == "Original"])
+```
+
+The bottom of Figure \@ref(fig:Plot456Code) displays the distributions of the total QMP ratio for both original articles and replication protocols.
+Here we can see that the average QMP ratio in replication protocols is smaller (`r apa_num(Mean_Rat_Rep)`) than in original articles (`r apa_num(Mean_Rat_Org)`).
+The top of Figure \@ref(fig:Plot456Code) shows that original articles and replication protocols had different distributions of QMPs per category.
+The number of measures for which modification items were applicable also differed.
+In total `r QMP_NA_percentage` of all responses across all QMP items were non-applicable.
 
@@
 levels(plot_456_data$RepOrg) <- c("Original", "Replication")
-
-# calculating mean total QMP ratios
-Mean_Rat_Rep <- mean(plot_456_data$QMP_ratio_REV[
-  plot_456_data$QMP_type == "Total" & plot_456_data$RepOrg == "Replication"])
-Mean_Rat_Org <- mean(plot_456_data$QMP_ratio_REV[
-  plot_456_data$QMP_type == "Total" & plot_456_data$RepOrg == "Original"])
 
@@
 
-Table \@ref(tab:MeasurementReportingDescriptivesTable) shows additional descriptive information on measurement reporting based on counts of reported information that were not used to calculate QMP ratios.
-When it was not stated that existing materials were used, it was expected that the remaining articles would clearly specify that they newly created the materials, however this was not always the case for neither original articles (`r table(coded_data_original_shortened$sel_existing)[["False, materials were newly developped for this study"]]` out of `r nrow(coded_data_original_shortened) - table(coded_data_original_shortened$sel_existing)[["True, namely:"]]` relevant measures) nor replication protocols (`r table(coded_data_replications$sel_existing)[["False, materials were newly developped for this study"]]` out of `r nrow(coded_data_replications) - table(coded_data_replications$sel_existing)[["True, namely:"]]` relevant measures).
-
-```{r MeasurementReportingDescriptivesTable}
-# construct the replication descriptives table to be printed
-reporting_descriptives_table <- data.frame("Original Article" = c(length(coded_data_original_shortened$op_version[coded_data_original_shortened$op_version != ""]), table(coded_data_original_shortened$sel_existing)[["True, namely:"]], table(coded_data_original_shortened$sel_existing)[["False, materials were newly developped for this study"]], sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), table(coded_data_original_shortened$mod_check_REV)[["True"]], sum(coded_data_original_shortened$mod_time == "After/During"), nrow(coded_data_original_shortened)),
-                                             "Replication Protocol" = c(length(coded_data_replications$op_version[coded_data_replications$op_version != ""]), table(coded_data_replications$sel_existing)[["True, namely:"]], table(coded_data_replications$sel_existing)[["False, materials were newly developped for this study"]], sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), table(coded_data_replications$mod_check_REV)[["True"]], sum(coded_data_replications$mod_time == "After/During"), nrow(coded_data_replications)))
-
-# Changing rownames to reflect the variables
-rownames(reporting_descriptives_table) <- c("Specified measure version", "Used existing materials", "Specified being newly created", "Reported validity evidence", "N modified", "Modified after/during data collection", "Total")
-
-# Changing column names to be less robot speak
-colnames(reporting_descriptives_table) <- c("Original Article", "Replication Protocol")
-
-# converting columns to string to then add a superscript to one of the elements
-# in the table.
-reporting_descriptives_table$"Replication Protocol" <- as.character(reporting_descriptives_table$"Replication Protocol")
-
-# adding a superscript for a later footnote
-reporting_descriptives_table$"Replication Protocol"[3] <- "$1^a$"
-
-# print the table in apa formatting
-apa_table(
-  reporting_descriptives_table, align = c("l", "r", "r")
-  , caption = "Descriptives of Measurement Reporting Variables not used for calculating QMP Ratios for both Original Articles and Replication Protocols"
-  , note = "$^a$ the relevant question asking participants to rate how much they agreed with a certain quote remained the same, however the quote itself and the people it was attributed too were both completely new compared to the original"
-  , escape = FALSE, placement = "htp", midrules = 6)
-
-```
-
-Finally, table \@ref(tab:ReplicationRatioTable) displays the proportion of replication success based on the criteria of a meta-significance cutoff smaller than .05 per Many Labs project.
-
-```{r ReplicationRatioTable, warning = FALSE}
-# construct the replication ratio table to be printed
-replication_ratio_table <- data.frame("Many Labs Version" = c("1", "2", "3", "5", "Total"),
-                                      "N Total" = c(table(coded_data_replications$many_labs_version), nrow(coded_data_replications)), 
-                                      "N Replicated" = c(table(coded_data_replications$many_labs_version, coded_data_replications$hypothesis_support)[, "Yes"], table(coded_data_replications$hypothesis_support)["Yes"]))
-
-# calculate the replication ratio from the N measures whose studies were replicated
-# and the N total measures, per Many Labs study.
-replication_ratio_table$"Replication Ratio" <- round(replication_ratio_table$N.Replicated / replication_ratio_table$N.Total, digits = 2)
-
-# Changing column names to be less computer speak-y looking
-colnames(replication_ratio_table) <- c("Many Labs Version", "N Total", "N Replicated",
-                                       "Replication Ratio")
-
-# converting columns to string to then add a superscript to one of the elements
-# in the table.
-replication_ratio_table$"N Replicated" <- as.character(replication_ratio_table$"N Replicated")
-
-# adding a superscript for a later footnote
-replication_ratio_table$"N Replicated"[3] <- "$3^a$"
-
-# print the table in apa formatting
-apa_table(
-  replication_ratio_table, align = c("l", "r", "r", "r")
-  , caption = "Ratio of measures for which the effect was considered replicated, across many labs projects"
-  , note = "$^a$replication was assessed as unclear for three of the measures, since their effect was not fully replicated.
-These have been treated as not replicated within this table and further analyses throughout the article"
-  , escape = FALSE, placement = "htp", midrules = 4)
-
-```
-
-## Reliability
-Figure \@ref(fig:ReliabilityReportingFlowDiagram) illustrates that multiple item measures are most commonly not accompanied by a reported reliability coefficient in neither original articles (`r sum(coded_data_original_shortened$reliability_type[coded_data_original_shortened$N_items == "multiple item measure"] != "Not Reported")` out of `r sum(coded_data_original_shortened$N_items == "multiple item measure")` multiple item measures) nor replication protocols (`r sum(coded_data_replications$reliability_type[coded_data_replications$N_items == "multiple item measure"] != "Not Reported")` out of `r sum(coded_data_replications$N_items == "multiple item measure")` multiple item measures).
-Additionally, when comparing between the two using a chi square comparison, it was observed that reliability coefficients are reported significantly less often in replication protocols than in original articles ($\chi^{2}$(`r apa_num(H1_test_result$parameter)`) = `r apa_num(H1_test_result$statistic)`, *p* = `r apa_p(H1_test_result$p.value)`).
-These results are contradictory to hypothesis 1, which predicted the opposite.
-
-The ICC of the between-group (across different replication set) variance and within-group (lab locations within a replication set) variance in the Cronbach's alpha coefficient was approximately `r apa_num(ICC_alpha, digits = 3)`.
-Because this number is larger than .5, it suggests that the majority of the total variance in the calculated Cronbach's alpha was between replication sets rather than within.
-
-A more sophisticated, albeit not pre-registered, exploratory analysis was also performed using a meta-analysis of the calculated reliability coefficients.
-The tau score (the indicator of true differences in reliability scores between labs) is displayed for each replication set's calculated Cronbach's alpha coefficients in Figure \@ref(fig:Plot23AlphaCode).
-The tau scores vary considerably between replication sets, some had a Tau estimate of approximately 0, while others were above .1.
-The latter result implies that for the measurements on that replication set, the standard deviation of the distribution of true reliability coefficients between the replications from various lab locations was more than .1 point of Cronbach's alpha [@cooper2019handbook].
-Based on the Q-test for heterogeneity, `r sum(data_h3_avg$QEp < .05)` out of the total of `r nrow(data_h3_avg)` estimates of heterogeneity were significant.
-
-However, since the Q-test is sensitive to the number of studies in the meta-analyses [@li2015DilemmaHeterogeneityTests], some of the discrepancy in the estimate of heterogeneity based on this test may in part be due to the fact that for some measures the sample size of labs that used them was too low.
-Therefore, while consistent evidence for heterogeneity would imply true variance in Cronbach's alpha within replication sets would run counter to hypothesis 2, the evidence is inconsistent when looking across all studies, and remains sensitive to the sample size in the meta-analyses.
-
-Figure \@ref(fig:Plot23AlphaCode) further shows whether the replication sets were successful when judged at a meta-analytic significance level of .05, or not.
-A logistic regression was performed to detect if the calculated reliabilities related to the replication success.
-
-The logistic model indicated that Cronbach's alpha did not significantly relate to replication success in the main logistic regression model (Cronbach's alpha: `r H3_main_full_results_alpha_with_OR`).
-Similar results were found based on the calculated omega coefficient (see Appendix C) and in all of the multilevel sensitivity analyses models (see Appendix B).
-These results are contradictory to the expectation in hypothesis 3.
-However, the reliability coefficient could be calculated for only a small sample number of measures.
-As a result, the estimates of the relation between reliability and replication success obtained using these models each come with large uncertainty and remains inconclusive.
-
-## Questionable Measurement Practices
-
-The bottom pannel of Figure \@ref(fig:Plot456Code) already shows that original articles contained a significantly larger proportion of QMPs than replication protocols for the measures of the same effects.
-Beta-regression was used to test the difference in QMP ratio between original articles and replication protocols.
+In order to test whether this difference is significant, a beta-regression model was used.
+Beta regression models are similar to other generalized linear regression models.
+Beta-regression is suited to model dependent variables with values in the interval of $(0, 1)$, including ratios.
+Furthermore, they are robust for heteroskedastic and asymmetrically distributed dependent variables [@cribari2010beta].
+The beta regression model was implemented using the betareg function within the betareg package [@R-betareg_a; @R-betareg_b] with default parameters.
+
+```{r Hypothesis4Model, include = FALSE}
+## Hypothesis 4 beta regression model
+# running the models with revised QMP ratio's
+H4_test_results_REV <- betareg(QMP_REV_ratio ~ rep_org, data = data_h4)
+```
+
+Using a beta-regression model, the total QMP ratio was regressed on a dummy variable indicating whether the coded report was an original article or a replication protocol.
 The results of indicated that this difference was significant (`r betareg_output_to_apa_full(H4_test_results_REV)`).
@@
 
+### H5
+
+```{r Hypothesis5Model, include = FALSE}
+## Hypothesis 5 logistic regression model
+H5_test_results_REV <- apa_print(glm(hypothesis_support ~ QMP_REV_ratio, data = data_h5, family = binomial))
+
+H5_test_results_REV_with_OR <- OR_to_apa_full_supplier(H5_test_results_REV$full_result$QMP_REV_ratio, negative_b = TRUE)
+
+```
+
 A logistic regression model was used to test the association between the QMP ratio in replication protocols and replication success.
-Results showed that a decrease in the ratio of QMPs in replication protocols significantly related to successful replication (`r H5_test_results_REV_with_OR`).
+In line with hypothesis 5, results showed that a decrease in the ratio of QMPs in replication protocols significantly related to successful replication (`r H5_test_results_REV_with_OR`).
+
+### H6
+
+```{r Hypothesis6Model, include = FALSE}
+## Hypothesis 6 beta regression model
+H6_test_results_REV <- betareg(Rep_QMP_REV_ratio ~ QMP_REV_ratio, data = data_h6)
+
+```
+
+The relation between QMP ratios in the replication protocols and corresponding original articles were investigated using a beta regression model.
+Total QMP ratio in the original article was found to be significantly related to the total QMP ratio in the subsequent replication (`r betareg_output_to_apa_full(H6_test_results_REV)`).
+This result provides evidence in favor of hypothesis 6.
+Figure \@ref(fig:Plot46RevisedDataCode) displays this relationship visually.
 
@@
   xlab("QMP Ratio (Original Article)")
-```
-
-The relation between QMP ratios in the replication protocols and corresponding original articles were investigated using a beta regression model.
-It showed that total QMP ratio in the original article can significantly relates to the total QMP ratio in the subsequent replication (`r betareg_output_to_apa_full(H6_test_results_REV)`), which provides some evidence in favor of hypothesis 6.
-Figure \@ref(fig:Plot46RevisedDataCode) displays this relationship visually.
+
+```
 
@@
 
-In the current study, measurement error and QMPs were assessed in both replications and original research.
-These measurement related concepts were then linked to replicability in order to investigate them as potential causes inhibiting successful replications.
-The tests for the hypotheses were often underpowered.
-Additionally, some tests showed mixed results.
-However, when including exploratory and descriptive analyses, a clearer picture on measurement usage and quality in original and replication research emerges.
-
-## Risky Measurement Usage
-This study assessed the quality of measurement and measurement reporting in original and replication research by investigating the quality of measurement in the Many Labs projects, and the original articles they attempted to replicate.
-Findings were in line with similar investigations in the literature by @shaw2020measurement, @flake2017construct, and @flake2022construct.
-Those studies found that validity evidence and reliability coefficient reporting for measures was lacking in replications and original studies.
-This is a problem that has been addressed in literature on this topic for a long time [@vacha1999practices; @green2011recent], and illustrated yet again in our sample by the fact that reliability coefficients were reported in too small an amount to conduct the planned analysis for hypothesis 1.
-The adjusted test for hypothesis 1, while not able to test differences in actual coefficient values, did show contradictory to hypothesis 1 and similarly to @flake2022construct, that original articles reported reliability coefficients more often than replication studies.
-However, even for original articles `r round(100 * (table(coded_data_original_shortened$N_items)[["multiple item measure"]] - sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)])) / table(coded_data_original_shortened$N_items)[["multiple item measure"]], digits = 0)`% of the multiple item measures were reported without any reliability evidence.
-Interestingly, the reliability coefficients that were reported, were reported for measures that obtained large calculated reliabilities.
-
-Furthermore, of the `r nrow(coded_data_replications)` measures only `r sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")` in original articles and `r sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")` in replication protocols reported any validity evidence.
-Even the exact version of the measure was difficult to ascertain for neither original nor replication.
-
-This only covers part of the spectrum of the measures found across both original and replication studies, as less than half of the coded measures in the sample were multiple item scales.
-Research commonly made use of single item measures (see Figure \@ref(fig:ReliabilityReportingFlowDiagram) for more details), an observation that was also made by @shaw2020measurement.
-The use of single item measures comes with many risks with regard to validity [@diamantopoulos2012GuidelinesChoosingMultiItem; @nunnallyOverviewPsychologicalMeasurement1978].
-Additionally, by virtue of being singular they assume that whatever they are measuring is unidimensional, while not being able to test this assumption [@shaw2020measurement].
-
-Other results did show more promise.
-For instance, QMPs were found to be overall less common in replication protocols than they were in original articles, supporting hypothesis 4.
-This runs counter to the findings of @shaw2020measurement & @flake2022construct, who found that measures came with less validity evidence in replications compared to original studies, and shows that QMPs can be systematically reduced across a series of studies.
-The structured replication protocols that were used in the Many Labs projects, I suspect were the reason that the reporting practices were improved in replication protocols compared to original articles.
-Most replication protocols even contained a section under each replicated study, which listed deviations from the original, providing much relevant information.
-As a result many potential QMPs were averted.
-@protzko2020high already demonstrated that transparent reporting of methodology before conducting research can improve the robustness of psychological science, and I believe the same holds true here.
-
-## Impact on Replicability
-Indeed the robustness of the research investigated in this study, as judged by its replicability, did appear to be affected by the reporting of measurement details.
-In particular, support was found for hypothesis 5, showing that an increase in total QMP ratio was associated with a decrease in replicability.
+In this paper, we analyzed the data, protocols, and related original articles from four Many Labs projects to assess reliability and measurement (reporting) practices.
+We additionally looked at how these features might affect credibility, in particular through the relation with replicability.
+Overall, we found that not all measures were sufficiently reliable, nor where measures always equally reliable in each setting in which they were used.
+Regardless, we did not observe that reliability was related to replicability as predicted.
+However, a relation with replicability was observed for QMPs in replication research.
+In turn, we found that  QMPs in the replication were related to QMPs in the original research.
+
+## Reliability
+
+### Reliability varied within and between measures
+
+The measures in our sample varied in their reliability.
+While most measures showed sufficient average reliability for most purposes in psychological research (around .80), about a quarter of the measures had a reliability generally considered insufficient (around .60 or less) [@nunnally1994assessment].
+Furthermore, original research generally showed lower reliability than the average reliability in the replication samples, contrary to our hypothesis that there would be no difference.
+
+One explanation for this discrepancy might be that measurement was more rigid in the Many Labs replications, possibly because the sharing of data would make them more open to scrutiny [@wicherts2011willingness].
+Higher reliability would mean less noise around effect estimates, and in turn make this estimates more consistent.
+However, this relationship is complex and is further complicated by the fact that reliability is not a fixed aspect of a scale, but instead a feature of that scale within a sample [@cho2015cronbach].
+
+Indeed, our results show that reliability of a measure is different across samples, in some cases even showing signs of true variation, or heterogeneity, in reliability.
+Reliability heterogeneity was particularly common for measures with a lower average reliability.
+Meanwhile, some measures with higher average reliability showed indication of nearly zero heterogeneity.
+It is however difficult to draw clear conclusions since the number of investigated measures was small.
+Some measures were also used in only a small number of independent samples.
+This is particularly relevant here, since the tests for heterogeneity are known to be sensitive to the number of studies included [@li2015DilemmaHeterogeneityTests].
+Regardless, our results do demonstrate an often overlooked aspect about of measurement reliability: reliability is a sample-specific not a measurement-specific feature.
+
+### No observed relation between reliability and replicability 
+@stanley2014expectations illustrated that measurement error, when not attenuated for, can impact replication assessments.
+We observed no relation between reliability and replicability, even though our chosen replication index did not attenuate for measurement error.
+This result not only runs counter to the findings of @stanley2014expectations and hypothesis 3 of this study, but also the theoretical relationship between reliability and variability in effect size estimates.
+
+However, the relationship between reliability and replicability is complex.
+For example, reliability and replicability are theoretically only related when the true effect is not null.
+In our sample more than half of the effects were not replicated, indicating that many of these effects may be null effects.
+For these effects no relation would be expected.
+Furthermore, while reliability diminishes effects it can also reduce the observed true variance in the effects [@olsson-collentine2023UnreliableHeterogeneityHow].
+As a result, effect estimates from various studies will appear more similar than they truly are, seemingly replicating the original.
+These and other relations become even more complex when reliability itself is heterogeneous as was observed with several measures in our sample.
+
+With this in mind it is perhaps not surprising that we did not find an evidence for a relation between reliability and replicability in our sample.
+The was the number of measures for which reliability could be calculated small (n = `r apa_num(sum(!is.na(data_h3_avg$alpha)), numerals = FALSE)`).
+Furthermore, if a number of these effects are actually null effects, then there are even less measures for which the relation is expected.
+Combined with the complexity of the relationship between reliability and replicability, our non-significant finding is likely the result of a lack of power to detect this specific relation between reliability and replicability.
+
+The small number of relevant measures, and the small number of reported reliabilities is not only an issue for the power of our tests.
+It indicates that there is a lack of reliability evidence in both original and replication psychology literature.
+
+## Measurement Reporting
+
+### Measurement Reporting is often incomplete
+
+The reliability of measures was rarely reported in both original and replication research, which is in line with similar investigations in the literature [@shaw2020measurement; @flake2017construct; @flake2022construct].
+Reported reliabilities were so few, that the planned test for hypothesis 1 had too low power to be informative.
+In particular, we found that replication research reported reliability coefficients less than original research, which is in line with @flake2022construct.
+This pattern continued for validity evidence reporting.
+Of the `r nrow(coded_data_replications)` measures, validity evidence in the form of factor analysis or similar analyses was reported for `r sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")` measures in original articles, and `r sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")` measures in replication protocols.
+
+The underreporting of reliability and validity evidence has been addressed in literature for a long time [@vacha1999practices; @green2011recent].
+Our study illustrates three potential reasons for why this problem has persisted.
+Firstly, the studies in our sample commonly made use of single item measures, an observation that was also made by @shaw2020measurement.
+Calculating reliability for single-item measures is not as straightforward as for multiple item measures.
+
+Secondly, our results indicate that there may be bias in reporting reliability coefficients.
+Reliabilities were reported in original research for those measures that obtained large calculated reliabilities in the replication samples.
+If we take the calculated reliabilities in the replication sample as an accurate representation of the distribution of the true reliability for that measure, then this would imply that reliabilities are more often reported when the measure is truly reliable, and less when it is unreliable.
+Researchers may be reluctant to report reliability for unreliable measures, thus lowering the prevalence of reported reliabilities.
+This bias may cause researchers to be overly optimistic with regard to the reliability of measures in their field, similarly to how bias in publication causes issues for establishing estimates of true effect sizes in meta-analyses [@sutton2000empirical].
+
+Thirdly, when the replication protocols were written, no measurement based on these protocols had taken place.
+As a result, the data the replicating researchers could have calculated reliability and validity from was not yet available.
+This would explain why there was little reliability and validity evidence reported in replication protocols.
+However, if reliability and validity evidence are not being consulted before replicating research, it means that unvalidated measures are used.
+
+Beyond reporting of reliability and validity evidence, we also investigated other measurement reporting practices recorded using QMPs.
+We found that QMPs were less common in replication protocols compared to original articles.
+This is in line with hypothesis 4, but runs counter to the findings of @flake2022construct.
+We believe this discrepancy was the result of our sample being the Many Labs projects.
+These projects made use of structured replication protocols to document the way measurement was going to be conducted.
+One example of how this may have reduced QMPS is the inclusion of a section in several protocols for listing the deviations from the original measurement.
+
+### Incomplete measurement reporting hinders replicability
 Existing literature has already warned about the potential detrimental effects of QMPs on replications [@shaw2020measurement; @flake2022construct].
-This result provides further evidence supporting these claims.
-The effect of QMPs on replicability can additionally be traced back to the effect of original article QMPs on replication QMPs.
-The test for hypothesis 6 showed that, in line with expectations, there was a positive association between the total QMPs of an original study and the total QMPs in the protocol of the replication for that study.
-
-When information on, or support for the use of a measurement is lacking, any subsequent replication attempt is expected to also lack information on the measure.
-As a result, both the underreporting of measurement details and use of unverified measurements may persist in the replication.
-Consequently, ensuring that the original measurement is mimicked becomes difficult to verify when the measurement was not documented well originally.
-In turn, the relation between the original and replication studies may weaken [@flake2022construct].
-As a result, constructs are measured substantially differently, causing subsequent replication tests to substantially differ from the test in the original article.
-This implies that the observed effects in the replication may differ from the original not only due to sampling error, but also due to true differences in the assessed effect as the result of the measurement used.
-
-However, it is worth noting that these relations were only found for QMPs coded with the revised coding protocol.
-Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see Appendix D).
-The initial protocol was revised because the ratings based on that protocol were considered to stringent, and as a result, several items were reformulated so that criteria for what constituted sufficiently clear reporting were lowered.
-This meant that in the revised protocol, coded QMPs would need to clearly inhibit evaluation of the measurement, whereas for the initial protocol some aspects of the measurement reporting which were coded as questionable, may have been questionable only to a small degree.
-As a consequence, QMPs coded with the revised protocol represent measurement practices that represent on average more questionable practices than QMPs coded with the initial protocol.
-With this in mind, the difference between total QMP ratio of initial and revised protocol can be seen as a form of effect size difference.
-It could be that only replication QMPs that represented robust violations of good measurement practices significantly lower the probability of successful replication.
-In that case, a stronger relation between replicability and QMPs would be found with the revised protocol, since these QMPs represented more clearly questionable practices in measurement reporting than QMPs coded with the initial protocol, which would explain the disparate results that were found.
-
-What did not appear to affect the replicability of a study was the reliability of the measure used in the study.
-This result is surprising, given that @stanley2014expectations demonstrated the potential impact that measurement error can have on the veracity of determining replication success based on a significance test without attenuating for measurement error.
-The significance test cut-off criteria that was used in this study to assess replication success similarly did not attenuate for measurement error, and thus results in line with the simulation studies of @stanley2014expectations were expected.
-However contrary to both Hypothesis 3 and @stanley2014expectations, less reliable measures were not associated with a decrease in replicability.
-
-While no evidence for hypothesis 3 was found, caution in interpreting the test results is advised.
-The number of measures for which reliability was calculated was quite low (`r apa_num(sum(!is.na(data_h3_avg$alpha)), numerals = FALSE)`), it could be that the test was simply underpowered to detect the effect.
-On the other hand, it might be the result of measurement error's tendency to reduce heterogeneity in estimates of the same effect, making the observed effects more similar [@olsson-collentine2023UnreliableHeterogeneityHow].
-This may have resulted in effects that appeared to homogeneously show evidence in one direction.
-The relation becomes even more complicated for the measures that showed evidence of reliability heterogeneity, which while not many, does invalidate the use of reliability averages in the model for hypothesis 3.
-These factors may help to explain the differences in conclusions observed between this article and the simulation studies of @stanley2014expectations.
+It is challenging for replication researchers to mimic the measurement of an original article, when the original article does not document the measurement in sufficient detail.
+Consequently, the measurement in the replication may assess constructs substantially differently, weakening the relation between the test in original and replication studies [@flake2022construct].
+
+In line with hypothesis 5 and 6, we found indication of such a spillover effect in our sample.
+The total QMPs of an original study and the total QMPs in the protocol of the replication for the same study were positively associated.
+Furthermore, we found that QMPs may have negatively impacted replicability.
+An increase in total QMP ratio was associated with a decrease in replicability.
+These associations together indicate that poor measurement reporting in an original study could be a risk factor for subsequent replication attempts.
+
+However, it is worth noting that these associations were only found for QMPs coded with the revised coding protocol.
+Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see Appendix D[insert Link] for results based on the initial protocol).
 
 ## Limitations & Future Research
-The design of this study came with certain limitations.
-First of all, there was no (quasi-)experimental manipulation included.
-As a result, the ability to investigate the causal links between QMPs and replicability was limited.
-Secondly, alternative ways to analyse or expand the sample could have been used.
-The coding protocol was changed within the scope of this study, which illustrates that there was no validated methodology for analyzing the data, and there is no prior evidence validating the use of QMP ratios to represent questionable measurement practices.
-Future research can use this study as a basis to find relevant data sources, and develop methodologies that can be used to compliment and extend the findings of this study, or test causal links between measurement usage and replicability.
-
-It is important to also consider whether or not replication protocols and research articles can be fairly compared in terms of QMPs.
-Articles are generally longer than a study's description within a replication protocol, and thus it seems reasonable to expect research articles to generally contain more measurement details than replication protocols.
-Regardless, this study assumed that a replication protocol is comparable to an article in providing an overview of the measure and how it was used, as it was the only comparable source for such information that would not easily be found anywhere else.
-This assumption is practical if not tenable when the replication protocol is the only available sources of measurement details.
-However, in case more detailed information on a measurement is available in other sources, such as an online appendix, it could be important data to include when assessing QMPs.
-This research did not make use of any online appendices in assessing QMPs, future research may wish to include them and other sources as part of the data.
-
-As a final note on QMPs, it is worth highlighting a specific aspect about the way the QMP ratios were calculated.
-This relates to the fact that non-applicable items, while adjusted for by coding those items as 0 in both the numerator and denominator of the QMP ratio calculation, could exert a strong influence on the value of the QMP ratio.
-For example, for one measure all relevant information regarding the measure was reported, for another no information was provided on the measure at all and furthermore the items were all non-applicable.
-In both cases the QMP ratio would be 0.
-However, we would not consider the latter case to indicate the same quality of measurement reporting as the first.
-As a result, the relation between QMP ratio and measurement reporting quality is obscured[^5].
-There is no simple solution to this problem based on the current data.
-Regardless, future research may wish to include qualitative analyses of the informativeness of measurement reporting to provide a more thorough and complete picture.
-
-[^5]: Because the relation is obscured and since the scale was constructed as a means to capture QMPs as broadly as feasible, the QMP items should be held equivalent to a psychometric scale.
-For these reasons, psychometric evidence for the scale is not given, as it would hard to decide how Not Applicable responses should be treated, and because the goal of the scale was not to capture one or multiple latent constructs.
-
-The small sample of measures for which reliability coefficients could be assessed limited the robustness of the reliability analyses.
-While future research will also unlikely be able to increase the number of multiple item measures used by replications, future research can broaden their analyses to include a larger number of replications, or take into account a type of measure which this study mostly ignored in this study's analyses of reliability and validity: single-item measures.
-
-Reliability assessment for single item measures differs substantially from multiple item measures [@wanous1996estimating], and for this reason was not included as part of the analyses for this study.
-However, future research might consider methods specifically designed to assess the reliability of single item measures.
-This could prove to be a worthwhile contribution, given the proportionally large number of single item measures that were encountered in the data for this study (see Figure \@ref(fig:ReliabilityReportingFlowDiagram)).
-
-Finally, this paper investigated the consistency of measures, by assessing the variance in reliability across different labs wherein the measure was conducted, and comparing it to the variance in reliability between the different measures.
-Besides comparing the degree of reliability across labs, it is also possible to assess whether a measure assesses the same underlying construct across lab locations.
-This can be done through measurement invariance testing.
-Measurement invariance is a concept in latent factor modelling that illustrates the extent to which the relationship between items and factors is dependent on some other variable, usually a group [@mellenbergh1989item].
-@shaw2020measurement investigated measurement invariance for the responses to measures at each lab location within the replication sets of Many Labs 2.
-Investigations similar to this have also been suggested for future replication projects [@flake2022construct].
-For these reasons, future research should consider using measurement invariance tests to assess the measurement consistency in replications.
-
-## Implications for Research and Replications in Psychological Science
-
-Taking all the findings together, the following assessments will be relevant to consider for future replication research.
-The results suggest that the use of structured measurement reporting protocols may be an effective way of reducing QMPs, and may explain why the replication protocols had on average lower QMPs than original articles in this study.
-This suggests that reporting guidelines can be a successful tool in improving measurement reporting.
-However, not only was reliability and validity evidence rarely reported in both replication protocols in original articles, corroborating findings by @shaw2020measurement & @flake2022construct.
-Reliability and validity evidence was reported even less in the replication protocols, that made use of reporting guidelines, compared to original articles.
-It may therefore be necessary for reporting protocols to increase the attention they give to reporting reliability and validity evidence.
-
-Furthermore, the association between original paper and replication protocol QMPs demonstrates how a lack of information for measurement in the original can spill over to the reporting in replications.
-This could lead to issues for replication attempts if the measure in an original article has poor reliability and validity.
-In that case, the tests in the original article are based on data from measures that do not accurately capture the construct they were intended to measure.
-The results of any direct replication attempt will face the same issues, and as a consequence the replication is unlikely to provide a relevant test of a psychological theory, as the original study itself was not a robust test of that psychological theory to begin with [@isager2020deciding, @isager2021deciding, @nuijten2022assessing].
-Thus, future replicators should first evaluate the quality of the measurement (reporting) in an article before deciding to replicate.
-
-In case the quality appears low or the exact details of the measurement such as the version used was not clear, which was not uncommon in our sample, replication attempts can still proceed with some adjustments.
-One option is to change the focus of the replication to be conceptual rather than direct.
-In that case the measure and the operationalisation can be freely altered from the original, which means that a more sufficient test of the theory can be developed.
-If deemed necessary, a direct replication can always be performed later based on the conceptual replication.
-In that case, the direct replication will be able to provide a sufficient test of a psychological theory, on the condition that the conceptual replication's test improvements led to it becoming a sufficient test.
+Our study had several limitations.
+First of all, we encountered numerous challenges in operationalizing QMPs.
+This research used a novel way of operationalizing QMPs as a variable to assess measurement practices and their impact on replicability.
+However, this also means that it remains uncertain whether or not .
+Already we determined it necessary to revise our coding protocol to be more lenient with regard to more context dependent QMPs compared to the initial protocol.
+This revision was not trivial as it impacts the interpretation of our results.
+
+This relates to one of the most prominent challenges in assessing QMPs.
+It is difficult to determine when a practice is questionable, and what impact the context has on this decision.
+For example, in our sample the constructs that were measured were less commonly defined in replication protocols than in original articles.
+However, one may argue that it is not the responsibility of the replication to define the construct, as it is meant to be equivalent to the construct assessed in the original article.
+In that case, not defining the construct may not constitute a questionable practice at all.
+
+Another challenge in constructing a QMP variable was the way to treat practices that were not applicable to a particular measurement.
+We chose to make use of ratios to cancel out the effects of non-applicable items as much as possible.
+However, this has the consequence that that both a measure for which all relevant measurement-related information was reported, and a measure for which no item was applicable would have a QMP ratio of zero.
+However, we would not consider the latter case to indicate the same level of completeness as the first.
+A little more than one third of all responses was not applicable.
+This may have been enough to substantially obscure the relation between QMP ratio and measurement reporting completeness.
+
+The relation is further obscured because it is not clear how great a ratio of QMPs is too much.
+One might argue that any QMP is a sign of questionable research and thus that any ratio greater than zero is cause for alarm.
+However, this may be too harsh.
+As mentioned, not all violations may have detrimental consequences or be relevant in all contexts.
+Future research will be needed to determine the best way(s) to operationalize QMP ratios.
+???APA-MANUAL FOR EXAMPLES/INSPIRATION FOR FUTURE RESEARCH/ AERA et al., 2014???
+
+The second limitation is that our tests on reliability were largely underpowered.
+This was the result of the small number of reported reliability scores, and multiple item scales with available data.
+However, this limitation also illustrates two key findings of this study.
+One being that the reliability of measures were rarely reported in both original articles and replication protocols.
+
+The other finding is that around half of the measures used in our sample were single item-measures.
+The use of single item measures comes with psychometric risks [@diamantopoulos2012guidelines; @nunnally1978overview], and are more limited with respect to the type of reliability and validity evidence that can be determined [@shaw2020measurement].
+It could even be argued that the use of single-item measures constitutes a QMP in many instances.
+
+As a third limitation, it is important to consider whether or not replication protocols and research articles can be fairly compared in terms of QMPs.
+A study's description within a replication protocol is generally shorter than an article.
+The description within the protocol may therefore lack the space needed to report on the measurement in full detail.
+There are two main reasons why we believe protocols and articles remain comparable.
+Firstly, articles are often also restricted in the amount of space they have available to devote to measurement [@gardiner2019editorial].
+Secondly, in the revised protocol some information, such as example items, could also be reported only in supplementary materials and not be counted as a QMP.
+Still, future research may wish to further include supplementary materials as part of the primary data to get a more complete picture on the state of measurement reporting in both articles and protocols.
+
+The fourth limitation is that we made use of only one way to define replication success.
+Replication success can be estimated and framed in multiple ways, including methods that do not make use of significance testing.
+Multiple ways to define replication were used in the RPP [@osc2015estimating].
+The relationship that reliability has with different forms of replication success may differ.
+
+Finally it is worth noting that we did not make use of a causal design in our study.
+Therefore, we cannot attach definitive causal directions to the relations observed in this study.
+However, it would be useful for understanding the potential negative impact of reliability and QMPs on replicability., It may be possible to randomly assign original studies in a project like the Many Labs to either needing to report all the relevant measurement details as noted down by for example @flake2020measurement and @???APAMANUALREFERENCE???, or get no screening.
+The same would go for requiring the use of validated measures, or not.
+Tremendous coordination and funding would be required to integrate original studies into a large scale replication project from the start.
+While such efforts are not unprecedented [@protzko2020high], alternative methods also exist to assess causal relations on observational data.
+For example, @rohrer2018thinking has suggested researchers make use of Directed Acyclic Graphs to investigate causality in (non-)experimental settings by systematically taking into account confounding influences on the effect.
+Such an approach may also help in untangling the complex relationship between reliability and replicability.
+
+## Recommendations 
+Taking all the findings together, the following assessments will be relevant to consider for future research.
+Firstly, reliable and valid measures are a prerequisite for credible findings.
+The observation that many measures are not reported with such evidence is worrying, because it obscures the credibility of findings, and hampers scientific progress.
+Therefore, we suggest that for multiple item scales establishing the validity becomes a community standard for credible research.
+For reliability coefficients we go even further to state that these should by default always be reported for any multiple item scale.
+Researchers should only be exempt from this default, if they provide motivated reasoning for why they should be exempt.
+
+For direct replications to represent an as good as possible test of the credibility of a finding, it is important that the procedure and measurement of the original study can be mimicked.
+Therefore, researchers should make fully report on their measurement details, as specified for example in Table 1 in @flake2020measurement ???APA MANUAL???.
+Any details that could not fit in the article can then be shared with potential replicators via a public repository, such as the Open Science Framework [OSF; @soderberg2018using] or Zenodo [@zenodo2024open].
+
+Furthermore, we argue that researchers seeking to replicate a study should first evaluate the measurement of that study.
+Not only is it crucial for an informative replication that the measurement is reliable or valid.
+The original study should also report the measurement details necessary to reconstruct the original measurement.
+Otherwise it may be futile to attempt a direct replication.
+In that case we suggest that researchers instead use their resources to conduct a replication of a study with reliable, valid and well-documented measurement.
+When replicating another study is not an option, we advise the replicating researcher to first attempt a conceptual replication using reliable and valid measurement.
+Afterwards, a direct replication can be performed based on the conceptual replication to further assess the effect’s credibility.
 
 # Conclusion
-
-Overall, the observed quality of measurement and frequency of measurement reporting in psychological research and replications was low, which is in line with earlier research.
-Improvements in the reporting on measurement are needed for both original and replication research.
-The measure source, content, and how it was used should be described in detail, and evidence illustrating the reliability and validity of the measure should be provided.
-Not only would the clarity of research improve, higher quality of measurement reporting in replications was shown to be related to an increase in replicability of the findings related to that measure.
-Tentative evidence was also found for spill-over effects of the quality of measurement reporting from original study to replications.
-These results combined suggest that improvements in the reporting of measurements are necessary in both replications and original articles.
-Furthermore, future replicators should carefully consider the quality of measurement in a study before attempting a direct replication.
-A conceptual replication may be the better choice if the measurement in the original was not of sufficient quality.
-However, the evidence for the relationship between measurement quality and replicability was not robustly identified, and future research will be needed to confirm the exact nature of this relationship.
+Through our investigations into the reliability, validity, and reporting of measurement in the Many Labs replications and associated original studies, we found that reliability and validity evidence was reported infrequently.
+Furthermore, QMPs that obscured important information needed to evaluate and reconstruct the measurement were common, especially in original research.
+QMPs were in turn related to the replicability of a finding.
+Results with regard reliability of the measures were less clear due to low sample size.
+However, for a number of measures reliability showed signs of significant variation between studies.
+Combined these findings illustrate the need for more concrete standards in measurement reporting, and that before attempting a replication of a study, researchers should consider the validity and reporting completeness of the measurement.
 
@@
 
-# (APPENDIX) Appendix {-}
+# (APPENDIX) Appendix {.unnumbered}
 

### 2024-05-28 Scripts/source_script.R

@@ -992,6 +992,34 @@ Associations_H6_REV <- function(Data){
 
 
 # Plotting Related Functions ---------------------------------------------------
+### Data Structure Plot data prep
+data_prep_data_structure_plot <- function(Data){
+  data_structure_plot <- Data
+  data_structure_plot$appearance[18] <- 1
+  data_structure_plot$appearance[19] <- 2
+  
+  #unique(data_structure_plot$title)
+  
+  data_structure_plot$title[62] <- data_structure_plot$title[61]
+  data_structure_plot$title[77] <- data_structure_plot$title[76]
+  data_structure_plot$title[90] <- data_structure_plot$title[89]
+  data_structure_plot$title[91] <- data_structure_plot$title[89]
+  data_structure_plot$title[137] <- data_structure_plot$title[136]
+  data_structure_plot$title[149] <- data_structure_plot$title[148]
+  data_structure_plot$title[154] <- data_structure_plot$title[153]
+  
+  measure_count <- c(table(data_structure_plot$title))
+  
+  data_structure_plot <- data_structure_plot[!duplicated(
+    data_structure_plot$title),]
+  
+  data_structure_plot$measure_count <- measure_count
+  
+  return(data_structure_plot)
+}
+
+
+
 ### Plot 23 data prep
 data_prep_plot_23_alpha <- function(Data){
   Data$avg.alpha <- ave(Data$alpha, Data$g)

### 2024-07-01 Scripts/Manuscript/AppendixScripts/Appendix_initial_QMP_analyses.rmd
Incorporated feedback on the entire text from co-authors. Removed two figures, checked grammar.

@@
 
-This appendix contains all of the QMP analyses that in the article and appendices were based on the revised QMP, but then performed based on the QMPs obtained using the initial coding protocol.
+This appendix contains the QMP analyses that in the article and appendices were based on the revised QMP, but then performed based on the QMPs obtained using the initial coding protocol.
 
@@
 The data was initially coded using to the preregistered coding protocol.
-After the coding was completed using the preregistered coding protocol, it was determined that some of the initial ratings were possibly to stringent.
+After the coding was completed using the preregistered coding protocol, it was determined that some of the initial ratings were possibly too stringent.
 As a result, some of the items in the protocol were reformulated, so that the conclusions from the resulting analyses were based on a more lenient judgement of QMPs.
@@
 ### Results + Comparison Interpretation
-The figure below displays the distribution of observed QMP ratio's across original articles and replication protocols based on the initial coding protocol.
+The figure below displays the distribution of observed QMP ratios across original articles and replication protocols based on the initial coding protocol.
 
 ```{r Plot456CodeInitial, warning = FALSE, fig.cap = "QMP ratio counts for each QMP Type and QMP total ratio distribution grouped by whether the QMP ratio was obtained from an original article or a replication protocol.
-The top row shows for each QMP type the proportions of each QMP ratio obtained, darker colours represent proportionally more QMPS, grey means modification did not occur for that measure.
-The bottom graph shows the distributions of total QMP ratios for both replication protocols and original articles, with the line indicating the mean QMP ratio.
-The specific observed values are indicated along the bottom row with dots"}
+The top graph shows the distributions of total QMP ratios for both replication protocols and original articles, with the line indicating the mean QMP ratio.
+The specific observed values are indicated along the bottom row with dots.
+The bottom row shows for each QMP type the proportions of each QMP ratio obtained, darker colors represent proportionally more QMPS, grey means modification did not occur for that measure.."}
 # re-ordering the QMP-types, because it didn't save
@@
 # combining both plots and the legends into one figure
-grid.arrange(Plot_456_1, 
-             Plot_456_2, 
+grid.arrange(Plot_456_2, 
+             Plot_456_1, 
              legend_456_org,
              legend_456_rep,
-             layout_matrix = rbind(c(1, 3, 4),
-                                    c(2, 2, 2)),
+             layout_matrix = rbind(c(1, 1, 1),
+                                    c(2, 3, 4)),
               widths = c(8, 1, 1))
@@
 Contrary to the results based on the revised coding protocol, a decrease in QMP ratio based on the initial coding protocol did not significantly relate to replication success (`r H5_test_results_with_OR`).
-Thus not supporting hypothesis 5.
+Thus, not supporting hypothesis 5.
 
 Similarly to the previous test, the relation was not significant for the QMP ratios obtained with the initial protocol (`r betareg_output_to_apa_full(H6_test_results)`).
-Thus not supporting hypothesis 6.
+Thus, not supporting hypothesis 6.
 Figure \@ref(fig:Plot46InitialDataCode) displays this relationship visually.
 
-```{r Plot46InitialDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication total QMP ratio’s with linear regression line.
+```{r Plot46InitialDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication total QMP ratios with linear regression line.
 Each dot in the figure describes the QMP ratio in that graph across both the original article and its replication protocol.
-Note: jitter was applied to these dots in order to show the number of observations at points where multiple dots were present"}
+Note: jitter was applied to these dots to show the number of observations at points where multiple dots were present"}
 ggplot(plot_46_data[plot_46_data$QMP_type == "QMP.Ratio" & plot_46_data$QMP_Rep_type == "Rep.QMP.Ratio",], aes(QMP_ratio, QMP_Rep_ratio)) + 
@@
 
-```{r Plot46FullInitialDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication total QMP ratio’s obtained using the intial coding protocol with linear regression line.
+```{r Plot46FullInitialDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication total QMP ratios obtained using the intial coding protocol with linear regression line.
 Each dot in the figure describes the QMP ratio in that graph across both the original article and its replication protocol.
-Note: jitter was applied to these dots in order to show the number of observations at points where multiple dots were present"}
+Note: jitter was applied to these dots to show the number of observations at points where multiple dots were present"}
 # Initial

### 2024-07-01 Scripts/Manuscript/AppendixScripts/Appendix_multilevel_analyses.rmd
Incorporated feedback on the entire text from co-authors. Removed two figures, checked grammar.

@@
 In this data, replication attempts at different lab locations can be seen as nested within a replication set.
-In order to see if this nesting might impact the analyses of hypothesis 3, multilevel models are included here as sensitivity checks.
+To see if this nesting might impact the analyses of hypothesis 3, multilevel models are included here as sensitivity checks.
 
@@
 ### Explanation of Relevance
-The models used in the article to test hypotheses 5 & 6 had independence of observations as an assumption, the observations here referring to a replication set.
+The models used in the article to test Hypotheses 5 & 6 had independence of observations as an assumption, the observations here referring to a replication set.
 this is known to be false since the data is nested within four separate Many Labs projects.
@@
 ### Models
-In order to test if this nested structure might influence the relations described in hypothesis 5 & 6, random intercept and random slope multilevel models with each Many Labs project as a group were implemented as sensitivity analyses.
-As of writing this article the betareg package does not allow for estimation of multilevel models.
-As an approximation, Gaussian random-intercept multilevel models were implemented using the lmer function from the lme4 package [@R-lme4].
-The outcome QMP ratio variable was transformed using the logit link function (the default link function in the betareg package) to better fit the Gaussian model.
+To test if this nested structure might influence the relations described in Hypothesis 5 & 6, random intercept, and random slope multilevel models with each Many Labs project as a group were implemented as sensitivity analyses.
+As of writing this article the *betareg* package does not allow for estimation of multilevel models.
+As an approximation, Gaussian random-intercept multilevel models were implemented using the *lmer* function from the *lme4* package [@R-lme4].
+The outcome QMP ratio variable was transformed using the logit link function (the default link function in the *betareg* package) to better fit the Gaussian model.
 
@@
 ### Results
-For hypothesis 5, the sensitivity analyses using a random-intercept multilevel regression found a similar significant association as that found by the main test (`r check_h5_REV$full_result$hypothesis_supportTRUE`).
+For Hypothesis 5, the sensitivity analyses using a random-intercept multilevel regression found a similar significant association as that found by the main test (`r check_h5_REV$full_result$hypothesis_supportTRUE`).
 This result is in line with hypothesis 5.
@@
 
-For hypothesis 6, the sensitivity analyses using a random intercept logistic multilevel model resulted in non-significant results, which is contrary to the results found with the main test and is not in line with hypothesis 6 (revised protocol: `r check_h6_REV$full_result$QMP_REV`).
+For Hypothesis 6, the sensitivity analyses using a random intercept logistic multilevel model resulted in non-significant results, which is contrary to the results found with the main test and is not in line with hypothesis 6 (revised protocol: `r check_h6_REV$full_result$QMP_REV`).
 This result places some doubt in the results found through the main test reported in the article.

### 2024-07-01 Scripts/Manuscript/AppendixScripts/Appendix_omega_analyses.rmd
Incorporated feedback on the entire text from co-authors. Removed two figures, checked grammar.

@@
 ### explanation why
-Omega was included since it has been argued to be a more informative measure of score reliability than alpha, while also providing validity evidence for the scale [@crutzen2017scale; @deng2017testing].
-Omega was calculated using the omega function in the psych R package [@R-psych].
+Omega was included since it has been argued to be a more informative measure of reliability than alpha, while also providing validity evidence for the scale [@crutzen2017scale; @deng2017testing].
+Omega was calculated using the omega function in the *psych* R package [@R-psych].
 Default arguments were used in the function except the nfactors argument, which was set to 1.
@@
 ### Models
-In order to separate between and within variance in reliability, a multilevel random intercept model was specified with replication set as the grouping variable, which was the same model used for testing.
-The difference was that the omega value of a replication was used as dependent variable in this instance, using the lmer function from the lme4 package [@R-lme4].
+To separate between and within variance in reliability, a multilevel random intercept model was specified with replication set as the grouping variable, which was the same model used for testing.
+The difference was that the omega value of a replication was used as dependent variable in this instance, using the *lmer* function from the *lme4* package [@R-lme4].
 
@@
 
-The analysis for H3 related the calculated average reliability coefficients for each replication set to whether or not the replication was successful when judged at meta-significance level of $alpha <.05$.
+The analysis for H3 related the calculated average reliability coefficients for each replication set to whether the replication was successful when judged at meta-significance level of $alpha <.05$.
 
@@
 ```{r ReplicabilityReliabilityTestTableOmega, warning=FALSE}
-# creating the dataframe for the table <- separate the OMEGA from here???
+# creating the dataframe for the table 
 H3_table_dataframe_omega <- rbind(H3_test_result_main_omega$table, H3_test_result_int_sensitivity_omega$table, H3_test_result_slp_sensitivity_omega$table)
@@
   H3_table_for_printing_omega, align = c("l", "r", "r", "r", "r")
-  , caption = "Model Results from Tests of Hypothesis 3 based on the Omega COefficient"
+  , caption = "Model Results from Tests of Hypothesis 3 based on the Omega Coefficient"
   , escape = FALSE, placement= "htp", midrules = c(2, 4, 6))
@@
 
-Thus no evidence for hypothesis 3 was found.
+Thus, no evidence for hypothesis 3 was found.
 However, caution in interpreting the test results is needed.
@@
 It mostly resembles Figure \@ref(fig:Plot23AlphaCode) from the article, with some studies being omitted as the omega coefficient function did not converge or run properly on those data.
-Furthermore, information with regard to heterogeneity was not present since the standard error of omega was not known, and comparisons between reported coefficients were omitted, since no article reported any omega coefficients.
+Furthermore, information reagrding heterogeneity was not present since the standard error of omega was not known, and comparisons between reported coefficients were omitted, since no article reported any omega coefficients.
 

### 2024-07-01 Scripts/Manuscript/AppendixScripts/Appendix_pre-reg_analyses.Rmd
Incorporated feedback on the entire text from co-authors. Removed two figures, checked grammar.

@@
 On top of that, reliabilities could be calculated for each individual lab per replication set so that the variance of them could be assessed.
-In order to separate between and within variance in reliability, a multilevel random intercept model was specified with replication set as the grouping variable and the Cronbach's alpha or omega value of a replication as dependent using the lmer function from the lme4 package [@R-lme4] t.
+To separate between and within variance in reliability, a multilevel random intercept model was specified with replication set as the grouping variable and the Cronbach's alpha or omega value of a replication as dependent using the lmer function from the lme4 package [@R-lme4] t.
 
@@
 However, at the time of pre-registering we did not know of any formal test for the significance of within group variance after controlling for between group variance.
-Instead the intraclass correlation (ICC) coefficient was calculated an indicator of within vs.
+Instead, the intraclass correlation (ICC) coefficient was calculated an indicator of within vs.
 between variability.
@@
 This analysis was omitted from the article because it did not link well enough to hypothesis 2.
-THe test results also do not give use a very informative representations of variance in reliability in the data for us to draw further inferences from.
-For instance, it assumes that we should observe large differences in reliabilities between measures for this to provide an accurate test of whether or not the variance within measures is large or not.
+The test results also do not give use a very informative representations of variance in reliability in the data for us to draw further inferences from.
+For instance, it assumes that we should observe large differences in reliabilities between measures for this to provide an accurate test of whether the variance within measures is large or not.
 
@@
 The between-group and within-group variance for Cronbach's alpha were approximately `r apa_num(between_group_variance_alpha, digits = 3)` and `r apa_num(within_group_variance_alpha, digits = 3)` respectively.
-The resulting ICC, was approximately `r apa_num(ICC_alpha, digits = 3)`.
+The resulting ICC was approximately `r apa_num(ICC_alpha, digits = 3)`.
 This suggests that variance was larger between replication sets than within.
 These results are generally in line with hypothesis 2.
-However, this statistic does not necessarily gives a test of hypothesis 2, as outlined above.
+However, this statistic does not necessarily give a test of hypothesis 2, as outlined above.
 
@@
 
-In order to present additional validity evidence alongside the analyses of Cronbach's alpha and omega coefficients, the unidimensionality of each measure was investigated.
+To present additional validity evidence alongside the analyses of Cronbach's alpha and omega coefficients, the unidimensionality of each measure was investigated.
 To test this, each multiple item scalar measure had their factor structure investigated on the entire measure data of the replication set.
 
-This analysis was omitted from the main article due to the fact that determining when a measure should be unidimensional would require an in-depth review and expert evaluation for the literature surrounding the measure, which is outside of the scope of this article and the authors' expertise.
+This analysis was omitted from the main article since determining when a measure should be unidimensional would require an in-depth review and expert evaluation for the literature surrounding the measure, which is outside of the scope of this article and the authors' expertise.
 Additionally, this information may also simply not be available, further complicating the analyses.
@@
 
-Nevertheless, we present here the result of the analyses made under the assumpti on that the one score, one dimension heuristic holds, for the readers that are comfortable with this heuristic.
+Nevertheless, we present here the result of the analyses made under the assumption that the one score, one dimension heuristic holds, for the readers that are comfortable with this heuristic.
 
@@
 The results are shown in Table \@ref(tab:UnidimesnionalityTestResultsTable).
-A composite score based on the measurement responses was used for sixteen of the `r apa_num(nrow(cfa_results), numerals = FALSE)` measures to form a single variable in the analyses, and were thus regarded as intended to be unidimensional.
+A composite score based on the measurement responses was used for sixteen of the `r apa_num(nrow(cfa_results), numerals = FALSE)` measures to form a single variable in the analyses and were thus regarded as intended to be unidimensional.
 The number of dimensions for the remaining three were unclear.
@@
 for Measure Data", note = "N Factors refer to the number of factors suggested based on parallel analysis of the measure data.
-The word or abbreviation after the author names and year indicates the specific measure within that original article that was analysed.", escape = FALSE, row.names = FALSE, placement= "htp")
+The word or abbreviation after the author names and year indicates the specific measure within that original article that was analyed.", escape = FALSE, row.names = FALSE, placement= "htp")
 
@@
 For example, IQ is often used as a singular indicator, even though it consists of several factors [@weiss2013wisc].
-However, it should be noted that at least with respect to Many Labs 2, all of the measures that were considered unidimensional for the analyses in this study were also considered unidimensional in the investigation by @shaw2020measurement who also observed a lack of unidimensionality evidence in their investigation of Many Labs 2.
+However, it should be noted that at least with respect to Many Labs 2, all measures that were considered unidimensional for the analyses in this study were also considered unidimensional in the investigation by @shaw2020measurement who also observed a lack of unidimensionality evidence in their investigation of Many Labs 2.
 To conclude, there is an indication that validity evidence for measures used in replication research is lacking, and that this may have further implications beyond the measures for which it could be assessed here.
@@
 The relationships between original article QMP ratios and replication protocol QMP ratios were investigated for each QMP type separately.
-Figure \@ref(fig:Plot46RevisedDataCode) visually illustrates the relations of the revised QMP ratios from different QMP types between replication protocols and original articles.
+Figure \@ref(fig:Plot46FullRevisedDataCode) visually illustrates the relations of the revised QMP ratios from different QMP types between replication protocols and original articles.
 As shown in the figure, no relation was strong nor highly stable, and few were consistent between initial and revised coding protocols.
 
-```{r Plot46FullRevisedDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication QMP ratio’s per type with linear regression line.
+```{r Plot46FullRevisedDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication QMP ratios per type with linear regression line.
 The abbreviations on the axes relate to the QMP categories described in Table 1: Def.
@@
 Each dot in the figure relates to describes the QMP ratio for the types in that graph across an original article and its replication protocol.
-Note: jitter was applied to these dots in order to show the number of observations at points where multiple dots were present"}
+Note: jitter was applied to these dots to show the number of observations at points where multiple dots were present"}
 # Revised
@@
 The relations that are consistent are those between original article definition QMPs with replication selection and total QMPs, original article selection QMPs with replication total QMPs, and finally original article quantification QMPs with replication selection QMPs.
-All of these relations were positive across both coding protocols (see Appendix D), illustrating that a greater QMP ratio of the specified type in an original article is associated with an increase in QMP ratio for the specific QMP type, or total QMP ratio in the replication protocol.
+All these relations were positive across both coding protocols (see Appendix D), illustrating that a greater QMP ratio of the specified type in an original article is associated with an increase in QMP ratio for the specific QMP type, or total QMP ratio in the replication protocol.
 
@@
 Sample size for comparisons involving modification were lower since not all measures were modified.
-Therefore the standard errors are larger.
+Therefore, the standard errors are larger.
 $^* p < .05$"
@@
 These former are features of a measurement, which while preferably similar in a replication to the original, can and should be reported in the replication protocol even if the original article does not contain the details on these features itself.
-However, these are just speculations as the results showed no clear relations between different QMP types across original and replication (see Figure \@ref(fig:Plot46RevisedDataCode)), the number of tests were many while multiple testing was not corrected for, and finally testing of causal links was not possible with this data.
+However, these are just speculations as the results showed no clear relations between different QMP types across original and replication (see Figure \@ref(fig:Plot46FullRevisedDataCode)), the number of tests were many while multiple testing was not corrected for, and finally testing of causal links was not possible with this data.

### 2024-07-01 Scripts/Manuscript/manuscript.Rmd
Incorporated feedback on the entire text from co-authors. Removed two figures, checked grammar.

@@
 title             : "An Empirical Assessment of Reliable and Valid Measurement as a Prerequisite for Informative Replications"
-shorttitle        : "Measurement Quality and Informative Replications"
+shorttitle        : "Measurement and Informative Replications"
 
@@
     address       : "Professor Cobbenhagenlaan 125, 5037 DB, Tilburg, The Netherlands"
-    email         : "casgoos99@gmail.com"
+    email         : "c.goos@tilburguniversity.edu"
     role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
@@
 abstract: |
-  Psychological science has been facing threats to the credibility of its findings, particularly due to the lack of replicability of findings.
-  Recently, there has been increasing attention towards the impact that features of psychological measurement, specifically reliability and measurement reporting, has on replicability.
-  In this article, we assessed the reliability and measurement reporting within the Many Labs replications and the original studies they were based on. 
-  We then empirically investigated the associations of replicability with reliability and measurement reporting.
-  The results indicated that not all measures were sufficiently reliable across contexts. 
-  Additionally, reliability and validity evidence was rarely reported. 
-  Finally, incompleteness in measurement reporting was associated with lower replicability of the findings tested with that measure.
-  The results not only indicate potential issues in reliability and validity of measures, but also that incomplete measurement reporting may negatively affect replicability. 
-  These findings illustrate the importance of reliable measurement, and complete measurement reporting for establishing credible findings. 
-  The article ends with suggestions to improve measurement reporting. 
-  We further suggest that the reported measurement information should be evaluated when  researchers decide what studies to replicate.
-
-keywords          : "reliability, validity, measurement, measurement reporting, replicability, credibilitys"
-wordcount         : "182"
+  The credibility of psychological science and the ability to replicate earlier findings require good measurement.
+   Here, we assessed the reliability and measurement reporting of 77 measures within 56 Many Labs replications and related original psychological studies. 
+   We investigated their associations with replicability.
+   The results indicated that not all measures in the original and replication studies were sufficiently reliable across contexts. 
+   Additionally, evidence on reliability and validity was rarely reported. 
+   Finally, incompleteness in measurement reporting in replication studies was associated with lower replicability of the findings tested with that measure. 
+   These findings indicate a worrying lack of reported validating evidence for measurement in the literature, and its harm to credibility.
+   We offer suggestions on improving measurement validation and reporting practices, and argue that researchers should evaluate the reported measurement information when deciding what studies to replicate.
+
+keywords          : "reliability, validity, measurement, reporting, replicability, credibility"
+wordcount         : "135"
 
@@
 footnotelist      : no
+
+header-includes:
+  - |
+    \makeatletter
+    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-1em}%
+      {\normalfont\normalsize\bfseries\typesectitle}}
+
+    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-\z@\relax}%
+      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+    \makeatother
+
+csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
+documentclass     : "apa7"
 
@@
 rstudioapi::versionInfo()
+
 ```
@@
 
-# Introduction
+<!-- Introduction -->
 
@@
 Unfortunately, psychology seems to face several threats to the credibility of its findings.
-In this article, we investigate how the credibility of psychological findings may be affected by problems in psychological measurement, and in turn, how those problems may affect successful replication.
-
-### Credibility & Replicability
+In this article, we investigate how the credibility of psychological findings may be affected by problems in psychological measurement, and in turn, how those problems may affect subsequent replications.
+
+## Credibility & Replicability
 
 A prerequisite for a credible finding is that it is replicable [@vazire2022CredibilityReplicabilityImproving].
-This means that the observed effect should be comparable across the original study and subsequent replications as long as the differences between them are believed to be of little relevance to the effect [@nosek2022replicability].
-
-In practice, effects deviate substantially between original and replication research.
-In 2015, the Replication Project: Psychology (RPP) attempted replications of 100 research findings in psychology, they observed a substantial discrepancy between the replication findings as compared to the original findings [@osc2015estimating].
-Similarly, the Many Labs projects replicated the effects reported in original articles across different labs in various locations around the world [@klein2014investigating; @camerer2016evaluating; @camerer2018evaluating; @ebersole2016many; @ebersole2020many; @klein2018many; @klein2022many].
-There it was observed that effects were on average smaller in replication compared to original research.
-Furthermore, there was variation within the estimates of the effect between different lab locations.
-
-In response to this string of failed replications, there was widespread alarm regarding the credibility and robustness of findings in psychological science [@hughes2018psychology; @giner2019crisis].
-Simultaneously researchers sought to explain this discrepancy.
+This means that the observed effect should be comparable across the original study and subsequent replications if the differences between them are believed to be of little relevance to the effect [@nosek2022replicability].
+
+But replications often fail.
+In 2015, the Replication Project: Psychology (RPP) attempted replications of 100 research findings in psychology, they observed a substantial discrepancy between the replication findings and the original findings [@osc2015estimating].
+Similarly, the Many Labs projects aimed to replicate the effects reported in original articles across different labs in various locations around the world [@klein2014investigating; @ebersole2016many; @ebersole2020many; @klein2018many; @klein2022many], and often found smaller effects in replications compared to original research.
+Furthermore, the estimates of the effect varied between different lab locations.
+
+In response to this string of failed replications, there was widespread alarm regarding the credibility and robustness of findings in psychological science [@hughes2018psychology; @giner2019crisis], and efforts to explain failures to replicate.
 The factors that have been proposed include, questionable research practices [@simmons2011false; @john2012measuring; @cumming2014new; @wicherts2016degrees], questionable reporting practices [@bakker2011mis; @nuijten2016prevalence], and biased publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science].
-A factor that has gained more traction recently is the impact of measurement-related challenges on replicability.
-
-### Credibility & Measurement
-
-Measurement in psychological science is characterized in large part by one overarching issue: psychological constructs, such as affective state or intelligence, can usually not be measured directly [@flake2017construct].
-As a result, psychologists face two primary challenges in the use of measurement: First of all, because the measurement is indirect, it also comes with some degree of random error surrounding its assessment.
-Secondly, the responses on the measure have to relate to the psychological construct(s) of interest, but as the construct is not directly observable, this is difficult to assess.
+Another factor that has gained more traction recently is the impact of measurement-related challenges on replicability and credibility.
+
+## Credibility & Measurement
+
+Psychological constructs, such as affective state or intelligence, can not be measured directly [@flake2017construct].
+Psychological measurements involve random measurement errors and uncertainties about whether the targeted construct is indeed well reflected in the scores retrieved from the measurement procedure.
 
@@
 Reliability is a critical first step to obtaining credible findings.
-Because if the scores on a measure are not consistent with themselves, it is unlikely that any effect associated with the measure can be consistently established.
-
-The second issue relates to the concept of validity, and specifically construct validity.
-Validity in measurement refers to the overall extent to which a measure measures what it is supposed to [@borsboom2004concept], while construct validity refers to the substantial relation between the scores on a measure and the related psychological construct.
-A researcher cannot assume to have found a credible psychological effect, if the measures do not relate to a psychological construct [@cook2002experimental].
-
-### Replicability & Measurement
-
-Whereas both reliable and valid measurement and replicability are important elements that independently contribute to the overall credibility of a finding, there may also be a relation between the two.
-Indeed, recent studies have illustrated that both the reliability of the measure [@stanley2014expectations] and the reporting of the measure [@shaw2020measurement; @flake2017construct; @flake2020measurement] can affect the credibility of psychological studies, and in turn explain the lack of replication success.
-This study aims to investigate the influence of both measurement reliability and measurement reporting on replicability, using data and reports from the large scale Many Labs replication projects.
-
-### Many Labs Sample Description
-
-In the Many Labs projects each effect was directly replicated across multiple lab locations over the world.
-As a result the data obtained from these measures allows us to say something about the variability in these measures across different contexts.
-Another important aspect of the Many Labs projects is that the measurement was preregistered and documented in structured protocols that were used to instruct all the participating labs.
-We believe that these represent some of the best practices in measurement usage in psychology.
-Therefore, any problems with the measurement and its reporting encountered in this sample would not bode well for measurement in the rest of psychology.
+Because if the scores on a measure are not consistent with themselves, it is unlikely that any effect associated with the measure can credibly be established.
+Psychometrics offers various ways to assess reliability empirically [e.g.
+@nunnally1978overview; @mellenbergh2011conceptual].
+
+The second issue relates to the concept of validity, specifically construct validity, or the overall extent to which a measure measures what it is supposed to  measure [@borsboom2004concept].
+Construct validity of test scores is often assessed by comparing the test scores’ empirical associations to the theoretical associations of the constructs [@cronbach1955construct].
+A researcher cannot claim to have found a credible psychological effect, if the measures do not relate to the psychological construct [@cook2002experimental].
+
+## Replicability & Measurement
+
+While reliable and valid measurement, as well as replicability are important elements that independently contribute to the overall credibility of a finding, there may also be a relation between them.
+Indeed, recent studies have illustrated that both the reliability of the measure [@stanley2014expectations] and the reporting of information relevant to demonstrating the validity of the measurement [@shaw2020measurement; @flake2017construct; @flake2020measurement] may be related to the chance of successfully replicating a psychological finding.
+This study aims to investigate the relation of reliability and measurement reporting with replicability, using data and reports from the large scale Many Labs replication projects.
+
+## Many Labs Sample Description
+
+Because the Many Labs projects involved multiple lab locations over the world directly replicating the same effect, their data allows us to study the variability in these measures across different contexts.
+Furthermore, the Many Labs projects used preregistered and documented structured protocols, we therefore believe the measurement use in these projects represent a high standard within the field.
+Any issues in measurement here is thus taken as an indication that other replications are equally if not more likely to face the same issues.
 
@@
 While reliability is generally considered a measure specific feature, this is false.
-The reliability of a measure is context dependent [@cho2015cronbach; @pauly2018resampling], and as a result so are the scores obtained with that measure.
-The contextual variations in the measurement scores could explain the discrepancy between effects in original and replication research, as well as within replications of the same original effect.
+The reliability of a measure varies between samples, and thus  [@cho2015cronbach; @pauly2018resampling].
 Besides random variation due the sampling error, the variations can also reflect true variation in reliability, also known as reliability heterogeneity [@vacha-haase1998ReliabilityGeneralizationExploring].
@@
 
-However, even when reliability is the same across studies, reliability can still cause estimates of the same effect to vary significantly.
+The resulting variations in the measurement scores could contribute to the discrepancy between effects in original and replication research, as well as within replications of the same original effect.
+After all it has long been known that noise in measurement suppresses observed effects and associations [@spearman1904proof].
 @stanley2014expectations simulated data of items on a scale based on levels of sampling error and reliability similar to what is standard in psychological research.
-The results indicated that measurement error due to imperfect reliability caused variation in the observed effect sizes in the simulated replications, on top of sampling error.
-The added variation was substantial enough to cause replications of a positive small effect to observe anywhere between a medium negative effect and a large positive effect [@stanley2014expectations].
-This implies that studies using unreliable measures have a lower probability to be successfully replicated, even if the underlying effect is true and the measurement is equally reliable between original and replication.
+The results showed that the variation due to measurement error was substantial enough to cause replications of a positive small effect to observe anywhere between a medium negative effect and a large positive effect [@stanley2014expectations].
+In summary, studies using unreliable measures are less replicable, even when the measurement is equally reliable between original and replication.
 
@@
 
-Despite the importance of having reliable and valid measures, research has shown that Questionable Measurement Practices (QMPs) in reporting are not uncommon.
+Despite the importance of having reliable and valid measures, research has shown that Questionable Measurement Practices (QMPs) are not uncommon.
 QMPs are practices that raise doubts about a measurement's validity [@flake2020measurement], and have been coined as a conjugate term to Questionable Research Practices [QRPs, @john2012measuring].
 QMPs range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of measure and procedure of any sourced measures [@flake2020measurement].
-
-@flake2020measurement identified the main questions that the article should answer in relation to the measurement used: the definition of the construct, how the measure was selected, how the measure was operationalized, how the measure was quantified, whether it was modified or not and why, and the reasons and details of creating a measure if applicable.
-The questions together form the basis of the information that a researcher should present in order to be transparent and promote a more cumulative psychological science.
+More specifically,  @flake2020measurement identified six key questions than an article should answer to avoid QMPs: the definition of the construct, how the measure was selected, how the measure was operationalized, how the measure was quantified, whether it was modified or not and why, and the reasons and details of creating a measure if applicable.
+If these questions can be answered based on the reported measurement information, then reporting is sufficiently transparent to promote a more cumulative psychological science.
 
@@
 Besides limited reporting of validity and reliability evidence for the coded measures, @flake2022construct found that several of the measures in the RPP did not report the number of items, the response format, or the scoring of the scale.
-Furthermore, only 8 of the 40 translated scales contained validity evidence for the translated version of the scale.
+Furthermore, only eight of the 40 translated scales contained validity evidence for the translated version of the scale.
 Measures were similarly modified between original and replication in other ways without evidence showing that the modification did not invalidate the measurement.
 
-Further findings by @flake2022construct and others [@flake2017construct; @shaw2020measurement] illustrated how QMPs create challenges for replicating researchers.
-Replicating researchers will need detailed information on the measurement in the original study to reconstruct it.
-If the measure is not reconstructed exactly, original and replication may be measuring different construct(s).
-In that case, different effect size estimates in original compared to replication research may very well be due to the fact that the effects are between different constructs, and not because the effect was not robust to sampling error.
+Further findings by @flake2022construct and others [@flake2017construct; @shaw2020measurement] also illustrated how QMPs create challenges for replicating researchers.
+In order to reconstruct the measurement, replication researchers need to know the items that were used, how they were presented to the subjects, and how to compute the scores.
+If the measure is not reconstructed exactly, constructs measured by original and replication may differ.
+leading to differences in effect size estimates irrespective of the credibility of the original effect.
 
@@
 
-Our study aimed to investigate the influence of both measurement reliability and measurement reporting on replicability, using data and reports from the large scale Many Labs replication projects.
-Firstly, this study expands on the research by @stanley2014expectations using an empirical example.
-Our goal was to see whether reliability was related to replication success on real life replication data.
-In practical terms, we investigated whether or not replicated studies differed in their reliability scores from non-replicated studies.
-In their study @stanley2014expectations assumed reliability to be constant across studies, which we know to be an oversimplification.
-Therefore, to add further context to relation between reliability and replication, this study also investigated the variation in reliability as observed across separate measurement occasions.
+Our study investigated the relation of reliability and measurement reporting with replicability, using data and reports from the large scale Many Labs replication projects.
+First, this study expands on the research by @stanley2014expectations.
+Our goal was to see whether reliability was related to replication success on empirical replication data.
+Specifically, we investigated whether replicated studies differed in their reliability from non-replicated studies.
+@stanley2014expectations assumed reliability to be constant across studies, which we know to be an oversimplification.
+Therefore, to add further context to the relation between reliability and replication, this study also investigated the variation in reliability as observed across labs.
 
@@
 
-## Research Questions & Hypotheses:
+## Research Questions & Hypotheses
 
@@
 
-Measurement reliability varies across contexts. It is crucial for evaluating replications that differences between replication and original are understood and accounted for.
-
--   RQ1a. What is the degree of score reliability in replications of psychological research?
--   RQ1b. What is the degree of score reliability in original psychological research?
+Measurement reliability varies across samples. It is crucial for evaluating replications that differences between replication and original are understood and accounted for.
+
+-   RQ1a. What is the reliability in replications of psychological research?
+-   RQ1b. What is the reliability in original psychological research?
 
@@
 
--   H1. No difference is present in the degree of score reliability between replication research and original psychological research.
-
-Reliability has the potential to vary not only between replication and original research, but also within replications of the same effect [@vacha-haase1998ReliabilityGeneralizationExploring].
-
--   RQ2. To what degree do reliability estimates differ within a replication set of the same original study?
-
-Heterogeneity could be a major contributor to this variation.
-However for effect sizes there is little empirical evidence of widespread heterogeneity among the Many Labs replications [@klein2018many; @olsson2020heterogeneity].
-The same is expected to hold true for the heterogeneity in reliability coefficients among the Many Labs replications.
+-   H1. No difference is present in the reliability between replication research and original psychological research.
+
+Reliability has the potential to vary not only between replication and original research, but also across replicating labs assessing the same effect [@vacha-haase1998ReliabilityGeneralizationExploring].
+
+-   RQ2. Do reliability estimates differ between replicating labs?
+
+Heterogeneity in reliability may be contributing strongly to the variation in reliability between labs.
+However, for effect sizes there is little empirical evidence of widespread heterogeneity among the Many Labs replications [@klein2018many; @olsson2020heterogeneity].
+We expect the same for the heterogeneity in reliability coefficients.
 
@@
 
-In order to see if reliability has an impact on replication attempts, we investigated whether or not successfully replicated studies differ in the reliability of their measures as compared to non-replicated studies.
-
--   RQ3. What is the association between replication study score reliability and replication outcome?
+To see if reliability is related to replication success, we investigated whether successfully replicated studies differ in the reliability of their measures as compared to non-replicated studies.
+
+-   RQ3. What is the association between replication study reliability and replication outcome?
 
 Greater reliability means the variance around the estimate of the true effect is decreased [@nunnally1994assessment].
-Assuming that the true effect is not null, then the statistical conclusions tested with reliable measures are be more likely to converge to significance.
-
--   H3. Score reliability in replication research is positively associated with successful replication of an original finding.
+Assuming that the true effect is not null, then the statistical conclusions tested with reliable measures are more likely to converge to significance.
+
+-   H3. Reliability in replication research is positively associated with successful replication of an original finding.
 
@@
 
-With respect to measurement reporting, this study first of all aims to conceptually replicate some of the findings of @flake2022construct.
-
--   RQ4a. To what degree are QMPs present in replications of psychological research?
--   RQ4b. To what degree are QMPs present in original psychological research?
+This study aims to conceptually replicate the findings on measurement reporting of @flake2022construct.
+
+-   RQ4a. How common are QMPs in replications of psychological research?
+-   RQ4b. How common are QMPs in original psychological research?
 
 @flake2022construct found that QMPs were overall more common in the RPP replications as compared to the original research.
-We did not hypothesize this same effect to hold for the Many Labs sample, because of the use of structured protocols documenting the measurement.
-
--   H4. QMPs are expected to be more frequent in original psychological research than in replication research.
-
-Differences in measurement resulting from QMPs have been suspected to cause replication and original effects to deviate [@flake2022construct].
-Investigating the link between QMPs and non-replicability should put this suspicion to the test.
+We did not hypothesize this to be the case in the Many Labs sample, because of the use of structured protocols documenting the measurement.
+
+-   H4. QMPs are more frequent in original psychological research than in replication research.
+
+QMPs obscure information relevant to mimic measurement from original research in subsequent replication attempts.
+The resulting deviations in measurement may be partly responsible for deviations in replication and original effects [@flake2022construct].
 
@@
 A reduction in QMPs corresponds to greater transparency in reporting of measurement.
-Research on other transparency related practices have shown that these are associated with more robust estimates of effects [@wicherts2011willingness; @protzko2020high].
-We expect a similar effect for QMPs.
-
--   H5. QMPs in replication research are negatively associated with successful replication of an original finding.
-
-One of the reasons measurement in replication may deviate is because original articles did not report all the necessary information needed to mimic the original measurement.
-In this way a lack of information may carry over from the original article to the replication.
+In line with earlier research finding other transparency related practices to be associated with more robust estimates of effects [@wicherts2011willingness; @protzko2020high], we expect:
+
+-   H5. QMPs in replications are negatively associated with replication success.
+
+QMPs obscure information about a particular measurement. This in turn may cause issues for reconstructing that measurement in subsequent replication attempts.
 
@@
 
-Previous research by @flake2022construct has shown that QMPs in original articles cause issues for recreating measurements for replication research.
-Additionally, @shaw2020measurement found similar spill-over effects for validity.
-Based on these findings, QMPs in original research were expected to be associated with QMPs in replication research.
-
--   H6. Total number of QMPs in original psychological research is positively related to total number of QMPs in replication research.
+@flake2022construct already proposed that QMPs in original articles may cause issues for recreating measurements for replication research.
+@shaw2020measurement already found such a spill-over effect for validity.
+In line with this research we expect:
+
+-   H6. The total number of QMPs in original psychological research is positively related to the total number of QMPs in replication research.
 
@@
 
-Data collection, coding protocol, and planned analyses were all preregistered.
-The preregistration and supplementary materials can be found on this article's OSF page: <https://osf.io/9r8yt/>.
-Any deviations from the preregistration are explicitly mentioned in the text.
+We preregistered data collection, coding protocol, and planned analyses: <https://osf.io/9r8yt/>. Deviations from the preregistration are explicitly mentioned in the text.
 
@@
 
-This manuscript was created in Rstudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency.
-All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> & <https://osf.io/9r8yt/>.
+This manuscript was created in RStudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency.
+All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> and <https://osf.io/9r8yt/>.
 
@@
 
-We report how we determined all data exclusions, all manipulations, and all measures in the study. Our sample size was based on the number of usable studies in the Many Labs studies.
+We report how we determined all data exclusions, all manipulations, and all measures in the study. Our sample size was predetermined by the number of studies in the Many Labs projects.
 
@@
 
-This research was approved by the Tilburg University School of Social and Behavioral Sciences Ethical Review Board.
+This research was approved by the Tilburg University School of Social and Behavioral Sciences Ethical Review Board (nr. TSB_TP_REMA06).
 
@@
 
-The data used for the analyses in this study consists of three main sources: replication datasets, preregistered replication protocols, and original study articles.
-The data came from the Many Labs series of studies.
-In particular, data from Many Labs 1, 2, 3, & 5 was used [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many].
-Data from Many Labs 4 [@klein2022many] was not part of the sample, as there was no publicly available protocol which contains the information needed to code QMPs.
+The data used for the analyses consisted of three main sources: replication datasets, replication protocols, and original study articles.
+The data came from the Many Labs replication projects.
+Specifically, data from Many Labs 1, 2, 3, & 5 [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many].
+Many Labs 4 [@klein2022many] was excluded, as there was no publicly available replication protocol.
 Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study's focus on item-based measures.
@@
 
-Measures were identified using the preregistered replication protocols.
+The unit of analysis in this study was a measure of a psychological construct used in the primary analysis that was being replicated.
+We used the the replication protocols to identify these measures.
 Acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses were not included.
-The result was a total sample size of `r nrow(coded_data_replications)` measures used in both original and replication research[^1].
-
-[^1]: Initially the original articles contained 3 more measures than the replication protocols.
-This difference was due to the way that the moral foundations questionnaire was framed in the original articles compared to in the original article.
-In the original article it was framed as measuring five different moral foundations, while in the replication protocol the measure was described as measuring the two overarching categories that were used to test the main effect in the original and replication research.
-The measurement information reported was comparable across all five categories, and thus it was deemed that the measurement could be reduced to reflect two overarching categories to make comparison between original and replication easier.
 
@@
 
-The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>.
+We retrieved the data on the replication protocols, and replication datasets of Many Labs 1, 2, 3, & 5 from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>.
 Both the replication protocols and replication datasets were scanned through to ensure that the planned analyses were feasible.
 However, no coding or analysis of either of them had taken place before the analyses were preregistered.
-Further details on the search strategy can be found in the [coding protocol information file](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) supplementary materials.
+Further details on the search strategy can be found in the [coding protocol information file](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) in the supplementary materials.
 
@@
 
-The replication datasets refer to the publicly available datasets containing the data obtained from all of the labs that took part in one of the Many Labs studies.
-These datasets were accessed through their OSF page.
-For the analyses, the scores on the items of an identified measure were identified and extracted.
+The replication datasets refer to the publicly available datasets containing the data obtained from all labs that took part in a Many Labs study.
+For the analyses, we extracted the scores on the items of each previously identified measure that met our inclusion criteria specified below.
 When scores could not be clearly identified, any available codebooks, analysis scripts or study materials were used to identify the relevant scores.
 
-In order to be considered suitable for the planned analyses on calculated reliabilities, the measure had to be a scale consisting of multiple items.
+To be included in the planned analyses on calculated reliabilities, the measure had to be a scale consisting of multiple items.
 If cleaned data was available this was chosen over raw data, to ensure that variables were coded as intended (e.g.
@@
 Pilot data were omitted from the analyses entirely.
-These criteria resulted in suitable item score data from `r apa_num(length(unique(data_h3_multiple$g)), numerals = FALSE)` replication sets spread across on average `r apa_num(mean(table(data_h3_multiple$g)), digits = 0)` lab locations for the analyses of hypotheses 2 & 3.
+These criteria resulted in suitable item score data from `r apa_num(length(unique(data_h3_multiple$g)))` replication sets spread across on average approximately `r apa_num(mean(table(data_h3_multiple$g)), digits = 0)` lab locations for the analyses of Hypotheses 2 & 3.
 
@@
 
-### Preregistered Replication Protocols
-
-The preregistered replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each set of replications replicating a single original study across multiple labs.
-
-The OSF page for each Many Labs project was combed through, in order to identify the documents that contained information on the measurement practice and reported reliability.
-For Many Labs 2, & 3 a single replication protocol for all studies could be identified.
-For Many Labs 1, the Proposal_V1.1 provided the equivalent information, while for Many Labs 5 protocols were available for each set of replications separately.
-
-The relevant OSF page of each replication set was searched through for a file which contained protocol in its name.
-If available, a version of the protocol labelled as revised, post-review, peer-review, or endorsed was selected.
-Otherwise, the latest uploaded relevant protocol was selected.
-Protocols labelled as data collection, analysis protocol or anything similar were excluded[^2].
-
-[^2]: The steps taken to access the replication protocol data from Many Labs 5 were not preregistered, and only became clear upon further investigation of the accessible information.
-The specific names and locations of the files that were used as the datasets can be found in the data_search_details.pdf supplementary materials of this article <https://osf.io/gft46/%7D>.
-
-Finally, the published reports of the Many Labs projects [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many] were used to determine whether not the replication was considered successful.
+### Replication Protocols
+
+The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each set of replications replicating a single original study across multiple labs.
+These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [Data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document.
 
@@
 
-The original study articles are the published articles of the original effect on which the Many Labs replication sets were based.
-They were identified using the citations for these articles in each replication protocol.
-In the end all articles could be retrieved through searches on Web of Science, Google Scholar, and PsychInfo (in that order)[^3].
-
-[^3]: An issue was encountered while trying to access @hyman1950current. However, after contacting the first author of @klein2014investigating a suitable version of the article was obtained.
+The original study articles were identified using the citations for these articles in each replication protocol. All articles could be retrieved.
 
@@
 
-A structured coding protocol (available on the relevant OSF: <https://osf.io/9r8yt/>, and github pages: <https://github.com/CasGoos/measurement_and_replication.git>) was used to extract information on the reported measurement evidence and reporting quality for both replication protocols and original studies.
-The coding protocol and explanation of its use can be found in the coding protocols folder of the supplementary materials.
+We developed and used a coding protocol (the [coding protocol](../../SupplementaryMaterials/CodingProtocols/Measurement_Error_Reporting_Revised_Coding_Protocol.pdf) is available in the supplementary materials) to extract information on the reported measurement evidence and reporting quality for both replication protocols and original studies.
 
@@
 
-Because data from the Many Labs replications was available for each lab location within a replication set, it was possible to calculate score reliabilities for the item scale measure used for each lab location separately.
-This made it possible to assess the variation of score reliabilities of the same measure across different contexts.
-
-Cronbach's alpha was calculated as the main score reliability index used in the analyses, as it remains the most commonly used indicator of the reliability of a measure [@flake2017construct].
-This is important for facilitating comparison between the calculated replication reliabilities and the reported original article reliabilities.
-Cronbach's alpha was calculated using the alpha function from the psych R package [@R-psych].
-Default arguments were used for the function.
-Omega was pre-registered as an additional reliability index score, because it is regarded by numerous psychometricians as a more informative alternative to Cronbach’s Alpha.
+Because data from the Many Labs replications were available for each lab location within each replication set, it was possible to calculate reliabilities for any item scale measure used for each lab location separately.
+This made it possible to assess the variation of reliabilities of the same measure across different contexts.
+
+Cronbach's Alpha was calculated as the main reliability index used in the analyses, as it remains the most commonly used indicator of the reliability of a measure [@flake2017construct], thus allowing for comparisons with the reliabilities reported in original articles.
+Cronbach's Alpha was calculated using the alpha function from the psych R package [@R-psych] with default arguments.
+Omega was pre-registered as an additional index of reliability, because it is regarded by numerous psychometricians as a more informative alternative to Cronbach’s Alpha [@crutzen2017scale; @deng2017testing].
 The results based on Omega can be found in [Appendix C](AppendixScripts/Appendix_multilevel_analyses.Rmd).
@@
 
-In order to answer questions regarding reported reliability, the reported reliability coefficient of a measure was extracted from both the replication protocols and the original articles when present.
-Both the type (Cronbach's alpha, retest, interrater, etc.) and the value itself were extracted.
-Similarly, we coded the presence of any validity evidence, such as a factor analysis, alongside the measure.
-The aim here was to gauge the presence of factor analyses within the articles and protocols, for comparison with @shaw2020measurement.
-
-The tests for hypotheses 4, 5, & 6 were all based on the QMPs coded for both original articles and replication protocols.
-The QMPs we coded were in part based on @flake2022construct.
-Additional items were added to more fully reflect the broader questions regarding transparent measurement reporting laid out in @flake2020measurement.
+We extracted the reported reliability coefficient and type of index (Cronbach's Alpha, retest, interrater, etc.) of a measure from both the replication protocols and the original articles when present.
+Similarly, we coded the presence of any validity evidence, such as a factor analysis, that was presented alongside the measure.
+
+The tests for Hypotheses 4, 5, & 6 were all based on the QMPs coded for both original articles and replication protocols.
+We included items based on @flake2022construct, and additional items to further assess transparent measurement reporting as laid out in @flake2020measurement.
 In total, we coded `r sum(colnames(coded_data_replications) == "def1" | colnames(coded_data_replications) == "op_1" | colnames(coded_data_replications) == "op_2" | colnames(coded_data_replications) == "op_3" | colnames(coded_data_replications) == "op_4" | colnames(coded_data_replications) == "op_5" | colnames(coded_data_replications) == "sel_1" | colnames(coded_data_replications) == "sel_2" | colnames(coded_data_replications) == "sel_3" | colnames(coded_data_replications) == "sel_4" | colnames(coded_data_replications) == "quant_1" | colnames(coded_data_replications) == "quant_2" | colnames(coded_data_replications) == "quant_3" | colnames(coded_data_replications) == "quant_4" | colnames(coded_data_replications) == "mod_1" | colnames(coded_data_replications) == "mod_2" | colnames(coded_data_replications) == "mod_3" | colnames(coded_data_replications) == "mod_4" | colnames(coded_data_replications) == "mod_5" | colnames(coded_data_replications) == "mod_6")` different QMPs, categorized into five QMP type categories based on @flake2020measurement.
-An overview of the QMP categories and items can be seen in Table \@ref(tab:QMPCodingInfoTable).
+The QMP categories and example items can be seen in Table \@ref(tab:QMPCodingInfoTable).
 
@@
   , caption = "Information of QMP coding variables per category."
-  , note = "N Questions refers only to the questions considered used for calculating QMP ratios.
+  , note = "N Questions refers only to the questions used for calculating QMP ratios.
 Selection and creation share a category as the justifications and requirements in selecting a measure are similar to those for creating a new measure."
@@
 
-QMPs were all coded to be either true, false, or not applicable if not relevant for that particular measure (e.g.
+QMPs were all coded to be either true, false, or not applicable if not relevant for that measure (e.g.
 reporting results from a factor analysis for single item measures).
-For the analyses a ratio was calculated based on the responses to the QMP questions.
-This ratio was based on the number of true responses divided by the number of responses coded to be applicable.
-The ratio was calculated for each QMP type and across all QMPs together.
-
-After the initial coding was completed, we made a small revision to the preregistered coding protocol.
-The protocol was changed because some items were considered too stringent in their criteria for what constituted a QMP.
+For the analyses we calculated a ratio (both per QMP type and overall QMP) based on the number on the number of true responses divided by the number of responses coded to be applicable.
+
+After the initial coding, we made a small revision to the preregistered coding protocol, because `r length(coded_data_revised_raw[1, c("Op1", "Op2", "Op5", "Sel1", "Sel3", "Quant1", "Quant2", "Quant3", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` of the `r length(coded_data_initial_raw[1, c("Def1", "Op1", "Op2", "Op3", "Op4", "Op5", "Sel1", "Sel2", "Sel3", "Sel4", "Quant1", "Quant2", "Quant3", "Quant4", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` QMP items were considered too stringent in some of their criteria for what constituted a QMP.
 For example, in the initial protocol an example item had to be present within the article or protocol itself, or else this was counted as a QMP.
-In the revised protocol, references to online appendices with example items were also considered sufficient.
-The analyses, tables and figures presented in this article are all based on the revised coding protocol, the equivalent results based on QMPs obtained with the initial protocol can be found in [Appendix D](AppendixScripts/Appendix_initial_QMP_analyses.Rmd), the initial protocol data and analysis code is available on this article's OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages.
+In the revised protocol, references to online appendices with example items were also considered sufficient for this item.
+The analyses, tables and figures presented in this article are all based on the revised coding protocol, the equivalent results based on QMPs obtained with our initial protocol can be found in [Appendix D](AppendixScripts/Appendix_initial_QMP_analyses.Rmd).
 
@@
 
-Replication success was determined based on the significance of the meta-analytic effect of the replication set as reported in its respective Many Labs report.
-An effect was considered replicated if the meta-analytic effect was in the same direction as the original effect and had a p-value lower than .05.
+We used the published reports of the Many Labs projects [@klein2014investigating; @ebersole2016many; @ebersole2020many; @klein2018many] to determine replication success based on the reported significance of the meta-analytic effect.
+An effect was considered successfully replicated if the meta-analytic effect was in the same direction as the original effect and had a p-value lower than .05.
 
@@
 No correction for multiple testing was applied, to ensure that the rate of false negatives remained low.
-False negatives were considered more harmful than false positives, because with our hypothesis tests we exploratively investigated associations that have been alluded to in the literature, but not yet empirically tested.
+Our hypotheses are about associations that to the authors' knowledge have been proposed in the literature, but not yet empirically tested on real data.
+In this exploratory context, false negatives were considered more harmful than false positives.
 
@@
 
-The number of replication sets, measures, and measures per study that were extracted, as well as the ratio of successful replications can be seen in Table \@ref(tab:ReplicationRatioTable), for each of the Many Labs separately and in total.
+The number of replication sets, measures, and measures per study that were extracted, as well as the proportion of successful replications can be seen in Table \@ref(tab:ReplicationRatioTable), for each of the Many Labs separately and in total.
 
@@
 
-# converting columns to string to then add a superscript to one of the elements
-# in the table.
-replication_ratio_table$"Nr. Replicated" <- as.character(replication_ratio_table$"Nr. Replicated")
-
 # adding a superscript for a later footnote
-replication_ratio_table$"Nr. Replicated"[3] <- "$3^b$"
+replication_ratio_table$"Nr. Replicated"[3] <- "$3^a$"
 
@@
   , note = "Nr.
-measures refers to the total number of measures extracted, while Nr.
-replicated displays the number of measures for which the associated effect was replicated succesfully.
-$^a$ refers only to the number of identified primary measures, which this study is concerned with.
-$^b$replication was assessed as unclear for three other measures, since their effect was only partially replicated.
-These have been treated as not replicated within this table and further analyses throughout the article.
+measures refers to the total number of primary measures extracted, while Nr.
+replicated displays the number of measures for which the associated effect was replicated successfully.
+$^a$replication was assessed as unclear for three other measures, since their effect was only partially replicated.
+These have been treated as not replicated within this table and in further analyses throughout the article.
 "
@@
 
-The number of participants in the replication studies, and the associated articles are displayed in Figure \@ref(fig:DataStructurePlotCode).
-As might be expected, the Many Labs replications always had larger sample sizes than the original articles.
-Furthermore, the figure shows that the replications are nested in Many Labs projects, and for some replications multiple measures were used within one replication.
-
-```{r DataStructurePlotCode, warning = FALSE, fig.cap = "This figure displays the sample size for the included original articles and total sample size for multiple replications.
-The color of the point indicates whether it represents an original article or a replication.
-The point's shape relates to whether the hypothesis was supported or not, while the size indicates the number of measures for that article or replication.
-The figure is log10-scaled, each light grey vertical line represents a step of 500 in sample size.
-Two original articles are not represented in this figure due to them containing no reported sample size.", fig.height = 3.5, fig.width = 12}
-
-# plot of the multilevel data structure
-ggplot(plot_data_structure_data, aes(x = N, y = factor(many_labs_version, levels = c("5", "3", "2", "1")), 
-                                colour = rep_org, shape = hypothesis_support, size = measure_count)) +
-  geom_point(alpha = .33) +
-
-  scale_x_continuous(trans = "log10", breaks = c(10, 100, 1000, 10000), 
-                     labels = c(10, 100, 1000, 10000), limits = c(10, 10000),  
-                     minor_breaks = seq(500, 10000, 500)) +
-
-  theme_minimal() +
-  theme(plot.margin = unit(c(1, 6.5, 1, 1), "lines"), 
-        panel.grid.major.x = element_line(color = "grey",
-                                          size = 0.5,
-                                          linetype = 1)) +
-
-  guides(color = guide_legend(nrow = 1, byrow = TRUE)) +
-  guides(shape = guide_legend(nrow = 2, byrow = TRUE)) +
-  guides(size = guide_legend(nrow = 2, byrow = TRUE)) +
-
-  labs(x = "N", y = "Many Labs Version", color = "Obtained from:", 
-       size = "Nr. measures", shape = "Replicated")
-
-```
+Our data had a multilevel structure.
+Each replication was nested within one of four Many Labs projects.
+Furthermore, `r sum(coded_data_replications$appearance != 1)` replications used more than one primary measure, resulting in `r nrow(coded_data_replications)` measures in both `r sum(coded_data_replications$appearance == 1)` replications protocols and `r sum(coded_data_original$appearance == 1)` original articles[^1].
+Of these `r nrow(coded_data_replications)` measures `r sum(coded_data_replications$mod_check == "True")` were modified from the original to the replication.
+The total sample size in the replications was on average `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N), 0)` which was approximately `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N) / mean(coded_data_original_shortened[coded_data_original_shortened$appearance == 1 & !is.na(coded_data_original_shortened$N),]$N), 0)` times larger than the average in original studies.
+
+[^1]: Initially the original articles contained 3 more measures than the replication protocols.
+This difference was due to the way that the moral foundations questionnaire was framed in the original articles compared to in the original article.
+In the original article it was framed as measuring five different moral foundations, while in the replication protocol the measure assessed the two overarching categories that were used to test the main effect in both the original and replication research.
+The measurement information reported was comparable across all five categories, and thus it was deemed that the measurement could be reduced to reflect two overarching categories facilitate easier comparison between measurement in original and replication.
 
@@
 
-If data from a multiple item scale could be accessed, the Cronbach’s Alpha of that scale was calculated from that data for each lab that administered the scale.
-As a result, it was possible to include the multiple estimates of Cronbach’s Alpha into a meta-analysis of the reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analyses [@vacha-haase1998ReliabilityGeneralizationExploring; @botella2012ManagingHeterogeneityVariance; @lopez-ibanez2024ReliabilityGeneralizationMetaanalysis], for each of the measures.
-This enabled us to quantify the degree of true variation (or heterogeneity) in reliability coefficients across different studies.
-
-A meta-analysis requires an estimate of the standard error.
-For Cronbach's alpha, formulas 2 & 3 from @duhachek2004AlphaStandardError were used to calculate its standard error.
+If data from a multiple item scale could be accessed, we calculated the Cronbach’s Alpha of that scale from that data for each lab that administered the scale.
+As a result, it was possible to include the multiple estimates of Cronbach’s Alpha for those measures into a meta-analysis of the reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analysis [@vacha-haase1998ReliabilityGeneralizationExploring; @botella2012ManagingHeterogeneityVariance; @lopez-ibanez2024ReliabilityGeneralizationMetaanalysis].
+This enabled us to quantify the degree of true variation (or heterogeneity) in reliability coefficients across lab locations.
+
+For Cronbach's alpha, we used formulas 2 & 3 from @duhachek2004AlphaStandardError to calculate the standard error in the meta-analysis.
 Heterogeneity was estimated using the tau value, which indicates the standard deviation of the distribution of true Cronbach's alpha coefficients for a measure, and tested using the Cochran's Q test for each measure.
@@
 Defaults settings were used.
-No correction for bias was implemented, because the Many Labs replications were not at risk of publication bias.
+We implemented no correction for bias, because the Many Labs replications were not at risk of publication bias.
 
@@
 
-```{r Plot23AlphaCode, warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the eighteen distinct measures for which suitable raw data was available to calculate Cronbach’s alpha coefficients from.
+```{r Plot23AlphaCode, warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the eighteen distinct measures for which raw data was available from which Cronbach’s alpha coefficients could be calculated.
 The green lines indicate the meta-analytic prediction interval lower and upper bound.
-The blue triangles indicate the reported alpha coefficient for that measure from the original article, when available.
+The blue triangles indicate the reported alpha coefficient for that measure from the original article, when reported.
 The Tau column besides the figure shows the tau heterogeneity estimate based on a meta-analysis of the calculated reliabilities for each measure.
-Meta-analyses for which the Q-test for heterogeneity was signicant at alpha < .05 are in black, not significant results are left grey.
-The Diff column shows the difference between reported reliability and the average reliability calculated from the Many Labs data for the applicable measures, the differences in bold are for reported reliabilities that fell outside the 95% quantile of calculated reliability scores."}
+Meta-analyses for which the Q-test for heterogeneity was signicant at alpha < .05 are in black, while non-significant results are in grey.
+The Diff column shows the difference between reported reliability and the average reliability calculated from the Many Labs data for the applicable measures, the reported reliabilities that fell outside the 95% quantile of calculated reliability scores are shown in bold."}
 
@@
   xlab("Cronbach's alpha")
-```
-
-The distribution of the measures varies highly.
-Most of the measures near the bottom show average reliability scores of at least .80, corresponding to an adequate reliability for general research purposes [@nunnally1994assessment], with minimal variation between labs.
-However, other measures show not only considerably lower average reliability scores, but also greater variation.
-
-Finally, the blue triangles indicate the reported Cronbach’s Alpha.
-Noteworthy here is that the reliabilities were generally only reported for those measures with a large average calculated reliability.
+
+```
+
+The distribution of reliabilities varied across measures.
+Most of the measures near the bottom showed average reliability scores of at least .80, corresponding to adequate reliability for general research purposes [@nunnally1994assessment], with minimal variation between labs.
+However, other measures showed not only considerably lower average reliability scores, but also greater variation.
+
+Finally, the blue triangles indicate the Cronbach’s Alpha reported in the original articles.
+The reliabilities were generally only reported for those measures with a large average calculated reliability.
 
@@
 
-Initially, a Mann-Whitney U test was planned to test whether or not the value of the reported Cronbach’s Alpha was different for replications compared to original articles.
-However, there were not enough reported reliabilities to perform the test.
-However, if we take an exploratory look at Figure 2, we can see the difference between the reported reliability in the original article and the calculated average reliability in replications in the Diff column.
-The results show that the original article reliability is generally lower than the average calculated reliability of the same measure.
-These results are not in line with H1.
-However, more than half of the reported reliabilities fell within the 95 percentile range around the average.
+```{r ReportedReliabiltiesRetrieval}
+N_reported_reliabilities_original <- sum(coded_data_original_shortened$reliability_type != "Not Reported" & coded_data_original_shortened$reliability_type != "")
+
+N_reported_reliabilities_replications <- apa_num(sum(coded_data_replications$reliability_type != "Not Reported" & coded_data_replications$reliability_type != ""), numerals = FALSE)
+
+N_reported_reliabilities_replications_number_style <- apa_num(sum(coded_data_replications$reliability_type != "Not Reported" & coded_data_replications$reliability_type != ""))
+```
+
+The number of reported reliabilities were `r N_reported_reliabilities_original` in original articles and `r N_reported_reliabilities_replications` in replications, which was too low to ensure that the pre-registered Mann-Whitney U test can function as an informative test on the difference in the reported value of Cronbach's Alpha between original articles and replications.
+Instead, the difference between the reported reliability in the original article and the calculated average reliability in replications is displayed in the Diff column in Figure \@ref(fig:Plot23AlphaCode).
+Contrary to Hypothesis 1, this column shows that the reported reliability in original articles was generally lower than the average reliability in the replication sample.
+Still, more than half of the reported reliabilities did fall within the 95-percentile range around the replication average.
 
@@
 
-We used the RG meta-analyses to test if there was heterogeneity in these estimates, which would give us an indication of the true variability in these reliability scores.
-This analysis was not preregistered, because we were not aware of this technique at the time of preregistering.
-
-Figure \@ref(fig:Plot23AlphaCode) displays the tau score for each measure’s Cronbach’s Alpha, which indicates the true differences in reliability scores between labs.
-For some measures the tau estimate was approximately 0.
-But this was certainly not the case for all measures.
-For instance, for the top measure the Tau estimate was .108.
-This means that for the true effect one standard deviation is equal to .108 points of Cronbach’s Alpha.
-This estimate is without variance cause by sampling error.
-Figure \@ref(fig:Plot23AlphaCode) shows that for `r sum(data_h3_avg$QEp < .05)` out of the `r nrow(data_h3_avg)` measures, the Q-test for heterogeneity indicated that the true variation in reliability estimates was significant.
-
-These results would indeed indicate that for several measures in our sample, the reliability of the measures is heterogeneous, thus showing evidence in favor of rejecting H2.
-However, these results need to be taken with a grain of salt.
-Some of the measures had a lower number of studies and the Q-test is sensitive to sample size [@li2015DilemmaHeterogeneityTests].
-Furthermore, the evidence remains inconsistent when looking across all measures.
+To get an indication of the true variability in the reliability scores, we used the RG meta-analyses to test for heterogeneity in the reliabilities in the replications.
+This analysis deviated from the multilevel analysis we preregistered, as the preregistered analysis was later deemed not suitable for testing Hypothesis 2 (results from the preregistered analysis are shown in [Appendix A](AppendixScripts/Appendix_pre-reg_analyses.Rmd)).
+
+Figure \@ref(fig:Plot23AlphaCode) displays the tau estimates, which indicates the differences in true reliability scores between labs for a given measure.
+For `r sum(data_h3_avg$QEp > .05)` measures the tau estimate was not significantly different from 0, while for `r apa_num(sum(data_h3_avg$QEp < .05), numerals = FALSE)` measures, the true variation in reliability across labs was significant.
+The true reliability was quite variable for some measures.
+For instance, the estimate of the standard deviation of the true reliability of the top measure in the graph (a measure of conscientiousness from @gosling2003very used in the replication of @defruyt2000cloninger) equaled `r apa_num(plot_23_data_alpha_reordered[plot_23_data_alpha_reordered$g == "Albarracín et al.
+(2008), exp 5 math", "tau"][1], digits = 3, gt1 = FALSE)` points of Cronbach’s Alpha.
+
+Thus for around a quarter of measures, the reliability was heterogeneous.
+Although for the remaining measures, we found no significant heterogeneity in reliabilities, we note that power to detect small heterogeneity is often low (@ioannidis2007uncertainty; @olsson2020heterogeneity).
 
@@
 
-Figure \@ref(fig:Plot23AlphaCode) additionally indicates whether or not the measures were part of a successful or failed replication.
-A logistic regression model was used to test whether there was a significant difference in the average calculated reliability coefficient value based on whether or not the associated replication was successful or not based on the meta-significance of the effect.
+We used a logistic regression model to test whether replication success as reflected in a significant mean effect in the meta-analysis conducted across the replicating labs could be predicted by the average calculated reliabilities of the measures.
 
@@
 # well this OR is quite a ridiculous number now..., but then again a step from 0 alpha to 1, is quite a jump too...
-
-```
-
-Contradictory to hypothesis 3, the logistic model indicated that Cronbach's alpha did not significantly relate to replication success in the main logistic regression model (Cronbach's alpha: `r H3_main_full_results_alpha_with_OR`).
-However, it should be noted that the reliability coefficient could be calculated for only a small sample number of measures.
+H3_test_result_main_alpha$full_result$alpha
+
+```
+
+Cronbach's alpha did not significantly predict replication success in the main logistic regression model (`r H3_main_full_results_alpha_with_OR`).
+Results based on the Omega coefficient lead to a similar conclusion (see [Appendix C](AppendixScripts/Appendix_omega_analyses.Rmd).
+However, it should be noted that the reliability coefficient could be calculated for only `r nrow(data_h3_avg)` measures.
 As a result, the estimates of the relation between reliability and replication success obtained using these models each come with large uncertainty.
@@
 Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts the flow of measures in relation to reliability reporting.
-First of all, it shows that almost half of the measures in both replication (n = `r apa_num(table(coded_data_replications$N_items)["1 item measure"])`) and original research (n = `r apa_num(table(coded_data_original_shortened$N_items)["1 item measure"])`) were single item measures.
-When looking at the multiple item measures, the graph illustrates that `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` measures in the replication protocols and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles reported a reliability coefficient.
-The most commonly reported reliability coefficient was Cronbach's alpha, which accounted for `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles.
+First, it shows that almost half of the measures in both replication (n = `r apa_num(table(coded_data_replications$N_items)["1 item measure"])`) and original research (n = `r apa_num(table(coded_data_original_shortened$N_items)["1 item measure"])`) were single-item measures.
+When looking at the multiple item measures, the graph illustrates that `r N_reported_reliabilities_replications` measures in the replication protocols and `r N_reported_reliabilities_original` in the original articles reported a reliability coefficient.
+The most commonly reported reliability coefficient was Cronbach's Alpha, which accounted for `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", "alpha"]))` in the original articles.
 
@@
 
-```{r Hypothesis1Model, include = FALSE}
+```{r Hypothesis1RecycledModel, include = FALSE}
 # first some descriptives of reliability reporting
 # Measurement type per original and replication:
-H1_descriptive_table_1 <- table(data_h1$rep_org, data_h1$N_items)
+reliability_reporting_descriptive_table_1 <- table(data_h1$rep_org, data_h1$N_items)
 
@@
 # (given that measure is a multiple item measure):
-H1_descriptive_table_2 <- table(data_h1$rep_org[data_h1$N_items == "multiple item measure"], data_h1$reliability_type[data_h1$N_items == "multiple item measure"])
-
-# New H1 test
+reliability_reporting_descriptive_table_2 <- table(data_h1$rep_org[data_h1$N_items == "multiple item measure"], data_h1$reliability_type[data_h1$N_items == "multiple item measure"])
+
+# recycled H1 test
 # A chi square test for difference in N reliability reported for multiple 
 # item measures.
-H1_test_result <- chisq.test(data_h1$rep_org[data_h1$N_items == "multiple item measure"], data_h1$reliability_reported[data_h1$N_items == "multiple item measure"])
-
-```
-
-Reliability was more commonly reported in original as compared to replication research ($\chi^{2}$(`r apa_num(H1_test_result$parameter)`) = `r apa_num(H1_test_result$statistic)`, *p* = `r apa_p(H1_test_result$p.value)`).
+reliability_reporting_test_result <- chisq.test(data_h1$rep_org[data_h1$N_items == "multiple item measure"], data_h1$reliability_reported[data_h1$N_items == "multiple item measure"])
+
+```
+
+Reliability was more commonly reported in original (n = `r `N_reported_reliabilities_original`) as compared to replication research (n = `r N_reported_reliabilities_replications_number_style`), $\chi^{2}$(`r apa_num(reliability_reporting_test_result$parameter)`) = `r apa_num(reliability_reporting_test_result$statistic)`, *p* = `r apa_p(reliability_reporting_test_result$p.value)`.
 Validity evidence was similarly reported infrequently.
-The number of original articles that reported validity evidence from a factor analysis was `r sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")`, for replications this number was `r sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")`.
+`r apa_num(sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` original articles reported validity evidence from a factor analysis, while only `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` replications did.
 
@@
 
-The bottom of Figure \@ref(fig:Plot456Code) displays the distributions of the total QMP ratio for both original articles and replication protocols.
-Here we can see that the average QMP ratio in replication protocols is smaller (`r apa_num(Mean_Rat_Rep)`) than in original articles (`r apa_num(Mean_Rat_Org)`).
-The top of Figure \@ref(fig:Plot456Code) shows that original articles and replication protocols had different distributions of QMPs per category.
+The top part of Figure \@ref(fig:Plot456Code) displays the distributions of the total QMP ratio for both original articles and replication protocols, showing that the average QMP ratio in replication protocols was smaller (`r apa_num(Mean_Rat_Rep)`) than in original articles (`r apa_num(Mean_Rat_Org)`).
+The bottom of Figure \@ref(fig:Plot456Code) shows that original articles and replication protocols had different distributions of QMPs per category.
 The number of measures for which modification items were applicable also differed.
@@
 ```{r Plot456Code, warning = FALSE, fig.cap = "QMP ratio counts for each QMP Type and QMP total ratio distribution grouped by whether the QMP ratio was obtained from an original article or a replication protocol.
-The top row shows for each QMP type the proportions of each QMP ratio obtained, darker colours represent proportionally more QMPs, grey means modification did not occur for that measure.
-The bottom graph shows the distributions of total QMP ratios for both replication protocols and original articles, with the line indicating the mean QMP ratio.
-The specific observed values are indicated along the bottom row with dots"}
+The top graph shows the distributions of total QMP ratios for both replication protocols and original articles, with the line indicating the mean QMP ratio.
+The specific observed values are indicated along the bottom row with dots.
+The bottom row shows for each QMP type the proportions of each QMP ratio obtained, darker colors represent proportionally more QMPs, grey means modification did not occur for that measure."}
 
@@
 
-In order to test whether this difference is significant, a beta-regression model was used.
-Beta regression models are similar to other generalized linear regression models.
-Beta-regression is suited to model dependent variables with values in the interval of $(0, 1)$, including ratios.
+We used a beta-regression model to test the difference in QMP ratio between original and replication was significant using the *betareg* R package [@R-betareg_a; @R-betareg_b].
+Beta regression models are similar to other generalized linear regression models, but they are better suited to model dependent variables with values in the interval of $(0, 1)$, including ratios.
 Furthermore, they are robust for heteroskedastic and asymmetrically distributed dependent variables [@cribari2010beta].
-The beta regression model was implemented using the betareg function within the betareg package [@R-betareg_a; @R-betareg_b] with default parameters.
 
@@
 Using a beta-regression model, the total QMP ratio was regressed on a dummy variable indicating whether the coded report was an original article or a replication protocol.
-The results of indicated that this difference was significant (`r betareg_output_to_apa_full(H4_test_results_REV)`).
-This result is in line with hypothesis 4.
+The results supported Hypothesis 4 and indicated that this difference was significant (`r betareg_output_to_apa_full(H4_test_results_REV)`).
 
@@
 H5_test_results_REV_with_OR <- OR_to_apa_full_supplier(H5_test_results_REV$full_result$QMP_REV_ratio, negative_b = TRUE)
-
-```
-
-A logistic regression model was used to test the association between the QMP ratio in replication protocols and replication success.
-In line with hypothesis 5, results showed that a decrease in the ratio of QMPs in replication protocols significantly related to successful replication (`r H5_test_results_REV_with_OR`).
+H5_test_results_REV_with_OR
+
+```
+
+We used logistic regression to test the association between the QMP ratio in replication protocols and replication success.
+In line with Hypothesis 5, results showed that successful replications were associated with fewer QMPs compared to unsuccessful replications (`r H5_test_results_REV_with_OR`).
 
@@
 
-The relation between QMP ratios in the replication protocols and corresponding original articles were investigated using a beta regression model.
-Total QMP ratio in the original article was found to be significantly related to the total QMP ratio in the subsequent replication (`r betareg_output_to_apa_full(H6_test_results_REV)`).
-This result provides evidence in favor of hypothesis 6.
-Figure \@ref(fig:Plot46RevisedDataCode) displays this relationship visually.
-
-```{r Plot46RevisedDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication total QMP ratio’s with linear regression line.
-Each dot in the figure describes the QMP ratio in that graph across both the original article and its replication protocol.
-Note: jitter was applied to these dots in order to show the number of observations at points where multiple dots were present"}
-ggplot(plot_46_data_rev[plot_46_data_rev$QMP_type == "QMP.Ratio" & plot_46_data_rev$QMP_Rep_type == "Rep.QMP.Ratio",], aes(QMP_ratio, QMP_Rep_ratio)) + 
-  geom_point() +
-  geom_jitter(width = 0.01, height = 0.01) +
-  stat_smooth(method="lm") + 
-  theme_minimal() +
-  theme(strip.text.y = element_text(size = 7), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
-  ylab("QMP Ratio (Replication Protocol)") +
-  xlab("QMP Ratio (Original Article)")
-
-```
+Using a beta regression model, we found total QMP ratio in the original article to be significantly related to the total QMP ratio in the subsequent replication (`r betareg_output_to_apa_full(H6_test_results_REV)`).
+This result provides evidence in favor of Hypothesis 6.
 
@@
 
-In this paper, we analyzed the data, protocols, and related original articles from four Many Labs projects to assess reliability and measurement (reporting) practices.
-We additionally looked at how these features might affect credibility, in particular through the relation with replicability.
-Overall, we found that not all measures were sufficiently reliable, nor where measures always equally reliable in each setting in which they were used.
-Regardless, we did not observe that reliability was related to replicability as predicted.
-However, a relation with replicability was observed for QMPs in replication research.
-In turn, we found that  QMPs in the replication were related to QMPs in the original research.
+In this article, we analyzed the data, protocols, and related original articles from four Many Labs replication projects to assess reliability and measurement (reporting) practices.
+We additionally looked at how these features might be related to replication success, as a proxy of the credibility of findings.
+Overall, even though the average reliability was relatively high, we found that not all measures were sufficiently reliable, nor where measures always equally reliable in each setting in which they were used.
+Although, we did not observe reliability to significantly predict replication success, we did observe a negative relation between replication success and presence of QMPs in replication research.
+Finally, we found QMPs in the replication to be positively associated with QMPs in the original studies
 
@@
 
-The measures in our sample varied in their reliability.
 While most measures showed sufficient average reliability for most purposes in psychological research (around .80), about a quarter of the measures had a reliability generally considered insufficient (around .60 or less) [@nunnally1994assessment].
-Furthermore, original research generally showed lower reliability than the average reliability in the replication samples, contrary to our hypothesis that there would be no difference.
-
-One explanation for this discrepancy might be that measurement was more rigid in the Many Labs replications, possibly because the sharing of data would make them more open to scrutiny [@wicherts2011willingness].
-Higher reliability would mean less noise around effect estimates, and in turn make this estimates more consistent.
-However, this relationship is complex and is further complicated by the fact that reliability is not a fixed aspect of a scale, but instead a feature of that scale within a sample [@cho2015cronbach].
-
-Indeed, our results show that reliability of a measure is different across samples, in some cases even showing signs of true variation, or heterogeneity, in reliability.
+Furthermore, the reliability in original research was generally lower than in the replication samples, contrary to our hypothesis that reported reliability estimates would not differ significantly between replications and original articles.
+These differences may be due to features that were specific to the Many Labs projects.
+Large teams of researchers with diverse expertise were involved in the Many labs projects.
+It is possible that the pooling of expertise and use of structured procedures led to more reliable measurement compared to the original research.
+
+Our results additionally show that the reliability of a measure differs across samples, in some cases even showing signs of true variation, or heterogeneity, in reliability.
 Reliability heterogeneity was particularly common for measures with a lower average reliability.
-Meanwhile, some measures with higher average reliability showed indication of nearly zero heterogeneity.
-It is however difficult to draw clear conclusions since the number of investigated measures was small.
-Some measures were also used in only a small number of independent samples.
-This is particularly relevant here, since the tests for heterogeneity are known to be sensitive to the number of studies included [@li2015DilemmaHeterogeneityTests].
-Regardless, our results do demonstrate an often overlooked aspect about of measurement reliability: reliability is a sample-specific not a measurement-specific feature.
+However, the number of investigated measures was small, and some measures were only used in a small number of independent samples.
+This is particularly relevant, since the Q-test to test heterogeneity is sensitive to the number of studies included in each test [@li2015DilemmaHeterogeneityTests].
+Furthermore, most measures did not show evidence of significant reliability heterogeneity, a similar lack of widespread heterogeneity was also observed for effect sizes in replications [@klein2018many; @olsson2020heterogeneity].
+Regardless, our results do demonstrate an often-overlooked aspect of reliability: reliability is a sample-specific, not a measurement-specific feature.
 
@@
 @stanley2014expectations illustrated that measurement error, when not attenuated for, can impact replication assessments.
-We observed no relation between reliability and replicability, even though our chosen replication index did not attenuate for measurement error.
-This result not only runs counter to the findings of @stanley2014expectations and hypothesis 3 of this study, but also the theoretical relationship between reliability and variability in effect size estimates.
-
-However, the relationship between reliability and replicability is complex.
-For example, reliability and replicability are theoretically only related when the true effect is not null.
+However, we observed no relation between reliability and replicability, even though our chosen replication index did not attenuate for measurement error.
+This result is surprising not only because it runs counter to the findings of @stanley2014expectations and Hypothesis 3.
+It also runs counter to the fact that according to statistical theory, the increased noise in the data as the result of lower reliability decreases the effect size estimates based on those data.
+
+However, the relationship between reliability and replicability is complex [@willson1980research; @lebreton2014corrections; @oswald2015Imperfect; @zhang2024Metaanalysis].
+For example, reliability and replicability are only related when the true effect is not null.
 In our sample more than half of the effects were not replicated, indicating that many of these effects may be null effects.
-For these effects no relation would be expected.
-Furthermore, while reliability diminishes effects it can also reduce the observed true variance in the effects [@olsson-collentine2023UnreliableHeterogeneityHow].
+For these effects no relation is expected.
+Furthermore, while lower reliability decreases effect sizes it can also reduce the observed true variance in the effects [@olsson-collentine2023UnreliableHeterogeneityHow].
 As a result, effect estimates from various studies will appear more similar than they truly are, seemingly replicating the original.
-These and other relations become even more complex when reliability itself is heterogeneous as was observed with several measures in our sample.
-
-With this in mind it is perhaps not surprising that we did not find an evidence for a relation between reliability and replicability in our sample.
-The was the number of measures for which reliability could be calculated small (n = `r apa_num(sum(!is.na(data_h3_avg$alpha)), numerals = FALSE)`).
-Furthermore, if a number of these effects are actually null effects, then there are even less measures for which the relation is expected.
-Combined with the complexity of the relationship between reliability and replicability, our non-significant finding is likely the result of a lack of power to detect this specific relation between reliability and replicability.
-
-The small number of relevant measures, and the small number of reported reliabilities is not only an issue for the power of our tests.
-It indicates that there is a lack of reliability evidence in both original and replication psychology literature.
+These and other relations are further complicated by the fact that reliability is not a fixed aspect of a scale, but a feature of that scale within a sample [e.g., @vacha1999practices; @cho2015cronbach].
+
+The complexity of the relationship combined with the fact that we could only calculate reliability for a small number of measures meant we had low statistical power to detect the overall relation between reliability and replicability, which provides a likely explanation for our non-significant finding.
+
+The small number of relevant measures and reported reliabilities also indicates an important issue: we observed a lack of reliability evidence in both original and replication psychological research.
 
@@
 
-The reliability of measures was rarely reported in both original and replication research, which is in line with similar investigations in the literature [@shaw2020measurement; @flake2017construct; @flake2022construct].
-Reported reliabilities were so few, that the planned test for hypothesis 1 had too low power to be informative.
-In particular, we found that replication research reported reliability coefficients less than original research, which is in line with @flake2022construct.
+The reliability of measures was rarely reported in both original and replication research, which is in line with earlier investigations in the literature [@shaw2020measurement; @flake2017construct; @flake2022construct].
+Reported reliabilities were so few, that the preregistered test for Hypothesis 1 was no longer informative.
+We found that replication research reported reliability coefficients less often than original research, which is in line with @flake2022construct.
 This pattern continued for validity evidence reporting.
-Of the `r nrow(coded_data_replications)` measures, validity evidence in the form of factor analysis or similar analyses was reported for `r sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")` measures in original articles, and `r sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")` measures in replication protocols.
-
-The underreporting of reliability and validity evidence has been addressed in literature for a long time [@vacha1999practices; @green2011recent].
+Of the `r nrow(coded_data_replications)` measures, validity evidence in the form of factor analysis or similar analyses was reported for `r apa_num(sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` measures in original articles, and `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` measures in replication protocols.
+
+The underreporting of reliability and validity evidence has long been discussed [@willson1980research;@vacha1999practices; @green2011recent].
 Our study illustrates three potential reasons for why this problem has persisted.
-Firstly, the studies in our sample commonly made use of single item measures, an observation that was also made by @shaw2020measurement.
-Calculating reliability for single-item measures is not as straightforward as for multiple item measures.
+Firstly, the studies in our sample commonly used single-item measures, an observation that was also made by @shaw2020measurement.
+Calculating reliability for single-item measures is not as straightforward and less common as for multiple item measures [@wanous1996estimating].
 
 Secondly, our results indicate that there may be bias in reporting reliability coefficients.
-Reliabilities were reported in original research for those measures that obtained large calculated reliabilities in the replication samples.
-If we take the calculated reliabilities in the replication sample as an accurate representation of the distribution of the true reliability for that measure, then this would imply that reliabilities are more often reported when the measure is truly reliable, and less when it is unreliable.
+Reliabilities were reported in original research for those measures that obtained higher calculated reliabilities in the replication samples.
+If we take the calculated reliabilities in the replication sample as an accurate representation of the distribution of the true reliability for that measure, then this would imply that reliabilities are more often reported when the measure is truly reliable, and less when it is unreliable; a common issue of selective reporting.
 Researchers may be reluctant to report reliability for unreliable measures, thus lowering the prevalence of reported reliabilities.
-This bias may cause researchers to be overly optimistic with regard to the reliability of measures in their field, similarly to how bias in publication causes issues for establishing estimates of true effect sizes in meta-analyses [@sutton2000empirical].
-
-Thirdly, when the replication protocols were written, no measurement based on these protocols had taken place.
-As a result, the data the replicating researchers could have calculated reliability and validity from was not yet available.
+In turn, researchers may become overly optimistic about the reliability of measures in their field, similarly to how bias in publication causes issues for establishing estimates of true effect sizes in meta-analyses [@sutton2000empirical].
+
+Thirdly, the replication protocols were written before data were collected, which means no measurement based on these protocols had taken place yet.
+As a result, there was no data available yet from which the replicating researchers could have calculated reliability and validity.
 This would explain why there was little reliability and validity evidence reported in replication protocols.
-However, if reliability and validity evidence are not being consulted before replicating research, it means that unvalidated measures are used.
-
-Beyond reporting of reliability and validity evidence, we also investigated other measurement reporting practices recorded using QMPs.
-We found that QMPs were less common in replication protocols compared to original articles.
-This is in line with hypothesis 4, but runs counter to the findings of @flake2022construct.
+It may still represent a problem however, because original articles similarly rarely reported reliability and validity evidence.
+This implies that the replications commonly used measures that were not yet validated.
+
+On the other hand, we found that more general issues in the transparency of measurement reporting practices, as assessed by QMPs, were less common in replication protocols compared to original articles.
+This is in line with Hypothesis 4, but runs counter to the findings of @flake2022construct, who found less construct validity evidence in the replications from the RPP [@osc2015estimating] than in original articles.
 We believe this discrepancy was the result of our sample being the Many Labs projects.
 These projects made use of structured replication protocols to document the way measurement was going to be conducted.
-One example of how this may have reduced QMPS is the inclusion of a section in several protocols for listing the deviations from the original measurement.
+For example, several Many Labs replication protocols contained a section specifically listing the deviations from the original measurement.
 
 ### Incomplete measurement reporting hinders replicability
+
 Existing literature has already warned about the potential detrimental effects of QMPs on replications [@shaw2020measurement; @flake2022construct].
@@
 
-In line with hypothesis 5 and 6, we found indication of such a spillover effect in our sample.
+In line with Hypotheses 5 & 6, we found an indication of such a spillover effect in our sample.
 The total QMPs of an original study and the total QMPs in the protocol of the replication for the same study were positively associated.
@@
 However, it is worth noting that these associations were only found for QMPs coded with the revised coding protocol.
-Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see Appendix D[insert Link] for results based on the initial protocol).
+Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see [Appendix D](AppendixScripts/Appendix_initial_QMP_analyses.Rmd) for results based on the initial protocol).
 
 ## Limitations & Future Research
+
 Our study had several limitations.
-First of all, we encountered numerous challenges in operationalizing QMPs.
-This research used a novel way of operationalizing QMPs as a variable to assess measurement practices and their impact on replicability.
-However, this also means that it remains uncertain whether or not .
-Already we determined it necessary to revise our coding protocol to be more lenient with regard to more context dependent QMPs compared to the initial protocol.
-This revision was not trivial as it impacts the interpretation of our results.
-
-This relates to one of the most prominent challenges in assessing QMPs.
-It is difficult to determine when a practice is questionable, and what impact the context has on this decision.
+We encountered numerous challenges in operationalizing QMPs.
+Whereas previous research has focused on descriptives of specific QMPs detrimental to construct validity [@flake2022construct; @shaw2020measurement], we operationalized all coded QMPs together as a variable to assess measurement practices and evaluate their impact on replicability.
+However, this also means that it remains uncertain if our operationalization accurately captured the concept.
+We already deemed it necessary to revise our coding protocol to be more lenient regarding more context dependent QMPs compared to the initial protocol.
+This revision was not trivial, as it altered the interpretation of our results.
+Regardless, it reflects the challenges we encountered in operationalizing QMP in this novel way.
+Future research is needed to identify which way is the most rigorous and fair.
+
+One challenge in operationalizing was the difficulty in determining when a practice is questionable, and the impact of the context on this decision.
 For example, in our sample the constructs that were measured were less commonly defined in replication protocols than in original articles.
 However, one may argue that it is not the responsibility of the replication to define the construct, as it is meant to be equivalent to the construct assessed in the original article.
-In that case, not defining the construct may not constitute a questionable practice at all.
+In that case, not defining the construct may not be a questionable practice at all.
 
@@
 We chose to make use of ratios to cancel out the effects of non-applicable items as much as possible.
-However, this has the consequence that that both a measure for which all relevant measurement-related information was reported, and a measure for which no item was applicable would have a QMP ratio of zero.
-However, we would not consider the latter case to indicate the same level of completeness as the first.
-A little more than one third of all responses was not applicable.
-This may have been enough to substantially obscure the relation between QMP ratio and measurement reporting completeness.
-
-The relation is further obscured because it is not clear how great a ratio of QMPs is too much.
+However, this has the consequence that both a measure for which all relevant measurement-related information was reported, and a measure for which no item was applicable would have a QMP ratio of zero.
+Yet, we would not consider the latter case to indicate the same level of completeness as the first.
+A little more than one third of all responses were not applicable.
+As a result, the relation between QMP ratios and measurement reporting completeness may have been obscured to some extent.
+
+The relation is further complicated, as it is not clear how great a ratio of QMPs represents clear violations of good research practices.
 One might argue that any QMP is a sign of questionable research and thus that any ratio greater than zero is cause for alarm.
 However, this may be too harsh.
-As mentioned, not all violations may have detrimental consequences or be relevant in all contexts.
+As mentioned before, not all violations may have detrimental consequences or be relevant in all contexts.
 Future research will be needed to determine the best way(s) to operationalize QMP ratios.
-???APA-MANUAL FOR EXAMPLES/INSPIRATION FOR FUTURE RESEARCH/ AERA et al., 2014???
-
-The second limitation is that our tests on reliability were largely underpowered.
+Researchers can take inspiration from this study and earlier studies by @shaw2020measurement and @flake2022construct, as well as the criteria on measurement reporting as set out in the @aera2014standards.
+
+A second limitation is that our tests on reliability were underpowered.
 This was the result of the small number of reported reliability scores, and multiple item scales with available data.
-However, this limitation also illustrates two key findings of this study.
-One being that the reliability of measures were rarely reported in both original articles and replication protocols.
-
-The other finding is that around half of the measures used in our sample were single item-measures.
-The use of single item measures comes with psychometric risks [@diamantopoulos2012guidelines; @nunnally1978overview], and are more limited with respect to the type of reliability and validity evidence that can be determined [@shaw2020measurement].
-It could even be argued that the use of single-item measures constitutes a QMP in many instances.
-
-As a third limitation, it is important to consider whether or not replication protocols and research articles can be fairly compared in terms of QMPs.
-A study's description within a replication protocol is generally shorter than an article.
-The description within the protocol may therefore lack the space needed to report on the measurement in full detail.
-There are two main reasons why we believe protocols and articles remain comparable.
-Firstly, articles are often also restricted in the amount of space they have available to devote to measurement [@gardiner2019editorial].
-Secondly, in the revised protocol some information, such as example items, could also be reported only in supplementary materials and not be counted as a QMP.
-Still, future research may wish to further include supplementary materials as part of the primary data to get a more complete picture on the state of measurement reporting in both articles and protocols.
-
-The fourth limitation is that we made use of only one way to define replication success.
-Replication success can be estimated and framed in multiple ways, including methods that do not make use of significance testing.
-Multiple ways to define replication were used in the RPP [@osc2015estimating].
-The relationship that reliability has with different forms of replication success may differ.
-
-Finally it is worth noting that we did not make use of a causal design in our study.
-Therefore, we cannot attach definitive causal directions to the relations observed in this study.
-However, it would be useful for understanding the potential negative impact of reliability and QMPs on replicability., It may be possible to randomly assign original studies in a project like the Many Labs to either needing to report all the relevant measurement details as noted down by for example @flake2020measurement and @???APAMANUALREFERENCE???, or get no screening.
-The same would go for requiring the use of validated measures, or not.
-Tremendous coordination and funding would be required to integrate original studies into a large scale replication project from the start.
-While such efforts are not unprecedented [@protzko2020high], alternative methods also exist to assess causal relations on observational data.
-For example, @rohrer2018thinking has suggested researchers make use of Directed Acyclic Graphs to investigate causality in (non-)experimental settings by systematically taking into account confounding influences on the effect.
-Such an approach may also help in untangling the complex relationship between reliability and replicability.
+However, this limitation also illustrates two key findings.
+One finding is that reliability was rarely reported for measures in both original articles and replication protocols.
+
+The other finding is that around half of the measures in our sample were single item-measures.
+The use of single item measures comes with psychometric risks [@diamantopoulos2012guidelines; @nunnally1978overview], and is more limited with respect to the type of reliability and validity evidence that can be determined [@sarstedt2016selecting; @shaw2020measurement].
+Because of these issues, it could even be argued that the use of single-item measures is a QMP in certain contexts.
+
+As a third limitation, it is important to consider whether replication protocols and research articles can be fairly compared in terms of QMPs.
+The space for describing methodology within a replication protocol is generally shorter than an article.
+Furthermore, for direct replications the methodology may be seen as largely equivalent to the original article, thus measurement descriptions in the replication protocol may be considered superfluous.
+There are three main reasons why we believe protocols and articles remain comparable.
+Firstly, the majority of the measurements in our replication sample were modified in some way, it is therefore important that replication protocols still report on their measurement as it may deviate from the original.
+Secondly, articles are often also restricted in the amount of space they have available to devote to measurement [@gardiner2019editorial].
+Thirdly, supplementary materials were also included as a valid information source.
+Still, future research may wish to analyze supplementary materials in greater detail, to investigate to what extent these materials cover measurement details in both replication protocols and original articles.
+
+A fourth limitation is that we of only used one definition of replication success.
+Replication success can be estimated and framed in multiple ways [for an example in replication research see, @osc2015estimating], including methods that do not make use of significance testing, or that attenuate for (measurement) error.
+The relationship between reliability and other indices of replication success may differ.
+
+Finally, we note that we used an observational design which means that we cannot attach definitive causal directions to the relations observed in this study.
+To directly assess if there is a negative impact of reliability and QMPs on replicability, we would need experimental research.
+Future research could for example randomly assign original studies in a large scale replication project to either needing to report all relevant measurement information as noted down in Table 1 in @flake2020measurement, while other studies receive no such reporting requirements.
+Similarly, the requirement to use validated measures based on the criteria set out in section 1, 2, and 3 in the @aera2014standards standards, or lack thereof could be randomly assigned conditions.
+Although such experimental designs would be the most direct way to assess causality, it would take tremendous coordination and funding to integrate original studies into a large scale replication project from the start.
+While such efforts are not unprecedented [@protzko2020high], alternative methods also exist to assess causal relations on observational data, at least to some extent.
+@rohrer2018thinking has suggested researchers make use of Directed Acyclic Graphs to investigate causality in (non-)experimental settings by systematically accounting for confounding influences on an effect.
 
 ## Recommendations
-Taking all the findings together, the following assessments will be relevant to consider for future research.
+
+Taking all the findings together, the following statements will be relevant to consider for future research.
 Firstly, reliable and valid measures are a prerequisite for credible findings.
 The observation that many measures are not reported with such evidence is worrying, because it obscures the credibility of findings, and hampers scientific progress.
-Therefore, we suggest that for multiple item scales establishing the validity becomes a community standard for credible research.
-For reliability coefficients we go even further to state that these should by default always be reported for any multiple item scale.
-Researchers should only be exempt from this default, if they provide motivated reasoning for why they should be exempt.
-
-For direct replications to represent an as good as possible test of the credibility of a finding, it is important that the procedure and measurement of the original study can be mimicked.
-Therefore, researchers should make fully report on their measurement details, as specified for example in Table 1 in @flake2020measurement ???APA MANUAL???.
-Any details that could not fit in the article can then be shared with potential replicators via a public repository, such as the Open Science Framework [OSF; @soderberg2018using] or Zenodo [@zenodo2024open].
+Therefore, we join earlier recommendations [@hogan2004empirical; @barry2014validity; @flake2020measurement; @flake2022construct] that establishing validity evidence for multiple item scales should become a community standard for credible research.
+Furthermore, reliability coefficient estimates for multiple item scales should by default always be reported, since these estimates can easily be obtained with most statistical software, and provide important information on a measure’s performance.
+Only researchers that can provide reasoning to the contrary for their research should be exempt from this default.
+
+Secondly, researchers should report their procedure and measurement in detail, as specified in for example Table 1 in @flake2020measurement, or section 3.6 in @apa2020publication on measures and measurement.
+This is important so that it can be mimicked in replications if needed.
+The remaining information that could not fit in the article can be made available on a public repository, such as the Open Science Framework (OSF; @soderberg2018using) or Zenodo [@zenodo2024open].
 
 Furthermore, we argue that researchers seeking to replicate a study should first evaluate the measurement of that study.
-Not only is it crucial for an informative replication that the measurement is reliable or valid.
-The original study should also report the measurement details necessary to reconstruct the original measurement.
-Otherwise it may be futile to attempt a direct replication.
-In that case we suggest that researchers instead use their resources to conduct a replication of a study with reliable, valid and well-documented measurement.
-When replicating another study is not an option, we advise the replicating researcher to first attempt a conceptual replication using reliable and valid measurement.
+It is crucial for an informative replication that the measurement is reliable or valid.
+Otherwise it may be futile to attempt a direct replication [see also @nuijten2022assessing].
+If the measurement is insufficiently reliable or valid, we suggest that researchers instead use their resources to conduct a replication of a study with reliable, valid and well-documented measurement.
+When replicating another study is not an option, we advise the replicating researcher to first attempt a conceptual replication using reliable and valid measurement, or use both the original and their own preferred measure [as in @stoevenbelt2018rrr].
 Afterwards, a direct replication can be performed based on the conceptual replication to further assess the effect’s credibility.
@@
 # Conclusion
-Through our investigations into the reliability, validity, and reporting of measurement in the Many Labs replications and associated original studies, we found that reliability and validity evidence was reported infrequently.
+
+Through our investigations into the reliability, and reporting of measurement in the Many Labs replications and associated original studies, we found that reliability and validity evidence was reported infrequently.
 Furthermore, QMPs that obscured important information needed to evaluate and reconstruct the measurement were common, especially in original research.
 QMPs were in turn related to the replicability of a finding.
-Results with regard reliability of the measures were less clear due to low sample size.
-However, for a number of measures reliability showed signs of significant variation between studies.
-Combined these findings illustrate the need for more concrete standards in measurement reporting, and that before attempting a replication of a study, researchers should consider the validity and reporting completeness of the measurement.
+Results were less clear for reliability differences between original and replication, due to lack of power.
+However, around a quarter of measures showed signs of significant variation in reliability across labs.
+Combined these findings illustrate the need for more concrete standards in measurement reporting, and that researchers should consider the validity and reporting completeness of a study's measurement before attempting to replicate it.
 

### 2024-07-01 SupplementaryMaterials/data_retrieval_information.Rmd
Incorporated feedback on the entire text from co-authors. Removed two figures, checked grammar.

--- 2024-03-18 SupplementaryMaterials/reproducible_data_retrieval_information.Rmd
@@
-# Reproducible data retrieval information
+# Data retrieval information
 
-This supplementary material file contains detailed information on the specific path files and names of the used registered replication protocols and datasets.
+This supplementary material file contains information on the search strategy that was used to retrieve the three main data sources used in this study: the replication protocols, replication datasets, and the original articles.
 
-## Registered Replication Protocols
+Furthermore, for the replications protocols and replication datasets, we specify here the exact OSF file paths and file names of the specific protocols and datasets that were retrieved.
+
+## Replication Protocols
+
+### Search
+
+The OSF page for each Many Labs project was combed through, in order to identify the documents that contained information on the measurement practice and reported reliability.
+For Many Labs 1 2, & 3 a single replication protocol for all studies could be identified, while for Many Labs 5 protocols were available for each set of replications separately.
+For Many Labs 5 for each replication set the relevant OSF page was searched through for a protocol file.
+
+If available, a version of the protocol labelled as revised, post-review, peer-review, or endorsed was selected.
+Otherwise, the latest uploaded relevant protocol was selected.
+Protocols labelled as data collection, analysis protocol or anything similar were excluded.
+
+The steps taken to access the replication protocol data from Many Labs 5 were not preregistered, and only became clear upon further investigation of the accessible information.
+
+### OSF pages
 
 Below are the relevant OSF pages, and exact path and file names of the relevant pre-registered replication protocols that were extracted, to be then coded on measurement reporting information in the Many Labs replications projects.
-
-???look up and add osf pages + project path + file names, and format like:???
 
@@
 -	Data File: ML5_fulldataset_with_suspicion.csv
+
+## Original Articles
+The original articles were identified using the citations for these articles in each replication protocol.
+They were then retrieved and extracted through searches on Web of Science, Google Scholar, and PsycINFO (in that order).
+All articles except Hyman and Sheatsley (1950) could be retrieved through this method.
+Howeever, after contacting the first author of Klein et al.
+(2014) a suitable version of the article was obtained.
+Thus in the end all original articles could be retrieved.
+
+# Plot of data information
+
+This can only be run after data is loaded with the main manuscript file.
+
+```{r DataStructurePlotCode, warning = FALSE, fig.cap = "This figure displays the sample size for the included original articles and total sample size for multiple replications.
+The color of each point indicates whether it represents an original article or a replication.
+Each point's shape relates to whether the hypothesis was supported or not, while the size indicates the number of measures used within that article or replication.
+The figure is log10-scaled, each light grey vertical line represents a step of 500 in sample size.
+Two original articles are not represented in this figure due to them containing no reported sample size.", fig.height = 4, fig.width = 12}
+
+# plot of the multilevel data structure
+ggplot(plot_data_structure_data, aes(x = N, y = factor(many_labs_version, levels = c("5", "3", "2", "1")), 
+                                colour = rep_org, shape = hypothesis_support, size = measure_count)) +
+  geom_point(alpha = .33) +
+
+  scale_x_continuous(trans = "log10", breaks = c(10, 100, 1000, 10000), 
+                     labels = c(10, 100, 1000, 10000), limits = c(10, 10000),  
+                     minor_breaks = seq(500, 10000, 500)) +
+
+  theme_minimal() +
+  theme(plot.margin = unit(c(1, 6.5, 1, 1), "lines"), 
+        panel.grid.major.x = element_line(color = "grey",
+                                          size = 0.5,
+                                          linetype = 1),
+        text = element_text(size = 15)) +
+
+  guides(color = guide_legend(nrow = 1, byrow = TRUE)) +
+  guides(shape = guide_legend(nrow = 2, byrow = TRUE)) +
+  guides(size = guide_legend(nrow = 2, byrow = TRUE)) +
+
+  labs(x = "N", y = "Many Labs Version", color = "Obtained from:", 
+       size = "Nr. measures", shape = "Replicated")
+
+```

### 2024-07-01 Scripts/source_script.R

@@ -773,10 +773,17 @@ OR_to_apa_full_supplier <- function(apa_print_result, negative_b = FALSE){
   OR <- round(exp(as.numeric(substr(apa_print_result, start = 6, 
                                     stop = 9 + negative_b))), 3) 
   
+  ORCILO <- round(exp(as.numeric(substr(apa_print_result, start = 23 + negative_b, 
+                                        stop = 26 + negative_b*2))), 3) 
+  
+  ORCIHI <- round(exp(as.numeric(substr(apa_print_result, start = 29 + negative_b * 2, 
+                                        stop = 33 + negative_b * 2))), 3)
+  
   result_string_with_OR <- paste0(substr(apa_print_result, start = 0, 
-                                  stop = 12 + negative_b), "$OR = ", OR, "$, ", 
+                                  stop = 12 + negative_b), "$OR = ", OR, 
+                                  "$, 95\\% $[", ORCILO, ", ", ORCIHI,
                                   substr(apa_print_result, 
-                                         start = 13 + negative_b, stop = 99))
+                                         start = 34 + negative_b * 2, stop = 99))
   
   return(result_string_with_OR)
 }

### 2024-07-09 Data/Data_package_description.Rmd
made inline code more consistent, removed the data structure plot data, clarified source script functions, added Orcid IDs, and added the basic structure for funding information.

@@
 
-### plot_data_structure_data.csv
-
-*Explanation*: Contain all of the data from the data_h4.csv filtered based on having a unique title (that was not due to a typo or copying error) to extract the individual studies and replication rather than individual measures into a dataset.
-Furthermore, the total count of measures for each study or replication was added to this dataset.
-
 ### plot_23_data_alpha.csv

### 2024-07-09 Scripts/Manuscript/manuscript.Rmd
made inline code more consistent, removed the data structure plot data, clarified source script functions, added Orcid IDs, and added the basic structure for funding information.

@@
     role:
+      - "Conceptualization"
       - "Supervision"
@@
 Pilot data were omitted from the analyses entirely.
-These criteria resulted in suitable item score data from `r apa_num(length(unique(data_h3_multiple$g)))` replication sets spread across on average approximately `r apa_num(mean(table(data_h3_multiple$g)), digits = 0)` lab locations for the analyses of Hypotheses 2 & 3.
+These criteria resulted in suitable item score data from `r apa_num(nrow(data_h3_avg))` replication sets spread across on average approximately `r apa_num(mean(table(data_h3_multiple$g)), digits = 0)` lab locations for the analyses of Hypotheses 2 & 3.
 
@@
 ## graphs
-# plot for data visualization overview
-plot_data_structure_data <- data_prep_data_structure_plot(data_h4)
 # plot accompanying the results for Hypotheses 4, 5, & 6.
@@
     deparse(substitute(data_h3_avg))), ".yml"))
-
-open_data(data = plot_data_structure_data, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(plot_data_structure_data))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(plot_data_structure_data))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(plot_data_structure_data))), ".yml"))
 
@@
 Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts the flow of measures in relation to reliability reporting.
-First, it shows that almost half of the measures in both replication (n = `r apa_num(table(coded_data_replications$N_items)["1 item measure"])`) and original research (n = `r apa_num(table(coded_data_original_shortened$N_items)["1 item measure"])`) were single-item measures.
+First, it shows that almost half of the measures in both replication (n = `r apa_num(sum(coded_data_replications$N_items == "1 item measure"))`) and original research (n = `r apa_num(sum(coded_data_original_shortened$N_items == "1 item measure"))`) were single-item measures.
 When looking at the multiple item measures, the graph illustrates that `r N_reported_reliabilities_replications` measures in the replication protocols and `r N_reported_reliabilities_original` in the original articles reported a reliability coefficient.
-The most commonly reported reliability coefficient was Cronbach's Alpha, which accounted for `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", "alpha"]))` in the original articles.
+The most commonly reported reliability coefficient was Cronbach's Alpha, which accounted for `r apa_num(sum(coded_data_replications$reliability_type == "alpha"), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(coded_data_original_shortened$reliability_type == "alpha"))` in the original articles.
 
@@
 
+## ORCID iDs
+Cas Goos https://orcid.org/0009-0005-3792-4148
+Marjan Bakker https://orcid.org/0000-0001-9024-337X
+Jelte M. Wicherts https://orcid.org/0000-0003-2415-2933
+Michèle B. Nuijten https://orcid.org/0000-0002-1468-8585
+
+## Funding
+The preparation of this article was supported by the veni grant ???
+awarded to Michèle Nuijten, and the vici grant ???
+awarded to Jelte M.
+Wicherts from the Netherlands Organization for Scientific Research (NWO).
+
 \newpage

### 2024-07-09 Scripts/source_script.R

@@ -1,5 +1,6 @@
 # source_script
 
+
 # Data Cleaning Functions ------------------------------------------------------
 ### renaming the columns and rows to accommodate the joining of the three 
 ### datasets.
@@ -102,7 +103,8 @@ restructuring <- function(Data){
 
 ### Recoding Dataset Content for Analysis
 recoding <- function(Data){
-  # changing the variable types for each column
+  # changing the variable types for each column to better represent their 
+  # intended variable type
   class(Data$many_labs_version) <- "numeric"
   Data$rep_org <- droplevels(as.factor(Data$rep_org))
   Data$multi <- droplevels(as.factor(Data$multi))
@@ -218,6 +220,7 @@ calculating <- function(Data){
   return(Data)
 }
 
+
 # QMP Related Functions --------------------------------------------------------
 ### Hypothesis 4 
 # data load and prep function
@@ -234,13 +237,15 @@ data_prep_H4 <- function(Data_Original, Data_Replications){
   return(Data_H4)
 }
 
+
 # modelling and results returning function
 Model_H4 <- function(Data){
   return_list <- list(first = 0, revised = 0)
-  # running the models one with none revised QMP ratio's and one with
+  # running the model with initial QMP ratio's
   Model_H4 <- betareg(QMP_ratio ~ rep_org, data = Data)
   return_list[[1]] <- summary(Model_H4)$coefficients
   
+  # running the model with revised QMP ratio's
   Model_H4_REV <- betareg(QMP_REV_ratio ~ rep_org, data = Data)
   return_list[[2]] <- summary(Model_H4_REV)$coefficients
   
@@ -269,18 +274,21 @@ data_prep_H5 <- function(Data_Replications){
   return(Data_H5)
 }
 
+
 # modelling and results returning function
 Model_H5 <- function(Data){
   return_list <- list(first = 0, revised = 0)
-  # running the models one with none revised QMP ratio's and one with
+  # running the model with initial QMP ratio's
   Model_H5 <- betareg(QMP_ratio ~ hypothesis_support, data = Data)
   return_list[[1]] <- summary(Model_H5)$coefficients
   
+  # running the model with revised QMP ratio's
   Model_H5_REV <- betareg(QMP_REV_ratio ~ hypothesis_support, data = Data)
[…]

### 2024-07-09 Scripts/Manuscript/manuscript.Rmd
altered the reliability reporting diagram.

@@
 ```{r ReliabilityReportingFlowDiagram, fig.cap = "Reliability reporting flow diagram.
-Figure shows the number of measures as reported in both the replication protocols and original article, which meet the criterion in the box within the diagram and those criteria before it."}
+Figure shows the number of measures as reported in both the replication protocols and original article, which meet the criterion in the box within the diagram and those criteria before it.", out.height = "60%"}
 knitr::include_graphics(path = "../../SupplementaryMaterials/reliability_reporting_flow_diagram.png")

### 2024-07-17 Scripts/Manuscript/manuscript.Rmd
Implemented writing feedback, fixed betareg to apa full CI code, and moved the appendix files to the supplementary materials.

@@
     email         : "c.goos@tilburguniversity.edu"
-    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
-      - "Conceptualization"
-      - "Data curation"
-      - "Formal Analysis"
-      - "Investigation"
-      - "Methodology"
-      - "Project Administration"
-      - "Software"
-      - "Visualization"
-      - "Writing - Original Draft Preparation"
-      - "Writing - Review & Editing"
+
   - name          : "Bakker, M."
     affiliation   : "1"
-    role:
-      - "Conceptualization"
-      - "Supervision"
-      - "Writing - Review & Editing"
+
   - name          : "Wicherts, J.M."
     affiliation   : "1"
-    role:
-      - "Conceptualization"
-      - "Supervision"
-      - "Writing - Review & Editing"
+
   - name          : "Nuijten, M.B."
     affiliation   : "1"
-    role:
-      - "Conceptualization"
-      - "Project Administration"
-      - "Supervision"
-      - "Validation"
-      - "Writing - Review & Editing"
 
@@
 
+  The authors made the following contributions.
+CG: Conceptualization, Data curation, Formal Analysis, Investigation, Methodology, Project Administration, Software, Visualization, Writing - Original Draft Preparation, Writing - Review & Editing; MB: Conceptualization, Supervision, Writing - Review & Editing; JW: Conceptualization, Supervision, Writing - Review & Editing; MN: Conceptualization, Project Administration, Supervision, Validation, Writing - Review & Editing.
+
 abstract: |
-  The credibility of psychological science and the ability to replicate earlier findings require good measurement.
-   Here, we assessed the reliability and measurement reporting of 77 measures within 56 Many Labs replications and related original psychological studies. 
-   We investigated their associations with replicability.
-   The results indicated that not all measures in the original and replication studies were sufficiently reliable across contexts. 
-   Additionally, evidence on reliability and validity was rarely reported. 
-   Finally, incompleteness in measurement reporting in replication studies was associated with lower replicability of the findings tested with that measure. 
-   These findings indicate a worrying lack of reported validating evidence for measurement in the literature, and its harm to credibility.
-   We offer suggestions on improving measurement validation and reporting practices, and argue that researchers should evaluate the reported measurement information when deciding what studies to replicate.
-
-keywords          : "reliability, validity, measurement, reporting, replicability, credibility"
-wordcount         : "135"
+  Recent studies have shown that challenges in measurement practices in original and replication research may have contributed to the “replication crisis” in psychological science. 
+  However, the exact nature and extent of the association between measurement and replicability is not yet clear. 
+  We investigated the reliability and measurement reporting of 77 measures within 56 Many Labs replications [@klein2014investigating; @ebersole2016many; @klein2018many; @ebersole2020many] and related original psychological studies, and whether these were associated with replicability.
+  Results from logistic regression models indicated that questionable practices in measurement reporting in replication studies (b = -5.60, OR = 0.004, 95% [0,0.156]), but not the reliability of the measurement (b = 8.21, OR = 3677.542, 95% [1.271,1727601729.241]), was associated with lower replicability of the findings tested with that measure.
+<!-- the code for these two results is: ???; these lines will only work after code chunks 1, 2, 12, & 19 have been ran.
+-->
+  Furthermore, not all measures in the original and replication studies were sufficiently reliable across contexts. 
+  Additionally, we found that evidence on reliability and validity was rarely reported. 
+  These findings corroborate existing research that shows that validity evidence is rarely reported, and that these reporting practices may have negative consequences for the informativeness of replications.
+  We offer suggestions on improving measurement validation and reporting practices. 
+  Finally, we argue that researchers should evaluate the reported measurement information when deciding what studies to replicate.
+
+keywords          : "reliability, validity, measurement, reporting, replicability, credibility, psychology"
+wordcount         : "203"
 
@@
 Unfortunately, psychology seems to face several threats to the credibility of its findings.
-In this article, we investigate how the credibility of psychological findings may be affected by problems in psychological measurement, and in turn, how those problems may affect subsequent replications.
+In this article, we investigate how the credibility of psychological findings may be related to problems in psychological measurement, and in turn, how those problems may affect subsequent replications.
 
@@
 A prerequisite for a credible finding is that it is replicable [@vazire2022CredibilityReplicabilityImproving].
-This means that the observed effect should be comparable across the original study and subsequent replications if the differences between them are believed to be of little relevance to the effect [@nosek2022replicability].
+This means that the observed effect should be comparable across the original study and subsequent replications in new samples if the differences between them are believed to be of little relevance to the effect [@nosek2022replicability].
 
 But replications often fail.
-In 2015, the Replication Project: Psychology (RPP) attempted replications of 100 research findings in psychology, they observed a substantial discrepancy between the replication findings and the original findings [@osc2015estimating].
-Similarly, the Many Labs projects aimed to replicate the effects reported in original articles across different labs in various locations around the world [@klein2014investigating; @ebersole2016many; @ebersole2020many; @klein2018many; @klein2022many], and often found smaller effects in replications compared to original research.
+In 2015, the Replication Project: Psychology [RPP; @osc2015estimating] attempted replications of 100 research findings in psychology, they observed a substantial discrepancy between the replication findings and the original findings .
+Similarly, the Many Labs projects aimed to replicate the effects reported in original articles across different labs in various locations around the world [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many], and often found smaller effects in replications compared to original research.
 Furthermore, the estimates of the effect varied between different lab locations.
 
-In response to this string of failed replications, there was widespread alarm regarding the credibility and robustness of findings in psychological science [@hughes2018psychology; @giner2019crisis], and efforts to explain failures to replicate.
+In response to this string of failed replications, there was widespread alarm regarding the credibility and robustness of findings in psychological science [@hughes2018psychology; @giner2019crisis], and efforts to explain the low replication rate.
 The factors that have been proposed include, questionable research practices [@simmons2011false; @john2012measuring; @cumming2014new; @wicherts2016degrees], questionable reporting practices [@bakker2011mis; @nuijten2016prevalence], and biased publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science].
@@
 
-Psychological constructs, such as affective state or intelligence, can not be measured directly [@flake2017construct].
+Psychological constructs, such as affective state or intelligence, cannot be measured directly [@flake2017construct].
 Psychological measurements involve random measurement errors and uncertainties about whether the targeted construct is indeed well reflected in the scores retrieved from the measurement procedure.
@@
 
-## Many Labs Sample Description
-
-Because the Many Labs projects involved multiple lab locations over the world directly replicating the same effect, their data allows us to study the variability in these measures across different contexts.
-Furthermore, the Many Labs projects used preregistered and documented structured protocols, we therefore believe the measurement use in these projects represent a high standard within the field.
-Any issues in measurement here is thus taken as an indication that other replications are equally if not more likely to face the same issues.
+Because the Many Labs projects [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many] are large-scale collaborations in which multiple lab locations directly replicated the same set of studies, their data allows us to study the variability in their measures across different contexts.
+Furthermore, as the Many Labs projects used preregistered and documented structured protocols, we therefore believe the measurement use in these projects represent a high standard within the field.
+Any issues in measurement here might suggest that other replications could face similar or greater challenges.
 
@@
 While reliability is generally considered a measure specific feature, this is false.
-The reliability of a measure varies between samples, and thus  [@cho2015cronbach; @pauly2018resampling].
+The reliability of a measure varies between samples [@cho2015cronbach; @pauly2018resampling].
 Besides random variation due the sampling error, the variations can also reflect true variation in reliability, also known as reliability heterogeneity [@vacha-haase1998ReliabilityGeneralizationExploring].
@@
 Despite the importance of having reliable and valid measures, research has shown that Questionable Measurement Practices (QMPs) are not uncommon.
-QMPs are practices that raise doubts about a measurement's validity [@flake2020measurement], and have been coined as a conjugate term to Questionable Research Practices [QRPs, @john2012measuring].
-QMPs range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of measure and procedure of any sourced measures [@flake2020measurement].
+QMPs are practices that raise doubts about a measurement's validity [@flake2020measurement], and have been coined as a term analogous to Questionable Research Practices [QRPs, @john2012measuring].
+QMPs range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of a measure and procedure of an existing measure [@flake2020measurement].
 More specifically,  @flake2020measurement identified six key questions than an article should answer to avoid QMPs: the definition of the construct, how the measure was selected, how the measure was operationalized, how the measure was quantified, whether it was modified or not and why, and the reasons and details of creating a measure if applicable.
@@
 In order to reconstruct the measurement, replication researchers need to know the items that were used, how they were presented to the subjects, and how to compute the scores.
-If the measure is not reconstructed exactly, constructs measured by original and replication may differ.
-leading to differences in effect size estimates irrespective of the credibility of the original effect.
+If the measure is not reconstructed exactly, constructs measured by original and replication may differ, which may lead to differences in effect size estimates irrespective of the credibility of the original effect.
 
@@
 First, this study expands on the research by @stanley2014expectations.
-Our goal was to see whether reliability was related to replication success on empirical replication data.
-Specifically, we investigated whether replicated studies differed in their reliability from non-replicated studies.
+Our goal was to see whether reliability was related to replication success in empirical replication data.
+Specifically, we investigated whether successfully replicated studies differed in reliability from non-replicated studies.
 @stanley2014expectations assumed reliability to be constant across studies, which we know to be an oversimplification.
@@
 The Many Labs studies were intended as direct replications.
-In direct replications, any deviations from the original research are believed to be irrelevant for testing the same effect as the original study [@nosek2022replicability].
-In that case, the reliability of measurements in replications should also not deviate systematically from the original research.
+In direct replications, any remaining deviations from the original research should be irrelevant for testing the same effect as the original study [@nosek2022replicability].
+This means that, the reliability of measurements in replications should also not deviate systematically from the original research.
 
@@
 
-We preregistered data collection, coding protocol, and planned analyses: <https://osf.io/9r8yt/>. Deviations from the preregistration are explicitly mentioned in the text.
-
-### Data, materials, and online resources
+We preregistered data collection, coding protocol, and planned analyses: <https://osf.io/jgxyu>. Deviations from the preregistration are explicitly mentioned in the text.
+
+### Data, Materials, and Online Resources
 
@@
 
-### Unit of analysis
-
-The unit of analysis in this study was a measure of a psychological construct used in the primary analysis that was being replicated.
+### Unit of Analysis
+
+The unit of analysis in this study was a measure of a single psychological construct used in the primary analysis that was being replicated.
+Multiple psychological constructs could be measured per original study or replication.
 We used the the replication protocols to identify these measures.
@@
 no reverse-coded items).
-Pilot data were omitted from the analyses entirely.
+Pilot data were omitted from the analyses.
 These criteria resulted in suitable item score data from `r apa_num(nrow(data_h3_avg))` replication sets spread across on average approximately `r apa_num(mean(table(data_h3_multiple$g)), digits = 0)` lab locations for the analyses of Hypotheses 2 & 3.
@@
 Cronbach's Alpha was calculated as the main reliability index used in the analyses, as it remains the most commonly used indicator of the reliability of a measure [@flake2017construct], thus allowing for comparisons with the reliabilities reported in original articles.
-Cronbach's Alpha was calculated using the alpha function from the psych R package [@R-psych] with default arguments.
+Cronbach's Alpha was calculated using the alpha function from the psych R package [*v`r getNamespaceVersion("psych")[[1]]`*; @R-psych] with default arguments.
 Omega was pre-registered as an additional index of reliability, because it is regarded by numerous psychometricians as a more informative alternative to Cronbach’s Alpha [@crutzen2017scale; @deng2017testing].
-The results based on Omega can be found in [Appendix C](AppendixScripts/Appendix_multilevel_analyses.Rmd).
+The results based on Omega can be found in [Appendix C](../../SupplementaryMaterials/AppendixScripts/Appendix_multilevel_analyses.Rmd).
 
@@
 
-After the initial coding, we made a small revision to the preregistered coding protocol, because `r length(coded_data_revised_raw[1, c("Op1", "Op2", "Op5", "Sel1", "Sel3", "Quant1", "Quant2", "Quant3", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` of the `r length(coded_data_initial_raw[1, c("Def1", "Op1", "Op2", "Op3", "Op4", "Op5", "Sel1", "Sel2", "Sel3", "Sel4", "Quant1", "Quant2", "Quant3", "Quant4", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` QMP items were considered too stringent in some of their criteria for what constituted a QMP.
+After the initial coding, we made minor revisions to `r length(coded_data_revised_raw[1, c("Op1", "Op2", "Op5", "Sel1", "Sel3", "Quant1", "Quant2", "Quant3", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` of the `r length(coded_data_initial_raw[1, c("Def1", "Op1", "Op2", "Op3", "Op4", "Op5", "Sel1", "Sel2", "Sel3", "Sel4", "Quant1", "Quant2", "Quant3", "Quant4", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` QMP items in the preregistered coding protocol, because they were considered too stringent in some of their criteria for what constituted a QMP.
 For example, in the initial protocol an example item had to be present within the article or protocol itself, or else this was counted as a QMP.
 In the revised protocol, references to online appendices with example items were also considered sufficient for this item.
-The analyses, tables and figures presented in this article are all based on the revised coding protocol, the equivalent results based on QMPs obtained with our initial protocol can be found in [Appendix D](AppendixScripts/Appendix_initial_QMP_analyses.Rmd).
+The analyses, tables and figures presented in this article are all based on the revised coding protocol, the results of the equivalent analyses based on QMPs obtained with our initial protocol can be found in [Appendix D](../../SupplementaryMaterials/AppendixScripts/Appendix_initial_QMP_analyses.Rmd).
 
@@
 No correction for multiple testing was applied, to ensure that the rate of false negatives remained low.
-Our hypotheses are about associations that to the authors' knowledge have been proposed in the literature, but not yet empirically tested on real data.
-In this exploratory context, false negatives were considered more harmful than false positives.
+Our hypotheses are about associations that have been proposed in the literature, but to the best of our knowledge have not yet been empirically tested on real data.
+In this exploratory context, false negatives were considered more detrimental than false positives.
 
@@
 
-The number of replication sets, measures, and measures per study that were extracted, as well as the proportion of successful replications can be seen in Table \@ref(tab:ReplicationRatioTable), for each of the Many Labs separately and in total.
+Table \@ref(tab:ReplicationRatioTable) shows the number of replication sets, measures, and measures per study that were extracted, as well as the proportion of successful replications, for each of the Many Labs separately and in total.
 
@@
 Of these `r nrow(coded_data_replications)` measures `r sum(coded_data_replications$mod_check == "True")` were modified from the original to the replication.
-The total sample size in the replications was on average `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N), 0)` which was approximately `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N) / mean(coded_data_original_shortened[coded_data_original_shortened$appearance == 1 & !is.na(coded_data_original_shortened$N),]$N), 0)` times larger than the average in original studies.
+In the replications, the data of responses on the measures was further nested in several labs per replication.
+The combined sample size of all labs in the replications was on average `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N), 0)` which was approximately `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N) / mean(coded_data_original_shortened[coded_data_original_shortened$appearance == 1 & !is.na(coded_data_original_shortened$N),]$N), 0)` times larger than the average in original studies, which were conducted in single labs.
 
@@
 
-The RG meta-analysis was performed using the *rma* function from the *metafor* R package [@R-metafor].
+The RG meta-analysis was performed using the *rma* function from the *metafor* R package [*v`r getNamespaceVersion("metafor")[[1]]`*; @R-metafor].
 Defaults settings were used.
@@
 
-### H1
+### Hypothesis 1: Reliability Reporting in Original Compared to Replication Research.
 
@@
 
-The number of reported reliabilities were `r N_reported_reliabilities_original` in original articles and `r N_reported_reliabilities_replications` in replications, which was too low to ensure that the pre-registered Mann-Whitney U test can function as an informative test on the difference in the reported value of Cronbach's Alpha between original articles and replications.
+The number of reported reliabilities was `r N_reported_reliabilities_original` in original articles and `r N_reported_reliabilities_replications` in replications, which was too low to ensure that the pre-registered Mann-Whitney U test can function as an informative test on the difference in the reported value of Cronbach's Alpha between original articles and replications.
 Instead, the difference between the reported reliability in the original article and the calculated average reliability in replications is displayed in the Diff column in Figure \@ref(fig:Plot23AlphaCode).
@@
 
-### H2
+### Hypotheis 2: Within Study Variation in Reliability.
 
 To get an indication of the true variability in the reliability scores, we used the RG meta-analyses to test for heterogeneity in the reliabilities in the replications.
-This analysis deviated from the multilevel analysis we preregistered, as the preregistered analysis was later deemed not suitable for testing Hypothesis 2 (results from the preregistered analysis are shown in [Appendix A](AppendixScripts/Appendix_pre-reg_analyses.Rmd)).
+This analysis deviated from the multilevel analysis we preregistered, as the preregistered analysis was later deemed not suitable for testing Hypothesis 2 (results from the preregistered analysis are shown in [Appendix A](../../SupplementaryMaterials/AppendixScripts/Appendix_pre-reg_analyses.Rmd)).
 
@@
 
-### H3
+### Hypotyhesis 3: Reliability and Replicability
 
@@
 
-# well this OR is quite a ridiculous number now..., but then again a step from 0 alpha to 1, is quite a jump too...
+# well this OR is quite a ridiculous number..., but then again a step from 0 alpha to 1 is quite a jump too...
 H3_test_result_main_alpha$full_result$alpha
@@
 Cronbach's alpha did not significantly predict replication success in the main logistic regression model (`r H3_main_full_results_alpha_with_OR`).
-Results based on the Omega coefficient lead to a similar conclusion (see [Appendix C](AppendixScripts/Appendix_omega_analyses.Rmd).
+Results based on the Omega coefficient lead to a similar conclusion (see [Appendix C](../../SupplementaryMaterials/AppendixScripts/Appendix_omega_analyses.Rmd)).
 However, it should be noted that the reliability coefficient could be calculated for only `r nrow(data_h3_avg)` measures.
@@
 
-Reliability was more commonly reported in original (n = `r `N_reported_reliabilities_original`) as compared to replication research (n = `r N_reported_reliabilities_replications_number_style`), $\chi^{2}$(`r apa_num(reliability_reporting_test_result$parameter)`) = `r apa_num(reliability_reporting_test_result$statistic)`, *p* = `r apa_p(reliability_reporting_test_result$p.value)`.
+Reliability was more commonly reported in original (n = `r N_reported_reliabilities_original`) as compared to replication research (n = `r N_reported_reliabilities_replications_number_style`), $\chi^{2}$(`r apa_num(reliability_reporting_test_result$parameter)`) = `r apa_num(reliability_reporting_test_result$statistic)`, *p* = `r apa_p(reliability_reporting_test_result$p.value)`.
 Validity evidence was similarly reported infrequently.
@@
 
-### H4
+### Hypothesis 4: QMPs in Original Compared to Replication Research.
 
@@
 
-We used a beta-regression model to test the difference in QMP ratio between original and replication was significant using the *betareg* R package [@R-betareg_a; @R-betareg_b].
+We used a beta-regression model to test the difference in QMP ratio between original and replication was significant using the *betareg* R package [*v`r getNamespaceVersion("betareg")[[1]]`*; @R-betareg_a; @R-betareg_b].
 Beta regression models are similar to other generalized linear regression models, but they are better suited to model dependent variables with values in the interval of $(0, 1)$, including ratios.
@@
 
-### H5
+### Hypothesis 5: Replication Research QMPs and Replicability.
 
@@
 H5_test_results_REV_with_OR <- OR_to_apa_full_supplier(H5_test_results_REV$full_result$QMP_REV_ratio, negative_b = TRUE)
-H5_test_results_REV_with_OR
+
+# and the same model using the QMPs from the initial coding protocol
+H5_test_results <- apa_print(glm(hypothesis_support ~ QMP_ratio, data = data_h5, family = binomial))
+
+H5_test_results_with_OR <- OR_to_apa_full_supplier(H5_test_results$full_result$QMP_ratio, negative_b = TRUE, not_significant = TRUE)
 
@@
 In line with Hypothesis 5, results showed that successful replications were associated with fewer QMPs compared to unsuccessful replications (`r H5_test_results_REV_with_OR`).
-
-### H6
+However, we did not find the association when based on the initial protocol (`r H5_test_results_with_OR`).
+
+### Hypothesis 6: Relation Between QMPs in Original and Replication Research.
 
@@
 
+# and the same model using the QMPs from the initial coding protocol
+H6_test_results <- betareg(Rep_QMP_ratio ~ QMP_ratio, data = data_h6)
+
 ```
@@
 This result provides evidence in favor of Hypothesis 6.
+However, this association was sensitive to changes in the QMP protocol, as we did not observe a significant relation between original and replication QMP ratios based on QMPs from the initial protocol (`r betareg_output_to_apa_full(H6_test_results)`).
 
@@
 Overall, even though the average reliability was relatively high, we found that not all measures were sufficiently reliable, nor where measures always equally reliable in each setting in which they were used.
-Although, we did not observe reliability to significantly predict replication success, we did observe a negative relation between replication success and presence of QMPs in replication research.
-Finally, we found QMPs in the replication to be positively associated with QMPs in the original studies
+Although we did not observe reliability to significantly predict replication success, we did observe a negative relation between replication success and presence of QMPs in replication research.
+Finally, we found QMPs in the original studies to be positively associated with QMPs in the replications.
 
@@
 
-### Reliability varied within and between measures
+### Reliability Varied Within and Between Measures
 
@@
 
-### No observed relation between reliability and replicability
+### No Observed Relation Between Reliability and Replicability
 @stanley2014expectations illustrated that measurement error, when not attenuated for, can impact replication assessments.
@@
 For example, reliability and replicability are only related when the true effect is not null.
-In our sample more than half of the effects were not replicated, indicating that many of these effects may be null effects.
-For these effects no relation is expected.
+In our sample, more than half of the effects were not replicated, indicating that many of these effects may be null effects.
+For these effects no relation between reliability and replicability is expected.
 Furthermore, while lower reliability decreases effect sizes it can also reduce the observed true variance in the effects [@olsson-collentine2023UnreliableHeterogeneityHow].
@@
 
-The complexity of the relationship combined with the fact that we could only calculate reliability for a small number of measures meant we had low statistical power to detect the overall relation between reliability and replicability, which provides a likely explanation for our non-significant finding.
-
+The complexity of the relationship combined with the fact that we could only calculate reliability for a small number of measures meant we had low statistical power to detect the overall relation between reliability and replicability, which provides another possible explanation for our non-significant finding.
 The small number of relevant measures and reported reliabilities also indicates an important issue: we observed a lack of reliability evidence in both original and replication psychological research.
@@
 
-### Measurement Reporting is often incomplete
+### Measurement Reporting is Often Incomplete
 
@@
 
-### Incomplete measurement reporting hinders replicability
+### Incomplete Measurement Reporting Hinders Replicability
 
@@
 However, it is worth noting that these associations were only found for QMPs coded with the revised coding protocol.
-Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see [Appendix D](AppendixScripts/Appendix_initial_QMP_analyses.Rmd) for results based on the initial protocol).
+Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see [Appendix D](../../SupplementaryMaterials/AppendixScripts/Appendix_initial_QMP_analyses.Rmd) for results based on the initial protocol).
 
@@
 We encountered numerous challenges in operationalizing QMPs.
-Whereas previous research has focused on descriptives of specific QMPs detrimental to construct validity [@flake2022construct; @shaw2020measurement], we operationalized all coded QMPs together as a variable to assess measurement practices and evaluate their impact on replicability.
+Whereas previous research has focused on descriptives of specific QMPs detrimental to construct validity [@flake2022construct; @shaw2020measurement], we combined all coded QMPs together as an operationalization to assess measurement practices and evaluate their impact on replicability.
 However, this also means that it remains uncertain if our operationalization accurately captured the concept.
-We already deemed it necessary to revise our coding protocol to be more lenient regarding more context dependent QMPs compared to the initial protocol.
+We encountered particular difficulty in determining when a practice is questionable, and the impact of the context on this decision.
+As a result, we already deemed it necessary to revise our coding protocol to be more lenient regarding more context dependent QMPs compared to the initial protocol.
 This revision was not trivial, as it altered the interpretation of our results.
-Regardless, it reflects the challenges we encountered in operationalizing QMP in this novel way.
-Future research is needed to identify which way is the most rigorous and fair.
-
-One challenge in operationalizing was the difficulty in determining when a practice is questionable, and the impact of the context on this decision.
-For example, in our sample the constructs that were measured were less commonly defined in replication protocols than in original articles.
-However, one may argue that it is not the responsibility of the replication to define the construct, as it is meant to be equivalent to the construct assessed in the original article.
-In that case, not defining the construct may not be a questionable practice at all.
+This finding reflects the challenges we encountered in operationalizing QMPs in a single index.
 
 Another challenge in constructing a QMP variable was the way to treat practices that were not applicable to a particular measurement.
-We chose to make use of ratios to cancel out the effects of non-applicable items as much as possible.
+We chose to construct ratios to cancel out the effects of non-applicable items as much as possible.
 However, this has the consequence that both a measure for which all relevant measurement-related information was reported, and a measure for which no item was applicable would have a QMP ratio of zero.
@@
 
-The relation is further complicated, as it is not clear how great a ratio of QMPs represents clear violations of good research practices.
+Interpreting any relation between QMP ratios and measurement reporting is complex, as it is not clear how high a ratio of QMPs should be to represent clear violations of good research practices.
 One might argue that any QMP is a sign of questionable research and thus that any ratio greater than zero is cause for alarm.
@@
 
-A second limitation is that our tests on reliability were underpowered.
-This was the result of the small number of reported reliability scores, and multiple item scales with available data.
+A second limitation is that some of our tests were likely underpowered.
+Especially the tests on reliability, because of the small number of reported reliability scores, and multiple item scales with available data.
 However, this limitation also illustrates two key findings.
@@
 Firstly, the majority of the measurements in our replication sample were modified in some way, it is therefore important that replication protocols still report on their measurement as it may deviate from the original.
-Secondly, articles are often also restricted in the amount of space they have available to devote to measurement [@gardiner2019editorial].
-Thirdly, supplementary materials were also included as a valid information source.
+Secondly, articles are often also restricted in the amount of space they have available to devote to measurement, so space restrictions are no reason per se to not report important measurement information [@gardiner2019editorial].
+Thirdly, supplementary materials were also included as a valid information source, which increase the space available to describe the measurement, further equalizing reporting space in original articles and replication protocols.
 Still, future research may wish to analyze supplementary materials in greater detail, to investigate to what extent these materials cover measurement details in both replication protocols and original articles.
@@
 A fourth limitation is that we of only used one definition of replication success.
-Replication success can be estimated and framed in multiple ways [for an example in replication research see, @osc2015estimating], including methods that do not make use of significance testing, or that attenuate for (measurement) error.
+Replication success can be estimated and framed in multiple ways [for an example in replication research, see @osc2015estimating], including methods that do not make use of significance testing, or that attenuate for (measurement) error.
 The relationship between reliability and other indices of replication success may differ.
@@
 Future research could for example randomly assign original studies in a large scale replication project to either needing to report all relevant measurement information as noted down in Table 1 in @flake2020measurement, while other studies receive no such reporting requirements.
-Similarly, the requirement to use validated measures based on the criteria set out in section 1, 2, and 3 in the @aera2014standards standards, or lack thereof could be randomly assigned conditions.
+Similarly, the requirement to use validated measures based on the criteria set out in section 1, 2, and 3 in the @aera2014standards standards, or lack thereof could be randomly assigned to conditions.
 Although such experimental designs would be the most direct way to assess causality, it would take tremendous coordination and funding to integrate original studies into a large scale replication project from the start.
@@
 
-Taking all the findings together, the following statements will be relevant to consider for future research.
+Taking all the findings together, we formulated several recommendations.
 Firstly, reliable and valid measures are a prerequisite for credible findings.
@@
 Furthermore, we argue that researchers seeking to replicate a study should first evaluate the measurement of that study.
-It is crucial for an informative replication that the measurement is reliable or valid.
-Otherwise it may be futile to attempt a direct replication [see also @nuijten2022assessing].
+It is crucial for an informative replication that the measurement is reliable or valid, otherwise it may be futile to attempt a direct replication [see also @nuijten2022assessing].
 If the measurement is insufficiently reliable or valid, we suggest that researchers instead use their resources to conduct a replication of a study with reliable, valid and well-documented measurement.
@@
 
-Through our investigations into the reliability, and reporting of measurement in the Many Labs replications and associated original studies, we found that reliability and validity evidence was reported infrequently.
+Through our investigations into the reliability and reporting of measurement in the Many Labs replications and associated original studies, we found that reliability and validity evidence was often not reported.
 Furthermore, QMPs that obscured important information needed to evaluate and reconstruct the measurement were common, especially in original research.
-QMPs were in turn related to the replicability of a finding.
-Results were less clear for reliability differences between original and replication, due to lack of power.
-However, around a quarter of measures showed signs of significant variation in reliability across labs.
-Combined these findings illustrate the need for more concrete standards in measurement reporting, and that researchers should consider the validity and reporting completeness of a study's measurement before attempting to replicate it.
+We observed results suggesting that QMPs in turn related to the replicability of a finding.
+Results were less clear for reliability differences between original and replication, most likely because the analysis lacked  of power to detect a difference.
+However, we did observe that around a quarter of measures showed signs of significant variation in reliability across labs.
+Combined these findings illustrate the need for widespread adoption of measurement reporting standards, and that researchers should consider the validity and reporting completeness of a study's measurement before attempting to replicate it.
 
@@
 Cas Goos https://orcid.org/0009-0005-3792-4148
+
 Marjan Bakker https://orcid.org/0000-0001-9024-337X
+
 Jelte M. Wicherts https://orcid.org/0000-0003-2415-2933
+
 Michèle B. Nuijten https://orcid.org/0000-0002-1468-8585
@@
 :::
-
-\newpage
-
-# (APPENDIX) Appendix {.unnumbered}
-
-```{r child = "AppendixScripts/Appendix_pre-reg_analyses.Rmd"}
-```
-
-```{r child = "AppendixScripts/Appendix_multilevel_analyses.Rmd"}
-```
-
-```{r child = "AppendixScripts/Appendix_omega_analyses.Rmd"}
-```
-
-```{r child = "AppendixScripts/Appendix_initial_QMP_analyses.Rmd"}
-```

### 2024-07-17 SupplementaryMaterials/AppendixScripts/Appendix_initial_QMP_analyses.rmd
Implemented writing feedback, fixed betareg to apa full CI code, and moved the appendix files to the supplementary materials.

--- 2024-07-01 Scripts/Manuscript/AppendixScripts/Appendix_initial_QMP_analyses.rmd
@@
 
-# Initial Coding Protocol QMP Analyses
+```{r analysis-preferences}
+# Seed for random number generation
+set.seed(17042023)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+```
+
+# Appendix D: Initial Coding Protocol QMP Analyses
 
@@
 In this appendix we run the model based on the QMP ratios obtained using the initial protocol.
+The relation between QMP ratios in the replication protocols and corresponding original articles were investigated using a beta regression model.
+Appendix B already contained the results of the multilevel sensitivity models for hypothesis 5 & 6 based on the QMP ratios obtained using the revised coding protocol.
+In this appendix we show the result for the same models based on the QMP ratios obtained using the initial protocol.
 
@@
 
-H5_test_results_with_OR <- OR_to_apa_full_supplier(H5_test_results$full_result$QMP_ratio, negative_b = TRUE)
+H5_test_results_with_OR <- OR_to_apa_full_supplier(H5_test_results$full_result$QMP_ratio, negative_b = TRUE, not_significant = TRUE)
 
 ```
-
-The relation between QMP ratios in the replication protocols and corresponding original articles were investigated using a beta regression model.
 
@@
 ```
-
-Appendix B already contained the results of the multilevel sensitivity models for hypothesis 5 & 6 based on the QMP ratios obtained using the revised coding protocol.
-In this appendix we show the result for the same models based on the QMP ratios obtained using the initial protocol.
 
@@
 
-### Results + Comparison Interpretation
+### Results & Comparison Interpretation
 The figure below displays the distribution of observed QMP ratios across original articles and replication protocols based on the initial coding protocol.
@@
 Figure \@ref(fig:Plot46InitialDataCode) displays this relationship visually.
+Table \@ref(tab:H6ExploratoryAssociationsInitialTable) shows the relations between original and replication QMP ratios for each QMP type based on the initial protocol.
+Figure \@ref(fig:Plot46FullInitialDataCode) shows the same relations displayed visually.
 
@@
 ```
-
-Table \@ref(tab:H6ExploratoryAssociationsInitialTable) shows the relations between original and replication QMP ratios for each QMP type based on the initial protocol.
-Figure \@ref(fig:Plot46FullInitialDataCode) shows the same relations displayed visually.
 
@@
 Now looking at the multilevel sensitivity analyses (see appendix B), only now using the QMP ratios based on the initial coding protocol.
-
 Contrary to the results of the multilevel sensitivity model testing hypothesis 5 using QMP ratios obtained with the revised coding protocol, the relationship in the multilevel model was no longer significant for QMP ratios obtained with the initial coding protocol (`r check_h5$full_result$hypothesis_supportTRUE`).

### 2024-07-17 SupplementaryMaterials/AppendixScripts/Appendix_multilevel_analyses.rmd
Implemented writing feedback, fixed betareg to apa full CI code, and moved the appendix files to the supplementary materials.

--- 2024-07-01 Scripts/Manuscript/AppendixScripts/Appendix_multilevel_analyses.rmd
@@
 
-# Multilevel Analyses
+```{r analysis-preferences}
+# Seed for random number generation
+set.seed(17042023)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+```
+
+# Appendix B: Multilevel Analyses
 
 This appendix contains the multilevel model versions of the models used to test Hypothesis 3, 5, & 6.
-These models were excluded from the published article for the sake of brevity, and because the sample size was not large enough to support multilevel modelling in most cases.
+These models were excluded from the main text for the sake of brevity, and because the sample size was not large enough to support multilevel modelling in most cases.
 
-## Hypothesis 3, nested within replication set
+## Hypothesis 3, Nested Within Replication Sets
 ### Explanation of Relevance

### 2024-07-17 SupplementaryMaterials/AppendixScripts/Appendix_omega_analyses.rmd
Implemented writing feedback, fixed betareg to apa full CI code, and moved the appendix files to the supplementary materials.

--- 2024-07-01 Scripts/Manuscript/AppendixScripts/Appendix_omega_analyses.rmd
@@
 
-# Omega Coefficient Analyses
+```{r analysis-preferences}
+# Seed for random number generation
+set.seed(17042023)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+```
+
+# Appendix C: Omega Coefficient Analyses
 
@@
 
-### explanation why
+### Explanation of Relevance
 Omega was included since it has been argued to be a more informative measure of reliability than alpha, while also providing validity evidence for the scale [@crutzen2017scale; @deng2017testing].
+We focused our attention on the Cronbach’s Alpha in the main text, because Cronbach’s Alpha is used more commonly in research allowing us to make comparisons between calculated and reported reliabilities.
+Furthermore, we were able to calculate the standard error of alpha to be used in the Reliability Generalization meta-analysis.
 Omega was calculated using the omega function in the *psych* R package [@R-psych].
@@
 To separate between and within variance in reliability, a multilevel random intercept model was specified with replication set as the grouping variable, which was the same model used for testing.
-The difference was that the omega value of a replication was used as dependent variable in this instance, using the *lmer* function from the *lme4* package [@R-lme4].
+The difference was that the omega value of a replication was used as dependent variable in this instance, using the *lmer* function from the *lme4* package [*v`r getNamespaceVersion("lme4")[[1]]`*; @R-lme4].
 
@@
 The ICC was calculated similarly based on the omega as was done for Cronbach's alpha in the article.
+The analysis for H3 related the calculated average reliability coefficients for each replication set to whether the replication was successful when judged at meta-significance level of $alpha <.05$.
+A multilevel random-intercept, and a random-slope equivalent model to the model above were also run for Omega, similarly to what was done for Cronbach's alpha in Appendix B.
 
@@
 ```
-
-The analysis for H3 related the calculated average reliability coefficients for each replication set to whether the replication was successful when judged at meta-significance level of $alpha <.05$.
 
@@
 ```
-
-A multilevel random-intercept, and a random-slope equivalent model to the model above were also run for Omega, similarly to what was done for Cronbach's alpha in Appendix B.
 
@@
 
-### Results + Comparison Interpretation
+### Results & Comparison Interpretation
 For omega the mean (values calculated in the population across replication sets) was `r apa_num(mean(data_h3_multiple$omega, na.rm = TRUE), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`.

### 2024-07-17 SupplementaryMaterials/AppendixScripts/Appendix_pre-reg_analyses.Rmd
Implemented writing feedback, fixed betareg to apa full CI code, and moved the appendix files to the supplementary materials.

--- 2024-07-01 Scripts/Manuscript/AppendixScripts/Appendix_pre-reg_analyses.Rmd
@@
 
-# Pre-registration Analyses
+```{r analysis-preferences}
+# Seed for random number generation
+set.seed(17042023)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+```
+
+# Appendix A: Pre-registration Analyses
 
@@
 
-## Intraclasscorelation assessment for within measure variation in reliability
+## Intraclasscorelation Assessment for Within Measure Variation in Reliability
 
@@
 On top of that, reliabilities could be calculated for each individual lab per replication set so that the variance of them could be assessed.
-To separate between and within variance in reliability, a multilevel random intercept model was specified with replication set as the grouping variable and the Cronbach's alpha or omega value of a replication as dependent using the lmer function from the lme4 package [@R-lme4] t.
+To separate between and within variance in reliability, a multilevel random intercept model was specified with replication set as the grouping variable and the Cronbach's alpha or omega value of a replication as dependent using the *lmer* function from the *lme4* package [*v`r getNamespaceVersion("lme4")[[1]]`*; @R-lme4].
 
@@
 
-To present additional validity evidence alongside the analyses of Cronbach's alpha and omega coefficients, the unidimensionality of each measure was investigated.
+To present additional validity evidence alongside the analyses of Cronbach's alpha and omega coefficients, we investigated the unidimensionality of each measure.
 To test this, each multiple item scalar measure had their factor structure investigated on the entire measure data of the replication set.
@@
 As a result, the use of a single score in the analyses cannot be taken as evidence that the construct is considered unidimensional by neither the authors, nor the broader literature on the topic.
-
-Nevertheless, we present here the result of the analyses made under the assumption that the one score, one dimension heuristic holds, for the readers that are comfortable with this heuristic.
+Nevertheless, we present here the result of the analyses made under the assumption that the one score, one dimension heuristic holds.
 
@@
 
-A single factor confirmatory factor analysis was implemented using the *fa* function from the *psych* package [@R-psych] in R.
+A single factor confirmatory factor analysis was implemented using the *fa* function from the *psych* package [*v`r getNamespaceVersion("psych")[[1]]`*; @R-psych] in R.
 The maximum likelihood factoring method was used, with defaults being used for all other function arguments.
 From this analysis, the RMSEA of the one factor solution was extracted.
-Additionally, a parallel test was conducted using the *fa.parallel* function also from the psych package.
+Additionally, a parallel test was conducted using the *fa.parallel* function also from the *psych* package.
 If either the RMSEA score \< .08, or the parallel analysis returned a one factor solution, unidimensionality was coded as true, otherwise it was coded as false.
@@
 Follow-up analyses were preregistered for hypothesis 6.
-Using a similar model to the main hypothesis test with all unique combination of the five different QMP types being tested across original and replication data.
+The pre-registered plan was to make use of contingency tables to compare relations between all five QMP types across original and replication studies.
 The goal of these analyses was to see if there are any type specific carry-over effects in QMPs between original and replication.
@@
 It is partly this large number of tests, as well as the resulting lack of clear interpretability in the results that caused this analysis to be omitted from the main article.
-However, for completeness and transparency it is reported here.
+.
+However, This analysis was anyhow intended not as supplementary to the main test for hypothesis 6.
+Furthermore, the analyses would regardless have to be changed from the pre-registered analyses to beta-regressions for each unique combination of the QMP categories across original and replication.
+For completeness and transparency the analyses using beta-regressions are reported here.
 

### 2024-07-17 Scripts/source_script.R

@@ -555,20 +555,20 @@ betareg_output_to_apa_full<- function(betareg_output, coefficient_number = 2){
   std_error <- sum_object[2]
   z_value <- sum_object[3]
   p_value <- sum_object[4]
-  n <- betareg_output$n
   
   # calculating the confidence intervals
   if(z_value < 0){
-    CI_HI <- estimate - z_value * (std_error / sqrt(n))
-    CI_LO <- estimate + z_value * (std_error / sqrt(n))
+    CI_HI <- estimate - (1.96 * std_error)
+    CI_LO <- estimate + (1.96 * std_error)
   } else{
-    CI_LO <- estimate - z_value * (std_error / sqrt(n))
-    CI_HI <- estimate + z_value * (std_error / sqrt(n))
+    CI_LO <- estimate - (1.96 * std_error)
+    CI_HI <- estimate + (1.96 * std_error)
   }
   
   # formatting the statistics for printing
   estimate_string <- paste0("$b = ", apa_num(estimate), "$, ")
-  CI_string <- paste0("95\\% CI $[", apa_num(CI_LO), ", ", apa_num(CI_HI), "]$, ")
+  CI_string <- paste0("95\\% CI $[", apa_num(CI_LO), ", ", 
+                      apa_num(CI_HI), "]$, ")
   z_string <- paste0("$z = ", apa_num(z_value), "$, ")
   p_string <- paste0("$p = ", apa_p(p_value), "$")
   
@@ -790,25 +790,25 @@ Data_prep_H3_avg <- function(Data_H5, Data_H3_multiple){
 
 
 # function to add Odds-Ratio to apa_full output of logistic regressions
-OR_to_apa_full_supplier <- function(apa_print_result, negative_b = FALSE){
+OR_to_apa_full_supplier <- function(apa_print_result, negative_b = FALSE, not_significant = FALSE){
   # the odds-ratio
   OR <- round(exp(as.numeric(substr(apa_print_result, start = 6, 
                                     stop = 9 + negative_b))), 3) 
   
   # the lower bound 95% confidence interval for the odds-ratio
   ORCILO <- round(exp(as.numeric(substr(apa_print_result, start = 23 + negative_b, 
-                                        stop = 26 + negative_b*2))), 3) 
+                                        stop = 26 + negative_b * 2))), 3) 
   
   # the upper bound 95% confidence interval for the odds-ratio
[…]

### 2024-07-25 Scripts/Manuscript/manuscript.Rmd
rewriting based on feedback

@@
 abstract: |
-  Recent studies have shown that challenges in measurement practices in original and replication research may have contributed to the “replication crisis” in psychological science. 
-  However, the exact nature and extent of the association between measurement and replicability is not yet clear. 
-  We investigated the reliability and measurement reporting of 77 measures within 56 Many Labs replications [@klein2014investigating; @ebersole2016many; @klein2018many; @ebersole2020many] and related original psychological studies, and whether these were associated with replicability.
-  Results from logistic regression models indicated that questionable practices in measurement reporting in replication studies (b = -5.60, OR = 0.004, 95% [0,0.156]), but not the reliability of the measurement (b = 8.21, OR = 3677.542, 95% [1.271,1727601729.241]), was associated with lower replicability of the findings tested with that measure.
-<!-- the code for these two results is: ???; these lines will only work after code chunks 1, 2, 12, & 19 have been ran.
--->
-  Furthermore, not all measures in the original and replication studies were sufficiently reliable across contexts. 
-  Additionally, we found that evidence on reliability and validity was rarely reported. 
-  These findings corroborate existing research that shows that validity evidence is rarely reported, and that these reporting practices may have negative consequences for the informativeness of replications.
-  We offer suggestions on improving measurement validation and reporting practices. 
-  Finally, we argue that researchers should evaluate the reported measurement information when deciding what studies to replicate.
+  Recent studies have shown that challenges in measurement practices may have contributed to the “replication crisis” in psychological science. 
+  However, the nature and extent of the association between measurement and replicability remains unclear. 
+  We investigated the reliability and measurement reporting of 77 measures within 56 Many Labs replications and related original articles [@klein2014investigating; @ebersole2016many; @klein2018many; @ebersole2020many], and their association with replicability.
+  Results from logistic regressions indicated that questionable practices in reporting on measurement (QMPs) in replication studies (b = -5.60, p = .006), but not its reliability (b = 8.21, p =.
+106) was associated with lower replicability.
+<!-- the code to retrieve these two results is: paste0("$b = ", H3_test_result_main_alpha$table$estimate[[2]], "$, p = ", H3_test_result_main_alpha$table$p.value[[2]], "$") & paste0("$b = ", H5_test_results_REV$table$estimate[[2]], "$, p = ", H5_test_results_REV$table$p.value[[2]], "$"); these lines will only work after code chunks 1, 2, 12, & 19 have been ran.-->
+  Furthermore, Reliability Generalization Meta-analysis revealed that not all measures were sufficiently reliable across contexts. 
+  We additionally found that reliability and validity evidence was rarely reported. 
+  These findings corroborate existing research that construct validity in published research is low and that may have negative consequences for replications. 
+  We offer suggestions on improving measurement practices, and argue that reported measurement information should inform the decision to replicate.
 
@@
 library(metafor)
+library(sandwich)
+library(lmtest)
 
@@
 But replications often fail.
-In 2015, the Replication Project: Psychology [RPP; @osc2015estimating] attempted replications of 100 research findings in psychology, they observed a substantial discrepancy between the replication findings and the original findings .
+In 2015, the Replication Project: Psychology [RPP\; @osc2015estimating] attempted replications of 100 research findings in psychology, they observed a substantial discrepancy between the replication findings and the original findings .
 Similarly, the Many Labs projects aimed to replicate the effects reported in original articles across different labs in various locations around the world [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many], and often found smaller effects in replications compared to original research.
@@
 Because if the scores on a measure are not consistent with themselves, it is unlikely that any effect associated with the measure can credibly be established.
-Psychometrics offers various ways to assess reliability empirically [e.g.
-@nunnally1978overview; @mellenbergh2011conceptual].
+Psychometrics offers various ways to assess reliability empirically [@nunnally1978overview; @mellenbergh2011conceptual].
 
@@
 Despite the importance of having reliable and valid measures, research has shown that Questionable Measurement Practices (QMPs) are not uncommon.
-QMPs are practices that raise doubts about a measurement's validity [@flake2020measurement], and have been coined as a term analogous to Questionable Research Practices [QRPs, @john2012measuring].
+QMPs are practices that raise doubts about a measurement's validity [@flake2020measurement], and have been coined as a term analogous to Questionable Research Practices [QRPs\; @john2012measuring].
 QMPs range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of a measure and procedure of an existing measure [@flake2020measurement].
@@
 
-Measurement reliability varies across samples. It is crucial for evaluating replications that differences between replication and original are understood and accounted for.
-
--   RQ1a. What is the reliability in replications of psychological research?
--   RQ1b. What is the reliability in original psychological research?
+Measurement reliability varies across samples. Therefore, we investigated what the reliability is in replications of psychological research (RQ1a) and original psychological research (RQ1b).
 
@@
 In direct replications, any remaining deviations from the original research should be irrelevant for testing the same effect as the original study [@nosek2022replicability].
-This means that, the reliability of measurements in replications should also not deviate systematically from the original research.
-
--   H1. No difference is present in the reliability between replication research and original psychological research.
-
-Reliability has the potential to vary not only between replication and original research, but also across replicating labs assessing the same effect [@vacha-haase1998ReliabilityGeneralizationExploring].
-
--   RQ2. Do reliability estimates differ between replicating labs?
+As a result, we expected that there would be, no difference present in the reliability between replication research and original psychological research (H1).
+
+Reliability has the potential to vary not only between replication and original research, but also across labs assessing the same effect [@vacha-haase1998ReliabilityGeneralizationExploring].
+We thus investigated whether reliability estimates differed between replicating labs (RQ2).
 
@@
 However, for effect sizes there is little empirical evidence of widespread heterogeneity among the Many Labs replications [@klein2018many; @olsson2020heterogeneity].
-We expect the same for the heterogeneity in reliability coefficients.
-
--   H2. There is no significant variation in the reliability estimates of replications of the same original study.
-
-To see if reliability is related to replication success, we investigated whether successfully replicated studies differ in the reliability of their measures as compared to non-replicated studies.
-
--   RQ3. What is the association between replication study reliability and replication outcome?
+We expected that there would be no significant variation in the reliability estimates of replications of the same original study (H2) as well.
+
+To see if reliability is related to replication success, we investigated whether there is an association between successfully replicated study reliability and replication outcome (RQ3).
 
@@
 Assuming that the true effect is not null, then the statistical conclusions tested with reliable measures are more likely to converge to significance.
-
--   H3. Reliability in replication research is positively associated with successful replication of an original finding.
+THus, we expected to observe a positive association between reliability in replication research and successful replication of an original finding (H3).
 
 ### Measurement Reporting
-
 This study aims to conceptually replicate the findings on measurement reporting of @flake2022construct.
-
--   RQ4a. How common are QMPs in replications of psychological research?
--   RQ4b. How common are QMPs in original psychological research?
+To do so we evaluate how common QMPs are in replications of psychological research (RQ4a) and original psychological research (RQ4b).
 
 @flake2022construct found that QMPs were overall more common in the RPP replications as compared to the original research.
-We did not hypothesize this to be the case in the Many Labs sample, because of the use of structured protocols documenting the measurement.
-
--   H4. QMPs are more frequent in original psychological research than in replication research.
+We hypothesized that for our Many Labs sample QMPs would be more frequent in original psychological research than in replication research (H4), because of the use of structured protocols documenting the measurement.
 
@@
 The resulting deviations in measurement may be partly responsible for deviations in replication and original effects [@flake2022construct].
-
--   RQ5. What is the association between QMPs in replication studies and replication outcome?
+Thus we investigated whether QMPs in replication protocols were associated with the replication outcome (RQ5).
 
 A reduction in QMPs corresponds to greater transparency in reporting of measurement.
-In line with earlier research finding other transparency related practices to be associated with more robust estimates of effects [@wicherts2011willingness; @protzko2020high], we expect:
-
--   H5. QMPs in replications are negatively associated with replication success.
-
-QMPs obscure information about a particular measurement. This in turn may cause issues for reconstructing that measurement in subsequent replication attempts.
-
--   RQ6. What is the association between QMPs in original research and QMPs in replications of psychological research?
+In line with earlier research finding other transparency related practices to be associated with more robust estimates of effects [@wicherts2011willingness; @protzko2020high], we expected QMPs in replications to be negatively associated with replication success (H5).
+
+QMPs obscure information about a particular measurement.
+This in turn may cause issues for reconstructing that measurement in subsequent replication attempts.
+We investigated the association between QMPs in original research and QMPs in replications of psychological research (RQ6).
 
@@
 @shaw2020measurement already found such a spill-over effect for validity.
-In line with this research we expect:
-
--   H6. The total number of QMPs in original psychological research is positively related to the total number of QMPs in replication research.
+In line with this research we expected the total number of QMPs in original psychological research to be positively related to the total number of QMPs in replication research (H6).
 
@@
 
-This manuscript was created in RStudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency.
+This manuscript was created in RStudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [*v`r getNamespaceVersion("worcs")[[1]]`*\; @vanlissaWORCS2021] to ensure reproducibility and transparency.
 All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> and <https://osf.io/9r8yt/>.
@@
 The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each set of replications replicating a single original study across multiple labs.
-These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [Data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document.
+These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [Data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document).
 
@@
 Cronbach's Alpha was calculated as the main reliability index used in the analyses, as it remains the most commonly used indicator of the reliability of a measure [@flake2017construct], thus allowing for comparisons with the reliabilities reported in original articles.
-Cronbach's Alpha was calculated using the alpha function from the psych R package [*v`r getNamespaceVersion("psych")[[1]]`*; @R-psych] with default arguments.
+Cronbach's Alpha was calculated using the alpha function from the *psych* R package [*v`r getNamespaceVersion("psych")[[1]]`*\; @R-psych] with default arguments.
 Omega was pre-registered as an additional index of reliability, because it is regarded by numerous psychometricians as a more informative alternative to Cronbach’s Alpha [@crutzen2017scale; @deng2017testing].
-The results based on Omega can be found in [Appendix C](../../SupplementaryMaterials/AppendixScripts/Appendix_multilevel_analyses.Rmd).
+The results based on Omega can be found in [Supplementary Analyses C](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_multilevel_analyses.Rmd).
 
@@
 In the revised protocol, references to online appendices with example items were also considered sufficient for this item.
-The analyses, tables and figures presented in this article are all based on the revised coding protocol, the results of the equivalent analyses based on QMPs obtained with our initial protocol can be found in [Appendix D](../../SupplementaryMaterials/AppendixScripts/Appendix_initial_QMP_analyses.Rmd).
+The analyses, tables and figures presented in this article are all based on the revised coding protocol, the results of the equivalent analyses based on QMPs obtained with our initial protocol can be found in [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd).
 
@@
 
-Table \@ref(tab:ReplicationRatioTable) shows the number of replication sets, measures, and measures per study that were extracted, as well as the proportion of successful replications, for each of the Many Labs separately and in total.
-
-```{r ReplicationRatioTable, warning = FALSE}
+Table \@ref(tab:ReplicationNrTable) shows the number of replication sets, measures, and measures per study that were extracted, as well as the proportion of successful replications, for each of the Many Labs separately and in total.
+
+```{r ReplicationNrTable, warning = FALSE}
 # construct the replication ratio table to be printed
-replication_ratio_table <- data.frame("Many Labs Version" = c("1", "2", "3", "5", "Total"),
+replication_nr_table <- data.frame("Many Labs Version" = c("1", "2", "3", "5", "Total"),
                                       "N Total" = c(table(coded_data_replications$many_labs_version), nrow(coded_data_replications)), 
@@
 
-# calculate the replication ratio from the N measures whose studies were replicated
-# and the N total measures, per Many Labs study.
-replication_ratio_table$"Replication Ratio" <- round(replication_ratio_table$N.Replicated / replication_ratio_table$N.Total, digits = 2)
-
 # Changing column names to be less computer speak-y looking
-colnames(replication_ratio_table) <- c("Many Labs Version", "Nr. Measures$^a$", 
-                                       "Nr. Replicated", "Replication Ratio")
+colnames(replication_nr_table) <- c("Many Labs Version", "Nr. Measures", 
+                                       "Nr. Replicated")
 
 # adding a superscript for a later footnote
-replication_ratio_table$"Nr. Replicated"[3] <- "$3^a$"
+replication_nr_table$"Nr. Replicated"[3] <- "$3^a$"
 
@@
 apa_table(
-  replication_ratio_table, align = c("l", "r", "r", "r")
+  replication_nr_table, align = c("l", "r", "r")
   , caption = "Ratio of measures for which the effect was considered replicated, across many labs projects"
@@
 
+```{r InformationOnMeasurementModification}
+# Here we determine whether items had the number of items changed, and how.
+
+# The code below indexes the scales for which either the number of items or 
+# number of response options were decreased.
+
+item_number_change_data <- coded_data_replications[!is.na(coded_data_replications$mod_5_REV) & coded_data_replications$mod_5_REV, c(1, 2, 3, 56)]
+
+# Extracted information on the modification of measurement items. When NA is 
+# reported it means that we found no modification of number of items.
+item_number_change_data$context <- c("from 3 questions about 15 topics -> 1 question about four topics", NA, "from a list of quotations to only the 1 of interest", "From four IATs to 1 IAT in replications", "Initial study used 6 items from an 8-item short scale, 25-item four factor scale suggested by original authors, but 5-item subscale of specific factor of interest", NA,  "Original research had 19 scenarios, replication participants got randomly assigned to 1 control and 3 moral dilemmas from the set of 19", " from a 10-item scale, to single-item scale.", NA, NA, "Compared to the 'longer lists of anagrams used' in previous research (226 for 4 dimensions) on the topic, they switched to a shorter 4 anagram task of the 1 dimension of interest.", "Original measure assessed 4 constructs with 24 item, For the replication they switched to a different scale measuring the 1 construct relevant to the effect using 7 items.")
+
+# Whether the change was a decrease or increase in items
+item_number_change_data$direction <- as.factor(c("decrease", NA, "decrease", "decrease", "decrease", NA, "decrease", "decrease", NA, NA, "decrease", "increase"))
+
+# sum(item_number_change_data$direction == "decrease", na.rm = TRUE)
+
+# creating indexes for decreasing items to see if there are noteworthy differences.
+decreased_items_index <- rep(FALSE, nrow(coded_data_replications))
+
+# setting to true in case items were decreased.
+decreased_items_index[as.numeric(rownames(item_number_change_data[item_number_change_data$direction == "decrease" & !is.na(item_number_change_data$direction),]))] <- TRUE
+
+# getting information on hypothesis support
+hypothesis_support_index <- coded_data_replications$hypothesis_support
+
+hypothesis_support_index[coded_data_replications$hypothesis_support == "Unclear"] <- "Yes"
+
+# coding Unclear into No instead of Yes didn't make a difference on the test.
+# hypothesis_support_index[coded_data_replications$hypothesis_support == "Unclear"] <- "No"
+
+# chi-squared test of differences in hypothesis support between measures for 
+# which items were decreased and for which it was not.
+chisq.test(decreased_items_index, coded_data_replications$hypothesis_support)
+
+# Interestingly, when item numbers were decreased, the replicability seemed to have increased in this scenario.
+# Although the difference was not significant and there were too few modifications to the items to get a stable estimate.
+
+#mean(coded_data_replications$hypothesis_support[!as.numeric(rownames(coded_data_replications)) %in% as.numeric(rownames(item_number_change_data[item_number_change_data$direction == "decrease" & !is.na(item_number_change_data$direction),]))] == "Yes")
+
+### Looking at the relevancy for Hypothesis tests.
+# H1
+coded_data_original_shortened$reliability_type[decreased_items_index]
+coded_data_replications$reliability_type[decreased_items_index]
+
+# Only one of these measures had a reported reliability in the original, so it
+# is unlikely to have been of much impact.
+
+# H2
+coded_data_original_shortened$reliability_coeff[decreased_items_index]
+coded_data_replications$reliability_coeff[decreased_items_index]
+
+data_h3_avg[data_h3_avg$reporting_index %in% as.numeric(rownames(item_number_change_data[item_number_change_data$direction == "decrease" & !is.na(item_number_change_data$direction),])),]
+
+# Of the measures we could calculate the reliability of, only the measure of 
+# persistence was decreased in item count. This was interestingly the one with
+# the lowest calculated average alpha in the sample.
+
+```
+
 [^1]: Initially the original articles contained 3 more measures than the replication protocols.
@@
 
+Because of this multilevel structure we initially planned to conduct multilevel models alongside our single-level regression models for testing Hypothesis 3, 5, and 6.
+However, these analyses were omitted, because group sizes were small.
+The results from these analyses are reported in [Supplementary Analyses B](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_multilevel_analyses.Rmd)) for the sake of completeness and transparency.
+
 ## Measurement Reliability
@@
 
-The RG meta-analysis was performed using the *rma* function from the *metafor* R package [*v`r getNamespaceVersion("metafor")[[1]]`*; @R-metafor].
+The RG meta-analysis was performed using the *rma* function from the *metafor* R package [*v`r getNamespaceVersion("metafor")[[1]]`*\; @R-metafor].
 Defaults settings were used.
@@
 To get an indication of the true variability in the reliability scores, we used the RG meta-analyses to test for heterogeneity in the reliabilities in the replications.
-This analysis deviated from the multilevel analysis we preregistered, as the preregistered analysis was later deemed not suitable for testing Hypothesis 2 (results from the preregistered analysis are shown in [Appendix A](../../SupplementaryMaterials/AppendixScripts/Appendix_pre-reg_analyses.Rmd)).
+This analysis deviated from the multilevel analysis we preregistered, as the preregistered analysis was later deemed not suitable for testing Hypothesis 2 (results from the preregistered analysis are shown in [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd)).
 
@@
 ## The main model to test hypothesis 3, through a logistic regression model.
-H3_test_result_main_alpha <- apa_print(glm(formula = replication ~ 1 + alpha, 
-                                      family = binomial(), data = data_h3_avg))
+H3_test_main_alpha <- glm(formula = replication ~ 1 + alpha, 
+                                 family = binomial(), data = data_h3_avg)
+
+H3_test_result_main_alpha <- apa_print(H3_test_main_alpha)
 
@@
 # well this OR is quite a ridiculous number..., but then again a step from 0 alpha to 1 is quite a jump too...
-H3_test_result_main_alpha$full_result$alpha
-
 ```
@@
 Cronbach's alpha did not significantly predict replication success in the main logistic regression model (`r H3_main_full_results_alpha_with_OR`).
-Results based on the Omega coefficient lead to a similar conclusion (see [Appendix C](../../SupplementaryMaterials/AppendixScripts/Appendix_omega_analyses.Rmd)).
-However, it should be noted that the reliability coefficient could be calculated for only `r nrow(data_h3_avg)` measures.
+Results based on the Omega coefficient lead to a similar conclusion (see [Supplementary Analyses C](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_omega_analyses.Rmd)).
+
+```{r Hypothesis3WhiteAdjustedSensitivityAnalysis, warning = FALSE}
+# We take the H3_test_main_alpha result from the main analysis on the aggregate
+# level as reported in the main text, and then calculate the White heteroskedastic 
+# variance/covariance matrix for the coefficients
+White_varcov_matrix <- vcovHC(H3_test_main_alpha, type = "HC1") # HC1 applies White's correction
+
+# now we apply this covariance matrix to get robust standard errors on our estimation
+H3_test_alpha_White_adjusted <- coeftest(H3_test_main_alpha, White_varcov_matrix)
+
+H3_coefficient_alpha_White_adjusted <- H3_test_alpha_White_adjusted[2,1]
+
+# first we calculate the odds-ratio
+OR_coefficient_alpha_White_adjusted <- round(exp(H3_coefficient_alpha_White_adjusted), 2)
+
+# then we also calculate the log-odds ratio CIs
+log_OR_CI_LOW <- H3_coefficient_alpha_White_adjusted - (1.96 * H3_test_alpha_White_adjusted[2,2])
+log_OR_CI_HI <- H3_coefficient_alpha_White_adjusted + (1.96 * H3_test_alpha_White_adjusted[2,2])
+
+# and then convert them to odds ratio CIs
+OR_CI_LOW <- round(exp(log_OR_CI_LOW), 2)
+OR_CI_HI <- round(exp(log_OR_CI_HI), 2)
+
+# now we create the string to print in text
+H3_test_result_alpha_White_adjusted <- paste0("$\\hat{\\beta} = ", round(H3_test_alpha_White_adjusted[2,1], 2), "$, $OR = ", OR_coefficient_alpha_White_adjusted, "$, 95\\% CI $[", OR_CI_LOW, ", ", OR_CI_HI, "]$, $z = ", round(H3_test_alpha_White_adjusted[2,3], 2), "$, $p = ", apa_p(H3_test_alpha_White_adjusted[2,4]), "$")
+
+```
+
+We additionally pre-registered a random intercept and random-slope multilevel regression model of the same relationship with each lab's unique reliability nested within the set of replication of an effect.
+However, because our dependent variable (replicability) is at the group level, we decided based on suggestions in the literature [@foster-johnson2018Predicting] to use a test on the aggregate level using White's heteroscedasticity adjustment to address the dependency.
+This analysis also showed a non-significant relation (`r H3_test_result_alpha_White_adjusted`).
+However, it should be noted that for these analyses the reliability coefficient could be calculated for only `r nrow(data_h3_avg)` measures.
 As a result, the estimates of the relation between reliability and replication success obtained using these models each come with large uncertainty.
@@
 `r apa_num(sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` original articles reported validity evidence from a factor analysis, while only `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` replications did.
+Furthermore, we conducted pre-registered exploratory analyses testing the unidimensionality of `r nrow(cfa_results)` measures with available replication data using a confirmatory factor analysis.
+We found that `r sum(cfa_results$Single_factor == "Yes")` of these measures met our criteria for unidimensionality (see [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd) for further details).
 
@@
 
-We used a beta-regression model to test the difference in QMP ratio between original and replication was significant using the *betareg* R package [*v`r getNamespaceVersion("betareg")[[1]]`*; @R-betareg_a; @R-betareg_b].
+We used a beta-regression model to test the difference in QMP ratio between original and replication was significant using the *betareg* R package [*v`r getNamespaceVersion("betareg")[[1]]`*\; @R-betareg_a; @R-betareg_b].
 Beta regression models are similar to other generalized linear regression models, but they are better suited to model dependent variables with values in the interval of $(0, 1)$, including ratios.
@@
 H4_test_results_REV <- betareg(QMP_REV_ratio ~ rep_org, data = data_h4)
+
 ```
@@
 
+```{r Hypotheses5ReportedMultilevelAnalyses, include = FALSE, warning = FALSE}
+## Hypothesis 5 sensitivity test using a random intercept Gaussian model.
+# create dummy H5 dataframe for use in sensitivity test
+data_h5_sens <- data_h5
+
+# convert outcome variable to be usable with Gaussian distribution via
+# logit transform.
+data_h5_sens$QMP <- log(data_h5_sens$QMP_ratio /(1 - data_h5_sens$QMP_ratio))
+
+# running the model with initial QMP ratio's
+random_intercept_h5<- apa_print(lmer(formula = QMP ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens))
+```
+
 We used logistic regression to test the association between the QMP ratio in replication protocols and replication success.
 In line with Hypothesis 5, results showed that successful replications were associated with fewer QMPs compared to unsuccessful replications (`r H5_test_results_REV_with_OR`).
-However, we did not find the association when based on the initial protocol (`r H5_test_results_with_OR`).
+However, we did not find the association with the initial protocol in neither the single-level (`r H5_test_results_with_OR`) nor the multilevel model (`r random_intercept_h5$full_result$QMP`)[^2].
+
+[^2]: As of writing this article the *betareg* package does not allow for estimation of multilevel models.
+As an approximation, Gaussian random-intercept multilevel models were implemented using the *lmer* function from the *lme4* package [@R-lme4].
+The outcome QMP ratio variable was transformed using the logit link function (the default link function in the *betareg* package) to fit the Gaussian model.
 
@@
 
+# Using a glm to check if results differs in direction and significance from the 
+# beta-regression, to check that including a linear regression line in figure 46
+# is representative of the relationship.
+H6_glm_test_REV <- glm(Rep_QMP_REV_ratio ~ QMP_REV_ratio, data = data_h6)
+
+H6_glm_test_results_REV <- apa_print(H6_glm_test_REV)$full_result$QMP_REV_ratio
+
 ```
@@
 This result provides evidence in favor of Hypothesis 6.
-However, this association was sensitive to changes in the QMP protocol, as we did not observe a significant relation between original and replication QMP ratios based on QMPs from the initial protocol (`r betareg_output_to_apa_full(H6_test_results)`).
+Figure \@ref(fig:Plot46RevisedDataCode) displays this relationship visually.
+
+```{r Plot46RevisedDataCode, error = FALSE, warning = FALSE, fig.cap = paste0("Scatterplot of original QMP ratios and replication total QMP ratios with a linear regression line.
+The linear regression line is included, as the result based on linear regression was similarly in direction and significance to the beta regression used to test Hypothesis 6 (", H6_glm_test_results_REV, "), while being easier to understand visually.
+Each dot in the figure describes the QMP ratio in that graph across both the original article and its replication protocol.
+Note: jitter was applied to these dots to show the number of observations at points where multiple dots were present.")}
+ggplot(plot_46_data_rev[plot_46_data_rev$QMP_type == "QMP.Ratio" & plot_46_data_rev$QMP_Rep_type == "Rep.QMP.Ratio",], aes(QMP_ratio,QMP_Rep_ratio)) + 
+  geom_point() +
+  geom_jitter(width = 0.01, height = 0.01) +
+  geom_smooth(method = "glm", formula = y ~ x) + 
+  theme_minimal() +
+  theme(strip.text.y = element_text(size = 7), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
+  ylab("QMP Ratio (Replication Protocol)") +
+  xlab("QMP Ratio (Original Article)")
+
+```
+
+```{r Hypotheses6ReportedMultilevelAnalyses, include = FALSE, warning = FALSE}
+## Hypothesis 6 sensitivity test using a random intercept Gaussian model.
+# create dummy H6 dataframe for use in sensitivity test
+data_h6_sens <- data_h6
+
+# convert outcome variable to be usable with Gaussian distribution via
+# logit transform. 
+data_h6_sens$QMP_REV <- log(data_h6_sens$QMP_REV_ratio /(1 - data_h6_sens$QMP_REV_ratio))
+data_h6_sens$Rep_QMP_REV <- log(data_h6_sens$Rep_QMP_REV_ratio /(1 - data_h6_sens$Rep_QMP_REV_ratio))
+data_h6_sens$QMP<- log(data_h6_sens$QMP_ratio /(1 - data_h6_sens$QMP_ratio))
+data_h6_sens$Rep_QMP <- log(data_h6_sens$Rep_QMP_ratio /(1 - data_h6_sens$Rep_QMP_ratio))
+
+# running the model with revised QMP ratio's
+random_intercept_h6_REV <- apa_print(lmer(formula = Rep_QMP_REV ~ 1 + QMP_REV + (1|many_labs_version), data = data_h6_sens))
+
+# running the model with initial QMP ratio's
+random_intercept_h6 <- apa_print(lmer(formula = Rep_QMP ~ 1 + QMP + (1|many_labs_version), data = data_h6_sens))
+```
+
+However, this association was sensitive to changes in the QMP protocol, as we did not observe a significant relation between original and replication QMP ratios based on QMPs from the initial protocol in neither the single-level (`r betareg_output_to_apa_full(H6_test_results)`) nor the multilevel model (`r random_intercept_h6$full_result$QMP`).
+Furthermore, in the multilevel model based on the revised QMPs the association was again not significant (`r random_intercept_h6_REV$full_result$QMP`).
+
+We additionally conducted planned exploratory analyses of the association for each unique combination of QMP types, but taking into account the limited sample size, we could not determine any clear relations between types (see [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd) and [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd) for further details on the analyses and results).
 
@@
 While most measures showed sufficient average reliability for most purposes in psychological research (around .80), about a quarter of the measures had a reliability generally considered insufficient (around .60 or less) [@nunnally1994assessment].
-Furthermore, the reliability in original research was generally lower than in the replication samples, contrary to our hypothesis that reported reliability estimates would not differ significantly between replications and original articles.
+Furthermore, the reliability in original research was generally lower than in the replication samples, contrary to our Hypothesis 1 that reported reliability estimates would not differ significantly between replications and original articles.
 These differences may be due to features that were specific to the Many Labs projects.
@@
 
-Our results additionally show that the reliability of a measure differs across samples, in some cases even showing signs of true variation, or heterogeneity, in reliability.
+In some cases, the reliability of measures showed signs of true variation, or heterogeneity, across samples.
 Reliability heterogeneity was particularly common for measures with a lower average reliability.
@@
 Furthermore, most measures did not show evidence of significant reliability heterogeneity, a similar lack of widespread heterogeneity was also observed for effect sizes in replications [@klein2018many; @olsson2020heterogeneity].
-Regardless, our results do demonstrate an often-overlooked aspect of reliability: reliability is a sample-specific, not a measurement-specific feature.
+Regardless, our results do demonstrate an often-overlooked aspect of reliability: reliability is a sample-specific, not a measurement-specific feature [@vacha1999practices; @cho2015cronbach].
 
@@
 As a result, effect estimates from various studies will appear more similar than they truly are, seemingly replicating the original.
-These and other relations are further complicated by the fact that reliability is not a fixed aspect of a scale, but a feature of that scale within a sample [e.g., @vacha1999practices; @cho2015cronbach].
-
-The complexity of the relationship combined with the fact that we could only calculate reliability for a small number of measures meant we had low statistical power to detect the overall relation between reliability and replicability, which provides another possible explanation for our non-significant finding.
-The small number of relevant measures and reported reliabilities also indicates an important issue: we observed a lack of reliability evidence in both original and replication psychological research.
+These and other relations are further complicated, because as mentioned earlier reliability is not a fixed aspect of a scale, but a feature of that scale within a sample.
+
+The complexity of the relationship combined with the fact that we could only calculate reliability for a small number of measures meant we had low statistical power to detect the overall relation between reliability and replicability, even more so for the multilevel model, which provides another possible explanation for our non-significant findings.
+The small number of relevant measures and reported reliabilities does however indicate an important issue: we observed a lack of reliability evidence in both original and replication psychological research.
 
@@
 Calculating reliability for single-item measures is not as straightforward and less common as for multiple item measures [@wanous1996estimating].
+Concerns with the use of single-item measures go beyond reliability, validity may also be at risk.
+Single-item measures because they are singular come with an assumption of unidimensionality regarding the construct they, which our exploratory analyses revealed is an assumption that did not frequently hold for multiple-item measures in our sample.
+However, we did not explore validity concerns unrelated to reporting in-depth, therefore future research is needed to determine the extent of problems with validity.
 
@@
 However, it is worth noting that these associations were only found for QMPs coded with the revised coding protocol.
-Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see [Appendix D](../../SupplementaryMaterials/AppendixScripts/Appendix_initial_QMP_analyses.Rmd) for results based on the initial protocol).
+Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd) for results based on the initial protocol).
+Furthermore, these Hypotheses were supported by only one of the multilevel models.
+However, these models were limited in group and sample size making their interpretation precarious.
 
@@
 This is important so that it can be mimicked in replications if needed.
-The remaining information that could not fit in the article can be made available on a public repository, such as the Open Science Framework (OSF; @soderberg2018using) or Zenodo [@zenodo2024open].
+The remaining information that could not fit in the article can be made available on a public repository, such as the Open Science Framework [OSF\; @soderberg2018using] or Zenodo [@zenodo2024open].
 
@@
 ## Funding
-The preparation of this article was supported by the veni grant ???
-awarded to Michèle Nuijten, and the vici grant ???
+The preparation of this article was supported by the veni grant VI.Veni.201G.003 awarded to Michèle Nuijten, and the vici grant ???
 awarded to Jelte M.

### 2024-07-25 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.rmd
rewriting based on feedback

--- 2024-07-17 SupplementaryMaterials/AppendixScripts/Appendix_initial_QMP_analyses.rmd
@@
-<!-- Appendix D -->
+<!-- Supplementary Analyses D -->
 
@@
 
-# Appendix D: Initial Coding Protocol QMP Analyses
+# Supplementary Analyses D: Initial Coding Protocol QMP Analyses
 
@@
 
-For hypothesis 5, a logistic regression model was used to test the association between the QMP ratio in replication protocols and replication success.
+For Hypothesis 5, a logistic regression model was used to test the association between the QMP ratio in replication protocols and replication success.
 In this appendix we run the model based on the QMP ratios obtained using the initial protocol.
 The relation between QMP ratios in the replication protocols and corresponding original articles were investigated using a beta regression model.
-Appendix B already contained the results of the multilevel sensitivity models for hypothesis 5 & 6 based on the QMP ratios obtained using the revised coding protocol.
+[Supplementary Analyses B](Supplementary_multilevel_analyses.Rmd) already contained the results of the multilevel sensitivity models for Hypothesis 5 & 6 based on the QMP ratios obtained using the revised coding protocol.
 In this appendix we show the result for the same models based on the QMP ratios obtained using the initial protocol.
@@
 ```{r Hypotheses5And6SensitivityAnalysesInitial}
-## Hypothesis 5 sensitivity test using a random intercept Guassian model.
+## Hypothesis 5 sensitivity test using a random intercept and a random slope Gaussian model.
 # create dummy H5 dataframe for use in sensitivity test
@@
 # logit transform.
-data_h5_sens$QMP <- log(data_h5_sens$QMP_ratio /(1 - data_h5_sens$QMP_ratio)) # TO INITIAL APPENDIX
+data_h5_sens$QMP <- log(data_h5_sens$QMP_ratio /(1 - data_h5_sens$QMP_ratio))
 
-check_h5 <- apa_print(lmer(formula = QMP ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens))
+# running the models
+random_intercept_h5_REV <- apa_print(lmer(formula = QMP ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens))
 
-## Hypothesis 6 sensitivity test using a random intercept Guassian model.
+random_slope_h5_REV <- apa_print(lmer(formula = QMP ~ 1 + hypothesis_support + (1+hypothesis_support|many_labs_version), data = data_h5_sens))
+
+## Hypothesis 6 sensitivity test using a random intercept and a random slope Gaussian model.
 # create dummy H6 dataframe for use in sensitivity test
@@
 # convert outcome variable to be usable with Gaussian distribution via
-# logit transform. FIRST ELEMENTS TO INITIAL APPENDIX
+# logit transform.
 data_h6_sens$QMP <- log(data_h6_sens$QMP_ratio /(1 - data_h6_sens$QMP_ratio))
@@
 
-# running the models one with none revised QMP ratio's and one with
-check_h6 <- apa_print(lmer(formula = Rep_QMP ~ 1 + QMP + (1|many_labs_version), data = data_h6_sens))
+# running the models one with initial QMP ratio's
+random_intercept_h6_REV <- apa_print(lmer(formula = Rep_QMP ~ 1 + QMP + (1|many_labs_version), data = data_h6_sens))
+
+random_slope_h6_REV <- apa_print(lmer(formula = Rep_QMP ~ 1 + QMP + (1+QMP|many_labs_version), data = data_h6_sens))
 
@@
 H6_n_check_results <- betareg(Rep_op_ratio ~ mod_ratio, data = data_h6)$n
+
+# Using a glm to check if results differs in direction and significance from the 
+# beta-regression, to check that including a linear regression line in figure 46
+# is representative of the relationship.
+H6_glm_test <- glm(Rep_QMP_ratio ~ QMP_ratio, data = data_h6)
+
+H6_glm_test_results <- apa_print(H6_glm_test)$full_result$QMP_ratio
 
@@
 The results of this test indicated that this difference was significant (`r betareg_output_to_apa_full(H4_test_results)`).
-This result is similar to the result found using the revised coding protocol in line with hypothesis 4.
+This result is similar to the result found using the revised coding protocol in line with Hypothesis 4.
 
 Contrary to the results based on the revised coding protocol, a decrease in QMP ratio based on the initial coding protocol did not significantly relate to replication success (`r H5_test_results_with_OR`).
-Thus, not supporting hypothesis 5.
+Thus, not supporting Hypothesis 5.
 
 Similarly to the previous test, the relation was not significant for the QMP ratios obtained with the initial protocol (`r betareg_output_to_apa_full(H6_test_results)`).
-Thus, not supporting hypothesis 6.
+Thus, not supporting Hypothesis 6.
 Figure \@ref(fig:Plot46InitialDataCode) displays this relationship visually.
@@
 
-```{r Plot46InitialDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication total QMP ratios with linear regression line.
+```{r Plot46InitialDataCode, error = FALSE, warning = FALSE, fig.cap = paste0("Scatterplot of original QMP ratios and replication total QMP ratios based on the initial protocol with a linear regression line.
+The linear regression line is included, as the result based on linear regression was similarly in direction and significance to the beta regression used to test Hypothesis 6 (", H6_glm_test_results, "), while being easier to understand visually.
 Each dot in the figure describes the QMP ratio in that graph across both the original article and its replication protocol.
-Note: jitter was applied to these dots to show the number of observations at points where multiple dots were present"}
+Note: jitter was applied to these dots to show the number of observations at points where multiple dots were present.")}
 ggplot(plot_46_data[plot_46_data$QMP_type == "QMP.Ratio" & plot_46_data$QMP_Rep_type == "Rep.QMP.Ratio",], aes(QMP_ratio, QMP_Rep_ratio)) + 
@@
   xlab("QMP Ratio (Original Article)")
+
 ```
@@
 
-```{r Plot46FullInitialDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication total QMP ratios obtained using the intial coding protocol with linear regression line.
+```{r Plot46FullInitialDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original QMP ratios and replication total QMP ratios obtained using the intial coding protocol with linear regression lines.
 Each dot in the figure describes the QMP ratio in that graph across both the original article and its replication protocol.
@@
 
-Now looking at the multilevel sensitivity analyses (see appendix B), only now using the QMP ratios based on the initial coding protocol.
-Contrary to the results of the multilevel sensitivity model testing hypothesis 5 using QMP ratios obtained with the revised coding protocol, the relationship in the multilevel model was no longer significant for QMP ratios obtained with the initial coding protocol (`r check_h5$full_result$hypothesis_supportTRUE`).
+Now we look at the multilevel sensitivity analyses using the QMP ratios based on the initial coding protocol.
+Contrary to the results of the model presented in the main text and the random intercept model testing Hypothesis 5 using QMP ratios obtained with the revised coding protocol, the relationship in the random intercept and random slope was no longer significant for QMP ratios obtained with the initial coding protocol (random intercept: `r random_intercept_h5_REV$full_result$hypothesis_supportTRUE`; random slope: `r random_slope_h5_REV$full_result$hypothesis_supportTRUE`).
 
-Similarly to the results of the multilevel sensitivity model testing hypothesis 5 using QMP ratios obtained with the revised coding protocol, the relationship in the multilevel model was not significant for QMP ratios obtained with the initial coding protocol (`r check_h6$full_result$QMP`).
+For Hypothesis 6, similarly to the results of the multilevel sensitivity analysis models testing Hypothesis 5, using QMP ratios obtained with the revised coding protocol, the relationship in both the random intercept and random slope models was not significant for QMP ratios obtained with the initial coding protocol (random intercept: `r random_intercept_h6_REV$full_result$QMP`; random slope: `r random_slope_h6_REV$full_result$QMP`).

### 2024-07-25 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_multilevel_analyses.rmd
rewriting based on feedback

<!-- Supplementary Analyses B -->

```{r analysis-preferences}
# Seed for random number generation
set.seed(17042023)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)

```

# Supplementary Analyses B: Multilevel Analyses

This appendix contains the multilevel model versions of the models used to test Hypothesis 3, 5, & 6 in the main text (additional multilevel models can be found in [Supplementary Analyses C](Supplementary_omega_analyses.Rmd) and [Supplementary Analyses D](Supplementary_initial_QMP_analyses.Rmd)). These models were omitted from the main text because the sample sizes were not large enough to support multilevel modelling. Guidelines suggest to have at least within the range of 10 to 30 groups with 10 to 30 cases each for multilevel models, with more groups and cases each being necessary for more complex models, such as random-slope models (Kreft, 1996; Snijders and Bosker, 1993; Hox, 1998, 2010). For Hypothesis 3 we had `r nrow(table(data_h3_multiple$g))` groups with on average `r round(mean(table(data_h3_multiple$g)),3)` cases. For Hypothesis 5 and 6 we had `r nrow(table(coded_data_replications$many_labs_version))` groups with on average `r mean(table(coded_data_replications$many_labs_version))` cases. Therefore, while we have may have had a sufficient number of cases per group for simple models, we likely lacked a sufficient number of groups to estimate multilevel models, especially more complex models. In 4 (all random slope models) of the 12 multilevel models we ran we encountered convergence issues, further illustrating that our sample size was likely inadequate for these models.

Additionally, our dependent variable (replication success) was at the group level in all of these models. In this case, it is advised in most cases to run analyses with all variables aggregated at the group level and adjust the standard errors of the coefficients using White's heteroscedasticity adjustment (Foster-Johnson & Kromrey, 2018). We therefore also show analyses with this adjustment for Hypothesis 3. Aggregation would make little sense for Hypothesis 5 and 6, as there were only four groups here, which would lead to a model with only 4 cases.

## Hypothesis 3, Nested Within Replication Sets

### Explanation of Relevance

In this data, replication attempts at different lab locations can be seen as nested within a replication set. To see if this nesting might impact the analyses of hypothesis 3, multilevel models are included here as sensitivity checks.

### Model

The specific models used were a multilevel logistic regression random intercept and random slope model. The dependent variable remains replication success at the replication set level, while Cronbach's alpha was no longer averaged across locations.

```{r Hypothesis3MultilevelModelSensitivityAnalyses, warning = FALSE}
## sensitivity analyses.
# running a random intercept multilevel logistic model
H3_test_result_int_sensitivity_alpha <- apa_print(glmer(formula = replication ~ 1 
                                                + alpha + (1|g), family = 
                                                binomial(), data = 
                                                data_h3_multiple))

# same as for non-multilevel model

# running a random slope multilevel logistic model
H3_test_result_slp_sensitivity_alpha <- apa_print(glmer(formula = replication ~ 1 
                                                + alpha + (1 + alpha|g), 
                                                family = binomial(), data =
                                                data_h3_multiple))

# did not converge
```

### Results

The random-intercept model did not show a significant relation between reliability and replication (`r H3_test_result_int_sensitivity_alpha$full_result$alpha`). This corroborates the findings in the article, only now using a random intercept multilevel model. However, also similarly to the results in the article and perhaps even more so for the multilevel model, the small sample size for these tests means that caution should be taken in interpreting these results. The random slope model did not converge.

## Hypotheses 5 & 6, nested within Many Labs

### Explanation of Relevance

The models used in the article to test Hypotheses 5 & 6 had independence of observations as an assumption, the observations here referring to a replication set. this is known to be false since the data is nested within four separate Many Labs projects.

### Models

To test if this nested structure might influence the relations described in Hypothesis 5 & 6, random intercept, and random slope multilevel models with each Many Labs project as a group were implemented as sensitivity analyses. As of writing this article the *betareg* package does not allow for estimation of multilevel models. As an approximation, Gaussian random-intercept multilevel models were implemented using the *lmer* function from the *lme4* package [@R-lme4]. The outcome QMP ratio variable was transformed using the logit link function (the default link function in the *betareg* package) to fit the Gaussian model.

```{r Hypotheses5And6SensitivityAnalyses, warning = FALSE}
## Hypothesis 5 sensitivity test using a random intercept and random slope Gaussian model.
# create dummy H5 dataframe for use in sensitivity test
data_h5_sens <- data_h5

# convert outcome variable to be usable with Gaussian distribution via
# logit transform.
data_h5_sens$QMP_REV <- log(data_h5_sens$QMP_REV_ratio /(1 - data_h5_sens$QMP_REV_ratio))

# running the models
random_intercept_h5_REV <- apa_print(lmer(formula = QMP_REV ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens))

random_slope_h5_REV <- apa_print(lmer(formula = QMP_REV ~ 1 + hypothesis_support + (1 + hypothesis_support|many_labs_version), data = data_h5_sens))

## Hypothesis 6 sensitivity test using a random intercept and random slope Gaussian model.
# create dummy H6 dataframe for use in sensitivity test
data_h6_sens <- data_h6

# convert outcome variable to be usable with Gaussian distribution via
# logit transform. 
data_h6_sens$QMP_REV <- log(data_h6_sens$QMP_REV_ratio /(1 - data_h6_sens$QMP_REV_ratio))
data_h6_sens$Rep_QMP_REV <- log(data_h6_sens$Rep_QMP_REV_ratio /(1 - data_h6_sens$Rep_QMP_REV_ratio))

# running the models with revised QMP ratio's
random_intercept_h6_REV <- apa_print(lmer(formula = Rep_QMP_REV ~ 1 + QMP_REV + (1|many_labs_version), data = data_h6_sens))

random_slope_h6_REV <- apa_print(lmer(formula = Rep_QMP_REV ~ 1 + QMP_REV + (1 + QMP_REV|many_labs_version), data = data_h6_sens))

# n of mod ratio's that are present (check)
H6_n_check_results_REV <- betareg(Rep_op_REV_ratio ~ mod_REV_ratio, data = data_h6)$n

```

### Results

For Hypothesis 5, the sensitivity analyses using a random-intercept multilevel regression found a similar significant association as that found by the main test (`r random_intercept_h5_REV$full_result$hypothesis_supportTRUE`). This result corroborates Hypothesis 5. The random slope model did not converge.

For Hypothesis 6, the sensitivity analyses using a random intercept logistic multilevel model resulted in non-significant results, which is different from the results found with the main test (revised protocol: `r random_intercept_h6_REV$full_result$QMP_REV`). This result does not corroborate Hypothesis 6. The random slope model did not converge.

# References
Foster-Johnson, L., & Kromrey, J. D. (2018). Predicting group-level outcome variables: An empirical comparison of analysis strategies. *Behavior Research Methods*, *50(6)*, 2461–2479. <https://doi.org/10.3758/s13428-018-1025-8>

Hox, J. (1998). Multilevel Modeling: When and Why. In: Balderjahn, I., Mathar, R., Schader, M. (eds) Classification, Data Analysis, and Data Highways. Studies in Classification, Data Analysis, and Knowledge Organization. *Springer, Berlin, Heidelberg*. <https://doi.org/10.1007/978-3-642-72087-1_17>

Hox, J., Moerbeek, M., & van de Schoot, R. (2010). Multilevel Analysis: Techniques and Applications, Second Edition (2nd ed.). *Routledge*. <https://doi.org/10.4324/9780203852279>

Kreft, I. G. (1996). Are multilevel techniques necessary? An overview, including simulation studies. *Unpublished manuscript, California State University, Los Angeles*.

Snijders, T. A. B., & Bosker, R. J. (1993). Standard Errors and Sample Sizes for Two-Level Research. *Journal of Educational Statistics*, *18(3)*, 237-259. <https://doi.org/10.3102/10769986018003237>

### 2024-07-25 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_omega_analyses.rmd
rewriting based on feedback

--- 2024-07-17 SupplementaryMaterials/AppendixScripts/Appendix_omega_analyses.rmd
@@
-<!-- Appendix C -->
+<!-- Supplementary Analyses C -->
 
@@
 
-# Appendix C: Omega Coefficient Analyses
+# Supplementary Analyses C: Omega Coefficient Analyses
 
@@
 Furthermore, we were able to calculate the standard error of alpha to be used in the Reliability Generalization meta-analysis.
-Omega was calculated using the omega function in the *psych* R package [@R-psych].
+Omega was calculated using the omega function in the *psych* R package [*v`r getNamespaceVersion("psych")[[1]]`*; @R-psych].
 Default arguments were used in the function except the nfactors argument, which was set to 1.
@@
 The analysis for H3 related the calculated average reliability coefficients for each replication set to whether the replication was successful when judged at meta-significance level of $alpha <.05$.
-A multilevel random-intercept, and a random-slope equivalent model to the model above were also run for Omega, similarly to what was done for Cronbach's alpha in Appendix B.
+A multilevel random-intercept, and a random-slope equivalent model to the model above were also run for Omega, similarly to what was done for Cronbach's alpha in [Supplementary Analyses B](Supplementary_multilevel_analyses.Rmd).
 
@@
 
-# well this OR is still quite a ridiculous number now..., but then again a step from 0 omega to 1, is quite a jump too...
 ```
@@
 The calculated Omega coefficient did not significantly relate to replication success in the main logistic regression model.
-Similarly, non-significance was also observed in the multilevel random-intercept and random-slope models (random intercept: `r H3_test_result_int_sensitivity_omega$full_result$omega`; random slope: `r H3_test_result_slp_sensitivity_omega$full_result$omega`).
+Similarly, non-significance was also observed in the multilevel random-intercept model (`r H3_test_result_int_sensitivity_omega$full_result$omega`).
+The random slope model did not converge.
 
@@
 
-Thus, no evidence for hypothesis 3 was found.
+Thus, no evidence in favor of Hypothesis 3 was found.
 However, caution in interpreting the test results is needed.
@@
 It mostly resembles Figure \@ref(fig:Plot23AlphaCode) from the article, with some studies being omitted as the omega coefficient function did not converge or run properly on those data.
-Furthermore, information reagrding heterogeneity was not present since the standard error of omega was not known, and comparisons between reported coefficients were omitted, since no article reported any omega coefficients.
+Furthermore, information regarding heterogeneity was not present since the standard error of omega was not known, and comparisons between reported coefficients were omitted, since no article reported any omega coefficients.
 

### 2024-07-25 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd
rewriting based on feedback

--- 2024-07-17 SupplementaryMaterials/AppendixScripts/Appendix_pre-reg_analyses.Rmd
@@
-<!-- Appendix A -->
+<!-- Supplementary Analyses A -->
 
@@
 
-# Appendix A: Pre-registration Analyses
+# Supplementary Analyses A: Pre-registration Analyses
 
@@
 
-This analysis was omitted from the article because it did not link well enough to hypothesis 2.
+This analysis was omitted from the article because it did not link well enough to Hypothesis 2.
 The test results also do not give use a very informative representations of variance in reliability in the data for us to draw further inferences from.
@@
 
-For the sake of this analysis the simple heuristic was chosen that if the measure was used as a single composite variable in the analyses, then it should be uni-dimensional.
+For the sake of this analysis the simple heuristic was chosen that if the measure was used as a single composite variable in the analyses, then it should be unidimensional.
 This is somewhat similar to what was done by @shaw2020measurement, but for the sake of this article it was deemed to strong an assumption to make that this heuristic would always hold.
@@
 ```{r cfaResultsStoring, include = FALSE, eval = FALSE}
-# storing the cfa_results, so they can be referenced within the main manuscript.
+# storing the cfa_results, so they can be referenced within the main manuscript. THIS DOES NOT NEED TO BE RUN FOR REPRODUCING THE RESULTS.
 open_data(data = cfa_results, filename = paste0(paste0(
@@
 The goal of these analyses was to see if there are any type specific carry-over effects in QMPs between original and replication.
+Theses analyses were changed from the pre-registered analyses to beta-regressions for each unique combination of the QMP categories across original and replication, as the original analysis using contingency tables was later deemed improper for our data and hypothesis 6.
+
 Due to the large number of tests, the focus was exploratory using visualization rather than inference.
-
-It is partly this large number of tests, as well as the resulting lack of clear interpretability in the results that caused this analysis to be omitted from the main article.
-.
-However, This analysis was anyhow intended not as supplementary to the main test for hypothesis 6.
-Furthermore, the analyses would regardless have to be changed from the pre-registered analyses to beta-regressions for each unique combination of the QMP categories across original and replication.
+It is the large number of tests combined with the fact that our sample size was not large enough to support that number of tests that we omitted these analyses from the main text.
+Furthermore, this analysis was intended as supplementary to the main test for hypothesis 6, and was pre-registered as exploratory.
 For completeness and transparency the analyses using beta-regressions are reported here.

### 2024-07-25 Scripts/source_script.R

@@ -722,6 +722,14 @@ data_prep_H2 <- function(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean,
                                rep(56, 20), rep(57, 21), rep(59, 21), 
                                rep(62, 4), rep(63, 4), rep(71, 8), rep(73, 5))
   
+  
+  # one index 51 is being assigned not to Monin and miller, some, but instead to cacioppo, nfc, while that Monin and Miller has gotten the 57 from cacciopo
+  # The 56 and 57 isn't correct for Cacciopo: 59 for argument quality, and 60 for nfc.
+  # De Fruyt should link to 61 instead of 59
+  
+  
+  #data_5.1.1_clean: 65, data_5.1.2_clean: 66, data_5.7_clean: 74, data_5.9.1_clean: 76
+  
   colnames(Data_H2) <- c("alpha", "omega", "ASE", "tau", "QEp", "pi.lb", 
                          "pi.ub", "g", "reporting_index")
   
@@ -793,15 +801,15 @@ Data_prep_H3_avg <- function(Data_H5, Data_H3_multiple){
 OR_to_apa_full_supplier <- function(apa_print_result, negative_b = FALSE, not_significant = FALSE){
   # the odds-ratio
   OR <- round(exp(as.numeric(substr(apa_print_result, start = 6, 
-                                    stop = 9 + negative_b))), 3) 
+                                    stop = 9 + negative_b))), 2) 
   
   # the lower bound 95% confidence interval for the odds-ratio
   ORCILO <- round(exp(as.numeric(substr(apa_print_result, start = 23 + negative_b, 
-                                        stop = 26 + negative_b * 2))), 3) 
+                                        stop = 26 + negative_b * 2))), 2) 
   
   # the upper bound 95% confidence interval for the odds-ratio
   ORCIHI <- round(exp(as.numeric(substr(apa_print_result, start = 29 + negative_b * 2, 
-                                        stop = 33 + negative_b * (2 - not_significant)))), 3)
+                                        stop = 33 + negative_b * (2 - not_significant)))), 2)
   
   # combining the calculated and existing results into a printable string
   result_string_with_OR <- paste0(substr(apa_print_result, start = 0, 

### 2024-07-26 Data/AnalysisData/codebook_item_number_change_data.Rmd
added supplementary analyses regarding the influence of number of items modification, and checked some data loading and storing.

--- 2024-03-19 Data/AnalysisData/codebook_cfa_results.Rmd
@@
 ---
-title: "Codebook created on 2024-03-18 at 2024-03-18 14:12:52.006764"
+title: "Codebook created on 2024-07-26 at 2024-07-26 14:09:18.516523"
 output: github_document
@@
 ## Dataset description
-The data contains 19 cases and 3 variables.
+The data contains 12 cases and 6 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_cfa_results.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_item_number_change_data.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2024-07-26 Data/AnalysisData/codebook_plot_456_data.Rmd
added supplementary analyses regarding the influence of number of items modification, and checked some data loading and storing.

@@
 ---
-title: "Codebook created on 2024-02-27 at 2024-02-27 16:22:04.046895"
+title: "Codebook created on 2024-07-26 at 2024-07-26 14:28:36.553505"
 output: github_document
@@
 ## Dataset description
-The data contains 924 cases and 4 variables.
+The data contains 924 cases and 6 variables.
 

### 2024-07-26 Data/Data_package_description.Rmd
added supplementary analyses regarding the influence of number of items modification, and checked some data loading and storing.

@@
 
+### item_number_change_data.csv
+
+*Explanation:* Contains the many_labs_version, rep_org, title, and mod_5_rev variablefrom the coded_data_replication.csv dataset of the observations where the mod_5_rev variable was TRUE (meaning that the measure's number of items and/or number of response options was modified from original to replication.
+Additionally, two variables were added to determine whether for that measure the number of items were decreased from original to replication.
+
+*Variables*:
+
+-   **context:** A description of the change in item numbers from original to replication. NA means that for that measure the number of items was not changed.
+
+-   **direction:** A factor indicating whether the number of items was decreased, increased, or no change (NA) from original to replication.
+
 ### plot_23_data_alpha.csv

### 2024-07-26 Scripts/Manuscript/manuscript.Rmd
added supplementary analyses regarding the influence of number of items modification, and checked some data loading and storing.

@@
 ```{r FinalPreparationData, include = FALSE, eval = FALSE}
-##### Data already available, code does not need to be run!
+##### Data already available, code does not need to be run
 ### this code prepares the various pieces of data to be ready to use for the 
@@
 # for hypothesis 3
-data_h3_multiple <- Data_prep_H3_multiple(data_h5, data_h2)
-data_h3_avg <- Data_prep_H3_avg(data_h5, data_h3_multiple)
+data_h3_multiple <- Data_prep_H3_multiple(coded_data_replications, data_h2)
+data_h3_avg <- Data_prep_H3_avg(coded_data_replications, data_h3_multiple)
 
@@
 Furthermore, `r sum(coded_data_replications$appearance != 1)` replications used more than one primary measure, resulting in `r nrow(coded_data_replications)` measures in both `r sum(coded_data_replications$appearance == 1)` replications protocols and `r sum(coded_data_original$appearance == 1)` original articles[^1].
-Of these `r nrow(coded_data_replications)` measures `r sum(coded_data_replications$mod_check == "True")` were modified from the original to the replication.
+Of these `r nrow(coded_data_replications)` measures `r sum(coded_data_replications$mod_check == "True")` were modified from the original to the replication[^2].
 In the replications, the data of responses on the measures was further nested in several labs per replication.
 The combined sample size of all labs in the replications was on average `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N), 0)` which was approximately `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N) / mean(coded_data_original_shortened[coded_data_original_shortened$appearance == 1 & !is.na(coded_data_original_shortened$N),]$N), 0)` times larger than the average in original studies, which were conducted in single labs.
-
-```{r InformationOnMeasurementModification}
-# Here we determine whether items had the number of items changed, and how.
-
-# The code below indexes the scales for which either the number of items or 
-# number of response options were decreased.
-
-item_number_change_data <- coded_data_replications[!is.na(coded_data_replications$mod_5_REV) & coded_data_replications$mod_5_REV, c(1, 2, 3, 56)]
-
-# Extracted information on the modification of measurement items. When NA is 
-# reported it means that we found no modification of number of items.
-item_number_change_data$context <- c("from 3 questions about 15 topics -> 1 question about four topics", NA, "from a list of quotations to only the 1 of interest", "From four IATs to 1 IAT in replications", "Initial study used 6 items from an 8-item short scale, 25-item four factor scale suggested by original authors, but 5-item subscale of specific factor of interest", NA,  "Original research had 19 scenarios, replication participants got randomly assigned to 1 control and 3 moral dilemmas from the set of 19", " from a 10-item scale, to single-item scale.", NA, NA, "Compared to the 'longer lists of anagrams used' in previous research (226 for 4 dimensions) on the topic, they switched to a shorter 4 anagram task of the 1 dimension of interest.", "Original measure assessed 4 constructs with 24 item, For the replication they switched to a different scale measuring the 1 construct relevant to the effect using 7 items.")
-
-# Whether the change was a decrease or increase in items
-item_number_change_data$direction <- as.factor(c("decrease", NA, "decrease", "decrease", "decrease", NA, "decrease", "decrease", NA, NA, "decrease", "increase"))
-
-# sum(item_number_change_data$direction == "decrease", na.rm = TRUE)
-
-# creating indexes for decreasing items to see if there are noteworthy differences.
-decreased_items_index <- rep(FALSE, nrow(coded_data_replications))
-
-# setting to true in case items were decreased.
-decreased_items_index[as.numeric(rownames(item_number_change_data[item_number_change_data$direction == "decrease" & !is.na(item_number_change_data$direction),]))] <- TRUE
-
-# getting information on hypothesis support
-hypothesis_support_index <- coded_data_replications$hypothesis_support
-
-hypothesis_support_index[coded_data_replications$hypothesis_support == "Unclear"] <- "Yes"
-
-# coding Unclear into No instead of Yes didn't make a difference on the test.
-# hypothesis_support_index[coded_data_replications$hypothesis_support == "Unclear"] <- "No"
-
-# chi-squared test of differences in hypothesis support between measures for 
-# which items were decreased and for which it was not.
-chisq.test(decreased_items_index, coded_data_replications$hypothesis_support)
-
-# Interestingly, when item numbers were decreased, the replicability seemed to have increased in this scenario.
-# Although the difference was not significant and there were too few modifications to the items to get a stable estimate.
-
-#mean(coded_data_replications$hypothesis_support[!as.numeric(rownames(coded_data_replications)) %in% as.numeric(rownames(item_number_change_data[item_number_change_data$direction == "decrease" & !is.na(item_number_change_data$direction),]))] == "Yes")
-
-### Looking at the relevancy for Hypothesis tests.
-# H1
-coded_data_original_shortened$reliability_type[decreased_items_index]
-coded_data_replications$reliability_type[decreased_items_index]
-
-# Only one of these measures had a reported reliability in the original, so it
-# is unlikely to have been of much impact.
-
-# H2
-coded_data_original_shortened$reliability_coeff[decreased_items_index]
-coded_data_replications$reliability_coeff[decreased_items_index]
-
-data_h3_avg[data_h3_avg$reporting_index %in% as.numeric(rownames(item_number_change_data[item_number_change_data$direction == "decrease" & !is.na(item_number_change_data$direction),])),]
-
-# Of the measures we could calculate the reliability of, only the measure of 
-# persistence was decreased in item count. This was interestingly the one with
-# the lowest calculated average alpha in the sample.
-
-```
 
@@
 The measurement information reported was comparable across all five categories, and thus it was deemed that the measurement could be reduced to reflect two overarching categories facilitate easier comparison between measurement in original and replication.
+
+[^2]: For 7 measures the number of items were modified from the original article to the replication.
+To check whether or not this had a confounding impact on our results, we re-ran the analyses testing the hypotheses excluding data from these studies.
+We found that removing these measures' data had minimal impact on the overall results.
+Therefore, the results presented below were based on data from all the measures.
 
@@
 In line with Hypothesis 5, results showed that successful replications were associated with fewer QMPs compared to unsuccessful replications (`r H5_test_results_REV_with_OR`).
-However, we did not find the association with the initial protocol in neither the single-level (`r H5_test_results_with_OR`) nor the multilevel model (`r random_intercept_h5$full_result$QMP`)[^2].
-
-[^2]: As of writing this article the *betareg* package does not allow for estimation of multilevel models.
+However, we did not find the association with the initial protocol in neither the single-level (`r H5_test_results_with_OR`) nor the multilevel model (`r random_intercept_h5$full_result$QMP`)[^3].
+
+[^3]: As of writing this article the *betareg* package does not allow for estimation of multilevel models.
 As an approximation, Gaussian random-intercept multilevel models were implemented using the *lmer* function from the *lme4* package [@R-lme4].

### 2024-07-26 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_item_reduced_measures_analyses.Rmd
added supplementary analyses regarding the influence of number of items modification, and checked some data loading and storing.

<!-- Supplementary Analyses E -->

```{r analysis-preferences}
# Seed for random number generation
set.seed(17042023)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Supplementary Analyses E: Item Reduced Measures Analyses

This appendix contains analyses on the impact that measures with a changed number of items had on the results. These analyses were not pre-registered, but were conducted to check for the potentially confoudning influence of these measures. The results of these supplementary analyses show that this impact was minimal.

```{r ExtractingItemReducedMeasures, include = FALSE}
# Here we determine whether items had the number of items changed, and how.

# The code below indexes the scales for which either the number of items or 
# number of response options were decreased.

item_number_change_data <- coded_data_replications[!is.na(coded_data_replications$mod_5_REV) & coded_data_replications$mod_5_REV, c(1, 2, 3, 56)]

# Extracted information on the modification of measurement items. When NA is 
# reported it means that we found no modification of number of items.
item_number_change_data$context <- c("from 3 questions about 15 topics -> 1 question about four topics", NA, "from a list of quotations to only the 1 of interest", "From four IATs to 1 IAT in replications", "Initial study used 6 items from an 8-item short scale, 25-item four factor scale suggested by original authors, but 5-item subscale of specific factor of interest", NA,  "Original research had 19 scenarios, replication participants got randomly assigned to 1 control and 3 moral dilemmas from the set of 19", " from a 10-item scale, to single-item scale.", NA, NA, "Compared to the 'longer lists of anagrams used' in previous research (226 for 4 dimensions) on the topic, they switched to a shorter 4 anagram task of the 1 dimension of interest.", "Original measure assessed 4 constructs with 24 item, For the replication they switched to a different scale measuring the 1 construct relevant to the effect using 7 items.")

# Whether the change was a decrease or increase in items
item_number_change_data$direction <- as.factor(c("decrease", NA, "decrease", "decrease", "decrease", NA, "decrease", "decrease", NA, NA, "decrease", "increase"))

# sum(item_number_change_data$direction == "decrease", na.rm = TRUE)

# creating indexes for decreasing items to see if there are noteworthy 
# differences in the analyses.
decreased_items_index <- rep(FALSE, nrow(coded_data_replications))

# setting to true in case items were decreased.
decreased_items_index[as.numeric(rownames(item_number_change_data[item_number_change_data$direction == "decrease" & !is.na(item_number_change_data$direction),]))] <- TRUE

```

```{r StoringItemReducedMeasureData}
# Storing the data on the Measures for which the number of items and/or response 
# options was altered from original to replication (of main interest are the
# measures for which the number of items were changed).
open_data(data = item_number_change_data, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(item_number_change_data))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(item_number_change_data))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(item_number_change_data))), ".yml"))

```

There were overall `r sum(decreased_items_index)` measures for which the number of items were reduced. In the following analyses we will see their impact on the results

```{r ReplicationSuccessDifferent}
# getting information on hypothesis support/replication success
hypothesis_support_index <- coded_data_replications$hypothesis_support

hypothesis_support_index[coded_data_replications$hypothesis_support == "Unclear"] <- "Yes"

# coding Unclear into No instead of Yes didn't make a difference on the test.
# hypothesis_support_index[coded_data_replications$hypothesis_support == "Unclear"] <- "No"

# chi-squared test of differences in hypothesis support/replication success 
# between measures for which items were decreased and for which it was not.
decreased_items_replicability_impact_test <- chisq.test(decreased_items_index, coded_data_replications$hypothesis_support)

decreased_items_replicability_impact_test_result <- paste0("$Chi^2 = ", apa_num(decreased_items_replicability_impact_test$statistic), "$, df = ",
decreased_items_replicability_impact_test$parameter, "$, p = ",
apa_p(decreased_items_replicability_impact_test$p.value), "$")

```

Interestingly, when item numbers decreased, the replicability seemed to have increased . Although the difference was not significant (`r decreased_items_replicability_impact_test_result`), and there were too few modifications to the items to get a stable estimate.

## Reliability
### H1

```{r H1Difference}
# H1
coded_data_original_shortened$reliability_type[decreased_items_index]
coded_data_replications$reliability_type[decreased_items_index]
```

Only one of these measures had a reported reliability in the original, so it is unlikely to have been of much impact.

### H2 & H3

```{r H2H3Difference}
# H2 & H3
coded_data_original_shortened$reliability_coeff[decreased_items_index]
coded_data_replications$reliability_coeff[decreased_items_index]

# running the H3 model
data_h3_avg[data_h3_avg$reporting_index %in% as.numeric(rownames(item_number_change_data[item_number_change_data$direction == "decrease" & !is.na(item_number_change_data$direction),])),]

```

Of the measures in the replication protocol that we could calculate the reliability of, none from what we can observe in our coded data was decreased in item count.

## Measurement Reporting
### H4

```{r OriginalQMPDIfference}
# comparing the mean and sd original QMP ratio 
print(c("mean decreased" = mean(data_h6$QMP_REV_ratio[decreased_items_index]),
      "sd decreased" = sd(data_h6$QMP_REV_ratio[decreased_items_index]),

      "mean non-decreased" = mean(data_h6$QMP_REV_ratio[-decreased_items_index]),
      "sd non-decreased" = sd(data_h6$QMP_REV_ratio[-decreased_items_index])))
```

No clear difference in original QMPs between modified and non-modified measures. Original measures weren't modified after all, but if QMPs were high for the changed measures, the change may be justified from the standpoint that: change was necessary, the original measurement had too many QMPs.

```{r OriginalQMPDIfference}
# comparing the mean and sd replication QMP ratio 
print(c("mean decreased" = mean(data_h6$Rep_QMP_REV_ratio[decreased_items_index]),
      "sd decreased" = sd(data_h6$Rep_QMP_REV_ratio[decreased_items_index]),

      "mean non-decreased" = mean(data_h6$Rep_QMP_REV_ratio[-decreased_items_index]),
      "sd non-decreased" = sd(data_h6$Rep_QMP_REV_ratio[-decreased_items_index])))
```

The measures for which the number of items was reduced, had somewhat more QMPs than those measures for which this was not the case. Suggesting that when the number of items are reduced, there are likely also other issues at play.

```{r H4Difference}
# running the h4 models
# only decreased item measures
betareg_output_to_apa_full(betareg(QMP_REV_ratio ~ rep_org, data = data_h4[c(decreased_items_index, decreased_items_index),]))

# only non-decreased item measures
betareg_output_to_apa_full(betareg(QMP_REV_ratio ~ rep_org, data = data_h4[-c(decreased_items_index, decreased_items_index),]))

# all (originally)
betareg_output_to_apa_full(betareg(QMP_REV_ratio ~ rep_org, data = data_h4))
```

The effect is in the same direction, but smaller and no longer significant (although this could also be due to reduction in sample size). Overall, their removal had almost no impact on the results.

### H5

```{r H5Difference}
# running the h5 models
apa_print(glm(hypothesis_support ~ QMP_REV_ratio, data = data_h5[decreased_items_index[c(53:55)],], family = binomial))$full_result$QMP_REV_ratio

apa_print(glm(hypothesis_support ~ QMP_REV_ratio, data = data_h5[-decreased_items_index[c(53:55)],], family = binomial))$full_result$QMP_REV_ratio

apa_print(glm(hypothesis_support ~ QMP_REV_ratio, data = data_h5, family = binomial))$full_result$QMP_REV_ratio

```

The association between replication QMP ratio and replicability was stronger for measures whose items were decreased, but difficult to say with so few observations. Furthermore, their removal had negligible impact on the results.

### H6

```{r H6Difference}
# running the h6 models
betareg_output_to_apa_full(betareg(Rep_QMP_REV_ratio ~ QMP_REV_ratio, data = data_h6[decreased_items_index,]))

betareg_output_to_apa_full(betareg(Rep_QMP_REV_ratio ~ QMP_REV_ratio, data = data_h6[-decreased_items_index,]))

betareg_output_to_apa_full(betareg(Rep_QMP_REV_ratio ~ QMP_REV_ratio, data = data_h6))

```

The association between original and replication QMPs was reduced and no longer significant for measures whose items were decreased, but again there are limited observations for which the number of items were decreased. Overall, their removal had limited impact on the results.

### 2024-07-26 Scripts/source_script.R

@@ -258,9 +258,13 @@ Model_H4 <- function(Data){
 data_prep_H5 <- function(Data_Replications){
   # data prep for model (using the (y * (n - 1) + 0.5) / n to adjust for any 0 
   # or 1 proportions in the data).
+  
+  # removing the cases with unclear hypothesis support
   Data_H5 <- Data_Replications[-c(53:55),]
   Data_H5$hypothesis_support <- droplevels(Data_H5$hypothesis_support)
   levels(Data_H5$hypothesis_support) <- c(FALSE, TRUE)
+  
+  # recalculating the QMP ratio
   Data_H5$hypothesis_support <- as.logical(Data_H5$hypothesis_support)
   Data_H5$QMP_ratio <- ((Data_H5$QMP_ratio * (77 - 1) + 0.5) / 77)
   Data_H5$QMP_REV_ratio <- ((Data_H5$QMP_REV_ratio * (77 - 1) + 0.5) / 77)
@@ -273,6 +277,7 @@ data_prep_H5 <- function(Data_Replications){
   
   return(Data_H5)
 }
+
 
 
 # modelling and results returning function
@@ -557,13 +562,9 @@ betareg_output_to_apa_full<- function(betareg_output, coefficient_number = 2){
   p_value <- sum_object[4]
   
   # calculating the confidence intervals
-  if(z_value < 0){
-    CI_HI <- estimate - (1.96 * std_error)
-    CI_LO <- estimate + (1.96 * std_error)
-  } else{
-    CI_LO <- estimate - (1.96 * std_error)
-    CI_HI <- estimate + (1.96 * std_error)
-  }
+  CI_LO <- estimate - (1.96 * std_error)
+  CI_HI <- estimate + (1.96 * std_error)
+  
   
   # formatting the statistics for printing
   estimate_string <- paste0("$b = ", apa_num(estimate), "$, ")
@@ -719,16 +720,9 @@ data_prep_H2 <- function(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean,
                                rep(14, 36), rep(29, 74), rep(30, 74), 
                                rep(31, 74), rep(34, 61), rep(39, 60), 
                                rep(42, 58), rep(51, 21), rep(51, 21), 
-                               rep(56, 20), rep(57, 21), rep(59, 21), 
-                               rep(62, 4), rep(63, 4), rep(71, 8), rep(73, 5))
+                               rep(59, 20), rep(60, 21), rep(61, 21), 
[…]

### 2024-07-26 Scripts/Manuscript/manuscript.Rmd
minor technical corrections

@@
 keywords          : "reliability, validity, measurement, reporting, replicability, credibility, psychology"
-wordcount         : "203"
+wordcount         : "159"
 
@@
 
-This manuscript was created in RStudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [*v`r getNamespaceVersion("worcs")[[1]]`*\; @vanlissaWORCS2021] to ensure reproducibility and transparency.
+This manuscript was created in RStudio [*v`r rstudioapi::versionInfo()$version`*\;@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [*v`r getNamespaceVersion("worcs")[[1]]`*\; @vanlissaWORCS2021] to ensure reproducibility and transparency.
 All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> and <https://osf.io/9r8yt/>.
@@
 [^2]: For 7 measures the number of items were modified from the original article to the replication.
-To check whether or not this had a confounding impact on our results, we re-ran the analyses testing the hypotheses excluding data from these studies.
+To check whether or not this had a confounding impact on our results, we re-ran the analyses testing the hypotheses excluding data from these studies (see [Supplementary Analyses E](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_item_reduced_measures_analyses.Rmd)).
 We found that removing these measures' data had minimal impact on the overall results.
@@
 However, these analyses were omitted, because group sizes were small.
-The results from these analyses are reported in [Supplementary Analyses B](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_multilevel_analyses.Rmd)) for the sake of completeness and transparency.
+The results from these analyses are reported in [Supplementary Analyses B](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_multilevel_analyses.Rmd) for the sake of completeness and transparency.
 
@@
 
-```{r ReorderPlot23Data}
+```{r ReorderPlot23Data, warning = FALSE}
 # data re-ordering (factor order was not saved in export)

### 2024-08-15 Scripts/Manuscript/manuscript.Rmd
minor code and text fixes

@@
 author: 
-  - name          : "Goos, C."
+  - name          : "Goos, Cas"
     affiliation   : "1"
@@
   We investigated the reliability and measurement reporting of 77 measures within 56 Many Labs replications and related original articles [@klein2014investigating; @ebersole2016many; @klein2018many; @ebersole2020many], and their association with replicability.
-  Results from logistic regressions indicated that questionable practices in reporting on measurement (QMPs) in replication studies (b = -5.60, p = .006), but not its reliability (b = 8.21, p =.
-106) was associated with lower replicability.
+  Reliability Generalization Meta-analysis revealed that not all measures were sufficiently reliable across contexts. 
+  We additionally found that reliability and validity evidence was rarely reported. 
+  Furthermore, logistic regression results indicated that "questionable measurement practices" (QMPs) in replication studies were associated with lower replicability (b = -5.60, p = .006), while study reliability was not (b = 8.21, p =.
+106) .
 <!-- the code to retrieve these two results is: paste0("$b = ", H3_test_result_main_alpha$table$estimate[[2]], "$, p = ", H3_test_result_main_alpha$table$p.value[[2]], "$") & paste0("$b = ", H5_test_results_REV$table$estimate[[2]], "$, p = ", H5_test_results_REV$table$p.value[[2]], "$"); these lines will only work after code chunks 1, 2, 12, & 19 have been ran.-->
-  Furthermore, Reliability Generalization Meta-analysis revealed that not all measures were sufficiently reliable across contexts. 
-  We additionally found that reliability and validity evidence was rarely reported. 
-  These findings corroborate existing research that construct validity in published research is low and that may have negative consequences for replications. 
+  These findings corroborate existing research that construct validity in published research is unknown, which may have negative consequences for replications. 
   We offer suggestions on improving measurement practices, and argue that reported measurement information should inform the decision to replicate.
 
-keywords          : "reliability, validity, measurement, reporting, replicability, credibility, psychology"
-wordcount         : "159"
+keywords          : "reliability, construct validity, measurement, reporting, questionable measurement practices, replicability, credibility, psychology"
+wordcount         : "166"
 
@@
 r_refs("r-references.bib")
-
-# manually retrieving the Rstudio version
-rstudioapi::versionInfo()
-
 ```
@@
 
-Measurement reliability varies across samples. Therefore, we investigated what the reliability is in replications of psychological research (RQ1a) and original psychological research (RQ1b).
-
-The Many Labs studies were intended as direct replications.
-In direct replications, any remaining deviations from the original research should be irrelevant for testing the same effect as the original study [@nosek2022replicability].
-As a result, we expected that there would be, no difference present in the reliability between replication research and original psychological research (H1).
+Measurement reliability varies across samples.
+Accounting for the differences between original and replication is crucial for evaluating replications.
+This includes variation in measurement reliability.
+Therefore, we investigated the reliability in replication (Research Question 1a; RQ1a[^1]) and original psychological research (RQ1b).
+The Many Labs studies were intended as direct replications, which implies that any remaining deviations from the original research should be irrelevant for testing the same effect as the original study [@nosek2022replicability].
+Therefore, we expected that there would be, no difference in reliability between replication research and original research (Hypothesis 1; H1).
+
+[^1]: The numbering of the research questions and hypotheses matches the numbering in the preregistration
 
 Reliability has the potential to vary not only between replication and original research, but also across labs assessing the same effect [@vacha-haase1998ReliabilityGeneralizationExploring].
-We thus investigated whether reliability estimates differed between replicating labs (RQ2).
-
-Heterogeneity in reliability may be contributing strongly to the variation in reliability between labs.
-However, for effect sizes there is little empirical evidence of widespread heterogeneity among the Many Labs replications [@klein2018many; @olsson2020heterogeneity].
-We expected that there would be no significant variation in the reliability estimates of replications of the same original study (H2) as well.
-
-To see if reliability is related to replication success, we investigated whether there is an association between successfully replicated study reliability and replication outcome (RQ3).
-
+We empirically investigated this in our sample by investigating whether reliability estimates differed between replicating labs (RQ2).
+For effect sizes there is little empirical evidence of widespread heterogeneity among the Many Labs replications [@klein2018many; @olsson2020heterogeneity].
+We expect that there is no significant variation in the reliability estimates of replications of the same original study (H2) either.
+
+In theory, there should be a positive relation between reliability and replicability.
 Greater reliability means the variance around the estimate of the true effect is decreased [@nunnally1994assessment].
 Assuming that the true effect is not null, then the statistical conclusions tested with reliable measures are more likely to converge to significance.
-THus, we expected to observe a positive association between reliability in replication research and successful replication of an original finding (H3).
+To empirically assess this, we investigated whether there is an association between replication study reliability and replication outcome (RQ3).
+We expected to observe a positive association between reliability in replication research and successful replication of an original finding (H3).
 
@@
 @flake2022construct found that QMPs were overall more common in the RPP replications as compared to the original research.
-We hypothesized that for our Many Labs sample QMPs would be more frequent in original psychological research than in replication research (H4), because of the use of structured protocols documenting the measurement.
-
-QMPs obscure information relevant to mimic measurement from original research in subsequent replication attempts.
+We hypothesized that for our Many Labs sample QMPs would be more frequent in original psychological research than in replication research (H4), because othe Many :abs replications used structured protocols documenting the measurement.
+
+QMPs obscure information about a particular measurement.
+This in turn may cause issues for reconstructing that measurement in subsequent replication attempts.
 The resulting deviations in measurement may be partly responsible for deviations in replication and original effects [@flake2022construct].
-Thus we investigated whether QMPs in replication protocols were associated with the replication outcome (RQ5).
+Therefore, we investigated whether QMPs in replication protocols were associated with the replication outcome (RQ5).
 
@@
 
-QMPs obscure information about a particular measurement.
-This in turn may cause issues for reconstructing that measurement in subsequent replication attempts.
-We investigated the association between QMPs in original research and QMPs in replications of psychological research (RQ6).
-
 @flake2022construct already proposed that QMPs in original articles may cause issues for recreating measurements for replication research.
 @shaw2020measurement already found such a spill-over effect for validity.
-In line with this research we expected the total number of QMPs in original psychological research to be positively related to the total number of QMPs in replication research (H6).
+In line with this research we investigated the association between QMPs in original research and QMPs in replications of psychological research (RQ6).
+We expected the total number of QMPs in original psychological research to be positively related to the total number of QMPs in replication research (H6).
 
@@
 Multiple psychological constructs could be measured per original study or replication.
-We used the the replication protocols to identify these measures.
+We used the replication protocols to identify these measures.
 Acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses were not included.
@@
 However, no coding or analysis of either of them had taken place before the analyses were preregistered.
-Further details on the search strategy can be found in the [coding protocol information file](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) in the supplementary materials.
+Further details on the search strategy can be found in the [coding protocol information file](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) (URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd>) in the supplementary materials.
 
@@
 
-To be included in the planned analyses on calculated reliabilities, the measure had to be a scale consisting of multiple items.
+To be included in the planned analyses on calculated reliabilities (RQ1, RQ2, and RQ3), the measure had to be a scale consisting of multiple items.
 If cleaned data was available this was chosen over raw data, to ensure that variables were coded as intended (e.g.
@@
 The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each set of replications replicating a single original study across multiple labs.
-These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [Data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document).
+These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [Data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd>).
 
@@
 
-We developed and used a coding protocol (the [coding protocol](../../SupplementaryMaterials/CodingProtocols/Measurement_Error_Reporting_Revised_Coding_Protocol.pdf) is available in the supplementary materials) to extract information on the reported measurement evidence and reporting quality for both replication protocols and original studies.
+We developed a [coding protocol](../../SupplementaryMaterials/CodingProtocols/Measurement_Error_Reporting_Revised_Coding_Protocol.pdf) (available in the supplementary materials; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd>) to extract information on the reported measurements for both replication protocols and original studies.
 
@@
 
+# adding replication ratio's to the Nr. Replicated column
+replication_ratio <- apa_num(replication_nr_table$"Nr. Replicated" / replication_nr_table$"Nr. Measures", gt1 = FALSE)
+
+replication_nr_table$"Nr. Replicated"[c(1, 2, 4, 5)] <- paste(replication_nr_table$"Nr. Replicated"[c(1, 2, 4, 5)], paste0("(", replication_ratio[c(1, 2, 4, 5)], ")"))
+
 # adding a superscript for a later footnote
-replication_nr_table$"Nr. Replicated"[3] <- "$3^a$"
+replication_nr_table$"Nr. Replicated"[3] <- paste(paste0(replication_nr_table$"Nr. Replicated"[3], "$^a$"), paste0("(", replication_ratio[3], ")"))
 
@@
 replicated displays the number of measures for which the associated effect was replicated successfully.
+The value between brackets represent the ratio of replications.
 $^a$replication was assessed as unclear for three other measures, since their effect was only partially replicated.
@@
 Each replication was nested within one of four Many Labs projects.
-Furthermore, `r sum(coded_data_replications$appearance != 1)` replications used more than one primary measure, resulting in `r nrow(coded_data_replications)` measures in both `r sum(coded_data_replications$appearance == 1)` replications protocols and `r sum(coded_data_original$appearance == 1)` original articles[^1].
-Of these `r nrow(coded_data_replications)` measures `r sum(coded_data_replications$mod_check == "True")` were modified from the original to the replication[^2].
+Furthermore, `r sum(coded_data_replications$appearance != 1)` replications used more than one primary measure, resulting in `r nrow(coded_data_replications)` measures in both `r sum(coded_data_replications$appearance == 1)` replications protocols and `r sum(coded_data_original$appearance == 1)` original articles[^2].
+Of these `r nrow(coded_data_replications)` measures `r sum(coded_data_replications$mod_check == "True")` were modified from the original to the replication[^3].
 In the replications, the data of responses on the measures was further nested in several labs per replication.
@@
 
-[^1]: Initially the original articles contained 3 more measures than the replication protocols.
+[^2]: Initially the original articles contained 3 more measures than the replication protocols.
 This difference was due to the way that the moral foundations questionnaire was framed in the original articles compared to in the original article.
@@
 
-[^2]: For 7 measures the number of items were modified from the original article to the replication.
+[^3]: For 7 measures the number of items were modified from the original article to the replication.
 To check whether or not this had a confounding impact on our results, we re-ran the analyses testing the hypotheses excluding data from these studies (see [Supplementary Analyses E](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_item_reduced_measures_analyses.Rmd)).
@@
 
-### Hypothesis 1: Reliability Reporting in Original Compared to Replication Research.
+### Hypothesis 1: Reliability Reporting in Original and Replication Research.
 
@@
 
-### Hypotheis 2: Within Study Variation in Reliability.
+### Hypothesis 2: Within Study Variation in Reliability.
 
@@
 
-We used a logistic regression model to test whether replication success as reflected in a significant mean effect in the meta-analysis conducted across the replicating labs could be predicted by the average calculated reliabilities of the measures.
-
 ```{r Hypothesis3MainTest, include = FALSE}
@@
 
+We used a logistic regression model to test whether replication success as reflected in a significant mean effect in the meta-analysis conducted across the replicating labs could be predicted by the average calculated reliabilities of the measures.
 Cronbach's alpha did not significantly predict replication success in the main logistic regression model (`r H3_main_full_results_alpha_with_OR`).
@@
 # first we calculate the odds-ratio
-OR_coefficient_alpha_White_adjusted <- round(exp(H3_coefficient_alpha_White_adjusted), 2)
+OR_coefficient_alpha_White_adjusted <- round(exp(H3_coefficient_alpha_White_adjusted), 1)
 
@@
 # and then convert them to odds ratio CIs
-OR_CI_LOW <- round(exp(log_OR_CI_LOW), 2)
-OR_CI_HI <- round(exp(log_OR_CI_HI), 2)
+OR_CI_LOW <- round(exp(log_OR_CI_LOW), 1)
+OR_CI_HI <- round(exp(log_OR_CI_HI), 1)
 
@@
 We additionally pre-registered a random intercept and random-slope multilevel regression model of the same relationship with each lab's unique reliability nested within the set of replication of an effect.
-However, because our dependent variable (replicability) is at the group level, we decided based on suggestions in the literature [@foster-johnson2018Predicting] to use a test on the aggregate level using White's heteroscedasticity adjustment to address the dependency.
+However, because our dependent variable (replicability) is at the group level, we decided to use a test on the aggregate level using White's heteroscedasticity adjustment to address the dependency [as suggested by @foster-johnson2018Predicting].
 This analysis also showed a non-significant relation (`r H3_test_result_alpha_White_adjusted`).
@@
 
-# recycled H1 test
+# recycled H1 tests
 # A chi square test for difference in N reliability reported for multiple 
@@
 
+# whether there was evidence from a factor analysis 
+factor_present <- c(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)", coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")
+
+# A chi square test for difference in N factor analysis evidence reported for multiple 
+# item measures.
+factor_reporting_test_result <- chisq.test(data_h1$rep_org, factor_present)
+
 ```
@@
 Validity evidence was similarly reported infrequently.
-`r apa_num(sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` original articles reported validity evidence from a factor analysis, while only `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` replications did.
-Furthermore, we conducted pre-registered exploratory analyses testing the unidimensionality of `r nrow(cfa_results)` measures with available replication data using a confirmatory factor analysis.
+Validity evidence from a factor analysis was reported in `r apa_num(sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` original articles, while in only `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` replications.
+This difference was not significant, however the total number of factor analyses reported were few ($\chi^{2}$(`r apa_num(factor_reporting_test_result$parameter)`) = `r apa_num(factor_reporting_test_result$statistic)`, *p* = `r apa_p(factor_reporting_test_result$p.value)`).
+
+To gain a better understanding of the validity of the included measurements, we also conducted pre-registered exploratory analyses testing the unidimensionality of `r nrow(cfa_results)` measures with available replication data using a confirmatory factor analysis.
+We reasoned that most of the included measures should theoretically tap into a single construct, so evidence for unidimensionality would serve as a proxy for evidence of higher construct validity.
 We found that `r sum(cfa_results$Single_factor == "Yes")` of these measures met our criteria for unidimensionality (see [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd) for further details).
@@
 In line with Hypothesis 5, results showed that successful replications were associated with fewer QMPs compared to unsuccessful replications (`r H5_test_results_REV_with_OR`).
-However, we did not find the association with the initial protocol in neither the single-level (`r H5_test_results_with_OR`) nor the multilevel model (`r random_intercept_h5$full_result$QMP`)[^3].
-
-[^3]: As of writing this article the *betareg* package does not allow for estimation of multilevel models.
+However, we did not find the association with the initial protocol in neither the single-level (`r H5_test_results_with_OR`) nor the multilevel model (`r random_intercept_h5$full_result$QMP`)[^4].
+
+[^4]: The *betareg* package currently does not allow for estimation of multilevel models.
 As an approximation, Gaussian random-intercept multilevel models were implemented using the *lmer* function from the *lme4* package [@R-lme4].
@@
 
-We additionally conducted planned exploratory analyses of the association for each unique combination of QMP types, but taking into account the limited sample size, we could not determine any clear relations between types (see [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd) and [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd) for further details on the analyses and results).
+We additionally conducted planned exploratory analyses of the association for each unique combination of QMP types, but taking into account the limited sample size, we could not determine any clear relations between the separate QMP types and replicability (see [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd) and [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd) for further details on the analyses and results).
 
@@
 Firstly, the studies in our sample commonly used single-item measures, an observation that was also made by @shaw2020measurement.
-Calculating reliability for single-item measures is not as straightforward and less common as for multiple item measures [@wanous1996estimating].
+Calculating reliability for single-item measures is less straightforward and common than for multiple item measures [@wanous1996estimating].
 Concerns with the use of single-item measures go beyond reliability, validity may also be at risk.
@@
 These associations together indicate that poor measurement reporting in an original study could be a risk factor for subsequent replication attempts.
-
-However, it is worth noting that these associations were only found for QMPs coded with the revised coding protocol.
+We did observe that unidimensionality was not universal among the measures for which we could run a factor analysis, which assuming that the measures were meant to be unidimensional would indicate that measures may not have assessed their construct as they were intended to.
+
+However, it is worth noting that the spillover effect was only observed for QMPs coded with the revised coding protocol.
 Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd) for results based on the initial protocol).
-Furthermore, these Hypotheses were supported by only one of the multilevel models.
-However, these models were limited in group and sample size making their interpretation precarious.
+Furthermore, these hypotheses were supported by only one of the multilevel models.
+However, these models were limited in group and sample size making their interpretation uncertain.
 
@@
 Our study had several limitations.
-We encountered numerous challenges in operationalizing QMPs.
+We encountered several challenges in operationalizing QMPs.
 Whereas previous research has focused on descriptives of specific QMPs detrimental to construct validity [@flake2022construct; @shaw2020measurement], we combined all coded QMPs together as an operationalization to assess measurement practices and evaluate their impact on replicability.
@@
 This revision was not trivial, as it altered the interpretation of our results.
-This finding reflects the challenges we encountered in operationalizing QMPs in a single index.
-
-Another challenge in constructing a QMP variable was the way to treat practices that were not applicable to a particular measurement.
+This finding reflects the challenges in operationalizing QMPs in a single index.
+
+Another challenge in constructing one overarching QMP variable was the way to treat practices that were not applicable to a particular measurement.
 We chose to construct ratios to cancel out the effects of non-applicable items as much as possible.
@@
 
-A fourth limitation is that we of only used one definition of replication success.
+A fourth limitation is that we used only one definition of replication success.
 Replication success can be estimated and framed in multiple ways [for an example in replication research, see @osc2015estimating], including methods that do not make use of significance testing, or that attenuate for (measurement) error.

### 2024-08-15 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_item_reduced_measures_analyses.Rmd
minor code and text fixes

@@
 knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+```
+
+```{r setup, include = FALSE}
+# loading R libraries
+library(papaja)
+library(worcs)
+library(tidyr)
+library(betareg)
+library(lmerTest)
+library(psych)
+library(sandwich)
+library(lmtest)
+
+# loading source script
+source(file = "../../Scripts/source_script.R")
+
+# Code below loads the processed data. The raw data was prepared for analysis in 'prepare_data.R.
+load_data() 
 ```
@@
 
-```{r OriginalQMPDIfference}
+```{r ReplicationQMPDIfference}
 # comparing the mean and sd replication QMP ratio 

### 2024-08-15 Scripts/source_script.R

@@ -798,15 +798,15 @@ Data_prep_H3_avg <- function(Coded_Data_Replications, Data_H3_multiple){
 OR_to_apa_full_supplier <- function(apa_print_result, negative_b = FALSE, not_significant = FALSE){
   # the odds-ratio
   OR <- round(exp(as.numeric(substr(apa_print_result, start = 6, 
-                                    stop = 9 + negative_b))), 2) 
+                                    stop = 9 + negative_b))), 1) 
   
   # the lower bound 95% confidence interval for the odds-ratio
   ORCILO <- round(exp(as.numeric(substr(apa_print_result, start = 23 + negative_b, 
-                                        stop = 26 + negative_b * 2))), 2) 
+                                        stop = 26 + negative_b * 2))), 1) 
   
   # the upper bound 95% confidence interval for the odds-ratio
   ORCIHI <- round(exp(as.numeric(substr(apa_print_result, start = 29 + negative_b * 2, 
-                                        stop = 33 + negative_b * (2 - not_significant)))), 2)
+                                        stop = 33 + negative_b * (2 - not_significant)))), 1)
   
   # combining the calculated and existing results into a printable string
   result_string_with_OR <- paste0(substr(apa_print_result, start = 0, 

### 2024-08-29 Data/AnalysisData/codebook_data_h23.Rmd
implemented code review suggested changes

--- 2024-02-28 Data/AnalysisData/codebook_data_H3_multiple.Rmd
@@
 ---
-title: "Codebook created on 2024-02-26 at 2024-02-26 14:50:09.116352"
+title: "Codebook created on 2024-08-23 at 2024-08-23 14:40:06.442418"
 output: github_document
@@
 ```{r}
-summaries <- read.csv("codebook_data_h3_multiple.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_h23.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2024-08-29 Data/AnalysisData/codebook_data_h23_avg.Rmd
implemented code review suggested changes

--- 2024-08-29 Data/AnalysisData/codebook_data_h23.Rmd
@@
 ---
-title: "Codebook created on 2024-08-23 at 2024-08-23 14:40:06.442418"
+title: "Codebook created on 2024-08-23 at 2024-08-23 15:29:42.304822"
 output: github_document
@@
 ## Dataset description
-The data contains 670 cases and 10 variables.
+The data contains 19 cases and 13 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_h23.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_h23_avg.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2024-08-29 Data/AnalysisData/codebook_data_h456_original.Rmd
implemented code review suggested changes

--- 2024-08-29 Data/AnalysisData/codebook_data_h23.Rmd
@@
 ---
-title: "Codebook created on 2024-08-23 at 2024-08-23 14:40:06.442418"
+title: "Codebook created on 2024-08-23 at 2024-08-23 14:39:56.135612"
 output: github_document
@@
 ## Dataset description
-The data contains 670 cases and 10 variables.
+The data contains 77 cases and 92 variables.
 
@@
 ```{r}
-summaries <- read.csv("codebook_data_h23.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_h456_original.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2024-08-29 Data/AnalysisData/codebook_data_h456_replications.Rmd
implemented code review suggested changes

--- 2024-08-29 Data/AnalysisData/codebook_data_h456_original.Rmd
@@
 ---
-title: "Codebook created on 2024-08-23 at 2024-08-23 14:39:56.135612"
+title: "Codebook created on 2024-08-23 at 2024-08-23 14:39:58.831191"
 output: github_document
@@
 ```{r}
-summaries <- read.csv("codebook_data_h456_original.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("codebook_data_h456_replications.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2024-08-29 Data/Data_package_description.Rmd
implemented code review suggested changes

@@
 
-### data_H1.csv
+### data_H1.csv DELETE???!!!
 
@@
 
-### data_H2.csv
+### data_H23.csv
 
@@
 
--   **g:** index showing that the alpha values belonged to a particular single measure.
+-   **g:** a short reference to the specific Many Labs replication (and if necessary the particular measure and construct) each alpha was associated with.
 
--   **reporting_index:** same as above, only now the numbers correspond to the row in the coded_data_replication.csv dataset that the indexed measure belongs to.
+-   **reporting_index:** index of the row in the data_h456.csv dataset that the indexed measure belongs to.
 
-### data_H3_avg.csv
+-   **replication_success:** boolean variable indicating whether or not the measure's related effect was successfully replicated or not when looking at the significance of the meta-analytic p-value.
 
-*Explanation*: For each measure, the mean of the variables from data_H2.csv, excluding the g indexing variable.
-Additionally, a boolean indicator that indicated whether or not the original effect was replicated in the many labs replications when looking at the significance of the meta-analytic p-value was also included.
+### data_H23_avg.csv
 
-### data_H3_multiple.csv
+*Explanation*: For each measure, the mean of the variables from data_H23.csv, and the related g variable. Additionally, some data comparing the reported and replicated alpha was added.
 
-*Explanation*: Combination of data_H2.csv and a boolean indicator that indicated whether or not the original effect was replicated in the many labs replications when looking at the significance of the meta-analytic p-value.
+*Variables*:
 
-### data_H4.csv
+-   **coefficient_reported**: If present, the reported alpha reliability coefficient in the original article for the measure in this row.
 
-*Explanation*: Contain all of the data from the coded_data_original_shortened.csv and coded_data_replications.csv except for an empty column that was meant to contain any types of reported psychometric evidence not included in the multiple choice response options, since it caused codebook generation issues.
-The two datasets of which this dataset was composed were bound so that each row contained both the coded data of the original article and the coded data on the same measure as described in the replication protocols.
-Additionally, it contains two variables of the total QMP ratio based on both the initial and revised coded QMPs for each measure with some correction applied to the 0 and 1 total QMP scores as they caused issues for the beta regression model.
+-   **coefficient_difference**: The difference between the reported alpha coefficient and the average coefficient calculated from the replication data (negative values indicate that the reported coefficient is lower than the calculated average)
 
-### data_H5.csv
+-   **siginificance_reported_coefficient**: boolean value indicating whether or not the coeffcient_reported value of a measure is outside the 95% percentile of calculated alpha coefficient score of the same measure.
 
-*Explanation*: Contain all of the data from the coded_data_replications.csv except for two empty columns that were meant to contain any types of reported psychometric evidence and reliability measures respectively not included in the multiple choice response options, since it caused codebook generation issues.
-3 rows were omitted from this analysis due to the fact that the support for the hypothesis was coded as being unclear.
-The support for hypothesis, variable, based on the significance of the meta-analytic p-value, was afterwards recoded from a factor to a boolean variable with True for support and False for no support.
-The many labs version variable was recoded from numeric into a factor.
-Additionally, it contains two variables of the total QMP ratio based on both the initial and revised coded QMPs for each measure with some correction applied to the 0 and 1 total QMP scores as they caused issues for the beta regression model.
-It furthermore contains
+### data_H456_original.csv
 
-### data_H6.csv
+*Explanation*: Contain all of the data from the coded_data_original_shortened.csv and one more variable indicating whether reliability was reported or not.
 
-*Explanation*: Contain all of the data from the coded_data_original_shortened.csv and coded_data_replications.csv.
-The two datasets of which this dataset was composed were bound so that each row contained both the coded data of the original article and the coded data on the same measure as described in the replication protocols.
-Additionally, the QMP ratio for each of the initial and revised QMP categories for both the original and revised codes had some correction applied to the 0 and 1 total QMP scores as they caused issues for the beta regression model.
+*Variables*:
+
+-   **reliability_reported**: boolean variable indicating whether any response other than nothing or "Not Reported" was given to the **reliability_type** variable.
+
+### data_H456_replication.csv
+
+*Explanation*: Contain all of the data from the coded_data_replications.csv and one more variable indicating whether reliability was reported or not.
+
+*Variables*:
+
+-   **reliability_reported**: boolean variable indicating whether any response other than nothing or "Not Reported" was given to the **reliability_type** variable.
 
@@
 
-*Explanation*: Contain all of the data from the data_h3_multiple.csv that had a calculated alpha level larger than 0.
+*Explanation*: Contain all of the data from the data_h23.csv that had a calculated alpha level larger than 0.
 Additionally, it contains a column of alpha scores averaged across many lab locations for each article.
-For each remaining replication, the g indexing variable was changed to reflect the names of the articles were adjusted to look better in the figure this dataset was used for.
-
-### plot_23_data_reported_alpha.csv
-
-*Explanation:* Contains reported alpha reliability coefficients extracted from original articles from which such data was available, and for which data was available from the replications from the Many Labs data to calculate reliabilities for.
-The goal of this data was to be superimposed on top of figure 2 (plot_23_alpha) to compare calculated reliability coefficients with reported reliability coefficients.
-
-*Variables*:
-
--   **title:** The title of the article relating to the particular measure of that row, extracted from coded_data_original_shortened.csv
-
--   **graph_title:** author, year, and optional word indicating the specific measure. Relates directly to the indication of the measures as shown in figure 2 (plot_23_alpha).
-
--   **article_order:** numerical variable giving the index for placing the reliability coefficients in the right row in figure 2 (plot_23_alpha).
-
--   **coefficient_reported:** the value for the reported alpha coefficient for the specific measure as extracted from the original article the measure was reported in.
-
--   **coefficient_calculated:** the mean value of the calculated alpha coefficients for the specific measure in the row.
-
--   **coefficient_difference:** The difference between coefficient_reported and coefficient_calculated.
-
--   **significance:** boolean value indicating whether or not the coeffcient_reported value of a measure is outside the 95% percentile of calculated alpha coefficient score of the same measure.
+Finally, the replication_success was changed to a boolean variable, returning TRUE in case it was coded as "Yes", and as FALSE otherwise.
 
@@
 Additionally, it contains a column of omega scores averaged across many lab locations for each article.
-The g indexing variable was changed to reflect the names of the articles were adjusted to look better in the figure this dataset was used for.
+Finally, the replication_success was changed to a boolean variable, returning TRUE in case it was coded as "Yes", and as FALSE otherwise.
 
@@
 The rows are ordered to have the original studies first and then the replications, then they are ordered based on QMP type from Definition to Operationalization to Selection to Quantification to Modification to Total.
-Within each type the QMPs are ordering matches the order of the studies/articles as in the coded_data_replications.csv and coded_data_original_shortened.csv.
+Within each type the QMPs are ordering matches the order of the studies/articles as in the data_h456_replications.csv and data_h456_original.csv.
 
@@
 The QMP_Rep_type column indicates the specific QMP type the QMP_Rep_ratio column belongs to.
-The rows are ordered so that within each QMP type it matches the order of the studies/articles as in the coded_data_replications.csv and coded_data_original_shortened.csv.
+The rows are ordered so that within each QMP type it matches the order of the studies/articles as in the data_h456_replications.csv and data_h456_original.csv.
 

### 2024-08-29 Scripts/Manuscript/manuscript.Rmd
implemented code review suggested changes

@@
 ### Measurement Reporting
+
 This study aims to conceptually replicate the findings on measurement reporting of @flake2022construct.
@@
 
-This manuscript was created in RStudio [*v`r rstudioapi::versionInfo()$version`*\;@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [*v`r getNamespaceVersion("worcs")[[1]]`*\; @vanlissaWORCS2021] to ensure reproducibility and transparency.
+This manuscript was created in RStudio [*v`r rstudioapi::versionInfo()$version`*\; @R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [*v`r getNamespaceVersion("worcs")[[1]]`*\; @vanlissaWORCS2021] to ensure reproducibility and transparency.
 All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> and <https://osf.io/9r8yt/>.
@@
 Pilot data were omitted from the analyses.
-These criteria resulted in suitable item score data from `r apa_num(nrow(data_h3_avg))` replication sets spread across on average approximately `r apa_num(mean(table(data_h3_multiple$g)), digits = 0)` lab locations for the analyses of Hypotheses 2 & 3.
+These criteria resulted in suitable item score data from `r apa_num(nrow(data_h23_avg))` replication sets spread across on average approximately `r apa_num(mean(table(data_h23$g)), digits = 0)` lab locations for the analyses of Hypotheses 2 & 3.
 
 ```{r CleaningReplicationDatasetsData, include = FALSE, eval = FALSE}
-##### Data already available, code does not need to be run!
-### ML 1
+##### This code can be used to rerun the data preparation to convert the raw 
+##### (input) data of the Many Labs replications into intermediate data.
+##### However, because the intermediate data is also available in this project,
+##### the manuscript can also be reproduced without running this code block.
+
+### Below we extract the relevant data from the Many Labs' datasets. The first
+### number in each dataset refers to the Many Labs project it is related to.
+### The second number to which study the data is from in order of appearance in
+### the Many Labs pre-registered protocols, or in the case of Many Labs 5, 
+### within the OSF folder structure. If there is a third number, the study had 
+### multiple relevant measures this refers to the order of appearance of the 
+### measure where the data is from within the study's description in the Many 
+### Labs protocol or OSF folder structure. A fourth number indicates which part
+### of the data of this measure was taken, in case the measure assessed multiple
+### constructs, as these were treated separately for some analyses.
+
+## ML 1
 # 1.3
@@
 
-### ML 2
+## ML 2
 # 2.2
@@
 
-### ML 3
+## ML 3
 # 3.2.1
@@
 
-### ML 5
+## ML 5
 # 5.1.1
@@
 
-### to summarize
-# total number of likely usable: 15 (1.10, 1.11, 1.12.3.1, 1.12.3.2, 2.10.1, 
-# 2.12.1, 2.12.2, 2.12.3, 2.15, 2.23, 3.7.1, 3.7.2, 3.8.2, 5.7, 5.9.1)
-# total number of maybe usable: 6 (1.3, 2.20, 3.2.1.1, 3.2.1.2, 5.1.1, 5.4)
-# total alpha coefficient comparison usable: 3 
-#                                           1.11: 0.82
-#                                           3.7.2: 0.67
-#                                           5.9.1: 0.84
-
 ### Saving to Intermediate Data Folder
@@
 ```{r CleaningCodedData, include = FALSE, eval = FALSE}
-##### Data already available, code does not need to be run!
+##### This code can be used to rerun the data preparation to convert the raw 
+##### (input) data of the coded data into intermediate data. However, because 
+##### the intermediate data is also available in this project, the manuscript  
+##### can also be reproduced without running this code block.
 # Selecting the relevant rows and columns for the data
@@
 ```{r FinalPreparationData, include = FALSE, eval = FALSE}
-##### Data already available, code does not need to be run
+##### This code can be used to rerun the data preparation to convert the 
+##### intermediate data into the analysis data. However, because the analysis
+##### data is also available in this project, the manuscript can also be 
+##### reproduced without running this code block.
 ### this code prepares the various pieces of data to be ready to use for the 
@@
 ## confirmatory analyses
-# for hypothesis 4
-data_h4 <- data_prep_H4(coded_data_original_shortened, coded_data_replications)
-# for hypothesis 5
-data_h5 <- data_prep_H5(coded_data_replications)
-# for hypothesis 6
-data_h6 <- data_prep_H6(coded_data_original_shortened, coded_data_replications)
-
-# for hypothesis 1
-data_h1 <- data_prep_H1(coded_data_original_shortened, coded_data_replications)
-# for hypothesis 2
-data_h2 <- data_prep_H2(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, data_1.12.3.2_clean, data_2.12.1_clean, data_2.12.2_clean, data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.1_clean, data_3.7.2_clean, data_3.8.2_clean, data_5.1.1_clean, data_5.1.2_clean, data_5.7_clean, data_5.9.1_clean)
-# for hypothesis 3
-data_h3_multiple <- Data_prep_H3_multiple(coded_data_replications, data_h2)
-data_h3_avg <- Data_prep_H3_avg(coded_data_replications, data_h3_multiple)
+# for hypotheses 4, 5, & 6
+data_h456_original <- data_prep_h456(coded_data_original_shortened)
+data_h456_replications <- data_prep_h456(coded_data_replications)
+
+# for hypotheses 2 and 3
+data_h23 <- data_prep_H23(list(data_1.10_clean, data_1.11_clean, 
+    data_1.12.3.1_clean, data_1.12.3.2_clean, data_2.12.1_clean, 
+    data_2.12.2_clean, data_2.12.3_clean, data_2.15_clean, data_2.20_clean, 
+    data_2.23_clean, data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.1_clean,
+    data_3.7.2_clean, data_3.8.2_clean, data_5.1.1_clean, data_5.1.2_clean, 
+    data_5.7_clean, data_5.9.1_clean), coded_data_replications)
+
+# the averaged across studies version with added information on reported alpha
+data_h23_avg <- Data_prep_H23_avg(data_h23, data_h456_original)
 
@@
 # plot accompanying the results for Hypotheses 4, 5, & 6.
-plot_456_data <- data_prep_plot_456(data_h6)
+plot_456_data <- data_prep_plot_456(data_h456_original, data_h456_replications)
 # plot accompanying the results for Hypotheses 4, & 6
-plot_46_data <- data_prep_plot_46(data_h6[c(3, 6, 9, 12, 15, 18, 36, 39, 42, 45, 48, 51)])
-plot_46_data_rev <- data_prep_plot_46(data_h6[c(3, 21, 24, 27, 30, 33, 36, 54, 57, 60, 63, 66)])
+plot_46_data <- data_prep_plot_46(data_h456_original[c("def_ratio", "op_ratio", "sel_ratio", "quant_ratio", "mod_ratio", "QMP_ratio")], data_h456_replications[c("def_ratio", "op_ratio", "sel_ratio", "quant_ratio", "mod_ratio", "QMP_ratio")])
+plot_46_data_rev <- data_prep_plot_46(data_h456_original[c("def_ratio", "op_REV_ratio", "sel_REV_ratio", "quant_REV_ratio", "mod_REV_ratio", "QMP_REV_ratio")], data_h456_replications[c("def_ratio", "op_REV_ratio", "sel_REV_ratio", "quant_REV_ratio", "mod_REV_ratio", "QMP_REV_ratio")])
+
 # plot accompanying the results for Hypotheses 2, & 3
-plot_23_data_alpha <- data_prep_plot_23_alpha(data_h3_multiple)
-plot_23_data_omega <- data_prep_plot_23_omega(data_h3_multiple)
-plot_23_data_reported_alpha <- data_prep_plot_23_alpha_reported(coded_data_original_shortened, data_h3_avg, data_h3_multiple)
+plot_23_data_alpha <- data_prep_plot_23_alpha(data_h23)
+plot_23_data_omega <- data_prep_plot_23_omega(data_h23)
 
@@
 # the open data
-open_data(data = data_h4, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_h4))), ".csv"),
+open_data(data = data_h456_original, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_h456_original))), ".csv"),
   codebook = paste0(paste0(
     "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_h4))), ".Rmd"),
+    deparse(substitute(data_h456_original))), ".Rmd"),
   value_labels = paste0(paste0(
     "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_h4))), ".yml"))
-
-open_data(data = data_h6, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_h6))), ".csv"),
+    deparse(substitute(data_h456_original))), ".yml"))
+
+open_data(data = data_h456_replications, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_h456_replications))), ".csv"),
   codebook = paste0(paste0(
     "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_h6))), ".Rmd"),
+    deparse(substitute(data_h456_replications))), ".Rmd"),
   value_labels = paste0(paste0(
     "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_h6))), ".yml"))
-
-open_data(data = data_h5, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_h5))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_h5))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_h5))), ".yml"))
-
-open_data(data = data_h1, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_h1))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_h1))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_h1))), ".yml"))
+    deparse(substitute(data_h456_replications))), ".yml"))
 
@@
 
-open_data(data = data_h2, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_h2))), ".csv"),
+open_data(data = data_h23, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_h23))), ".csv"),
   codebook = paste0(paste0(
     "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_h2))), ".Rmd"),
+    deparse(substitute(data_h23))), ".Rmd"),
   value_labels = paste0(paste0(
     "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_h2))), ".yml"))
-
-open_data(data = data_h3_multiple, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_h3_multiple))), ".csv"),
+    deparse(substitute(data_h23))), ".yml"))
+
+open_data(data = data_h23_avg, filename = paste0(paste0(
+  "Data/AnalysisData/", deparse(substitute(data_h23_avg))), ".csv"),
   codebook = paste0(paste0(
     "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_h3_multiple))), ".Rmd"),
+    deparse(substitute(data_h23_avg))), ".Rmd"),
   value_labels = paste0(paste0(
     "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_h3_multiple))), ".yml"))
-
-open_data(data = data_h3_avg, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_h3_avg))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_h3_avg))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_h3_avg))), ".yml"))
+    deparse(substitute(data_h23_avg))), ".yml"))
 
@@
 
-open_data(data = plot_23_data_reported_alpha, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(plot_23_data_reported_alpha))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(plot_23_data_reported_alpha))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(plot_23_data_reported_alpha))), ".yml")) 
 ```
@@
 replication_nr_table <- data.frame("Many Labs Version" = c("1", "2", "3", "5", "Total"),
-                                      "N Total" = c(table(coded_data_replications$many_labs_version), nrow(coded_data_replications)), 
-                                      "N Replicated" = c(table(coded_data_replications$many_labs_version, coded_data_replications$hypothesis_support)[, "Yes"], table(coded_data_replications$hypothesis_support)["Yes"]))
+                                      "N Total" = c(table(data_h456_replications$many_labs_version), nrow(data_h456_replications)), 
+                                      "N Replicated" = c(table(data_h456_replications$many_labs_version, data_h456_replications$hypothesis_support)[, "Yes"], table(data_h456_replications$hypothesis_support)["Yes"]))
 
@@
 Each replication was nested within one of four Many Labs projects.
-Furthermore, `r sum(coded_data_replications$appearance != 1)` replications used more than one primary measure, resulting in `r nrow(coded_data_replications)` measures in both `r sum(coded_data_replications$appearance == 1)` replications protocols and `r sum(coded_data_original$appearance == 1)` original articles[^2].
-Of these `r nrow(coded_data_replications)` measures `r sum(coded_data_replications$mod_check == "True")` were modified from the original to the replication[^3].
+Furthermore, `r sum(data_h456_replications$appearance != 1)` replications used more than one primary measure, resulting in `r nrow(data_h456_replications)` measures in both `r sum(data_h456_replications$appearance == 1)` replications protocols and `r sum(coded_data_original$appearance == 1)` original articles[^2].
+Of these `r nrow(data_h456_replications)` measures `r sum(data_h456_replications$mod_check == "True")` were modified from the original to the replication[^3].
 In the replications, the data of responses on the measures was further nested in several labs per replication.
-The combined sample size of all labs in the replications was on average `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N), 0)` which was approximately `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N) / mean(coded_data_original_shortened[coded_data_original_shortened$appearance == 1 & !is.na(coded_data_original_shortened$N),]$N), 0)` times larger than the average in original studies, which were conducted in single labs.
+The combined sample size of all labs in the replications was on average `r round(mean(data_h456_replications[data_h456_replications$appearance == 1]$N), 0)` which was approximately `r round(mean(data_h456_replications[data_h456_replications$appearance == 1]$N) / mean(data_h456_original[data_h456_original$appearance == 1 & !is.na(data_h456_original$N),]$N), 0)` times larger than the average in original studies, which were conducted in single labs.
 
@@
 
-The average calculated Cronbach's alpha coefficient across replication sets was `r apa_num(mean(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$alpha, na.rm = TRUE), digits = 3)`.
+The average calculated Cronbach's alpha coefficient across replication sets was `r apa_num(mean(data_h23$alpha), digits = 3)` with a standard deviation of `r apa_num(sd(data_h23$alpha, na.rm = TRUE), digits = 3)`.
 Figure \@ref(fig:Plot23AlphaCode) displays the distributions of the calculated Cronbach’s Alpha scores from each lab for each measure, separated by successful and unsuccessful replication.
@@
 # data re-ordering (factor order was not saved in export)
-plot_23_data_alpha_reordered <- data_prep_plot_23_alpha(plot_23_data_alpha)
+plot_23_data_alpha_reordered <- plot_23_data_alpha
+plot_23_data_alpha_reordered$g <- fct_inorder(as.factor(plot_23_data_alpha$g), ordered = NA)
+
+data_h23_avg$graph_index <- NA
+# adding an index to which row in the plot data the row in data_h23_avg belongs to
+for (i in 1:nrow(data_h23_avg)){
+  data_h23_avg$graph_index[which(unique(plot_23_data_alpha_reordered$g)[i] == data_h23_avg$g)] <- i
+}
 ```
@@
 
-### use ggarange for aranging things at the side of this graph
-
 # plot for alpha
@@
   # adding in the alpha annotations
-   annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[1], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[1], "bold", "plain"))), ymin = 1, ymax = 1, xmin = 1.24, xmax = 1.24) +
-  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[2], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[2], "bold", "plain"))), ymin = 2, ymax = 2, xmin = 1.24, xmax = 1.24) +
-  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[3], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[3], "bold", "plain"))), ymin = 3, ymax = 3, xmin = 1.24, xmax = 1.24) +
-  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[4], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[4], "bold", "plain"))), ymin = 5, ymax = 5, xmin = 1.24, xmax = 1.24) +
-  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[5], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[5], "bold", "plain"))), ymin = 8, ymax = 8, xmin = 1.25, xmax = 1.25) +
-  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[6], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[6], "bold", "plain"))), ymin = 9, ymax = 9, xmin = 1.24, xmax = 1.24) +
-  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[7], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[7], "bold", "plain"))), ymin = 10, ymax = 10, xmin = 1.24, xmax = 1.24) +
-  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[8], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[8], "bold", "plain"))), ymin = 11, ymax = 11, xmin = 1.24, xmax = 1.24) +
-  annotation_custom(grob = textGrob(label = format(round(plot_23_data_reported_alpha$coefficient_difference[9], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(plot_23_data_reported_alpha$significance[9], "bold", "plain"))), ymin = 12, ymax = 12, xmin = 1.25, xmax = 1.25) +
+  annotation_custom(grob = textGrob(label = format(round(data_h23_avg$coeficient_difference[1], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(data_h23_avg$significance_reported_coefficient[1], "bold", "plain"))), ymin = data_h23_avg$graph_index[1], ymax = data_h23_avg$graph_index[1], xmin = 1.24, xmax = 1.24) +
+
+  annotation_custom(grob = textGrob(label = format(round(data_h23_avg$coeficient_difference[2], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(data_h23_avg$significance_reported_coefficient[2], "bold", "plain"))), ymin = data_h23_avg$graph_index[2], ymax = data_h23_avg$graph_index[2], xmin = 1.24, xmax = 1.24) +
+
+  annotation_custom(grob = textGrob(label = format(round(data_h23_avg$coeficient_difference[3], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(data_h23_avg$significance_reported_coefficient[3], "bold", "plain"))), ymin = data_h23_avg$graph_index[3], ymax = data_h23_avg$graph_index[3], xmin = 1.24, xmax = 1.24) +
+
+  annotation_custom(grob = textGrob(label = format(round(data_h23_avg$coeficient_difference[4], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(data_h23_avg$significance_reported_coefficient[4], "bold", "plain"))), ymin = data_h23_avg$graph_index[4], ymax = data_h23_avg$graph_index[4], xmin = 1.24, xmax = 1.24) +
+
+  annotation_custom(grob = textGrob(label = format(round(data_h23_avg$coeficient_difference[5], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(data_h23_avg$significance_reported_coefficient[5], "bold", "plain"))), ymin = data_h23_avg$graph_index[5], ymax = data_h23_avg$graph_index[5], xmin = 1.24, xmax = 1.24) +
+
+  annotation_custom(grob = textGrob(label = format(round(data_h23_avg$coeficient_difference[6], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(data_h23_avg$significance_reported_coefficient[6], "bold", "plain"))), ymin = data_h23_avg$graph_index[6], ymax = data_h23_avg$graph_index[6], xmin = 1.24, xmax = 1.24) +
+
+  annotation_custom(grob = textGrob(label = format(round(data_h23_avg$coeficient_difference[7], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(data_h23_avg$significance_reported_coefficient[7], "bold", "plain"))), ymin = data_h23_avg$graph_index[7], ymax = data_h23_avg$graph_index[7], xmin = 1.24, xmax = 1.24) +
+
+  annotation_custom(grob = textGrob(label = format(round(data_h23_avg$coeficient_difference[8], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(data_h23_avg$significance_reported_coefficient[8], "bold", "plain"))), ymin = data_h23_avg$graph_index[8], ymax = data_h23_avg$graph_index[8], xmin = 1.24, xmax = 1.24) +
+
+  annotation_custom(grob = textGrob(label = format(round(data_h23_avg$coeficient_difference[18], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(data_h23_avg$significance_reported_coefficient[18], "bold", "plain"))), ymin = data_h23_avg$graph_index[18], ymax = data_h23_avg$graph_index[18], xmin = 1.24, xmax = 1.24) +
 
@@
   # adding the blue triangles for reported reliability and green prediction intervals
-  geom_point(data = plot_23_data_reported_alpha, mapping = aes(x = coefficient_reported, y = article_order), color = "blue", shape = 17, size = 3) +
+  geom_point(data = data_h23_avg, mapping = aes(x = coefficient_reported, y = graph_index), color = "blue", shape = 17, size = 3) +
   geom_point(mapping = aes(x = pi.lb), color = "green", shape = 124, size = 2.5) + 
@@
 ```{r ReportedReliabiltiesRetrieval}
-N_reported_reliabilities_original <- sum(coded_data_original_shortened$reliability_type != "Not Reported" & coded_data_original_shortened$reliability_type != "")
-
-N_reported_reliabilities_replications <- apa_num(sum(coded_data_replications$reliability_type != "Not Reported" & coded_data_replications$reliability_type != ""), numerals = FALSE)
-
-N_reported_reliabilities_replications_number_style <- apa_num(sum(coded_data_replications$reliability_type != "Not Reported" & coded_data_replications$reliability_type != ""))
+N_reported_reliabilities_original <- sum(data_h456_original$reliability_type != "Not Reported" & data_h456_original$reliability_type != "")
+
+N_reported_reliabilities_replications <- apa_num(sum(data_h456_replications$reliability_type != "Not Reported" & data_h456_replications$reliability_type != ""), numerals = FALSE)
+
+N_reported_reliabilities_replications_number_style <- apa_num(sum(data_h456_replications$reliability_type != "Not Reported" & data_h456_replications$reliability_type != ""))
 ```
@@
 Figure \@ref(fig:Plot23AlphaCode) displays the tau estimates, which indicates the differences in true reliability scores between labs for a given measure.
-For `r sum(data_h3_avg$QEp > .05)` measures the tau estimate was not significantly different from 0, while for `r apa_num(sum(data_h3_avg$QEp < .05), numerals = FALSE)` measures, the true variation in reliability across labs was significant.
+For `r sum(data_h23_avg$QEp > .05)` measures the tau estimate was not significantly different from 0, while for `r apa_num(sum(data_h23_avg$QEp < .05), numerals = FALSE)` measures, the true variation in reliability across labs was significant.
 The true reliability was quite variable for some measures.
-For instance, the estimate of the standard deviation of the true reliability of the top measure in the graph (a measure of conscientiousness from @gosling2003very used in the replication of @defruyt2000cloninger) equaled `r apa_num(plot_23_data_alpha_reordered[plot_23_data_alpha_reordered$g == "Albarracín et al.
-(2008), exp 5 math", "tau"][1], digits = 3, gt1 = FALSE)` points of Cronbach’s Alpha.
+For instance, the estimate of the standard deviation of the true reliability of the top measure in the graph (a measure of conscientiousness from @gosling2003very used in the replication of @defruyt2000cloninger) equaled `r apa_num(plot_23_data_alpha_reordered[plot_23_data_alpha_reordered$g == "De Fruyt et al.
+(2000)", "tau"][1], digits = 3, gt1 = FALSE)` points of Cronbach’s Alpha.
 
 Thus for around a quarter of measures, the reliability was heterogeneous.
-Although for the remaining measures, we found no significant heterogeneity in reliabilities, we note that power to detect small heterogeneity is often low (@ioannidis2007uncertainty; @olsson2020heterogeneity).
+Although for the remaining measures, we found no significant heterogeneity in reliabilities, we note that power to detect small heterogeneity is often low [@ioannidis2007uncertainty; @olsson2020heterogeneity].
 
@@
 ## The main model to test hypothesis 3, through a logistic regression model.
-H3_test_main_alpha <- glm(formula = replication ~ 1 + alpha, 
-                                 family = binomial(), data = data_h3_avg)
+H3_test_main_alpha <- glm(formula = replication_success ~ 1 + alpha, 
+                                 family = binomial(), data = data_h23_avg)
 
@@
 # well this OR is quite a ridiculous number..., but then again a step from 0 alpha to 1 is quite a jump too...
+
+### rerunning the analyses but now with a standardized alpha value
+# transforming the alpha variable 
+scaled_alpha <- scale(data_h23_avg$alpha)
+scaled_alpha
+
+# rerunning the model with the transformed alpha variable Nr.2
+H3_test_interpretable_alpha <- glm(formula = data_h23_avg$replication_success ~ 1 + scaled_alpha, family = binomial())
+
+H3_test_result_interpretable_alpha <- apa_print(H3_test_interpretable_alpha)
+
+H3_interpretable_full_results_alpha_with_OR <- OR_to_apa_full_supplier(H3_test_result_interpretable_alpha$full_result$scaled_alpha, negative_b = FALSE, not_significant = TRUE) # with this method the result is contained to more sensible numbers.
+However, we opt to report the unstandardized numbers without Odds-ratio, to more transparently reflect the instability in our estimate due to alpha's boundedness, the small sample, and limited observed variation in alpha.
 ```
@@
 We used a logistic regression model to test whether replication success as reflected in a significant mean effect in the meta-analysis conducted across the replicating labs could be predicted by the average calculated reliabilities of the measures.
-Cronbach's alpha did not significantly predict replication success in the main logistic regression model (`r H3_main_full_results_alpha_with_OR`).
+Cronbach's alpha did not significantly predict replication success in the main logistic regression model (`r H3_test_result_main_alpha$full_result$alpha`)[^4].
 Results based on the Omega coefficient lead to a similar conclusion (see [Supplementary Analyses C](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_omega_analyses.Rmd)).
+
+[^4]: We omitted the Odds ratio and Odds ratio confidence intervals from this result.
+Because alpha is bounded between 0 and 1, and we furthermore observed in most alpha values little variation from the mean of `r mean(data_h23_avg$alpha)`, a change from alpha by 1 point had an extremely large coefficient.
+Combined with the large uncertainty in our estimates due to the small sample, meant that the odds ratio confidence interval contained extremely large numbers (OR CI95 upper bound: `r substr(H3_main_full_results_alpha_with_OR, start = 40, stop = 52)`)
 
@@
 
+## we then convert it to apa_num format
+# first we calculate the log-odds ratio CIs
+log_OR_CI_LOW <- H3_coefficient_alpha_White_adjusted - (1.96 * H3_test_alpha_White_adjusted[2,2])
+log_OR_CI_HI <- H3_coefficient_alpha_White_adjusted + (1.96 * H3_test_alpha_White_adjusted[2,2])
+
+# then we create the string to print in text
+H3_test_result_alpha_White_adjusted <- paste0("$\\hat{\\beta} = ", round(H3_test_alpha_White_adjusted[2,1], 2), "$, 95\\% CI $[", round(log_OR_CI_LOW, 1), ", ", round(log_OR_CI_HI, 1), "]$, $z = ", round(H3_test_alpha_White_adjusted[2,3], 2), "$, $p = ", apa_p(H3_test_alpha_White_adjusted[2,4]), "$")
+
+### This version contains the Odds-ratio
 # first we calculate the odds-ratio
 OR_coefficient_alpha_White_adjusted <- round(exp(H3_coefficient_alpha_White_adjusted), 1)
-
-# then we also calculate the log-odds ratio CIs
-log_OR_CI_LOW <- H3_coefficient_alpha_White_adjusted - (1.96 * H3_test_alpha_White_adjusted[2,2])
-log_OR_CI_HI <- H3_coefficient_alpha_White_adjusted + (1.96 * H3_test_alpha_White_adjusted[2,2])
 
@@
 # now we create the string to print in text
-H3_test_result_alpha_White_adjusted <- paste0("$\\hat{\\beta} = ", round(H3_test_alpha_White_adjusted[2,1], 2), "$, $OR = ", OR_coefficient_alpha_White_adjusted, "$, 95\\% CI $[", OR_CI_LOW, ", ", OR_CI_HI, "]$, $z = ", round(H3_test_alpha_White_adjusted[2,3], 2), "$, $p = ", apa_p(H3_test_alpha_White_adjusted[2,4]), "$")
+H3_OR_test_result_alpha_White_adjusted <- paste0("$\\hat{\\beta} = ", round(H3_test_alpha_White_adjusted[2,1], 2), "$, $OR = ", OR_coefficient_alpha_White_adjusted, "$, 95\\% CI $[", OR_CI_LOW, ", ", OR_CI_HI, "]$, $z = ", round(H3_test_alpha_White_adjusted[2,3], 2), "$, $p = ", apa_p(H3_test_alpha_White_adjusted[2,4]), "$") # again, however, we omit this version from the main text for the same reasons as given in the code block above.
 
@@
 This analysis also showed a non-significant relation (`r H3_test_result_alpha_White_adjusted`).
-However, it should be noted that for these analyses the reliability coefficient could be calculated for only `r nrow(data_h3_avg)` measures.
+However, it should be noted that for these analyses the reliability coefficient could be calculated for only `r nrow(data_h23_avg)` measures.
 As a result, the estimates of the relation between reliability and replication success obtained using these models each come with large uncertainty.
@@
 Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts the flow of measures in relation to reliability reporting.
-First, it shows that almost half of the measures in both replication (n = `r apa_num(sum(coded_data_replications$N_items == "1 item measure"))`) and original research (n = `r apa_num(sum(coded_data_original_shortened$N_items == "1 item measure"))`) were single-item measures.
+First, it shows that almost half of the measures in both replication (n = `r apa_num(sum(data_h456_replications$N_items == "1 item measure"))`) and original research (n = `r apa_num(sum(data_h456_original$N_items == "1 item measure"))`) were single-item measures.
 When looking at the multiple item measures, the graph illustrates that `r N_reported_reliabilities_replications` measures in the replication protocols and `r N_reported_reliabilities_original` in the original articles reported a reliability coefficient.
-The most commonly reported reliability coefficient was Cronbach's Alpha, which accounted for `r apa_num(sum(coded_data_replications$reliability_type == "alpha"), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(coded_data_original_shortened$reliability_type == "alpha"))` in the original articles.
+The most commonly reported reliability coefficient was Cronbach's Alpha, which accounted for `r apa_num(sum(data_h456_replications$reliability_type == "alpha"), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(data_h456_original$reliability_type == "alpha"))` in the original articles.
 
@@
 
-```{r Hypothesis1RecycledModel, include = FALSE}
-# first some descriptives of reliability reporting
+```{r ReportingInformation, include = FALSE}
+## first some descriptives of reliability reporting
+# we get these descriptives from the combination of both replication and original
+# QMP data.
+reporting_data <- rbind(data_h456_original, data_h456_replications)
+
 # Measurement type per original and replication:
-reliability_reporting_descriptive_table_1 <- table(data_h1$rep_org, data_h1$N_items)
+reliability_reporting_descriptive_table_1 <- table(reporting_data$rep_org, reporting_data$N_items)
 
@@
 # (given that measure is a multiple item measure):
-reliability_reporting_descriptive_table_2 <- table(data_h1$rep_org[data_h1$N_items == "multiple item measure"], data_h1$reliability_type[data_h1$N_items == "multiple item measure"])
-
-# recycled H1 tests
+reliability_reporting_descriptive_table_2 <- table(reporting_data$rep_org[reporting_data$N_items == "multiple item measure"], reporting_data$reliability_type[reporting_data$N_items == "multiple item measure"])
+
 # A chi square test for difference in N reliability reported for multiple 
 # item measures.
-reliability_reporting_test_result <- chisq.test(data_h1$rep_org[data_h1$N_items == "multiple item measure"], data_h1$reliability_reported[data_h1$N_items == "multiple item measure"])
-
-# whether there was evidence from a factor analysis 
-factor_present <- c(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)", coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")
+reliability_reporting_test_result <- chisq.test(reporting_data$rep_org[reporting_data$N_items == "multiple item measure"], reporting_data$reliability_reported[reporting_data$N_items == "multiple item measure"])
+
+# a variable indicating whether there was evidence from a factor analysis 
+factor_present <- c(reporting_data$sel_psychometric_evidence_REV != "None" & reporting_data$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")
 
@@
 # item measures.
-factor_reporting_test_result <- chisq.test(data_h1$rep_org, factor_present)
+factor_reporting_test_result <- chisq.test(reporting_data$rep_org, factor_present)
 
@@
 Validity evidence was similarly reported infrequently.
-Validity evidence from a factor analysis was reported in `r apa_num(sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` original articles, while in only `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` replications.
+Validity evidence from a factor analysis was reported in `r apa_num(sum(data_h456_original$sel_psychometric_evidence_REV != "None" & data_h456_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` original articles, while in only `r apa_num(sum(data_h456_replications$sel_psychometric_evidence_REV != "None" & data_h456_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` replications.
 This difference was not significant, however the total number of factor analyses reported were few ($\chi^{2}$(`r apa_num(factor_reporting_test_result$parameter)`) = `r apa_num(factor_reporting_test_result$statistic)`, *p* = `r apa_p(factor_reporting_test_result$p.value)`).
@@
 ```{r numberNAsForQMPRatio}
-ratio_of_NAs <- sum(is.na(data_h4$def1) + is.na(data_h4$op_1_REV) + is.na(data_h4$op_2_REV) + is.na(data_h4$op_3) + is.na(data_h4$op_4) + is.na(data_h4$op_5_REV) + is.na(data_h4$sel_1_REV) + is.na(data_h4$sel_1) + is.na(data_h4$sel_2) + is.na(data_h4$sel_3_REV) + is.na(data_h4$sel_4) + is.na(data_h4$quant_1_REV) + is.na(data_h4$quant_2_REV) + is.na(data_h4$quant_3_REV) + is.na(data_h4$quant_4) + is.na(data_h4$mod_1_REV) + is.na(data_h4$mod_2_REV) + is.na(data_h4$mod_3_REV) + is.na(data_h4$mod_4_REV) + is.na(data_h4$mod_5_REV) + is.na(data_h4$mod_6_REV)) / (20 * 154)
+# calculating the ratio of NA responses for the revised QMP items, or the initial
+# items in case those items were not revised.
+ratio_of_NAs <- sum(is.na(reporting_data$def1) + is.na(reporting_data$op_1_REV) + is.na(reporting_data$op_2_REV) + is.na(reporting_data$op_3) + is.na(reporting_data$op_4) + is.na(reporting_data$op_5_REV) + is.na(reporting_data$sel_1_REV) + is.na(reporting_data$sel_1) + is.na(reporting_data$sel_2) + is.na(reporting_data$sel_3_REV) + is.na(reporting_data$sel_4) + is.na(reporting_data$quant_1_REV) + is.na(reporting_data$quant_2_REV) + is.na(reporting_data$quant_3_REV) + is.na(reporting_data$quant_4) + is.na(reporting_data$mod_1_REV) + is.na(reporting_data$mod_2_REV) + is.na(reporting_data$mod_3_REV) + is.na(reporting_data$mod_4_REV) + is.na(reporting_data$mod_5_REV) + is.na(reporting_data$mod_6_REV)) / (20 * 154)
 
@@
 # calculating mean total QMP ratios
-Mean_Rat_Rep <- mean(plot_456_data$QMP_ratio_REV[
-  plot_456_data$QMP_type == "Total" & plot_456_data$RepOrg == "Replication"])
-Mean_Rat_Org <- mean(plot_456_data$QMP_ratio_REV[
-  plot_456_data$QMP_type == "Total" & plot_456_data$RepOrg == "Original"])
+Mean_Rat_Rep <- mean(reporting_data$QMP_REV_ratio[reporting_data$rep_org == "Replication"])
+
+Mean_Rat_Org <- mean(reporting_data$QMP_REV_ratio[reporting_data$rep_org == "Original"])
 ```
@@
 ## Hypothesis 4 beta regression model
+# for H4 we have to combine the replication and original data together
+data_h4 <- rbind(data_h456_original, data_h456_replications)
+
 # running the models with revised QMP ratio's
@@
 ## Hypothesis 5 logistic regression model
+# first removing any hypotheses from the data that were rated as being unclear
+data_h5 <- data_h456_replications
+data_h5 <- data_h5[data_h5$hypothesis_support != "Unclear",]
+data_h5$hypothesis_support <- droplevels.factor(data_h5$hypothesis_support)
+
+# running the model using the QMPs from the revised coding protocol
 H5_test_results_REV <- apa_print(glm(hypothesis_support ~ QMP_REV_ratio, data = data_h5, family = binomial))
@@
 # running the model with initial QMP ratio's
-random_intercept_h5<- apa_print(lmer(formula = QMP ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens))
+random_intercept_h5 <- apa_print(lmer(formula = QMP ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens))
 ```
@@
 In line with Hypothesis 5, results showed that successful replications were associated with fewer QMPs compared to unsuccessful replications (`r H5_test_results_REV_with_OR`).
-However, we did not find the association with the initial protocol in neither the single-level (`r H5_test_results_with_OR`) nor the multilevel model (`r random_intercept_h5$full_result$QMP`)[^4].
-
-[^4]: The *betareg* package currently does not allow for estimation of multilevel models.
+However, we did not find the association with the initial protocol in neither the single-level (`r H5_test_results_with_OR`) nor the multilevel model (`r random_intercept_h5$full_result$hypothesis_supportYes`)[^5].
+
+[^5]: The *betareg* package currently does not allow for estimation of multilevel models.
 As an approximation, Gaussian random-intercept multilevel models were implemented using the *lmer* function from the *lme4* package [@R-lme4].
@@
 ## Hypothesis 6 beta regression model
+# first we combine the datasets of the original studies and the replications 
+# together
+# adding "Rep_" to separate replication from original columns in the combined dataset
+data_h456_Rep <- data_h456_replications
+colnames(data_h456_Rep) <- paste0("Rep_", colnames(data_h456_Rep))
+
+# combine the dataset
+data_h6 <- cbind(data_h456_original, data_h456_Rep)
+
+# running the model using the QMPs from the revised coding protocol
 H6_test_results_REV <- betareg(Rep_QMP_REV_ratio ~ QMP_REV_ratio, data = data_h6)
@@
 ### No Observed Relation Between Reliability and Replicability
+
 @stanley2014expectations illustrated that measurement error, when not attenuated for, can impact replication assessments.
@@
 This pattern continued for validity evidence reporting.
-Of the `r nrow(coded_data_replications)` measures, validity evidence in the form of factor analysis or similar analyses was reported for `r apa_num(sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` measures in original articles, and `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` measures in replication protocols.
-
-The underreporting of reliability and validity evidence has long been discussed [@willson1980research;@vacha1999practices; @green2011recent].
+Of the `r nrow(data_h456_replications)` measures, validity evidence in the form of factor analysis or similar analyses was reported for `r apa_num(sum(data_h456_original$sel_psychometric_evidence_REV != "None" & data_h456_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` measures in original articles, and `r apa_num(sum(data_h456_replications$sel_psychometric_evidence_REV != "None" & data_h456_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` measures in replication protocols.
+
+The underreporting of reliability and validity evidence has long been discussed [@willson1980research; @vacha1999practices; @green2011recent].
 Our study illustrates three potential reasons for why this problem has persisted.
@@
 ## ORCID iDs
-Cas Goos https://orcid.org/0009-0005-3792-4148
-
-Marjan Bakker https://orcid.org/0000-0001-9024-337X
-
-Jelte M. Wicherts https://orcid.org/0000-0003-2415-2933
-
-Michèle B. Nuijten https://orcid.org/0000-0002-1468-8585
+
+Cas Goos <https://orcid.org/0009-0005-3792-4148>
+
+Marjan Bakker <https://orcid.org/0000-0001-9024-337X>
+
+Jelte M. Wicherts <https://orcid.org/0000-0003-2415-2933>
+
+Michèle B. Nuijten <https://orcid.org/0000-0002-1468-8585>
 
 ## Funding
+
 The preparation of this article was supported by the veni grant VI.Veni.201G.003 awarded to Michèle Nuijten, and the vici grant ???

### 2024-08-29 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.rmd
implemented code review suggested changes

@@
 ## Hypothesis 4 beta regression model
+data_h4 <- rbind(data_h456_original, data_h456_replications)
+
 # running the model with none revised QMP ratio's
@@
 ## Hypothesis 5 logistic regression model
+# first removing any hypotheses from the data that were rated as being unclear
+data_h5 <- data_h456_replications
+data_h5 <- data_h5[data_h5$hypothesis_support != "Unclear",]
+data_h5$hypothesis_support <- droplevels.factor(data_h5$hypothesis_support)
+
+# running the model using the QMPs from the initial coding protocol
 H5_test_results <- apa_print(glm(hypothesis_support ~ QMP_ratio, data = data_h5, family = binomial))
@@
 ## Hypothesis 6 beta regression model
+# first we combine the datasets of the original studies and the replications 
+# together
+# adding "Rep_" to separate replication from original columns in the combined dataset
+data_h456_Rep <- data_h456_replications
+colnames(data_h456_Rep) <- paste0("Rep_", colnames(data_h456_Rep))
+
+# combine the dataset
+data_h6 <- cbind(data_h456_original, data_h456_Rep)
+
+# running the model using the QMPs from the initial coding protocol
 H6_test_results <- betareg(Rep_QMP_ratio ~ QMP_ratio, data = data_h6)
@@
 
+```{r Hypothesis6Associations, warning = FALSE}
+## Associations between the QMP categories
+# associations are generated using a helper function available in the source_ 
+# script. These associations correspond to the coefficients between replication
+# and original article QMPs of the various QMP types, as estimated through a 
+# beta regression.
+# Associations between the QMP categories (original QMP coding) MOVE THIS ANALYSIS TO INITIAL CODING APPENDIX
+Results_H6_between <- Associations_H6(data_h456_replications[59:76], 
+                                      data_h456_original[59:76])
+
+# keep in mind mod_ratio (not Rep) is based on a very small sample size, less
+# of a concern for the revised.
+```
+
 ```{r H6ExploratoryAssociationsInitialTable, warning = FALSE}
@@
   Results_H6_between$def_sel, Results_H6_between$def_quant, Results_H6_between$def_mod, 
-  Results_H6_between$op_def, Results_H6_between$op_op, Results_H6_between$op_sel, 
-  Results_H6_between$op_quant, Results_H6_between$op_mod, Results_H6_between$sel_def, 
-  Results_H6_between$sel_op, Results_H6_between$sel_sel, Results_H6_between$sel_quant, 
-  Results_H6_between$sel_mod)
+  Results_H6_between$def_tot, Results_H6_between$op_def, Results_H6_between$op_op, 
+  Results_H6_between$op_sel, Results_H6_between$op_quant, Results_H6_between$op_mod, 
+  Results_H6_between$op_tot, Results_H6_between$sel_def, Results_H6_between$sel_op, 
+  Results_H6_between$sel_sel, Results_H6_between$sel_quant, Results_H6_between$sel_mod, 
+  Results_H6_between$sel_tot)
 
@@
   Results_H6_between$quant_sel, Results_H6_between$quant_quant, Results_H6_between$quant_mod, 
-  Results_H6_between$mod_def, Results_H6_between$mod_op, Results_H6_between$mod_sel, 
-  Results_H6_between$mod_quant, Results_H6_between$mod_mod, Results_H6_between$tot_def, 
-  Results_H6_between$tot_op, Results_H6_between$tot_sel, Results_H6_between$tot_quant, 
-  Results_H6_between$tot_mod)
+  Results_H6_between$quant_tot, Results_H6_between$mod_def, Results_H6_between$mod_op, 
+  Results_H6_between$mod_sel, Results_H6_between$mod_quant, Results_H6_between$mod_mod, 
+  Results_H6_between$mod_tot, Results_H6_between$tot_def, Results_H6_between$tot_op, 
+  Results_H6_between$tot_sel, Results_H6_between$tot_quant, Results_H6_between$tot_mod, 
+  Results_H6_between$tot_tot)
 
@@
 # adding asterices for significance to the significant p in the dataframe
-H6_table_dataframe[8,3] <- paste0(H6_table_dataframe[8,3], "$^*$")
-H6_table_dataframe[11,3] <- paste0(H6_table_dataframe[11,3], "$^*$")
-H6_table_dataframe[14,3] <- paste0(H6_table_dataframe[14,3], "$^*$")
-H6_table_dataframe[8,6] <- paste0(H6_table_dataframe[8,6], "$^*$")
+H6_table_dataframe[9,3] <- paste0(H6_table_dataframe[9,3], "$^*$")
+H6_table_dataframe[13,3] <- paste0(H6_table_dataframe[13,3], "$^*$")
+H6_table_dataframe[16,3] <- paste0(H6_table_dataframe[16,3], "$^*$")
+H6_table_dataframe[7,6] <- paste0(H6_table_dataframe[7,6], "$^*$")
 H6_table_dataframe[9,6] <- paste0(H6_table_dataframe[9,6], "$^*$")
-H6_table_dataframe[11,6] <- paste0(H6_table_dataframe[11,6], "$^*$")
 H6_table_dataframe[13,6] <- paste0(H6_table_dataframe[13,6], "$^*$")
+H6_table_dataframe[15,6] <- paste0(H6_table_dataframe[15,6], "$^*$")
 
 # adding a column to help indicate the original QMP type
-H6_table_dataframe_expanded <- cbind(c("Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification"), H6_table_dataframe)
+H6_table_dataframe_expanded <- cbind(c("Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Total", "Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Total", "Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Total"), H6_table_dataframe)
 

### 2024-08-29 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_item_reduced_measures_analyses.Rmd
implemented code review suggested changes

@@
 
-item_number_change_data <- coded_data_replications[!is.na(coded_data_replications$mod_5_REV) & coded_data_replications$mod_5_REV, c(1, 2, 3, 56)]
+item_number_change_data <- data_h456_replications[!is.na(data_h456_replications$mod_5_REV) & data_h456_replications$mod_5_REV, c(1, 2, 3, 56)]
 
@@
 # getting information on hypothesis support/replication success
-hypothesis_support_index <- coded_data_replications$hypothesis_support
+hypothesis_support_index <- data_h456_replications$hypothesis_support
 
-hypothesis_support_index[coded_data_replications$hypothesis_support == "Unclear"] <- "Yes"
+hypothesis_support_index[data_h456_replications$hypothesis_support == "Unclear"] <- "Yes"
 
 # coding Unclear into No instead of Yes didn't make a difference on the test.
-# hypothesis_support_index[coded_data_replications$hypothesis_support == "Unclear"] <- "No"
+# hypothesis_support_index[data_h456_replications$hypothesis_support == "Unclear"] <- "No"
 
@@
 # between measures for which items were decreased and for which it was not.
-decreased_items_replicability_impact_test <- chisq.test(decreased_items_index, coded_data_replications$hypothesis_support)
+decreased_items_replicability_impact_test <- chisq.test(decreased_items_index, data_h456_replications$hypothesis_support)
 
@@
 # H1
-coded_data_original_shortened$reliability_type[decreased_items_index]
-coded_data_replications$reliability_type[decreased_items_index]
+data_h456_original$reliability_type[decreased_items_index]
+data_h456_replications$reliability_type[decreased_items_index]
 ```
@@
 # H2 & H3
-coded_data_original_shortened$reliability_coeff[decreased_items_index]
-coded_data_replications$reliability_coeff[decreased_items_index]
+data_h456_original$reliability_coeff[decreased_items_index]
+data_h456_replications$reliability_coeff[decreased_items_index]
 
 # running the H3 model
-data_h3_avg[data_h3_avg$reporting_index %in% as.numeric(rownames(item_number_change_data[item_number_change_data$direction == "decrease" & !is.na(item_number_change_data$direction),])),]
+data_h23_avg[data_h23_avg$reporting_index %in% as.numeric(rownames(item_number_change_data[item_number_change_data$direction == "decrease" & !is.na(item_number_change_data$direction),])),]
 
@@
 ```{r OriginalQMPDIfference}
+# first we combine the datasets of the original studies and the replications 
+# together
+# adding "Rep_" to separate replication from original columns in the combined dataset
+data_h456_Rep <- data_h456_replications
+colnames(data_h456_Rep) <- paste0("Rep_", colnames(data_h456_Rep))
+
+# combine the dataset
+data_h6 <- cbind(data_h456_original, data_h456_Rep)
+
 # comparing the mean and sd original QMP ratio 
@@
 ```{r H4Difference}
+# for H4 we have to combine the replication and original data together
+data_h4 <- rbind(data_h456_original, data_h456_replications)
+
 # running the h4 models
@@
 ```{r H5Difference}
-# running the h5 models
+## running the h5 models
+# first removing any hypotheses from the data that were rated as being unclear
+data_h5 <- data_h456_replications
+data_h5 <- data_h5[data_h5$hypothesis_support != "Unclear",]
+data_h5$hypothesis_support <- droplevels.factor(data_h5$hypothesis_support)
+
+# running the model using the QMPs from the revised coding protocol
 apa_print(glm(hypothesis_support ~ QMP_REV_ratio, data = data_h5[decreased_items_index[c(53:55)],], family = binomial))$full_result$QMP_REV_ratio

### 2024-08-29 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_multilevel_analyses.rmd
implemented code review suggested changes

@@
 Guidelines suggest to have at least within the range of 10 to 30 groups with 10 to 30 cases each for multilevel models, with more groups and cases each being necessary for more complex models, such as random-slope models (Kreft, 1996; Snijders and Bosker, 1993; Hox, 1998, 2010).
-For Hypothesis 3 we had `r nrow(table(data_h3_multiple$g))` groups with on average `r round(mean(table(data_h3_multiple$g)),3)` cases.
-For Hypothesis 5 and 6 we had `r nrow(table(coded_data_replications$many_labs_version))` groups with on average `r mean(table(coded_data_replications$many_labs_version))` cases.
+For Hypothesis 3 we had `r nrow(table(data_h23$g))` groups with on average `r round(mean(table(data_h23$g)),3)` cases.
+For Hypothesis 5 and 6 we had `r nrow(table(data_h456_replications$many_labs_version))` groups with on average `r mean(table(data_h456_replications$many_labs_version))` cases.
 Therefore, while we have may have had a sufficient number of cases per group for simple models, we likely lacked a sufficient number of groups to estimate multilevel models, especially more complex models.
@@
 # running a random intercept multilevel logistic model
-H3_test_result_int_sensitivity_alpha <- apa_print(glmer(formula = replication ~ 1 
+H3_test_result_int_sensitivity_alpha <- apa_print(glmer(formula = replication_success ~ 1 
                                                 + alpha + (1|g), family = 
                                                 binomial(), data = 
-                                                data_h3_multiple))
+                                                data_h23))
 
@@
 # running a random slope multilevel logistic model
-H3_test_result_slp_sensitivity_alpha <- apa_print(glmer(formula = replication ~ 1 
+H3_test_result_slp_sensitivity_alpha <- apa_print(glmer(formula = replication_success ~ 1 
                                                 + alpha + (1 + alpha|g), 
                                                 family = binomial(), data =
-                                                data_h3_multiple))
+                                                data_h23))
 
@@
 # create dummy H5 dataframe for use in sensitivity test
-data_h5_sens <- data_h5
+data_h5_sens <- data_h456_replications
+data_h5_sens <- data_h5_sens[data_h5_sens$hypothesis_support != "Unclear",]
+data_h5_sens$hypothesis_support <- droplevels.factor(data_h5_sens$hypothesis_support)
 

### 2024-08-29 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_omega_analyses.rmd
implemented code review suggested changes

@@
 # intercept only model to check the within and between group variance.
-H2_test_result_omega <- lmer(formula = omega ~ 1 + (1|g), data = data_h2[complete.cases(data_h2),])
+H2_test_result_omega <- lmer(formula = omega ~ 1 + (1|g), data = data_h23[complete.cases(data_h23),])
 
@@
 ## The main model to test hypothesis 3, through a logistic regression model.
-H3_test_result_main_omega <- apa_print(glm(formula = replication ~ 1 + 
+H3_test_result_main_omega <- apa_print(glm(formula = replication_success ~ 1 + 
                                      omega, family = binomial(), 
-                                     data = data_h3_avg))
+                                     data = data_h23_avg))
 
@@
 # running a random intercept multilevel logistic model
-H3_test_result_int_sensitivity_omega <- apa_print(glmer(formula = replication ~ 1 
+H3_test_result_int_sensitivity_omega <- apa_print(glmer(formula = replication_success ~ 1 
                                                 + omega + (1|g), family = 
                                                   binomial(), data = 
-                                                  data_h3_multiple))
+                                                  data_h23))
 
@@
 # running a random slope multilevel logistic model
-H3_test_result_slp_sensitivity_omega <- apa_print(glmer(formula = replication ~ 1 
+H3_test_result_slp_sensitivity_omega <- apa_print(glmer(formula = replication_success ~ 1 
                                                 + omega + (1 + omega|g), 
                                                 family = binomial(), data =
-                                                data_h3_multiple))
+                                                data_h23))
 
@@
 ### Results & Comparison Interpretation
-For omega the mean (values calculated in the population across replication sets) was `r apa_num(mean(data_h3_multiple$omega, na.rm = TRUE), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`.
+For omega the mean (values calculated in the population across replication sets) was `r apa_num(mean(data_h23$omega, na.rm = TRUE), digits = 3)` with a standard deviation of `r apa_num(sd(data_h23$omega, na.rm = TRUE), digits = 3)`.
 
@@
 However, caution in interpreting the test results is needed.
-The number of measures for which the omega coefficient could be and was calculated was quite low (`r apa_num(sum(!is.na(data_h3_avg$omega)), numerals = FALSE)`).
+The number of measures for which the omega coefficient could be and was calculated was quite low (`r apa_num(sum(!is.na(data_h23$omega)), numerals = FALSE)`).
 

### 2024-08-29 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd
implemented code review suggested changes

@@
 # intercept only model to check the within and between group variance.
-H2_test_result_alpha <- lmer(formula = alpha ~ 1 + (1|g), data = data_h2)
+H2_test_result_alpha <- lmer(formula = alpha ~ 1 + (1|g), data = data_h23)
 
@@
 # beta regression.
-# Associations between the QMP categories (original QMP coding) MOVE THIS ANALYSIS TO INITIAL CODING APPENDIX
-Results_H6_between <- Associations_H6(data_h6)
+# Associations between the QMP categories (revised QMP coding)
+Results_H6_between_REV <- Associations_H6(data_h456_replications[c(59:61, 77:91)], 
+                                      data_h456_original[c(59:61, 77:91)])
 
-# keep in mind mod_ratio (not Rep) is based on a very small sample size, less
-# of a concern for the revised.
-
-# Associations between the QMP categories (revised QMP coding)
-Results_H6_between_REV <- Associations_H6_REV(data_h6)
-
+# keep in mind mod_ratio (not Rep) is based on a somewhat small sample size
 ```
@@
   Results_H6_between_REV$def_sel, Results_H6_between_REV$def_quant, Results_H6_between_REV$def_mod, 
-  Results_H6_between_REV$op_def, Results_H6_between_REV$op_op, Results_H6_between_REV$op_sel, 
-  Results_H6_between_REV$op_quant, Results_H6_between_REV$op_mod, Results_H6_between_REV$sel_def, 
-  Results_H6_between_REV$sel_op, Results_H6_between_REV$sel_sel, Results_H6_between_REV$sel_quant, 
-  Results_H6_between_REV$sel_mod)
+  Results_H6_between_REV$def_tot, Results_H6_between_REV$op_def, Results_H6_between_REV$op_op, 
+  Results_H6_between_REV$op_sel, Results_H6_between_REV$op_quant, Results_H6_between_REV$op_mod, 
+  Results_H6_between_REV$op_tot, Results_H6_between_REV$sel_def, Results_H6_between_REV$sel_op, 
+  Results_H6_between_REV$sel_sel, Results_H6_between_REV$sel_quant, Results_H6_between_REV$sel_mod, 
+  Results_H6_between_REV$sel_tot)
 
@@
   Results_H6_between_REV$quant_sel, Results_H6_between_REV$quant_quant, Results_H6_between_REV$quant_mod, 
-  Results_H6_between_REV$mod_def, Results_H6_between_REV$mod_op, Results_H6_between_REV$mod_sel, 
-  Results_H6_between_REV$mod_quant, Results_H6_between_REV$mod_mod, Results_H6_between_REV$tot_def, 
-  Results_H6_between_REV$tot_op, Results_H6_between_REV$tot_sel, Results_H6_between_REV$tot_quant, 
-  Results_H6_between_REV$tot_mod)
+  Results_H6_between_REV$quant_tot, Results_H6_between_REV$mod_def, Results_H6_between_REV$mod_op, 
+  Results_H6_between_REV$mod_sel, Results_H6_between_REV$mod_quant, Results_H6_between_REV$mod_mod, 
+  Results_H6_between_REV$mod_tot, Results_H6_between_REV$tot_def, Results_H6_between_REV$tot_op, 
+  Results_H6_between_REV$tot_sel, Results_H6_between_REV$tot_quant, Results_H6_between_REV$tot_mod, 
+  Results_H6_between_REV$tot_tot)
 
@@
 # adding asterices for significance to the significant p in the dataframe
-H6_table_dataframe_REV[11,3] <- paste0(H6_table_dataframe_REV[11,3], "$^*$")
 H6_table_dataframe_REV[13,3] <- paste0(H6_table_dataframe_REV[13,3], "$^*$")
-H6_table_dataframe_REV[14,3] <- paste0(H6_table_dataframe_REV[14,3], "$^*$")
+H6_table_dataframe_REV[15,3] <- paste0(H6_table_dataframe_REV[15,3], "$^*$")
+H6_table_dataframe_REV[16,3] <- paste0(H6_table_dataframe_REV[16,3], "$^*$")
+H6_table_dataframe_REV[18,3] <- paste0(H6_table_dataframe_REV[18,3], "$^*$")
 H6_table_dataframe_REV[4,6] <- paste0(H6_table_dataframe_REV[4,6], "$^*$")
-H6_table_dataframe_REV[11,6] <- paste0(H6_table_dataframe_REV[11,6], "$^*$")
 H6_table_dataframe_REV[13,6] <- paste0(H6_table_dataframe_REV[13,6], "$^*$")
-H6_table_dataframe_REV[14,6] <- paste0(H6_table_dataframe_REV[14,6], "$^*$")
+H6_table_dataframe_REV[15,6] <- paste0(H6_table_dataframe_REV[15,6], "$^*$")
+H6_table_dataframe_REV[16,6] <- paste0(H6_table_dataframe_REV[16,6], "$^*$")
 
 # adding a column to help indicate the original QMP type
-H6_table_dataframe_REV_expanded <- cbind(c("Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification"), H6_table_dataframe_REV)
+H6_table_dataframe_REV_expanded <- cbind(c("Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Total", "Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Total", "Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Total"), H6_table_dataframe_REV)
 

### 2024-08-29 Scripts/source_script.R

@@ -8,7 +8,7 @@ renaming <- function(Data){
   # renaming columns
   colnames(Data) <- 
     c("many_labs_version", "rep_org", "title", "measure_name", "variable_name",
-      "multi", "appearance", "N", "N_items", "hypothesis_support", 
+      "multi", "variable_order", "N", "N_items", "hypothesis_support", 
       "reliability_type", "reliability_type_text", "reliability_coeff",
       "def1", "op_version", "op_1", "op_2", "op_3", "op_4", "op_5", 
       "sel_existing", "sel_existing_text", "sel_1", "sel_2", "sel_3", "sel_4",
@@ -106,9 +106,10 @@ recoding <- function(Data){
   # changing the variable types for each column to better represent their 
   # intended variable type
   class(Data$many_labs_version) <- "numeric"
+  Data$many_labs_version <- as.factor(Data$many_labs_version)
   Data$rep_org <- droplevels(as.factor(Data$rep_org))
   Data$multi <- droplevels(as.factor(Data$multi))
-  Data$appearance <- droplevels(as.factor(Data$appearance))
+  Data$variable_order <- droplevels(as.factor(Data$variable_order))
   class(Data$N) <- "numeric"
   Data$N_items <- droplevels(as.factor(Data$N_items))
   Data$hypothesis_support <- droplevels(as.factor(Data$hypothesis_support))
@@ -222,77 +223,42 @@ calculating <- function(Data){
 
 
 # QMP Related Functions --------------------------------------------------------
-### Hypothesis 4 
-# data load and prep function
-data_prep_H4 <- function(Data_Original, Data_Replications){
-  # data prep for model (using the (y * (n - 1) + 0.5) / n to adjust for any 0 
-  # or 1 proportions in the data).
-  Data_H4 <- rbind(Data_Original, Data_Replications)
-  Data_H4$QMP_ratio <- ((Data_H4$QMP_ratio * (77 - 1) + 0.5) / 77)
-  Data_H4$QMP_REV_ratio <- ((Data_H4$QMP_REV_ratio * (77 - 1) + 0.5) / 77)
+# main data load and prep function
+data_prep_h456 <- function(Data){
[…]

### 2024-10-21 Scripts/Manuscript/manuscript.Rmd
final co-author feedback processing, before first submission.

@@
 ---
-title             : "An Empirical Assessment of Reliable and Valid Measurement as a Prerequisite for Informative Replications"
+title             : "Assessing Reliable and Valid Measurement for Informative Replications in Psychology"
 shorttitle        : "Measurement and Informative Replications"
@@
 
-  - name          : "Bakker, M."
+  - name          : "Bakker, Marjan"
     affiliation   : "1"
 
-  - name          : "Wicherts, J.M."
+  - name          : "Wicherts, Jelte M."
     affiliation   : "1"
 
-  - name          : "Nuijten, M.B."
+  - name          : "Nuijten, Michèle B."
     affiliation   : "1"
@@
 abstract: |
-  Recent studies have shown that challenges in measurement practices may have contributed to the “replication crisis” in psychological science. 
-  However, the nature and extent of the association between measurement and replicability remains unclear. 
-  We investigated the reliability and measurement reporting of 77 measures within 56 Many Labs replications and related original articles [@klein2014investigating; @ebersole2016many; @klein2018many; @ebersole2020many], and their association with replicability.
-  Reliability Generalization Meta-analysis revealed that not all measures were sufficiently reliable across contexts. 
-  We additionally found that reliability and validity evidence was rarely reported. 
-  Furthermore, logistic regression results indicated that "questionable measurement practices" (QMPs) in replication studies were associated with lower replicability (b = -5.60, p = .006), while study reliability was not (b = 8.21, p =.
-106) .
-<!-- the code to retrieve these two results is: paste0("$b = ", H3_test_result_main_alpha$table$estimate[[2]], "$, p = ", H3_test_result_main_alpha$table$p.value[[2]], "$") & paste0("$b = ", H5_test_results_REV$table$estimate[[2]], "$, p = ", H5_test_results_REV$table$p.value[[2]], "$"); these lines will only work after code chunks 1, 2, 12, & 19 have been ran.-->
-  These findings corroborate existing research that construct validity in published research is unknown, which may have negative consequences for replications. 
-  We offer suggestions on improving measurement practices, and argue that reported measurement information should inform the decision to replicate.
+  For a replication to be informative, measurement should be reliable and valid in both original and replication studies. 
+  Recent studies have identified problems with measurement and measurement reporting in both original and replication studies, although the association between measurement and replicability remains unclear.
+  We investigated the reliability and measurement reporting of 77 measures within 56 Many Labs replications and related original articles [@klein2014investigating; @ebersole2016many; @klein2018many; @ebersole2020many] and studied their association with replicability.
+  We found that not all measures were sufficiently reliable across contexts, and that only few measures were accompanied with reliability and validity evidence. 
+  Furthermore, “questionable measurement practices” (QMPs) in replication studies were associated with lower replicability, while original study reliability was not. 
+  These results corroborate existing findings that construct validity in published research is often unknown, which may complicate replication research. 
+  We offer suggestions on improving measurement practices and argue that reported measurement information should inform the decision to replicate.
 
 keywords          : "reliability, construct validity, measurement, reporting, questionable measurement practices, replicability, credibility, psychology"
-wordcount         : "166"
+wordcount         : "159"
 
@@
 
-For solid scientific progress in psychology, we need to be able to rely on previous findings - findings should be credible.
-Unfortunately, psychology seems to face several threats to the credibility of its findings.
-In this article, we investigate how the credibility of psychological findings may be related to problems in psychological measurement, and in turn, how those problems may affect subsequent replications.
-
-## Credibility & Replicability
-
-A prerequisite for a credible finding is that it is replicable [@vazire2022CredibilityReplicabilityImproving].
-This means that the observed effect should be comparable across the original study and subsequent replications in new samples if the differences between them are believed to be of little relevance to the effect [@nosek2022replicability].
-
-But replications often fail.
-In 2015, the Replication Project: Psychology [RPP\; @osc2015estimating] attempted replications of 100 research findings in psychology, they observed a substantial discrepancy between the replication findings and the original findings .
-Similarly, the Many Labs projects aimed to replicate the effects reported in original articles across different labs in various locations around the world [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many], and often found smaller effects in replications compared to original research.
-Furthermore, the estimates of the effect varied between different lab locations.
-
+Findings from psychological research should be credible to build and extend upon them.
+A credible finding must be replicable [@vazire2022CredibilityReplicabilityImproving], such that the observed effect is sufficiently comparable across the original study and subsequent replications in new samples and using nearly identical designs [@nosek2022replicability].
+In this article, we investigate how the credibility of psychological findings relates to problems in psychological measurement and how measurement problems may affect subsequent replications.
+
+Unfortunately, the Reproducibility Project: Psychology [RPP\; @osc2015estimating] and other large-scale replication projects that sought to replicate earlier and seminal findings [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many] typically yielded smaller effects in replications compared to original studies, with Many-Labs projects featuring different locations and samples.
 In response to this string of failed replications, there was widespread alarm regarding the credibility and robustness of findings in psychological science [@hughes2018psychology; @giner2019crisis], and efforts to explain the low replication rate.
-The factors that have been proposed include, questionable research practices [@simmons2011false; @john2012measuring; @cumming2014new; @wicherts2016degrees], questionable reporting practices [@bakker2011mis; @nuijten2016prevalence], and biased publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science].
-Another factor that has gained more traction recently is the impact of measurement-related challenges on replicability and credibility.
+The factors that have been proposed include questionable research practices [@simmons2011false; @john2012measuring; @cumming2014new; @wicherts2016degrees], questionable reporting practices [@bakker2011mis; @nuijten2016prevalence], and biased publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science].
+Another important factor is the impact of measurement-related challenges on replicability and credibility.
 
 ## Credibility & Measurement
-
-Psychological constructs, such as affective state or intelligence, cannot be measured directly [@flake2017construct].
+Psychological constructs, such as affective states or intelligence, cannot be measured directly.
 Psychological measurements involve random measurement errors and uncertainties about whether the targeted construct is indeed well reflected in the scores retrieved from the measurement procedure.
 
-The first issue relates to the concept of reliability, which gives an indication of how consistent the responses on a measurement are.
+Reliability estimates provide an indication of how consistent the responses on a measurement are.
 Reliability is a critical first step to obtaining credible findings.
@@
 
-The second issue relates to the concept of validity, specifically construct validity, or the overall extent to which a measure measures what it is supposed to measure [@borsboom2004concept].
-Construct validity of test scores is often assessed by comparing the test scores’ empirical associations to the theoretical associations of the constructs [@cronbach1955construct].
-A researcher cannot claim to have found a credible psychological effect, if the measures do not relate to the psychological construct [@cook2002experimental].
+Moreover, researchers cannot claim to have found a credible psychological effect if the measures do not relate to the psychological constructs [@cook2002experimental].
+Validity indicates the extent to which a measure measures what it is supposed to measure [@borsboom2004concept] and can be studied by comparing the test scores’ empirical associations to the theoretical associations of the constructs [@cronbach1955construct].
 
@@
 
-While reliable and valid measurement, as well as replicability are important elements that independently contribute to the overall credibility of a finding, there may also be a relation between them.
-Indeed, recent studies have illustrated that both the reliability of the measure [@stanley2014expectations] and the reporting of information relevant to demonstrating the validity of the measurement [@shaw2020measurement; @flake2017construct; @flake2020measurement] may be related to the chance of successfully replicating a psychological finding.
-This study aims to investigate the relation of reliability and measurement reporting with replicability, using data and reports from the large scale Many Labs replication projects.
-
+Replicability and reliable and valid measurement are essential elements of the credibility of a finding, and are related to each other.
+Indeed, recent studies have illustrated that both the reliability of the measure [@stanley2014expectations] and the reporting of information relevant to demonstrating the validity of the measurement [@shaw2020measurement; @flake2017construct; @flake2020measurement] may predict the replicability of psychological findings.
+
+In this study, we investigate the relation of reliability and measurement reporting with replicability, using data and reports from the large-scale Many Labs replication projects.
 Because the Many Labs projects [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many] are large-scale collaborations in which multiple lab locations directly replicated the same set of studies, their data allows us to study the variability in their measures across different contexts.
-Furthermore, as the Many Labs projects used preregistered and documented structured protocols, we therefore believe the measurement use in these projects represent a high standard within the field.
+Furthermore, because the Many Labs projects used preregistered and documented structured protocols, we expect the measurement used in these projects to represent a high standard within the field.
 Any issues in measurement here might suggest that other replications could face similar or greater challenges.
@@
 
-While reliability is generally considered a measure specific feature, this is false.
-The reliability of a measure varies between samples [@cho2015cronbach; @pauly2018resampling].
-Besides random variation due the sampling error, the variations can also reflect true variation in reliability, also known as reliability heterogeneity [@vacha-haase1998ReliabilityGeneralizationExploring].
-For instance, measures are known to generally show lower reliability in more homogeneous samples as compared to heterogeneous samples [@pike1998reliability].
-
-The resulting variations in the measurement scores could contribute to the discrepancy between effects in original and replication research, as well as within replications of the same original effect.
-After all it has long been known that noise in measurement suppresses observed effects and associations [@spearman1904proof].
+Notwithstanding the common yet mistaken belief that reliability is a measure-specific feature, the reliability of a measure typically varies between samples differing in latent trait variance and/or the latent measurement model [@cho2015cronbach; @pauly2018resampling].
+Besides random variation due to the sampling error, the variations can also reflect true variation in reliability, also known as reliability heterogeneity [@vacha-haase1998ReliabilityGeneralizationExploring].
+For instance, measures will normally show lower reliability in more homogeneous samples than heterogeneous samples [@pike1998reliability], which follows from reliability being a function of the variability in true scores.
+In modern latent variable modelling, group differences in reliability can also emerge because of failures of measurement invariance across groups (e.g., differences in factor loadings or item difficulty parameters across groups).
+
+Variations in reliability could contribute to the discrepancy between effects in original and replication studies, as well as within replications of the same original effect.
+After all, it has long been known that measurement error suppresses observed effects and associations [@spearman1904proof].
 @stanley2014expectations simulated data of items on a scale based on levels of sampling error and reliability similar to what is standard in psychological research.
@@
 
-Despite the importance of having reliable and valid measures, research has shown that Questionable Measurement Practices (QMPs) are not uncommon.
-QMPs are practices that raise doubts about a measurement's validity [@flake2020measurement], and have been coined as a term analogous to Questionable Research Practices [QRPs\; @john2012measuring].
-QMPs range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of a measure and procedure of an existing measure [@flake2020measurement].
-More specifically, @flake2020measurement identified six key questions than an article should answer to avoid QMPs: the definition of the construct, how the measure was selected, how the measure was operationalized, how the measure was quantified, whether it was modified or not and why, and the reasons and details of creating a measure if applicable.
-If these questions can be answered based on the reported measurement information, then reporting is sufficiently transparent to promote a more cumulative psychological science.
+Despite the importance of reliable and valid measurement, research has shown that Questionable Measurement Practices (QMPs) are not uncommon.
+QMPs are practices that raise doubts about a measurement’s validity [@flake2020measurement] and have been coined as a term analogous to Questionable Research Practices [QRPs\; @john2012measuring].
+QMPs range from lack of transparency and unclear motivation in choice of measure to poor justification for modifications of a measure and procedure of an existing measure [@flake2020measurement].
+Specifically, @flake2020measurement identified six key questions that an article should answer to avoid QMPs: the definition of the construct, how and why the measure was selected, how the measure operationalizes the construct, how the measure was quantified, whether it was modified or not and why, and the reasons and details of creating a measure if applicable.
+If these questions can be answered clearly based on the reported measurement information, then reporting is sufficiently transparent to promote a more cumulative psychological science.
 
@@
 Further findings by @flake2022construct and others [@flake2017construct; @shaw2020measurement] also illustrated how QMPs create challenges for replicating researchers.
-In order to reconstruct the measurement, replication researchers need to know the items that were used, how they were presented to the subjects, and how to compute the scores.
-If the measure is not reconstructed exactly, constructs measured by original and replication may differ, which may lead to differences in effect size estimates irrespective of the credibility of the original effect.
+To reconstruct the measurement, replication researchers need to know the items that were used, how they were presented to the subjects, and how to compute the scores.
+If the measure is not reconstructed exactly, constructs measured by original and replication may differ, possibly creating differences in effect sizes between original and replication studies, resulting in less informative replications.
 
@@
 
-Our study investigated the relation of reliability and measurement reporting with replicability, using data and reports from the large scale Many Labs replication projects.
-First, this study expands on the research by @stanley2014expectations.
-Our goal was to see whether reliability was related to replication success in empirical replication data.
-Specifically, we investigated whether successfully replicated studies differed in reliability from non-replicated studies.
+Our study investigates the relation of reliability and measurement reporting with replicability, using data and reports from the large-scale Many Labs replication projects.
+First, this study expands on the research by  @stanley2014expectations, to see if reliability is related to replication success in empirical replication data.
+Specifically, we investigate whether successfully replicated studies differed in reliability from non-replicated studies.
 @stanley2014expectations assumed reliability to be constant across studies, which we know to be an oversimplification.
-Therefore, to add further context to the relation between reliability and replication, this study also investigated the variation in reliability as observed across labs.
-
-Furthermore, this research conceptually replicates the study by @flake2022construct on QMPs in replications and original research, now in the context of the Many Labs projects.
-We then expand on @flake2022construct by exploring associations between QMPs and the replicability of psychological findings.
+Therefore, to add further context to the relation between reliability and replication, we also investigate the variation in reliability as observed across labs.
+
+Furthermore, we conceptually replicate the study by @flake2022construct on QMPs in replications and original research in the context of the Many Labs projects.
+We expand on @flake2022construct by exploring associations between QMPs and the replicability of psychological findings.
 
@@
 
-Measurement reliability varies across samples.
-Accounting for the differences between original and replication is crucial for evaluating replications.
-This includes variation in measurement reliability.
-Therefore, we investigated the reliability in replication (Research Question 1a; RQ1a[^1]) and original psychological research (RQ1b).
-The Many Labs studies were intended as direct replications, which implies that any remaining deviations from the original research should be irrelevant for testing the same effect as the original study [@nosek2022replicability].
-Therefore, we expected that there would be, no difference in reliability between replication research and original research (Hypothesis 1; H1).
+Measurement reliability can vary across samples, because the residual variance or the true variance in the item scores, or both, differs between samples.
+While differences in these variances across samples is inevitable, these differences should not be systematic between replication and original samples for their results to remain comparable.
+Therefore, we investigated the reliability in replication (Research Question 1a; RQ1a ) and original psychological research (RQ1b).
+The Many Labs studies were intended as direct replications, which implies that deviations from the original research should be irrelevant for testing the effect [@nosek2022replicability], including systematic differences in reliability (Hypothesis 1; H1).
 
@@
 
-Reliability has the potential to vary not only between replication and original research, but also across labs assessing the same effect [@vacha-haase1998ReliabilityGeneralizationExploring].
-We empirically investigated this in our sample by investigating whether reliability estimates differed between replicating labs (RQ2).
-For effect sizes there is little empirical evidence of widespread heterogeneity among the Many Labs replications [@klein2018many; @olsson2020heterogeneity].
-We expect that there is no significant variation in the reliability estimates of replications of the same original study (H2) either.
+Additionally, for the results of direct replications to be comparable with each other, the differences in reliability should be comparable.
+Systematic differences in reliability could indicate that measurement assesses fundamentally different constructs.
+Therefore, we investigated  whether reliability estimates differed systematically between replicating labs (RQ2).
+For effect sizes, there is little empirical evidence of widespread heterogeneity among the Many Labs replications [@klein2018many; @olsson2020heterogeneity].
+We expect that there is no systematic variation in the reliability estimates of replications of the same original study (H2) either.
 
@@
 Greater reliability means the variance around the estimate of the true effect is decreased [@nunnally1994assessment].
-Assuming that the true effect is not null, then the statistical conclusions tested with reliable measures are more likely to converge to significance.
-To empirically assess this, we investigated whether there is an association between replication study reliability and replication outcome (RQ3).
-We expected to observe a positive association between reliability in replication research and successful replication of an original finding (H3).
+If the true effect is not null, then the statistical tests with reliable measures are more likely to be significant.
+To empirically assess this, we investigated the association between replication study reliability and replication outcome (RQ3).
+We expected that reliability in the replications would be positively associated with replication success (H3).
 
@@
 
-This study aims to conceptually replicate the findings on measurement reporting of @flake2022construct.
-To do so we evaluate how common QMPs are in replications of psychological research (RQ4a) and original psychological research (RQ4b).
-
-@flake2022construct found that QMPs were overall more common in the RPP replications as compared to the original research.
-We hypothesized that for our Many Labs sample QMPs would be more frequent in original psychological research than in replication research (H4), because othe Many :abs replications used structured protocols documenting the measurement.
-
-QMPs obscure information about a particular measurement.
-This in turn may cause issues for reconstructing that measurement in subsequent replication attempts.
-The resulting deviations in measurement may be partly responsible for deviations in replication and original effects [@flake2022construct].
-Therefore, we investigated whether QMPs in replication protocols were associated with the replication outcome (RQ5).
-
-A reduction in QMPs corresponds to greater transparency in reporting of measurement.
-In line with earlier research finding other transparency related practices to be associated with more robust estimates of effects [@wicherts2011willingness; @protzko2020high], we expected QMPs in replications to be negatively associated with replication success (H5).
-
-@flake2022construct already proposed that QMPs in original articles may cause issues for recreating measurements for replication research.
-@shaw2020measurement already found such a spill-over effect for validity.
-In line with this research we investigated the association between QMPs in original research and QMPs in replications of psychological research (RQ6).
+We conceptually replicate the findings on measurement reporting of @flake2022construct by documenting the frequency of QMPs in replications of psychological research (RQ4a) and original psychological research (RQ4b).
+@flake2022construct found that RPP replications averaged more QMPs than original studies.
+We hypothesized that for our Many Labs sample, QMPs would be more frequent in original psychological research than in replication research (H4), because the Many Labs replications used structured protocols documenting the measurement.
+
+QMPs obscure information about a particular measurement, which may cause issues reconstructing that measurement in subsequent replication attempts.
+Because resulting deviations in measurement may be partly responsible for deviations in replication and original effects [@flake2022construct], we investigated whether QMPs in replication protocols were associated with the replication outcome (RQ5).
+A reduction in QMPs corresponds to greater transparency in measurement reporting.
+In line with earlier research finding that other transparency-related practices are associated with more robust estimates of effects [@wicherts2011willingness; @protzko2020high], we expected QMPs in replications to be negatively associated with replication success (H5).
+
+@flake2022construct proposed that QMPs in original articles may impede recreating measurements for replications, and indeed @shaw2020measurement found evidence for such a spill-over effect for validity.
+In line with this research, we investigated the association between QMPs in original research and QMPs in replications of psychological research (RQ6).
 We expected the total number of QMPs in original psychological research to be positively related to the total number of QMPs in replication research (H6).
@@
 The data came from the Many Labs replication projects.
-Specifically, data from Many Labs 1, 2, 3, & 5 [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many].
+Specifically, data from Many Labs 1, 2, 3, & 5 [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many] was included.
 Many Labs 4 [@klein2022many] was excluded, as there was no publicly available replication protocol.
-Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study's focus on item-based measures.
+Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures.
 
@@
 
-The unit of analysis in this study was a measure of a single psychological construct used in the primary analysis that was being replicated.
+The unit of analysis in this study was a measure of a single psychological construct used in the primary analysis that was targeted in the replication.
 Multiple psychological constructs could be measured per original study or replication.
 We used the replication protocols to identify these measures.
-Acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses were not included.
+We did not include acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses.
 
@@
 
-We retrieved the data on the replication protocols, and replication datasets of Many Labs 1, 2, 3, & 5 from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>.
-Both the replication protocols and replication datasets were scanned through to ensure that the planned analyses were feasible.
-However, no coding or analysis of either of them had taken place before the analyses were preregistered.
-Further details on the search strategy can be found in the [coding protocol information file](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) (URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd>) in the supplementary materials.
+We retrieved the data on the replication protocols and replication datasets of Many Labs 1, 2, 3, & 5 from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>.
+Both the replication protocols and replication datasets were scanned to ensure the planned analyses were feasible.
+However, no coding or analysis of either of them had taken place before we preregistered the analyses.
+Further details on the search strategy can be found in the [supplementary materials](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) (URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd>).
 
@@
 
-The replication datasets refer to the publicly available datasets containing the data obtained from all labs that took part in a Many Labs study.
+The replication datasets refer to the publicly available datasets containing the data obtained from all labs partaking in a Many Labs study.
 For the analyses, we extracted the scores on the items of each previously identified measure that met our inclusion criteria specified below.
-When scores could not be clearly identified, any available codebooks, analysis scripts or study materials were used to identify the relevant scores.
+When scores could not be clearly identified, any available codebooks, analysis scripts, or study materials were used to identify the relevant scores.
 
 To be included in the planned analyses on calculated reliabilities (RQ1, RQ2, and RQ3), the measure had to be a scale consisting of multiple items.
-If cleaned data was available this was chosen over raw data, to ensure that variables were coded as intended (e.g.
-no reverse-coded items).
-Pilot data were omitted from the analyses.
+If cleaned data were available, we chose these over raw data, to ensure that variables were coded as intended (e.g., no reverse-coded items).
+We omitted pilot data from the analyses.
 These criteria resulted in suitable item score data from `r apa_num(nrow(data_h23_avg))` replication sets spread across on average approximately `r apa_num(mean(table(data_h23$g)), digits = 0)` lab locations for the analyses of Hypotheses 2 & 3.
@@
 ### Replication Protocols
-
-The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each set of replications replicating a single original study across multiple labs.
-These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [Data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd>).
+The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each set of replications of a given original study across multiple labs.
+These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd>).
 
@@
 
-The original study articles were identified using the citations for these articles in each replication protocol. All articles could be retrieved.
+We identified and retrieved all original study articles using the citations for these articles in each replication protocol.
 
@@
 
-Because data from the Many Labs replications were available for each lab location within each replication set, it was possible to calculate reliabilities for any item scale measure used for each lab location separately.
-This made it possible to assess the variation of reliabilities of the same measure across different contexts.
-
-Cronbach's Alpha was calculated as the main reliability index used in the analyses, as it remains the most commonly used indicator of the reliability of a measure [@flake2017construct], thus allowing for comparisons with the reliabilities reported in original articles.
-Cronbach's Alpha was calculated using the alpha function from the *psych* R package [*v`r getNamespaceVersion("psych")[[1]]`*\; @R-psych] with default arguments.
-Omega was pre-registered as an additional index of reliability, because it is regarded by numerous psychometricians as a more informative alternative to Cronbach’s Alpha [@crutzen2017scale; @deng2017testing].
+Because data from the Many Labs replications were available for each lab location within each replication set, we could calculate reliabilities for any item scale measure used for each lab location separately.
+This allowed us to assess the variation of reliabilities of the same measure across different contexts.
+
+We calculated Cronbach’s Alpha, as it remains the most commonly used indicator of the reliability of a measure [@flake2017construct], to compare the reliabilities reported in original articles and across replicating labs.
+We calculated Cronbach’s Alpha using the alpha function from the *psych* R package [*v`r getNamespaceVersion("psych")[[1]]`*\; @R-psych] with default arguments.
+We had preregistered Omega as an additional index of reliability, because it is regarded by numerous psychometricians as a more informative alternative to Cronbach’s Alpha [@crutzen2017scale; @deng2017testing].
 The results based on Omega can be found in [Supplementary Analyses C](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_multilevel_analyses.Rmd).
@@
 
-We extracted the reported reliability coefficient and type of index (Cronbach's Alpha, retest, interrater, etc.) of a measure from both the replication protocols and the original articles when present.
+We extracted the reported reliability coefficient and type of index (Cronbach’s Alpha, retest, interrater, etc.) of a measure from both the replication protocols and the original articles when present.
 Similarly, we coded the presence of any validity evidence, such as a factor analysis, that was presented alongside the measure.
@@
 The tests for Hypotheses 4, 5, & 6 were all based on the QMPs coded for both original articles and replication protocols.
-We included items based on @flake2022construct, and additional items to further assess transparent measurement reporting as laid out in @flake2020measurement.
-In total, we coded `r sum(colnames(coded_data_replications) == "def1" | colnames(coded_data_replications) == "op_1" | colnames(coded_data_replications) == "op_2" | colnames(coded_data_replications) == "op_3" | colnames(coded_data_replications) == "op_4" | colnames(coded_data_replications) == "op_5" | colnames(coded_data_replications) == "sel_1" | colnames(coded_data_replications) == "sel_2" | colnames(coded_data_replications) == "sel_3" | colnames(coded_data_replications) == "sel_4" | colnames(coded_data_replications) == "quant_1" | colnames(coded_data_replications) == "quant_2" | colnames(coded_data_replications) == "quant_3" | colnames(coded_data_replications) == "quant_4" | colnames(coded_data_replications) == "mod_1" | colnames(coded_data_replications) == "mod_2" | colnames(coded_data_replications) == "mod_3" | colnames(coded_data_replications) == "mod_4" | colnames(coded_data_replications) == "mod_5" | colnames(coded_data_replications) == "mod_6")` different QMPs, categorized into five QMP type categories based on @flake2020measurement.
+We included items based on Flake et al.
+(2022), and additional items to further assess transparent measurement reporting as laid out in Flake and Fried (2020).
+In total, we coded `r sum(colnames(coded_data_replications) == "def1" | colnames(coded_data_replications) == "op_1" | colnames(coded_data_replications) == "op_2" | colnames(coded_data_replications) == "op_3" | colnames(coded_data_replications) == "op_4" | colnames(coded_data_replications) == "op_5" | colnames(coded_data_replications) == "sel_1" | colnames(coded_data_replications) == "sel_2" | colnames(coded_data_replications) == "sel_3" | colnames(coded_data_replications) == "sel_4" | colnames(coded_data_replications) == "quant_1" | colnames(coded_data_replications) == "quant_2" | colnames(coded_data_replications) == "quant_3" | colnames(coded_data_replications) == "quant_4" | colnames(coded_data_replications) == "mod_1" | colnames(coded_data_replications) == "mod_2" | colnames(coded_data_replications) == "mod_3" | colnames(coded_data_replications) == "mod_4" | colnames(coded_data_replications) == "mod_5" | colnames(coded_data_replications) == "mod_6")` different QMPs, categorized into five QMP type categories based on Flake and Fried (2020).
 The QMP categories and example items can be seen in Table \@ref(tab:QMPCodingInfoTable).
@@
 
-QMPs were all coded to be either true, false, or not applicable if not relevant for that measure (e.g.
-reporting results from a factor analysis for single item measures).
-For the analyses we calculated a ratio (both per QMP type and overall QMP) based on the number on the number of true responses divided by the number of responses coded to be applicable.
-
-After the initial coding, we made minor revisions to `r length(coded_data_revised_raw[1, c("Op1", "Op2", "Op5", "Sel1", "Sel3", "Quant1", "Quant2", "Quant3", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` of the `r length(coded_data_initial_raw[1, c("Def1", "Op1", "Op2", "Op3", "Op4", "Op5", "Sel1", "Sel2", "Sel3", "Sel4", "Quant1", "Quant2", "Quant3", "Quant4", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` QMP items in the preregistered coding protocol, because they were considered too stringent in some of their criteria for what constituted a QMP.
-For example, in the initial protocol an example item had to be present within the article or protocol itself, or else this was counted as a QMP.
+QMPs were all coded to be either true, false, or not applicable if not relevant for that measure (e.g., reporting results from a factor analysis for single-item measures).
+For the analyses, we calculated a ratio (both per QMP type and overall QMP) based on the number on the number of true responses divided by the number of responses coded to be applicable.
+
+After the initial coding, we made minor revisions to `r length(coded_data_revised_raw[1, c("Op1", "Op2", "Op5", "Sel1", "Sel3", "Quant1", "Quant2", "Quant3", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` of the `r length(coded_data_initial_raw[1, c("Def1", "Op1", "Op2", "Op3", "Op4", "Op5", "Sel1", "Sel2", "Sel3", "Sel4", "Quant1", "Quant2", "Quant3", "Quant4", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` QMP items in the preregistered coding protocol, because we considered them overly stringent in practice.
+For example, in the initial protocol, an example item had to be present within the article or protocol itself, or else this was counted as a QMP.
 In the revised protocol, references to online appendices with example items were also considered sufficient for this item.
-The analyses, tables and figures presented in this article are all based on the revised coding protocol, the results of the equivalent analyses based on QMPs obtained with our initial protocol can be found in [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd).
+The analyses, tables, and figures presented in this article are all based on the revised coding protocol, the results of the equivalent analyses based on QMPs obtained with our initial protocol can be found in [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd).
 
@@
 
-We used the published reports of the Many Labs projects [@klein2014investigating; @ebersole2016many; @ebersole2020many; @klein2018many] to determine replication success based on the reported significance of the meta-analytic effect.
+We used the published reports of the Many Labs projects [@klein2014investigating; @ebersole2016many; @ebersole2020many; @klein2018many]) to determine replication success based on the reported significance of the meta-analytic effect.
 An effect was considered successfully replicated if the meta-analytic effect was in the same direction as the original effect and had a p-value lower than .05.
@@
 Every hypothesis test in this study was a two-sided test with an alpha of .05.
-No correction for multiple testing was applied, to ensure that the rate of false negatives remained low.
+We applied no correction for multiple testing to ensure that the rate of false negatives remained low.
 Our hypotheses are about associations that have been proposed in the literature, but to the best of our knowledge have not yet been empirically tested on real data.
-In this exploratory context, false negatives were considered more detrimental than false positives.
+In this exploratory context, we considered false negatives more detrimental than false positives.
 
@@
 
-Table \@ref(tab:ReplicationNrTable) shows the number of replication sets, measures, and measures per study that were extracted, as well as the proportion of successful replications, for each of the Many Labs separately and in total.
+Table \@ref(tab:ReplicationNrTable) shows the number of replication sets, measures, and measures per study, as well as the proportion of successful replications, for each of the Many Labs separately and in total.
 
@@
   , note = "Nr.
-measures refers to the total number of primary measures extracted, while Nr.
+measures refer to the total number of primary measures extracted, while Nr.
 replicated displays the number of measures for which the associated effect was replicated successfully.
-The value between brackets represent the ratio of replications.
+The value between brackets represents the ratio of replications.
 $^a$replication was assessed as unclear for three other measures, since their effect was only partially replicated.
@@
 
-Our data had a multilevel structure.
-Each replication was nested within one of four Many Labs projects.
+Because each replication was nested within one of four Many Labs projects, our data had a multilevel structure.
 Furthermore, `r sum(data_h456_replications$appearance != 1)` replications used more than one primary measure, resulting in `r nrow(data_h456_replications)` measures in both `r sum(data_h456_replications$appearance == 1)` replications protocols and `r sum(coded_data_original$appearance == 1)` original articles[^2].
@@
 In the replications, the data of responses on the measures was further nested in several labs per replication.
-The combined sample size of all labs in the replications was on average `r round(mean(data_h456_replications[data_h456_replications$appearance == 1]$N), 0)` which was approximately `r round(mean(data_h456_replications[data_h456_replications$appearance == 1]$N) / mean(data_h456_original[data_h456_original$appearance == 1 & !is.na(data_h456_original$N),]$N), 0)` times larger than the average in original studies, which were conducted in single labs.
+The combined sample size of all labs in the replications was on average `r round(mean(data_h456_replications[data_h456_replications$appearance == 1]$N), 0)`, which was approximately `r round(mean(data_h456_replications[data_h456_replications$appearance == 1]$N) / mean(data_h456_original[data_h456_original$appearance == 1 & !is.na(data_h456_original$N),]$N), 0)` times larger than the average in original studies, which were conducted in single labs.
 
 [^2]: Initially the original articles contained 3 more measures than the replication protocols.
-This difference was due to the way that the moral foundations questionnaire was framed in the original articles compared to in the original article.
+This difference was due to the way that the moral foundations questionnaire was framed in the original article compared to in the replication protocol.
 In the original article it was framed as measuring five different moral foundations, while in the replication protocol the measure assessed the two overarching categories that were used to test the main effect in both the original and replication research.
@@
 To check whether or not this had a confounding impact on our results, we re-ran the analyses testing the hypotheses excluding data from these studies (see [Supplementary Analyses E](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_item_reduced_measures_analyses.Rmd)).
-We found that removing these measures' data had minimal impact on the overall results.
+We found that removing these measures’ data had minimal impact on the overall results.
 Therefore, the results presented below were based on data from all the measures.
 
-Because of this multilevel structure we initially planned to conduct multilevel models alongside our single-level regression models for testing Hypothesis 3, 5, and 6.
-However, these analyses were omitted, because group sizes were small.
-The results from these analyses are reported in [Supplementary Analyses B](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_multilevel_analyses.Rmd) for the sake of completeness and transparency.
+Because of this multilevel structure we preregistered multilevel random-intercept and random-slope models alongside our single-level regression models for testing Hypothesis 3, 5, and 6.
+However, because group sizes turned out to be too small to support random slope models, we omitted the results from these analyses from the main article and  instead report them in [Supplementary Analyses B](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_multilevel_analyses.Rmd) for the sake of completeness and transparency.
 
@@
 
-If data from a multiple item scale could be accessed, we calculated the Cronbach’s Alpha of that scale from that data for each lab that administered the scale.
-As a result, it was possible to include the multiple estimates of Cronbach’s Alpha for those measures into a meta-analysis of the reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analysis [@vacha-haase1998ReliabilityGeneralizationExploring; @botella2012ManagingHeterogeneityVariance; @lopez-ibanez2024ReliabilityGeneralizationMetaanalysis].
+If data from a multiple-item scale could be accessed, we calculated the Cronbach’s Alpha of that scale from that data for each lab that administered the scale.
+Subsequently, we included the multiple estimates of Cronbach’s Alpha for those measures into an unregistered meta-analysis of the reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analysis [@vacha-haase1998ReliabilityGeneralizationExploring; @botella2012ManagingHeterogeneityVariance; @lopez-ibanez2024ReliabilityGeneralizationMetaanalysis].
 This enabled us to quantify the degree of true variation (or heterogeneity) in reliability coefficients across lab locations.
 
-For Cronbach's alpha, we used formulas 2 & 3 from @duhachek2004AlphaStandardError to calculate the standard error in the meta-analysis.
-Heterogeneity was estimated using the tau value, which indicates the standard deviation of the distribution of true Cronbach's alpha coefficients for a measure, and tested using the Cochran's Q test for each measure.
-
-The RG meta-analysis was performed using the *rma* function from the *metafor* R package [*v`r getNamespaceVersion("metafor")[[1]]`*\; @R-metafor].
-Defaults settings were used.
+For Cronbach’s alpha, we used formulas 2 & 3 from Duhachek and Lacobucci (2004) to calculate the standard error in the meta-analysis.
+Heterogeneity was estimated using the tau value, which indicates the standard deviation of the distribution of true Cronbach’s alpha coefficients for a measure, and tested using the Cochran’s Q test for each measure.
+We performed the RG meta-analysis using the *rma* function from the *metafor* R package [*v`r getNamespaceVersion("metafor")[[1]]`*\; @R-metafor] and default settings.
 We implemented no correction for bias, because the Many Labs replications were not at risk of publication bias.
 
-The average calculated Cronbach's alpha coefficient across replication sets was `r apa_num(mean(data_h23$alpha), digits = 3)` with a standard deviation of `r apa_num(sd(data_h23$alpha, na.rm = TRUE), digits = 3)`.
+The average calculated Cronbach’s alpha coefficient across replication sets was `r apa_num(mean(data_h23$alpha), digits = 3)` with a standard deviation `r apa_num(sd(data_h23$alpha, na.rm = TRUE), digits = 3)`.
 Figure \@ref(fig:Plot23AlphaCode) displays the distributions of the calculated Cronbach’s Alpha scores from each lab for each measure, separated by successful and unsuccessful replication.
@@
 
-```{r Plot23AlphaCode, warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the eighteen distinct measures for which raw data was available from which Cronbach’s alpha coefficients could be calculated.
+```{r Plot23AlphaCode, warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the eighteen measures for which raw data was available from which Cronbach’s alpha coefficients could be calculated.
 The green lines indicate the meta-analytic prediction interval lower and upper bound.
@@
 However, other measures showed not only considerably lower average reliability scores, but also greater variation.
-
-Finally, the blue triangles indicate the Cronbach’s Alpha reported in the original articles.
-The reliabilities were generally only reported for those measures with a large average calculated reliability.
-
-### Hypothesis 1: Reliability Reporting in Original and Replication Research.
+Finally, the blue triangles indicate Cronbach’s Alpha reported in the original articles.
+The reliabilities were generally only reported in original studies for those measures with a large average calculated reliability in the replications.
+
+### Hypothesis 1: Reliability Reporting in Original and Replication Research
 
@@
 
-The number of reported reliabilities was `r N_reported_reliabilities_original` in original articles and `r N_reported_reliabilities_replications` in replications, which was too low to ensure that the pre-registered Mann-Whitney U test can function as an informative test on the difference in the reported value of Cronbach's Alpha between original articles and replications.
-Instead, the difference between the reported reliability in the original article and the calculated average reliability in replications is displayed in the Diff column in Figure \@ref(fig:Plot23AlphaCode).
+Because we counted only `r N_reported_reliabilities_original` reported reliabilities in original articles and `r N_reported_reliabilities_replications` reliabilities reported in replications, we decided against using our pre-registered Mann-Whitney U test to test the difference in the reported value of Cronbach’s Alpha between original articles and replications.
+Instead, we displayed the difference between the reported reliability in the original article and the calculated average reliability in replications in the Diff column in Figure \@ref(fig:Plot23AlphaCode).
 Contrary to Hypothesis 1, this column shows that the reported reliability in original articles was generally lower than the average reliability in the replication sample.
-Still, more than half of the reported reliabilities did fall within the 95-percentile range around the replication average.
-
-### Hypothesis 2: Within Study Variation in Reliability.
-
-To get an indication of the true variability in the reliability scores, we used the RG meta-analyses to test for heterogeneity in the reliabilities in the replications.
-This analysis deviated from the multilevel analysis we preregistered, as the preregistered analysis was later deemed not suitable for testing Hypothesis 2 (results from the preregistered analysis are shown in [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd)).
-
-Figure \@ref(fig:Plot23AlphaCode) displays the tau estimates, which indicates the differences in true reliability scores between labs for a given measure.
-For `r sum(data_h23_avg$QEp > .05)` measures the tau estimate was not significantly different from 0, while for `r apa_num(sum(data_h23_avg$QEp < .05), numerals = FALSE)` measures, the true variation in reliability across labs was significant.
+Still, more than half of the reported reliabilities in original studies fell within the 95-percentile range around the replication average.
+
+### Hypothesis 2: Within Study Variation in Reliability
+
+To get an indication of the true variability in the reliability scores, we used the RG meta-analyses to test for heterogeneity in the reliabilities across replication labs.
+Even though, we preregistered the ICC of reliability in a multilevel model as an indicator of within study variation in reliability relative to between study variation, we opted for the heterogeneity test to obtain a more informative absolute estimate of the within study variation in true reliability score to test Hypothesis 2.
+(results from the preregistered analysis are shown in [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd)).
+
+Figure \@ref(fig:Plot23AlphaCode) displays the estimates of tau, which indicates the differences in true reliability scores between labs for a given measure.
+For `r sum(data_h23_avg$QEp > .05)` measures, the tau estimate was not significantly different from 0, while the true variation in reliability across labs was significant for `r apa_num(sum(data_h23_avg$QEp <= .05), numerals = FALSE)` measures.
 The true reliability was quite variable for some measures.
-For instance, the estimate of the standard deviation of the true reliability of the top measure in the graph (a measure of conscientiousness from @gosling2003very used in the replication of @defruyt2000cloninger) equaled `r apa_num(plot_23_data_alpha_reordered[plot_23_data_alpha_reordered$g == "De Fruyt et al.
-(2000)", "tau"][1], digits = 3, gt1 = FALSE)` points of Cronbach’s Alpha.
-
-Thus for around a quarter of measures, the reliability was heterogeneous.
-Although for the remaining measures, we found no significant heterogeneity in reliabilities, we note that power to detect small heterogeneity is often low [@ioannidis2007uncertainty; @olsson2020heterogeneity].
-
-### Hypotyhesis 3: Reliability and Replicability
+For instance, the estimate of the standard deviation of the true reliability of the top measure in the graph (a measure of conscientiousness from @gosling2003very used in the replication of @defruyt2000cloninger) equaled `r apa_num(data_h23_avg$tau[data_h23_avg$g == "De Fruyt et al.
+(2000)"], digits = 3, gt1 = FALSE)` points of Cronbach’s Alpha.
+
+Thus, for around a quarter of the measures, the reliability was heterogeneous across labs.
+Although for the remaining measures, we found no significant heterogeneity in reliabilities, we note that the power to detect small heterogeneity is often low  [@ioannidis2007uncertainty; @olsson2020heterogeneity].
+
+### Hypothesis 3: Reliability and Replicability
 
@@
 We used a logistic regression model to test whether replication success as reflected in a significant mean effect in the meta-analysis conducted across the replicating labs could be predicted by the average calculated reliabilities of the measures.
-Cronbach's alpha did not significantly predict replication success in the main logistic regression model (`r H3_test_result_main_alpha$full_result$alpha`)[^4].
+Cronbach’s alpha did not significantly predict replication success in the main logistic regression model (`r H3_test_result_main_alpha$full_result$alpha`)[^4].
 Results based on the Omega coefficient lead to a similar conclusion (see [Supplementary Analyses C](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_omega_analyses.Rmd)).
 
-[^4]: We omitted the Odds ratio and Odds ratio confidence intervals from this result.
-Because alpha is bounded between 0 and 1, and we furthermore observed in most alpha values little variation from the mean of `r mean(data_h23_avg$alpha)`, a change from alpha by 1 point had an extremely large coefficient.
-Combined with the large uncertainty in our estimates due to the small sample, meant that the odds ratio confidence interval contained extremely large numbers (OR CI95 upper bound: `r substr(H3_main_full_results_alpha_with_OR, start = 40, stop = 52)`)
+[^4]: The log-odds ratio’s CIs are reported instead of the odds-ratios CIs for this result, as the latter were extremely wide due to Cronbach alpha’s boundedness and the small number of calculated reliabilities.
 
@@
 
-We additionally pre-registered a random intercept and random-slope multilevel regression model of the same relationship with each lab's unique reliability nested within the set of replication of an effect.
-However, because our dependent variable (replicability) is at the group level, we decided to use a test on the aggregate level using White's heteroscedasticity adjustment to address the dependency [as suggested by @foster-johnson2018Predicting].
+We additionally pre-registered multilevel regression model of the same relationship with each lab’s unique reliability nested within the set of replications of an effect.
+However, because our dependent variable (replicability) is at the group level, we decided to use a test on the aggregate level using White’s heteroscedasticity adjustment to address the dependency [as suggested by @foster-johnson2018Predicting].
 This analysis also showed a non-significant relation (`r H3_test_result_alpha_White_adjusted`).
@@
 Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts the flow of measures in relation to reliability reporting.
-First, it shows that almost half of the measures in both replication (n = `r apa_num(sum(data_h456_replications$N_items == "1 item measure"))`) and original research (n = `r apa_num(sum(data_h456_original$N_items == "1 item measure"))`) were single-item measures.
-When looking at the multiple item measures, the graph illustrates that `r N_reported_reliabilities_replications` measures in the replication protocols and `r N_reported_reliabilities_original` in the original articles reported a reliability coefficient.
-The most commonly reported reliability coefficient was Cronbach's Alpha, which accounted for `r apa_num(sum(data_h456_replications$reliability_type == "alpha"), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(data_h456_original$reliability_type == "alpha"))` in the original articles.
+First, it shows that almost half of the measures in both replication (N = `r apa_num(sum(data_h456_replications$N_items == "1 item measure"))`) and original research (N = `r apa_num(sum(data_h456_original$N_items == "1 item measure"))`) were single-item measures.
+When looking at the multiple-item measures, the graph illustrates that r N_reported_reliabilities_replications` measures in the replication protocols (`r apa_num((as.numeric(N_reported_reliabilities_replications_number_style) / sum(data_h456_replications$N_items != "1 item measure")) * 100, digits = 1)` \%) and `r N_reported_reliabilities_original` measures in the original articles (`r apa_num((as.numeric(N_reported_reliabilities_original) / sum(data_h456_original$N_items != "1 item measure")) * 100, digits = 1)` \%) reported a reliability coefficient.
+The most commonly reported reliability coefficient was Cronbach’s Alpha, which accounted for `r apa_num(sum(data_h456_replications$reliability_type == "alpha"), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(data_h456_original$reliability_type == "alpha"))` in the original articles.
 
@@
 
-Reliability was more commonly reported in original (n = `r N_reported_reliabilities_original`) as compared to replication research (n = `r N_reported_reliabilities_replications_number_style`), $\chi^{2}$(`r apa_num(reliability_reporting_test_result$parameter)`) = `r apa_num(reliability_reporting_test_result$statistic)`, *p* = `r apa_p(reliability_reporting_test_result$p.value)`.
+Reliability was more commonly reported in original (N = `r N_reported_reliabilities_original`; `r apa_num((as.numeric(N_reported_reliabilities_original) / nrow(data_h456_original)) * 100, digits = 1)` \%) as compared to replication research = `r N_reported_reliabilities_replications_number_style`; `r apa_num((as.numeric(N_reported_reliabilities_replications_number_style) / nrow(data_h456_replications)) * 100, digits = 1)` \%), $\chi^{2}$(`r apa_num(reliability_reporting_test_result$parameter)`) = `r apa_num(reliability_reporting_test_result$statistic)`, *p* = `r apa_p(reliability_reporting_test_result$p.value)`.
 Validity evidence was similarly reported infrequently.
 Validity evidence from a factor analysis was reported in `r apa_num(sum(data_h456_original$sel_psychometric_evidence_REV != "None" & data_h456_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` original articles, while in only `r apa_num(sum(data_h456_replications$sel_psychometric_evidence_REV != "None" & data_h456_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` replications.
-This difference was not significant, however the total number of factor analyses reported were few ($\chi^{2}$(`r apa_num(factor_reporting_test_result$parameter)`) = `r apa_num(factor_reporting_test_result$statistic)`, *p* = `r apa_p(factor_reporting_test_result$p.value)`).
+This difference was not significant, however the total number of factor analyses reported was low  ($\chi^{2}$(`r apa_num(factor_reporting_test_result$parameter)`) = `r apa_num(factor_reporting_test_result$statistic)`, *p* = `r apa_p(factor_reporting_test_result$p.value)`).
 
@@
 We reasoned that most of the included measures should theoretically tap into a single construct, so evidence for unidimensionality would serve as a proxy for evidence of higher construct validity.
-We found that `r sum(cfa_results$Single_factor == "Yes")` of these measures met our criteria for unidimensionality (see [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd) for further details).
-
-### Hypothesis 4: QMPs in Original Compared to Replication Research.
+We found that `r sum(cfa_results$Single_factor == "Yes", na.rm = TRUE)` of these measures (`r apa_num((sum(cfa_results$Single_factor == "Yes", na.rm = TRUE) / nrow(cfa_results)) * 100, digits = 1)` \%) met our criteria for unidimensionality (see [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd) for further details).
+
+### Hypothesis 4: QMPs in Original Compared to Replication Research
 
@@
 
-QMP_NA_percentage <- paste0(apa_num(ratio_of_NAs * 100), "%")
+QMP_NA_percentage <- paste0(apa_num(ratio_of_NAs * 100, digits = 1), "%")
 
@@
 
+Overall, the QMP ratios (i.e., the ratio of the total number of measurement practices that were not transparently and fully reported on) were low in both original and replication studies.
 The top part of Figure \@ref(fig:Plot456Code) displays the distributions of the total QMP ratio for both original articles and replication protocols, showing that the average QMP ratio in replication protocols was smaller (`r apa_num(Mean_Rat_Rep)`) than in original articles (`r apa_num(Mean_Rat_Org)`).
-The bottom of Figure \@ref(fig:Plot456Code) shows that original articles and replication protocols had different distributions of QMPs per category.
-The number of measures for which modification items were applicable also differed.
+The bottom of Figure \@ref(fig:Plot456Code) displays the observed QMP ratios per QMP type for both original articles and replication protocols, showing that original articles tended to contain fewer Definition QMPs, but more selection and operationalization QMPS, with Quantification QMPs being comparable.
+The number of measures that were modified also differed between original and replication.
 In total `r QMP_NA_percentage` of all responses across all QMP items were non-applicable.
@@
 ```{r Plot456Code, warning = FALSE, fig.cap = "QMP ratio counts for each QMP Type and QMP total ratio distribution grouped by whether the QMP ratio was obtained from an original article or a replication protocol.
-The top graph shows the distributions of total QMP ratios for both replication protocols and original articles, with the line indicating the mean QMP ratio.
+The top graph shows the distributions of total QMP ratios for both replication protocols and original articles, with the vertical line indicating the mean QMP ratio.
 The specific observed values are indicated along the bottom row with dots.
@@
 
-We used a beta-regression model to test the difference in QMP ratio between original and replication was significant using the *betareg* R package [*v`r getNamespaceVersion("betareg")[[1]]`*\; @R-betareg_a; @R-betareg_b].
-Beta regression models are similar to other generalized linear regression models, but they are better suited to model dependent variables with values in the interval of $(0, 1)$, including ratios.
+We used a beta-regression model in the *betareg* R package [*v`r getNamespaceVersion("betareg")[[1]]`*\; @R-betareg_a; @R-betareg_b] to test the difference in QMP ratio between original and replication.
+Beta regression models are similar to other generalized linear regression models, but they are better suited to model dependent variables with values in the interval of (0,1), including ratios.
 Furthermore, they are robust for heteroskedastic and asymmetrically distributed dependent variables [@cribari2010beta].
@@
 Using a beta-regression model, the total QMP ratio was regressed on a dummy variable indicating whether the coded report was an original article or a replication protocol.
-The results supported Hypothesis 4 and indicated that this difference was significant (`r betareg_output_to_apa_full(H4_test_results_REV)`).
-
-### Hypothesis 5: Replication Research QMPs and Replicability.
+The results supported Hypothesis 4 and indicated that indeed original articles contained on average more QMPs than replication protocols (`r betareg_output_to_apa_full(H4_test_results_REV)`).
+
+### Hypothesis 5: Replication Research QMPs and Replicability
 
@@
 
-### Hypothesis 6: Relation Between QMPs in Original and Replication Research.
+### Hypothesis 6: Relation Between QMPs in Original and Replication Research
 
@@
 Using a beta regression model, we found total QMP ratio in the original article to be significantly related to the total QMP ratio in the subsequent replication (`r betareg_output_to_apa_full(H6_test_results_REV)`).
-This result provides evidence in favor of Hypothesis 6.
+This result supports Hypothesis 6.
 Figure \@ref(fig:Plot46RevisedDataCode) displays this relationship visually.
@@
 Furthermore, in the multilevel model based on the revised QMPs the association was again not significant (`r random_intercept_h6_REV$full_result$QMP`).
-
 We additionally conducted planned exploratory analyses of the association for each unique combination of QMP types, but taking into account the limited sample size, we could not determine any clear relations between the separate QMP types and replicability (see [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd) and [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd) for further details on the analyses and results).
@@
 
-In this article, we analyzed the data, protocols, and related original articles from four Many Labs replication projects to assess reliability and measurement (reporting) practices.
-We additionally looked at how these features might be related to replication success, as a proxy of the credibility of findings.
-Overall, even though the average reliability was relatively high, we found that not all measures were sufficiently reliable, nor where measures always equally reliable in each setting in which they were used.
-Although we did not observe reliability to significantly predict replication success, we did observe a negative relation between replication success and presence of QMPs in replication research.
+In this article, we analyzed the data, protocols, and related original articles from four Many Labs replication projects to assess reliability and measurement (reporting) practices and study their relationship with replication success, as a proxy of the credibility of findings.
+Overall, even though the average reliability was relatively high, we found that not all measures were sufficiently reliable and that reliabilities can vary across labs/settings in replication projects.
+Although we did not observe reliability to significantly predict replication success, we did observe a negative relation between replication success and presence of Questionable Measurement Practices in replication research.
 Finally, we found QMPs in the original studies to be positively associated with QMPs in the replications.
@@
 
-While most measures showed sufficient average reliability for most purposes in psychological research (around .80), about a quarter of the measures had a reliability generally considered insufficient (around .60 or less) [@nunnally1994assessment].
-Furthermore, the reliability in original research was generally lower than in the replication samples, contrary to our Hypothesis 1 that reported reliability estimates would not differ significantly between replications and original articles.
+While most measures showed sufficient average reliability for most purposes in psychological research (around .80), about a quarter of the measures had reliabilities generally considered insufficient (around .60 or less) [@nunnally1994assessment].
+Furthermore, the reliability in original research was generally lower than in the replication samples, contrary to our Hypothesis 1 stating that reported reliability estimates would not differ significantly between replications and original articles.
 These differences may be due to features that were specific to the Many Labs projects.
-Large teams of researchers with diverse expertise were involved in the Many labs projects.
-It is possible that the pooling of expertise and use of structured procedures led to more reliable measurement compared to the original research.
+Large teams of researchers with diverse expertise were involved in these projects and it is possible that the pooling of expertise and use of structured procedures led to more reliable measurement compared to the original research.
 
@@
 Reliability heterogeneity was particularly common for measures with a lower average reliability.
-However, the number of investigated measures was small, and some measures were only used in a small number of independent samples.
+However, the number of investigated measures was small, and some measures were only used in few independent samples.
 This is particularly relevant, since the Q-test to test heterogeneity is sensitive to the number of studies included in each test [@li2015DilemmaHeterogeneityTests].
@@
 @stanley2014expectations illustrated that measurement error, when not attenuated for, can impact replication assessments.
-However, we observed no relation between reliability and replicability, even though our chosen replication index did not attenuate for measurement error.
-This result is surprising not only because it runs counter to the findings of @stanley2014expectations and Hypothesis 3.
-It also runs counter to the fact that according to statistical theory, the increased noise in the data as the result of lower reliability decreases the effect size estimates based on those data.
-
+However, we observed no relation between reliability and replicability.
+This result also runs counter to the fact that according to statistical theory, the increased noise in the data implied by lower reliability decreases the effect size estimates based on those data.
 However, the relationship between reliability and replicability is complex [@willson1980research; @lebreton2014corrections; @oswald2015Imperfect; @zhang2024Metaanalysis].
-For example, reliability and replicability are only related when the true effect is not null.
-In our sample, more than half of the effects were not replicated, indicating that many of these effects may be null effects.
-For these effects no relation between reliability and replicability is expected.
-Furthermore, while lower reliability decreases effect sizes it can also reduce the observed true variance in the effects [@olsson-collentine2023UnreliableHeterogeneityHow].
+Combined with the fact that we could only calculate reliability for a small number of measures meant we had low statistical power to detect the overall relation between reliability and replicability, which provides the most likely explanation for our non-significant findings.
+
+This problem is exacerbated further since in our sample, more than half of the effects were not replicated, indicating that many of these effects may be null effects.
+For null effects, no relation between reliability and replicability is expected, lowering our power to detect the relation further.
+Additionally, while lower reliability decreases effect sizes it can also reduce the observed true variance in the effects [@olsson-collentine2023UnreliableHeterogeneityHow].
 As a result, effect estimates from various studies will appear more similar than they truly are, seemingly replicating the original.
-These and other relations are further complicated, because as mentioned earlier reliability is not a fixed aspect of a scale, but a feature of that scale within a sample.
-
-The complexity of the relationship combined with the fact that we could only calculate reliability for a small number of measures meant we had low statistical power to detect the overall relation between reliability and replicability, even more so for the multilevel model, which provides another possible explanation for our non-significant findings.
-The small number of relevant measures and reported reliabilities does however indicate an important issue: we observed a lack of reliability evidence in both original and replication psychological research.
+Regardless, the small number of relevant measures and reported reliabilities does indicate an important issue: we observed a lack of reliability evidence in both original and replication psychological research.
 
@@
 
-The reliability of measures was rarely reported in both original and replication research, which is in line with earlier investigations in the literature [@shaw2020measurement; @flake2017construct; @flake2022construct].
+The reliability of measures was rarely reported in both original and replication research, which is in line with earlier investigations of the psychological literature [@shaw2020measurement; @flake2017construct; @flake2022construct].
 Reported reliabilities were so few, that the preregistered test for Hypothesis 1 was no longer informative.
-We found that replication research reported reliability coefficients less often than original research, which is in line with @flake2022construct.
+We found that replication research reported reliability coefficients less often than original research, which aligns with findings by @flake2022construct.
 This pattern continued for validity evidence reporting.
-Of the `r nrow(data_h456_replications)` measures, validity evidence in the form of factor analysis or similar analyses was reported for `r apa_num(sum(data_h456_original$sel_psychometric_evidence_REV != "None" & data_h456_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` measures in original articles, and `r apa_num(sum(data_h456_replications$sel_psychometric_evidence_REV != "None" & data_h456_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` measures in replication protocols.
+Of the `r nrow(data_h456_replications)` measures, validity evidence in the form of factor analysis or similar analyses was reported for `r apa_num(sum(data_h456_original$sel_psychometric_evidence_REV != "None" & data_h456_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` measures in original articles, and `r apa_num(sum(data_h456_replications$sel_psychometric_evidence_REV != "None" & data_h456_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` measures in replication protocols, implying that less than 10% of articles report sufficient information to judge the validity of key measures used in the study.
 
@@
 Our study illustrates three potential reasons for why this problem has persisted.
-Firstly, the studies in our sample commonly used single-item measures, an observation that was also made by @shaw2020measurement.
-Calculating reliability for single-item measures is less straightforward and common than for multiple item measures [@wanous1996estimating].
-Concerns with the use of single-item measures go beyond reliability, validity may also be at risk.
-Single-item measures because they are singular come with an assumption of unidimensionality regarding the construct they, which our exploratory analyses revealed is an assumption that did not frequently hold for multiple-item measures in our sample.
+First, the studies in our sample commonly used single-item measures, an observation that was also made by @shaw2020measurement.
+Calculating reliability for single-item measures is less straightforward and common than for multiple-item measures [@wanous1996estimating].
+Single-item measures can be expected to generally be less reliable than a multiple-item measure, and validity may also be at risk.
+Single-item measures, because they are singular, come with an assumption of unidimensionality regarding the construct they reflect, which our exploratory analyses revealed is an assumption that did not frequently hold for multiple-item measures in our sample.
 However, we did not explore validity concerns unrelated to reporting in-depth, therefore future research is needed to determine the extent of problems with validity.
 
-Secondly, our results indicate that there may be bias in reporting reliability coefficients.
+Second, our results indicate that there may be bias in reporting reliability coefficients.
 Reliabilities were reported in original research for those measures that obtained higher calculated reliabilities in the replication samples.
-If we take the calculated reliabilities in the replication sample as an accurate representation of the distribution of the true reliability for that measure, then this would imply that reliabilities are more often reported when the measure is truly reliable, and less when it is unreliable; a common issue of selective reporting.
-Researchers may be reluctant to report reliability for unreliable measures, thus lowering the prevalence of reported reliabilities.
+If we take the calculated reliabilities in the replication sample as a good predictor of the reliabilities in the original studies, this suggests that researchers may be reluctant to report reliability for unreliable measures.
 In turn, researchers may become overly optimistic about the reliability of measures in their field, similarly to how bias in publication causes issues for establishing estimates of true effect sizes in meta-analyses [@sutton2000empirical].
 
-Thirdly, the replication protocols were written before data were collected, which means no measurement based on these protocols had taken place yet.
-As a result, there was no data available yet from which the replicating researchers could have calculated reliability and validity.
+Third, the replication protocols were written before data were collected, which means no measurement based on these protocols had not taken place yet.
+As a result, no data were available yet from which the replicating researchers could have calculated reliability and validity.
 This would explain why there was little reliability and validity evidence reported in replication protocols.
-It may still represent a problem however, because original articles similarly rarely reported reliability and validity evidence.
-This implies that the replications commonly used measures that were not yet validated.
+It may still represent a problem, however, because original articles similarly rarely reported evidence on reliability and validity.
+This implies that the replications commonly picked measures for which validity could not be checked.
 
 On the other hand, we found that more general issues in the transparency of measurement reporting practices, as assessed by QMPs, were less common in replication protocols compared to original articles.
-This is in line with Hypothesis 4, but runs counter to the findings of @flake2022construct, who found less construct validity evidence in the replications from the RPP [@osc2015estimating] than in original articles.
+This is in line with Hypothesis 4 but runs counter to the findings of @flake2022construct), who found less evidence on construct validity in the replications from the RPP [@osc2015estimating] than in original articles.
 We believe this discrepancy was the result of our sample being the Many Labs projects.
@@
 
-Existing literature has already warned about the potential detrimental effects of QMPs on replications [@shaw2020measurement; @flake2022construct].
-It is challenging for replication researchers to mimic the measurement of an original article, when the original article does not document the measurement in sufficient detail.
-Consequently, the measurement in the replication may assess constructs substantially differently, weakening the relation between the test in original and replication studies [@flake2022construct].
+When the original article does not document the measurement in sufficient detail, it becomes challenging for replication researchers to mimic the measurement of an original study,.
+Consequently, the measurement in the replication may assess constructs substantially differently, weakening the relation between the test in original and replication studies [@shaw2020measurement; @flake2022construct].
 
@@
 These associations together indicate that poor measurement reporting in an original study could be a risk factor for subsequent replication attempts.
-We did observe that unidimensionality was not universal among the measures for which we could run a factor analysis, which assuming that the measures were meant to be unidimensional would indicate that measures may not have assessed their construct as they were intended to.
+We did observe that unidimensionality was not universal among the measures for which we could run a factor analysis, which raises doubts on the validity of the measures and substantive interpretations based on them.
+Furthermore, when replications use unvalidated measures these replications are unlikely to be informative.
 
 However, it is worth noting that the spillover effect was only observed for QMPs coded with the revised coding protocol.
-Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd) for results based on the initial protocol).
+Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd for results based on the initial protocol).
 Furthermore, these hypotheses were supported by only one of the multilevel models.
-However, these models were limited in group and sample size making their interpretation uncertain.
+However, these models were limited in group and sample size, leading to results that are somewhat uncertain.
 
@@
 Our study had several limitations.
-We encountered several challenges in operationalizing QMPs.
-Whereas previous research has focused on descriptives of specific QMPs detrimental to construct validity [@flake2022construct; @shaw2020measurement], we combined all coded QMPs together as an operationalization to assess measurement practices and evaluate their impact on replicability.
+We encountered Including challenges we encountered in operationalizing QMPs.
+Whereas previous research has focused on descriptives of specific QMPs detrimental to construct validity [@flake2022construct; @shaw2020measurement], we combined all coded QMPs together as an index to assess measurement practices and evaluate their impact on replicability.
 However, this also means that it remains uncertain if our operationalization accurately captured the concept.
@@
 
-Another challenge in constructing one overarching QMP variable was the way to treat practices that were not applicable to a particular measurement.
-We chose to construct ratios to cancel out the effects of non-applicable items as much as possible.
+Another challenge in constructing one overarching QMP variable was how to quantify it..
+We constructed ratios to cancel out the effects of non-applicable items.
 However, this has the consequence that both a measure for which all relevant measurement-related information was reported, and a measure for which no item was applicable would have a QMP ratio of zero.
 Yet, we would not consider the latter case to indicate the same level of completeness as the first.
-A little more than one third of all responses were not applicable.
+A little more than one-third of all responses were not applicable.
 As a result, the relation between QMP ratios and measurement reporting completeness may have been obscured to some extent.
-
-Interpreting any relation between QMP ratios and measurement reporting is complex, as it is not clear how high a ratio of QMPs should be to represent clear violations of good research practices.
-One might argue that any QMP is a sign of questionable research and thus that any ratio greater than zero is cause for alarm.
-However, this may be too harsh.
-As mentioned before, not all violations may have detrimental consequences or be relevant in all contexts.
-Future research will be needed to determine the best way(s) to operationalize QMP ratios.
-Researchers can take inspiration from this study and earlier studies by @shaw2020measurement and @flake2022construct, as well as the criteria on measurement reporting as set out in the @aera2014standards.
+Additionally, it is not obvious from observing a QMP ratio whether good research practices were clearly violated.
+One might argue that any QMP is a sign of questionable research making any ratio greater than zero problematic.
+However, not all violations may have detrimental consequences or are relevant in all contexts.
+
+These challenges are potential threats to the validity of our assessment of QMPs.
+To assess the validity of QMP measurement, construct validity would not be appropriate as QMPs are no latent construct.
+Instead, validity can be evaluated based on the extent to which a measured QMP score can be used to predict other variables it is expected to be associated with.
+For this future research will be needed to develop a framework of the associations between QMPs and other variables, and then test whether measured QMP scores are associated with those variables.
+To develop this framework, researchers can use this study and earlier studies by @shaw2020measurement and @flake2022construct.
+To improve upon previous measures, the criteria on measurement reporting as set out in the @aera2014standards can be used as an additional source.
 
 A second limitation is that some of our tests were likely underpowered.
-Especially the tests on reliability, because of the small number of reported reliability scores, and multiple item scales with available data.
+Especially the tests on reliability, because of the small number of reported reliabilities, and multiple item scales with available data.
 However, this limitation also illustrates two key findings.
 One finding is that reliability was rarely reported for measures in both original articles and replication protocols.
-
-The other finding is that around half of the measures in our sample were single item-measures.
-The use of single item measures comes with psychometric risks [@diamantopoulos2012guidelines; @nunnally1978overview], and is more limited with respect to the type of reliability and validity evidence that can be determined [@sarstedt2016selecting; @shaw2020measurement].
-Because of these issues, it could even be argued that the use of single-item measures is a QMP in certain contexts.
+The other finding is that around half of the measures in our sample were single-item measures.
+The use of single-item measures comes with psychometric risks [@diamantopoulos2012guidelines; @nunnally1978overview] and is more limited with respect to the type of reliability and validity evidence that can be determined [@sarstedt2016selecting; @shaw2020measurement].
+Because of these issues, it could even be argued that using single-item measures is a QMP in certain contexts.
 
@@
 There are three main reasons why we believe protocols and articles remain comparable.
-Firstly, the majority of the measurements in our replication sample were modified in some way, it is therefore important that replication protocols still report on their measurement as it may deviate from the original.
-Secondly, articles are often also restricted in the amount of space they have available to devote to measurement, so space restrictions are no reason per se to not report important measurement information [@gardiner2019editorial].
-Thirdly, supplementary materials were also included as a valid information source, which increase the space available to describe the measurement, further equalizing reporting space in original articles and replication protocols.
-Still, future research may wish to analyze supplementary materials in greater detail, to investigate to what extent these materials cover measurement details in both replication protocols and original articles.
+First, most of the measurements in our replication sample were modified in some way, it is therefore important that replication protocols still report on their measurement as it may deviate from the original.
+Second, articles are often also restricted in the amount of space they have available to devote to measurement, so space restrictions in measurement reporting are not unique to replication protocols [@gardiner2019editorial].
+Third, supplementary materials were also included as a valid information source, which increased the space available to describe the measurement, further equalizing reporting space in original articles and replication protocols.
+Still, future research may wish to analyze supplementary materials in greater detail to investigate to what extent these materials cover measurement details in both replication protocols and original articles.
 
@@
 
-Finally, we note that we used an observational design which means that we cannot attach definitive causal directions to the relations observed in this study.
+Finally, we note that we used an observational design meaning that we cannot attach definitive causal directions to the relations observed in this study.
 To directly assess if there is a negative impact of reliability and QMPs on replicability, we would need experimental research.
-Future research could for example randomly assign original studies in a large scale replication project to either needing to report all relevant measurement information as noted down in Table 1 in @flake2020measurement, while other studies receive no such reporting requirements.
-Similarly, the requirement to use validated measures based on the criteria set out in section 1, 2, and 3 in the @aera2014standards standards, or lack thereof could be randomly assigned to conditions.
-Although such experimental designs would be the most direct way to assess causality, it would take tremendous coordination and funding to integrate original studies into a large scale replication project from the start.
+Future research could for example randomly assign original studies in a large-scale replication project to either needing to report all relevant measurement information as noted down in Table 1 in @flake2020measurement, while other studies receive no such reporting requirements.
+Similarly, the requirement to use validated measures based on the criteria set out in Sections 1, 2, and 3 in the @aera2014standards standards, or lack thereof could be randomly assigned to conditions.
+Although such experimental designs would be the most direct way to assess causality, it would take tremendous coordination and funding to integrate original studies into a large-scale replication project from the start.
 While such efforts are not unprecedented [@protzko2020high], alternative methods also exist to assess causal relations on observational data, at least to some extent.
@@
 Taking all the findings together, we formulated several recommendations.
-Firstly, reliable and valid measures are a prerequisite for credible findings.
-The observation that many measures are not reported with such evidence is worrying, because it obscures the credibility of findings, and hampers scientific progress.
-Therefore, we join earlier recommendations [@hogan2004empirical; @barry2014validity; @flake2020measurement; @flake2022construct] that establishing validity evidence for multiple item scales should become a community standard for credible research.
-Furthermore, reliability coefficient estimates for multiple item scales should by default always be reported, since these estimates can easily be obtained with most statistical software, and provide important information on a measure’s performance.
-Only researchers that can provide reasoning to the contrary for their research should be exempt from this default.
-
-Secondly, researchers should report their procedure and measurement in detail, as specified in for example Table 1 in @flake2020measurement, or section 3.6 in @apa2020publication on measures and measurement.
+First, reliable and valid measures are a prerequisite for credible findings.
+The observation that many measures are not reported with such evidence is worrying because it obscures the credibility of findings and hampers scientific progress.
+Therefore, we join earlier recommendations [@hogan2004empirical; @barry2014validity; @flake2020measurement; @flake2022construct] that establishing evidence for the validity of scales should become a community standard for credible research.
+Furthermore, reliability coefficient estimates for multiple-item scales should, by default, always be reported since these estimates can readily be obtained with most statistical software and provide important information on a measure’s performance.
+Only researchers who can provide reasoning to the contrary for their research should be exempt from this default.
+
+Second, researchers should report their procedure and measurement in detail, as specified in, for example, Table 1 in @flake2020measurement, or Section 3.6 in @apa2020publication on measures and measurement.
 This is important so that it can be mimicked in replications if needed.
-The remaining information that could not fit in the article can be made available on a public repository, such as the Open Science Framework [OSF\; @soderberg2018using] or Zenodo [@zenodo2024open].
+The remaining information that does not fit in the article can be made available on a public repository, such as the Open Science Framework [OSF\; @soderberg2018using] or Zenodo [@zenodo2024open].
 
@@
 It is crucial for an informative replication that the measurement is reliable or valid, otherwise it may be futile to attempt a direct replication [see also @nuijten2022assessing].
-If the measurement is insufficiently reliable or valid, we suggest that researchers instead use their resources to conduct a replication of a study with reliable, valid and well-documented measurement.
-When replicating another study is not an option, we advise the replicating researcher to first attempt a conceptual replication using reliable and valid measurement, or use both the original and their own preferred measure [as in @stoevenbelt2018rrr].
+If the measurement is insufficiently reliable or valid, we suggest that researchers instead use their resources to replicate a study with reliable, valid, and well-documented measurement.
+When replicating another study is not an option, we advise the replicating researcher to first attempt a conceptual replication using reliable and valid measurement or use both the original and their own preferred measure [as in @stoevenbelt2018rrr].
 Afterwards, a direct replication can be performed based on the conceptual replication to further assess the effect’s credibility.
@@
 
-Through our investigations into the reliability and reporting of measurement in the Many Labs replications and associated original studies, we found that reliability and validity evidence was often not reported.
+Through our investigations into the reliability and reporting of measurement in the Many Labs replications and associated original studies, we found that reliability and validity evidence was often missing from articles.
 Furthermore, QMPs that obscured important information needed to evaluate and reconstruct the measurement were common, especially in original research.
 We observed results suggesting that QMPs in turn related to the replicability of a finding.
-Results were less clear for reliability differences between original and replication, most likely because the analysis lacked of power to detect a difference.
+Results were less clear for reliability differences between original and replication, most likely because the analysis lacked the power to detect a difference.
 However, we did observe that around a quarter of measures showed signs of significant variation in reliability across labs.
-Combined these findings illustrate the need for widespread adoption of measurement reporting standards, and that researchers should consider the validity and reporting completeness of a study's measurement before attempting to replicate it.
+Combined, these findings illustrate the need for widespread adoption of measurement reporting standards and that researchers should consider the validity and reporting completeness of a study’s measurement before attempting to replicate it.
+
+## Conflicts of Interest
+
+The author(s) declare that there were no conflicts of interest with respect to the authorship or the publication of this article.
 
@@
 
-The preparation of this article was supported by the veni grant VI.Veni.201G.003 awarded to Michèle Nuijten, and the vici grant ???
-awarded to Jelte M.
-Wicherts from the Netherlands Organization for Scientific Research (NWO).
+The preparation of this article was supported by the Veni grant VI.Veni.201G.003 awarded to Michèle Nuijten, and the Vici grant VI.C.221.100 awarded to Jelte M.
+Wicherts from the Dutch Research Council (NWO).
 

### 2024-10-21 Scripts/source_script.R

@@ -486,7 +486,12 @@ betareg_output_to_apa_full<- function(betareg_output, coefficient_number = 2){
   CI_string <- paste0("95\\% CI $[", apa_num(CI_LO), ", ", 
                       apa_num(CI_HI), "]$, ")
   z_string <- paste0("$z = ", apa_num(z_value), "$, ")
-  p_string <- paste0("$p = ", apa_p(p_value), "$")
+  
+  if(p_value < 0.001){
+    p_string <- paste0("$p ", apa_p(p_value), "$")
+  } else{
+    p_string <- paste0("$p = ", apa_p(p_value), "$")
+  }
   
   
   return(paste0(estimate_string, CI_string, z_string, p_string))

### 2024-10-23 Scripts/Manuscript/manuscript.Rmd
clean-up before uploading pre-print.

@@
 ---
-title             : "Assessing Reliable and Valid Measurement for Informative Replications in Psychology"
+title             : "Assessing Reliable and Valid Measurement as a Prerequisite for Informative Replications in Psychology"
 shorttitle        : "Measurement and Informative Replications"
@@
 author: 
-  - name          : "Goos, Cas"
+  - name          : Cas Goos
     affiliation   : "1"
@@
 
-  - name          : "Bakker, Marjan"
+  - name          : Marjan Bakker
     affiliation   : "1"
 
-  - name          : "Wicherts, Jelte M."
+  - name          : Jelte M. Wicherts
     affiliation   : "1"
 
-  - name          : "Nuijten, Michèle B."
+  - name          : Michèle B. Nuijten
     affiliation   : "1"
 
-affiliation:
-  - id            : "1"
-    institution   : "Tilburg University"
-
 authornote: |
-  1 Department of Methodology and Statistics, Tilburg School of Social and Behavioral Sciences, Tilburg University, Tilburg, NL.
-
   The authors made the following contributions.
@@
 keywords          : "reliability, construct validity, measurement, reporting, questionable measurement practices, replicability, credibility, psychology"
-wordcount         : "159"
+wordcount         : "158"
 
@@
     \makeatother
+  - \renewcommand\author[1]{}
+  - \renewcommand\affiliation[1]{}
+  - \authorsnames[1, 1, 1, 1]{Cas Goos, Marjan Bakker, Jelte M. Wicherts, Michèle B. Nuijten}
+  - \authorsaffiliations{{Department of Methodology and Statistics, Tilburg School of Social and Behavioral Sciences, Tilburg University, Tilburg, NL.}}
 
@@
 
-classoption       : "man"
+classoption       : man
 output            : papaja::apa6_pdf
@@
 Unfortunately, the Reproducibility Project: Psychology [RPP\; @osc2015estimating] and other large-scale replication projects that sought to replicate earlier and seminal findings [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many] typically yielded smaller effects in replications compared to original studies, with Many-Labs projects featuring different locations and samples.
-In response to this string of failed replications, there was widespread alarm regarding the credibility and robustness of findings in psychological science [@hughes2018psychology; @giner2019crisis], and efforts to explain the low replication rate.
+In response to this string of failed replications, there was widespread alarm regarding the credibility and robustness of findings in psychological science [@hughes2018psychology; @giner2019crisis], combined with efforts to explain the low replication rate.
 The factors that have been proposed include questionable research practices [@simmons2011false; @john2012measuring; @cumming2014new; @wicherts2016degrees], questionable reporting practices [@bakker2011mis; @nuijten2016prevalence], and biased publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science].
@@
 
-Replicability and reliable and valid measurement are essential elements of the credibility of a finding, and are related to each other.
+Replicability and reliable and valid measurement are essential to the credibility of a finding, and are related to each other.
 Indeed, recent studies have illustrated that both the reliability of the measure [@stanley2014expectations] and the reporting of information relevant to demonstrating the validity of the measurement [@shaw2020measurement; @flake2017construct; @flake2020measurement] may predict the replicability of psychological findings.
@@
 Furthermore, only eight of the 40 translated scales contained validity evidence for the translated version of the scale.
-Measures were similarly modified between original and replication in other ways without evidence showing that the modification did not invalidate the measurement.
+Evidence showing that this and other modifications between original and replication did not invalidate the measurement was rarely reported.
 
@@
 While differences in these variances across samples is inevitable, these differences should not be systematic between replication and original samples for their results to remain comparable.
-Therefore, we investigated the reliability in replication (Research Question 1a; RQ1a ) and original psychological research (RQ1b).
+Therefore, we investigated the reliability in replication (Research Question 1a; RQ1a[^1]) and original psychological research (RQ1b).
 The Many Labs studies were intended as direct replications, which implies that deviations from the original research should be irrelevant for testing the effect [@nosek2022replicability], including systematic differences in reliability (Hypothesis 1; H1).
@@
 We conceptually replicate the findings on measurement reporting of @flake2022construct by documenting the frequency of QMPs in replications of psychological research (RQ4a) and original psychological research (RQ4b).
-@flake2022construct found that RPP replications averaged more QMPs than original studies.
+@flake2022construct found that RPP replications contained on average more QMPs than original studies.
 We hypothesized that for our Many Labs sample, QMPs would be more frequent in original psychological research than in replication research (H4), because the Many Labs replications used structured protocols documenting the measurement.
 
-QMPs obscure information about a particular measurement, which may cause issues reconstructing that measurement in subsequent replication attempts.
+QMPs obscure information about a particular measurement, which may cause issues when reconstructing that measurement in subsequent replication attempts.
 Because resulting deviations in measurement may be partly responsible for deviations in replication and original effects [@flake2022construct], we investigated whether QMPs in replication protocols were associated with the replication outcome (RQ5).
 A reduction in QMPs corresponds to greater transparency in measurement reporting.
-In line with earlier research finding that other transparency-related practices are associated with more robust estimates of effects [@wicherts2011willingness; @protzko2020high], we expected QMPs in replications to be negatively associated with replication success (H5).
-
-@flake2022construct proposed that QMPs in original articles may impede recreating measurements for replications, and indeed @shaw2020measurement found evidence for such a spill-over effect for validity.
+In line with earlier research finding that other transparency-related practices are associated with more robust estimates of effects [@wicherts2011willingness], we expected QMPs in replications to be negatively associated with replication success (H5).
+
+@flake2022construct proposed that QMPs in original articles may impede recreating measurements for replications, and indeed @shaw2020measurement found evidence for such a spill-over effect with validity.
 In line with this research, we investigated the association between QMPs in original research and QMPs in replications of psychological research (RQ6).
@@
 
-We used the published reports of the Many Labs projects [@klein2014investigating; @ebersole2016many; @ebersole2020many; @klein2018many]) to determine replication success based on the reported significance of the meta-analytic effect.
+We used the published reports of the Many Labs projects [@klein2014investigating; @ebersole2016many; @ebersole2020many; @klein2018many] to determine replication success based on the reported significance of the meta-analytic effect.
 An effect was considered successfully replicated if the meta-analytic effect was in the same direction as the original effect and had a p-value lower than .05.
@@
 Table \@ref(tab:ReplicationNrTable) shows the number of replication sets, measures, and measures per study, as well as the proportion of successful replications, for each of the Many Labs separately and in total.
+Because each replication was nested within one of four Many Labs projects, our data had a multilevel structure.
+Furthermore, `r sum(data_h456_replications$appearance != 1)` replications used more than one primary measure, resulting in `r nrow(data_h456_replications)` measures in both `r sum(data_h456_replications$appearance == 1)` replications protocols and `r sum(coded_data_original$appearance == 1)` original articles[^2].
+Of these `r nrow(data_h456_replications)` measures `r sum(data_h456_replications$mod_check == "True")` were modified from the original to the replication[^3].
+In the replications, the data of responses on the measures was further nested in several labs per replication.
+The combined sample size of all labs in the replications was on average `r round(mean(data_h456_replications[data_h456_replications$appearance == 1]$N), 0)`, which was approximately `r round(mean(data_h456_replications[data_h456_replications$appearance == 1]$N) / mean(data_h456_original[data_h456_original$appearance == 1 & !is.na(data_h456_original$N),]$N), 0)` times larger than the average in original studies, which were conducted in single labs.
+
+[^2]: Initially the original articles contained 3 more measures than the replication protocols.
+This difference was due to the way that the moral foundations questionnaire was framed in the original article compared to in the replication protocol.
+In the original article it was framed as measuring five different moral foundations, while in the replication protocol the measure assessed the two overarching categories that were used to test the main effect in both the original and replication research.
+The measurement information reported was comparable across all five categories, and thus it was deemed that the measurement could be reduced to reflect two overarching categories facilitate easier comparison between measurement in original and replication.
+
+[^3]: For 7 measures the number of items were modified from the original article to the replication.
+To check whether or not this had a confounding impact on our results, we re-ran the analyses testing the hypotheses excluding data from these studies (see [Supplementary Analyses E](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_item_reduced_measures_analyses.Rmd)).
+We found that removing these measures’ data had minimal impact on the overall results.
+Therefore, the results presented below are based on data from all the measures.
 
@@
 
-Because each replication was nested within one of four Many Labs projects, our data had a multilevel structure.
-Furthermore, `r sum(data_h456_replications$appearance != 1)` replications used more than one primary measure, resulting in `r nrow(data_h456_replications)` measures in both `r sum(data_h456_replications$appearance == 1)` replications protocols and `r sum(coded_data_original$appearance == 1)` original articles[^2].
-Of these `r nrow(data_h456_replications)` measures `r sum(data_h456_replications$mod_check == "True")` were modified from the original to the replication[^3].
-In the replications, the data of responses on the measures was further nested in several labs per replication.
-The combined sample size of all labs in the replications was on average `r round(mean(data_h456_replications[data_h456_replications$appearance == 1]$N), 0)`, which was approximately `r round(mean(data_h456_replications[data_h456_replications$appearance == 1]$N) / mean(data_h456_original[data_h456_original$appearance == 1 & !is.na(data_h456_original$N),]$N), 0)` times larger than the average in original studies, which were conducted in single labs.
-
-[^2]: Initially the original articles contained 3 more measures than the replication protocols.
-This difference was due to the way that the moral foundations questionnaire was framed in the original article compared to in the replication protocol.
-In the original article it was framed as measuring five different moral foundations, while in the replication protocol the measure assessed the two overarching categories that were used to test the main effect in both the original and replication research.
-The measurement information reported was comparable across all five categories, and thus it was deemed that the measurement could be reduced to reflect two overarching categories facilitate easier comparison between measurement in original and replication.
-
-[^3]: For 7 measures the number of items were modified from the original article to the replication.
-To check whether or not this had a confounding impact on our results, we re-ran the analyses testing the hypotheses excluding data from these studies (see [Supplementary Analyses E](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_item_reduced_measures_analyses.Rmd)).
-We found that removing these measures’ data had minimal impact on the overall results.
-Therefore, the results presented below were based on data from all the measures.
-
 Because of this multilevel structure we preregistered multilevel random-intercept and random-slope models alongside our single-level regression models for testing Hypothesis 3, 5, and 6.
@@
 Figure \@ref(fig:Plot23AlphaCode) displays the estimates of tau, which indicates the differences in true reliability scores between labs for a given measure.
-For `r sum(data_h23_avg$QEp > .05)` measures, the tau estimate was not significantly different from 0, while the true variation in reliability across labs was significant for `r apa_num(sum(data_h23_avg$QEp <= .05), numerals = FALSE)` measures.
-The true reliability was quite variable for some measures.
+For `r sum(data_h23_avg$QEp > .05)` measures, the tau estimate was not significantly different from 0, meaning the true variation in reliability across labs was not significant.
+However, for the other `r apa_num(sum(data_h23_avg$QEp <= .05), numerals = FALSE)` measures the true reliability was quite variable.
 For instance, the estimate of the standard deviation of the true reliability of the top measure in the graph (a measure of conscientiousness from @gosling2003very used in the replication of @defruyt2000cloninger) equaled `r apa_num(data_h23_avg$tau[data_h23_avg$g == "De Fruyt et al.
@@
 First, it shows that almost half of the measures in both replication (N = `r apa_num(sum(data_h456_replications$N_items == "1 item measure"))`) and original research (N = `r apa_num(sum(data_h456_original$N_items == "1 item measure"))`) were single-item measures.
-When looking at the multiple-item measures, the graph illustrates that r N_reported_reliabilities_replications` measures in the replication protocols (`r apa_num((as.numeric(N_reported_reliabilities_replications_number_style) / sum(data_h456_replications$N_items != "1 item measure")) * 100, digits = 1)` \%) and `r N_reported_reliabilities_original` measures in the original articles (`r apa_num((as.numeric(N_reported_reliabilities_original) / sum(data_h456_original$N_items != "1 item measure")) * 100, digits = 1)` \%) reported a reliability coefficient.
+When looking at the multiple-item measures, the graph illustrates that `r N_reported_reliabilities_replications` measures in the replication protocols (`r apa_num((as.numeric(N_reported_reliabilities_replications_number_style) / sum(data_h456_replications$N_items != "1 item measure")) * 100, digits = 1)` \%) and `r N_reported_reliabilities_original` measures in the original articles (`r apa_num((as.numeric(N_reported_reliabilities_original) / sum(data_h456_original$N_items != "1 item measure")) * 100, digits = 1)` \%) reported a reliability coefficient.
 The most commonly reported reliability coefficient was Cronbach’s Alpha, which accounted for `r apa_num(sum(data_h456_replications$reliability_type == "alpha"), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(data_h456_original$reliability_type == "alpha"))` in the original articles.
@@
 # QMP data.
+
 reporting_data <- rbind(data_h456_original, data_h456_replications)
@@
 
-Reliability was more commonly reported in original (N = `r N_reported_reliabilities_original`; `r apa_num((as.numeric(N_reported_reliabilities_original) / nrow(data_h456_original)) * 100, digits = 1)` \%) as compared to replication research = `r N_reported_reliabilities_replications_number_style`; `r apa_num((as.numeric(N_reported_reliabilities_replications_number_style) / nrow(data_h456_replications)) * 100, digits = 1)` \%), $\chi^{2}$(`r apa_num(reliability_reporting_test_result$parameter)`) = `r apa_num(reliability_reporting_test_result$statistic)`, *p* = `r apa_p(reliability_reporting_test_result$p.value)`.
+Reliability was more commonly reported in original (N = `r N_reported_reliabilities_original`; `r apa_num((as.numeric(N_reported_reliabilities_original) / nrow(data_h456_original)) * 100, digits = 1)` \%) as compared to replication research (N = `r N_reported_reliabilities_replications_number_style`; `r apa_num((as.numeric(N_reported_reliabilities_replications_number_style) / nrow(data_h456_replications)) * 100, digits = 1)` \%, $\chi^{2}$(`r apa_num(reliability_reporting_test_result$parameter)`) = `r apa_num(reliability_reporting_test_result$statistic)`, *p* = `r apa_p(reliability_reporting_test_result$p.value)`).
 Validity evidence was similarly reported infrequently.
 Validity evidence from a factor analysis was reported in `r apa_num(sum(data_h456_original$sel_psychometric_evidence_REV != "None" & data_h456_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` original articles, while in only `r apa_num(sum(data_h456_replications$sel_psychometric_evidence_REV != "None" & data_h456_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` replications.
-This difference was not significant, however the total number of factor analyses reported was low  ($\chi^{2}$(`r apa_num(factor_reporting_test_result$parameter)`) = `r apa_num(factor_reporting_test_result$statistic)`, *p* = `r apa_p(factor_reporting_test_result$p.value)`).
+This difference was not significant ($\chi^{2}$(`r apa_num(factor_reporting_test_result$parameter)`) = `r apa_num(factor_reporting_test_result$statistic)`, *p* = `r apa_p(factor_reporting_test_result$p.value)`), however the total number of factor analyses reported was low.
 
@@
 The top part of Figure \@ref(fig:Plot456Code) displays the distributions of the total QMP ratio for both original articles and replication protocols, showing that the average QMP ratio in replication protocols was smaller (`r apa_num(Mean_Rat_Rep)`) than in original articles (`r apa_num(Mean_Rat_Org)`).
-The bottom of Figure \@ref(fig:Plot456Code) displays the observed QMP ratios per QMP type for both original articles and replication protocols, showing that original articles tended to contain fewer Definition QMPs, but more selection and operationalization QMPS, with Quantification QMPs being comparable.
+The bottom of Figure \@ref(fig:Plot456Code) displays the observed QMP ratios per QMP type for both original articles and replication protocols, showing that original articles tended to contain fewer Definition QMPs, but more selection and operationalization QMPs, with Quantification QMPs being comparable.
 The number of measures that were modified also differed between original and replication.
@@
 # re-ordering the QMP-types, because it didn't save
-plot_456_data$QMP_type <- factor(plot_456_data$QMP_type, levels = c("Definition", "Selection", "Operationalization", "Quantification", "Modification", "Total"))
+plot_456_data$QMP_type <- factor(plot_456_data$QMP_type, levels = c("Definition", "Selection", "Operationalisation", "Quantification", "Modification", "Total"))
 
@@
 
+## Code for exporting figures to high resolution PNGs.
+# png("manuscript_files/figure-self-export/plot_46_revised.png", width=1800, height=1200, res=300)
+## #PLACE FIGURE CODE HERE#
+# dev.off()
 ```
@@
 @stanley2014expectations illustrated that measurement error, when not attenuated for, can impact replication assessments.
-However, we observed no relation between reliability and replicability.
+However, we did not observe a relation between reliability and replicability.
 This result also runs counter to the fact that according to statistical theory, the increased noise in the data implied by lower reliability decreases the effect size estimates based on those data.
@@
 
-Third, the replication protocols were written before data were collected, which means no measurement based on these protocols had not taken place yet.
+Third, the replication protocols were written before data were collected, which means measurement based on these protocols had not taken place yet.
 As a result, no data were available yet from which the replicating researchers could have calculated reliability and validity.
@@
 It may still represent a problem, however, because original articles similarly rarely reported evidence on reliability and validity.
-This implies that the replications commonly picked measures for which validity could not be checked.
+This implies that the replications commonly picked measures for which reliability and validity could not be checked.
 
@@
 Furthermore, these hypotheses were supported by only one of the multilevel models.
-However, these models were limited in group and sample size, leading to results that are somewhat uncertain.
+These were limited in group and sample size however, making their results uncertain.
 
@@
 Our study had several limitations.
-We encountered Including challenges we encountered in operationalizing QMPs.
+We encountered challenges in operationalizing QMPs.
 Whereas previous research has focused on descriptives of specific QMPs detrimental to construct validity [@flake2022construct; @shaw2020measurement], we combined all coded QMPs together as an index to assess measurement practices and evaluate their impact on replicability.
@@
 
-Another challenge in constructing one overarching QMP variable was how to quantify it..
+Another challenge in constructing one overarching QMP variable was how to quantify it.
 We constructed ratios to cancel out the effects of non-applicable items.
@@
 One might argue that any QMP is a sign of questionable research making any ratio greater than zero problematic.
-However, not all violations may have detrimental consequences or are relevant in all contexts.
+However, not all violations may have detrimental consequences or be relevant in all contexts.
 
 These challenges are potential threats to the validity of our assessment of QMPs.
-To assess the validity of QMP measurement, construct validity would not be appropriate as QMPs are no latent construct.
-Instead, validity can be evaluated based on the extent to which a measured QMP score can be used to predict other variables it is expected to be associated with.
+The validity of QMPS could be evaluated based on the extent to which a measured QMP score can be used to predict other variables it is expected to be associated with.
 For this future research will be needed to develop a framework of the associations between QMPs and other variables, and then test whether measured QMP scores are associated with those variables.
 To develop this framework, researchers can use this study and earlier studies by @shaw2020measurement and @flake2022construct.
-To improve upon previous measures, the criteria on measurement reporting as set out in the @aera2014standards can be used as an additional source.
+To improve upon previous measures of QMPs, the criteria on measurement reporting as set out in the @aera2014standards can be used as an additional source.
 
 A second limitation is that some of our tests were likely underpowered.
-Especially the tests on reliability, because of the small number of reported reliabilities, and multiple item scales with available data.
+Especially the tests on reliability, because of the small number of reported reliabilities and multiple item scales with available data.
 However, this limitation also illustrates two key findings.
@@
 Although such experimental designs would be the most direct way to assess causality, it would take tremendous coordination and funding to integrate original studies into a large-scale replication project from the start.
-While such efforts are not unprecedented [@protzko2020high], alternative methods also exist to assess causal relations on observational data, at least to some extent.
+Alternative methods exist to assess causal relations on observational data, at least to some extent.
 @rohrer2018thinking has suggested researchers make use of Directed Acyclic Graphs to investigate causality in (non-)experimental settings by systematically accounting for confounding influences on an effect.
@@
 Therefore, we join earlier recommendations [@hogan2004empirical; @barry2014validity; @flake2020measurement; @flake2022construct] that establishing evidence for the validity of scales should become a community standard for credible research.
-Furthermore, reliability coefficient estimates for multiple-item scales should, by default, always be reported since these estimates can readily be obtained with most statistical software and provide important information on a measure’s performance.
+Furthermore, reliability coefficient estimates for multiple-item scales of a single construct should, by default, always be reported since these estimates can readily be obtained with most statistical software and provide important information on a measure’s performance.
 Only researchers who can provide reasoning to the contrary for their research should be exempt from this default.

### 2024-10-23 Scripts/source_script.R

@@ -854,11 +854,11 @@ data_prep_plot_456 <- function(Data_original, Data_replication){
   
   # creating nicer names for in the graph
   levels(Plot_456_ratio_data_REV$QMP_type) <- c("Definition", 
-                                                "Operationalization",
+                                                "Operationalisation",
                                                 "Selection", "Quantification", 
                                                 "Modification", "Total")
   levels(Plot_456_ratio_rep_data_REV$QMP_type) <- c("Definition", 
-                                                    "Operationalization", "Selection", 
+                                                    "Operationalisation", "Selection", 
                                                     "Quantification", "Modification", 
                                                     "Total")
   

### 2024-10-23 Scripts/Manuscript/manuscript.Rmd
additional clean-up before pre-print

@@
 ## Credibility & Measurement
+
 Psychological constructs, such as affective states or intelligence, cannot be measured directly.
@@
 This manuscript was created in RStudio [*v`r rstudioapi::versionInfo()$version`*\; @R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [*v`r getNamespaceVersion("worcs")[[1]]`*\; @vanlissaWORCS2021] to ensure reproducibility and transparency.
-All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> and <https://osf.io/9r8yt/>.
+All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> and <https://osf.io/9r8yt/> (DOI: 10.17605/OSF.IO/9R8YT).
 
@@
 ### Replication Protocols
+
 The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each set of replications of a given original study across multiple labs.
@@
 First, it shows that almost half of the measures in both replication (N = `r apa_num(sum(data_h456_replications$N_items == "1 item measure"))`) and original research (N = `r apa_num(sum(data_h456_original$N_items == "1 item measure"))`) were single-item measures.
-When looking at the multiple-item measures, the graph illustrates that `r N_reported_reliabilities_replications` measures in the replication protocols (`r apa_num((as.numeric(N_reported_reliabilities_replications_number_style) / sum(data_h456_replications$N_items != "1 item measure")) * 100, digits = 1)` \%) and `r N_reported_reliabilities_original` measures in the original articles (`r apa_num((as.numeric(N_reported_reliabilities_original) / sum(data_h456_original$N_items != "1 item measure")) * 100, digits = 1)` \%) reported a reliability coefficient.
+When looking at the multiple-item measures, the graph illustrates that `r N_reported_reliabilities_replications` measures in the replication protocols (`r apa_num((as.numeric(N_reported_reliabilities_replications_number_style) / sum(data_h456_replications$N_items != "1 item measure")) * 100, digits = 1)` %) and `r N_reported_reliabilities_original` measures in the original articles (`r apa_num((as.numeric(N_reported_reliabilities_original) / sum(data_h456_original$N_items != "1 item measure")) * 100, digits = 1)` %) reported a reliability coefficient.
 The most commonly reported reliability coefficient was Cronbach’s Alpha, which accounted for `r apa_num(sum(data_h456_replications$reliability_type == "alpha"), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(data_h456_original$reliability_type == "alpha"))` in the original articles.
@@
 
-Reliability was more commonly reported in original (N = `r N_reported_reliabilities_original`; `r apa_num((as.numeric(N_reported_reliabilities_original) / nrow(data_h456_original)) * 100, digits = 1)` \%) as compared to replication research (N = `r N_reported_reliabilities_replications_number_style`; `r apa_num((as.numeric(N_reported_reliabilities_replications_number_style) / nrow(data_h456_replications)) * 100, digits = 1)` \%, $\chi^{2}$(`r apa_num(reliability_reporting_test_result$parameter)`) = `r apa_num(reliability_reporting_test_result$statistic)`, *p* = `r apa_p(reliability_reporting_test_result$p.value)`).
+Reliability was more commonly reported in original (N = `r N_reported_reliabilities_original`; `r apa_num((as.numeric(N_reported_reliabilities_original) / nrow(data_h456_original)) * 100, digits = 1)` %) as compared to replication research (N = `r N_reported_reliabilities_replications_number_style`; `r apa_num((as.numeric(N_reported_reliabilities_replications_number_style) / nrow(data_h456_replications)) * 100, digits = 1)` %, $\chi^{2}$(`r apa_num(reliability_reporting_test_result$parameter)`) = `r apa_num(reliability_reporting_test_result$statistic)`, *p* = `r apa_p(reliability_reporting_test_result$p.value)`).
 Validity evidence was similarly reported infrequently.
@@
 We reasoned that most of the included measures should theoretically tap into a single construct, so evidence for unidimensionality would serve as a proxy for evidence of higher construct validity.
-We found that `r sum(cfa_results$Single_factor == "Yes", na.rm = TRUE)` of these measures (`r apa_num((sum(cfa_results$Single_factor == "Yes", na.rm = TRUE) / nrow(cfa_results)) * 100, digits = 1)` \%) met our criteria for unidimensionality (see [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd) for further details).
+We found that `r sum(cfa_results$Single_factor == "Yes", na.rm = TRUE)` of these measures (`r apa_num((sum(cfa_results$Single_factor == "Yes", na.rm = TRUE) / nrow(cfa_results)) * 100, digits = 1)` %) met our criteria for unidimensionality (see [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd) for further details).
 
@@
 However, it is worth noting that the spillover effect was only observed for QMPs coded with the revised coding protocol.
-Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd for results based on the initial protocol).
+Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd%20for%20results%20based%20on%20the%20initial%20protocol).
 Furthermore, these hypotheses were supported by only one of the multilevel models.

### 2025-06-27 Scripts/Manuscript/manuscript.Rmd
Rough First Redraft -Discussion of the Descriptive Version of the study (version 2)

--- 2024-10-23 Scripts/Manuscript/manuscript.Rmd
@@
   For a replication to be informative, measurement should be reliable and valid in both original and replication studies.
-  Recent studies have identified problems with measurement and measurement reporting in both original and replication studies, although the association between measurement and replicability remains unclear.
-  We investigated the reliability and measurement reporting of 77 measures within 56 Many Labs replications and related original articles [@klein2014investigating; @ebersole2016many; @klein2018many; @ebersole2020many] and studied their association with replicability.
-  We found that not all measures were sufficiently reliable across contexts, and that only few measures were accompanied with reliability and validity evidence. 
-  Furthermore, “questionable measurement practices” (QMPs) in replication studies were associated with lower replicability, while original study reliability was not. 
-  These results corroborate existing findings that construct validity in published research is often unknown, which may complicate replication research. 
-  We offer suggestions on improving measurement practices and argue that reported measurement information should inform the decision to replicate.
-
-keywords          : "reliability, construct validity, measurement, reporting, questionable measurement practices, replicability, credibility, psychology"
-wordcount         : "158"
+
+keywords          : "reliability, construct validity, measurement, reporting, questionable measurement practices, replications, informative replications, psychology"
+wordcount         : "1"
 
@@
 library(worcs)
-library(tidyr)
-library(betareg)
-library(lmerTest)
+library(lavaan)
 library(psych)
+library(metafor)
 library(forcats)
-library(GPArotation)
 library(ggplot2)
-library(ggridges)
-library(GGally)
-library(ggforce)
 library(grid)
-library(gridExtra)
-library(metafor)
-library(sandwich)
-library(lmtest)
-
-# loading source script
-source(file = "../source_script.R")
-
-# Code below loads the processed data. The raw data was prepared for analysis in 'prepare_data.R.
+
+# loading script with helper functions
+# source(file = "../helper_functions.R") !!!needs to still be created
+
+# Code below loads all data. The raw data was loaded within the 'prepare_data.R script.
 load_data()
 
-# creates a reference list for all used R packages and the installed R version (does not automatically include Rstudio)
+# the code below removes the raw data to preserve disk space.
+# If you want to rerun the data cleaning and preparations steps, DO NOT run
+# this code.
+# If you want to only rerun the analyses, YOU CAN run the code below.
+rm(coded_data_initial_raw, coded_data_revised_raw, coded_data_vignette_raw,
+   data_2.10.1, data_2.12, data_2.15, data_2.19.1, data_2.2, data_2.20, 
+   data_2.23, data_2.3, data_2.4.1, data_2.4.2, data_2.8.2, data_3.5, data_5.1,
+   data_5.4, data_5.5, data_5.7, data_5.9.1, data_ml1, data_ml3)
+
+# creates a reference list for all used R packages and the installed R version 
+# (does not include Rstudio)
 r_refs("r-references.bib")
@@
 # Seed for random number generation
-set.seed(17042023)
+set.seed(26052025)
 knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
@@
 
+```{r helper_functions}
+##### PUT THIS ALL IN A SEPARATE R SCRIPT FILE.
+
+# Function for storing data openly in the intermediate data folder
+saving_to_intermediate_data <- function(data){
+  open_data(data = data, filename = paste0(paste0(
+    "Data/IntermediateData/", deparse(substitute(data))), ".csv"),
+    codebook = NULL, value_labels = NULL) 
+}
+
+# Function for storing data openly in the analysis data folder
+saving_to_analysis_data <- function(data){
+  open_data(data = data, filename = paste0(paste0(
+    "Data/AnalysisData/", deparse(substitute(data))), ".csv"),
+    codebook = NULL, value_labels = NULL) 
+}
+
+# function for changing QMP data to their ratio equivalent
+Create_QMP_descriptive_case <- function(practice_name, original_coded_var, replication_coded_var){
+  # add practice name to first row
+  Practice <- practice_name
+
+  # Sum all QMP/GMP (Good Measurement Practice), keeping NA items out of
+  # the equation
+  original_n_QMPs <- sum(original_coded_var == "FALSE", na.rm = TRUE)
+  replication_n_QMPs <- sum(replication_coded_var == "FALSE", na.rm = TRUE)
+
+  original_n_GMPs <- sum(original_coded_var == "TRUE", na.rm = TRUE)
+  replication_n_GMPs <- sum(replication_coded_var == "TRUE", na.rm = TRUE)
+
+  # calculating the N of applicable items for originals
+  N_applicable_original <- original_n_QMPs + original_n_GMPs
+
+  # checking that we are not dividing by 0, and then calculating the ratio of 
+  # QMPs for applicable items for originals
+  if(N_applicable_original != 0){
+    QMP_percentage_original <- round(original_n_QMPs / (N_applicable_original), 2)
+  } else{
+    QMP_percentage_original <- 0
+  }
+
+  # calculating the N of applicable items for replications
+  N_applicable_replication <- replication_n_QMPs + replication_n_GMPs
+
+  # checking that we are not dividing by 0, and then calculating the ratio of 
+  # QMPs for applicable items for replications
+  if(N_applicable_replication != 0){
+    QMP_percentage_replication <- round(replication_n_QMPs / (N_applicable_replication), 2)
+  } else{
+    QMP_percentage_replication <- 0
+  }
+
+  # calculating the Phi coefficient to estimate the relation between variables
+  Phi <- phi(matrix(c(original_n_QMPs, original_n_GMPs, replication_n_QMPs, 
+                      replication_n_GMPs), nrow = 2, byrow = TRUE))
+
+  return(c(Practice, QMP_percentage_original, N_applicable_original, QMP_percentage_replication, N_applicable_replication, Phi))
+}
+
+```
+
 <!-- Introduction -->
 
-Findings from psychological research should be credible to build and extend upon them.
-A credible finding must be replicable [@vazire2022CredibilityReplicabilityImproving], such that the observed effect is sufficiently comparable across the original study and subsequent replications in new samples and using nearly identical designs [@nosek2022replicability].
-In this article, we investigate how the credibility of psychological findings relates to problems in psychological measurement and how measurement problems may affect subsequent replications.
-
-Unfortunately, the Reproducibility Project: Psychology [RPP\; @osc2015estimating] and other large-scale replication projects that sought to replicate earlier and seminal findings [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many] typically yielded smaller effects in replications compared to original studies, with Many-Labs projects featuring different locations and samples.
-In response to this string of failed replications, there was widespread alarm regarding the credibility and robustness of findings in psychological science [@hughes2018psychology; @giner2019crisis], combined with efforts to explain the low replication rate.
-The factors that have been proposed include questionable research practices [@simmons2011false; @john2012measuring; @cumming2014new; @wicherts2016degrees], questionable reporting practices [@bakker2011mis; @nuijten2016prevalence], and biased publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science].
-Another important factor is the impact of measurement-related challenges on replicability and credibility.
-
-## Credibility & Measurement
-Psychological constructs, such as affective states or intelligence, cannot be measured directly.
-Psychological measurements involve random measurement errors and uncertainties about whether the targeted construct is indeed well reflected in the scores retrieved from the measurement procedure.
+In psychological research we are often interested in establishing a robust effect involving one or more latent constructs (e.g., IQ and conscientiousness) that describes a psychological phenomenon (like increased conscientiousness causing a person to develop higher IQ).
+However in the wake of the replication crisis the robustness of effects in psychology has been called into question.
+The Reproducibility Project: Psychology [RPP\; @osc2015estimating] and other large-scale replication projects [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many] and typically yielded smaller effects in replications compared to original studies.
+Replicability is one of the key ways to establish the robustness of an effect (Nosek RRR & …).
+If an effect does not replicate, it is likely not robust.
+Numerous factors have been proposed to explain why the original effects did not appear robust, including questionable research practices [@simmons2011false; @john2012measuring; @cumming2014new; @wicherts2016degrees], questionable reporting practices [@bakker2011mis; @nuijten2016prevalence], biased publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science], and more.
+
+These replication efforts and the subsequent lines of research have been of instrumental value in determining the lack of robustness in effects, uncovering what the causes of this lack of robustness are, and spearheading initiatives like … to help improve the robustness of effects.
+However, robustness was only one aspect of the goal highlighted at the beginning of this article, the other aspect, the fact that the effect should describe a true psychological phenomenon has received relatively less attention, although this is changing (SOME CITATIONS).
+
+In this article, we contribute to the rising research investigating the soundness of measurement in research.
+After all, a true psychological phenomenon is requires accurate measurement on the relevant constructs.
+Our aim is to create a greater understanding of the extent to which this.
+We provide a descriptive account of the measurement reporting practices in the Many Labs replications and related original research, in tandem with the measure’s reliability and internal structure analyzed from the accompanying openly available data.
+
+## Measurement Quality
+
+To understand a psychological phenomenon you need to be able to accurately capture the relevant constructs.
+While this premise underlines the core idea behind the use of measures for psychological constructs, it is difficult to guarantee in practice.
+In general, there are two aspects of a measurement between which we distinguish: validity and reliability.
+What complicates things is that there are multiple aspects to validity and multiple ways to assess these aspects of validity and reliability.
+So a researcher needs to know which type of assessment for validity and reliability is important for a measure, and on top of that it can be a complicated task to establish validity and reliability.
+
+Validity is an umbrella term for many different types of validity (construct, predictive, content, internal, external, etc.) and applies to (nearly) all aspects of the research design (CITATIONs INCLUDING VAZIRE et al.).
+For the purposes of this research we focus on construct validity of the applied measurement, which includes the measure and some aspects of the research design involving the administration of the measure.
+Construct validity refers to … .
+It is key to (relevant for nearly all measurement to some extent, because …) … .
+Evaluating it requires … and …, which in practice means … and … .
+!!!make sure that this section highlights something about construct validity relevant for our research that most psychologists may not actively realize.!!!
 
 Reliability estimates provide an indication of how consistent the responses on a measurement are.
+…something about what this consistency is over [might relate to the different types: in CTT it is the correlation between scores on two equivalent forms of the test; but we are more focused on consistency as a basic requirement for an essentially valid measure, because no reliability means no validity].
 Reliability is a critical first step to obtaining credible findings.
 Because if the scores on a measure are not consistent with themselves, it is unlikely that any effect associated with the measure can credibly be established.
-Psychometrics offers various ways to assess reliability empirically [@nunnally1978overview; @mellenbergh2011conceptual].
-
-Moreover, researchers cannot claim to have found a credible psychological effect if the measures do not relate to the psychological constructs [@cook2002experimental].
-Validity indicates the extent to which a measure measures what it is supposed to measure [@borsboom2004concept] and can be studied by comparing the test scores’ empirical associations to the theoretical associations of the constructs [@cronbach1955construct].
-
-## Replicability & Measurement
-
-Replicability and reliable and valid measurement are essential to the credibility of a finding, and are related to each other.
-Indeed, recent studies have illustrated that both the reliability of the measure [@stanley2014expectations] and the reporting of information relevant to demonstrating the validity of the measurement [@shaw2020measurement; @flake2017construct; @flake2020measurement] may predict the replicability of psychological findings.
-
-In this study, we investigate the relation of reliability and measurement reporting with replicability, using data and reports from the large-scale Many Labs replication projects.
-Because the Many Labs projects [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many] are large-scale collaborations in which multiple lab locations directly replicated the same set of studies, their data allows us to study the variability in their measures across different contexts.
-Furthermore, because the Many Labs projects used preregistered and documented structured protocols, we expect the measurement used in these projects to represent a high standard within the field.
-Any issues in measurement here might suggest that other replications could face similar or greater challenges.
-
-## Existing Research
-
-### Reliability
-
-Notwithstanding the common yet mistaken belief that reliability is a measure-specific feature, the reliability of a measure typically varies between samples differing in latent trait variance and/or the latent measurement model [@cho2015cronbach; @pauly2018resampling].
-Besides random variation due to the sampling error, the variations can also reflect true variation in reliability, also known as reliability heterogeneity [@vacha-haase1998ReliabilityGeneralizationExploring].
-For instance, measures will normally show lower reliability in more homogeneous samples than heterogeneous samples [@pike1998reliability], which follows from reliability being a function of the variability in true scores.
-In modern latent variable modelling, group differences in reliability can also emerge because of failures of measurement invariance across groups (e.g., differences in factor loadings or item difficulty parameters across groups).
-
-Variations in reliability could contribute to the discrepancy between effects in original and replication studies, as well as within replications of the same original effect.
-After all, it has long been known that measurement error suppresses observed effects and associations [@spearman1904proof].
-@stanley2014expectations simulated data of items on a scale based on levels of sampling error and reliability similar to what is standard in psychological research.
-The results showed that the variation due to measurement error was substantial enough to cause replications of a positive small effect to observe anywhere between a medium negative effect and a large positive effect [@stanley2014expectations].
-In summary, studies using unreliable measures are less replicable, even when the measurement is equally reliable between original and replication.
-
-### Measurement Reporting
-
-Despite the importance of reliable and valid measurement, research has shown that Questionable Measurement Practices (QMPs) are not uncommon.
-QMPs are practices that raise doubts about a measurement’s validity [@flake2020measurement] and have been coined as a term analogous to Questionable Research Practices [QRPs\; @john2012measuring].
+Psychometrics offers various ways to assess reliability empirically [@nunnally1978overview; @mellenbergh2011conceptual], … test-retest … interrater … internal consistency (this in turn relates back to construct validity)….
+[something about the fact that reliability is sample specific and not measurement specific in nearly all cases of us assessing it]
+
+## Measurement Reporting
+
+To summarize the previous section, the measurement of a study need to be both valid and reliable to be able to assess the phenomenon of interest.
+However, recent research has shown that the reliability and validity can often not be discerned from the reported information.
+Questionable Measurement Practices (QMPs) raise doubts about a measurement’s validity [@flake2020measurement] and have been coined as a term analogous to Questionable Research Practices [QRPs\; @john2012measuring].
 QMPs range from lack of transparency and unclear motivation in choice of measure to poor justification for modifications of a measure and procedure of an existing measure [@flake2020measurement].
-Specifically, @flake2020measurement identified six key questions that an article should answer to avoid QMPs: the definition of the construct, how and why the measure was selected, how the measure operationalizes the construct, how the measure was quantified, whether it was modified or not and why, and the reasons and details of creating a measure if applicable.
-If these questions can be answered clearly based on the reported measurement information, then reporting is sufficiently transparent to promote a more cumulative psychological science.
 
 @flake2022construct documented QMPs among 100 replications and their respective original articles from the RPP [@osc2015estimating].
-They coded the number of measures, the number of items in the measure, and the information that was reported describing the measure and providing evidence justifying its use.
-Besides limited reporting of validity and reliability evidence for the coded measures, @flake2022construct found that several of the measures in the RPP did not report the number of items, the response format, or the scoring of the scale.
+They coded the number of measures, the number of items in the measure, and the information that was reported describing the measure and justifying its use.
+They observed limited reporting of evidence demonstrating the reliability and validity of the measurement.
+Furthermore, auxiliary information on the number of items, the response format, the scoring of the scale, was also not reported for several measures in the RPP.
 Furthermore, only eight of the 40 translated scales contained validity evidence for the translated version of the scale.
-Evidence showing that this and other modifications between original and replication did not invalidate the measurement was rarely reported.
-
-Further findings by @flake2022construct and others [@flake2017construct; @shaw2020measurement] also illustrated how QMPs create challenges for replicating researchers.
-To reconstruct the measurement, replication researchers need to know the items that were used, how they were presented to the subjects, and how to compute the scores.
-If the measure is not reconstructed exactly, constructs measured by original and replication may differ, possibly creating differences in effect sizes between original and replication studies, resulting in less informative replications.
-
-### Research Contribution
-
-Our study investigates the relation of reliability and measurement reporting with replicability, using data and reports from the large-scale Many Labs replication projects.
-First, this study expands on the research by  @stanley2014expectations, to see if reliability is related to replication success in empirical replication data.
-Specifically, we investigate whether successfully replicated studies differed in reliability from non-replicated studies.
-@stanley2014expectations assumed reliability to be constant across studies, which we know to be an oversimplification.
-Therefore, to add further context to the relation between reliability and replication, we also investigate the variation in reliability as observed across labs.
-
-Furthermore, we conceptually replicate the study by @flake2022construct on QMPs in replications and original research in the context of the Many Labs projects.
-We expand on @flake2022construct by exploring associations between QMPs and the replicability of psychological findings.
-
-## Research Questions & Hypotheses
-
-### Reliability
-
-Measurement reliability can vary across samples, because the residual variance or the true variance in the item scores, or both, differs between samples.
-While differences in these variances across samples is inevitable, these differences should not be systematic between replication and original samples for their results to remain comparable.
-Therefore, we investigated the reliability in replication (Research Question 1a; RQ1a[^1]) and original psychological research (RQ1b).
-The Many Labs studies were intended as direct replications, which implies that deviations from the original research should be irrelevant for testing the effect [@nosek2022replicability], including systematic differences in reliability (Hypothesis 1; H1).
-
-[^1]: The numbering of the research questions and hypotheses matches the numbering in the preregistration
-
-Additionally, for the results of direct replications to be comparable with each other, the differences in reliability should be comparable.
-Systematic differences in reliability could indicate that measurement assesses fundamentally different constructs.
-Therefore, we investigated  whether reliability estimates differed systematically between replicating labs (RQ2).
-For effect sizes, there is little empirical evidence of widespread heterogeneity among the Many Labs replications [@klein2018many; @olsson2020heterogeneity].
-We expect that there is no systematic variation in the reliability estimates of replications of the same original study (H2) either.
-
-In theory, there should be a positive relation between reliability and replicability.
-Greater reliability means the variance around the estimate of the true effect is decreased [@nunnally1994assessment].
-If the true effect is not null, then the statistical tests with reliable measures are more likely to be significant.
-To empirically assess this, we investigated the association between replication study reliability and replication outcome (RQ3).
-We expected that reliability in the replications would be positively associated with replication success (H3).
-
-### Measurement Reporting
-
-We conceptually replicate the findings on measurement reporting of @flake2022construct by documenting the frequency of QMPs in replications of psychological research (RQ4a) and original psychological research (RQ4b).
-@flake2022construct found that RPP replications contained on average more QMPs than original studies.
-We hypothesized that for our Many Labs sample, QMPs would be more frequent in original psychological research than in replication research (H4), because the Many Labs replications used structured protocols documenting the measurement.
-
-QMPs obscure information about a particular measurement, which may cause issues when reconstructing that measurement in subsequent replication attempts.
-Because resulting deviations in measurement may be partly responsible for deviations in replication and original effects [@flake2022construct], we investigated whether QMPs in replication protocols were associated with the replication outcome (RQ5).
-A reduction in QMPs corresponds to greater transparency in measurement reporting.
-In line with earlier research finding that other transparency-related practices are associated with more robust estimates of effects [@wicherts2011willingness], we expected QMPs in replications to be negatively associated with replication success (H5).
-
-@flake2022construct proposed that QMPs in original articles may impede recreating measurements for replications, and indeed @shaw2020measurement found evidence for such a spill-over effect with validity.
-In line with this research, we investigated the association between QMPs in original research and QMPs in replications of psychological research (RQ6).
-We expected the total number of QMPs in original psychological research to be positively related to the total number of QMPs in replication research (H6).
-
-# Disclosures
-
-### Preregistration
-
-We preregistered data collection, coding protocol, and planned analyses: <https://osf.io/jgxyu>. Deviations from the preregistration are explicitly mentioned in the text.
-
-### Data, Materials, and Online Resources
-
-This manuscript was created in RStudio [*v`r rstudioapi::versionInfo()$version`*\; @R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [*v`r getNamespaceVersion("worcs")[[1]]`*\; @vanlissaWORCS2021] to ensure reproducibility and transparency.
-All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> and <https://osf.io/9r8yt/>.
-
-### Reporting
-
-We report how we determined all data exclusions, all manipulations, and all measures in the study. Our sample size was predetermined by the number of studies in the Many Labs projects.
-
-### Ethical Approval
-
-This research was approved by the Tilburg University School of Social and Behavioral Sciences Ethical Review Board (nr. TSB_TP_REMA06).
+Evidence showing that this and other modifications between original and replication did not invalidate the measurement was rare.
+
+!!!Especially worrisome because @shaw2020measurement shows that when running factor analyses on the available data the structural evidence does not always show a good construct validity, so that the lack of reported validity evidence may be hiding psychometrical skeletons in the closet; Reliability something … [Hussey’s work].
+!!!
+
+Further findings by  @flake2022construct and others [@flake2017construct; @shaw2020measurement] also show that QMPs not only limit the reported validity of a measurement in a study, the lack of information also creates challenges for replicating researchers.
+If it is not clear what items were used, how they were scored, and how they were administered, the reconstructed measure used in the replication may be assessing the relevant construct(s) differently, or even assess different construct(s).
+If different construct(s) are assessed, the replication may not be a test of the same phenomenon as the original.
+If constructs are assessed differently, the estimated effects in the replication cannot easily be substantially compared to the effects in the original study.
+In either case, the replication is hardly informative with regards to the phenomenon of interest.
+Given replication’s importance in cumulative knowledge gain in science, this is worrisome.
+
+## Research Aim
+
+Our aim is to further investigate the reliability, validity, and measurement reporting practices in the Many Labs replications and related original research.
+We provide a descriptive account of the measurement reporting practices in tandem with the measure’s reliability and validity evidence, obtained from the openly available data from the Many Labs replication projects.
+
+Existing literature has looked at reported reliability, validity, and general measurement features in both original and replication studies before.
+Previous studies have also recalculated reliabilities from reported information and reanalyzed the validity from original data.
+Our research provides a unique contribution by combining the reported measurement information in original and replication studies, with reliability and validity re-analyses performed on openly available data from those replication studies, with the added benefit of having data across multiple labs so that variation in reliability and validity across multiple instances can be investigated.
+
+# Disclosures ???Where & How???
 
@@
 
-## Sample
-
-### Data Source
-
-The data used for the analyses consisted of three main sources: replication datasets, replication protocols, and original study articles.
-The data came from the Many Labs replication projects.
-Specifically, data from Many Labs 1, 2, 3, & 5 [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many] was included.
-Many Labs 4 [@klein2022many] was excluded, as there was no publicly available replication protocol.
-Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures.
-
-### Unit of Analysis
-
-The unit of analysis in this study was a measure of a single psychological construct used in the primary analysis that was targeted in the replication.
+## Data Source
+The data source is the Many Labs replication projects.
+These were a series of high profile replication projects wherein multiple psychological studies considered relevant by the community were chosen to be replicated across multiple labs over the world.
+Practices encountered with measurement in this sample of original articles and replications are a representative reflection of these practices more broadly.
+
+Furthermore, because each study was replicated across multiple labs and the data collected from each lab is publicly available, we can calculate reliability coefficients and perform factor analyses for each measurement across multiple data points and investigate the variance in these estimates.
+
+## Unit of Analysis
+Our unit of analysis is a measure of a single psychological construct within a replication protocol/article.
 Multiple psychological constructs could be measured per original study or replication.
@@
 ## Data Collection
-
-We retrieved the data on the replication protocols and replication datasets of Many Labs 1, 2, 3, & 5 from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>.
-Both the replication protocols and replication datasets were scanned to ensure the planned analyses were feasible.
-However, no coding or analysis of either of them had taken place before we preregistered the analyses.
-Further details on the search strategy can be found in the [supplementary materials](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) (URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd>).
+The data consists of three main sources: replication datasets, replication protocols, and original study articles.
+We retrieved the data of Many Labs 1, 2, 3, & 5 [@klein2014investigating; @ebersole2016many; @klein2018many; @ebersole2020many] from their respective OSF pages.
+Many Labs 4 [@klein2022many] was excluded, as there was no publicly available replication protocol.
+Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures.
+We checked the Many Labs data source prior to registering our coding protocol, to check the feasibility of which data could be extracted and how.
+However, the actual coding took place after registering the coding protocol … Further details can be found in supplement XXX.
 
 ### Replication Datasets
-
 The replication datasets refer to the publicly available datasets containing the data obtained from all labs partaking in a Many Labs study.
@@
 
-To be included in the planned analyses on calculated reliabilities (RQ1, RQ2, and RQ3), the measure had to be a scale consisting of multiple items.
+To be included in our reliability recalculations and factor analysis checks, the measure had to be a scale consisting of multiple items.
 If cleaned data were available, we chose these over raw data, to ensure that variables were coded as intended (e.g., no reverse-coded items).
 We omitted pilot data from the analyses.
-These criteria resulted in suitable item score data from `r apa_num(nrow(data_h23_avg))` replication sets spread across on average approximately `r apa_num(mean(table(data_h23$g)), digits = 0)` lab locations for the analyses of Hypotheses 2 & 3.
+These criteria and the nature of the available format(s) of each dataset resulted in suitable item score data from 19 replication sets spread across on average approximately 35 lab locations for our analyses.
 
@@
 ### Saving to Intermediate Data Folder
-open_data(data = data_1.3_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_1.3_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_1.3_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_1.3_clean))), ".yml"))
-
-open_data(data = data_1.10_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_1.10_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_1.10_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_1.10_clean))), ".yml"))
-
-open_data(data = data_1.11_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_1.11_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_1.11_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_1.11_clean))), ".yml"))
-
-open_data(data = data_1.12.3.1_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_1.12.3.1_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_1.12.3.1_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_1.12.3.1_clean))), ".yml"))
-
-open_data(data = data_1.12.3.2_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_1.12.3.2_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_1.12.3.2_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_1.12.3.2_clean))), ".yml"))
-
-open_data(data = data_2.10.1_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_2.10.1_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_2.10.1_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_2.10.1_clean))), ".yml"))
-
-open_data(data = data_2.12.1_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_2.12.1_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_2.12.1_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_2.12.1_clean))), ".yml"))
-
-open_data(data = data_2.12.2_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_2.12.2_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_2.12.2_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_2.12.2_clean))), ".yml"))
-
-open_data(data = data_2.12.3_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_2.12.3_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_2.12.3_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_2.12.3_clean))), ".yml"))
-
-open_data(data = data_2.15_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_2.15_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_2.15_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_2.15_clean))), ".yml"))
-
-open_data(data = data_2.20_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_2.20_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_2.20_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_2.20_clean))), ".yml"))
-
-open_data(data = data_2.23_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_2.23_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_2.23_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_2.23_clean))), ".yml"))
-
-open_data(data = data_3.2.1.1_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_3.2.1.1_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_3.2.1.1_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_3.2.1.1_clean))), ".yml"))
-
-open_data(data = data_3.2.1.2_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_3.2.1.2_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_3.2.1.2_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_3.2.1.2_clean))), ".yml"))
-
-open_data(data = data_3.7.1_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_3.7.1_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_3.7.1_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_3.7.1_clean))), ".yml"))
-
-open_data(data = data_3.7.2_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_3.7.2_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_3.7.2_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_3.7.2_clean))), ".yml"))
-
-open_data(data = data_3.8.2_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_3.8.2_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_3.8.2_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_3.8.2_clean))), ".yml"))
-
-open_data(data = data_5.1.1_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_5.1.1_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_5.1.1_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_5.1.1_clean))), ".yml"))
-
-open_data(data = data_5.1.2_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_5.1.2_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_5.1.2_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_5.1.2_clean))), ".yml"))
-
-open_data(data = data_5.4_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_5.4_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_5.4_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_5.4_clean))), ".yml"))
-
-open_data(data = data_5.7_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_5.7_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_5.7_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_5.7_clean))), ".yml"))
-
-open_data(data = data_5.9.1_clean, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(data_5.9.1_clean))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(data_5.9.1_clean))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(data_5.9.1_clean))), ".yml"))
+### !!!! OMIT INTERMEDIATE DATA & KEEP FUNCTION THAT REMOVE ALL NON RAW DATA 
+### WHEN LOADING THE DATA IN!!!!
+saving_to_intermediate_data(data_1.3_clean)
+saving_to_intermediate_data(data_1.10_clean)
+saving_to_intermediate_data(data_1.11_clean)
+saving_to_intermediate_data(data_1.12.3.1_clean)
+saving_to_intermediate_data(data_1.12.3.2_clean)
+saving_to_intermediate_data(data_2.10.1_clean)
+saving_to_intermediate_data(data_2.12.1_clean)
+saving_to_intermediate_data(data_2.12.2_clean)
+saving_to_intermediate_data(data_2.12.3_clean)
+saving_to_intermediate_data(data_2.15_clean)
+saving_to_intermediate_data(data_2.20_clean)
+saving_to_intermediate_data(data_2.23_clean)
+saving_to_intermediate_data(data_3.2.1.1_clean)
+saving_to_intermediate_data(data_3.2.1.2_clean)
+saving_to_intermediate_data(data_3.7.1_clean)
+saving_to_intermediate_data(data_3.7.2_clean)
+saving_to_intermediate_data(data_3.8.2_clean)
+saving_to_intermediate_data(data_5.1.1_clean)
+saving_to_intermediate_data(data_5.1.2_clean)
+saving_to_intermediate_data(data_5.4_clean)
+saving_to_intermediate_data(data_5.7_clean)
+saving_to_intermediate_data(data_5.9.1_clean)
 
@@
 The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each set of replications of a given original study across multiple labs.
-These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd>).
+These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the data retrieval information supplementary document; URL https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd).
 
 ### Original Articles
-
 We identified and retrieved all original study articles using the citations for these articles in each replication protocol.
@@
 coded_data_revised_sel <- coded_data_revised_raw[3:160, 18:38]
-coded_data_vignette_raw <- coded_data_vignette_raw[3:160, 2]
+coded_data_vignette_sel <- coded_data_vignette_raw[3:160, 2]
 
@@
 coded_data_full <- cbind(coded_data_initial_sel, 
-                         cbind(coded_data_revised_sel, coded_data_vignette_raw))
+                         cbind(coded_data_revised_sel, coded_data_vignette_sel))
 
@@
 
-### creating the cleaned dataset using the functions in the source code 
-coded_data_clean <- calculating(recoding(restructuring(fixing(
-  renaming(coded_data_full)))))
-
-### Saving to Intermediate Data Folder
-# Splitting data into replication and original
-coded_data_replications <- coded_data_clean[1:77,]
-coded_data_original <- coded_data_clean[78:157,]
-
-# difference in dataset row number is due to the fact that the moral foundations
-# questionnaire in original 2.4 is reported using all 5 of its factors, whereas
-# in replication 2.4 only the two overarching groups of binding and 
-# individualizing foundations are described.
-# For that reason a shortened original dataset will be used for any direct
-# comparisons between original and replication coding.
-coded_data_original_shortened <- coded_data_original[c(1:17, 19, 22:80),] 
-coded_data_original_shortened[c(18,19),5] <- 
-  c("individualizing moral foundations", "binding moral foundations")
-coded_data_original_shortened[18,13] <- NA
-coded_data_original_shortened[19,13] <- NA
+### data preparation
+# renaming columns
+colnames(coded_data_full) <- c("many_labs_version", "rep_org", "title", "measure_name", 
+      "variable_name", "multi", "variable_order", "N", "N_items", 
+      "hypothesis_support", "reliability_type", "reliability_type_text", 
+      "reliability_coeff", "def_1", "op_version", "op_1", "op_2", "op_3", "op_4", 
+      "op_5", "sel_existing", "sel_existing_text", "sel_1", "sel_2", "sel_3", 
+      "sel_4", "sel_psychometric_evidence", "sel_psychometric_evidence_text", 
+      "quant_1", "quant_2", "quant_3", "quant_4", "mod_check", "mod_1", "mod_2", 
+      "mod_3", "mod_4", "mod_5", "mod_6", "mod_time", "op_1_REV", "op_2_REV",
+      "op_5_REV", "sel_1_REV", "sel_3_REV", "sel_psychometric_evidence_REV", 
+      "sel_psychometric_evidence_text_REV", "quant_1_REV", "quant_2_REV", 
+      "quant_3_REV", "mod_check_REV", "mod_1_REV", "mod_2_REV", "mod_3_REV", 
+      "mod_4_REV", "mod_5_REV", "mod_6_REV", "inseperable_material")
+
+# renaming rows
+rownames(coded_data_full) <- 1:nrow(coded_data_full)
+
+# fixing some coding mistakes
+coded_data_full$variable_name[79] <- "quote attribution effect"
+coded_data_full$N[3] <- "5284"
+coded_data_full$N[158] <- "1202"
+coded_data_full$reliability_type[50] <- "Not Reported"
+coded_data_full$reliability_type[127] <- "Not Reported"
+coded_data_full$op_1[145] <- "False"
+coded_data_full$op_3[121] <- "True"
+coded_data_full$op_5[157] <- "True"
+coded_data_full$sel_1[59] <- "True"
+coded_data_full$quant_2[113] <- "True"
+coded_data_full$mod_time[1] <- "Before"
+
+# removing missing entry 77
+coded_data_full <- data.frame(coded_data_full)[-77,]
+
+# Many labs 2.25 and 2.26, as well as 3.4 and 3.5 (for replications) were coded 
+# in reverse order thus need to be swapped in right order. Additionally, some
+# of the entries were included later than following their order, due to some
+# minor coding oversights.
+Coded_Data_Full_Restructured <- coded_data_full[c(1:18, 148, 19:23, 147, 24:28, 
+                                                  153, 29:40, 154, 42, 41, 155, 
+                                                  43:49, 156, 51, 50, 52:76, 
+                                                  157, 77:88, 149:152, 89:146),]
+
+# rename the rownames to match the new order
+rownames(Coded_Data_Full_Restructured) <- 1:nrow(Coded_Data_Full_Restructured)
+
+# changing the variable types for each column to better represent their 
+# intended variable type
+class(Coded_Data_Full_Restructured$many_labs_version) <- "numeric"
+Coded_Data_Full_Restructured$many_labs_version <- as.factor(Coded_Data_Full_Restructured$many_labs_version)
+Coded_Data_Full_Restructured$rep_org <- droplevels(as.factor(Coded_Data_Full_Restructured$rep_org))
+Coded_Data_Full_Restructured$multi <- droplevels(as.factor(Coded_Data_Full_Restructured$multi))
+Coded_Data_Full_Restructured$variable_order <- droplevels(as.factor(Coded_Data_Full_Restructured$variable_order))
+class(Coded_Data_Full_Restructured$N) <- "numeric"
+Coded_Data_Full_Restructured$N_items <- droplevels(as.factor(Coded_Data_Full_Restructured$N_items))
+Coded_Data_Full_Restructured$hypothesis_support <- droplevels(as.factor(Coded_Data_Full_Restructured$hypothesis_support))
+levels(Coded_Data_Full_Restructured$hypothesis_support) <- c("No", "Unclear", "Yes")
+Coded_Data_Full_Restructured$reliability_type <- droplevels(as.factor(Coded_Data_Full_Restructured$reliability_type))
+class(Coded_Data_Full_Restructured$reliability_coeff) <- "numeric"
+Coded_Data_Full_Restructured$def_1 <- as.logical(Coded_Data_Full_Restructured$def_1)
+Coded_Data_Full_Restructured$op_1 <- as.logical(Coded_Data_Full_Restructured$op_1)
+Coded_Data_Full_Restructured$op_2 <- as.logical(Coded_Data_Full_Restructured$op_2)
+Coded_Data_Full_Restructured$op_3 <- as.logical(Coded_Data_Full_Restructured$op_3)
+Coded_Data_Full_Restructured$op_4 <- as.logical(Coded_Data_Full_Restructured$op_4)
+Coded_Data_Full_Restructured$op_5 <- as.logical(Coded_Data_Full_Restructured$op_5)
+Coded_Data_Full_Restructured$sel_existing <- droplevels(as.factor(Coded_Data_Full_Restructured$sel_existing))
+Coded_Data_Full_Restructured$sel_1 <- as.logical(Coded_Data_Full_Restructured$sel_1)
+Coded_Data_Full_Restructured$sel_2 <- as.logical(Coded_Data_Full_Restructured$sel_2)
+Coded_Data_Full_Restructured$sel_3 <- as.logical(Coded_Data_Full_Restructured$sel_3)
+Coded_Data_Full_Restructured$sel_4 <- as.logical(Coded_Data_Full_Restructured$sel_4)
+Coded_Data_Full_Restructured$sel_psychometric_evidence <- droplevels(as.factor(Coded_Data_Full_Restructured$sel_psychometric_evidence))
+Coded_Data_Full_Restructured$quant_1 <- as.logical(Coded_Data_Full_Restructured$quant_1)
+Coded_Data_Full_Restructured$quant_2 <- as.logical(Coded_Data_Full_Restructured$quant_2)
+Coded_Data_Full_Restructured$quant_3 <- as.logical(Coded_Data_Full_Restructured$quant_3)
+Coded_Data_Full_Restructured$quant_4 <- as.logical(Coded_Data_Full_Restructured$quant_4)
+Coded_Data_Full_Restructured$mod_check <- droplevels(as.factor(Coded_Data_Full_Restructured$mod_check))
+Coded_Data_Full_Restructured$mod_1 <- as.logical(Coded_Data_Full_Restructured$mod_1)
+Coded_Data_Full_Restructured$mod_2 <- as.logical(Coded_Data_Full_Restructured$mod_2)
+Coded_Data_Full_Restructured$mod_3 <- as.logical(Coded_Data_Full_Restructured$mod_3)
+Coded_Data_Full_Restructured$mod_4 <- as.logical(Coded_Data_Full_Restructured$mod_4)
+Coded_Data_Full_Restructured$mod_5 <- as.logical(Coded_Data_Full_Restructured$mod_5)
+Coded_Data_Full_Restructured$mod_6 <- as.logical(Coded_Data_Full_Restructured$mod_6)
+Coded_Data_Full_Restructured$mod_time <- droplevels(as.factor(Coded_Data_Full_Restructured$mod_time))
+Coded_Data_Full_Restructured$op_1_REV <- as.logical(Coded_Data_Full_Restructured$op_1_REV)
+Coded_Data_Full_Restructured$op_2_REV <- as.logical(Coded_Data_Full_Restructured$op_2_REV)
+Coded_Data_Full_Restructured$op_5_REV <- as.logical(Coded_Data_Full_Restructured$op_5_REV)
+Coded_Data_Full_Restructured$sel_1_REV <- as.logical(Coded_Data_Full_Restructured$sel_1_REV)
+Coded_Data_Full_Restructured$sel_3_REV <- as.logical(Coded_Data_Full_Restructured$sel_3_REV)
+Coded_Data_Full_Restructured$sel_psychometric_evidence_REV <- droplevels(as.factor(Coded_Data_Full_Restructured$sel_psychometric_evidence_REV))
+Coded_Data_Full_Restructured$quant_1_REV <- as.logical(Coded_Data_Full_Restructured$quant_1_REV)
+Coded_Data_Full_Restructured$quant_2_REV <- as.logical(Coded_Data_Full_Restructured$quant_2_REV)
+Coded_Data_Full_Restructured$quant_3_REV <- as.logical(Coded_Data_Full_Restructured$quant_3_REV)
+Coded_Data_Full_Restructured$mod_check_REV <- droplevels(as.factor(Coded_Data_Full_Restructured$mod_check_REV))
+Coded_Data_Full_Restructured$mod_1_REV <- as.logical(Coded_Data_Full_Restructured$mod_1_REV)
+Coded_Data_Full_Restructured$mod_2_REV <- as.logical(Coded_Data_Full_Restructured$mod_2_REV)
+Coded_Data_Full_Restructured$mod_3_REV <- as.logical(Coded_Data_Full_Restructured$mod_3_REV)
+Coded_Data_Full_Restructured$mod_4_REV <- as.logical(Coded_Data_Full_Restructured$mod_4_REV)
+Coded_Data_Full_Restructured$mod_5_REV <- as.logical(Coded_Data_Full_Restructured$mod_5_REV)
+Coded_Data_Full_Restructured$mod_6_REV <- as.logical(Coded_Data_Full_Restructured$mod_6_REV)
+Coded_Data_Full_Restructured$inseperable_material <- droplevels(as.factor(Coded_Data_Full_Restructured$inseperable_material)
+
+# the moral foundations questionnaire in original 2.4 is reported using all 5 of 
+# its factors, whereas in replication 2.4 only the two overarching groups of 
+# binding and individualizing foundations are described. For that reason a 
+# shortened original dataset will be used for any direct comparisons between 
+# original and replication coding.
+
+Coded_Data_Full_Shortened <- Coded_Data_Full_Restructured[c(1:94, 96, 99:157),] 
+Coded_Data_Full_Shortened[c(95,96),5] <- c("individualizing moral foundations", "binding moral foundations")
+Coded_Data_Full_Shortened[95,13] <- NA
+Coded_Data_Full_Shortened[96,13] <- NA
+
+# separating the replication and original data from each other.
+coded_data_replications <- Coded_Data_Full_Shortened[1:77,]
+coded_data_original <- Coded_Data_Full_Shortened[78:154,]
 
 # exporting cleaned data
-open_data(data = coded_data_replications, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(coded_data_replications))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(coded_data_replications))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(coded_data_replications))), ".yml"))
-
-open_data(data = coded_data_original, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(coded_data_original))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(coded_data_original))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(coded_data_original))), ".yml"))
-
-open_data(data = coded_data_original_shortened, filename = paste0(paste0(
-  "Data/IntermediateData/", deparse(substitute(coded_data_original_shortened))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/IntermediateData/codebook_", 
-    deparse(substitute(coded_data_original_shortened))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/IntermediateData/value_labels_", 
-    deparse(substitute(coded_data_original_shortened))), ".yml"))
-
-# clearing up memory space by removing raw files from the environment
-rm(coded_data_initial_raw, coded_data_revised_raw, coded_data_vignette_raw, 
-   data_2.10.1, data_2.12, data_2.15, data_2.19.1, data_2.2, data_2.20, 
-   data_2.23, data_2.3, data_2.4.1, data_2.4.2, data_2.8.2, data_3.5, data_5.1,
-   data_5.4, data_5.5, data_5.7, data_5.9.1, data_ml1, data_ml3)
-
-```
-
-## Measures {#Measures}
-
-We developed a [coding protocol](../../SupplementaryMaterials/CodingProtocols/Measurement_Error_Reporting_Revised_Coding_Protocol.pdf) (available in the supplementary materials; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd>) to extract information on the reported measurements for both replication protocols and original studies.
-
-### Measures of Reliability
-
-Because data from the Many Labs replications were available for each lab location within each replication set, we could calculate reliabilities for any item scale measure used for each lab location separately.
-This allowed us to assess the variation of reliabilities of the same measure across different contexts.
-
-We calculated Cronbach’s Alpha, as it remains the most commonly used indicator of the reliability of a measure [@flake2017construct], to compare the reliabilities reported in original articles and across replicating labs.
-We calculated Cronbach’s Alpha using the alpha function from the *psych* R package [*v`r getNamespaceVersion("psych")[[1]]`*\; @R-psych] with default arguments.
-We had preregistered Omega as an additional index of reliability, because it is regarded by numerous psychometricians as a more informative alternative to Cronbach’s Alpha [@crutzen2017scale; @deng2017testing].
-The results based on Omega can be found in [Supplementary Analyses C](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_multilevel_analyses.Rmd).
-
-```{r ReliabilityValidityTestabilityCheck, include = FALSE, warning = FALSE}
-## Checking the measures to recalculate the reliability and factor analysis for.
-## The question: "Are they psychometrics scales or not?", is key here.
-View(coded_data_replications)
-
-# Likely reliability: 1.10, 1.11, 1.12.3, 2.4.1, 2.4.2, 2.8.2, 2.10.1, 2.12.1, 
-# 2.12.2, 2.12.3, 2.15, 2.19.2, 2.23, 3.7.1, 3.7.2, 3.8.1, 3.8.2, 5.7, 5.9.1
-# Likely factor: 1.10, 1.11, 1.12.3, 2.4.1, 2.4.2, 2.8.2, 2.10.1, 2.12.1, 2.12.2,
-# 2,12,3, 2.15, 2.19.2, 2.23, 3.7.1, 3.7.2, 3.8.1, 3.8.2, 5.7, 5.9.1
-# Maybe reliability: 1.3, 1.12.1, 2.2, 2.3, 2.19.1, 2.20, 3.2.1, 3.5, 5.1.1, 
-# 5.1.2, 5.4, 5.5.1, 5.5.2
-# Maybe factor: 1.3, 1.12.1, 2.3, 2.19.1, 2.20, 3.2.1, 3.5, 5.1.1, 5.1.2, 5.4,
-# 5.5.1, 5.5.2
-
-# 1.9 is difficult, might be a scale as dv rather than voting behavior.
-```
-
-### Measures of Measurement Reporting
-
-We extracted the reported reliability coefficient and type of index (Cronbach’s Alpha, retest, interrater, etc.) of a measure from both the replication protocols and the original articles when present.
-Similarly, we coded the presence of any validity evidence, such as a factor analysis, that was presented alongside the measure.
-
-The tests for Hypotheses 4, 5, & 6 were all based on the QMPs coded for both original articles and replication protocols.
-We included items based on Flake et al.
-(2022), and additional items to further assess transparent measurement reporting as laid out in Flake and Fried (2020).
-In total, we coded `r sum(colnames(coded_data_replications) == "def1" | colnames(coded_data_replications) == "op_1" | colnames(coded_data_replications) == "op_2" | colnames(coded_data_replications) == "op_3" | colnames(coded_data_replications) == "op_4" | colnames(coded_data_replications) == "op_5" | colnames(coded_data_replications) == "sel_1" | colnames(coded_data_replications) == "sel_2" | colnames(coded_data_replications) == "sel_3" | colnames(coded_data_replications) == "sel_4" | colnames(coded_data_replications) == "quant_1" | colnames(coded_data_replications) == "quant_2" | colnames(coded_data_replications) == "quant_3" | colnames(coded_data_replications) == "quant_4" | colnames(coded_data_replications) == "mod_1" | colnames(coded_data_replications) == "mod_2" | colnames(coded_data_replications) == "mod_3" | colnames(coded_data_replications) == "mod_4" | colnames(coded_data_replications) == "mod_5" | colnames(coded_data_replications) == "mod_6")` different QMPs, categorized into five QMP type categories based on Flake and Fried (2020).
-The QMP categories and example items can be seen in Table \@ref(tab:QMPCodingInfoTable).
+saving_to_intermediate_data(coded_data_replications)
+saving_to_intermediate_data(coded_data_original)
+
+```
+
+## Measures
+### Coding Protocol
+We developed a coding protocol to extract reported measurement information from the original articles and replication protocols.
+We extracted the reported reliability coefficient and type of index (Cronbach’s Alpha, retest, interrater, etc.) when present.
+Similarly, we coded if any construct validity evidence, such as a factor analysis, was presented alongside the measure.
+We additionally included twenty items that were based on the QMP table presented in Flake & Fried.
+These items recorded whether or not certain information was reported and were all coded to be either true, false, or not applicable if not relevant for that measure (e.g., reporting results from a factor analysis for single-item measures).
+Example items can been in Table 1.
 
@@
 Selection and creation share a category as the justifications and requirements in selecting a measure are similar to those for creating a new measure."
-  , escape = FALSE, placement= "htp", booktabs = TRUE)
-
-```
-
-QMPs were all coded to be either true, false, or not applicable if not relevant for that measure (e.g., reporting results from a factor analysis for single-item measures).
-For the analyses, we calculated a ratio (both per QMP type and overall QMP) based on the number on the number of true responses divided by the number of responses coded to be applicable.
-
-After the initial coding, we made minor revisions to `r length(coded_data_revised_raw[1, c("Op1", "Op2", "Op5", "Sel1", "Sel3", "Quant1", "Quant2", "Quant3", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` of the `r length(coded_data_initial_raw[1, c("Def1", "Op1", "Op2", "Op3", "Op4", "Op5", "Sel1", "Sel2", "Sel3", "Sel4", "Quant1", "Quant2", "Quant3", "Quant4", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` QMP items in the preregistered coding protocol, because we considered them overly stringent in practice.
+  , escape = FALSE, placement = "htp", booktabs = TRUE)
+
+```
+
+After the initial coding, we made minor revisions to 14 of the 20 QMP items in the preregistered coding protocol, because we considered them overly stringent in practice.
 For example, in the initial protocol, an example item had to be present within the article or protocol itself, or else this was counted as a QMP.
 In the revised protocol, references to online appendices with example items were also considered sufficient for this item.
-The analyses, tables, and figures presented in this article are all based on the revised coding protocol, the results of the equivalent analyses based on QMPs obtained with our initial protocol can be found in [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd).
-
-### Measure of Replication Success
-
-We used the published reports of the Many Labs projects [@klein2014investigating; @ebersole2016many; @ebersole2020many; @klein2018many] to determine replication success based on the reported significance of the meta-analytic effect.
-An effect was considered successfully replicated if the meta-analytic effect was in the same direction as the original effect and had a p-value lower than .05.
-
-```{r FinalPreparationData, include = FALSE, eval = FALSE}
-##### This code can be used to rerun the data preparation to convert the 
-##### intermediate data into the analysis data. However, because the analysis
-##### data is also available in this project, the manuscript can also be 
-##### reproduced without running this code block.
-### this code prepares the various pieces of data to be ready to use for the 
-### analyses.
-## confirmatory analyses
-# for hypotheses 4, 5, & 6
-data_h456_original <- data_prep_h456(coded_data_original_shortened)
-data_h456_replications <- data_prep_h456(coded_data_replications)
-
-# for hypotheses 2 and 3
-data_h23 <- data_prep_H23(list(data_1.10_clean, data_1.11_clean, 
+The analyses, tables, and figures presented in this article are all based on the revised coding protocol, the results of the equivalent analyses based on QMPs obtained with our initial protocol can be found in Supplementary Analyses D.
+
+We initially intended to form a QMP index using these QMP items and explore relations in the data using this index, but this index could not be validated properly (more information on the index can be found in the Supplement).
+These items are therefore currently used on their own to give a descriptive overview of the reporting practices in our sample.
+
+```{r Calculating_QMP_Data, include = FALSE, eval = FALSE}
+original_QMP_data <- coded_data_original[c("def_1", "sel_2", "op_4", "reliability_type", "sel_existing", "op_version", "op_1_REV", "sel_1_REV", "sel_3_REV", "sel_4", "sel_psychometric_evidence", "op_2_REV", "op_3", "quant_1_REV", "quant_2_REV", "quant_3_REV", "quant_4", "op_5_REV", "mod_1_REV", "mod_2_REV", "mod_3_REV", "mod_4_REV", "mod_5_REV", "mod_6_REV")]
+
+replication_QMP_data <- coded_data_replications[c("def_1", "sel_2", "op_4", "reliability_type", "sel_existing", "op_version", "op_1_REV", "sel_1_REV", "sel_3_REV", "sel_4", "sel_psychometric_evidence", "op_2_REV", "op_3", "quant_1_REV", "quant_2_REV", "quant_3_REV", "quant_4", "op_5_REV", "mod_1_REV", "mod_2_REV", "mod_3_REV", "mod_4_REV", "mod_5_REV", "mod_6_REV")]
+
+# create an empty dataset to add a recoded TRUE and FALSE response for QMPs to 
+QMP_data <- data.frame(delete_this = rep(NA, 77))
+
+QMP_data$reliability_reported_org <- ifelse(original_QMP_data$reliability_type != "Not Reported" & original_QMP_data$reliability_type != "" & !is.na(original_QMP_data$reliability_type), TRUE, ifelse(original_QMP_data$reliability_type == "Not Reported", FALSE, NA))
+
+QMP_data$reliability_reported_rep <- ifelse(replication_QMP_data$reliability_type != "Not Reported" & replication_QMP_data$reliability_type != "" & !is.na(replication_QMP_data$reliability_type), FALSE, ifelse(replication_QMP_data$reliability_type == "Not Reported", TRUE, NA))
+
+# add if clearly specified if measure existed or not
+QMP_data$select_or_create_clarity_org <- original_QMP_data$sel_existing == "Not Clearly Stated"
+
+QMP_data$select_or_create_clarity_rep <- replication_QMP_data$sel_existing == "Not Clearly Stated"
+
+# add if version was clearly specified
+QMP_data$version_clarity_org <- original_QMP_data$op_1_REV == FALSE | original_QMP_data$op_version == "" & original_QMP_data$sel_existing == "True, namely:"
+
+QMP_data$version_clarity_rep <- replication_QMP_data$op_1_REV == FALSE | replication_QMP_data$op_version == "" & replication_QMP_data$sel_existing == "True, namely:"
+
+# add if factor structure was analysed
+QMP_data$factor_analysis_org <- ifelse(original_QMP_data$sel_psychometric_evidence == "None", FALSE, ifelse(original_QMP_data$sel_psychometric_evidence != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)", TRUE, NA))
+
+QMP_data$factor_analysis_rep <- ifelse(replication_QMP_data$sel_psychometric_evidence == "None", FALSE, ifelse(replication_QMP_data$sel_psychometric_evidence != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)", TRUE, NA))
+
+# direct copies
+QMP_data$justified_definition_org <- original_QMP_data$def_1
+QMP_data$justified_definition_rep <- replication_QMP_data$def_1
+QMP_data$justified_selection_org <- original_QMP_data$sel_2
+QMP_data$justified_selection_rep <- replication_QMP_data$sel_2
+QMP_data$justified_operationalisation_org <- original_QMP_data$op_4
+QMP_data$justified_operationalisation_rep <- replication_QMP_data$op_4
+QMP_data$source_org <- original_QMP_data$sel_1_REV
+QMP_data$source_rep <- replication_QMP_data$sel_1_REV
+QMP_data$in_psychometric_org <- original_QMP_data$sel_3_REV
+QMP_data$in_psychometric_rep <- replication_QMP_data$sel_3_REV
+QMP_data$out_psychometric_org <- original_QMP_data$sel_4
+QMP_data$out_psychometric_rep <- replication_QMP_data$sel_4
+QMP_data$admin_format_org <- original_QMP_data$op_2_REV
+QMP_data$admin_format_rep <- replication_QMP_data$op_2_REV
+QMP_data$admin_procedure_org <- original_QMP_data$op_3
+QMP_data$admin_procedure_rep <- replication_QMP_data$op_3
+QMP_data$N_items_org <- original_QMP_data$quant_1_REV
+QMP_data$N_items_rep <- replication_QMP_data$quant_1_REV
+QMP_data$N_response_org <- original_QMP_data$quant_2_REV
+QMP_data$N_response_rep <- replication_QMP_data$quant_2_REV
+QMP_data$recoding_org <- original_QMP_data$quant_3_REV
+QMP_data$recoding_rep <- replication_QMP_data$quant_3_REV
+QMP_data$aggregation_org <- original_QMP_data$quant_4
+QMP_data$aggregation_rep <- replication_QMP_data$quant_4
+QMP_data$example_items_org <- original_QMP_data$op_5_REV
+QMP_data$example_items_rep <- replication_QMP_data$op_5_REV
+QMP_data$mod_admin_format_org <- original_QMP_data$mod_1_REV
+QMP_data$mod_admin_format_rep <- replication_QMP_data$mod_1_REV
+QMP_data$mod_admin_format_support_org <- original_QMP_data$mod_2_REV
+QMP_data$mod_admin_format_support_rep <- replication_QMP_data$mod_2_REV
+QMP_data$mod_language_org <- original_QMP_data$mod_3_REV
+QMP_data$mod_language_rep <- replication_QMP_data$mod_3_REV
+QMP_data$mod_language_support_org <- original_QMP_data$mod_4_REV
+QMP_data$mod_language_support_rep <- replication_QMP_data$mod_4_REV
+QMP_data$mod_N_items_or_response_org <- original_QMP_data$mod_5_REV
+QMP_data$mod_N_items_or_response_rep <- replication_QMP_data$mod_5_REV
+QMP_data$mod_N_items_or_response_support_org <- original_QMP_data$mod_6_REV
+QMP_data$mod_N_items_or_response_support_rep <- replication_QMP_data$mod_6_REV
+
+QMP_data <- QMP_data[,!(names(QMP_data) %in% "delete_this")]
+
+QMP_data$source_org <- original_QMP_data$sel_1_REV
+QMP_data$source_rep <- replication_QMP_data$sel_1_REV
+
+QMP_data$select_or_create_clarity_org <- original_QMP_data$sel_existing == "Not Clearly Stated"
+QMP_data$select_or_create_clarity_rep <- replication_QMP_data$sel_existing == "Not Clearly Stated"
+
+QMP_data$version_clarity_org <- original_QMP_data$op_1_REV == FALSE | original_QMP_data$op_version == "" & original_QMP_data$sel_existing == "True, namely"
+QMP_data$version_clarity_rep <- replication_QMP_data$op_1_REV == FALSE | replication_QMP_data$op_version == "" & replication_QMP_data$sel_existing == "True, namely"
+
+### QMP ratio data
+# create the empty QMP ratio dataset
+QMP_ratio_data <- data.frame(Practice = rep("", ncol(QMP_data)/2),
+                   QMP_percentage_original = rep(0, ncol(QMP_data)/2),
+                   N_applicable_original = rep(0, ncol(QMP_data)/2),
+                   QMP_percentage_replication = rep(0, ncol(QMP_data)/2),
+                   N_applicable_replication = rep(0, ncol(QMP_data)/2),
+                   Phi = rep(0, ncol(QMP_data)/2))
+
+# we loop through the length of the number of Measurement Practices (MPs) 
+# ignoring doubles due to having both original and replication
+for(i in 1:(ncol(QMP_data)/2)){
+  # we create the name of the variable by taking the name and removing the 
+  # _org suffix. Then we for each column except the NA initial column
+  # we take the original MP and the related replication MP, and calculate
+  # their QMP
+  QMP_ratio_data[i,] <- Create_QMP_descriptive_case(substr(names(QMP_data)[i*2], 1, nchar(names(QMP_data)[i*2]) - 4), QMP_data[[(i*2)-1]], QMP_data[[i*2]])
+  }
+
+# store QMP ratio data in the analysis data folder
+saving_to_analysis_data(QMP_ratio_data)
+```
+
+Recalculating Data
+We furthermore, used the replication datasets to calculate reliability for each measure with appropriate data for each lab the measure was used in.
+We calculated both Cronbach’s alpha, as well as its standard error using formulas 2 & 3 from Duhachek and Lacobucci (2004) to calculate the standard error in the meta-analysis.
+Then combining these two values we conducted a meta-analysis of the reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analysis (Botella & Suero, 2012; López-Ibáñez et al., 2024; Vacha-Haase, 1998).
+This enabled us to quantify the degree of true variation (or heterogeneity) in reliability coefficients across lab locations.
+We performed the RG meta-analysis using the rma function from the metafor R package (v4.4-0 ; Viechtbauer, 2010) and default settings.
+We implemented no correction for bias, because the Many Labs replications were not at risk of publication bias.
+
+Our analyses will focus on Cronbach’s Alpha, because Cronbach’s Alpha is used more commonly in research allowing us to make comparisons between calculated and reported reliabilities.
+Furthermore, we were able to calculate the standard error of alpha to be used in the Reliability Generalization meta-analysis.
+However, we additionally estimated McDonald’s Omega, since it has been argued to be a more informative measure of reliability than alpha, while also simultaneously providing some validity evidence [@crutzen2017scale; @deng2017testing].
+Omega was calculated using the omega function in the *psych* R package [*v`r getNamespaceVersion("psych")[[1]]`*; @R-psych].
+Default arguments were used in the function except the nfactors argument, which was set to 1.
+
+Finally, We probed the three assumptions of Cronbach’s alpha for our included nineteen measures.
+First, we tested for unidimensionality using the fit indices of a one-dimensional Confirmatory Factor Analysis (CFA), and the outcome from a parallel test.
+!!!
+explain parallel test !!!
+.
+Second, we compared the unidimensional model to a unidimensional model that was restricted to be Tau equivalent (equal loading of all items on the common factor), and used model comparison to test whether the restricted model fitted significantly worse or not.
+Third, for the unidimensional model, we tested the assumption of uncorrelated errors by freely estimated the five highest correlations between individual item pairs and then used a model comparison to test whether the model with freely estimated errors fitted significantly better or not.
+Besides testing the assumptions for Cronbach’s alpha, the results regarding unidimensionality combined with McDonald’s Omega also gives us some indication of the construct validity, since these measures were checked to all have been used to create a singular index.
+If a unidimensional model would thus lack fit according to our tests, it would put into question the use of these measures to estimate a singular variable of interest.
+
+```{r calculated_reliability_across_labs, include = FALSE, eval = FALSE}
+# creating an empty data frame to insert all the responses into
+calculated_reliability_lab_data <- data.frame(alpha = 0, omega.tot = 0, 
+                                          omega.hier = 0, ASE = 0, g = 0)
+
+# Combining the data together 1.3, & 5.4 were omitted, because data was not
+# recorded in usable numeric format
+extracted_score_data <- list(data_1.10_clean, data_1.11_clean, 
     data_1.12.3.1_clean, data_1.12.3.2_clean, data_2.12.1_clean, 
@@
     data_3.7.2_clean, data_3.8.2_clean, data_5.1.1_clean, data_5.1.2_clean, 
-    data_5.7_clean, data_5.9.1_clean), coded_data_replications)
-
-# the averaged across studies version with added information on reported alpha
-data_h23_avg <- Data_prep_H23_avg(data_h23, data_h456_original)
-
-## graphs
-# plot accompanying the results for Hypotheses 4, 5, & 6.
-plot_456_data <- data_prep_plot_456(data_h456_original, data_h456_replications)
-# plot accompanying the results for Hypotheses 4, & 6
-plot_46_data <- data_prep_plot_46(data_h456_original[c("def_ratio", "op_ratio", "sel_ratio", "quant_ratio", "mod_ratio", "QMP_ratio")], data_h456_replications[c("def_ratio", "op_ratio", "sel_ratio", "quant_ratio", "mod_ratio", "QMP_ratio")])
-plot_46_data_rev <- data_prep_plot_46(data_h456_original[c("def_ratio", "op_REV_ratio", "sel_REV_ratio", "quant_REV_ratio", "mod_REV_ratio", "QMP_REV_ratio")], data_h456_replications[c("def_ratio", "op_REV_ratio", "sel_REV_ratio", "quant_REV_ratio", "mod_REV_ratio", "QMP_REV_ratio")])
-
-# plot accompanying the results for Hypotheses 2, & 3
-plot_23_data_alpha <- data_prep_plot_23_alpha(data_h23)
-plot_23_data_omega <- data_prep_plot_23_omega(data_h23)
-
-### Exporting the final datasets for the analyses
-# the open data
-open_data(data = data_h456_original, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_h456_original))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_h456_original))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_h456_original))), ".yml"))
-
-open_data(data = data_h456_replications, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_h456_replications))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_h456_replications))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_h456_replications))), ".yml"))
-
-open_data(data = plot_456_data, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(plot_456_data))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(plot_456_data))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(plot_456_data))), ".yml"))
-
-open_data(data = plot_46_data, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(Plot_46_data))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(Plot_46_data))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(Plot_46_data))), ".yml"))
-
-open_data(data = plot_46_data_rev, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(plot_46_data_rev))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(plot_46_data_rev))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(plot_46_data_rev))), ".yml"))
-
-open_data(data = data_h23, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_h23))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_h23))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_h23))), ".yml"))
-
-open_data(data = data_h23_avg, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(data_h23_avg))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(data_h23_avg))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(data_h23_avg))), ".yml"))
-
-open_data(data = plot_23_data_alpha, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(plot_23_data_alpha))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(plot_23_data_alpha))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(plot_23_data_alpha))), ".yml"))
-
-open_data(data = plot_23_data_omega, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(plot_23_data_omega))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(plot_23_data_omega))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(plot_23_data_omega))), ".yml"))
-
-```
-
-## Analyses
-
-Every hypothesis test in this study was a two-sided test with an alpha of .05.
-We applied no correction for multiple testing to ensure that the rate of false negatives remained low.
-Our hypotheses are about associations that have been proposed in the literature, but to the best of our knowledge have not yet been empirically tested on real data.
-In this exploratory context, we considered false negatives more detrimental than false positives.
+    data_5.7_clean, data_5.9.1_clean)
+
+# obtaining the omega and alpha values for a measure in one lab.
+get_omega_and_alpha_values <- function(Data){
+  # first we calculate alpha and ase separately in case the omega function goes haywire
+  alpha <- psych::alpha(Data)$total[["std.alpha"]]
+  ase <- psych::alpha(Data)$total[["ase"]]
+
+  # try to calculate the omega
+  result <- c(NA, NA)
+  tryCatch({
+      result <- omega(Data)
+    }, error = function(e) {
+      result <- c(NA, NA)
+    }, warning = function(w) {
+      result <- c(NA, NA)
+    })
+
+  # combine the information in one vector
+  omega_and_alpha_vec <- as.numeric(c(alpha, result[c(4, 1)], ase))
+
+  return(omega_and_alpha_vec)
+}
+
+# calculate the alpha, omega.tot, omega.hier, & ASE for all relevant datasets
+# for each lab.
+for (i in 1:length(extracted_score_data)){
+  calculated_reliability_instance <- tapply(extracted_score_data[[i]][-1], 
+                                            extracted_score_data[[i]]$g, 
+                                            get_omega_and_alpha_values)
+
+  calculated_reliability_instance <- data.frame(matrix(unlist(
+    calculated_reliability_instance), ncol = 4, byrow = TRUE))
+
+  # make sure the var names match the complete dataframe
+  colnames(calculated_reliability_instance) <- c("alpha", "omega.tot", 
+                                                 "omega.hier", "ASE")
+  # adding the measure as a group (g) indicator
+  calculated_reliability_instance$g <- i
+
+  # adding this measure's data to the total
+  calculated_reliability_lab_data <- rbind(calculated_reliability_lab_data, 
+                                       calculated_reliability_instance)
+}
+
+# removing the empty first row
+calculated_reliability_lab_data <- calculated_reliability_lab_data[-1,]
+
+# making sure group (g) is a factor
+calculated_reliability_lab_data$g <- as.factor(calculated_reliability_lab_data$g)
+
+# indexing the meta-analysis results with a specific index relating to a 
+# row (measure) in coded_data_replications
+calculated_reliability_lab_data$coded_data_index <- c(rep(10, 36), rep(11, 36), 
+  rep(14, 36), rep(14, 36), rep(29, 74), rep(30, 74), rep(31, 74), rep(34, 61), 
+  rep(39, 60), rep(42, 58), rep(51, 21), rep(51, 21), rep(59, 20), rep(60, 21), 
+  rep(61, 21), rep(65, 4), rep(66, 4), rep(74, 8), rep(76, 5))
+
+# changing the group variable to reflect measure descriptions from the text.
+# checked using:
+# coded_data_replications[unique(calculated_reliability_data$reporting_index), 3], and
+# coded_data_replications[unique(calculated_reliability_data$reporting_index), 5]
+levels(calculated_reliability_lab_data$g) <- c("Caruso et al. (2012)", 
+    "Husnu & Crisp (2010)", "Nosek et al. (2002), Math", "Nosek et al. (2002), Art", 
+    "Anderson et al. (2012), SWL", "Anderson et al. (2012), PA", 
+    "Anderson et al. (2012), NA", "Giessner & Schubert, (2007)", 
+    "Norenzayan et al. (2002)", "Zhong & Lijenquist (2006)", 
+    "Monin & Miller (2001), most", "Monin & Miller (2001), some", 
+    "Cacioppo et al. (1983), arg",  "Cacioppo et al. (1983), nfc", 
+    "De Fruyt et al. (2000)", "Albarracín et al. (2008), exp 5 verb", 
+    "Albarracín et al. (2008), exp 5 math", "Shnabel & Nadler (2008)",
+    "Vohs & Schooler (2008)")
+
+calculated_reliability_lab_data$g <- factor(calculated_reliability_lab_data$g, 
+    labels = c("Caruso et al. (2012)", 
+    "Husnu & Crisp (2010)", "Nosek et al. (2002), Math", 
+    "Nosek et al. (2002), Art", "Anderson et al. (2012), SWL", 
+    "Anderson et al. (2012), PA", "Anderson et al. (2012), NA", 
+    "Giessner & Schubert, (2007)", "Norenzayan et al. (2002)", 
+    "Zhong & Lijenquist (2006)", "Monin & Miller (2001), most", 
+    "Monin & Miller (2001), some", "Cacioppo et al. (1983), arg",  
+    "Cacioppo et al. (1983), nfc", "De Fruyt et al. (2000)", 
+    "Albarracín et al. (2008), exp 5 verb", 
+    "Albarracín et al. (2008), exp 5 math", "Shnabel & Nadler (2008)", 
+    "Vohs & Schooler (2008)"))
+
+# adding whether or not an effect replicated based on what was coded from the 
+# replication report.
+calculated_reliability_lab_data$replication_success <- c(coded_data_replications[
+    calculated_reliability_lab_data$coded_data_index, "hypothesis_support"])
+
+# store per lab calculated reliability data in the analysis data folder
+saving_to_analysis_data(calculated_reliability_lab_data)
+```
+
+```{r averaged_reliability, include = FALSE, eval = FALSE}
+# function to assess the heterogeneity in the calculated Cronbach's Alpha values
+# and get Cronbach's Alpha prediction intervals
+assess_heterogeneity<- function(data_on_alpha){
+  # run a random effects meta-analysis
+  rma_model <- rma(yi = data_on_alpha$alpha, sei = data_on_alpha$ASE, 
+                   method = "REML", control = list(stepadj = 0.5, maxiter = 1000))
+
+  # extract the relevant heterogeneity information
+  temp_tau <- sqrt(rma_model$tau2)
+  temp_QEp <- rma_model$QEp
+
+  # get prediction intervals for alpha
+  rma_prediction <- predict(rma_model)
+  temp_pi.lb <- rma_prediction$pi.lb
+  temp_pi.ub <- rma_prediction$pi.ub
+
+  return(c(temp_tau, temp_QEp, temp_pi.lb, temp_pi.ub))
+}
+
+# function to convert the lab specifc reliability to averaged
+convert_reliability_data_to_avg <- function(reliability_data){
+  # conducting the reliability-generalization meta-analysis for each measure
+  heterogeneity_results <- assess_heterogeneity(reliability_data[c(1, 4)])
+
+  # getting the avearage reliability scores for each measure
+  avg_reliabilities <- colMeans(reliability_data[1:4], na.rm = TRUE)
+
+  # indicates the measure
+  g <- reliability_data$g[[1]]
+
+  # we need one of the indices per measure as they are all the same across labs
+  coded_data_index <- reliability_data$coded_data_index[[1]]
+
+  # we need one of the indices per measure as they are all the same across labs
+  replication_success <- reliability_data$replication_success[[1]]
+
+  # extracting the reported reliability coefficient 
+  coefficient_reported <- coded_data_original$reliability_coeff[coded_data_index]
+
+  # calculating the difference between reported and calculated average 
+  # reliability coefficient
+  coeficient_difference <- coefficient_reported - avg_reliabilities[[1]]
+
+  # testing whether or not (for those studies that had a reported alpha) if
+  # it was out of the 95% bounds around the mean calculated alpha
+  population_95_bounds <- quantile(reliability_data$alpha, probs = c(0.025, 0.975))
+
+  significance_reported_coefficient <- coefficient_reported < population_95_bounds[1] | 
+                                          coefficient_reported > population_95_bounds[2]
+
+  # return all the data as a single row in the dataframe
+  return(data.frame(alpha = avg_reliabilities[[1]], omega.tot = avg_reliabilities[[2]], 
+                    omega.hier = avg_reliabilities[[3]], ASE = avg_reliabilities[[4]], 
+                    tau = heterogeneity_results[[1]], QEp = heterogeneity_results[[2]],
+                    pi.lb = heterogeneity_results[[3]], pi.ub = heterogeneity_results[[4]], 
+                    g = g, coded_data_index = coded_data_index, 
+                    replication_success, reported_coefficient = coefficient_reported, 
+                    coefficient_difference = coeficient_difference, 
+                    significance_reported_coefficient = significance_reported_coefficient))
+}
+
+# calculate the average reliability data + heterogeneity test + reported and calculated
+# reliability coefficient comparison
+avg_reliability_list <- tapply(calculated_reliability_lab_data, calculated_reliability_lab_data$g, convert_reliability_data_to_avg)
+
+# convert data output to a dataframe
+measure_reliability_data <- do.call(rbind.data.frame, avg_reliability_list)
+
+# store per measure  reliability data in the analysis data folder
+saving_to_analysis_data(measure_reliability_data)
+```
 
 # Results
-
-## Descriptives
-
-Table \@ref(tab:ReplicationNrTable) shows the number of replication sets, measures, and measures per study, as well as the proportion of successful replications, for each of the Many Labs separately and in total.
-Because each replication was nested within one of four Many Labs projects, our data had a multilevel structure.
-Furthermore, `r sum(data_h456_replications$appearance != 1)` replications used more than one primary measure, resulting in `r nrow(data_h456_replications)` measures in both `r sum(data_h456_replications$appearance == 1)` replications protocols and `r sum(coded_data_original$appearance == 1)` original articles[^2].
-Of these `r nrow(data_h456_replications)` measures `r sum(data_h456_replications$mod_check == "True")` were modified from the original to the replication[^3].
-In the replications, the data of responses on the measures was further nested in several labs per replication.
-The combined sample size of all labs in the replications was on average `r round(mean(data_h456_replications[data_h456_replications$appearance == 1]$N), 0)`, which was approximately `r round(mean(data_h456_replications[data_h456_replications$appearance == 1]$N) / mean(data_h456_original[data_h456_original$appearance == 1 & !is.na(data_h456_original$N),]$N), 0)` times larger than the average in original studies, which were conducted in single labs.
-
-[^2]: Initially the original articles contained 3 more measures than the replication protocols.
-This difference was due to the way that the moral foundations questionnaire was framed in the original article compared to in the replication protocol.
-In the original article it was framed as measuring five different moral foundations, while in the replication protocol the measure assessed the two overarching categories that were used to test the main effect in both the original and replication research.
-The measurement information reported was comparable across all five categories, and thus it was deemed that the measurement could be reduced to reflect two overarching categories facilitate easier comparison between measurement in original and replication.
-
-[^3]: For 7 measures the number of items were modified from the original article to the replication.
-To check whether or not this had a confounding impact on our results, we re-ran the analyses testing the hypotheses excluding data from these studies (see [Supplementary Analyses E](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_item_reduced_measures_analyses.Rmd)).
-We found that removing these measures’ data had minimal impact on the overall results.
-Therefore, the results presented below are based on data from all the measures.
-
-```{r ReplicationNrTable, warning = FALSE}
-# construct the replication ratio table to be printed
-replication_nr_table <- data.frame("Many Labs Version" = c("1", "2", "3", "5", "Total"),
-                                      "N Total" = c(table(data_h456_replications$many_labs_version), nrow(data_h456_replications)), 
-                                      "N Replicated" = c(table(data_h456_replications$many_labs_version, data_h456_replications$hypothesis_support)[, "Yes"], table(data_h456_replications$hypothesis_support)["Yes"]))
+## Reliability & Validity reporting
+Figure 1 depicts the flow of measures in relation to reliability reporting.
+First, it shows that almost half of the measures in both replication (N = 37) and original research (N = 35) were single-item measures.
+Only thirteen measures in original and four in replications were reported with a reliability indicator.
+Cronbach’s Alpha was the most commonly reported reliability indicator.
+
+```{r ReliabilityReportingFlowDiagram, fig.cap = "Reliability reporting flow diagram.
+Figure shows the number of measures as reported in both the replication protocols and original article, which meet the criterion in the box within the diagram and those criteria before it.", out.height = "60%"}
+knitr::include_graphics(path = "../../SupplementaryMaterials/reliability_reporting_flow_diagram.png")
+```
+
+Validity evidence was even less common than reliability evidence.
+Only, `r sum(coded_data_original$sel_psychometric_evidence_REV != "None" & coded_data_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_original$sel_3_REV == TRUE, na.rm = TRUE)` original studies and `r sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_replications$sel_3_REV == TRUE, na.rm = TRUE)` replications reported psychometric evidence on the .
+Most commonly exploratory factor analyses or convergent validity information were presented.
+Only `r sum(coded_data_original$sel_4 == TRUE, na.rm = TRUE)` original studies & `r sum(coded_data_replications$sel_4 == TRUE, na.rm = TRUE)` replications reported psychometric validity evidence from previous studies.
+
+```{r code on the reporting of validity evidence}
+table(coded_data_original$sel_psychometric_evidence_REV)
+table(coded_data_replications$sel_psychometric_evidence_REV)
+
+sum(coded_data_original$sel_psychometric_evidence_REV != "None" & coded_data_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_original$sel_3_REV == TRUE, na.rm = TRUE)
+sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_replications$sel_3_REV == TRUE, na.rm = TRUE)
+
+table(coded_data_original$sel_psychometric_evidence_text_REV)
+table(coded_data_replications$sel_psychometric_evidence_text_REV)
+
+# internal
+table(coded_data_original$sel_3_REV)
+table(coded_data_replications$sel_3_REV)
+# external
+table(coded_data_original$sel_4)
+table(coded_data_replications$sel_4)
+
+sum(coded_data_original$sel_4 == TRUE, na.rm = TRUE)
+sum(coded_data_replications$sel_4 == TRUE, na.rm = TRUE)
+
+sum(coded_data_original$sel_existing == "True, namely:")
+sum(coded_data_replications$sel_existing == "True, namely:")
+
+sum(coded_data_original$op_1_REV[coded_data_original$sel_existing == "True, namely:"] == TRUE, na.rm = TRUE)
+sum(coded_data_replications$op_1_REV[coded_data_replications$sel_existing == "True, namely:"] == TRUE , na.rm = TRUE)
+
+```
+
+It was clear that existing measures were used in `r sum(coded_data_original$sel_existing == "True, namely:")` original and `r sum(coded_data_replications$sel_existing == "True, namely:")` replication cases, with specific version reported in `r sum(coded_data_original$op_1_REV[coded_data_original$sel_existing == "True, namely:"] == TRUE, na.rm = TRUE)` original and `r sum(coded_data_replications$op_1_REV[coded_data_replications$sel_existing == "True, namely:"] == TRUE , na.rm = TRUE)` replication cases.
+
+???check if reporting of reliability/validity (ALL QMPS) more commonm for existing and sourced measures than new ones (relates to the idea of reporting bias I explore in the piece)???
+
+## Questionable Measurement Practices
+
+Besides Reliability and validity evidence it is also relevant to know what was measured to evaluate if it was measured well.
+What we found however was that for XXX original and XXX replication a clear variable assessed by the measurement was defined.
+The logic behind how that variable was operationalized was reported for XXX original and XXX replication.
+Finally, a reason was given for selecting an existing measure or creating a new measure in XXX original and XXX replication.
+
+Several items also indicated how the measurement was implemented: XXX the administration format was indicated, XXX the assessment environment described, XXX the steps to administer the measure were described.
+To recreate/understand the items of the measure we looked at if they reported: XXX the number of items were described, XXX the number of response options were described, XXX any example items were shown.
+Finally, to use the item scores for analyses you need to know the following: XXX any recoding was explained, XXX the calculation of an index (if used) was described.
+
+The concept of consistency in assessing a phenomenon across original and replication is important but also complex and difficult to access because … .
+However, we do we have some information on when modifications were made to certain aspects of the measure between original and replication.
+For XXX replications any administration format change was indicated, and for XXX of those that choice was justified/validated.
+For XXX replications any assessment environment change was indicated, and for XXX of those that choice was justified/validated.
+For XXX replications any change in the number of items or the number of response options was indicated, and for XXX of those that choice was justified/validated … some practical examples of numbers of items being changed ???to showcase that happening and prep that for discussion as being a reasonable reason to say that the same phenomenon may not even be assessed at that point???.
+
+Table 2 below shows for both original and replication for all of the QMP items the ratio of QMPs and for how many of the 77 measures the QMP was applicable.
+Meanwhile, the Phi coefficient indicates the “correlation” between the MP being questionable or good in the original and the same for the replication.
+The average Phi was … .
+
+```{r qmp_table}
+# create informative Measurement Practice Labels
+MPractice <- c("Reliability is reported", "It is clear if the measure existed or is newly created", 
+  "Specifc version of the measure is specified", "Validity evidence from a factor analysis is presented",
+  "The measured variable is defined", "The choice of measure selection or creation is justified", 
+  "The implemented operationalisation is justified", "The source of the measure is provided", 
+  "Psychometric evidence from the study is given", "Psychometric evidence from an earlier study is given", 
+  "The administration format and environment are described", "The administration procedure is described",
+  "The number of items are described", "The number of response options are described", 
+  "The recoding of responses is described", "The creation of the index is described", 
+  "Example items are presented in text or supplement", "Any administration format changes are mentioned", 
+  "Administration format changes are justified/validated", "Any translations are mentioned", 
+  "Translated measures are justified/validated", "Any changes in number of items or response options are mentioned", 
+  "Changes in number of items or response options are justified/validated")
+
+# construct the QMP table to be printed
+QMP_table <- data.frame("Practice" = MPractice,
+                        "QMP original" = paste0(qmp_ratio_data$QMP_percentage_original, 
+                                                " (", qmp_ratio_data$N_applicable_original, ")"),
+                        "QMP Replication" = paste0(qmp_ratio_data$QMP_percentage_replication, 
+                                                " (", qmp_ratio_data$N_applicable_replication, ")"),
+                        "Phi" = qmp_ratio_data$Phi)
 
 # Changing column names to be less computer speak-y looking
-colnames(replication_nr_table) <- c("Many Labs Version", "Nr. Measures", 
-                                    "Nr. Replicated")
-
-# adding replication ratio's to the Nr. Replicated column
-replication_ratio <- apa_num(replication_nr_table$"Nr. Replicated" / replication_nr_table$"Nr. Measures", gt1 = FALSE)
-
-replication_nr_table$"Nr. Replicated"[c(1, 2, 4, 5)] <- paste(replication_nr_table$"Nr. Replicated"[c(1, 2, 4, 5)], paste0("(", replication_ratio[c(1, 2, 4, 5)], ")"))
-
-# adding a superscript for a later footnote
-replication_nr_table$"Nr. Replicated"[3] <- paste(paste0(replication_nr_table$"Nr. Replicated"[3], "$^a$"), paste0("(", replication_ratio[3], ")"))
+colnames(QMP_table) <- c("Practice", "QMP org", "QMP rep", "Phi")
 
@@
 apa_table(
-  replication_nr_table, align = c("l", "r", "r")
-  , caption = "Ratio of measures for which the effect was considered replicated, across many labs projects"
-  , note = "Nr.
-measures refer to the total number of primary measures extracted, while Nr.
-replicated displays the number of measures for which the associated effect was replicated successfully.
-The value between brackets represents the ratio of replications.
-$^a$replication was assessed as unclear for three other measures, since their effect was only partially replicated.
-These have been treated as not replicated within this table and in further analyses throughout the article.
-"
-  , escape = FALSE, placement = "htp", midrules = 4)
-
-```
-
-Because of this multilevel structure we preregistered multilevel random-intercept and random-slope models alongside our single-level regression models for testing Hypothesis 3, 5, and 6.
-However, because group sizes turned out to be too small to support random slope models, we omitted the results from these analyses from the main article and  instead report them in [Supplementary Analyses B](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_multilevel_analyses.Rmd) for the sake of completeness and transparency.
+  QMP_table, align = c("l", "r", "r", "r")
+  , caption = "Ratio of QMPs and number of applicable measures, for original and replication"
+  , note = "The first number in QMP org and QMP rep is the ratio of measures for which the practice in that row was not conducted well by our standards.
+The number between brackets indicates the number of measures for which the practice was applicable."
+  , escape = FALSE, placement = "htp")
+
+```
 
 ## Measurement Reliability
-
-If data from a multiple-item scale could be accessed, we calculated the Cronbach’s Alpha of that scale from that data for each lab that administered the scale.
-Subsequently, we included the multiple estimates of Cronbach’s Alpha for those measures into an unregistered meta-analysis of the reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analysis [@vacha-haase1998ReliabilityGeneralizationExploring; @botella2012ManagingHeterogeneityVariance; @lopez-ibanez2024ReliabilityGeneralizationMetaanalysis].
-This enabled us to quantify the degree of true variation (or heterogeneity) in reliability coefficients across lab locations.
-
-For Cronbach’s alpha, we used formulas 2 & 3 from Duhachek and Lacobucci (2004) to calculate the standard error in the meta-analysis.
-Heterogeneity was estimated using the tau value, which indicates the standard deviation of the distribution of true Cronbach’s alpha coefficients for a measure, and tested using the Cochran’s Q test for each measure.
-We performed the RG meta-analysis using the *rma* function from the *metafor* R package [*v`r getNamespaceVersion("metafor")[[1]]`*\; @R-metafor] and default settings.
-We implemented no correction for bias, because the Many Labs replications were not at risk of publication bias.
-
-The average calculated Cronbach’s alpha coefficient across replication sets was `r apa_num(mean(data_h23$alpha), digits = 3)` with a standard deviation `r apa_num(sd(data_h23$alpha, na.rm = TRUE), digits = 3)`.
-Figure \@ref(fig:Plot23AlphaCode) displays the distributions of the calculated Cronbach’s Alpha scores from each lab for each measure, separated by successful and unsuccessful replication.
-
-```{r ReorderPlot23Data, warning = FALSE}
-# data re-ordering (factor order was not saved in export)
-plot_23_data_alpha_reordered <- plot_23_data_alpha
-plot_23_data_alpha_reordered$g <- fct_inorder(as.factor(plot_23_data_alpha$g), ordered = NA)
-
-data_h23_avg$graph_index <- NA
-# adding an index to which row in the plot data the row in data_h23_avg belongs to
-for (i in 1:nrow(data_h23_avg)){
-  data_h23_avg$graph_index[which(unique(plot_23_data_alpha_reordered$g)[i] == data_h23_avg$g)] <- i
-}
-```
-
-```{r Plot23AlphaCode, warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the eighteen measures for which raw data was available from which Cronbach’s alpha coefficients could be calculated.
+The average calculated Cronbach’s alpha coefficient across replication sets was 0.787 with a standard deviation 0.167.
+Figure 2 displays the distributions of the calculated Cronbach’s Alpha scores from each lab for each measure, separated by successful and unsuccessful replication, based on the meta-analytic p-value (alpha , .05) retrieved from the Many Labs reports.
+
+```{r alpha_distributions_data_prep}
+### PREPARE CODE FOR THE ALPHA DISTRIBUTIONS FIGURE 
+calculated_alpha_plot_data <- calculated_reliability_lab_data
+
+# calculating the average alpha per group
+calculated_alpha_plot_data$avg.alpha <- ave(calculated_reliability_lab_data$alpha, 
+                                            calculated_reliability_lab_data$g)
+
+# making replication success a Boolean which can affect order
+calculated_alpha_plot_data$replication_success <- ifelse(
+  calculated_alpha_plot_data$replication_success == "Yes", TRUE, FALSE)
+
+# reordering the plot from least to most reliable split by replication success
+calculated_alpha_plot_data <- calculated_alpha_plot_data[order(-calculated_alpha_plot_data$replication_success, -calculated_alpha_plot_data$avg.alpha),]
+
+# Making sure there are no calculated alpha's that fell below 0 in the plot.
+calculated_alpha_plot_data <- calculated_alpha_plot_data[calculated_alpha_plot_data$alpha > 0,]
+
+# reordering 
+calculated_alpha_plot_data$g <- fct_inorder(as.factor(calculated_alpha_plot_data$g), ordered = NA)
+
+# adding an index to which row in the plot data the row in measure_reliability_data belongs to
+measure_reliability_data$graph_index <- NA
+
+for (i in 1:nrow(measure_reliability_data)){
+  measure_reliability_data$graph_index[which(unique(calculated_alpha_plot_data$g)[i] == measure_reliability_data$g)] <- i
+}
+
+```
+
+```{r plot_alpha_distributions, warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the nineteen measures for which raw data was available from which Cronbach’s alpha coefficients could be calculated.
 The green lines indicate the meta-analytic prediction interval lower and upper bound.
@@
 The Tau column besides the figure shows the tau heterogeneity estimate based on a meta-analysis of the calculated reliabilities for each measure.
-Meta-analyses for which the Q-test for heterogeneity was signicant at alpha < .05 are in black, while non-significant results are in grey.
-The Diff column shows the difference between reported reliability and the average reliability calculated from the Many Labs data for the applicable measures, the reported reliabilities that fell outside the 95% quantile of calculated reliability scores are shown in bold."}
-
-# plot for alpha
-ggplot(plot_23_data_alpha_reordered, aes(x = alpha, y = g)) +
+Meta-analyses for which the Q-test for heterogeneity was significant at alpha < .05 are in black, while non-significant results are in grey.
+The Diff column shows the difference between reported reliability and the average reliability calculated from the Many Labs data for the applicable measures, the reported reliabilities that fell outside the 95% quantile of calculated reliability scores are shown in black, otherwise in grey."}
+measure_reliability_data[!is.na(measure_reliability_data$coefficient_difference),]$graph_index
+
+# plot for distribution of alpha
+ggplot(calculated_alpha_plot_data, aes(x = alpha, y = g)) +
   geom_boxplot(outlier.shape = NA) +
@@
   # adding in the tau values
-  geom_text(label = format(plot_23_data_alpha_reordered$tau, digits = 1), x = 1.15, size = 2.8, alpha = ifelse(plot_23_data_alpha_reordered$QEp < .05, 1, 0)) +
-  geom_text(label = format(plot_23_data_alpha_reordered$tau, digits = 1), x = 1.15, size = 2.8, alpha = ifelse(plot_23_data_alpha_reordered$QEp >= .05, 1, 0), colour = "grey") +
-
-  # adding in the alpha annotations
-  annotation_custom(grob = textGrob(label = format(round(data_h23_avg$coeficient_difference[1], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(data_h23_avg$significance_reported_coefficient[1], "bold", "plain"))), ymin = data_h23_avg$graph_index[1], ymax = data_h23_avg$graph_index[1], xmin = 1.24, xmax = 1.24) +
-
-  annotation_custom(grob = textGrob(label = format(round(data_h23_avg$coeficient_difference[2], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(data_h23_avg$significance_reported_coefficient[2], "bold", "plain"))), ymin = data_h23_avg$graph_index[2], ymax = data_h23_avg$graph_index[2], xmin = 1.24, xmax = 1.24) +
-
-  annotation_custom(grob = textGrob(label = format(round(data_h23_avg$coeficient_difference[3], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(data_h23_avg$significance_reported_coefficient[3], "bold", "plain"))), ymin = data_h23_avg$graph_index[3], ymax = data_h23_avg$graph_index[3], xmin = 1.24, xmax = 1.24) +
-
-  annotation_custom(grob = textGrob(label = format(round(data_h23_avg$coeficient_difference[4], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(data_h23_avg$significance_reported_coefficient[4], "bold", "plain"))), ymin = data_h23_avg$graph_index[4], ymax = data_h23_avg$graph_index[4], xmin = 1.24, xmax = 1.24) +
-
-  annotation_custom(grob = textGrob(label = format(round(data_h23_avg$coeficient_difference[5], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(data_h23_avg$significance_reported_coefficient[5], "bold", "plain"))), ymin = data_h23_avg$graph_index[5], ymax = data_h23_avg$graph_index[5], xmin = 1.24, xmax = 1.24) +
-
-  annotation_custom(grob = textGrob(label = format(round(data_h23_avg$coeficient_difference[6], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(data_h23_avg$significance_reported_coefficient[6], "bold", "plain"))), ymin = data_h23_avg$graph_index[6], ymax = data_h23_avg$graph_index[6], xmin = 1.24, xmax = 1.24) +
-
-  annotation_custom(grob = textGrob(label = format(round(data_h23_avg$coeficient_difference[7], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(data_h23_avg$significance_reported_coefficient[7], "bold", "plain"))), ymin = data_h23_avg$graph_index[7], ymax = data_h23_avg$graph_index[7], xmin = 1.24, xmax = 1.24) +
-
-  annotation_custom(grob = textGrob(label = format(round(data_h23_avg$coeficient_difference[8], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(data_h23_avg$significance_reported_coefficient[8], "bold", "plain"))), ymin = data_h23_avg$graph_index[8], ymax = data_h23_avg$graph_index[8], xmin = 1.24, xmax = 1.24) +
-
-  annotation_custom(grob = textGrob(label = format(round(data_h23_avg$coeficient_difference[18], 2), nsmall = 2), hjust = 0, gp = gpar(fontsize = 8, fontface = ifelse(data_h23_avg$significance_reported_coefficient[18], "bold", "plain"))), ymin = data_h23_avg$graph_index[18], ymax = data_h23_avg$graph_index[18], xmin = 1.24, xmax = 1.24) +
-
+  geom_text(data = measure_reliability_data, label = format(measure_reliability_data$tau, digits = 1), x = 1.15, y = measure_reliability_data$graph_index, color = ifelse(measure_reliability_data$QEp < .05, "black", "grey"), size = 2.8) +
+
+  # adding in the difference in alpha coefficients
+  geom_text(data = measure_reliability_data[c(1:8, 18),], label = format(measure_reliability_data$coefficient_difference[c(1:8, 18)], digits = 2), x = 1.28, y = measure_reliability_data[!is.na(measure_reliability_data$coefficient_difference),]$graph_index, color = ifelse(measure_reliability_data$significance_reported_coefficient[c(1:8, 18)], "black", "grey"), size = 2.8) +
+
+  # setting the theme
   theme_minimal() +
@@
   annotation_custom(grob = textGrob(label = "Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 6, ymax = 6, xmin = 0.01, xmax = 0.01) +
-  annotation_custom(grob = textGrob(label = "Tau", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.08, xmax = 1.08) +
+  annotation_custom(grob = textGrob(label = "Tau", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.1, xmax = 1.1) +
   annotation_custom(grob = textGrob(label = "Diff", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.24, xmax = 1.24) +
@@
   # adding the blue triangles for reported reliability and green prediction intervals
-  geom_point(data = data_h23_avg, mapping = aes(x = coefficient_reported, y = graph_index), color = "blue", shape = 17, size = 3) +
-  geom_point(mapping = aes(x = pi.lb), color = "green", shape = 124, size = 2.5) + 
-  geom_point(mapping = aes(x = pi.ub), color = "green", shape = 124, size = 2.5) +
+  geom_point(data = measure_reliability_data, mapping = aes(x = reported_coefficient, y = graph_index), color = "blue", shape = 17, size = 3) +
+  # we remove 14 & 15 lower bound because they are below 0
+  geom_point(data = measure_reliability_data[-c(14, 15),], mapping = aes(x = pi.lb, y = graph_index), color = "green", shape = 124, size = 2.5) + 
+  geom_point(data = measure_reliability_data, mapping = aes(x = pi.ub, y = graph_index), color = "green", shape = 124, size = 2.5) +
 
@@
 
-The distribution of reliabilities varied across measures.
-Most of the measures near the bottom showed average reliability scores of at least .80, corresponding to adequate reliability for general research purposes [@nunnally1994assessment], with minimal variation between labs.
-However, other measures showed not only considerably lower average reliability scores, but also greater variation.
-Finally, the blue triangles indicate Cronbach’s Alpha reported in the original articles.
-The reliabilities were generally only reported in original studies for those measures with a large average calculated reliability in the replications.
-
-### Hypothesis 1: Reliability Reporting in Original and Replication Research
-
-```{r ReportedReliabiltiesRetrieval}
-N_reported_reliabilities_original <- sum(data_h456_original$reliability_type != "Not Reported" & data_h456_original$reliability_type != "")
-
-N_reported_reliabilities_replications <- apa_num(sum(data_h456_replications$reliability_type != "Not Reported" & data_h456_replications$reliability_type != ""), numerals = FALSE)
-
-N_reported_reliabilities_replications_number_style <- apa_num(sum(data_h456_replications$reliability_type != "Not Reported" & data_h456_replications$reliability_type != ""))
-```
-
-Because we counted only `r N_reported_reliabilities_original` reported reliabilities in original articles and `r N_reported_reliabilities_replications` reliabilities reported in replications, we decided against using our pre-registered Mann-Whitney U test to test the difference in the reported value of Cronbach’s Alpha between original articles and replications.
-Instead, we displayed the difference between the reported reliability in the original article and the calculated average reliability in replications in the Diff column in Figure \@ref(fig:Plot23AlphaCode).
-Contrary to Hypothesis 1, this column shows that the reported reliability in original articles was generally lower than the average reliability in the replication sample.
-Still, more than half of the reported reliabilities in original studies fell within the 95-percentile range around the replication average.
-
-### Hypothesis 2: Within Study Variation in Reliability
-
-To get an indication of the true variability in the reliability scores, we used the RG meta-analyses to test for heterogeneity in the reliabilities across replication labs.
-Even though, we preregistered the ICC of reliability in a multilevel model as an indicator of within study variation in reliability relative to between study variation, we opted for the heterogeneity test to obtain a more informative absolute estimate of the within study variation in true reliability score to test Hypothesis 2.
-(results from the preregistered analysis are shown in [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd)).
-
-Figure \@ref(fig:Plot23AlphaCode) displays the estimates of tau, which indicates the differences in true reliability scores between labs for a given measure.
-For `r sum(data_h23_avg$QEp > .05)` measures, the tau estimate was not significantly different from 0, meaning the true variation in reliability across labs was not significant.
-However, for the other `r apa_num(sum(data_h23_avg$QEp <= .05), numerals = FALSE)` measures the true reliability was quite variable.
-For instance, the estimate of the standard deviation of the true reliability of the top measure in the graph (a measure of conscientiousness from @gosling2003very used in the replication of @defruyt2000cloninger) equaled `r apa_num(data_h23_avg$tau[data_h23_avg$g == "De Fruyt et al.
-(2000)"], digits = 3, gt1 = FALSE)` points of Cronbach’s Alpha.
-
-Thus, for around a quarter of the measures, the reliability was heterogeneous across labs.
-Although for the remaining measures, we found no significant heterogeneity in reliabilities, we note that the power to detect small heterogeneity is often low  [@ioannidis2007uncertainty; @olsson2020heterogeneity].
-
-### Hypothesis 3: Reliability and Replicability
-
-```{r Hypothesis3MainTest, include = FALSE}
-## The main model to test hypothesis 3, through a logistic regression model.
-H3_test_main_alpha <- glm(formula = replication_success ~ 1 + alpha, 
-                                 family = binomial(), data = data_h23_avg)
-
-H3_test_result_main_alpha <- apa_print(H3_test_main_alpha)
-
-# coefficient is positive but not significant.
-
-# adding OR to the result
-H3_main_full_results_alpha_with_OR <- OR_to_apa_full_supplier(H3_test_result_main_alpha$full_result$alpha, negative_b = FALSE)
-
-# well this OR is quite a ridiculous number..., but then again a step from 0 alpha to 1 is quite a jump too...
-
-### rerunning the analyses but now with a standardized alpha value
-# transforming the alpha variable 
-scaled_alpha <- scale(data_h23_avg$alpha)
-scaled_alpha
-
-# rerunning the model with the transformed alpha variable Nr.2
-H3_test_interpretable_alpha <- glm(formula = data_h23_avg$replication_success ~ 1 + scaled_alpha, family = binomial())
-
-H3_test_result_interpretable_alpha <- apa_print(H3_test_interpretable_alpha)
-
-H3_interpretable_full_results_alpha_with_OR <- OR_to_apa_full_supplier(H3_test_result_interpretable_alpha$full_result$scaled_alpha, negative_b = FALSE, not_significant = TRUE) # with this method the result is contained to more sensible numbers.
-However, we opt to report the unstandardized numbers without Odds-ratio, to more transparently reflect the instability in our estimate due to alpha's boundedness, the small sample, and limited observed variation in alpha.
-```
-
-We used a logistic regression model to test whether replication success as reflected in a significant mean effect in the meta-analysis conducted across the replicating labs could be predicted by the average calculated reliabilities of the measures.
-Cronbach’s alpha did not significantly predict replication success in the main logistic regression model (`r H3_test_result_main_alpha$full_result$alpha`)[^4].
-Results based on the Omega coefficient lead to a similar conclusion (see [Supplementary Analyses C](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_omega_analyses.Rmd)).
-
-[^4]: The log-odds ratio’s CIs are reported instead of the odds-ratios CIs for this result, as the latter were extremely wide due to Cronbach alpha’s boundedness and the small number of calculated reliabilities.
-
-```{r Hypothesis3WhiteAdjustedSensitivityAnalysis, warning = FALSE}
-# We take the H3_test_main_alpha result from the main analysis on the aggregate
-# level as reported in the main text, and then calculate the White heteroskedastic 
-# variance/covariance matrix for the coefficients
-White_varcov_matrix <- vcovHC(H3_test_main_alpha, type = "HC1") # HC1 applies White's correction
-
-# now we apply this covariance matrix to get robust standard errors on our estimation
-H3_test_alpha_White_adjusted <- coeftest(H3_test_main_alpha, White_varcov_matrix)
-
-H3_coefficient_alpha_White_adjusted <- H3_test_alpha_White_adjusted[2,1]
-
-## we then convert it to apa_num format
-# first we calculate the log-odds ratio CIs
-log_OR_CI_LOW <- H3_coefficient_alpha_White_adjusted - (1.96 * H3_test_alpha_White_adjusted[2,2])
-log_OR_CI_HI <- H3_coefficient_alpha_White_adjusted + (1.96 * H3_test_alpha_White_adjusted[2,2])
-
-# then we create the string to print in text
-H3_test_result_alpha_White_adjusted <- paste0("$\\hat{\\beta} = ", round(H3_test_alpha_White_adjusted[2,1], 2), "$, 95\\% CI $[", round(log_OR_CI_LOW, 1), ", ", round(log_OR_CI_HI, 1), "]$, $z = ", round(H3_test_alpha_White_adjusted[2,3], 2), "$, $p = ", apa_p(H3_test_alpha_White_adjusted[2,4]), "$")
-
-### This version contains the Odds-ratio
-# first we calculate the odds-ratio
-OR_coefficient_alpha_White_adjusted <- round(exp(H3_coefficient_alpha_White_adjusted), 1)
-
-# and then convert them to odds ratio CIs
-OR_CI_LOW <- round(exp(log_OR_CI_LOW), 1)
-OR_CI_HI <- round(exp(log_OR_CI_HI), 1)
-
-# now we create the string to print in text
-H3_OR_test_result_alpha_White_adjusted <- paste0("$\\hat{\\beta} = ", round(H3_test_alpha_White_adjusted[2,1], 2), "$, $OR = ", OR_coefficient_alpha_White_adjusted, "$, 95\\% CI $[", OR_CI_LOW, ", ", OR_CI_HI, "]$, $z = ", round(H3_test_alpha_White_adjusted[2,3], 2), "$, $p = ", apa_p(H3_test_alpha_White_adjusted[2,4]), "$") # again, however, we omit this version from the main text for the same reasons as given in the code block above.
-
-```
-
-We additionally pre-registered multilevel regression model of the same relationship with each lab’s unique reliability nested within the set of replications of an effect.
-However, because our dependent variable (replicability) is at the group level, we decided to use a test on the aggregate level using White’s heteroscedasticity adjustment to address the dependency [as suggested by @foster-johnson2018Predicting].
-This analysis also showed a non-significant relation (`r H3_test_result_alpha_White_adjusted`).
-However, it should be noted that for these analyses the reliability coefficient could be calculated for only `r nrow(data_h23_avg)` measures.
-As a result, the estimates of the relation between reliability and replication success obtained using these models each come with large uncertainty.
-
-## Measurement Reporting
-
-### Reliability & Validity Reporting
-
-Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts the flow of measures in relation to reliability reporting.
-First, it shows that almost half of the measures in both replication (N = `r apa_num(sum(data_h456_replications$N_items == "1 item measure"))`) and original research (N = `r apa_num(sum(data_h456_original$N_items == "1 item measure"))`) were single-item measures.
-When looking at the multiple-item measures, the graph illustrates that `r N_reported_reliabilities_replications` measures in the replication protocols (`r apa_num((as.numeric(N_reported_reliabilities_replications_number_style) / sum(data_h456_replications$N_items != "1 item measure")) * 100, digits = 1)` \%) and `r N_reported_reliabilities_original` measures in the original articles (`r apa_num((as.numeric(N_reported_reliabilities_original) / sum(data_h456_original$N_items != "1 item measure")) * 100, digits = 1)` \%) reported a reliability coefficient.
-The most commonly reported reliability coefficient was Cronbach’s Alpha, which accounted for `r apa_num(sum(data_h456_replications$reliability_type == "alpha"), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(data_h456_original$reliability_type == "alpha"))` in the original articles.
-
-```{r ReliabilityReportingFlowDiagram, fig.cap = "Reliability reporting flow diagram.
-Figure shows the number of measures as reported in both the replication protocols and original article, which meet the criterion in the box within the diagram and those criteria before it.", out.height = "60%"}
-knitr::include_graphics(path = "../../SupplementaryMaterials/reliability_reporting_flow_diagram.png")
-```
-
-```{r ReportingInformation, include = FALSE}
-## first some descriptives of reliability reporting
-# we get these descriptives from the combination of both replication and original
-# QMP data.
-
-reporting_data <- rbind(data_h456_original, data_h456_replications)
-
-# Measurement type per original and replication:
-reliability_reporting_descriptive_table_1 <- table(reporting_data$rep_org, reporting_data$N_items)
-
-# amount of reliability reported per original and replication 
-# (given that measure is a multiple item measure):
-reliability_reporting_descriptive_table_2 <- table(reporting_data$rep_org[reporting_data$N_items == "multiple item measure"], reporting_data$reliability_type[reporting_data$N_items == "multiple item measure"])
-
-# A chi square test for difference in N reliability reported for multiple 
-# item measures.
-reliability_reporting_test_result <- chisq.test(reporting_data$rep_org[reporting_data$N_items == "multiple item measure"], reporting_data$reliability_reported[reporting_data$N_items == "multiple item measure"])
-
-# a variable indicating whether there was evidence from a factor analysis 
-factor_present <- c(reporting_data$sel_psychometric_evidence_REV != "None" & reporting_data$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")
-
-# A chi square test for difference in N factor analysis evidence reported for multiple 
-# item measures.
-factor_reporting_test_result <- chisq.test(reporting_data$rep_org, factor_present)
-
-```
-
-Reliability was more commonly reported in original (N = `r N_reported_reliabilities_original`; `r apa_num((as.numeric(N_reported_reliabilities_original) / nrow(data_h456_original)) * 100, digits = 1)` \%) as compared to replication research (N = `r N_reported_reliabilities_replications_number_style`; `r apa_num((as.numeric(N_reported_reliabilities_replications_number_style) / nrow(data_h456_replications)) * 100, digits = 1)` \%, $\chi^{2}$(`r apa_num(reliability_reporting_test_result$parameter)`) = `r apa_num(reliability_reporting_test_result$statistic)`, *p* = `r apa_p(reliability_reporting_test_result$p.value)`).
-Validity evidence was similarly reported infrequently.
-Validity evidence from a factor analysis was reported in `r apa_num(sum(data_h456_original$sel_psychometric_evidence_REV != "None" & data_h456_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` original articles, while in only `r apa_num(sum(data_h456_replications$sel_psychometric_evidence_REV != "None" & data_h456_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` replications.
-This difference was not significant ($\chi^{2}$(`r apa_num(factor_reporting_test_result$parameter)`) = `r apa_num(factor_reporting_test_result$statistic)`, *p* = `r apa_p(factor_reporting_test_result$p.value)`), however the total number of factor analyses reported was low.
-
-To gain a better understanding of the validity of the included measurements, we also conducted pre-registered exploratory analyses testing the unidimensionality of `r nrow(cfa_results)` measures with available replication data using a confirmatory factor analysis.
-We reasoned that most of the included measures should theoretically tap into a single construct, so evidence for unidimensionality would serve as a proxy for evidence of higher construct validity.
-We found that `r sum(cfa_results$Single_factor == "Yes", na.rm = TRUE)` of these measures (`r apa_num((sum(cfa_results$Single_factor == "Yes", na.rm = TRUE) / nrow(cfa_results)) * 100, digits = 1)` \%) met our criteria for unidimensionality (see [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd) for further details).
-
-### Hypothesis 4: QMPs in Original Compared to Replication Research
-
-```{r numberNAsForQMPRatio}
-# calculating the ratio of NA responses for the revised QMP items, or the initial
-# items in case those items were not revised.
-ratio_of_NAs <- sum(is.na(reporting_data$def1) + is.na(reporting_data$op_1_REV) + is.na(reporting_data$op_2_REV) + is.na(reporting_data$op_3) + is.na(reporting_data$op_4) + is.na(reporting_data$op_5_REV) + is.na(reporting_data$sel_1_REV) + is.na(reporting_data$sel_1) + is.na(reporting_data$sel_2) + is.na(reporting_data$sel_3_REV) + is.na(reporting_data$sel_4) + is.na(reporting_data$quant_1_REV) + is.na(reporting_data$quant_2_REV) + is.na(reporting_data$quant_3_REV) + is.na(reporting_data$quant_4) + is.na(reporting_data$mod_1_REV) + is.na(reporting_data$mod_2_REV) + is.na(reporting_data$mod_3_REV) + is.na(reporting_data$mod_4_REV) + is.na(reporting_data$mod_5_REV) + is.na(reporting_data$mod_6_REV)) / (20 * 154)
-
-QMP_NA_percentage <- paste0(apa_num(ratio_of_NAs * 100, digits = 1), "%")
-
-```
-
-```{r MeanQMPCode, warning = FALSE, include = FALSE}
-# calculating mean total QMP ratios
-Mean_Rat_Rep <- mean(reporting_data$QMP_REV_ratio[reporting_data$rep_org == "Replication"])
-
-Mean_Rat_Org <- mean(reporting_data$QMP_REV_ratio[reporting_data$rep_org == "Original"])
-```
-
-Overall, the QMP ratios (i.e., the ratio of the total number of measurement practices that were not transparently and fully reported on) were low in both original and replication studies.
-The top part of Figure \@ref(fig:Plot456Code) displays the distributions of the total QMP ratio for both original articles and replication protocols, showing that the average QMP ratio in replication protocols was smaller (`r apa_num(Mean_Rat_Rep)`) than in original articles (`r apa_num(Mean_Rat_Org)`).
-The bottom of Figure \@ref(fig:Plot456Code) displays the observed QMP ratios per QMP type for both original articles and replication protocols, showing that original articles tended to contain fewer Definition QMPs, but more selection and operationalization QMPs, with Quantification QMPs being comparable.
-The number of measures that were modified also differed between original and replication.
-In total `r QMP_NA_percentage` of all responses across all QMP items were non-applicable.
-
-```{r Plot456Code, warning = FALSE, fig.cap = "QMP ratio counts for each QMP Type and QMP total ratio distribution grouped by whether the QMP ratio was obtained from an original article or a replication protocol.
-The top graph shows the distributions of total QMP ratios for both replication protocols and original articles, with the vertical line indicating the mean QMP ratio.
-The specific observed values are indicated along the bottom row with dots.
-The bottom row shows for each QMP type the proportions of each QMP ratio obtained, darker colors represent proportionally more QMPs, grey means modification did not occur for that measure."}
-
-# re-ordering the QMP-types, because it didn't save
-plot_456_data$QMP_type <- factor(plot_456_data$QMP_type, levels = c("Definition", "Selection", "Operationalisation", "Quantification", "Modification", "Total"))
-
-# shortening the replication and original labels for nicer plot 1
-levels(plot_456_data$RepOrg) <- c("Org.", "Rep.")
-
-### ratio (REV) Original and Rep
-# QMP type specific QMP ratios
-Plot_456_1 <- ggplot(plot_456_data[plot_456_data$QMP_type != "Total",], 
-                      aes(x = RepOrg, fill = as.factor(QMP_ratio_1_REV))) + 
-  geom_bar(position = "fill") +
+We found some indication of heterogeneity for fourteen of the nineteen measures.
+We observe that for most measures the reported reliabilities were generally lower than the reliabilities calculated for the replication labs.
+We also observed that original reliabilities were more commonly reported for those measures that had higher average reliabilities among the replications (>.80) compared to on average less reliable measures.
+
+However,  to be able to interpret Cronbach’s alpha, the underlying assumptions have to be met: undimensionality, uncorrelated item errors, and Tau equivalence.
+Our CFA results show (summarized in Table 3 below) that … .
+
+```{r validity_and_alpha_assumption_tests, include = FALSE, eval = FALSE}
+# function that runs all our checks for Cronbach's alpha. Also functions as some basic validity checks
+validity_and_alpha_assumption_tests <- function(data){
+  ### Tests for Unidimensionality
+  # Test 1a: obtaining single factor model cfa RMSEA value for evaluation
+  RMSEA_values <- c(NA, NA)
+  tryCatch({
+    # creating the base function for the model (it is unidimensional)
+    model_free <- "Factor =~ "
+
+    for (item_name in names(data)[-1]){
+      # adding all of the items from the scale to the model formula
+      model_free <- paste0(model_free, item_name, " + ")
+    }
+
+    # trimming the excess " + "
+    model_free <- substring(model_free, 1, nchar(model_free) - 3)
+
+    # fitting the free coefficient estimated single dimensional model
+    fit.modelfree <- cfa(model_free, 
+                              data = data, 
+                              std.lv = TRUE, 
+                              estimator = "MLM")
+
+    rmsea <- fitMeasures(fit.modelfree)["rmsea"] 
+    rmsea.ci.upper <- fitMeasures(fit.modelfree)["rmsea.ci.upper"]
+    rmsea.se <- (rmsea.ci.upper - rmsea) / 1.645
+    RMSEA_values <- c(rmsea, rmsea.se)
+
+  }, error = function(e) {
+    RMSEA_values <- c(NA, NA)
+  })
+
+  # Test 1b: conducting parallel test to check if one factor solution is best.
+  parallel_N_factors <- NA
+  tryCatch({
+      parallel_N_factors <- suppressWarnings(fa.parallel(data[-1], fa = "fa", plot = FALSE))$nfact
+
+    }, error = function(e) {
+      parallel_N_factors <- NA
+  })
+
+  # adding a single factor check indicator value
+  if(is.null(RMSEA_values[[1]]) | is.null(parallel_N_factors)){
+    single_factor <- NA
+  } else{
+    single_factor <- ifelse(RMSEA_values[[1]] < 0.08 | parallel_N_factors == 1, "Yes", "No")
+  }
+
+  ### Test 2: Test for Tau equivalence
+  Tau_results <- c(NA, NA, NA)
+  tryCatch({
+    # creating the base function for the fixed model (it is unidimensional)
+    model_tau_restrict <- "Factor =~ "
+
+    for (item_name in names(data)[-1]){
+      # adding all of the items from the scale to the model formula
+      # estimated with the same coefficient a to emulate a Tau equivalent model
+      model_tau_restrict <- paste0(model_tau_restrict, "a*", item_name, " + ")
+    }
+
+    # trimming the excess " + "
+    model_tau_restrict <- substring(model_tau_restrict, 1, nchar(model_tau_restrict) - 3)
+
+    # fitting the tau restricted model
+    fit.modeltaurestrict <- cfa(model_tau_restrict, 
+                                     data = data, 
+                                     std.lv = TRUE, 
+                                     estimator = "MLM")
+
+    #summary(fit.modelfree, fit.measures = TRUE)
+    #summary(fit.modeltaurestrict, fit.measures = TRUE)
+
+    # conducting the fit test between the free coefficient model and the tau
+    # restricted model
+    fit.test <- anova(fit.modelfree, fit.modeltaurestrict)
+
+    # extract the relevant results
+    Tau_results <- fit.test[2, c("Chisq diff", "Df diff", "Pr(>Chisq)")]
+    }, error = function(e) {
+      Tau_results <- c(NA, NA, NA)
+  })
+
+  ### Test 3: Assessment of uncorrelated errors
+  error_cor_results <- rep(NA, 4)
+
+  tryCatch({
+    # copying the tau restricted model as the baseline.
+    model_freed_errors <- model_tau_restrict
+    fit.modelfreed <- fit.modeltaurestrict
+
+    # create empty vector to put data into
+    spec.all.vec <- rep(NA, 5)
+
+    # looping through five instances of freeing the highest mod index error 
+    # covariance parameter estimation. We loop 5 times rather than adding the top 5
+    # highest mod index, because when one parameter is freed it will affect the extent 
+    # to which other error covariances impact the fit since (part of) their additional 
+    # explained variance may have already been captured in the parameter just freed.
+    for (i in 1:5) {
+      modindex_highest <- suppressWarnings(modindices(fit.modelfreed, sort = TRUE))[1,]
+
+      # store the fully standardized estimated coefficient change for the highest
+      # mod index freed parameter
+      spec.all.vec[i] <- modindex_highest[[7]]
+
+      # add the freeing of the parameter into the model code
+      model_freed_errors <- paste(model_freed_errors, "\n", modindex_highest[[1]], modindex_highest[[2]], modindex_highest[[3]])
+
+      # rerun the model
+      fit.modelfreed  <- cfa(model_freed_errors, 
+                             data = data, 
+                             std.lv = TRUE, 
+                             estimator = "MLM")
+    }
+
+    # perform a model comparison between the model with the top 5 error covariances
+    # freely estimated and the model with Tau equivalence.
+    fit.test2 <- anova(fit.modeltaurestrict, fit.modelfreed)
+
+    error_cor_test_results <- fit.test2[2, c("Chisq diff", "Df diff", "Pr(>Chisq)")]
+
+    # calculate the mean of the fully standardized estimated coefficient change for
+    # all the highest mod index freed parameters
+    spec.all.mean <- mean(spec.all.vec)
+
+    # store all error related results
+    error_cor_results <- unlist(c(spec.all.mean, error_cor_test_results))
+
+    }, error = function(e) {
+      error_cor_results <- NA
+  })
+
+  ### storing all of the data
+  FA_data <- c(RMSEA_values, parallel_N_factors, single_factor, 
+               Tau_results, error_cor_results)
+
+  # returning the FA data
+  return(FA_data)
+}
+
+extracted_data_list <- list(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, data_1.12.3.2_clean, data_2.12.1_clean, data_2.12.2_clean, data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.1_clean, data_3.7.2_clean, data_3.8.2_clean, data_5.1.1_clean, data_5.1.2_clean, data_5.7_clean, data_5.9.1_clean)
+
+# list to store the data in
+FA_list <- list(NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
+                NA, NA, NA, NA, NA, NA, NA, NA, NA)
+
+# running the validity/alpha assumption checks for all of the extracted datasets
+for (i in 1:length(extracted_data_list)){
+  # applying the function across each individual lab
+  FA_data <- tapply(extracted_data_list[[i]], extracted_data_list[[i]]$g,
+                    validity_and_alpha_assumption_tests)
+
+  # transforming the returned list to a dataframe
+  FA_data_frame <- do.call(rbind.data.frame, FA_data)
+
+  # Setting the column names
+  names(FA_data_frame) <- c("RMSEA", "RMSEA_se", "N_factors", "unidimensional", "Tau_chisq_diff", 
+                            "Tau_Df_diff", "Tau_p_diff", "mean_spec", "err_chisq_diff", 
+                            "err_Df_diff", "err_p_diff")
+
+  # append results to the overarching FA results list
+  FA_list[[i]] <- FA_data_frame
+}
+
+# store all dataframes with the list of the assumption test data in 
+# the analysis data folder
+fa_Caruso_2012 <- FA_list[[1]]
+saving_to_analysis_data(fa_Caruso_2012)
+fa_Husnu_2010 <- FA_list[[2]]
+saving_to_analysis_data(fa_Husnu_2010)
+fa_Nosek_2002_Math <- FA_list[[3]]
+saving_to_analysis_data(fa_Nosek_2002_Math)
+fa_Nosek_2002_Art <- FA_list[[4]]
+saving_to_analysis_data(fa_Nosek_2002_Art)
+fa_Anderson_2012_SWL <- FA_list[[5]]
+saving_to_analysis_data(fa_Anderson_2012_SWL)
+fa_Anderson_2012_PA <- FA_list[[6]]
+saving_to_analysis_data(fa_Anderson_2012_PA)
+fa_Anderson_2012_NA <- FA_list[[7]]
+saving_to_analysis_data(fa_Anderson_2012_NA)
+fa_Giessner_2007 <- FA_list[[8]]
+saving_to_analysis_data(fa_Giessner_2007)
+fa_Norenzayan_2002 <- FA_list[[9]]
+saving_to_analysis_data(fa_Norenzayan_2002)
+fa_Zhong_2006 <- FA_list[[10]]
+saving_to_analysis_data(fa_Zhong_2006)
+fa_Monin_2001_most <- FA_list[[11]]
+saving_to_analysis_data(fa_Monin_2001_most)
+fa_Monin_2001_some <- FA_list[[12]]
+saving_to_analysis_data(fa_Monin_2001_some)
+fa_Cacioppo_1983_arg <- FA_list[[13]]
+saving_to_analysis_data(fa_Cacioppo_1983_arg)
+fa_Cacioppo_1983_nfc <- FA_list[[14]]
+saving_to_analysis_data(fa_Cacioppo_1983_nfc)
+fa_De_Fruyt_2000 <- FA_list[[15]]
+saving_to_analysis_data(fa_De_Fruyt_2000)
+fa_Albarracin_2008_verb <- FA_list[[16]]
+saving_to_analysis_data(fa_Albarracin_2008_verb)
+fa_Albarracin_2008_math <- FA_list[[17]]
+saving_to_analysis_data(fa_Albarracin_2008_math)
+fa_Shnabel_2008 <- FA_list[[18]]
+saving_to_analysis_data(fa_Shnabel_2008)
+fa_Vohs_2008 <- FA_list[[19]]
+saving_to_analysis_data(fa_Vohs_2008)
+
+rm(extracted_data_list)
+
+```
+
+```{r internal_structure_information}
+Mode <- function(x) {
+  ux <- unique(x)
+  ux[which.max(tabulate(match(x, ux)))]
+}
+
+FA_aggregate_data <- data.frame(RMSEA = rep(NA, 19), 
+                                RMSEA_se = rep(NA, 19), 
+                                RMSEA_global_mean = rep(NA, 19), 
+                                RMSEA_mean_sd = rep(NA, 19), 
+                                N_factors_mode = rep(NA, 19),
+                                unidimensional_ratio = rep(NA, 19),
+                                Tau_N_P_10 = rep(NA, 19),
+                                Tau_N_P_05 = rep(NA, 19),
+                                Tau_N_P_01 = rep(NA, 19),
+                                global_mean_spec = rep(NA, 19),
+                                global_sd_spec = rep(NA, 19),
+                                err_N_P_10 = rep(NA, 19),
+                                err_N_P_05 = rep(NA, 19),
+                                err_N_P_01 = rep(NA, 19))
+
+### recreate FA_list
+FA_list <- list(fa_caruso_2012, fa_husnu_2010, fa_nosek_2002_math, fa_nosek_2002_art,
+                fa_anderson_2012_swl, fa_anderson_2012_pa, fa_anderson_2012_na,
+                fa_giessner_2007, fa_norenzayan_2002, fa_zhong_2006, fa_monin_2001_most,
+                fa_monin_2001_some, fa_cacioppo_1983_arg, fa_cacioppo_1983_nfc, 
+                fa_de_fruyt_2000, fa_albarracin_2008_verb, fa_albarracin_2008_math,
+                fa_shnabel_2008, fa_vohs_2008)
+
+for (i in 1:19){
+  data <- FA_list[[i]]
+
+  tryCatch({
+    RMSEA_estimate <- rma(yi = as.numeric(RMSEA), sei = as.numeric(RMSEA_se), data = data) # inverse variance weighting is on by default
+    FA_aggregate_data$RMSEA[i] <- RMSEA_estimate$b
+    FA_aggregate_data$RMSEA_se[i] <- RMSEA_estimate$se
+
+  }, error = function(e) {
+
+  })
+
+  FA_aggregate_data$RMSEA_global_mean[i] <- mean(as.numeric(data$RMSEA), na.rm = TRUE)
+  FA_aggregate_data$RMSEA_mean_sd[i] <- sd(as.numeric(data$RMSEA), na.rm = TRUE)
+
+  FA_aggregate_data$N_factors_mode[i] <- Mode(data$N_factors)
+
+  if("Yes" %in% data$unidimensional){
+    FA_aggregate_data$unidimensional_ratio[i] <- table(data$unidimensional)[["Yes"]] / length(data$unidimensional)
+  } else{
+    FA_aggregate_data$unidimensional_ratio[i] <- 0
+  }
+
+  # count number of Tau differences (don't know anything better for now)
+  FA_aggregate_data$Tau_N_P_10[i] <- sum(as.numeric(data$Tau_p_diff) < .1, na.rm = TRUE) / length(na.omit(data$Tau_p_diff))
+  FA_aggregate_data$Tau_N_P_05[i] <- sum(as.numeric(data$Tau_p_diff) < .05, na.rm = TRUE) / length(na.omit(data$Tau_p_diff))
+  FA_aggregate_data$Tau_N_P_01[i] <- sum(as.numeric(data$Tau_p_diff) < .01, na.rm = TRUE) / length(na.omit(data$Tau_p_diff))
+
+  FA_aggregate_data$global_mean_spec[i] <- mean(as.numeric(data$mean_spec), na.rm = TRUE)
+  FA_aggregate_data$global_sd_spec[i] <- sd(as.numeric(data$mean_spec), na.rm = TRUE)
+
+  # count number of err differences (don't know anything better for now)
+  FA_aggregate_data$err_N_P_10[i] <- sum(as.numeric(data$err_p_diff) < .1, na.rm = TRUE) / length(na.omit(data$err_p_diff))
+  FA_aggregate_data$err_N_P_05[i] <- sum(as.numeric(data$err_p_diff) < .05, na.rm = TRUE) / length(na.omit(data$err_p_diff))
+  FA_aggregate_data$err_N_P_01[i] <- sum(as.numeric(data$err_p_diff) < .01, na.rm = TRUE) / length(na.omit(data$err_p_diff))
+}
+
+### PLOTs
+# ggplot(FA_aggregate_data[-15,], aes(x = RMSEA_global_mean, y = 0)) +
+#   geom_boxplot(outlier.shape = NA, width = 2) +
+#   geom_point(alpha = 0.7) +
+#   xlab("Global Mean of RMSEA for Single Factor Model") +
+#   ylim(-10, 10) +
+#   theme_apa(base_size = 20)
+# 
+# ggplot(FA_aggregate_data[-15,], aes(x = unidimensional_ratio, y = 0)) +
+#   geom_boxplot(outlier.shape = NA, width = 2) +
+#   geom_point(alpha = 0.7) +
+#   ylim(-10, 10) +
+#   xlab("Ratio of Labs with Unidimensional Factor Solution") +
+#   theme_apa(base_size = 20)
+# 
+# ggplot(FA_aggregate_data[-15,], aes(x = N_factors_mode)) +
+#   geom_histogram(stat = "count", colour = "#28292A") +
+#   scale_y_continuous(breaks = seq(0, 12, by = 2)) +
+#   xlab("Mode of N Factors Selected by Parallel Analysis") +
+#   theme_apa(base_size = 20)
+
+# apa_table(
+#   FA_aggregate_data, align = c("l", rep("r", 13))
+#   , caption = "Internal Structure indicators of applicable measures"
+#   , note = "Because of a lack of convergence in the meta-analytic model, there are no meta-analytic RMSEA results.
+Measure fifteen had failed to deliver results for most steps during the individual factor analysis phase of the analyses.
+"
+#   , escape = FALSE, placement = "htp")
+
+print(FA_aggregate_data)
+```
+
+Besides testing for Cronbach’s assumptions, we can also use the more informative Omega coefficient. … This one shows XXX, compared to our CFA + reliability results this shows … .
+
+```{r omega_distributions_data_prep}
+# checking for each data row that they have a calculated omega coefficient,
+# and only extracting those.
+calculated_omega_plot_data <- calculated_reliability_lab_data[!is.na(calculated_reliability_lab_data$omega.tot), ]
+
+# making replication success a boolean which can affect order
+calculated_omega_plot_data$replication_success <- ifelse(
+  calculated_omega_plot_data$replication_success == "Yes", TRUE, FALSE)
+
+# calculating the average omega per group
+calculated_omega_plot_data$avg.omega <- ave(calculated_omega_plot_data$omega.tot, calculated_omega_plot_data$g)
+
+# reordering the plot from least to most reliable split by replication success
+calculated_omega_plot_data <- calculated_omega_plot_data[order(-calculated_omega_plot_data$replication_success, -calculated_omega_plot_data$avg.omega),]
+calculated_omega_plot_data$g <- fct_inorder(as.factor(calculated_omega_plot_data$g), ordered = NA)
+
+table(calculated_omega_plot_data$g)
+
+# reorder the total values to fit with the omega ordering
+table(calculated_reliability_lab_data$g)[c(15, 16, 17, 14, 11, 18, 4, 3, 10, 6,
+                                           5, 8, 19, 7, 13, 2, 1, 12, 9)]
+
+```
+
+```{r  plot_omega_distributions, warning = FALSE,  fig.cap = "Distributions of calculated McDonald’s Omega t  calculated for the responses on a measure at each lab location, across the eighteen measures for which raw data was available from which McDonald’s Omega t coefficients could be calculated.
+The N.Omg column besides the figure shows the number of lab locations for which an Omega coefficient could be successfully calculated.
+Due to lack of underlying model convergence an Omega coefficient could not be calculated for all lab locations, or any lab locations for the Der Fruyt et al.
+(2000) measure.
+The N.tot column shows the total number of lab locations at which the measure was taken.
+Any difference between N.omg and N.tot can be seen as an indication of the instability to get a stable estimate of an underlying facto model for some lab locations for that measure."}
+# plot for omega
+ggplot(calculated_omega_plot_data, aes(x = omega.tot, y = g)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_point(alpha = 0.1) +
+
+  # adding labels to show the number of labs per measure for which a total omega could be calculated
+  geom_text(data = calculated_omega_plot_data[1:18,], label = table(calculated_omega_plot_data$g)[1:18], x = 1.15, y = 1:18, size = 2.8) +
+  # adding labels to show the number of labs per measure
+  geom_text(data = calculated_omega_plot_data[1:18,], label = table(calculated_reliability_lab_data$g)[c(15, 16, 17, 14, 11, 18, 4, 3, 10, 6, 5, 8, 19, 7, 13, 2, 1, 12)], x = 1.35, y = 1:18, size = 2.8) +
+
+  # theming
   theme_minimal() +
-  scale_fill_manual(values = c("#ff766c", "#ef6f65", "#ce5f57", "#be5851", "#aa4f48", "#994741", "#803b36", "#672f2b", "#562824", "#411e1b", "#341816", "#030101","#4366ff", "#4265fc", "#3551cb", "#324dc1", "#324cbe", "#2d44aa", "#2c44a9", "#283d99", "#223380", "#162255", "#10193e", "#010206", "#000102")) + # gradient for the colors was found by changing the brightness of the colour in a hsl color editor (in GIMP) to be equal to the inverse of the QMP ratio value.
-  facet_grid(~ QMP_type) + 
-  theme(legend.position = "none", strip.text = element_text(size = 7)) +
-  ylab("Relative Prevalence of\nQMP Ratio in Sample") +
-  xlab("QMP Type") +
-  ggtitle("QMP Ratio's Per QMP Type Grouped by Original and Replication")
-
-# changing the replication and original labels back for plot 2
-levels(plot_456_data$RepOrg) <- c("Original", "Replication")
-
-# total QMP ratios
-Plot_456_2 <- ggplot(plot_456_data[plot_456_data$QMP_type == "Total",], 
-       aes(x = QMP_ratio_REV, fill = RepOrg, colour = RepOrg)) +
-  geom_density(alpha = 0.2) +
-  geom_point(y = 0, alpha = 0.2, size = 3) +
-  geom_segment(aes(x = Mean_Rat_Rep, xend = Mean_Rat_Rep, y = 0, yend = 2.66)
-               , color = "blue4") +
-  geom_segment(aes(x = Mean_Rat_Org, xend = Mean_Rat_Org, y = 0, yend = 2.183)
-               , color = "brown") +
-  coord_cartesian(xlim = c(0, 1)) +
-  theme_ridges() + 
-  theme(axis.text.y=element_blank(),
-        axis.ticks.y=element_blank(),
-        axis.text.x = element_text(size = 8)) +
-  scale_fill_manual(values=c("brown", "blue4")) +
-  scale_color_manual(values=c("brown2", "blue")) +
-  scale_x_continuous(breaks = c(0, Mean_Rat_Rep, 0.25, Mean_Rat_Org, 
-                                0.5, 0.75, 1), 
-                     labels = c("0", "0.18", "0.25", "0.31", "0.5", 
-                                "0.75", "1")) + 
-  ggtitle("Distribution of Total QMP Ratio's by Original and Replication") +
-  guides(color = "none") +
-  labs(fill = "Coded from") +
+  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), 
+                                                     "lines")) +
+
+  # adding the replication line
+  geom_hline(yintercept = 6.5, color = "red", size = 1) +
+
+  # adding the necessary indicative texts
+  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 7.25, ymax = 7.25, xmin = 0.01, xmax = 0.01) +
+  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 6, ymax = 6, xmin = 0.01, xmax = 0.01) +
+  annotation_custom(grob = textGrob(label = "N.Omg", hjust = 0, gp = gpar(fontsize = 12)), ymin = 19.2, ymax = 19.2, xmin = 1.08, xmax = 1.08) +
+  annotation_custom(grob = textGrob(label = "N.Tot", hjust = 0, gp = gpar(fontsize = 12)), ymin = 19.2, ymax = 19.2, xmin = 1.28, xmax = 1.28) +
+
+  coord_cartesian(xlim = c(0, 1), clip = "off") +
+
   ylab("") +
-  xlab("")
-
-## the following two plots are constructed solely for the purpose of extracting
-# a legend from them.
-for_legend_plot_456_org <- ggplot(plot_456_data[plot_456_data$QMP_type != "Total",], 
-                                  aes(x = RepOrg, y = abs(QMP_ratio_REV - 1), fill = abs(QMP_ratio_REV - 1))) + 
-  geom_bar(stat = "identity") +
-  theme_minimal() +
-  scale_fill_gradient(name = "Original", low = "#030101", high = "#ff766c", limits = c(0, 1), 
-                      breaks = c(0.001, 0.5, 0.999), labels = c(1, 0.5, 0)) +
-  theme(legend.title=element_text(size = 9)) + 
-  facet_grid(~ QMP_type)
-
-for_legend_plot_456_rep <- ggplot(plot_456_data[plot_456_data$QMP_type != "Total",], 
-                                  aes(x = RepOrg, y = abs(QMP_ratio_REV - 1), fill = abs(QMP_ratio_REV - 1))) + 
-  geom_bar(stat = "identity") +
-  theme_minimal() +
-  scale_fill_gradient(name = "Replication", low = "#000102", high = "#4366ff", limits = c(0, 1), 
-                      breaks = c(0.001, 0.5, 0.999), labels = c(1, 0.5, 0)) +
-  theme(legend.title=element_text(size = 9)) + 
-  facet_grid(~ QMP_type)
-
-# extracting the legends from the plot
-legend_456_org <- get_legend(for_legend_plot_456_org) 
-legend_456_rep <- get_legend(for_legend_plot_456_rep)
-
-# combining both plots and the legends into one figure
-grid.arrange(Plot_456_2, 
-             Plot_456_1, 
-             legend_456_org,
-             legend_456_rep,
-             layout_matrix = rbind(c(1, 1, 1),
-                                    c(2, 3, 4)),
-              widths = c(8, 1, 1))
-
-```
-
-We used a beta-regression model in the *betareg* R package [*v`r getNamespaceVersion("betareg")[[1]]`*\; @R-betareg_a; @R-betareg_b] to test the difference in QMP ratio between original and replication.
-Beta regression models are similar to other generalized linear regression models, but they are better suited to model dependent variables with values in the interval of (0,1), including ratios.
-Furthermore, they are robust for heteroskedastic and asymmetrically distributed dependent variables [@cribari2010beta].
-
-```{r Hypothesis4Model, include = FALSE}
-## Hypothesis 4 beta regression model
-# for H4 we have to combine the replication and original data together
-data_h4 <- rbind(data_h456_original, data_h456_replications)
-
-# running the models with revised QMP ratio's
-H4_test_results_REV <- betareg(QMP_REV_ratio ~ rep_org, data = data_h4)
-
-```
-
-Using a beta-regression model, the total QMP ratio was regressed on a dummy variable indicating whether the coded report was an original article or a replication protocol.
-The results supported Hypothesis 4 and indicated that indeed original articles contained on average more QMPs than replication protocols (`r betareg_output_to_apa_full(H4_test_results_REV)`).
-
-### Hypothesis 5: Replication Research QMPs and Replicability
-
-```{r Hypothesis5Model, include = FALSE}
-## Hypothesis 5 logistic regression model
-# first removing any hypotheses from the data that were rated as being unclear
-data_h5 <- data_h456_replications
-data_h5 <- data_h5[data_h5$hypothesis_support != "Unclear",]
-data_h5$hypothesis_support <- droplevels.factor(data_h5$hypothesis_support)
-
-# running the model using the QMPs from the revised coding protocol
-H5_test_results_REV <- apa_print(glm(hypothesis_support ~ QMP_REV_ratio, data = data_h5, family = binomial))
-
-H5_test_results_REV_with_OR <- OR_to_apa_full_supplier(H5_test_results_REV$full_result$QMP_REV_ratio, negative_b = TRUE)
-
-# and the same model using the QMPs from the initial coding protocol
-H5_test_results <- apa_print(glm(hypothesis_support ~ QMP_ratio, data = data_h5, family = binomial))
-
-H5_test_results_with_OR <- OR_to_apa_full_supplier(H5_test_results$full_result$QMP_ratio, negative_b = TRUE, not_significant = TRUE)
-
-```
-
-```{r Hypotheses5ReportedMultilevelAnalyses, include = FALSE, warning = FALSE}
-## Hypothesis 5 sensitivity test using a random intercept Gaussian model.
-# create dummy H5 dataframe for use in sensitivity test
-data_h5_sens <- data_h5
-
-# convert outcome variable to be usable with Gaussian distribution via
-# logit transform.
-data_h5_sens$QMP <- log(data_h5_sens$QMP_ratio /(1 - data_h5_sens$QMP_ratio))
-
-# running the model with initial QMP ratio's
-random_intercept_h5 <- apa_print(lmer(formula = QMP ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens))
-```
-
-We used logistic regression to test the association between the QMP ratio in replication protocols and replication success.
-In line with Hypothesis 5, results showed that successful replications were associated with fewer QMPs compared to unsuccessful replications (`r H5_test_results_REV_with_OR`).
-However, we did not find the association with the initial protocol in neither the single-level (`r H5_test_results_with_OR`) nor the multilevel model (`r random_intercept_h5$full_result$hypothesis_supportYes`)[^5].
-
-[^5]: The *betareg* package currently does not allow for estimation of multilevel models.
-As an approximation, Gaussian random-intercept multilevel models were implemented using the *lmer* function from the *lme4* package [@R-lme4].
-The outcome QMP ratio variable was transformed using the logit link function (the default link function in the *betareg* package) to fit the Gaussian model.
-
-### Hypothesis 6: Relation Between QMPs in Original and Replication Research
-
-```{r Hypothesis6Model, include = FALSE}
-## Hypothesis 6 beta regression model
-# first we combine the datasets of the original studies and the replications 
-# together
-# adding "Rep_" to separate replication from original columns in the combined dataset
-data_h456_Rep <- data_h456_replications
-colnames(data_h456_Rep) <- paste0("Rep_", colnames(data_h456_Rep))
-
-# combine the dataset
-data_h6 <- cbind(data_h456_original, data_h456_Rep)
-
-# running the model using the QMPs from the revised coding protocol
-H6_test_results_REV <- betareg(Rep_QMP_REV_ratio ~ QMP_REV_ratio, data = data_h6)
-
-# and the same model using the QMPs from the initial coding protocol
-H6_test_results <- betareg(Rep_QMP_ratio ~ QMP_ratio, data = data_h6)
-
-# Using a glm to check if results differs in direction and significance from the 
-# beta-regression, to check that including a linear regression line in figure 46
-# is representative of the relationship.
-H6_glm_test_REV <- glm(Rep_QMP_REV_ratio ~ QMP_REV_ratio, data = data_h6)
-
-H6_glm_test_results_REV <- apa_print(H6_glm_test_REV)$full_result$QMP_REV_ratio
-
-```
-
-Using a beta regression model, we found total QMP ratio in the original article to be significantly related to the total QMP ratio in the subsequent replication (`r betareg_output_to_apa_full(H6_test_results_REV)`).
-This result supports Hypothesis 6.
-Figure \@ref(fig:Plot46RevisedDataCode) displays this relationship visually.
-
-```{r Plot46RevisedDataCode, error = FALSE, warning = FALSE, fig.cap = paste0("Scatterplot of original QMP ratios and replication total QMP ratios with a linear regression line.
-The linear regression line is included, as the result based on linear regression was similarly in direction and significance to the beta regression used to test Hypothesis 6 (", H6_glm_test_results_REV, "), while being easier to understand visually.
-Each dot in the figure describes the QMP ratio in that graph across both the original article and its replication protocol.
-Note: jitter was applied to these dots to show the number of observations at points where multiple dots were present.")}
-ggplot(plot_46_data_rev[plot_46_data_rev$QMP_type == "QMP.Ratio" & plot_46_data_rev$QMP_Rep_type == "Rep.QMP.Ratio",], aes(QMP_ratio,QMP_Rep_ratio)) + 
-  geom_point() +
-  geom_jitter(width = 0.01, height = 0.01) +
-  geom_smooth(method = "glm", formula = y ~ x) + 
-  theme_minimal() +
-  theme(strip.text.y = element_text(size = 7), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
-  ylab("QMP Ratio (Replication Protocol)") +
-  xlab("QMP Ratio (Original Article)")
-
-## Code for exporting figures to high resolution PNGs.
-# png("manuscript_files/figure-self-export/plot_46_revised.png", width=1800, height=1200, res=300)
-## #PLACE FIGURE CODE HERE#
-# dev.off()
-```
-
-```{r Hypotheses6ReportedMultilevelAnalyses, include = FALSE, warning = FALSE}
-## Hypothesis 6 sensitivity test using a random intercept Gaussian model.
-# create dummy H6 dataframe for use in sensitivity test
-data_h6_sens <- data_h6
-
-# convert outcome variable to be usable with Gaussian distribution via
-# logit transform. 
-data_h6_sens$QMP_REV <- log(data_h6_sens$QMP_REV_ratio /(1 - data_h6_sens$QMP_REV_ratio))
-data_h6_sens$Rep_QMP_REV <- log(data_h6_sens$Rep_QMP_REV_ratio /(1 - data_h6_sens$Rep_QMP_REV_ratio))
-data_h6_sens$QMP<- log(data_h6_sens$QMP_ratio /(1 - data_h6_sens$QMP_ratio))
-data_h6_sens$Rep_QMP <- log(data_h6_sens$Rep_QMP_ratio /(1 - data_h6_sens$Rep_QMP_ratio))
-
-# running the model with revised QMP ratio's
-random_intercept_h6_REV <- apa_print(lmer(formula = Rep_QMP_REV ~ 1 + QMP_REV + (1|many_labs_version), data = data_h6_sens))
-
-# running the model with initial QMP ratio's
-random_intercept_h6 <- apa_print(lmer(formula = Rep_QMP ~ 1 + QMP + (1|many_labs_version), data = data_h6_sens))
-```
-
-However, this association was sensitive to changes in the QMP protocol, as we did not observe a significant relation between original and replication QMP ratios based on QMPs from the initial protocol in neither the single-level (`r betareg_output_to_apa_full(H6_test_results)`) nor the multilevel model (`r random_intercept_h6$full_result$QMP`).
-Furthermore, in the multilevel model based on the revised QMPs the association was again not significant (`r random_intercept_h6_REV$full_result$QMP`).
-We additionally conducted planned exploratory analyses of the association for each unique combination of QMP types, but taking into account the limited sample size, we could not determine any clear relations between the separate QMP types and replicability (see [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd) and [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd) for further details on the analyses and results).
-
-# Discussion
-
-In this article, we analyzed the data, protocols, and related original articles from four Many Labs replication projects to assess reliability and measurement (reporting) practices and study their relationship with replication success, as a proxy of the credibility of findings.
-Overall, even though the average reliability was relatively high, we found that not all measures were sufficiently reliable and that reliabilities can vary across labs/settings in replication projects.
-Although we did not observe reliability to significantly predict replication success, we did observe a negative relation between replication success and presence of Questionable Measurement Practices in replication research.
-Finally, we found QMPs in the original studies to be positively associated with QMPs in the replications.
-
-## Reliability
-
-### Reliability Varied Within and Between Measures
-
-While most measures showed sufficient average reliability for most purposes in psychological research (around .80), about a quarter of the measures had reliabilities generally considered insufficient (around .60 or less) [@nunnally1994assessment].
-Furthermore, the reliability in original research was generally lower than in the replication samples, contrary to our Hypothesis 1 stating that reported reliability estimates would not differ significantly between replications and original articles.
-These differences may be due to features that were specific to the Many Labs projects.
-Large teams of researchers with diverse expertise were involved in these projects and it is possible that the pooling of expertise and use of structured procedures led to more reliable measurement compared to the original research.
-
-In some cases, the reliability of measures showed signs of true variation, or heterogeneity, across samples.
-Reliability heterogeneity was particularly common for measures with a lower average reliability.
-However, the number of investigated measures was small, and some measures were only used in few independent samples.
-This is particularly relevant, since the Q-test to test heterogeneity is sensitive to the number of studies included in each test [@li2015DilemmaHeterogeneityTests].
-Furthermore, most measures did not show evidence of significant reliability heterogeneity, a similar lack of widespread heterogeneity was also observed for effect sizes in replications [@klein2018many; @olsson2020heterogeneity].
-Regardless, our results do demonstrate an often-overlooked aspect of reliability: reliability is a sample-specific, not a measurement-specific feature [@vacha1999practices; @cho2015cronbach].
-
-### No Observed Relation Between Reliability and Replicability
-
-@stanley2014expectations illustrated that measurement error, when not attenuated for, can impact replication assessments.
-However, we did not observe a relation between reliability and replicability.
-This result also runs counter to the fact that according to statistical theory, the increased noise in the data implied by lower reliability decreases the effect size estimates based on those data.
-However, the relationship between reliability and replicability is complex [@willson1980research; @lebreton2014corrections; @oswald2015Imperfect; @zhang2024Metaanalysis].
-Combined with the fact that we could only calculate reliability for a small number of measures meant we had low statistical power to detect the overall relation between reliability and replicability, which provides the most likely explanation for our non-significant findings.
-
-This problem is exacerbated further since in our sample, more than half of the effects were not replicated, indicating that many of these effects may be null effects.
-For null effects, no relation between reliability and replicability is expected, lowering our power to detect the relation further.
-Additionally, while lower reliability decreases effect sizes it can also reduce the observed true variance in the effects [@olsson-collentine2023UnreliableHeterogeneityHow].
-As a result, effect estimates from various studies will appear more similar than they truly are, seemingly replicating the original.
-Regardless, the small number of relevant measures and reported reliabilities does indicate an important issue: we observed a lack of reliability evidence in both original and replication psychological research.
-
-## Measurement Reporting
-
-### Measurement Reporting is Often Incomplete
-
-The reliability of measures was rarely reported in both original and replication research, which is in line with earlier investigations of the psychological literature [@shaw2020measurement; @flake2017construct; @flake2022construct].
-Reported reliabilities were so few, that the preregistered test for Hypothesis 1 was no longer informative.
-We found that replication research reported reliability coefficients less often than original research, which aligns with findings by @flake2022construct.
-This pattern continued for validity evidence reporting.
-Of the `r nrow(data_h456_replications)` measures, validity evidence in the form of factor analysis or similar analyses was reported for `r apa_num(sum(data_h456_original$sel_psychometric_evidence_REV != "None" & data_h456_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` measures in original articles, and `r apa_num(sum(data_h456_replications$sel_psychometric_evidence_REV != "None" & data_h456_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` measures in replication protocols, implying that less than 10% of articles report sufficient information to judge the validity of key measures used in the study.
-
-The underreporting of reliability and validity evidence has long been discussed [@willson1980research; @vacha1999practices; @green2011recent].
-Our study illustrates three potential reasons for why this problem has persisted.
-First, the studies in our sample commonly used single-item measures, an observation that was also made by @shaw2020measurement.
-Calculating reliability for single-item measures is less straightforward and common than for multiple-item measures [@wanous1996estimating].
-Single-item measures can be expected to generally be less reliable than a multiple-item measure, and validity may also be at risk.
-Single-item measures, because they are singular, come with an assumption of unidimensionality regarding the construct they reflect, which our exploratory analyses revealed is an assumption that did not frequently hold for multiple-item measures in our sample.
-However, we did not explore validity concerns unrelated to reporting in-depth, therefore future research is needed to determine the extent of problems with validity.
-
-Second, our results indicate that there may be bias in reporting reliability coefficients.
-Reliabilities were reported in original research for those measures that obtained higher calculated reliabilities in the replication samples.
-If we take the calculated reliabilities in the replication sample as a good predictor of the reliabilities in the original studies, this suggests that researchers may be reluctant to report reliability for unreliable measures.
-In turn, researchers may become overly optimistic about the reliability of measures in their field, similarly to how bias in publication causes issues for establishing estimates of true effect sizes in meta-analyses [@sutton2000empirical].
-
-Third, the replication protocols were written before data were collected, which means measurement based on these protocols had not taken place yet.
-As a result, no data were available yet from which the replicating researchers could have calculated reliability and validity.
-This would explain why there was little reliability and validity evidence reported in replication protocols.
-It may still represent a problem, however, because original articles similarly rarely reported evidence on reliability and validity.
-This implies that the replications commonly picked measures for which reliability and validity could not be checked.
-
-On the other hand, we found that more general issues in the transparency of measurement reporting practices, as assessed by QMPs, were less common in replication protocols compared to original articles.
-This is in line with Hypothesis 4 but runs counter to the findings of @flake2022construct), who found less evidence on construct validity in the replications from the RPP [@osc2015estimating] than in original articles.
-We believe this discrepancy was the result of our sample being the Many Labs projects.
-These projects made use of structured replication protocols to document the way measurement was going to be conducted.
-For example, several Many Labs replication protocols contained a section specifically listing the deviations from the original measurement.
-
-### Incomplete Measurement Reporting Hinders Replicability
-
-When the original article does not document the measurement in sufficient detail, it becomes challenging for replication researchers to mimic the measurement of an original study,.
-Consequently, the measurement in the replication may assess constructs substantially differently, weakening the relation between the test in original and replication studies [@shaw2020measurement; @flake2022construct].
-
-In line with Hypotheses 5 & 6, we found an indication of such a spillover effect in our sample.
-The total QMPs of an original study and the total QMPs in the protocol of the replication for the same study were positively associated.
-Furthermore, we found that QMPs may have negatively impacted replicability.
-An increase in total QMP ratio was associated with a decrease in replicability.
-These associations together indicate that poor measurement reporting in an original study could be a risk factor for subsequent replication attempts.
-We did observe that unidimensionality was not universal among the measures for which we could run a factor analysis, which raises doubts on the validity of the measures and substantive interpretations based on them.
-Furthermore, when replications use unvalidated measures these replications are unlikely to be informative.
-
-However, it is worth noting that the spillover effect was only observed for QMPs coded with the revised coding protocol.
-Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd for results based on the initial protocol).
-Furthermore, these hypotheses were supported by only one of the multilevel models.
-These were limited in group and sample size however, making their results uncertain.
-
-## Limitations & Future Research
-
-Our study had several limitations.
-We encountered challenges in operationalizing QMPs.
-Whereas previous research has focused on descriptives of specific QMPs detrimental to construct validity [@flake2022construct; @shaw2020measurement], we combined all coded QMPs together as an index to assess measurement practices and evaluate their impact on replicability.
-However, this also means that it remains uncertain if our operationalization accurately captured the concept.
-We encountered particular difficulty in determining when a practice is questionable, and the impact of the context on this decision.
-As a result, we already deemed it necessary to revise our coding protocol to be more lenient regarding more context dependent QMPs compared to the initial protocol.
-This revision was not trivial, as it altered the interpretation of our results.
-This finding reflects the challenges in operationalizing QMPs in a single index.
-
-Another challenge in constructing one overarching QMP variable was how to quantify it.
-We constructed ratios to cancel out the effects of non-applicable items.
-However, this has the consequence that both a measure for which all relevant measurement-related information was reported, and a measure for which no item was applicable would have a QMP ratio of zero.
-Yet, we would not consider the latter case to indicate the same level of completeness as the first.
-A little more than one-third of all responses were not applicable.
-As a result, the relation between QMP ratios and measurement reporting completeness may have been obscured to some extent.
-Additionally, it is not obvious from observing a QMP ratio whether good research practices were clearly violated.
-One might argue that any QMP is a sign of questionable research making any ratio greater than zero problematic.
-However, not all violations may have detrimental consequences or be relevant in all contexts.
-
-These challenges are potential threats to the validity of our assessment of QMPs.
-The validity of QMPS could be evaluated based on the extent to which a measured QMP score can be used to predict other variables it is expected to be associated with.
-For this future research will be needed to develop a framework of the associations between QMPs and other variables, and then test whether measured QMP scores are associated with those variables.
-To develop this framework, researchers can use this study and earlier studies by @shaw2020measurement and @flake2022construct.
-To improve upon previous measures of QMPs, the criteria on measurement reporting as set out in the @aera2014standards can be used as an additional source.
-
-A second limitation is that some of our tests were likely underpowered.
-Especially the tests on reliability, because of the small number of reported reliabilities and multiple item scales with available data.
-However, this limitation also illustrates two key findings.
-One finding is that reliability was rarely reported for measures in both original articles and replication protocols.
-The other finding is that around half of the measures in our sample were single-item measures.
-The use of single-item measures comes with psychometric risks [@diamantopoulos2012guidelines; @nunnally1978overview] and is more limited with respect to the type of reliability and validity evidence that can be determined [@sarstedt2016selecting; @shaw2020measurement].
-Because of these issues, it could even be argued that using single-item measures is a QMP in certain contexts.
-
-As a third limitation, it is important to consider whether replication protocols and research articles can be fairly compared in terms of QMPs.
-The space for describing methodology within a replication protocol is generally shorter than an article.
-Furthermore, for direct replications the methodology may be seen as largely equivalent to the original article, thus measurement descriptions in the replication protocol may be considered superfluous.
-There are three main reasons why we believe protocols and articles remain comparable.
-First, most of the measurements in our replication sample were modified in some way, it is therefore important that replication protocols still report on their measurement as it may deviate from the original.
-Second, articles are often also restricted in the amount of space they have available to devote to measurement, so space restrictions in measurement reporting are not unique to replication protocols [@gardiner2019editorial].
-Third, supplementary materials were also included as a valid information source, which increased the space available to describe the measurement, further equalizing reporting space in original articles and replication protocols.
-Still, future research may wish to analyze supplementary materials in greater detail to investigate to what extent these materials cover measurement details in both replication protocols and original articles.
-
-A fourth limitation is that we used only one definition of replication success.
-Replication success can be estimated and framed in multiple ways [for an example in replication research, see @osc2015estimating], including methods that do not make use of significance testing, or that attenuate for (measurement) error.
-The relationship between reliability and other indices of replication success may differ.
-
-Finally, we note that we used an observational design meaning that we cannot attach definitive causal directions to the relations observed in this study.
-To directly assess if there is a negative impact of reliability and QMPs on replicability, we would need experimental research.
-Future research could for example randomly assign original studies in a large-scale replication project to either needing to report all relevant measurement information as noted down in Table 1 in @flake2020measurement, while other studies receive no such reporting requirements.
-Similarly, the requirement to use validated measures based on the criteria set out in Sections 1, 2, and 3 in the @aera2014standards standards, or lack thereof could be randomly assigned to conditions.
-Although such experimental designs would be the most direct way to assess causality, it would take tremendous coordination and funding to integrate original studies into a large-scale replication project from the start.
-Alternative methods exist to assess causal relations on observational data, at least to some extent.
-@rohrer2018thinking has suggested researchers make use of Directed Acyclic Graphs to investigate causality in (non-)experimental settings by systematically accounting for confounding influences on an effect.
-
-## Recommendations
-
-Taking all the findings together, we formulated several recommendations.
-First, reliable and valid measures are a prerequisite for credible findings.
-The observation that many measures are not reported with such evidence is worrying because it obscures the credibility of findings and hampers scientific progress.
-Therefore, we join earlier recommendations [@hogan2004empirical; @barry2014validity; @flake2020measurement; @flake2022construct] that establishing evidence for the validity of scales should become a community standard for credible research.
-Furthermore, reliability coefficient estimates for multiple-item scales of a single construct should, by default, always be reported since these estimates can readily be obtained with most statistical software and provide important information on a measure’s performance.
-Only researchers who can provide reasoning to the contrary for their research should be exempt from this default.
-
-Second, researchers should report their procedure and measurement in detail, as specified in, for example, Table 1 in @flake2020measurement, or Section 3.6 in @apa2020publication on measures and measurement.
-This is important so that it can be mimicked in replications if needed.
-The remaining information that does not fit in the article can be made available on a public repository, such as the Open Science Framework [OSF\; @soderberg2018using] or Zenodo [@zenodo2024open].
-
-Furthermore, we argue that researchers seeking to replicate a study should first evaluate the measurement of that study.
-It is crucial for an informative replication that the measurement is reliable or valid, otherwise it may be futile to attempt a direct replication [see also @nuijten2022assessing].
-If the measurement is insufficiently reliable or valid, we suggest that researchers instead use their resources to replicate a study with reliable, valid, and well-documented measurement.
-When replicating another study is not an option, we advise the replicating researcher to first attempt a conceptual replication using reliable and valid measurement or use both the original and their own preferred measure [as in @stoevenbelt2018rrr].
-Afterwards, a direct replication can be performed based on the conceptual replication to further assess the effect’s credibility.
-
-# Conclusion
-
-Through our investigations into the reliability and reporting of measurement in the Many Labs replications and associated original studies, we found that reliability and validity evidence was often missing from articles.
-Furthermore, QMPs that obscured important information needed to evaluate and reconstruct the measurement were common, especially in original research.
-We observed results suggesting that QMPs in turn related to the replicability of a finding.
-Results were less clear for reliability differences between original and replication, most likely because the analysis lacked the power to detect a difference.
-However, we did observe that around a quarter of measures showed signs of significant variation in reliability across labs.
-Combined, these findings illustrate the need for widespread adoption of measurement reporting standards and that researchers should consider the validity and reporting completeness of a study’s measurement before attempting to replicate it.
+  xlab("Omega")
+
+```
 

### 2025-06-27 Scripts/prepare_data.R

@@ -6,8 +6,8 @@
 
 # set-up -----------------------------------------------------------------------
 library(worcs) # reproducible workflow template package
-library(foreign)
-library(readxl)
+library(foreign) # used for importing SPSS datasets
+library(readxl) # used for importing excel sheets
 set.seed(17042023) # seed for random number generators
 
 
@@ -90,6 +90,7 @@ Coded_Data_Vignette_raw <- read.csv("Data/LocalInputData/CodedData/Coded Data (V
 
 
 # Data Storing -----------------------------------------------------------------
+# Retrieved Data
 open_data(data = Data_ML1, 
           filename = "Data/InputData/Data_ML1.csv",
           codebook = NULL, value_labels = NULL, 
@@ -186,7 +187,7 @@ open_data(data = Data_5.9.1,
           load_expression = read.csv(file = filename, stringsAsFactors = FALSE)) 
 
 
-
+# the Coded Data
 open_data(data = Coded_Data_Initial_raw, 
           filename = "Data/InputData/Coded_Data_Initial_raw.csv",
   codebook = NULL, value_labels = NULL, 

### 2025-06-27 Scripts/source_script.R

@@ -919,6 +919,3 @@ data_prep_plot_46 <- function(Data_original, Data_replication){
   return(Plot_46_data)
 }
 
-
-
-

### 2025-08-18 Scripts/Manuscript/manuscript.Rmd
rewrote the article into complete rough draft of descriptive version

@@
 ```{r helper_functions}
-##### PUT THIS ALL IN A SEPARATE R SCRIPT FILE.
-
 # Function for storing data openly in the intermediate data folder
@@
 
-# function for changing QMP data to their ratio equivalent
-Create_QMP_descriptive_case <- function(practice_name, original_coded_var, replication_coded_var){
-  # add practice name to first row
-  Practice <- practice_name
-
-  # Sum all QMP/GMP (Good Measurement Practice), keeping NA items out of
-  # the equation
-  original_n_QMPs <- sum(original_coded_var == "FALSE", na.rm = TRUE)
-  replication_n_QMPs <- sum(replication_coded_var == "FALSE", na.rm = TRUE)
-
-  original_n_GMPs <- sum(original_coded_var == "TRUE", na.rm = TRUE)
-  replication_n_GMPs <- sum(replication_coded_var == "TRUE", na.rm = TRUE)
-
-  # calculating the N of applicable items for originals
-  N_applicable_original <- original_n_QMPs + original_n_GMPs
-
-  # checking that we are not dividing by 0, and then calculating the ratio of 
-  # QMPs for applicable items for originals
-  if(N_applicable_original != 0){
-    QMP_percentage_original <- round(original_n_QMPs / (N_applicable_original), 2)
-  } else{
-    QMP_percentage_original <- 0
-  }
-
-  # calculating the N of applicable items for replications
-  N_applicable_replication <- replication_n_QMPs + replication_n_GMPs
-
-  # checking that we are not dividing by 0, and then calculating the ratio of 
-  # QMPs for applicable items for replications
-  if(N_applicable_replication != 0){
-    QMP_percentage_replication <- round(replication_n_QMPs / (N_applicable_replication), 2)
-  } else{
-    QMP_percentage_replication <- 0
-  }
-
-  # calculating the Phi coefficient to estimate the relation between variables
-  Phi <- phi(matrix(c(original_n_QMPs, original_n_GMPs, replication_n_QMPs, 
-                      replication_n_GMPs), nrow = 2, byrow = TRUE))
-
-  return(c(Practice, QMP_percentage_original, N_applicable_original, QMP_percentage_replication, N_applicable_replication, Phi))
-}
-
 ```
@@
 
-In psychological research we are often interested in establishing a robust effect involving one or more latent constructs (e.g., IQ and conscientiousness) that describes a psychological phenomenon (like increased conscientiousness causing a person to develop higher IQ).
-However in the wake of the replication crisis the robustness of effects in psychology has been called into question.
-The Reproducibility Project: Psychology [RPP\; @osc2015estimating] and other large-scale replication projects [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many] and typically yielded smaller effects in replications compared to original studies.
-Replicability is one of the key ways to establish the robustness of an effect (Nosek RRR & …).
-If an effect does not replicate, it is likely not robust.
-Numerous factors have been proposed to explain why the original effects did not appear robust, including questionable research practices [@simmons2011false; @john2012measuring; @cumming2014new; @wicherts2016degrees], questionable reporting practices [@bakker2011mis; @nuijten2016prevalence], biased publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science], and more.
-
-These replication efforts and the subsequent lines of research have been of instrumental value in determining the lack of robustness in effects, uncovering what the causes of this lack of robustness are, and spearheading initiatives like … to help improve the robustness of effects.
-However, robustness was only one aspect of the goal highlighted at the beginning of this article, the other aspect, the fact that the effect should describe a true psychological phenomenon has received relatively less attention, although this is changing (SOME CITATIONS).
-
-In this article, we contribute to the rising research investigating the soundness of measurement in research.
-After all, a true psychological phenomenon is requires accurate measurement on the relevant constructs.
-Our aim is to create a greater understanding of the extent to which this.
-We provide a descriptive account of the measurement reporting practices in the Many Labs replications and related original research, in tandem with the measure’s reliability and internal structure analyzed from the accompanying openly available data.
-
-## Measurement Quality
-
-To understand a psychological phenomenon you need to be able to accurately capture the relevant constructs.
-While this premise underlines the core idea behind the use of measures for psychological constructs, it is difficult to guarantee in practice.
-In general, there are two aspects of a measurement between which we distinguish: validity and reliability.
-What complicates things is that there are multiple aspects to validity and multiple ways to assess these aspects of validity and reliability.
-So a researcher needs to know which type of assessment for validity and reliability is important for a measure, and on top of that it can be a complicated task to establish validity and reliability.
-
-Validity is an umbrella term for many different types of validity (construct, predictive, content, internal, external, etc.) and applies to (nearly) all aspects of the research design (CITATIONs INCLUDING VAZIRE et al.).
-For the purposes of this research we focus on construct validity of the applied measurement, which includes the measure and some aspects of the research design involving the administration of the measure.
-Construct validity refers to … .
-It is key to (relevant for nearly all measurement to some extent, because …) … .
-Evaluating it requires … and …, which in practice means … and … .
-!!!make sure that this section highlights something about construct validity relevant for our research that most psychologists may not actively realize.!!!
-
-Reliability estimates provide an indication of how consistent the responses on a measurement are.
-…something about what this consistency is over [might relate to the different types: in CTT it is the correlation between scores on two equivalent forms of the test; but we are more focused on consistency as a basic requirement for an essentially valid measure, because no reliability means no validity].
-Reliability is a critical first step to obtaining credible findings.
-Because if the scores on a measure are not consistent with themselves, it is unlikely that any effect associated with the measure can credibly be established.
-Psychometrics offers various ways to assess reliability empirically [@nunnally1978overview; @mellenbergh2011conceptual], … test-retest … interrater … internal consistency (this in turn relates back to construct validity)….
-[something about the fact that reliability is sample specific and not measurement specific in nearly all cases of us assessing it]
+The challenge with measurement in quantitative psychological research is that psychological constructs cannot be directly measured like height or weight.
+Instead, we use scores from a measurement as a proxy indicator for that psychological construct.
+However, we cannot simply assume that any measure we create will form a good indicator of the construct.
+We have to substantiate this.
+Psychometrics can be used to statistically estimate properties of the measure that are indicative of its validity.
+The effort of validating a measure represents a research effort all on its own.
+Regardless, the burden of validating a measure – besides some well-established psychiatric and personality measures – is most often placed on the researcher using a measure as part of their broader aim to study a psychological phenomena.
+When the effort involved in validating a measure is relegated to being only a component of a study that is more focused on the testing of a phenomena, we have to wonder, how well does this measurement validation process go?
+
+## Measurement Validation
+
+When we validate a measure using psychometrics, we evaluate it mainly on two aspects: construct validity & reliability.
+Construct validity refers to whether the variance in the measured item scores between participants can be attributed to variance in the unobserved constructs of interest between participants (Cronbach & Meehl, 1955; Vazire et al., 2022).
+Whereas reliability refers to how consistent a participant's responses on a measurement are [@nunnally1978overview; @mellenbergh2011conceptual].
+Reliability is part of the validation of a measure because an unreliable measure cannot consistently capture a construct through the items, and therefore cannot be assumed to properly capture the construct of interest (Crutzen & Ygram Peters, 2015).
+Suppose we have a measure and we want it to measure general intelligence, and we want to validate this as a measure of general intelligence.
+We would see our measurement as construct valid if being more intelligent resulted in generally scoring higher on our test, and our measurement would be reliable if the score of people on our measure consistently reflected their actual intelligence.
+
+In practice construct validity is often evaluated through factor analysis.
+In factor analysis, a model is fitted to explain as much of the variance of multiple items through a smaller number of factors, which are each weighted averages of the item scores.
+The number of factors are first specified, and then the fit of a model involving those number of factors is determined.
+Preferably, a model with the number of factors corresponding to the number of constructs of interest should show adequate fit.
+Additionally, the items aimed at the same construct should be statistically related to the same factor.
+For example, suppose items 1 through 5 from our general intelligence measure are meant to capture verbal intelligence, and items 6 through 10 are distinctly about mathematical intelligence.
+To establish construct validity, we want to find that a two factor model shows adequate fit, with one factor to which items 1 through 5 relate, and one to which items 6 through 10 relate.
+However, even in this scenario we cannot be certain that the second factor relates to mathematical intelligence and not for example abstract thinking, other types of validity checks as well as theoretical underpinnings will be necessary.
+Additionally, the factor relations may not be stable for this measure in other contexts and implementations, a concept known as measurement invariance (Horn et al., 1983; Cheung & Rebecca, 2012).
+
+Reliability gives us an indication of how much our measure captures the signal of our measured variables over noise.
+Psychometrics offers various ways to assess reliability empirically [@nunnally1978overview; @mellenbergh2011conceptual].
+For example, we can compare scores on multiple equivalent forms of the test, between multiple different raters, or between multiple different timepoints of the same test.
+Still, the most common way to assess reliability is through an indication of consistency within the measure itself, and the most common among these indicators is the Cronbach's Alpha coefficient.
+The Cronbach's Alpha coefficient is defined as “the average of all the possible split-half coefficients for a given test” (Cronbach, 1951).
+Here split-half coefficients being the correlation between two halves of the same test.
+It can be calculated by taking the ratio of interitem covariance to total variance and multiplying it by n / (n - 1), where n is the number of items in the scale.
+However, Cronbach's Alpha comes with strong assumptions on the underlying factor structure, including that the measure is unidimensional, so a single factor.
+Furthermore, because Cronbach's alpha is proportional to the total variance in the target variable in the sample, it is an indicator of reliability of a measurement, and not the measure itself.
+In spite of this many researchers report and interpret Cronbach's Alpha as such (Cortina, 1993; Schmitt, 1996).
+
+Thus, psychometric tests are useful but they are not always easy to perform in practice.
+Even simple factor analysis requires sample sizes of at least around 100, unless the amount of variance explained by the factors is large and the factor structure is clear (Gorsuch, 1983; MacCallum et al., 1999).
+However, even in the latter case factor analysis does not converge with low sample sizes.
+Furthermore, if we want to know not just the reliability and validity of one measurement but for the measure across multiple contexts, we need to conduct multiple studies with approximately 400 people per group to detect meaningful effects (Meade & Bauer, 2007; French & Finch, 2016; Koziol & Bovaird, 2018).
+However, what we observe in the literature is that most measures are reused once or never (THE NOT HUSSEY PAPER ABOUT TOOTHBRUSH MEASURES; also the other Hussey paper with the blocks).
+Finally, \@shaw2020measurement checked the factor structure and reliability of measures used in the Many Labs 2 replication project [@klein2018many] on the available data, the results.
+They observed that for none of the scales they assessed, a factor structure congruent with the use of the scales met all of their evaluation criteria, and reliability was rarely consistently above an acceptable threshold.
 
@@
 
-To summarize the previous section, the measurement of a study need to be both valid and reliable to be able to assess the phenomenon of interest.
-However, recent research has shown that the reliability and validity can often not be discerned from the reported information.
-Questionable Measurement Practices (QMPs) raise doubts about a measurement’s validity [@flake2020measurement] and have been coined as a term analogous to Questionable Research Practices [QRPs\; @john2012measuring].
-QMPs range from lack of transparency and unclear motivation in choice of measure to poor justification for modifications of a measure and procedure of an existing measure [@flake2020measurement].
-
-@flake2022construct documented QMPs among 100 replications and their respective original articles from the RPP [@osc2015estimating].
+As illustrated in the previous section, validating measurement is a complex but essential part of doing psychological research.
+Yet the scientific community has not fully stepped up to this challenge (FLAKE & FRIED 2020).
+A large number of measures used in the psychological literature lack information on the validity and reliability of the measure (Hogan & Agnello, 2004; Flake et al., 2017; Flake et al., 2022).
+
+Questionable Measurement Practices (QMPs) are practices that raise doubts about a measurement’s validity [@flake2020measurement] and have been coined as a term analogous to Questionable Research Practices [QRPs; @simmons2011false; @john2012measuring; @wicherts2016degrees].
+QMPs range from lack of transparency in the reporting of the measure and unclear motivation in choice of measure to poor justification for modifications of a measure and procedure of an existing measure [@flake2020measurement].
+@flake2022construct documented QMPs among 100 replications and their respective original articles from the Reproduciiblity Project Psychology [@osc2015estimating].
 They coded the number of measures, the number of items in the measure, and the information that was reported describing the measure and justifying its use.
 They observed limited reporting of evidence demonstrating the reliability and validity of the measurement.
-Furthermore, auxiliary information on the number of items, the response format, the scoring of the scale, was also not reported for several measures in the RPP.
-Furthermore, only eight of the 40 translated scales contained validity evidence for the translated version of the scale.
-Evidence showing that this and other modifications between original and replication did not invalidate the measurement was rare.
-
-!!!Especially worrisome because @shaw2020measurement shows that when running factor analyses on the available data the structural evidence does not always show a good construct validity, so that the lack of reported validity evidence may be hiding psychometrical skeletons in the closet; Reliability something … [Hussey’s work].
-!!!
+Additionally, only eight of the 40 translated scales contained validity evidence for the translated version.
+But reporting of reliability and validity evidence is not only low, but may also be biased as well.
+!!!HUSSEY et al., 2023/2025!!!
+observed a disproportional amount of Cronbach's Alpha values at the common acceptably reliable threshold value of .70, and low reporting just below .70.
+Thus the lack of reported measurement evidence may on occasion be hiding psychometric skeletons in the closet.
 
 Further findings by @flake2022construct and others [@flake2017construct; @shaw2020measurement] also show that QMPs not only limit the reported validity of a measurement in a study, the lack of information also creates challenges for replicating researchers.
-If it is not clear what items were used, how they were scored, and how they were administered, the reconstructed measure used in the replication may be assessing the relevant construct(s) differently, or even assess different construct(s).
-If different construct(s) are assessed, the replication may not be a test of the same phenomenon as the original.
+Basic content descriptions such as the number of items, the response format, the scoring of the scale were irregular (exact numbers).
+If it is not clear what items were used, how they were scored, and how they were administered, then it is challenging to reconstruct the measurement for a replication study.
+In turn, the replication may assess the constructs in a substantially similar way, or they even assess different constructs.
+If different constructs are assessed, the replication cannot be seen as a test of the same phenomenon as the original.
 If constructs are assessed differently, the estimated effects in the replication cannot easily be substantially compared to the effects in the original study.
-In either case, the replication is hardly informative with regards to the phenomenon of interest.
-Given replication’s importance in cumulative knowledge gain in science, this is worrisome.
+In either case, substantial comparisons between original and replication are hindered.
 
@@
 
-Our aim is to further investigate the reliability, validity, and measurement reporting practices in the Many Labs replications and related original research.
-We provide a descriptive account of the measurement reporting practices in tandem with the measure’s reliability and validity evidence, obtained from the openly available data from the Many Labs replication projects.
-
-Existing literature has looked at reported reliability, validity, and general measurement features in both original and replication studies before.
-Previous studies have also recalculated reliabilities from reported information and reanalyzed the validity from original data.
-Our research provides a unique contribution by combining the reported measurement information in original and replication studies, with reliability and validity re-analyses performed on openly available data from those replication studies, with the added benefit of having data across multiple labs so that variation in reliability and validity across multiple instances can be investigated.
+Our aim is to provide a descriptive account of the reliability, validity, and reporting practices of measurement in replications and related original research.
+We coded several aspects of the measurement reporting practices in replications and original articles.
+Additionally, we estimated the reliability and validity evidence using openly available replication data of the measurement item responses from across multiple labs.
+Our unique contribution is by evaluating reported and the recalculated measurement information for each measure together.
+This allows us to capture a "double whammy" scenario where there is uncertainty in the reliability and validity of these measures when we calculate these ourselves, and where QMPs obscure the ability to evaluate the measure as well as inhibiting future researchers to recreate the measurement to validate it in a new study.
+Besides this, our study also functions as a conceptual replication of earlier research looking at reporting practices and measurement validation using different questions and analyses on a different set of replications and original research.
+While the theory underlying the measurement is important to evaluate how the content of the measure fits to the constructs of interest, because evaluating the theory of a measurement requires domain specific knowledge for each measure we do not address it in this study, we refer interested readers to articles discussing theory in measurement elsewhere (Gehlbach & Brinkworth, 2011; Humphry, 2017; Borgstede and Eggert, 2023; Hasselman, 2023).
 
@@
 ## Data Source
-The data source is the Many Labs replication projects.
-These were a series of high profile replication projects wherein multiple psychological studies considered relevant by the community were chosen to be replicated across multiple labs over the world.
-Practices encountered with measurement in this sample of original articles and replications are a representative reflection of these practices more broadly.
-
-Furthermore, because each study was replicated across multiple labs and the data collected from each lab is publicly available, we can calculate reliability coefficients and perform factor analyses for each measurement across multiple data points and investigate the variance in these estimates.
-
-## Unit of Analysis
-Our unit of analysis is a measure of a single psychological construct within a replication protocol/article.
-Multiple psychological constructs could be measured per original study or replication.
-We used the replication protocols to identify these measures.
-We did not include acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses.
-
-## Data Collection
+
 The data consists of three main sources: replication datasets, replication protocols, and original study articles.
@@
 Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures.
-We checked the Many Labs data source prior to registering our coding protocol, to check the feasibility of which data could be extracted and how.
-However, the actual coding took place after registering the coding protocol … Further details can be found in supplement XXX.
+
+## Unit of Analysis
+
+Our unit of analysis is a measure of a single variable within a replication protocol or original article that was used in the main analysis that was replicated.
+We allowed for multiple variables to be measured per study.
+We used the replication protocols to identify the measure of each variable.
+We did not include acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses.
+
+## Data Collection
+
+The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>.
+Both the replication protocols and replication datasets were scanned through to ensure that the planned analyses were feasible.
+However, no coding or analysis of either of them had taken place before the analyses were preregistered.
+Further details on the search strategy can be found in the coding protocol information file in the supplementary materials.
 
 ### Replication Datasets
-The replication datasets refer to the publicly available datasets containing the data obtained from all labs partaking in a Many Labs study.
-For the analyses, we extracted the scores on the items of each previously identified measure that met our inclusion criteria specified below.
+
+The replication datasets refer to the publicly available datasets containing the data obtained from all labs of a Many Labs replication.
+For the analyses, we extracted the scores on the items of each previously identified measure that also met our inclusion criteria specified in the paragraph below.
 When scores could not be clearly identified, any available codebooks, analysis scripts, or study materials were used to identify the relevant scores.
 
-To be included in our reliability recalculations and factor analysis checks, the measure had to be a scale consisting of multiple items.
+To be included in our reliability recalculations and factor analyses, the measure had to be a scale of multiple items.
 If cleaned data were available, we chose these over raw data, to ensure that variables were coded as intended (e.g., no reverse-coded items).
 We omitted pilot data from the analyses.
-These criteria and the nature of the available format(s) of each dataset resulted in suitable item score data from 19 replication sets spread across on average approximately 35 lab locations for our analyses.
+These criteria combined with difficulties in retrieving suitable data from some datasets resulted in a set of item score data from `r length(unique(calculated_reliability_lab_data\$g))` replication sets spread across on average approximately `r round(mean(table(calculated_reliability_lab_data\$g)), 0)` lab locations for our analyses.
 
@@
 ### Replication Protocols
-The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each set of replications of a given original study across multiple labs.
-These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the data retrieval information supplementary document; URL https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd).
+
+The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of the replication of an original study.
+These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the data retrieval information XXX supplementary document; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd>).
 
 ### Original Articles
+
 We identified and retrieved all original study articles using the citations for these articles in each replication protocol.
@@
 ##### can also be reproduced without running this code block.
+
 # Selecting the relevant rows and columns for the data
@@
 coded_data_full$mod_time[1] <- "Before"
+coded_data_full$psychometric_evidence_text_REV[coded_data_full$sel_psychometric_evidence_text_REV == "convergent validitiy"] <- "convergent validity"
 
@@
 ## Measures
+
 ### Coding Protocol
-We developed a coding protocol to extract reported measurement information from the original articles and replication protocols.
+
+We extracted reported measurement information from the original articles and replication protocols using our preregistered coding protocol.
 We extracted the reported reliability coefficient and type of index (Cronbach’s Alpha, retest, interrater, etc.) when present.
-Similarly, we coded if any construct validity evidence, such as a factor analysis, was presented alongside the measure.
-We additionally included twenty items that were based on the QMP table presented in Flake & Fried.
-These items recorded whether or not certain information was reported and were all coded to be either true, false, or not applicable if not relevant for that measure (e.g., reporting results from a factor analysis for single-item measures).
-Example items can been in Table 1.
+Similarly, we coded if any psychometric construct validity evidence, such as a factor analysis, was presented for the measure.
+We additionally included twenty items that were based on the QMP table presented in Flake & Fried (2020).
+For each of these items we a piece information we would want to see reported with regards to the measurement was described.
+If the information was clearly reported we coded the item as true; false if not or not clear enough; or not applicable if not relevant for that measure (e.g., reporting results from a factor analysis for single-item measures).
+Example items can be seen in Table 1.
 
@@
 
-After the initial coding, we made minor revisions to 14 of the 20 QMP items in the preregistered coding protocol, because we considered them overly stringent in practice.
+After the initial coding, we made minor revisions to 14 of the 20 QMP items from the preregistered coding protocol.
+These items were changed after familiarizing ourselves with the way measurement was reported, and it became clear that our criteria were too stringent in the exact way and degree of detail in which to present things.
 For example, in the initial protocol, an example item had to be present within the article or protocol itself, or else this was counted as a QMP.
 In the revised protocol, references to online appendices with example items were also considered sufficient for this item.
-The analyses, tables, and figures presented in this article are all based on the revised coding protocol, the results of the equivalent analyses based on QMPs obtained with our initial protocol can be found in Supplementary Analyses D.
-
-We initially intended to form a QMP index using these QMP items and explore relations in the data using this index, but this index could not be validated properly (more information on the index can be found in the Supplement).
-These items are therefore currently used on their own to give a descriptive overview of the reporting practices in our sample.
+The analyses, tables, and figures presented in this article are all based on the revised coding protocol.
+The results of the equivalent analyses based on QMPs obtained with our initial protocol can be found in Supplementary Analyses D.
+
+We initially intended to form a QMP index using these QMP items and perform regression analyses using this index, but this index could not be validated properly and its results would be misleading to present here.
+A more detailed explanation of what was omitted and why, as well as the results from the preregistered analyses themselves can be found in Supplementary Materials XXX.
+The items are currently used as individual descriptives on the reporting practices in our sample.
 
 ```{r Calculating_QMP_Data, include = FALSE, eval = FALSE}
+# function for changing QMP data to their ratio equivalent
+Create_QMP_descriptive_case <- function(practice_name, original_coded_var, replication_coded_var){
+  # add practice name to first row
+  Practice <- practice_name
+
+  # Sum all QMP/GMP (Good Measurement Practice), keeping NA items out of
+  # the equation
+  original_n_QMPs <- sum(original_coded_var == "FALSE", na.rm = TRUE)
+  replication_n_QMPs <- sum(replication_coded_var == "FALSE", na.rm = TRUE)
+
+  original_n_GMPs <- sum(original_coded_var == "TRUE", na.rm = TRUE)
+  replication_n_GMPs <- sum(replication_coded_var == "TRUE", na.rm = TRUE)
+
+  # calculating the N of applicable items for originals
+  N_applicable_original <- original_n_QMPs + original_n_GMPs
+
+  # checking that we are not dividing by 0, and then calculating the ratio of 
+  # QMPs for applicable items for originals
+  if(N_applicable_original != 0){
+    QMP_percentage_original <- round(original_n_QMPs / (N_applicable_original), 2)
+  } else{
+    QMP_percentage_original <- 0
+  }
+
+  # calculating the N of applicable items for replications
+  N_applicable_replication <- replication_n_QMPs + replication_n_GMPs
+
+  # checking that we are not dividing by 0, and then calculating the ratio of 
+  # QMPs for applicable items for replications
+  if(N_applicable_replication != 0){
+    QMP_percentage_replication <- round(replication_n_QMPs / N_applicable_replication, 2)
+  } else{
+    QMP_percentage_replication <- 0
+  }
+
+  # calculating the Phi coefficient to estimate the relation between variables
+  Phi <- phi(matrix(c(original_n_QMPs, original_n_GMPs, replication_n_QMPs, 
+                      replication_n_GMPs), nrow = 2, byrow = TRUE))
+
+  return(c(Practice, QMP_percentage_original, N_applicable_original, QMP_percentage_replication, N_applicable_replication, Phi))
+}
+
+# loading the relevant items
 original_QMP_data <- coded_data_original[c("def_1", "sel_2", "op_4", "reliability_type", "sel_existing", "op_version", "op_1_REV", "sel_1_REV", "sel_3_REV", "sel_4", "sel_psychometric_evidence", "op_2_REV", "op_3", "quant_1_REV", "quant_2_REV", "quant_3_REV", "quant_4", "op_5_REV", "mod_1_REV", "mod_2_REV", "mod_3_REV", "mod_4_REV", "mod_5_REV", "mod_6_REV")]
@@
 
-QMP_data$reliability_reported_rep <- ifelse(replication_QMP_data$reliability_type != "Not Reported" & replication_QMP_data$reliability_type != "" & !is.na(replication_QMP_data$reliability_type), FALSE, ifelse(replication_QMP_data$reliability_type == "Not Reported", TRUE, NA))
+QMP_data$reliability_reported_rep <- ifelse(replication_QMP_data$reliability_type != "Not Reported" & replication_QMP_data$reliability_type != "" & !is.na(replication_QMP_data$reliability_type), TRUE, ifelse(replication_QMP_data$reliability_type == "Not Reported", FALSE, NA))
 
@@
 
-QMP_data$source_org <- original_QMP_data$sel_1_REV
-QMP_data$source_rep <- replication_QMP_data$sel_1_REV
-
-QMP_data$select_or_create_clarity_org <- original_QMP_data$sel_existing == "Not Clearly Stated"
-QMP_data$select_or_create_clarity_rep <- replication_QMP_data$sel_existing == "Not Clearly Stated"
-
-QMP_data$version_clarity_org <- original_QMP_data$op_1_REV == FALSE | original_QMP_data$op_version == "" & original_QMP_data$sel_existing == "True, namely"
-QMP_data$version_clarity_rep <- replication_QMP_data$op_1_REV == FALSE | replication_QMP_data$op_version == "" & replication_QMP_data$sel_existing == "True, namely"
-
 ### QMP ratio data
@@
 
-Recalculating Data
-We furthermore, used the replication datasets to calculate reliability for each measure with appropriate data for each lab the measure was used in.
+### Recalculating Data
+
+We calculated reliability for each measure from the replication datasets with suitable data for each lab the measure was used in.
 We calculated both Cronbach’s alpha, as well as its standard error using formulas 2 & 3 from Duhachek and Lacobucci (2004) to calculate the standard error in the meta-analysis.
-Then combining these two values we conducted a meta-analysis of the reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analysis (Botella & Suero, 2012; López-Ibáñez et al., 2024; Vacha-Haase, 1998).
-This enabled us to quantify the degree of true variation (or heterogeneity) in reliability coefficients across lab locations.
-We performed the RG meta-analysis using the rma function from the metafor R package (v4.4-0 ; Viechtbauer, 2010) and default settings.
+Then we entered these two values into a meta-analysis of the reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analysis (Botella & Suero, 2012; López-Ibáñez et al., 2024; Vacha-Haase, 1998).
+Using RG Meta-Analysis we quantified the degree of true variation (or heterogeneity) in reliability coefficients across lab locations.
+We performed the RG Meta-Analysis using the rma function from the metafor R package (v4.4-0; Viechtbauer, 2010) and default settings.
+We evaluated the heterogeneity using the tau statistic and the Cochran's Q-test (CITATION Cochran 1954).
+These indicators have received criticism as indicators of heterogeneity, especially when within study sample sizes are small and power to detect heterogeneity is low (Hoaglin 2015; Pereira et al.
+2010).
+Therefore, we also present the prediction interval and suggest that the heterogeneity results should be viewed with a critical eye (Borenstein 2024 CITATION).
 We implemented no correction for bias, because the Many Labs replications were not at risk of publication bias.
 
-Our analyses will focus on Cronbach’s Alpha, because Cronbach’s Alpha is used more commonly in research allowing us to make comparisons between calculated and reported reliabilities.
-Furthermore, we were able to calculate the standard error of alpha to be used in the Reliability Generalization meta-analysis.
-However, we additionally estimated McDonald’s Omega, since it has been argued to be a more informative measure of reliability than alpha, while also simultaneously providing some validity evidence [@crutzen2017scale; @deng2017testing].
-Omega was calculated using the omega function in the *psych* R package [*v`r getNamespaceVersion("psych")[[1]]`*; @R-psych].
+Our analyses will focus on Cronbach’s Alpha, because its common use in research allows us to make comparisons between calculated and reported reliabilities.
+Furthermore, we were able to calculate the standard error of alpha to be used in the RG meta-analysis.
+We additionally estimated McDonald’s Omega for each lab from the same set of replications as for Cronbach's Alpha, since it has been argued to be a more informative measure of reliability than Cronbach's Alpha, while also simultaneously providing some validity evidence [@crutzen2017scale; @deng2017testing].
+McDonald’s Omega was calculated using the omega function in the *psych* R package [*v`r getNamespaceVersion("psych")[[1]]`*; @R-psych].
 Default arguments were used in the function except the nfactors argument, which was set to 1.
-
-Finally, We probed the three assumptions of Cronbach’s alpha for our included nineteen measures.
-First, we tested for unidimensionality using the fit indices of a one-dimensional Confirmatory Factor Analysis (CFA), and the outcome from a parallel test.
-!!!
-explain parallel test !!!
-.
-Second, we compared the unidimensional model to a unidimensional model that was restricted to be Tau equivalent (equal loading of all items on the common factor), and used model comparison to test whether the restricted model fitted significantly worse or not.
-Third, for the unidimensional model, we tested the assumption of uncorrelated errors by freely estimated the five highest correlations between individual item pairs and then used a model comparison to test whether the model with freely estimated errors fitted significantly better or not.
-Besides testing the assumptions for Cronbach’s alpha, the results regarding unidimensionality combined with McDonald’s Omega also gives us some indication of the construct validity, since these measures were checked to all have been used to create a singular index.
-If a unidimensional model would thus lack fit according to our tests, it would put into question the use of these measures to estimate a singular variable of interest.
+No RG Meta-Analysis was performed on McDonald's Omega, as we could not find a formula for calculating its standard error.
 
@@
 
-# Results
-## Reliability & Validity reporting
-Figure 1 depicts the flow of measures in relation to reliability reporting.
-First, it shows that almost half of the measures in both replication (N = 37) and original research (N = 35) were single-item measures.
-Only thirteen measures in original and four in replications were reported with a reliability indicator.
-Cronbach’s Alpha was the most commonly reported reliability indicator.
-
-```{r ReliabilityReportingFlowDiagram, fig.cap = "Reliability reporting flow diagram.
-Figure shows the number of measures as reported in both the replication protocols and original article, which meet the criterion in the box within the diagram and those criteria before it.", out.height = "60%"}
-knitr::include_graphics(path = "../../SupplementaryMaterials/reliability_reporting_flow_diagram.png")
-```
-
-Validity evidence was even less common than reliability evidence.
-Only, `r sum(coded_data_original$sel_psychometric_evidence_REV != "None" & coded_data_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_original$sel_3_REV == TRUE, na.rm = TRUE)` original studies and `r sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_replications$sel_3_REV == TRUE, na.rm = TRUE)` replications reported psychometric evidence on the .
-Most commonly exploratory factor analyses or convergent validity information were presented.
-Only `r sum(coded_data_original$sel_4 == TRUE, na.rm = TRUE)` original studies & `r sum(coded_data_replications$sel_4 == TRUE, na.rm = TRUE)` replications reported psychometric validity evidence from previous studies.
-
-```{r code on the reporting of validity evidence}
-table(coded_data_original$sel_psychometric_evidence_REV)
-table(coded_data_replications$sel_psychometric_evidence_REV)
-
-sum(coded_data_original$sel_psychometric_evidence_REV != "None" & coded_data_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_original$sel_3_REV == TRUE, na.rm = TRUE)
-sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_replications$sel_3_REV == TRUE, na.rm = TRUE)
-
-table(coded_data_original$sel_psychometric_evidence_text_REV)
-table(coded_data_replications$sel_psychometric_evidence_text_REV)
-
-# internal
-table(coded_data_original$sel_3_REV)
-table(coded_data_replications$sel_3_REV)
-# external
-table(coded_data_original$sel_4)
-table(coded_data_replications$sel_4)
-
-sum(coded_data_original$sel_4 == TRUE, na.rm = TRUE)
-sum(coded_data_replications$sel_4 == TRUE, na.rm = TRUE)
-
-sum(coded_data_original$sel_existing == "True, namely:")
-sum(coded_data_replications$sel_existing == "True, namely:")
-
-sum(coded_data_original$op_1_REV[coded_data_original$sel_existing == "True, namely:"] == TRUE, na.rm = TRUE)
-sum(coded_data_replications$op_1_REV[coded_data_replications$sel_existing == "True, namely:"] == TRUE , na.rm = TRUE)
-
-```
-
-It was clear that existing measures were used in `r sum(coded_data_original$sel_existing == "True, namely:")` original and `r sum(coded_data_replications$sel_existing == "True, namely:")` replication cases, with specific version reported in `r sum(coded_data_original$op_1_REV[coded_data_original$sel_existing == "True, namely:"] == TRUE, na.rm = TRUE)` original and `r sum(coded_data_replications$op_1_REV[coded_data_replications$sel_existing == "True, namely:"] == TRUE , na.rm = TRUE)` replication cases.
-
-???check if reporting of reliability/validity (ALL QMPS) more commonm for existing and sourced measures than new ones (relates to the idea of reporting bias I explore in the piece)???
-
-## Questionable Measurement Practices
-
-Besides Reliability and validity evidence it is also relevant to know what was measured to evaluate if it was measured well.
-What we found however was that for XXX original and XXX replication a clear variable assessed by the measurement was defined.
-The logic behind how that variable was operationalized was reported for XXX original and XXX replication.
-Finally, a reason was given for selecting an existing measure or creating a new measure in XXX original and XXX replication.
-
-Several items also indicated how the measurement was implemented: XXX the administration format was indicated, XXX the assessment environment described, XXX the steps to administer the measure were described.
-To recreate/understand the items of the measure we looked at if they reported: XXX the number of items were described, XXX the number of response options were described, XXX any example items were shown.
-Finally, to use the item scores for analyses you need to know the following: XXX any recoding was explained, XXX the calculation of an index (if used) was described.
-
-The concept of consistency in assessing a phenomenon across original and replication is important but also complex and difficult to access because … .
-However, we do we have some information on when modifications were made to certain aspects of the measure between original and replication.
-For XXX replications any administration format change was indicated, and for XXX of those that choice was justified/validated.
-For XXX replications any assessment environment change was indicated, and for XXX of those that choice was justified/validated.
-For XXX replications any change in the number of items or the number of response options was indicated, and for XXX of those that choice was justified/validated … some practical examples of numbers of items being changed ???to showcase that happening and prep that for discussion as being a reasonable reason to say that the same phenomenon may not even be assessed at that point???.
-
-Table 2 below shows for both original and replication for all of the QMP items the ratio of QMPs and for how many of the 77 measures the QMP was applicable.
-Meanwhile, the Phi coefficient indicates the “correlation” between the MP being questionable or good in the original and the same for the replication.
-The average Phi was … .
-
-```{r qmp_table}
-# create informative Measurement Practice Labels
-MPractice <- c("Reliability is reported", "It is clear if the measure existed or is newly created", 
-  "Specifc version of the measure is specified", "Validity evidence from a factor analysis is presented",
-  "The measured variable is defined", "The choice of measure selection or creation is justified", 
-  "The implemented operationalisation is justified", "The source of the measure is provided", 
-  "Psychometric evidence from the study is given", "Psychometric evidence from an earlier study is given", 
-  "The administration format and environment are described", "The administration procedure is described",
-  "The number of items are described", "The number of response options are described", 
-  "The recoding of responses is described", "The creation of the index is described", 
-  "Example items are presented in text or supplement", "Any administration format changes are mentioned", 
-  "Administration format changes are justified/validated", "Any translations are mentioned", 
-  "Translated measures are justified/validated", "Any changes in number of items or response options are mentioned", 
-  "Changes in number of items or response options are justified/validated")
-
-# construct the QMP table to be printed
-QMP_table <- data.frame("Practice" = MPractice,
-                        "QMP original" = paste0(qmp_ratio_data$QMP_percentage_original, 
-                                                " (", qmp_ratio_data$N_applicable_original, ")"),
-                        "QMP Replication" = paste0(qmp_ratio_data$QMP_percentage_replication, 
-                                                " (", qmp_ratio_data$N_applicable_replication, ")"),
-                        "Phi" = qmp_ratio_data$Phi)
-
-# Changing column names to be less computer speak-y looking
-colnames(QMP_table) <- c("Practice", "QMP org", "QMP rep", "Phi")
-
-# print the table in apa formatting
-apa_table(
-  QMP_table, align = c("l", "r", "r", "r")
-  , caption = "Ratio of QMPs and number of applicable measures, for original and replication"
-  , note = "The first number in QMP org and QMP rep is the ratio of measures for which the practice in that row was not conducted well by our standards.
-The number between brackets indicates the number of measures for which the practice was applicable."
-  , escape = FALSE, placement = "htp")
-
-```
-
-## Measurement Reliability
-The average calculated Cronbach’s alpha coefficient across replication sets was 0.787 with a standard deviation 0.167.
-Figure 2 displays the distributions of the calculated Cronbach’s Alpha scores from each lab for each measure, separated by successful and unsuccessful replication, based on the meta-analytic p-value (alpha , .05) retrieved from the Many Labs reports.
-
-```{r alpha_distributions_data_prep}
-### PREPARE CODE FOR THE ALPHA DISTRIBUTIONS FIGURE 
-calculated_alpha_plot_data <- calculated_reliability_lab_data
-
-# calculating the average alpha per group
-calculated_alpha_plot_data$avg.alpha <- ave(calculated_reliability_lab_data$alpha, 
-                                            calculated_reliability_lab_data$g)
-
-# making replication success a Boolean which can affect order
-calculated_alpha_plot_data$replication_success <- ifelse(
-  calculated_alpha_plot_data$replication_success == "Yes", TRUE, FALSE)
-
-# reordering the plot from least to most reliable split by replication success
-calculated_alpha_plot_data <- calculated_alpha_plot_data[order(-calculated_alpha_plot_data$replication_success, -calculated_alpha_plot_data$avg.alpha),]
-
-# Making sure there are no calculated alpha's that fell below 0 in the plot.
-calculated_alpha_plot_data <- calculated_alpha_plot_data[calculated_alpha_plot_data$alpha > 0,]
-
-# reordering 
-calculated_alpha_plot_data$g <- fct_inorder(as.factor(calculated_alpha_plot_data$g), ordered = NA)
-
-# adding an index to which row in the plot data the row in measure_reliability_data belongs to
-measure_reliability_data$graph_index <- NA
-
-for (i in 1:nrow(measure_reliability_data)){
-  measure_reliability_data$graph_index[which(unique(calculated_alpha_plot_data$g)[i] == measure_reliability_data$g)] <- i
-}
-
-```
-
-```{r plot_alpha_distributions, warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the nineteen measures for which raw data was available from which Cronbach’s alpha coefficients could be calculated.
-The green lines indicate the meta-analytic prediction interval lower and upper bound.
-The blue triangles indicate the reported alpha coefficient for that measure from the original article, when reported.
-The Tau column besides the figure shows the tau heterogeneity estimate based on a meta-analysis of the calculated reliabilities for each measure.
-Meta-analyses for which the Q-test for heterogeneity was significant at alpha < .05 are in black, while non-significant results are in grey.
-The Diff column shows the difference between reported reliability and the average reliability calculated from the Many Labs data for the applicable measures, the reported reliabilities that fell outside the 95% quantile of calculated reliability scores are shown in black, otherwise in grey."}
-measure_reliability_data[!is.na(measure_reliability_data$coefficient_difference),]$graph_index
-
-# plot for distribution of alpha
-ggplot(calculated_alpha_plot_data, aes(x = alpha, y = g)) +
-  geom_boxplot(outlier.shape = NA) +
-  geom_hline(yintercept = 6.5, color = "red", size = 1) +
-  geom_point(alpha = 0.1) +
-
-  # adding in the tau values
-  geom_text(data = measure_reliability_data, label = format(measure_reliability_data$tau, digits = 1), x = 1.15, y = measure_reliability_data$graph_index, color = ifelse(measure_reliability_data$QEp < .05, "black", "grey"), size = 2.8) +
-
-  # adding in the difference in alpha coefficients
-  geom_text(data = measure_reliability_data[c(1:8, 18),], label = format(measure_reliability_data$coefficient_difference[c(1:8, 18)], digits = 2), x = 1.28, y = measure_reliability_data[!is.na(measure_reliability_data$coefficient_difference),]$graph_index, color = ifelse(measure_reliability_data$significance_reported_coefficient[c(1:8, 18)], "black", "grey"), size = 2.8) +
-
-  # setting the theme
-  theme_minimal() +
-  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), "lines")) +
-
-  # adding the necessary indicative texts
-  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 7.25, ymax = 7.25, xmin = 0.01, xmax = 0.01) +
-  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 6, ymax = 6, xmin = 0.01, xmax = 0.01) +
-  annotation_custom(grob = textGrob(label = "Tau", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.1, xmax = 1.1) +
-  annotation_custom(grob = textGrob(label = "Diff", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.24, xmax = 1.24) +
-
-  coord_cartesian(xlim = c(0, 1), clip = "off") +
-
-  # adding the blue triangles for reported reliability and green prediction intervals
-  geom_point(data = measure_reliability_data, mapping = aes(x = reported_coefficient, y = graph_index), color = "blue", shape = 17, size = 3) +
-  # we remove 14 & 15 lower bound because they are below 0
-  geom_point(data = measure_reliability_data[-c(14, 15),], mapping = aes(x = pi.lb, y = graph_index), color = "green", shape = 124, size = 2.5) + 
-  geom_point(data = measure_reliability_data, mapping = aes(x = pi.ub, y = graph_index), color = "green", shape = 124, size = 2.5) +
-
-  ylab("") +
-  xlab("Cronbach's alpha")
-
-```
-
-We found some indication of heterogeneity for fourteen of the nineteen measures.
-We observe that for most measures the reported reliabilities were generally lower than the reliabilities calculated for the replication labs.
-We also observed that original reliabilities were more commonly reported for those measures that had higher average reliabilities among the replications (>.80) compared to on average less reliable measures.
-
-However,  to be able to interpret Cronbach’s alpha, the underlying assumptions have to be met: undimensionality, uncorrelated item errors, and Tau equivalence.
-Our CFA results show (summarized in Table 3 below) that … .
+Finally, we also tested these measures for unidimensionality.
+Our unidimensionality check serves a double purpose.
+First, unidimensionality is one of the assumptions of Cronbach's Alpha.
+If this assumption does not hold for a measure, Cronbach's Alpha gives a biased and uninformative estimate of the reliability.
+Second, all measurement items for which unidimensionality was checked, were used to form a singular index of one latent vasriable.
+Certainly, not all singular indexes require the underlying latent factor model to be unidimensional (e.g., general intelligence can be used as a variable on its own or sub-divided in multiple components such as numerical and verbal intelligence).
+Still, we believe it is not unreasonable to assume that for most of our measures we should observe a unidimensional factor model to have at least adequate fit.
+
+We tested for unidimensionality using two tests on the data from each lab for each measure.
+If at least one of these tests was passed, the measure in that lab was marked as unidimensional.
+For the first test we fit a Confirmatory Factor Analysis (CFA) model with one factor to the data, and we then evaluate the RMSEA value.
+If this value is below .08, the test is passed.
+For the second test we run a parallel analysis.
+This runs multiple Exploratory Factor Analyses (EFA) where the number of factors in the model is increased by 1 until the number of factors is one less than the number of items.
+It then compares the eigenvalues (an indication of how much variance is explained by that factor) of each factor to the eigenvalues for that factor if the data matrix was effectively random.
+If only the single factor has an eigenvalue that is significantly higher than the eigenvalue when the data matrix is random, the test is passed.
+We chose a combination of these two tests, as the RMSEA is known to be biased for models with small degrees of freedom (Kenny et al., 2015), while the parallel analysis may be less suited if a two or more factor solution would also fit the sample item data.
 
@@
 rm(extracted_data_list)
-
-```
-
-```{r internal_structure_information}
-Mode <- function(x) {
-  ux <- unique(x)
-  ux[which.max(tabulate(match(x, ux)))]
-}
-
-FA_aggregate_data <- data.frame(RMSEA = rep(NA, 19), 
-                                RMSEA_se = rep(NA, 19), 
-                                RMSEA_global_mean = rep(NA, 19), 
-                                RMSEA_mean_sd = rep(NA, 19), 
-                                N_factors_mode = rep(NA, 19),
-                                unidimensional_ratio = rep(NA, 19),
-                                Tau_N_P_10 = rep(NA, 19),
-                                Tau_N_P_05 = rep(NA, 19),
-                                Tau_N_P_01 = rep(NA, 19),
-                                global_mean_spec = rep(NA, 19),
-                                global_sd_spec = rep(NA, 19),
-                                err_N_P_10 = rep(NA, 19),
-                                err_N_P_05 = rep(NA, 19),
-                                err_N_P_01 = rep(NA, 19))
-
-### recreate FA_list
-FA_list <- list(fa_caruso_2012, fa_husnu_2010, fa_nosek_2002_math, fa_nosek_2002_art,
-                fa_anderson_2012_swl, fa_anderson_2012_pa, fa_anderson_2012_na,
-                fa_giessner_2007, fa_norenzayan_2002, fa_zhong_2006, fa_monin_2001_most,
-                fa_monin_2001_some, fa_cacioppo_1983_arg, fa_cacioppo_1983_nfc, 
-                fa_de_fruyt_2000, fa_albarracin_2008_verb, fa_albarracin_2008_math,
-                fa_shnabel_2008, fa_vohs_2008)
+```
+
+# Results
+
+## Reported Reliability & Validity Evidence
+
+Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts the flow of measures in relation to reliability reporting.
+First, it shows that almost half of the measures in both replication (N = `r sum(coded_data_replications$N_items == "1 item measure")`) and original research (N = `r sum(coded_data_original$N_items == "1 item measure")`) were single-item measures.
+Second, only `r apa_num(sum(coded_data_original$reliability_type != "Not Reported" & coded_data_original$reliability_type != ""), numerals = FALSE)` measures in original and `r apa_num(sum(coded_data_replications$reliability_type != "Not Reported" & coded_data_replications$reliability_type != ""), numerals = FALSE)` in replications were reported alongside a reliability indicator.
+Cronbach’s Alpha was the most commonly reported reliability indicator.
+
+```{r ReliabilityReportingFlowDiagram, fig.cap = "Reliability reporting flow diagram.
+Figure shows the number of measures as reported in both the replication protocols and original article, which meet the criterion in the box within the diagram and those criteria before it.", out.height = "60%"}
+knitr::include_graphics(path = "../../SupplementaryMaterials/reliability_reporting_flow_diagram.png")
+```
+
+For validity evidence the pattern was similar.
+Only, `r apa_num(sum(coded_data_original$sel_psychometric_evidence_REV != "None" & coded_data_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_original$sel_3_REV == TRUE, na.rm = TRUE), numerals = FALSE)` original studies and `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_replications$sel_3_REV == TRUE, na.rm = TRUE), numerals = FALSE)` replications reported psychometric validity evidence on the measurement.
+Replications reported both less reliability and validity evidence.
+Exploratory factor analyses (original: `r apa_num(sum(coded_data_original$sel_psychometric_evidence_REV == "Exploratory Factor Analysis"), numerals = FALSE)`, replications: `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV == "Exploratory Factor Analysis"))`) and convergent validity evidence (original: `r apa_num(sum(coded_data_original$sel_psychometric_evidence_text_REV == "convergent validity"), numerals = FALSE)`, replications: `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_text_REV == "convergent validity"), numerals = FALSE)`) were the most common.
+Psychometric validity evidence from previous studies was reported in `r apa_num(sum(coded_data_original$sel_4 == TRUE, na.rm = TRUE), numerals = FALSE)` original studies and `r apa_num(sum(coded_data_replications$sel_4 == TRUE, na.rm = TRUE), numerals = FALSE)` replications.
+For single-item measures, `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_text_REV[coded_data_replications$N_items == "1 item measure"] != ""), numerals = FALSE)` were reported with validity evidence – specifically, all were convergent validity – in the replication protocols.
+In the original studies, `r apa_num(sum(coded_data_original$sel_psychometric_evidence_text_REV[coded_data_original$N_items == "1 item measure"] != ""), numerals = FALSE)` single-item measures came with reported validity evidence.
+
+```{r validity_evidence_reporting}
+table(coded_data_original$sel_psychometric_evidence_REV)
+table(coded_data_replications$sel_psychometric_evidence_REV)
+
+# how much psychometric validity evidence was reported
+sum(coded_data_original$sel_psychometric_evidence_REV != "None" & coded_data_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_original$sel_3_REV == TRUE, na.rm = TRUE)
+sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_replications$sel_3_REV == TRUE, na.rm = TRUE)
+
+table(coded_data_original$sel_psychometric_evidence_text_REV)
+table(coded_data_replications$sel_psychometric_evidence_text_REV)
+
+# internal
+table(coded_data_original$sel_3_REV)
+table(coded_data_replications$sel_3_REV)
+# external
+table(coded_data_original$sel_4)
+table(coded_data_replications$sel_4)
+
+sum(coded_data_original$sel_4 == TRUE, na.rm = TRUE)
+sum(coded_data_replications$sel_4 == TRUE, na.rm = TRUE)
+
+# how many existing measures were used
+sum(coded_data_original$sel_existing == "True, namely:")
+sum(coded_data_replications$sel_existing == "True, namely:")
+
+# for existing measures, how many had the specific version reported
+sum(coded_data_original$op_1_REV[coded_data_original$sel_existing == "True, namely:"] == TRUE, na.rm = TRUE)
+sum(coded_data_replications$op_1_REV[coded_data_replications$sel_existing == "True, namely:"] == TRUE , na.rm = TRUE)
+
+# for measures how much exploratory factor analysis validity evidence was reported
+sum(coded_data_original$sel_psychometric_evidence_REV == "Exploratory Factor Analysis")
+sum(coded_data_replications$sel_psychometric_evidence_REV == "Exploratory Factor Analysis")
+
+# for measures how much convergent validity evidence was reported
+sum(coded_data_original$sel_psychometric_evidence_text_REV == "convergent validity")
+sum(coded_data_replications$sel_psychometric_evidence_text_REV == "convergent validity")
+
+# for single item measures was any validity evidence reported
+apa_num(sum(coded_data_replications$sel_psychometric_evidence_text_REV[coded_data_replications$N_items == "1 item measure"] != ""), numerals = FALSE)
+
+apa_num(sum(coded_data_original$sel_psychometric_evidence_text_REV[coded_data_original$N_items == "1 item measure"] != ""), numerals = FALSE)
+
+# if an existing measure was used, how did that affect the reporting of reliability
+# and validity evidence
+table(coded_data_original$sel_existing, coded_data_original$reliability_type) # reliability does appear to indicate more reporting for existing reliabilities
+
+table(coded_data_original$sel_existing, coded_data_original$sel_psychometric_evidence_REV) # not much to go on for psychometric validity evidence
+
+# overall not substantive enough data too highlight in the article (would require a test to evaluate)
+```
+
+## Calculated Reliability & Validity Evidence
+
+The average calculated Cronbach’s alpha coefficient across individual replications was `r apa_num(mean(calculated_reliability_lab_data$alpha))` with a standard deviation of `r apa_num(sd(calculated_reliability_lab_data$alpha))`.
+Figure 2 displays the distributions of the calculated Cronbach’s Alpha scores from each lab for each measure, separated by successful and unsuccessful replication, based on the meta-analytic p-value (alpha \< .05) retrieved from the Many Labs reports.
+
+```{r alpha_distributions_data_prep}
+### Preparation code for the alpha distribution figure
+# creating an editable copy of the calculated_reliability_lab_data
+calculated_alpha_plot_data <- calculated_reliability_lab_data
+
+# calculating the average alpha per group
+calculated_alpha_plot_data$avg.alpha <- ave(calculated_reliability_lab_data$alpha, 
+                                            calculated_reliability_lab_data$g)
+
+# making replication success a Boolean, so we can order the dataset by it.
+calculated_alpha_plot_data$replication_success <- ifelse(
+  calculated_alpha_plot_data$replication_success == "Yes", TRUE, FALSE)
+
+# reordering the plot from succesfully replicated to unsuccesfully replicated, and then from least to most reliable.
+calculated_alpha_plot_data <- calculated_alpha_plot_data[order(-calculated_alpha_plot_data$replication_success, -calculated_alpha_plot_data$avg.alpha),]
+
+# Removing calculated alpha's that fell below 0 to make everythign fit nicely in the plot.
+calculated_alpha_plot_data <- calculated_alpha_plot_data[calculated_alpha_plot_data$alpha > 0,]
+
+# reordering the grouping variable factor levels
+calculated_alpha_plot_data$g <- fct_inorder(as.factor(calculated_alpha_plot_data$g), ordered = NA)
+
+# adding an index to which row in the plot data the row in measure_reliability_data belongs to
+measure_reliability_data$graph_index <- NA
+
+for (i in 1:nrow(measure_reliability_data)){
+  measure_reliability_data$graph_index[which(unique(calculated_alpha_plot_data$g)[i] == measure_reliability_data$g)] <- i
+}
+
+```
+
+```{r plot_alpha_distributions, warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients calculated for the responses on a measure at each lab location, across the nineteen measures for which raw data was available from which Cronbach’s alpha coefficients could be calculated.
+Cronbach's alpha values that fell below 0 were excluded.
+The green lines indicate the meta-analytic prediction interval lower and upper bound.
+The blue triangles indicate the reported alpha coefficient for that measure from the original article, when reported.
+The Tau column besides the figure shows the tau heterogeneity estimate based on a meta-analysis of the calculated reliabilities for each measure.
+Meta-analyses for which the Q-test for heterogeneity was significant at alpha < .05 are in black, while non-significant results are in grey.
+The Diff column shows the difference between reported reliability and the average reliability calculated from the Many Labs data for the applicable measures.
+The reported reliabilities that fell outside the 95% quantile of calculated reliability scores are shown in black, otherwise in grey."}
+
+# plot for distribution of alpha
+ggplot(calculated_alpha_plot_data, aes(x = alpha, y = g)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_hline(yintercept = 6.5, color = "red", size = 1) +
+  geom_point(alpha = 0.1) +
+
+  # adding in the tau values
+  geom_text(data = measure_reliability_data, label = format(measure_reliability_data$tau, digits = 1), x = 1.15, y = measure_reliability_data$graph_index, color = ifelse(measure_reliability_data$QEp < .05, "black", "grey"), size = 2.8) +
+
+  # adding in the difference in alpha coefficients
+  geom_text(data = measure_reliability_data[c(1:8, 18),], label = format(measure_reliability_data$coefficient_difference[c(1:8, 18)], digits = 2), x = 1.28, y = measure_reliability_data[!is.na(measure_reliability_data$coefficient_difference),]$graph_index, color = ifelse(measure_reliability_data$significance_reported_coefficient[c(1:8, 18)], "black", "grey"), size = 2.8) +
+
+  # setting the theme
+  theme_minimal() +
+  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), "lines")) +
+
+  # adding the necessary indicative texts
+  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 7.25, ymax = 7.25, xmin = 0.01, xmax = 0.01) +
+  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 6, ymax = 6, xmin = 0.01, xmax = 0.01) +
+  annotation_custom(grob = textGrob(label = "Tau", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.1, xmax = 1.1) +
+  annotation_custom(grob = textGrob(label = "Diff", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.24, xmax = 1.24) +
+
+  coord_cartesian(xlim = c(0, 1), clip = "off") +
+
+  # adding the blue triangles for reported reliability and green prediction intervals
+  geom_point(data = measure_reliability_data, mapping = aes(x = reported_coefficient, y = graph_index), color = "blue", shape = 17, size = 3) +
+  # we remove 14 & 15 lower bound because they are below 0
+  geom_point(data = measure_reliability_data[-c(14, 15),], mapping = aes(x = pi.lb, y = graph_index), color = "green", shape = 124, size = 2.5) + 
+  geom_point(data = measure_reliability_data, mapping = aes(x = pi.ub, y = graph_index), color = "green", shape = 124, size = 2.5) +
+
+  ylab("") +
+  xlab("Cronbach's alpha")
+
+```
+
+We found statistically significant indication of heterogeneity in Cronbach's alpha for `r apa_num(sum(measure_reliability_data$QEp < .05), numerals = FALSE)` of the `r apa_num(nrow(measure_reliability_data), numerals = FALSE)` measures.
+However, as noted earlier a more accurate indication of the heterogeneity can be observed in the prediction intervals.
+The prediction intervals generally show larger indications of heterogeneity for some of the lower reliability measures and less for higher reliability measures when compared to the Tau test results.
+Number of labs also appears to be a factor for narrowing the prediction intervals.
+Additionally, we observe that for most measures the reported reliabilities were generally lower than the reliabilities calculated for the replication labs.
+Perhaps more interesting is that we observed that reported reliabilities in the original study were more common for those measures that had higher average reliabilities (\>.80) in the replications compared to on average less reliable measures.
+
+Figure \@ref(fig:Plot1Factor) below show the result of our unidimensionality test.
+`r apa_num((sum(unidimensionality_graph_data$RMSEA < .08, na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)` % of labs were below our RMSEA .08 threshold, while for `r apa_num((sum(unidimensionality_meta_data$beta < .08, na.rm = TRUE)), numerals = FALSE)` measures of the total `r apa_num(nrow(unidimensionality_meta_data), numerals = FALSE)` the mean across labs was below this threshold.
+Furthermore, the RMSEA shows considerable variation within measures, with the standard deviation ranging from `r apa_num(min(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))` as the lowest to all the way up to `r apa_num(max(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))`.
+The parallel analysis results similarly showed inconsistency both across and within measures.
+While `r apa_num((sum(unidimensionality_graph_data$N_factors_capped == "1", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% of labs returned a single factor solution, `r apa_num((sum(unidimensionality_graph_data$N_factors_capped == "2", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% returned a two-factor, and `r apa_num((sum(unidimensionality_graph_data$N_factors_capped == "2", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% returned three or more factors.
+The remainder did not converge.
+The lack of convergence was an also an issue for the CFA used for the RMSEA check.
+The CFA failed to converge for `r apa_num((sum(is.na(unidimensionality_graph_data$RMSEA)) / nrow(unidimensionality_graph_data)) * 100)`% of labs.
+In the case of the De Fruyt et al.
+(2000) measure all labs failed to converge.
+Convergence in the other cases was the result of either the severe misfit of our factor models or a lack of sample size to stably estimate these models.
+In the end, `r apa_num((sum(unidimensionality_graph_data$unidimensional == "Yes", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% of labs passed our unidimensionality check.
+
+```{r PlotData1FactorRMSEA}
+unidimensionality_graph_data <- data.frame(RMSEA = c(NA),
+                                           RMSEA_se = c(NA),
+                                           N_factors = NA,
+                                           unidimensional = NA,
+                                           g = NA)
+
+measured_variables <- c("caruso_2012", "husnu_2010", "nosek_2002_math", "nosek_2002_art", "anderson_2012_swl", "anderson_2012_pa", "anderson_2012_na", "giessner_2007", "norenzayan_2002", "zhong_2006", "monin_2001_most", "monin_2001_some", "cacioppo_1983_arg", "cacioppo_1983_nfc", "de_fruyt_2000", "albarracin_2008_verb", "albarracin_2008_math", "shnabel_2008", "vohs_2008")
 
 for (i in 1:19){
-  data <- FA_list[[i]]
+
+  g = measured_variables[i]
+
+  unidimensionality_graph_data <- rbind(unidimensionality_graph_data, cbind(FA_list[[i]][1:4], g))
+
+}
+
+# removing placeholder first row
+unidimensionality_graph_data <- unidimensionality_graph_data[-1, ]
+
+# ordering the levels of g to match the order in the reliability graph
+unidimensionality_graph_data$g <- factor(unidimensionality_graph_data$g, levels = c("nosek_2002_art", "nosek_2002_math", "shnabel_2008", "husnu_2010", "norenzayan_2002", "vohs_2008", "cacioppo_1983_arg", "anderson_2012_pa", "anderson_2012_na", "giessner_2007", "anderson_2012_swl", "caruso_2012", "zhong_2006", "monin_2001_some", "cacioppo_1983_nfc", "monin_2001_most", "albarracin_2008_verb", "albarracin_2008_math", "de_fruyt_2000"), labels = c("Nosek et al.
+(2002), Art", "Nosek et al.
+(2002), Math", "Shnabel & Nadler (2008)", "Husnu & Crisp (2010)", "Norenzayan et al.
+(2002)", "Vohs & Schooler (2008)", "Cacioppo et al.
+(1983), arg", "Anderson et al.
+(2012), PA", "Anderson et al.
+(2012), NA", "Giessner & Schubert, (2007)", "Anderson et al.
+(2012), SWL", "Caruso et al.
+(2012)", "Zhong & Lijenquist (2006)", "Monin & Miller (2001), some", "Cacioppo et al.
+(1983), nfc", "Monin & Miller (2001), most",  "Albarracín et al.
+(2008), exp 5 verb", "Albarracín et al.
+(2008), exp 5 math", "De Fruyt et al.
+(2000)"))
+
+# adding a capped of version of the N_factors variable as a category variable
+N_factors_capped <- rep(NA, nrow(unidimensionality_graph_data))
+
+N_factors_capped[unidimensionality_graph_data$N_factors == 1] <- "1"
+N_factors_capped[unidimensionality_graph_data$N_factors == 2] <- "2"
+N_factors_capped[unidimensionality_graph_data$N_factors >= 3] <- "3+"
+
+unidimensionality_graph_data$N_factors_capped <- as.factor(N_factors_capped)
+
+### meta-analyzing
+assess_undidimensionality_heterogeneity <- function(data_on_RMSEA){
+  temp_beta <- NA
+  temp_tau <- NA
+  temp_QEp <- NA
+  rma_prediction <- NA
+  temp_pi.lb <- NA
+  temp_pi.ub <- NA
 
   tryCatch({
-    RMSEA_estimate <- rma(yi = as.numeric(RMSEA), sei = as.numeric(RMSEA_se), data = data) # inverse variance weighting is on by default
-    FA_aggregate_data$RMSEA[i] <- RMSEA_estimate$b
-    FA_aggregate_data$RMSEA_se[i] <- RMSEA_estimate$se
+    # run a random effects meta-analysis
+    rma_model <- rma(yi = data_on_RMSEA$RMSEA, sei = data_on_RMSEA$RMSEA_se, 
+                     method = "REML", control = list(stepadj = 0.5, maxiter = 1000))
+    # estimated coefficient
+    temp_beta <- rma_model$beta
+
+    # extract the relevant heterogeneity information
+    temp_tau <- sqrt(rma_model$tau2)
+    temp_QEp <- rma_model$QEp
+
+    # get prediction intervals for alpha
+    rma_prediction <- predict(rma_model)
+    temp_pi.lb <- rma_prediction$pi.lb
+    temp_pi.ub <- rma_prediction$pi.ub
 
@@
 
-  FA_aggregate_data$RMSEA_global_mean[i] <- mean(as.numeric(data$RMSEA), na.rm = TRUE)
-  FA_aggregate_data$RMSEA_mean_sd[i] <- sd(as.numeric(data$RMSEA), na.rm = TRUE)
-
-  FA_aggregate_data$N_factors_mode[i] <- Mode(data$N_factors)
-
-  if("Yes" %in% data$unidimensional){
-    FA_aggregate_data$unidimensional_ratio[i] <- table(data$unidimensional)[["Yes"]] / length(data$unidimensional)
-  } else{
-    FA_aggregate_data$unidimensional_ratio[i] <- 0
-  }
-
-  # count number of Tau differences (don't know anything better for now)
-  FA_aggregate_data$Tau_N_P_10[i] <- sum(as.numeric(data$Tau_p_diff) < .1, na.rm = TRUE) / length(na.omit(data$Tau_p_diff))
-  FA_aggregate_data$Tau_N_P_05[i] <- sum(as.numeric(data$Tau_p_diff) < .05, na.rm = TRUE) / length(na.omit(data$Tau_p_diff))
-  FA_aggregate_data$Tau_N_P_01[i] <- sum(as.numeric(data$Tau_p_diff) < .01, na.rm = TRUE) / length(na.omit(data$Tau_p_diff))
-
-  FA_aggregate_data$global_mean_spec[i] <- mean(as.numeric(data$mean_spec), na.rm = TRUE)
-  FA_aggregate_data$global_sd_spec[i] <- sd(as.numeric(data$mean_spec), na.rm = TRUE)
-
-  # count number of err differences (don't know anything better for now)
-  FA_aggregate_data$err_N_P_10[i] <- sum(as.numeric(data$err_p_diff) < .1, na.rm = TRUE) / length(na.omit(data$err_p_diff))
-  FA_aggregate_data$err_N_P_05[i] <- sum(as.numeric(data$err_p_diff) < .05, na.rm = TRUE) / length(na.omit(data$err_p_diff))
-  FA_aggregate_data$err_N_P_01[i] <- sum(as.numeric(data$err_p_diff) < .01, na.rm = TRUE) / length(na.omit(data$err_p_diff))
-}
-
-### PLOTs
-# ggplot(FA_aggregate_data[-15,], aes(x = RMSEA_global_mean, y = 0)) +
-#   geom_boxplot(outlier.shape = NA, width = 2) +
-#   geom_point(alpha = 0.7) +
-#   xlab("Global Mean of RMSEA for Single Factor Model") +
-#   ylim(-10, 10) +
-#   theme_apa(base_size = 20)
-# 
-# ggplot(FA_aggregate_data[-15,], aes(x = unidimensional_ratio, y = 0)) +
-#   geom_boxplot(outlier.shape = NA, width = 2) +
-#   geom_point(alpha = 0.7) +
-#   ylim(-10, 10) +
-#   xlab("Ratio of Labs with Unidimensional Factor Solution") +
-#   theme_apa(base_size = 20)
-# 
-# ggplot(FA_aggregate_data[-15,], aes(x = N_factors_mode)) +
-#   geom_histogram(stat = "count", colour = "#28292A") +
-#   scale_y_continuous(breaks = seq(0, 12, by = 2)) +
-#   xlab("Mode of N Factors Selected by Parallel Analysis") +
-#   theme_apa(base_size = 20)
-
-# apa_table(
-#   FA_aggregate_data, align = c("l", rep("r", 13))
-#   , caption = "Internal Structure indicators of applicable measures"
-#   , note = "Because of a lack of convergence in the meta-analytic model, there are no meta-analytic RMSEA results.
-Measure fifteen had failed to deliver results for most steps during the individual factor analysis phase of the analyses.
-"
-#   , escape = FALSE, placement = "htp")
-
-print(FA_aggregate_data)
-```
-
-Besides testing for Cronbach’s assumptions, we can also use the more informative Omega coefficient. … This one shows XXX, compared to our CFA + reliability results this shows … .
-
-```{r omega_distributions_data_prep}
-# checking for each data row that they have a calculated omega coefficient,
-# and only extracting those.
-calculated_omega_plot_data <- calculated_reliability_lab_data[!is.na(calculated_reliability_lab_data$omega.tot), ]
-
-# making replication success a boolean which can affect order
-calculated_omega_plot_data$replication_success <- ifelse(
-  calculated_omega_plot_data$replication_success == "Yes", TRUE, FALSE)
-
-# calculating the average omega per group
-calculated_omega_plot_data$avg.omega <- ave(calculated_omega_plot_data$omega.tot, calculated_omega_plot_data$g)
-
-# reordering the plot from least to most reliable split by replication success
-calculated_omega_plot_data <- calculated_omega_plot_data[order(-calculated_omega_plot_data$replication_success, -calculated_omega_plot_data$avg.omega),]
-calculated_omega_plot_data$g <- fct_inorder(as.factor(calculated_omega_plot_data$g), ordered = NA)
-
-table(calculated_omega_plot_data$g)
-
-# reorder the total values to fit with the omega ordering
-table(calculated_reliability_lab_data$g)[c(15, 16, 17, 14, 11, 18, 4, 3, 10, 6,
-                                           5, 8, 19, 7, 13, 2, 1, 12, 9)]
-
-```
-
-```{r  plot_omega_distributions, warning = FALSE,  fig.cap = "Distributions of calculated McDonald’s Omega t  calculated for the responses on a measure at each lab location, across the eighteen measures for which raw data was available from which McDonald’s Omega t coefficients could be calculated.
+  return(c(temp_beta, temp_tau, temp_QEp, temp_pi.lb, temp_pi.ub, data_on_RMSEA$g[1]))
+}
+
+unidimensionality_meta_list <- tapply(unidimensionality_graph_data, unidimensionality_graph_data$g, assess_undidimensionality_heterogeneity)
+
+# convert data output to a dataframe
+unidimensionality_meta_data <- do.call(rbind.data.frame, unidimensionality_meta_list)
+
+names(unidimensionality_meta_data) <- c("beta", "tau", "QEp", "pi.lb", "pi.ub")
+
+# added the reporting or lack of reporting of psychometric validty evidence in the original to the meta data
+unidimensionality_meta_data$reported_psych_val <- coded_data_original$sel_psychometric_evidence_REV[measure_reliability_data$coded_data_index] != "None" & coded_data_original$sel_psychometric_evidence_REV[measure_reliability_data$coded_data_index] != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_original$sel_3_REV[measure_reliability_data$coded_data_index] == TRUE
+
+# adding the number of non-coverged factor models
+non_converged_list <- tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, is.na)
+
+non_converged_vec <- rep(0, 19)
+
+for (i in 1:19){
+  non_converged_vec[i] <- sum(non_converged_list[[i]])
+}
+
+```
+
+```{r Plot1Factor fig.cap = "Distributions of calculated RMSEA of a single-factor model fit calculated for the responses on a measure at each lab location, across the nineteen measures for which raw data was available on which a factor model could be fitted.
+The red horizontal line separate the replicated from the non-repicated measures.
+The red vertical line indicates our .08 RMSEA cutoff value.
+The N non-conv.
+column besides the graph shows the number of labs per measure for which the single-factor CFA did not converge.
+The color of each dot shows the number of factors that were selected for that measure for that lab location based on the parallel analyses.
+Psychometric validity evidence was reported in the original Husnu & Crips (2010) and Shnabel & Nadler (2008) studies."}
+
+# plot for distribution of alpha
+ggplot(unidimensionality_graph_data, aes(x = RMSEA, y = g, colour = as.factor(N_factors_capped))) +
+  geom_boxplot(outlier.shape = NA, colour = "black") +
+  geom_hline(yintercept = 6.5, color = "red", size = 1) +
+  geom_vline(xintercept = 0.08, color = "red", size = 1) +
+  geom_point(alpha = 0.3) +
+
+  # adding in the tau values
+  #geom_text(data = unidimensionality_meta_data, label = format(unidimensionality_meta_data$tau, digits = 1), x = 0.58, y = 1:19, color = ifelse(unidimensionality_meta_data$QEp < .05, "black", "grey"), size = 2.8) +
+
+  # adding in the N non converted
+  geom_text(data = unidimensionality_meta_data, label = format(non_converged_vec), x = 0.51, y = 1:19, size = 2.8, colour = "black") +
+
+  # setting the theme
+  theme_minimal() +
+  theme(legend.position = "bottom", plot.margin = unit(c(1, 5, 1, 1), "lines")) +
+
+  # adding the necessary indicative texts
+  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 7.25, ymax = 7.25, xmin = 0.33, xmax = 0.33) +
+  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 6, ymax = 6, xmin = 0.37, xmax = 0.37) +
+  #annotation_custom(grob = textGrob(label = "Tau", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 0.55, xmax = 0.55) +
+  annotation_custom(grob = textGrob(label = "N Non-Conv.", hjust = 0, gp = gpar(fontsize = 11)), ymin = 20.2, ymax = 20.2, xmin = 0.48, xmax = 0.48) +
+
+  coord_cartesian(xlim = c(0, 0.45), clip = "off") +
+
+  # we remove 7 & 15 lower bound because they are below 0
+  # geom_point(data = unidimensionality_meta_data[c(1:6, 8:14, 16:17),], mapping = aes(x = pi.lb, y = c(1:6, 8:13, 15:17) ), color = "green", shape = 124, size = 2.5) + 
+  # geom_point(data = unidimensionality_meta_data, mapping = aes(x = pi.ub, y = 1:19), color = "green", shape = 124, size = 2.5) +
+
+  scale_colour_manual(name = "N Factors (Parallel Analysis)", values = c("#0072B2", "#009E73", "#F0E442"), na.value = "#000000") + 
+  guides(colour = guide_legend(override.aes = list(alpha = 1))) +
+  ylab("") +
+  xlab("RMSEA (unidimensional CFA model)") 
+```
+
+```{r check_on_Omega_convergence}
+is_mostly_na <- function(x){
+  return((sum(is.na(x)) / length(x)) > .5) 
+}
+
+Omega_convergence_vector <- tapply(calculated_alpha_plot_data$omega.tot, calculated_alpha_plot_data$g, is_mostly_na)
+
+sum(Omega_convergence_vector)
+```
+
+Figure \@ref(fig:PlotOmegaDistributions) below shows the result of our Omega analyses.
+Note that while we show the distributions of omega values here, due to the lack of a formula to calculate the Omega standard error, we did not perform a meta-analysis on these results.
+Overall, our Omega coefficient analyses show a similar pattern between measures to that observed for the alpha coefficient albeit with generally higher coefficient scores across measures.
+However, not all improved.
+The two columns beside Figure \@ref(fig:PlotOmegaDistributions) show in how many labs each measure was used, as well as for how many labs an omega coefficient could be obtained, which was not always.
+In `r apa_num(sum(is.na(calculated_alpha_plot_data$omega.tot)) / nrow(calculated_alpha_plot_data) * 100)`% of labs, no omega coefficient could be obtained.
+For `r sum(Omega_convergence_vector)` measures the number of labs for which an Omega coefficient could not be obtained was even the majority.
+This relates to our findings from the unidimensionality tests, where some factor models did not converge.
+
+```{r PlotOmegaDistributions, warning = false, fig.cap = "Distributions of calculated McDonald’s Omega t  calculated for the responses on a measure at each lab location, across the eighteen measures for which raw data was available from which McDonald’s Omega t coefficients could be calculated.
 The N.Omg column besides the figure shows the number of lab locations for which an Omega coefficient could be successfully calculated.
@@
 # plot for omega
-ggplot(calculated_omega_plot_data, aes(x = omega.tot, y = g)) +
+ggplot(calculated_alpha_plot_data, aes(x = omega.tot, y = g)) +
   geom_boxplot(outlier.shape = NA) +
@@
   # adding labels to show the number of labs per measure for which a total omega could be calculated
-  geom_text(data = calculated_omega_plot_data[1:18,], label = table(calculated_omega_plot_data$g)[1:18], x = 1.15, y = 1:18, size = 2.8) +
+  geom_text(data = calculated_alpha_plot_data[1:19,], label = table(calculated_alpha_plot_data$g[!is.na(calculated_alpha_plot_data$omega.tot)]), x = 1.15, y = 1:19, size = 2.8) +
   # adding labels to show the number of labs per measure
-  geom_text(data = calculated_omega_plot_data[1:18,], label = table(calculated_reliability_lab_data$g)[c(15, 16, 17, 14, 11, 18, 4, 3, 10, 6, 5, 8, 19, 7, 13, 2, 1, 12)], x = 1.35, y = 1:18, size = 2.8) +
+  geom_text(data = calculated_alpha_plot_data[1:19,], label = table(calculated_alpha_plot_data$g), x = 1.35, y = 1:19, size = 2.8) +
 
@@
   annotation_custom(grob = textGrob(label = "Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 6, ymax = 6, xmin = 0.01, xmax = 0.01) +
-  annotation_custom(grob = textGrob(label = "N.Omg", hjust = 0, gp = gpar(fontsize = 12)), ymin = 19.2, ymax = 19.2, xmin = 1.08, xmax = 1.08) +
-  annotation_custom(grob = textGrob(label = "N.Tot", hjust = 0, gp = gpar(fontsize = 12)), ymin = 19.2, ymax = 19.2, xmin = 1.28, xmax = 1.28) +
+  annotation_custom(grob = textGrob(label = "N.Omg", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.08, xmax = 1.08) +
+  annotation_custom(grob = textGrob(label = "N.Tot", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.28, xmax = 1.28) +
 
@@
 
+## Questionable Measurement Practices
+
+Reliability and validity indicators are only one aspect of measurement reporting.
+We coded additional potential questionable measurement practices in reporting in general too.
+Table \@ref(tab:QMPTable) below shows for both original and replication for all of the QMP items the ratio of QMPs and for how many of the `r nrow(coded_data_original)` measures the QMP was applicable.
+Meanwhile, the Phi coefficient indicates the “correlation” between the MP being questionable or good in the original and the same for the replication.
+
+```{r QMPtable}
+# create informative Measurement Practice Labels 
+MPractice <- c("Reliability is reported", "It is clear if the measure existed or is newly created",    "Specifc version of the measure is specified", "Validity evidence from a factor analysis is presented",   "The measured variable is defined", "The choice of measure selection or creation is justified",    "The implemented operationalisation is justified", "The source of the measure is provided",    "Psychometric evidence from the study is given", "Psychometric evidence from an earlier study is given",    "The administration format and environment are described", "The administration procedure is described",   "The number of items are described", "The number of response options are described",    "The recoding of responses is described", "The creation of the index is described",    "Example items are presented in text or supplement", "Any administration format changes are mentioned",    "Administration format changes are justified/validated", "Any translations are mentioned",    "Translated measures are justified/validated", "Any changes in number of items or response options are mentioned",    "Changes in number of items or response options are justified/validated")
+
+# construct the QMP table to be printed 
+QMP_table <- data.frame("Practice" = MPractice, 
+                        "QMP original" = paste0(qmp_ratio_data$QMP_percentage_original, " (", qmp_ratio_data$N_applicable_original, ")"), 
+                        "QMP Replication" = paste0(qmp_ratio_data$QMP_percentage_replication, " (", qmp_ratio_data$N_applicable_replication, ")"), 
+                        "Phi" = qmp_ratio_data$Phi)
+
+# print the table in apa formatting 
+apa_table(QMP_table, align = c("l", "r", "r", "r"), caption = "Ratio of QMPs and number of applicable measures, for original and replication", note = "The first number in QMP org and QMP rep is the ratio of measures for which the practice in that row was not conducted well by our standards.
+The number between brackets indicates the number of measures for which the practice was applicable.", escape = FALSE, placement = "htp")
+```
+
+The Phi coefficients reveal little in the way of a consistent pattern on the relation of QMPs in original to QMPs in replications.
+However, if we look more conceptually we can also look at the reporting of information most relevant for reconstructing the measure, as well as modifications to the measure to learn about the relation between original and replication study.
+It was clear that existing measures were used for `r apa_num(sum(coded_data_original$sel_existing == "True, namely:") / nrow(coded_data_replications) * 100)`% original and `r sum(coded_data_replications$sel_existing == "True, namely:") / nrow(coded_data_original) * 100`% replication measures.
+It was not always clear which measures were used (`r sum(coded_data_original$sel_existing == "Not Clearly Stated") / nrow(coded_data_original) * 100`% original; `r sum(coded_data_replications$sel_existing == "Not Clearly Stated") / nrow(coded_data_replications) * 100`% replication), meaning they could not clearly be identified to be the same between original and replication.
+While the number of items (`r qmp_ratio_data$QMP_percentage_original[13]`% original; `r qmp_ratio_data$QMP_percentage_replication[13]`% replications) and response (`r qmp_ratio_data$QMP_percentage_original[14]`% original; `r qmp_ratio_data$QMP_percentage_replication[14]`% replications) were usually clear, and modifications were atypical, but did occur (`r qmp_ratio_data$QMP_percentage_original[22]`% original; `r qmp_ratio_data$QMP_percentage_replication[22]`% replications).
+It was however uncommon for this modification to be validated (`r qmp_ratio_data$QMP_percentage_original[23]`% original; `r qmp_ratio_data$QMP_percentage_replication[23]`% replication).
+QMPs were less common for language (`r qmp_ratio_data$QMP_percentage_original[20]`% original; `r qmp_ratio_data$QMP_percentage_replication[20]`% replications) and administration format modifications (`r qmp_ratio_data$QMP_percentage_original[18]`% original; `r qmp_ratio_data$QMP_percentage_replication[18]`% replications), .
+Validation was however still rare (language: `r qmp_ratio_data$QMP_percentage_original[21]`% original, `r qmp_ratio_data$QMP_percentage_replication[21]`% replications; administration format: `r qmp_ratio_data$QMP_percentage_original[19]`% original; `r qmp_ratio_data$QMP_percentage_replication[19]`% replications).
+While generally QMPs were not found for admin format and procedure in the replications (format: `r qmp_ratio_data$QMP_percentage_replication[11]`%; procedure: `r qmp_ratio_data$QMP_percentage_replication[12]`%), they did occur for original measures (format: `r qmp_ratio_data$QMP_percentage_original[11]`%; procedure: `r qmp_ratio_data$QMP_percentage_original[12]`%).
+In general, we observed that measurement was modified in some way from original to replication for `r sum(coded_data_replications$mod_check == "True") / nrow(coded_data_replications)`% of measures, and it was unclear whether modification occured for ``` r``sum(coded_data_replications$mod_check == "None Reported") / nrow(coded_data_replications) ```%.
+
+# Discussion
+
+To assess psychological phenomena we need measurement that is valid and reliable for our constructs.
+However, we noted first is that little reliability and validity evidence was reported.
+Second, our reanalysis of the reliability and validity of the measures showed inconsistent reliability and validity support.
+Finally, we observed a lack of transparent reporting, which makes it difficult for future researchers to reuse and build upon the validation of existing measurements.
+
+In line with existing research we found that for the majority of the measures in original and replication studies no reliability coefficient was reported, and psychometric validity evidence was even less common Beckman et al., 2004; Barry et al.
+2014; Flake, Pek, & Hehman, 2017; Shaw et al., 2020; Flake et al., 2022).
+Some part of this is due to around half of the measures in original and replication studies being single item measures.
+While it is possible to check the reliability and validity of single item measures, these methods often require multiple measures or studies to be able to cross-validate the measure with (Leppink and Pérez-Fuster, 2017; Sarstedt, 2016).
+Another factor may be observed in the fact that we observed that replications generally reported less reliability and psychometric validity evidence.
+This could be because replications implicitly defer the reporting of validity and reliability evidence to the original study.
+However, it was not uncommon for the replication to use different measures than the original study, and if it was not set in stone that the same measure as the original was used, then it stands to reason that the choice of measure should be motivated based on reliability and validity evidence.
+Furthermore, this does not explain the lack of reliability and validity reporting in the original studies.
+It may unfortunately be more reasonable to assume that many of these measures are just not validated before (or even after) use.
+
+This is not merely based on us guessing, when we recalculated the reliability coefficients and factor structure of the measures used in the replication projects, the observed reliability and validity of several measures did not convincingly show that these would be valid if presented alongside the measure in a study.
+While few measures were consistently not reliable and valid and some were even consistently reliable and valid, many were reliable and valid in a portion of the labs.
+We also noted that some measures had convergence issues, where for some labs we could not get the factor model nor Omega coefficient results.
+This may have been because of sample size issues, or the small number of items common in the replication measures, but gross misfit is also possible.
+Although, the psychometric indicators we used were applied rather broadly across a spectrum of different measures, and should not be used to make individual inferences for the measures.
+As a general overview, our results show that reliability and validity for these measures could be poor.
+
+We also observed at when measures which came with a reported Cronbach's Alpha in the original study, their average Cronbach's Alpha observed among the replications were all relatively high.
+This aligns with existing research indicating bias in reported Cronbach's Alpha values, with an excess of reported values at the common acceptably reliable threshold value of .70, and low reporting just below .70 (Hussey et al.
+2023/2025).
+Thus authors may be less inclined to report reliabilities that fall below an acceptable threshold.
+In combination with our inconsistent reliability and validity evidence this bias in reporting could create a false sense of security when looking only.
+It is possible that reliability and validity are only reported when they are sufficient, and not otherwise.
+
+After all, there is little incentive for researchers to report this information if they don't want to.
+Reporting standards for measurement reporting are not broadly applied, and we observed this also when we looked at the information needed to reconstruct a measure for reuse.
+Similar to Flake et al., 2022, we observed that QMPs were not infrequent.
+In particular, like Flake et al., 2022, we observed that original research undereported information needed to reconstruct the measurement In original research the administration format and procedure for each was not properly described for around a third of the applicable measures, the number of items and response options for each around an eight, and how the index was calculated, how the items were recoded and example items were presented for each a little under half.
+We also found that about two-thirds of the measurements were modified between original and replication, and specific modifications were rarely validated or justified.
+This raises some questions around the label direct replication.
+For example, the conscientiousness measure used for the replication of De Fruyt et al.
+(2000) was reduced from original NEO-PI-R 30-item measure to a two-item measure.
+It is highly unlikely that a measure with such a significant change would have a comparable validity and reliability to the original, and we did unsurprisingly observe convergence issues with validity as well as low reliability for this measure.
+
+One notable difference to Flake et al., 2022 is that replications did on average have less QMPs than original research.
+We believe that this is in part due to the structured way in which the Many Labs protocols were written up.
+Several Many Labs protocols even contained specific sections to declare any deviations from the original methodology.
+The other reason may be due to the more lenient coding of the QMPs in the revised protocol.
+We mostly checked that something relevant to a specific QMP item was reported, not whether that reporting thoroughly shared all the needed information.
+Regardless, any lack of information needed to recreate the measurement makes it harder for follow up research to validate the measure.
+
+Our goal with these findings is not to specifically scold the Many Labs replications nor the original studies.
+We commend the tremendous effort involved in the creation of the Many Labs projects, and we understand that for feasibility some corners had to be cut.
+Similarly, we understand that proper validation of psychological measures is not a responsibility that should be placed on any one original study.
+However, we would argue that full transparent measurement reporting is a responsibility both replications and original studies do carry.
+Furthermore, regardless of difficulty in validating measures, its necessity cannot be ignored if substantive interpretations based on the measurement data are desired.
+
+## Limitations & Future Research
+
+We focused primarily on a unidimensionality test from a factor analysis as our indicator of validity as recalculated from the data.
+However, our factor analyses were not informed by theory specific to each measure, and were instead applied the same across the board.
+It is quite possible that a measure fails at our checks and is still a valid and reliable measure to use in its specific use case.
+We consider these checks to be indicators of the overall construct validity in our sample.
+The checks should not be interpreted as concrete tests of measurement fit, nor should they be interpreted at the individual measurement level.
+Future research may want to deep dive into this specific topic and focus on doing theory informed factor analysis tests on measurement data.
+
+One of the most impactful limitations was that we were unable to construct tests to compare the measurement properties between original and replication study, and replicated and non-replicated studies.
+This was in large part because there were simply to few measures with the relevant information.
+we planned to test.
+We initially planned to test the significance of the difference in reported reliability between original and replication studies, and the relation between reliability and replication outcome.
+But due to the small number of reported reliabilities sand measures for which reliability could be calculated we were unable to perform these tests.
+However, this limitation is also one of our most important findings.
+While we were unable to perform our pre-registered tests, the fact that we couldn't, is telling regarding the lack of standards for reported measurement information in our sample.
+
+As another limitation, it is important to reflect on whether or not replication protocols and research articles can be fairly compared in terms of Measurement Practices.
+A study’s description within a replication protocol is generally shorter than an article.
+The protocol may therefore lack the space needed to report on the measurement in full detail.
+There are three reasons why we believe protocols and articles remain mostly comparable.
+Firstly, articles are often also restricted in the amount of space they have available to devote to measurement (Gardiner, 2019; maybe also some more???).
+Second, in the revised protocol some QMP items, such as whether example items were reported or not, also allowed for reporting this information in supplementary materials to count as good practice.
+Third, there are little to no other files outside the protocol and supplements where the measurement details for the replication could be found, as such the protocol and supplements represent the total available information on the measurement just like the original article does.
+A difference that was not resolved between articles and protocols was that the protocols were written before the measurement was conducted.
+Therefore we can not fairly compare protocol and replication on measurement information that is derived from the data – such as reliability coefficients and psychometric validity information.
+Still, future research should look if possible at replications that report on measurement information derived from the replication data.
+
+There were additional sources of information we could have included.
+Data from original studies could have been used to recalculate reliability and validity indicators from to compare with the replication results.
+However, it is unlikely that a substantial number would have shared their data (many were conducted before the OSF and other Open Science innitiatives were launched).
+This is likely different for more recent research (Hardwicke et al., 2022; Hamilton et al., 2023).
+Including replications of recent research could help resolve some of the sample size issues for our tests.
+Future research may wish to look at replications of more recent research to compare recalculated measurement information between original and replication.
+reliabilities and validity.
+
+## Recommendations
+
+The two main issues we believe that should be addressed are: the prevalence of using unvalidated measurement, and the lack of transparency surrounding measurement reporting.
+Unfortunately, there are no easy solutions to fix these issues.
+They will require significant efforts involving multiple members of the scientific community to bring about significant change.
+However, the positives are that these issues are interrelated, in that solving transparency will benefit greater validation of measures.
+
+Thus, first we recommend that reporting standards for measurement deserve a more central place.
+We found that reporting reliability and validity information was the exception rather than the rule, and even basic information such as how many items were in the measure was not always present.
+The AERA, APA, & NCME 2014 guidelines exist to guide researchers in the creation and validation of scales, but are not intended as general measurement reporting guidelines.
+Similarly, the APA guidelines (CITATION!!!) only briefly address reliability and validity information but say little on other measurement reporting.
+While statistical reporting standards and guidelines have proliferated, even resulting in official reccomendations from the ASA (???CITE???), a high-profile push for measurement reporting standards is lacking.
+We believe that measurement reporting standards deserve to be highlighted as much as statistical result reporting,.
+Even well reported statistics lack substantial interpretability without valid measurement, while a well reported measurement can be informative to future research on its own.
+
+Transparent measurement reporting also has the advantage that it enables future researchers to recreate the original measure.
+This point is critical to fueling our second recommendation: as a community we need to systematically evaluate and revise our existing measures.
+First, existing measures need to be reusable.
+Then researchers need to reuse existing measures.
+The obtained reliability and validity of the measure then need to be compared across multiple occasions, and finally a value judgement to determine in what contexts, if any, the measure is valid.
+Transparent reporting takes care of the first step.
+For the second step, Elson et al.
+2023 have suggested journals to implement the Standardisation Of BEhavior Research (SOBER) guidelines to specifically address issues of flexibility and norming in measurement.
+Furthermore, they propose an open repository of measurement protocols to facilitate the discovery of measures and sbuilding an evidence base.
+For the third and fourth step, the scientific community needs to analyse the validity and reliability of all uses of the measure such that they can be fairly compared to each other.
+For this it would be best if the original data of the item responses and demographics is shared for each use of the measure.
+This way the measure's validity and reliability can be recomputed similarly to what was done in our analyses, but with a closer link to theory.
+Otherwise, the summary statistics such as the variance-covariance structure, means, and standard deviations should be shared as these are sufficient for several factor analysis models.
+
+Furthermore, researchers should report and evaluate our measures using more informative indicators.
+Cronbach's Alpha on its own gives only limited information the quality of a scale, and comes with strong assumptions (Cortina, 1993; SIJTSMA CITATION).
+Factor analytical evidence and McDonald's Omega are more informative indicators that should be presented in favor of or in tandem with Cronbach's Alpha.
+
+Finally, we argue that researchers seeking to replicate a study should first evaluate the measurement of that study.
+Not only is it crucial for an informative replication that the measurement is reliable or valid.
+The original study should also report the measurement details necessary to reconstruct the original measurement.
+Otherwise it will be challenging to know if measurement was different between original and replication.
+If so, we suggest that researchers instead use their resources to conduct a replication of a study with reliable, valid and well-documented measurement.
+When replicating another study is not an option, we advise the replicating researcher to first attempt a conceptual replication using a validated measurement.
+Afterwards, a direct replication can be performed based on the conceptual replication to further assess the robustness.
+
+# Conclusion
+
+Cumulative knowledge on psychological phenomena starts with our ability to accurately capture the relevant constructs of interest.
+Based on the results from our sample and the findings of existing research, the validity and reliability of psychological measurements is rarely reported and based on our data cannot be assumed to be generally correct.
+The lack of transparent reporting on the measurement further complicates evaluating and reusing the existing measures.
+A change will be necessary.
+Otherwise, the basic premise that the measurement measures the variable it is intended to measure, will remain unsubstantiated for many psychological studies.
+Fortunately, even small steps towards improved reporting practices and single instances in cumulative measurement validation can already help proliferate validated measurement.
+
 ## Conflicts of Interest

### 2025-08-18 SupplementaryMaterials/SupplementaryAnalysesScripts/temporary_code_dump.R

@@ -1,0 +1,68 @@
+#####{r internal_structure_information}
+Mode <- function(x) {
+  ux <- unique(x)
+  ux[which.max(tabulate(match(x, ux)))]
+}
+
+FA_aggregate_data <- data.frame(RMSEA = rep(NA, 19), 
+                                RMSEA_se = rep(NA, 19), 
+                                RMSEA_global_mean = rep(NA, 19), 
+                                RMSEA_mean_sd = rep(NA, 19), 
+                                N_factors_mode = rep(NA, 19),
+                                unidimensional_ratio = rep(NA, 19),
+                                Tau_N_P_10 = rep(NA, 19),
+                                Tau_N_P_05 = rep(NA, 19),
+                                Tau_N_P_01 = rep(NA, 19),
+                                global_mean_spec = rep(NA, 19),
+                                global_sd_spec = rep(NA, 19),
+                                err_N_P_10 = rep(NA, 19),
+                                err_N_P_05 = rep(NA, 19),
+                                err_N_P_01 = rep(NA, 19))
+
+
+### recreate FA_list
+FA_list <- list(fa_caruso_2012, fa_husnu_2010, fa_nosek_2002_math, fa_nosek_2002_art,
+                fa_anderson_2012_swl, fa_anderson_2012_pa, fa_anderson_2012_na,
+                fa_giessner_2007, fa_norenzayan_2002, fa_zhong_2006, fa_monin_2001_most,
+                fa_monin_2001_some, fa_cacioppo_1983_arg, fa_cacioppo_1983_nfc, 
+                fa_de_fruyt_2000, fa_albarracin_2008_verb, fa_albarracin_2008_math,
+                fa_shnabel_2008, fa_vohs_2008)
+
+
+
+for (i in 1:19){
+  data <- FA_list[[i]]
+  
+  tryCatch({
+    RMSEA_estimate <- rma(yi = as.numeric(RMSEA), sei = as.numeric(RMSEA_se), data = data) # inverse variance weighting is on by default
+    FA_aggregate_data$RMSEA[i] <- RMSEA_estimate$b
+    FA_aggregate_data$RMSEA_se[i] <- RMSEA_estimate$se
+    
+  }, error = function(e) {
+    
+  })
+  
[…]

### 2025-08-25 Data/Data_package_description.Rmd
adjusted the supplementary materials to reflect the new project structure, fixed references, and removed depricated files.

@@
 
-<!-- Should look into the datasets that were considered not usable and see what I might find for them now. Particularly Data_2.4.1, Data_2.4.2, Data_5.5, and Data_2.19.2 -->
-
 # IntermediateData
@@
 
-*Explanation*: contains all coded data on the original articles with renamed columns, fixed bad data, restructured to match the ordering of the protocols more eligibly, recoded to be close to suitable for analysis, and with several composite variables added that were calculated from the raw data.
+*Explanation*: contains all coded data on the original articles with renamed columns, fixed bad data, restructured to match the ordering of the protocols more eligibly, recoded to be close to suitable for analysis.
+Additionally, he coded data on 3 measures that did not appear in the replication protocols were removed to allow for easier comparisons between replications and original studies.
 
@@
 
--   **\_count variables**: a sum of the total number of TRUE coded variables within the named QMP category or the total across all categories.
-
--   **\_total variables**: the sum of all the variables within the named QMP category or the total across all categories that was not coded as Not Applicable or No Modification.
-
--   **\_ratio variables**: the ratio (rounded to four decimals) between the count of TRUE scores and the total applicable variables within the named QMP category or the total across all categories.
-
-### coded_data_original_shortened.csv
-
-*Explanation*: similar to the coded_data_original.csv only with the coded data on 3 measures that did not appear in the replication protocols being removed to allow for easier comparisons between replications and original studies.
-
 ### coded_data_replications.csv
 
-*Explanation*: contains all coded data on the replications as described in the many labs protocols with renamed columns, fixed bad data, restructured to match the ordering of the protocols more ineligibly, recoded to be close to suitable for analysis, and with several composite variables added that were calculated from the raw data.
+*Explanation*: contains all coded data on the replications as described in the many labs protocols with renamed columns, fixed bad data, restructured to match the ordering of the protocols more ineligibly, recoded to be close to suitable for analysis.
 
@@
 -   **Inseparable material:** the Vignette variable from the Coded_Data_Vignette_raw.csv dataset.
-
--   **\_count variables**: a sum of the total number of TRUE coded variables within the named QMP category or the total across all categories.
-
--   **\_total variables**: the sum of all the variables within the named QMP category or the total across all categories that was not coded as Not Applicable or No Modification.
-
--   **\_ratio variables**: the ratio (rounded to four decimals) between the count of TRUE scores and the total applicable variables within the named QMP category or the total across all categories.
 
@@
 
-### cfa_results.csv
-
-*Explanation:* contains the results obtained from the exploratory unidimensionality check analyses based on factor analyses of the measures related to the data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, data_1.12.3.2_clean,data_2.12.1_clean, data_2.12.2_clean, data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.1_clean, data_3.7.2_clean, data_3.8.2_clean, data_5.1.1_clean, data_5.1.2_clean, data_5.7_clean, & data_5.9.1_clean datasets.
-This is part of the pre-registered exploratory analyses documented in appendix A.
-
-*Variables:*
-
--   **RMSEA:** the rmsea value for a single factor confirmatory factor analysis model when in turn applied to each of the datasets under consideration.
-
--   **N factors:** the number of factors selected for each of the datasets based on the parallel test for selecting factors.
-
--   **Single_factor:** a boolean variable indicating whether or not the measure was unidimensional based on the criteria that either the rmsea for the single factor model was smaller than .08, or the parallel test returned a single factor solution.
-
-### data_H1.csv DELETE???!!!
-
-*Explanation*: Contain all of the data from the coded_data_original_shortened.csv and coded_data_replications.csv except for an empty column that was meant to contain any types of reported psychometric evidence not included in the multiple choice response options, since it caused codebook generation issues.
-The two datasets of which this dataset was composed were bound so that each row contained both the coded data of the original article and the coded data on the same measure as described in the replication protocols.
-An additional variable was added which indicated for the multiple item measures only whether or not any form of reliability evidence was reported or not as a boolean variable.
-
-### data_H23.csv
+### calculated_reliability_lab_data.csv
 
@@
 
--   **omega:** McDonald's omega calculated for a measure at a particular lab location within a single study/questionnaire as extracted from the Many Labs datasets.
+-   **omega.tot:** McDonald's omega for the overarching factor as an estimate of the total reliability of a test calculated for a measure at a particular lab location within a single study/questionnaire as extracted from the Many Labs datasets.
 
--   **ASE:** Standard error of Cronbach's alpha at a particular lab location, based on formulas 2 & 3 from @duhachek2004AlphaStandardError.
+-   **omega.hier:** McDonald's hierarchical omega as the estimate of the general factor saturation of a test (not refered to much in study) calculated for a measure at a particular lab location within a single study/questionnaire as extracted from the Many Labs datasets.
+
+-   **ASE:** Standard error of Cronbach's alpha at a particular lab location, based on formulas 2 & 3 from @duhachekAlphasStandardError2004a.
+
+-   **g:** a short reference to the specific Many Labs replication (and if necessary the particular measure and construct) each alpha was associated with.
+
+-   **coded_data_index:** index of the row in the coded_data_original.csv or coded_data_replication.csv dataset that the indexed measure belongs to.
+
+-   **replication_success:** boolean variable indicating whether or not the measure's related effect was successfully replicated or not when looking at the significance of the meta-analytic p-value.
+
+### FA_Albarracin_2008_math.csv
+
+*Explanation*: This dataset describes for each lab location of study several unidimensionality, factor analysis, and Cronbach's Alpha assumptions tests for study 1 (as stated by order in Table 1.
+in the Many Labs 5 manuscript) from Many Labs 5 that was checked for reliability and unidimensionality.
+
+*Variables*:
+
+-   **RMSEA:** the RMSEA of a single factor model fitted to the data of this particular lab.
+
+-   **RMSEA_se:** the standard error of the RMSEA of a single factor model fitted to the data of this particular lab.
+
+-   **N_factors:** the number of factors suggested by the parallel analysis on the data of this particular lab.
+
+-   **unidimensional:** the result of our unidimensionality decision rule (RMSEA \<.08 or N_Factors = 1) for this particular lab.
+
+-   **Tau_chisq_diff**: the chi square difference between the Tau restricted single factor model and the non-tau-restricted single factor model each fitted to the data of this particular lab.
+
+-   **Tau_Df_diff**: the degrees of freedom difference between the Tau restricted single factor model and the non-tau-restricted single factor model each fitted to the data of this particular lab.
+
+-   **Tau_p_diff**: the p value of the chi square test between the Tau restricted single factor model and the non-tau-restricted single factor model each fitted to the data of this particular lab.
+
+-   **mean_spec:** the mean of the fully standardized estimated coefficient change for all the five highest mod index freed parameters for the unidimensional model for this particular lab.
+
+-   **err_chisq_diff**: the chi square difference between the single factor model with the five (sequentially) highest mod index freed parameters freed and the non-freed parameters single factor model each fitted to the data of this particular lab.
+
+-   **err_Df_diff**: the degrees of freedom difference between the single factor model with the five (sequentially) highest mod index freed parameters freed and the non-freed parameters single factor model each fitted to the data of this particular lab.
+
+-   **err_p_diff**: the p value of the chi square test between the single factor model with the five (sequentially) highest mod index freed parameters freed and the non-freed parameters single factor model each fitted to the data of this particular lab.
+
+### FA_Albarracin_2008_verb.csv
+
+*Explanation*: This dataset describes for each lab location of study several unidimensionality, factor analysis, and Cronbach's Alpha assumptions tests for study 1 (as ordered in Table 1.
+in the Many Labs 5 manuscript) from Many Labs 5 that was checked for reliability and unidimensionality.
+
+*Variables*:
+
+-   Same as FA_Albarracin_2008_math.csv
+
+### FA_Anderson_2012_NA.csv
+
+*Explanation*: This dataset describes for each lab location of study several unidimensionality, factor analysis, and Cronbach's Alpha assumptions tests for study 12 (as stated in the Many Labs 2 protocol) from Many Labs 2 that was checked for reliability and unidimensionality.
+
+*Variables*:
+
+-   Same as FA_Albarracin_2008_math.csv
+
+### FA_Anderson_2012_PA.csv
+
+*Explanation*: This dataset describes for each lab location of study several unidimensionality, factor analysis, and Cronbach's Alpha assumptions tests for study 12 (as stated in the Many Labs 2 protocol) from Many Labs 2 that was checked for reliability and unidimensionality.
+
+*Variables*:
+
+-   Same as FA_Albarracin_2008_math.csv
+
+### FA_Anderson_2012_SWL.csv
+
+*Explanation*: This dataset describes for each lab location of study several unidimensionality, factor analysis, and Cronbach's Alpha assumptions tests for study 12 (as stated in the Many Labs 2 protocol) from Many Labs 2 that was checked for reliability and unidimensionality.
+
+*Variables*:
+
+-   Same as FA_Albarracin_2008_math.csv
+
+### FA_Cacioppo_1983_arg.csv
+
+*Explanation*: This dataset describes for each lab location of study several unidimensionality, factor analysis, and Cronbach's Alpha assumptions tests for study 7 (as stated in the Many Labs 3 protocol) from Many Labs 3 that was checked for reliability and unidimensionality.
+
+*Variables*:
+
+-   Same as FA_Albarracin_2008_math.csv
+
+### FA_Cacioppo_1983_nfc.csv
+
+*Explanation*: This dataset describes for each lab location of study several unidimensionality, factor analysis, and Cronbach's Alpha assumptions tests for study 7 (as stated in the Many Labs 3 protocol) from Many Labs 3 that was checked for reliability and unidimensionality.
+
+*Variables*:
+
+-   Same as FA_Albarracin_2008_math.csv
+
+### FA_Caruso_2012.csv
+
+*Explanation*: This dataset describes for each lab location of study several unidimensionality, factor analysis, and Cronbach's Alpha assumptions tests for study 10 (as stated in the Many Labs 1 Proposal_V1.1) from Many Labs 1 that was checked for reliability and unidimensionality.
+
+*Variables*:
+
+-   Same as FA_Albarracin_2008_math.csv
+
+### FA_De_Fruyt_2000.csv
+
+*Explanation*: This dataset describes for each lab location of study several unidimensionality, factor analysis, and Cronbach's Alpha assumptions tests for study 8 (as stated in the Many Labs 3 protocol) from Many Labs 3 that was checked for reliability and unidimensionality.
+
+*Variables*:
+
+-   Same as FA_Albarracin_2008_math.csv
+
+### FA_Giessner_2007.csv
+
+*Explanation*: This dataset describes for each lab location of study several unidimensionality, factor analysis, and Cronbach's Alpha assumptions tests for study 15 (as stated in the Many Labs 2 protocol) from Many Labs 2 that was checked for reliability and unidimensionality.
+
+*Variables*:
+
+-   Same as FA_Albarracin_2008_math.csv
+
+### FA_Husnu_2010.csv
+
+*Explanation*: This dataset describes for each lab location of study several unidimensionality, factor analysis, and Cronbach's Alpha assumptions tests for study 11 (as stated in the Many Labs 1 Proposal_V1.1) from Many Labs 1 that was checked for reliability and unidimensionality.
+
+*Variables*:
+
+-   Same as FA_Albarracin_2008_math.csv
+
+### FA_Monin_2001_most.csv
+
+*Explanation*: This dataset describes for each lab location of study several unidimensionality, factor analysis, and Cronbach's Alpha assumptions tests for study 2 (as stated in the Many Labs 3 protocol) from Many Labs 3 that was checked for reliability and unidimensionality.
+
+*Variables*:
+
+-   Same as FA_Albarracin_2008_math.csv
+
+### FA_Monin_2001_some.csv
+
+*Explanation*: This dataset describes for each lab location of study several unidimensionality, factor analysis, and Cronbach's Alpha assumptions tests for study 2 (as stated in the Many Labs 3 protocol) from Many Labs 3 that was checked for reliability and unidimensionality.
+
+*Variables*:
+
+-   Same as FA_Albarracin_2008_math.csv
+
+### FA_Norenzayan_2002.csv
+
+*Explanation*: This dataset describes for each lab location of study several unidimensionality, factor analysis, and Cronbach's Alpha assumptions tests for study 20 (as stated in the Many Labs 2 protocol) from Many Labs 2 that was checked for reliability and unidimensionality.
+
+*Variables*:
+
+-   Same as FA_Albarracin_2008_math.csv
+
+### FA_Nosek_2002_Art.csv
+
+*Explanation*: This dataset describes for each lab location of study several unidimensionality, factor analysis, and Cronbach's Alpha assumptions tests for study 12 (as stated in the Many Labs 1 Proposal_V1.1) from Many Labs 1 that was checked for reliability and unidimensionality.
+
+*Variables*:
+
+-   Same as FA_Albarracin_2008_math.csv
+
+### FA_Nosek_2002_Math.csv
+
+*Explanation*: This dataset describes for each lab location of study several unidimensionality, factor analysis, and Cronbach's Alpha assumptions tests for study 12 (as stated in the Many Labs 1 Proposal_V1.1) from Many Labs 1 that was checked for reliability and unidimensionality.
+
+*Variables*:
+
+-   Same as FA_Albarracin_2008_math.csv
+
+### FA_Shnabel_2008.csv
+
+*Explanation*: This dataset describes for each lab location of study several unidimensionality, factor analysis, and Cronbach's Alpha assumptions tests for study 7 (as ordered in Table 1.
+in the Many Labs 5 manuscript) from Many Labs 5 that was checked for reliability and unidimensionality.
+
+*Variables*:
+
+-   Same as FA_Albarracin_2008_math.csv
+
+### FA_Vohs_2008.csv
+
+*Explanation*: This dataset describes for each lab location of study several unidimensionality, factor analysis, and Cronbach's Alpha assumptions tests for study 9 (as ordered in Table 1.
+in the Many Labs 5 manuscript) from Many Labs 5 that was checked for reliability and unidimensionality.
+
+*Variables*:
+
+-   Same as FA_Albarracin_2008_math.csv
+
+### FA_Zhong_2006.csv
+
+*Explanation*: This dataset describes for each lab location of study several unidimensionality, factor analysis, and Cronbach's Alpha assumptions tests for study 23 (as stated in the Many Labs 2 protocol) from Many Labs 2 that was checked for reliability and unidimensionality.
+
+*Variables*:
+
+-   Same as FA_Albarracin_2008_math.csv
+
+### measure_reliability_data.csv
+
+*Explanation*: For each measure, the mean of the variables from calculated_reliability_lab_data.csv, and the related g variable.
+Additionally, some data comparing the reported and replicated alpha was added.
+
+*Variables*:
+
+-   **alpha:** Cronbach's alpha calculated for a measure across lab locations as extracted from the Many Labs datasets.
+
+-   **omega.tot:** McDonald's omega for the overarching factor as an estimate of the total reliability of a test calculated for a measure across lab locations as extracted from the Many Labs datasets.
+
+-   **omega.hier:** McDonald's hierarchical omega as the estimate of the general factor saturation of a test (not refered to much in study) calculated for a measure across lab locations as extracted from the Many Labs datasets.
+
+-   **ASE:** Standard error of Cronbach's alpha across lab locations, based on formulas 2 & 3 from @duhachekAlphasStandardError2004a.
 
@@
 
--   **reporting_index:** index of the row in the data_h456.csv dataset that the indexed measure belongs to.
+-   **coded_data_index:** index of the row in the coded_data_original.csv or coded_data_replication.csv dataset that the indexed measure belongs to.
 
@@
 
-### data_H23_avg.csv
+-   **reported_coefficient**: If present, the reported alpha reliability coefficient in the original article for the measure in this row.
 
-*Explanation*: For each measure, the mean of the variables from data_H23.csv, and the related g variable. Additionally, some data comparing the reported and replicated alpha was added.
+-   **coefficient_difference**: The difference between the reported alpha coefficient and the average coefficient calculated from the replication data (negative values indicate that the reported coefficient is lower than the calculated average)
+
+-   **significance_reported_coefficient**: boolean value indicating whether or not the reported_coeffcient value of a measure is outside the 95% percentile of calculated alpha coefficient score of the same measure.
+
+### QMP_ratio_data.csv
+
+Percentage of measures that have a QMP for each of our QMP items and the number of measures for which they are applicable by both original and replication.
+The data is organized by QMP item in rows, and the percentages & number of applicable measures being the variables for both original and replication.
+We also calculated a Phi Coefficient as a correlation between the original QMP and replication QMP being present.
 
@@
 
--   **coefficient_reported**: If present, the reported alpha reliability coefficient in the original article for the measure in this row.
+-   **Practice:** a description of the reporting practice for which we count the percentage of QMPs.
 
--   **coefficient_difference**: The difference between the reported alpha coefficient and the average coefficient calculated from the replication data (negative values indicate that the reported coefficient is lower than the calculated average)
+-   **QMP_percentage_original:** the QMP percentage for a particular measurement information in the original studies.
+This is done by dividing the number of measures for which the relevant measurement information was not available by the total number of measures for which the particular item was applicable.
 
--   **siginificance_reported_coefficient**: boolean value indicating whether or not the coeffcient_reported value of a measure is outside the 95% percentile of calculated alpha coefficient score of the same measure.
+-   **N_applicable_original:** the number of measures in the original studies for which the measurement item is applicable (factor analytic evidence reporting for single-item measures for instance would not be applicable).
 
-### data_H456_original.csv
+-   **QMP_percentage_replication:** the QMP percentage for a particular measurement information in the replication projects.
+This is done by dividing the number of measures for which the relevant measurement information was not available by the total number of measures for which the particular item was applicable.
 
-*Explanation*: Contain all of the data from the coded_data_original_shortened.csv and one more variable indicating whether reliability was reported or not.
+-   **N_applicable_replication:** the number of measures in the replication projects for which the measurement item is applicable (factor analytic evidence reporting for single-item measures for instance would not be applicable).
 
-*Variables*:
-
--   **reliability_reported**: boolean variable indicating whether any response other than nothing or "Not Reported" was given to the **reliability_type** variable.
-
-### data_H456_replication.csv
-
-*Explanation*: Contain all of the data from the coded_data_replications.csv and one more variable indicating whether reliability was reported or not.
-
-*Variables*:
-
--   **reliability_reported**: boolean variable indicating whether any response other than nothing or "Not Reported" was given to the **reliability_type** variable.
-
-### item_number_change_data.csv
-
-*Explanation:* Contains the many_labs_version, rep_org, title, and mod_5_rev variablefrom the coded_data_replication.csv dataset of the observations where the mod_5_rev variable was TRUE (meaning that the measure's number of items and/or number of response options was modified from original to replication.
-Additionally, two variables were added to determine whether for that measure the number of items were decreased from original to replication.
-
-*Variables*:
-
--   **context:** A description of the change in item numbers from original to replication. NA means that for that measure the number of items was not changed.
-
--   **direction:** A factor indicating whether the number of items was decreased, increased, or no change (NA) from original to replication.
-
-### plot_23_data_alpha.csv
-
-*Explanation*: Contain all of the data from the data_h23.csv that had a calculated alpha level larger than 0.
-Additionally, it contains a column of alpha scores averaged across many lab locations for each article.
-Finally, the replication_success was changed to a boolean variable, returning TRUE in case it was coded as "Yes", and as FALSE otherwise.
-
-### plot_23_data_omega.csv
-
-*Explanation*: Contain all of the data from the data_h3_multiple.csv.
-Additionally, it contains a column of omega scores averaged across many lab locations for each article.
-Finally, the replication_success was changed to a boolean variable, returning TRUE in case it was coded as "Yes", and as FALSE otherwise.
-
-### plot_456_data.csv
-
-*Explanation*: Contains four variables for each QMP type for all the replication studies and original articles that were coded on QMPs.
-The rows are ordered to have the original studies first and then the replications, then they are ordered based on QMP type from Definition to Operationalization to Selection to Quantification to Modification to Total.
-Within each type the QMPs are ordering matches the order of the studies/articles as in the data_h456_replications.csv and data_h456_original.csv.
-
-*Variables:*
-
--   **QMP_ratio:** float number between 0 and 1 that indicates the QMP ratio based on the initial coding protocol for that QMP type for that study/article.
-
--   **QMP_ratio_1:** transformed version of the QMP_ratio column, where QMPs for all original articles have a 1 added to their ratio.
-This was done for the sake of making the figure possible in ggplot as it is right now.
-
--   **QMP_type:** factor that indicates the QMP type the QMP ratio belongs to (Definition, Operationalization, Selection, Quantification, or Modification).
-
--   **QMP_ratio_REV:** float number between 0 and 1 that indicates the QMP ratio based on the revised coding protocol for that QMP type for that study/article.
-
--   **RepOrg:** factor that indicates whether the QMP ratio belongs to a replication or an original article.
-
--   **QMP_ratio_1_REV:** transformed version of the QMP_ratio_REV column, where QMPs for all original articles have a 1 added to their ratio.
-This was done for the sake of making the figure possible in ggplot as it is right now.
-
-### plot_46_data.csv
-
-*Explanation*: Contains four variables for each QMP type (including total) for both replication studies and original articles combined per row.
-The QMP_ratio column indicates the initial QMP ratio for the specific QMP type for that original article.
-The QMP_type column indicates the specific QMP type the QMP_ratio column belongs to.
-The QMP_Rep_ratio column indicates the initial QMP ratio for the specific QMP type for that replication study.
-The QMP_Rep_type column indicates the specific QMP type the QMP_Rep_ratio column belongs to.
-The rows are ordered so that within each QMP type it matches the order of the studies/articles as in the data_h456_replications.csv and data_h456_original.csv.
-
-### plot_46_data_REV.csv
-
-*Explanation*: Contains four variables for each QMP type (including total) for both replication studies and original articles combined per row.
-The QMP_ratio column indicates the revised QMP ratio for the specific QMP type for that original article.
-The QMP_type column indicates the specific QMP type the QMP_ratio column belongs to.
-The QMP_Rep_ratio column indicates the revised QMP ratio for the specific QMP type for that replication study.
-The QMP_Rep_type column indicates the specific QMP type the QMP_Rep_ratio column belongs to.
-The rows are ordered so that within each QMP type it matches the order of the studies/articles as in the coded_data_replications.csv and coded_data_original_shortened.csv.
+-   **Phi:** the phi coefficient is a correlation between the original QMP percentage and replication QMP percentage.

### 2025-08-25 Scripts/Manuscript/manuscript.Rmd
adjusted the supplementary materials to reflect the new project structure, fixed references, and removed depricated files.

@@
 
-# loading script with helper functions
-# source(file = "../helper_functions.R") !!!needs to still be created
-
 # Code below loads all data. The raw data was loaded within the 'prepare_data.R script.
@@
 
-\renewcommand{\arraystretch}{0.7}
-
-<!-- reducing the line spacing within tables -->
-
-\renewcommand{\topfraction}{.8}
-
-<!-- max fraction of page for floats at top -->
-
-\renewcommand{\bottomfraction}{.8}
-
-<!-- max fraction of page for floats at bottom -->
-
-\renewcommand{\textfraction}{.15}
-
-<!-- min fraction of page for text -->
-
-\renewcommand{\floatpagefraction}{.8}
-
-<!-- min fraction of page that should have floats .66 -->
+\renewcommand{\arraystretch}{0.7} <!-- reducing the line spacing within tables -->
+
+\renewcommand{\topfraction}{.8} <!-- max fraction of page for floats at top -->
+
+\renewcommand{\bottomfraction}{.8} <!-- max fraction of page for floats at bottom -->
+
+\renewcommand{\textfraction}{.15} <!-- min fraction of page for text -->
+
+\renewcommand{\floatpagefraction}{.8} <!-- min fraction of page that should have floats .66 -->
 
@@
 }
-
 ```
@@
 When we validate a measure using psychometrics, we evaluate it mainly on two aspects: construct validity & reliability.
-Construct validity refers to whether the variance in the measured item scores between participants can be attributed to variance in the unobserved constructs of interest between participants (Cronbach & Meehl, 1955; Vazire et al., 2022).
-Whereas reliability refers to how consistent a participant's responses on a measurement are [@nunnally1978overview; @mellenbergh2011conceptual].
-Reliability is part of the validation of a measure because an unreliable measure cannot consistently capture a construct through the items, and therefore cannot be assumed to properly capture the construct of interest (Crutzen & Ygram Peters, 2015).
+Construct validity refers to whether the variance in the measured item scores between participants can be attributed to variance in the unobserved constructs of interest between participants [@cronbachConstructValidityPsychological1955; @vazireCredibilityReplicabilityImproving2022].
+Whereas reliability refers to how consistent a participant's responses on a measurement are [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011].
+Reliability is part of the validation of a measure because an unreliable measure cannot consistently capture a construct through the items, and therefore cannot be assumed to properly capture the construct of interest [@crutzenScaleQualityAlpha2017b].
 Suppose we have a measure and we want it to measure general intelligence, and we want to validate this as a measure of general intelligence.
@@
 However, even in this scenario we cannot be certain that the second factor relates to mathematical intelligence and not for example abstract thinking, other types of validity checks as well as theoretical underpinnings will be necessary.
-Additionally, the factor relations may not be stable for this measure in other contexts and implementations, a concept known as measurement invariance (Horn et al., 1983; Cheung & Rebecca, 2012).
+Additionally, the factor relations may not be stable for this measure in other contexts and implementations, a concept known as measurement invariance [@hornPracticalTheoreticalGuide1992; @cheungDirectComparisonApproach2012].
 
 Reliability gives us an indication of how much our measure captures the signal of our measured variables over noise.
-Psychometrics offers various ways to assess reliability empirically [@nunnally1978overview; @mellenbergh2011conceptual].
+Psychometrics offers various ways to assess reliability empirically [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011].
 For example, we can compare scores on multiple equivalent forms of the test, between multiple different raters, or between multiple different timepoints of the same test.
 Still, the most common way to assess reliability is through an indication of consistency within the measure itself, and the most common among these indicators is the Cronbach's Alpha coefficient.
-The Cronbach's Alpha coefficient is defined as “the average of all the possible split-half coefficients for a given test” (Cronbach, 1951).
+The Cronbach's Alpha coefficient is defined as “the average of all the possible split-half coefficients for a given test” [@cronbachCoefficientAlphaInternal1951].
 Here split-half coefficients being the correlation between two halves of the same test.
@@
 Furthermore, because Cronbach's alpha is proportional to the total variance in the target variable in the sample, it is an indicator of reliability of a measurement, and not the measure itself.
-In spite of this many researchers report and interpret Cronbach's Alpha as such (Cortina, 1993; Schmitt, 1996).
+In spite of this many researchers report and interpret Cronbach's Alpha as such [@cortinaWhatCoefficientAlpha1993; @schmittUsesAbusesCoefficient1996].
 
@@
 However, even in the latter case factor analysis does not converge with low sample sizes.
-Furthermore, if we want to know not just the reliability and validity of one measurement but for the measure across multiple contexts, we need to conduct multiple studies with approximately 400 people per group to detect meaningful effects (Meade & Bauer, 2007; French & Finch, 2016; Koziol & Bovaird, 2018).
-However, what we observe in the literature is that most measures are reused once or never (THE NOT HUSSEY PAPER ABOUT TOOTHBRUSH MEASURES; also the other Hussey paper with the blocks).
-Finally, \@shaw2020measurement checked the factor structure and reliability of measures used in the Many Labs 2 replication project [@klein2018many] on the available data, the results.
+Furthermore, if we want to know not just the reliability and validity of one measurement but for the measure across multiple contexts, we need to conduct multiple studies with generally even larger sample sizes per group to detect meaningful effects [@meadePowerPrecisionConfirmatory2007; @frenchMeasurementInvarianceTechniques2016; @koziolImpactModelParameterization2018].
+However, what we observe in the literature is that most measures are reused once or never [@elsonPsychologicalMeasuresArent2023; @anvariFragmentedFieldConstruct2025; @anvariDefragmentingPsychology2025].
+Finally, @maireadshawMeasurementPracticesLargescale2020 checked the factor structure and reliability of measures used in the Many Labs 2 replication project [@kleinManyLabs22018b] on the available data, the results.
 They observed that for none of the scales they assessed, a factor structure congruent with the use of the scales met all of their evaluation criteria, and reliability was rarely consistently above an acceptable threshold.
@@
 As illustrated in the previous section, validating measurement is a complex but essential part of doing psychological research.
-Yet the scientific community has not fully stepped up to this challenge (FLAKE & FRIED 2020).
-A large number of measures used in the psychological literature lack information on the validity and reliability of the measure (Hogan & Agnello, 2004; Flake et al., 2017; Flake et al., 2022).
-
-Questionable Measurement Practices (QMPs) are practices that raise doubts about a measurement’s validity [@flake2020measurement] and have been coined as a term analogous to Questionable Research Practices [QRPs; @simmons2011false; @john2012measuring; @wicherts2016degrees].
-QMPs range from lack of transparency in the reporting of the measure and unclear motivation in choice of measure to poor justification for modifications of a measure and procedure of an existing measure [@flake2020measurement].
-@flake2022construct documented QMPs among 100 replications and their respective original articles from the Reproduciiblity Project Psychology [@osc2015estimating].
+Yet the scientific community has not fully stepped up to this challenge [@flakeMeasurementSchmeasurementQuestionable2020].
+A large number of measures used in the psychological literature lack information on the validity and reliability of the measure [@hoganEmpiricalStudyReporting2004; @flakeConstructValidationSocial2017; @flakeConstructValidityValidity2022].
+
+Questionable Measurement Practices (QMPs) are practices that raise doubts about a measurement’s validity [@flakeMeasurementSchmeasurementQuestionable2020] and have been coined as a term analogous to Questionable Research Practices [QRPs; @simmonsFalsePositivePsychologyUndisclosed2011a; @johnMeasuringPrevalenceQuestionable2012a; @wichertsDegreesFreedomPlanning2016a].
+QMPs range from lack of transparency in the reporting of the measure and unclear motivation in choice of measure to poor justification for modifications of a measure and procedure of an existing measure [@flakeMeasurementSchmeasurementQuestionable2020].
+@flakeConstructValidityValidity2022 documented QMPs among 100 replications and their respective original articles from the Reproduciblity Project Psychology [@opensciencecollaborationEstimatingReproducibilityPsychological2015].
 They coded the number of measures, the number of items in the measure, and the information that was reported describing the measure and justifying its use.
@@
 But reporting of reliability and validity evidence is not only low, but may also be biased as well.
-!!!HUSSEY et al., 2023/2025!!!
-observed a disproportional amount of Cronbach's Alpha values at the common acceptably reliable threshold value of .70, and low reporting just below .70.
+@husseyAberrantAbundanceCronbachs2023 observed a disproportional amount of Cronbach's Alpha values at the common acceptably reliable threshold value of .70, and low reporting just below .70.
 Thus the lack of reported measurement evidence may on occasion be hiding psychometric skeletons in the closet.
 
-Further findings by @flake2022construct and others [@flake2017construct; @shaw2020measurement] also show that QMPs not only limit the reported validity of a measurement in a study, the lack of information also creates challenges for replicating researchers.
-Basic content descriptions such as the number of items, the response format, the scoring of the scale were irregular (exact numbers).
+Further findings by @flakeConstructValidityValidity2022 and others [@flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020] also show that QMPs not only limit the reported validity of a measurement in a study, the lack of information also creates challenges for replicating researchers.
+Basic content descriptions such as the number of items, the response format, the scoring of the scale were irregular (!!!exact numbers!!!).
 If it is not clear what items were used, how they were scored, and how they were administered, then it is challenging to reconstruct the measurement for a replication study.
@@
 Besides this, our study also functions as a conceptual replication of earlier research looking at reporting practices and measurement validation using different questions and analyses on a different set of replications and original research.
-While the theory underlying the measurement is important to evaluate how the content of the measure fits to the constructs of interest, because evaluating the theory of a measurement requires domain specific knowledge for each measure we do not address it in this study, we refer interested readers to articles discussing theory in measurement elsewhere (Gehlbach & Brinkworth, 2011; Humphry, 2017; Borgstede and Eggert, 2023; Hasselman, 2023).
-
-# Disclosures ???Where & How???
+While the theory underlying the measurement is important to evaluate how the content of the measure fits to the constructs of interest, because evaluating the theory of a measurement requires domain specific knowledge for each measure we do not address it in this study, we refer interested readers to articles discussing theory in measurement elsewhere [@gehlbachMeasureTwiceCut2011; @humphryPsychologicalMeasurementTheory2017; @borgstedeMeaningfulMeasurementRequires2023; @hasselmanGoingSquaresTheorybased2023].
+
+# Disclosures
+
+## Preregistration
+We preregistered data collection, coding protocol, and planned analyses: <https://osf.io/jgxyu>.
+We deviated from our coding protocol as is explained further in the text.
+Our pre-registered analyses have been move to the [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd) in favor of focusing on the descriptive results.
+
+## Data, Materials, and Online Resources
+TThis manuscript was created in RStudio [*v`r rstudioapi::versionInfo()$version`*\; @R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [*v`r getNamespaceVersion("worcs")[[1]]`*\; @R-worcs] to ensure reproducibility and transparency.
+All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> and <https://osf.io/9r8yt/> (DOI: 10.17605/OSF.IO/9R8YT).
+
+## Reporting
+We report how we determined all data exclusions, all manipulations, and all measures in the study. Our sample size was predetermined by the number of studies in the Many Labs projects.
+
+## Ethical Approval
+This research was approved by the Tilburg University School of Social and Behavioral Sciences Ethical Review Board (nr. TSB_TP_REMA06).
 
@@
 The data consists of three main sources: replication datasets, replication protocols, and original study articles.
-We retrieved the data of Many Labs 1, 2, 3, & 5 [@klein2014investigating; @ebersole2016many; @klein2018many; @ebersole2020many] from their respective OSF pages.
+We retrieved the data of Many Labs 1, 2, 3, & 5 [@kleinInvestigatingVariationReplicability2014a; @ebersoleManyLabs32016; @kleinManyLabs22018b; @ebersoleManyLabs52020d] from their respective OSF pages.
 Many Labs 4 [@klein2022many] was excluded, as there was no publicly available replication protocol.
-Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures.
+Additionally, the replication of [@crosbyWhereWeLook2008a] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures.
 
@@
 However, no coding or analysis of either of them had taken place before the analyses were preregistered.
-Further details on the search strategy can be found in the coding protocol information file in the supplementary materials.
+Further details on the search strategy can be found in the [coding protocol information file](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) in the supplementary materials.
 
@@
 ### Saving to Intermediate Data Folder
-### !!!! OMIT INTERMEDIATE DATA & KEEP FUNCTION THAT REMOVE ALL NON RAW DATA 
-### WHEN LOADING THE DATA IN!!!!
 saving_to_intermediate_data(data_1.3_clean)
@@
 The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of the replication of an original study.
-These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the data retrieval information XXX supplementary document; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd>).
+These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd>).
 
@@
 Similarly, we coded if any psychometric construct validity evidence, such as a factor analysis, was presented for the measure.
-We additionally included twenty items that were based on the QMP table presented in Flake & Fried (2020).
+We additionally included twenty items that were based on the QMP table presented in @flakeMeasurementSchmeasurementQuestionable2020.
 For each of these items we a piece information we would want to see reported with regards to the measurement was described.
 If the information was clearly reported we coded the item as true; false if not or not clear enough; or not applicable if not relevant for that measure (e.g., reporting results from a factor analysis for single-item measures).
-Example items can be seen in Table 1.
+Example items can be seen in Table \@ref(tab:QMPCodingInfoTable).
 
@@
 The analyses, tables, and figures presented in this article are all based on the revised coding protocol.
-The results of the equivalent analyses based on QMPs obtained with our initial protocol can be found in Supplementary Analyses D.
+The equivalent QMP descriptives obtained with the initial protocol can be found in [Supplementary Analyses B](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_ratio_table.rmd).
 
 We initially intended to form a QMP index using these QMP items and perform regression analyses using this index, but this index could not be validated properly and its results would be misleading to present here.
-A more detailed explanation of what was omitted and why, as well as the results from the preregistered analyses themselves can be found in Supplementary Materials XXX.
+A more detailed explanation of what was omitted and why, as well as the results from the preregistered analyses themselves can be found in [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd).
 The items are currently used as individual descriptives on the reporting practices in our sample.
@@
 We calculated reliability for each measure from the replication datasets with suitable data for each lab the measure was used in.
-We calculated both Cronbach’s alpha, as well as its standard error using formulas 2 & 3 from Duhachek and Lacobucci (2004) to calculate the standard error in the meta-analysis.
-Then we entered these two values into a meta-analysis of the reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analysis (Botella & Suero, 2012; López-Ibáñez et al., 2024; Vacha-Haase, 1998).
+We calculated both Cronbach’s alpha, as well as its standard error using formulas 2 & 3 from @duhachekAlphasStandardError2004a to calculate the standard error in the meta-analysis.
+Then we entered these two values into a meta-analysis of the reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analysis [@botellaManagingHeterogeneityVariance2012; @lopez-ibanezReliabilityGeneralizationMetaanalysis2024; @vacha-haaseReliabilityGeneralizationExploring1998].
 Using RG Meta-Analysis we quantified the degree of true variation (or heterogeneity) in reliability coefficients across lab locations.
-We performed the RG Meta-Analysis using the rma function from the metafor R package (v4.4-0; Viechtbauer, 2010) and default settings.
-We evaluated the heterogeneity using the tau statistic and the Cochran's Q-test (CITATION Cochran 1954).
-These indicators have received criticism as indicators of heterogeneity, especially when within study sample sizes are small and power to detect heterogeneity is low (Hoaglin 2015; Pereira et al.
-2010).
-Therefore, we also present the prediction interval and suggest that the heterogeneity results should be viewed with a critical eye (Borenstein 2024 CITATION).
+We performed the RG Meta-Analysis using the rma function from the metafor R package [*v`r getNamespaceVersion("metafor")[[1]]`*; @R-metafor] and default settings.
+We evaluated the heterogeneity using the tau statistic and the Cochran's Q-test [@cochranCombinationEstimatesDifferent1954].
+These indicators have received criticism as indicators of heterogeneity, especially when within study sample sizes are small and power to detect heterogeneity is low [@hoaglinMisunderstandingsCochransTest2016; @pereiraCriticalInterpretationCochrans2010].
+Therefore, we also present the prediction interval and suggest that the heterogeneity results should be viewed with a critical eye [@borensteinAvoidingCommonMistakes2024].
 We implemented no correction for bias, because the Many Labs replications were not at risk of publication bias.
@@
 Furthermore, we were able to calculate the standard error of alpha to be used in the RG meta-analysis.
-We additionally estimated McDonald’s Omega for each lab from the same set of replications as for Cronbach's Alpha, since it has been argued to be a more informative measure of reliability than Cronbach's Alpha, while also simultaneously providing some validity evidence [@crutzen2017scale; @deng2017testing].
+We additionally estimated McDonald’s Omega for each lab from the same set of replications as for Cronbach's Alpha, since it has been argued to be a more informative measure of reliability than Cronbach's Alpha, while also simultaneously providing some validity evidence [@crutzenScaleQualityAlpha2017b; @dengTestingDifferenceReliability2017].
 McDonald’s Omega was calculated using the omega function in the *psych* R package [*v`r getNamespaceVersion("psych")[[1]]`*; @R-psych].
@@
 If only the single factor has an eigenvalue that is significantly higher than the eigenvalue when the data matrix is random, the test is passed.
-We chose a combination of these two tests, as the RMSEA is known to be biased for models with small degrees of freedom (Kenny et al., 2015), while the parallel analysis may be less suited if a two or more factor solution would also fit the sample item data.
+We chose a combination of these two tests, as the RMSEA is known to be biased for models with small degrees of freedom [@kennyPerformanceRMSEAModels2015], while the parallel analysis may be less suited if a two or more factor solution would also fit the sample item data.
 
@@
 The average calculated Cronbach’s alpha coefficient across individual replications was `r apa_num(mean(calculated_reliability_lab_data$alpha))` with a standard deviation of `r apa_num(sd(calculated_reliability_lab_data$alpha))`.
-Figure 2 displays the distributions of the calculated Cronbach’s Alpha scores from each lab for each measure, separated by successful and unsuccessful replication, based on the meta-analytic p-value (alpha \< .05) retrieved from the Many Labs reports.
+Figure \@ref(fig:PlotAlphaDistributions) displays the distributions of the calculated Cronbach’s Alpha scores from each lab for each measure, separated by successful and unsuccessful replication, based on the meta-analytic p-value (alpha \< .05) retrieved from the Many Labs reports.
 
@@
 
-```{r plot_alpha_distributions, warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients calculated for the responses on a measure at each lab location, across the nineteen measures for which raw data was available from which Cronbach’s alpha coefficients could be calculated.
+```{r PlotAlphaDistributions, warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients calculated for the responses on a measure at each lab location, across the nineteen measures for which raw data was available from which Cronbach’s alpha coefficients could be calculated.
 Cronbach's alpha values that fell below 0 were excluded.
@@
 The CFA failed to converge for `r apa_num((sum(is.na(unidimensionality_graph_data$RMSEA)) / nrow(unidimensionality_graph_data)) * 100)`% of labs.
-In the case of the De Fruyt et al.
-(2000) measure all labs failed to converge.
+In the case of the @defruytCloningersPsychobiologicalModel2000 measure all labs failed to converge.
 Convergence in the other cases was the result of either the severe misfit of our factor models or a lack of sample size to stably estimate these models.
@@
 
-```{r Plot1Factor fig.cap = "Distributions of calculated RMSEA of a single-factor model fit calculated for the responses on a measure at each lab location, across the nineteen measures for which raw data was available on which a factor model could be fitted.
+```{r Plot1Factor, fig.cap = "Distributions of calculated RMSEA of a single-factor model fit calculated for the responses on a measure at each lab location, across the nineteen measures for which raw data was available on which a factor model could be fitted.
 The red horizontal line separate the replicated from the non-repicated measures.
@@
 While generally QMPs were not found for admin format and procedure in the replications (format: `r qmp_ratio_data$QMP_percentage_replication[11]`%; procedure: `r qmp_ratio_data$QMP_percentage_replication[12]`%), they did occur for original measures (format: `r qmp_ratio_data$QMP_percentage_original[11]`%; procedure: `r qmp_ratio_data$QMP_percentage_original[12]`%).
-In general, we observed that measurement was modified in some way from original to replication for `r sum(coded_data_replications$mod_check == "True") / nrow(coded_data_replications)`% of measures, and it was unclear whether modification occured for ``` r``sum(coded_data_replications$mod_check == "None Reported") / nrow(coded_data_replications) ```%.
+In general, we observed that measurement was modified in some way from original to replication for `r sum(coded_data_replications$mod_check == "True") / nrow(coded_data_replications)`% of measures, and it was unclear whether modification occured for `r sum(coded_data_replications$mod_check == "None Reported") / nrow(coded_data_replications)`%.
 
@@
 
-In line with existing research we found that for the majority of the measures in original and replication studies no reliability coefficient was reported, and psychometric validity evidence was even less common Beckman et al., 2004; Barry et al.
-2014; Flake, Pek, & Hehman, 2017; Shaw et al., 2020; Flake et al., 2022).
+In line with existing research we found that for the majority of the measures in original and replication studies no reliability coefficient was reported, and psychometric validity evidence was even less common [@beckmanHowReliableAre2004; @barryValidityReliabilityReporting2014; @flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020; @flakeConstructValidityValidity2022].
 Some part of this is due to around half of the measures in original and replication studies being single item measures.
-While it is possible to check the reliability and validity of single item measures, these methods often require multiple measures or studies to be able to cross-validate the measure with (Leppink and Pérez-Fuster, 2017; Sarstedt, 2016).
+While it is possible to check the reliability and validity of single item measures, these methods often require multiple measures or studies to be able to cross-validate the measure with [@leppinkWeNeedMore2017; @sarstedtSelectingSingleItems2016].
 Another factor may be observed in the fact that we observed that replications generally reported less reliability and psychometric validity evidence.
@@
 We also observed at when measures which came with a reported Cronbach's Alpha in the original study, their average Cronbach's Alpha observed among the replications were all relatively high.
-This aligns with existing research indicating bias in reported Cronbach's Alpha values, with an excess of reported values at the common acceptably reliable threshold value of .70, and low reporting just below .70 (Hussey et al.
-2023/2025).
+This aligns with existing research indicating bias in reported Cronbach's Alpha values, with an excess of reported values at the common acceptably reliable threshold value of .70, and low reporting just below .70 [@husseyAberrantAbundanceCronbachs2023].
 Thus authors may be less inclined to report reliabilities that fall below an acceptable threshold.
@@
 Reporting standards for measurement reporting are not broadly applied, and we observed this also when we looked at the information needed to reconstruct a measure for reuse.
-Similar to Flake et al., 2022, we observed that QMPs were not infrequent.
-In particular, like Flake et al., 2022, we observed that original research undereported information needed to reconstruct the measurement In original research the administration format and procedure for each was not properly described for around a third of the applicable measures, the number of items and response options for each around an eight, and how the index was calculated, how the items were recoded and example items were presented for each a little under half.
+Similar to @flakeConstructValidityValidity2022, we observed that QMPs were not infrequent.
+In particular, like @flakeConstructValidityValidity2022, we observed that original research underreported information needed to reconstruct the measurement In original research the administration format and procedure for each was not properly described for around a third of the applicable measures, the number of items and response options for each around an eight, and how the index was calculated, how the items were recoded and example items were presented for each a little under half.
 We also found that about two-thirds of the measurements were modified between original and replication, and specific modifications were rarely validated or justified.
 This raises some questions around the label direct replication.
-For example, the conscientiousness measure used for the replication of De Fruyt et al.
-(2000) was reduced from original NEO-PI-R 30-item measure to a two-item measure.
+For example, the conscientiousness measure used for the replication of @defruytCloningersPsychobiologicalModel2000 was reduced from original NEO-PI-R 30-item measure to a two-item measure.
 It is highly unlikely that a measure with such a significant change would have a comparable validity and reliability to the original, and we did unsurprisingly observe convergence issues with validity as well as low reliability for this measure.
 
-One notable difference to Flake et al., 2022 is that replications did on average have less QMPs than original research.
+One notable difference to @flakeConstructValidityValidity2022 is that replications did on average have less QMPs than original research.
 We believe that this is in part due to the structured way in which the Many Labs protocols were written up.
@@
 There are three reasons why we believe protocols and articles remain mostly comparable.
-Firstly, articles are often also restricted in the amount of space they have available to devote to measurement (Gardiner, 2019; maybe also some more???).
+Firstly, articles are often also restricted in the amount of space they have available to devote to measurement [@gardinerEditorialMethodsPapers2019; @zogmaisterAssessingTransparencyMethods2024].
 Second, in the revised protocol some QMP items, such as whether example items were reported or not, also allowed for reporting this information in supplementary materials to count as good practice.
@@
 Data from original studies could have been used to recalculate reliability and validity indicators from to compare with the replication results.
-However, it is unlikely that a substantial number would have shared their data (many were conducted before the OSF and other Open Science innitiatives were launched).
-This is likely different for more recent research (Hardwicke et al., 2022; Hamilton et al., 2023).
+However, it is unlikely that a substantial number would have shared their data (many were conducted before the OSF and other Open Science initiatives were launched).
+This is likely different for more recent research [@hardwickeEstimatingPrevalenceTransparency2022; @hamiltonPrevalencePredictorsData2023a].
 Including replications of recent research could help resolve some of the sample size issues for our tests.
@@
 
-The two main issues we believe that should be addressed are: the prevalence of using unvalidated measurement, and the lack of transparency surrounding measurement reporting.
+The two main issues we believe that should be addressed are: the prevalence of using non-validated measurement, and the lack of transparency surrounding measurement reporting.
 Unfortunately, there are no easy solutions to fix these issues.
@@
 We found that reporting reliability and validity information was the exception rather than the rule, and even basic information such as how many items were in the measure was not always present.
-The AERA, APA, & NCME 2014 guidelines exist to guide researchers in the creation and validation of scales, but are not intended as general measurement reporting guidelines.
-Similarly, the APA guidelines (CITATION!!!) only briefly address reliability and validity information but say little on other measurement reporting.
-While statistical reporting standards and guidelines have proliferated, even resulting in official reccomendations from the ASA (???CITE???), a high-profile push for measurement reporting standards is lacking.
+The @americaneducationalresearchassociationStandardsEducationalPsychological2014 guidelines exist to guide researchers in the creation and validation of scales, but are not intended as general measurement reporting guidelines.
+Similarly, the APA guidelines (???CITE???) only briefly address reliability and validity information but say little on other measurement reporting.
+While statistical reporting standards and guidelines have proliferated, even resulting in official recommendations from the ASA [@wassersteinASAStatementPValues2016], a high-profile push for measurement reporting standards is lacking.
 We believe that measurement reporting standards deserve to be highlighted as much as statistical result reporting,.
@@
 Transparent reporting takes care of the first step.
-For the second step, Elson et al.
-2023 have suggested journals to implement the Standardisation Of BEhavior Research (SOBER) guidelines to specifically address issues of flexibility and norming in measurement.
-Furthermore, they propose an open repository of measurement protocols to facilitate the discovery of measures and sbuilding an evidence base.
+For the second step, @elsonPsychologicalMeasuresArent2023 have suggested journals to implement the Standardisation Of BEhavior Research (SOBER) guidelines to specifically address issues of flexibility and norming in measurement.
+Furthermore, they propose an open repository of measurement protocols to facilitate the discovery of measures and building an evidence base.
 For the third and fourth step, the scientific community needs to analyse the validity and reliability of all uses of the measure such that they can be fairly compared to each other.
@@
 Furthermore, researchers should report and evaluate our measures using more informative indicators.
-Cronbach's Alpha on its own gives only limited information the quality of a scale, and comes with strong assumptions (Cortina, 1993; SIJTSMA CITATION).
+Cronbach's Alpha on its own gives only limited information the quality of a scale, and comes with strong assumptions [@cortinaWhatCoefficientAlpha1993; @sijtsmaUseMisuseVery2009].
 Factor analytical evidence and McDonald's Omega are more informative indicators that should be presented in favor of or in tandem with Cronbach's Alpha.

### 2025-08-25 SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd
adjusted the supplementary materials to reflect the new project structure, fixed references, and removed depricated files.

@@
 ## Item origin & modifications
-Eleven out of twenty of the QMP variables used to calculate the QMP ratio have an equivalent in the coding key of @flake2022construct.
-The remaining nine were altered from the coding key to better fit the QMP counting operationalization.
+Eleven out of twenty of the QMP variables used to calculate the QMP ratio have an equivalent in the coding key of @flakeConstructValidityValidity2022 The remaining nine were altered from the coding key to better fit the QMP counting operationalization.
 Because QMPs were aggregated they would need to have equivalent weighting in the importance of the overall QMP judgement of the protocol or article being evaluated.
 
-All of the newly created or modified items were based on the definitions of the QMP categories and their criteria as specified in @flake2020measurement.
-The information to report for each of the categories as presented in Table 1 in @flake2020measurement were used to determine what information there should be questions about in the protocol.
+All of the newly created or modified items were based on the definitions of the QMP categories and their criteria as specified in @flakeMeasurementSchmeasurementQuestionable2020 The information to report for each of the categories as presented in Table 1 in @flakeMeasurementSchmeasurementQuestionable2020 were used to determine what information there should be questions about in the protocol.
 However, feasibility of coding the information was also taken into account, and whether a lack of information could clearly be labelled as a QMP.
 
-Two of the qualitative items have an equivalent in the coding key of Variables related to the specific measurement scaling and purpose in the paper, were omitted from the analyses of this study as they were deemed neither relevant for the analyses of this study, nor necessary in matching this study to the key results of @flake2022construct.
-Questions about more general measurement features such as the number of items and how scores were aggregated were altered from @flake2022construct to be used for obtaining QMP ratios.
+Two of the qualitative items have an equivalent in the coding key of Variables related to the specific measurement scaling and purpose in the paper, were omitted from the analyses of this study as they were deemed neither relevant for the analyses of this study, nor necessary in matching this study to the key results of @flakeConstructValidityValidity2022 Questions about more general measurement features such as the number of items and how scores were aggregated were altered from @flakeConstructValidityValidity2022 to be used for obtaining QMP ratios.
 
-These (qualitative) variables assessed with two having an equivalent in @flake2022construct: the specific version of the measure (if reported); whether and what previous materials were used for the study; what, if any, psychometric evidence beyond reliability score (e.g.
+These (qualitative) variables assessed with two having an equivalent in @flakeConstructValidityValidity2022: the specific version of the measure (if reported); whether and what previous materials were used for the study; what, if any, psychometric evidence beyond reliability score (e.g.
 factor analysis, IRT model, convergent validity) was provided; and whether it was specified or not that the measure was or was not modified.

### 2025-08-25 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd
adjusted the supplementary materials to reflect the new project structure, fixed references, and removed depricated files.

<!-- Supplementary Analyses A -->

```{r additional setup}
### NOTE: also run the setup code in the manuscript
library(lmerTest)
library(betareg)
library(statmod)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(17042023)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r data_prep}
# combine replication and original data 
is_replication <- c(rep(FALSE, 77), rep(TRUE, 77))

combi_org_rep <- rbind(coded_data_original, coded_data_replications)

combi_org_rep <- cbind(combi_org_rep, is_replication)

combi_org_rep$has_reliability <- combi_org_rep$reliability_type != "Not Reported" & combi_org_rep$reliability_type != ""

# function to calculate QMP ratios
calculating <- function(Data){
  QMP_data <- data.frame(def_ratio = rep(NA, 154),
                         op_ratio = rep(NA, 154),
                         sel_ratio = rep(NA, 154),
                         quant_ratio = rep(NA, 154),
                         mod_ratio = rep(NA, 154),
                         QMP_ratio = rep(NA, 154),
                         op_REV_ratio = rep(NA, 154),
                         sel_REV_ratio = rep(NA, 154),
                         quant_REV_ratio = rep(NA, 154),
                         mod_REV_ratio = rep(NA, 154),
                         QMP_REV_ratio = rep(NA, 154))

  def_count <- as.numeric(Data$def_1)
  def_count[is.na(def_count)] <- 0
  def_total <- as.numeric(!is.na(Data$def_1))
  QMP_data$def_ratio <- 1 - round(def_count / def_total, 4) 
  QMP_data$def_ratio[is.na(Data$def_ratio)] <- 0

  op_count <- rowSums(Data[16:20], na.rm = TRUE)
  op_total <- rowSums(!is.na(Data[16:20]))
  QMP_data$op_ratio <- 1 - round(op_count / op_total, 4)

  sel_count <- rowSums(Data[23:26], na.rm = TRUE)
  sel_total <- rowSums(!is.na(Data[23:26]))
  QMP_data$sel_ratio <- 1 - round(sel_count / sel_total, 4)

  quant_count <- rowSums(Data[29:32], na.rm = TRUE)
  quant_total <- rowSums(!is.na(Data[29:32]))
  QMP_data$quant_ratio <- 1 - round(quant_count / quant_total, 4)

  mod_count <- rowSums(Data[34:39], na.rm = TRUE)
  mod_total <- rowSums(!is.na(Data[34:39]))
  QMP_data$mod_ratio <- 1 - round(mod_count / mod_total, 4)

  MP_total <- def_total + op_total + sel_total + quant_total + mod_total
  MP_count <- def_count + op_count + sel_count + quant_count + mod_count
  QMP_data$QMP_ratio <- 1 - round(MP_count / MP_total, 4)

  op_REV_count <- rowSums(Data[c(18,19,41,42,43)], na.rm = TRUE)
  op_REV_total <- rowSums(!is.na(Data[c(18,19,41,42,43)]))
  QMP_data$op_REV_ratio <- 1 - round(op_REV_count / op_REV_total, 4)

  sel_REV_count <- rowSums(Data[c(24,26,44,45)], na.rm = TRUE)
  sel_REV_total <- rowSums(!is.na(Data[c(24,26,44,45)]))
  QMP_data$sel_REV_ratio <- 1 - round(sel_REV_count / sel_REV_total, 4)

  quant_REV_count <- rowSums(Data[c(32,48,49,50)], na.rm = TRUE)
  quant_REV_total <- rowSums(!is.na(Data[c(32,48,49,50)]))
  QMP_data$quant_REV_ratio <- 1 - round(quant_REV_count / quant_REV_total, 4)

  mod_REV_count <- rowSums(Data[52:57], na.rm = TRUE)
  mod_REV_total <- rowSums(!is.na(Data[52:57]))
  QMP_data$mod_REV_ratio <- 1 - round(mod_REV_count / mod_REV_total, 4)

  MP_REV_count <- def_count + op_REV_count + sel_REV_count + quant_REV_count + mod_REV_count
  MP_REV_total <- def_total + op_REV_total + sel_REV_total + quant_REV_total + mod_REV_total
  QMP_data$QMP_REV_ratio <- 1 - round(MP_REV_count / MP_REV_total, 4)

  return(QMP_data)
}

# calculating the QMP ratios for each QMP item.
QMP_Ratio_data <- calculating(combi_org_rep)

QMP_Ratio_data <- cbind(QMP_Ratio_data, is_replication)

```

# Supplementary Analyses A: Pre-registration & Exploratory Analyses
This appendix contains two things. First of all the pre-registered exploratory analyses. Additionally, it also includes the revised analyses shared in the pre-print for this article as found in: <https://osf.io/2gau8_v1>.

Every hypothesis test used an alpha significance cutoff of .05. No correction for multiple testing was applied, to avoid inflating type II error rate. The generally small sample size and consequently low power of these analyses meant that a smaller alpha would increase the number of false negatives. On top of that, these analyses were considered as exploratory. In this exploratory context, the rate of discovery of any potential true effects was given more value relative to decreasing any false positives compared to typical confirmatory research. That as a consequence obtaining false positives was more likely has been accepted, as false negatives were deemed more harmful to this study's aims.

Some of these analyses were also conducted after removing the potentially confounding factor of measures for which the number of items were reduced in the replications. These results can be found in [Supplementary Analyses C](Supplementary_item_reduced_measure_analyses.Rmd).

# Initial Analysis Goals & Process and Reasoning of Omission
We initially had planned to explore relations between both measurement reporting and reliability with replication outcome. This involved regression models wherein an outcome - either the replication outcome from the Many Labs replications or our QMP indicator - and a predictor - reliability, our QMP indicator, or whether it is an original study or a replication. The idea of doing this was based on earlier research that has shown that reliability is related to replication success. The reason for this is because lower reliability introduces more noise into our data, which leads to less stable estimates across multiple studies of the same effects, which leads to less replicable effects. We also wanted to check for measurement-based predictors for replicability more broadly, which includes QMPs from the measurement reporting side of things. The reason for doing this was because knowing what predicts replicability can help us understand the various forces that can inhibit replicability and inform us in when and how to choose what to replicate. This last point is something we still explore in the article itself, albeit using descriptive information and more logic-based inferences rather than statistical testing.

The reason we omitted these analyses is largely for two reasons: (1) if we want to model a relationship between two variables, we also need to account for all potentially relevant confounders to get a good estimate; (2) predicting replicability as a goal may not really be all that interesting theoretically or practically. To elaborate on point 1, what we lack in our case is a theoretical model to understand all the various influences on replicability. Without knowing these, we could technically still use reliability as a predictor, but our goal and motivation to check reliability was to test the theoretical relation between reliability and replicability in practice. The "in practice" part becomes difficult however because practice is messy and we have to account for that messiness, but we can't, because we don't know what to account for. Trying to create a model for this or do simulations to figure this out drifts from the main goal of the article: to understand the reporting, reliability, and validity of measurement in original; and addressing confounds to replication success is just simply beyond the article's scope. To elaborate on point 2, while there are some reasons to predict replicability for practical reasons - mostly for deciding which study to replicate. But as we stated in point 1, it is difficult to effectively predict replicability in our study. So then we are left with the potential theoretical interest of predicting replicability. The idea here is that if we want to understand why something may not replicate, then trying to find predictors for replicability should give us an understanding of what makes something replicable or not. But understanding what makes something replicable is missing the goal of why we care for replicability, which to some extent is that we don't care about replicability. What we care about is getting accurate estimates of an effect of interest, or less statistically is we want to have some certainty that our understanding of how much a psychological phenomenon exists - if it exists at all. But if we just look at trying to see how we can get the most replicable effects possible that's easy, we just conduct Stroop-tasks and other basic psychology 101 tests and we can replicate around the clock. Making studies replicable should not be a goal in and of itself, what we desire is to get accurate estimates of a phenomenon of interest.

There is another key element from the first pre-print version of the article and the pre-registration: we developed a QMP index to allow us to test the relation between measurement reporting and replication outcome statistically. The QMP index was essentially the same as the QMP ratio presented in the article, the number of QMP items that were rated as insufficiently reported on divided by the total number of applicable items. There were two differences, one is that we also created QMP ratios per specific QMP category (definition, selection/creation, operationalization, quantification, and modification); second is that we created this QMP ratio as a variable, thus treating our QMP items collectively as an index. Having an index means that it should be validated in some way (a point we make throughout the article too). Now, we did not make a measure of a construct, so construct validity was not a concern of ours. However, an indicator should have some predictive validity, which requires us to validate that that is the case before we actually use the measure. We did not have the means nor the method nor any idea on how to do this within our study in a way that would be appropriate. We can propose that QMPs should predict replciabiltiy and then show that this is the case, but if our analysis itself is to investigate whether this is the case, then we can't treat it as validating our measure, because before doing that analysis there was no guarantee that it should be related, and thus we can't use observing that relationship as evidence that the measure worked as intended.

So, what would we advice future researchers interested in probing relations with replication and/or creating a QMP index. First, we would advise you to only probe relations with replication if you have a practical reason for wanting to predict replicability. If you want to look into this relation for theoretical reasons, we would advise you to switch your goals. Instead, try and focus on understanding what makes for accurate and robust estimates. This is closer to what we are actually interested in, so if there is something we should want to understand on a deeper level, it is this. Doing so would require taking a more meta-analytic approach to your outcomes, as that can give you more undeerstanding of an effect's robustness compared to the overall p-value that we used as an indicator of replication success. Second, if you want to create a predictve index or even just a general useful descriptive rating scale based on reporting practices, such as QMPs, we would advise you to first of all make this its own study (or studies) as this is likely an involved process. Then, you may want to look at measurement quality standards, such as the @americaneducationalresearchassociationStandardsEducationalPsychological2014 guidelines, to get something more substantially theoretical as a background for what you mean with what should be reported about a measure. Finally, make use of existing research on measurement reporting such as this one (you can look at our coding protocol supplements and the revisions we did to understand what problems may be smart to avoid), but also @flakeConstructValidationSocial2017, @maireadshawMeasurementPracticesLargescale2020, and @flakeConstructValidityValidity2022 have done work on this and have openly available materials. While we made use of these materials, in our goal to make a QMP indicator, we regret mostly (1) not deciding on a strong definition of what good measurement reporting should in the end do, as well as (2) an outcome that reflects the impact of good measurement reporting as we defined it.. We therefore decided to leave creating an index behind for this project, but hopefully this information ahs been useful to inform future research.

Below are the results for our pre-registered analyses for those interested. Take all of them with a big grain of salt.

## Hypothesis 1
As a first step it is worth investigating what the state of measurement error is in original and replication research in psychology. Thus, this study investigated the following:

-   RQ1a. What is the degree of score reliability in replications of psychological research?

-   RQ1b. What is the degree of score reliability in original psychological research?

Since direct replications intend to investigate effects in nearly identical scenarios with nearly identical measures as the original study, it is expected that measurement errors are as present in replication research as in original psychological research.

-   H1. No difference is present in the degree of score reliability between replication research and original psychological research.

### Analysis
There were too few reported reliability coefficients, therefore the test for hypothesis 1 was changed from the pre-registration, and we won't try to do that pre-reg analysis because they are simply to few. Thus for testing hypothesis 1, instead of comparing the reported Cronbach's alpha coefficient between original and replication, the total number of reported reliability coefficients were compared instead. This total also included reliability coefficients other than Cronbach's alpha. This comparison was implemented via a chi-square test using the base R stats package [@R-base].

```{r Hypothesis1Model, include = FALSE}
# New H1 test
# A chi square test for difference in N reliability reported for multiple 
# item measures.
H1_test_result <- chisq.test(combi_org_rep$is_replication[combi_org_rep$N_items == "multiple item measure"], combi_org_rep$has_reliability[combi_org_rep$N_items == "multiple item measure"])

```

Reliabilities were found to be more commonly reported in original articles compared to replication protocols ($\chi^{2}$(`r apa_num(H1_test_result$parameter)`) = `r apa_num(H1_test_result$statistic)`, *p* = `r apa_p(H1_test_result$p.value)`). These results are contradictory to hypothesis 1.

## Hypothesis 2
While reliability estimates are generally considered a measure specific feature, this is false. They are context dependent, and as a result the estimates of an effect can differ across contexts [@cho2015cronbach; @pauly2018resampling]. With large enough differences across contexts, the effect estimates between different replication attempts could deviate from each other beyond direct comparison. To investigate this potential problem, the variation in score reliability is assessed for each measure when used in different contexts.

-   RQ2. To what degree do reliability estimates differ within a replication set of the same original study?

Even though reliability estimates are context dependent, sufficient protocol structure can counteract the variance in reliability estimates. It is possible to reduce variability as the result of context using structured protocols, as was done in the Many Labs projects this study analyzed.

-   H2. There is no significant variation in the reliability estimates of replications of the same original study.

### Analysis
Using the lmer function from the lme4 package [@R-lme4], a multilevel null model with the Cronbach's alpha or omega coefficient of a replication as dependent was specified, where the random intercept was grouped by replication set. The formulas for this model, where $alpha_{ij}$ represents the calculated Cronbach's alpha coefficient of a single study at one lab location with $i = 1,..., n_{locations}$ and $j = 1,...,n_{replications}$ look as follows:

```{=tex}
\begin{align}
& Level 1: alpha_{ij} = \beta_{0j} + e_{ij} \qquad\qquad\quad e_{ij} \sim N(0, \sigma_{e}^{2}) (\#eq:level1H2) \\
& Level 2: \beta_{0j} = \gamma_{00} + u_{0j} \qquad\qquad\qquad u_{0j} \sim N(0, \sigma_{u0}^{2}) (\#eq:level2H2) \\
& Mixed: alpha_{ij} = \gamma_{00} + u_{0j} + e_{ij} (\#eq:mixedH2)
\end{align}
```

The purpose of this analysis was to investigate variability in calculated reliability coefficients within and between replication sets.

```{r Hypothesis2Model, include = FALSE}
# intercept only model to check the within and between group variance.
H2_test_result_alpha <- lmer(formula = alpha ~ 1 + (1|g), data = calculated_reliability_lab_data)

# and same analyses for omega
# intercept only model to check the within and between group variance.
H2_test_result_omega <- lmer(formula = omega.tot ~ 1 + (1|g), data = calculated_reliability_lab_data[complete.cases(calculated_reliability_lab_data),])
```

```{r ICCCalculations, include = FALSE}
# alpha
within_group_variance_alpha <- attr(VarCorr(H2_test_result_alpha), "sc")^2
between_group_variance_alpha <- attr(VarCorr(H2_test_result_alpha)$g, "stddev")^2

ICC_alpha <- between_group_variance_alpha / (within_group_variance_alpha + between_group_variance_alpha)

# omega
within_group_variance_omega <- attr(VarCorr(H2_test_result_omega), "sc")^2
between_group_variance_omega <- attr(VarCorr(H2_test_result_omega)$g, "stddev")^2

ICC_omega <- between_group_variance_omega / (within_group_variance_omega + between_group_variance_omega)
```

The between-group and within-group variance for Cronbach's alpha were approximately `r apa_num(between_group_variance_alpha, digits = 3)` and `r apa_num(within_group_variance_alpha, digits = 3)` respectively. The resulting ICC, obtained using formula \@ref(eq:ICC), was approximately `r apa_num(ICC_alpha, digits = 3)`. This suggests that variance was larger between replication sets than within. The same analysis for omega coefficients even showed a relatively larger degree of between group variance (between-group variance `r apa_num(within_group_variance_omega, digits = 3)`, within-group variance `r apa_num(between_group_variance_omega, digits = 3)`, ICC = `r apa_num(ICC_omega, digits = 3)`). Both results are in line with hypothesis 2, although caution in interpreting this result is advised due to the small sample size and the lack of an available inferential test.

## Hypothesis 3
This study investigated the relationship between reliability and replicability, by using data from real life replication projects.

-   RQ3. What is the association between replication study score reliability and replication outcome?

Greater score-reliability means greater consistency in estimation as variance around the estimate of the true effect is decreased. Consequently measures across different occasions, including between original and replication, should also become more consistent [@nunnaly1994assessment]. When original and replication research share consistent result, and as long as the studied effect is true, then on average their statistical conclusions should converge.

-   H3. Score reliability in replication research is positively associated with successful replication of an original finding.

### Analysis
In order to test hypothesis 3, the average calculated Cronbach's alpha level within a replication set is used as a predictor of replication success. Replication success was either set to 1 if it reached meta analytic significance at an alpha of .05 in the same direction as that found in the original study, or 0 otherwise. This test aligns with a logistic regression model. With $i = 1,..., n_{replications}$, $p_{replicated}$ being binomially distributed, and $alpha$ referring to the averaged calculated Cronbach's alpha coefficient, the following regression equation was used to model the relation:

```{=tex}
\begin{equation}
f(replicated_{i}) = \beta_{0} + \beta_{1} alpha_{i} (\#eq:H3Main)
\end{equation}
```
Where:

```{=tex}
\begin{equation}
f(.) = log\frac{p_{replicated}}{1 - p_{replicated}} (\#eq:LogitLink)
\end{equation}
```

```{r Hypothesis3MainTest, include = FALSE}
## The main model to test hypothesis 3, through a logistic regression model.
H3_test_result_main_alpha <- apa_print(glm(formula = replication_success ~ 1 + alpha, 
                                      family = binomial(), data = measure_reliability_data))

# and for omega
H3_test_result_main_omega <- apa_print(glm(formula = replication_success ~ 1 + 
                                     omega.tot, family = binomial(), 
                                     data = measure_reliability_data))

# alpha says negative, omega says positive, neither are significant though.

```

In this data, replication attempts at different lab locations can be seen as nested within a replication set. In order to see if this nesting might impact the analyses of hypothesis 3, multilevel logistic regression models were included as sensitivity checks. The dependent variable remains replication success at the replication set level, while Cronbach's Alpha is no longer averaged across locations. The models used were a multilevel logistic random intercept and random slope model.

```{r Hypothesis3MultilevelModelSensitivityAnalyses, include = FALSE}
## sensitivity analyses.
# running a random intercept multilevel logistic model
H3_test_result_int_sensitivity_alpha <- apa_print(glmer(formula = replication_success ~ 1 
                                                + alpha + (1|g), family = 
                                                binomial(), data = 
                                                measure_reliability_data))

# and for omega
H3_test_result_int_sensitivity_omega <- apa_print(glmer(formula = replication_success ~ 1 
                                                + omega.tot + (1|g), family = 
                                                  binomial(), data = 
                                                  measure_reliability_data))

# same as for non-multilevel model

# running a random slope multilevel logistic model
H3_test_result_slp_sensitivity_alpha <- apa_print(glmer(formula = replication_success ~ 1 
                                                + alpha + (1 + alpha|g), 
                                                family = binomial(), data =
                                                measure_reliability_data))

# and for omega
H3_test_result_slp_sensitivity_omega <- apa_print(glmer(formula = replication_success ~ 1 
                                                + omega.tot + (1 + omega.tot|g), 
                                                family = binomial(), data =
                                                measure_reliability_data))

# alpha and omega did not converge.
```

The results of the logistic and multilevel logistic models are shown in Table \@ref(tab:ReplicabilityReliabilityTestTable) for both Cronbach's alpha and omega reliability coefficients.

```{r ReplicabilityReliabilityTestTable, warning = FALSE}
# creating the dtaframe for the table
H3_table_dataframe <- rbind(H3_test_result_main_alpha$table, H3_test_result_int_sensitivity_alpha$table, H3_test_result_main_omega$table, H3_test_result_int_sensitivity_omega$table)

# adding rows to give indication of specific sections (apa_table being awkward)
H3_table_for_printing <- rbind(c("Alpha", "", "", "", ""), c("Logistic Regression Model", "", "", "", ""), H3_table_dataframe[1:2,], c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(3:4),], c("Omega", "", "", "", ""), c("Logistic Regression Model", "", "", "", ""), H3_table_dataframe[(5:6),], c("Random-Intercept Multilevel Logistic Model", "", "", "", ""), H3_table_dataframe[(7:8),])

# print the table in apa formatting
apa_table(
  H3_table_for_printing, align = c("l", "r", "r", "r", "r")
  , caption = "Model Results from Tests of Hypothesis 3"
  , note = "The Alpha and Omega sections show the models where the independent variable was the calculated Cronbach's alpha and omega coefficient respectively. The random slope model for Cronbach's alpha did not converge, thus it results are not shown here. $^* p < .05$"
  , escape = FALSE, placement= "htp", midrules = c(1, 2, 5, 7, 8, 9, 12))

```

Cronbach's alpha and omega did not significantly relate to replication success in the main logistic regression model (Cronbachs alpha: `r H3_test_result_main_alpha$full_result$alpha`; omega: `r H3_test_result_main_omega$full_result$omega`), nor in any of the multilevel sensitivity analyses models (see Table \@ref(tab:ReplicabilityReliabilityTestTable)). This is contradictory to the expectation in hypothesis 3. However, the results from these analyses should be evaluated with caution, given the small sample number of measures used to estimate these models.

## Hypothesis 4, 5, & 6
Hypothesis 4, 5, & 6 were all tested using a model with the same dependent variable: total QMP ratio. In order to model a ratio dependent variable, beta regression was used. Beta regression models operate similarly to standard generalized linear models with similar interpretations of the results. What differentiates them is that they are suitable to model dependent variables with values in the interval of $(0, 1)$, meaning ratios. Furthermore, they are well suited for modelling heteroskedastic and asymmetrically distributed dependent variables [@cribari2010beta]. The beta regression model was implemented using the betareg function within the betareg package [@R-betareg_a; @R-betareg_b]. Defaults were used for all function parameters besides the model formula and data. All beta regression models used the beta link function, which is as follows:

```{=tex}
\begin{equation}
g(.) = (0, 1) \mapsto \mathbb{R} (\#eq:BetaLink)
\end{equation}
```

All of these models assume that the QMPs are the same across each replication set. The reason being that only one protocol was analysed per replication set, and several of the questions regarding QMPs focus solely on the reporting of relevant measurement information. This assumption was deemed likely, since each replication within a set was based on the same protocol. Furthermore, the goal of these protocols is to ensure that the measurement practices are equal across the different replication studies of the same original effect.

## Hypothesis 4
This study seeks to conceptually replicate some of @flake2022construct findings within the Many Labs replication projects.

-   RQ4a. To what degree are QMPs present in replications of psychological research?
-   RQ4b. To what degree are QMPs present in original psychological research?

The structured and preregistered protocols used for the Many Labs projects were hypothesized to lead to consistent reporting of important measurement details, and as a result contain less QMPs.

-   H4. QMPs are expected to be more frequent in original psychological research than in replication research.

### Analysis
To test hypothesis 4, the total QMP ratios between replication and original research was compared. The model formula for this test looked as follows:

```{=tex}
\begin{equation}
g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replication_{i} (\#eq:H4Main)
\end{equation}
```

```{r Hypothesis4Model, include = FALSE}
## Hypothesis 4 beta regression model
# running the model with none revised QMP ratio's
H4_test_results <- betareg(QMP_ratio ~ is_replication, data = QMP_Ratio_data)

# running the models with revised QMP ratio's
H4_test_results_REV  <- betareg(QMP_REV_ratio ~ is_replication, data = QMP_Ratio_data)

```

Where $replication_{i}$ is a dummy coded variable, which was coded as 1 in case the reported QMP ratio belonged to a replications, and 0 if it belonged to an original study.

Results showed that original articles contained a significantly larger proportion of QMPs than replication protocols for the measures of the same effects (beta(`r H4_test_results_REV$df.null`) = `r apa_num(H4_test_results_REV$coefficients$mu[[2]])`, *p* = `r apa_p(summary(H4_test_results_REV)[1]$coefficients$mu[2,4])`), and results based on the initial QMPs showed similar significance (beta(`r H4_test_results$df.null`) = `r apa_num(H4_test_results$coefficients$mu[[2]])`, *p* = `r apa_p(summary(H4_test_results)[1]$coefficients$mu[2,4])`). This result is in line with hypothesis 4.

## Hypothesis 5
If a replication does not properly measure the variables of the original effect, the effect analysed within the replication may not be the same as the original. Establishing a link between QMPs and non-replicability should confirm suspicions of their detrimental effects on replications.

-   RQ5. What is the association between QMPs in replication studies and replication outcome?

Several earlier findings point towards a positive relation between successful replication and various types of good research practices. A similar relation is expected for good measurement practices.

-   H5. QMPs in replication research are negatively associated with replication of an original finding.

### Analysis
For hypothesis 5 a similar formula was used:

```{=tex}
\begin{equation}
g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replicated_{i} (\#eq:H5Main)
\end{equation}
```

Where $replicated_{i}$ is a dummy coded variable, which was coded as 1 if the meta-analytic effect in the replication set matches the original effect in direction at a significance alpha level of .05, and 0 otherwise. Note here that unlike in the test for hypothesis 4, $QMP\_ratio_{i}$ refers only to the QMP ratios of the replications, meaning that original article QMPs were not included in this analysis.

```{r Hypothesis5Model, include = FALSE}
## Hypothesis 5 beta regression model
H5_test_results <- betareg(QMP_Ratio_data[QMP_Ratio_data$is_replication,]$QMP_ratio ~ coded_data_replications$hypothesis_support)

H5_test_results_REV <- betareg(QMP_Ratio_data[QMP_Ratio_data$is_replication,]$QMP_REV_ratio ~ coded_data_replications$hypothesis_support)

```

Results showed that successful replication significantly related to a decrease in the ratio of QMPs in replication protocols (beta(`r H5_test_results_REV$df.null`) = `r apa_num(H5_test_results_REV$coefficients$mu[[2]])`, *p* = `r apa_p(summary(H5_test_results)[1]$coefficients$mu[2,4])`). This result is in line with hypothesis 5. However, the results based on the initial QMPs did not show significant results (beta(`r H5_test_results$df.null`) = `r apa_num(H5_test_results$coefficients$mu[[2]])`, *p* = `r apa_p(summary(H5_test_results)[1]$coefficients$mu[2,4])`).

## Hypothesis 6
If essential information on a measure is not available in an original article, it may be difficult to know the specifics of that measure when used in a replication. In that case, the lack of proper reporting on measurement would impact the transparency and validity of future replications. To provide insight into this issue, an investigation of the relationship between original and replication QMPs was included.

-   RQ6. What is the association between QMPs in original research and QMPs in replications of psychological research?

If the relationship exists, it is expected that questionable measurement practices in an original paper might cause a spill-over effect of QMPs into the replication. Thus, QMPs are expected to be associated across original and replication studies.

-   H6. Total number of QMPs in original psychological research is positively related to total number of QMPs in replication research.

### Analysis
The relationship between original article QMPs and replication protocol QMPs was modelled to test hypothesis 6. The outcome variable remains the same as in the model for hypothesis 5. The independent variable is changed to the QMP ratio for original articles. The resulting model formula is as follows:

```{=tex}
\begin{equation}
g(QMP\_ratio\_replication_{i}) = \beta_{0} + \beta_{1} QMP\_ratio\_original_{i} (\#eq:H6Main)
\end{equation}
```

```{r Hypothesis6Model, include = FALSE}
## Hypothesis 6 beta regression model
H6_test_results <- betareg(QMP_Ratio_data[!QMP_Ratio_data$is_replication,]$QMP_ratio ~ QMP_Ratio_data[QMP_Ratio_data$is_replication,]$QMP_ratio)

H6_test_results_REV <- betareg(QMP_Ratio_data[!QMP_Ratio_data$is_replication,]$QMP_REV_ratio ~ QMP_Ratio_data[QMP_Ratio_data$is_replication,]$QMP_REV_ratio)

```

The results showed that total QMP ratio in the original article significantly predicted total QMP ratio in the subsequent replication (beta(`r H6_test_results_REV$df.null`) = `r apa_num(H6_test_results_REV$coefficients$mu[[2]])`, *p* = `r apa_p(summary(H6_test_results_REV)[1]$coefficients$mu[2,4])`), which provides some evidence in favor of hypothesis 6. However, this relation was not significant for the QMP ratios obtained with the initial protocol (beta(`r H6_test_results$df.null`) = `r apa_num(H6_test_results$coefficients$mu[[2]])`, *p* = `r apa_p(summary(H6_test_results)[1]$coefficients$mean[2,4])`).

## Pre-registration Analysis Justification & Reason for Omission

Follow-up analyses were preregistered for hypothesis 6. The goal of these analyses was to see if there are any type specific carry-over effects in QMPs between original and replication. Theses analyses were changed from the pre-registered analyses to beta-regressions for each unique combination of the QMP categories across original and replication, as the original analysis using contingency tables was later deemed improper for our data and hypothesis 6. Furthermore, these models no longer converged in this version of the article and so are therefore omitted. These analyses can be found in the first pre-print release of this project in the supplementary materials.

### 2025-08-25 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_ratio_table.rmd
adjusted the supplementary materials to reflect the new project structure, fixed references, and removed depricated files.

<!-- Supplementary Analyses B -->

```{r analysis-preferences}
# Seed for random number generation
set.seed(17042023)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Supplementary Analyses B: Initial Coding Protocol QMP Table

This appendix contains the QMP Table equivalent based on the QMPs obtained using the initial coding protocol.

### Explanation
The data was initially coded using to the preregistered coding protocol. After the coding was completed using the preregistered coding protocol, it was determined that some of the initial ratings were possibly too stringent. As a result, some of the items in the protocol were reformulated, so that the conclusions from the resulting analyses were based on a more lenient judgement of QMPs. The coded data using the initial protocol was still separately available, and because this protocol was the one that was pre-registered the QMP table based on these QMPs is shown here.

### Table
Table \@ref(tab:QMPtableInitial) below shows for both original and replication for all of the QMP items the ratio of QMPs and for how many of the `r nrow(coded_data_original)` measures the QMP was applicable. Meanwhile, the Phi coefficient indicates the “correlation” between the MP being questionable or good in the original and the same for the replication. Compared to the revised protocol, the QMP rates are much higher, especially for modification items as we had specific criteria for this that required things to be reported all in the article/protocol with specific details for what  should be there.

```{r Calculating_initial_QMP_Data, include = FALSE, eval = FALSE}
# function for changing QMP data to their ratio equivalent (copied from main manuscript file)
Create_QMP_descriptive_case <- function(practice_name, original_coded_var, replication_coded_var){
  # add practice name to first row
  Practice <- practice_name

  # Sum all QMP/GMP (Good Measurement Practice), keeping NA items out of
  # the equation
  original_n_QMPs <- sum(original_coded_var == "FALSE", na.rm = TRUE)
  replication_n_QMPs <- sum(replication_coded_var == "FALSE", na.rm = TRUE)

  original_n_GMPs <- sum(original_coded_var == "TRUE", na.rm = TRUE)
  replication_n_GMPs <- sum(replication_coded_var == "TRUE", na.rm = TRUE)

  # calculating the N of applicable items for originals
  N_applicable_original <- original_n_QMPs + original_n_GMPs

  # checking that we are not dividing by 0, and then calculating the ratio of 
  # QMPs for applicable items for originals
  if(N_applicable_original != 0){
    QMP_percentage_original <- round(original_n_QMPs / (N_applicable_original), 2)
  } else{
    QMP_percentage_original <- 0
  }

  # calculating the N of applicable items for replications
  N_applicable_replication <- replication_n_QMPs + replication_n_GMPs

  # checking that we are not dividing by 0, and then calculating the ratio of 
  # QMPs for applicable items for replications
  if(N_applicable_replication != 0){
    QMP_percentage_replication <- round(replication_n_QMPs / N_applicable_replication, 2)
  } else{
    QMP_percentage_replication <- 0
  }

  # calculating the Phi coefficient to estimate the relation between variables
  Phi <- phi(matrix(c(original_n_QMPs, original_n_GMPs, replication_n_QMPs, 
                      replication_n_GMPs), nrow = 2, byrow = TRUE))

  return(c(Practice, QMP_percentage_original, N_applicable_original, QMP_percentage_replication, N_applicable_replication, Phi))
}

# loading the relevant items
original_QMP_data_initial <- coded_data_original[c("def_1", "sel_2", "op_4", "reliability_type", "sel_existing", "op_version", "op_1", "sel_1", "sel_3", "sel_4", "sel_psychometric_evidence", "op_2", "op_3", "quant_1", "quant_2", "quant_3", "quant_4", "op_5", "mod_1", "mod_2", "mod_3", "mod_4", "mod_5", "mod_6")]

replication_QMP_data_initial <- coded_data_replications[c("def_1", "sel_2", "op_4", "reliability_type", "sel_existing", "op_version", "op_1", "sel_1", "sel_3", "sel_4", "sel_psychometric_evidence", "op_2", "op_3", "quant_1", "quant_2", "quant_3", "quant_4", "op_5", "mod_1", "mod_2", "mod_3", "mod_4", "mod_5", "mod_6")]

# create an empty dataset to add a recoded TRUE and FALSE response for QMPs to 
QMP_data_initial <- data.frame(delete_this = rep(NA, 77))

QMP_data_initial$reliability_reported_org <- ifelse(original_QMP_data_initial$reliability_type != "Not Reported" & original_QMP_data_initial$reliability_type != "" & !is.na(original_QMP_data_initial$reliability_type), TRUE, ifelse(original_QMP_data_initial$reliability_type == "Not Reported", FALSE, NA))

QMP_data_initial$reliability_reported_rep <- ifelse(replication_QMP_data_initial$reliability_type != "Not Reported" & replication_QMP_data_initial$reliability_type != "" & !is.na(replication_QMP_data_initial$reliability_type), TRUE, ifelse(replication_QMP_data_initial$reliability_type == "Not Reported", FALSE, NA))

# add if clearly specified if measure existed or not
QMP_data_initial$select_or_create_clarity_org <- original_QMP_data_initial$sel_existing == "Not Clearly Stated"

QMP_data_initial$select_or_create_clarity_rep <- replication_QMP_data_initial$sel_existing == "Not Clearly Stated"

# add if version was clearly specified
QMP_data_initial$version_clarity_org <- original_QMP_data_initial$op_1 == FALSE | original_QMP_data_initial$op_version == "" & original_QMP_data_initial$sel_existing == "True, namely:"

QMP_data_initial$version_clarity_rep <- replication_QMP_data_initial$op_1 == FALSE | replication_QMP_data_initial$op_version == "" & replication_QMP_data_initial$sel_existing == "True, namely:"

# add if factor structure was analysed
QMP_data_initial$factor_analysis_org <- ifelse(original_QMP_data_initial$sel_psychometric_evidence == "None", FALSE, ifelse(original_QMP_data_initial$sel_psychometric_evidence != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)", TRUE, NA))

QMP_data_initial$factor_analysis_rep <- ifelse(replication_QMP_data_initial$sel_psychometric_evidence == "None", FALSE, ifelse(replication_QMP_data_initial$sel_psychometric_evidence != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)", TRUE, NA))

# direct copies
QMP_data_initial$justified_definition_org <- original_QMP_data_initial$def_1
QMP_data_initial$justified_definition_rep <- replication_QMP_data_initial$def_1
QMP_data_initial$justified_selection_org <- original_QMP_data_initial$sel_2
QMP_data_initial$justified_selection_rep <- replication_QMP_data_initial$sel_2
QMP_data_initial$justified_operationalisation_org <- original_QMP_data_initial$op_4
QMP_data_initial$justified_operationalisation_rep <- replication_QMP_data_initial$op_4
QMP_data_initial$source_org <- original_QMP_data_initial$sel_1
QMP_data_initial$source_rep <- replication_QMP_data_initial$sel_1
QMP_data_initial$in_psychometric_org <- original_QMP_data_initial$sel_3
QMP_data_initial$in_psychometric_rep <- replication_QMP_data_initial$sel_3
QMP_data_initial$out_psychometric_org <- original_QMP_data_initial$sel_4
QMP_data_initial$out_psychometric_rep <- replication_QMP_data_initial$sel_4
QMP_data_initial$admin_format_org <- original_QMP_data_initial$op_2
QMP_data_initial$admin_format_rep <- replication_QMP_data_initial$op_2
QMP_data_initial$admin_procedure_org <- original_QMP_data_initial$op_3
QMP_data_initial$admin_procedure_rep <- replication_QMP_data_initial$op_3
QMP_data_initial$N_items_org <- original_QMP_data_initial$quant_1
QMP_data_initial$N_items_rep <- replication_QMP_data_initial$quant_1
QMP_data_initial$N_response_org <- original_QMP_data_initial$quant_2
QMP_data_initial$N_response_rep <- replication_QMP_data_initial$quant_2
QMP_data_initial$recoding_org <- original_QMP_data_initial$quant_3
QMP_data_initial$recoding_rep <- replication_QMP_data_initial$quant_3
QMP_data_initial$aggregation_org <- original_QMP_data_initial$quant_4
QMP_data_initial$aggregation_rep <- replication_QMP_data_initial$quant_4
QMP_data_initial$example_items_org <- original_QMP_data_initial$op_5
QMP_data_initial$example_items_rep <- replication_QMP_data_initial$op_5
QMP_data_initial$mod_admin_format_org <- original_QMP_data_initial$mod_1
QMP_data_initial$mod_admin_format_rep <- replication_QMP_data_initial$mod_1
QMP_data_initial$mod_admin_format_support_org <- original_QMP_data_initial$mod_2
QMP_data_initial$mod_admin_format_support_rep <- replication_QMP_data_initial$mod_2
QMP_data_initial$mod_language_org <- original_QMP_data_initial$mod_3
QMP_data_initial$mod_language_rep <- replication_QMP_data_initial$mod_3
QMP_data_initial$mod_language_support_org <- original_QMP_data_initial$mod_4
QMP_data_initial$mod_language_support_rep <- replication_QMP_data_initial$mod_4
QMP_data_initial$mod_N_items_or_response_org <- original_QMP_data_initial$mod_5
QMP_data_initial$mod_N_items_or_response_rep <- replication_QMP_data_initial$mod_5
QMP_data_initial$mod_N_items_or_response_support_org <- original_QMP_data_initial$mod_6
QMP_data_initial$mod_N_items_or_response_support_rep <- replication_QMP_data_initial$mod_6

QMP_data_initial <- QMP_data_initial[,!(names(QMP_data_initial) %in% "delete_this")]

### QMP ratio data
# create the empty QMP ratio dataset
QMP_ratio_data_initial <- data.frame(Practice = rep("", ncol(QMP_data_initial)/2),
                                     QMP_percentage_original = rep(0, ncol(QMP_data_initial)/2),
                                     N_applicable_original = rep(0, ncol(QMP_data_initial)/2),
                                     QMP_percentage_replication = rep(0, ncol(QMP_data_initial)/2),
                                     N_applicable_replication = rep(0, ncol(QMP_data_initial)/2),
                                     Phi = rep(0, ncol(QMP_data_initial)/2))

# we loop through the length of the number of Measurement Practices (MPs) 
# ignoring doubles due to having both original and replication
for(i in 1:(ncol(QMP_data_initial)/2)){
  # we create the name of the variable by taking the name and removing the 
  # _org suffix. Then we for each column except the NA initial column
  # we take the original MP and the related replication MP, and calculate
  # their QMP
  QMP_ratio_data_initial[i,] <- Create_QMP_descriptive_case(substr(names(QMP_data_initial)[i*2], 1, nchar(names(QMP_data_initial)[i*2]) - 4), QMP_data_initial[[(i*2)-1]], QMP_data_initial[[i*2]])
  }

```

```{r QMPtableInitial}
# create informative Measurement Practice Labels 
MPractice <- c("Reliability is reported", "It is clear if the measure existed or is newly created",    "Specifc version of the measure is specified", "Validity evidence from a factor analysis is presented",   "The measured variable is defined", "The choice of measure selection or creation is justified",    "The implemented operationalisation is justified", "The source of the measure is provided",    "Psychometric evidence from the study is given", "Psychometric evidence from an earlier study is given",    "The administration format and environment are described", "The administration procedure is described",   "The number of items are described", "The number of response options are described",    "The recoding of responses is described", "The creation of the index is described",    "Example items are presented in text or supplement", "Any administration format changes are mentioned",    "Administration format changes are justified/validated", "Any translations are mentioned",    "Translated measures are justified/validated", "Any changes in number of items or response options are mentioned",    "Changes in number of items or response options are justified/validated")

# construct the QMP table to be printed 
QMP_table_initial <- data.frame("Practice" = MPractice, 
                        "QMP original" = paste0(QMP_ratio_data_initial$QMP_percentage_original, " (", QMP_ratio_data_initial$N_applicable_original, ")"), 
                        "QMP Replication" = paste0(QMP_ratio_data_initial$QMP_percentage_replication, " (", QMP_ratio_data_initial$N_applicable_replication, ")"), 
                        "Phi" = QMP_ratio_data_initial$Phi)

# print the table in apa formatting 
apa_table(QMP_table_initial, align = c("l", "r", "r", "r"), caption = "Ratio of QMPs and number of applicable measures, for original and replication", note = "The first number in QMP org and QMP rep is the ratio of measures for which the practice in that row was not conducted well by our standards. The number between brackets indicates the number of measures for which the practice was applicable.", escape = FALSE, placement = "htp")
```

### 2025-08-25 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_item_reduced_measures_analyses.Rmd
adjusted the supplementary materials to reflect the new project structure, fixed references, and removed depricated files.

--- 2024-07-26 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_item_reduced_measures_analyses.Rmd
@@
-<!-- Supplementary Analyses E -->
+<!-- Supplementary Analyses C -->
 
@@
 
-# Supplementary Analyses E: Item Reduced Measures Analyses
+```{r setup, include = FALSE}
+# loading R libraries
+library(papaja)
+library(betareg)
+library(statmod)
+```
 
-This appendix contains analyses on the impact that measures with a changed number of items had on the results.
-These analyses were not pre-registered, but were conducted to check for the potentially confoudning influence of these measures.
-The results of these supplementary analyses show that this impact was minimal.
+```{r data_prep}
+# combine replication and original data 
+is_replication <- c(rep(FALSE, 77), rep(TRUE, 77))
+
+combi_org_rep <- rbind(coded_data_original, coded_data_replications)
+
+combi_org_rep <- cbind(combi_org_rep, is_replication)
+
+combi_org_rep$has_reliability <- combi_org_rep$reliability_type != "Not Reported" & combi_org_rep$reliability_type != ""
+
+# function to calculate QMP ratios
+calculating <- function(Data){
+  QMP_data <- data.frame(def_ratio = rep(NA, 154),
+                         op_ratio = rep(NA, 154),
+                         sel_ratio = rep(NA, 154),
+                         quant_ratio = rep(NA, 154),
+                         mod_ratio = rep(NA, 154),
+                         QMP_ratio = rep(NA, 154),
+                         op_REV_ratio = rep(NA, 154),
+                         sel_REV_ratio = rep(NA, 154),
+                         quant_REV_ratio = rep(NA, 154),
+                         mod_REV_ratio = rep(NA, 154),
+                         QMP_REV_ratio = rep(NA, 154))
+
+  def_count <- as.numeric(Data$def_1)
+  def_count[is.na(def_count)] <- 0
+  def_total <- as.numeric(!is.na(Data$def_1))
+  QMP_data$def_ratio <- 1 - round(def_count / def_total, 4) 
+  QMP_data$def_ratio[is.na(Data$def_ratio)] <- 0
+
+  op_count <- rowSums(Data[16:20], na.rm = TRUE)
+  op_total <- rowSums(!is.na(Data[16:20]))
+  QMP_data$op_ratio <- 1 - round(op_count / op_total, 4)
+
+  sel_count <- rowSums(Data[23:26], na.rm = TRUE)
+  sel_total <- rowSums(!is.na(Data[23:26]))
+  QMP_data$sel_ratio <- 1 - round(sel_count / sel_total, 4)
+
+  quant_count <- rowSums(Data[29:32], na.rm = TRUE)
+  quant_total <- rowSums(!is.na(Data[29:32]))
+  QMP_data$quant_ratio <- 1 - round(quant_count / quant_total, 4)
+
+  mod_count <- rowSums(Data[34:39], na.rm = TRUE)
+  mod_total <- rowSums(!is.na(Data[34:39]))
+  QMP_data$mod_ratio <- 1 - round(mod_count / mod_total, 4)
+
+  MP_total <- def_total + op_total + sel_total + quant_total + mod_total
+  MP_count <- def_count + op_count + sel_count + quant_count + mod_count
+  QMP_data$QMP_ratio <- 1 - round(MP_count / MP_total, 4)
+
+  op_REV_count <- rowSums(Data[c(18,19,41,42,43)], na.rm = TRUE)
+  op_REV_total <- rowSums(!is.na(Data[c(18,19,41,42,43)]))
+  QMP_data$op_REV_ratio <- 1 - round(op_REV_count / op_REV_total, 4)
+
+  sel_REV_count <- rowSums(Data[c(24,26,44,45)], na.rm = TRUE)
+  sel_REV_total <- rowSums(!is.na(Data[c(24,26,44,45)]))
+  QMP_data$sel_REV_ratio <- 1 - round(sel_REV_count / sel_REV_total, 4)
+
+  quant_REV_count <- rowSums(Data[c(32,48,49,50)], na.rm = TRUE)
+  quant_REV_total <- rowSums(!is.na(Data[c(32,48,49,50)]))
+  QMP_data$quant_REV_ratio <- 1 - round(quant_REV_count / quant_REV_total, 4)
+
+  mod_REV_count <- rowSums(Data[52:57], na.rm = TRUE)
+  mod_REV_total <- rowSums(!is.na(Data[52:57]))
+  QMP_data$mod_REV_ratio <- 1 - round(mod_REV_count / mod_REV_total, 4)
+
+  MP_REV_count <- def_count + op_REV_count + sel_REV_count + quant_REV_count + mod_REV_count
+  MP_REV_total <- def_total + op_REV_total + sel_REV_total + quant_REV_total + mod_REV_total
+  QMP_data$QMP_REV_ratio <- 1 - round(MP_REV_count / MP_REV_total, 4)
+
+  return(QMP_data)
+}
+
+# calculating the QMP ratios for each QMP item.
+QMP_Ratio_data <- calculating(combi_org_rep)
+
+QMP_Ratio_data <- cbind(QMP_Ratio_data, is_replication)
+
+```
+
+# Supplementary Analyses C: Item Reduced Measures Analyses
+
+This appendix contains the analyses on the impact that measures with a changed number of items had on the main results from  Supplementary Analyses A.
+These analyses were not pre-registered, but were conducted to check for the potentially confounding influence of these measures.
+The results of these supplementary analyses show that this impact was minimal overall.
 
@@
 
-```{r StoringItemReducedMeasureData}
-# Storing the data on the Measures for which the number of items and/or response 
-# options was altered from original to replication (of main interest are the
-# measures for which the number of items were changed).
-open_data(data = item_number_change_data, filename = paste0(paste0(
-  "Data/AnalysisData/", deparse(substitute(item_number_change_data))), ".csv"),
-  codebook = paste0(paste0(
-    "Data/AnalysisData/codebook_", 
-    deparse(substitute(item_number_change_data))), ".Rmd"),
-  value_labels = paste0(paste0(
-    "Data/AnalysisData/value_labels_", 
-    deparse(substitute(item_number_change_data))), ".yml"))
-
-```
-
 There were overall `r sum(decreased_items_index)` measures for which the number of items were reduced. In the following analyses we will see their impact on the results
@@
 hypothesis_support_index[coded_data_replications$hypothesis_support == "Unclear"] <- "Yes"
-
-# coding Unclear into No instead of Yes didn't make a difference on the test.
-# hypothesis_support_index[coded_data_replications$hypothesis_support == "Unclear"] <- "No"
 
@@
 
-Interestingly, when item numbers decreased, the replicability seemed to have increased .
+Interestingly, when item numbers decreased, the replicability seemed to have increased.
 Although the difference was not significant (`r decreased_items_replicability_impact_test_result`), and there were too few modifications to the items to get a stable estimate.
@@
 # H1
-coded_data_original_shortened$reliability_type[decreased_items_index]
+coded_data_original$reliability_type[decreased_items_index]
 coded_data_replications$reliability_type[decreased_items_index]
@@
 # H2 & H3
-coded_data_original_shortened$reliability_coeff[decreased_items_index]
+coded_data_original$reliability_coeff[decreased_items_index]
 coded_data_replications$reliability_coeff[decreased_items_index]
@@
 # running the H3 model
-data_h3_avg[data_h3_avg$reporting_index %in% as.numeric(rownames(item_number_change_data[item_number_change_data$direction == "decrease" & !is.na(item_number_change_data$direction),])),]
+measure_reliability_data[measure_reliability_data$reporting_index %in% as.numeric(rownames(item_number_change_data[item_number_change_data$direction == "decrease" & !is.na(item_number_change_data$direction),])),]
 
@@
 ```{r OriginalQMPDIfference}
+# first we combine the datasets of the original studies and the replications 
+# together
+# adding "Rep_" to separate replication from original columns in the combined dataset
+data_h4_Rep <- QMP_Ratio_data[QMP_Ratio_data$is_replication,]
+colnames(data_h4_Rep) <- paste0("Rep_", colnames(data_h4_Rep))
+
+# combine the dataset
+data_h4 <- cbind(QMP_Ratio_data[!QMP_Ratio_data$is_replication,], data_h4_Rep)
+
 # comparing the mean and sd original QMP ratio 
-print(c("mean decreased" = mean(data_h6$QMP_REV_ratio[decreased_items_index]),
-      "sd decreased" = sd(data_h6$QMP_REV_ratio[decreased_items_index]),
+print(c("mean decreased" = mean(data_h4$QMP_REV_ratio[decreased_items_index]),
+      "sd decreased" = sd(data_h4$QMP_REV_ratio[decreased_items_index]),
 
-      "mean non-decreased" = mean(data_h6$QMP_REV_ratio[-decreased_items_index]),
-      "sd non-decreased" = sd(data_h6$QMP_REV_ratio[-decreased_items_index])))
+      "mean non-decreased" = mean(data_h4$QMP_REV_ratio[-decreased_items_index]),
+      "sd non-decreased" = sd(data_h4$QMP_REV_ratio[-decreased_items_index])))
 ```
@@
 
-```{r OriginalQMPDIfference}
+```{r ReplicationQMPDIfference}
 # comparing the mean and sd replication QMP ratio 
-print(c("mean decreased" = mean(data_h6$Rep_QMP_REV_ratio[decreased_items_index]),
-      "sd decreased" = sd(data_h6$Rep_QMP_REV_ratio[decreased_items_index]),
+print(c("mean decreased" = mean(data_h4$Rep_QMP_REV_ratio[decreased_items_index]),
+      "sd decreased" = sd(data_h4$Rep_QMP_REV_ratio[decreased_items_index]),
 
-      "mean non-decreased" = mean(data_h6$Rep_QMP_REV_ratio[-decreased_items_index]),
-      "sd non-decreased" = sd(data_h6$Rep_QMP_REV_ratio[-decreased_items_index])))
+      "mean non-decreased" = mean(data_h4$Rep_QMP_REV_ratio[-decreased_items_index]),
+      "sd non-decreased" = sd(data_h4$Rep_QMP_REV_ratio[-decreased_items_index])))
 ```
@@
 ```{r H4Difference}
+# for H4 we have to combine the replication and original data together
+data_h4 <- rbind(data_h456_original, data_h456_replications)
+
 # running the h4 models
 # only decreased item measures
-betareg_output_to_apa_full(betareg(QMP_REV_ratio ~ rep_org, data = data_h4[c(decreased_items_index, decreased_items_index),]))
+betareg(QMP_REV_ratio ~ is_replication, data = QMP_Ratio_data[decreased_items_index,])
 
 # only non-decreased item measures
-betareg_output_to_apa_full(betareg(QMP_REV_ratio ~ rep_org, data = data_h4[-c(decreased_items_index, decreased_items_index),]))
+betareg(QMP_REV_ratio ~ is_replication, data = QMP_Ratio_data[!decreased_items_index,])
 
 # all (originally)
-betareg_output_to_apa_full(betareg(QMP_REV_ratio ~ rep_org, data = data_h4))
+betareg(QMP_REV_ratio ~ is_replication, data = QMP_Ratio_data)
+
 ```
@@
 ```{r H5Difference}
-# running the h5 models
-apa_print(glm(hypothesis_support ~ QMP_REV_ratio, data = data_h5[decreased_items_index[c(53:55)],], family = binomial))$full_result$QMP_REV_ratio
+## running the h5 models
+# first making data with and without decreased item measures
+Diff_QMP_Ratio_data <- QMP_Ratio_data[QMP_Ratio_data$is_replication,]
+Diff_QMP_Ratio_data <- Diff_QMP_Ratio_data[decreased_items_index,]
+UnDiff_QMP_Ratio_data <- QMP_Ratio_data[QMP_Ratio_data$is_replication,]
+UnDiff_QMP_Ratio_data <- UnDiff_QMP_Ratio_data[-decreased_items_index,]
+Diff_coded_data_replications <- coded_data_replications[decreased_items_index,]
+UnDiff_coded_data_replications <- coded_data_replications[-decreased_items_index,]
 
-apa_print(glm(hypothesis_support ~ QMP_REV_ratio, data = data_h5[-decreased_items_index[c(53:55)],], family = binomial))$full_result$QMP_REV_ratio
+# running the model using the QMPs from the revised coding protocol
+betareg(Diff_QMP_Ratio_data$QMP_REV_ratio ~ Diff_coded_data_replications$hypothesis_support)
 
-apa_print(glm(hypothesis_support ~ QMP_REV_ratio, data = data_h5, family = binomial))$full_result$QMP_REV_ratio
+betareg(UnDiff_QMP_Ratio_data$QMP_REV_ratio ~ UnDiff_coded_data_replications$hypothesis_support)
 
+betareg(QMP_Ratio_data[QMP_Ratio_data$is_replication,]$QMP_REV_ratio ~ coded_data_replications$hypothesis_support)
 ```
@@
 # running the h6 models
-betareg_output_to_apa_full(betareg(Rep_QMP_REV_ratio ~ QMP_REV_ratio, data = data_h6[decreased_items_index,]))
+betareg(QMP_Ratio_data[!QMP_Ratio_data$is_replication,]$QMP_REV_ratio[decreased_items_index] ~ QMP_Ratio_data[QMP_Ratio_data$is_replication,]$QMP_REV_ratio[decreased_items_index])
 
-betareg_output_to_apa_full(betareg(Rep_QMP_REV_ratio ~ QMP_REV_ratio, data = data_h6[-decreased_items_index,]))
+betareg(QMP_Ratio_data[!QMP_Ratio_data$is_replication,]$QMP_REV_ratio[!decreased_items_index] ~ QMP_Ratio_data[QMP_Ratio_data$is_replication,]$QMP_REV_ratio[!decreased_items_index])
 
-betareg_output_to_apa_full(betareg(Rep_QMP_REV_ratio ~ QMP_REV_ratio, data = data_h6))
+betareg(QMP_Ratio_data[!QMP_Ratio_data$is_replication,]$QMP_REV_ratio ~ QMP_Ratio_data[QMP_Ratio_data$is_replication,]$QMP_REV_ratio)
 

### 2025-08-25 SupplementaryMaterials/data_retrieval_information.Rmd
adjusted the supplementary materials to reflect the new project structure, fixed references, and removed depricated files.

@@
 
+full_coded_data <- rbind(coded_data_original, coded_data_replications)
+
+plot_data_structure_data <- data.frame()
+
+for (i in 1:nrow(full_coded_data)){
+  if(full_coded_data$variable_order[i] == 1){
+    plot_data_structure_data <- rbind(plot_data_structure_data, full_coded_data[i,])
+  }
+
+  if(full_coded_data$variable_order[i] != 1){
+    plot_data_structure_data[nrow(plot_data_structure_data),] <- full_coded_data[i,]
+  }
+}
+
 # plot of the multilevel data structure
 ggplot(plot_data_structure_data, aes(x = N, y = factor(many_labs_version, levels = c("5", "3", "2", "1")), 
-                                colour = rep_org, shape = hypothesis_support, size = measure_count)) +
+                                colour = rep_org, shape = hypothesis_support, size = variable_order)) +
   geom_point(alpha = .33) +

### 2025-08-25 Scripts/source_script.R

@@ -1,921 +1,0 @@
-# source_script
-
-
-# Data Cleaning Functions ------------------------------------------------------
-### renaming the columns and rows to accommodate the joining of the three 
-### datasets.
-renaming <- function(Data){
-  # renaming columns
-  colnames(Data) <- 
-    c("many_labs_version", "rep_org", "title", "measure_name", "variable_name",
-      "multi", "variable_order", "N", "N_items", "hypothesis_support", 
-      "reliability_type", "reliability_type_text", "reliability_coeff",
-      "def1", "op_version", "op_1", "op_2", "op_3", "op_4", "op_5", 
-      "sel_existing", "sel_existing_text", "sel_1", "sel_2", "sel_3", "sel_4",
-      "sel_psychometric_evidence", "sel_psychometric_evidence_text", "quant_1",
-      "quant_2", "quant_3", "quant_4", "mod_check", "mod_1", "mod_2", "mod_3",
-      "mod_4", "mod_5", "mod_6", "mod_time", "op_1_REV", "op_2_REV",
-      "op_5_REV", "sel_1_REV", "sel_3_REV", "sel_psychometric_evidence_REV", 
-      "sel_psychometric_evidence_text_REV", "quant_1_REV", "quant_2_REV", 
-      "quant_3_REV", "mod_check_REV", "mod_1_REV", "mod_2_REV", "mod_3_REV", 
-      "mod_4_REV", "mod_5_REV", "mod_6_REV", "inseperable_material")
-  
-  # renaming rows
-  rownames(Data) <- 1:nrow(Data)
-  
-  return(Data)
-}
-
-
-### Fixing some coding misses.
-fixing <- function(Data){
-  Data$variable_name[79] <- "quote attribution effect"
-  Data$N[3] <- "5284"
-  Data$N[158] <- "1202"
-  Data$reliability_type[50] <- "Not Reported"
-  Data$reliability_type[127] <- "Not Reported"
-  Data$op_1[145] <- "False"
-  Data$op_3[121] <- "True"
-  Data$op_5[157] <- "True"
-  Data$sel_1[59] <- "True"
-  Data$quant_2[113] <- "True"
-  Data$mod_time[1] <- "Before"
-  
-  return(Data)
-}
-
-
-
-### Moving around of entries
-restructuring <- function(Data){
-  # removing missing entry 77
-  Data <- data.frame(Data)[-77,]
-  
[…]

### 2025-08-25 SupplementaryMaterials/SupplementaryAnalysesScripts/temporary_code_dump.R

@@ -1,68 +1,0 @@
-#####{r internal_structure_information}
-Mode <- function(x) {
-  ux <- unique(x)
-  ux[which.max(tabulate(match(x, ux)))]
-}
-
-FA_aggregate_data <- data.frame(RMSEA = rep(NA, 19), 
-                                RMSEA_se = rep(NA, 19), 
-                                RMSEA_global_mean = rep(NA, 19), 
-                                RMSEA_mean_sd = rep(NA, 19), 
-                                N_factors_mode = rep(NA, 19),
-                                unidimensional_ratio = rep(NA, 19),
-                                Tau_N_P_10 = rep(NA, 19),
-                                Tau_N_P_05 = rep(NA, 19),
-                                Tau_N_P_01 = rep(NA, 19),
-                                global_mean_spec = rep(NA, 19),
-                                global_sd_spec = rep(NA, 19),
-                                err_N_P_10 = rep(NA, 19),
-                                err_N_P_05 = rep(NA, 19),
-                                err_N_P_01 = rep(NA, 19))
-
-
-### recreate FA_list
-FA_list <- list(fa_caruso_2012, fa_husnu_2010, fa_nosek_2002_math, fa_nosek_2002_art,
-                fa_anderson_2012_swl, fa_anderson_2012_pa, fa_anderson_2012_na,
-                fa_giessner_2007, fa_norenzayan_2002, fa_zhong_2006, fa_monin_2001_most,
-                fa_monin_2001_some, fa_cacioppo_1983_arg, fa_cacioppo_1983_nfc, 
-                fa_de_fruyt_2000, fa_albarracin_2008_verb, fa_albarracin_2008_math,
-                fa_shnabel_2008, fa_vohs_2008)
-
-
-
-for (i in 1:19){
-  data <- FA_list[[i]]
-  
-  tryCatch({
-    RMSEA_estimate <- rma(yi = as.numeric(RMSEA), sei = as.numeric(RMSEA_se), data = data) # inverse variance weighting is on by default
-    FA_aggregate_data$RMSEA[i] <- RMSEA_estimate$b
-    FA_aggregate_data$RMSEA_se[i] <- RMSEA_estimate$se
-    
-  }, error = function(e) {
-    
-  })
-  
[…]

### 2025-08-26 Scripts/Manuscript/manuscript.Rmd
fixed minor errors in the Rmarkdown text.

@@
 ---
-title             : "Assessing Reliable and Valid Measurement as a Prerequisite for Informative Replications in Psychology"
-shorttitle        : "Measurement and Informative Replications"
+title             : "Measurement Reliabily, Validity, and Reporting in Replicaitons and Original Research"
+shorttitle        : "Measurement Reliability, Validity, and Reporting"
 
@@
 
-The challenge with measurement in quantitative psychological research is that psychological constructs cannot be directly measured like height or weight.
-Instead, we use scores from a measurement as a proxy indicator for that psychological construct.
+The challenge with measurement in quantitative psychological research is that unlike height or weight, psychological constructs cannot be directly measured.
+Instead we use scores from a measurement as a proxy indicator for that psychological construct.
 However, we cannot simply assume that any measure we create will form a good indicator of the construct.
 We have to substantiate this.
-Psychometrics can be used to statistically estimate properties of the measure that are indicative of its validity.
-The effort of validating a measure represents a research effort all on its own.
-Regardless, the burden of validating a measure – besides some well-established psychiatric and personality measures – is most often placed on the researcher using a measure as part of their broader aim to study a psychological phenomena.
-When the effort involved in validating a measure is relegated to being only a component of a study that is more focused on the testing of a phenomena, we have to wonder, how well does this measurement validation process go?
+Psychometrics can be used to statistically estimate the measure's validity, still validating a measure entails a substantial research effort.
+Regardless, the burden of validating a measure – besides some well-established psychiatric and personality measures – is most often placed on the researcher conducting a study of a psychological phenomenon.
+When the effort involved in validating a measure is relegated to be only a component of a study, then how well does the measurement validation process go?
 
 ## Measurement Validation
-
-When we validate a measure using psychometrics, we evaluate it mainly on two aspects: construct validity & reliability.
-Construct validity refers to whether the variance in the measured item scores between participants can be attributed to variance in the unobserved constructs of interest between participants [@cronbachConstructValidityPsychological1955; @vazireCredibilityReplicabilityImproving2022].
-Whereas reliability refers to how consistent a participant's responses on a measurement are [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011].
-Reliability is part of the validation of a measure because an unreliable measure cannot consistently capture a construct through the items, and therefore cannot be assumed to properly capture the construct of interest [@crutzenScaleQualityAlpha2017b].
-Suppose we have a measure and we want it to measure general intelligence, and we want to validate this as a measure of general intelligence.
+When validating a measure of a psychological construct, two main psychometric components are of interest: construct validity & reliability.
+Construct validity refers to whether the variance in the measured item scores between participants can be attributed to variance in unobserved constructs between participants [@cronbachConstructValidityPsychological1955; @vazireCredibilityReplicabilityImproving2022].
+Reliability refers to how consistent a participant's responses on a measurement are [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011].
+Reliability is part of the validation of a measure because a measure that does not consistently capture a participant's response, cannot accurately capture a construct [@crutzenScaleQualityAlpha2017b].
+As an example, suppose we have a measure and we want it to measure general intelligence, and we want to validate this as a measure of general intelligence.
 We would see our measurement as construct valid if being more intelligent resulted in generally scoring higher on our test, and our measurement would be reliable if the score of people on our measure consistently reflected their actual intelligence.
@@
 In practice construct validity is often evaluated through factor analysis.
-In factor analysis, a model is fitted to explain as much of the variance of multiple items through a smaller number of factors, which are each weighted averages of the item scores.
-The number of factors are first specified, and then the fit of a model involving those number of factors is determined.
-Preferably, a model with the number of factors corresponding to the number of constructs of interest should show adequate fit.
+In factor analysis, a model is fitted to explain as much of the variance of multiple items through a smaller number of factors, or weighted averages of the item scores.
+To fit a factor model, the number of factors are first specified, and then the fit of that model on the data can be evaluated.
+Preferably, a model with the number of factors corresponding to the number of constructs of interest should show adequate fit on the data.
 Additionally, the items aimed at the same construct should be statistically related to the same factor.
 For example, suppose items 1 through 5 from our general intelligence measure are meant to capture verbal intelligence, and items 6 through 10 are distinctly about mathematical intelligence.
-To establish construct validity, we want to find that a two factor model shows adequate fit, with one factor to which items 1 through 5 relate, and one to which items 6 through 10 relate.
-However, even in this scenario we cannot be certain that the second factor relates to mathematical intelligence and not for example abstract thinking, other types of validity checks as well as theoretical underpinnings will be necessary.
-Additionally, the factor relations may not be stable for this measure in other contexts and implementations, a concept known as measurement invariance [@hornPracticalTheoreticalGuide1992; @cheungDirectComparisonApproach2012].
+To establish construct validity, we want to find that a two factor model on our intelligence measure to show adequate fit, with one factor to which only items 1 through 5 relate strongly, and one to which only items 6 through 10 relate strongly.
+However, even in this ideal scenario, the factor relations may not be stable for this measure in other contexts and implementations, a concept known as measurement invariance [@hornPracticalTheoreticalGuide1992; @cheungDirectComparisonApproach2012].
 
@@
 For example, we can compare scores on multiple equivalent forms of the test, between multiple different raters, or between multiple different timepoints of the same test.
-Still, the most common way to assess reliability is through an indication of consistency within the measure itself, and the most common among these indicators is the Cronbach's Alpha coefficient.
+Still, the most common way to assess reliability for single measurement instances is through internal consistency indicators.
+The most common internal consistency indicator is the Cronbach's Alpha coefficient.
 The Cronbach's Alpha coefficient is defined as “the average of all the possible split-half coefficients for a given test” [@cronbachCoefficientAlphaInternal1951].
@@
 However, Cronbach's Alpha comes with strong assumptions on the underlying factor structure, including that the measure is unidimensional, so a single factor.
-Furthermore, because Cronbach's alpha is proportional to the total variance in the target variable in the sample, it is an indicator of reliability of a measurement, and not the measure itself.
-In spite of this many researchers report and interpret Cronbach's Alpha as such [@cortinaWhatCoefficientAlpha1993; @schmittUsesAbusesCoefficient1996].
-
-Thus, psychometric tests are useful but they are not always easy to perform in practice.
-Even simple factor analysis requires sample sizes of at least around 100, unless the amount of variance explained by the factors is large and the factor structure is clear (Gorsuch, 1983; MacCallum et al., 1999).
-However, even in the latter case factor analysis does not converge with low sample sizes.
-Furthermore, if we want to know not just the reliability and validity of one measurement but for the measure across multiple contexts, we need to conduct multiple studies with generally even larger sample sizes per group to detect meaningful effects [@meadePowerPrecisionConfirmatory2007; @frenchMeasurementInvarianceTechniques2016; @koziolImpactModelParameterization2018].
-However, what we observe in the literature is that most measures are reused once or never [@elsonPsychologicalMeasuresArent2023; @anvariFragmentedFieldConstruct2025; @anvariDefragmentingPsychology2025].
-Finally, @maireadshawMeasurementPracticesLargescale2020 checked the factor structure and reliability of measures used in the Many Labs 2 replication project [@kleinManyLabs22018b] on the available data, the results.
-They observed that for none of the scales they assessed, a factor structure congruent with the use of the scales met all of their evaluation criteria, and reliability was rarely consistently above an acceptable threshold.
+Furthermore, because Cronbach's alpha is proportional to the total variance in the target variable in the sample, it is an indicator of reliability within a particular sample and not of the reliability of the measure in general.
+Despite this many researchers report and interpret Cronbach's Alpha as a universal quality of the measure [@cortinaWhatCoefficientAlpha1993; @schmittUsesAbusesCoefficient1996].
+
+Thus, psychometric tests are useful but they have their limitations.
+Even simple factor analyses - unless the amount of variance explained by the factors is large and the factor structure is clear - require sample sizes of at least 100 [@maccallumSampleSizeFactor1999; @gorsuchFactorAnalysis2013].
+Furthermore, even in the latter case factor analysis may not converge with small sample sizes.
+If we want to know the reliability and validity of not just one measurement but for the measure across multiple contexts, we need to conduct multiple studies.
+Additionally, larger sample sizes per relevant group to detect meaningful effects when checking for measurement invariance across groups [@meadePowerPrecisionConfirmatory2007; @frenchMeasurementInvarianceTechniques2016; @koziolImpactModelParameterization2018].
+However, what we observe in the literature is that most measures are reused once or never [@elsonPsychologicalMeasuresArent2023; @anvariFragmentedFieldConstruct2025; @anvariDefragmentingPsychology2025], let alone that they are systematically tested on reliability and validity.
+@maireadshawMeasurementPracticesLargescale2020 checked the factor structure and reliability of measures used in the Many Labs 2 replication project [@kleinManyLabs22018b] on the available data.
+They observed that for the scales they assessed, no factor model fit congruent with the use of the scales met all of their evaluation criteria.
+Furthermore, the overall sample Cronbach's alpha level of all scales was below .5, a level of reliability far below what many would consider acceptable for almost all research purposes.
 
@@
 Additionally, only eight of the 40 translated scales contained validity evidence for the translated version.
-But reporting of reliability and validity evidence is not only low, but may also be biased as well.
+Furthermore, reporting of reliability may not only be little, but also biased.
 @husseyAberrantAbundanceCronbachs2023 observed a disproportional amount of Cronbach's Alpha values at the common acceptably reliable threshold value of .70, and low reporting just below .70.
@@
 
-Further findings by @flakeConstructValidityValidity2022 and others [@flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020] also show that QMPs not only limit the reported validity of a measurement in a study, the lack of information also creates challenges for replicating researchers.
-Basic content descriptions such as the number of items, the response format, the scoring of the scale were irregular (!!!exact numbers!!!).
+Further findings by @flakeConstructValidityValidity2022 and others [@flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020] also show that QMPs not only limit the reported validity of that measurement.
+The lack of information also creates challenges for replicating researchers.
+Basic content descriptions such as the number of items, the response format, and the scoring of the scale were irregular (!!!exact numbers!!!).
 If it is not clear what items were used, how they were scored, and how they were administered, then it is challenging to reconstruct the measurement for a replication study.
-In turn, the replication may assess the constructs in a substantially similar way, or they even assess different constructs.
+In turn, the replication may assess the constructs in a substantially different way, or even assess different constructs.
 If different constructs are assessed, the replication cannot be seen as a test of the same phenomenon as the original.
-If constructs are assessed differently, the estimated effects in the replication cannot easily be substantially compared to the effects in the original study.
+On the other hand, if the same constructs are assessed very differently, the estimated effects in the replication cannot easily be substantially compared to the effects in the original study.
 In either case, substantial comparisons between original and replication are hindered.
@@
 Our aim is to provide a descriptive account of the reliability, validity, and reporting practices of measurement in replications and related original research.
-We coded several aspects of the measurement reporting practices in replications and original articles.
-Additionally, we estimated the reliability and validity evidence using openly available replication data of the measurement item responses from across multiple labs.
-Our unique contribution is by evaluating reported and the recalculated measurement information for each measure together.
-This allows us to capture a "double whammy" scenario where there is uncertainty in the reliability and validity of these measures when we calculate these ourselves, and where QMPs obscure the ability to evaluate the measure as well as inhibiting future researchers to recreate the measurement to validate it in a new study.
-Besides this, our study also functions as a conceptual replication of earlier research looking at reporting practices and measurement validation using different questions and analyses on a different set of replications and original research.
-While the theory underlying the measurement is important to evaluate how the content of the measure fits to the constructs of interest, because evaluating the theory of a measurement requires domain specific knowledge for each measure we do not address it in this study, we refer interested readers to articles discussing theory in measurement elsewhere [@gehlbachMeasureTwiceCut2011; @humphryPsychologicalMeasurementTheory2017; @borgstedeMeaningfulMeasurementRequires2023; @hasselmanGoingSquaresTheorybased2023].
+We coded several measurement reporting practices in replications and original articles.
+Additionally, we estimated reliability and validity from openly available replication data on item responses.
+This replication data was available across multiple labs.
+Our unique contribution is based on the combination of reported and the recalculated measurement information.
+These two sources combined allows us to capture a "double whammy" scenario where there is uncertainty in the reliability and validity of these measures when we calculate these ourselves, and where QMPs obscure the ability to evaluate the measure as well as inhibiting future researchers to recreate the measurement and validate it in a new study.
+Besides this, our study also functions as a conceptual replication of existing research on reporting practices and measurement validation, by assessing measurement reporting differently and using a novel set of replications and original research.
+While theoretical considerations are  key for evaluating how the content of the measure fits to the constructs of interest, we do not look into these here.
+Evaluating the theory of a measurement requires domain specific knowledge for each measure which is outside of this article's scope.
+We refer interested readers to articles discussing theory in measurement elsewhere [e.g.; @gehlbachMeasureTwiceCut2011; @humphryPsychologicalMeasurementTheory2017; @borgstedeMeaningfulMeasurementRequires2023; @hasselmanGoingSquaresTheorybased2023].
 
@@
 We retrieved the data of Many Labs 1, 2, 3, & 5 [@kleinInvestigatingVariationReplicability2014a; @ebersoleManyLabs32016; @kleinManyLabs22018b; @ebersoleManyLabs52020d] from their respective OSF pages.
-Many Labs 4 [@klein2022many] was excluded, as there was no publicly available replication protocol.
+Many Labs 4 [@kleinManyLabs42022] was excluded, as there was no publicly available replication protocol.
 Additionally, the replication of [@crosbyWhereWeLook2008a] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures.
@@
 
-The replication datasets refer to the publicly available datasets containing the data obtained from all labs of a Many Labs replication.
+The replication datasets refer to the publicly available datasets containing the data obtained from all labs of each Many Labs replication.
 For the analyses, we extracted the scores on the items of each previously identified measure that also met our inclusion criteria specified in the paragraph below.
@@
 We omitted pilot data from the analyses.
-These criteria combined with difficulties in retrieving suitable data from some datasets resulted in a set of item score data from `r length(unique(calculated_reliability_lab_data\$g))` replication sets spread across on average approximately `r round(mean(table(calculated_reliability_lab_data\$g)), 0)` lab locations for our analyses.
+These criteria combined with difficulties in retrieving suitable data from some datasets resulted in a set of item score data from `r length(unique(calculated_reliability_lab_data$g))` replication sets spread across on average approximately `r round(mean(table(calculated_reliability_lab_data$g)), 0)` lab locations for our analyses.
 
@@
 
-After the initial coding, we made minor revisions to 14 of the 20 QMP items from the preregistered coding protocol.
+After the initial coding, we made minor revisions to fourteen of the twenty QMP items from the preregistered coding protocol.
 These items were changed after familiarizing ourselves with the way measurement was reported, and it became clear that our criteria were too stringent in the exact way and degree of detail in which to present things.
@@
 
-We initially intended to form a QMP index using these QMP items and perform regression analyses using this index, but this index could not be validated properly and its results would be misleading to present here.
-A more detailed explanation of what was omitted and why, as well as the results from the preregistered analyses themselves can be found in [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd).
-The items are currently used as individual descriptives on the reporting practices in our sample.
+We initially intended to form a QMP index using these QMP items and perform regression analyses using this index, but this index could not be validated properly and its results would be misleading to present here in the main article.
+A more detailed explanation of what was omitted and why, as well as the results from these preregistered analyses can be found in [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd).
 
@@
 We calculated reliability for each measure from the replication datasets with suitable data for each lab the measure was used in.
-We calculated both Cronbach’s alpha, as well as its standard error using formulas 2 & 3 from @duhachekAlphasStandardError2004a to calculate the standard error in the meta-analysis.
-Then we entered these two values into a meta-analysis of the reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analysis [@botellaManagingHeterogeneityVariance2012; @lopez-ibanezReliabilityGeneralizationMetaanalysis2024; @vacha-haaseReliabilityGeneralizationExploring1998].
+We calculated both Cronbach’s alpha, as well as its standard error using formulas 2 & 3 from @duhachekAlphasStandardError2004a.
+Then we entered these two values into a meta-analysis of the measure's reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analysis [@botellaManagingHeterogeneityVariance2012; @lopez-ibanezReliabilityGeneralizationMetaanalysis2024; @vacha-haaseReliabilityGeneralizationExploring1998].
 Using RG Meta-Analysis we quantified the degree of true variation (or heterogeneity) in reliability coefficients across lab locations.
@@
 These indicators have received criticism as indicators of heterogeneity, especially when within study sample sizes are small and power to detect heterogeneity is low [@hoaglinMisunderstandingsCochransTest2016; @pereiraCriticalInterpretationCochrans2010].
-Therefore, we also present the prediction interval and suggest that the heterogeneity results should be viewed with a critical eye [@borensteinAvoidingCommonMistakes2024].
+Therefore, we also present the prediction interval and implore that the heterogeneity results should be viewed critically [@borensteinAvoidingCommonMistakes2024].
 We implemented no correction for bias, because the Many Labs replications were not at risk of publication bias.
 
-Our analyses will focus on Cronbach’s Alpha, because its common use in research allows us to make comparisons between calculated and reported reliabilities.
+Our analyses will focus on Cronbach’s Alpha, because it is common in research, which also allows us to make comparisons between calculated and reported reliabilities.
 Furthermore, we were able to calculate the standard error of alpha to be used in the RG meta-analysis.
@@
 First, unidimensionality is one of the assumptions of Cronbach's Alpha.
-If this assumption does not hold for a measure, Cronbach's Alpha gives a biased and uninformative estimate of the reliability.
-Second, all measurement items for which unidimensionality was checked, were used to form a singular index of one latent vasriable.
+If this assumption does not hold for a measure, our Cronbach's Alpha estimates give a biased estimate of the reliability.
+Second, all measurement items for which unidimensionality was checked, were used to form a singular index of one latent variable.
 Certainly, not all singular indexes require the underlying latent factor model to be unidimensional (e.g., general intelligence can be used as a variable on its own or sub-divided in multiple components such as numerical and verbal intelligence).
-Still, we believe it is not unreasonable to assume that for most of our measures we should observe a unidimensional factor model to have at least adequate fit.
+Still, we believe it is not unreasonable to assume that for most of the single index measures we should observe a unidimensional factor model to have at least adequate fit.
 
@@
 It then compares the eigenvalues (an indication of how much variance is explained by that factor) of each factor to the eigenvalues for that factor if the data matrix was effectively random.
-If only the single factor has an eigenvalue that is significantly higher than the eigenvalue when the data matrix is random, the test is passed.
+If only the first factor has an eigenvalue that is significantly higher than the eigenvalue when the data matrix is random, the test is passed.
 We chose a combination of these two tests, as the RMSEA is known to be biased for models with small degrees of freedom [@kennyPerformanceRMSEAModels2015], while the parallel analysis may be less suited if a two or more factor solution would also fit the sample item data.
@@
 
-```{r validity_evidence_reporting}
+```{r validity_evidence_reporting, include = FALSE, eval = FALSE}
 table(coded_data_original$sel_psychometric_evidence_REV)
@@
 
-Figure \@ref(fig:Plot1Factor) below show the result of our unidimensionality test.
-`r apa_num((sum(unidimensionality_graph_data$RMSEA < .08, na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)` % of labs were below our RMSEA .08 threshold, while for `r apa_num((sum(unidimensionality_meta_data$beta < .08, na.rm = TRUE)), numerals = FALSE)` measures of the total `r apa_num(nrow(unidimensionality_meta_data), numerals = FALSE)` the mean across labs was below this threshold.
-Furthermore, the RMSEA shows considerable variation within measures, with the standard deviation ranging from `r apa_num(min(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))` as the lowest to all the way up to `r apa_num(max(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))`.
-The parallel analysis results similarly showed inconsistency both across and within measures.
-While `r apa_num((sum(unidimensionality_graph_data$N_factors_capped == "1", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% of labs returned a single factor solution, `r apa_num((sum(unidimensionality_graph_data$N_factors_capped == "2", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% returned a two-factor, and `r apa_num((sum(unidimensionality_graph_data$N_factors_capped == "2", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% returned three or more factors.
-The remainder did not converge.
-The lack of convergence was an also an issue for the CFA used for the RMSEA check.
-The CFA failed to converge for `r apa_num((sum(is.na(unidimensionality_graph_data$RMSEA)) / nrow(unidimensionality_graph_data)) * 100)`% of labs.
-In the case of the @defruytCloningersPsychobiologicalModel2000 measure all labs failed to converge.
-Convergence in the other cases was the result of either the severe misfit of our factor models or a lack of sample size to stably estimate these models.
-In the end, `r apa_num((sum(unidimensionality_graph_data$unidimensional == "Yes", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% of labs passed our unidimensionality check.
-
-```{r PlotData1FactorRMSEA}
+```{r PlotData1FactorRMSEA, warning = FALSE}
+# load in the FA_list data
+FA_list <- list(fa_caruso_2012, fa_husnu_2010, fa_nosek_2002_math, fa_nosek_2002_art,
+                fa_anderson_2012_swl, fa_anderson_2012_pa, fa_anderson_2012_na,
+                fa_giessner_2007, fa_norenzayan_2002, fa_zhong_2006, fa_monin_2001_most,
+                fa_monin_2001_some, fa_cacioppo_1983_arg, fa_cacioppo_1983_nfc, 
+                fa_de_fruyt_2000, fa_albarracin_2008_verb, fa_albarracin_2008_math,
+                fa_shnabel_2008, fa_vohs_2008)
+
+# create the base dataframe
 unidimensionality_graph_data <- data.frame(RMSEA = c(NA),
@@
 
+# adding the info from the FA_list to our data.
 for (i in 1:19){
@@
 
-```{r Plot1Factor, fig.cap = "Distributions of calculated RMSEA of a single-factor model fit calculated for the responses on a measure at each lab location, across the nineteen measures for which raw data was available on which a factor model could be fitted.
+Figure \@ref(fig:Plot1Factor) below show the result of our unidimensionality test.
+`r apa_num((sum(unidimensionality_graph_data$RMSEA < .08, na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)` % of labs were below our RMSEA .08 threshold, while for `r apa_num((sum(unidimensionality_meta_data$beta < .08, na.rm = TRUE)), numerals = FALSE)` measures of the total `r apa_num(nrow(unidimensionality_meta_data), numerals = FALSE)` the mean across labs was below this threshold.
+Furthermore, the RMSEA shows considerable variation within measures, with the standard deviation ranging from `r apa_num(min(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))` as the lowest to all the way up to `r apa_num(max(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))`.
+The parallel analysis results similarly showed inconsistency both across and within measures.
+While `r apa_num((sum(unidimensionality_graph_data$N_factors_capped == "1", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% of labs returned a single factor solution, `r apa_num((sum(unidimensionality_graph_data$N_factors_capped == "2", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% returned a two-factor, and `r apa_num((sum(unidimensionality_graph_data$N_factors_capped == "2", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% returned three or more factors.
+The remainder did not converge.
+The lack of convergence was an also an issue for the CFA used for the RMSEA check.
+The CFA failed to converge for `r apa_num((sum(is.na(unidimensionality_graph_data$RMSEA)) / nrow(unidimensionality_graph_data)) * 100)`% of labs.
+In the case of the @defruytCloningersPsychobiologicalModel2000 measure all labs failed to converge.
+Convergence in the other cases was the result of either the severe misfit of our factor models or a lack of sample size to stably estimate these models.
+In the end, `r apa_num((sum(unidimensionality_graph_data$unidimensional == "Yes", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% of labs passed our unidimensionality check.
+
+```{r Plot1Factor, warning = FALSE, fig.cap = "Distributions of calculated RMSEA of a single-factor model fit calculated for the responses on a measure at each lab location, across the nineteen measures for which raw data was available on which a factor model could be fitted.
 The red horizontal line separate the replicated from the non-repicated measures.
@@
 
-```{r check_on_Omega_convergence}
+```{r check_on_Omega_convergence, warning = FALSE}
 is_mostly_na <- function(x){
@@
 
-sum(Omega_convergence_vector)
+# sum(Omega_convergence_vector)
 ```
@@
 
-```{r PlotOmegaDistributions, warning = false, fig.cap = "Distributions of calculated McDonald’s Omega t  calculated for the responses on a measure at each lab location, across the eighteen measures for which raw data was available from which McDonald’s Omega t coefficients could be calculated.
+```{r PlotOmegaDistributions, warning = FALSE, fig.cap = "Distributions of calculated McDonald’s Omega t  calculated for the responses on a measure at each lab location, across the eighteen measures for which raw data was available from which McDonald’s Omega t coefficients could be calculated.
 The N.Omg column besides the figure shows the number of lab locations for which an Omega coefficient could be successfully calculated.
@@
 
-```{r QMPtable}
+```{r QMPTable}
 # create informative Measurement Practice Labels 
-MPractice <- c("Reliability is reported", "It is clear if the measure existed or is newly created",    "Specifc version of the measure is specified", "Validity evidence from a factor analysis is presented",   "The measured variable is defined", "The choice of measure selection or creation is justified",    "The implemented operationalisation is justified", "The source of the measure is provided",    "Psychometric evidence from the study is given", "Psychometric evidence from an earlier study is given",    "The administration format and environment are described", "The administration procedure is described",   "The number of items are described", "The number of response options are described",    "The recoding of responses is described", "The creation of the index is described",    "Example items are presented in text or supplement", "Any administration format changes are mentioned",    "Administration format changes are justified/validated", "Any translations are mentioned",    "Translated measures are justified/validated", "Any changes in number of items or response options are mentioned",    "Changes in number of items or response options are justified/validated")
+MPractice <- c("Reliability is reported", "It is clear if the measure existed or is newly created",    "Exact version of the measure is specified", "Validity evidence from a factor analysis is presented",   "Measured variable is defined", "Choice of measure selection or creation is justified",    "Implemented operationalisation is justified", "Source of the measure is provided",    "Psychometric evidence from the study is given", "Psychometric evidence from an earlier study is given",    "Administration format and environment are described", "Administration procedure is described",   "N items are described", "N response options are described", "Recoding of responses is described", "Creation of the index is described", "Text or supplement has example items", "Administration format changes are mentioned",    "Administration format changes are justified/validated", "Translations are mentioned",    "Translated measures are justified/validated", "Changes in N items or response options are mentioned",    "Changes in N items or response options are justified/validated")
 
@@
 # print the table in apa formatting 
-apa_table(QMP_table, align = c("l", "r", "r", "r"), caption = "Ratio of QMPs and number of applicable measures, for original and replication", note = "The first number in QMP org and QMP rep is the ratio of measures for which the practice in that row was not conducted well by our standards.
-The number between brackets indicates the number of measures for which the practice was applicable.", escape = FALSE, placement = "htp")
+apa_table(QMP_table, align = c("l", "r", "r", "r"), 
+          caption = "Ratio of QMPs and number of applicable measures, for original and replication", 
+          note = "The first number in QMP org and QMP rep is the ratio of measures for which the practice in that row was not conducted well by our standards.
+The number between brackets indicates the number of measures for which the practice was applicable.", escape = FALSE, placement = "htp", booktabs = TRUE)
 ```
@@
 To assess psychological phenomena we need measurement that is valid and reliable for our constructs.
-However, we noted first is that little reliability and validity evidence was reported.
-Second, our reanalysis of the reliability and validity of the measures showed inconsistent reliability and validity support.
-Finally, we observed a lack of transparent reporting, which makes it difficult for future researchers to reuse and build upon the validation of existing measurements.
+However, we noted that little reliability and validity evidence was reported, and our reanalysis of the reliability and validity of the measures showed inconsistent reliability and validity support.
+Furthermore, we observed a lack of transparent reporting, which makes it difficult for future researchers to reuse and build upon the validation of existing measurements.
 
@@
 Another factor may be observed in the fact that we observed that replications generally reported less reliability and psychometric validity evidence.
-This could be because replications implicitly defer the reporting of validity and reliability evidence to the original study.
-However, it was not uncommon for the replication to use different measures than the original study, and if it was not set in stone that the same measure as the original was used, then it stands to reason that the choice of measure should be motivated based on reliability and validity evidence.
+This could be because replications implicitly defer the responsibility of reporting validity and reliability evidence to the original study.
+However, it was not uncommon for the replication to use modified or different measures from the original study.
+If it was not set in stone that the same measure as the original was used, then it stands to reason that in any case the choice of measure should be motivated based on reliability and validity evidence.
 Furthermore, this does not explain the lack of reliability and validity reporting in the original studies.
-It may unfortunately be more reasonable to assume that many of these measures are just not validated before (or even after) use.
-
-This is not merely based on us guessing, when we recalculated the reliability coefficients and factor structure of the measures used in the replication projects, the observed reliability and validity of several measures did not convincingly show that these would be valid if presented alongside the measure in a study.
-While few measures were consistently not reliable and valid and some were even consistently reliable and valid, many were reliable and valid in a portion of the labs.
-We also noted that some measures had convergence issues, where for some labs we could not get the factor model nor Omega coefficient results.
-This may have been because of sample size issues, or the small number of items common in the replication measures, but gross misfit is also possible.
+It may unfortunately be more likely that many of these measures are simply not validated before (or even after) use.
+
+This is not merely based on guessing.
+When we recalculated the reliability coefficients and factor structure of the measures used in the replication projects, the observed reliability and validity of several measures did not convincingly show that these would be valid if presented alongside the measure in a study.
+While some measures were consistently not reliable and valid and some others were consistently reliable and valid, most were reliable and valid in some labs but not others.
+We also noted that some measures had convergence issues, where for some labs we could not get the factor model to fit nor Omega coefficient results.
+This may have been because of sample size issues, or the small number of items we often observed in the replication measures.
+However, gross misfit is also possible.
 Although, the psychometric indicators we used were applied rather broadly across a spectrum of different measures, and should not be used to make individual inferences for the measures.
-As a general overview, our results show that reliability and validity for these measures could be poor.
-
-We also observed at when measures which came with a reported Cronbach's Alpha in the original study, their average Cronbach's Alpha observed among the replications were all relatively high.
+As a general overview, our results strongly indicate that these measures were frequently neither reliable nor valid for the contexts they were used in.
+
+We also observed that when a Cronbach's Alpha was reported for a measure in an original study, then their average Cronbach's Alpha observed among the replications were consistently relatively high.
+Meanwhile when no Cronbach's Alpha was reported in the original study, the reliability was often relatively low.
 This aligns with existing research indicating bias in reported Cronbach's Alpha values, with an excess of reported values at the common acceptably reliable threshold value of .70, and low reporting just below .70 [@husseyAberrantAbundanceCronbachs2023].
-Thus authors may be less inclined to report reliabilities that fall below an acceptable threshold.
-In combination with our inconsistent reliability and validity evidence this bias in reporting could create a false sense of security when looking only.
-It is possible that reliability and validity are only reported when they are sufficient, and not otherwise.
+Authors may be less inclined to report reliabilities when they fall below an acceptable threshold, but not otherwise.
+In combination with our inconsistent reliability and validity evidence this bias in reporting could create a false sense of security when looking only at the information that is reported in the literature.
 
@@
 We also found that about two-thirds of the measurements were modified between original and replication, and specific modifications were rarely validated or justified.
-This raises some questions around the label direct replication.
-For example, the conscientiousness measure used for the replication of @defruytCloningersPsychobiologicalModel2000 was reduced from original NEO-PI-R 30-item measure to a two-item measure.
+This raises some questions around atributing the label direct replication to some of these studies.
+For example, the conscientiousness measure used for the replication of @defruytCloningersPsychobiologicalModel2000 was reduced from original NEO-PI-R 30-item measure to a two-item measure in the replication.
 It is highly unlikely that a measure with such a significant change would have a comparable validity and reliability to the original, and we did unsurprisingly observe convergence issues with validity as well as low reliability for this measure.
 
-One notable difference to @flakeConstructValidityValidity2022 is that replications did on average have less QMPs than original research.
+One notable difference compared to @flakeConstructValidityValidity2022 is that in our results replications did on average have less QMPs than original research.
 We believe that this is in part due to the structured way in which the Many Labs protocols were written up.
@@
 We commend the tremendous effort involved in the creation of the Many Labs projects, and we understand that for feasibility some corners had to be cut.
-Similarly, we understand that proper validation of psychological measures is not a responsibility that should be placed on any one original study.
-However, we would argue that full transparent measurement reporting is a responsibility both replications and original studies do carry.
-Furthermore, regardless of difficulty in validating measures, its necessity cannot be ignored if substantive interpretations based on the measurement data are desired.
+Similarly, we understand that complete validation of psychological measures is not a responsibility that should or can be placed on any one study.
+However, we would argue that full transparent measurement reporting is a responsibility both replications and original studies do have.
+Furthermore, even though validating measures is difficult, its necessity cannot be ignored.
+At one point this measure has to be validated properly, or else we cannot be certain that substantive interpretations on the basis of this measure are substantiated.
 
@@
 We consider these checks to be indicators of the overall construct validity in our sample.
-The checks should not be interpreted as concrete tests of measurement fit, nor should they be interpreted at the individual measurement level.
+The checks should not be interpreted as complete tests of validity, nor should they be interpreted at the individual measurement level.
 Future research may want to deep dive into this specific topic and focus on doing theory informed factor analysis tests on measurement data.
@@
 
-The two main issues we believe that should be addressed are: the prevalence of using non-validated measurement, and the lack of transparency surrounding measurement reporting.
-Unfortunately, there are no easy solutions to fix these issues.
-They will require significant efforts involving multiple members of the scientific community to bring about significant change.
-However, the positives are that these issues are interrelated, in that solving transparency will benefit greater validation of measures.
-
-Thus, first we recommend that reporting standards for measurement deserve a more central place.
+The two main issues we believe that should be addressed in the literature are: the common use of non-validated measurement, and the lack of transparency surrounding measurement reporting.
+Unfortunately, there is no easy fix to these issues.
+Significant efforts are required, involving multiple members of the scientific community to bring about significant change.
+However, the positives are that these issues are interrelated, because solving transparency will benefit greater validation of measures, and that every little bit can help.
+
+First we recommend that reporting standards for measurement deserve a more central place.
 We found that reporting reliability and validity information was the exception rather than the rule, and even basic information such as how many items were in the measure was not always present.
-The @americaneducationalresearchassociationStandardsEducationalPsychological2014 guidelines exist to guide researchers in the creation and validation of scales, but are not intended as general measurement reporting guidelines.
-Similarly, the APA guidelines (???CITE???) only briefly address reliability and validity information but say little on other measurement reporting.
-While statistical reporting standards and guidelines have proliferated, even resulting in official recommendations from the ASA [@wassersteinASAStatementPValues2016], a high-profile push for measurement reporting standards is lacking.
-We believe that measurement reporting standards deserve to be highlighted as much as statistical result reporting,.
-Even well reported statistics lack substantial interpretability without valid measurement, while a well reported measurement can be informative to future research on its own.
+The @americaneducationalresearchassociationStandardsEducationalPsychological2014 guidelines exist to guide researchers in the creation and validation of scales, but are not tailored as guidelines for general measurement reporting.
+The APA guidelines [@AmericanPsychologicalAssociation2020] do address many of the same reporting practices we assessed, however our findings and those of other research shows that uptake of these standards is minimal.
+Meanwhile, statistical reporting standards and guidelines have had a stronger place in the field and among journals, including recommendations from the ASA [@wassersteinASAStatementPValues2016].
+A high-profile push for measurement reporting standards is lacking.
+We believe that measurement reporting standards deserve to be highlighted as much as statistical result reporting.
+after all, even well reported statistics lack have to be understood within the context of the measurement.
 
 Transparent measurement reporting also has the advantage that it enables future researchers to recreate the original measure.
-This point is critical to fueling our second recommendation: as a community we need to systematically evaluate and revise our existing measures.
-First, existing measures need to be reusable.
+This point is critical to fueling our second recommendation: as a community we need to systematically evaluate and revise our measures.
+To do so existing measures need to first of all be reusable.
 Then researchers need to reuse existing measures.
@@
 Furthermore, they propose an open repository of measurement protocols to facilitate the discovery of measures and building an evidence base.
-For the third and fourth step, the scientific community needs to analyse the validity and reliability of all uses of the measure such that they can be fairly compared to each other.
+For the third and fourth step, two things are needed.
+First, there should be a space in the scientific literature for persistent measurement evaluation.
+Second, the data obtained from the measurement should be reusable in a more comprehensive analyses of the measure across contexts.
 For this it would be best if the original data of the item responses and demographics is shared for each use of the measure.
-This way the measure's validity and reliability can be recomputed similarly to what was done in our analyses, but with a closer link to theory.
-Otherwise, the summary statistics such as the variance-covariance structure, means, and standard deviations should be shared as these are sufficient for several factor analysis models.
-
-Furthermore, researchers should report and evaluate our measures using more informative indicators.
+This way the measure's validity and reliability can be recomputed similarly to what was done in our analyses, but hopefully with a closer link to theory.
+Otherwise, the summary statistics such as the variance-covariance structure, means, and standard deviations should be shared as these are sufficient for many basic factor analysis models.
+
+Furthermore, researchers should report and evaluate their measures using more informative indicators.
 Cronbach's Alpha on its own gives only limited information the quality of a scale, and comes with strong assumptions [@cortinaWhatCoefficientAlpha1993; @sijtsmaUseMisuseVery2009].

### 2025-10-06 Scripts/Manuscript/manuscript.Rmd
Rewrites

@@
 classoption       : man
-output            : papaja::apa6_pdf
+output            : papaja::apa6_docx
 knit              : worcs::cite_all
@@
 library(grid)
+library(patchwork)
 
@@
 
-\renewcommand{\arraystretch}{0.7} <!-- reducing the line spacing within tables -->
-
-\renewcommand{\topfraction}{.8} <!-- max fraction of page for floats at top -->
-
-\renewcommand{\bottomfraction}{.8} <!-- max fraction of page for floats at bottom -->
-
-\renewcommand{\textfraction}{.15} <!-- min fraction of page for text -->
-
-\renewcommand{\floatpagefraction}{.8} <!-- min fraction of page that should have floats .66 -->
+\renewcommand{\arraystretch}{0.7}
+
+<!-- reducing the line spacing within tables -->
+
+\renewcommand{\topfraction}{.8}
+
+<!-- max fraction of page for floats at top -->
+
+\renewcommand{\bottomfraction}{.8}
+
+<!-- max fraction of page for floats at bottom -->
+
+\renewcommand{\textfraction}{.15}
+
+<!-- min fraction of page for text -->
+
+\renewcommand{\floatpagefraction}{.8}
+
+<!-- min fraction of page that should have floats .66 -->
 
@@
 
-The challenge with measurement in quantitative psychological research is that unlike height or weight, psychological constructs cannot be directly measured.
-Instead we use scores from a measurement as a proxy indicator for that psychological construct.
-However, we cannot simply assume that any measure we create will form a good indicator of the construct.
-We have to substantiate this.
-Psychometrics can be used to statistically estimate the measure's validity, still validating a measure entails a substantial research effort.
-Regardless, the burden of validating a measure – besides some well-established psychiatric and personality measures – is most often placed on the researcher conducting a study of a psychological phenomenon.
-When the effort involved in validating a measure is relegated to be only a component of a study, then how well does the measurement validation process go?
-
-## Measurement Validation
-When validating a measure of a psychological construct, two main psychometric components are of interest: construct validity & reliability.
-Construct validity refers to whether the variance in the measured item scores between participants can be attributed to variance in unobserved constructs between participants [@cronbachConstructValidityPsychological1955; @vazireCredibilityReplicabilityImproving2022].
-Reliability refers to how consistent a participant's responses on a measurement are [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011].
-Reliability is part of the validation of a measure because a measure that does not consistently capture a participant's response, cannot accurately capture a construct [@crutzenScaleQualityAlpha2017b].
-As an example, suppose we have a measure and we want it to measure general intelligence, and we want to validate this as a measure of general intelligence.
-We would see our measurement as construct valid if being more intelligent resulted in generally scoring higher on our test, and our measurement would be reliable if the score of people on our measure consistently reflected their actual intelligence.
-
-In practice construct validity is often evaluated through factor analysis.
-In factor analysis, a model is fitted to explain as much of the variance of multiple items through a smaller number of factors, or weighted averages of the item scores.
-To fit a factor model, the number of factors are first specified, and then the fit of that model on the data can be evaluated.
-Preferably, a model with the number of factors corresponding to the number of constructs of interest should show adequate fit on the data.
-Additionally, the items aimed at the same construct should be statistically related to the same factor.
-For example, suppose items 1 through 5 from our general intelligence measure are meant to capture verbal intelligence, and items 6 through 10 are distinctly about mathematical intelligence.
-To establish construct validity, we want to find that a two factor model on our intelligence measure to show adequate fit, with one factor to which only items 1 through 5 relate strongly, and one to which only items 6 through 10 relate strongly.
-However, even in this ideal scenario, the factor relations may not be stable for this measure in other contexts and implementations, a concept known as measurement invariance [@hornPracticalTheoreticalGuide1992; @cheungDirectComparisonApproach2012].
-
-Reliability gives us an indication of how much our measure captures the signal of our measured variables over noise.
-Psychometrics offers various ways to assess reliability empirically [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011].
-For example, we can compare scores on multiple equivalent forms of the test, between multiple different raters, or between multiple different timepoints of the same test.
-Still, the most common way to assess reliability for single measurement instances is through internal consistency indicators.
-The most common internal consistency indicator is the Cronbach's Alpha coefficient.
-The Cronbach's Alpha coefficient is defined as “the average of all the possible split-half coefficients for a given test” [@cronbachCoefficientAlphaInternal1951].
-Here split-half coefficients being the correlation between two halves of the same test.
-It can be calculated by taking the ratio of interitem covariance to total variance and multiplying it by n / (n - 1), where n is the number of items in the scale.
-However, Cronbach's Alpha comes with strong assumptions on the underlying factor structure, including that the measure is unidimensional, so a single factor.
-Furthermore, because Cronbach's alpha is proportional to the total variance in the target variable in the sample, it is an indicator of reliability within a particular sample and not of the reliability of the measure in general.
-Despite this many researchers report and interpret Cronbach's Alpha as a universal quality of the measure [@cortinaWhatCoefficientAlpha1993; @schmittUsesAbusesCoefficient1996].
-
-Thus, psychometric tests are useful but they have their limitations.
-Even simple factor analyses - unless the amount of variance explained by the factors is large and the factor structure is clear - require sample sizes of at least 100 [@maccallumSampleSizeFactor1999; @gorsuchFactorAnalysis2013].
-Furthermore, even in the latter case factor analysis may not converge with small sample sizes.
-If we want to know the reliability and validity of not just one measurement but for the measure across multiple contexts, we need to conduct multiple studies.
-Additionally, larger sample sizes per relevant group to detect meaningful effects when checking for measurement invariance across groups [@meadePowerPrecisionConfirmatory2007; @frenchMeasurementInvarianceTechniques2016; @koziolImpactModelParameterization2018].
-However, what we observe in the literature is that most measures are reused once or never [@elsonPsychologicalMeasuresArent2023; @anvariFragmentedFieldConstruct2025; @anvariDefragmentingPsychology2025], let alone that they are systematically tested on reliability and validity.
-@maireadshawMeasurementPracticesLargescale2020 checked the factor structure and reliability of measures used in the Many Labs 2 replication project [@kleinManyLabs22018b] on the available data.
-They observed that for the scales they assessed, no factor model fit congruent with the use of the scales met all of their evaluation criteria.
-Furthermore, the overall sample Cronbach's alpha level of all scales was below .5, a level of reliability far below what many would consider acceptable for almost all research purposes.
+The challenge with measurement in quantitative psychological research is that unlike height or weight, psychological constructs cannot be directly measured, as they cannot be directly observed.
+Instead, we use scores from a measurement as an indicator for a psychological construct.
+Yet, it cannot simply be assumed that any measure will form a good indicator of the constructs of interest.
+The measure has to be validated by establishing the reliability and construct validity of the measure.
+"Reliability refers to the consistency of scale scores when a construct is assessed multiple times or in multiple ways" [@crutzenScaleQualityAlpha2017b; pp.
+244].
+Meanwhile, construct validity refers to whether the variance in the measured item scores between participants can be attributed to the variance in the unobserved construct(s) of interest between participants [@cronbachConstructValidityPsychological1955; @vazireCredibilityReplicabilityImproving2022].
+
+However, research indicates that measures often lack reliability and construct validity evidence !!!CITE!!!, either because the evidence is not reported, or because the measures are not validated.
+@flakeMeasurementSchmeasurementQuestionable2020 dubbed these practices - that raise doubts about a measurement’s validity - Questionable Measurement Practices (QMPs), being a term analogous to Questionable Research Practices [QRPs; Simmons et al.
+(2011); John et al.
+(2012); Wicherts et al.
+(2016)].
+Existing research has already shown practices that reflect QMPs to be relatively common in both replication and original studies !!!CITE!!!.
+The purpose of this study is to provide a combined overview of the information on the reporting practices of measurement in replication and original with reliability and construct validity indices obtained from the shared item response data.
+By combining information on reporting with our own calculated indices, we can reflect on which validity issues lie in reporting and which are an issue with the measurement itself.
 
@@
 
-As illustrated in the previous section, validating measurement is a complex but essential part of doing psychological research.
-Yet the scientific community has not fully stepped up to this challenge [@flakeMeasurementSchmeasurementQuestionable2020].
-A large number of measures used in the psychological literature lack information on the validity and reliability of the measure [@hoganEmpiricalStudyReporting2004; @flakeConstructValidationSocial2017; @flakeConstructValidityValidity2022].
-
-Questionable Measurement Practices (QMPs) are practices that raise doubts about a measurement’s validity [@flakeMeasurementSchmeasurementQuestionable2020] and have been coined as a term analogous to Questionable Research Practices [QRPs; @simmonsFalsePositivePsychologyUndisclosed2011a; @johnMeasuringPrevalenceQuestionable2012a; @wichertsDegreesFreedomPlanning2016a].
-QMPs range from lack of transparency in the reporting of the measure and unclear motivation in choice of measure to poor justification for modifications of a measure and procedure of an existing measure [@flakeMeasurementSchmeasurementQuestionable2020].
-@flakeConstructValidityValidity2022 documented QMPs among 100 replications and their respective original articles from the Reproduciblity Project Psychology [@opensciencecollaborationEstimatingReproducibilityPsychological2015].
-They coded the number of measures, the number of items in the measure, and the information that was reported describing the measure and justifying its use.
+One issue that has been observed with respect to measurement validation is that the reported measurement information is typically insufficient for readers to understand, evaluate, and reuse the measurement that was used [!!!CITE].
+@flakeConstructValidityValidity2022 documented the measurement reporting practices among 100 replications and their respective original articles from the Reproducibility Project Psychology [@opensciencecollaborationEstimatingReproducibilityPsychological2015].
+They coded the number of measures, the content of the measures, and information describing and justifying the measurement.
 They observed limited reporting of evidence demonstrating the reliability and validity of the measurement.
 Additionally, only eight of the 40 translated scales contained validity evidence for the translated version.
-Furthermore, reporting of reliability may not only be little, but also biased.
-@husseyAberrantAbundanceCronbachs2023 observed a disproportional amount of Cronbach's Alpha values at the common acceptably reliable threshold value of .70, and low reporting just below .70.
-Thus the lack of reported measurement evidence may on occasion be hiding psychometric skeletons in the closet.
-
-Further findings by @flakeConstructValidityValidity2022 and others [@flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020] also show that QMPs not only limit the reported validity of that measurement.
-The lack of information also creates challenges for replicating researchers.
-Basic content descriptions such as the number of items, the response format, and the scoring of the scale were irregular (!!!exact numbers!!!).
-If it is not clear what items were used, how they were scored, and how they were administered, then it is challenging to reconstruct the measurement for a replication study.
-In turn, the replication may assess the constructs in a substantially different way, or even assess different constructs.
+A similar lack of reliability and validity reporting has been observed in other studies as well [@hoganEmpiricalStudyReporting2004; @flakeConstructValidationSocial2017].
+If readers cannot glance the construct validity and reliability of a measure from the reported information, then readers lack the basic information needed to determine whether the measured variables are actually related to the constructs of interest.
+In turn, if we cannot determine whether the constructs of interest are captured in the measured variables or not, then the relation of the results of the statistical analysis using these variables and any psychological phenomena of interest is also strenuous.
+In short, if the reported information does not show that the measurement was valid, then any substantive conclusions from the data are unfortunately left unsubstantiated.
+
+Further findings by @flakeConstructValidityValidity2022 and others [@flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020] show that measurement reporting was not only limited in terms of the reliability and validity evidence needed to evaluate the measure.
+The lack of information was also observed for basic content descriptions such as the number of items, the response format, and the scoring of the scale were irregular.
+This creates challenges for future researchers that want to reuse to measurement.
+Specifically for replication studies attempting to reconstruct the measurement from these incomplete descriptions, they may end up with a measurement that assesses the constructs in a substantially different way from the original study, or even assess different constructs altogether.
 If different constructs are assessed, the replication cannot be seen as a test of the same phenomenon as the original.
-On the other hand, if the same constructs are assessed very differently, the estimated effects in the replication cannot easily be substantially compared to the effects in the original study.
+If the same constructs are assessed, but in a substantially different way, the estimated effects in the replication cannot easily be put side-by-side with the effects in the original study.
 In either case, substantial comparisons between original and replication are hindered.
-
-## Research Aim
-
-Our aim is to provide a descriptive account of the reliability, validity, and reporting practices of measurement in replications and related original research.
-We coded several measurement reporting practices in replications and original articles.
-Additionally, we estimated reliability and validity from openly available replication data on item responses.
-This replication data was available across multiple labs.
-Our unique contribution is based on the combination of reported and the recalculated measurement information.
-These two sources combined allows us to capture a "double whammy" scenario where there is uncertainty in the reliability and validity of these measures when we calculate these ourselves, and where QMPs obscure the ability to evaluate the measure as well as inhibiting future researchers to recreate the measurement and validate it in a new study.
-Besides this, our study also functions as a conceptual replication of existing research on reporting practices and measurement validation, by assessing measurement reporting differently and using a novel set of replications and original research.
-While theoretical considerations are  key for evaluating how the content of the measure fits to the constructs of interest, we do not look into these here.
-Evaluating the theory of a measurement requires domain specific knowledge for each measure which is outside of this article's scope.
-We refer interested readers to articles discussing theory in measurement elsewhere [e.g.; @gehlbachMeasureTwiceCut2011; @humphryPsychologicalMeasurementTheory2017; @borgstedeMeaningfulMeasurementRequires2023; @hasselmanGoingSquaresTheorybased2023].
+The inability to reuse a measure does not only affect replications however, it also limits our ability to validate the measure thoroughly.
+Even if the measure is shown to be construct valid in one context, the factor relations may not be stable for this measure in other contexts and implementations, a concept known as measurement invariance [@hornPracticalTheoreticalGuide1992; @cheungDirectComparisonApproach2012].
+While it is important to assess measurement (in)variance before using measures in a new context, if that measure is not reusable, the invariance cannot even be assessed.
+
+Our first aim is to extend these existing findings on measurement reporting practices with a descriptive account of these practices for the Many Labs replications and the related original studies.
+We evaluate to what extent the reporting and use of item-based measurement scales in our sample allows us to evaluate and reuse the measurement.
+We do not ourselves evaluate whether the reported measurement information provide sufficient justification for its use, merely that information is reported such that that part of the measurement can be evaluated.
+We extend earlier investigations through new questions about the presence of justification for measurement selection or creation, item transformations such as reverse coding being described, the administration format being described, a change in the number of items from the source, whether changes in items response options, or number of items, or administration were validated or justified.
+All of our measurement reporting items were inspired by and categorized based on the QMP table in @flakeMeasurementSchmeasurementQuestionable2020.
+
+We chose the Many Labs replications and associated original studies as our sample, due to them being of particular interest.
+The Many Labs replications were a series of large-scale collaborations in which multiple labs across the world directly replicated classic and contemporary psychological studies [@kleinInvestigatingVariationReplicability2014a; @ebersoleManyLabs32016; @kleinManyLabs22018b; @ebersoleManyLabs52020d; @kleinManyLabs42022].
+The original studies chosen for replication in the Many Labs were not only picked based on ease and feasibility, but importantly for us they were also picked to display a diverse range of effects that were also of key interest to the field.
+This makes these studies an important sample to evaluate, because the replicated effects represent a broad range of relevant findings.
+Furthermore, because the Many Labs projects used preregistered and documented structured protocols, we expect the measurement reporting for the replications to represent a high standard within the field.
+Any issues in measurement reporting here might suggest that other replications could face similar or greater challenges.
+
+## Reliability
+
+Psychometrics offers various ways in which to assess construct validity and reliability [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011].
+It is often the results from these psychometric analyses that form one of the pre-requisite pieces of evidence for assessing whether or not the measure is valid or not.
+
+When psychometric indicators are reported - which as mentioned earlier is not common - it is often limited to Cronbach's Alpha, a commonly used indicator for reliability.
+Cronbach's Alpha comes with strong assumptions that are themselves rarely tested [@crutzenScaleQualityAlpha2017b].
+Furthermore, research by @husseyAberrantAbundanceCronbachs2023 has shown evidence that the reporting of reliability may not only be little, but also biased.
+They observed a disproportional amount of Cronbach's Alpha values at the common acceptably reliable threshold value of .70, and relatively low reporting below .70.
+Thus, the lack of reported measurement evidence may on occasion be hiding psychometric skeletons in the closet.
+
+As a result, if we want to evaluate the reliability of measurement in our sample, we cannot rely on the reported information alone to give us a representative picture.
+Thus, we evaluate the measurement reliability within the Many Labs original and replication studies by estimating it from the item response data.
+The data on the item responses are openly available per lab for our sample.
+As a result, we can evaluate not only the reliability per measure, but also the variation in reliability across labs.
+The variation is relevant because Cronbach's alpha is an indicator of reliability within a particular sample and not of the reliability of the measure in general, as it is proportional to the total variance in the target variable in the sample.
+Despite this many researchers report and interpret Cronbach's Alpha as a universal quality of the measure [@cortinaWhatCoefficientAlpha1993; @schmittUsesAbusesCoefficient1996].
+@maireadshawMeasurementPracticesLargescale2020 has so far observed that for Many Labs 2 the overall sample Cronbach's alpha level across scales was below .5, a degree of reliability far below what many would consider acceptable for most research purposes.
+It is our second aim to empirically evaluate both the degree as well as the variation of reliability of the measures in our sample that includes the other Many Labs projects.
+
+## Unidimensionality
+
+Reliability is a pre-requisite to construct validity, because a measure for which a participant’s response is not consistent, cannot capture a stable construct [Kaplan and Saccuzzo (2013, pp.
+154–155)].
+Another, important pre-requisite for many measures is unidimensionality.
+Unidimensionality means that the items on a measure assess, show evidence of measuring a single construct.
+Thus, if a set of items are intended to measure the same one construct, then unidimensionality is key to the construct validity of that set of items.
+Additionally, most reliability indicators - including Cronbach's Alpha - cannot be assessed without first making sure that the measure is unidimensional.
+Thus for our third aim we again used the item response data.
+This time hitting two birds with one stone.
+We check the measures' construct validity, and we check if one of the key assumptions of Cronbach's Alpha is met.
+
+!!!substantively belangrijk, want de scores worden als unidimensioneel geinterpreteerd.
+Alpha assumptie testen, als kleiner deel bespreken; Reliability kan in sommige gevallen slecht zijn als de schaal gewoon multi-dimensioneel is.
+Eerst een beetje techniek, daarna meer kwalitatief oordeel dat het gewoon belangrijk is voor interpretatie!!!
+
+@maireadshawMeasurementPracticesLargescale2020 checked the factor structure on the openly available item data from Many Labs 2 [@kleinManyLabs22018b].
+They observed that no scales in their sample did the results from the factor analysis meet all of their evaluation criteria for unidimensionality.
+@maireadshawMeasurementPracticesLargescale2020 had access to measures that were used across multiple contexts to evaluate their validity across more than one instance.
+However, in practice, measures are frequently made on the fly and reused maybe once or never [@weidmanJingleJangleEmotion2017; @elsonPsychologicalMeasuresArent2023; @anvariFragmentedFieldConstruct2025; @anvariDefragmentingPsychology2025].
+This is dangerous, because these measures are often not validated before use, and if they cannot be reused, they are not going to be validated afterwards either.
+Furthermore, validating a scale requires substantial sample sizes in most cases [@maccallumSampleSizeFactor1999, @gorsuchFactorAnalysis2013], sample sizes that many original studies cannot obtain, in which case these measures are reliant on future research to obtain the required sample size to validate the measure.
+
+Thus, for our third research aim - similarly to our aim with reliability - we check the unidimensionality of measures from the Many Labs projects per lab with meta-analytic assessment of the variation in unidimensionality across labs.
+The combined goal of our three research aims is to create a description of the measurement use in our data.
 
@@
 ## Preregistration
+
 We preregistered data collection, coding protocol, and planned analyses: <https://osf.io/jgxyu>.
 We deviated from our coding protocol as is explained further in the text.
-Our pre-registered analyses have been move to the [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd) in favor of focusing on the descriptive results.
+Our pre-registered analyses have been move to the [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd) in favor of focusing on the descriptive results here.
 
 ## Data, Materials, and Online Resources
-TThis manuscript was created in RStudio [*v`r rstudioapi::versionInfo()$version`*\; @R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [*v`r getNamespaceVersion("worcs")[[1]]`*\; @R-worcs] to ensure reproducibility and transparency.
+
+This manuscript was created in RStudio [*v`r rstudioapi::versionInfo()$version`*; @R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [*v`r getNamespaceVersion("worcs")[[1]]`*; @R-worcs] to ensure reproducibility and transparency.
 All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> and <https://osf.io/9r8yt/> (DOI: 10.17605/OSF.IO/9R8YT).
@@
 ## Reporting
+
 We report how we determined all data exclusions, all manipulations, and all measures in the study. Our sample size was predetermined by the number of studies in the Many Labs projects.
@@
 ## Ethical Approval
+
 This research was approved by the Tilburg University School of Social and Behavioral Sciences Ethical Review Board (nr. TSB_TP_REMA06).
@@
 Our unit of analysis is a measure of a single variable within a replication protocol or original article that was used in the main analysis that was replicated.
-We allowed for multiple variables to be measured per study.
+For example, if conscientiousness and agreeableness were both measured using a big-five personality questionnaire, each of which was a variable in a replicated effect, then both the conscientiousness and agreeableness part of that questionnaire would be coded as their own unit of analysis.
+We also allowed for multiple variables to be measured per study.
 We used the replication protocols to identify the measure of each variable.
 We did not include acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses.
+Our final sample size was `r nrow(coded_data_replications)` measures of unique variables for both original and replication studies\^[Initially the original articles contained 3 more measures of unique variables than the replication protocols.
+This difference was due to the way that the moral foundations questionnaire was framed in the original article compared to in the replication protocol.
+In the original article it was framed as measuring five different moral foundations, while in the replication protocol the measure assessed the two overarching categories that were used to test the main effect in both the original and replication research.
+The measurement information reported was comparable across all five categories, and thus it was deemed that the measurement could be reduced to reflect two overarching categories facilitate easier comparison between measurement in original and replication.]
 
@@
 The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>.
-Both the replication protocols and replication datasets were scanned through to ensure that the planned analyses were feasible.
+Both the replication protocols and replication datasets were scanned through to ensure that they were the correct files to code measurement reporting information from.
 However, no coding or analysis of either of them had taken place before the analyses were preregistered.
@@
 We additionally included twenty items that were based on the QMP table presented in @flakeMeasurementSchmeasurementQuestionable2020.
-For each of these items we a piece information we would want to see reported with regards to the measurement was described.
+For each of these items we checked if a piece information we would want to see reported with regards to the measurement was described.
 If the information was clearly reported we coded the item as true; false if not or not clear enough; or not applicable if not relevant for that measure (e.g., reporting results from a factor analysis for single-item measures).
@@
 
-We initially intended to form a QMP index using these QMP items and perform regression analyses using this index, but this index could not be validated properly and its results would be misleading to present here in the main article.
+We initially intended to construct a QMP index from the QMP items and perform regression analyses between this index and replication outcomes.
+However, this index could not be validated properly and its results would be misleading to present here in the main article.
 A more detailed explanation of what was omitted and why, as well as the results from these preregistered analyses can be found in [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd).
@@
 
-QMP_data$reliability_reported_org <- ifelse(original_QMP_data$reliability_type != "Not Reported" & original_QMP_data$reliability_type != "" & !is.na(original_QMP_data$reliability_type), TRUE, ifelse(original_QMP_data$reliability_type == "Not Reported", FALSE, NA))
-
-QMP_data$reliability_reported_rep <- ifelse(replication_QMP_data$reliability_type != "Not Reported" & replication_QMP_data$reliability_type != "" & !is.na(replication_QMP_data$reliability_type), TRUE, ifelse(replication_QMP_data$reliability_type == "Not Reported", FALSE, NA))
+QMP_data$reliability_reported_org <- ifelse(coded_data_original$N_items == "multiple item measure", ifelse(original_QMP_data$reliability_type != "Not Reported" & original_QMP_data$reliability_type != "" & !is.na(original_QMP_data$reliability_type), TRUE, ifelse(original_QMP_data$reliability_type == "Not Reported", FALSE, NA)), NA)
+
+QMP_data$reliability_reported_rep <- ifelse(coded_data_replications$N_items == "multiple item measure", ifelse(replication_QMP_data$reliability_type != "Not Reported" & replication_QMP_data$reliability_type != "" & !is.na(replication_QMP_data$reliability_type), TRUE, ifelse(replication_QMP_data$reliability_type == "Not Reported", FALSE, NA)), NA)
 
@@
 
-### Recalculating Data
+### Calculating Reliaiblity
 
@@
 We calculated both Cronbach’s alpha, as well as its standard error using formulas 2 & 3 from @duhachekAlphasStandardError2004a.
-Then we entered these two values into a meta-analysis of the measure's reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analysis [@botellaManagingHeterogeneityVariance2012; @lopez-ibanezReliabilityGeneralizationMetaanalysis2024; @vacha-haaseReliabilityGeneralizationExploring1998].
-Using RG Meta-Analysis we quantified the degree of true variation (or heterogeneity) in reliability coefficients across lab locations.
+We used these values to conduct a meta-analysis of the measure's reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analysis [@botellaManagingHeterogeneityVariance2012; @lopez-ibanezReliabilityGeneralizationMetaanalysis2024; @vacha-haaseReliabilityGeneralizationExploring1998].
 We performed the RG Meta-Analysis using the rma function from the metafor R package [*v`r getNamespaceVersion("metafor")[[1]]`*; @R-metafor] and default settings.
-We evaluated the heterogeneity using the tau statistic and the Cochran's Q-test [@cochranCombinationEstimatesDifferent1954].
+We then used the results from the meta-analysis to evaluate the heterogeneity via the tau statistic and the Cochran's Q-test [@cochranCombinationEstimatesDifferent1954].
 These indicators have received criticism as indicators of heterogeneity, especially when within study sample sizes are small and power to detect heterogeneity is low [@hoaglinMisunderstandingsCochransTest2016; @pereiraCriticalInterpretationCochrans2010].
@@
 Furthermore, we were able to calculate the standard error of alpha to be used in the RG meta-analysis.
-We additionally estimated McDonald’s Omega for each lab from the same set of replications as for Cronbach's Alpha, since it has been argued to be a more informative measure of reliability than Cronbach's Alpha, while also simultaneously providing some validity evidence [@crutzenScaleQualityAlpha2017b; @dengTestingDifferenceReliability2017].
-McDonald’s Omega was calculated using the omega function in the *psych* R package [*v`r getNamespaceVersion("psych")[[1]]`*; @R-psych].
-Default arguments were used in the function except the nfactors argument, which was set to 1.
-No RG Meta-Analysis was performed on McDonald's Omega, as we could not find a formula for calculating its standard error.
+However, Cronbach's Alpha comes with strong assumptions on the underlying factor structure, including that the measure is unidimensional, which means that there should a single factor underlying the measurement scores.
+Therefore, we also estimated McDonald’s Omega for each lab from the same set of replications as for Cronbach's Alpha, since it has been argued to be a more informative measure of reliability than Cronbach's Alpha with less strict assumptions [@crutzenScaleQualityAlpha2017b; @dengTestingDifferenceReliability2017].
+The results based on Omega can be found in [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_omega_analyses.Rmd).
 
@@
 
-Finally, we also tested these measures for unidimensionality.
-Our unidimensionality check serves a double purpose.
-First, unidimensionality is one of the assumptions of Cronbach's Alpha.
-If this assumption does not hold for a measure, our Cronbach's Alpha estimates give a biased estimate of the reliability.
-Second, all measurement items for which unidimensionality was checked, were used to form a singular index of one latent variable.
-Certainly, not all singular indexes require the underlying latent factor model to be unidimensional (e.g., general intelligence can be used as a variable on its own or sub-divided in multiple components such as numerical and verbal intelligence).
-Still, we believe it is not unreasonable to assume that for most of the single index measures we should observe a unidimensional factor model to have at least adequate fit.
-
-We tested for unidimensionality using two tests on the data from each lab for each measure.
-If at least one of these tests was passed, the measure in that lab was marked as unidimensional.
-For the first test we fit a Confirmatory Factor Analysis (CFA) model with one factor to the data, and we then evaluate the RMSEA value.
-If this value is below .08, the test is passed.
-For the second test we run a parallel analysis.
-This runs multiple Exploratory Factor Analyses (EFA) where the number of factors in the model is increased by 1 until the number of factors is one less than the number of items.
+### Unidimensionality
+
+All measurement items for which we checked unidimensionality, were used to form a singular index of one latent variable.
+Therefore, unidimensionality presents a valuable indication of the construct validity of a measure in our dataset.
+To test for unidimensionality, we fit a single-factor model on the item response data of each individual lab with the relevant measurement data.
+This was done to simulate the inference a lab would make if they were to check for unidimensionality.
+Our inference of unidimensionality is based on a set of five model fit indices.
+If the indices point towards a good unidimensional fit that is also consistent across labs - as we also evaluate the variability across labs - then we can say that with this preliminary evidence at least, we did not observe any issues with the construct validity of that measure.
+If the indices point towards a lack of unidimensionality in a substantial number of labs, that would be a warning sign for the lack of construct validity for that measure.
+Our goal is not to fully check the validity of these measures, this requires additional steps that are beyond the scope of this study.
+
+For the first four of our five fit indices we fit a Confirmatory Factor Analysis (CFA) model with one factor to the data, and we then evaluate the RMSEA value, CFI value, SRMR value, and the result from the exact fit test.
+For the RMSEA and SRMR value we checked if it was below .08.
+For the CFI value we checked if the value was above .90.
+Finally, for the exact fit test we evaluated if the fit test was statistically significant at an alpha of .05.
+These values are based on common thresholds used to determine adequate fit.
+We consider the use of these thresholds sufficient for our descriptive aim, even though we understand apprehension against rules of thumb when used to evaluate measurement in individual studies.
+
+For the final index we ran a parallel analysis.
+A parallel analysis runs multiple Exploratory Factor Analyses where the number of factors in the model is increased by 1 until the number of factors is one less than the number of items.
 It then compares the eigenvalues (an indication of how much variance is explained by that factor) of each factor to the eigenvalues for that factor if the data matrix was effectively random.
 If only the first factor has an eigenvalue that is significantly higher than the eigenvalue when the data matrix is random, the test is passed.
-We chose a combination of these two tests, as the RMSEA is known to be biased for models with small degrees of freedom [@kennyPerformanceRMSEAModels2015], while the parallel analysis may be less suited if a two or more factor solution would also fit the sample item data.
-
-```{r validity_and_alpha_assumption_tests, include = FALSE, eval = FALSE}
+We chose a combination of indices since each one has their own limitations, and combining them gives us a more robust picture of the unidimensionality of the measures.
+
+```{r unidimensionality_tests, include = FALSE, eval = FALSE}
 # function that runs all our checks for Cronbach's alpha. Also functions as some basic validity checks
@@
   ### Tests for Unidimensionality
-  # Test 1a: obtaining single factor model cfa RMSEA value for evaluation
+  # Test 1a: obtaining single factor model cfa RMSEA, CFI, SRMR, and exact fit test results
   RMSEA_values <- c(NA, NA)
+  CFI <- NA
+  SRMR <- NA
+  fit_results <- c(NA, NA, NA)
   tryCatch({
@@
 
-    rmsea <- fitMeasures(fit.modelfree)["rmsea"] 
-    rmsea.ci.upper <- fitMeasures(fit.modelfree)["rmsea.ci.upper"]
+    # extracting the fit measures
+    fit_measures <- fitMeasures(fit.modelfree, c("chisq", "df", "pvalue", "rmsea", "rmsea.ci.upper", "cfi", "srmr"))
+
+    # extracting RMSEA and its standard error
+    rmsea <- fit_measures["rmsea"] 
+    rmsea.ci.upper <- fit_measures["rmsea.ci.upper"]
     rmsea.se <- (rmsea.ci.upper - rmsea) / 1.645
@@
 
+    # extracting CFI
+    CFI <- fit_measures["cfi"]
+
+    # extracting SRMR
+    SRMR <- fit_measures["srmr"]
+
+    # extracting exact fit test measures
+    fit_chisq <- fit_measures["chisq"]
+    fit_df <- fit_measures["df"]
+    fit_pvalue <- fit_measures["pvalue"]
+    fit_results <- c(fit_chisq, fit_df, fit_pvalue)
+
   }, error = function(e) {
     RMSEA_values <- c(NA, NA)
+    CFI <- NA
+    SRMR <- NA
+    fit_results <- c(NA, NA, NA)
   })
@@
 
-  # adding a single factor check indicator value
+  # adding a single factor check count
   if(is.null(RMSEA_values[[1]]) | is.null(parallel_N_factors)){
-    single_factor <- NA
+    unidimensional_check_count <- NA
   } else{
-    single_factor <- ifelse(RMSEA_values[[1]] < 0.08 | parallel_N_factors == 1, "Yes", "No")
+    unidimensional_check_count <- sum(RMSEA_values[[1]] < .08, CFI > .90, SRMR < .08, fit_results[[3]] < .05, parallel_N_factors == 1)
   }
@@
   ### storing all of the data
-  FA_data <- c(RMSEA_values, parallel_N_factors, single_factor, 
-               Tau_results, error_cor_results)
+  FA_data <- c(RMSEA_values, CFI, SRMR, fit_results, parallel_N_factors, 
+               unidimensional_check_count, Tau_results, error_cor_results)
 
@@
   # Setting the column names
-  names(FA_data_frame) <- c("RMSEA", "RMSEA_se", "N_factors", "unidimensional", "Tau_chisq_diff", 
+  names(FA_data_frame) <- c("RMSEA", "RMSEA_se", "CFI", "SRMR", "fit_chisq", "fit_df", 
+                            "fit_pvalue", "N_factors", "unidimensional_check_count", "Tau_chisq_diff", 
                             "Tau_Df_diff", "Tau_p_diff", "mean_spec", "err_chisq_diff", 
@@
 
-## Reported Reliability & Validity Evidence
+## Measurement Reporting
+
+### Reliability
 
@@
 First, it shows that almost half of the measures in both replication (N = `r sum(coded_data_replications$N_items == "1 item measure")`) and original research (N = `r sum(coded_data_original$N_items == "1 item measure")`) were single-item measures.
-Second, only `r apa_num(sum(coded_data_original$reliability_type != "Not Reported" & coded_data_original$reliability_type != ""), numerals = FALSE)` measures in original and `r apa_num(sum(coded_data_replications$reliability_type != "Not Reported" & coded_data_replications$reliability_type != ""), numerals = FALSE)` in replications were reported alongside a reliability indicator.
-Cronbach’s Alpha was the most commonly reported reliability indicator.
+Second, only `r apa_num(sum(coded_data_original$reliability_type != "Not Reported" & coded_data_original$reliability_type != ""), numerals = FALSE)` measures out of `r sum(coded_data_original$N_items == "multiple item measure")` (`r round((sum(coded_data_original$reliability_type != "Not Reported" & coded_data_original$reliability_type != "") / sum(coded_data_original$N_items == "multiple item measure")) * 100, 1)` %) multi-item scales in original and `r apa_num(sum(coded_data_replications$reliability_type != "Not Reported" & coded_data_replications$reliability_type != ""), numerals = FALSE)` out of `r sum(coded_data_replications$N_items == "multiple item measure")` (`r round((sum(coded_data_replications$reliability_type != "Not Reported" & coded_data_replications$reliability_type != "") / sum(coded_data_replications$N_items == "multiple item measure")) * 100, 1)` %) multi-item scales in replications were reported alongside a reliability indicator.
+@flakeConstructValidityValidity2022 observed a much larger degree of reliability coefficient reporting in both original (60.8%) and replications (37.1%).
+However, similarly to @flakeConstructValidityValidity2022, we observed that reliability reporting was more common in original studies as compared to replication studies, and that Cronbach’s Alpha was the most commonly reported reliability indicator in our sample as well.
 
@@
 
+### Validity
+
 For validity evidence the pattern was similar.
-Only, `r apa_num(sum(coded_data_original$sel_psychometric_evidence_REV != "None" & coded_data_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_original$sel_3_REV == TRUE, na.rm = TRUE), numerals = FALSE)` original studies and `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_replications$sel_3_REV == TRUE, na.rm = TRUE), numerals = FALSE)` replications reported psychometric validity evidence on the measurement.
-Replications reported both less reliability and validity evidence.
-Exploratory factor analyses (original: `r apa_num(sum(coded_data_original$sel_psychometric_evidence_REV == "Exploratory Factor Analysis"), numerals = FALSE)`, replications: `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV == "Exploratory Factor Analysis"))`) and convergent validity evidence (original: `r apa_num(sum(coded_data_original$sel_psychometric_evidence_text_REV == "convergent validity"), numerals = FALSE)`, replications: `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_text_REV == "convergent validity"), numerals = FALSE)`) were the most common.
+Only, `r apa_num(sum(coded_data_original$sel_psychometric_evidence_REV != "None" & coded_data_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_original$sel_3_REV == TRUE, na.rm = TRUE), numerals = FALSE)` (`r round((sum(coded_data_original$sel_psychometric_evidence_REV != "None" & coded_data_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_original$sel_3_REV == TRUE, na.rm = TRUE) / nrow(coded_data_original)) * 100, 1)` %) original studies and `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_replications$sel_3_REV == TRUE, na.rm = TRUE), numerals = FALSE)` (`r round((sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_replications$sel_3_REV == TRUE, na.rm = TRUE) / nrow(coded_data_replications)) * 100, 1)`) replications reported psychometric validity evidence on their measurement.
+These proportions align with the results from @flakeConstructValidityValidity2022 for both original (9.3%) and replication studies (6.2%), and again, similar to @flakeConstructValidityValidity2022 we observe that validity evidence is also more commonly reported in original compared to replication studies.
+Exploratory factor analyses (original: `r apa_num(sum(coded_data_original$sel_psychometric_evidence_REV == "Exploratory Factor Analysis"), numerals = FALSE)`, replications: `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV == "Exploratory Factor Analysis"))`) and convergent validity evidence (original: `r apa_num(sum(coded_data_original$sel_psychometric_evidence_text_REV == "convergent validity"), numerals = FALSE)`, replications: `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_text_REV == "convergent validity"), numerals = FALSE)`) were the most commonly reported validity indicators.
 Psychometric validity evidence from previous studies was reported in `r apa_num(sum(coded_data_original$sel_4 == TRUE, na.rm = TRUE), numerals = FALSE)` original studies and `r apa_num(sum(coded_data_replications$sel_4 == TRUE, na.rm = TRUE), numerals = FALSE)` replications.
@@
 
-## Calculated Reliability & Validity Evidence
+### Questionable Measurement Practices
+
+We also coded the reporting of measurement information besides reliability and validity reporting.
+Table \@ref(tab:QMPTable) below shows the ratio of measurements that aligned with that row's practice of reporting a specific piece of measurement information and for how many of the `r nrow(coded_data_original)` measures the reporting of that measurement information was applicable for both original and replications.
+The ratio is based on the number of measures that reported that piece of measurement information for the measures for which that item was applicable.
+A higher ratio thus indicates better measurement reporting.
+
+```{r QMPTable}
+# create informative Measurement Practice Labels 
+MPractice <- c("Reliability is reported", "It is clear if the measure existed or is newly created",    "Exact version of the measure is specified", "Validity evidence from a factor analysis is presented",   "Measured variable is defined", "Choice of measure selection or creation is justified",    "Implemented operationalisation is justified", "Source of the measure is provided",    "Psychometric evidence from the study is given", "Psychometric evidence from an earlier study is given",    "Administration format and environment are described", "Administration procedure is described",   "N items are described", "N response options are described", "Recoding of responses is described", "Creation of the index is described", "Text or supplement has example items", "Administration format changes are mentioned",    "Administration format changes are justified/validated", "Translations are mentioned",    "Translated measures are justified/validated", "Changes in N items or response options are mentioned",    "Changes in N items or response options are justified/validated")
+
+# construct the QMP table to be printed 
+QMP_table <- data.frame("Practice" = MPractice, 
+                        "Original" = paste0(1 - qmp_ratio_data$QMP_percentage_original, " (", qmp_ratio_data$N_applicable_original, ")"), 
+                        "Replication" = paste0(1 - qmp_ratio_data$QMP_percentage_replication, " (", qmp_ratio_data$N_applicable_replication, ")"))
+
+QMP_table_formatted <- rbind(rbind(rbind(rbind(rbind(c("Definition", "", ""), QMP_table[5,]),
+                                               c("Operationalisation", "", ""), QMP_table[c(3, 11, 12, 7, 17),]),
+                                         c("Selection/Creation", "", ""), QMP_table[c(2, 6, 8, 9, 10, 1, 4),]),
+                                   c("Quantification", "", ""), QMP_table[c(13, 14, 15, 16),]),
+                             c("Modification", "", ""), QMP_table[18:23,])
+
+# print the table in apa formatting 
+apa_table(QMP_table_formatted, align = c("l", "r", "r"), 
+          caption = "Ratio of QMPs and number of applicable measures, for original and replication", 
+          note = "The first number in both Original and Replication is the ratio of measures for which that reporting practice contained sufficient information.
+The number between brackets indicates the number of measures for which the practice was applicable.", escape = FALSE, placement = "htp", booktabs = TRUE)
+```
+
+For our purposes, we can focus on the reporting of information most relevant for reconstructing the measure in future research, as well as the modification reporting practices to learn about the relation between original and replication studies.
+It was clear that existing measures were used for `r round(sum(coded_data_original$sel_existing == "True, namely:") / nrow(coded_data_replications) * 100, 1)`% original and `r round(sum(coded_data_replications$sel_existing == "True, namely:") / nrow(coded_data_original) * 100, 1)`% replication measures.
+It was not always clear which measures were used (`r round(sum(coded_data_original$sel_existing == "Not Clearly Stated") / nrow(coded_data_original) * 100, 1)`% original; `r round(sum(coded_data_replications$sel_existing == "Not Clearly Stated") / nrow(coded_data_replications) * 100, 1)`% replication), meaning they could not clearly be identified to be the same between original and replication .
+The number of items (`r round((1 - qmp_ratio_data$QMP_percentage_original[13]) * 100, 1)`% original (n = `r qmp_ratio_data$N_applicable_original[13]`); `r round((1 - qmp_ratio_data$QMP_percentage_replication[13]) * 100, 1)`% replications (n = `r qmp_ratio_data$N_applicable_replication[13]`)) and response options (`r round((1 - qmp_ratio_data$QMP_percentage_original[14]) * 100, 1)`% original (n = `r qmp_ratio_data$N_applicable_original[14]`); `r round((1 - qmp_ratio_data$QMP_percentage_replication[14]) * 100, 1)`% replications (n = `r qmp_ratio_data$N_applicable_replication[14]`)) were usually clear, and modifications to these being unclearly reported was atypical, but did occur (`r round((1 - qmp_ratio_data$QMP_percentage_original[22]) * 100, 1)`% original (n = `r qmp_ratio_data$N_applicable_original[22]`); `r round((1 - qmp_ratio_data$QMP_percentage_replication[22]) * 100, 1)`% replications (n = `r qmp_ratio_data$N_applicable_replication[22]`)).
+The percentage of numbers of items reported was similar to @flakeConstructValidityValidity2022 (original: 92%; replication 85.6%).
+The proportion to which the number of items were changed from original to replication was also similar (`r round(sum(!is.na(coded_data_replications$mod_5_REV)) / nrow(coded_data_replications) * 100, 1)`) to @flakeConstructValidityValidity2022 (16%).
+In general, modifications could only rarely be identified for original studies.
+In replication studies we observe that not all modifications were validated or justified (language: `r round((1 - qmp_ratio_data$QMP_percentage_replication[21]) * 100, 1)`% (n = `r qmp_ratio_data$N_applicable_replication[21]`); administration format: `r round((1 - qmp_ratio_data$QMP_percentage_replication[19]) * 100, 1)`% (n = `r qmp_ratio_data$N_applicable_replication[19]`)), especially for changes in items and response options (`round((1 - qmp_ratio_data$QMP_percentage_replication[23]) * 100, 1)`(n = `r qmp_ratio_data$N_applicable_replication[23]`)).
+In general, we observed that measurement was modified in some way from original to replication for `r round((sum(coded_data_replications$mod_check == "True") / nrow(coded_data_replications)) * 100, 1)`% of measures, and it was unclear whether modification occurred for `r round((sum(coded_data_replications$mod_check == "None Reported") / nrow(coded_data_replications)) * 100, 1)`%.
+
+???LEFTOVER RESULTS from @flakeConstructValidityValidity2022.
+- had a citation flake:original ::: 29% - response format reported flake:original :: 94% - scale scoring flake:original :: 49% - citing existing validity evidence flake:original :: 29% - citing existing validity evidence flake:replication :: 38% - translation validated flake:replication :: 20% ???
+
+## Measurement Response Data Analysis
+
+### Calculated Reliability Coefficients
 
@@
 The prediction intervals generally show larger indications of heterogeneity for some of the lower reliability measures and less for higher reliability measures when compared to the Tau test results.
-Number of labs also appears to be a factor for narrowing the prediction intervals.
+An increase in the number of labs also appears to be a factor for narrowing the prediction intervals.
 Additionally, we observe that for most measures the reported reliabilities were generally lower than the reliabilities calculated for the replication labs.
-Perhaps more interesting is that we observed that reported reliabilities in the original study were more common for those measures that had higher average reliabilities (\>.80) in the replications compared to on average less reliable measures.
-
-```{r PlotData1FactorRMSEA, warning = FALSE}
+Another interesting observation is that reported reliabilities in the original study were more common for those measures that had higher average calculated reliabilities (\>.80) in the replications compared to on average less reliable measures.
+
+### Unidimensionality assessment
+
+```{r PlotData1Factor, warning = FALSE}
 # load in the FA_list data
@@
 # create the base dataframe
-unidimensionality_graph_data <- data.frame(RMSEA = c(NA),
-                                           RMSEA_se = c(NA),
+unidimensionality_graph_data <- data.frame(RMSEA = NA,
+                                           RMSEA_se = NA,
+                                           CFI = NA,
+                                           SRMR = NA,
+                                           fit_chisq = NA,
+                                           fit_df = NA,
+                                           fit_pvalue = NA,
                                            N_factors = NA,
-                                           unidimensional = NA,
+                                           unidimensional_check_count = NA,
                                            g = NA)
@@
 
-  unidimensionality_graph_data <- rbind(unidimensionality_graph_data, cbind(FA_list[[i]][1:4], g))
+  unidimensionality_graph_data <- rbind(unidimensionality_graph_data, cbind(FA_list[[i]][1:9], g))
 
@@
 
-### meta-analyzing
+### meta-analyzing RMSEA
 assess_undidimensionality_heterogeneity <- function(data_on_RMSEA){
@@
 
-names(unidimensionality_meta_data) <- c("beta", "tau", "QEp", "pi.lb", "pi.ub")
+names(unidimensionality_meta_data) <- c("beta", "tau", "QEp", "pi.lb", "pi.ub", "g")
+
+# add the count of significant p_values for the exact test to the meta_dataframe
+
+count_significant_results <- function(p){
+  significance <- sum(p > .05, na.rm = TRUE)
+  number_of_converged <- sum(!is.na(p))
+  return(c(significance, number_of_converged))
+}
+
+p_meta_list <- tapply(unidimensionality_graph_data$fit_pvalue, unidimensionality_graph_data$g, count_significant_results)
+
+p_meta_data <- do.call(rbind.data.frame, p_meta_list)
+
+names(p_meta_data) <- c("p_count", "converged_count")
+
+unidimensionality_meta_data <- cbind(unidimensionality_meta_data, p_meta_data)
 
@@
 
+# creating a string that shows the ratio of nonconverged to total
+convergence_rate_vec <- paste0(unidimensionality_meta_data$converged_count, "/", unidimensionality_meta_data$converged_count + non_converged_vec)
+
+# adding a star for De Fruyt et al. (2000)
+convergence_rate_vec <- c(convergence_rate_vec[1:18], paste0(convergence_rate_vec[19], "*"))
+
 ```
 
-Figure \@ref(fig:Plot1Factor) below show the result of our unidimensionality test.
+Figure \@ref(fig:Plot1FactorRMSEA) below show the result of our unidimensionality test.
 `r apa_num((sum(unidimensionality_graph_data$RMSEA < .08, na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)` % of labs were below our RMSEA .08 threshold, while for `r apa_num((sum(unidimensionality_meta_data$beta < .08, na.rm = TRUE)), numerals = FALSE)` measures of the total `r apa_num(nrow(unidimensionality_meta_data), numerals = FALSE)` the mean across labs was below this threshold.
-Furthermore, the RMSEA shows considerable variation within measures, with the standard deviation ranging from `r apa_num(min(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))` as the lowest to all the way up to `r apa_num(max(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))`.
+Furthermore, the RMSEA shows considerable variation within measures, with the standard deviation ranging from `r apa_num(min(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))` to `r apa_num(max(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))` (mean sd = `r apa_num(mean(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))`).
+
 The parallel analysis results similarly showed inconsistency both across and within measures.
@@
 The remainder did not converge.
-The lack of convergence was an also an issue for the CFA used for the RMSEA check.
+The lack of convergence was also an issue for the CFA used for the RMSEA check.
 The CFA failed to converge for `r apa_num((sum(is.na(unidimensionality_graph_data$RMSEA)) / nrow(unidimensionality_graph_data)) * 100)`% of labs.
-In the case of the @defruytCloningersPsychobiologicalModel2000 measure all labs failed to converge.
-Convergence in the other cases was the result of either the severe misfit of our factor models or a lack of sample size to stably estimate these models.
-In the end, `r apa_num((sum(unidimensionality_graph_data$unidimensional == "Yes", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% of labs passed our unidimensionality check.
-
-```{r Plot1Factor, warning = FALSE, fig.cap = "Distributions of calculated RMSEA of a single-factor model fit calculated for the responses on a measure at each lab location, across the nineteen measures for which raw data was available on which a factor model could be fitted.
+Convergence in most cases was the result of either the severe misfit of our factor models or a lack of sample size to stably estimate these models.
+A consistent pattern was also lacking for the results from the exact fit tests.
+For `r sum((unidimensionality_meta_data$p_count[1:18] / unidimensionality_meta_data$converged_count[1:18]) >= .75)` out of `r sum(unidimensionality_meta_data$converged_count != 0)` measures with converged factor analyses, three quarters or more labs showed statistical significant fit, for `r sum((unidimensionality_meta_data$p_count[1:18] / unidimensionality_meta_data$converged_count[1:18]) <= .25)` a quarter or less did, and for the remaining `r sum((unidimensionality_meta_data$p_count[1:18] / unidimensionality_meta_data$converged_count[1:18]) > .25 & (unidimensionality_meta_data$p_count[1:18] / unidimensionality_meta_data$converged_count[1:18]) < .75)` the proportion lay somewhere in between.
+
+```{r Plot1FactorRMSEA, warning = FALSE, fig.cap = "Distributions of calculated RMSEA of a single-factor model fit calculated for the responses on a measure at each lab location, across the nineteen measures for which raw data was available on which a factor model could be fitted.
 The red horizontal line separate the replicated from the non-repicated measures.
 The red vertical line indicates our .08 RMSEA cutoff value.
-The N non-conv.
-column besides the graph shows the number of labs per measure for which the single-factor CFA did not converge.
+The first number in the Conv.
+column besides the graph shows the number of labs per measure for which the single-factor CFA converged, with second number showing the total number of labs.
 The color of each dot shows the number of factors that were selected for that measure for that lab location based on the parallel analyses.
-Psychometric validity evidence was reported in the original Husnu & Crips (2010) and Shnabel & Nadler (2008) studies."}
-
-# plot for distribution of alpha
+Psychometric validity evidence was reported in the original Husnu & Crips (2010) and Shnabel & Nadler (2008) studies.
+* The Conscientiousness measure used in De Fruyt et al.
+(2000) consisted of two items, which are too few items to fit a factor model on.
+Therefore, none of these models converged."}
+
+# plot for distribution of RMSEA and exact fit test
 ggplot(unidimensionality_graph_data, aes(x = RMSEA, y = g, colour = as.factor(N_factors_capped))) +
@@
 
-  # adding in the tau values
-  #geom_text(data = unidimensionality_meta_data, label = format(unidimensionality_meta_data$tau, digits = 1), x = 0.58, y = 1:19, color = ifelse(unidimensionality_meta_data$QEp < .05, "black", "grey"), size = 2.8) +
-
-  # adding in the N non converted
-  geom_text(data = unidimensionality_meta_data, label = format(non_converged_vec), x = 0.51, y = 1:19, size = 2.8, colour = "black") +
+  # adding in the convergence rate
+  geom_text(data = unidimensionality_meta_data, label = format(convergence_rate_vec), x = 0.51, y = 1:19, size = 2.8, colour = "black") +
+
+  # adding in the proportion of significant p-values
+  geom_text(data = unidimensionality_meta_data, label = format(c(round(unidimensionality_meta_data$p_count[1:18] / unidimensionality_meta_data$converged_count[1:18], 2), "")), x = 0.58, y = 1:19, size = 2.8, colour = "black") +
+
+  # setting the theme
+  theme_minimal() +
+  theme(legend.position = "bottom", plot.margin = unit(c(2, 5, 1, 1), "lines")) +
+
+  # adding the necessary indicative texts
+  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 7.25, ymax = 7.25, xmin = 0.33, xmax = 0.33) +
+  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 6, ymax = 6, xmin = 0.37, xmax = 0.37) +
+  annotation_custom(grob = textGrob(label = "Conv.", hjust = 0, gp = gpar(fontsize = 11)), ymin = 20.2, ymax = 20.2, xmin = 0.48, xmax = 0.48) +
+  annotation_custom(grob = textGrob(label = "Sig.\nProp.", hjust = 0, gp = gpar(fontsize = 11)), ymin = 20.9, ymax = 20.9, xmin = 0.55, xmax = 0.56) +
+
+  coord_cartesian(xlim = c(0, 0.45), clip = "off") +
+
+  # we remove 7 & 15 lower bound because they are below 0
+  # geom_point(data = unidimensionality_meta_data[c(1:6, 8:14, 16:17),], mapping = aes(x = pi.lb, y = c(1:6, 8:13, 15:17) ), color = "green", shape = 124, size = 2.5) + 
+  # geom_point(data = unidimensionality_meta_data, mapping = aes(x = pi.ub, y = 1:19), color = "green", shape = 124, size = 2.5) +
+
+  scale_colour_manual(name = "N Factors (Parallel Analysis)", values = c("#0049b8", "#02bd8a", "#f2e30f"), na.value = "#000000") + 
+  guides(colour = guide_legend(override.aes = list(alpha = 1))) +
+  ylab("") +
+  xlab("RMSEA (unidimensional CFA model)")
+
+```
+
+Figure \@ref(fig:Plot1FactorSRMRCFI) below shows the SRMR, and CFI fit indices for the same single factor model as was used to estimate the RMSEA and exact fit test.
+`r apa_num((sum(unidimensionality_graph_data$SRMR < .08, na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% of labs were below our SRMR .08 threshold and `r apa_num((sum(unidimensionality_graph_data$CFI < .9, na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% were above our CFI .90 threshold.
+For the `r apa_num(nrow(unidimensionality_meta_data), numerals = FALSE)` measures, the mean SRMR was below .08 for `r apa_num((sum(tapply(unidimensionality_graph_data$SRMR, unidimensionality_graph_data$g, mean, na.rm = TRUE) < .08, na.rm = TRUE)), numerals = FALSE)` measures, while the mean CFI was above .90 for for `r apa_num((sum(tapply(unidimensionality_graph_data$CFI, unidimensionality_graph_data$g, mean, na.rm = TRUE) > .9, na.rm = TRUE)), numerals = FALSE)` measures.The mean standard deviation of the SRMR fit index is `r apa_num(mean(tapply(unidimensionality_graph_data$SRMR, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$SRMR, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))`.
+For CFI this was `r apa_num(mean(tapply(unidimensionality_graph_data$CFI, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$CFI, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))`.
+Overall, compared to the RMSEA, the SRMR and CFI fit indices show a more stable unidimensional fit.
+Especially the SRMR index shows considerably better fit compared to the RMSEA.
+When combining the results from all five unidimensionality checks together we observe that at least one of the five unidimensionality checks was passed for `r round((sum(unidimensionality_graph_data$unidimensional_check_count >= 1, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100, 2)`% of the `r sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))` labs with converged factor models, at least two for `r round((sum(unidimensionality_graph_data$unidimensional_check_count >= 2, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100, 2)`%, at least three for `r round((sum(unidimensionality_graph_data$unidimensional_check_count >= 3, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100, 2)`%, at least three for `r round((sum(unidimensionality_graph_data$unidimensional_check_count >= 4, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100, 2)`%, and all five for `r round((sum(unidimensionality_graph_data$unidimensional_check_count == 5, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100, 2)`%.
+The mean number of unidimensionality check passed was `r round(mean(unidimensionality_graph_data$unidimensional_check_count, nar.rm = TRUE), 2)`.
+
+```{r Plot1FactorSRMRCFI, warning = FALSE, fig.cap = "Distributions of calculated SRMR and calculated CFI of a single-factor model fit calculated for the responses on a measure at each lab location, across the nineteen measures for which raw data was available on which a factor model could be fitted.
+The left figure shows the SRMR result, where the red vertical line indicates our .08 RMSR cutoff value.
+The right figure shows the CFI results, where the red vertical line indicates our .90 CFI cutoff value.
+In both figures the red horizontal line separate the replicated from the non-repicated measures."}
+
+# plot for distribution of SRMR
+SRMR_plot <- ggplot(unidimensionality_graph_data, aes(x = SRMR, y = g, colour = as.factor(N_factors_capped))) +
+  geom_boxplot(outlier.shape = NA, colour = "black") +
+  geom_point(alpha = 0.3) +
+  geom_hline(yintercept = 6.5, color = "red", size = 1) +
+  geom_vline(xintercept = 0.08, color = "red", size = 1) +
 
@@
   theme(legend.position = "bottom", plot.margin = unit(c(1, 5, 1, 1), "lines")) +
+  scale_x_continuous(breaks = round(c(0, 0.1, 0.2),1)) +
 
   # adding the necessary indicative texts
-  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 7.25, ymax = 7.25, xmin = 0.33, xmax = 0.33) +
-  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 6, ymax = 6, xmin = 0.37, xmax = 0.37) +
-  #annotation_custom(grob = textGrob(label = "Tau", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 0.55, xmax = 0.55) +
-  annotation_custom(grob = textGrob(label = "N Non-Conv.", hjust = 0, gp = gpar(fontsize = 11)), ymin = 20.2, ymax = 20.2, xmin = 0.48, xmax = 0.48) +
-
-  coord_cartesian(xlim = c(0, 0.45), clip = "off") +
-
-  # we remove 7 & 15 lower bound because they are below 0
-  # geom_point(data = unidimensionality_meta_data[c(1:6, 8:14, 16:17),], mapping = aes(x = pi.lb, y = c(1:6, 8:13, 15:17) ), color = "green", shape = 124, size = 2.5) + 
-  # geom_point(data = unidimensionality_meta_data, mapping = aes(x = pi.ub, y = 1:19), color = "green", shape = 124, size = 2.5) +
-
-  scale_colour_manual(name = "N Factors (Parallel Analysis)", values = c("#0072B2", "#009E73", "#F0E442"), na.value = "#000000") + 
+  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0, gp = gpar(fontsize = 8)), ymin = 7.25, ymax = 7.25, xmin = 0.18, xmax = 0.18) +
+  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0, gp = gpar(fontsize = 8)), ymin = 6, ymax = 6, xmin = 0.18, xmax = 0.18) +
+
+  coord_cartesian(xlim = c(0, 0.2), clip = "off") +
+
+  scale_colour_manual(name = "N Factors (Parallel Analysis)", values = c("#0049b8", "#02bd8a", "#f2e30f"), na.value = "#000000") + 
   guides(colour = guide_legend(override.aes = list(alpha = 1))) +
   ylab("") +
-  xlab("RMSEA (unidimensional CFA model)") 
+  xlab("SRMR (unidimensional CFA model)")
+
+# plot for distribution of CFI
+CFI_plot <- ggplot(unidimensionality_graph_data, aes(x = CFI, y = g, colour = as.factor(N_factors_capped))) +
+  geom_boxplot(outlier.shape = NA, colour = "black") +
+  geom_hline(yintercept = 6.5, color = "red", size = 1) +
+  geom_vline(xintercept = 0.9, color = "red", size = 1) +
+  geom_point(alpha = 0.3) +
+
+  # setting the theme
+  theme_minimal() +
+  theme(legend.position = "none", plot.margin = unit(c(1, 5, 1, 1), "lines"), axis.text.y = element_blank()) +
+  scale_x_continuous(breaks = round(c(0, 0.2, 0.4, 0.6, 0.8, 1),1)) +
+
+  coord_cartesian(xlim = c(0, 1), clip = "off") +
+
+  scale_colour_manual(name = "N Factors (Parallel Analysis)", values = c("#0049b8", "#02bd8a", "#f2e30f"), na.value = "#000000") + 
+  guides(colour = guide_legend(override.aes = list(alpha = 1))) +
+  ylab("") +
+  xlab("CFI (unidimensional CFA model)")
+
+(SRMR_plot + CFI_plot)
+
 ```
 
-```{r check_on_Omega_convergence, warning = FALSE}
-is_mostly_na <- function(x){
-  return((sum(is.na(x)) / length(x)) > .5) 
-}
-
-Omega_convergence_vector <- tapply(calculated_alpha_plot_data$omega.tot, calculated_alpha_plot_data$g, is_mostly_na)
-
-# sum(Omega_convergence_vector)
-```
-
-Figure \@ref(fig:PlotOmegaDistributions) below shows the result of our Omega analyses.
-Note that while we show the distributions of omega values here, due to the lack of a formula to calculate the Omega standard error, we did not perform a meta-analysis on these results.
-Overall, our Omega coefficient analyses show a similar pattern between measures to that observed for the alpha coefficient albeit with generally higher coefficient scores across measures.
-However, not all improved.
-The two columns beside Figure \@ref(fig:PlotOmegaDistributions) show in how many labs each measure was used, as well as for how many labs an omega coefficient could be obtained, which was not always.
-In `r apa_num(sum(is.na(calculated_alpha_plot_data$omega.tot)) / nrow(calculated_alpha_plot_data) * 100)`% of labs, no omega coefficient could be obtained.
-For `r sum(Omega_convergence_vector)` measures the number of labs for which an Omega coefficient could not be obtained was even the majority.
-This relates to our findings from the unidimensionality tests, where some factor models did not converge.
-
-```{r PlotOmegaDistributions, warning = FALSE, fig.cap = "Distributions of calculated McDonald’s Omega t  calculated for the responses on a measure at each lab location, across the eighteen measures for which raw data was available from which McDonald’s Omega t coefficients could be calculated.
-The N.Omg column besides the figure shows the number of lab locations for which an Omega coefficient could be successfully calculated.
-Due to lack of underlying model convergence an Omega coefficient could not be calculated for all lab locations, or any lab locations for the Der Fruyt et al.
-(2000) measure.
-The N.tot column shows the total number of lab locations at which the measure was taken.
-Any difference between N.omg and N.tot can be seen as an indication of the instability to get a stable estimate of an underlying facto model for some lab locations for that measure."}
-# plot for omega
-ggplot(calculated_alpha_plot_data, aes(x = omega.tot, y = g)) +
-  geom_boxplot(outlier.shape = NA) +
-  geom_point(alpha = 0.1) +
-
-  # adding labels to show the number of labs per measure for which a total omega could be calculated
-  geom_text(data = calculated_alpha_plot_data[1:19,], label = table(calculated_alpha_plot_data$g[!is.na(calculated_alpha_plot_data$omega.tot)]), x = 1.15, y = 1:19, size = 2.8) +
-  # adding labels to show the number of labs per measure
-  geom_text(data = calculated_alpha_plot_data[1:19,], label = table(calculated_alpha_plot_data$g), x = 1.35, y = 1:19, size = 2.8) +
-
-  # theming
-  theme_minimal() +
-  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), 
-                                                     "lines")) +
-
-  # adding the replication line
-  geom_hline(yintercept = 6.5, color = "red", size = 1) +
-
-  # adding the necessary indicative texts
-  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 7.25, ymax = 7.25, xmin = 0.01, xmax = 0.01) +
-  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 6, ymax = 6, xmin = 0.01, xmax = 0.01) +
-  annotation_custom(grob = textGrob(label = "N.Omg", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.08, xmax = 1.08) +
-  annotation_custom(grob = textGrob(label = "N.Tot", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.28, xmax = 1.28) +
-
-  coord_cartesian(xlim = c(0, 1), clip = "off") +
-
-  ylab("") +
-  xlab("Omega")
-
-```
-
-## Questionable Measurement Practices
-
-Reliability and validity indicators are only one aspect of measurement reporting.
-We coded additional potential questionable measurement practices in reporting in general too.
-Table \@ref(tab:QMPTable) below shows for both original and replication for all of the QMP items the ratio of QMPs and for how many of the `r nrow(coded_data_original)` measures the QMP was applicable.
-Meanwhile, the Phi coefficient indicates the “correlation” between the MP being questionable or good in the original and the same for the replication.
-
-```{r QMPTable}
-# create informative Measurement Practice Labels 
-MPractice <- c("Reliability is reported", "It is clear if the measure existed or is newly created",    "Exact version of the measure is specified", "Validity evidence from a factor analysis is presented",   "Measured variable is defined", "Choice of measure selection or creation is justified",    "Implemented operationalisation is justified", "Source of the measure is provided",    "Psychometric evidence from the study is given", "Psychometric evidence from an earlier study is given",    "Administration format and environment are described", "Administration procedure is described",   "N items are described", "N response options are described", "Recoding of responses is described", "Creation of the index is described", "Text or supplement has example items", "Administration format changes are mentioned",    "Administration format changes are justified/validated", "Translations are mentioned",    "Translated measures are justified/validated", "Changes in N items or response options are mentioned",    "Changes in N items or response options are justified/validated")
-
-# construct the QMP table to be printed 
-QMP_table <- data.frame("Practice" = MPractice, 
-                        "QMP original" = paste0(qmp_ratio_data$QMP_percentage_original, " (", qmp_ratio_data$N_applicable_original, ")"), 
-                        "QMP Replication" = paste0(qmp_ratio_data$QMP_percentage_replication, " (", qmp_ratio_data$N_applicable_replication, ")"), 
-                        "Phi" = qmp_ratio_data$Phi)
-
-# print the table in apa formatting 
-apa_table(QMP_table, align = c("l", "r", "r", "r"), 
-          caption = "Ratio of QMPs and number of applicable measures, for original and replication", 
-          note = "The first number in QMP org and QMP rep is the ratio of measures for which the practice in that row was not conducted well by our standards.
-The number between brackets indicates the number of measures for which the practice was applicable.", escape = FALSE, placement = "htp", booktabs = TRUE)
-```
-
-The Phi coefficients reveal little in the way of a consistent pattern on the relation of QMPs in original to QMPs in replications.
-However, if we look more conceptually we can also look at the reporting of information most relevant for reconstructing the measure, as well as modifications to the measure to learn about the relation between original and replication study.
-It was clear that existing measures were used for `r apa_num(sum(coded_data_original$sel_existing == "True, namely:") / nrow(coded_data_replications) * 100)`% original and `r sum(coded_data_replications$sel_existing == "True, namely:") / nrow(coded_data_original) * 100`% replication measures.
-It was not always clear which measures were used (`r sum(coded_data_original$sel_existing == "Not Clearly Stated") / nrow(coded_data_original) * 100`% original; `r sum(coded_data_replications$sel_existing == "Not Clearly Stated") / nrow(coded_data_replications) * 100`% replication), meaning they could not clearly be identified to be the same between original and replication.
-While the number of items (`r qmp_ratio_data$QMP_percentage_original[13]`% original; `r qmp_ratio_data$QMP_percentage_replication[13]`% replications) and response (`r qmp_ratio_data$QMP_percentage_original[14]`% original; `r qmp_ratio_data$QMP_percentage_replication[14]`% replications) were usually clear, and modifications were atypical, but did occur (`r qmp_ratio_data$QMP_percentage_original[22]`% original; `r qmp_ratio_data$QMP_percentage_replication[22]`% replications).
-It was however uncommon for this modification to be validated (`r qmp_ratio_data$QMP_percentage_original[23]`% original; `r qmp_ratio_data$QMP_percentage_replication[23]`% replication).
-QMPs were less common for language (`r qmp_ratio_data$QMP_percentage_original[20]`% original; `r qmp_ratio_data$QMP_percentage_replication[20]`% replications) and administration format modifications (`r qmp_ratio_data$QMP_percentage_original[18]`% original; `r qmp_ratio_data$QMP_percentage_replication[18]`% replications), .
-Validation was however still rare (language: `r qmp_ratio_data$QMP_percentage_original[21]`% original, `r qmp_ratio_data$QMP_percentage_replication[21]`% replications; administration format: `r qmp_ratio_data$QMP_percentage_original[19]`% original; `r qmp_ratio_data$QMP_percentage_replication[19]`% replications).
-While generally QMPs were not found for admin format and procedure in the replications (format: `r qmp_ratio_data$QMP_percentage_replication[11]`%; procedure: `r qmp_ratio_data$QMP_percentage_replication[12]`%), they did occur for original measures (format: `r qmp_ratio_data$QMP_percentage_original[11]`%; procedure: `r qmp_ratio_data$QMP_percentage_original[12]`%).
-In general, we observed that measurement was modified in some way from original to replication for `r sum(coded_data_replications$mod_check == "True") / nrow(coded_data_replications)`% of measures, and it was unclear whether modification occured for `r sum(coded_data_replications$mod_check == "None Reported") / nrow(coded_data_replications)`%.
+???Compared to Shaw ,!!!
+- mean CFI of scales is: `r  mean(0.919, 0.966, 0.877, 0.946, 0.616, 0.92, 0.889, 0.873)` 0.919 - mean SRMR of scales is: `r  mean(0.066, 0.028, 0.047, 0.045, 0.267, 0.04, 0.059, 0.036)` 0.066 - mean of RMSEA of scales is: `r  mean(0.056, 0.082, 0.093, 0.059, 0.262, 0.191, 0.174, 0.085)` 0.056.
+However these are means of scales and not per lab???
 
@@
 To assess psychological phenomena we need measurement that is valid and reliable for our constructs.
-However, we noted that little reliability and validity evidence was reported, and our reanalysis of the reliability and validity of the measures showed inconsistent reliability and validity support.
-Furthermore, we observed a lack of transparent reporting, which makes it difficult for future researchers to reuse and build upon the validation of existing measurements.
+However, we noted that little reliability and validity evidence was reported, and that all the information needed to understand and recreate the measurement was rarely all available.
+Furthermore our reanalysis of the reliability and validity of the measures showed inconsistent reliability and validity support.
+
+!!!Korte samenvatting van wat we gedaan hebben; daarna voor alle drie aims de resultaten bescrhijven; gebruik QMPs als framework, maar niet veel expliciet bescrhijven (future research, er zijn nog meer QMPs); blijf de volgorde aanhouden!!!
 
@@
 While it is possible to check the reliability and validity of single item measures, these methods often require multiple measures or studies to be able to cross-validate the measure with [@leppinkWeNeedMore2017; @sarstedtSelectingSingleItems2016].
-Another factor may be observed in the fact that we observed that replications generally reported less reliability and psychometric validity evidence.
+Another reason can be found in our observation that replications generally reported less reliability and psychometric validity evidence.
 This could be because replications implicitly defer the responsibility of reporting validity and reliability evidence to the original study.
-However, it was not uncommon for the replication to use modified or different measures from the original study.
-If it was not set in stone that the same measure as the original was used, then it stands to reason that in any case the choice of measure should be motivated based on reliability and validity evidence.
-Furthermore, this does not explain the lack of reliability and validity reporting in the original studies.
+However, as we noted before, and as our analyses of the reliability and unidimensionality reiterate, the reliability and validity of a measure varies across contexts.
+It is therefore still important for the reliability and validity to be described for the replications studies too.
+
+We also noted that about two-thirds of the measurements were modified between replication and original study.
+While minor differences between replication and original study are inevitable, substantial changes between original and replication study raises questions about labeling those replications as direct.
+For example, the conscientiousness measure used for the replication of @defruytCloningersPsychobiologicalModel2000 was reduced from the original NEO-PI-R 30-item measure to a two-item measure in the replication.
+It is highly unlikely that a measure with such a significant change would have a comparable validity and reliability to the original, and we did unsurprisingly observe convergence issues with validity as well as low reliability for this measure.
+The regularity at which measures were modified also provides a response to the argument that replications do not need to report as many measurement details, since the reporting of these .
+If measurement is modified, then the new use and validity of the measurement has to be documented by the replication.
+Additionally, if changing the measurement between original and replication study is fair game, then the choice of measure has to also be substantially motivated beyond: "the original study did it that way".
+Finally, none of this explains away the lack of reliability and validity reporting in the original studies.
 It may unfortunately be more likely that many of these measures are simply not validated before (or even after) use.
 
-This is not merely based on guessing.
-When we recalculated the reliability coefficients and factor structure of the measures used in the replication projects, the observed reliability and validity of several measures did not convincingly show that these would be valid if presented alongside the measure in a study.
-While some measures were consistently not reliable and valid and some others were consistently reliable and valid, most were reliable and valid in some labs but not others.
-We also noted that some measures had convergence issues, where for some labs we could not get the factor model to fit nor Omega coefficient results.
-This may have been because of sample size issues, or the small number of items we often observed in the replication measures.
-However, gross misfit is also possible.
-Although, the psychometric indicators we used were applied rather broadly across a spectrum of different measures, and should not be used to make individual inferences for the measures.
-As a general overview, our results strongly indicate that these measures were frequently neither reliable nor valid for the contexts they were used in.
-
-We also observed that when a Cronbach's Alpha was reported for a measure in an original study, then their average Cronbach's Alpha observed among the replications were consistently relatively high.
-Meanwhile when no Cronbach's Alpha was reported in the original study, the reliability was often relatively low.
-This aligns with existing research indicating bias in reported Cronbach's Alpha values, with an excess of reported values at the common acceptably reliable threshold value of .70, and low reporting just below .70 [@husseyAberrantAbundanceCronbachs2023].
-Authors may be less inclined to report reliabilities when they fall below an acceptable threshold, but not otherwise.
-In combination with our inconsistent reliability and validity evidence this bias in reporting could create a false sense of security when looking only at the information that is reported in the literature.
-
-After all, there is little incentive for researchers to report this information if they don't want to.
-Reporting standards for measurement reporting are not broadly applied, and we observed this also when we looked at the information needed to reconstruct a measure for reuse.
-Similar to @flakeConstructValidityValidity2022, we observed that QMPs were not infrequent.
-In particular, like @flakeConstructValidityValidity2022, we observed that original research underreported information needed to reconstruct the measurement In original research the administration format and procedure for each was not properly described for around a third of the applicable measures, the number of items and response options for each around an eight, and how the index was calculated, how the items were recoded and example items were presented for each a little under half.
-We also found that about two-thirds of the measurements were modified between original and replication, and specific modifications were rarely validated or justified.
-This raises some questions around atributing the label direct replication to some of these studies.
-For example, the conscientiousness measure used for the replication of @defruytCloningersPsychobiologicalModel2000 was reduced from original NEO-PI-R 30-item measure to a two-item measure in the replication.
-It is highly unlikely that a measure with such a significant change would have a comparable validity and reliability to the original, and we did unsurprisingly observe convergence issues with validity as well as low reliability for this measure.
+The information needed to reconstruct a measure for reuse was also not consistently clearly reported.
+In particular, like @flakeConstructValidityValidity2022, we observed that original research underreported information needed to reconstruct the measurement In future research.
+The administration format and procedure for each was not properly described for around a third of the applicable measures.
+The number of items and response options were unclear for both in around an eight of the applicable measures, while how the index was calculated, how the items were recoded and example items were presented for each a little under half of the applicable measures.
 
@@
 We mostly checked that something relevant to a specific QMP item was reported, not whether that reporting thoroughly shared all the needed information.
-Regardless, any lack of information needed to recreate the measurement makes it harder for follow up research to validate the measure.
-
-Our goal with these findings is not to specifically scold the Many Labs replications nor the original studies.
+In particular, for our items checking whether a particular practice was justified or validated, we accepted any reason that was given, we did not check whether that reason was sufficient.
+For example, even if we did not code QMPs in validating modifications to measurement, this does not mean that Measurement Invariance was empirically established, even if it might have been important to do so.
+
+Inconsistency was not only observed in the reporting of measurement.
+When we recalculated the reliability coefficients and factor structure of the measures used in the replication projects, the observed reliability and validity varied considerably across labs.
+We also noted that some measures had convergence issues, where for some labs we could not get the factor model to fit.
+This may have been because of sample size issues, or the small number of items we often observed in the replication measures.
+However, gross misfit is also possible.
+Although, the psychometric indicators we used were applied rather broadly across a spectrum of different measures, and should not be used to make individual inferences for the measures.
+As a general overview, our results do carry the warning that we cannot merely assume that the measures used in our sample were valid and can be used for substantive interpretations.
+
+We also observed that when a Cronbach's Alpha was reported for a measure in an original study, then their average Cronbach's Alpha observed among the replications were consistently relatively high.
+Meanwhile when no Cronbach's Alpha was reported in the original study, the reliability was often relatively low.
+This aligns with existing research indicating bias in reported Cronbach's Alpha values, with an excess of reported values at the common acceptably reliable threshold value of .70, and low reporting just below .70 [@husseyAberrantAbundanceCronbachs2023].
+Authors may be less inclined to report reliabilities when they fall below an acceptable threshold, but not otherwise.
+In combination with our inconsistent reliability and validity evidence, this bias in reporting could create a false sense of security when looking only at what is reported.
+
+Overall, our intent is not to specifically scold the Many Labs replications nor the original studies.
 We commend the tremendous effort involved in the creation of the Many Labs projects, and we understand that for feasibility some corners had to be cut.
@@
 However, we would argue that full transparent measurement reporting is a responsibility both replications and original studies do have.
-Furthermore, even though validating measures is difficult, its necessity cannot be ignored.
-At one point this measure has to be validated properly, or else we cannot be certain that substantive interpretations on the basis of this measure are substantiated.
+Based on our results and the results of existing research, we believe that with current measurement reporting, you cannot reliably expect to observe the information you need to evaluate and understand the measurement that was used in a study.
+Even though a substantial proportion of measurement information was frequently reported - when looking at our intentionally non-strict coding protocol - information was almost never consistently clearly reported across our sample.
+Furthermore, critical information on reliability and validity in particular was rare.
+Finally, even though validating measures is difficult, its necessity cannot be ignored.
+If validity evidence for a measure is never obtained, it becomes questionable to draw substantive interpretations on the basis of responses to that measure.
+
+!!!detecting meaningful effects when checking for measurement invariance across groups requires large sample sizes [@meadePowerPrecisionConfirmatory2007; @frenchMeasurementInvarianceTechniques2016; @koziolImpactModelParameterization2018].!!!
 
@@
 
-We focused primarily on a unidimensionality test from a factor analysis as our indicator of validity as recalculated from the data.
-However, our factor analyses were not informed by theory specific to each measure, and were instead applied the same across the board.
-It is quite possible that a measure fails at our checks and is still a valid and reliable measure to use in its specific use case.
-We consider these checks to be indicators of the overall construct validity in our sample.
-The checks should not be interpreted as complete tests of validity, nor should they be interpreted at the individual measurement level.
-Future research may want to deep dive into this specific topic and focus on doing theory informed factor analysis tests on measurement data.
-
-One of the most impactful limitations was that we were unable to construct tests to compare the measurement properties between original and replication study, and replicated and non-replicated studies.
-This was in large part because there were simply to few measures with the relevant information.
-we planned to test.
+Our main indicator of construct validity obtained from the response data was our unidimensionality test from a factor analysis.
+However, our factor analyses were not informed by theory, and were not specific to each measure.
+Instead the structure of the model and the test was the same for all measures.
+It is quite possible that a measure fails at our checks and is still a valid and reliable measure in its specific use case.
+We use these checks to get an assessment of one element of construct validitty within our sample, not to make inferences for particular measures, nor to test construct validity completely.
+Future research may want to deep dive into this specific topic and focus on doing theory informed construct validity tests using openly available measurement reponse data.
+
+One of the most impactful limitations to our study design was that we were unable to conduct informative inferential tests on our data.
+This was in large part because there were simply to few measures with the relevant information for our test.
 We initially planned to test the significance of the difference in reported reliability between original and replication studies, and the relation between reliability and replication outcome.
-But due to the small number of reported reliabilities sand measures for which reliability could be calculated we were unable to perform these tests.
+But due to the small number of reported reliabilities and measures for which reliability could be calculated we were unable to perform these tests.
 However, this limitation is also one of our most important findings.
-While we were unable to perform our pre-registered tests, the fact that we couldn't, is telling regarding the lack of standards for reported measurement information in our sample.
+While we were unable to perform our pre-registered tests, the fact that we couldn't, is telling with respect to the lack of consistent measurement information reporting in our sample.
+
+!!!limited usefulness of the data!!!
 
@@
 
+???move to the paragraph above, the section in the discussion that describes the argument that replications dont have to report what is presumed to be in the original together with the counter-argument that modificaitons are regular, and as such measurement choice is fair game and should be motivated + an extra sentence that often information is not available in the original so it can hardly be relied upon???
+
 There were additional sources of information we could have included.
@@
 This is likely different for more recent research [@hardwickeEstimatingPrevalenceTransparency2022; @hamiltonPrevalencePredictorsData2023a].
-Including replications of recent research could help resolve some of the sample size issues for our tests.
+Including replications of recent original research could enable more comparisons based on open data from the original studies.
 Future research may wish to look at replications of more recent research to compare recalculated measurement information between original and replication.
-reliabilities and validity.
+
+!!!niet representatieief, kodnen niet alles doen, maar voor vervolgonderzoek mogelijk!!!
 
@@
 
-The two main issues we believe that should be addressed in the literature are: the common use of non-validated measurement, and the lack of transparency surrounding measurement reporting.
+There are two main issues we believe that should be addressed in the literature to improve measurement practices: the common use of non-validated measurement, and the lack of transparency surrounding measurement reporting.
 Unfortunately, there is no easy fix to these issues.
-Significant efforts are required, involving multiple members of the scientific community to bring about significant change.
-However, the positives are that these issues are interrelated, because solving transparency will benefit greater validation of measures, and that every little bit can help.
-
-First we recommend that reporting standards for measurement deserve a more central place.
-We found that reporting reliability and validity information was the exception rather than the rule, and even basic information such as how many items were in the measure was not always present.
+The widespread use of validated measurement requires measures for a large range of topics to be validated, a practice that currently occurs only rarely.
+Meanwhile improving transparency in reporting is an issue that many have tried to address in relation to other parts of , but universal success has remained elusive here ???CITATIONS???.
+However, the positives are first that these two issues are interrelated, because solving transparency will benefit greater validation of measures, and second that every instance of transparent reporting and validation helps reduce the current problem.
+
+Our first reccomendation is that reporting standards for measurement deserve a more central place.
+We found that reporting reliability and validity information was the exception rather than the rule, and even basic information such as how many items were in the measure was reported with little consistency among our sample of measures.
 The @americaneducationalresearchassociationStandardsEducationalPsychological2014 guidelines exist to guide researchers in the creation and validation of scales, but are not tailored as guidelines for general measurement reporting.
@@
 This point is critical to fueling our second recommendation: as a community we need to systematically evaluate and revise our measures.
-To do so existing measures need to first of all be reusable.
-Then researchers need to reuse existing measures.
-The obtained reliability and validity of the measure then need to be compared across multiple occasions, and finally a value judgement to determine in what contexts, if any, the measure is valid.
+To do so, we first need measures to be reusable.
+Second, researchers need to reuse existing measures.
+Third, the obtained reliability and validity of the measure then need to be compared across multiple occasions, and finally a value judgement to determine in what contexts, if any, the measure is valid has to be made.
 Transparent reporting takes care of the first step.
-For the second step, @elsonPsychologicalMeasuresArent2023 have suggested journals to implement the Standardisation Of BEhavior Research (SOBER) guidelines to specifically address issues of flexibility and norming in measurement.
+For the second step, @elsonPsychologicalMeasuresArent2023 have suggested journals to implement the Standardisation Of BEhavior Research (SOBER) guidelines to specifically address issues of flexibility and norming in measurement so that measures are reused in a comparable state.
 Furthermore, they propose an open repository of measurement protocols to facilitate the discovery of measures and building an evidence base.
 For the third and fourth step, two things are needed.
-First, there should be a space in the scientific literature for persistent measurement evaluation.
-Second, the data obtained from the measurement should be reusable in a more comprehensive analyses of the measure across contexts.
+First, there should be a space in the scientific literature for persistent measurement evaluation, just like how a place for replication studies in the literature has been suggested to provide persistent evaluation of effects.
+In fact, if replications were to play closer attention to measurement evaluation and reporting, they can function as an excellent validation test of the measure as well.
+Second, the data obtained from the measurement should be available for a comprehensive validaity analyses of the measure within different contexts.
 For this it would be best if the original data of the item responses and demographics is shared for each use of the measure.
-This way the measure's validity and reliability can be recomputed similarly to what was done in our analyses, but hopefully with a closer link to theory.
+This way the measure's validity and reliability can be recomputed similarly to what was done in our analyses, but with a closer link to theory.
 Otherwise, the summary statistics such as the variance-covariance structure, means, and standard deviations should be shared as these are sufficient for many basic factor analysis models.
@@
 Based on the results from our sample and the findings of existing research, the validity and reliability of psychological measurements is rarely reported and based on our data cannot be assumed to be generally correct.
-The lack of transparent reporting on the measurement further complicates evaluating and reusing the existing measures.
+The lack of consistent transparency in measurement reporting further complicates evaluating and reusing the existing measures.
 A change will be necessary.
 Otherwise, the basic premise that the measurement measures the variable it is intended to measure, will remain unsubstantiated for many psychological studies.
-Fortunately, even small steps towards improved reporting practices and single instances in cumulative measurement validation can already help proliferate validated measurement.
+Fortunately, even small steps towards improved reporting practices and single instances in cumulative measurement validation can already help to proliferate validated measurement.
 

### 2025-10-06 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_Omega_analyses.rmd
Rewrites

<!-- Supplementary Analyses B -->

```{r analysis-preferences}
# Seed for random number generation
set.seed(17042023)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Supplementary Analyses D: Omega Results

This appendix contains

We additionally estimated McDonald’s Omega for each lab from the same set of replications as for Cronbach's Alpha, since it has been argued to be a more informative measure of reliability than Cronbach's Alpha, while also simultaneously providing some validity evidence [@crutzenScaleQualityAlpha2017b; @dengTestingDifferenceReliability2017]. McDonald’s Omega was calculated using the omega function in the *psych* R package [*v`r getNamespaceVersion("psych")[[1]]`*; @R-psych]. Default arguments were used in the function except the nfactors argument, which was set to 1. No RG Meta-Analysis was performed on McDonald's Omega, as we could not find a formula for calculating its standard error.

## Results

```{r check_on_Omega_convergence, warning = FALSE}
is_mostly_na <- function(x){
  return((sum(is.na(x)) / length(x)) > .5) 
}

Omega_convergence_vector <- tapply(calculated_alpha_plot_data$omega.tot, calculated_alpha_plot_data$g, is_mostly_na)

# sum(Omega_convergence_vector)
```

Figure \@ref(fig:PlotOmegaDistributions) below shows the result of our Omega analyses. Note that while we show the distributions of omega values here, due to the lack of a formula to calculate the Omega standard error, we did not perform a meta-analysis on these results. Overall, our Omega coefficient analyses show a similar pattern between measures to that observed for the alpha coefficient albeit with generally higher coefficient scores across measures. However, not all improved. The two columns beside Figure \@ref(fig:PlotOmegaDistributions) show in how many labs each measure was used, as well as for how many labs an omega coefficient could be obtained, which was not always. In `r apa_num(sum(is.na(calculated_alpha_plot_data$omega.tot)) / nrow(calculated_alpha_plot_data) * 100)`% of labs, no omega coefficient could be obtained. For `r sum(Omega_convergence_vector)` measures the number of labs for which an Omega coefficient could not be obtained was even the majority. This relates to our findings from the unidimensionality tests, where some factor models did not converge.

```{r PlotOmegaDistributions, warning = FALSE, fig.cap = "Distributions of calculated McDonald’s Omega t  calculated for the responses on a measure at each lab location, across the eighteen measures for which raw data was available from which McDonald’s Omega t coefficients could be calculated. The N.Omg column besides the figure shows the number of lab locations for which an Omega coefficient could be successfully calculated. Due to lack of underlying model convergence an Omega coefficient could not be calculated for all lab locations, or any lab locations for the Der Fruyt et al. (2000) measure. The N.tot column shows the total number of lab locations at which the measure was taken. Any difference between N.omg and N.tot can be seen as an indication of the instability to get a stable estimate of an underlying facto model for some lab locations for that measure."}
# plot for omega
ggplot(calculated_alpha_plot_data, aes(x = omega.tot, y = g)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(alpha = 0.1) +

  # adding labels to show the number of labs per measure for which a total omega could be calculated
  geom_text(data = calculated_alpha_plot_data[1:19,], label = table(calculated_alpha_plot_data$g[!is.na(calculated_alpha_plot_data$omega.tot)]), x = 1.15, y = 1:19, size = 2.8) +
  # adding labels to show the number of labs per measure
  geom_text(data = calculated_alpha_plot_data[1:19,], label = table(calculated_alpha_plot_data$g), x = 1.35, y = 1:19, size = 2.8) +

  # theming
  theme_minimal() +
  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), 
                                                     "lines")) +

  # adding the replication line
  geom_hline(yintercept = 6.5, color = "red", size = 1) +

  # adding the necessary indicative texts
  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 7.25, ymax = 7.25, xmin = 0.01, xmax = 0.01) +
  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 6, ymax = 6, xmin = 0.01, xmax = 0.01) +
  annotation_custom(grob = textGrob(label = "N.Omg", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.08, xmax = 1.08) +
  annotation_custom(grob = textGrob(label = "N.Tot", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.28, xmax = 1.28) +

  coord_cartesian(xlim = c(0, 1), clip = "off") +

  ylab("") +
  xlab("Omega")

```

### 2025-12-02 Scripts/Manuscript/manuscript.Rmd
November manuscript rewrites.

@@
 ---
-title             : "Measurement Reliabily, Validity, and Reporting in Replicaitons and Original Research"
+title             : "Measurement Reliability, Construct Validity, and Transparent Reporting in Original and Replication Research"
 shorttitle        : "Measurement Reliability, Validity, and Reporting"
@@
 abstract: |
-  For a replication to be informative, measurement should be reliable and valid in both original and replication studies.
-
-keywords          : "reliability, construct validity, measurement, reporting, questionable measurement practices, replications, informative replications, psychology"
-wordcount         : "1"
+  To assess psychological phenomena we need reliable and valid measurement of the construct(s) of interest.
+Information should therefore be reported alongside the measure to enable the evaluation of reliability and validity.
+Additionally, to ensure that reliable and valid measures can be reused in future research, the measure should be documented in sufficient detail.
+Therefore, we investigated the measurement reporting in a sample of 77 measures within 56 Many Labs replications and related original articles (Ebersole et al., 2016, 2020; Klein et al., 2014, 2018).
+We found that the information relevant for the reuse of a measure was reported in full for around half the replication measures, and only 5.2% of the original studies.
+We also observed that only around a third of multi-item measures in original studies and 11.4% in replications reported a reliability coefficient, with comparable proportions for reporting any psychometric validity evidence.
+Besides reporting, we also performed checks of the reliability and construct validity using the openly available Many Labs item response data.
+We observed that the reliability and construct validity of the measures was rarely stable across contexts.
+These results corroborate existing findings that measurement reporting in published research lacks transparency, and that this transparency may in certain contexts cover up insufficient reliability and valdity.
+Finally, we offer suggestions on how to increase measurement reporting transparancy and the use of validated measures.
+
+keywords          : "reliability, construct validity, measurement, reporting, transparent reporting, replications, psychology"
+wordcount         : "225"
 
@@
 floatsintext      : yes
-linenumbers       : no
+linenumbers       : yes
 draft             : no
@@
 
-csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
+csl               : "vancouver.csl"
 documentclass     : "apa7"
@@
 The challenge with measurement in quantitative psychological research is that unlike height or weight, psychological constructs cannot be directly measured, as they cannot be directly observed.
-Instead, we use scores from a measurement as an indicator for a psychological construct.
+Instead, we use scores from a measure as an indicator for a psychological construct.
 Yet, it cannot simply be assumed that any measure will form a good indicator of the constructs of interest.
 The measure has to be validated by establishing the reliability and construct validity of the measure.
-"Reliability refers to the consistency of scale scores when a construct is assessed multiple times or in multiple ways" [@crutzenScaleQualityAlpha2017b; pp.
+Following the definition of Crutzen and Peters, “[r]eliability refers to the consistency of scale scores when a construct is assessed multiple times or in multiple ways” [@crutzenScaleQualityAlpha2017b; pp.
 244].
-Meanwhile, construct validity refers to whether the variance in the measured item scores between participants can be attributed to the variance in the unobserved construct(s) of interest between participants [@cronbachConstructValidityPsychological1955; @vazireCredibilityReplicabilityImproving2022].
-
-However, research indicates that measures often lack reliability and construct validity evidence !!!CITE!!!, either because the evidence is not reported, or because the measures are not validated.
-@flakeMeasurementSchmeasurementQuestionable2020 dubbed these practices - that raise doubts about a measurement’s validity - Questionable Measurement Practices (QMPs), being a term analogous to Questionable Research Practices [QRPs; Simmons et al.
-(2011); John et al.
-(2012); Wicherts et al.
-(2016)].
-Existing research has already shown practices that reflect QMPs to be relatively common in both replication and original studies !!!CITE!!!.
-The purpose of this study is to provide a combined overview of the information on the reporting practices of measurement in replication and original with reliability and construct validity indices obtained from the shared item response data.
-By combining information on reporting with our own calculated indices, we can reflect on which validity issues lie in reporting and which are an issue with the measurement itself.
+In turn, construct validity refers to whether the variance in the measured item scores between participants can be attributed to the variance in the unobserved construct(s) of interest between participants [@cronbachConstructValidityPsychological1955].
+In practice, the measure itself is always validated within one or more use cases of a specific measurement procedure and the context in which that measurement took place, such as the sample characteristics, location, and time.
+
+However, psychological measures often lack reliability and construct validity evidence, either because the evidence is not reported, or because the measures are not validated at all [@beckmanHowReliableAre2004; @barryValidityReliabilityReporting2014; @flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020; @flakeConstructValidityValidity2022].
+Flake et al @flakeMeasurementSchmeasurementQuestionable2020 dubbed these such practices --- that raise doubts about the validity of a measurement --- “Questionable Measurement Practices” (QMPs), being a term analogous to Questionable Research Practices [QRPs; @simmonsFalsePositivePsychologyUndisclosed2011a; @johnMeasuringPrevalenceQuestionable2012a; @wichertsDegreesFreedomPlanning2016a].
+A recent line of research has already shown QMPs to be relatively common in both original and replication psychology studies, damaging the trustworthiness and applicability of psychological research findings [@flakeConstructValidityValidity2022; @husseyAberrantAbundanceCronbachs2023].
+
+The purpose of this study is to assess the measurement reporting practices of item-based measures in a diverse and seminal sample of original and replication studies in psychology.
+In addition, we will use the available item response data to calculate reliability and construct validity indices.
+Through the combination of assessing the measurement reporting and the calculated indices, we reflect on the apparent validity of the measurement based on the reported information, compared to the validity assessment when going beyond the reported information and checking the item response data.
 
@@
 
-One issue that has been observed with respect to measurement validation is that the reported measurement information is typically insufficient for readers to understand, evaluate, and reuse the measurement that was used [!!!CITE].
-@flakeConstructValidityValidity2022 documented the measurement reporting practices among 100 replications and their respective original articles from the Reproducibility Project Psychology [@opensciencecollaborationEstimatingReproducibilityPsychological2015].
+One issue that has been observed with respect to measurement validation is that the reported measurement information is typically insufficient for readers to understand, evaluate, and reuse the measurement that was used.
+Flake et al @flakeConstructValidityValidity2022 documented the measurement reporting practices among 100 original psychology articles and their respective replications from the Reproducibility Project Psychology [@opensciencecollaborationEstimatingReproducibilityPsychological2015].
 They coded the number of measures, the content of the measures, and information describing and justifying the measurement.
@@
 A similar lack of reliability and validity reporting has been observed in other studies as well [@hoganEmpiricalStudyReporting2004; @flakeConstructValidationSocial2017].
-If readers cannot glance the construct validity and reliability of a measure from the reported information, then readers lack the basic information needed to determine whether the measured variables are actually related to the constructs of interest.
-In turn, if we cannot determine whether the constructs of interest are captured in the measured variables or not, then the relation of the results of the statistical analysis using these variables and any psychological phenomena of interest is also strenuous.
-In short, if the reported information does not show that the measurement was valid, then any substantive conclusions from the data are unfortunately left unsubstantiated.
-
-Further findings by @flakeConstructValidityValidity2022 and others [@flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020] show that measurement reporting was not only limited in terms of the reliability and validity evidence needed to evaluate the measure.
-The lack of information was also observed for basic content descriptions such as the number of items, the response format, and the scoring of the scale were irregular.
-This creates challenges for future researchers that want to reuse to measurement.
-Specifically for replication studies attempting to reconstruct the measurement from these incomplete descriptions, they may end up with a measurement that assesses the constructs in a substantially different way from the original study, or even assess different constructs altogether.
-If different constructs are assessed, the replication cannot be seen as a test of the same phenomenon as the original.
-If the same constructs are assessed, but in a substantially different way, the estimated effects in the replication cannot easily be put side-by-side with the effects in the original study.
+If readers cannot infer the construct validity and reliability of a measure from the reported information, then readers lack the basic information needed to determine whether the measured variables are actually related to the constructs of interest.
+In turn, if we cannot determine whether the constructs of interest are captured in the measured variables or not, then the relation of the results of the statistical analysis using these variables and any psychological phenomena of interest is also tenuous.
+In short, if the reported information does not show that the measurement was valid, then any substantive conclusions from the data are left unsupported.
+
+Further findings by Flake et al @flakeConstructValidityValidity2022 and others [@flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020] show that measurement reporting was not only limited in terms of the reliability and validity evidence.
+A lack of clearly reported information was also observed for basic content descriptions such as the number of items, the response format, and the scoring of the scale.
+This creates challenges for future researchers who want to reuse the measure to assess the same construct.
+Specifically, replication studies attempting to reconstruct the measurement from these incomplete descriptions may end up with a measurement that assesses the constructs in a substantially different way from the original study, or even assess different constructs altogether.
+If different constructs are assessed, the replication cannot be seen as a test of the same phenomenon as in the original study.
+If the same constructs are assessed, but in a substantially different way, the estimated effects in the replication cannot be easily compared to the effects in the original study.
 In either case, substantial comparisons between original and replication are hindered.
-The inability to reuse a measure does not only affect replications however, it also limits our ability to validate the measure thoroughly.
-Even if the measure is shown to be construct valid in one context, the factor relations may not be stable for this measure in other contexts and implementations, a concept known as measurement invariance [@hornPracticalTheoreticalGuide1992; @cheungDirectComparisonApproach2012].
-While it is important to assess measurement (in)variance before using measures in a new context, if that measure is not reusable, the invariance cannot even be assessed.
-
-Our first aim is to extend these existing findings on measurement reporting practices with a descriptive account of these practices for the Many Labs replications and the related original studies.
-We evaluate to what extent the reporting and use of item-based measurement scales in our sample allows us to evaluate and reuse the measurement.
-We do not ourselves evaluate whether the reported measurement information provide sufficient justification for its use, merely that information is reported such that that part of the measurement can be evaluated.
-We extend earlier investigations through new questions about the presence of justification for measurement selection or creation, item transformations such as reverse coding being described, the administration format being described, a change in the number of items from the source, whether changes in items response options, or number of items, or administration were validated or justified.
-All of our measurement reporting items were inspired by and categorized based on the QMP table in @flakeMeasurementSchmeasurementQuestionable2020.
-
-We chose the Many Labs replications and associated original studies as our sample, due to them being of particular interest.
-The Many Labs replications were a series of large-scale collaborations in which multiple labs across the world directly replicated classic and contemporary psychological studies [@kleinInvestigatingVariationReplicability2014a; @ebersoleManyLabs32016; @kleinManyLabs22018b; @ebersoleManyLabs52020d; @kleinManyLabs42022].
-The original studies chosen for replication in the Many Labs were not only picked based on ease and feasibility, but importantly for us they were also picked to display a diverse range of effects that were also of key interest to the field.
-This makes these studies an important sample to evaluate, because the replicated effects represent a broad range of relevant findings.
-Furthermore, because the Many Labs projects used preregistered and documented structured protocols, we expect the measurement reporting for the replications to represent a high standard within the field.
+
+Our first aim is to extend the existing findings on measurement reporting practices with a descriptive account of these practices for the Many Labs replications and the related original studies.
+We will evaluate to what extent the reporting of item-based scales in our sample are transparent enough to facilitate the evaluation and reuse of these measurements.
+The Many Labs replications are a series of large-scale collaborations, in which multiple labs across the world directly replicated classic and contemporary psychological studies [@kleinInvestigatingVariationReplicability2014a; @ebersoleManyLabs32016; @kleinManyLabs22018b; @ebersoleManyLabs52020d; @kleinManyLabs42022].
+The original studies chosen for replication in the Many Labs were not only picked based on feasibility, but importantly for us the sample of effects to replicate was chosen to contain a diverse range of seminal effects.
+Furthermore, because the Many Labs projects used preregistered and documented structured protocols, we expected the measurement reporting for the replications to represent a high standard within the field.
 Any issues in measurement reporting here might suggest that other replications could face similar or greater challenges.
@@
 
-Psychometrics offers various ways in which to assess construct validity and reliability [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011].
-It is often the results from these psychometric analyses that form one of the pre-requisite pieces of evidence for assessing whether or not the measure is valid or not.
-
-When psychometric indicators are reported - which as mentioned earlier is not common - it is often limited to Cronbach's Alpha, a commonly used indicator for reliability.
-Cronbach's Alpha comes with strong assumptions that are themselves rarely tested [@crutzenScaleQualityAlpha2017b].
-Furthermore, research by @husseyAberrantAbundanceCronbachs2023 has shown evidence that the reporting of reliability may not only be little, but also biased.
-They observed a disproportional amount of Cronbach's Alpha values at the common acceptably reliable threshold value of .70, and relatively low reporting below .70.
-Thus, the lack of reported measurement evidence may on occasion be hiding psychometric skeletons in the closet.
-
-As a result, if we want to evaluate the reliability of measurement in our sample, we cannot rely on the reported information alone to give us a representative picture.
-Thus, we evaluate the measurement reliability within the Many Labs original and replication studies by estimating it from the item response data.
+Two key aspects of measurement quality are reliability and construct validity.
+Psychometrics offers various methods for assessing these properties [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011].
+The results of such psychometric analyses often serve as essential evidence for evaluating a measure’s validity.
+
+Reliability serves as a pre-requisite for a valid measure in most cases, because a measure for which a participant’s response is not consistent, cannot capture a stable construct [Kaplan and Saccuzzo (2013, pp.
+154–155)].
+It is therefore concerning that --- as mentioned earlier --- the reporting of psychometric indicators of reliability is not common, and is often limited to Cronbach’s Alpha.
+Unfortunate, because Cronbach’s Alpha comes with strong assumptions that are rarely tested [@crutzenScaleQualityAlpha2017b].
+Furthermore, research by Hussey et al @husseyAberrantAbundanceCronbachs2023 has shown evidence that the reporting of reliability may not only be uncommon, but also biased.
+They observed a disproportional number of Cronbach’s Alpha values at the common acceptably reliability threshold value of .70, and relatively low reporting below .70.
+Thus, the lack of reported measurement evidence may indicate psychometric skeletons hiding in the closet.
+
+As a result, if we want to evaluate the reliability of a measure in our sample, we cannot rely on the reported information alone to paint us a representative picture.
+Therefore, we also evaluated the measurement reliability within the Many Labs original and replication studies by estimating it from the item response data.
 The data on the item responses are openly available per lab for our sample.
-As a result, we can evaluate not only the reliability per measure, but also the variation in reliability across labs.
-The variation is relevant because Cronbach's alpha is an indicator of reliability within a particular sample and not of the reliability of the measure in general, as it is proportional to the total variance in the target variable in the sample.
-Despite this many researchers report and interpret Cronbach's Alpha as a universal quality of the measure [@cortinaWhatCoefficientAlpha1993; @schmittUsesAbusesCoefficient1996].
-@maireadshawMeasurementPracticesLargescale2020 has so far observed that for Many Labs 2 the overall sample Cronbach's alpha level across scales was below .5, a degree of reliability far below what many would consider acceptable for most research purposes.
-It is our second aim to empirically evaluate both the degree as well as the variation of reliability of the measures in our sample that includes the other Many Labs projects.
-
-## Unidimensionality
-
-Reliability is a pre-requisite to construct validity, because a measure for which a participant’s response is not consistent, cannot capture a stable construct [Kaplan and Saccuzzo (2013, pp.
-154–155)].
-Another, important pre-requisite for many measures is unidimensionality.
-Unidimensionality means that the items on a measure assess, show evidence of measuring a single construct.
-Thus, if a set of items are intended to measure the same one construct, then unidimensionality is key to the construct validity of that set of items.
-Additionally, most reliability indicators - including Cronbach's Alpha - cannot be assessed without first making sure that the measure is unidimensional.
-Thus for our third aim we again used the item response data.
-This time hitting two birds with one stone.
-We check the measures' construct validity, and we check if one of the key assumptions of Cronbach's Alpha is met.
-
-!!!substantively belangrijk, want de scores worden als unidimensioneel geinterpreteerd.
-Alpha assumptie testen, als kleiner deel bespreken; Reliability kan in sommige gevallen slecht zijn als de schaal gewoon multi-dimensioneel is.
-Eerst een beetje techniek, daarna meer kwalitatief oordeel dat het gewoon belangrijk is voor interpretatie!!!
-
-@maireadshawMeasurementPracticesLargescale2020 checked the factor structure on the openly available item data from Many Labs 2 [@kleinManyLabs22018b].
-They observed that no scales in their sample did the results from the factor analysis meet all of their evaluation criteria for unidimensionality.
-@maireadshawMeasurementPracticesLargescale2020 had access to measures that were used across multiple contexts to evaluate their validity across more than one instance.
-However, in practice, measures are frequently made on the fly and reused maybe once or never [@weidmanJingleJangleEmotion2017; @elsonPsychologicalMeasuresArent2023; @anvariFragmentedFieldConstruct2025; @anvariDefragmentingPsychology2025].
-This is dangerous, because these measures are often not validated before use, and if they cannot be reused, they are not going to be validated afterwards either.
-Furthermore, validating a scale requires substantial sample sizes in most cases [@maccallumSampleSizeFactor1999, @gorsuchFactorAnalysis2013], sample sizes that many original studies cannot obtain, in which case these measures are reliant on future research to obtain the required sample size to validate the measure.
-
-Thus, for our third research aim - similarly to our aim with reliability - we check the unidimensionality of measures from the Many Labs projects per lab with meta-analytic assessment of the variation in unidimensionality across labs.
-The combined goal of our three research aims is to create a description of the measurement use in our data.
+Therefore, we can evaluate not only the reliability per measure, but also the variation in reliability across labs.
+The variation is relevant because Cronbach’s Alpha is an indicator of reliability within a particular sample and not of the reliability of the measure in general, as it is proportional to the total variance in the target variable in the sample.
+Still, many researchers report and interpret Cronbach’s Alpha as a universal quality of the measure [@cortinaWhatCoefficientAlpha1993; @schmittUsesAbusesCoefficient1996].
+@maireadshawMeasurementPracticesLargescale2020 have already observed that for Many Labs 2 the overall sample Cronbach’s Alpha level across scales was below .5, a degree of reliability far below what many would consider acceptable for most research purposes.
+Our second research aim is therefore to extend these findings by empirically evaluating both the degree as well as the variation of reliability of the measures in Many Labs projects 1, 2, 3, and 5.
+
+## Construct Validity and Unidimensionality
+
+Besides reliability, construct validity is key to establish for any measure.
+A multi-stage process is required to statistically and substantially establish a link between the measurement and the construct of interest.
+For example, the way a measure's items relate to each other and to the underlying concept (the factor relations) can differ substantially across contexts, a concept known as measurement invariance [@hornPracticalTheoreticalGuide1992; @cheungDirectComparisonApproach2012].
+Thus, we cannot assume that the measure is valid in each context it is used in or meant to be used in, it is something that has to be established for each context.
+Besides investigating the factor structure, the measure should also be backed up substantively and logically [@borgstedeMeaningfulMeasurementRequires2023].
+However, what we typically observe in psychological research is that measures are rarely substantiated with validity evidence [@beckmanHowReliableAre2004; @barryValidityReliabilityReporting2014; @flakeConstructValidationSocial2017; @flakeConstructValidityValidity2022].
+This may in part be because the sample sizes required in validating a scale can often be larger than many studies are able to obtain [@maccallumSampleSizeFactor1999, @gorsuchFactorAnalysis2013].
+Alternatively, researchers may not recognize measurement validation as part of their research method.
+Yet what has also been observed in the literature is that many measures are created ad hoc and reused maybe once or not at all [@weidmanJingleJangleEmotion2017; @elsonPsychologicalMeasuresArent2023; @anvariFragmentedFieldConstruct2025; @anvariDefragmentingPsychology2025].
+This makes it extremely unlikely that the validity of these measure will ever be assessed at all, let alone be thoroughly investigated by analyzing measurement invariance across multiple groups using substantial sample sizes [@meadePowerPrecisionConfirmatory2007; @frenchMeasurementInvarianceTechniques2016; @koziolImpactModelParameterization2018].
+
+One preliminary psychometric check that could easily be conducted is to see if the number of constructs measured by the items of the measurement match the intended number of constructs.
+Most often the scores on a measure or subscales of a measure are aggregated and interpreted as a singular index.
+In that case, the measure should be unidimensional.
+Otherwise, the researcher is interpreting a set of scores to be one concept when in fact they are multiple distinct concepts.
+Additionally, most reliability indicators --- including Cronbach’s Alpha --- cannot properly estimate true variance when it is spread across distinct constructs, and will thus give an inaccurate estimate of reliability [@schmittUsesAbusesCoefficient1996; @crutzenScaleQualityAlpha2017b].
+
+Mairead shaw et al @maireadshawMeasurementPracticesLargescale2020 checked the dimensionality of the measurements from Many Labs 2 [@kleinManyLabs22018b], and while some support for unidimensionality was present, they found that none of the scales in their sample met all of their criteria for unidimensionality.
+Because the Many Labs replications reused existing measures across contexts, Mairead shaw et al @maireadshawMeasurementPracticesLargescale2020 could assess validity across contexts.
+Our third research aim is to extend these findings.
+We will perform our own checks of unidimensionality on measures from Many Labs 1, 2, 3, and 5 per lab, and include a meta-analytic assessment of the variation in unidimensionality across labs.
+The combined goal of our three research aims is to provide a descriptive account of the reliability, construct validity, and reporting of measurement in the included Many Labs study pairs.
 
@@
 We deviated from our coding protocol as is explained further in the text.
-Our pre-registered analyses have been move to the [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd) in favor of focusing on the descriptive results here.
+The results from our preregistered analyses are described in [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd).
+In the main text, we focus on the descriptive results.
 
@@
 ## Data Source
-
 The data consists of three main sources: replication datasets, replication protocols, and original study articles.
 We retrieved the data of Many Labs 1, 2, 3, & 5 [@kleinInvestigatingVariationReplicability2014a; @ebersoleManyLabs32016; @kleinManyLabs22018b; @ebersoleManyLabs52020d] from their respective OSF pages.
-Many Labs 4 [@kleinManyLabs42022] was excluded, as there was no publicly available replication protocol.
-Additionally, the replication of [@crosbyWhereWeLook2008a] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures.
+Many Labs 4 [@kleinManyLabs42022] was excluded, as there were no publicly available replication protocols.
+Additionally, we excluded the replication of [@crosbyWhereWeLook2008a] in Many Labs 5, as it made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures.
 
@@
 Our unit of analysis is a measure of a single variable within a replication protocol or original article that was used in the main analysis that was replicated.
-For example, if conscientiousness and agreeableness were both measured using a big-five personality questionnaire, each of which was a variable in a replicated effect, then both the conscientiousness and agreeableness part of that questionnaire would be coded as their own unit of analysis.
+For example, if conscientiousness and agreeableness were both measured using the Big 5 Personality Test, each of which was a variable in a replicated effect, then both the conscientiousness and agreeableness part of that questionnaire would be coded as their own unit of analysis.
 We also allowed for multiple variables to be measured per study.
@@
 We did not include acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses.
-Our final sample size was `r nrow(coded_data_replications)` measures of unique variables for both original and replication studies\^[Initially the original articles contained 3 more measures of unique variables than the replication protocols.
+Our final sample size was `r nrow(coded_data_replications)` measures of unique variables for both original and replication studies.
+Initially, the original articles contained 3 more measures of unique variables than the replication protocols.
 This difference was due to the way that the moral foundations questionnaire was framed in the original article compared to in the replication protocol.
 In the original article it was framed as measuring five different moral foundations, while in the replication protocol the measure assessed the two overarching categories that were used to test the main effect in both the original and replication research.
-The measurement information reported was comparable across all five categories, and thus it was deemed that the measurement could be reduced to reflect two overarching categories facilitate easier comparison between measurement in original and replication.]
+The measurement information reported was comparable across all five categories, and thus it was deemed that the measurement could be reduced to reflect two overarching categories to facilitate easier comparison between measurement in original and replication.
 
@@
 The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>.
-Both the replication protocols and replication datasets were scanned through to ensure that they were the correct files to code measurement reporting information from.
+We skimmed both the replication protocols and replication datasets to ensure that they were the correct files to code measurement reporting information from.
 However, no coding or analysis of either of them had taken place before the analyses were preregistered.
@@
 For the analyses, we extracted the scores on the items of each previously identified measure that also met our inclusion criteria specified in the paragraph below.
-When scores could not be clearly identified, any available codebooks, analysis scripts, or study materials were used to identify the relevant scores.
-
-To be included in our reliability recalculations and factor analyses, the measure had to be a scale of multiple items.
+When scores could not be clearly identified based on the information available in the dataset and the replication protocol, any available codebooks, analysis scripts, or study materials were used to identify the relevant scores.
+
+To be included as part of the subset of measures we analyzed in our reliability recalculations and factor analyses, the measure had to be a scale of multiple items.
 If cleaned data were available, we chose these over raw data, to ensure that variables were coded as intended (e.g., no reverse-coded items).
 We omitted pilot data from the analyses.
-These criteria combined with difficulties in retrieving suitable data from some datasets resulted in a set of item score data from `r length(unique(calculated_reliability_lab_data$g))` replication sets spread across on average approximately `r round(mean(table(calculated_reliability_lab_data$g)), 0)` lab locations for our analyses.
+These criteria combined with our inability to definitively determine which variables in the dataset corresponded to the items on the measure of interest resulted in a set of item score data from `r length(unique(calculated_reliability_lab_data$g))` replication sets spread across on average approximately `r round(mean(table(calculated_reliability_lab_data$g)), 0)` lab locations for our analyses.
 
@@
 The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of the replication of an original study.
-These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd>).
+These were retrieved from the Open Science Framework (OSF) pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd>).
 
@@
 
-### Coding Protocol
-
-We extracted reported measurement information from the original articles and replication protocols using our preregistered coding protocol.
-We extracted the reported reliability coefficient and type of index (Cronbach’s Alpha, retest, interrater, etc.) when present.
-Similarly, we coded if any psychometric construct validity evidence, such as a factor analysis, was presented for the measure.
-We additionally included twenty items that were based on the QMP table presented in @flakeMeasurementSchmeasurementQuestionable2020.
-For each of these items we checked if a piece information we would want to see reported with regards to the measurement was described.
-If the information was clearly reported we coded the item as true; false if not or not clear enough; or not applicable if not relevant for that measure (e.g., reporting results from a factor analysis for single-item measures).
-Example items can be seen in Table \@ref(tab:QMPCodingInfoTable).
+### Measurement Reporting
+
+We evaluated the transparency of the measurement reporting practices within the original articles and replication protocols using our preregistered coding protocol containing items assessing twenty three reporting practices.
+The items were based on Table \@ref(tab:QMPCodingInfoTable) presented in Flake et al @flakeMeasurementSchmeasurementQuestionable2020, listing what measurement information to report.
+We coded an item as “true” if the relevant measurement information was clearly reported, “false” if it was missing or unclear, and “not applicable” if it was irrelevant for that measure (e.g., reporting factor analysis results for single-item measures).
+These items thus indicate transparent reporting practices, which can be seen as the opposite of QMPs.
+We grouped the items into five categories, each representing a different element in measurement reporting.
+Example items are listed in Table \@ref(tab:QMPCodingInfoTable).
 
 ```{r QMPCodingInfoTable, warning = FALSE}
-QMP_info_dataframe <- data.frame(Category = c("Definition", "", "", "Operationalisation", "", "", "", "Selection/Creation", "", "", "Quantification", "Modification", "", "", "", "", ""),
-           'N Questions' = c("1", "", "", "5", "", "", "", "4", "", "", "4", "6", "", "", "", "", ""),
-           'Example Question' = c("A psychological/sociological definition",
+QMP_info_dataframe <- data.frame(Category = c("Definition", "", "", "Operationalisation", "", "", "", "", "Selection/Creation", "", "", "Quantification", "Modification", "", "", "", "", ""),
+           'N Items' = c("1", "", "", "5", "", "", "", "", "7", "", "", "4", "6", "", "", "", "", ""),
+           'Example Item' = c("A psychological/sociological definition",
             "is given to the name of the measured",
@@
             "public/in a lab) are described (Note:",
-            "both should be present for a true rating).", 
+            "both should be present for this item to be", 
+            "rated as “true”).", 
             "The source of the scale is provided",
@@
 # making the column names look less robot speak-y.
-colnames(QMP_info_dataframe) <- c("Category", "N Questions", "Example Question")
+colnames(QMP_info_dataframe) <- c("Category", "N Items", "Example Item")
 
@@
   QMP_info_dataframe, align = c("l", "r", "l")
-  , caption = "Information of QMP coding variables per category."
-  , note = "N Questions refers only to the questions used for calculating QMP ratios.
-Selection and creation share a category as the justifications and requirements in selecting a measure are similar to those for creating a new measure."
+  , caption = "Example items used to code transparent measurement reporting practices across five categories linking to different aspects of measurement"
+  , note = "Selection and creation of a measure share a category because the justifications and requirements in selecting a measure are similar to those for creating a new measure."
   , escape = FALSE, placement = "htp", booktabs = TRUE)
@@
 
-After the initial coding, we made minor revisions to fourteen of the twenty QMP items from the preregistered coding protocol.
-These items were changed after familiarizing ourselves with the way measurement was reported, and it became clear that our criteria were too stringent in the exact way and degree of detail in which to present things.
-For example, in the initial protocol, an example item had to be present within the article or protocol itself, or else this was counted as a QMP.
+Included within the list of measurement reporting information is crucially also the reported reliability coefficient and type of index (Cronbach’s Alpha, test-retest correlation, inter-rater reliability coefficient, etc.) when present.
+As well as the presence of any psychometric construct validity evidence for the measure, such as the results from a factor analysis.
+
+After the initial coding, we made minor alterations from the preregistered coding protocol for fourteen of the twenty three measurement reporting practice items.
+These items were changed after familiarizing ourselves with the way measurement was reported, and it became clear that our criteria were too stringent.
+For example, in the initial protocol, an example item of the measure had to be present within the article or protocol itself, for the measurement practice to be considered clearly reported.
 In the revised protocol, references to online appendices with example items were also considered sufficient for this item.
 The analyses, tables, and figures presented in this article are all based on the revised coding protocol.
-The equivalent QMP descriptives obtained with the initial protocol can be found in [Supplementary Analyses B](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_ratio_table.rmd).
-
-We initially intended to construct a QMP index from the QMP items and perform regression analyses between this index and replication outcomes.
-However, this index could not be validated properly and its results would be misleading to present here in the main article.
+The equivalent measurement reporting descriptives obtained with the initial protocol can be found in [Supplementary Analyses B](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_ratio_table.rmd).
+
+We initially intended to construct an index from the transparent measurement reporting items and perform regression analyses on this index and associated replication outcomes.
+However, this index could not be validated properly, due to a lack of reported information and because we do not have any theorized outcome that could function as a suitable index for predictive validity.
+Results based on this index would be misleading to present here in the main article.
 A more detailed explanation of what was omitted and why, as well as the results from these preregistered analyses can be found in [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd).
@@
 
-### Calculating Reliaiblity
-
-We calculated reliability for each measure from the replication datasets with suitable data for each lab the measure was used in.
-We calculated both Cronbach’s alpha, as well as its standard error using formulas 2 & 3 from @duhachekAlphasStandardError2004a.
-We used these values to conduct a meta-analysis of the measure's reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analysis [@botellaManagingHeterogeneityVariance2012; @lopez-ibanezReliabilityGeneralizationMetaanalysis2024; @vacha-haaseReliabilityGeneralizationExploring1998].
+### Calculating Reliability
+
+We calculated reliability from the item responses on each measure for each lab the measure was used in based on the replication datasets with suitable data.
+We calculated both Cronbach’s Alpha, as well as its standard error using formulas 2 & 3 from Duhachek and Lacobucci @duhachekAlphasStandardError2004a.
+We used these values to conduct a meta-analysis of the measure’s reliability, also referred to as a Reliability Generalization (RG) Meta-Analysis [@botellaManagingHeterogeneityVariance2012; @lopez-ibanezReliabilityGeneralizationMetaanalysis2024; @vacha-haaseReliabilityGeneralizationExploring1998].
 We performed the RG Meta-Analysis using the rma function from the metafor R package [*v`r getNamespaceVersion("metafor")[[1]]`*; @R-metafor] and default settings.
-We then used the results from the meta-analysis to evaluate the heterogeneity via the tau statistic and the Cochran's Q-test [@cochranCombinationEstimatesDifferent1954].
+We then used the results from the meta-analysis to evaluate the heterogeneity via the tau statistic and the Cochran’s Q-test [@cochranCombinationEstimatesDifferent1954].
 These indicators have received criticism as indicators of heterogeneity, especially when within study sample sizes are small and power to detect heterogeneity is low [@hoaglinMisunderstandingsCochransTest2016; @pereiraCriticalInterpretationCochrans2010].
-Therefore, we also present the prediction interval and implore that the heterogeneity results should be viewed critically [@borensteinAvoidingCommonMistakes2024].
-We implemented no correction for bias, because the Many Labs replications were not at risk of publication bias.
-
-Our analyses will focus on Cronbach’s Alpha, because it is common in research, which also allows us to make comparisons between calculated and reported reliabilities.
+Therefore, we also present the 95% prediction interval (the interval within which a the measure’s Cronbach’s Alpha is expected to fall if used again within the same population) and implore that the heterogeneity results should be viewed critically [@borensteinAvoidingCommonMistakes2024].
+We implemented no correction for publication bias, because the Many Labs replications were guaranteed to be published regardless of their outcomes.
+
+Our analyses will focus on Cronbach’s Alpha, because it is the most commonly reported reliability indicator, which also allows us to make comparisons between calculated and reported reliabilities.
 Furthermore, we were able to calculate the standard error of alpha to be used in the RG meta-analysis.
-However, Cronbach's Alpha comes with strong assumptions on the underlying factor structure, including that the measure is unidimensional, which means that there should a single factor underlying the measurement scores.
-Therefore, we also estimated McDonald’s Omega for each lab from the same set of replications as for Cronbach's Alpha, since it has been argued to be a more informative measure of reliability than Cronbach's Alpha with less strict assumptions [@crutzenScaleQualityAlpha2017b; @dengTestingDifferenceReliability2017].
-The results based on Omega can be found in [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_omega_analyses.Rmd).
+However, Cronbach’s Alpha comes with strong assumptions on the underlying factor structure, including that the measure is unidimensional, which means that there should a single factor underlying the measurement scores.
+Therefore, we also estimated McDonald’s Omega for each lab from the same set of replications as for Cronbach’s Alpha, since it has been argued to be a more informative measure of reliability than Cronbach’s Alpha with less strict assumptions [@crutzenScaleQualityAlpha2017b; @dengTestingDifferenceReliability2017].
+The results based on McDonald’s Omega can be found in [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_omega_analyses.Rmd).
 
@@
 
-All measurement items for which we checked unidimensionality, were used to form a singular index of one latent variable.
+All measurement items for which we checked unidimensionality were used to form a singular index of one latent variable in their respective replications.
 Therefore, unidimensionality presents a valuable indication of the construct validity of a measure in our dataset.
-To test for unidimensionality, we fit a single-factor model on the item response data of each individual lab with the relevant measurement data.
-This was done to simulate the inference a lab would make if they were to check for unidimensionality.
-Our inference of unidimensionality is based on a set of five model fit indices.
-If the indices point towards a good unidimensional fit that is also consistent across labs - as we also evaluate the variability across labs - then we can say that with this preliminary evidence at least, we did not observe any issues with the construct validity of that measure.
-If the indices point towards a lack of unidimensionality in a substantial number of labs, that would be a warning sign for the lack of construct validity for that measure.
-Our goal is not to fully check the validity of these measures, this requires additional steps that are beyond the scope of this study.
-
-For the first four of our five fit indices we fit a Confirmatory Factor Analysis (CFA) model with one factor to the data, and we then evaluate the RMSEA value, CFI value, SRMR value, and the result from the exact fit test.
-For the RMSEA and SRMR value we checked if it was below .08.
-For the CFI value we checked if the value was above .90.
-Finally, for the exact fit test we evaluated if the fit test was statistically significant at an alpha of .05.
-These values are based on common thresholds used to determine adequate fit.
+To test for unidimensionality, we fit a single-factor model on the item responses of each lab with suitable data.
+Our inference of unidimensionality is based on a set of four model fit indices and their commonly used thresholds indicating adequate fit: RMSEA (threshold: < .08), SRMR (< .08), CFI (> .90), and the exact fit test (statistically significant at .05).
 We consider the use of these thresholds sufficient for our descriptive aim, even though we understand apprehension against rules of thumb when used to evaluate measurement in individual studies.
-
-For the final index we ran a parallel analysis.
-A parallel analysis runs multiple Exploratory Factor Analyses where the number of factors in the model is increased by 1 until the number of factors is one less than the number of items.
+As a fifth additional fit index we ran a parallel analysis.
+A parallel analysis runs multiple Exploratory Factor Analyses where the number of factors in the model is increased by one until the number of factors is one less than the number of items.
 It then compares the eigenvalues (an indication of how much variance is explained by that factor) of each factor to the eigenvalues for that factor if the data matrix was effectively random.
 If only the first factor has an eigenvalue that is significantly higher than the eigenvalue when the data matrix is random, the test is passed.
-We chose a combination of indices since each one has their own limitations, and combining them gives us a more robust picture of the unidimensionality of the measures.
+We chose a combination of indices to test unidimensionality, since each one has their own limitations, and combining them gives us a more robust picture of the unidimensionality of the measures.
+
+These unidimensionality checks are not intended as a complete validation of the measures in our sample.
+That would require additional steps that are beyond the scope of this study.
+Instead, the unidimensionality is checked as a prerequisite for validity.
+Practically speaking this means that if we observe a lack of unidimensional fit for our measures, then we have reason to question their validity.
+On the other hand, if we observe good undimensional fit, then based on this preliminary evidence we conclude that we do not observe an issue with this prerequisite for validity.
+We also evaluated the variation in the unidimensionality indices across labs, to observe how consistently measures showed undimensional fit, or if this varried considerably across context.
 
@@
 
-### Reliability
-
-Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts the flow of measures in relation to reliability reporting.
-First, it shows that almost half of the measures in both replication (N = `r sum(coded_data_replications$N_items == "1 item measure")`) and original research (N = `r sum(coded_data_original$N_items == "1 item measure")`) were single-item measures.
-Second, only `r apa_num(sum(coded_data_original$reliability_type != "Not Reported" & coded_data_original$reliability_type != ""), numerals = FALSE)` measures out of `r sum(coded_data_original$N_items == "multiple item measure")` (`r round((sum(coded_data_original$reliability_type != "Not Reported" & coded_data_original$reliability_type != "") / sum(coded_data_original$N_items == "multiple item measure")) * 100, 1)` %) multi-item scales in original and `r apa_num(sum(coded_data_replications$reliability_type != "Not Reported" & coded_data_replications$reliability_type != ""), numerals = FALSE)` out of `r sum(coded_data_replications$N_items == "multiple item measure")` (`r round((sum(coded_data_replications$reliability_type != "Not Reported" & coded_data_replications$reliability_type != "") / sum(coded_data_replications$N_items == "multiple item measure")) * 100, 1)` %) multi-item scales in replications were reported alongside a reliability indicator.
-@flakeConstructValidityValidity2022 observed a much larger degree of reliability coefficient reporting in both original (60.8%) and replications (37.1%).
-However, similarly to @flakeConstructValidityValidity2022, we observed that reliability reporting was more common in original studies as compared to replication studies, and that Cronbach’s Alpha was the most commonly reported reliability indicator in our sample as well.
+### Transparency and Reusability
+
+Table \@ref(tab:QMPTable) lists the prevalence of different measurement reporting practices in original and replication studies.
+Specifically, we calculated the proportion of measures that transparently reported on the item compared to the total number of measures to which the item was applicable.
+A higher proportion indicates more transparent measurement reporting.
+
+```{r QMPTable}
+# create informative Measurement Practice Labels 
+MPractice <- c("Reliability is reported", "It is clear if the measure existed or is newly created",    "Exact version of the measure is specified", "Validity evidence from a factor analysis is presented",   "Measured variable is defined", "Choice of measure selection or creation is justified",    "Implemented operationalisation is justified", "Source of the measure is provided",    "Psychometric evidence from the study is given", "Psychometric evidence from an earlier study is given",    "Administration format and environment are described", "Administration procedure is described",   "N items are described", "N response options are described", "Recoding of responses is described", "Creation of the index is described", "Text or supplement has example items", "Administration format changes are mentioned",    "Administration format changes are justified/validated", "Translations are mentioned",    "Translated measures are justified/validated", "Changes in N items or response options are mentioned",    "Changes in N items or response options are justified/validated")
+
+# construct the QMP table to be printed 
+QMP_table <- data.frame("Item" = MPractice, 
+                        "Original" = paste0(format(round(1 - qmp_ratio_data$QMP_percentage_original, digits = 2), nsmall = 2), " (", qmp_ratio_data$N_applicable_original, ")"), 
+                        "Replication" = paste0(format(round(1 - qmp_ratio_data$QMP_percentage_replication, digits = 2), nsmall = 2), " (", qmp_ratio_data$N_applicable_replication, ")"))
+
+QMP_table_formatted <- rbind(rbind(rbind(rbind(rbind(c("Definition", "", ""), QMP_table[5,]),
+                                               c("Operationalisation", "", ""), QMP_table[c(3, 11, 12, 7, 17),]),
+                                         c("Selection/Creation", "", ""), QMP_table[c(2, 6, 8, 9, 10, 1, 4),]),
+                                   c("Quantification", "", ""), QMP_table[c(13, 14, 15, 16),]),
+                             c("Modification", "", ""), QMP_table[18:23,])
+
+# set the zero N Items to "- (0)"
+QMP_table_formatted[23, 2] <- "- (0)"
+QMP_table_formatted[24, 2] <- "- (0)"
+
+# print the table in apa formatting 
+apa_table(QMP_table_formatted, align = c("l", "r", "r"), 
+          caption = "Proportion of measures that met each of the item criteria, for both original and replication studies.
+Proportions are calculated based on the total number of measures to which an item was applicable (in brackets).",
+          note = "The first number in both Original and Replication is the ratio of measures for which that reporting practice contained sufficient information.
+The number between brackets indicates the number of measures for which the practice was applicable.", escape = FALSE, placement = "htp", booktabs = TRUE)
+```
+
+```{r ReuseCompleteInfoPercent}
+reuse_complete_percent_original <- round((sum((coded_data_original$op_1_REV | is.na(coded_data_original$op_1_REV)) & (coded_data_original$op_2_REV | is.na(coded_data_original$op_2_REV)) & (coded_data_original$op_3 | is.na(coded_data_original$op_3)) & (coded_data_original$op_4 | is.na(coded_data_original$op_4)) & (coded_data_original$op_5_REV | is.na(coded_data_original$op_5_REV)) & coded_data_original$sel_existing != "Not Clearly Stated" & (coded_data_original$sel_1_REV | is.na(coded_data_original$sel_1_REV)) & (coded_data_original$quant_1_REV | is.na(coded_data_original$quant_1_REV)) & (coded_data_original$quant_2_REV | is.na(coded_data_original$quant_2_REV)) & (coded_data_original$quant_3_REV | is.na(coded_data_original$quant_3_REV)) & (coded_data_original$quant_4 | is.na(coded_data_original$quant_4))) / nrow(coded_data_original)) * 100, 1)
+
+reuse_complete_percent_replication <- round((sum((coded_data_replications$op_1_REV | is.na(coded_data_replications$op_1_REV)) & (coded_data_replications$op_2_REV | is.na(coded_data_replications$op_2_REV)) & (coded_data_replications$op_3 | is.na(coded_data_replications$op_3)) & (coded_data_replications$op_4 | is.na(coded_data_replications$op_4)) & (coded_data_replications$op_5_REV | is.na(coded_data_replications$op_5_REV)) & coded_data_replications$sel_existing != "Not Clearly Stated" & (coded_data_replications$sel_1_REV | is.na(coded_data_replications$sel_1_REV)) & (coded_data_replications$quant_1_REV | is.na(coded_data_replications$quant_1_REV)) & (coded_data_replications$quant_2_REV | is.na(coded_data_replications$quant_2_REV)) & (coded_data_replications$quant_3_REV | is.na(coded_data_replications$quant_3_REV)) & (coded_data_replications$quant_4 | is.na(coded_data_replications$quant_4))) / nrow(coded_data_replications)) * 100, 1)
+```
+
+For the description of the results, we highlight the reporting practices most relevant for reusing the measure in future research, as well as the modification reporting practices to understand the relation between original and replication studies.
+It was not always clear which measures were used  (`r round(sum(coded_data_original$sel_existing == "Not Clearly Stated") / nrow(coded_data_original) * 100, 1)`% original; `r round(sum(coded_data_replications$sel_existing == "Not Clearly Stated") / nrow(coded_data_replications) * 100, 1)`% replication), which also implies that in these cases we could not be sure that the same measure was used in original and replication studies.
+While the number of items (`r round((1 - qmp_ratio_data$QMP_percentage_original[13]) * 100, 1)`% original (n = `r qmp_ratio_data$N_applicable_original[13]`); `r round((1 - qmp_ratio_data$QMP_percentage_replication[13]) * 100, 1)`% replications (n = `r qmp_ratio_data$N_applicable_replication[13]`)) and response options (`r round((1 - qmp_ratio_data$QMP_percentage_original[14]) * 100, 1)`% original (n = `r qmp_ratio_data$N_applicable_original[14]`); `r round((1 - qmp_ratio_data$QMP_percentage_replication[14]) * 100, 1)`% replications (n = `r qmp_ratio_data$N_applicable_replication[14]`)) were usually reported, even these were not always clear.
+How the responses should be recoded if at all (`r round((1 - qmp_ratio_data$QMP_percentage_original[15]) * 100, 1)`% original (n = `r qmp_ratio_data$N_applicable_original[15]`); `r round((1 - qmp_ratio_data$QMP_percentage_replication[15]) * 100, 1)`% replication (n = `r qmp_ratio_data$N_applicable_replication[15]`)), and how an index was created from the items (`r round((1 - qmp_ratio_data$QMP_percentage_original[16]) * 100, 1)`% original (n = `r qmp_ratio_data$N_applicable_original[16]`); `r round((1 - qmp_ratio_data$QMP_percentage_replication[16]) * 100, 1)`% replication (n = `r qmp_ratio_data$N_applicable_replication[16]`)) was clear a lot less.
+The operationalisation of the measure was usually reported clearly in the replication studies (format: `r round((1 - qmp_ratio_data$QMP_percentage_replication[11]) * 100, 1)`, procedure: `r round((1 - qmp_ratio_data$QMP_percentage_replication[12]) * 100, 1)`, justification: `r round((1 - qmp_ratio_data$QMP_percentage_replication[7]) * 100, 1)`, example items: `r round((1 - qmp_ratio_data$QMP_percentage_replication[17]) * 100, 1)`), but less so in original studies (format: `r round((1 - qmp_ratio_data$QMP_percentage_original[11]) * 100, 1)`, procedure: `r round((1 - qmp_ratio_data$QMP_percentage_original[12]) * 100, 1)`, justification: `r round((1 - qmp_ratio_data$QMP_percentage_original[7]) * 100, 1)`, example items: `r round((1 - qmp_ratio_data$QMP_percentage_original[17]) * 100, 1)`).
+If we look across all of the items mentioned above, the measures for which all applicable items were clearly reported on was `r reuse_complete_percent_original`% of all measures in original studies and `r reuse_complete_percent_replication`% in replications.
+
+Modifications to the number of items compared to preceding research were rare but did occur for `r round((qmp_ratio_data$QMP_percentage_original[22]) * 100, 1)`% of measures in original studies (n = `r qmp_ratio_data$N_applicable_original[22]`) and `r round((1 - qmp_ratio_data$QMP_percentage_replication[22]) * 100, 1)`% for replications (n = `r qmp_ratio_data$N_applicable_replication[22]`)).
+Furthermore, similar to the findings of Flake et al @flakeConstructValidityValidity2022 (original: 92%; replication 85.6%), most studies reported the number of items for their measures (original: `r round((1 - qmp_ratio_data$QMP_percentage_original[13]) * 100, 1)`%; replications: `r round((1 - qmp_ratio_data$QMP_percentage_replication[13]) * 100, 1)`%).
+The total proportion of measures for which the number of items was changed from original to replication was also similar (`r round(sum(!is.na(coded_data_replications$mod_5_REV)) / nrow(coded_data_replications) * 100, 1)`)% to Flake et al @flakeConstructValidityValidity2022 (16%).
+In general, it was uncommon for measures in original studies to have been modified.
+In replication studies, we noted that not all modifications were validated or justified (language: `r round((1 - qmp_ratio_data$QMP_percentage_replication[21]) * 100, 1)`% (n = `r qmp_ratio_data$N_applicable_replication[21]`); administration format: `r round((1 - qmp_ratio_data$QMP_percentage_replication[19]) * 100, 1)`% (n = `r qmp_ratio_data$N_applicable_replication[19]`)), especially for changes in items and response options, the modification was validated or justified for only a little more than half of the measures (`r round((1 - qmp_ratio_data$QMP_percentage_replication[23]) * 100, 1)`% (n = `r qmp_ratio_data$N_applicable_replication[23]`)).
+In general, we observed that measurement was modified in some way from original to replication for `r round((sum(coded_data_replications$mod_check == "True") / nrow(coded_data_replications)) * 100, 1)`% of measures, and it was unclear whether modification occurred for `r round((sum(coded_data_replications$mod_check == "None Reported") / nrow(coded_data_replications)) * 100, 1)`%.
+
+### Reliability Reporting
+
+Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts a flowchart of measure types and reliability reporting in original and replication studies.
+First, of the total of 77 measures, it shows that almost half of the measures in both replication (N = `r sum(coded_data_replications$N_items == "1 item measure")`) and original research (N = `r sum(coded_data_original$N_items == "1 item measure")`) were single-item measures.
+Second, for only `r apa_num(sum(coded_data_original$reliability_type != "Not Reported" & coded_data_original$reliability_type != ""), numerals = FALSE)` measures out of `r sum(coded_data_original$N_items == "multiple item measure")` (`r round((sum(coded_data_original$reliability_type != "Not Reported" & coded_data_original$reliability_type != "") / sum(coded_data_original$N_items == "multiple item measure")) * 100, 1)` %) multi-item scales in original and `r apa_num(sum(coded_data_replications$reliability_type != "Not Reported" & coded_data_replications$reliability_type != ""), numerals = FALSE)` out of `r sum(coded_data_replications$N_items == "multiple item measure")` (`r round((sum(coded_data_replications$reliability_type != "Not Reported" & coded_data_replications$reliability_type != "") / sum(coded_data_replications$N_items == "multiple item measure")) * 100, 1)`%) in replications, a reliability indicator was reported.
+Flake et al @flakeConstructValidityValidity2022 observed a much higher degree of reliability coefficient reporting in both original (60.8%) and replications (37.1%).
+However, similarly to Flake et al @flakeConstructValidityValidity2022, we observed that reliability reporting was more common in original studies as compared to replication studies, and that Cronbach’s Alpha was the most commonly reported reliability indicator in our sample as well.
 
@@
 
-### Validity
+### Validity Reporting
 
 For validity evidence the pattern was similar.
-Only, `r apa_num(sum(coded_data_original$sel_psychometric_evidence_REV != "None" & coded_data_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_original$sel_3_REV == TRUE, na.rm = TRUE), numerals = FALSE)` (`r round((sum(coded_data_original$sel_psychometric_evidence_REV != "None" & coded_data_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_original$sel_3_REV == TRUE, na.rm = TRUE) / nrow(coded_data_original)) * 100, 1)` %) original studies and `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_replications$sel_3_REV == TRUE, na.rm = TRUE), numerals = FALSE)` (`r round((sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_replications$sel_3_REV == TRUE, na.rm = TRUE) / nrow(coded_data_replications)) * 100, 1)`) replications reported psychometric validity evidence on their measurement.
-These proportions align with the results from @flakeConstructValidityValidity2022 for both original (9.3%) and replication studies (6.2%), and again, similar to @flakeConstructValidityValidity2022 we observe that validity evidence is also more commonly reported in original compared to replication studies.
-Exploratory factor analyses (original: `r apa_num(sum(coded_data_original$sel_psychometric_evidence_REV == "Exploratory Factor Analysis"), numerals = FALSE)`, replications: `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV == "Exploratory Factor Analysis"))`) and convergent validity evidence (original: `r apa_num(sum(coded_data_original$sel_psychometric_evidence_text_REV == "convergent validity"), numerals = FALSE)`, replications: `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_text_REV == "convergent validity"), numerals = FALSE)`) were the most commonly reported validity indicators.
-Psychometric validity evidence from previous studies was reported in `r apa_num(sum(coded_data_original$sel_4 == TRUE, na.rm = TRUE), numerals = FALSE)` original studies and `r apa_num(sum(coded_data_replications$sel_4 == TRUE, na.rm = TRUE), numerals = FALSE)` replications.
-For single-item measures, `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_text_REV[coded_data_replications$N_items == "1 item measure"] != ""), numerals = FALSE)` were reported with validity evidence – specifically, all were convergent validity – in the replication protocols.
-In the original studies, `r apa_num(sum(coded_data_original$sel_psychometric_evidence_text_REV[coded_data_original$N_items == "1 item measure"] != ""), numerals = FALSE)` single-item measures came with reported validity evidence.
+Psychometric validity evidence was reported for only, `r apa_num(sum(coded_data_original$sel_psychometric_evidence_REV != "None" & coded_data_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_original$sel_3_REV == TRUE, na.rm = TRUE), numerals = FALSE)` (`r round((sum(coded_data_original$sel_psychometric_evidence_REV != "None" & coded_data_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_original$sel_3_REV == TRUE, na.rm = TRUE) / sum(coded_data_original$N_items == "multiple item measure")) * 100, 1)`%) multiple item measures in original studies and `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_replications$sel_3_REV == TRUE, na.rm = TRUE), numerals = FALSE)` (`r round((sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_replications$sel_3_REV == TRUE, na.rm = TRUE) / sum(coded_data_replications$N_items == "multiple item measure")) * 100, 1)`%) in replications.
+These proportions align with the results from Flake et al @flakeConstructValidityValidity2022 for both original (9.3%) and replication studies (6.2%), and again, similar to Flake et al @flakeConstructValidityValidity2022 we observe that validity evidence is also more commonly reported in original compared to replication studies.
+Exploratory factor analyses (original: `r apa_num(sum(coded_data_original$sel_psychometric_evidence_REV == "Exploratory Factor Analysis"), numerals = FALSE)`, replications: `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV == "Exploratory Factor Analysis"), numerals = FALSE, zero_string = "zero")`) and convergent validity evidence (original: `r apa_num(sum(coded_data_original$sel_psychometric_evidence_text_REV == "convergent validity"), numerals = FALSE)`, replications: `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_text_REV == "convergent validity"), numerals = FALSE)`) --- in which a measure is correlated to a measure of a theoretically related construct --- were the most commonly reported validity indicators.
+`r apa_num(sum(coded_data_original$sel_4 == TRUE, na.rm = TRUE), numerals = FALSE)` original studies and `r apa_num(sum(coded_data_replications$sel_4 == TRUE, na.rm = TRUE), numerals = FALSE)` replications reported psychometric validity evidence from previous studies.
+For single-item measures, validity evidence was reported in `r apa_num(sum(coded_data_original$sel_psychometric_evidence_text_REV[coded_data_original$N_items == "1 item measure"] != ""), numerals = FALSE, zero_string = "none")` of the original studies, and only `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_text_REV[coded_data_replications$N_items == "1 item measure"] != ""), numerals = FALSE)` replication protocols (in both cases evidence of convergent validity).
 
@@
 
-### Questionable Measurement Practices
-
-We also coded the reporting of measurement information besides reliability and validity reporting.
-Table \@ref(tab:QMPTable) below shows the ratio of measurements that aligned with that row's practice of reporting a specific piece of measurement information and for how many of the `r nrow(coded_data_original)` measures the reporting of that measurement information was applicable for both original and replications.
-The ratio is based on the number of measures that reported that piece of measurement information for the measures for which that item was applicable.
-A higher ratio thus indicates better measurement reporting.
-
-```{r QMPTable}
-# create informative Measurement Practice Labels 
-MPractice <- c("Reliability is reported", "It is clear if the measure existed or is newly created",    "Exact version of the measure is specified", "Validity evidence from a factor analysis is presented",   "Measured variable is defined", "Choice of measure selection or creation is justified",    "Implemented operationalisation is justified", "Source of the measure is provided",    "Psychometric evidence from the study is given", "Psychometric evidence from an earlier study is given",    "Administration format and environment are described", "Administration procedure is described",   "N items are described", "N response options are described", "Recoding of responses is described", "Creation of the index is described", "Text or supplement has example items", "Administration format changes are mentioned",    "Administration format changes are justified/validated", "Translations are mentioned",    "Translated measures are justified/validated", "Changes in N items or response options are mentioned",    "Changes in N items or response options are justified/validated")
-
-# construct the QMP table to be printed 
-QMP_table <- data.frame("Practice" = MPractice, 
-                        "Original" = paste0(1 - qmp_ratio_data$QMP_percentage_original, " (", qmp_ratio_data$N_applicable_original, ")"), 
-                        "Replication" = paste0(1 - qmp_ratio_data$QMP_percentage_replication, " (", qmp_ratio_data$N_applicable_replication, ")"))
-
-QMP_table_formatted <- rbind(rbind(rbind(rbind(rbind(c("Definition", "", ""), QMP_table[5,]),
-                                               c("Operationalisation", "", ""), QMP_table[c(3, 11, 12, 7, 17),]),
-                                         c("Selection/Creation", "", ""), QMP_table[c(2, 6, 8, 9, 10, 1, 4),]),
-                                   c("Quantification", "", ""), QMP_table[c(13, 14, 15, 16),]),
-                             c("Modification", "", ""), QMP_table[18:23,])
-
-# print the table in apa formatting 
-apa_table(QMP_table_formatted, align = c("l", "r", "r"), 
-          caption = "Ratio of QMPs and number of applicable measures, for original and replication", 
-          note = "The first number in both Original and Replication is the ratio of measures for which that reporting practice contained sufficient information.
-The number between brackets indicates the number of measures for which the practice was applicable.", escape = FALSE, placement = "htp", booktabs = TRUE)
-```
-
-For our purposes, we can focus on the reporting of information most relevant for reconstructing the measure in future research, as well as the modification reporting practices to learn about the relation between original and replication studies.
-It was clear that existing measures were used for `r round(sum(coded_data_original$sel_existing == "True, namely:") / nrow(coded_data_replications) * 100, 1)`% original and `r round(sum(coded_data_replications$sel_existing == "True, namely:") / nrow(coded_data_original) * 100, 1)`% replication measures.
-It was not always clear which measures were used (`r round(sum(coded_data_original$sel_existing == "Not Clearly Stated") / nrow(coded_data_original) * 100, 1)`% original; `r round(sum(coded_data_replications$sel_existing == "Not Clearly Stated") / nrow(coded_data_replications) * 100, 1)`% replication), meaning they could not clearly be identified to be the same between original and replication .
-The number of items (`r round((1 - qmp_ratio_data$QMP_percentage_original[13]) * 100, 1)`% original (n = `r qmp_ratio_data$N_applicable_original[13]`); `r round((1 - qmp_ratio_data$QMP_percentage_replication[13]) * 100, 1)`% replications (n = `r qmp_ratio_data$N_applicable_replication[13]`)) and response options (`r round((1 - qmp_ratio_data$QMP_percentage_original[14]) * 100, 1)`% original (n = `r qmp_ratio_data$N_applicable_original[14]`); `r round((1 - qmp_ratio_data$QMP_percentage_replication[14]) * 100, 1)`% replications (n = `r qmp_ratio_data$N_applicable_replication[14]`)) were usually clear, and modifications to these being unclearly reported was atypical, but did occur (`r round((1 - qmp_ratio_data$QMP_percentage_original[22]) * 100, 1)`% original (n = `r qmp_ratio_data$N_applicable_original[22]`); `r round((1 - qmp_ratio_data$QMP_percentage_replication[22]) * 100, 1)`% replications (n = `r qmp_ratio_data$N_applicable_replication[22]`)).
-The percentage of numbers of items reported was similar to @flakeConstructValidityValidity2022 (original: 92%; replication 85.6%).
-The proportion to which the number of items were changed from original to replication was also similar (`r round(sum(!is.na(coded_data_replications$mod_5_REV)) / nrow(coded_data_replications) * 100, 1)`) to @flakeConstructValidityValidity2022 (16%).
-In general, modifications could only rarely be identified for original studies.
-In replication studies we observe that not all modifications were validated or justified (language: `r round((1 - qmp_ratio_data$QMP_percentage_replication[21]) * 100, 1)`% (n = `r qmp_ratio_data$N_applicable_replication[21]`); administration format: `r round((1 - qmp_ratio_data$QMP_percentage_replication[19]) * 100, 1)`% (n = `r qmp_ratio_data$N_applicable_replication[19]`)), especially for changes in items and response options (`round((1 - qmp_ratio_data$QMP_percentage_replication[23]) * 100, 1)`(n = `r qmp_ratio_data$N_applicable_replication[23]`)).
-In general, we observed that measurement was modified in some way from original to replication for `r round((sum(coded_data_replications$mod_check == "True") / nrow(coded_data_replications)) * 100, 1)`% of measures, and it was unclear whether modification occurred for `r round((sum(coded_data_replications$mod_check == "None Reported") / nrow(coded_data_replications)) * 100, 1)`%.
-
-???LEFTOVER RESULTS from @flakeConstructValidityValidity2022.
-- had a citation flake:original ::: 29% - response format reported flake:original :: 94% - scale scoring flake:original :: 49% - citing existing validity evidence flake:original :: 29% - citing existing validity evidence flake:replication :: 38% - translation validated flake:replication :: 20% ???
-
-## Measurement Response Data Analysis
+## Analysis of Item Responses
 
@@
 
-The average calculated Cronbach’s alpha coefficient across individual replications was `r apa_num(mean(calculated_reliability_lab_data$alpha))` with a standard deviation of `r apa_num(sd(calculated_reliability_lab_data$alpha))`.
-Figure \@ref(fig:PlotAlphaDistributions) displays the distributions of the calculated Cronbach’s Alpha scores from each lab for each measure, separated by successful and unsuccessful replication, based on the meta-analytic p-value (alpha \< .05) retrieved from the Many Labs reports.
+We could calculate Cronbach’s Alpha for `r length(levels(calculated_reliability_lab_data$g))` measures across on average `r apa_num(mean(table(calculated_reliability_lab_data$g)))` labs, for which the required raw data was provided.
+The average Cronbach’s Alpha coefficient across measures was `r apa_num(mean(measure_reliability_data$alpha))` with a standard deviation of `r apa_num(sd(measure_reliability_data$alpha))`.
+Figure \@ref(fig:PlotAlphaDistributions) displays the distributions of the calculated Cronbach’s Alpha scores from each lab for each measure, separated by successful and unsuccessful replication, based on the meta-analytic p-value (alpha = .05) retrieved from the Many Labs reports.
 
@@
 
-```{r PlotAlphaDistributions, warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients calculated for the responses on a measure at each lab location, across the nineteen measures for which raw data was available from which Cronbach’s alpha coefficients could be calculated.
-Cronbach's alpha values that fell below 0 were excluded.
-The green lines indicate the meta-analytic prediction interval lower and upper bound.
-The blue triangles indicate the reported alpha coefficient for that measure from the original article, when reported.
+```{r PlotAlphaDistributions, warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s Alpha coefficients calculated for the responses on a measure at each lab location, across the nineteen measures for which the required raw data was available.
+Cronbach’s Alpha values that fell below 0 were excluded.
+The green lines indicate the meta-analytic 95% prediction interval lower and upper bound.
+The blue triangles indicate the reported Cronbach’s Alpha coefficient for that measure from the original article, when reported.
+The N column indicates the number of labs that the measure was used in.
 The Tau column besides the figure shows the tau heterogeneity estimate based on a meta-analysis of the calculated reliabilities for each measure.
-Meta-analyses for which the Q-test for heterogeneity was significant at alpha < .05 are in black, while non-significant results are in grey.
+Meta-analyses for which the Q-test for heterogeneity was significant at alpha = .05 are marked by a *.
 The Diff column shows the difference between reported reliability and the average reliability calculated from the Many Labs data for the applicable measures.
-The reported reliabilities that fell outside the 95% quantile of calculated reliability scores are shown in black, otherwise in grey."}
+The reported reliabilities that fell outside the 95% quantile of calculated reliability scores are marked by a *."}
 
@@
 
+  # adding in the number of labs per measures
+  geom_text(data = measure_reliability_data, label = as.numeric(table(calculated_alpha_plot_data$g)), x = 1.1, y = measure_reliability_data$graph_index, size = 2.8) +
+
   # adding in the tau values
-  geom_text(data = measure_reliability_data, label = format(measure_reliability_data$tau, digits = 1), x = 1.15, y = measure_reliability_data$graph_index, color = ifelse(measure_reliability_data$QEp < .05, "black", "grey"), size = 2.8) +
+  geom_text(data = measure_reliability_data, label = ifelse(measure_reliability_data$QEp < .05, paste0(format(measure_reliability_data$tau, digits = 1), "*"), paste0(format(measure_reliability_data$tau, digits = 1), " ")), x = 1.22, y = measure_reliability_data$graph_index, size = 2.8) +
 
   # adding in the difference in alpha coefficients
-  geom_text(data = measure_reliability_data[c(1:8, 18),], label = format(measure_reliability_data$coefficient_difference[c(1:8, 18)], digits = 2), x = 1.28, y = measure_reliability_data[!is.na(measure_reliability_data$coefficient_difference),]$graph_index, color = ifelse(measure_reliability_data$significance_reported_coefficient[c(1:8, 18)], "black", "grey"), size = 2.8) +
+  geom_text(data = measure_reliability_data[c(1:8, 18),], label = ifelse(measure_reliability_data$significance_reported_coefficient[c(1:8, 18)], paste0(format(measure_reliability_data$coefficient_difference[c(1:8, 18)], digits = 2), "*"), paste0(format(measure_reliability_data$coefficient_difference[c(1:8, 18)], digits = 2), " ")), x = 1.35, y = measure_reliability_data[!is.na(measure_reliability_data$coefficient_difference),]$graph_index, size = 2.8) +
 
@@
   annotation_custom(grob = textGrob(label = "Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 6, ymax = 6, xmin = 0.01, xmax = 0.01) +
-  annotation_custom(grob = textGrob(label = "Tau", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.1, xmax = 1.1) +
-  annotation_custom(grob = textGrob(label = "Diff", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.24, xmax = 1.24) +
+  annotation_custom(grob = textGrob(label = "N", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.08, xmax = 1.1) +
+  annotation_custom(grob = textGrob(label = "Tau", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.24, xmax = 1.1) +
+  annotation_custom(grob = textGrob(label = "Diff", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.37, xmax = 1.24) +
 
@@
 
-We found statistically significant indication of heterogeneity in Cronbach's alpha for `r apa_num(sum(measure_reliability_data$QEp < .05), numerals = FALSE)` of the `r apa_num(nrow(measure_reliability_data), numerals = FALSE)` measures.
-However, as noted earlier a more accurate indication of the heterogeneity can be observed in the prediction intervals.
+We found statistically significant indication of heterogeneity in Cronbach’s Alpha for `r apa_num(sum(measure_reliability_data$QEp < .05), numerals = FALSE)` of the `r apa_num(nrow(measure_reliability_data), numerals = FALSE)` measures.
+However, as noted earlier, a more accurate indication of the heterogeneity can be observed in the prediction intervals.
 The prediction intervals generally show larger indications of heterogeneity for some of the lower reliability measures and less for higher reliability measures when compared to the Tau test results.
-An increase in the number of labs also appears to be a factor for narrowing the prediction intervals.
-Additionally, we observe that for most measures the reported reliabilities were generally lower than the reliabilities calculated for the replication labs.
-Another interesting observation is that reported reliabilities in the original study were more common for those measures that had higher average calculated reliabilities (\>.80) in the replications compared to on average less reliable measures.
-
-### Unidimensionality assessment
+When comparing reported reliability in the original study when present to the calculated reliability averages, we first of all can see that reported reliabilities were generally lower than the average calculated reliabilities.
+Second, we can observe that reliabilities were reported more often in the original study if the measures had higher average calculated reliabilities (\>.80) in the replications.
+
+### Unidimensionality Test
 
@@
 
-# added the reporting or lack of reporting of psychometric validty evidence in the original to the meta data
+# added the reporting or lack of reporting of psychometric validity evidence in the original to the meta data
 unidimensionality_meta_data$reported_psych_val <- coded_data_original$sel_psychometric_evidence_REV[measure_reliability_data$coded_data_index] != "None" & coded_data_original$sel_psychometric_evidence_REV[measure_reliability_data$coded_data_index] != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_original$sel_3_REV[measure_reliability_data$coded_data_index] == TRUE
 
-# adding the number of non-coverged factor models
+# adding the number of non-converged factor models
 non_converged_list <- tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, is.na)
@@
 
-Figure \@ref(fig:Plot1FactorRMSEA) below show the result of our unidimensionality test.
-`r apa_num((sum(unidimensionality_graph_data$RMSEA < .08, na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)` % of labs were below our RMSEA .08 threshold, while for `r apa_num((sum(unidimensionality_meta_data$beta < .08, na.rm = TRUE)), numerals = FALSE)` measures of the total `r apa_num(nrow(unidimensionality_meta_data), numerals = FALSE)` the mean across labs was below this threshold.
-Furthermore, the RMSEA shows considerable variation within measures, with the standard deviation ranging from `r apa_num(min(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))` to `r apa_num(max(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))` (mean sd = `r apa_num(mean(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))`).
+Figure \@ref(fig:Plot1FactorRMSEA) shows the result of our unidimensionality test.
+The mean obtained RMSEAs were below the threshold of .08 for `r apa_num(sum(as.numeric(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, mean, na.rm = TRUE)) < .08, na.rm = TRUE), numerals = FALSE)` of the `r apa_num(nrow(unidimensionality_meta_data), numerals = FALSE)` measures (`r apa_num(sum(as.numeric(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, mean, na.rm = TRUE)) < .08, na.rm = TRUE) / nrow(unidimensionality_meta_data) * 100)`%).
+Furthermore, the RMSEA shows considerable variation within measures, with the standard deviation ranging from `r apa_num(min(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))` to `r apa_num(max(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))` (mean SD = `r apa_num(mean(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))`).
 
 The parallel analysis results similarly showed inconsistency both across and within measures.
-While `r apa_num((sum(unidimensionality_graph_data$N_factors_capped == "1", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% of labs returned a single factor solution, `r apa_num((sum(unidimensionality_graph_data$N_factors_capped == "2", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% returned a two-factor, and `r apa_num((sum(unidimensionality_graph_data$N_factors_capped == "2", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% returned three or more factors.
+While `r apa_num((sum(unidimensionality_graph_data$N_factors_capped == "1", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% of labs returned a single factor solution, `r apa_num((sum(unidimensionality_graph_data$N_factors_capped == "2", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% returned a two-factor, and `r apa_num((sum(unidimensionality_graph_data$N_factors_capped == "3+", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% returned three or more factors.
 The remainder did not converge.
@@
 The CFA failed to converge for `r apa_num((sum(is.na(unidimensionality_graph_data$RMSEA)) / nrow(unidimensionality_graph_data)) * 100)`% of labs.
-Convergence in most cases was the result of either the severe misfit of our factor models or a lack of sample size to stably estimate these models.
-A consistent pattern was also lacking for the results from the exact fit tests.
-For `r sum((unidimensionality_meta_data$p_count[1:18] / unidimensionality_meta_data$converged_count[1:18]) >= .75)` out of `r sum(unidimensionality_meta_data$converged_count != 0)` measures with converged factor analyses, three quarters or more labs showed statistical significant fit, for `r sum((unidimensionality_meta_data$p_count[1:18] / unidimensionality_meta_data$converged_count[1:18]) <= .25)` a quarter or less did, and for the remaining `r sum((unidimensionality_meta_data$p_count[1:18] / unidimensionality_meta_data$converged_count[1:18]) > .25 & (unidimensionality_meta_data$p_count[1:18] / unidimensionality_meta_data$converged_count[1:18]) < .75)` the proportion lay somewhere in between.
+In most cases, the convergence problems were the result of either the severe misfit of our factor models or a lack of sample size to stably estimate these models.
+Furthermore, the results from the exact fit tests showed varying dimensionality across labs.
+In total, the factor analyses converged for eighteen measures.
+For `r apa_num(sum((unidimensionality_meta_data$p_count[1:18] / unidimensionality_meta_data$converged_count[1:18]) >= .75), numerals = FALSE)` of these measures, there was substantive evidence for a one-factor solution (statistical fit in >75% of labs), whereas for `r apa_num(sum((unidimensionality_meta_data$p_count[1:18] / unidimensionality_meta_data$converged_count[1:18]) <= .25), numerals = FALSE)` measures, there was low evidence for a one-factor solution (statistical fit in <25% of labs).
+The evidence for a one-factor solution for the remaining measures was mixed.
 
 ```{r Plot1FactorRMSEA, warning = FALSE, fig.cap = "Distributions of calculated RMSEA of a single-factor model fit calculated for the responses on a measure at each lab location, across the nineteen measures for which raw data was available on which a factor model could be fitted.
-The red horizontal line separate the replicated from the non-repicated measures.
+The red horizontal line separates the replicated from the non-replicated measures.
 The red vertical line indicates our .08 RMSEA cutoff value.
@@
 column besides the graph shows the number of labs per measure for which the single-factor CFA converged, with second number showing the total number of labs.
+The Sig.
+Prop.
+column indicates the proportion of converged studies for which the 1-factor CFA exact fit test returned a statistically significant p-value at Alpha = .05.
 The color of each dot shows the number of factors that were selected for that measure for that lab location based on the parallel analyses.
@@
   annotation_custom(grob = textGrob(label = "Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 6, ymax = 6, xmin = 0.37, xmax = 0.37) +
-  annotation_custom(grob = textGrob(label = "Conv.", hjust = 0, gp = gpar(fontsize = 11)), ymin = 20.2, ymax = 20.2, xmin = 0.48, xmax = 0.48) +
+  annotation_custom(grob = textGrob(label = "1-Fac\nConv.", hjust = 0, gp = gpar(fontsize = 11)), ymin = 20.9, ymax = 20.9, xmin = 0.48, xmax = 0.48) +
   annotation_custom(grob = textGrob(label = "Sig.\nProp.", hjust = 0, gp = gpar(fontsize = 11)), ymin = 20.9, ymax = 20.9, xmin = 0.55, xmax = 0.56) +
@@
 
-Figure \@ref(fig:Plot1FactorSRMRCFI) below shows the SRMR, and CFI fit indices for the same single factor model as was used to estimate the RMSEA and exact fit test.
-`r apa_num((sum(unidimensionality_graph_data$SRMR < .08, na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% of labs were below our SRMR .08 threshold and `r apa_num((sum(unidimensionality_graph_data$CFI < .9, na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% were above our CFI .90 threshold.
-For the `r apa_num(nrow(unidimensionality_meta_data), numerals = FALSE)` measures, the mean SRMR was below .08 for `r apa_num((sum(tapply(unidimensionality_graph_data$SRMR, unidimensionality_graph_data$g, mean, na.rm = TRUE) < .08, na.rm = TRUE)), numerals = FALSE)` measures, while the mean CFI was above .90 for for `r apa_num((sum(tapply(unidimensionality_graph_data$CFI, unidimensionality_graph_data$g, mean, na.rm = TRUE) > .9, na.rm = TRUE)), numerals = FALSE)` measures.The mean standard deviation of the SRMR fit index is `r apa_num(mean(tapply(unidimensionality_graph_data$SRMR, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$SRMR, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))`.
-For CFI this was `r apa_num(mean(tapply(unidimensionality_graph_data$CFI, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$CFI, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))`.
+Figure \@ref(fig:Plot1FactorSRMRCFI) shows the SRMR, and CFI fit indices for the same single factor model as was used to estimate the RMSEA and exact fit test.
+We found that, the mean SRMR was below .08 for `r apa_num((sum(tapply(unidimensionality_graph_data$SRMR, unidimensionality_graph_data$g, mean, na.rm = TRUE) < .08, na.rm = TRUE)), numerals = FALSE)` measures `r apa_num(sum(tapply(unidimensionality_graph_data$SRMR, unidimensionality_graph_data$g, mean, na.rm = TRUE) < .08, na.rm = TRUE) / length(levels(unidimensionality_graph_data$g)) * 100)`%, while the mean CFI was above .90 for `r apa_num((sum(tapply(unidimensionality_graph_data$CFI, unidimensionality_graph_data$g, mean, na.rm = TRUE) > .90, na.rm = TRUE)), numerals = FALSE)` measures `r apa_num(sum(tapply(unidimensionality_graph_data$CFI, unidimensionality_graph_data$g, mean, na.rm = TRUE) > .90, na.rm = TRUE) / length(levels(unidimensionality_graph_data$g)) * 100)`%.
+The mean standard deviation of the SRMR fit index across measures is `r apa_num(mean(tapply(unidimensionality_graph_data$SRMR, unidimensionality_graph_data$g, sd, na.rm = TRUE), na.rm = TRUE))`.
+For CFI this was `r apa_num(mean(tapply(unidimensionality_graph_data$CFI, unidimensionality_graph_data$g, sd, na.rm = TRUE), na.rm = TRUE))`.
 Overall, compared to the RMSEA, the SRMR and CFI fit indices show a more stable unidimensional fit.
 Especially the SRMR index shows considerably better fit compared to the RMSEA.
-When combining the results from all five unidimensionality checks together we observe that at least one of the five unidimensionality checks was passed for `r round((sum(unidimensionality_graph_data$unidimensional_check_count >= 1, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100, 2)`% of the `r sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))` labs with converged factor models, at least two for `r round((sum(unidimensionality_graph_data$unidimensional_check_count >= 2, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100, 2)`%, at least three for `r round((sum(unidimensionality_graph_data$unidimensional_check_count >= 3, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100, 2)`%, at least three for `r round((sum(unidimensionality_graph_data$unidimensional_check_count >= 4, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100, 2)`%, and all five for `r round((sum(unidimensionality_graph_data$unidimensional_check_count == 5, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100, 2)`%.
-The mean number of unidimensionality check passed was `r round(mean(unidimensionality_graph_data$unidimensional_check_count, nar.rm = TRUE), 2)`.
+When combining the results from all five unidimensionality checks, we observe that at least one of the five unidimensionality checks was passed for `r round((sum(unidimensionality_graph_data$unidimensional_check_count >= 1, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100, 2)`% of the `r sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))` labs with converged factor models, at least two for `r round((sum(unidimensionality_graph_data$unidimensional_check_count >= 2, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100, 2)`%, at least three for `r round((sum(unidimensionality_graph_data$unidimensional_check_count >= 3, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100, 2)`%, at least four for `r round((sum(unidimensionality_graph_data$unidimensional_check_count >= 4, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100, 2)`%, and all five for `r round((sum(unidimensionality_graph_data$unidimensional_check_count == 5, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100, 2)`%.
+The mean number of unidimensionality check passed was `r round(mean(unidimensionality_graph_data$unidimensional_check_count, na.rm = TRUE), 2)`.
 
@@
   theme_minimal() +
-  theme(legend.position = "bottom", plot.margin = unit(c(1, 5, 1, 1), "lines")) +
+  theme(legend.position = "bottom", plot.margin = unit(c(1, .5, 1, 1), "lines")) +
   scale_x_continuous(breaks = round(c(0, 0.1, 0.2),1)) +
@@
   ylab("") +
-  xlab("SRMR (unidimensional CFA model)")
+  xlab("SRMR (unidimensional\nCFA model)")
 
@@
   theme_minimal() +
-  theme(legend.position = "none", plot.margin = unit(c(1, 5, 1, 1), "lines"), axis.text.y = element_blank()) +
+  theme(legend.position = "none", plot.margin = unit(c(1, .5, 1, 1), "lines"), axis.text.y = element_blank()) +
   scale_x_continuous(breaks = round(c(0, 0.2, 0.4, 0.6, 0.8, 1),1)) +
@@
   ylab("") +
-  xlab("CFI (unidimensional CFA model)")
+  xlab("CFI (unidimensional\nCFA model)")
 
@@
 
-???Compared to Shaw ,!!!
-- mean CFI of scales is: `r  mean(0.919, 0.966, 0.877, 0.946, 0.616, 0.92, 0.889, 0.873)` 0.919 - mean SRMR of scales is: `r  mean(0.066, 0.028, 0.047, 0.045, 0.267, 0.04, 0.059, 0.036)` 0.066 - mean of RMSEA of scales is: `r  mean(0.056, 0.082, 0.093, 0.059, 0.262, 0.191, 0.174, 0.085)` 0.056.
-However these are means of scales and not per lab???
-
 # Discussion
 
-To assess psychological phenomena we need measurement that is valid and reliable for our constructs.
-However, we noted that little reliability and validity evidence was reported, and that all the information needed to understand and recreate the measurement was rarely all available.
-Furthermore our reanalysis of the reliability and validity of the measures showed inconsistent reliability and validity support.
-
-!!!Korte samenvatting van wat we gedaan hebben; daarna voor alle drie aims de resultaten bescrhijven; gebruik QMPs als framework, maar niet veel expliciet bescrhijven (future research, er zijn nog meer QMPs); blijf de volgorde aanhouden!!!
-
-In line with existing research we found that for the majority of the measures in original and replication studies no reliability coefficient was reported, and psychometric validity evidence was even less common [@beckmanHowReliableAre2004; @barryValidityReliabilityReporting2014; @flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020; @flakeConstructValidityValidity2022].
-Some part of this is due to around half of the measures in original and replication studies being single item measures.
-While it is possible to check the reliability and validity of single item measures, these methods often require multiple measures or studies to be able to cross-validate the measure with [@leppinkWeNeedMore2017; @sarstedtSelectingSingleItems2016].
-Another reason can be found in our observation that replications generally reported less reliability and psychometric validity evidence.
-This could be because replications implicitly defer the responsibility of reporting validity and reliability evidence to the original study.
+To assess psychological phenomena we need valid and reliable measurement, but previous research has raised doubts regarding the quality of measurement and its reporting.
+In this study, we extracted measurement reporting information from `r nrow(coded_data_replications)` measures, reported in original and replication studies from the Many Labs projects, and where possible, calculated indices for reliability and construct validity based on item response data.
+We found that reliability and validity evidence was often not reported.
+Additionally, the information relevant for reconstructing the measure in another study was rarely reported in full, especially among original studies.
+Finally, based on the Cronbach's Alpha and Unidimensionality indices we recalculated from the item response data.
+We observed inconsistent support for the reliability and construct validity across labs.
+
+Similar to Flake et al @flakeConstructValidityValidity2022, we observed that many studies lacked the complete information needed to ensure the measurement could be reconstructed fully.
+In original studies, the administration format and procedure for each was not properly described for around a third of the applicable measures.
+The number of items and response options were each unclear for around an eighth of the applicable measures, while how the index was calculated, how the items were recoded and example items were presented for each a little under half of the applicable measures.
+One notable difference compared to Flake et al @flakeConstructValidityValidity2022 is that in our results replications did have more complete and transparent measurement reporting on this information compared to original research.
+We believe that this is in part due to the structured way in which the Many Labs protocols were written up.
+Several Many Labs protocols even contained specific sections to declare any deviations from the original methodology.
+The other reason may be due to the more lenient coding of transparent measurement reporting practices in our revised coding protocol.
+We primarily checked whether each piece of measurement information was reported at all, rather than the actual completeness or depth of that reporting.
+It is therefore possible that even if we coded a practice as being clearly reported, it may not be sufficiently detailed to fully facilitate reuse.
+However, if we coded a practice as unclear then --- given our lenient coding --- we can be fairly certain that that particular reporting practice was reported in insufficient detail.
+Therefore, it is concerning to note that even within our lenient coding scheme many key measurement information could not be traced in the reported information.
+
+In line with existing research, we also found that the majority of the measures in original and replication studies do not report a reliability coefficient nor psychometric validity evidence [@beckmanHowReliableAre2004; @barryValidityReliabilityReporting2014; @flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020; @flakeConstructValidityValidity2022].
+The lack of reliability reporting is in part due to the fact that around half of the measures in original and replication studies were single item measures.
+While it is possible to check the reliability and validity of single item measures, these methods often require multiple measures or studies to allow for cross-validation [@leppinkWeNeedMore2017; @sarstedtSelectingSingleItems2016].
+The additional effort required for this type of cross-validation, as we observed here is rarely taken.
+Still, even among multiple item measures reliability was reported for about one third of the measures in original studies, and only about a tenth in replication studies.
+Psychometric validity evidence was only checked for multiple item measures, and for these was reported even less commonly than reliability.
+Again, reporting was lower in replication studies.
+This could be because replications implicitly defer the responsibility of reporting psychometric validity evidence to the original study.
 However, as we noted before, and as our analyses of the reliability and unidimensionality reiterate, the reliability and validity of a measure varies across contexts.
 It is therefore still important for the reliability and validity to be described for the replications studies too.
-
-We also noted that about two-thirds of the measurements were modified between replication and original study.
-While minor differences between replication and original study are inevitable, substantial changes between original and replication study raises questions about labeling those replications as direct.
-For example, the conscientiousness measure used for the replication of @defruytCloningersPsychobiologicalModel2000 was reduced from the original NEO-PI-R 30-item measure to a two-item measure in the replication.
-It is highly unlikely that a measure with such a significant change would have a comparable validity and reliability to the original, and we did unsurprisingly observe convergence issues with validity as well as low reliability for this measure.
-The regularity at which measures were modified also provides a response to the argument that replications do not need to report as many measurement details, since the reporting of these .
-If measurement is modified, then the new use and validity of the measurement has to be documented by the replication.
-Additionally, if changing the measurement between original and replication study is fair game, then the choice of measure has to also be substantially motivated beyond: "the original study did it that way".
-Finally, none of this explains away the lack of reliability and validity reporting in the original studies.
-It may unfortunately be more likely that many of these measures are simply not validated before (or even after) use.
-
-The information needed to reconstruct a measure for reuse was also not consistently clearly reported.
-In particular, like @flakeConstructValidityValidity2022, we observed that original research underreported information needed to reconstruct the measurement In future research.
-The administration format and procedure for each was not properly described for around a third of the applicable measures.
-The number of items and response options were unclear for both in around an eight of the applicable measures, while how the index was calculated, how the items were recoded and example items were presented for each a little under half of the applicable measures.
-
-One notable difference compared to @flakeConstructValidityValidity2022 is that in our results replications did on average have less QMPs than original research.
-We believe that this is in part due to the structured way in which the Many Labs protocols were written up.
-Several Many Labs protocols even contained specific sections to declare any deviations from the original methodology.
-The other reason may be due to the more lenient coding of the QMPs in the revised protocol.
-We mostly checked that something relevant to a specific QMP item was reported, not whether that reporting thoroughly shared all the needed information.
-In particular, for our items checking whether a particular practice was justified or validated, we accepted any reason that was given, we did not check whether that reason was sufficient.
-For example, even if we did not code QMPs in validating modifications to measurement, this does not mean that Measurement Invariance was empirically established, even if it might have been important to do so.
-
-Inconsistency was not only observed in the reporting of measurement.
-When we recalculated the reliability coefficients and factor structure of the measures used in the replication projects, the observed reliability and validity varied considerably across labs.
-We also noted that some measures had convergence issues, where for some labs we could not get the factor model to fit.
-This may have been because of sample size issues, or the small number of items we often observed in the replication measures.
-However, gross misfit is also possible.
-Although, the psychometric indicators we used were applied rather broadly across a spectrum of different measures, and should not be used to make individual inferences for the measures.
-As a general overview, our results do carry the warning that we cannot merely assume that the measures used in our sample were valid and can be used for substantive interpretations.
-
-We also observed that when a Cronbach's Alpha was reported for a measure in an original study, then their average Cronbach's Alpha observed among the replications were consistently relatively high.
-Meanwhile when no Cronbach's Alpha was reported in the original study, the reliability was often relatively low.
-This aligns with existing research indicating bias in reported Cronbach's Alpha values, with an excess of reported values at the common acceptably reliable threshold value of .70, and low reporting just below .70 [@husseyAberrantAbundanceCronbachs2023].
-Authors may be less inclined to report reliabilities when they fall below an acceptable threshold, but not otherwise.
-In combination with our inconsistent reliability and validity evidence, this bias in reporting could create a false sense of security when looking only at what is reported.
-
-Overall, our intent is not to specifically scold the Many Labs replications nor the original studies.
-We commend the tremendous effort involved in the creation of the Many Labs projects, and we understand that for feasibility some corners had to be cut.
-Similarly, we understand that complete validation of psychological measures is not a responsibility that should or can be placed on any one study.
-However, we would argue that full transparent measurement reporting is a responsibility both replications and original studies do have.
-Based on our results and the results of existing research, we believe that with current measurement reporting, you cannot reliably expect to observe the information you need to evaluate and understand the measurement that was used in a study.
-Even though a substantial proportion of measurement information was frequently reported - when looking at our intentionally non-strict coding protocol - information was almost never consistently clearly reported across our sample.
-Furthermore, critical information on reliability and validity in particular was rare.
-Finally, even though validating measures is difficult, its necessity cannot be ignored.
-If validity evidence for a measure is never obtained, it becomes questionable to draw substantive interpretations on the basis of responses to that measure.
-
-!!!detecting meaningful effects when checking for measurement invariance across groups requires large sample sizes [@meadePowerPrecisionConfirmatory2007; @frenchMeasurementInvarianceTechniques2016; @koziolImpactModelParameterization2018].!!!
+However, because the replication protocols were written before data collection, it makes sense that this information was not reported there.
+Still, we could also not find such information in both the available supplementary materials that we checked and the Many Labs reports.
+
+The fact that the reliability and validity of a measurement was rarely reported is particularly concerning, because our analysis of the item response data revealed that the reliability and the unidimensionality of measures in our sample typically varied considerably across samples.
+While some measures did show consistently high reliability and stable unidimensionality, a similar number showed low average reliability and low unidimensionality.
+Most measures however fell somewhere in between, such that for the same measure reliability and unidimensionality met standards in some of the labs, while they were clearly below par in others.
+We also noted that some measures had convergence issues.
+Overall the inconsistent fit --- and in extreme cases lack of convergence ---  of the unidimensional factor model either indicates that these measures were not unidimensional, and thus not construct valid in this use case, or because our simplistic factor model itself was not an appropriate choice for the given data.
+Besides this split in potential explanations for our results, low sample size and a small number of items --- common with the replication measures --- likely also played a role in the lack of convergence.
+Combining all these points together, we stress that our results are not meant to be regarded as validity assessments of individual measures.
+This lies beyond the scope of our article and does not align with our analytical approach.
+Instead, our claim based on our results is that while for the measures we checked unidimensionality forms a prerequisite for them being construct valid, we observe that this prerequisite is not universally met across labs, for which we question the assurance of valid measurement within our sample.
+
+Besides difference across contexts, reliability and validity of the measures in our sample were also impacted because many of them were modified from the original study.
+In our sample we noted that about two-thirds of the measures in replications were modified in some way from the original study.
+With modifications being this common it is best to be explicit in reporting these modifications and also to document the reliability and validity in replications.
+Minor differences between replication and original study are inevitable, but substantial changes between original and replication study raises the question whether it is still justified to label them as "direct" replication.
+For example, the conscientiousness measure used for the replication of De Fruyt et al @defruytCloningersPsychobiologicalModel2000 was reduced from the original NEO-PI-R 48-item measure to a two-item measure in the replication.
+It is highly unlikely that a measure with such a significant change would have a comparable validity and reliability to the original, and we did unsurprisingly observe convergence issues with validity for this measure as well as low reliability.
+
+We observed some patterns that may indicate bias in measurement reporting.
+If a Cronbach’s Alpha in our sample was reported for a measure in an original study, then their average Cronbach’s Alpha observed among the replications were consistently relatively high.
+Meanwhile, if no Cronbach’s Alpha was reported in the original study, the reliability was often relatively low.
+If we take our replication results to be representative, it may indicate that authors are more inclined to report reliability coefficients when measures are above an acceptable threshold, but less so when they are below.
+This aligns with existing research indicating bias in reported Cronbach’s Alpha values, with an excess of reported values at the common acceptably reliable threshold value of .70, and low reporting just below .70 [@husseyAberrantAbundanceCronbachs2023].
+In combination with our inconsistent reliability and validity evidence, this reporting bias creates a false sense of security when readers judge the reliability and construct validity of a measure  based on the reported information in the literature.
+
+Our intent is not to specifically criticize the Many Labs replications nor these specific original studies, but rather use them as illustrative examples.
+Regardless, we would argue that full transparent measurement reporting is a responsibility of both replications and original studies.
+Otherwise, based on our results and the results of existing research, there is reason to distrust the reliability and validity of many psychological measures, especially when used in a new context.
+The validation required to ensure that we can trust that a measure is valid across contexts is simply not reported for most measures, and based on our own analyses of the item response data, there is reason to doubt that a measure is likely to be valid in any context.
+Even though validating measures is challenging and resource intensive, its necessity cannot be ignored.
+It is questionable to draw substantive interpretations from results based on responses to an unvalidated measure.
 
@@
 Instead the structure of the model and the test was the same for all measures.
-It is quite possible that a measure fails at our checks and is still a valid and reliable measure in its specific use case.
-We use these checks to get an assessment of one element of construct validitty within our sample, not to make inferences for particular measures, nor to test construct validity completely.
-Future research may want to deep dive into this specific topic and focus on doing theory informed construct validity tests using openly available measurement reponse data.
-
-One of the most impactful limitations to our study design was that we were unable to conduct informative inferential tests on our data.
-This was in large part because there were simply to few measures with the relevant information for our test.
-We initially planned to test the significance of the difference in reported reliability between original and replication studies, and the relation between reliability and replication outcome.
-But due to the small number of reported reliabilities and measures for which reliability could be calculated we were unable to perform these tests.
-However, this limitation is also one of our most important findings.
-While we were unable to perform our pre-registered tests, the fact that we couldn't, is telling with respect to the lack of consistent measurement information reporting in our sample.
-
-!!!limited usefulness of the data!!!
-
-As another limitation, it is important to reflect on whether or not replication protocols and research articles can be fairly compared in terms of Measurement Practices.
+Even though we believe this is a reasonable proxy for construct validity --- as all measures we checked were used to form a singular index of one latent variable --- it is quite possible that a measure fails at our checks and is still a valid and reliable measure in its specific use case.
+These checks are designed as preliminary checks of construct validity that provide a general overview, not a complete thorough investigation of construct validity.
+Future research may want to deep dive into construct validity for one or a few measures and conduct thorough theory informed construct validity tests using openly available measurement response data to provide a complementary qualitative assessment of measurement validity in psychological research.
+
+One of the most impactful limitations to our analyses was that we were unable to conduct informative inferential tests on our data.
+This was in large part because there were simply too few measures with the relevant information for our purposes.
+We initially planned to test the difference in reported reliability between original and replication studies, and the relation between reliability and replication outcome.
+However, due to the small number of reported reliabilities and measures for which reliability could be calculated we were unable to perform these tests.
+However, this limitation also highlights one of our most important findings.
+While we were unable to perform our preregistered tests, the fact that we could not is telling of the lack of measurement information reporting in our sample.
+
+As another limitation, it is important to reflect on whether or not replication protocols and research articles can be fairly compared in terms of measurement reporting practices.
 A study’s description within a replication protocol is generally shorter than an article.
@@
 Firstly, articles are often also restricted in the amount of space they have available to devote to measurement [@gardinerEditorialMethodsPapers2019; @zogmaisterAssessingTransparencyMethods2024].
-Second, in the revised protocol some QMP items, such as whether example items were reported or not, also allowed for reporting this information in supplementary materials to count as good practice.
-Third, there are little to no other files outside the protocol and supplements where the measurement details for the replication could be found, as such the protocol and supplements represent the total available information on the measurement just like the original article does.
+Second, in the revised protocol some measurement reporting items, such as whether example items were reported or not, also allowed for reporting this information in supplementary materials to count as good practice.
+Third, while we also allowed supplementary materials, few other files besides the protocol described the measurement details for the replication in any details, as such the protocol represent most of the available information on the measurement just like the original article does.
+If the information could not be found in the protocol, it was unlikely to be found anywhere else.
 A difference that was not resolved between articles and protocols was that the protocols were written before the measurement was conducted.
-Therefore we can not fairly compare protocol and replication on measurement information that is derived from the data – such as reliability coefficients and psychometric validity information.
-Still, future research should look if possible at replications that report on measurement information derived from the replication data.
-
-???move to the paragraph above, the section in the discussion that describes the argument that replications dont have to report what is presumed to be in the original together with the counter-argument that modificaitons are regular, and as such measurement choice is fair game and should be motivated + an extra sentence that often information is not available in the original so it can hardly be relied upon???
+Therefore we cannot directly compare protocol and replication on measurement information that is derived from the data – such as reliability coefficients and psychometric validity information.
+Still, future research should look if possible at replications that report on measurement information derived from the item response data.
 
@@
 This is likely different for more recent research [@hardwickeEstimatingPrevalenceTransparency2022; @hamiltonPrevalencePredictorsData2023a].
-Including replications of recent original research could enable more comparisons based on open data from the original studies.
-Future research may wish to look at replications of more recent research to compare recalculated measurement information between original and replication.
-
-!!!niet representatieief, kodnen niet alles doen, maar voor vervolgonderzoek mogelijk!!!
+The original studies and replications of the Many Labs projects may also not be representative of typical original or replication research in psychology.
+Although we maintain the Many Labs projects are a relevant and high-quality source of studies, it may represent a standard that is not common throughout the field.
+Future research may wish to look at more representative replications and replications of more recent research.
 
@@
 
-There are two main issues we believe that should be addressed in the literature to improve measurement practices: the common use of non-validated measurement, and the lack of transparency surrounding measurement reporting.
-Unfortunately, there is no easy fix to these issues.
-The widespread use of validated measurement requires measures for a large range of topics to be validated, a practice that currently occurs only rarely.
-Meanwhile improving transparency in reporting is an issue that many have tried to address in relation to other parts of , but universal success has remained elusive here ???CITATIONS???.
-However, the positives are first that these two issues are interrelated, because solving transparency will benefit greater validation of measures, and second that every instance of transparent reporting and validation helps reduce the current problem.
-
-Our first reccomendation is that reporting standards for measurement deserve a more central place.
-We found that reporting reliability and validity information was the exception rather than the rule, and even basic information such as how many items were in the measure was reported with little consistency among our sample of measures.
-The @americaneducationalresearchassociationStandardsEducationalPsychological2014 guidelines exist to guide researchers in the creation and validation of scales, but are not tailored as guidelines for general measurement reporting.
-The APA guidelines [@AmericanPsychologicalAssociation2020] do address many of the same reporting practices we assessed, however our findings and those of other research shows that uptake of these standards is minimal.
-Meanwhile, statistical reporting standards and guidelines have had a stronger place in the field and among journals, including recommendations from the ASA [@wassersteinASAStatementPValues2016].
-A high-profile push for measurement reporting standards is lacking.
-We believe that measurement reporting standards deserve to be highlighted as much as statistical result reporting.
-after all, even well reported statistics lack have to be understood within the context of the measurement.
-
-Transparent measurement reporting also has the advantage that it enables future researchers to recreate the original measure.
-This point is critical to fueling our second recommendation: as a community we need to systematically evaluate and revise our measures.
-To do so, we first need measures to be reusable.
-Second, researchers need to reuse existing measures.
-Third, the obtained reliability and validity of the measure then need to be compared across multiple occasions, and finally a value judgement to determine in what contexts, if any, the measure is valid has to be made.
-Transparent reporting takes care of the first step.
-For the second step, @elsonPsychologicalMeasuresArent2023 have suggested journals to implement the Standardisation Of BEhavior Research (SOBER) guidelines to specifically address issues of flexibility and norming in measurement so that measures are reused in a comparable state.
-Furthermore, they propose an open repository of measurement protocols to facilitate the discovery of measures and building an evidence base.
-For the third and fourth step, two things are needed.
-First, there should be a space in the scientific literature for persistent measurement evaluation, just like how a place for replication studies in the literature has been suggested to provide persistent evaluation of effects.
-In fact, if replications were to play closer attention to measurement evaluation and reporting, they can function as an excellent validation test of the measure as well.
-Second, the data obtained from the measurement should be available for a comprehensive validaity analyses of the measure within different contexts.
-For this it would be best if the original data of the item responses and demographics is shared for each use of the measure.
-This way the measure's validity and reliability can be recomputed similarly to what was done in our analyses, but with a closer link to theory.
-Otherwise, the summary statistics such as the variance-covariance structure, means, and standard deviations should be shared as these are sufficient for many basic factor analysis models.
-
-Furthermore, researchers should report and evaluate their measures using more informative indicators.
-Cronbach's Alpha on its own gives only limited information the quality of a scale, and comes with strong assumptions [@cortinaWhatCoefficientAlpha1993; @sijtsmaUseMisuseVery2009].
-Factor analytical evidence and McDonald's Omega are more informative indicators that should be presented in favor of or in tandem with Cronbach's Alpha.
-
-Finally, we argue that researchers seeking to replicate a study should first evaluate the measurement of that study.
-Not only is it crucial for an informative replication that the measurement is reliable or valid.
-The original study should also report the measurement details necessary to reconstruct the original measurement.
-Otherwise it will be challenging to know if measurement was different between original and replication.
-If so, we suggest that researchers instead use their resources to conduct a replication of a study with reliable, valid and well-documented measurement.
+There are two main issues that we believe should be addressed to improve measurement practices: the common use of measures without established validity, and the lack of transparent measurement reporting.
+Unfortunately, fixing these issues requires considerable time and resources.
+Establishing validity would for a start require that the reliability and construct validity of each measure is analysed  within each context it is used in, a practice that currently occurs only rarely beyond a handful of common (clinical and personality) questionnaires [@anvariFragmentedFieldConstruct2025].
+Meanwhile, improving transparency in reporting is an issue that many have tried to address for other aspects of academic articles such as preregistration deviations [@willrothBestLaidPlans2024], and constraints on generality [@simonsConstraintsGeneralityCOG2017], but widespread success has remained elusive.
+Despite these challenges, we remain optimistic that even small interventions can accelerate improvement.
+First of all, these two issues are interdependent.
+Improving transparency in measurement reporting can in turn facilitate validation efforts.
+Moreover, even incremental progress, such as establishing validity for a subset of frequently used measures, can meaningfully enhance the overall quality and credibility of psychological research.
+
+Thus, our first recommendation is that reporting standards for measurement deserve a more central place in psychological science.
+We found that reporting reliability and validity information was the exception rather than the rule, and even basic information such as how many items were in the measure was reported with little consistency in our sample.
+The American Educational Research Association @americaneducationalresearchassociationStandardsEducationalPsychological2014 guidelines exist to guide researchers in the creation and validation of scales, but not how to report the measurement details when in use.
+The APA guidelines [@AmericanPsychologicalAssociation2020] do address many of the same reporting practices we assessed, however our findings and those of other research shows that uptake of these standards is still minimal.
+One aspect where reporting standards has seen some changes is in statistical reporting [@hardwickeStatisticalGuidanceAuthors2023].
+Statistical reporting standards and guidelines have received, including recommendations from the American Statistical Association [@wassersteinASAStatementPValues2016].
+The uptake of statistical reporting guidelines is even seen among journals.
+Although, in practice the guidelines vary in their content and enforcement [@hardwickeStatisticalGuidanceAuthors2023].
+Still, we believe that for measurement any increase in reporting standards will be a welcome change compared to no push, and that a similar high-profile push is at least as relevant for measurement reporting standards as it is for improving scientific robustness as it is for statistical result reporting.
+After all, the data obtained through measurement is the foundation for nearly all empirical quantitative psychological research results.
+
+As a related recommendation that could become a standard, we suggest that researchers should report and evaluate their measures using more informative indicators.
+Cronbach’s Alpha on its own gives only limited information the quality of a scale, and comes with strong assumptions [@cortinaWhatCoefficientAlpha1993; @sijtsmaUseMisuseVery2009].
+Factor analytical evidence and McDonald’s Omega are more informative indicators that should be presented in favor of or in tandem with Cronbach’s Alpha.
+
+Our second recommendation is that, as a scientific community, we need to systematically validate a greater proportion of our measures.
+But to able to do so, the measures should first of all be reusable --- here, transparent measurement reporting is crucial.
+Then, researchers should actually reuse existing validated measures, rather than make new ones on the fly and use these unvalidated measures.
+To encourage and enable the reuse of existing measures, Elson et al @elsonPsychologicalMeasuresArent2023 have proposed an open repository of measurement protocols to facilitate the discovery of measures and building an evidence base.
+Furthermore, they suggested that journals should implement the Standardisation Of BEhavior Research (SOBER) guidelines to specifically address issues of flexibility and norming in measurement so that measures remain comparable across studies.
+If researchers then reuse a measure across different context its reliability and validity needs to be compared across multiple occasions to assess in which contexts, if any, the measure is valid.
+
+If more systematic measurement validation is to take place, it is equally important that the resulting evidence becomes an integral and respected part of the scientific literature.
+We therefore suggest that the scientific literature should include a dedicated space for systematic and continuous measurement validation studies, similar to the space proposed for replication studies to assess the robustness of effects.
+Moreover, replication studies themselves could contribute to measurement validation: by paying closer attention to measurement evaluation and reporting, replication efforts could simultaneously serve as a robustness of an effect and a validation test of the measure.
+Finally, to enable cumulative progress, a greater proportion of item response data should be made available to the scientific community.
+Ideally, this includes item-level responses and relevant participant characteristics, allowing future researchers to (re-)evaluate a measure’s validity and reliability in relation to theory.
+When full data sharing is not possible, providing summary statistics (such as variance–covariance matrices, means, and standard deviations) can still allow others to conduct factor-analytic assessments of measurement quality and even meta-analytic evaluation across contexts.
+
+Finally, we recommend to researchers seeking to replicate a study that they should first evaluate the measurement of the original study before replicating.
+Reliable and valid measurement is essential for an informative replication.
+If the original measures are unreliable, discrepancies between the original and replication results become more likely, thereby reducing the interpretability and value of both studies.
+Moreover, repeating a study that relies on invalid measures does little to advance substantive knowledge and instead risks perpetuating misleading or meaningless findings.
+Furthermore, to make meaningful replication possible, original studies must report sufficient measurement details to allow others to reconstruct the instruments and procedures used.
+Without such transparency, it is impossible to know whether differences between the original and replication studies reflect true effects or merely differences in measurement.
+When the original measures are unreliable, invalid, or insufficiently documented, we recommend that researchers instead use their resources to conduct a replication of a study with reliable, valid and well-documented measurement.
 When replicating another study is not an option, we advise the replicating researcher to first attempt a conceptual replication using a validated measurement.
-Afterwards, a direct replication can be performed based on the conceptual replication to further assess the robustness.
+Afterwards, a direct replication can be performed based on the conceptual replication to further assess the robustness of the effect.
 
@@
 
-Cumulative knowledge on psychological phenomena starts with our ability to accurately capture the relevant constructs of interest.
-Based on the results from our sample and the findings of existing research, the validity and reliability of psychological measurements is rarely reported and based on our data cannot be assumed to be generally correct.
-The lack of consistent transparency in measurement reporting further complicates evaluating and reusing the existing measures.
-A change will be necessary.
-Otherwise, the basic premise that the measurement measures the variable it is intended to measure, will remain unsubstantiated for many psychological studies.
-Fortunately, even small steps towards improved reporting practices and single instances in cumulative measurement validation can already help to proliferate validated measurement.
+Cumulative knowledge on psychological phenomena starts with our ability to accurately measure the constructs of interest.
+For this we need valid and reliable measurement.
+Yet, in our sample of Many Labs replications and original studies we observed that the construct validity and reliability of psychological measurements is rarely reported and based on our analyses were seldom sufficient enough across contexts to assume that constructs are generally measures as intended.
+Furthermore, the lack of transparency in measurement reporting hampers the reuse of existing measures.
+A change in the use and reporting of measurement is necessary.
+Otherwise, psychological effects lack the measurement fundamental to establish that they are related to true psychological phenomena.
+Fortunately, even small steps towards improved reporting practices, data and materials sharing, and normalizing measurement validation can spark the proliferation of validated measurement.
 
@@
 
-The preparation of this article was supported by the Veni grant VI.Veni.201G.003 awarded to Michèle Nuijten, and the Vici grant VI.C.221.100 awarded to Jelte M.
-Wicherts from the Dutch Research Council (NWO).
+The preparation of this article was supported by the Vici grant VI.C.221.100 awarded to Jelte M. Wicherts from the Dutch Research Council (NWO).
 

### 2025-12-12 Scripts/Manuscript/manuscript.Rmd
Finalized rewrites for PLOS One version of pre-print.

@@
 ---
-title             : "Measurement Reliability, Construct Validity, and Transparent Reporting in Original and Replication Research"
+title             : "Measurement Reliability, Construct Validity, and Transparent Reporting in Original and Replication Psychological Research"
 shorttitle        : "Measurement Reliability, Validity, and Reporting"
@@
 abstract: |
-  To assess psychological phenomena we need reliable and valid measurement of the construct(s) of interest.
-Information should therefore be reported alongside the measure to enable the evaluation of reliability and validity.
-Additionally, to ensure that reliable and valid measures can be reused in future research, the measure should be documented in sufficient detail.
-Therefore, we investigated the measurement reporting in a sample of 77 measures within 56 Many Labs replications and related original articles (Ebersole et al., 2016, 2020; Klein et al., 2014, 2018).
-We found that the information relevant for the reuse of a measure was reported in full for around half the replication measures, and only 5.2% of the original studies.
-We also observed that only around a third of multi-item measures in original studies and 11.4% in replications reported a reliability coefficient, with comparable proportions for reporting any psychometric validity evidence.
-Besides reporting, we also performed checks of the reliability and construct validity using the openly available Many Labs item response data.
-We observed that the reliability and construct validity of the measures was rarely stable across contexts.
-These results corroborate existing findings that measurement reporting in published research lacks transparency, and that this transparency may in certain contexts cover up insufficient reliability and valdity.
-Finally, we offer suggestions on how to increase measurement reporting transparancy and the use of validated measures.
-
-keywords          : "reliability, construct validity, measurement, reporting, transparent reporting, replications, psychology"
-wordcount         : "225"
+  While published (replication) studies using measures to assess psychological phenomena need to transparently report information on measurement procedures, validity, and reliability to allow verification and use in future (replication) research, earlier results highlighted common poor reporting of psychological measurement.
+Here, we investigated the measurement reporting in a sample of 77 measures within 56 Many Labs replications and related original articles (14–17) and found that the information relevant for reusing measures was reported in full in around half the replication measures, and only 5.2% in the original studies.
+We also observed that only around a third of multiple-item measures in original studies and 11.4% in replications reported reliability coefficients, with comparable proportions for reporting any convergent, discrimant, predictive, or factorial validity evidence.
+We performed checks of the reliability and unidimensionality of multiple-item measures using the openly available Many Labs item response data.
+We observed that the reliability and unidimensionality of the measures was rarely stable across labs.
+These results corroborate existing findings that measurement reporting in published research lacks transparency, and that poor measurement reporting often obscure insufficient reliability and validity.
+We offer suggestions on how to improve measurement reporting practices and increase the use of validated measures.
+
+keywords          : "reliability, construct validity, measurement, reporting, transparency, replication, reproducibility"
+wordcount         : "198"
 
@@
 classoption       : man
-output            : papaja::apa6_docx
+output            : papaja::apa6_pdf
 knit              : worcs::cite_all
@@
 
-The challenge with measurement in quantitative psychological research is that unlike height or weight, psychological constructs cannot be directly measured, as they cannot be directly observed.
-Instead, we use scores from a measure as an indicator for a psychological construct.
-Yet, it cannot simply be assumed that any measure will form a good indicator of the constructs of interest.
-The measure has to be validated by establishing the reliability and construct validity of the measure.
-Following the definition of Crutzen and Peters, “[r]eliability refers to the consistency of scale scores when a construct is assessed multiple times or in multiple ways” [@crutzenScaleQualityAlpha2017b; pp.
-244].
-In turn, construct validity refers to whether the variance in the measured item scores between participants can be attributed to the variance in the unobserved construct(s) of interest between participants [@cronbachConstructValidityPsychological1955].
-In practice, the measure itself is always validated within one or more use cases of a specific measurement procedure and the context in which that measurement took place, such as the sample characteristics, location, and time.
-
-However, psychological measures often lack reliability and construct validity evidence, either because the evidence is not reported, or because the measures are not validated at all [@beckmanHowReliableAre2004; @barryValidityReliabilityReporting2014; @flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020; @flakeConstructValidityValidity2022].
-Flake et al @flakeMeasurementSchmeasurementQuestionable2020 dubbed these such practices --- that raise doubts about the validity of a measurement --- “Questionable Measurement Practices” (QMPs), being a term analogous to Questionable Research Practices [QRPs; @simmonsFalsePositivePsychologyUndisclosed2011a; @johnMeasuringPrevalenceQuestionable2012a; @wichertsDegreesFreedomPlanning2016a].
+Because psychological constructs cannot be directly measured, quantitative psychological researchers use scores from psychological measures to study psychological phenomena.
+Psychological measurement is no easy feat and so measures will not always form good indicators of the constructs they purport to measure.
+Measures need to be validated and associated with sufficient reliability to deal with systematic and unsystematic measurement errors to attribute observed variation in scores to the variance in the unobserved construct(s) of interest.
+Psychometrics offers a wide range of tools to assess reliability and to study validity, ranging from classic Cronbach’s Alpha to asses internal consistencies to item response theory and structural equation models allowing for fitting models that explicate the notion that supposed latent variables relate to observed items scores in the expected manner In practice, however, many psychological measures exhibit subpar (or unclear) reliabilities and are typically validated and psychometrically tested only in limited circumstances, samples, and measurement procedures, while it is likely that they do not behave psychometrically well in all relevant samples, locations, and time points [@maassenDireDisregardMeasurement2025].
+
+Moreover, many measures used in psychological research lack reliability and construct validity evidence altogether, either because the evidence is not reported in studies using them, or because the measures are not validated to begin with [@beckmanHowReliableAre2004; @barryValidityReliabilityReporting2014; @flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020; @flakeConstructValidityValidity2022].
+Such practices are rightly @flakeMeasurementSchmeasurementQuestionable2020 dubbed  “Questionable Measurement Practices” (QMPs), being a term analogous to Questionable Research Practices (QRPs; [@simmonsFalsePositivePsychologyUndisclosed2011a; @johnMeasuringPrevalenceQuestionable2012a; @wichertsDegreesFreedomPlanning2016a]).
 A recent line of research has already shown QMPs to be relatively common in both original and replication psychology studies, damaging the trustworthiness and applicability of psychological research findings [@flakeConstructValidityValidity2022; @husseyAberrantAbundanceCronbachs2023].
@@
 The purpose of this study is to assess the measurement reporting practices of item-based measures in a diverse and seminal sample of original and replication studies in psychology.
-In addition, we will use the available item response data to calculate reliability and construct validity indices.
-Through the combination of assessing the measurement reporting and the calculated indices, we reflect on the apparent validity of the measurement based on the reported information, compared to the validity assessment when going beyond the reported information and checking the item response data.
+In addition, we will use the available item response data to calculate reliability indices for multiple-item measures and perform a series of unidimensionality checks --- as a prerequisite check of construct validity.
+By assessing the measurement information as reported together with reliability and unidimensionality using the primary data, we reflect on the apparent validity of the measurement based on the reported information, compared to our validity assessment based on the item response data.
 
@@
 One issue that has been observed with respect to measurement validation is that the reported measurement information is typically insufficient for readers to understand, evaluate, and reuse the measurement that was used.
-Flake et al @flakeConstructValidityValidity2022 documented the measurement reporting practices among 100 original psychology articles and their respective replications from the Reproducibility Project Psychology [@opensciencecollaborationEstimatingReproducibilityPsychological2015].
+Flake et al.
+@flakeConstructValidityValidity2022 documented the measurement reporting practices among 100 original psychology articles and their respective replications from the Reproducibility Project Psychology [@opensciencecollaborationEstimatingReproducibilityPsychological2015].
 They coded the number of measures, the content of the measures, and information describing and justifying the measurement.
-They observed limited reporting of evidence demonstrating the reliability and validity of the measurement.
-Additionally, only eight of the 40 translated scales contained validity evidence for the translated version.
+The reporting of reliability evidence was assessed through whether Cronbach’s Alpha coefficients were reported.
+For validity evidence, they looked at citations to existing validity evidence from previous studies documenting the scale’s development or use, and results from a factor analysis providing structural evidence for the measure.
+They observed limited reporting of both reliability and validity evidence.
+Additionally, only 8 of the 40 translated scales referenced an existing validity study that described evidence for the translated version.
 A similar lack of reliability and validity reporting has been observed in other studies as well [@hoganEmpiricalStudyReporting2004; @flakeConstructValidationSocial2017].
-If readers cannot infer the construct validity and reliability of a measure from the reported information, then readers lack the basic information needed to determine whether the measured variables are actually related to the constructs of interest.
-In turn, if we cannot determine whether the constructs of interest are captured in the measured variables or not, then the relation of the results of the statistical analysis using these variables and any psychological phenomena of interest is also tenuous.
-In short, if the reported information does not show that the measurement was valid, then any substantive conclusions from the data are left unsupported.
-
-Further findings by Flake et al @flakeConstructValidityValidity2022 and others [@flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020] show that measurement reporting was not only limited in terms of the reliability and validity evidence.
-A lack of clearly reported information was also observed for basic content descriptions such as the number of items, the response format, and the scoring of the scale.
+If the reported information does not reference any of the references to reliability or validity evidence, then readers lack the basic information needed to make an assessment of whether the measured variables relate to the constructs of interest.
+In turn, if the reported information does not exhibit some minimal level of validity --- through reliability coefficients, an existing validation study, or factor analysis results --- then any substantive conclusions drawn from the data are left unsupported.
+
+Further findings by Flake et al.
+@flakeConstructValidityValidity2022 and others [@flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020] show that issues in measurement reporting go beyond a lack of reporting reliability and validity evidence.
+Basic content descriptions such as the number of items, the response format, and the scoring of the scale are not always clearly reported.
 This creates challenges for future researchers who want to reuse the measure to assess the same construct.
@@
 Two key aspects of measurement quality are reliability and construct validity.
-Psychometrics offers various methods for assessing these properties [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011].
+These can be studied using various psychometric tools  [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011].
 The results of such psychometric analyses often serve as essential evidence for evaluating a measure’s validity.
 
-Reliability serves as a pre-requisite for a valid measure in most cases, because a measure for which a participant’s response is not consistent, cannot capture a stable construct [Kaplan and Saccuzzo (2013, pp.
-154–155)].
-It is therefore concerning that --- as mentioned earlier --- the reporting of psychometric indicators of reliability is not common, and is often limited to Cronbach’s Alpha.
-Unfortunate, because Cronbach’s Alpha comes with strong assumptions that are rarely tested [@crutzenScaleQualityAlpha2017b].
-Furthermore, research by Hussey et al @husseyAberrantAbundanceCronbachs2023 has shown evidence that the reporting of reliability may not only be uncommon, but also biased.
+Reliability serves as a pre-requisite for a valid measure in most cases, because a measure for which a participant’s response is not consistent, cannot capture a stable construct [@KaplanPsychologicalTestingPrinciples2013; p.
+154–5].
+It is therefore concerning that the reporting of psychometric indicators of reliability is often substandard  [@beckmanHowReliableAre2004; @barryValidityReliabilityReporting2014; @flakeConstructValidationSocial2017; @flakeConstructValidityValidity2022], Moreover, reliability reporting often limits itself to Cronbach’s Alpha, which comes with strong assumptions that are rarely tested [@crutzenScaleQualityAlpha2017b; @sijtsmaUseMisuseVery2009].
+Furthermore, research by Hussey et al.
+@husseyAberrantAbundanceCronbachs2023 has shown evidence that the reporting of reliability may not only be uncommon, but also biased.
 They observed a disproportional number of Cronbach’s Alpha values at the common acceptably reliability threshold value of .70, and relatively low reporting below .70.
@@
 
-As a result, if we want to evaluate the reliability of a measure in our sample, we cannot rely on the reported information alone to paint us a representative picture.
-Therefore, we also evaluated the measurement reliability within the Many Labs original and replication studies by estimating it from the item response data.
+As a result, the full evaluation of reliabilities is hindered by the possibly biased reporting in our sample of (replication) studies.
+Therefore, we also computed the measurement reliability within the Many Labs original and replication studies by estimating it from the raw item data.
 The data on the item responses are openly available per lab for our sample.
@@
 Still, many researchers report and interpret Cronbach’s Alpha as a universal quality of the measure [@cortinaWhatCoefficientAlpha1993; @schmittUsesAbusesCoefficient1996].
+Mairead Shaw et al.
 @maireadshawMeasurementPracticesLargescale2020 have already observed that for Many Labs 2 the overall sample Cronbach’s Alpha level across scales was below .5, a degree of reliability far below what many would consider acceptable for most research purposes.
@@
 A multi-stage process is required to statistically and substantially establish a link between the measurement and the construct of interest.
-For example, the way a measure's items relate to each other and to the underlying concept (the factor relations) can differ substantially across contexts, a concept known as measurement invariance [@hornPracticalTheoreticalGuide1992; @cheungDirectComparisonApproach2012].
+For example, the way a measure’s items relate to each other and to the underlying concept (the factor relations) can differ substantially across contexts, a concept known as measurement invariance [@hornPracticalTheoreticalGuide1992; @cheungDirectComparisonApproach2012].
 Thus, we cannot assume that the measure is valid in each context it is used in or meant to be used in, it is something that has to be established for each context.
 Besides investigating the factor structure, the measure should also be backed up substantively and logically [@borgstedeMeaningfulMeasurementRequires2023].
-However, what we typically observe in psychological research is that measures are rarely substantiated with validity evidence [@beckmanHowReliableAre2004; @barryValidityReliabilityReporting2014; @flakeConstructValidationSocial2017; @flakeConstructValidityValidity2022].
-This may in part be because the sample sizes required in validating a scale can often be larger than many studies are able to obtain [@maccallumSampleSizeFactor1999, @gorsuchFactorAnalysis2013].
-Alternatively, researchers may not recognize measurement validation as part of their research method.
-Yet what has also been observed in the literature is that many measures are created ad hoc and reused maybe once or not at all [@weidmanJingleJangleEmotion2017; @elsonPsychologicalMeasuresArent2023; @anvariFragmentedFieldConstruct2025; @anvariDefragmentingPsychology2025].
-This makes it extremely unlikely that the validity of these measure will ever be assessed at all, let alone be thoroughly investigated by analyzing measurement invariance across multiple groups using substantial sample sizes [@meadePowerPrecisionConfirmatory2007; @frenchMeasurementInvarianceTechniques2016; @koziolImpactModelParameterization2018].
-
-One preliminary psychometric check that could easily be conducted is to see if the number of constructs measured by the items of the measurement match the intended number of constructs.
-Most often the scores on a measure or subscales of a measure are aggregated and interpreted as a singular index.
+However, what we typically observe in psychological research is that measures are rarely substantiated with validity evidence [@beckmanHowReliableAre2004; @barryValidityReliabilityReporting2014; @flakeConstructValidationSocial2017; @flakeConstructValidityValidity2022], and that many measures are made on the fly and reused maybe once or not at all [@weidmanJingleJangleEmotion2017; @elsonPsychologicalMeasuresArent2023; @anvariFragmentedFieldConstruct2025; @anvariDefragmentingPsychology2025].
+It is not entirely surprising that most psychological measures are not fully validated, as this requires its own line of research spanning several years, to determine the relation between measure and construct(s), and how this varies across contexts [@meadePowerPrecisionConfirmatory2007; @frenchMeasurementInvarianceTechniques2016; @koziolImpactModelParameterization2018], and over time [@marshlongitudinalstabilitylatent1994], among other aspects.
+
+However, there are prerequisite checks of construct validity that can be conducted by researchers in most scenarios [@gorsuchFactorAnalysis2013].
+One such check is to see if the number of constructs measured by the items of the measurement match the intended number of constructs.
+Often the scores on a measure or subscales of a measure are aggregated and used as a singular index when included as a variable in a statistical model.
 In that case, the measure should be unidimensional.
 Otherwise, the researcher is interpreting a set of scores to be one concept when in fact they are multiple distinct concepts.
-Additionally, most reliability indicators --- including Cronbach’s Alpha --- cannot properly estimate true variance when it is spread across distinct constructs, and will thus give an inaccurate estimate of reliability [@schmittUsesAbusesCoefficient1996; @crutzenScaleQualityAlpha2017b].
-
-Mairead shaw et al @maireadshawMeasurementPracticesLargescale2020 checked the dimensionality of the measurements from Many Labs 2 [@kleinManyLabs22018b], and while some support for unidimensionality was present, they found that none of the scales in their sample met all of their criteria for unidimensionality.
+Additionally, most reliability indicators --- including Cronbach’s Alpha --- cannot properly estimate true variance when it is spread across distinct constructs, and will result in an inaccurate estimate of reliability [@schmittUsesAbusesCoefficient1996; @crutzenScaleQualityAlpha2017b].
+Thus, unidimensionality checks offer researchers a practical wat to test if the construct validity of their measure is bound to sink or has the potential to swim.
+
+Mairead Shaw et al.
+@maireadshawMeasurementPracticesLargescale2020 checked the dimensionality of the measurements from Many Labs 2 [@kleinManyLabs22018b] and while some support for unidimensionality was present, they found that none of the scales in their sample met all of their criteria for unidimensionality.
 Because the Many Labs replications reused existing measures across contexts, Mairead shaw et al @maireadshawMeasurementPracticesLargescale2020 could assess validity across contexts.
@@
 We will perform our own checks of unidimensionality on measures from Many Labs 1, 2, 3, and 5 per lab, and include a meta-analytic assessment of the variation in unidimensionality across labs.
-The combined goal of our three research aims is to provide a descriptive account of the reliability, construct validity, and reporting of measurement in the included Many Labs study pairs.
+The combined goal of our three research aims is to provide a descriptive account of the reliability, unidimensionality, and reporting of measurement in the included Many Labs study pairs.
 
@@
 We preregistered data collection, coding protocol, and planned analyses: <https://osf.io/jgxyu>.
-We deviated from our coding protocol as is explained further in the text.
+We deviated from our coding protocol as is explained further below.
 The results from our preregistered analyses are described in [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd).
@@
 
-## Ethical Approval
-
-This research was approved by the Tilburg University School of Social and Behavioral Sciences Ethical Review Board (nr. TSB_TP_REMA06).
+## Ethics Approval
+
+This research was approved by the Tilburg University School of Social and Behavioral Sciences Ethics Review Board (under TSB_TP_REMA06).
 
@@
 The data consists of three main sources: replication datasets, replication protocols, and original study articles. 
-We retrieved the data of Many Labs 1, 2, 3, & 5 [@kleinInvestigatingVariationReplicability2014a; @ebersoleManyLabs32016; @kleinManyLabs22018b; @ebersoleManyLabs52020d] from their respective OSF pages.
+We retrieved the data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 [@kleinInvestigatingVariationReplicability2014a; @ebersoleManyLabs32016; @kleinManyLabs22018b; @ebersoleManyLabs52020d] from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>.
 Many Labs 4 [@kleinManyLabs42022] was excluded, as there were no publicly available replication protocols.
-Additionally, we excluded the replication of [@crosbyWhereWeLook2008a] in Many Labs 5, as it made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures.
-
-## Unit of Analysis
-
-Our unit of analysis is a measure of a single variable within a replication protocol or original article that was used in the main analysis that was replicated.
-For example, if conscientiousness and agreeableness were both measured using the Big 5 Personality Test, each of which was a variable in a replicated effect, then both the conscientiousness and agreeableness part of that questionnaire would be coded as their own unit of analysis.
-We also allowed for multiple variables to be measured per study.
-We used the replication protocols to identify the measure of each variable.
-We did not include acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses.
-Our final sample size was `r nrow(coded_data_replications)` measures of unique variables for both original and replication studies.
-Initially, the original articles contained 3 more measures of unique variables than the replication protocols.
-This difference was due to the way that the moral foundations questionnaire was framed in the original article compared to in the replication protocol.
-In the original article it was framed as measuring five different moral foundations, while in the replication protocol the measure assessed the two overarching categories that were used to test the main effect in both the original and replication research.
-The measurement information reported was comparable across all five categories, and thus it was deemed that the measurement could be reduced to reflect two overarching categories to facilitate easier comparison between measurement in original and replication.
-
-## Data Collection
-
-The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>.
+Additionally, we excluded the replication of Crosby et al.
+[@crosbyWhereWeLook2008a] in Many Labs 5, as it made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures.
 We skimmed both the replication protocols and replication datasets to ensure that they were the correct files to code measurement reporting information from.
@@
 
-### Replication Protocols
+### Replication Protocols & Original Articles
 
 The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of the replication of an original study.
-These were retrieved from the Open Science Framework (OSF) pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd>).
-
-### Original Articles
-
+These were retrieved from the Open Science Framework (OSF) pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document).
 We identified and retrieved all original study articles using the citations for these articles in each replication protocol.
@@
 
-## Measures
+## Unit of Analysis
+
+Our unit of analysis is a measure of a single variable within a replication protocol or original article that was used in the main analysis that was replicated.
+For example, if conscientiousness and agreeableness were both measured using the Big 5 Personality Test, each of which was a variable in a replicated effect, then both the conscientiousness and agreeableness part of that questionnaire would be coded as their own unit of analysis.
+We also allowed for multiple variables to be measured per study.
+We used the replication protocols to identify the measure of each variable.
+We did not include acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses.
+Our final sample size was `r nrow(coded_data_replications)` measures of unique variables for both original and replication studies.
+Initially, the original articles contained 3 more measures of unique variables than the replication protocols.
+This difference was due to the way that the moral foundations questionnaire was framed in the original article [@grahamLiberalsConservativesRely2009] compared to in the replication protocol for Many Labs 2 [@kleinManyLabs22018b].
+In the original article it was framed as measuring five different moral foundations, while in the replication protocol the measure assessed the two overarching categories that were used to test the main effect in both the original and replication research.
+The measurement information reported was comparable across all five categories, and thus it was deemed that the measurement could be reduced to reflect two overarching categories to facilitate easier comparison between measurement in original and replication.
+
+## Coding of Articles and Replications
 
@@
 
-We evaluated the transparency of the measurement reporting practices within the original articles and replication protocols using our preregistered coding protocol containing items assessing twenty three reporting practices.
-The items were based on Table \@ref(tab:QMPCodingInfoTable) presented in Flake et al @flakeMeasurementSchmeasurementQuestionable2020, listing what measurement information to report.
-We coded an item as “true” if the relevant measurement information was clearly reported, “false” if it was missing or unclear, and “not applicable” if it was irrelevant for that measure (e.g., reporting factor analysis results for single-item measures).
-These items thus indicate transparent reporting practices, which can be seen as the opposite of QMPs.
-We grouped the items into five categories, each representing a different element in measurement reporting.
-Example items are listed in Table \@ref(tab:QMPCodingInfoTable).
-
-```{r QMPCodingInfoTable, warning = FALSE}
-QMP_info_dataframe <- data.frame(Category = c("Definition", "", "", "Operationalisation", "", "", "", "", "Selection/Creation", "", "", "Quantification", "Modification", "", "", "", "", ""),
-           'N Items' = c("1", "", "", "5", "", "", "", "", "7", "", "", "4", "6", "", "", "", "", ""),
-           'Example Item' = c("A psychological/sociological definition",
-            "is given to the name of the measured",
-            "variable within the paper.", 
-            "The administration format (pen-and-",
-            "paper/computer) and environment (in",
-            "public/in a lab) are described (Note:",
-            "both should be present for this item to be", 
-            "rated as “true”).", 
-            "The source of the scale is provided",
-            "(in case the scale was newly developed",
-            "this should be clearly stated).", 
-            "The number of items are described.", 
-            "Any format changes are mentioned",
-            "(paper-and-pencil <–> computer), if no",
-            "changes were made to the format, and",
-            "this was mentioned then code as No",
-            "modification. If it is not clear, then code",
-            "as False."))
-
-# making the column names look less robot speak-y.
-colnames(QMP_info_dataframe) <- c("Category", "N Items", "Example Item")
-
-# transfer the data to an APA table for printing
-apa_table(
-  QMP_info_dataframe, align = c("l", "r", "l")
-  , caption = "Example items used to code transparent measurement reporting practices across five categories linking to different aspects of measurement"
-  , note = "Selection and creation of a measure share a category because the justifications and requirements in selecting a measure are similar to those for creating a new measure."
-  , escape = FALSE, placement = "htp", booktabs = TRUE)
-
-```
+We evaluated the transparency of the measurement reporting practices within the original articles and replication protocols using our preregistered coding protocol containing 23 reporting practices.
+The criteria were based on Table 1 presented in Flake et al.
+@flakeMeasurementSchmeasurementQuestionable2020, listing what measurement information to report.
+We coded a criterion as “true” if the relevant measurement information was clearly reported, “false” if it was missing or unclear, and “not applicable” if it was irrelevant for that measure (e.g., reporting factor analysis results for single-item measures).
+These criteria for transparent reporting practices can be seen as contra-indicators of QMPs.
+We grouped the criteria into five categories (Definition, Operationalisation, Selection/Creation, Quantification, Modification), each representing a different element in measurement reporting.
+Selection and creation of a measure share a category because the criteria for selecting a measure are similar to those for creating a new measure.
+Examples of criteria are: "The administration format (pen-and-paper/computer) and environment (in public/in a lab) are described" (Operationalisation); "The number of items are described" (Quantification).
+The full coding protocol can be found in the [Revised Coding Protocol](../../SupplementaryMaterials/Measurement_Error_Reporting_Revised_Coding_Protocol.pdf) supplementary document.
 
 Included within the list of measurement reporting information is crucially also the reported reliability coefficient and type of index (Cronbach’s Alpha, test-retest correlation, inter-rater reliability coefficient, etc.) when present.
-As well as the presence of any psychometric construct validity evidence for the measure, such as the results from a factor analysis.
-
-After the initial coding, we made minor alterations from the preregistered coding protocol for fourteen of the twenty three measurement reporting practice items.
-These items were changed after familiarizing ourselves with the way measurement was reported, and it became clear that our criteria were too stringent.
+As well as the presence of any psychometric convergent, discriminant, predictive or factorial validity evidence for the measure.
+
+After the initial coding, we made minor alterations from the preregistered coding protocol for 14 of the 23 measurement reporting practices.
+We revised these coded criteria because early results indicated that our original criteria were too stringent.
 For example, in the initial protocol, an example item of the measure had to be present within the article or protocol itself, for the measurement practice to be considered clearly reported.
-In the revised protocol, references to online appendices with example items were also considered sufficient for this item.
+In the revised protocol, references to online appendices with example items were also considered sufficient for this criterion.
 The analyses, tables, and figures presented in this article are all based on the revised coding protocol.
@@
 
-We initially intended to construct an index from the transparent measurement reporting items and perform regression analyses on this index and associated replication outcomes.
-However, this index could not be validated properly, due to a lack of reported information and because we do not have any theorized outcome that could function as a suitable index for predictive validity.
+We initially intended to construct an index from the transparent measurement reporting criteria and perform regression analyses on this index and associated replication outcomes.
+However, this index could not be validated properly, due to the lack of reported information, including information that could be used to construct a suitable outcome to assess the index' predictive validity.
 Results based on this index would be misleading to present here in the main article.
@@
 
-We calculated reliability from the item responses on each measure for each lab the measure was used in based on the replication datasets with suitable data.
+We calculated internal consistency reliabilities from the item responses on each multiple-item measure for each lab separately using available data.
 We calculated both Cronbach’s Alpha, as well as its standard error using formulas 2 & 3 from Duhachek and Lacobucci @duhachekAlphasStandardError2004a.
 We used these values to conduct a meta-analysis of the measure’s reliability, also referred to as a Reliability Generalization (RG) Meta-Analysis [@botellaManagingHeterogeneityVariance2012; @lopez-ibanezReliabilityGeneralizationMetaanalysis2024; @vacha-haaseReliabilityGeneralizationExploring1998].
-We performed the RG Meta-Analysis using the rma function from the metafor R package [*v`r getNamespaceVersion("metafor")[[1]]`*; @R-metafor] and default settings.
+We performed the RG Meta-Analysis using the *rma* function from the *metafor* R package (*v`r getNamespaceVersion("metafor")[[1]]`*; @R-metafor) and default settings.
 We then used the results from the meta-analysis to evaluate the heterogeneity via the tau statistic and the Cochran’s Q-test [@cochranCombinationEstimatesDifferent1954].
-These indicators have received criticism as indicators of heterogeneity, especially when within study sample sizes are small and power to detect heterogeneity is low [@hoaglinMisunderstandingsCochransTest2016; @pereiraCriticalInterpretationCochrans2010].
-Therefore, we also present the 95% prediction interval (the interval within which a the measure’s Cronbach’s Alpha is expected to fall if used again within the same population) and implore that the heterogeneity results should be viewed critically [@borensteinAvoidingCommonMistakes2024].
+we note that these indicators have low power to detect heterogeneity when within study sample sizes are small [@hoaglinMisunderstandingsCochransTest2016; @pereiraCriticalInterpretationCochrans2010].
+Therefore, we also present the 95% prediction interval (the interval within which the measure’s Cronbach’s Alpha is expected to fall if used again within the same population) and implore that the heterogeneity results should be viewed critically [@borensteinAvoidingCommonMistakes2024].
 We implemented no correction for publication bias, because the Many Labs replications were guaranteed to be published regardless of their outcomes.
 
-Our analyses will focus on Cronbach’s Alpha, because it is the most commonly reported reliability indicator, which also allows us to make comparisons between calculated and reported reliabilities.
-Furthermore, we were able to calculate the standard error of alpha to be used in the RG meta-analysis.
-However, Cronbach’s Alpha comes with strong assumptions on the underlying factor structure, including that the measure is unidimensional, which means that there should a single factor underlying the measurement scores.
+Our analyses will focus on Cronbach’s Alpha, because it is the most reported reliability indicator,allowing a comparison between originally reported and newly calculated reliabilities.
+Furthermore, the standard errors of Alpha caused in the RG meta-analysis to study variation in reliabilities across labs using the same measures.
+However, Cronbach’s Alpha comes with strong assumptions on the underlying factor structure, including unidimensionality of the underlying factor structure.
 Therefore, we also estimated McDonald’s Omega for each lab from the same set of replications as for Cronbach’s Alpha, since it has been argued to be a more informative measure of reliability than Cronbach’s Alpha with less strict assumptions [@crutzenScaleQualityAlpha2017b; @dengTestingDifferenceReliability2017].
@@
 
-All measurement items for which we checked unidimensionality were used to form a singular index of one latent variable in their respective replications.
+The replicators formed a singular index of one latent variable for all measures for which we checked unidimensionality.
 Therefore, unidimensionality presents a valuable indication of the construct validity of a measure in our dataset.
@@
 
-These unidimensionality checks are not intended as a complete validation of the measures in our sample.
-That would require additional steps that are beyond the scope of this study.
+These unidimensionality checks are not intended as a complete validation procedure of the measures in our sample.
+That would require an extended research process that is beyond the scope of this study.
 Instead, the unidimensionality is checked as a prerequisite for validity.
-Practically speaking this means that if we observe a lack of unidimensional fit for our measures, then we have reason to question their validity.
-On the other hand, if we observe good undimensional fit, then based on this preliminary evidence we conclude that we do not observe an issue with this prerequisite for validity.
-We also evaluated the variation in the unidimensionality indices across labs, to observe how consistently measures showed undimensional fit, or if this varried considerably across context.
+Practically speaking a lack of unidimensional fit in one of the measures corresponds to the conclusion that a prerequisite for construct validity has been violated.
+On the other hand, if we observe good unidimensional fit, then based on this preliminary evidence we conclude that we do not yet observe an issue with validity.
+We also include the variation in the unidimensionality indices across labs in our evaluation, to determine if measures meeting the unidimensionality requirement is consistent across contexts or not.
 
@@
 
-Table \@ref(tab:QMPTable) lists the prevalence of different measurement reporting practices in original and replication studies.
+We coded `r nrow(coded_data_original)` measures used across the original and replication studies.
+Table \@ref(tab:QMPTable) lists the prevalence of different transparent measurement reporting practices in original and replication studies.
 Specifically, we calculated the proportion of measures that transparently reported on the item compared to the total number of measures to which the item was applicable.
-A higher proportion indicates more transparent measurement reporting.
 
@@
 # create informative Measurement Practice Labels 
-MPractice <- c("Reliability is reported", "It is clear if the measure existed or is newly created",    "Exact version of the measure is specified", "Validity evidence from a factor analysis is presented",   "Measured variable is defined", "Choice of measure selection or creation is justified",    "Implemented operationalisation is justified", "Source of the measure is provided",    "Psychometric evidence from the study is given", "Psychometric evidence from an earlier study is given",    "Administration format and environment are described", "Administration procedure is described",   "N items are described", "N response options are described", "Recoding of responses is described", "Creation of the index is described", "Text or supplement has example items", "Administration format changes are mentioned",    "Administration format changes are justified/validated", "Translations are mentioned",    "Translated measures are justified/validated", "Changes in N items or response options are mentioned",    "Changes in N items or response options are justified/validated")
+MPractice <- c("Reliability is reported", "Clear if the measure is newly created or not",    "Exact version of the measure is specified", "Factor analytical results are presented",   "Measured variable is defined", "Measure selection or creation is justified",    "Implemented operationalisation is justified", "Source of the measure is provided",    "Psychometric evidence from the study is given", "Pre-existing psychometric evidence is given",    "Administration format and place are described", "Administration procedure is described",   "Number of items is described", "Number of response options is described", "Recoding of responses is described", "Creation of the index is described", "Text or supplement has example items", "Administration format changes are mentioned",    "Administration format changes are justified", "Translations are mentioned",    "Translated measures are justified", "Change in N items/response options mentioned",    "Change in N items/response options are justified")
 
 # construct the QMP table to be printed 
-QMP_table <- data.frame("Item" = MPractice, 
+QMP_table <- data.frame("Categories" = NA,
+                        "Criterion" = MPractice, 
                         "Original" = paste0(format(round(1 - qmp_ratio_data$QMP_percentage_original, digits = 2), nsmall = 2), " (", qmp_ratio_data$N_applicable_original, ")"), 
@@
 
-QMP_table_formatted <- rbind(rbind(rbind(rbind(rbind(c("Definition", "", ""), QMP_table[5,]),
-                                               c("Operationalisation", "", ""), QMP_table[c(3, 11, 12, 7, 17),]),
-                                         c("Selection/Creation", "", ""), QMP_table[c(2, 6, 8, 9, 10, 1, 4),]),
-                                   c("Quantification", "", ""), QMP_table[c(13, 14, 15, 16),]),
-                             c("Modification", "", ""), QMP_table[18:23,])
+QMP_table_formatted <- QMP_table[c(5, 3, 11, 12, 7, 17, 2, 6, 8, 9, 10, 1, 4, 13, 14, 15, 16, 18:23),]
+
+QMP_table_formatted$Categories <- c("Definition", rep("Operationalisation", 5), rep("Selection/Creation", 7), rep("Quantification", 4), rep("Modification", 6))
 
 # set the zero N Items to "- (0)"
-QMP_table_formatted[23, 2] <- "- (0)"
-QMP_table_formatted[24, 2] <- "- (0)"
+QMP_table_formatted[18, 3] <- "- (0)"
+QMP_table_formatted[19, 3] <- "- (0)"
 
 # print the table in apa formatting 
-apa_table(QMP_table_formatted, align = c("l", "r", "r"), 
-          caption = "Proportion of measures that met each of the item criteria, for both original and replication studies.
-Proportions are calculated based on the total number of measures to which an item was applicable (in brackets).",
-          note = "The first number in both Original and Replication is the ratio of measures for which that reporting practice contained sufficient information.
-The number between brackets indicates the number of measures for which the practice was applicable.", escape = FALSE, placement = "htp", booktabs = TRUE)
+apa_table(QMP_table_formatted, align = c("l", "l", "r", "r"), 
+          caption = "Proportion of measures that met each of the criteria, for both original and replication studies.
+Proportions are calculated based on the total number of measures to which an item was applicable (in brackets).", escape = FALSE, placement = "htp", booktabs = TRUE)
+
 ```
@@
 ```{r ReuseCompleteInfoPercent}
-reuse_complete_percent_original <- round((sum((coded_data_original$op_1_REV | is.na(coded_data_original$op_1_REV)) & (coded_data_original$op_2_REV | is.na(coded_data_original$op_2_REV)) & (coded_data_original$op_3 | is.na(coded_data_original$op_3)) & (coded_data_original$op_4 | is.na(coded_data_original$op_4)) & (coded_data_original$op_5_REV | is.na(coded_data_original$op_5_REV)) & coded_data_original$sel_existing != "Not Clearly Stated" & (coded_data_original$sel_1_REV | is.na(coded_data_original$sel_1_REV)) & (coded_data_original$quant_1_REV | is.na(coded_data_original$quant_1_REV)) & (coded_data_original$quant_2_REV | is.na(coded_data_original$quant_2_REV)) & (coded_data_original$quant_3_REV | is.na(coded_data_original$quant_3_REV)) & (coded_data_original$quant_4 | is.na(coded_data_original$quant_4))) / nrow(coded_data_original)) * 100, 1)
-
-reuse_complete_percent_replication <- round((sum((coded_data_replications$op_1_REV | is.na(coded_data_replications$op_1_REV)) & (coded_data_replications$op_2_REV | is.na(coded_data_replications$op_2_REV)) & (coded_data_replications$op_3 | is.na(coded_data_replications$op_3)) & (coded_data_replications$op_4 | is.na(coded_data_replications$op_4)) & (coded_data_replications$op_5_REV | is.na(coded_data_replications$op_5_REV)) & coded_data_replications$sel_existing != "Not Clearly Stated" & (coded_data_replications$sel_1_REV | is.na(coded_data_replications$sel_1_REV)) & (coded_data_replications$quant_1_REV | is.na(coded_data_replications$quant_1_REV)) & (coded_data_replications$quant_2_REV | is.na(coded_data_replications$quant_2_REV)) & (coded_data_replications$quant_3_REV | is.na(coded_data_replications$quant_3_REV)) & (coded_data_replications$quant_4 | is.na(coded_data_replications$quant_4))) / nrow(coded_data_replications)) * 100, 1)
+reuse_complete_percent_original <- sprintf("%.1f", (sum((coded_data_original$op_1_REV | is.na(coded_data_original$op_1_REV)) & (coded_data_original$op_2_REV | is.na(coded_data_original$op_2_REV)) & (coded_data_original$op_3 | is.na(coded_data_original$op_3)) & (coded_data_original$op_4 | is.na(coded_data_original$op_4)) & (coded_data_original$op_5_REV | is.na(coded_data_original$op_5_REV)) & coded_data_original$sel_existing != "Not Clearly Stated" & (coded_data_original$sel_1_REV | is.na(coded_data_original$sel_1_REV)) & (coded_data_original$quant_1_REV | is.na(coded_data_original$quant_1_REV)) & (coded_data_original$quant_2_REV | is.na(coded_data_original$quant_2_REV)) & (coded_data_original$quant_3_REV | is.na(coded_data_original$quant_3_REV)) & (coded_data_original$quant_4 | is.na(coded_data_original$quant_4))) / nrow(coded_data_original)) * 100)
+
+reuse_complete_percent_replication <- sprintf("%.1f", (sum((coded_data_replications$op_1_REV | is.na(coded_data_replications$op_1_REV)) & (coded_data_replications$op_2_REV | is.na(coded_data_replications$op_2_REV)) & (coded_data_replications$op_3 | is.na(coded_data_replications$op_3)) & (coded_data_replications$op_4 | is.na(coded_data_replications$op_4)) & (coded_data_replications$op_5_REV | is.na(coded_data_replications$op_5_REV)) & coded_data_replications$sel_existing != "Not Clearly Stated" & (coded_data_replications$sel_1_REV | is.na(coded_data_replications$sel_1_REV)) & (coded_data_replications$quant_1_REV | is.na(coded_data_replications$quant_1_REV)) & (coded_data_replications$quant_2_REV | is.na(coded_data_replications$quant_2_REV)) & (coded_data_replications$quant_3_REV | is.na(coded_data_replications$quant_3_REV)) & (coded_data_replications$quant_4 | is.na(coded_data_replications$quant_4))) / nrow(coded_data_replications)) * 100)
 ```
@@
 For the description of the results, we highlight the reporting practices most relevant for reusing the measure in future research, as well as the modification reporting practices to understand the relation between original and replication studies.
-It was not always clear which measures were used  (`r round(sum(coded_data_original$sel_existing == "Not Clearly Stated") / nrow(coded_data_original) * 100, 1)`% original; `r round(sum(coded_data_replications$sel_existing == "Not Clearly Stated") / nrow(coded_data_replications) * 100, 1)`% replication), which also implies that in these cases we could not be sure that the same measure was used in original and replication studies.
-While the number of items (`r round((1 - qmp_ratio_data$QMP_percentage_original[13]) * 100, 1)`% original (n = `r qmp_ratio_data$N_applicable_original[13]`); `r round((1 - qmp_ratio_data$QMP_percentage_replication[13]) * 100, 1)`% replications (n = `r qmp_ratio_data$N_applicable_replication[13]`)) and response options (`r round((1 - qmp_ratio_data$QMP_percentage_original[14]) * 100, 1)`% original (n = `r qmp_ratio_data$N_applicable_original[14]`); `r round((1 - qmp_ratio_data$QMP_percentage_replication[14]) * 100, 1)`% replications (n = `r qmp_ratio_data$N_applicable_replication[14]`)) were usually reported, even these were not always clear.
-How the responses should be recoded if at all (`r round((1 - qmp_ratio_data$QMP_percentage_original[15]) * 100, 1)`% original (n = `r qmp_ratio_data$N_applicable_original[15]`); `r round((1 - qmp_ratio_data$QMP_percentage_replication[15]) * 100, 1)`% replication (n = `r qmp_ratio_data$N_applicable_replication[15]`)), and how an index was created from the items (`r round((1 - qmp_ratio_data$QMP_percentage_original[16]) * 100, 1)`% original (n = `r qmp_ratio_data$N_applicable_original[16]`); `r round((1 - qmp_ratio_data$QMP_percentage_replication[16]) * 100, 1)`% replication (n = `r qmp_ratio_data$N_applicable_replication[16]`)) was clear a lot less.
-The operationalisation of the measure was usually reported clearly in the replication studies (format: `r round((1 - qmp_ratio_data$QMP_percentage_replication[11]) * 100, 1)`, procedure: `r round((1 - qmp_ratio_data$QMP_percentage_replication[12]) * 100, 1)`, justification: `r round((1 - qmp_ratio_data$QMP_percentage_replication[7]) * 100, 1)`, example items: `r round((1 - qmp_ratio_data$QMP_percentage_replication[17]) * 100, 1)`), but less so in original studies (format: `r round((1 - qmp_ratio_data$QMP_percentage_original[11]) * 100, 1)`, procedure: `r round((1 - qmp_ratio_data$QMP_percentage_original[12]) * 100, 1)`, justification: `r round((1 - qmp_ratio_data$QMP_percentage_original[7]) * 100, 1)`, example items: `r round((1 - qmp_ratio_data$QMP_percentage_original[17]) * 100, 1)`).
-If we look across all of the items mentioned above, the measures for which all applicable items were clearly reported on was `r reuse_complete_percent_original`% of all measures in original studies and `r reuse_complete_percent_replication`% in replications.
-
-Modifications to the number of items compared to preceding research were rare but did occur for `r round((qmp_ratio_data$QMP_percentage_original[22]) * 100, 1)`% of measures in original studies (n = `r qmp_ratio_data$N_applicable_original[22]`) and `r round((1 - qmp_ratio_data$QMP_percentage_replication[22]) * 100, 1)`% for replications (n = `r qmp_ratio_data$N_applicable_replication[22]`)).
-Furthermore, similar to the findings of Flake et al @flakeConstructValidityValidity2022 (original: 92%; replication 85.6%), most studies reported the number of items for their measures (original: `r round((1 - qmp_ratio_data$QMP_percentage_original[13]) * 100, 1)`%; replications: `r round((1 - qmp_ratio_data$QMP_percentage_replication[13]) * 100, 1)`%).
-The total proportion of measures for which the number of items was changed from original to replication was also similar (`r round(sum(!is.na(coded_data_replications$mod_5_REV)) / nrow(coded_data_replications) * 100, 1)`)% to Flake et al @flakeConstructValidityValidity2022 (16%).
-In general, it was uncommon for measures in original studies to have been modified.
-In replication studies, we noted that not all modifications were validated or justified (language: `r round((1 - qmp_ratio_data$QMP_percentage_replication[21]) * 100, 1)`% (n = `r qmp_ratio_data$N_applicable_replication[21]`); administration format: `r round((1 - qmp_ratio_data$QMP_percentage_replication[19]) * 100, 1)`% (n = `r qmp_ratio_data$N_applicable_replication[19]`)), especially for changes in items and response options, the modification was validated or justified for only a little more than half of the measures (`r round((1 - qmp_ratio_data$QMP_percentage_replication[23]) * 100, 1)`% (n = `r qmp_ratio_data$N_applicable_replication[23]`)).
-In general, we observed that measurement was modified in some way from original to replication for `r round((sum(coded_data_replications$mod_check == "True") / nrow(coded_data_replications)) * 100, 1)`% of measures, and it was unclear whether modification occurred for `r round((sum(coded_data_replications$mod_check == "None Reported") / nrow(coded_data_replications)) * 100, 1)`%.
+It was not always clear if the measure already existed or not (`r sprintf("%.0f", (1 - qmp_ratio_data$QMP_percentage_original[qmp_ratio_data$Practice == "select_or_create_clarity"]) * 100)`% original (N = `r qmp_ratio_data$N_applicable_original[qmp_ratio_data$Practice == "select_or_create_clarity"]`); `r sprintf("%.0f", (1 - qmp_ratio_data$QMP_percentage_replication[qmp_ratio_data$Practice == "select_or_create_clarity"]) * 100)`% replication (N = `r qmp_ratio_data$N_applicable_replication[qmp_ratio_data$Practice == "select_or_create_clarity"]`)), which also implies that in these cases we were unsure whether the same measure was used in original and replication studies.
+While the number of items (`r sprintf("%.0f", (1 - qmp_ratio_data$QMP_percentage_original[13]) * 100)`% original (N = `r qmp_ratio_data$N_applicable_original[13]`); `r sprintf("%.0f", (1 - qmp_ratio_data$QMP_percentage_replication[13]) * 100)`% replications (N = `r qmp_ratio_data$N_applicable_replication[13]`)) and response options (`r sprintf("%.0f", (1 - qmp_ratio_data$QMP_percentage_original[14]) * 100)`% original (N = `r qmp_ratio_data$N_applicable_original[14]`); `r sprintf("%.0f", (1 - qmp_ratio_data$QMP_percentage_replication[14]) * 100)`% replications (N = `r qmp_ratio_data$N_applicable_replication[14]`)) were usually reported, even such basic aspects were not always clearly reported.
+How the responses should be recoded if at all (`r sprintf("%.0f", (1 - qmp_ratio_data$QMP_percentage_original[15]) * 100)`% original (N = `r qmp_ratio_data$N_applicable_original[15]`); `r sprintf("%.0f", (1 - qmp_ratio_data$QMP_percentage_replication[15]) * 100)`% replication (N = `r qmp_ratio_data$N_applicable_replication[15]`)), and how an index was created from the items (`r sprintf("%.0f", (1 - qmp_ratio_data$QMP_percentage_original[16]) * 100)`% original (N = `r qmp_ratio_data$N_applicable_original[16]`); `r sprintf("%.0f", (1 - qmp_ratio_data$QMP_percentage_replication[16]) * 100)`% replication (N = `r qmp_ratio_data$N_applicable_replication[16]`)) was also often unclear.
+The operationalisation of the measure was usually reported clearly in the replication studies (format: `r sprintf("%.0f", (1 - qmp_ratio_data$QMP_percentage_replication[11]) * 100)`%, procedure: `r sprintf("%.0f", (1 - qmp_ratio_data$QMP_percentage_replication[12]) * 100)`%, justification: `r sprintf("%.0f", (1 - qmp_ratio_data$QMP_percentage_replication[7]) * 100)`%, example items: `r sprintf("%.0f", (1 - qmp_ratio_data$QMP_percentage_replication[17]) * 100)`%), but less so in original studies (format: `r sprintf("%.0f", (1 - qmp_ratio_data$QMP_percentage_original[11]) * 100)`%, procedure: `r sprintf("%.0f", (1 - qmp_ratio_data$QMP_percentage_original[12]) * 100)`%, justification: `r sprintf("%.0f", (1 - qmp_ratio_data$QMP_percentage_original[7]) * 100)`%, example items: `r sprintf("%.0f", (1 - qmp_ratio_data$QMP_percentage_original[17]) * 100)`%).
+The measures for which all criteria relevant for reuse were clearly reported on was `r reuse_complete_percent_original`% of all measures in original studies and `r reuse_complete_percent_replication`% in replications.
+
+We observed that measurement was modified in some way for `r sprintf("%.0f", (sum(coded_data_original$mod_check == "True") / nrow(coded_data_original)) * 100)`% of measures in original studies.
+Modifications were more common from original to replication `r sprintf("%.1f", (sum(coded_data_replications$mod_check == "True") / nrow(coded_data_replications)) * 100)`%.
+A justification that the modification did not cause issues for validity for all modified measures in original studies and `r sprintf("%.0f", (sum(coded_data_replications$mod_2_REV, na.rm = TRUE) + sum(coded_data_replications$mod_4_REV, na.rm = TRUE) + sum(coded_data_replications$mod_6_REV, na.rm = TRUE)) / (sum(!is.na(coded_data_replications$mod_2_REV)) + sum(!is.na(coded_data_replications$mod_4_REV)) + sum(!is.na(coded_data_replications$mod_6_REV))) * 100)`% in replications for instances were modifications occurred.
 
@@
 Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts a flowchart of measure types and reliability reporting in original and replication studies.
-First, of the total of 77 measures, it shows that almost half of the measures in both replication (N = `r sum(coded_data_replications$N_items == "1 item measure")`) and original research (N = `r sum(coded_data_original$N_items == "1 item measure")`) were single-item measures.
-Second, for only `r apa_num(sum(coded_data_original$reliability_type != "Not Reported" & coded_data_original$reliability_type != ""), numerals = FALSE)` measures out of `r sum(coded_data_original$N_items == "multiple item measure")` (`r round((sum(coded_data_original$reliability_type != "Not Reported" & coded_data_original$reliability_type != "") / sum(coded_data_original$N_items == "multiple item measure")) * 100, 1)` %) multi-item scales in original and `r apa_num(sum(coded_data_replications$reliability_type != "Not Reported" & coded_data_replications$reliability_type != ""), numerals = FALSE)` out of `r sum(coded_data_replications$N_items == "multiple item measure")` (`r round((sum(coded_data_replications$reliability_type != "Not Reported" & coded_data_replications$reliability_type != "") / sum(coded_data_replications$N_items == "multiple item measure")) * 100, 1)`%) in replications, a reliability indicator was reported.
-Flake et al @flakeConstructValidityValidity2022 observed a much higher degree of reliability coefficient reporting in both original (60.8%) and replications (37.1%).
-However, similarly to Flake et al @flakeConstructValidityValidity2022, we observed that reliability reporting was more common in original studies as compared to replication studies, and that Cronbach’s Alpha was the most commonly reported reliability indicator in our sample as well.
+First, it shows that almost half of the measures in both original (N = `r paste0(sum(coded_data_original$N_items == "1 item measure"), "/", nrow(coded_data_original))`) and replication research (N = `r paste0(sum(coded_data_replications$N_items == "1 item measure"), "/", nrow(coded_data_replications))`) were single-item measures.
+Second, reliability indicators were reported for multiple-item measures in only `r sum(coded_data_original$reliability_type != "Not Reported" & coded_data_original$reliability_type != "")` out of `r sum(coded_data_original$N_items == "multiple item measure")`  (`r sprintf("%.1f", (sum(coded_data_original$reliability_type != "Not Reported" & coded_data_original$reliability_type != "") / sum(coded_data_original$N_items == "multiple item measure")) * 100)` %) original studies and `r sum(coded_data_replications$reliability_type != "Not Reported" & coded_data_replications$reliability_type != "")` out of `r sum(coded_data_replications$N_items == "multiple item measure")` (`r sprintf("%.1f", (sum(coded_data_replications$reliability_type != "Not Reported" & coded_data_replications$reliability_type != "") / sum(coded_data_replications$N_items == "multiple item measure")) * 100)`%) replications, which was appreciably lower than found in Flake et al.
+[@flakeConstructValidityValidity2022].
+on reliability coefficient reporting in both original studies (60.8%) and replications (37.1%).
+However, similarly to Flake et al.
+@flakeConstructValidityValidity2022, we observed that reliability reporting was more common in original studies as compared to replication studies, and that Cronbach’s Alpha was the most commonly reported reliability indicator in our sample as well.
 
@@
 For validity evidence the pattern was similar.
-Psychometric validity evidence was reported for only, `r apa_num(sum(coded_data_original$sel_psychometric_evidence_REV != "None" & coded_data_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_original$sel_3_REV == TRUE, na.rm = TRUE), numerals = FALSE)` (`r round((sum(coded_data_original$sel_psychometric_evidence_REV != "None" & coded_data_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_original$sel_3_REV == TRUE, na.rm = TRUE) / sum(coded_data_original$N_items == "multiple item measure")) * 100, 1)`%) multiple item measures in original studies and `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_replications$sel_3_REV == TRUE, na.rm = TRUE), numerals = FALSE)` (`r round((sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_replications$sel_3_REV == TRUE, na.rm = TRUE) / sum(coded_data_replications$N_items == "multiple item measure")) * 100, 1)`%) in replications.
-These proportions align with the results from Flake et al @flakeConstructValidityValidity2022 for both original (9.3%) and replication studies (6.2%), and again, similar to Flake et al @flakeConstructValidityValidity2022 we observe that validity evidence is also more commonly reported in original compared to replication studies.
-Exploratory factor analyses (original: `r apa_num(sum(coded_data_original$sel_psychometric_evidence_REV == "Exploratory Factor Analysis"), numerals = FALSE)`, replications: `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV == "Exploratory Factor Analysis"), numerals = FALSE, zero_string = "zero")`) and convergent validity evidence (original: `r apa_num(sum(coded_data_original$sel_psychometric_evidence_text_REV == "convergent validity"), numerals = FALSE)`, replications: `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_text_REV == "convergent validity"), numerals = FALSE)`) --- in which a measure is correlated to a measure of a theoretically related construct --- were the most commonly reported validity indicators.
-`r apa_num(sum(coded_data_original$sel_4 == TRUE, na.rm = TRUE), numerals = FALSE)` original studies and `r apa_num(sum(coded_data_replications$sel_4 == TRUE, na.rm = TRUE), numerals = FALSE)` replications reported psychometric validity evidence from previous studies.
+Validity evidence was reported for only, `r apa_num(sum(coded_data_original$sel_psychometric_evidence_REV != "None" & coded_data_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_original$sel_3_REV == TRUE, na.rm = TRUE), numerals = FALSE)` (`r sprintf("%.1f", (sum(coded_data_original$sel_psychometric_evidence_REV != "None" & coded_data_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_original$sel_3_REV == TRUE, na.rm = TRUE) / sum(coded_data_original$N_items == "multiple item measure")) * 100)`%) multiple item measures in original studies and `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_replications$sel_3_REV == TRUE, na.rm = TRUE), numerals = FALSE)` (`r sprintf("%.1f", (sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_replications$sel_3_REV == TRUE, na.rm = TRUE) / sum(coded_data_replications$N_items == "multiple item measure")) * 100)`%) in replications.
+These proportions are slightly larger than found by Flake et al.
+@flakeConstructValidityValidity2022 for both original (9.3%) and replication studies (6.2%).
+The reported psychometric indicators we could identify were `r apa_num(sum(coded_data_original$sel_psychometric_evidence_REV == "Exploratory Factor Analysis"), numerals = FALSE)` exploratory factor analyses in the original, and `r apa_num(sum(coded_data_original$sel_psychometric_evidence_text_REV == "convergent validity" | coded_data_original$sel_psychometric_evidence_text_REV == "convergent validitiy"), numerals = FALSE)` pieces of convergent validity evidence in original studies and `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_text_REV == "convergent validity" | coded_data_replications$sel_psychometric_evidence_text_REV == "convergent validitiy"), numerals = FALSE)` in replications.
+Psychometric validity evidence in terms of convergent, discriminant, predictive, or factorial evidence from previous studies was reported for `r apa_num(sum(coded_data_original$sel_4 == TRUE, na.rm = TRUE), numerals = FALSE)` original studies and `r apa_num(sum(coded_data_replications$sel_4 == TRUE, na.rm = TRUE), numerals = FALSE)` replications.
 For single-item measures, validity evidence was reported in `r apa_num(sum(coded_data_original$sel_psychometric_evidence_text_REV[coded_data_original$N_items == "1 item measure"] != ""), numerals = FALSE, zero_string = "none")` of the original studies, and only `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_text_REV[coded_data_replications$N_items == "1 item measure"] != ""), numerals = FALSE)` replication protocols (in both cases evidence of convergent validity).
@@
 
-We could calculate Cronbach’s Alpha for `r length(levels(calculated_reliability_lab_data$g))` measures across on average `r apa_num(mean(table(calculated_reliability_lab_data$g)))` labs, for which the required raw data was provided.
+We could calculate Cronbach’s Alpha for `r length(levels(calculated_reliability_lab_data$g))` measures across on average `r sprintf("%.1f", mean(table(calculated_reliability_lab_data$g)))` labs, for which the required raw data were available online.
 The average Cronbach’s Alpha coefficient across measures was `r apa_num(mean(measure_reliability_data$alpha))` with a standard deviation of `r apa_num(sd(measure_reliability_data$alpha))`.
-Figure \@ref(fig:PlotAlphaDistributions) displays the distributions of the calculated Cronbach’s Alpha scores from each lab for each measure, separated by successful and unsuccessful replication, based on the meta-analytic p-value (alpha = .05) retrieved from the Many Labs reports.
+Figure \@ref(fig:PlotAlphaDistributions) displays the distributions of the calculated Cronbach’s Alpha scores from each lab for each measure, separated by successful and unsuccessful replication, based on the meta-analytic p-value (nominal Alpha = .05) for the global replication effect size estimate retrieved from the Many Labs reports.
 
@@
 The Tau column besides the figure shows the tau heterogeneity estimate based on a meta-analysis of the calculated reliabilities for each measure.
-Meta-analyses for which the Q-test for heterogeneity was significant at alpha = .05 are marked by a *.
+Meta-analyses for which the Q-test for heterogeneity was significant at alpha = .05 are marked by a $*$.
 The Diff column shows the difference between reported reliability and the average reliability calculated from the Many Labs data for the applicable measures.
-The reported reliabilities that fell outside the 95% quantile of calculated reliability scores are marked by a *."}
+The reported reliabilities that fell outside the 95% quantile of calculated reliability scores are marked by a $*$."}
 
@@
   # adding in the difference in alpha coefficients
-  geom_text(data = measure_reliability_data[c(1:8, 18),], label = ifelse(measure_reliability_data$significance_reported_coefficient[c(1:8, 18)], paste0(format(measure_reliability_data$coefficient_difference[c(1:8, 18)], digits = 2), "*"), paste0(format(measure_reliability_data$coefficient_difference[c(1:8, 18)], digits = 2), " ")), x = 1.35, y = measure_reliability_data[!is.na(measure_reliability_data$coefficient_difference),]$graph_index, size = 2.8) +
+  geom_text(data = measure_reliability_data[c(1:8, 18),], label = ifelse(measure_reliability_data$significance_reported_coefficient[c(1:8, 18)], paste0(format(measure_reliability_data$coefficient_difference[c(1:8, 18)], digits = 2), "*"), paste0(format(measure_reliability_data$coefficient_difference[c(1:8, 18)], digits = 2), " ")), x = 1.38, y = measure_reliability_data[!is.na(measure_reliability_data$coefficient_difference),]$graph_index, size = 2.8) +
 
@@
   annotation_custom(grob = textGrob(label = "Replicated", hjust = 0, gp = gpar(fontsize = 10)), ymin = 6, ymax = 6, xmin = 0.01, xmax = 0.01) +
-  annotation_custom(grob = textGrob(label = "N", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.08, xmax = 1.1) +
-  annotation_custom(grob = textGrob(label = "Tau", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.24, xmax = 1.1) +
-  annotation_custom(grob = textGrob(label = "Diff", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.37, xmax = 1.24) +
+  annotation_custom(grob = textGrob(label = "N", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.08, xmax = 1.08) +
+  annotation_custom(grob = textGrob(label = "Tau", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.16, xmax = 1.16) +
+  annotation_custom(grob = textGrob(label = "Diff", hjust = 0, gp = gpar(fontsize = 12)), ymin = 20.2, ymax = 20.2, xmin = 1.32, xmax = 1.32) +
 
@@
 
-We found statistically significant indication of heterogeneity in Cronbach’s Alpha for `r apa_num(sum(measure_reliability_data$QEp < .05), numerals = FALSE)` of the `r apa_num(nrow(measure_reliability_data), numerals = FALSE)` measures.
+We found statistically significant indication of heterogeneity across labs in Cronbach’s Alpha for `r sum(measure_reliability_data$QEp < .05)` of the `r nrow(measure_reliability_data)` measures.
 However, as noted earlier, a more accurate indication of the heterogeneity can be observed in the prediction intervals.
 The prediction intervals generally show larger indications of heterogeneity for some of the lower reliability measures and less for higher reliability measures when compared to the Tau test results.
-When comparing reported reliability in the original study when present to the calculated reliability averages, we first of all can see that reported reliabilities were generally lower than the average calculated reliabilities.
-Second, we can observe that reliabilities were reported more often in the original study if the measures had higher average calculated reliabilities (\>.80) in the replications.
+If we compare the reported reliability in the original study to the average calculated reliability in the replications, two things stand out.
+The reported reliabilities were typically lower than the average calculated reliabilities, and in this sample reliabilities were reported more often in the original study if the measures had higher average calculated reliabilities (\>.80) in the replications.
 
@@
 
-Figure \@ref(fig:Plot1FactorRMSEA) shows the result of our unidimensionality test.
-The mean obtained RMSEAs were below the threshold of .08 for `r apa_num(sum(as.numeric(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, mean, na.rm = TRUE)) < .08, na.rm = TRUE), numerals = FALSE)` of the `r apa_num(nrow(unidimensionality_meta_data), numerals = FALSE)` measures (`r apa_num(sum(as.numeric(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, mean, na.rm = TRUE)) < .08, na.rm = TRUE) / nrow(unidimensionality_meta_data) * 100)`%).
-Furthermore, the RMSEA shows considerable variation within measures, with the standard deviation ranging from `r apa_num(min(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))` to `r apa_num(max(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))` (mean SD = `r apa_num(mean(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))`).
-
-The parallel analysis results similarly showed inconsistency both across and within measures.
-While `r apa_num((sum(unidimensionality_graph_data$N_factors_capped == "1", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% of labs returned a single factor solution, `r apa_num((sum(unidimensionality_graph_data$N_factors_capped == "2", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% returned a two-factor, and `r apa_num((sum(unidimensionality_graph_data$N_factors_capped == "3+", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% returned three or more factors.
-The remainder did not converge.
+Figure \@ref(fig:Plot1FactorRMSEA) shows the result of our unidimensionality tests of `r nrow(unidimensionality_meta_data)` measures.
+The mean obtained RMSEAs were below the threshold of .08 for `r sum(as.numeric(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, mean, na.rm = TRUE)) < .08, na.rm = TRUE)` of these measures (`r sprintf("%.1f", sum(as.numeric(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, mean, na.rm = TRUE)) < .08, na.rm = TRUE) / nrow(unidimensionality_meta_data) * 100)`%).
+Furthermore, the RMSEA shows considerable variation across labs, with the standard deviation ranging from `r apa_num(min(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))` to `r apa_num(max(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))` (mean SD = `r apa_num(mean(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE)[!is.na(tapply(unidimensionality_graph_data$RMSEA, unidimensionality_graph_data$g, sd, na.rm = TRUE))]))`).
+
+The parallel analysis results showed inconsistency both across labs.
+While `r sprintf("%.1f", (sum(unidimensionality_graph_data$N_factors_capped == "1", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% of labs returned a single factor solution, `r sprintf("%.1f", (sum(unidimensionality_graph_data$N_factors_capped == "2", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% returned a two-factor, and `r sprintf("%.1f", (sum(unidimensionality_graph_data$N_factors_capped == "3+", na.rm = TRUE) / nrow(unidimensionality_graph_data)) * 100)`% returned three or more factors.
+The remaining analyses did not converge.
 The lack of convergence was also an issue for the CFA used for the RMSEA check.
-The CFA failed to converge for `r apa_num((sum(is.na(unidimensionality_graph_data$RMSEA)) / nrow(unidimensionality_graph_data)) * 100)`% of labs.
+The CFA failed to converge for `r sprintf("%.1f", sum(is.na(unidimensionality_graph_data$RMSEA)) / nrow(unidimensionality_graph_data) * 100)`% of labs.
 In most cases, the convergence problems were the result of either the severe misfit of our factor models or a lack of sample size to stably estimate these models.
@@
 In total, the factor analyses converged for eighteen measures.
-For `r apa_num(sum((unidimensionality_meta_data$p_count[1:18] / unidimensionality_meta_data$converged_count[1:18]) >= .75), numerals = FALSE)` of these measures, there was substantive evidence for a one-factor solution (statistical fit in >75% of labs), whereas for `r apa_num(sum((unidimensionality_meta_data$p_count[1:18] / unidimensionality_meta_data$converged_count[1:18]) <= .25), numerals = FALSE)` measures, there was low evidence for a one-factor solution (statistical fit in <25% of labs).
+For `r apa_num(sum((unidimensionality_meta_data$p_count[1:18] / unidimensionality_meta_data$converged_count[1:18]) >= .75), numerals = FALSE)` of these measures, there was substantive evidence for a one-factor solution (statistical fit in >75% of labs), whereas for `r sum((unidimensionality_meta_data$p_count[1:18] / unidimensionality_meta_data$converged_count[1:18]) <= .25)` measures, there was low evidence for a one-factor solution (statistical fit in <25% of labs).
 The evidence for a one-factor solution for the remaining measures was mixed.
@@
 The color of each dot shows the number of factors that were selected for that measure for that lab location based on the parallel analyses.
-Psychometric validity evidence was reported in the original Husnu & Crips (2010) and Shnabel & Nadler (2008) studies.
 * The Conscientiousness measure used in De Fruyt et al.
 (2000) consisted of two items, which are too few items to fit a factor model on.
-Therefore, none of these models converged."}
+The factor analysis results can be ignored for this study."}
 
@@
 Figure \@ref(fig:Plot1FactorSRMRCFI) shows the SRMR, and CFI fit indices for the same single factor model as was used to estimate the RMSEA and exact fit test.
-We found that, the mean SRMR was below .08 for `r apa_num((sum(tapply(unidimensionality_graph_data$SRMR, unidimensionality_graph_data$g, mean, na.rm = TRUE) < .08, na.rm = TRUE)), numerals = FALSE)` measures `r apa_num(sum(tapply(unidimensionality_graph_data$SRMR, unidimensionality_graph_data$g, mean, na.rm = TRUE) < .08, na.rm = TRUE) / length(levels(unidimensionality_graph_data$g)) * 100)`%, while the mean CFI was above .90 for `r apa_num((sum(tapply(unidimensionality_graph_data$CFI, unidimensionality_graph_data$g, mean, na.rm = TRUE) > .90, na.rm = TRUE)), numerals = FALSE)` measures `r apa_num(sum(tapply(unidimensionality_graph_data$CFI, unidimensionality_graph_data$g, mean, na.rm = TRUE) > .90, na.rm = TRUE) / length(levels(unidimensionality_graph_data$g)) * 100)`%.
+We found that, the mean SRMR was below .08 for `r apa_num((sum(tapply(unidimensionality_graph_data$SRMR, unidimensionality_graph_data$g, mean, na.rm = TRUE) < .08, na.rm = TRUE)), numerals = FALSE)` measures `r sprintf("%.1f", sum(tapply(unidimensionality_graph_data$SRMR, unidimensionality_graph_data$g, mean, na.rm = TRUE) < .08, na.rm = TRUE) / length(levels(unidimensionality_graph_data$g)) * 100)`%, while the mean CFI was above .90 for `r apa_num((sum(tapply(unidimensionality_graph_data$CFI, unidimensionality_graph_data$g, mean, na.rm = TRUE) > .90, na.rm = TRUE)), numerals = FALSE)` measures `r sprintf("%.1f", sum(tapply(unidimensionality_graph_data$CFI, unidimensionality_graph_data$g, mean, na.rm = TRUE) > .90, na.rm = TRUE) / length(levels(unidimensionality_graph_data$g)) * 100)`%.
 The mean standard deviation of the SRMR fit index across measures is `r apa_num(mean(tapply(unidimensionality_graph_data$SRMR, unidimensionality_graph_data$g, sd, na.rm = TRUE), na.rm = TRUE))`.
 For CFI this was `r apa_num(mean(tapply(unidimensionality_graph_data$CFI, unidimensionality_graph_data$g, sd, na.rm = TRUE), na.rm = TRUE))`.
-Overall, compared to the RMSEA, the SRMR and CFI fit indices show a more stable unidimensional fit.
-Especially the SRMR index shows considerably better fit compared to the RMSEA.
-When combining the results from all five unidimensionality checks, we observe that at least one of the five unidimensionality checks was passed for `r round((sum(unidimensionality_graph_data$unidimensional_check_count >= 1, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100, 2)`% of the `r sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))` labs with converged factor models, at least two for `r round((sum(unidimensionality_graph_data$unidimensional_check_count >= 2, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100, 2)`%, at least three for `r round((sum(unidimensionality_graph_data$unidimensional_check_count >= 3, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100, 2)`%, at least four for `r round((sum(unidimensionality_graph_data$unidimensional_check_count >= 4, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100, 2)`%, and all five for `r round((sum(unidimensionality_graph_data$unidimensional_check_count == 5, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100, 2)`%.
-The mean number of unidimensionality check passed was `r round(mean(unidimensionality_graph_data$unidimensional_check_count, na.rm = TRUE), 2)`.
 
@@
 The right figure shows the CFI results, where the red vertical line indicates our .90 CFI cutoff value.
-In both figures the red horizontal line separate the replicated from the non-repicated measures."}
+In both figures the red horizontal line separate the replicated from the non-replicated measures."}
 
@@
 
+Taken together, our factor analytic tests for unidimensionality showed that while almost all measures were unidimensional in at least one of the labs they were used in, very few were consistently unidimensional.
+The severity of non-unidimensionality depends on which check is referenced.
+Based on the RMSEA we would conclude that in most labs the measures were not unidimensional, whereas based on the model fit test we would conclude that in most they were unidimensional.
+Based on the CFI, SRMR, and parallel analysis the proportion of labs where the measure was unidimensional is around half.
+If we compile the results from all five unidimensionality checks, we observe that at least one of the five unidimensionality checks was passed for `r sprintf("%.1f", (sum(unidimensionality_graph_data$unidimensional_check_count >= 1, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100)`% of the `r sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))` labs with converged factor models, at least two for `r sprintf("%.1f", (sum(unidimensionality_graph_data$unidimensional_check_count >= 2, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100)`%, at least three for `r sprintf("%.1f", (sum(unidimensionality_graph_data$unidimensional_check_count >= 3, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100)`%, at least four for `r sprintf("%.1f", (sum(unidimensionality_graph_data$unidimensional_check_count >= 4, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100)`%, and all five for `r sprintf("%.1f", (sum(unidimensionality_graph_data$unidimensional_check_count == 5, na.rm = TRUE) / sum(!is.na(unidimensionality_graph_data$unidimensional_check_count))) * 100)`%.
+The mean number of unidimensionality check passed was `r sprintf("%.2f", mean(unidimensionality_graph_data$unidimensional_check_count, na.rm = TRUE))`.
+
 # Discussion
 
-To assess psychological phenomena we need valid and reliable measurement, but previous research has raised doubts regarding the quality of measurement and its reporting.
-In this study, we extracted measurement reporting information from `r nrow(coded_data_replications)` measures, reported in original and replication studies from the Many Labs projects, and where possible, calculated indices for reliability and construct validity based on item response data.
-We found that reliability and validity evidence was often not reported.
-Additionally, the information relevant for reconstructing the measure in another study was rarely reported in full, especially among original studies.
-Finally, based on the Cronbach's Alpha and Unidimensionality indices we recalculated from the item response data.
-We observed inconsistent support for the reliability and construct validity across labs.
-
-Similar to Flake et al @flakeConstructValidityValidity2022, we observed that many studies lacked the complete information needed to ensure the measurement could be reconstructed fully.
-In original studies, the administration format and procedure for each was not properly described for around a third of the applicable measures.
-The number of items and response options were each unclear for around an eighth of the applicable measures, while how the index was calculated, how the items were recoded and example items were presented for each a little under half of the applicable measures.
-One notable difference compared to Flake et al @flakeConstructValidityValidity2022 is that in our results replications did have more complete and transparent measurement reporting on this information compared to original research.
-We believe that this is in part due to the structured way in which the Many Labs protocols were written up.
-Several Many Labs protocols even contained specific sections to declare any deviations from the original methodology.
-The other reason may be due to the more lenient coding of transparent measurement reporting practices in our revised coding protocol.
-We primarily checked whether each piece of measurement information was reported at all, rather than the actual completeness or depth of that reporting.
-It is therefore possible that even if we coded a practice as being clearly reported, it may not be sufficiently detailed to fully facilitate reuse.
-However, if we coded a practice as unclear then --- given our lenient coding --- we can be fairly certain that that particular reporting practice was reported in insufficient detail.
-Therefore, it is concerning to note that even within our lenient coding scheme many key measurement information could not be traced in the reported information.
-
-In line with existing research, we also found that the majority of the measures in original and replication studies do not report a reliability coefficient nor psychometric validity evidence [@beckmanHowReliableAre2004; @barryValidityReliabilityReporting2014; @flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020; @flakeConstructValidityValidity2022].
-The lack of reliability reporting is in part due to the fact that around half of the measures in original and replication studies were single item measures.
-While it is possible to check the reliability and validity of single item measures, these methods often require multiple measures or studies to allow for cross-validation [@leppinkWeNeedMore2017; @sarstedtSelectingSingleItems2016].
-The additional effort required for this type of cross-validation, as we observed here is rarely taken.
-Still, even among multiple item measures reliability was reported for about one third of the measures in original studies, and only about a tenth in replication studies.
-Psychometric validity evidence was only checked for multiple item measures, and for these was reported even less commonly than reliability.
-Again, reporting was lower in replication studies.
-This could be because replications implicitly defer the responsibility of reporting psychometric validity evidence to the original study.
-However, as we noted before, and as our analyses of the reliability and unidimensionality reiterate, the reliability and validity of a measure varies across contexts.
-It is therefore still important for the reliability and validity to be described for the replications studies too.
-However, because the replication protocols were written before data collection, it makes sense that this information was not reported there.
-Still, we could also not find such information in both the available supplementary materials that we checked and the Many Labs reports.
-
-The fact that the reliability and validity of a measurement was rarely reported is particularly concerning, because our analysis of the item response data revealed that the reliability and the unidimensionality of measures in our sample typically varied considerably across samples.
-While some measures did show consistently high reliability and stable unidimensionality, a similar number showed low average reliability and low unidimensionality.
-Most measures however fell somewhere in between, such that for the same measure reliability and unidimensionality met standards in some of the labs, while they were clearly below par in others.
+Valid and reliable measurement is crucial to robustly study psychological phenomena, but previous research has highlighted common substandard measurement and poor reporting of measures in psychological studies.
+In this study, we extracted measurement reporting information from `r nrow(coded_data_replications)` measures, reported in original and replication studies from the Many Labs projects, and calculated indices for reliability and unidimensionality based on available item response data.
+We found that information needed to reconstruct the measure was rarely fully reported, especially in original studies.
+Additionally, evidence on reliability and validity of measures was often not reported in these sets of impactful publications.
+Finally, recalculated Cronbach’s Alpha and unidimensionality indices showed inconsistent support for reliability and presumed factorial structures of measures across labs.
+Beyond exposing poor reporting of how measurement had taken place, our study of large-scale replication projects highlighted that many measures show varying reliabilities across labs and that many supposedly unidimensional measures fail to meet the requirement of unidimensionality as a core requisite of construct validity.
+
+As in Flake et al.
+[@flakeConstructValidityValidity2022], many studies lacked sufficient information to fully reconstruct the measure.
+In original studies, administration format and procedure was not properly described for about one-third of applicable measures; the number of items and response options were unclear for roughly one-eighth; and details on how an index was calculated, item recoding, and example items were omitted for just under half.
+One notable difference compared to Flake et al.
+[@flakeConstructValidityValidity2022] is that overall replications provided more complete and transparent measurement reporting than original research.
+We believe that this is in part due to the structured format of the Many Labs protocols, which also sometimes included specific sections for declaring deviations from the original methodology.
+
+About two-thirds of the measures in replications were modified in some way.
+Given how common modifications are, it is important to report them explicitly and document reliability and validity in replications.
+While minor differences are inevitable, substantial changes call into question whether these studies can still be considered “direct” replications.
+For example, the conscientiousness measure used for the replication of De Fruyt et al.
+[@defruytCloningersPsychobiologicalModel2000] was reduced from the original NEO-PI-R 48-item measure to a two-item measure in the replication.
+It is highly unlikely that a measure with such a significant change would have a comparable validity and reliability to the original.
+
+Corroborating earlier meta-research [@beckmanHowReliableAre2004; @barryValidityReliabilityReporting2014; @flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020; @flakeConstructValidityValidity2022], we found that most measures were used in original and replication studies without reporting a reliability coefficient or validity evidence in the form of results from a factor analysis or convergent validity.
+We note that around half of the measures in our sample of studies were single item measures.
+While it is possible to check the reliability and validity of single item measures, these methods often require multiple measures or studies to allow for validation [@leppinkWeNeedMore2017; @sarstedtSelectingSingleItems2016], an effort that is rarely taken.
+For example, only `r sum(coded_data_replications$sel_psychometric_evidence_text_REV[coded_data_replications$N_items == "1 item measure"] != "")` of the `r sum(coded_data_replications$N_items == "1 item measure")` single-item measures in our sample of replication studies and `r apa_num(sum(coded_data_original$sel_psychometric_evidence_text_REV[coded_data_original$N_items == "1 item measure"] != ""), numerals = FALSE, zero_string = "none")` in the original studies reported any validity evidence, in both cases convergent validity.
+Even among multiple item measures, reporting issues persisted.
+Here we observed that reliability and validity were more poorly reported in replications than in original studies.
+This could be because replications implicitly defer the responsibility of demonstrating the validity of the measure to the original study.
+However, as we noted before, and as our reliability and unidimensionality analyses show, a measure’s reliability and factorial structure can vary across contexts.
+Because measurement problems could affect replication outcomes, it is important to report this information for replication studies as well.
+However, since the replication protocols were written before data collection, it is understandable that this information was not included there.
+Still, we were unable to find these details in the available supplementary materials or in the Many Labs reports.
+
+It is concerning that most studies neither discussed nor studied the reliability of their measures by means of measures of internal consistency and the validity by means of checks of convergent, discriminant, or predictive validity or the factorial nature of their measures.
+Especially given that our item response analysis showed that the reliability and unidimensionality often varied considerably across samples.
+While some measures did show consistently high reliability and stable unidimensionality, for a similar number of measures, both were low.
+Most measures however fell somewhere in between, such that the same measure’s reliability and unidimensionality met standards in some of the labs, while they were clearly below par in others.
 We also noted that some measures had convergence issues.
-Overall the inconsistent fit --- and in extreme cases lack of convergence ---  of the unidimensional factor model either indicates that these measures were not unidimensional, and thus not construct valid in this use case, or because our simplistic factor model itself was not an appropriate choice for the given data.
-Besides this split in potential explanations for our results, low sample size and a small number of items --- common with the replication measures --- likely also played a role in the lack of convergence.
-Combining all these points together, we stress that our results are not meant to be regarded as validity assessments of individual measures.
-This lies beyond the scope of our article and does not align with our analytical approach.
-Instead, our claim based on our results is that while for the measures we checked unidimensionality forms a prerequisite for them being construct valid, we observe that this prerequisite is not universally met across labs, for which we question the assurance of valid measurement within our sample.
-
-Besides difference across contexts, reliability and validity of the measures in our sample were also impacted because many of them were modified from the original study.
-In our sample we noted that about two-thirds of the measures in replications were modified in some way from the original study.
-With modifications being this common it is best to be explicit in reporting these modifications and also to document the reliability and validity in replications.
-Minor differences between replication and original study are inevitable, but substantial changes between original and replication study raises the question whether it is still justified to label them as "direct" replication.
-For example, the conscientiousness measure used for the replication of De Fruyt et al @defruytCloningersPsychobiologicalModel2000 was reduced from the original NEO-PI-R 48-item measure to a two-item measure in the replication.
-It is highly unlikely that a measure with such a significant change would have a comparable validity and reliability to the original, and we did unsurprisingly observe convergence issues with validity for this measure as well as low reliability.
-
-We observed some patterns that may indicate bias in measurement reporting.
-If a Cronbach’s Alpha in our sample was reported for a measure in an original study, then their average Cronbach’s Alpha observed among the replications were consistently relatively high.
-Meanwhile, if no Cronbach’s Alpha was reported in the original study, the reliability was often relatively low.
-If we take our replication results to be representative, it may indicate that authors are more inclined to report reliability coefficients when measures are above an acceptable threshold, but less so when they are below.
-This aligns with existing research indicating bias in reported Cronbach’s Alpha values, with an excess of reported values at the common acceptably reliable threshold value of .70, and low reporting just below .70 [@husseyAberrantAbundanceCronbachs2023].
-In combination with our inconsistent reliability and validity evidence, this reporting bias creates a false sense of security when readers judge the reliability and construct validity of a measure  based on the reported information in the literature.
-
-Our intent is not to specifically criticize the Many Labs replications nor these specific original studies, but rather use them as illustrative examples.
+Overall the inconsistent fit — and in extreme cases lack of convergence — of the unidimensional factor model suggests either that the measures were not truly unidimensional (and thus not construct valid as a measure of one targeted latent variable in this  context) or that our oversimplified factor model was inappropriate for the data.
+In addition to these potential explanations, low sample size and few items --- common in the replication measures --- likely contributed to the lack of convergence.
+Taken together, our results should not be interpreted as validity assessments of individual measures, which is beyond the scope of this article and inconsistent with our analytical approach.
+Rather, our findings indicate that unidimensionality --- as a prerequisite for construct validity --- is not universally met across labs, casting doubt on the construct validity of the measures included in our sample.
+
+We observed patterns that may indicate bias in measurement reporting.
+If an original study reported a Cronbach’s Alpha, the corresponding replications typically showed relatively high reliability.
+Meanwhile, if no Cronbach’s Alpha was reported in the original study, the reliability in the replications was often relatively low.
+This suggests that authors may preferentially report reliability when it meets an acceptable threshold, consistent with prior research showing an excess of reported alphas around the commonly acceptable threshold of .70 [@husseyAberrantAbundanceCronbachs2023].
+Combined with our evidence of inconsistent reliability and validity, such reporting bias can give readers a false sense of confidence in the measures.
+
+Our intent is not to specifically criticize the Many Labs replications nor these original studies, but rather use them as illustrative examples.
 Regardless, we would argue that full transparent measurement reporting is a responsibility of both replications and original studies.
-Otherwise, based on our results and the results of existing research, there is reason to distrust the reliability and validity of many psychological measures, especially when used in a new context.
-The validation required to ensure that we can trust that a measure is valid across contexts is simply not reported for most measures, and based on our own analyses of the item response data, there is reason to doubt that a measure is likely to be valid in any context.
+Otherwise, based on our results and the results of earlier research [@maireadshawMeasurementPracticesLargescale2020; @husseyAberrantAbundanceCronbachs2023; @maassenDireDisregardMeasurement2025], there is reason to doubt the reliability and validity of many psychological measures, especially when used in a new context and not accompanied by transparent reporting or results of standard psychometric tests for reliability and factorial composition that researchers could apply readily.
+Important information on the reliability and validity of measures across contexts is often not reported despite the real possibility that the measures fail to meet basic psychometric standards that are relevant in understanding the robustness of psychological phenomena in different contexts [@maassenDireDisregardMeasurement2025].
 Even though validating measures is challenging and resource intensive, its necessity cannot be ignored.
-It is questionable to draw substantive interpretations from results based on responses to an unvalidated measure.
+Use of unvalidated measures might invalidate substantive interpretations drawn from both original and replication studies.
 
@@
 
-Our main indicator of construct validity obtained from the response data was our unidimensionality test from a factor analysis.
-However, our factor analyses were not informed by theory, and were not specific to each measure.
-Instead the structure of the model and the test was the same for all measures.
-Even though we believe this is a reasonable proxy for construct validity --- as all measures we checked were used to form a singular index of one latent variable --- it is quite possible that a measure fails at our checks and is still a valid and reliable measure in its specific use case.
-These checks are designed as preliminary checks of construct validity that provide a general overview, not a complete thorough investigation of construct validity.
-Future research may want to deep dive into construct validity for one or a few measures and conduct thorough theory informed construct validity tests using openly available measurement response data to provide a complementary qualitative assessment of measurement validity in psychological research.
-
-One of the most impactful limitations to our analyses was that we were unable to conduct informative inferential tests on our data.
-This was in large part because there were simply too few measures with the relevant information for our purposes.
-We initially planned to test the difference in reported reliability between original and replication studies, and the relation between reliability and replication outcome.
-However, due to the small number of reported reliabilities and measures for which reliability could be calculated we were unable to perform these tests.
-However, this limitation also highlights one of our most important findings.
-While we were unable to perform our preregistered tests, the fact that we could not is telling of the lack of measurement information reporting in our sample.
-
-As another limitation, it is important to reflect on whether or not replication protocols and research articles can be fairly compared in terms of measurement reporting practices.
-A study’s description within a replication protocol is generally shorter than an article.
-The protocol may therefore lack the space needed to report on the measurement in full detail.
-There are three reasons why we believe protocols and articles remain mostly comparable.
-Firstly, articles are often also restricted in the amount of space they have available to devote to measurement [@gardinerEditorialMethodsPapers2019; @zogmaisterAssessingTransparencyMethods2024].
-Second, in the revised protocol some measurement reporting items, such as whether example items were reported or not, also allowed for reporting this information in supplementary materials to count as good practice.
-Third, while we also allowed supplementary materials, few other files besides the protocol described the measurement details for the replication in any details, as such the protocol represent most of the available information on the measurement just like the original article does.
-If the information could not be found in the protocol, it was unlikely to be found anywhere else.
-A difference that was not resolved between articles and protocols was that the protocols were written before the measurement was conducted.
-Therefore we cannot directly compare protocol and replication on measurement information that is derived from the data – such as reliability coefficients and psychometric validity information.
-Still, future research should look if possible at replications that report on measurement information derived from the item response data.
+The original studies and replications of the Many Labs projects may not be representative of typical original or replication research in psychology.
+Although we maintain the Many Labs projects are a relevant and high-quality source of studies, it may represent a standard that is not common throughout the field.
+Future research may wish to look at more representative replications and replications of more recent research, as well as a broader scope of original studies.
+
+Another limitation inherent in our data is that replication protocols are typically shorter than research articles, which may prevent full reporting of measurement details and complicate direct comparisons of reporting practices.
+We believe, however, that protocols and articles remain largely comparable for three reasons.
+First, research articles are also often restricted in the space available for reporting measurement details [@gardinerEditorialMethodsPapers2019; @zogmaisterAssessingTransparencyMethods2024].
+Second, the revised protocol allowed certain items --- such as reporting example items --- to be fulfilled via supplementary materials, similar to good practice in articles.
+Third, beyond the protocols, few other files contained measurement details, meaning the protocol represented most of the available information, just as an article does for the original study.
+In other words, if a detail was missing from the protocol, it was unlikely to be found elsewhere.
+A difference between research articles and protocols that was not resolved was that the protocols were written before data collection.
+This means the protocols cannot report measurement information derived from the data, such as reliability coefficients and psychometric validity information.
+Future research could examine replications that do provide such data to allow more direct comparisons.
 
 There were additional sources of information we could have included.
-Data from original studies could have been used to recalculate reliability and validity indicators from to compare with the replication results.
-However, it is unlikely that a substantial number would have shared their data (many were conducted before the OSF and other Open Science initiatives were launched).
+We could have used data from original studies to recalculate reliability and validity indicators to compare with the replication results.
+However, it is unlikely that a substantial number of studies would have shared their data (many were conducted before the OSF and other Open Science initiatives were launched).
 This is likely different for more recent research [@hardwickeEstimatingPrevalenceTransparency2022; @hamiltonPrevalencePredictorsData2023a].
-The original studies and replications of the Many Labs projects may also not be representative of typical original or replication research in psychology.
-Although we maintain the Many Labs projects are a relevant and high-quality source of studies, it may represent a standard that is not common throughout the field.
-Future research may wish to look at more representative replications and replications of more recent research.
+
+We originally planned to formally test the difference in reported reliability between original and replication studies, and the relation between reliability and replication outcomes.
+However, due to the small number of reported reliabilities and measures for which reliability could be calculated, we were unable to perform these tests with sufficient power.
+Importantly, this limitation itself highlights a key finding: the inability to perform our preregistered analyses underscores the widespread lack of measurement information reporting in our sample.
 
@@
 
-There are two main issues that we believe should be addressed to improve measurement practices: the common use of measures without established validity, and the lack of transparent measurement reporting.
+We see two key issues to address for better measurement practices: the common use of measures without established validity and the lack of transparent measurement reporting.
 Unfortunately, fixing these issues requires considerable time and resources.
-Establishing validity would for a start require that the reliability and construct validity of each measure is analysed  within each context it is used in, a practice that currently occurs only rarely beyond a handful of common (clinical and personality) questionnaires [@anvariFragmentedFieldConstruct2025].
+Fully validating a measure requires a lengthy and resource intensive research program spanning across years, a practice that understandably occurs only rarely beyond a handful of common (clinical and personality) questionnaires [@anvariFragmentedFieldConstruct2025].
 Meanwhile, improving transparency in reporting is an issue that many have tried to address for other aspects of academic articles such as preregistration deviations [@willrothBestLaidPlans2024], and constraints on generality [@simonsConstraintsGeneralityCOG2017], but widespread success has remained elusive.
@@
 
-Thus, our first recommendation is that reporting standards for measurement deserve a more central place in psychological science.
-We found that reporting reliability and validity information was the exception rather than the rule, and even basic information such as how many items were in the measure was reported with little consistency in our sample.
+Thus, our first recommendation is that measurement reporting standards should be given greater prominence in psychological science.
+We found that reporting information on reliability and validity was the exception rather than the rule, and even basic information such as how many items were in the measure was reported with little consistency in our sample.
 The American Educational Research Association @americaneducationalresearchassociationStandardsEducationalPsychological2014 guidelines exist to guide researchers in the creation and validation of scales, but not how to report the measurement details when in use.
@@
 One aspect where reporting standards has seen some changes is in statistical reporting [@hardwickeStatisticalGuidanceAuthors2023].
-Statistical reporting standards and guidelines have received, including recommendations from the American Statistical Association [@wassersteinASAStatementPValues2016].
+Statistical reporting standards and guidelines have received a substantial push, including recommendations from the American Statistical Association [@wassersteinASAStatementPValues2016].
 The uptake of statistical reporting guidelines is even seen among journals.
-Although, in practice the guidelines vary in their content and enforcement [@hardwickeStatisticalGuidanceAuthors2023].
-Still, we believe that for measurement any increase in reporting standards will be a welcome change compared to no push, and that a similar high-profile push is at least as relevant for measurement reporting standards as it is for improving scientific robustness as it is for statistical result reporting.
-After all, the data obtained through measurement is the foundation for nearly all empirical quantitative psychological research results.
-
-As a related recommendation that could become a standard, we suggest that researchers should report and evaluate their measures using more informative indicators.
-Cronbach’s Alpha on its own gives only limited information the quality of a scale, and comes with strong assumptions [@cortinaWhatCoefficientAlpha1993; @sijtsmaUseMisuseVery2009].
-Factor analytical evidence and McDonald’s Omega are more informative indicators that should be presented in favor of or in tandem with Cronbach’s Alpha.
-
-Our second recommendation is that, as a scientific community, we need to systematically validate a greater proportion of our measures.
-But to able to do so, the measures should first of all be reusable --- here, transparent measurement reporting is crucial.
-Then, researchers should actually reuse existing validated measures, rather than make new ones on the fly and use these unvalidated measures.
-To encourage and enable the reuse of existing measures, Elson et al @elsonPsychologicalMeasuresArent2023 have proposed an open repository of measurement protocols to facilitate the discovery of measures and building an evidence base.
-Furthermore, they suggested that journals should implement the Standardisation Of BEhavior Research (SOBER) guidelines to specifically address issues of flexibility and norming in measurement so that measures remain comparable across studies.
-If researchers then reuse a measure across different context its reliability and validity needs to be compared across multiple occasions to assess in which contexts, if any, the measure is valid.
-
-If more systematic measurement validation is to take place, it is equally important that the resulting evidence becomes an integral and respected part of the scientific literature.
-We therefore suggest that the scientific literature should include a dedicated space for systematic and continuous measurement validation studies, similar to the space proposed for replication studies to assess the robustness of effects.
-Moreover, replication studies themselves could contribute to measurement validation: by paying closer attention to measurement evaluation and reporting, replication efforts could simultaneously serve as a robustness of an effect and a validation test of the measure.
-Finally, to enable cumulative progress, a greater proportion of item response data should be made available to the scientific community.
-Ideally, this includes item-level responses and relevant participant characteristics, allowing future researchers to (re-)evaluate a measure’s validity and reliability in relation to theory.
-When full data sharing is not possible, providing summary statistics (such as variance–covariance matrices, means, and standard deviations) can still allow others to conduct factor-analytic assessments of measurement quality and even meta-analytic evaluation across contexts.
-
-Finally, we recommend to researchers seeking to replicate a study that they should first evaluate the measurement of the original study before replicating.
+Although, in practice guidelines on statistical reporting vary in their content and enforcement [@hardwickeStatisticalGuidanceAuthors2023].
+Still, any improvement in measurement reporting standards is valuable.
+Therefore, a similar high-profile push for transparent measurement reporting would be of great importance and at least as warranted as efforts to improve scientific robustness or statistical reporting, since measurement data form the foundation of nearly all empirical quantitative research in psychology.
+
+Moreover, researchers should report and evaluate measures using more informative indicators.
+Cronbach’s Alpha alone provides limited information the scale quality and relies on strong assumptions [@cortinaWhatCoefficientAlpha1993; @sijtsmaUseMisuseVery2009].
+Factor-analytic evidence, such as an assessment of unidimensionality, and McDonald’s Omega offer more informative alternatives and should be reported alongside or instead of Cronbach’s Alpha.
+
+Our second recommendation is that the scientific community should focus on creating, reporting, and reusing measures in a way that allows systematic validation.
+To do so, measures first need to be reusable, which requires transparent measurement reporting.
+Researchers should then reuse existing validated measures rather than creating new, unvalidated ones.
+To support this, Elson et al.
+@elsonPsychologicalMeasuresArent2023 proposed an open repository of measurement protocols to facilitate the discovery of measures and building an evidence base.
+They also recommended that journals should implement the Standardisation Of BEhavior Research (SOBER) guidelines to address flexibility and norming in measurement, ensuring comparability across studies.
+Finally, when a measure is reused across different context, its reliability and validity should be assessed across multiple occasions to determine in which contexts, if any, it is valid.
+
+Finally, we recommend that researchers seeking to replicate a study first evaluate the measurement of the original study before proceeding.
 Reliable and valid measurement is essential for an informative replication.
@@
 When replicating another study is not an option, we advise the replicating researcher to first attempt a conceptual replication using a validated measurement.
-Afterwards, a direct replication can be performed based on the conceptual replication to further assess the robustness of the effect.
+Afterwards, a direct replication can be performed based on the conceptual replication to further assess the robustness of effects or associations.
 
@@
 For this we need valid and reliable measurement.
-Yet, in our sample of Many Labs replications and original studies we observed that the construct validity and reliability of psychological measurements is rarely reported and based on our analyses were seldom sufficient enough across contexts to assume that constructs are generally measures as intended.
-Furthermore, the lack of transparency in measurement reporting hampers the reuse of existing measures.
-A change in the use and reporting of measurement is necessary.
-Otherwise, psychological effects lack the measurement fundamental to establish that they are related to true psychological phenomena.
-Fortunately, even small steps towards improved reporting practices, data and materials sharing, and normalizing measurement validation can spark the proliferation of validated measurement.
+Yet, in our sample of Many Labs replications and original studies, reliability and construct validity evidence were rarely reported and, based on our analyses, seldom sufficient across contexts to assume that constructs were measured as intended.
+Furthermore, poor transparency in measurement reporting hinders the reuse of existing measures.
+Changes in both the use and reporting of measurement are necessary; without them, psychological effects lack the measurement foundation needed to justify their connection to true phenomena.
+Fortunately, even small improvements in reporting, data and materials sharing, and normalizing measurement validation can spark the proliferation of validated measurement.
 
